### 2018-12-13 ongoing/deprecated/article/article.tex
Sketch proof of bound

\documentclass[12pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}

\author{Tzu-Yu Jeng}
\date{\today}
\title{Proposal (Sketch)}
\begin{document}
\maketitle

\section{Introduction}

Multiple-input multiple-output (MIMO) systems with a large number of antennae of both sides (hereafter massive MIMO) is expected to improve spectral efficiency, but presents new obstacles as well.
The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
It is important to devise feasible simulation method, as the systems themselves are growing more complicated, and the cost of simulations is large.

Though the problem of finding precoder is old, often times we encounter new settings that suggests us to use a technique that is more agnostic to the actual traits of the channel.
For example, when 3D channel is considered with 2D active antenna arrays used, new precoding technique is required.
3D channel considers not only the horizontal position, but also the height, and using expressions that involves longitudinal as well as azimuthal angles.

We apply a precoding matrix \(W\) chosen among the Fourier-kernel-like matrix, which has entry that solely consists of roots of unity, and study the sum rate with respect to \(HW\).
Despite the extensive discussion of precoding matrices out of the academic interest, in reality usually the Fourier-kernel-like rows and columns are used.
In short, every row of the precoding matrix is a vector consisting of the roots of unity with equally spaced arguments.
This is true according to (for example) 3GPP Release 14, justifying our decision.

We choose the sum rate to be the target function.
The reader may think that the channel capacity, which let us call \(C\), is the quantity to be maximized, but in fact the explicit expression of \(C\) in 
nor is it clear what it means by ``capacity''.
In fact, we usually say ``capacity regions'', and no single number can represent for that.
As a result, researchers often use sum rate \(\log\det(I+H)\) for normalized AWGN case.

Previous literature, I believe, usually simplifies the scenario in two aspects, that is, the consideration of a large number \(K\) of subcarriers, and the two-staged precoding.

Love et.\ al.\ (2003) transform the precoding problem as a line packing problem on Grassmannian manifold with respect to a self-defined distance function, 
Sohrabi and Yu (2016a) consider a single given instance of the channel matrix.
And another paper by Sohrabi and Yu (2016b), as a follow up of their previous work, deals moreover with the case of several subcarriers, but pulls them out and did not exploit more possibility of much more optimization.
[....??]

Two-staged precoding is hardly seen fomulated in literature, which is something I don't understand.
Two-staged precoding is actually considered in 3GPP release 13, and is beneficial 
If we set (for example in Li et.\ al.\ 2016)
\begin{gather*}
W =W_2 W_1
\end{gather*}
Such distinction do not add complexity without reason, but \(W_2\) can take account of slow-varying channel traits, and \(W_1\) of fast-varying ones.

These are both extremely realistic concerns, and it seems not to be fully investigated.

Since it not easy to derive analytical result, I gather maybe metaheuristic algorithms may be used.

\section{Problem formulation}

For convenience, denote by \(\mathbb{M}(N_1',N_2')\) family of matrices having dimension \(N_1'\) by \(N_2'\).
Let \(0 \leq N_D \leq N_H\), where \(N_D,N_H \in \mathbb{N}\).

Define matrices
\begin{gather*}
W_1(m), W_2(m,n) \in \mathbb{M}(N_D,N_H)
\end{gather*}
here, for predefined set of matrices \(\mathcal{W}_1\) and \(\mathcal{W}_2\),
\begin{gather*}
W_1(m) \in \mathcal{W}_1,\quad
W_2(m,n) \in \mathcal{W}_2.
\end{gather*}

Moreover, let random instances of channel matrices for different subcarriers be given,
\begin{gather*}
H(m,n,l) \in M(N_H,N_H),\; m=1,\dotsc,M,\; n=1,\dotsc,N,\; l=1,\dotsc,L
\end{gather*}
\(H(m,n,l)\)'s may in general be correlated.

Then define the problem
\begin{align*}
& \hat{W}_1(m),\; \hat{W}_2(m,n),\; m=1,\dotsc,M,\; n=1,\dotsc,N \\
\leftarrow &\underset{\in \mathcal{W}_1(m) \in \mathcal{W}_1,\; W_2(m,n) \in \mathcal{W}_2}{\mathrm{argmax}}
\sum_{m=1}^M \sum_{n=1}^N \sum_{l=1}^L \log \det (I +G(m,n,l) G(m,n,l)^\dagger),\\
& G(m,n,l) =H(m,n,l) W_2(m,n) W_1(m).
\end{align*}

Question: Are there algorithms that, when averaged through instances of \(H(m,n,l)\), find the optimal \(\hat{W}_1(m), \hat{W}_2(m,n)\) with low complexity?

As realisitic setting is, say, that there are 1200 subcarriers for every symbol.
Among them, there are 100 subcarriers for every resource block (giving 12 resource blocks indexed by \(m\)), and 4 subcarriers for every subbands (giving 25 subbands indexed by \(n\) every resource block).

\section{Plan}

I want to simulate the two-stage precoding problem for randomly given channel instances, using metaheuristic methods like simulated annealing.
Although the choice of precoding matrix is confined within a finitely-many set, the search is highly non-trivial, considering the complexity would be large 
It may then be necessary to design, in addition, a data structure to facilitate such search.

I will look up analysis of such algorithm, and compare theoretical prediction to performance.
However, it is hard to imagine there will be closed form solution, and thus, it is not clear what quantitative justification that matches simulation can be given.

It is also natural to extend such technique if successful for dual-stage precoding to hybrid precoding, and that may be easier to be published.

\section{References}

\begin{enumerate}

\item F Sohrabi and W Yu, ``Hybrid Digital and Analog Beamforming Design for Large-Scale Antenna Arrays'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol. 10, No. 3, April 2016.

\item F Sohrabi and W Yu, ``Hybrid Analog and Digital Beamforming for OFDM-Based Large-Scale MIMO Systems''. 2016 IEEE 17th International Workshop on Signal Processing Advances in Wireless Communications (SPAWC).

\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath, ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol. 21, No.5, June 2003.

\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed, ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems''. \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol. 10, No. 3, April 2016.

\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.

\item 3GPP Specifications, TS 36.213 V14.7.0. Retrived from: \\ ``http://www.3gpp.org/specifications''.

\end{enumerate}

\end{document}

### 2018-12-13 ongoing/deprecated/slides/slides.tex
Sketch proof of bound

\documentclass{beamer}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}

\author{Presenter: Tzu-Yu Jeng \\ Advisor: Prof. Hsuan-Jung Su}
\date{\today}
\title{Precoding Design by Simulated Annealing}
\begin{document}
\maketitle

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Outline}
	\begin{itemize}
\item Motivation
\item Problem Setting
\item Algorithm Description
\item Convergence Results
\item Simulation
\item Future Work
\item References
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Motivation}
	\begin{itemize}
	\item Massive MIMO is expected to improve spectral efficiency, but hardware overhead due to large number of antennas increases complexity and power consumption
	\item We may want devise feasible simulation method to deal with increasingly complicated systems
	\item Metaheuristic algorithms, like simulated annealing
(SA), might provide a sufficiently good solution to the optimization problem with incomplete knowledge or limited computation power
	\item We present a problem setting with shared precoders of a large number of users and subcarriers with SA
	\item Certain convergence results of SA has been claimed, but much remains to be investigated
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Problem Setting (1/3)}
	\begin{itemize}
	\item \(R(u,k) =\log(1 +I(u,k))\)
	\item \(I(u,k) =\dfrac{\phi(u,k)}{1 +\Phi(k) -\phi(u,k)}\)

	\item \(\Phi(k) =\sum_{u=1}^U \phi(u,k)\)
	\item \(\phi(u,k) =\|H_{\mathrm{eff}}(u,k)\|_F^2\)
	\item \(F =F(u,k) =F(u_f(u), k_f(k))\)
	\item \(H_{\mathrm{eff}}(u,k) =H(k) F(k_f(k),u_f(u))\)
	\item where \(u =1,\dotsc,U\), \(k =1,\dotsc,K\), \(u_f =1,\dotsc,U_f\), \(k_f =1,\dotsc,K_f\), with
	\begin{gather*}
    k_f(k) =\lceil k/b_k \rceil \\
    u_f(u) =\lceil u/b_u \rceil
	\end{gather*}
	\end{itemize}

\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Problem Setting (2/3)}
	\begin{itemize}
\item The channel model \(H(k)\)
	\begin{gather*}
H(k) =\sum_{n_c=1}^{N_c} \sum_{n_s=1}^{N_s} \alpha(n_c,n_s) a(\theta_r(n_c,n_s)) a(\theta_t(n_c,n_s))^\dagger \\
a(\theta') =\langle 1, e^{i \theta'}, \dotsc e^{i (N-1) \theta'} \rangle
	\end{gather*}
	are random instances of \(\theta_r, \theta_t\).
	\item \(k =1,\dotsc,K\) for subcarriers, \(n_c =1,\dotsc,N_c\) for clusters, \(n_s =1,\dotsc,N_s\) for scatterers.
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Problem Setting (3/3)}
	\begin{itemize}
	\item The main problem reads now
	\begin{gather*}
\min_{F(k_f,u_f)} L \\
L =\sum_{k=1}^K \sum_{u=1}^U R(u,k) \\
\|F(u_f,k_f)\|_F \leq P
	\end{gather*}
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Target Distribution}
	\begin{itemize}
	\item Let \(S \in \mathbb{R}^d\) be a compact set with its boundary having Lebesgue measure 0.
	Let \(\mathcal{B}\) be the Borel \(\sigma\)-field on \(S\).
	And let strictly positive, continuous \(g\) be given as probability density.
	\item \textbf{Definition}. A target distribution \(\pi\) satisfies
	\begin{gather*}
	\pi(A)
	=\int_A g(x) dx,
	\quad \forall A \in \mathcal{B}
	\end{gather*}
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Acceptance Probability Function}
	\begin{itemize}
	\item \textbf{Definition}. Let \(\beta\) be a function on \(S^2\) so that
	\item \(0 <\delta \leq \beta(x,y) \leq 1\) for some \(\delta >0\)
	\item \(\beta(x,y)\) is jointly measurable on \(S^2\)
	\item \(\beta(x,y) g(x) =\beta(y,x) g(y)\), \(\forall x,y \in S\).
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{A General Random Walk Algorithm}
	\begin{enumerate}
    \item Choose a starting point \(x_0\)	in the interior of \(S\)
    \item \(t \leftarrow 0\)
    \item Choose randomly a unit vector \(\theta_t\) on the unit sphere
    \item Choose randomly a length \(\lambda_t >0\)
    \item \(x' \leftarrow x +\theta_t \lambda_t\)
    \item If \(x' \in S\), assign \(x \leftarrow x'\) with probability \(\beta(x,x')\)
    \item \(t \leftarrow t+1\)
	\end{enumerate}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Markov Kernel}
	\begin{itemize}
	\item \textbf{Definition}. A Markov kernel on \((S,\mathcal{B})\) is a nonnegative function \(P\) defined on \((S \times \mathcal{B})\) such that
	\item (i) \(\forall x \in S\), \(P(x, \cdot)\) is a probability measure on \(\mathcal{B}\)
	\item (ii) \(\forall A \in \mathcal{B}\), \(P(\cdot, A)\) is a measurable function of \(S\) 
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Reversibility}
	\begin{itemize}
	\item \textbf{Definition}. A Markov kernel \(P\) is reversible if
	\begin{gather*}
	\int_A P(x,B) \pi(dx)
	=\int_B P(x,A) \pi(dx)
	\quad A,B \in \mathcal{B}
	\end{gather*}
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{A Reversible Markov Kernel}
	\begin{itemize}
	\item \textbf{Lemma 1}. The following Markov kernel \(P\) is reversible:
	\begin{gather*}
    P(x,A)
    =\int_A p(x,y) \pi(dy)
    +\mathbf{1}_A(x) \left( 1 -\int_S p(x,y) \pi(dy) \right)
	\end{gather*}
	where \(\mathbf{1}\) is the indicator function, for any \(p\) satisfying \(p(x,y) =p(y,x)\).

	\item \textbf{Lemma 2}. Suppose that a Markov kernel \(P\) is reversible w.r.t.\ a probability measure \(\pi\), then \(\pi\) is a stationary distribution for \(P\).
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Markov Kernel of Random Walk}
	\begin{itemize}
	\item \textbf{Proposition 3}. For the random walk algorithm just introduced, the Markov kernel is given by the expression in Lemma 1, where
	\begin{gather*}
	p(x,y)
	=\beta(x,y) \frac {h\left( \frac{y-x}{|x-y|} \right) +h\left( \frac{x-y}{|x-y|} \right) } {(\partial D) \cdot \mathrm{diam}(S) g(y)}
	\end{gather*}
	for some \(h\), \(\partial D\) the surface area of unit ball, \(\mathrm{diam}(S)\) the diameter of \(S\), \(g(y)\) the probability density of \(\pi\).
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Random Walk Converges}
	\begin{itemize}
	\item \textbf{Proposition 4}. The Markov kernel \(P\) described in Proposition 3 is reversible, and corresponding \(\pi\) is stationary.

	\item \textbf{Proposition 5}. Continue the configuration in random walk algorithm.
	Starting from \(\forall X_0 =x_0 \in S\), let the Markov chain \(X_n\), \(n=0,1,2,\dotsc\) be determined.
	Then,
	\begin{gather*}
	\lim_{n \to \infty} \mathcal{P}(X_n \in B)
	=\pi(B),
	\quad \forall B \in \mathcal{B}
	\end{gather*}
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Simulation Setting (1/2)}
	\begin{itemize}
	\item Number of antennae \(N =7\)
	\item Number of subcarriers \(K =4\), where \(b_k =2\) subcarriers share a precoder
	\item Number of users \(U =6\), where \(b_u =2\) users share a precoder
	\item Number of clusters \(N_c =6\), number of scatterers \(N_s =6\)
	\item Maximum power (Frobenious norm of precoders) \(P =10^6\)
	\item Record every 100 time indices, initial temperature \(T=1\), change temperature \(T \leftarrow r_T T\) every 10 time indices
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Simulation Setting (2/2)}
	\begin{itemize}
	\item For probability
	\begin{gather*}	
	e^{-(L'-L)/T}
	\end{gather*}
	a candidate \(F'\) in the neighborhood is accepted so that \(F \leftarrow F'\)
	\item To account for power constraint, we multiply to the sum rate a punishment
	\begin{gather*}
	\frac{1}{\prod_{k_f} \prod_{u_f} \left( 1 +e^{ (P-\|H(u,k) F'(u,k)\|_F)^2} \right) }
	\end{gather*}
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Simulation: \(N=4\)}
	Temperature changing ratio \(r_T =0.99, 0.98, 0.97, 0.96\) (resp., red, green, cyan, blue)
	\begin{center}
	\includegraphics[scale=0.60]{n_4.png}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Simulation: \(N=5\)}
	Temperature changing ratio \(r_T =0.99, 0.98, 0.97, 0.96\)
	\begin{center}
	\includegraphics[scale=0.60]{n_5.png}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Simulation: \(N=7\)}
	Temperature changing ratio \(r_T =0.99, 0.98, 0.97, 0.96\)
	\begin{center}
	\includegraphics[scale=0.60]{n_7.png}
	\end{center}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
	\frametitle{Difficulty and Future Work}
	\begin{itemize}
\item Study effective parameters for SA
\item Implement other beamforming algorithms too
\item Accounting for discrete precoders set
\item Generalization to hybrid beamforming
\item Description of neighborhood of linear operator
\item Operations regarding linear operator
\item Explicit generalization of the SA convergence proof to present problem of beamforming
\item A more rigorous, statistical-mechanics interpretation of SA proof
	\end{itemize}
\end{frame}

% % % % % % % % % % % %

\begin{frame}
\frametitle{References}
\begin{enumerate}
\scriptsize {

\item C J P B\'elisle, ``Convergence Theorems for a Class of Simulated Annealing Algorithms on \(\mathbb{R}^d\)''. \textit{Journal of Applied Probability}, Vol.\ 29, No.\ 4 , pp. 885-895, Dec 1992

\item C J P B\'elisle, H E Romeijn, and R L Smith, ``Hit-and-Run Algorithms for Generating Multivariate Distributions''. \textit{Mathematics of Operations Research}, Vol.\ 18, No.\ 2, pp.\ 255-266, May 1993.

\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U. Press.

\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems''. \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.10, No.3

\item H E Romeijn and R L Smith, ``Simulated Annealing for Constrained Global Optimization''. \textit{Journal of Global Optimization}, Vol.\ 5, pp.\ 101-126, 1994.

\item F Sohrabi and W Yu, ``Hybrid Digital and Analog Beamforming Design for Large-Scale Antenna Arrays'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol. 10, No. 3, April 2016.

\item F Sohrabi and W Yu, ``Hybrid Analog and Digital Beamforming for OFDM-Based Large-Scale MIMO Systems''. 2016 IEEE 17th International Workshop on Signal Processing Advances in Wireless Communications (SPAWC).

}

\end{enumerate}
\end{frame}

\end{document}

### 2018-12-13 ongoing/report/article.tex
Sketch proof of bound

\documentclass[12pt]{article}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}

\author{Tzu-Yu Jeng}
\date{\today}
\title{An Explicit Probability Bound for Estimation of Multipath Millimeter Channel}
\begin{document}
\maketitle

\section{Abstract}

Multiple-input-multiple-output (MIMO) communication is adopted as the next generation of wireless communication scheme.
However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibration.
It is then a non-trivial problem to estimate real-world wireless channels

Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing.
A promiment estimator is The Dantzig Selector proposed by Tao and Cand\'es.
In this article, we extend their proof to derive a specific bound in the setting of estimation of millimeter wave channel, utilizing an all-phase-shifter combiner in the receiver end.
Simulation compares our result and the

\section{Introduction}

\subsection{Background}

Millimeter waves communication has been proposed to be the next-generation specification.
The smaller wavelength entails higher frequency bands, and thus wider available bandwith to be available.
In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
Multiple-input multiple-output (MIMO) systems with a large number of antennae of both sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.

But MIMO presents new obstacles as well.
The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
It is important to devise feasible simulation method, as the systems themselves are growing more complicated, and the cost of simulations is large.

The figure of merit of a MIMO system is usually considered to be the channel capacity.
The capacity \(C\) of a MIMO channel \(H\) at perfect CSI (here, the matrix form of \(H\)) is well-known, which is first proved by Teletar.
But that knowledge is hardly always available.
What makes things more difficult is the case that \(H\) is determined from not only \(n(\omega)\), but also parameter \(\theta\).
It is pointed out that the explicit form of \(C(\theta)\) is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Consequently, the perfect-CSI expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.

In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
With more antennae present, conventional algorithms also increase in complexity and storage.
A design of new algorithms that addressed these issues is thus in need.

\subsection{The Dantzig Selector}

It is a recent developemnt that the estimation of channels is facilitated by advances of compressed sensing.
A series of paper by Cand\`es and Tao (2006) marks its advent.
The idea is that, in many important statsitical applications, the number of variables or parameters \(p\) is much larger than the number of observations \(n\).
In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?
Of course, more assumption must be made to make the question meaningful.
Cand\`es and Tao's pioneering work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.

Particularly relevant and inspiring to the present article is Cand\`es and Tao (2006), where they proposed a convex program called The Dantzig Selector (hencefore DS).
Cand\`es and Tao argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).

Several notions related to compressed sensing are necessary in the presentation of results:

\textbf{Definition}. We call \(h \in \mathbb{R}^p\) to be \(S\)-sparse, for \(S =1,2,3,\dotsc\), if only \(S\) components of \(h\) is nonzero.

Denote as \(X_T\) the columns of \(X\) having indices in \(T\), where \(T \subset \{1,\dotsc,p\}\).

\textbf{Definition}.
Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
\begin{gather*}
(1-\delta_S) \|\theta\|^2
\leq \|X_T \theta\|_2^2
\leq (1+\delta_S) \|\theta\|^2
\end{gather*}
RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).

Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
\begin{gather*}
| \langle X_T c, X_{T'} c' \rangle |
\leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
\end{gather*}

It is shown that (Cand\'es and Tao 2005), in the noiseless case, the convex program
\begin{gather*}
\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\
\mathrm{subject}\; \mathrm{to} \quad X \hat{h} =y
\end{gather*}
recovers \(\hat{h}\) completely if \(\delta_{S} +\delta_{2S} +\delta_{3S} <1\).

For concreteness, consider a channel with noise,
\begin{gather*}
y =\sqrt{\mathcal{E}} X h +z
\end{gather*}
where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
(They also discussed specially the noiseless case, but we will not pursue the bounds here.)

How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
Let the following linear program, DS, be defined
\begin{gather*}
\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\
\mathrm{subject}\; \mathrm{to} \quad \|X^\dagger r\|_\infty \leq \lambda_p \sigma
\end{gather*}
where \(r =y -X \hat{h}\).

DS may be written as
\begin{gather*}
\min_{x \in \mathbb{R}^p}  \|x\|_1 \\
\mathrm{subject}\; \mathrm{to} \quad \|Ax+b\|_\infty \leq c
\end{gather*}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

The proof of DS is non-constructive, and it is not clear at first what matrices serves as the RIP condition.
But later, () have found there is a particularly convenient sufficient condition to verify RIP.
Tao explicitly remarked that the bound can be refined, but they did not undergo such task.

\subsection{Compressed Channel Sensing}

Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
For example, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
They explore the estimation of single-antenna channel response with respect to time.
Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability.

To explain the idea, consider a simplified scenario.
Let \(x[t] \in \mathbb{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
Consider a linear time-invariant channel with
\begin{gather*}
y[t] =(x[t] \star h[t]) +z[t]
\end{gather*}
where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
\begin{gather*}
y =X h
\end{gather*}
where \(X\) takes the form
\begin{align*}
X
=\begin{bmatrix}
x_1, &0, &\cdots, &0 \\
x_2, &x_1, &\cdots, &0 \\
\vdots, &\vdots, &\ddots, &0 \\
x_N, &x_{N-1}, &\cdots, &x_1
\end{bmatrix}
\end{align*}
We seek to get \(h\) in this undertermined system.

Then \(X\) is RIP of overwhelmingly probability.

\subsection{Contribution}

This being said, previous work only makes the assumption on the bound of the norm of the channel matrix, and, to the best knowledge of the author, has not characterized the such probability bounds as involving, say, number of channel paths and vector of array response.
This article suggests a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.

\section{Problem Setting}

\subsection{Notation}

We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product.
The complex numbers has natural interpretation as the phasor of electronic waves.
Boldface lower case Latin alphabets denote vectors, and boldface upper case Latin alphabets denote matrices.
Let \(\omega =(\omega_1, \omega_2, \omega_3) \in \Omega =[0,1)^3\) denote the overall index of the probability space.
\(\omega_1\) stands for the probability index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.

Define the uniform linear array, which can be modeled as
\begin{gather*}
\mathbf{a}(\phi')
=\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
\end{gather*}
where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.

And consider channel of the form
\begin{gather*}
H
=\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
\end{gather*}
The physical meaning of  \(\theta_l\) is the \(l\)-th angle of arrival, and \(\theta_l\) the \(l\)-th angle of arrival.
It is noted that in real scenario, the exponent \(i n \phi_l\) should be multiplied by a factor accounting for the spacing of two adjacent antenna.
But, since we consider uniform distribution of \(\theta_l, \phi_l\)'s, it suffices to absorb such factors into the values of \(\theta_l, \phi_l\)'s.

Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.

\textbf{Definition.} Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
\begin{gather*}
\mathbf{u} =F \mathbf{v}
\end{gather*}
where each entry of the matrix \(F\) is defined to be
\begin{gather*}
F_{k,n} =e^{2\pi ikn/N},
\quad k,n =0,1,2,\dotsc, N-1
\end{gather*}

\(H\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
This way, we get
\begin{gather*}
\tilde{H}_n
:=H \mathbf{u}_n
=\sum_{l=0}^L \alpha_l \exp(-i n \theta_l) \mathbf{a}(\phi_l)
\end{gather*}
If we absorb angle of incidence (formed by the ray of electronic wave and the normal line)
\((d/\lambda) \sin \tilde{\theta}_l\)

\section{Results and Proofs}

\textbf{Lemma.} Let \(\phi(\omega_3)\) be a uniformly distributed in \([0,2\pi)\) according to probability space index \(\omega_3 \in \Omega\).
And the function \(\mathbf{a}(\phi)\) is defined as in \eqref{}.
Then the discrete Fourier transform

To find the \(l\)-th path's contribution to the frequency domain, recall the identity
\begin{align*}
S(\phi)
:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\
=&\left| \frac{e^{i N \phi} -1}{e^{i \phi} -1} \right| \\
=&\left| \frac{e^{i N \phi/2} -e^{-i N \phi/2}}{e^{i \phi /2} -e^{-i \phi /2}} \cdot e^{i (N-1) \phi/2} \right| \\
=&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
\quad 0 \leq \phi \leq \pi
\end{align*}
By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
\begin{align*}
S(\phi)
\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\
=& \frac{-48}{\phi^3 -24\phi}
\quad 0 \leq \phi \leq \pi,
\end{align*}

The fraction above can be bounded.

By the same token, more generally,
\begin{align*}
&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\
=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\
=&\frac{1}{N} S(\pi \phi') \\
\leq& \frac{48}{N \pi^3 (\phi'^3 -24 \phi' /\pi^2)}
\end{align*}
where \(\phi' =k/N -\phi/2\pi\), and the cubic expression is split.
We wish to bound the tail of \(S(\pi \phi')\), and apply the na\"ive bound
\begin{align*}
&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\phi'^3 -24 \phi' /\pi^2}
 d\phi' \\
=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\
\leq& \frac{1}{\pi^2} \log \frac{L}{N}
\end{align*}
Here, the integral in the first line is immediate.
The second term in the bracket is smaller than 0 and is dropped in the last inequality.
The bound is satisfying enough, though refinement is surely possible.
Indeed, \(\log L/N \to 0\) as \(N \to \infty\) and limited by the number of paths \(L\).

%A =\mathrm{supp} \beta

where
\begin{gather*}
\mathcal{A}, \mathca{B}, \mathcal{C} \subset \mathbb{N} \\
\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varempty \\
A \cup B \cup C =\{1, \dotsc, N\}.
\end{gather*}

\textbf{Proposition}.
Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in \eqref{}.
Then
\begin{align*}
\|h_A\|_1 -\|\eta_A\|_1 +\|\eta_C\|_1 -\|h_C\|_1
\leq& \|h +\eta\|_1 \\
\leq& \|h\|_1
\end{align*}

\textbf{Proof}.

\begin{align*}
\|X^\dagger_{AB} X \eta\|_\infty
<&\|X^\dagger X \eta\|_\infty \\
\leq& 2 \lambda_p
\end{align*}

\begin{align*}
\|\eta_Ah\|_2
\leq K_1 \|X^\dagger_{AB} X \eta\|_2 +K_2 \|\eta_C\|_2
\end{align*}
Tao, Lemma 1-1

Tao, Lemma 1-2
\begin{align*}
\|\eta\|_2^2
\leq \|\eta_{AB}\|_2^2 +K_3 \|\eta_C\|_2^2
\end{align*}

Another difference is that this article solves the optimization problem solely using the method of greatest descent.
While OMP is widely used 
With the analysis of [], OMP is usually used
But

% % % % % % % % % % % % % % % %

\section{References}

\begin{enumerate}

\item F Sohrabi and W Yu, ``Hybrid Digital and Analog Beamforming Design for Large-Scale Antenna Arrays'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol. 10, No. 3, April 2016.

\item F Sohrabi and W Yu, ``Hybrid Analog and Digital Beamforming for OFDM-Based Large-Scale MIMO Systems''. 2016 IEEE 17th International Workshop on Signal Processing Advances in Wireless Communications (SPAWC).

\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath, ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol. 21, No.5, June 2003.

\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed, ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems''. \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol. 10, No. 3, April 2016.

\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.

\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels''. Proceedings of the IEEE, Vol.98, No.6.

\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing''. 2008 42nd Annual Conference on Information Sciences and Systems.

\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U. Press.

\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.2.

\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming''. Retrieved from ``https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf''.

\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming.'' \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.

\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.12.

\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)''. \textit{The Annals of Statistics}, Vol.35, No.6.

\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems''. \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.10, No.3

\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices''. \textit{Constructive Approximation} \textbf{28}: 253–263

\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation''. \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6

\end{enumerate}

\end{document}

### 2018-12-13 ongoing/code/src/class.h

@@ -1,7 +1,17 @@
-#ifndef CLASS_H
-#define CLASS_H
 
-
-
-#endif
-
+class Parameters
+{
+public:
+   Parameters();
+   Parameters(int, int);
+   ~Parameters();
+   void generate_new_instance();
+   Mat get_channel();
+   
+private:
+   int nn_path;
+   std::vector<double> list_ang_dep;
+   std::vector<double> list_ang_arr;
+   std::vector<Comp> list_amp;
+   
+}

### 2018-12-13 ongoing/code/src/functions.cpp

@@ -1,126 +1,25 @@
 #include <iostream>
-#include <cstdio>      /* printf, scanf, puts, NULL */
-#include <cstdlib>     /* srand, rand */
-#include <ctime>       /* time */
+#include <cstdio>
+#include <cstdlib>
+#include <ctime>
+#include <random>
 
 #include <boost/numeric/ublas/matrix.hpp>
 #include <boost/numeric/ublas/io.hpp>
 #include <boost/numeric/ublas/matrix_proxy.hpp>
 #include <boost/numeric/ublas/lu.hpp>
-
 #include "constants.h"
 
-// stackoverflow.com/questions/29877760/boostublas-how-to-get-determinant-of-int-matrix?rq=1
-Comp determinant(const Mat& mm)
+
+
+void newton_method(std::vector<double> list_ang_dep, std::vector<double> list_ang_arr, std::vector<Comp> list_amp)
 {
-    Mat m =mm;
-    ublas::permutation_matrix<std::size_t> pivots( m.size1() );
-    auto be_singular = ublas::lu_factorize(m, pivots);
-    if (be_singular) {return 0;}
-
-    Comp det = 1;
-    for (std::size_t i = 0; i < pivots.size(); ++i) 
-    {
-        if (pivots(i) != i) {det *= -1;}
-        det *= m(i,i);
-    //std::cout << "det= " << det << std::endl; //XXX
-    }
-
-    return det;
+   
 }
 
-double frob_norm(const Mat& m)
+void walk_one_step(Parameters& param)
 {
-   double ret =0;
-   for(std::size_t i=0; i<=cst::nn-1; i++)
-      for(std::size_t j=0; j<=cst::nn-1; j++)
-      {
-         double hold_abs =std::abs( m(i,j) );
-         ret =ret +hold_abs *hold_abs; // hold
-      }
-   ret =std::sqrt(ret);
-   return ret;
-}
-
-Mat get_array_response(double psi, std::size_t len)
-{
-   Mat ret(len,1);
-   for(std::size_t n=0; n <=len -1; n++)
-   {
-      ret(n,0) =std::exp(cst::ii *static_cast<double>(n) *psi);
-   }
-   return ret;
-}
-
-void set_rand_channel( Mat& h )
-{
-   h =ublas::zero_matrix <Comp> (cst::nn, cst::nn);
[…]

### 2018-12-13 ongoing/deprecated/code/src/constants.cpp

@@ -1,0 +1,32 @@
+#include <map>
+#include <complex>
+#include <boost/numeric/ublas/matrix.hpp>
+#include <boost/numeric/ublas/io.hpp>
+#include "constants.h"
+
+namespace cst
+{
+   extern const double pi =3.14159265358979;
+   extern const std::complex<double> ii =std::sqrt( static_cast<Comp>(-1) );
+   extern const double a_t_phase =0.5; // a phase factor in uniform linear array of Tx
+   extern const double a_r_phase =0.6; // a phase factor in uniform linear array of Rx
+   extern const double spread =0.1; // relative spread of cluster
+   extern const std::size_t nn =7; // # of antennae, assumed same in Tx and Rx
+   extern const std::size_t kk =4; // # of subcarrier
+   extern const std::size_t s_blk_kk  =2; // # of subcarriers that share a precoder
+   extern const std::size_t nn_blk_kk  =kk /s_blk_kk;
+   extern const std::size_t uu =6; // # of user
+   extern const std::size_t s_blk_uu  =2; // # of users that share a precoder
+   extern const std::size_t nn_blk_uu  =kk /s_blk_uu;
+   extern const std::size_t ff =(kk/s_blk_kk) *(uu/s_blk_uu); // # of different precoders
+   extern const std::size_t nn_c =6; // # of cluster
+   extern const std::size_t nn_s =6; // # of scatterer
+   extern const double pp =1e5; // maximum power
+   extern const std::size_t t_record =100; // interval between subsequent record
+   extern const std::size_t t_change_temp =10; // interval between subsequent record
+   extern const double max_iter =800;
+   extern const double step_size =1.3;
+   extern const double delta =0.3; // simulation step
+   extern const double temp_init =1; // initial temperature
+   extern const double arr_cooling_param[] ={0.97, 0.96, 0.95, 0.94};
+}

### 2018-12-13 ongoing/deprecated/code/src/constants.h

@@ -7,9 +7,9 @@
 #include <boost/numeric/ublas/io.hpp>
 
 namespace ublas = boost::numeric::ublas;
-typedef std::complex <double> Comp;
+typedef std::complex<double> Comp;
 typedef ublas::matrix <Comp> Mat;
-//typedef std::map< std::size_t, Mat> Map_mat;
+typedef std::map< std::size_t, Mat> Map_mat;
 
 namespace cst
 {
@@ -19,10 +19,23 @@ namespace cst
    extern const double a_r_phase;
    extern const double spread;
    extern const std::size_t nn;
+   extern const std::size_t kk;
+   extern const std::size_t s_blk_kk;
+   extern const std::size_t nn_blk_kk;
+   extern const std::size_t uu;
+   extern const std::size_t s_blk_uu;
+   extern const std::size_t nn_blk_uu;
+   extern const std::size_t ff;
    extern const std::size_t nn_c;
    extern const std::size_t nn_s;
+   extern const double pp;
+   extern const std::size_t t_record;
+   extern const std::size_t t_change_temp;
    extern const double max_iter;
    extern const double step_size;
+   extern const double delta;
+   extern const double temp_init;
+   extern const double arr_cooling_param[4];
 }
 
 #endif

### 2018-12-13 ongoing/deprecated/code/src/functions.cpp

@@ -1,0 +1,167 @@
+#include <iostream>
+#include <cstdio>      /* printf, scanf, puts, NULL */
+#include <cstdlib>     /* srand, rand */
+#include <ctime>       /* time */
+
+#include <boost/numeric/ublas/matrix.hpp>
+#include <boost/numeric/ublas/io.hpp>
+#include <boost/numeric/ublas/matrix_proxy.hpp>
+#include <boost/numeric/ublas/lu.hpp>
+
+#include "constants.h"
+
+// stackoverflow.com/questions/29877760/boostublas-how-to-get-determinant-of-int-matrix?rq=1
+Comp determinant(const Mat& mm)
+{
+    Mat m =mm;
+    ublas::permutation_matrix<std::size_t> pivots( m.size1() );
+    auto be_singular = ublas::lu_factorize(m, pivots);
+    if (be_singular) {return 0;}
+
+    Comp det = 1;
+    for (std::size_t i = 0; i < pivots.size(); ++i) 
+    {
+        if (pivots(i) != i) {det *= -1;}
+        det *= m(i,i);
+    //std::cout << "det= " << det << std::endl; //XXX
+    }
+
+    return det;
+}
+
+double frob_norm(const Mat& m)
+{
+   double ret =0;
+   for(std::size_t i=0; i<=cst::nn-1; i++)
+      for(std::size_t j=0; j<=cst::nn-1; j++)
+      {
+         double hold_abs =std::abs( m(i,j) );
+         ret =ret +hold_abs *hold_abs; // hold
+      }
+   ret =std::sqrt(ret);
+   return ret;
+}
+
+Mat get_array_response(double psi, std::size_t len)
+{
+   Mat ret(len,1);
+   for(std::size_t n=0; n <=len -1; n++)
+   {
+      ret(n,0) =std::exp(cst::ii *static_cast<double>(n) *psi);
+   }
+   return ret;
+}
+
+void set_rand_channel( Mat& h )
+{
+   h =ublas::zero_matrix <Comp> (cst::nn, cst::nn);
+   for(std::size_t n_c=0; n_c <cst::nn_c-1; n_c++)
+   {
+      double mu =static_cast<double> (rand()) /RAND_MAX;
+      mu =2*mu -1;// [-1,1]
+      for(std::size_t n_s=0; n_s <cst::nn_s-1; n_s++)
+      {
[…]

### 2018-12-13 ongoing/deprecated/code/src/functions.h

@@ -1,0 +1,17 @@
+#ifndef FUNCION_H
+#define FUNCION_H
+
+#include "constants.h"
+//extern typedef Vec;
+
+Comp determinant(const Mat&);
+double frob_norm(const Mat&);
+Mat get_array_response(double, std::size_t);
+void set_rand_channel( Mat& );
+void accept_random_step(Map_mat*, Map_mat*);
+void set_random_step(Map_mat*);
+double find_new_sum_rate(Map_mat*, Map_mat*, Map_mat*);
+void write_idx( std::ostream* );
+void simulated_annealing( double, std::ostream* );
+
+#endif

### 2018-12-25 ongoing/report/article.tex
Create project: DS and OMP comparison

@@
 
-\usepackage{amsmath,amssymb}
+\usepackage{mathtools}
+\usepackage{amssymb}
 \usepackage{graphicx}
+\usepackage[linkcolor=blue]{hyperref}
+\usepackage{xcolor}
+\usepackage[ocgcolorlinks]{ocgx2}
 
@@
 \date{\today}
-\title{An Explicit Probability Bound for Estimation of Multipath Millimeter Channel}
+\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
+
+\newcounter{numResult}
+%\setcounter{numResult}{1}
+\newcommand{\myCount}
+{
+   \stepcounter{numResult}
+   \textbf{\arabic{numResult}}
+}
+
 \begin{document}
+
 \maketitle
+
+\section{Acknowledgement}
 
@@
 Multiple-input-multiple-output (MIMO) communication is adopted as the next generation of wireless communication scheme.
-However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibration.
+However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
 It is then a non-trivial problem to estimate real-world wireless channels
@@
 
-\textbf{Definition}. We call \(h \in \mathbb{R}^p\) to be \(S\)-sparse, for \(S =1,2,3,\dotsc\), if only \(S\) components of \(h\) is nonzero.
+\myCount
+\textbf{Definition}.
+We call \(h \in \mathbb{R}^p\) to be \(S\)-sparse, for \(S =1,2,3,\dotsc\), if only \(S\) components of \(h\) is nonzero.
 
@@
 
+\myCount
 \textbf{Definition}.
@@
 For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
-\begin{gather*}
+\begin{gather}
 (1-\delta_S) \|\theta\|^2
@@
 \leq (1+\delta_S) \|\theta\|^2
-\end{gather*}
+\end{gather}
 RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).
@@
 Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
-\begin{gather*}
+\begin{gather}
 | \langle X_T c, X_{T'} c' \rangle |
 \leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
-\end{gather*}
+\end{gather}
 
 It is shown that (Cand\'es and Tao 2005), in the noiseless case, the convex program
-\begin{gather*}
-\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\
+\begin{gather}
+\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\ \notag
 \mathrm{subject}\; \mathrm{to} \quad X \hat{h} =y
-\end{gather*}
+\end{gather}
 recovers \(\hat{h}\) completely if \(\delta_{S} +\delta_{2S} +\delta_{3S} <1\).
@@
 For concreteness, consider a channel with noise,
-\begin{gather*}
+\begin{gather}
 y =\sqrt{\mathcal{E}} X h +z
-\end{gather*}
+\end{gather}
 where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
@@
 Let the following linear program, DS, be defined
-\begin{gather*}
-\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\
+\begin{gather}
+\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\ \notag
 \mathrm{subject}\; \mathrm{to} \quad \|X^\dagger r\|_\infty \leq \lambda_p \sigma
-\end{gather*}
+\end{gather}
 where \(r =y -X \hat{h}\).
@@
 DS may be written as
-\begin{gather*}
-\min_{x \in \mathbb{R}^p}  \|x\|_1 \\
+\begin{gather}
+\min_{x \in \mathbb{R}^p}  \|x\|_1 \\ \notag
 \mathrm{subject}\; \mathrm{to} \quad \|Ax+b\|_\infty \leq c
-\end{gather*}
+\end{gather}
 And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.
@@
 Consider a linear time-invariant channel with
-\begin{gather*}
+\begin{gather}
 y[t] =(x[t] \star h[t]) +z[t]
-\end{gather*}
+\end{gather}
 where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
 Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
-\begin{gather*}
+\begin{gather}
 y =X h
-\end{gather*}
+\end{gather}
 where \(X\) takes the form
-\begin{align*}
+\begin{align}
 X
@@
 \end{bmatrix}
-\end{align*}
+\end{align}
 We seek to get \(h\) in this undertermined system.
@@
 
+The literature on CSS has since been vast, and we need not and cannot go through all of them here.
+For example, Rao and Lau (2014) considers a rather complicated distributed algorithm where CSS is applied.
+They consider a MU-MIMO problem that channels seen by various users share the same support, and proposes a modified joint OMP algorithm.
+However, the sparsity of the channel is likewise merely made as an assumption.
+
+Since the notice of hybrid beamforming, scholars have applied
+
+J Lee, Gil, and Lee (2016), as an example, considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
+Here, as usual, the beambook phase is quantized, and they have specifed a particular set of angles and argues the superiority.
+
+Alkhateeb, Leus, and Heath Jr.\ poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
+
+They work simplified combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
+However, their work mainly focuses on numerical simulation, rather than mathematical proof.
+
+This being said, previous work only makes the assumption on the bound of the norm of the channel matrix, and, to the best knowledge of the author, has not characterized the such probability bounds as involving, say, number of channel paths and vector of array response.
+
 \subsection{Contribution}
 
-This being said, previous work only makes the assumption on the bound of the norm of the channel matrix, and, to the best knowledge of the author, has not characterized the such probability bounds as involving, say, number of channel paths and vector of array response.
 This article suggests a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
 Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.
+
+It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
+
+Meanwhile, 
+This serves partly as the foundation of performance analysis of 
+An analysis of comparison of OMP with DS
+Particularly worthy to note
+
+But, in view of the requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than
+
+Many papers have since cite Tropp and Gilbert (2007) only for justifying bound
+But not always is a elementwise i.i.d.\ Gaussian.
+
+After its advent, OMP becomes one of the most widely used channel estimation technique.
+The sparsity of channel 
+The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
+The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.
+
+Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm.
+Given a (beam) code book that corresponds to quantized AoA and AoD, they compare the power of (beam) code words in it, and choosing the column with 
+Interestingly, their proof for probability bound of mistaken event does not base on Gilbert and Tropp (2007), but only involves the union bound and direct probabilistic integration.
+
+Meanwhile Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
+characterizes on MIP matrices.
+Ben-Haim et.\ al.\ follow up their work and refine their bounds, also considering MIP conditions.
+The \(\mu\) is easier to verify.
+They serve as the guarantee for Alkhateeb et.\ al.\ (2015).
+
+For example, Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ as the main foundation for OMP perfomance bound.
+Ben-Haim et.\ al.\ conclude that OMP is better when
+
+These works are very technical, and the author does not wish to dispute their accuracy.
+Still, it remains unclear which of l1 and greedy is better.
+The comparison on Ben-Haim splits the category of convex optimization and greedy.
+
+The author argues that this article nevertheless considers a new configuration that, to the best of our knowledge, has not been dealt with.
+First, we do not assume, like Lee et.\ al., that the virtual channel model is naturally quantized in its angle of departure and of arrival.
+Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
+The combiner made of relatively phase shifters serves readily as the sensing matrix that satisfy the RIP consideration.
+Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
+Our simple but typical model is expect to shed light on how CSS should be designed in face of phase quantizing and channel parameters available such as path numbers.
+
+Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices.
+in a modified basis pursuit problem.
+
+Tropp and Gilbert put their techical proof on a standalone online document.
+They restrict to i.i.d.\ Gaussian matrix.
 
@@
 
+Before we start, let us remind that in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the title may be different from the source, but such case will be specified.
+
 We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product.
-The complex numbers has natural interpretation as the phasor of electronic waves.
+Here the complex numbers has natural interpretation as the phasor of electronic waves.
 Boldface lower case Latin alphabets denote vectors, and boldface upper case Latin alphabets denote matrices.
-Let \(\omega =(\omega_1, \omega_2, \omega_3) \in \Omega =[0,1)^3\) denote the overall index of the probability space.
+
+Denote \(\mathbb{E}\)
+Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
+Let the direct product
+%
+\begin{gather}
+\Omega
+=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
+\end{gather}
+%
+denote the overall sample space, where:
+%
+\begin{itemize}
+\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
+\item \(\Omega_h\) denotes that of the communication channel,
+\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
+\item \(\Omega_r\) denotes that at the receiver end.
+\end{itemize}
+%
 \(\omega_1\) stands for the probability index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.
 
-Define the uniform linear array, which can be modeled as
-\begin{gather*}
+\subsection{Channel Model}
+
+We restrict our consideration to the uniform linear array, which can be modeled as
+\begin{gather}
 \mathbf{a}(\phi')
 =\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
-\end{gather*}
+\end{gather}
 where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.
 
-And consider channel of the form
-\begin{gather*}
+And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
+\begin{gather}
 H
 =\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
-\end{gather*}
+\end{gather}
 The physical meaning of \(\theta_l\) is the \(l\)-th angle of arrival, and \(\theta_l\) the \(l\)-th angle of arrival.
-It is noted that in real scenario, the exponent \(i n \phi_l\) should be multiplied by a factor accounting for the spacing of two adjacent antenna.
+It is noted that in real scenario, the exponent \(i n \phi_l\) should be multiplied by a factor \((1/\lambda) \sin \eta\), \(\eta\) being the incident angle, accounting for the spacing of two adjacent antenna.
 But, since we consider uniform distribution of \(\theta_l, \phi_l\)'s, it suffices to absorb such factors into the values of \(\theta_l, \phi_l\)'s.
@@
 
+\myCount
+\textbf{Definition.}
+Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
+
+\myCount
+\textbf{Definition.}
+For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
+Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
+\myCount
+\textbf{Lemma.}
+
+\myCount
 \textbf{Definition.} Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
 We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
-\begin{gather*}
+\begin{gather}
 \mathbf{u} =F \mathbf{v}
-\end{gather*}
+\end{gather}
 where each entry of the matrix \(F\) is defined to be
-\begin{gather*}
+\begin{gather}
 F_{k,n} =e^{2\pi ikn/N},
 \quad k,n =0,1,2,\dotsc, N-1
-\end{gather*}
+\end{gather}
 
@@
 This way, we get
-\begin{gather*}
+\begin{gather}
 \tilde{H}_n
@@
 =\sum_{l=0}^L \alpha_l \exp(-i n \theta_l) \mathbf{a}(\phi_l)
-\end{gather*}
+\end{gather}
 If we absorb angle of incidence (formed by the ray of electronic wave and the normal line)
@@
 
+\subsection{Proposed Algorithm}
+
 \section{Results and Proofs}
 
+\stepcounter{numResult}
+\arabic{numResult}
 \textbf{Lemma.} Let \(\phi(\omega_3)\) be a uniformly distributed in \([0,2\pi)\) according to probability space index \(\omega_3 \in \Omega\).
@@
 To find the \(l\)-th path's contribution to the frequency domain, recall the identity
-\begin{align*}
+\begin{align}
 S(\phi)
-:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\
-=&\left| \frac{e^{i N \phi} -1}{e^{i \phi} -1} \right| \\
-=&\left| \frac{e^{i N \phi/2} -e^{-i N \phi/2}}{e^{i \phi /2} -e^{-i \phi /2}} \cdot e^{i (N-1) \phi/2} \right| \\
+:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
+=&\left| \frac{e^{i N \phi} -1}{e^{i \phi} -1} \right| \\ \notag
+=&\left| \frac{e^{i N \phi/2} -e^{-i N \phi/2}}{e^{i \phi /2} -e^{-i \phi /2}} \cdot e^{i (N-1) \phi/2} \right| \\ \notag
 =&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
 \quad 0 \leq \phi \leq \pi
-\end{align*}
+\end{align}
 By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
-\begin{align*}
+\begin{align}
 S(\phi)
-\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\
+\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\ \notag
 =& \frac{-48}{\phi^3 -24\phi}
 \quad 0 \leq \phi \leq \pi,
-\end{align*}
+\end{align}
 
@@
 By the same token, more generally,
-\begin{align*}
-&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\
-=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\
-=&\frac{1}{N} S(\pi \phi') \\
+\begin{align}
+&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\ \notag
+=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\ \notag
+=&\frac{1}{N} S(\pi \phi') \\ \notag
 \leq& \frac{48}{N \pi^3 (\phi'^3 -24 \phi' /\pi^2)}
-\end{align*}
+\end{align}
 where \(\phi' =k/N -\phi/2\pi\), and the cubic expression is split.
 We wish to bound the tail of \(S(\pi \phi')\), and apply the na\"ive bound
-\begin{align*}
+\begin{align}
 &\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\phi'^3 -24 \phi' /\pi^2}
- d\phi' \\
-=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\
+ d\phi' \\ \notag
+=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\ \notag
 \leq& \frac{1}{\pi^2} \log \frac{L}{N}
-\end{align*}
+\end{align}
 Here, the integral in the first line is immediate.
@@
 where
-\begin{gather*}
-\mathcal{A}, \mathca{B}, \mathcal{C} \subset \mathbb{N} \\
-\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varempty \\
+\begin{gather}
+\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \mathbb{N} \\ \notag
+\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\ \notag
 A \cup B \cup C =\{1, \dotsc, N\}.
-\end{gather*}
+\end{gather}
 
@@
 Then
-\begin{align*}
+\begin{align}
 \|h_A\|_1 -\|\eta_A\|_1 +\|\eta_C\|_1 -\|h_C\|_1
-\leq& \|h +\eta\|_1 \\
+\leq& \|h +\eta\|_1 \\ \notag
 \leq& \|h\|_1
-\end{align*}
+\end{align}
 
@@
 
-\begin{align*}
+\begin{align}
 \|X^\dagger_{AB} X \eta\|_\infty
-<&\|X^\dagger X \eta\|_\infty \\
+<&\|X^\dagger X \eta\|_\infty \\ \notag
 \leq& 2 \lambda_p
-\end{align*}
+\end{align}
 
-\begin{align*}
+From ``Dantzig Selector'' (Cand\`es and T Tao 2007), Lemma 1, first equation.
+
+\stepcounter{numResult}
+\arabic{numResult}
+\textbf{Lemma}.
+\begin{align}
 \|\eta_Ah\|_2
 \leq K_1 \|X^\dagger_{AB} X \eta\|_2 +K_2 \|\eta_C\|_2
-\end{align*}
-Tao, Lemma 1-1
+\end{align}
 
-Tao, Lemma 1-2
-\begin{align*}
+From ``Dantzig Selector'' (Cand\`es and T Tao 2007), Lemma 1, second equation.
+
+\stepcounter{numResult}
+\arabic{numResult}
+\textbf{Lemma}.
+\begin{align}
 \|\eta\|_2^2
 \leq \|\eta_{AB}\|_2^2 +K_3 \|\eta_C\|_2^2
-\end{align*}
+\end{align}
 
@@
 With the analysis of [], OMP is usually used
-But
+
+\section{Simulation}
+
+Since our setting is slightly different
+In this section we first describe the DS algorithm, which is our target of investigation, and briefly review the OMP algorithm, for sake of comparison.
+As we see in the above, Dantzig Selector 
+We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is well-known for convex optimization problems.
 
@@
 
+\section{Conclusion and Future Work}
+
+Firstly,
+Meanwhile, DS goes not without criticism for large complexity.
+Indeed it is clear, even from the primal-dual implementation above, that DS requires large dimensional vector
+
+Secondly
+And comparison of bounds of OMP and DS
+The author criticises the tendency of current literature to mix up results for DS and OMP without clear justification, since they are two quite different approaches to the compressed sensing problem.
+It is however not trivial to make meaningful comparison, since DS works with a RIP matrix, and OMP for Gaussian... the distinction is slight but definite...
+The author critizises In OMP we don't know whether the measurement matrix is the same as channel
+And OMP has stricter condition than DS
+Tao, however, specifies a noise relation
+
+Bounds of performance in different setting are often nontrivial to obtain, and one cannot think OMP, or indeed every algorithm, as a universal solution.
+OMP trades off precision for time complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
+All in all, different problems requires different technique and algorihm within the constraint at hand, as is probably true in every discipline of engineering.
+
 \section{References}
+
+References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.
 
@@
 
-\item F Sohrabi and W Yu, ``Hybrid Digital and Analog Beamforming Design for Large-Scale Antenna Arrays'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol. 10, No. 3, April 2016.
+\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6
 
-\item F Sohrabi and W Yu, ``Hybrid Analog and Digital Beamforming for OFDM-Based Large-Scale MIMO Systems''.
-2016 IEEE 17th International Workshop on Signal Processing Advances in Wireless Communications (SPAWC).
+\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.
+5.
 
-\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath, ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol. 21, No.5, June 2003.
+\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}
 
-\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed, ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems''.
-\textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.
-10, No.
-3, April 2016.
+\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.98, No.6.
 
-\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.
+\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
 
-\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels''. Proceedings of the IEEE, Vol.98, No.6.
+\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
 
-\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing''. 2008 42nd Annual Conference on Information Sciences and Systems.
+\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.
 
@@
 
-\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming''. Retrieved from ``https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf''.
+\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
 
-\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming.'' \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
+\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
 
@@
 
-\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)''. \textit{The Annals of Statistics}, Vol.35, No.6.
+\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
 
-\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems''.
-\textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.10, No.3
+\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', \textit{IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.
 
-\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices''. \textit{Constructive Approximation} \textbf{28}: 253–263
+\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', \textit{IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.
 
-\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation''. \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6
+\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.\ 35, No.\ 6.
+
+\item Z Gao, L Dai, Z Wang, and S Chen (2015).
+``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.
+
+\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.
+
+\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.
+
+\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', \textit{IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.
+
+\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.
+
+\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.
+
+\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
+Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
+
+\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
 

### 2018-12-25 ongoing/code/make.sh

@@ -1,11 +1,10 @@
 #!/usr/bin/env bash
 
-#OBJS="main.o functions.o constants.o"
-#CC="g++"
-#CFLAGS="-Wall -g"
-#eval "${CC}" "${CFLAGS}" -o "${OBJS}"
+OBJS="main.o functions.o constants.o channel.cpp oommpp.cpp"
+CPPS="src/main.cpp src/functions.cpp src/const.cpp src/channel.cpp src/oommpp.cpp src/ddss.cpp"
+CC="g++"
+CFLAGS="-I lib/ -Wall -g -O3 -o"
+#CFLAGS="-I lib/ -no-canonical-prefixes -Wall -g -O3 -o"
+NAME="main"
 
-g++ -Wall -O3 -o ./bin/main.o ./src/main.cpp ./src/functions.cpp ./src/constants.cpp 
-#g++ -Wall -g -o ./bin/main.o ./src/main.cpp ./src/functions.cpp ./src/constants.cpp 
-
-
+eval "${CC}" "${CFLAGS}" "${NAME}" "${CPPS}"

### 2018-12-25 ongoing/code/src/channel.h

@@ -1,0 +1,29 @@
+#ifndef CLASS_H
+#define CLASS_H
+
+#include <vector>
+#include "const.h"
+
+//class Comp;
+//class Mat;
+//class Vec;
+
+class Channel
+{
+public:
+   Channel();
+   Channel(int, int);
+   ~Channel();
+   void realize();
+   Mat get_matrix();
+
+private:
+   int nn_path;
+   std::vector<double> list_ang_dep;
+   std::vector<double> list_ang_arr;
+   std::vector<Comp> list_amp;
+
+};
+
+
+#endif

### 2018-12-25 ongoing/code/src/const.cpp

@@ -1,0 +1,15 @@
+#include <map>
+#include <complex>
+#include <Eigen/Dense>
+#include "const.h"
+
+
+const double Const::pi =3.14159265358979;
+const std::complex<double> Const::ii =std::sqrt( static_cast<Comp>(-1) );
+const double Const::array_t_phase =0.5;
+const double Const::array_r_phase =0.6;
+const int Const::nn_hh =24;
+const int Const::nn_rr =12;
+const int Const::nn_bb =4;
+const int Const::max_idx_ssnnrr =10;
+const double Const::step_ssnnrr =0.3;

### 2018-12-25 ongoing/code/src/const.h

@@ -1,0 +1,29 @@
+#ifndef CONST_H
+#define CONST_H
+
+#include <map>
+#include <complex>
+#include <Eigen/Dense>
+
+typedef std::complex <double> Comp;
+typedef Eigen::MatrixXcd Mat;
+typedef Eigen::VectorXcd Vec;
+
+
+class Const
+{
+public:
+   static const double pi;
+   static const std::complex<double> ii;
+   static const double array_t_phase; // a phase factor in uniform linear array of Tx
+   static const double array_r_phase; // a phase factor in uniform linear array of Rx
+   static const int nn_hh; // # of antennae
+   static const int nn_rr; // dim. of analog stage
+   static const int nn_bb; // dim. of digital stage
+   static const int max_idx_ssnnrr; // maximum index of SNR
+   static const double step_ssnnrr; // maximum index of SNR
+
+private:
+};
+
+#endif

### 2018-12-25 ongoing/code/src/ddss.h

@@ -1,0 +1,7 @@
+#ifndef DDSS_H
+#define DDSS_H
+
+#include "const.h"
+
+
+#endif

### 2018-12-25 ongoing/code/src/functions.cpp

@@ -3,81 +3,44 @@
 #include <cstdlib>
 #include <ctime>
 #include <random>
+#include <cassert>
 
-#include <boost/numeric/ublas/matrix.hpp>
-#include <boost/numeric/ublas/io.hpp>
-#include <boost/numeric/ublas/matrix_proxy.hpp>
-#include <boost/numeric/ublas/lu.hpp>
-#include "constants.h"
+#include <Eigen/Dense>
 
-
-
-void newton_method(std::vector<double> list_ang_dep, std::vector<double> list_ang_arr, std::vector<Comp> list_amp)
-{
-   
-}
-
-void walk_one_step(Parameters& param)
-{
-   
-}
+#include "const.h"
+#include "functions.h"
+#include "channel.h"
+#include "ddss.h"
+#include "oommpp.h"
 
 void write_idx( std::ostream* p_ios )
 {
-   for(std::size_t idx=0; idx <=cst::max_iter-1; idx++)
-   {
-      if( idx %cst::t_record ==0 ){ (*p_ios) << idx << ' '; }
-   }
+   for(int ssnnrr=0; ssnnrr <=Const::max_idx_ssnnrr -1; ssnnrr++)
+      { (*p_ios) << ssnnrr << ' '; }
+
    (*p_ios) << std::endl;
 }
 
-double infty_norm(const Mat& m)
-{
-   double ret =0;
-   for(std::size_t i=0; i<=cst::nn-1; i++)
-      for(std::size_t j=0; j<=cst::nn-1; j++)
-      {
-         double hold_abs =std::abs( m(i,j) );
-         if(hold_abs >ret){ ret =hold_abs; }
-      }
-   return ret;
-}
-
-double get_normalized_uniform()
+double get_uniform()
 {
    std::random_device dev;
    std::mt19937 gen(dev());
-   std::uniform_real_distribution<> dist(0.0, 1.0);
-   return dist(gen);
+   std::uniform_real_distribution<> distri(0.0, 1.0);
+   return distri(gen);
 }
 
-double get_normalized_gaussian()
+double get_normal()
 {
    std::default_random_engine gen;
-   std::normal_distribution<double> dist(0,1);
-   return x+dist(gen);
+   std::normal_distribution<double> distri(0,1);
+   return distri(gen);
 }
 
-double mod_2_pi(double x)
+Vec get_array_response(double ang, int nn)
 {
[…]

### 2018-12-25 ongoing/deprecated_one/code/make.sh

@@ -1,0 +1,11 @@
+#!/usr/bin/env bash
+
+#OBJS="main.o functions.o constants.o"
+#CC="g++"
+#CFLAGS="-Wall -g"
+#eval "${CC}" "${CFLAGS}" -o "${OBJS}"
+
+g++ -Wall -O3 -o ./bin/main.o ./src/main.cpp ./src/functions.cpp ./src/constants.cpp 
+#g++ -Wall -g -o ./bin/main.o ./src/main.cpp ./src/functions.cpp ./src/constants.cpp 
+
+

### 2018-12-25 ongoing/deprecated_one/code/run.sh

@@ -1,0 +1,7 @@
+#!/usr/bin/env bash
+
+#lldb ./bin/main.o ./dat/table.txt
+rm -f ./dat/table.txt ./plt/fig.png
+./bin/main.o ./dat/table.txt
+./src/read_and_draw.py ./dat/table.txt 
+

### 2018-12-29 ongoing/report/article.tex
Complete basic problem formulation

@@
 \newcounter{numResult}
-%\setcounter{numResult}{1}
 \newcommand{\myCount}
@@
 }
+%\newcommand{\qed}{\tag*{$\blacksquare$}}
 
@@
 
+If we absorb angle of incidence (formed by the ray of electronic wave and the normal line)
+\((d/\lambda) \sin \tilde{\theta}_l\)
 Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.
@@
 \begin{gather}
-F_{k,n} =e^{2\pi ikn/N},
-\quad k,n =0,1,2,\dotsc, N-1
+F_{m,n} =e^{2\pi ikm/N},
+\quad m,n =0,1,2,\dotsc, N-1
 \end{gather}
 
-\(H\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
-This way, we get
+In summary, the effective channel may be written as
 \begin{gather}
-\tilde{H}_n
-:=H \mathbf{u}_n
-=\sum_{l=0}^L \alpha_l \exp(-i n \theta_l) \mathbf{a}(\phi_l)
+Y (\omega_h, \omega_z)
+:=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
 \end{gather}
-If we absorb angle of incidence (formed by the ray of electronic wave and the normal line)
-\((d/\lambda) \sin \tilde{\theta}_l\)
+Supress the probabilistic index for simplicity, we restate the same equation as
+\begin{gather}
+Y
+:=W_B W_R ( H F_R F_B \mathbf{u}_m +z )
+\end{gather}
 
-\subsection{Proposed Algorithm}
+\subsection{Proposed Method}
+
+The effective channel \(Y\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
+This way, we may denote the acquired effective channel matrix \(Y\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
+\begin{gather}
+Y_{:,n}
+:=W_B W_R ( H F_R F_B \mathbf{u}_m +z ), \quad
+n =1, 2, \dotsc, N_B
+\end{gather}
+The crux of the matter is the recovery of \(H\) with knowledge of \(Y\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
+
+We recall that, as the author has argued above, existent literature often makes use of OMP, and exploit the relation
+
+\begin{gather}
+\mathrm{vec}(Y) -z
+=\big[ (F_R^\dagger F_B^\dagger) \otimes (W_B W_R) \big] \mathrm{vec}(H)
+\end{gather}
+
+as sparse recovery problem of \(\mathrm{vec}(H)\).
+But that suffers the problem of grid quantization, and 
+On the other hand, the author argues in favor of DS, since it is provably ideal in certain senses, guaranteed even under noisy condition,
+So why do we not simply formulate the recovery of \(H\) as a DS program?
+DS is an \(\ell_1\)-minimization problem, and, since it is well known to be convex, it is no less tractable than OMP.
+
+In addition, observe that, if we write
+\begin{gather}
+G =K^\dagger H
+\end{gather}
+as the spatial frequency domain representation of \(H\), then
+\begin{gather}
+Y
+:=W_B W_R K ( G F_R F_B +K^\dagger z ), \quad
+n =1, 2, \dotsc, N_B
+\end{gather}
+If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
+
+That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
+\begin{gather}
+\mathrm{vec}(Y)
+\approx \big[ (K F_R^\dagger F_B^\dagger) \otimes (W_B W_R) \big] \mathrm{vec}(H)
+\end{gather}
+If so, our program reads
+
+\myCount
+\textbf{Program}.
+Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
+Suppose \(Y\) is the acquired effective channel matrix under noisy observation.
+Set the beamspace vector representation of \(H\) to be
+\begin{gather}
+\tilde{h} := \mathrm{vec}(H) \\
+\tilde{y} := \mathrm{vec}(Y) \\
+A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
+\end{gather}
+and set
+\begin{gather}
+r =\tilde{y} -A \tilde{h}
+\end{gather}
+Then, with parameter \(\gamma\) specified, define the following program
+\begin{gather}
+\hat{\tilde{g}}
+=\underset {{\tilde{h}}} {\mathrm{min}} \|\tilde{h}\|_1 \quad
+\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
+\end{gather}
+And convert \(\hat{\tilde{g}}\) back to the space domain as
+\begin{gather}
+\hat{\tilde{h}}
+=K^\dagger \hat{\tilde{g}}.
+\end{gather}
+And finally recover the estimated \(H\) as
+\begin{gather}
+\hat{H} =\mathrm{vec}^{-1} (\hat{\tilde{h}}) \quad \blacksquare
+\end{gather}
+
+It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as below.
 
@@
 
-From ``Dantzig Selector'' (Cand\`es and T Tao 2007), Lemma 1, first equation.
+From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation.
 
@@
 
-From ``Dantzig Selector'' (Cand\`es and T Tao 2007), Lemma 1, second equation.
+From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation.
 
@@
 \section{Simulation}
+
+With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
+
+\subsection{Main Problem Written as an Convex Optimization Program}
+
+\subsection{Primal-Dual Algorithm for Our DS Program}
 

### 2018-12-31 ongoing/report/article.tex
Complete basic literature survey

@@
 
-\newcounter{numResult}
+\newcounter{NumResult}
 \newcommand{\myCount}
 {
-   \stepcounter{numResult}
-   \textbf{\arabic{numResult}}
+   \stepcounter{NumResult}
+   \textbf{\arabic{NumResult}}
 }
-%\newcommand{\qed}{\tag*{$\blacksquare$}}
+
+\newcommand {\Result} [2]
+{
+   \bigskip
+   \myCount \textbf{#1} \par
+   {#2} \par
+   \hfill \(\blacksquare\)
+   \bigskip
+}
 
@@
 
-Multiple-input-multiple-output (MIMO) communication is adopted as the next generation of wireless communication scheme.
+Multiple-input-multiple-output (MIMO) communication is widely expected to be the next-generation wireless communication scheme.
 However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
-It is then a non-trivial problem to estimate real-world wireless channels
+It is then a non-trivial problem to estimate real-world wireless channels.
 
 Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
-If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing.
-A promiment estimator is The Dantzig Selector proposed by Tao and Cand\'es.
-In this article, we extend their proof to derive a specific bound in the setting of estimation of millimeter wave channel, utilizing an all-phase-shifter combiner in the receiver end.
-Simulation compares our result and the
+If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing, an active area that has recently emerged.
+A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context.
+However, Orthogonal Matching Pursuit (OMP) later emerges as a low-complexity solution, and following-up literature usually used OMP rather than DS as a result.
+
+In this article, we utilize a hybrid structure at both transmitter and receiver end, consisting of both digital and analog percoders and combiners.
+We argue in favor of DS, and verify that DS is, as originally perceived, ideal in certain senses.
+DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, and as in its allowance of noise corruption.
+Moreover, we extend their proof to derive a stronger bound in the setting of estimation of millimeter wave channel for almost-sparse channel matrix
+
+We show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
+Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.
 
@@
 
+This section is organized as follows.
+Before we start, we introduce our notation in the very beginning, since the literature survery quickly goes into technical details.
+And we first provide the motivation, and then overview the existent literature on channel estimation.
+Particularly, we will summerize present results on DS and OMP, and argue that DS is a viable solution that has been ignored, and then claim our contribution in this article that will be shown in the later sections.
+
+\subsection{Notation}
+
+Before we start, let us remind that, in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the classification may be different from its source.
+
+We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
+Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.
+
+Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
+Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
+
 \subsection{Background}
 
-Millimeter waves communication has been proposed to be the next-generation specification.
-The smaller wavelength entails higher frequency bands, and thus wider available bandwith to be available.
-In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
-Multiple-input multiple-output (MIMO) systems with a large number of antennae of both sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.
-
+Multiple-input multiple-output (MIMO) communication system has been proposed to be the next-generation specification.
+With a large number of antennae of both transmitter and receiver sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.
 But MIMO presents new obstacles as well.
 The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
-It is important to devise feasible simulation method, as the systems themselves are growing more complicated, and the cost of simulations is large.
+It is important to devise a feasible scheme, as the systems themselves are growing more complicated.
+Meanwhile, millimeter waves, having smaller wavelength, entails higher frequency bands, and thus wider available bandwith to be available.
+In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
+Consequently, this article considers MIMO in the millimeter r\`egime.
 
 The figure of merit of a MIMO system is usually considered to be the channel capacity.
-The capacity \(C\) of a MIMO channel \(H\) at perfect CSI (here, the matrix form of \(H\)) is well-known, which is first proved by Teletar.
+The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
 But that knowledge is hardly always available.
-What makes things more difficult is the case that \(H\) is determined from not only \(n(\omega)\), but also parameter \(\theta\).
-It is pointed out that the explicit form of \(C(\theta)\) is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
-Consequently, the perfect-CSI expression of channel capacity is often used regardless of these issues.
+What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
+It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
+Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
 Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
+
 Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
 Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
-
+With more antennae present, conventional training-based algorithm also increase in complexity and storage.
 In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
-With more antennae present, conventional algorithms also increase in complexity and storage.
 A design of new algorithms that addressed these issues is thus in need.
 
-\subsection{The Dantzig Selector}
+\subsection{Recovery of Sparse Vector in the Noiseless Case}
 
@@
 
-Particularly relevant and inspiring to the present article is Cand\`es and Tao (2006), where they proposed a convex program called The Dantzig Selector (hencefore DS).
-Cand\`es and Tao argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
-From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
-Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
+They showed that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
 
-Several notions related to compressed sensing are necessary in the presentation of results:
+\Result
+{Definition}
+{
+\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
+\begin{gather} 
+\# \{\mathrm{supp}(x)\} \leq s
+\end{gather}
+That is, only at most \(s\) components of vector \(x\) is nonzero.
+}
 
-\myCount
-\textbf{Definition}.
-We call \(h \in \mathbb{R}^p\) to be \(S\)-sparse, for \(S =1,2,3,\dotsc\), if only \(S\) components of \(h\) is nonzero.
+\Result
+{Program}
+{
+Let \(A,y\) be given.
+Find \(x\) with
+\begin{gather}
+\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
+\mathrm{s.t.} \quad Ax =y
+\end{gather}
+}
 
-Denote as \(X_T\) the columns of \(X\) having indices in \(T\), where \(T \subset \{1,\dotsc,p\}\).
+\Result
+{Theorem}
+{
+Let \(y =Ax\).
+Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
+That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
+\begin{gather}
+\delta_{S} +\delta_{2S} +\delta_{3S} <1
+\end{gather}
+}
 
-\myCount
-\textbf{Definition}.
+\Result
+{Notation}
+{
+Let \(T \subset \mathbb{N}\).
+Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
+}
+
+\Result
+{Definition}.
+{
 Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
@@
 \end{gather}
+}
+
 RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).
@@
 
-It is shown that (Cand\'es and Tao 2005), in the noiseless case, the convex program
+\subsection{The Dantzig Selector}
+
+Later Cand\`es and Tao  obtained a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006, which will be a main reference of this article), with a convex program called The Dantzig Selector they proposed (hencefore DS), they can recover the noisy case too.
+They argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
+From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
+Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
+
+For concreteness, consider a liear transformation with noise,
 \begin{gather}
-\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad X \hat{h} =y
-\end{gather}
-recovers \(\hat{h}\) completely if \(\delta_{S} +\delta_{2S} +\delta_{3S} <1\).
-
-For concreteness, consider a channel with noise,
-\begin{gather}
-y =\sqrt{\mathcal{E}} X h +z
+y =Ax +z
 \end{gather}
 where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
-(They also discussed specially the noiseless case, but we will not pursue the bounds here.)
+How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
 
-How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
-Let the following linear program, DS, be defined
+\Result
+{Program}
+{
+Let \(A,y\) be given.
+Find \(x\) with
 \begin{gather}
-\min_{\hat{h} \in \mathbb{R}^p}  \|\hat{h}\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad \|X^\dagger r\|_\infty \leq \lambda_p \sigma
+\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
+\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
 \end{gather}
-where \(r =y -X \hat{h}\).
-
-DS may be written as
-\begin{gather}
-\min_{x \in \mathbb{R}^p}  \|x\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad \|Ax+b\|_\infty \leq c
-\end{gather}
+where \(r =y -A \hat{x}\).
+}
 And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.
 
-The proof of DS is non-constructive, and it is not clear at first what matrices serves as the RIP condition.
-But later, () have found there is a particularly convenient sufficient condition to verify RIP.
-Tao explicitly remarked that the bound can be refined, but they did not undergo such task.
+\subsection{Condition of RIP Linear Transformation}
+
+The constant \(\delta\) in the proof of DS is significant.
+Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(A\) is fully unitary.
+
+Here, it is not clear at first what matrices serves as the RIP condition.
+But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.
+
+\Result
+{Theorem}
+{
+Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
+Then, with \(0 <\epsilon <1\),
+\begin{gather}
+   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
+   \leq 2 \exp(-n c_0(\epsilon))
+\end{gather}
+where we have
+\begin{gather}
+c_0(\epsilon)
+=\epsilon^2/4 -\epsilon^3/6.
+\end{gather}
+}
 
@@
 
+We have summarised results in compressed sensing, and we now relate the matter to the communication scenario.
+Recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
 Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
-For example, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
-They explore the estimation of single-antenna channel response with respect to time.
-Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability.
+Some scholars thus has applied compressive sensing techniques to the problem.
+
+One of the first papers, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
+What they explored was the estimation of single-antenna channel response with respect to time.
+Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability, providing the ground for the former paper.
 
@@
 
-Then \(X\) is RIP of overwhelmingly probability.
+Bajwa et.\ al.\ was able to show that \(X\) is RIP of overwhelmingly probability.
+
+\subsection{Orthogonal Matching Pursuit}
+
+Around that time, Tropp and A C Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit, that a i.i.d.\ matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.
+
+The setting here is \(y =Ax\), the noiseless, real-number case.
+Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
+We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).
+
+\Result
+{Algorithm}
+{
+\begin{enumerate}
+\item
+\end{enumerate}
+}
+
+\Result
+{Theorem}
+{
+   Following the setting described above, suppose, for \(0 <\delta <1\),
+\begin{gather}
+   M \geq 16s \log (N/\delta)
+\end{gather}
+Then   Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
+}
+
+For the proof, see the technical report: Tropp and A C Gilbert (2007a).
+
+It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
+Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
+To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
+Let signal \(x\) be sent, and \(y\) be receiverd, that is
+\begin{gather}
+y =WHF x
+\end{gather}
+
+\Result
+{Definition}
+{
+Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
+}
+
+\Result
+{Definition.}
+{
+For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
+Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
+}
+
+With (), scholars often exploit the relation
+\begin{gather}
+\mathrm{vec}(Y)
+=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
+\end{gather}
+
+The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
+The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.
+
+\subsection{Further development on CSS}
 
 The literature on CSS has since been vast, and we need not and cannot go through all of them here.
-For example, Rao and Lau (2014) considers a rather complicated distributed algorithm where CSS is applied.
-They consider a MU-MIMO problem that channels seen by various users share the same support, and proposes a modified joint OMP algorithm.
-However, the sparsity of the channel is likewise merely made as an assumption.
+Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.
 
-Since the notice of hybrid beamforming, scholars have applied
+Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same support.
 
-J Lee, Gil, and Lee (2016), as an example, considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
-Here, as usual, the beambook phase is quantized, and they have specifed a particular set of angles and argues the superiority.
+Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm, using a (beam) code book with quantized AoA and AoD.
 
-Alkhateeb, Leus, and Heath Jr.\ poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
+Alkhateeb, Leus, and Heath Jr.\ (2015) poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
+They work simplified all-phase-shifter combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
+Their work mainly focuses on numerical simulation, rather than mathematical proof.
 
-They work simplified combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
-However, their work mainly focuses on numerical simulation, rather than mathematical proof.
+Since the notice of hybrid beamforming, scholars have also applied the same idea to hybrid systems.
+Lee, Gil, and Lee (2016) considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
+The beambook phase is quantized, which may have been a source of error, and they have specifed a particular grid set of angles and argues the superiority.
+One of their simulations experiments utilizes DFT and permutated DFT matrix, instead of as originally suggested by Tropp and Gilbert (2007).
 
-This being said, previous work only makes the assumption on the bound of the norm of the channel matrix, and, to the best knowledge of the author, has not characterized the such probability bounds as involving, say, number of channel paths and vector of array response.
+Meanwhile, the improvement of OMP bound is also going on.
+Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
+Indeed, MIP deals with correlation of columns of the sensing matrix, rather than the almost-unitarity, making the condition easier to verify.
+
+Ben-Haim et.\ al.\ (2010) follow up their work and refine their bounds, also considering MIP conditions.
+They conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
+Still, since the setting of OMP and DS is rather different, it remains unclear which of is better.
+
+Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ (2010) as the main foundation for OMP perfomance bound.
+
+Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices in a modified basis pursuit problem.
 
@@
 
-This article suggests a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
+We remark several observation on past literature, that has been, to the best of our knowledge, lacking or less than ideal.
+
+\begin{enumerate}
+\item As said, previous work the favor on OMP rather than DS (let alone other sparse algorithm) is evident.
+\item In view of The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than Cand\`es and Tao (2007).
+\item Previous work only takes the assumption on the bound of the norm of the channel matrix to be granted.
+\item Likewise, such probability bounds on the sparsity of the channel as involving, say, number of channel paths and vector of array response has not be explored.
+\end{enumerate}
+
+We consider a system model where both digital and analog beamformer are i.i.d.\ random matrix combiner that serve readily as the sensing matrix satisfying the RIP property.
+We apply a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
 Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.
 
-It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
+Our contribution include:
 
-Meanwhile, 
-This serves partly as the foundation of performance analysis of 
-An analysis of comparison of OMP with DS
-Particularly worthy to note
-
-But, in view of the requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than
-
-Many papers have since cite Tropp and Gilbert (2007) only for justifying bound
-But not always is a elementwise i.i.d.\ Gaussian.
-
-After its advent, OMP becomes one of the most widely used channel estimation technique.
-The sparsity of channel 
-The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
-The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.
-
-Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm.
-Given a (beam) code book that corresponds to quantized AoA and AoD, they compare the power of (beam) code words in it, and choosing the column with 
-Interestingly, their proof for probability bound of mistaken event does not base on Gilbert and Tropp (2007), but only involves the union bound and direct probabilistic integration.
-
-Meanwhile Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
-characterizes on MIP matrices.
-Ben-Haim et.\ al.\ follow up their work and refine their bounds, also considering MIP conditions.
-The \(\mu\) is easier to verify.
-They serve as the guarantee for Alkhateeb et.\ al.\ (2015).
-
-For example, Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ as the main foundation for OMP perfomance bound.
-Ben-Haim et.\ al.\ conclude that OMP is better when
-
-These works are very technical, and the author does not wish to dispute their accuracy.
-Still, it remains unclear which of l1 and greedy is better.
-The comparison on Ben-Haim splits the category of convex optimization and greedy.
-
-The author argues that this article nevertheless considers a new configuration that, to the best of our knowledge, has not been dealt with.
-First, we do not assume, like Lee et.\ al., that the virtual channel model is naturally quantized in its angle of departure and of arrival.
-Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
-The combiner made of relatively phase shifters serves readily as the sensing matrix that satisfy the RIP consideration.
-Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
-Our simple but typical model is expect to shed light on how CSS should be designed in face of phase quantizing and channel parameters available such as path numbers.
-
-Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices.
-in a modified basis pursuit problem.
-
-Tropp and Gilbert put their techical proof on a standalone online document.
-They restrict to i.i.d.\ Gaussian matrix.
+\begin{enumerate}
+\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
+\item We do not assume that the virtual channel model is naturally quantized in its angle of departure and of arrival, thus removes concern of the quantization error within the proof.
+\item Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
+\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
+\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
+\end{enumerate}
 
@@
 
-\subsection{Notation}
-
-Before we start, let us remind that in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the title may be different from the source, but such case will be specified.
-
-We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product.
-Here the complex numbers has natural interpretation as the phasor of electronic waves.
-Boldface lower case Latin alphabets denote vectors, and boldface upper case Latin alphabets denote matrices.
-
-Denote \(\mathbb{E}\)
-Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
 Let the direct product
@@
 \myCount
-\textbf{Definition.}
-Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
-
-\myCount
-\textbf{Definition.}
-For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
-Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
-\myCount
-\textbf{Lemma.}
-
-\myCount
 \textbf{Definition.} Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
@@
 
-We recall that, as the author has argued above, existent literature often makes use of OMP, and exploit the relation
-
-\begin{gather}
-\mathrm{vec}(Y) -z
-=\big[ (F_R^\dagger F_B^\dagger) \otimes (W_B W_R) \big] \mathrm{vec}(H)
-\end{gather}
-
 as sparse recovery problem of \(\mathrm{vec}(H)\).
@@
 \begin{gather}
-\tilde{h} := \mathrm{vec}(H) \\
+h := \mathrm{vec}(H) \\
 \tilde{y} := \mathrm{vec}(Y) \\
@@
 \begin{gather}
-r =\tilde{y} -A \tilde{h}
+r =\tilde{y} -A h
 \end{gather}
@@
 \hat{\tilde{g}}
-=\underset {{\tilde{h}}} {\mathrm{min}} \|\tilde{h}\|_1 \quad
+=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
 \mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
@@
 \begin{gather}
-\hat{\tilde{h}}
+\hat{h}
 =K^\dagger \hat{\tilde{g}}.
@@
 \begin{gather}
-\hat{H} =\mathrm{vec}^{-1} (\hat{\tilde{h}}) \quad \blacksquare
+\hat{H} =\mathrm{vec}^{-1} (\hat{h})
 \end{gather}
@@
 
-\stepcounter{numResult}
-\arabic{numResult}
+\myCount
 \textbf{Lemma.} Let \(\phi(\omega_3)\) be a uniformly distributed in \([0,2\pi)\) according to probability space index \(\omega_3 \in \Omega\).
@@
 
-\stepcounter{numResult}
-\arabic{numResult}
-\textbf{Lemma}.
+\Result
+{Lemma}
+{
 \begin{align}
@@
 \end{align}
+}
 
@@
 \end{align}
-
-Another difference is that this article solves the optimization problem solely using the method of greatest descent.
-While OMP is widely used 
-With the analysis of [], OMP is usually used
+}
 
@@
 
-\subsection{Main Problem Written as an Convex Optimization Program}
+As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\mathcal{R}(h)\).
+But it is not the end.
+In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-magic'' transforms DS into a linear program (LP), but that does not directly applies
+Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
+Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
+Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-magic''.
 
-\subsection{Primal-Dual Algorithm for Our DS Program}
+\subsection{Transformation into Second Order Cone Problem}
 
-Since our setting is slightly different
-In this section we first describe the DS algorithm, which is our target of investigation, and briefly review the OMP algorithm, for sake of comparison.
-As we see in the above, Dantzig Selector 
-We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is well-known for convex optimization problems.
+Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem.
+Recapitulate that, as we explained in the above, DS involves a 
+We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
 
@@
 
-\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U. Press.
+\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
 

### 2018-12-31 ongoing/report/article.tex
Outline theorem proofs

@@
 
-In this article, we utilize a hybrid structure at both transmitter and receiver end, consisting of both digital and analog percoders and combiners.
+In this article, we utilize a hybrid structure at both transmitter and receiver end, each of them having both digital and analog percoders and combiners.
 We argue in favor of DS, and verify that DS is, as originally perceived, ideal in certain senses.
@@
 
-Let the direct product
+\subsection{Channel Model}
+
+Since expression involving probability will get very complecated, introduce the direct product
 %
@@
 %
-denote the overall sample space, where:
+to denote the overall sample space, where
 %
@@
 %
-\(\omega_1\) stands for the probability index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.
-
-\subsection{Channel Model}
+\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.
 
@@
 H
+=\sum_{l=0}^L \alpha_l \mathbf{a}\big( \frac{d}{\lambda} \sin \phi_l' \big) \mathbf{a}\big( \frac{d}{\lambda} \sin \theta_l' \big)^\dagger
+\end{gather}
+The physical meaning of \(\theta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\theta_l\), the \(l\)-th that of arrival wave.
+
+For our purpose, we may absorb the argument of \(\mathbf{a}\) as
+\begin{gather}
+\phi_l
+=\frac{d}{\lambda} \sin \phi_l' \\
+\theta_l
+=\frac{d}{\lambda} \sin \theta_l'
+\end{gather}
+to get a simpler form
+\begin{gather}
+H
 =\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
 \end{gather}
-The physical meaning of \(\theta_l\) is the \(l\)-th angle of arrival, and \(\theta_l\) the \(l\)-th angle of arrival.
-It is noted that in real scenario, the exponent \(i n \phi_l\) should be multiplied by a factor \((1/\lambda) \sin \eta\), \(\eta\) being the incident angle, accounting for the spacing of two adjacent antenna.
-But, since we consider uniform distribution of \(\theta_l, \phi_l\)'s, it suffices to absorb such factors into the values of \(\theta_l, \phi_l\)'s.
 
-If we absorb angle of incidence (formed by the ray of electronic wave and the normal line)
-\((d/\lambda) \sin \tilde{\theta}_l\)
 Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.
 
-\myCount
-\textbf{Definition.} Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
+\Result
+{Definition.}
+{
+Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
 We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
 \begin{gather}
-\mathbf{u} =F \mathbf{v}
+\mathbf{u} =\dagger F \mathbf{v}
 \end{gather}
-where each entry of the matrix \(F\) is defined to be
+where each entry of the matrix \(K\) is defined to be
 \begin{gather}
-F_{m,n} =e^{2\pi ikm/N},
+   K(m,n) =\frac{1}{\sqrt{N}} e^{2\pi imn/N},
 \quad m,n =0,1,2,\dotsc, N-1
 \end{gather}
+where \(i =\sqrt{-1}\).
+}
+
+\subsection{System Model}
+
+We consider the situation with a hybrid structure at both transmitter and receiver end.
+Each end consists of both digital and analog percoders and combiners.
+In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
+Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
+Recall that analog precoder is restricted to have value with magnitude being unity.
+To set up notation, we list them as below.
+\begin{gather}
+F_B \in \mathbb{R}^{N_r \cdot N_s} \\
+F_R \in \mathbb{R}^{N_h \cdot N_r}, |F_R(i,j)| =1 \\
+F_B \in \mathbb{R}^{N_r \cdot N_h} \\
+F_B \in \mathbb{R}^{N_s \cdot N_r}, |F_R(i,j)| =1.
+\end{gather}
+And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
+Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.
 
@@
 \begin{gather}
-Y (\omega_h, \omega_z)
+U (\omega_h, \omega_e)
 :=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
@@
 
-The effective channel \(Y\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
-This way, we may denote the acquired effective channel matrix \(Y\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
+The effective channel \(U\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
+This way, we may denote the acquired effective channel matrix \(U\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
 \begin{gather}
@@
 \end{gather}
-The crux of the matter is the recovery of \(H\) with knowledge of \(Y\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
+The crux of the matter is the recovery of \(H\) with knowledge of \(U\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
 
-as sparse recovery problem of \(\mathrm{vec}(H)\).
-But that suffers the problem of grid quantization, and 
-On the other hand, the author argues in favor of DS, since it is provably ideal in certain senses, guaranteed even under noisy condition,
-So why do we not simply formulate the recovery of \(H\) as a DS program?
-DS is an \(\ell_1\)-minimization problem, and, since it is well known to be convex, it is no less tractable than OMP.
+Following previous work on CSS, we write
+\begin{gather}
+h := \mathrm{vec}(H) \\
+u := \mathrm{vec}(U) \\
+A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
+\end{gather}
+to formulate our goal as sparse recovery problem of \(\mathrm{vec}(H)\).
+But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
+What shall we do?
 
-In addition, observe that, if we write
+Observe that, if we write
 \begin{gather}
@@
 If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
+To the best of our knowledge, no work has explicitly considered the beamspace CSS.
 
@@
 \mathrm{vec}(Y)
-\approx \big[ (K F_R^\dagger F_B^\dagger) \otimes (W_B W_R) \big] \mathrm{vec}(H)
+\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \mathrm{vec}(H)
+\end{gather}
+To simplify notation, set 
+\begin{gather}
+P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
+\end{gather}
+The instances of \(P\) is completely determined in the transmitter and receiver end, that is
+\begin{gather}
+P =P(\omega_t, \omega_r)
 \end{gather}
@@
 
-\myCount
-\textbf{Program}.
+\Result
+{Program}
+{
 Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
-Suppose \(Y\) is the acquired effective channel matrix under noisy observation.
-Set the beamspace vector representation of \(H\) to be
+Suppose \(U\) is the acquired effective channel matrix under noisy observation.
+\(A\) is defined just above in ().
+Set
 \begin{gather}
-h := \mathrm{vec}(H) \\
-\tilde{y} := \mathrm{vec}(Y) \\
-A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
-\end{gather}
-and set
-\begin{gather}
-r =\tilde{y} -A h
+r =u -P h
 \end{gather}
@@
 \begin{gather}
-\hat{\tilde{g}}
+\hat{g}
 =\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
@@
 \end{gather}
-And convert \(\hat{\tilde{g}}\) back to the space domain as
+And convert \(\hat{g}\) back to the space domain as
 \begin{gather}
 \hat{h}
-=K^\dagger \hat{\tilde{g}}.
+=K^\dagger \hat{g}.
 \end{gather}
@@
 \end{gather}
+}
 
-It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as below.
+It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
 
@@
 
-\myCount
-\textbf{Lemma.} Let \(\phi(\omega_3)\) be a uniformly distributed in \([0,2\pi)\) according to probability space index \(\omega_3 \in \Omega\).
-And the function \(\mathbf{a}(\phi)\) is defined as in \eqref{}.
-Then the discrete Fourier transform
+We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
+The sparse vector to be recovered of our investigation is \(g \in \mathbb{R}^{N_H^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
 
-To find the \(l\)-th path's contribution to the frequency domain, recall the identity
+We first establish a technical lemma that shows \(\mathrm{supp}(g)\) has roughly cardinal \(L\).
+At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
+
+Consider
+\begin{gather}
+d =g -\hat{g}
+\end{gather}
+And let
+\begin{itemize}
+\item \(\mathcal{A}\) be the largest \(L\) position of \(g\).
+\item \(\mathcal{B}\) be the largest \(L\) position of \(d\) except on \(\mathcal{A}\).
+\item \(\mathcal{C} =\{1, \dotsc, N_H^2\} -( \mathcal{B} \cup \mathcal{C} )\), i.e., the complementary index set.
+\end{itemize}
+So \(\mathcal{A}, \mathcal{B}, \mathcal{C}\) are mutually exclusive index sets by construction:
+\begin{gather}
+\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \{1, \dotsc, N_H^2\} \\
+\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\
+A \cup B \cup C =\{1, \dotsc, N\}.
+\end{gather}
+
+\Result
+{Lemma.}
+{
+Let \(\phi(\omega_h)\) and \(\theta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
+\begin{gather}
+\|g\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
+\end{gather}
+
+To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
 \begin{align}
@@
 :=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
-=&\left| \frac{e^{i N \phi} -1}{e^{i \phi} -1} \right| \\ \notag
-=&\left| \frac{e^{i N \phi/2} -e^{-i N \phi/2}}{e^{i \phi /2} -e^{-i \phi /2}} \cdot e^{i (N-1) \phi/2} \right| \\ \notag
 =&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
@@
 The second term in the bracket is smaller than 0 and is dropped in the last inequality.
+}
+
 The bound is satisfying enough, though refinement is surely possible.
@@
 
-%A =\mathrm{supp} \beta
+The rest follows ``The Dantzig Selector'' very closely.
 
-where
-\begin{gather}
-\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \mathbb{N} \\ \notag
-\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\ \notag
-A \cup B \cup C =\{1, \dotsc, N\}.
-\end{gather}
-
-\textbf{Proposition}.
-Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in \eqref{}.
+\Result
+{Proposition}
+{
+Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in ().
 Then
 \begin{align}
-\|h_A\|_1 -\|\eta_A\|_1 +\|\eta_C\|_1 -\|h_C\|_1
-\leq& \|h +\eta\|_1 \\ \notag
-\leq& \|h\|_1
+\|d_{BC}\|_1
+\leq \|d_A\|_1 +\|g_{BC}\|_1
 \end{align}
-
-\textbf{Proof}.
-
+}
+To show this, observe
 \begin{align}
-\|X^\dagger_{AB} X \eta\|_\infty
-<&\|X^\dagger X \eta\|_\infty \\ \notag
-\leq& 2 \lambda_p
+\|g\|_1 -\|d_A\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1
+\leq& \|g +d\|_1 \\ \notag
+\leq& \|g\|_1
 \end{align}
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation.
+In the first line, we recall \(g =g_A\).
 
@@
 \begin{align}
-\|\eta_Ah\|_2
-\leq K_1 \|X^\dagger_{AB} X \eta\|_2 +K_2 \|\eta_C\|_2
+|\langle e, P_{:,j} \rangle| \leq \sqrt{2 \log p}
 \end{align}
 }
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation.
 
@@
 \begin{align}
-\|\eta\|_2^2
-\leq \|\eta_{AB}\|_2^2 +K_3 \|\eta_C\|_2^2
+\|P^\dagger P d\|_\infty
+\leq& 2 \sqrt{2 \log p}.
 \end{align}
 }
+To show this, start with
+\begin{align}
+\langle e -r, P_{:,j} \rangle
+=\langle P \hat{g} -P g, P_{:,j} \rangle
+=\langle P g, P_{:,j} \rangle
+\end{align}
+Result follows from triangle inequality, and Lemma ().
+
+From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
+
+\Result
+{Lemma}
+{
+\begin{align}
+\|d_A\|_2
+\leq \frac{1}{1-\delta} \|P^\dagger_{AB} P \eta\|_2 +\frac{\theta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
+\end{align}
+}
+
+From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
+
+\Result
+{Lemma}
+{
+\begin{align}
+\|d\|_2^2
+\leq \|d_{AB}\|_2^2 +\frac{1}{L} \|d_C\|_1^2
+\end{align}
+}
+
+We can formulate our main theorem:
+
+(To be done)
 

### 2019-01-01 ongoing/report/article.tex
Express as SOCP

@@
 \usepackage[ocgcolorlinks]{ocgx2}
+\usepackage{stackengine}
 
@@
 \title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
+
+\newcommand{\MB}[1]{\mathbb{#1}}
+\newcommand{\MC}[1]{\mathcal{#1}}
+\newcommand{\MF}[1]{\mathfrak{#1}}
+\newcommand{\RM}[1]{\mathrm{#1}}
+\newcommand{\T}[1]{\tilde{#1}}
+\newcommand{\V}[1]{\stackunder[1.2pt]{$#1$}{\rule{.9ex}{.075ex}}}
+\newcommand{\M}[1]{\V{\V{#1}}}
+
+\newcommand{\LA}{\langle}
+\newcommand{\RA}{\rangle}
 
@@
 
-We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
-Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.
+We restrict our discussion to the Hilbert space over the field of \(\MB{R}\) or \(\MB{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
+We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
+Lower case Latin alphabets with single underline, like \(\V{a}\), denote vectors, and upper case Latin alphabets with double underlines, like \(\M{A}\), denote matrices.
+To avoid being too pedantic, we simply write \(\V{a} \in \MB{C}^N\) to stress \(\V{a}\) is a \(N\)-dimensional vector, and the role it plays in the vector space is understood.
+Similarly, we also write \(\V{A} \in \MB{M}(M,N)\) to stress \(\V{A}\) is a \(M\) by \(N\) matrix, and the role it plays as linear transformation is understood.
+Inner product is denoted as \(\LA \MB{a}, \MB{b} \RA\).
+Slightly abusing notation, denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
+Especially, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).
 
-Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
-Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
+\(|a|\) denotes the magnitude for real or complex numbers.
+\(\|\V{a}\|_p\) denotes the \(\ell_\infty\)-norm of \(\V{a}\).
+Recall that \(\ell_\infty\)-norm is the maximum-magnitude norm.
+The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(\MF{Re}(a) +i \MF{Im}(a)\)
+
+Denote as \(\MB{P}(X)\) the probability, \(\MB{E}(X)\) the expectation, \(\MB{Var}(X)\) the variance.
+Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\MB{P}\) and \(\MB{E}\).
 
@@
 The figure of merit of a MIMO system is usually considered to be the channel capacity.
-The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
+The capacity \(C\) of a MIMO channel \(\M{H}\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\RM{SNR})\).
 But that knowledge is hardly always available.
-What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
+What makes things more difficult is the case that \(\M{H}\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
 It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
 Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
+Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\RM{SNR})\).
 
-Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
-Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
+Therefore the real-time estimation, \(\hat{\M{H}}\), of \(\M{H}\) is of paramount importance.
+Needless to say, when the \(\hat{\M{H}}\) is imprecise, resulting analysis is also undermined.
 With more antennae present, conventional training-based algorithm also increase in complexity and storage.
@@
 {
-\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
+\(x \in \MB{K}^N\) is called \(s\)-sparse, if
 \begin{gather} 
-\# \{\mathrm{supp}(x)\} \leq s
+\# \{\RM{supp}(x)\} \leq s
 \end{gather}
@@
 \begin{gather}
-\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
-\mathrm{s.t.} \quad Ax =y
+\RM{min}_{x' \in \MB{R}^K} \quad \|x'\|_1
+\RM{s.t.} \quad Ax =y
 \end{gather}
@@
 {
-Let \(T \subset \mathbb{N}\).
+Let \(T \subset \MB{N}\).
 Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
@@
 Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
-For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
+For each integer \(S \in \MB{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\vartheta\) with \(\|\vartheta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
 \begin{gather}
-(1-\delta_S) \|\theta\|^2
-\leq \|X_T \theta\|_2^2
-\leq (1+\delta_S) \|\theta\|^2
+(1-\delta_S) \|\vartheta\|^2
+\leq \|X_T \vartheta\|_2^2
+\leq (1+\delta_S) \|\vartheta\|^2
 \end{gather}
@@
 
-RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).
+RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\vartheta_S\).
 
-Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
+Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
 \begin{gather}
-| \langle X_T c, X_{T'} c' \rangle |
-\leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
+| \LA X_T c, X_{T'} c' \RA |
+\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
 \end{gather}
@@
 \begin{gather}
-\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
+\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \notag
+\RM{subject}\; \RM{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
 \end{gather}
@@
 {
-Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
+Let each entry of random matrix \(A \in \MB{V}(M \cdot N)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
 Then, with \(0 <\epsilon <1\),
 \begin{gather}
-   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
+   \MB{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
    \leq 2 \exp(-n c_0(\epsilon))
@@
 To explain the idea, consider a simplified scenario.
-Let \(x[t] \in \mathbb{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
+Let \(x[t] \in \MB{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
 Consider a linear time-invariant channel with
@@
 \end{gather}
-where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
+where \(h[t] \in \MB{R}^L\) is the channel's impulse response, \(x[t] \in \MB{R}^N\) as the input, \(y[t] \in \MB{R}^N\) as the output, and \(z[t] \in \MB{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
 Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
@@
 The setting here is \(y =Ax\), the noiseless, real-number case.
-Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
+Same as before, let \(y \in \MB{V}(M)\), \(x \in \MB{V}(N)\) which is \(s\)-sparse, while \(M \ll N\).
 We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).
@@
 Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
-To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
+To see this, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
 Let signal \(x\) be sent, and \(y\) be receiverd, that is
 \begin{gather}
-y =WHF x
+   \V{y} =\M{W} \M{H} \M{F} \V{x}
 \end{gather}
@@
 {
-Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
+Define \(\RM{vec}(\M{A}) \in \MB{K}^{nm}\) to be the vectorization of \(\M{A} \in \MB{M}(n,m)\).
 }
@@
 {
-For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
-Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
+For \(\RM{vec}(A) \in \MB{M}(n,m)\) and \(\RM{vec}(A) \in \MB{M}(n,m)\)
+Define the Kronecker product \(\RM{vec}(A) \in \MB{K}^{nm}\) 
 }
@@
 \begin{gather}
-\mathrm{vec}(Y)
-=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
+\RM{vec}(Y)
+=\big[ (F^\dagger) \otimes W \big] \RM{vec}(\M{H})
 \end{gather}
@@
 \begin{gather}
-\mathbf{a}(\phi')
-=\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
+\V{a}(\varphi')
+=\sum_{n=1}^{N} \RM{e}^{n \varphi' i} \V{u}_n
 \end{gather}
-where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.
+where \(i\) is the imaginary unit, \(\V{u}_n\) is the unit vector of the \(n\)-th component.
 
@@
 H
-=\sum_{l=0}^L \alpha_l \mathbf{a}\big( \frac{d}{\lambda} \sin \phi_l' \big) \mathbf{a}\big( \frac{d}{\lambda} \sin \theta_l' \big)^\dagger
+=\sum_{l=0}^L \alpha_l \V{a}\big( \frac{d}{\lambda} \sin \varphi_l' \big) \V{a}\big( \frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l' \big)^\dagger
 \end{gather}
-The physical meaning of \(\theta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\theta_l\), the \(l\)-th that of arrival wave.
-
-For our purpose, we may absorb the argument of \(\mathbf{a}\) as
+The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
+For our purpose, we may absorb the argument of \(\V{a}\) as
 \begin{gather}
-\phi_l
-=\frac{d}{\lambda} \sin \phi_l' \\
-\theta_l
-=\frac{d}{\lambda} \sin \theta_l'
+\varphi_l
+=\frac{d_{\RM{arr}}}{\lambda} \sin \varphi_l' \\
+\vartheta_l
+=\frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l'
 \end{gather}
@@
 H
-=\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
+=\sum_{l=0}^L \alpha_l \V{a}(\varphi_l) \V{a}(\vartheta_l)^\dagger
 \end{gather}
-
-Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.
 
@@
 {
-Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
-We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
-\begin{gather}
-\mathbf{u} =\dagger F \mathbf{v}
-\end{gather}
-where each entry of the matrix \(K\) is defined to be
-\begin{gather}
-   K(m,n) =\frac{1}{\sqrt{N}} e^{2\pi imn/N},
-\quad m,n =0,1,2,\dotsc, N-1
-\end{gather}
-where \(i =\sqrt{-1}\).
 }
@@
 Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
-Recall that analog precoder is restricted to have value with magnitude being unity.
 To set up notation, we list them as below.
 \begin{gather}
-F_B \in \mathbb{R}^{N_r \cdot N_s} \\
-F_R \in \mathbb{R}^{N_h \cdot N_r}, |F_R(i,j)| =1 \\
-F_B \in \mathbb{R}^{N_r \cdot N_h} \\
-F_B \in \mathbb{R}^{N_s \cdot N_r}, |F_R(i,j)| =1.
+F_B \in \MB{C}^{N_r \cdot N_y} \\
+F_R \in \MB{C}^{N_h \cdot N_r} \\
+F_B \in \MB{C}^{N_r \cdot N_h} \\
+F_B \in \MB{C}^{N_y \cdot N_r}.
 \end{gather}
+Recall that analog precoder is restricted to have value with magnitude being unity.
+\begin{gather}
+ |F_R(n_1,n_2)| =1, \quad
+ n_1 =1, \dotsc N_h, \quad
+n_2 =1, \dotsc N_r \\
+ |W_R(n_1,n_2)| =1, \quad
+ n_1 =1, \dotsc N_r, \quad
+n_2 =1, \dotsc N_h
+\end{gather}
+
 And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
@@
 \begin{gather}
-U (\omega_h, \omega_e)
-:=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
+Y (\omega_h, \omega_e)
+:=W_B(\omega_r) W_R(\omega_r) ( H(\omega_h) F_R(\omega_t) F_B(\omega_t) +Z(\omega_z) )
 \end{gather}
-Supress the probabilistic index for simplicity, we restate the same equation as
+Supress the event space index for brevity, we restate the same equation as
 \begin{gather}
 Y
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z )
+:=W_B W_R ( H F_R F_B +z )
 \end{gather}
@@
 
-The effective channel \(U\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
-This way, we may denote the acquired effective channel matrix \(U\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
+The effective channel \(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
+This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
 \begin{gather}
-Y_{:,n}
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z ), \quad
-n =1, 2, \dotsc, N_B
+\M{Y}(:,n)
+:=\M{W}_B \M{W}_R ( \M{H} \M{F}_R \M{F}_B \V{u}_m +\V{z} ), \quad
+n =1, 2, \dotsc, N_y
 \end{gather}
-The crux of the matter is the recovery of \(H\) with knowledge of \(U\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
+The crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), and of course \(\M{W}_R, \M{W}_B, \M{F}_R, \M{F}_B\) which are in our control.
 
@@
 \begin{gather}
-h := \mathrm{vec}(H) \\
-u := \mathrm{vec}(U) \\
-A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
+\V{h} := \RM{vec}(\M{H}) \\
+\V{y} := \RM{vec}(\M{Y}) \\
+\M{P}' :=(\M{F}_R \M{F}_B) \otimes (\M{W}_B \M{W}_R)
 \end{gather}
-to formulate our goal as sparse recovery problem of \(\mathrm{vec}(H)\).
+to formulate our goal as sparse recovery problem of \(\RM{vec}(H)\) to be
+\begin{gather}
+\V{y} =\M{P}' \V{h} +\V{z}
+\end{gather}
 But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
@@
 
-Observe that, if we write
+Introduce the discrete Fourier matrix \(K\) defined to be
 \begin{gather}
-G =K^\dagger H
+\M{K} \in \MB{M}(N_h, N_h) \\
+\M{K}(n_1, n_2) =\frac{1}{\sqrt{N}} \RM{e}^{2\pi i n_1 n_2 /N},
+\quad n_1, n_2 =0,1,2,\dotsc, N-1
 \end{gather}
-as the spatial frequency domain representation of \(H\), then
+where \(i =\sqrt{-1}\).
+And observe that, if we write
 \begin{gather}
-Y
-:=W_B W_R K ( G F_R F_B +K^\dagger z ), \quad
-n =1, 2, \dotsc, N_B
+\M{G}
+=\M{K}^\dagger \M{H}
+\end{gather}
+which has the interpretation as the spatial frequency domain representation of \(H\), then
+\begin{gather}
+\M{Y}
+:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{F}_R \M{F}_B +\M{K}^\dagger \M{Z} )
 \end{gather}
@@
 \begin{gather}
-\mathrm{vec}(Y)
-\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \mathrm{vec}(H)
+\RM{vec}(Y)
+\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \RM{vec}(H)
 \end{gather}
@@
 Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
-Suppose \(U\) is the acquired effective channel matrix under noisy observation.
-\(A\) is defined just above in ().
-Set
-\begin{gather}
-r =u -P h
-\end{gather}
+Suppose \(Y\) is the acquired effective channel matrix under corruption of noise \(z\).
+\(P\) is defined just above in ().
 Then, with parameter \(\gamma\) specified, define the following program
@@
 \hat{g}
-=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
-\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
+=\underset {{h}} {\RM{min}} \|h\|_1 \quad
+\RM{s.t.}\;\; \|P^\dagger (y -P h)\|_\infty \leq \gamma
 \end{gather}
@@
 \hat{h}
-=K^\dagger \hat{g}.
+=K \hat{g}.
 \end{gather}
@@
 \begin{gather}
-\hat{H} =\mathrm{vec}^{-1} (\hat{h})
+\hat{H} =\RM{vec}^{-1} (\hat{h})
 \end{gather}
@@
 
-It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
+It, then, will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
 
@@
 We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \(g \in \mathbb{R}^{N_H^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
+The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_h^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
 
-We first establish a technical lemma that shows \(\mathrm{supp}(g)\) has roughly cardinal \(L\).
+We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\).
 At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
@@
 \begin{itemize}
-\item \(\mathcal{A}\) be the largest \(L\) position of \(g\).
-\item \(\mathcal{B}\) be the largest \(L\) position of \(d\) except on \(\mathcal{A}\).
-\item \(\mathcal{C} =\{1, \dotsc, N_H^2\} -( \mathcal{B} \cup \mathcal{C} )\), i.e., the complementary index set.
+\item \(\MC{A}\) be the largest \(L\) position of \(g\).
+\item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
+\item \(\MC{C} =\{1, \dotsc, N_h^2\} -( \MC{B} \cup \MC{C} )\), i.e., the complementary index set.
 \end{itemize}
-So \(\mathcal{A}, \mathcal{B}, \mathcal{C}\) are mutually exclusive index sets by construction:
+So \(\MC{A}, \MC{B}, \MC{C}\) are mutually exclusive index sets by construction:
 \begin{gather}
-\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \{1, \dotsc, N_H^2\} \\
-\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\
-A \cup B \cup C =\{1, \dotsc, N\}.
+\MC{A}, \MC{B}, \MC{C} \subset \{1, \dotsc, N_h^2\} \\
+   \MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
+\MC{A} \cup \MC{C} \cup \MC{C} =\{1, \dotsc, N\}.
 \end{gather}
@@
 {
-Let \(\phi(\omega_h)\) and \(\theta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
+Let \(\varphi(\omega_h)\) and \(\vartheta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
 \begin{gather}
-\|g\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
+\|g_{\MC{A}}\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
 \end{gather}
+}
 
@@
 \begin{align}
-S(\phi)
-:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
-\quad 0 \leq \phi \leq \pi
+D(\varphi)
+:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi} \right| \\ \notag
+=&\frac{|\sin(N \varphi/2)|}{|\sin(\varphi /2)|},
+\quad 0 \leq \varphi \leq \pi
 \end{align}
-By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
+where \(\RM{e}\) is the base of natural logarithm, and \(i =\sqrt{-1}\).
+
+By taking the first two term of the expansion
 \begin{align}
-S(\phi)
-\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\ \notag
-=& \frac{-48}{\phi^3 -24\phi}
-\quad 0 \leq \phi \leq \pi,
+\sin x =x -x^3/6 + \MC{O}(x^5), \quad x \ll 1
 \end{align}
-
+and noting the monotony of the first two terms,
+\begin{align}
+D(\varphi)
+\leq& \frac{1}{\varphi/2 -(\varphi/2)^3/6} \notag \\
+=& \frac{-48}{\varphi^3 -24\varphi}
+\quad 0 \leq \varphi \leq \pi,
+\end{align}
 The fraction above can be bounded.
@@
 \begin{align}
-&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\ \notag
-=&\frac{1}{N} S(\pi \phi') \\ \notag
-\leq& \frac{48}{N \pi^3 (\phi'^3 -24 \phi' /\pi^2)}
+&\left| \frac{1}{N} \sum_{n=0}^{N-1} \RM{e}^{-2\pi i k n/N} \RM{e}^{i n \varphi} \right| \notag \\
+=&\frac{1}{N} S(\pi \varphi') \notag \\
+\leq& \frac{48}{N \pi^3 (\varphi'^3 -24 \varphi' /\pi^2)}
 \end{align}
-where \(\phi' =k/N -\phi/2\pi\), and the cubic expression is split.
-We wish to bound the tail of \(S(\pi \phi')\), and apply the na\"ive bound
+where \(\varphi' =k/N -\varphi/2\pi\), and the cubic expression is split.
+We wish to bound the tail of \(S(\pi \varphi')\), and apply the na\"ive bound
 \begin{align}
-&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\phi'^3 -24 \phi' /\pi^2}
- d\phi' \\ \notag
-=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\ \notag
+&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\varphi'^3 -24 \varphi' /\pi^2}
+ d\varphi' \notag \\
+=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \notag \\
 \leq& \frac{1}{\pi^2} \log \frac{L}{N}
@@
 The second term in the bracket is smaller than 0 and is dropped in the last inequality.
-}
+The proof of Lemma () is complete.
 
@@
 Indeed, \(\log L/N \to 0\) as \(N \to \infty\) and limited by the number of paths \(L\).
+Intuitively, this says that when there are few paths, but many antennas, we expect the spatial frequency domain of the virtual channel to be sparse too.
 
@@
 {
-Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in ().
+Let \(h \in \MB{R}^n\) and \(\eta \in \MB{R}^p\) are defined as in ().
 Then
@@
 \|d_{BC}\|_1
-\leq \|d_A\|_1 +\|g_{BC}\|_1
+\leq \|d_{\MC{A}}\|_1 +\|g_{BC}\|_1
 \end{align}
 }
+
 To show this, observe
 \begin{align}
-\|g\|_1 -\|d_A\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1
-\leq& \|g +d\|_1 \\ \notag
+&\|g\|_1 -\|d_{\MC{A}}\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1 \\
+\leq& \|g +d\|_1 \notag \\
 \leq& \|g\|_1
 \end{align}
-In the first line, we recall \(g =g_A\).
+In the first line, we recall \(g =g_{\MC{A}}\).
 
@@
 \begin{align}
-|\langle e, P_{:,j} \rangle| \leq \sqrt{2 \log p}
+|\LA e, P_{:,j} \RA| \leq \sqrt{2 \log p}
 \end{align}
@@
 }
+
 To show this, start with
 \begin{align}
-\langle e -r, P_{:,j} \rangle
-=\langle P \hat{g} -P g, P_{:,j} \rangle
-=\langle P g, P_{:,j} \rangle
+\LA e -r, P_{:,j} \RA
+=\LA P \hat{g} -P g, P_{:,j} \RA
+=\LA P g, P_{:,j} \RA
 \end{align}
@@
 From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
+The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
+Of course the interpretation of modulus and the inner product changes accordingly.
 
@@
 \begin{align}
-\|d_A\|_2
-\leq \frac{1}{1-\delta} \|P^\dagger_{AB} P \eta\|_2 +\frac{\theta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
+\|d_{\MC{A}}\|_2
+\leq \frac{1}{1-\delta} \|P^\dagger_{\MC{A}\MC{B}} P \eta\|_2 +\frac{\vartheta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
 \end{align}
@@
 From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
+Again, their proof works with complex vector spaces in place of real ones.
 
@@
 \|d\|_2^2
-\leq \|d_{AB}\|_2^2 +\frac{1}{L} \|d_C\|_1^2
+\leq \|d_{\MC{A}\MC{B}}\|_2^2 +\frac{1}{L} \|d_{\MC{C}}\|_1^2
 \end{align}
@@
 
-We can formulate our main theorem:
+We can formulate our main theorem.
 
@@
 
-As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\mathcal{R}(h)\).
+As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\MC{R}(h)\).
 But it is not the end.
@@
 
-Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem.
-Recapitulate that, as we explained in the above, DS involves a 
-We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
+Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem, as follows.
+Recapitulate that, as we explained in the above, DS involves the calculation of \(\ell_1\)-1 norm.
+This, for real vectors, can be transformed into a linear program (LP).
+But in the complex case, that becomes a quadratic expression of the real and imaginary part of the vector, and is no longer equivalent to an LP.
+Still, the comparison arising from primal-dual problem is not easily done in complex numbers, and we cast it into a real \(\ell_1\)-1 norm problem.
+Afterwards we will further transform the SOCP to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
+The bound in the previous section is valid, since in the course of transformation, nothing is lost or weakened.
 
-% % % % % % % % % % % % % % % %
+For convenience, define the following function that maps a complex vector to the real representation of it.
+
+\Result
+{Definition}
+{
+For \(x \in \MB{R}^N\), We say \(\MC{R}(x) \in \MB{V}(2N)\) is the real representation of \(x\), defined by
+\begin{gather}
+x \in \MB{V}(2N^2) \notag \\
+x(n) =
+\begin{cases}
+\MF{Re}(x(n)), &n =2n' \\
+\MF{Im}(x(n)), &n =2n'+1
+\end{cases} \\
+n' =1, \dotsc, N \notag
+\end{gather}
+}
+
+A moment's reflection shows the following definition of real representation of matrices.
+
+\Result
+{Definition}
+{
+For \(A \in \MB{M}(N_1,N_2)\), We say \(\MC{R}(A) \in \MB{M}(2N_1,2N_2)\) is the real representation of \(A\), defined by
+\begin{gather}
+A \in \MB{V}(2N^2) \notag \\
+A(n_1,n_2) =
+\begin{cases}
+\MF{Re}(A(n_1,n_2)), &n_1 =2n_1'-1,\; n_2 =2n_2'-1  \\
+\MF{Im}(A(n_1,n_2)), &n_1 =2n_1',\; n_2 =2n_2'-1  \\
+-\MF{Im}(A(n_1,n_2)), &n_1 =2n_1'-1,\; n_2 =2n_2'  \\
+\MF{Re}(A(n_1,n_2)), &n_1 =2n_1',\; n_2 =2n_2'  \\
+\end{cases} \\
+n_1' = 1, \dotsc, N_1 \notag \\
+n_2' = 1, \dotsc, N_2 \notag
+\end{gather}
+}
+
+We continue the notation of program ().
+
+\begin{gather}
+\V{\T{y}}
+=\MC{R}(y) \in \MB{V}(N_h) \\
+\V{\T{g}}
+=\MC{R}(g) \in \MB{V}(N_h) \\
+\M{\T{P}}
+=\MC{R}(\M{P}) \in \MB{M}(2 N_y^2, 2 N_h^2)
+\end{gather}
+such that
+\begin{gather}
+\V{\T{y}} =\M{\T{P}} \V{\T{g}} +\V{\T{z}}
+\end{gather}
+where by construction
+\begin{gather}
+\V{\T{z}}
+=\MC{R}(\V{z}) \in \MB{V}(N_y)
+\end{gather}
+
+Finally, introduce these indicator matrices to identify the place where we want to take \(\ell_2\)-norm.
+
+\begin{gather}
+I_{n_y}^{(y)} \in \MB{M}(N_y, N_y) \\
+I_{n_y}^{(y)}(n_y')
+=\begin{cases}
+1, &n_y' =2n_y \quad \RM{or} \quad n_y' =2n_y+1 \notag \\
+0, &\RM{otherwise}
+\end{cases} \\
+n_h =1, \dotsc, N_h \notag \\
+I_{n_h}^{(h)} \in \MB{M}(N_h, N_h) \\
+I_{n_h}^{(h)}(n_h')
+=\begin{cases}
+1, &n_h' =2n_h \quad \RM{or} \quad n_h' =2n_h+1 \notag \\
+0, &\RM{otherwise}
+\end{cases} \\
+n_h =1, \dotsc, N_h \notag
+\end{gather}
+
+If we introduce vector \(\V{m}\) to denote the entrywise complex modulus, we see that Program () now take the form
+
+\Result
+{Program}
+{
+Given are \(\T{P}, \T{y}, \gamma\).
+Find \(\T{g}\) with
+\begin{gather}
+   \min_{\T{g}, \V{m}} \LA \V{1}, \V{m} \RA \notag \\
+\RM{s.t.}
+\begin{cases}
+\| I_{n_h}^{(h)} \T{g} \|_2
+   \leq \LA \V{y}_{n_h}, \V{m} \RA \\
+\| I_{n_y}^{(y)} \T{P}^\dagger ( \T{P} \T{g} - \T{y} ) \|_2
+\leq \gamma  \\
+\end{cases}
+\end{gather}
+where \(\V{1}\) is the all-1 vector.
+}
+
+which is an SOCP.
+
+We further rewrite Program () into a stricter, extended block matrix form to make the point clearer.
+
+\subsection{Primal-Dual Interior Point Algorithm}
+
+It remains to convert primal-dual interior point algorithm to make the SOCP easier to calculate.
+Of course it is not the only way to do this.
+We mention, again, Boyd and Vandenberghe (2004), \textit{Convex Optimization} chap.11 as a standard reference, and ``\(\ell_1\)-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.
+
+To clarify notation and for complentess of exposition, we derive the dual problem here.
+Start with the Lagrangian \(\MC{L}\), where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \(\ell_2\)-norm constraint.
+
+\begin{align}
+   &\MC{L}(\V{m}, \T{g}, \mu^{(h)}, \mu^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \notag \\
+=& \LA \V{1}, m \RA 
+   +\sum_{n_h} \big[ \LA \mu^{(h)}, I_{n_h}^{(h)} \T{g} \RA -\lambda^{(h)} \LA \V{y}_{n_h}, \V{m} \RA \big] \notag \\
+\quad & +\sum_{n_y} \big[ \LA \mu^{(h)}, I_{n_y}^{(y)} \T{P}^\dagger ( \T{P} \T{g} -\T{u} ) \RA -\lambda^{(h)} \gamma \big]
+\end{align}
 
@@
 
-Firstly,
-Meanwhile, DS goes not without criticism for large complexity.
-Indeed it is clear, even from the primal-dual implementation above, that DS requires large dimensional vector
+This article applies DS rather than OMP, like many of previous work, as the algorithm via which we estimate the millimeter wave channel.
 
-Secondly
-And comparison of bounds of OMP and DS
-The author criticises the tendency of current literature to mix up results for DS and OMP without clear justification, since they are two quite different approaches to the compressed sensing problem.
-It is however not trivial to make meaningful comparison, since DS works with a RIP matrix, and OMP for Gaussian... the distinction is slight but definite...
-The author critizises In OMP we don't know whether the measurement matrix is the same as channel
-And OMP has stricter condition than DS
-Tao, however, specifies a noise relation
+We should keep in mind that DS goes not without criticism for large complexity of it (Friedlander and Saunders 2007).
+Indeed it is clear, even from the primal-dual implementation above, that DS requires memory for large dimensional vector, but OMP does not.
 
-Bounds of performance in different setting are often nontrivial to obtain, and one cannot think OMP, or indeed every algorithm, as a universal solution.
-OMP trades off precision for time complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
-All in all, different problems requires different technique and algorihm within the constraint at hand, as is probably true in every discipline of engineering.
+And a meaningful comparison of bounds of OMP and DS is not easy, as their settings are somewhat different.
+The author thus criticises the tendency of current literature to mix up results for DS and OMP without clear justification.
+It is however not trivial to make meaningful comparison, since their setting is different.
+Indeed, the distinction is slight but definite.
+DS calls for a RIP matrix and guarantees such performance even in noisy observation (Cand\`es and Tao 2005, 2007), while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
+On the other hand, as of OMP, besides the original justification of entrywise i.i.d.\ Gaussian sensing matrix (Tropp and Gilbert 2007a), and existent attempt to characterize MIP condition, there is much to be done OMP for Gaussian.
+
+Since, as we have seen, bounds of performance in different setting are often nontrivial to obtain, and one cannot think OMP, or indeed every algorithm, as a universal solution.
+OMP trades off precision for time and space complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
+All in all, different problems requires different technique and algorihm within the current constraint, as is probably true in every discipline of engineering.
 

### 2019-01-03 ongoing/report/article.tex
Use underscore for matrices & vectors; Ready to reduce length of survey

@@
 \date{\today}
+
 \title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
@@
 \newcommand{\RM}[1]{\mathrm{#1}}
-\newcommand{\T}[1]{\tilde{#1}}
 \newcommand{\V}[1]{\stackunder[1.2pt]{$#1$}{\rule{.9ex}{.075ex}}}
 \newcommand{\M}[1]{\V{\V{#1}}}
+\newcommand{\T}[1]{\tilde{#1}}
+\newcommand{\IP}[1]{\langle #1 \rangle}
 
-\newcommand{\LA}{\langle}
-\newcommand{\RA}{\rangle}
+\renewcommand{\H}{\dagger}
 
@@
 Similarly, we also write \(\V{A} \in \MB{M}(M,N)\) to stress \(\V{A}\) is a \(M\) by \(N\) matrix, and the role it plays as linear transformation is understood.
-Inner product is denoted as \(\LA \MB{a}, \MB{b} \RA\).
+Inner product is denoted as \(\IP{ \MB{a}, \MB{b} }\).
 Slightly abusing notation, denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
@@
 \begin{gather} 
-\# \{\RM{supp}(x)\} \leq s
+\# \RM{supp}(x) \leq s
 \end{gather}
@@
 \begin{gather}
-\RM{min}_{x' \in \MB{R}^K} \quad \|x'\|_1
-\RM{s.t.} \quad Ax =y
+\RM{min}_{x' \in \MB{R}^K}
+\quad \|x'\|_1
+\quad \RM{s.t.} \quad A x' =y
 \end{gather}
@@
 \Result
-{Notation}
-{
-Let \(T \subset \MB{N}\).
-Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
-}
-
-\Result
 {Definition}.
 {
-Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
-For each integer \(S \in \MB{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\vartheta\) with \(\|\vartheta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
+Let \(A\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
+For each integer \(S \in \MB{N}\), we say that \(A\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
 \begin{gather}
-(1-\delta_S) \|\vartheta\|^2
-\leq \|X_T \vartheta\|_2^2
-\leq (1+\delta_S) \|\vartheta\|^2
+(1-\delta_S) \|x\|^2
+\leq \|A_T x\|_2^2
+\leq (1+\delta_S) \|x\|^2
 \end{gather}
@@
 
-RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\vartheta_S\).
+RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\delta_S\).
 
@@
 \begin{gather}
-| \LA X_T c, X_{T'} c' \RA |
+| \IP{ X_T c, X_{T'} c' } |
 \leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
@@
 \min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \notag
-\RM{subject}\; \RM{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
+\RM{subject}\; \RM{to} \quad \|A^\H r\|_\infty \leq \lambda_p \sigma
 \end{gather}
@@
 \RM{vec}(Y)
-=\big[ (F^\dagger) \otimes W \big] \RM{vec}(\M{H})
+=\big[ (F^\H) \otimes W \big] \RM{vec}(\M{H})
 \end{gather}
@@
 Since expression involving probability will get very complecated, introduce the direct product
-%
 \begin{gather}
@@
 \end{gather}
-%
 to denote the overall sample space, where
-%
+
 \begin{itemize}
@@
 \begin{gather}
-\V{a}(\varphi')
-=\sum_{n=1}^{N} \RM{e}^{n \varphi' i} \V{u}_n
+\V{a} \in \MB{V}(N_h) \\
+\V{a}(\psi')
+=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
 \end{gather}
@@
 H
-=\sum_{l=0}^L \alpha_l \V{a}\big( \frac{d}{\lambda} \sin \varphi_l' \big) \V{a}\big( \frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l' \big)^\dagger
+=\sum_{l=0}^L \alpha_l \V{a}\big( \frac{d}{\lambda} \sin \varphi_l' \big) \V{a}\big( \frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l' \big)^\H
 \end{gather}
@@
 H
-=\sum_{l=0}^L \alpha_l \V{a}(\varphi_l) \V{a}(\vartheta_l)^\dagger
+=\sum_{l=0}^L \alpha_l \V{a}(\varphi_l) \V{a}(\vartheta_l)^\H
 \end{gather}
@@
 \M{Y}(:,n)
-:=\M{W}_B \M{W}_R ( \M{H} \M{F}_R \M{F}_B \V{u}_m +\V{z} ), \quad
-n =1, 2, \dotsc, N_y
+:=\M{W}_B \M{W}_R ( \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} ), \quad
+n_y =1, 2, \dotsc, N_y
 \end{gather}
@@
 
-Introduce the discrete Fourier matrix \(K\) defined to be
+Introduce the discrete Fourier matrix \(\M{K}\) defined to be
 \begin{gather}
@@
 \M{G}
-=\M{K}^\dagger \M{H}
+=\M{K}^\H \M{H}
 \end{gather}
-which has the interpretation as the spatial frequency domain representation of \(H\), then
+which has the interpretation as the spatial frequency domain representation of \(\M{H}\), then
 \begin{gather}
 \M{Y}
-:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{F}_R \M{F}_B +\M{K}^\dagger \M{Z} )
+:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
 \end{gather}
-If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
+If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.
 To the best of our knowledge, no work has explicitly considered the beamspace CSS.
 
-That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
+That is to say, \(\M{K}^\H \V{z}\) may be absorbed, and a similar Kronecker product may be used.
 \begin{gather}
-\RM{vec}(Y)
-\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \RM{vec}(H)
+\RM{vec}(\M{Y})
+\approx \big[ (\M{F}_B^\H \M{F}_R^\H) \otimes (\M{W}_B \M{W}_R \M{K}) \big] \RM{vec}(\M{H})
 \end{gather}
@@
 \begin{gather}
-P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
+\M{P} =(\M{F}_B^\H \M{F}_R^\H) \otimes (\M{W}_B \M{W}_R \M{K})
 \end{gather}
-The instances of \(P\) is completely determined in the transmitter and receiver end, that is
+The instances of \(\M{P}\) is completely determined in the transmitter and receiver end, that is
 \begin{gather}
-P =P(\omega_t, \omega_r)
+\M{P} =\M{P}(\omega_t, \omega_r)
 \end{gather}
@@
 {
-Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
-Suppose \(Y\) is the acquired effective channel matrix under corruption of noise \(z\).
-\(P\) is defined just above in ().
+Let \(\M{H}(\omega_h, \omega_n)\) be the virtual channel, and \(\M{W}_R(\omega_r)\) the random analog combiner, \(\M{W}_B(\omega_r)\) the random analog combiner, \(\M{F}_R(\omega_t)\) the random analog combiner, \(\M{F}_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
+Suppose \(\M{Y}\) is the acquired effective channel matrix under corruption of noise \(\V{z}\).
+\(\M{P}\) is defined just above in ().
 Then, with parameter \(\gamma\) specified, define the following program
 \begin{gather}
-\hat{g}
-=\underset {{h}} {\RM{min}} \|h\|_1 \quad
-\RM{s.t.}\;\; \|P^\dagger (y -P h)\|_\infty \leq \gamma
+\hat{\V{g}}
+=\underset {\V{h}} {\RM{min}} \|\V{h}\|_1 \quad
+\RM{s.t.}\quad \|P^\H (y -P h)\|_\infty \leq \gamma
 \end{gather}
@@
 \MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
-\MC{A} \cup \MC{C} \cup \MC{C} =\{1, \dotsc, N\}.
+\MC{A} \cup \MC{B} \cup \MC{C} =\{1, \dotsc, N\}.
 \end{gather}
@@
 \Result
-{Lemma.}
+{Notation}
+{
+Let \(T \subset \MB{N}\).
+Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
+}
+
+\Result
+{Lemma}
 {
@@
 \begin{align}
-|\LA e, P_{:,j} \RA| \leq \sqrt{2 \log p}
+|\IP{ e, P_{:,j} }| \leq \sqrt{2 \log p}
 \end{align}
@@
 \begin{align}
-\|P^\dagger P d\|_\infty
+\|P^\H P d\|_\infty
 \leq& 2 \sqrt{2 \log p}.
@@
 \begin{align}
-\LA e -r, P_{:,j} \RA
-=\LA P \hat{g} -P g, P_{:,j} \RA
-=\LA P g, P_{:,j} \RA
+\IP{ z -(y -P h), P(:,n_y) }
+=\IP{ P \hat{g} -P g, P(:,n_y) }
+=\IP{ P g, P(:,n_y) }
 \end{align}
@@
 
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
+From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result as below.
 The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
@@
 \|d_{\MC{A}}\|_2
-\leq \frac{1}{1-\delta} \|P^\dagger_{\MC{A}\MC{B}} P \eta\|_2 +\frac{\vartheta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
+\leq \frac{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P \eta\|_2 +\frac{\vartheta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
 \end{align}
@@
 
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
-Again, their proof works with complex vector spaces in place of real ones.
+From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result as below.
+Again, their proof works with complex vector spaces in place of real ones too.
 
@@
 {
-For \(x \in \MB{R}^N\), We say \(\MC{R}(x) \in \MB{V}(2N)\) is the real representation of \(x\), defined by
+For \(x \in \MB{V}(M)\), We say \(\MC{R}(x) \in \MB{V}(2M)\) is the real representation of \(x\), defined by
 \begin{gather}
-x \in \MB{V}(2N^2) \notag \\
-x(n) =
+x \in \MB{V}(2M^2) \notag \\
+x(m) =
 \begin{cases}
-\MF{Re}(x(n)), &n =2n' \\
-\MF{Im}(x(n)), &n =2n'+1
+\MF{Re}(x(m)), &m =2m' \\
+\MF{Im}(x(m)), &m =2m'+1
 \end{cases} \\
-n' =1, \dotsc, N \notag
+m' =1, \dotsc, M \notag
 \end{gather}
@@
 {
-For \(A \in \MB{M}(N_1,N_2)\), We say \(\MC{R}(A) \in \MB{M}(2N_1,2N_2)\) is the real representation of \(A\), defined by
+For \(A \in \MB{M}(m_1,m_2)\), We say \(\MC{R}(A) \in \MB{M}(2m_1,2m_2)\) is the real representation of \(A\), defined by
 \begin{gather}
-A \in \MB{V}(2N^2) \notag \\
-A(n_1,n_2) =
+A \in \MB{V}(2M^2) \notag \\
+A(m_1,m_2) =
 \begin{cases}
-\MF{Re}(A(n_1,n_2)), &n_1 =2n_1'-1,\; n_2 =2n_2'-1  \\
-\MF{Im}(A(n_1,n_2)), &n_1 =2n_1',\; n_2 =2n_2'-1  \\
--\MF{Im}(A(n_1,n_2)), &n_1 =2n_1'-1,\; n_2 =2n_2'  \\
-\MF{Re}(A(n_1,n_2)), &n_1 =2n_1',\; n_2 =2n_2'  \\
+\MF{Re}(A(m_1,m_2)), &m_1 =2m_1'-1,\; m_2 =2m_2'-1  \\
+\MF{Im}(A(m_1,m_2)), &m_1 =2m_1',\; m_2 =2m_2'-1  \\
+-\MF{Im}(A(m_1,m_2)), &m_1 =2m_1'-1,\; m_2 =2m_2'  \\
+\MF{Re}(A(m_1,m_2)), &m_1 =2m_1',\; m_2 =2m_2'  \\
 \end{cases} \\
-n_1' = 1, \dotsc, N_1 \notag \\
-n_2' = 1, \dotsc, N_2 \notag
+m_1' = 1, \dotsc, m_1 \notag \\
+m_2' = 1, \dotsc, m_2 \notag
 \end{gather}
@@
 \begin{gather}
-   \min_{\T{g}, \V{m}} \LA \V{1}, \V{m} \RA \notag \\
+   \min_{\T{g}, \V{m}} \IP{ \V{1}, \V{m} } \notag \\
 \RM{s.t.}
@@
 \| I_{n_h}^{(h)} \T{g} \|_2
-   \leq \LA \V{y}_{n_h}, \V{m} \RA \\
-\| I_{n_y}^{(y)} \T{P}^\dagger ( \T{P} \T{g} - \T{y} ) \|_2
+   \leq \IP{ \V{y}_{n_h}, \V{m} } \\
+\| I_{n_y}^{(y)} \T{P}^\H ( \T{P} \T{g} - \T{y} ) \|_2
 \leq \gamma  \\
@@
    &\MC{L}(\V{m}, \T{g}, \mu^{(h)}, \mu^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \notag \\
-=& \LA \V{1}, m \RA 
-   +\sum_{n_h} \big[ \LA \mu^{(h)}, I_{n_h}^{(h)} \T{g} \RA -\lambda^{(h)} \LA \V{y}_{n_h}, \V{m} \RA \big] \notag \\
-\quad & +\sum_{n_y} \big[ \LA \mu^{(h)}, I_{n_y}^{(y)} \T{P}^\dagger ( \T{P} \T{g} -\T{u} ) \RA -\lambda^{(h)} \gamma \big]
+=& \IP{ \V{1}, m } 
+   +\sum_{n_h} \big[ \IP{ \mu^{(h)}, I_{n_h}^{(h)} \T{g} } -\lambda^{(h)} \IP{ \V{y}_{n_h}, \V{m} } \big] \notag \\
+\quad & +\sum_{n_y} \big[ \IP{ \mu^{(h)}, I_{n_y}^{(y)} \T{P}^\H ( \T{P} \T{g} -\T{u} ) } -\lambda^{(h)} \gamma \big]
 \end{align}

### 2019-01-05 ongoing/report/sec_0_front_matter.tex
Split files

--- 2018-12-31 ongoing/report/article.tex
@@
-\documentclass[12pt]{article}
+\subsection{Acknowledgement}
 
-\usepackage{mathtools}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage[linkcolor=blue]{hyperref}
-\usepackage{xcolor}
-\usepackage[ocgcolorlinks]{ocgx2}
-
-\author{Tzu-Yu Jeng}
-\date{\today}
-\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
-
-\newcounter{NumResult}
-\newcommand{\myCount}
-{
-   \stepcounter{NumResult}
-   \textbf{\arabic{NumResult}}
-}
-
-\newcommand {\Result} [2]
-{
-   \bigskip
-   \myCount \textbf{#1} \par
-   {#2} \par
-   \hfill \(\blacksquare\)
-   \bigskip
-}
-
-\begin{document}
-
-\maketitle
-
-\section{Acknowledgement}
-
-\section{Abstract}
+\subsection{Abstract}
 
@@
 Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.
-
-\section{Introduction}
-
-This section is organized as follows.
-Before we start, we introduce our notation in the very beginning, since the literature survery quickly goes into technical details.
-And we first provide the motivation, and then overview the existent literature on channel estimation.
-Particularly, we will summerize present results on DS and OMP, and argue that DS is a viable solution that has been ignored, and then claim our contribution in this article that will be shown in the later sections.
-
-\subsection{Notation}
-
-Before we start, let us remind that, in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the classification may be different from its source.
-
-We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
-Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.
-
-Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
-Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
-
-\subsection{Background}
-
-Multiple-input multiple-output (MIMO) communication system has been proposed to be the next-generation specification.
-With a large number of antennae of both transmitter and receiver sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.
-But MIMO presents new obstacles as well.
-The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
-It is important to devise a feasible scheme, as the systems themselves are growing more complicated.
-Meanwhile, millimeter waves, having smaller wavelength, entails higher frequency bands, and thus wider available bandwith to be available.
-In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
-Consequently, this article considers MIMO in the millimeter r\`egime.
-
-The figure of merit of a MIMO system is usually considered to be the channel capacity.
-The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
-But that knowledge is hardly always available.
-What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
-It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
-Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
-
-Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
-Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
-With more antennae present, conventional training-based algorithm also increase in complexity and storage.
-In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
-A design of new algorithms that addressed these issues is thus in need.
-
-\subsection{Recovery of Sparse Vector in the Noiseless Case}
-
-It is a recent developemnt that the estimation of channels is facilitated by advances of compressed sensing.
-A series of paper by Cand\`es and Tao (2006) marks its advent.
-The idea is that, in many important statsitical applications, the number of variables or parameters \(p\) is much larger than the number of observations \(n\).
-In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?
-Of course, more assumption must be made to make the question meaningful.
-Cand\`es and Tao's pioneering work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
-They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
-Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
-
-They showed that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
-
-\Result
-{Definition}
-{
-\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
-\begin{gather} 
-\# \{\mathrm{supp}(x)\} \leq s
-\end{gather}
-That is, only at most \(s\) components of vector \(x\) is nonzero.
-}
-
-\Result
-{Program}
-{
-Let \(A,y\) be given.
-Find \(x\) with
-\begin{gather}
-\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
-\mathrm{s.t.} \quad Ax =y
-\end{gather}
-}
-
-\Result
-{Theorem}
-{
-Let \(y =Ax\).
-Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
-That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
-\begin{gather}
-\delta_{S} +\delta_{2S} +\delta_{3S} <1
-\end{gather}
-}
-
-\Result
-{Notation}
-{
-Let \(T \subset \mathbb{N}\).
-Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
-}
-
-\Result
-{Definition}.
-{
-Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
-For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
-\begin{gather}
-(1-\delta_S) \|\theta\|^2
-\leq \|X_T \theta\|_2^2
-\leq (1+\delta_S) \|\theta\|^2
-\end{gather}
-}
-
-RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).
-
-Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
-\begin{gather}
-| \langle X_T c, X_{T'} c' \rangle |
-\leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
-\end{gather}
-
-\subsection{The Dantzig Selector}
-
-Later Cand\`es and Tao  obtained a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006, which will be a main reference of this article), with a convex program called The Dantzig Selector they proposed (hencefore DS), they can recover the noisy case too.
-They argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
-From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
-Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
-
-For concreteness, consider a liear transformation with noise,
-\begin{gather}
-y =Ax +z
-\end{gather}
-where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
-How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
-
-\Result
-{Program}
-{
-Let \(A,y\) be given.
-Find \(x\) with
-\begin{gather}
-\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
-\end{gather}
-where \(r =y -A \hat{x}\).
-}
-And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.
-
-\subsection{Condition of RIP Linear Transformation}
-
-The constant \(\delta\) in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(A\) is fully unitary.
-
-Here, it is not clear at first what matrices serves as the RIP condition.
-But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.
-
-\Result
-{Theorem}
-{
-Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
-Then, with \(0 <\epsilon <1\),
-\begin{gather}
-   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
-   \leq 2 \exp(-n c_0(\epsilon))
-\end{gather}
-where we have
-\begin{gather}
-c_0(\epsilon)
-=\epsilon^2/4 -\epsilon^3/6.
-\end{gather}
-}
-
-\subsection{Compressed Channel Sensing}
-
-We have summarised results in compressed sensing, and we now relate the matter to the communication scenario.
-Recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
-Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
-Some scholars thus has applied compressive sensing techniques to the problem.
-
-One of the first papers, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
-What they explored was the estimation of single-antenna channel response with respect to time.
-Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability, providing the ground for the former paper.
-
-To explain the idea, consider a simplified scenario.
-Let \(x[t] \in \mathbb{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
-Consider a linear time-invariant channel with
-\begin{gather}
-y[t] =(x[t] \star h[t]) +z[t]
-\end{gather}
-where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
-Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
-\begin{gather}
-y =X h
-\end{gather}
-where \(X\) takes the form
-\begin{align}
-X
-=\begin{bmatrix}
-x_1, &0, &\cdots, &0 \\
-x_2, &x_1, &\cdots, &0 \\
-\vdots, &\vdots, &\ddots, &0 \\
-x_N, &x_{N-1}, &\cdots, &x_1
-\end{bmatrix}
-\end{align}
-We seek to get \(h\) in this undertermined system.
-
-Bajwa et.\ al.\ was able to show that \(X\) is RIP of overwhelmingly probability.
-
-\subsection{Orthogonal Matching Pursuit}
-
-Around that time, Tropp and A C Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit, that a i.i.d.\ matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.
-
-The setting here is \(y =Ax\), the noiseless, real-number case.
-Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
-We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).
-
-\Result
-{Algorithm}
-{
-\begin{enumerate}
-\item
-\end{enumerate}
-}
-
-\Result
-{Theorem}
-{
-   Following the setting described above, suppose, for \(0 <\delta <1\),
-\begin{gather}
-   M \geq 16s \log (N/\delta)
-\end{gather}
-Then   Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
-}
-
-For the proof, see the technical report: Tropp and A C Gilbert (2007a).
-
-It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
-Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
-To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
-Let signal \(x\) be sent, and \(y\) be receiverd, that is
-\begin{gather}
-y =WHF x
-\end{gather}
-
-\Result
-{Definition}
-{
-Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
-}
-
-\Result
-{Definition.}
-{
-For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
-Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
-}
-
-With (), scholars often exploit the relation
-\begin{gather}
-\mathrm{vec}(Y)
-=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
-\end{gather}
-
-The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
-The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.
-
-\subsection{Further development on CSS}
-
-The literature on CSS has since been vast, and we need not and cannot go through all of them here.
-Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.
-
-Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same support.
-
-Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm, using a (beam) code book with quantized AoA and AoD.
-
-Alkhateeb, Leus, and Heath Jr.\ (2015) poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
-They work simplified all-phase-shifter combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
-Their work mainly focuses on numerical simulation, rather than mathematical proof.
-
-Since the notice of hybrid beamforming, scholars have also applied the same idea to hybrid systems.
-Lee, Gil, and Lee (2016) considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
-The beambook phase is quantized, which may have been a source of error, and they have specifed a particular grid set of angles and argues the superiority.
-One of their simulations experiments utilizes DFT and permutated DFT matrix, instead of as originally suggested by Tropp and Gilbert (2007).
-
-Meanwhile, the improvement of OMP bound is also going on.
-Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
-Indeed, MIP deals with correlation of columns of the sensing matrix, rather than the almost-unitarity, making the condition easier to verify.
-
-Ben-Haim et.\ al.\ (2010) follow up their work and refine their bounds, also considering MIP conditions.
-They conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
-Still, since the setting of OMP and DS is rather different, it remains unclear which of is better.
-
-Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ (2010) as the main foundation for OMP perfomance bound.
-
-Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices in a modified basis pursuit problem.
-
-\subsection{Contribution}
-
-We remark several observation on past literature, that has been, to the best of our knowledge, lacking or less than ideal.
-
-\begin{enumerate}
-\item As said, previous work the favor on OMP rather than DS (let alone other sparse algorithm) is evident.
-\item In view of The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than Cand\`es and Tao (2007).
-\item Previous work only takes the assumption on the bound of the norm of the channel matrix to be granted.
-\item Likewise, such probability bounds on the sparsity of the channel as involving, say, number of channel paths and vector of array response has not be explored.
-\end{enumerate}
-
-We consider a system model where both digital and analog beamformer are i.i.d.\ random matrix combiner that serve readily as the sensing matrix satisfying the RIP property.
-We apply a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
-Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.
-
-Our contribution include:
-
-\begin{enumerate}
-\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
-\item We do not assume that the virtual channel model is naturally quantized in its angle of departure and of arrival, thus removes concern of the quantization error within the proof.
-\item Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
-\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
-\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
-\end{enumerate}
-
-\section{Problem Setting}
-
-\subsection{Channel Model}
-
-Since expression involving probability will get very complecated, introduce the direct product
-%
-\begin{gather}
-\Omega
-=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
-\end{gather}
-%
-to denote the overall sample space, where
-%
-\begin{itemize}
-\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
-\item \(\Omega_h\) denotes that of the communication channel,
-\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
-\item \(\Omega_r\) denotes that at the receiver end.
-\end{itemize}
-%
-\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.
-
-We restrict our consideration to the uniform linear array, which can be modeled as
-\begin{gather}
-\mathbf{a}(\phi')
-=\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
-\end{gather}
-where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.
-
-And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}\big( \frac{d}{\lambda} \sin \phi_l' \big) \mathbf{a}\big( \frac{d}{\lambda} \sin \theta_l' \big)^\dagger
-\end{gather}
-The physical meaning of \(\theta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\theta_l\), the \(l\)-th that of arrival wave.
-
-For our purpose, we may absorb the argument of \(\mathbf{a}\) as
-\begin{gather}
-\phi_l
-=\frac{d}{\lambda} \sin \phi_l' \\
-\theta_l
-=\frac{d}{\lambda} \sin \theta_l'
-\end{gather}
-to get a simpler form
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
-\end{gather}
-
-Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.
-
-\Result
-{Definition.}
-{
-Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
-We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
-\begin{gather}
-\mathbf{u} =\dagger F \mathbf{v}
-\end{gather}
-where each entry of the matrix \(K\) is defined to be
-\begin{gather}
-   K(m,n) =\frac{1}{\sqrt{N}} e^{2\pi imn/N},
-\quad m,n =0,1,2,\dotsc, N-1
-\end{gather}
-where \(i =\sqrt{-1}\).
-}
-
-\subsection{System Model}
-
-We consider the situation with a hybrid structure at both transmitter and receiver end.
-Each end consists of both digital and analog percoders and combiners.
-In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
-Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
-Recall that analog precoder is restricted to have value with magnitude being unity.
-To set up notation, we list them as below.
-\begin{gather}
-F_B \in \mathbb{R}^{N_r \cdot N_s} \\
-F_R \in \mathbb{R}^{N_h \cdot N_r}, |F_R(i,j)| =1 \\
-F_B \in \mathbb{R}^{N_r \cdot N_h} \\
-F_B \in \mathbb{R}^{N_s \cdot N_r}, |F_R(i,j)| =1.
-\end{gather}
-And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
-Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.
-
-In summary, the effective channel may be written as
-\begin{gather}
-U (\omega_h, \omega_e)
-:=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
-\end{gather}
-Supress the probabilistic index for simplicity, we restate the same equation as
-\begin{gather}
-Y
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z )
-\end{gather}
-
-\subsection{Proposed Method}
-
-The effective channel \(U\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
-This way, we may denote the acquired effective channel matrix \(U\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
-\begin{gather}
-Y_{:,n}
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-The crux of the matter is the recovery of \(H\) with knowledge of \(U\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
-
-Following previous work on CSS, we write
-\begin{gather}
-h := \mathrm{vec}(H) \\
-u := \mathrm{vec}(U) \\
-A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
-\end{gather}
-to formulate our goal as sparse recovery problem of \(\mathrm{vec}(H)\).
-But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
-What shall we do?
-
-Observe that, if we write
-\begin{gather}
-G =K^\dagger H
-\end{gather}
-as the spatial frequency domain representation of \(H\), then
-\begin{gather}
-Y
-:=W_B W_R K ( G F_R F_B +K^\dagger z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
-To the best of our knowledge, no work has explicitly considered the beamspace CSS.
-
-That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
-\begin{gather}
-\mathrm{vec}(Y)
-\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \mathrm{vec}(H)
-\end{gather}
-To simplify notation, set 
-\begin{gather}
-P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
-\end{gather}
-The instances of \(P\) is completely determined in the transmitter and receiver end, that is
-\begin{gather}
-P =P(\omega_t, \omega_r)
-\end{gather}
-If so, our program reads
-
-\Result
-{Program}
-{
-Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
-Suppose \(U\) is the acquired effective channel matrix under noisy observation.
-\(A\) is defined just above in ().
-Set
-\begin{gather}
-r =u -P h
-\end{gather}
-Then, with parameter \(\gamma\) specified, define the following program
-\begin{gather}
-\hat{g}
-=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
-\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
-\end{gather}
-And convert \(\hat{g}\) back to the space domain as
-\begin{gather}
-\hat{h}
-=K^\dagger \hat{g}.
-\end{gather}
-And finally recover the estimated \(H\) as
-\begin{gather}
-\hat{H} =\mathrm{vec}^{-1} (\hat{h})
-\end{gather}
-}
-
-It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
-
-\section{Results and Proofs}
-
-We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \(g \in \mathbb{R}^{N_H^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
-
-We first establish a technical lemma that shows \(\mathrm{supp}(g)\) has roughly cardinal \(L\).
-At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
-
-Consider
-\begin{gather}
-d =g -\hat{g}
-\end{gather}
-And let
-\begin{itemize}
-\item \(\mathcal{A}\) be the largest \(L\) position of \(g\).
-\item \(\mathcal{B}\) be the largest \(L\) position of \(d\) except on \(\mathcal{A}\).
-\item \(\mathcal{C} =\{1, \dotsc, N_H^2\} -( \mathcal{B} \cup \mathcal{C} )\), i.e., the complementary index set.
-\end{itemize}
-So \(\mathcal{A}, \mathcal{B}, \mathcal{C}\) are mutually exclusive index sets by construction:
-\begin{gather}
-\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \{1, \dotsc, N_H^2\} \\
-\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\
-A \cup B \cup C =\{1, \dotsc, N\}.
-\end{gather}
-
-\Result
-{Lemma.}
-{
-Let \(\phi(\omega_h)\) and \(\theta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
-\begin{gather}
-\|g\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
-\end{gather}
-
-To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
-\begin{align}
-S(\phi)
-:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
-\quad 0 \leq \phi \leq \pi
-\end{align}
-By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
-\begin{align}
-S(\phi)
-\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\ \notag
-=& \frac{-48}{\phi^3 -24\phi}
-\quad 0 \leq \phi \leq \pi,
-\end{align}
-
-The fraction above can be bounded.
-
-By the same token, more generally,
-\begin{align}
-&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\ \notag
-=&\frac{1}{N} S(\pi \phi') \\ \notag
-\leq& \frac{48}{N \pi^3 (\phi'^3 -24 \phi' /\pi^2)}
-\end{align}
-where \(\phi' =k/N -\phi/2\pi\), and the cubic expression is split.
-We wish to bound the tail of \(S(\pi \phi')\), and apply the na\"ive bound
-\begin{align}
-&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\phi'^3 -24 \phi' /\pi^2}
- d\phi' \\ \notag
-=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\ \notag
-\leq& \frac{1}{\pi^2} \log \frac{L}{N}
-\end{align}
-Here, the integral in the first line is immediate.
-The second term in the bracket is smaller than 0 and is dropped in the last inequality.
-}
-
-The bound is satisfying enough, though refinement is surely possible.
-Indeed, \(\log L/N \to 0\) as \(N \to \infty\) and limited by the number of paths \(L\).
-
-The rest follows ``The Dantzig Selector'' very closely.
-
-\Result
-{Proposition}
-{
-Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in ().
-Then
-\begin{align}
-\|d_{BC}\|_1
-\leq \|d_A\|_1 +\|g_{BC}\|_1
-\end{align}
-}
-To show this, observe
-\begin{align}
-\|g\|_1 -\|d_A\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1
-\leq& \|g +d\|_1 \\ \notag
-\leq& \|g\|_1
-\end{align}
-In the first line, we recall \(g =g_A\).
-
-\Result
-{Lemma}
-{
-\begin{align}
-|\langle e, P_{:,j} \rangle| \leq \sqrt{2 \log p}
-\end{align}
-}
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|P^\dagger P d\|_\infty
-\leq& 2 \sqrt{2 \log p}.
-\end{align}
-}
-To show this, start with
-\begin{align}
-\langle e -r, P_{:,j} \rangle
-=\langle P \hat{g} -P g, P_{:,j} \rangle
-=\langle P g, P_{:,j} \rangle
-\end{align}
-Result follows from triangle inequality, and Lemma ().
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|d_A\|_2
-\leq \frac{1}{1-\delta} \|P^\dagger_{AB} P \eta\|_2 +\frac{\theta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
-\end{align}
-}
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|d\|_2^2
-\leq \|d_{AB}\|_2^2 +\frac{1}{L} \|d_C\|_1^2
-\end{align}
-}
-
-We can formulate our main theorem:
-
-(To be done)
-
-\section{Simulation}
-
-With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
-
-As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\mathcal{R}(h)\).
-But it is not the end.
-In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-magic'' transforms DS into a linear program (LP), but that does not directly applies
-Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
-Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
-Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-magic''.
-
-\subsection{Transformation into Second Order Cone Problem}
-
-Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem.
-Recapitulate that, as we explained in the above, DS involves a 
-We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
-
-% % % % % % % % % % % % % % % %
-
-\section{Conclusion and Future Work}
-
-Firstly,
-Meanwhile, DS goes not without criticism for large complexity.
-Indeed it is clear, even from the primal-dual implementation above, that DS requires large dimensional vector
-
-Secondly
-And comparison of bounds of OMP and DS
-The author criticises the tendency of current literature to mix up results for DS and OMP without clear justification, since they are two quite different approaches to the compressed sensing problem.
-It is however not trivial to make meaningful comparison, since DS works with a RIP matrix, and OMP for Gaussian... the distinction is slight but definite...
-The author critizises In OMP we don't know whether the measurement matrix is the same as channel
-And OMP has stricter condition than DS
-Tao, however, specifies a noise relation
-
-Bounds of performance in different setting are often nontrivial to obtain, and one cannot think OMP, or indeed every algorithm, as a universal solution.
-OMP trades off precision for time complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
-All in all, different problems requires different technique and algorihm within the constraint at hand, as is probably true in every discipline of engineering.
-
-\section{References}
-
-References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.
-
-\begin{enumerate}
-
-\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6
-
-\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.
-5.
-
-\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}
-
-\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.98, No.6.
-
-\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
-
-\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
-
-\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.
-
-\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-
-\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.2.
-
-\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
-
-\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-
-\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.12.
-
-\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
-
-\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', \textit{IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.
-
-\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', \textit{IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.
-
-\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.\ 35, No.\ 6.
-
-\item Z Gao, L Dai, Z Wang, and S Chen (2015).
-``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.
-
-\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.
-
-\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.
-
-\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', \textit{IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.
-
-\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.
-
-\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.
-
-\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
-Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
-
-\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
-
-\end{enumerate}
-
-\end{document}

### 2019-01-05 ongoing/report/sec_1_introduction.tex
Split files

--- 2018-12-31 ongoing/report/article.tex
@@
-\documentclass[12pt]{article}
-
-\usepackage{mathtools}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage[linkcolor=blue]{hyperref}
-\usepackage{xcolor}
-\usepackage[ocgcolorlinks]{ocgx2}
-
-\author{Tzu-Yu Jeng}
-\date{\today}
-\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
-
-\newcounter{NumResult}
-\newcommand{\myCount}
-{
-   \stepcounter{NumResult}
-   \textbf{\arabic{NumResult}}
-}
-
-\newcommand {\Result} [2]
-{
-   \bigskip
-   \myCount \textbf{#1} \par
-   {#2} \par
-   \hfill \(\blacksquare\)
-   \bigskip
-}
-
-\begin{document}
-
-\maketitle
-
-\section{Acknowledgement}
-
-\section{Abstract}
-
-Multiple-input-multiple-output (MIMO) communication is widely expected to be the next-generation wireless communication scheme.
-However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
-It is then a non-trivial problem to estimate real-world wireless channels.
-
-Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
-If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing, an active area that has recently emerged.
-A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context.
-However, Orthogonal Matching Pursuit (OMP) later emerges as a low-complexity solution, and following-up literature usually used OMP rather than DS as a result.
-
-In this article, we utilize a hybrid structure at both transmitter and receiver end, each of them having both digital and analog percoders and combiners.
-We argue in favor of DS, and verify that DS is, as originally perceived, ideal in certain senses.
-DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, and as in its allowance of noise corruption.
-Moreover, we extend their proof to derive a stronger bound in the setting of estimation of millimeter wave channel for almost-sparse channel matrix
-
-We show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
-Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.
-
-\section{Introduction}
-
 This section is organized as follows.
@@
 
-We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
-Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.
+\(|a|\) denotes the magnitude for real or complex numbers \(a\).
+The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(a =\MF{Re}(a) +i \MF{Im}(a)\)
 
-Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
-Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
+We restrict our discussion to \(\MB{R}^N\) or \(\MB{C}^N\) seen as the Hilbert space , equipped with standard inner product.
+Lower case Latin alphabets with single underline, like \(\V{a}\), denote vectors, and upper case Latin alphabets with double underlines, like \(\M{A}\), denote matrices.
+Particularly, define \(\V{1} =\IP{ 1, \dotsc, 1 }\) and \(\V{1} =\IP{ 1, \dotsc, 1 }\).
+
+In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
+Of course, scalar operation on \(\MB{R}^N\) is over field \(\MB{R}\), and that on \(\MB{C}^N\) is over field \(\MB{C}\).
+We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
+Not to avoid confusion, we call the Hilbert space \(\MB{K}^N\) over \(\MB{K}\) to be \(\MB{V}_{\MB{K}} (N)\).
+We also call the collection of \(M\) by \(N\) matrices to be \(\MB{M}_{\MB{K}}(M,N)\), and its role as linear transformation is understood.
+Inner product of \(\V{a}\) and \(\V{b}\) is denoted as \(\IP{ \V{a}, \V{b} }\).
+Slightly abusing notation, we denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
+Particularly, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).
+\(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm of vector \(\V{a}\).
+Recall that \(\ell_\infty\)-norm is the maximum-magnitude norm.
+
+Denote as \(\MB{P}(X)\) the probability, and \(\MB{E}(X)\) the expectation.
+Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.
 
@@
 The figure of merit of a MIMO system is usually considered to be the channel capacity.
-The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
-But that knowledge is hardly always available.
-What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
+In vague terms, the capacity \(C\) of a MIMO channel \(\M{H}\) at perfect channel state information is well-known to be roughly in the form \(\log \det (I +\RM{SNR})\), but that knowledge is hardly always available.
+What makes things more difficult is the case that \(\M{H}\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
 It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
-Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
+Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
+Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\RM{SNR})\).
 
-Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
-Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
-With more antennae present, conventional training-based algorithm also increase in complexity and storage.
+Therefore the real-time estimation, \(\hat{\M{H}}\), of \(\M{H}\) is of paramount importance.
+Needless to say, when the \(\hat{\M{H}}\) is imprecise, resulting analysis is also undermined.
+With more antennae present, conventional training-based algorithms also increase in complexity and storage.
 In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
-A design of new algorithms that addressed these issues is thus in need.
+A design of new algorithms that addressed these issues is thus necessary.
 
-\subsection{Recovery of Sparse Vector in the Noiseless Case}
+\subsection{The Dantzig Selector}
 
-It is a recent developemnt that the estimation of channels is facilitated by advances of compressed sensing.
+It is a recent developement that the estimation of channels is facilitated by advances of compressed sensing.
 A series of paper by Cand\`es and Tao (2006) marks its advent.
-The idea is that, in many important statsitical applications, the number of variables or parameters \(p\) is much larger than the number of observations \(n\).
+
+To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p\) is much larger than the number of observations \(N_o\).
+Here, we consider
+\Disp{
+N_p \gg N_o
+}
+
 In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?
+
 Of course, more assumption must be made to make the question meaningful.
-Cand\`es and Tao's pioneering work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
+They showed frst that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
+The work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
+
+Later they established a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006), with another \(\ell_1\)-1 minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
 They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
 Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
+In addition, they derived a probability bound of mean suqare error, showing the probability of successful recovery is overwhelming.
 
-They showed that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
+From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
+Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
+
+In this article we focuss on DS, and we introduce several notions before we describe their wok.
+To facilitate reader's understanding, in this section we will consistently use \(N_s\) and \(N_s\) to denote matrix dimensions.
+Following Cand\`es and Tao, we borrow the term ``support'' from the context of analysis, where it denotes the set on which a function is nonzero.
 
@@
 {
-\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
-\begin{gather} 
-\# \{\mathrm{supp}(x)\} \leq s
-\end{gather}
+We say \(T (N) =\{1, \dotsc, N\}\), \(N \in \MB{N}\) is the support of vector space \(\MB{V}_{\MB{K}} (N)\).
+}
+
+\Result
+{Definition}
+{
+Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_1, N_2)\).
+Let \(\MC{T} \subset T (N_2)\).
+Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
+}
+
+\Result
+{Definition}
+{
+\(x \in \MB{V}_{\MB{K}} (N)\) is called \(s\)-sparse with support \(\MC{A}\), \(s \in \MB{N}\), if there is \(\MC{A} \subset T (N)\) such that
+%
+\Disp{ 
+x_{T (N) -\MC{A}} =\V{0}
+}
+with
+\Disp{ 
+\# \MC{A} \leq s.
+}
+%
 That is, only at most \(s\) components of vector \(x\) is nonzero.
@@
 Find \(x\) with
-\begin{gather}
-\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
-\mathrm{s.t.} \quad Ax =y
-\end{gather}
+%
+\Disp{
+\min_{x' \in \MB{V}_\MB{K}(K)}
+\quad \|x'\|_1
+\quad \RM{s.t.} \quad A x' =y
+}
+%
 }
@@
 That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
-\begin{gather}
+%
+\Disp{
 \delta_{S} +\delta_{2S} +\delta_{3S} <1
-\end{gather}
+}
+%
 }
@@
 \Result
-{Notation}
+{Definition}
 {
-Let \(T \subset \mathbb{N}\).
-Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
+Let \(A\) be an \(n \times p\) matrix, with
+%
+\Disp{
+\delta_{S} +\delta_{2S} +\delta_{3S} <1
+}
+%
+
+having unit \(\ell_2\)-norm columns.
+For each integer \(S \in \MB{N}\), we say that \(A\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
+%
+\Disp{
+(1-\delta_S) \|x\|^2
+\leq \|A_T x\|_2^2
+\leq (1+\delta_S) \|x\|^2
+}
+%
 }
 
-\Result
-{Definition}.
-{
-Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
-For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
-\begin{gather}
-(1-\delta_S) \|\theta\|^2
-\leq \|X_T \theta\|_2^2
-\leq (1+\delta_S) \|\theta\|^2
-\end{gather}
+RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\delta_S\).
+
+Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
+%
+\Disp{
+| \IP{ X_T c, X_{T'} c' } |
+\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
 }
+%
 
-RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).
-
-Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
-\begin{gather}
-| \langle X_T c, X_{T'} c' \rangle |
-\leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
-\end{gather}
-
-\subsection{The Dantzig Selector}
-
-Later Cand\`es and Tao  obtained a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006, which will be a main reference of this article), with a convex program called The Dantzig Selector they proposed (hencefore DS), they can recover the noisy case too.
-They argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
-From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
-Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
-
-For concreteness, consider a liear transformation with noise,
-\begin{gather}
+For concreteness, consider a linear transformation with noise,
+%
+\Disp{
 y =Ax +z
-\end{gather}
+}
+%
 where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
@@
 Find \(x\) with
-\begin{gather}
-\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
-\end{gather}
+%
+\Disp{
+\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \NT
+\RM{subject}\; \RM{to} \quad \|A^\H r\|_\infty \leq \lambda_p \sigma
+}
+%
 where \(r =y -A \hat{x}\).
@@
 {
-Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
+Let each entry of random matrix \(A \in \MB{V}_\MB{K}(M \cdot N)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
 Then, with \(0 <\epsilon <1\),
-\begin{gather}
-   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
-   \leq 2 \exp(-n c_0(\epsilon))
-\end{gather}
+%
+\Disp{
+   \MB{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
+   \leq 2 \exp (-n c_0(\epsilon))
+}
+%
 where we have
-\begin{gather}
+%
+\Disp{
 c_0(\epsilon)
 =\epsilon^2/4 -\epsilon^3/6.
-\end{gather}
+}
+%
 }
@@
 To explain the idea, consider a simplified scenario.
-Let \(x[t] \in \mathbb{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
+Let \(x[t] \in \MB{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
 Consider a linear time-invariant channel with
-\begin{gather}
+%
+\Disp{
 y[t] =(x[t] \star h[t]) +z[t]
-\end{gather}
-where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
+}
+%
+where \(h[t] \in \MB{R}^L\) is the channel's impulse response, \(x[t] \in \MB{R}^N\) as the input, \(y[t] \in \MB{R}^N\) as the output, and \(z[t] \in \MB{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
 Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
-\begin{gather}
+%
+\Disp{
 y =X h
-\end{gather}
+}
+%
 where \(X\) takes the form
-\begin{align}
+%
+\Disp{
 X
@@
 \end{bmatrix}
-\end{align}
+}
+%
 We seek to get \(h\) in this undertermined system.
@@
 The setting here is \(y =Ax\), the noiseless, real-number case.
-Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
+Same as before, let \(y \in \MB{V}_\MB{K}(M)\), \(x \in \MB{V}_\MB{K}(N)\) which is \(s\)-sparse, while \(M \ll N\).
 We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).
@@
    Following the setting described above, suppose, for \(0 <\delta <1\),
-\begin{gather}
+%
+\Disp{
    M \geq 16s \log (N/\delta)
-\end{gather}
+}
+%
 Then Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
@@
 Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
-To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
+To see this, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
 Let signal \(x\) be sent, and \(y\) be receiverd, that is
-\begin{gather}
-y =WHF x
-\end{gather}
+%
+\Disp{
+   \V{y} =\M{W} \M{H} \M{F} \V{x}
+}
+%
 
@@
 {
-Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
+Define \(\RM{vec}(\M{A}) \in \MB{K}^{nm}\) to be the vectorization of \(\M{A} \in \MB{M}_{\MB{K}}(n,m)\).
 }
@@
 {
-For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
-Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
+For \(\RM{vec}(A) \in \MB{M}_{\MB{K}}(n,m)\) and \(\RM{vec}(A) \in \MB{M}_{\MB{K}}(n,m)\)
+Define the Kronecker product \(\RM{vec}(A) \in \MB{K}^{nm}\) 
 }
@@
 With (), scholars often exploit the relation
-\begin{gather}
-\mathrm{vec}(Y)
-=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
-\end{gather}
+%
+\Disp{
+\RM{vec}(Y)
+=\big[ (F^\H) \otimes W \big] \RM{vec}(\M{H})
+}
+%
 
@@
 
-\subsection{Further development on CSS}
+\subsection{Further Development on Compressive Channel Sensing}
 
-The literature on CSS has since been vast, and we need not and cannot go through all of them here.
+The literature on Compressive Channel Sensing has since been vast, and we need not and cannot go through all of them here.
 Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.
@@
 \end{enumerate}
-
-\section{Problem Setting}
-
-\subsection{Channel Model}
-
-Since expression involving probability will get very complecated, introduce the direct product
-%
-\begin{gather}
-\Omega
-=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
-\end{gather}
-%
-to denote the overall sample space, where
-%
-\begin{itemize}
-\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
-\item \(\Omega_h\) denotes that of the communication channel,
-\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
-\item \(\Omega_r\) denotes that at the receiver end.
-\end{itemize}
-%
-\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.
-
-We restrict our consideration to the uniform linear array, which can be modeled as
-\begin{gather}
-\mathbf{a}(\phi')
-=\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
-\end{gather}
-where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.
-
-And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}\big( \frac{d}{\lambda} \sin \phi_l' \big) \mathbf{a}\big( \frac{d}{\lambda} \sin \theta_l' \big)^\dagger
-\end{gather}
-The physical meaning of \(\theta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\theta_l\), the \(l\)-th that of arrival wave.
-
-For our purpose, we may absorb the argument of \(\mathbf{a}\) as
-\begin{gather}
-\phi_l
-=\frac{d}{\lambda} \sin \phi_l' \\
-\theta_l
-=\frac{d}{\lambda} \sin \theta_l'
-\end{gather}
-to get a simpler form
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
-\end{gather}
-
-Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.
-
-\Result
-{Definition.}
-{
-Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
-We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
-\begin{gather}
-\mathbf{u} =\dagger F \mathbf{v}
-\end{gather}
-where each entry of the matrix \(K\) is defined to be
-\begin{gather}
-   K(m,n) =\frac{1}{\sqrt{N}} e^{2\pi imn/N},
-\quad m,n =0,1,2,\dotsc, N-1
-\end{gather}
-where \(i =\sqrt{-1}\).
-}
-
-\subsection{System Model}
-
-We consider the situation with a hybrid structure at both transmitter and receiver end.
-Each end consists of both digital and analog percoders and combiners.
-In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
-Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
-Recall that analog precoder is restricted to have value with magnitude being unity.
-To set up notation, we list them as below.
-\begin{gather}
-F_B \in \mathbb{R}^{N_r \cdot N_s} \\
-F_R \in \mathbb{R}^{N_h \cdot N_r}, |F_R(i,j)| =1 \\
-F_B \in \mathbb{R}^{N_r \cdot N_h} \\
-F_B \in \mathbb{R}^{N_s \cdot N_r}, |F_R(i,j)| =1.
-\end{gather}
-And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
-Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.
-
-In summary, the effective channel may be written as
-\begin{gather}
-U (\omega_h, \omega_e)
-:=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
-\end{gather}
-Supress the probabilistic index for simplicity, we restate the same equation as
-\begin{gather}
-Y
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z )
-\end{gather}
-
-\subsection{Proposed Method}
-
-The effective channel \(U\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
-This way, we may denote the acquired effective channel matrix \(U\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
-\begin{gather}
-Y_{:,n}
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-The crux of the matter is the recovery of \(H\) with knowledge of \(U\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
-
-Following previous work on CSS, we write
-\begin{gather}
-h := \mathrm{vec}(H) \\
-u := \mathrm{vec}(U) \\
-A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
-\end{gather}
-to formulate our goal as sparse recovery problem of \(\mathrm{vec}(H)\).
-But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
-What shall we do?
-
-Observe that, if we write
-\begin{gather}
-G =K^\dagger H
-\end{gather}
-as the spatial frequency domain representation of \(H\), then
-\begin{gather}
-Y
-:=W_B W_R K ( G F_R F_B +K^\dagger z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
-To the best of our knowledge, no work has explicitly considered the beamspace CSS.
-
-That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
-\begin{gather}
-\mathrm{vec}(Y)
-\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \mathrm{vec}(H)
-\end{gather}
-To simplify notation, set 
-\begin{gather}
-P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
-\end{gather}
-The instances of \(P\) is completely determined in the transmitter and receiver end, that is
-\begin{gather}
-P =P(\omega_t, \omega_r)
-\end{gather}
-If so, our program reads
-
-\Result
-{Program}
-{
-Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
-Suppose \(U\) is the acquired effective channel matrix under noisy observation.
-\(A\) is defined just above in ().
-Set
-\begin{gather}
-r =u -P h
-\end{gather}
-Then, with parameter \(\gamma\) specified, define the following program
-\begin{gather}
-\hat{g}
-=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
-\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
-\end{gather}
-And convert \(\hat{g}\) back to the space domain as
-\begin{gather}
-\hat{h}
-=K^\dagger \hat{g}.
-\end{gather}
-And finally recover the estimated \(H\) as
-\begin{gather}
-\hat{H} =\mathrm{vec}^{-1} (\hat{h})
-\end{gather}
-}
-
-It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
-
-\section{Results and Proofs}
-
-We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \(g \in \mathbb{R}^{N_H^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
-
-We first establish a technical lemma that shows \(\mathrm{supp}(g)\) has roughly cardinal \(L\).
-At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
-
-Consider
-\begin{gather}
-d =g -\hat{g}
-\end{gather}
-And let
-\begin{itemize}
-\item \(\mathcal{A}\) be the largest \(L\) position of \(g\).
-\item \(\mathcal{B}\) be the largest \(L\) position of \(d\) except on \(\mathcal{A}\).
-\item \(\mathcal{C} =\{1, \dotsc, N_H^2\} -( \mathcal{B} \cup \mathcal{C} )\), i.e., the complementary index set.
-\end{itemize}
-So \(\mathcal{A}, \mathcal{B}, \mathcal{C}\) are mutually exclusive index sets by construction:
-\begin{gather}
-\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \{1, \dotsc, N_H^2\} \\
-\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\
-A \cup B \cup C =\{1, \dotsc, N\}.
-\end{gather}
-
-\Result
-{Lemma.}
-{
-Let \(\phi(\omega_h)\) and \(\theta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
-\begin{gather}
-\|g\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
-\end{gather}
-
-To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
-\begin{align}
-S(\phi)
-:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
-\quad 0 \leq \phi \leq \pi
-\end{align}
-By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
-\begin{align}
-S(\phi)
-\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\ \notag
-=& \frac{-48}{\phi^3 -24\phi}
-\quad 0 \leq \phi \leq \pi,
-\end{align}
-
-The fraction above can be bounded.
-
-By the same token, more generally,
-\begin{align}
-&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\ \notag
-=&\frac{1}{N} S(\pi \phi') \\ \notag
-\leq& \frac{48}{N \pi^3 (\phi'^3 -24 \phi' /\pi^2)}
-\end{align}
-where \(\phi' =k/N -\phi/2\pi\), and the cubic expression is split.
-We wish to bound the tail of \(S(\pi \phi')\), and apply the na\"ive bound
-\begin{align}
-&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\phi'^3 -24 \phi' /\pi^2}
- d\phi' \\ \notag
-=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\ \notag
-\leq& \frac{1}{\pi^2} \log \frac{L}{N}
-\end{align}
-Here, the integral in the first line is immediate.
-The second term in the bracket is smaller than 0 and is dropped in the last inequality.
-}
-
-The bound is satisfying enough, though refinement is surely possible.
-Indeed, \(\log L/N \to 0\) as \(N \to \infty\) and limited by the number of paths \(L\).
-
-The rest follows ``The Dantzig Selector'' very closely.
-
-\Result
-{Proposition}
-{
-Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in ().
-Then
-\begin{align}
-\|d_{BC}\|_1
-\leq \|d_A\|_1 +\|g_{BC}\|_1
-\end{align}
-}
-To show this, observe
-\begin{align}
-\|g\|_1 -\|d_A\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1
-\leq& \|g +d\|_1 \\ \notag
-\leq& \|g\|_1
-\end{align}
-In the first line, we recall \(g =g_A\).
-
-\Result
-{Lemma}
-{
-\begin{align}
-|\langle e, P_{:,j} \rangle| \leq \sqrt{2 \log p}
-\end{align}
-}
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|P^\dagger P d\|_\infty
-\leq& 2 \sqrt{2 \log p}.
-\end{align}
-}
-To show this, start with
-\begin{align}
-\langle e -r, P_{:,j} \rangle
-=\langle P \hat{g} -P g, P_{:,j} \rangle
-=\langle P g, P_{:,j} \rangle
-\end{align}
-Result follows from triangle inequality, and Lemma ().
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|d_A\|_2
-\leq \frac{1}{1-\delta} \|P^\dagger_{AB} P \eta\|_2 +\frac{\theta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
-\end{align}
-}
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|d\|_2^2
-\leq \|d_{AB}\|_2^2 +\frac{1}{L} \|d_C\|_1^2
-\end{align}
-}
-
-We can formulate our main theorem:
-
-(To be done)
-
-\section{Simulation}
-
-With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
-
-As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\mathcal{R}(h)\).
-But it is not the end.
-In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-magic'' transforms DS into a linear program (LP), but that does not directly applies
-Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
-Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
-Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-magic''.
-
-\subsection{Transformation into Second Order Cone Problem}
-
-Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem.
-Recapitulate that, as we explained in the above, DS involves a 
-We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
-
-% % % % % % % % % % % % % % % %
-
-\section{Conclusion and Future Work}
-
-Firstly,
-Meanwhile, DS goes not without criticism for large complexity.
-Indeed it is clear, even from the primal-dual implementation above, that DS requires large dimensional vector
-
-Secondly
-And comparison of bounds of OMP and DS
-The author criticises the tendency of current literature to mix up results for DS and OMP without clear justification, since they are two quite different approaches to the compressed sensing problem.
-It is however not trivial to make meaningful comparison, since DS works with a RIP matrix, and OMP for Gaussian... the distinction is slight but definite...
-The author critizises In OMP we don't know whether the measurement matrix is the same as channel
-And OMP has stricter condition than DS
-Tao, however, specifies a noise relation
-
-Bounds of performance in different setting are often nontrivial to obtain, and one cannot think OMP, or indeed every algorithm, as a universal solution.
-OMP trades off precision for time complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
-All in all, different problems requires different technique and algorihm within the constraint at hand, as is probably true in every discipline of engineering.
-
-\section{References}
-
-References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.
-
-\begin{enumerate}
-
-\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6
-
-\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.
-5.
-
-\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}
-
-\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.98, No.6.
-
-\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
-
-\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
-
-\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.
-
-\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-
-\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.2.
-
-\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
-
-\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-
-\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.12.
-
-\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
-
-\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', \textit{IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.
-
-\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', \textit{IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.
-
-\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.\ 35, No.\ 6.
-
-\item Z Gao, L Dai, Z Wang, and S Chen (2015).
-``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.
-
-\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.
-
-\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.
-
-\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', \textit{IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.
-
-\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.
-
-\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.
-
-\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
-Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
-
-\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
-
-\end{enumerate}
-
-\end{document}

### 2019-01-05 ongoing/report/sec_2_problem_setting.tex
Split files

\subsection{Channel Model}

Since expression involving probability will get very complecated, sometimes we will explicit mark the independence on event space index.
Introduce the direct product
%
\Disp{
\Omega
=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
}
%
to denote the overall event space, where

\begin{itemize}
\item \(\Omega_t\) denotes the event space of the transmitter end,
\item \(\Omega_h\) denotes the event space of the communication channel itself,
\item \(\Omega_z\) denotes the event space of the noise arising in the communication channel,
\item \(\Omega_r\) denotes the event space of the receiver end.
\end{itemize}
%

We restrict our consideration to the uniform linear array, which can be modeled as
%
\Disp{
\V{a} \in \MB{V}_\MB{K} (N_h) \\
\V{a} (\psi')
=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
}
%
where \(\RM{e}\) is the base of natural logarithm, and \(i\) the imaginary unit.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
%
\Disp{
H
=\sum_{l=1}^L \alpha_l \V{a} \left( \frac{d} {\lambda} \sin \varphi_l' \right) \V{a} \left( \frac{d_{\RM{arr}}} {\lambda} \sin \vartheta_l' \right)^\H
}
%
The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
%
\Disp{
\varphi_l
=\frac{d_{\RM{arr}}} {\lambda} \sin \varphi_l' \\
\vartheta_l
=\frac{d_{\RM{arr}}} {\lambda} \sin \vartheta_l'
}
%
to get a simpler form
%
\Disp{
H
=\sum_{l=0}^L \alpha_l \V{a} (\varphi_l) \V{a} (\vartheta_l)^\H
}
%

\Result
{Definition.}
{
}

\subsection{System Model}

We consider the hybrid configuration at both transmitter and receiver end.
That is to say, each end consists of both digital and analog percoders and combiners, as follows.
In the transmitter end, there are, in order seeing from the end, digital precoder \(F_B\) and analog precoder \(F_R\).
Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \(W_B\) and analog combiner \(W_R\).
To set up notation, we list them as below.
%
\Disp{
\M{F}_B \in &\MB{M}_{\MB{C}} (N_r, N_y) \\
\M{F}_R \in &\MB{M}_{\MB{C}} (N_h, N_r) \\
\M{W}_R \in &\MB{M}_{\MB{C}} (N_r, N_h) \\
\M{W}_B \in &\MB{M}_{\MB{C}} (N_y, N_r).
}
%
Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
%
\Disp{
|\M{F}_R (n_h, n_r)| =&1, \\
|\M{W}_R (n_r, n_h)| =&1, \\
n_h =&1, \dotsc N_h, \NT \\
n_r =&1, \dotsc N_r \NT
}
%
And we assume
\Disp{
N_h \gg &N_r \\
N_r \gg &N_s
}

This is analogous to (), and we will exploit the fact when applying compressive sensing techinique.

We consider zero-mean, unity-variance additive white Gaussian noise \(z\).
Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.

We may introduce the effective channel
%
\Disp{
Y (\omega_h, \omega_e)
:=W_B (\omega_r) W_R (\omega_r) \Big[ H (\omega_h) F_R (\omega_t) F_B (\omega_t) +Z (\omega_z) \Big]
}
%
Supress the event space index for brevity, we restate the same equation as
%
\Disp{
Y
:=W_B W_R ( H F_R F_B +z )
}

\subsection{Proposed Method}

\(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
%
\Disp{
\M{Y} (:,n_y)
:=\M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \quad
n_y =1, 2, \dotsc, N_y
}
%
The crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), while \(\M{W}_R\), \(\M{W}_B\), \(\M{F}_R\), and \(\M{F}_B\) are in our control.

Following previous work on CSS, we write
%
\Disp{
\V{h}
:= &\RM{vec} (\M{H})
\in \MB{V}_{\MB{C}} (N_h^2) \\
\V{y}
:= &\RM{vec} (\M{Y})
\in \MB{M}_{\MB{C}} (N_y^2) \\
\V{z}^\star
:= &\RM{vec} (\M{Z})
\in \MB{M}_{\MB{C}} (N_y^2) \\
\M{P}^\star
:= &(\M{F}_R \M{F}_B) \otimes (\M{W}_B \M{W}_R)
\in \MB{M}_{\MB{C}} (N_h, N_h).
}
%
to formulate our goal as sparse recovery problem of \(\RM{vec} (H)\) to be
%
\Disp{
\V{y} =\M{P}^\star \V{h} +\V{z}^\star
}
%
But, as we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
What shall we do?

Introduce the discrete Fourier matrix \(\M{K}\) defined to be
%
\Disp{
\M{K} \in &\MB{M}_{\MB{C}} (N_h, N_h) \notag \\
\M{K} (n_1, n_2) =&\frac{1} {\sqrt{N}} \RM{e}^{2\pi i n_1 n_2 /N}, \\
\quad n_1, n_2 =&0, 1, \dotsc, N_h-1 \notag
}
%
Observe that, if we write
%
\Disp{
\M{G}
=\M{K}^\H \M{H} \M{K}
}
%
which has the interpretation as the spatial frequency domain representation of \(\M{H}\), then
%
\Disp{
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
}
%
If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.
To the best of our knowledge, no work has explicitly considered the beamspace CSS.

That is to say, \(\M{K}^\H \V{z}\) may be absorbed, and a similar Kronecker product may be used.
To simplify notation, set 
%
\Disp{
\M{P}
=(\M{F}_B^\H \M{F}_R^\H K) \otimes (\M{W}_B \M{W}_R \M{K})
\in \MB{M}_{\MB{C}} (N_y^2, N_h^2)
}
%
And accordingly
\Disp{
\V{z}
:= &\RM{vec} (\M{K}^\H \M{Z})
\in \MB{V}_{\MB{C}} (N_y^2)
}
%
Then
%
\Disp{
\V{y}
=\M{P} \V{g} +\V{z}
}
%
If so, our program reads

\Result
{Program}
{
Let \(\M{P}, \V{y}\) be defined just above in ().
Then, with parameter \(\gamma\) specified, define the following program
%
\Disp{
\hat{\V{g}}
=\underset {\V{h}} {\RM{min}} \|\V{h}\|_1 \quad
\RM{subject}\; \RM{to}\quad \|P^\H (y -P h)\|_\infty \leq \gamma
}
%
And convert \(\hat{g}\) back to the space domain as
%
\Disp{
\hat{h}
=K \hat{g}.
}
%
And finally recover the estimated \(H\) as
%
\Disp{
\hat{H} =\RM{vec}^{-1} (\hat{h})
}
%
}

It, then, will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.

### 2019-01-05 ongoing/report/sec_3_theorems_and_proofs.tex
Split files

--- 2018-12-31 ongoing/report/article.tex
@@
-\documentclass[12pt]{article}
+We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
+The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_h^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
 
-\usepackage{mathtools}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage[linkcolor=blue]{hyperref}
-\usepackage{xcolor}
-\usepackage[ocgcolorlinks]{ocgx2}
+We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\).
+At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
 
-\author{Tzu-Yu Jeng}
-\date{\today}
-\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
-
-\newcounter{NumResult}
-\newcommand{\myCount}
-{
-   \stepcounter{NumResult}
-   \textbf{\arabic{NumResult}}
+Consider
+%
+\Disp{
+d =g -\hat{g}
+}
+%
+And let
+\begin{itemize}
+\item \(\MC{A}\) be the largest \(L\) position of \(g\).
+\item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
+\item \(\MC{C} =\{1, \dotsc, N_h^2\} -( \MC{B} \cup \MC{C} )\), i.e., the complementary index set.
+\end{itemize}
+So \(\MC{A}, \MC{B}, \MC{C}\) are mutually exclusive index sets by construction:
+%
+\Disp{
+\MC{A}, \MC{B}, \MC{C} \subset \{1, \dotsc, N_h^2\} \\
+\MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
+\MC{A} \cup \MC{B} \cup \MC{C} =\{1, \dotsc, N\}.
 }
 
-\newcommand {\Result} [2]
-{
-   \bigskip
-   \myCount \textbf{#1} \par
-   {#2} \par
-   \hfill \(\blacksquare\)
-   \bigskip
-}
-
-\begin{document}
-
-\maketitle
-
-\section{Acknowledgement}
-
-\section{Abstract}
-
-Multiple-input-multiple-output (MIMO) communication is widely expected to be the next-generation wireless communication scheme.
-However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
-It is then a non-trivial problem to estimate real-world wireless channels.
-
-Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
-If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing, an active area that has recently emerged.
-A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context.
-However, Orthogonal Matching Pursuit (OMP) later emerges as a low-complexity solution, and following-up literature usually used OMP rather than DS as a result.
-
-In this article, we utilize a hybrid structure at both transmitter and receiver end, each of them having both digital and analog percoders and combiners.
-We argue in favor of DS, and verify that DS is, as originally perceived, ideal in certain senses.
-DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, and as in its allowance of noise corruption.
-Moreover, we extend their proof to derive a stronger bound in the setting of estimation of millimeter wave channel for almost-sparse channel matrix
-
-We show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
-Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.
-
-\section{Introduction}
-
-This section is organized as follows.
-Before we start, we introduce our notation in the very beginning, since the literature survery quickly goes into technical details.
-And we first provide the motivation, and then overview the existent literature on channel estimation.
-Particularly, we will summerize present results on DS and OMP, and argue that DS is a viable solution that has been ignored, and then claim our contribution in this article that will be shown in the later sections.
-
-\subsection{Notation}
-
-Before we start, let us remind that, in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the classification may be different from its source.
-
-We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
-Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.
-
-Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
-Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
-
-\subsection{Background}
-
-Multiple-input multiple-output (MIMO) communication system has been proposed to be the next-generation specification.
-With a large number of antennae of both transmitter and receiver sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.
-But MIMO presents new obstacles as well.
-The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
-It is important to devise a feasible scheme, as the systems themselves are growing more complicated.
-Meanwhile, millimeter waves, having smaller wavelength, entails higher frequency bands, and thus wider available bandwith to be available.
-In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
-Consequently, this article considers MIMO in the millimeter r\`egime.
-
-The figure of merit of a MIMO system is usually considered to be the channel capacity.
-The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
-But that knowledge is hardly always available.
-What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
-It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
-Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
-
-Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
-Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
-With more antennae present, conventional training-based algorithm also increase in complexity and storage.
-In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
-A design of new algorithms that addressed these issues is thus in need.
-
-\subsection{Recovery of Sparse Vector in the Noiseless Case}
-
-It is a recent developemnt that the estimation of channels is facilitated by advances of compressed sensing.
-A series of paper by Cand\`es and Tao (2006) marks its advent.
-The idea is that, in many important statsitical applications, the number of variables or parameters \(p\) is much larger than the number of observations \(n\).
-In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?
-Of course, more assumption must be made to make the question meaningful.
-Cand\`es and Tao's pioneering work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
-They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
-Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
-
-They showed that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
+Recall the definition () in section 1.
 
@@
 {
-\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
-\begin{gather} 
-\# \{\mathrm{supp}(x)\} \leq s
-\end{gather}
-That is, only at most \(s\) components of vector \(x\) is nonzero.
+Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_1, N_2)\).
+Let \(\MC{T} \subset T (N_2)\).
+Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
 }
-
-\Result
-{Program}
-{
-Let \(A,y\) be given.
-Find \(x\) with
-\begin{gather}
-\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
-\mathrm{s.t.} \quad Ax =y
-\end{gather}
-}
-
-\Result
-{Theorem}
-{
-Let \(y =Ax\).
-Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
-That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
-\begin{gather}
-\delta_{S} +\delta_{2S} +\delta_{3S} <1
-\end{gather}
-}
-
-\Result
-{Notation}
-{
-Let \(T \subset \mathbb{N}\).
-Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
-}
-
-\Result
-{Definition}.
-{
-Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
-For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
-\begin{gather}
-(1-\delta_S) \|\theta\|^2
-\leq \|X_T \theta\|_2^2
-\leq (1+\delta_S) \|\theta\|^2
-\end{gather}
-}
-
-RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).
-
-Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
-\begin{gather}
-| \langle X_T c, X_{T'} c' \rangle |
-\leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
-\end{gather}
-
-\subsection{The Dantzig Selector}
-
-Later Cand\`es and Tao  obtained a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006, which will be a main reference of this article), with a convex program called The Dantzig Selector they proposed (hencefore DS), they can recover the noisy case too.
-They argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
-From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
-Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
-
-For concreteness, consider a liear transformation with noise,
-\begin{gather}
-y =Ax +z
-\end{gather}
-where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
-How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
-
-\Result
-{Program}
-{
-Let \(A,y\) be given.
-Find \(x\) with
-\begin{gather}
-\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
-\end{gather}
-where \(r =y -A \hat{x}\).
-}
-And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.
-
-\subsection{Condition of RIP Linear Transformation}
-
-The constant \(\delta\) in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(A\) is fully unitary.
-
-Here, it is not clear at first what matrices serves as the RIP condition.
-But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.
-
-\Result
-{Theorem}
-{
-Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
-Then, with \(0 <\epsilon <1\),
-\begin{gather}
-   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
-   \leq 2 \exp(-n c_0(\epsilon))
-\end{gather}
-where we have
-\begin{gather}
-c_0(\epsilon)
-=\epsilon^2/4 -\epsilon^3/6.
-\end{gather}
-}
-
-\subsection{Compressed Channel Sensing}
-
-We have summarised results in compressed sensing, and we now relate the matter to the communication scenario.
-Recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
-Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
-Some scholars thus has applied compressive sensing techniques to the problem.
-
-One of the first papers, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
-What they explored was the estimation of single-antenna channel response with respect to time.
-Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability, providing the ground for the former paper.
-
-To explain the idea, consider a simplified scenario.
-Let \(x[t] \in \mathbb{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
-Consider a linear time-invariant channel with
-\begin{gather}
-y[t] =(x[t] \star h[t]) +z[t]
-\end{gather}
-where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
-Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
-\begin{gather}
-y =X h
-\end{gather}
-where \(X\) takes the form
-\begin{align}
-X
-=\begin{bmatrix}
-x_1, &0, &\cdots, &0 \\
-x_2, &x_1, &\cdots, &0 \\
-\vdots, &\vdots, &\ddots, &0 \\
-x_N, &x_{N-1}, &\cdots, &x_1
-\end{bmatrix}
-\end{align}
-We seek to get \(h\) in this undertermined system.
-
-Bajwa et.\ al.\ was able to show that \(X\) is RIP of overwhelmingly probability.
-
-\subsection{Orthogonal Matching Pursuit}
-
-Around that time, Tropp and A C Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit, that a i.i.d.\ matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.
-
-The setting here is \(y =Ax\), the noiseless, real-number case.
-Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
-We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).
-
-\Result
-{Algorithm}
-{
-\begin{enumerate}
-\item
-\end{enumerate}
-}
-
-\Result
-{Theorem}
-{
-   Following the setting described above, suppose, for \(0 <\delta <1\),
-\begin{gather}
-   M \geq 16s \log (N/\delta)
-\end{gather}
-Then   Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
-}
-
-For the proof, see the technical report: Tropp and A C Gilbert (2007a).
-
-It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
-Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
-To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
-Let signal \(x\) be sent, and \(y\) be receiverd, that is
-\begin{gather}
-y =WHF x
-\end{gather}
 
@@
 {
-Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
+The function \(S:\; \MB{V}_{\MB{K}}(N) \mapsto \MB{V}_{\MB{K}}(N)\), \(N \in \MB{N}\), sorts the vector \(x \in \MB{V}_{\MB{K}}(N))\), so that
+\Disp{
+S (x)(n_1) \geq S (x)(n_2),
+\quad n_1, n_2 \in T (N).
+}
+Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \(S\) throughout this article.
+For definiteness, we may compare the first component first, and the second, and so on.
+If still there is a tie for a certain component (for complex numbers), we compare the real part first, then the imaginary part.
 }
@@
 \Result
-{Definition.}
+{Definition}
 {
-For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
-Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
+Let function \(f:\; T (N) \mapsto \MB{R}_+\), \(N \in \MB{N}\), be given.
+For \(x \in \MB{V}_{\MB{K}}(N)\), we say \(x\) is confined in sorted magnitude according to \(f\), if
+\Disp{
+x (n) <f (n),
+\quad n \in T (N).
+}
 }
 
-With (), scholars often exploit the relation
-\begin{gather}
-\mathrm{vec}(Y)
-=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
-\end{gather}
-
-The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
-The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.
-
-\subsection{Further development on CSS}
-
-The literature on CSS has since been vast, and we need not and cannot go through all of them here.
-Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.
-
-Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same support.
-
-Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm, using a (beam) code book with quantized AoA and AoD.
-
-Alkhateeb, Leus, and Heath Jr.\ (2015) poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
-They work simplified all-phase-shifter combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
-Their work mainly focuses on numerical simulation, rather than mathematical proof.
-
-Since the notice of hybrid beamforming, scholars have also applied the same idea to hybrid systems.
-Lee, Gil, and Lee (2016) considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
-The beambook phase is quantized, which may have been a source of error, and they have specifed a particular grid set of angles and argues the superiority.
-One of their simulations experiments utilizes DFT and permutated DFT matrix, instead of as originally suggested by Tropp and Gilbert (2007).
-
-Meanwhile, the improvement of OMP bound is also going on.
-Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
-Indeed, MIP deals with correlation of columns of the sensing matrix, rather than the almost-unitarity, making the condition easier to verify.
-
-Ben-Haim et.\ al.\ (2010) follow up their work and refine their bounds, also considering MIP conditions.
-They conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
-Still, since the setting of OMP and DS is rather different, it remains unclear which of is better.
-
-Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ (2010) as the main foundation for OMP perfomance bound.
-
-Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices in a modified basis pursuit problem.
-
-\subsection{Contribution}
-
-We remark several observation on past literature, that has been, to the best of our knowledge, lacking or less than ideal.
-
-\begin{enumerate}
-\item As said, previous work the favor on OMP rather than DS (let alone other sparse algorithm) is evident.
-\item In view of The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than Cand\`es and Tao (2007).
-\item Previous work only takes the assumption on the bound of the norm of the channel matrix to be granted.
-\item Likewise, such probability bounds on the sparsity of the channel as involving, say, number of channel paths and vector of array response has not be explored.
-\end{enumerate}
-
-We consider a system model where both digital and analog beamformer are i.i.d.\ random matrix combiner that serve readily as the sensing matrix satisfying the RIP property.
-We apply a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
-Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.
-
-Our contribution include:
-
-\begin{enumerate}
-\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
-\item We do not assume that the virtual channel model is naturally quantized in its angle of departure and of arrival, thus removes concern of the quantization error within the proof.
-\item Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
-\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
-\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
-\end{enumerate}
-
-\section{Problem Setting}
-
-\subsection{Channel Model}
-
-Since expression involving probability will get very complecated, introduce the direct product
+\Result
+{Lemma}
+{
+Let \(\varphi (\omega_h)\) be uniformly, independently distributed in \([0,2\pi)\), and array response \(\V{a} (\varphi)\) defined as in ().
 %
-\begin{gather}
-\Omega
-=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
-\end{gather}
+\Disp{
+\| \V{a} (\varphi) \|_1
+\leq \frac{1}{\pi^2} \log \frac{L}{N}.
+}
 %
-to denote the overall sample space, where
-%
-\begin{itemize}
-\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
-\item \(\Omega_h\) denotes that of the communication channel,
-\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
-\item \(\Omega_r\) denotes that at the receiver end.
-\end{itemize}
-%
-\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.
-
-We restrict our consideration to the uniform linear array, which can be modeled as
-\begin{gather}
-\mathbf{a}(\phi')
-=\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
-\end{gather}
-where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.
-
-And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}\big( \frac{d}{\lambda} \sin \phi_l' \big) \mathbf{a}\big( \frac{d}{\lambda} \sin \theta_l' \big)^\dagger
-\end{gather}
-The physical meaning of \(\theta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\theta_l\), the \(l\)-th that of arrival wave.
-
-For our purpose, we may absorb the argument of \(\mathbf{a}\) as
-\begin{gather}
-\phi_l
-=\frac{d}{\lambda} \sin \phi_l' \\
-\theta_l
-=\frac{d}{\lambda} \sin \theta_l'
-\end{gather}
-to get a simpler form
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
-\end{gather}
-
-Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.
-
-\Result
-{Definition.}
-{
-Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
-We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
-\begin{gather}
-\mathbf{u} =\dagger F \mathbf{v}
-\end{gather}
-where each entry of the matrix \(K\) is defined to be
-\begin{gather}
-   K(m,n) =\frac{1}{\sqrt{N}} e^{2\pi imn/N},
-\quad m,n =0,1,2,\dotsc, N-1
-\end{gather}
-where \(i =\sqrt{-1}\).
 }
 
-\subsection{System Model}
+To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
+%
+\Disp{
+D (\varphi)
+:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi} \right| \\ \NT
+=&\frac{|\sin (N \varphi/2)|}{|\sin (\varphi /2)|},
+\quad 0 \leq \varphi \leq \pi
+}
+%
 
-We consider the situation with a hybrid structure at both transmitter and receiver end.
-Each end consists of both digital and analog percoders and combiners.
-In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
-Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
-Recall that analog precoder is restricted to have value with magnitude being unity.
-To set up notation, we list them as below.
-\begin{gather}
-F_B \in \mathbb{R}^{N_r \cdot N_s} \\
-F_R \in \mathbb{R}^{N_h \cdot N_r}, |F_R(i,j)| =1 \\
-F_B \in \mathbb{R}^{N_r \cdot N_h} \\
-F_B \in \mathbb{R}^{N_s \cdot N_r}, |F_R(i,j)| =1.
-\end{gather}
-And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
-Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.
-
-In summary, the effective channel may be written as
-\begin{gather}
-U (\omega_h, \omega_e)
-:=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
-\end{gather}
-Supress the probabilistic index for simplicity, we restate the same equation as
-\begin{gather}
-Y
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z )
-\end{gather}
-
-\subsection{Proposed Method}
-
-The effective channel \(U\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
-This way, we may denote the acquired effective channel matrix \(U\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
-\begin{gather}
-Y_{:,n}
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-The crux of the matter is the recovery of \(H\) with knowledge of \(U\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
-
-Following previous work on CSS, we write
-\begin{gather}
-h := \mathrm{vec}(H) \\
-u := \mathrm{vec}(U) \\
-A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
-\end{gather}
-to formulate our goal as sparse recovery problem of \(\mathrm{vec}(H)\).
-But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
-What shall we do?
-
-Observe that, if we write
-\begin{gather}
-G =K^\dagger H
-\end{gather}
-as the spatial frequency domain representation of \(H\), then
-\begin{gather}
-Y
-:=W_B W_R K ( G F_R F_B +K^\dagger z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
-To the best of our knowledge, no work has explicitly considered the beamspace CSS.
-
-That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
-\begin{gather}
-\mathrm{vec}(Y)
-\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \mathrm{vec}(H)
-\end{gather}
-To simplify notation, set 
-\begin{gather}
-P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
-\end{gather}
-The instances of \(P\) is completely determined in the transmitter and receiver end, that is
-\begin{gather}
-P =P(\omega_t, \omega_r)
-\end{gather}
-If so, our program reads
-
-\Result
-{Program}
-{
-Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
-Suppose \(U\) is the acquired effective channel matrix under noisy observation.
-\(A\) is defined just above in ().
-Set
-\begin{gather}
-r =u -P h
-\end{gather}
-Then, with parameter \(\gamma\) specified, define the following program
-\begin{gather}
-\hat{g}
-=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
-\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
-\end{gather}
-And convert \(\hat{g}\) back to the space domain as
-\begin{gather}
-\hat{h}
-=K^\dagger \hat{g}.
-\end{gather}
-And finally recover the estimated \(H\) as
-\begin{gather}
-\hat{H} =\mathrm{vec}^{-1} (\hat{h})
-\end{gather}
+By taking the first two term of the expansion
+%
+\Disp{
+\sin x =x -x^3/6 + \MC{O}(x^5), \quad x \ll 1
 }
-
-It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
-
-\section{Results and Proofs}
-
-We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \(g \in \mathbb{R}^{N_H^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
-
-We first establish a technical lemma that shows \(\mathrm{supp}(g)\) has roughly cardinal \(L\).
-At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
-
-Consider
-\begin{gather}
-d =g -\hat{g}
-\end{gather}
-And let
-\begin{itemize}
-\item \(\mathcal{A}\) be the largest \(L\) position of \(g\).
-\item \(\mathcal{B}\) be the largest \(L\) position of \(d\) except on \(\mathcal{A}\).
-\item \(\mathcal{C} =\{1, \dotsc, N_H^2\} -( \mathcal{B} \cup \mathcal{C} )\), i.e., the complementary index set.
-\end{itemize}
-So \(\mathcal{A}, \mathcal{B}, \mathcal{C}\) are mutually exclusive index sets by construction:
-\begin{gather}
-\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \{1, \dotsc, N_H^2\} \\
-\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\
-A \cup B \cup C =\{1, \dotsc, N\}.
-\end{gather}
-
-\Result
-{Lemma.}
-{
-Let \(\phi(\omega_h)\) and \(\theta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
-\begin{gather}
-\|g\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
-\end{gather}
-
-To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
-\begin{align}
-S(\phi)
-:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
-\quad 0 \leq \phi \leq \pi
-\end{align}
-By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
-\begin{align}
-S(\phi)
-\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\ \notag
-=& \frac{-48}{\phi^3 -24\phi}
-\quad 0 \leq \phi \leq \pi,
-\end{align}
-
+%
+and noting the monotony of the first two terms,
+%
+\Disp{
+D (\varphi)
+\leq& \frac{1}{\varphi/2 -(\varphi/2)^3/6} \NT \\
+=& \frac{-48}{\varphi^3 -24\varphi} \\
+\quad 0 \leq \varphi \leq \pi,
+}
+%
 The fraction above can be bounded.
@@
 By the same token, more generally,
-\begin{align}
-&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\ \notag
-=&\frac{1}{N} S(\pi \phi') \\ \notag
-\leq& \frac{48}{N \pi^3 (\phi'^3 -24 \phi' /\pi^2)}
-\end{align}
-where \(\phi' =k/N -\phi/2\pi\), and the cubic expression is split.
-We wish to bound the tail of \(S(\pi \phi')\), and apply the na\"ive bound
-\begin{align}
-&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\phi'^3 -24 \phi' /\pi^2}
- d\phi' \\ \notag
-=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\ \notag
+%
+\Disp{
+\frac{1}{N} S (\pi \varphi')
+=&\left| \frac{1}{N} \sum_{n=0}^{N-1} \RM{e}^{-2\pi i k n/N} \RM{e}^{i n \varphi} \right| \NT \\
+\leq& \frac{48}{N \pi^3 (\varphi'^3 -24 \varphi' /\pi^2)}
+}
+%
+where \(\varphi' =k/N -\varphi/2\pi\), and the cubic expression is split.
+We wish to bound the tail of \(S (\pi \varphi')\), and apply the na\"ive bound
+%
+\Disp{
+&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\varphi'^3 -24 \varphi' /\pi^2}
+ d\varphi' \NT \\
+=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \NT \\
 \leq& \frac{1}{\pi^2} \log \frac{L}{N}
-\end{align}
+}
+%
 Here, the integral in the first line is immediate.
 The second term in the bracket is smaller than 0 and is dropped in the last inequality.
-}
+The proof of Lemma () is complete.
 
@@
 {
-Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in ().
+Let \(h \in \MB{R}^n\) and \(\eta \in \MB{R}^p\) are defined as in ().
 Then
-\begin{align}
+%
+\Disp{
 \|d_{BC}\|_1
-\leq \|d_A\|_1 +\|g_{BC}\|_1
-\end{align}
+\leq \|d_{\MC{A}}\|_1 +\|g_{BC}\|_1
 }
+%
+}
+
 To show this, observe
-\begin{align}
-\|g\|_1 -\|d_A\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1
-\leq& \|g +d\|_1 \\ \notag
+%
+\Disp{
+&\|g\|_1 -\|d_{\MC{A}}\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1 \\
+\leq& \|g +d\|_1 \NT \\
 \leq& \|g\|_1
-\end{align}
-In the first line, we recall \(g =g_A\).
+}
+%
+In the first line, we recall \(g =g_{\MC{A}}\).
 
@@
 {
-\begin{align}
-|\langle e, P_{:,j} \rangle| \leq \sqrt{2 \log p}
-\end{align}
+%
+\Disp{
+|\IP{ e, P_{:,j} }| \leq \sqrt{2 \log p}
+}
+%
 }
@@
 {
-\begin{align}
-\|P^\dagger P d\|_\infty
+%
+\Disp{
+\|P^\H P d\|_\infty
 \leq& 2 \sqrt{2 \log p}.
-\end{align}
 }
+%
+}
+
 To show this, start with
-\begin{align}
-\langle e -r, P_{:,j} \rangle
-=\langle P \hat{g} -P g, P_{:,j} \rangle
-=\langle P g, P_{:,j} \rangle
-\end{align}
+%
+\Disp{
+\IP{ z -(y -P h), P (:,n_y) }
+=\IP{ P \hat{g} -P g, P (:,n_y) }
+=\IP{ P g, P (:,n_y) }
+}
+%
 Result follows from triangle inequality, and Lemma ().
 
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
+From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result as below.
+The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
+Of course the interpretation of modulus and the inner product changes accordingly.
 
@@
 {
-\begin{align}
-\|d_A\|_2
-\leq \frac{1}{1-\delta} \|P^\dagger_{AB} P \eta\|_2 +\frac{\theta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
-\end{align}
+%
+\Disp{
+\|d_{\MC{A}}\|_2
+\leq \frac{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P \eta\|_2 +\frac{\vartheta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
+}
+%
 }
 
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
+From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result as below.
+Again, their proof works with complex vector spaces in place of real ones too.
 
@@
 {
-\begin{align}
+%
+\Disp{
 \|d\|_2^2
-\leq \|d_{AB}\|_2^2 +\frac{1}{L} \|d_C\|_1^2
-\end{align}
+\leq \|d_{\MC{A}\MC{B}}\|_2^2 +\frac{1}{L} \|d_{\MC{C}}\|_1^2
+}
+%
 }
 
-We can formulate our main theorem:
+We can formulate our main theorem.
 
-(To be done)
-
-\section{Simulation}
-
-With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
-
-As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\mathcal{R}(h)\).
-But it is not the end.
-In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-magic'' transforms DS into a linear program (LP), but that does not directly applies
-Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
-Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
-Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-magic''.
-
-\subsection{Transformation into Second Order Cone Problem}
-
-Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem.
-Recapitulate that, as we explained in the above, DS involves a 
-We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
-
-% % % % % % % % % % % % % % % %
-
-\section{Conclusion and Future Work}
-
-Firstly,
-Meanwhile, DS goes not without criticism for large complexity.
-Indeed it is clear, even from the primal-dual implementation above, that DS requires large dimensional vector
-
-Secondly
-And comparison of bounds of OMP and DS
-The author criticises the tendency of current literature to mix up results for DS and OMP without clear justification, since they are two quite different approaches to the compressed sensing problem.
-It is however not trivial to make meaningful comparison, since DS works with a RIP matrix, and OMP for Gaussian... the distinction is slight but definite...
-The author critizises In OMP we don't know whether the measurement matrix is the same as channel
-And OMP has stricter condition than DS
-Tao, however, specifies a noise relation
-
-Bounds of performance in different setting are often nontrivial to obtain, and one cannot think OMP, or indeed every algorithm, as a universal solution.
-OMP trades off precision for time complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
-All in all, different problems requires different technique and algorihm within the constraint at hand, as is probably true in every discipline of engineering.
-
-\section{References}
-
-References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.
-
-\begin{enumerate}
-
-\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6
-
-\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.
-5.
-
-\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}
-
-\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.98, No.6.
-
-\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
-
-\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
-
-\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.
-
-\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-
-\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.2.
-
-\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
-
-\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-
-\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.12.
-
-\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
-
-\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', \textit{IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.
-
-\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', \textit{IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.
-
-\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.\ 35, No.\ 6.
-
-\item Z Gao, L Dai, Z Wang, and S Chen (2015).
-``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.
-
-\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.
-
-\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.
-
-\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', \textit{IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.
-
-\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.
-
-\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.
-
-\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
-Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
-
-\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
-
-\end{enumerate}
-
-\end{document}
+{ \color{red} (To be done) }

### 2019-01-05 ongoing/report/sec_4_simulation.tex
Split files

--- 2018-12-31 ongoing/report/article.tex
@@
-\documentclass[12pt]{article}
+With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
 
-\usepackage{mathtools}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage[linkcolor=blue]{hyperref}
-\usepackage{xcolor}
-\usepackage[ocgcolorlinks]{ocgx2}
+As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\MC{R}(h)\).
+But it is not the end.
+In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
+Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
+Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
+Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-MAGIC''.
 
-\author{Tzu-Yu Jeng}
-\date{\today}
-\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
+\subsection{Transformation into Second Order Cone Problem}
 
-\newcounter{NumResult}
-\newcommand{\myCount}
-{
-   \stepcounter{NumResult}
-   \textbf{\arabic{NumResult}}
-}
+Since our setting is slightly different from ``\(\ell_1\)-MAGIC'', for completeness of exposition we write down derivation of the dual problem from the primal problem, as follows.
+Recapitulate that, as we explained in the above, DS involves the calculation of \(\ell_1\)-1 norm.
+This, for real vectors, can be transformed into a linear program (LP).
+But in the complex case, that becomes a quadratic expression of the real and imaginary part of the vector, and is no longer equivalent to an LP.
+Still, the comparison arising from primal-dual problem is not easily done in complex numbers, and we cast it into a real \(\ell_1\)-1 norm problem.
+Afterwards we will further transform the SOCP to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
+The bound in the previous section is valid, since in the course of transformation, nothing is lost or weakened.
 
-\newcommand {\Result} [2]
-{
-   \bigskip
-   \myCount \textbf{#1} \par
-   {#2} \par
-   \hfill \(\blacksquare\)
-   \bigskip
-}
-
-\begin{document}
-
-\maketitle
-
-\section{Acknowledgement}
-
-\section{Abstract}
-
-Multiple-input-multiple-output (MIMO) communication is widely expected to be the next-generation wireless communication scheme.
-However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
-It is then a non-trivial problem to estimate real-world wireless channels.
-
-Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
-If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing, an active area that has recently emerged.
-A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context.
-However, Orthogonal Matching Pursuit (OMP) later emerges as a low-complexity solution, and following-up literature usually used OMP rather than DS as a result.
-
-In this article, we utilize a hybrid structure at both transmitter and receiver end, each of them having both digital and analog percoders and combiners.
-We argue in favor of DS, and verify that DS is, as originally perceived, ideal in certain senses.
-DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, and as in its allowance of noise corruption.
-Moreover, we extend their proof to derive a stronger bound in the setting of estimation of millimeter wave channel for almost-sparse channel matrix
-
-We show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
-Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.
-
-\section{Introduction}
-
-This section is organized as follows.
-Before we start, we introduce our notation in the very beginning, since the literature survery quickly goes into technical details.
-And we first provide the motivation, and then overview the existent literature on channel estimation.
-Particularly, we will summerize present results on DS and OMP, and argue that DS is a viable solution that has been ignored, and then claim our contribution in this article that will be shown in the later sections.
-
-\subsection{Notation}
-
-Before we start, let us remind that, in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the classification may be different from its source.
-
-We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
-Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.
-
-Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
-Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
-
-\subsection{Background}
-
-Multiple-input multiple-output (MIMO) communication system has been proposed to be the next-generation specification.
-With a large number of antennae of both transmitter and receiver sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.
-But MIMO presents new obstacles as well.
-The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
-It is important to devise a feasible scheme, as the systems themselves are growing more complicated.
-Meanwhile, millimeter waves, having smaller wavelength, entails higher frequency bands, and thus wider available bandwith to be available.
-In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
-Consequently, this article considers MIMO in the millimeter r\`egime.
-
-The figure of merit of a MIMO system is usually considered to be the channel capacity.
-The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
-But that knowledge is hardly always available.
-What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
-It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
-Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
-
-Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
-Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
-With more antennae present, conventional training-based algorithm also increase in complexity and storage.
-In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
-A design of new algorithms that addressed these issues is thus in need.
-
-\subsection{Recovery of Sparse Vector in the Noiseless Case}
-
-It is a recent developemnt that the estimation of channels is facilitated by advances of compressed sensing.
-A series of paper by Cand\`es and Tao (2006) marks its advent.
-The idea is that, in many important statsitical applications, the number of variables or parameters \(p\) is much larger than the number of observations \(n\).
-In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?
-Of course, more assumption must be made to make the question meaningful.
-Cand\`es and Tao's pioneering work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
-They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
-Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
-
-They showed that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
+For convenience, define the following real representation function for complex vectors.
 
@@
 {
-\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
-\begin{gather} 
-\# \{\mathrm{supp}(x)\} \leq s
-\end{gather}
-That is, only at most \(s\) components of vector \(x\) is nonzero.
+For \(x \in \MB{V}(M)\), we say \(\MC{R}(x)\) is the real representation of \(x\), defined by
+%
+\Disp{
+\MC{R}(x) \in &\MB{V}(2M) \NT \\
+\MC{R}(x)(m) =
+&\begin{cases}
+\MF{Re}(\MC{R}(x)(m)), &m =2m' \\
+\MF{Im}(\MC{R}(x)(m)), &m =2m'+1
+\end{cases} \\
+m' =& 1, \dotsc, M \NT
 }
+%
+}
+
+A moment's reflection reveals the corresponding definition of real representation of matrices.
+
+\Result
+{Definition}
+{
+For \(A \in \MB{M}_{\MB{C}} (M_1, M_2)\), we say \(\MC{R}(A)\) is the real representation of \(A\), defined by
+%
+\Disp{
+A \in &\MB{V}_{\MB{R}} (2M_1, 2M_2) \NT \\
+A (m_1,m_2) =
+&\begin{cases}
+\MF{Re}(A (m_1,m_2)), &m_1 =2m_1'-1,\; m_2 =2m_2'-1  \\
+\MF{Im}(A (m_1,m_2)), &m_1 =2m_1',\; m_2 =2m_2'-1  \\
+-\MF{Im}(A (m_1,m_2)), &m_1 =2m_1'-1,\; m_2 =2m_2'  \\
+\MF{Re}(A (m_1,m_2)), &m_1 =2m_1',\; m_2 =2m_2'  \\
+\end{cases} \\
+m_1' = &1, \dotsc, m_1 \NT \\
+m_2' = &1, \dotsc, m_2 \NT
+}
+%
+}
+
+We continue the notation of program ().
+
+%
+\Disp{
+\V{\T{y}}
+=\MC{R}(y) \in \MB{V}(N_h) \\
+\V{\T{g}}
+=\MC{R}(g) \in \MB{V}(N_h) \\
+\M{\T{P}}
+=\MC{R}(\M{P}) \in \MB{M}_{\MB{C}} (2 N_y^2, 2 N_h^2)
+}
+%
+such that
+%
+\Disp{
+\V{\T{y}} =\M{\T{P}} \V{\T{g}} +\V{\T{z}}
+}
+%
+where by construction
+%
+\Disp{
+\V{\T{z}}
+=\MC{R}(\V{z}) \in \MB{V}(N_y)
+}
+%
+
+Finally, introduce these indicator matrices to identify the place where we want to take \(\ell_2\)-norm.
+
+%
+\Disp{
+I_{n_y}^{(y)} \in &\MB{M}_{\MB{C}} (N_y, N_y) \NT \\
+I_{n_y}^{(y)}(n_y')
+=&\begin{cases}
+1, &n_y' =2n_y \\
+1, &n_y' =2n_y +1 \\
+0, &\RM{otherwise}
+\end{cases} \\
+I_{n_h}^{(h)} \in &\MB{M}_{\MB{C}} (N_h, N_h) \NT \\
+I_{n_h}^{(h)}(n_h')
+=&\begin{cases}
+1, &n_h' =2n_h \\
+1, &n_h' =2n_h +1 \\
+0, &\RM{otherwise}
+\end{cases} \\
+n_y =&1, \dotsc, N_y \NT \\
+n_h =&1, \dotsc, N_h \NT
+}
+%
+
+If we introduce vector \(\V{m}\) to denote the entrywise complex modulus, we see that Program () now take the form
 
@@
 {
-Let \(A,y\) be given.
-Find \(x\) with
-\begin{gather}
-\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
-\mathrm{s.t.} \quad Ax =y
-\end{gather}
+   Given are \(\T{\M{P}}, \T{\V{y}}, \gamma\).
+Find \(\T{\V{g}}\) with
+%
+\Disp{
+&\min_{\T{\V{g}}, \V{m}} \IP{ \V{1}, \V{m} } \NT \\
+\RM{s.t.}
+&\begin{cases}
+\| I_{n_h}^{(h)} \T{\V{g}} \|_2
+\leq \IP{ \V{y}_{n_h}, \V{m} } \\
+\| I_{n_y}^{(y)} \T{\M{P}}^\H ( \T{\M{P}} \T{\V{g}} -\T{\V{y}} ) \|_2
+\leq \gamma  \\
+\end{cases}
+}
+%
+where \(\V{1}\) is the all-1 vector.
 }
 
-\Result
-{Theorem}
-{
-Let \(y =Ax\).
-Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
-That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
-\begin{gather}
-\delta_{S} +\delta_{2S} +\delta_{3S} <1
-\end{gather}
+The program, we see, is an SOCP.
+
+We further rewrite Program () into a stricter, extended block matrix form to make the point clearer.
+
+{ \color{red} (To be done) }
+
+\subsection{Primal-Dual Interior Point Algorithm}
+
+It remains to convert primal-dual interior point algorithm to make the SOCP easier to calculate.
+Of course it is not the only way to do this.
+We mention, again, Boyd and Vandenberghe (2004), \textit{Convex Optimization} chap.11 as a standard reference, and ``\(\ell_1\)-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.
+
+To clarify notation and for complentess of exposition, we derive the dual problem here.
+Start with the Lagrangian \(\MC{L}\), where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \(\ell_2\)-norm constraint.
+
+%
+\Disp{
+&\MC{L}(\V{m}, \T{g}, \mu^{(h)}, \mu^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NT \\
+=& \IP{ \V{1}, m } 
++\sum_{n_h} \big[ \IP{ \mu^{(h)}, I_{n_h}^{(h)} \T{g} } -\lambda^{(h)} \IP{ \V{y}_{n_h}, \V{m} } \big] \NT \\
+\quad & +\sum_{n_y} \big[ \IP{ \mu^{(h)}, I_{n_y}^{(y)} \T{P}^\H ( \T{P} \T{g} -\T{u} ) } -\lambda^{(h)} \gamma \big]
 }
+%
 
-\Result
-{Notation}
-{
-Let \(T \subset \mathbb{N}\).
-Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
-}
+\subsection{Discussion}
 
-\Result
-{Definition}.
-{
-Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
-For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
-\begin{gather}
-(1-\delta_S) \|\theta\|^2
-\leq \|X_T \theta\|_2^2
-\leq (1+\delta_S) \|\theta\|^2
-\end{gather}
-}
+On the other hand, DS goes not without criticism for large complexity of it (Friedlander and Saunders 2007).
+Indeed it is clear, even from the primal-dual implementation above, that DS requires memory for large dimensional vector, but OMP does not.
 
-RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).
-
-Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
-\begin{gather}
-| \langle X_T c, X_{T'} c' \rangle |
-\leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
-\end{gather}
-
-\subsection{The Dantzig Selector}
-
-Later Cand\`es and Tao  obtained a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006, which will be a main reference of this article), with a convex program called The Dantzig Selector they proposed (hencefore DS), they can recover the noisy case too.
-They argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
-From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
-Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
-
-For concreteness, consider a liear transformation with noise,
-\begin{gather}
-y =Ax +z
-\end{gather}
-where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
-How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
-
-\Result
-{Program}
-{
-Let \(A,y\) be given.
-Find \(x\) with
-\begin{gather}
-\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
-\end{gather}
-where \(r =y -A \hat{x}\).
-}
-And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.
-
-\subsection{Condition of RIP Linear Transformation}
-
-The constant \(\delta\) in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(A\) is fully unitary.
-
-Here, it is not clear at first what matrices serves as the RIP condition.
-But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.
-
-\Result
-{Theorem}
-{
-Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
-Then, with \(0 <\epsilon <1\),
-\begin{gather}
-   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
-   \leq 2 \exp(-n c_0(\epsilon))
-\end{gather}
-where we have
-\begin{gather}
-c_0(\epsilon)
-=\epsilon^2/4 -\epsilon^3/6.
-\end{gather}
-}
-
-\subsection{Compressed Channel Sensing}
-
-We have summarised results in compressed sensing, and we now relate the matter to the communication scenario.
-Recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
-Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
-Some scholars thus has applied compressive sensing techniques to the problem.
-
-One of the first papers, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
-What they explored was the estimation of single-antenna channel response with respect to time.
-Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability, providing the ground for the former paper.
-
-To explain the idea, consider a simplified scenario.
-Let \(x[t] \in \mathbb{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
-Consider a linear time-invariant channel with
-\begin{gather}
-y[t] =(x[t] \star h[t]) +z[t]
-\end{gather}
-where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
-Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
-\begin{gather}
-y =X h
-\end{gather}
-where \(X\) takes the form
-\begin{align}
-X
-=\begin{bmatrix}
-x_1, &0, &\cdots, &0 \\
-x_2, &x_1, &\cdots, &0 \\
-\vdots, &\vdots, &\ddots, &0 \\
-x_N, &x_{N-1}, &\cdots, &x_1
-\end{bmatrix}
-\end{align}
-We seek to get \(h\) in this undertermined system.
-
-Bajwa et.\ al.\ was able to show that \(X\) is RIP of overwhelmingly probability.
-
-\subsection{Orthogonal Matching Pursuit}
-
-Around that time, Tropp and A C Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit, that a i.i.d.\ matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.
-
-The setting here is \(y =Ax\), the noiseless, real-number case.
-Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
-We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).
-
-\Result
-{Algorithm}
-{
-\begin{enumerate}
-\item
-\end{enumerate}
-}
-
-\Result
-{Theorem}
-{
-   Following the setting described above, suppose, for \(0 <\delta <1\),
-\begin{gather}
-   M \geq 16s \log (N/\delta)
-\end{gather}
-Then   Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
-}
-
-For the proof, see the technical report: Tropp and A C Gilbert (2007a).
-
-It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
-Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
-To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
-Let signal \(x\) be sent, and \(y\) be receiverd, that is
-\begin{gather}
-y =WHF x
-\end{gather}
-
-\Result
-{Definition}
-{
-Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
-}
-
-\Result
-{Definition.}
-{
-For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
-Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
-}
-
-With (), scholars often exploit the relation
-\begin{gather}
-\mathrm{vec}(Y)
-=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
-\end{gather}
-
-The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
-The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.
-
-\subsection{Further development on CSS}
-
-The literature on CSS has since been vast, and we need not and cannot go through all of them here.
-Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.
-
-Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same support.
-
-Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm, using a (beam) code book with quantized AoA and AoD.
-
-Alkhateeb, Leus, and Heath Jr.\ (2015) poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
-They work simplified all-phase-shifter combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
-Their work mainly focuses on numerical simulation, rather than mathematical proof.
-
-Since the notice of hybrid beamforming, scholars have also applied the same idea to hybrid systems.
-Lee, Gil, and Lee (2016) considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
-The beambook phase is quantized, which may have been a source of error, and they have specifed a particular grid set of angles and argues the superiority.
-One of their simulations experiments utilizes DFT and permutated DFT matrix, instead of as originally suggested by Tropp and Gilbert (2007).
-
-Meanwhile, the improvement of OMP bound is also going on.
-Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
-Indeed, MIP deals with correlation of columns of the sensing matrix, rather than the almost-unitarity, making the condition easier to verify.
-
-Ben-Haim et.\ al.\ (2010) follow up their work and refine their bounds, also considering MIP conditions.
-They conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
-Still, since the setting of OMP and DS is rather different, it remains unclear which of is better.
-
-Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ (2010) as the main foundation for OMP perfomance bound.
-
-Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices in a modified basis pursuit problem.
-
-\subsection{Contribution}
-
-We remark several observation on past literature, that has been, to the best of our knowledge, lacking or less than ideal.
-
-\begin{enumerate}
-\item As said, previous work the favor on OMP rather than DS (let alone other sparse algorithm) is evident.
-\item In view of The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than Cand\`es and Tao (2007).
-\item Previous work only takes the assumption on the bound of the norm of the channel matrix to be granted.
-\item Likewise, such probability bounds on the sparsity of the channel as involving, say, number of channel paths and vector of array response has not be explored.
-\end{enumerate}
-
-We consider a system model where both digital and analog beamformer are i.i.d.\ random matrix combiner that serve readily as the sensing matrix satisfying the RIP property.
-We apply a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
-Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.
-
-Our contribution include:
-
-\begin{enumerate}
-\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
-\item We do not assume that the virtual channel model is naturally quantized in its angle of departure and of arrival, thus removes concern of the quantization error within the proof.
-\item Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
-\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
-\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
-\end{enumerate}
-
-\section{Problem Setting}
-
-\subsection{Channel Model}
-
-Since expression involving probability will get very complecated, introduce the direct product
-%
-\begin{gather}
-\Omega
-=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
-\end{gather}
-%
-to denote the overall sample space, where
-%
-\begin{itemize}
-\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
-\item \(\Omega_h\) denotes that of the communication channel,
-\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
-\item \(\Omega_r\) denotes that at the receiver end.
-\end{itemize}
-%
-\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.
-
-We restrict our consideration to the uniform linear array, which can be modeled as
-\begin{gather}
-\mathbf{a}(\phi')
-=\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
-\end{gather}
-where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.
-
-And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}\big( \frac{d}{\lambda} \sin \phi_l' \big) \mathbf{a}\big( \frac{d}{\lambda} \sin \theta_l' \big)^\dagger
-\end{gather}
-The physical meaning of \(\theta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\theta_l\), the \(l\)-th that of arrival wave.
-
-For our purpose, we may absorb the argument of \(\mathbf{a}\) as
-\begin{gather}
-\phi_l
-=\frac{d}{\lambda} \sin \phi_l' \\
-\theta_l
-=\frac{d}{\lambda} \sin \theta_l'
-\end{gather}
-to get a simpler form
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
-\end{gather}
-
-Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.
-
-\Result
-{Definition.}
-{
-Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
-We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
-\begin{gather}
-\mathbf{u} =\dagger F \mathbf{v}
-\end{gather}
-where each entry of the matrix \(K\) is defined to be
-\begin{gather}
-   K(m,n) =\frac{1}{\sqrt{N}} e^{2\pi imn/N},
-\quad m,n =0,1,2,\dotsc, N-1
-\end{gather}
-where \(i =\sqrt{-1}\).
-}
-
-\subsection{System Model}
-
-We consider the situation with a hybrid structure at both transmitter and receiver end.
-Each end consists of both digital and analog percoders and combiners.
-In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
-Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
-Recall that analog precoder is restricted to have value with magnitude being unity.
-To set up notation, we list them as below.
-\begin{gather}
-F_B \in \mathbb{R}^{N_r \cdot N_s} \\
-F_R \in \mathbb{R}^{N_h \cdot N_r}, |F_R(i,j)| =1 \\
-F_B \in \mathbb{R}^{N_r \cdot N_h} \\
-F_B \in \mathbb{R}^{N_s \cdot N_r}, |F_R(i,j)| =1.
-\end{gather}
-And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
-Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.
-
-In summary, the effective channel may be written as
-\begin{gather}
-U (\omega_h, \omega_e)
-:=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
-\end{gather}
-Supress the probabilistic index for simplicity, we restate the same equation as
-\begin{gather}
-Y
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z )
-\end{gather}
-
-\subsection{Proposed Method}
-
-The effective channel \(U\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
-This way, we may denote the acquired effective channel matrix \(U\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
-\begin{gather}
-Y_{:,n}
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-The crux of the matter is the recovery of \(H\) with knowledge of \(U\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
-
-Following previous work on CSS, we write
-\begin{gather}
-h := \mathrm{vec}(H) \\
-u := \mathrm{vec}(U) \\
-A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
-\end{gather}
-to formulate our goal as sparse recovery problem of \(\mathrm{vec}(H)\).
-But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
-What shall we do?
-
-Observe that, if we write
-\begin{gather}
-G =K^\dagger H
-\end{gather}
-as the spatial frequency domain representation of \(H\), then
-\begin{gather}
-Y
-:=W_B W_R K ( G F_R F_B +K^\dagger z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
-To the best of our knowledge, no work has explicitly considered the beamspace CSS.
-
-That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
-\begin{gather}
-\mathrm{vec}(Y)
-\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \mathrm{vec}(H)
-\end{gather}
-To simplify notation, set 
-\begin{gather}
-P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
-\end{gather}
-The instances of \(P\) is completely determined in the transmitter and receiver end, that is
-\begin{gather}
-P =P(\omega_t, \omega_r)
-\end{gather}
-If so, our program reads
-
-\Result
-{Program}
-{
-Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
-Suppose \(U\) is the acquired effective channel matrix under noisy observation.
-\(A\) is defined just above in ().
-Set
-\begin{gather}
-r =u -P h
-\end{gather}
-Then, with parameter \(\gamma\) specified, define the following program
-\begin{gather}
-\hat{g}
-=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
-\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
-\end{gather}
-And convert \(\hat{g}\) back to the space domain as
-\begin{gather}
-\hat{h}
-=K^\dagger \hat{g}.
-\end{gather}
-And finally recover the estimated \(H\) as
-\begin{gather}
-\hat{H} =\mathrm{vec}^{-1} (\hat{h})
-\end{gather}
-}
-
-It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
-
-\section{Results and Proofs}
-
-We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \(g \in \mathbb{R}^{N_H^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
-
-We first establish a technical lemma that shows \(\mathrm{supp}(g)\) has roughly cardinal \(L\).
-At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
-
-Consider
-\begin{gather}
-d =g -\hat{g}
-\end{gather}
-And let
-\begin{itemize}
-\item \(\mathcal{A}\) be the largest \(L\) position of \(g\).
-\item \(\mathcal{B}\) be the largest \(L\) position of \(d\) except on \(\mathcal{A}\).
-\item \(\mathcal{C} =\{1, \dotsc, N_H^2\} -( \mathcal{B} \cup \mathcal{C} )\), i.e., the complementary index set.
-\end{itemize}
-So \(\mathcal{A}, \mathcal{B}, \mathcal{C}\) are mutually exclusive index sets by construction:
-\begin{gather}
-\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \{1, \dotsc, N_H^2\} \\
-\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\
-A \cup B \cup C =\{1, \dotsc, N\}.
-\end{gather}
-
-\Result
-{Lemma.}
-{
-Let \(\phi(\omega_h)\) and \(\theta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
-\begin{gather}
-\|g\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
-\end{gather}
-
-To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
-\begin{align}
-S(\phi)
-:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
-\quad 0 \leq \phi \leq \pi
-\end{align}
-By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
-\begin{align}
-S(\phi)
-\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\ \notag
-=& \frac{-48}{\phi^3 -24\phi}
-\quad 0 \leq \phi \leq \pi,
-\end{align}
-
-The fraction above can be bounded.
-
-By the same token, more generally,
-\begin{align}
-&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\ \notag
-=&\frac{1}{N} S(\pi \phi') \\ \notag
-\leq& \frac{48}{N \pi^3 (\phi'^3 -24 \phi' /\pi^2)}
-\end{align}
-where \(\phi' =k/N -\phi/2\pi\), and the cubic expression is split.
-We wish to bound the tail of \(S(\pi \phi')\), and apply the na\"ive bound
-\begin{align}
-&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\phi'^3 -24 \phi' /\pi^2}
- d\phi' \\ \notag
-=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\ \notag
-\leq& \frac{1}{\pi^2} \log \frac{L}{N}
-\end{align}
-Here, the integral in the first line is immediate.
-The second term in the bracket is smaller than 0 and is dropped in the last inequality.
-}
-
-The bound is satisfying enough, though refinement is surely possible.
-Indeed, \(\log L/N \to 0\) as \(N \to \infty\) and limited by the number of paths \(L\).
-
-The rest follows ``The Dantzig Selector'' very closely.
-
-\Result
-{Proposition}
-{
-Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in ().
-Then
-\begin{align}
-\|d_{BC}\|_1
-\leq \|d_A\|_1 +\|g_{BC}\|_1
-\end{align}
-}
-To show this, observe
-\begin{align}
-\|g\|_1 -\|d_A\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1
-\leq& \|g +d\|_1 \\ \notag
-\leq& \|g\|_1
-\end{align}
-In the first line, we recall \(g =g_A\).
-
-\Result
-{Lemma}
-{
-\begin{align}
-|\langle e, P_{:,j} \rangle| \leq \sqrt{2 \log p}
-\end{align}
-}
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|P^\dagger P d\|_\infty
-\leq& 2 \sqrt{2 \log p}.
-\end{align}
-}
-To show this, start with
-\begin{align}
-\langle e -r, P_{:,j} \rangle
-=\langle P \hat{g} -P g, P_{:,j} \rangle
-=\langle P g, P_{:,j} \rangle
-\end{align}
-Result follows from triangle inequality, and Lemma ().
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|d_A\|_2
-\leq \frac{1}{1-\delta} \|P^\dagger_{AB} P \eta\|_2 +\frac{\theta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
-\end{align}
-}
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|d\|_2^2
-\leq \|d_{AB}\|_2^2 +\frac{1}{L} \|d_C\|_1^2
-\end{align}
-}
-
-We can formulate our main theorem:
-
-(To be done)
-
-\section{Simulation}
-
-With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
-
-As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\mathcal{R}(h)\).
-But it is not the end.
-In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-magic'' transforms DS into a linear program (LP), but that does not directly applies
-Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
-Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
-Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-magic''.
-
-\subsection{Transformation into Second Order Cone Problem}
-
-Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem.
-Recapitulate that, as we explained in the above, DS involves a 
-We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
-
-% % % % % % % % % % % % % % % %
-
-\section{Conclusion and Future Work}
-
-Firstly,
-Meanwhile, DS goes not without criticism for large complexity.
-Indeed it is clear, even from the primal-dual implementation above, that DS requires large dimensional vector
-
-Secondly
-And comparison of bounds of OMP and DS
-The author criticises the tendency of current literature to mix up results for DS and OMP without clear justification, since they are two quite different approaches to the compressed sensing problem.
-It is however not trivial to make meaningful comparison, since DS works with a RIP matrix, and OMP for Gaussian... the distinction is slight but definite...
-The author critizises In OMP we don't know whether the measurement matrix is the same as channel
-And OMP has stricter condition than DS
-Tao, however, specifies a noise relation
-
-Bounds of performance in different setting are often nontrivial to obtain, and one cannot think OMP, or indeed every algorithm, as a universal solution.
-OMP trades off precision for time complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
-All in all, different problems requires different technique and algorihm within the constraint at hand, as is probably true in every discipline of engineering.
-
-\section{References}
-
-References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.
-
-\begin{enumerate}
-
-\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6
-
-\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.
-5.
-
-\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}
-
-\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.98, No.6.
-
-\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
-
-\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
-
-\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.
-
-\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-
-\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.2.
-
-\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
-
-\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-
-\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.12.
-
-\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
-
-\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', \textit{IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.
-
-\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', \textit{IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.
-
-\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.\ 35, No.\ 6.
-
-\item Z Gao, L Dai, Z Wang, and S Chen (2015).
-``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.
-
-\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.
-
-\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.
-
-\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', \textit{IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.
-
-\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.
-
-\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.
-
-\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
-Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
-
-\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
-
-\end{enumerate}
-
-\end{document}
+And a meaningful comparison of bounds of OMP and DS is not easy, as their settings are somewhat different.
+The author thus criticises the tendency of current literature to mix up results for DS and OMP without clear justification.
+Indeed, DS calls for a RIP matrix and guarantees such performance even in noisy observation (Cand\`es and Tao 2005, 2007), while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
+On the other hand, as of OMP, besides the original justification of entrywise i.i.d.\ Gaussian sensing matrix (Tropp and Gilbert 2007a), and existent attempt to characterize MIP condition, there is much to be done OMP for Gaussian.

### 2019-01-05 ongoing/report/sec_5_back_matter.tex
Split files

--- 2018-12-31 ongoing/report/article.tex
@@
-\documentclass[12pt]{article}
+\subsection{Conclusion}
 
-\usepackage{mathtools}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage[linkcolor=blue]{hyperref}
-\usepackage{xcolor}
-\usepackage[ocgcolorlinks]{ocgx2}
+This article addresses the problem of effective and estimation of the millimeter wave channel by exploiting its sparsity.
+We motivated the problem, and provided a rather broad survey of recent literature.
+This article adopts The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
+Beside exploiting the sparsity of space domain representation as existing literature does, we proceed the estimation algorithm in the spatial frequency domain.
+The technique is surely inspiring to future work, as many bounds are ready to be obtained once we change the physical model of the channel.
+In addition, we have, as a secondary product, derived the generalization of DS for complex vectors.
 
-\author{Tzu-Yu Jeng}
-\date{\today}
-\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
+Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Cand\`es and Tao (2007), that the probability that the expected square error is bounded is overwhelming.
+We thus have derived a probability bound of performance on a fairly general setting, where the bounding constant is expressed as an explicit function of physical parameters, such as the number of path.
 
-\newcounter{NumResult}
-\newcommand{\myCount}
-{
-   \stepcounter{NumResult}
-   \textbf{\arabic{NumResult}}
-}
+Afterwards we transformed DS into an SOCP, which is quite different as in the original DS (where we have an LP instead).
+Simulation is done, and DS's performance is compared to OMP.
+{ \color{red} (To be done) }
 
-\newcommand {\Result} [2]
-{
-   \bigskip
-   \myCount \textbf{#1} \par
-   {#2} \par
-   \hfill \(\blacksquare\)
-   \bigskip
-}
+We cannot think OMP, or indeed every algorithm, as a universal solution.
+OMP trades off precision for time and space complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
+All in all, different problems requires different technique and algorihm within the current constraint, as is probably true in every discipline of engineering.
 
-\begin{document}
-
-\maketitle
-
-\section{Acknowledgement}
-
-\section{Abstract}
-
-Multiple-input-multiple-output (MIMO) communication is widely expected to be the next-generation wireless communication scheme.
-However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
-It is then a non-trivial problem to estimate real-world wireless channels.
-
-Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
-If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing, an active area that has recently emerged.
-A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context.
-However, Orthogonal Matching Pursuit (OMP) later emerges as a low-complexity solution, and following-up literature usually used OMP rather than DS as a result.
-
-In this article, we utilize a hybrid structure at both transmitter and receiver end, each of them having both digital and analog percoders and combiners.
-We argue in favor of DS, and verify that DS is, as originally perceived, ideal in certain senses.
-DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, and as in its allowance of noise corruption.
-Moreover, we extend their proof to derive a stronger bound in the setting of estimation of millimeter wave channel for almost-sparse channel matrix
-
-We show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
-Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.
-
-\section{Introduction}
-
-This section is organized as follows.
-Before we start, we introduce our notation in the very beginning, since the literature survery quickly goes into technical details.
-And we first provide the motivation, and then overview the existent literature on channel estimation.
-Particularly, we will summerize present results on DS and OMP, and argue that DS is a viable solution that has been ignored, and then claim our contribution in this article that will be shown in the later sections.
-
-\subsection{Notation}
-
-Before we start, let us remind that, in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the classification may be different from its source.
-
-We restrict our discussion to the Hilbert space over the field of \(\mathbb{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
-Boldface lower case Latin alphabets, like \(\mathbf{a}\), denote vectors, and boldface upper case Latin alphabets, like \(\mathbf{A}\), denote matrices.
-
-Denote \(\mathbb{E}(X)[\cdot]\) the probability, \(\mathbb{E}(X)[\cdot]\) the expectation, \(\mathbb{Var}(X)[\cdot]\) the variance.
-Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\mathbb{P}\) and \(\mathbb{E}\).
-
-\subsection{Background}
-
-Multiple-input multiple-output (MIMO) communication system has been proposed to be the next-generation specification.
-With a large number of antennae of both transmitter and receiver sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.
-But MIMO presents new obstacles as well.
-The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
-It is important to devise a feasible scheme, as the systems themselves are growing more complicated.
-Meanwhile, millimeter waves, having smaller wavelength, entails higher frequency bands, and thus wider available bandwith to be available.
-In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
-Consequently, this article considers MIMO in the millimeter r\`egime.
-
-The figure of merit of a MIMO system is usually considered to be the channel capacity.
-The capacity \(C\) of a MIMO channel \(H\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\mathrm{SNR})\).
-But that knowledge is hardly always available.
-What makes things more difficult is the case that \(H\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
-It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
-Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\mathrm{SNR})\).
-
-Therefore the real-time estimation, \(\hat{H}\), of \(H\) is of paramount importance.
-Needless to say, when the \(\hat{H}\) is imprecise, resulting analysis is also undermined.
-With more antennae present, conventional training-based algorithm also increase in complexity and storage.
-In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
-A design of new algorithms that addressed these issues is thus in need.
-
-\subsection{Recovery of Sparse Vector in the Noiseless Case}
-
-It is a recent developemnt that the estimation of channels is facilitated by advances of compressed sensing.
-A series of paper by Cand\`es and Tao (2006) marks its advent.
-The idea is that, in many important statsitical applications, the number of variables or parameters \(p\) is much larger than the number of observations \(n\).
-In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?
-Of course, more assumption must be made to make the question meaningful.
-Cand\`es and Tao's pioneering work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
-They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
-Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
-
-They showed that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
-
-\Result
-{Definition}
-{
-\(x \in \mathbb{R}^N\) is called \(s\)-sparse, if
-\begin{gather} 
-\# \{\mathrm{supp}(x)\} \leq s
-\end{gather}
-That is, only at most \(s\) components of vector \(x\) is nonzero.
-}
-
-\Result
-{Program}
-{
-Let \(A,y\) be given.
-Find \(x\) with
-\begin{gather}
-\mathrm{min}_{x' \in \mathbb{R}^N} \quad \|x'\|_1
-\mathrm{s.t.} \quad Ax =y
-\end{gather}
-}
-
-\Result
-{Theorem}
-{
-Let \(y =Ax\).
-Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
-That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
-\begin{gather}
-\delta_{S} +\delta_{2S} +\delta_{3S} <1
-\end{gather}
-}
-
-\Result
-{Notation}
-{
-Let \(T \subset \mathbb{N}\).
-Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
-}
-
-\Result
-{Definition}.
-{
-Let \(X\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
-For each integer \(S \in \mathbb{N}\), we say that \(X\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(\theta\) with \(\|\theta\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
-\begin{gather}
-(1-\delta_S) \|\theta\|^2
-\leq \|X_T \theta\|_2^2
-\leq (1+\delta_S) \|\theta\|^2
-\end{gather}
-}
-
-RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\theta_S\).
-
-Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\theta_{S,S'}\) be the smallest constant such that
-\begin{gather}
-| \langle X_T c, X_{T'} c' \rangle |
-\leq \theta_{S,S'} \cdot \| c \|_2 \|c'\|_2
-\end{gather}
-
-\subsection{The Dantzig Selector}
-
-Later Cand\`es and Tao  obtained a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006, which will be a main reference of this article), with a convex program called The Dantzig Selector they proposed (hencefore DS), they can recover the noisy case too.
-They argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
-From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
-Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
-
-For concreteness, consider a liear transformation with noise,
-\begin{gather}
-y =Ax +z
-\end{gather}
-where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
-How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
-
-\Result
-{Program}
-{
-Let \(A,y\) be given.
-Find \(x\) with
-\begin{gather}
-\min_{x' \in \mathbb{R}^p}  \|\hat{x'}\|_1 \\ \notag
-\mathrm{subject}\; \mathrm{to} \quad \|A^\dagger r\|_\infty \leq \lambda_p \sigma
-\end{gather}
-where \(r =y -A \hat{x}\).
-}
-And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.
-
-\subsection{Condition of RIP Linear Transformation}
-
-The constant \(\delta\) in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(A\) is fully unitary.
-
-Here, it is not clear at first what matrices serves as the RIP condition.
-But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.
-
-\Result
-{Theorem}
-{
-Let each entry of random matrix \(A \in \mathbb{R}^{M \cdot N}\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
-Then, with \(0 <\epsilon <1\),
-\begin{gather}
-   \mathbb{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
-   \leq 2 \exp(-n c_0(\epsilon))
-\end{gather}
-where we have
-\begin{gather}
-c_0(\epsilon)
-=\epsilon^2/4 -\epsilon^3/6.
-\end{gather}
-}
-
-\subsection{Compressed Channel Sensing}
-
-We have summarised results in compressed sensing, and we now relate the matter to the communication scenario.
-Recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
-Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
-Some scholars thus has applied compressive sensing techniques to the problem.
-
-One of the first papers, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
-What they explored was the estimation of single-antenna channel response with respect to time.
-Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability, providing the ground for the former paper.
-
-To explain the idea, consider a simplified scenario.
-Let \(x[t] \in \mathbb{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
-Consider a linear time-invariant channel with
-\begin{gather}
-y[t] =(x[t] \star h[t]) +z[t]
-\end{gather}
-where \(h[t] \in \mathbb{R}^L\) is the channel's impulse response, \(x[t] \in \mathbb{R}^N\) as the input, \(y[t] \in \mathbb{R}^N\) as the output, and \(z[t] \in \mathbb{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
-Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
-\begin{gather}
-y =X h
-\end{gather}
-where \(X\) takes the form
-\begin{align}
-X
-=\begin{bmatrix}
-x_1, &0, &\cdots, &0 \\
-x_2, &x_1, &\cdots, &0 \\
-\vdots, &\vdots, &\ddots, &0 \\
-x_N, &x_{N-1}, &\cdots, &x_1
-\end{bmatrix}
-\end{align}
-We seek to get \(h\) in this undertermined system.
-
-Bajwa et.\ al.\ was able to show that \(X\) is RIP of overwhelmingly probability.
-
-\subsection{Orthogonal Matching Pursuit}
-
-Around that time, Tropp and A C Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit, that a i.i.d.\ matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.
-
-The setting here is \(y =Ax\), the noiseless, real-number case.
-Same as before, let \(y \in \mathbb{R}^{M}\), \(x \in \mathbb{R}^{N}\) which is \(s\)-sparse, while \(M \ll N\).
-We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).
-
-\Result
-{Algorithm}
-{
-\begin{enumerate}
-\item
-\end{enumerate}
-}
-
-\Result
-{Theorem}
-{
-   Following the setting described above, suppose, for \(0 <\delta <1\),
-\begin{gather}
-   M \geq 16s \log (N/\delta)
-\end{gather}
-Then   Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
-}
-
-For the proof, see the technical report: Tropp and A C Gilbert (2007a).
-
-It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
-Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
-To see this, let \(F\) be the precoder and \(W\) the combiner, and \(H\) the channel, and consider the noiseless case.
-Let signal \(x\) be sent, and \(y\) be receiverd, that is
-\begin{gather}
-y =WHF x
-\end{gather}
-
-\Result
-{Definition}
-{
-Define \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) to be the vectorization of \(A \in \mathbb{M}(n,m)\).
-}
-
-\Result
-{Definition.}
-{
-For \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\) and \(\mathrm{vec}(A) \in \mathbb{M}(n,m)\)
-Define the Kronecker product \(\mathrm{vec}(A) \in \mathbb{R}^{nm}\) 
-}
-
-With (), scholars often exploit the relation
-\begin{gather}
-\mathrm{vec}(Y)
-=\big[ (F^\dagger) \otimes W \big] \mathrm{vec}(H)
-\end{gather}
-
-The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
-The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.
-
-\subsection{Further development on CSS}
-
-The literature on CSS has since been vast, and we need not and cannot go through all of them here.
-Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.
-
-Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same support.
-
-Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm, using a (beam) code book with quantized AoA and AoD.
-
-Alkhateeb, Leus, and Heath Jr.\ (2015) poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
-They work simplified all-phase-shifter combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
-Their work mainly focuses on numerical simulation, rather than mathematical proof.
-
-Since the notice of hybrid beamforming, scholars have also applied the same idea to hybrid systems.
-Lee, Gil, and Lee (2016) considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
-The beambook phase is quantized, which may have been a source of error, and they have specifed a particular grid set of angles and argues the superiority.
-One of their simulations experiments utilizes DFT and permutated DFT matrix, instead of as originally suggested by Tropp and Gilbert (2007).
-
-Meanwhile, the improvement of OMP bound is also going on.
-Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
-Indeed, MIP deals with correlation of columns of the sensing matrix, rather than the almost-unitarity, making the condition easier to verify.
-
-Ben-Haim et.\ al.\ (2010) follow up their work and refine their bounds, also considering MIP conditions.
-They conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
-Still, since the setting of OMP and DS is rather different, it remains unclear which of is better.
-
-Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ (2010) as the main foundation for OMP perfomance bound.
-
-Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices in a modified basis pursuit problem.
-
-\subsection{Contribution}
-
-We remark several observation on past literature, that has been, to the best of our knowledge, lacking or less than ideal.
-
-\begin{enumerate}
-\item As said, previous work the favor on OMP rather than DS (let alone other sparse algorithm) is evident.
-\item In view of The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than Cand\`es and Tao (2007).
-\item Previous work only takes the assumption on the bound of the norm of the channel matrix to be granted.
-\item Likewise, such probability bounds on the sparsity of the channel as involving, say, number of channel paths and vector of array response has not be explored.
-\end{enumerate}
-
-We consider a system model where both digital and analog beamformer are i.i.d.\ random matrix combiner that serve readily as the sensing matrix satisfying the RIP property.
-We apply a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
-Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.
-
-Our contribution include:
-
-\begin{enumerate}
-\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
-\item We do not assume that the virtual channel model is naturally quantized in its angle of departure and of arrival, thus removes concern of the quantization error within the proof.
-\item Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
-\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
-\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
-\end{enumerate}
-
-\section{Problem Setting}
-
-\subsection{Channel Model}
-
-Since expression involving probability will get very complecated, introduce the direct product
-%
-\begin{gather}
-\Omega
-=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
-\end{gather}
-%
-to denote the overall sample space, where
-%
-\begin{itemize}
-\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
-\item \(\Omega_h\) denotes that of the communication channel,
-\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
-\item \(\Omega_r\) denotes that at the receiver end.
-\end{itemize}
-%
-\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.
-
-We restrict our consideration to the uniform linear array, which can be modeled as
-\begin{gather}
-\mathbf{a}(\phi')
-=\sum_{n=1}^{N} e^{n \phi' i} \mathbf{u}_n
-\end{gather}
-where \(i\) is the imaginary unit, \(\mathbf{u}_n\) is the unit vector of the \(n\)-th component.
-
-And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}\big( \frac{d}{\lambda} \sin \phi_l' \big) \mathbf{a}\big( \frac{d}{\lambda} \sin \theta_l' \big)^\dagger
-\end{gather}
-The physical meaning of \(\theta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\theta_l\), the \(l\)-th that of arrival wave.
-
-For our purpose, we may absorb the argument of \(\mathbf{a}\) as
-\begin{gather}
-\phi_l
-=\frac{d}{\lambda} \sin \phi_l' \\
-\theta_l
-=\frac{d}{\lambda} \sin \theta_l'
-\end{gather}
-to get a simpler form
-\begin{gather}
-H
-=\sum_{l=0}^L \alpha_l \mathbf{a}(\phi_l) \mathbf{a}(\theta_l)^\dagger
-\end{gather}
-
-Moreover, let the convention for discrete Fourier transform be adopted as below for completeness of presentation.
-
-\Result
-{Definition.}
-{
-Let \(\mathbf{v} \in \mathbb{R}^m\) be given.
-We say \(u \in \mathbb{R}^m\) is the discrete Fourier transform of \(\mathbf{v}\), if
-\begin{gather}
-\mathbf{u} =\dagger F \mathbf{v}
-\end{gather}
-where each entry of the matrix \(K\) is defined to be
-\begin{gather}
-   K(m,n) =\frac{1}{\sqrt{N}} e^{2\pi imn/N},
-\quad m,n =0,1,2,\dotsc, N-1
-\end{gather}
-where \(i =\sqrt{-1}\).
-}
-
-\subsection{System Model}
-
-We consider the situation with a hybrid structure at both transmitter and receiver end.
-Each end consists of both digital and analog percoders and combiners.
-In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
-Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
-Recall that analog precoder is restricted to have value with magnitude being unity.
-To set up notation, we list them as below.
-\begin{gather}
-F_B \in \mathbb{R}^{N_r \cdot N_s} \\
-F_R \in \mathbb{R}^{N_h \cdot N_r}, |F_R(i,j)| =1 \\
-F_B \in \mathbb{R}^{N_r \cdot N_h} \\
-F_B \in \mathbb{R}^{N_s \cdot N_r}, |F_R(i,j)| =1.
-\end{gather}
-And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
-Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.
-
-In summary, the effective channel may be written as
-\begin{gather}
-U (\omega_h, \omega_e)
-:=W_B W_R ( H(\omega_h) F_R F_B \mathbf{u}_m +z(\omega_z) )
-\end{gather}
-Supress the probabilistic index for simplicity, we restate the same equation as
-\begin{gather}
-Y
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z )
-\end{gather}
-
-\subsection{Proposed Method}
-
-The effective channel \(U\) has \(N\) columns, but to estimate it, we may agree to send one pilot signal at one time, which consists of only one antenna sending signal, namely \(\mathbf{u}_n\).
-This way, we may denote the acquired effective channel matrix \(U\) under noisy observation as (borrowing Matlab's colon notation to denote submatrix)
-\begin{gather}
-Y_{:,n}
-:=W_B W_R ( H F_R F_B \mathbf{u}_m +z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-The crux of the matter is the recovery of \(H\) with knowledge of \(U\), and of course \(W_R, W_B, F_R, F_B\) which are in our control.
-
-Following previous work on CSS, we write
-\begin{gather}
-h := \mathrm{vec}(H) \\
-u := \mathrm{vec}(U) \\
-A =(K^\dagger F_R F_B) \otimes (W_B W_R K)
-\end{gather}
-to formulate our goal as sparse recovery problem of \(\mathrm{vec}(H)\).
-But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
-What shall we do?
-
-Observe that, if we write
-\begin{gather}
-G =K^\dagger H
-\end{gather}
-as the spatial frequency domain representation of \(H\), then
-\begin{gather}
-Y
-:=W_B W_R K ( G F_R F_B +K^\dagger z ), \quad
-n =1, 2, \dotsc, N_B
-\end{gather}
-If at the end of day, \(G\) is sparse, then we recover \(G\) instead, and our use of DS is fully justified.
-To the best of our knowledge, no work has explicitly considered the beamspace CSS.
-
-That is to say, \(K^\dagger z\) may be absorbed, and a similar Kronecker product may be used.
-\begin{gather}
-\mathrm{vec}(Y)
-\approx \big[ (F_B^\dagger F_R^\dagger) \otimes (W_B W_R K) \big] \mathrm{vec}(H)
-\end{gather}
-To simplify notation, set 
-\begin{gather}
-P =(F_B^\dagger F_R^\dagger) \otimes (W_B W_R K)
-\end{gather}
-The instances of \(P\) is completely determined in the transmitter and receiver end, that is
-\begin{gather}
-P =P(\omega_t, \omega_r)
-\end{gather}
-If so, our program reads
-
-\Result
-{Program}
-{
-Let \(H(\omega_h, \omega_n)\) be the virtual channel, and \(W_R(\omega_r)\) the random analog combiner, \(W_B(\omega_r)\) the random analog combiner, \(F_R(\omega_t)\) the random analog combiner, \(F_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
-Suppose \(U\) is the acquired effective channel matrix under noisy observation.
-\(A\) is defined just above in ().
-Set
-\begin{gather}
-r =u -P h
-\end{gather}
-Then, with parameter \(\gamma\) specified, define the following program
-\begin{gather}
-\hat{g}
-=\underset {{h}} {\mathrm{min}} \|h\|_1 \quad
-\mathrm{s.t.}\;\; \|A^\dagger r\|_\infty \leq \gamma
-\end{gather}
-And convert \(\hat{g}\) back to the space domain as
-\begin{gather}
-\hat{h}
-=K^\dagger \hat{g}.
-\end{gather}
-And finally recover the estimated \(H\) as
-\begin{gather}
-\hat{H} =\mathrm{vec}^{-1} (\hat{h})
-\end{gather}
-}
-
-It will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
-
-\section{Results and Proofs}
-
-We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \(g \in \mathbb{R}^{N_H^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
-
-We first establish a technical lemma that shows \(\mathrm{supp}(g)\) has roughly cardinal \(L\).
-At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
-
-Consider
-\begin{gather}
-d =g -\hat{g}
-\end{gather}
-And let
-\begin{itemize}
-\item \(\mathcal{A}\) be the largest \(L\) position of \(g\).
-\item \(\mathcal{B}\) be the largest \(L\) position of \(d\) except on \(\mathcal{A}\).
-\item \(\mathcal{C} =\{1, \dotsc, N_H^2\} -( \mathcal{B} \cup \mathcal{C} )\), i.e., the complementary index set.
-\end{itemize}
-So \(\mathcal{A}, \mathcal{B}, \mathcal{C}\) are mutually exclusive index sets by construction:
-\begin{gather}
-\mathcal{A}, \mathcal{B}, \mathcal{C} \subset \{1, \dotsc, N_H^2\} \\
-\mathcal{A} \cap \mathcal{B} =B \cap C =A \cap C =\varnothing \\
-A \cup B \cup C =\{1, \dotsc, N\}.
-\end{gather}
-
-\Result
-{Lemma.}
-{
-Let \(\phi(\omega_h)\) and \(\theta(\omega_h)\) be both uniformly, independently distributed in \([0,2\pi)\), and beamspace channel matrix \(G\) defined as in ().
-\begin{gather}
-\|g\|_1 \leq \frac{1}{\pi^2} \log \frac{L}{N}.
-\end{gather}
-
-To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
-\begin{align}
-S(\phi)
-:=&\left| \sum_{n=0}^{N-1} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin(N \phi/2)|}{|\sin(\phi /2)|},
-\quad 0 \leq \phi \leq \pi
-\end{align}
-By taking the first two term of the expansion \(\sin x =x -x^3/6 +- \dotsc\), and noting the monotony, 
-\begin{align}
-S(\phi)
-\leq& \frac{1}{\phi/2 -(\phi/2)^3/6} \\ \notag
-=& \frac{-48}{\phi^3 -24\phi}
-\quad 0 \leq \phi \leq \pi,
-\end{align}
-
-The fraction above can be bounded.
-
-By the same token, more generally,
-\begin{align}
-&\left| \frac{1}{N} \sum_{n=0}^{N-1} e^{-2\pi i k n/N} e^{i n \phi} \right| \\ \notag
-=&\frac{|\sin( \phi N /2 )|}{N |\sin( \pi k /N -\phi /2 )|} \\ \notag
-=&\frac{1}{N} S(\pi \phi') \\ \notag
-\leq& \frac{48}{N \pi^3 (\phi'^3 -24 \phi' /\pi^2)}
-\end{align}
-where \(\phi' =k/N -\phi/2\pi\), and the cubic expression is split.
-We wish to bound the tail of \(S(\pi \phi')\), and apply the na\"ive bound
-\begin{align}
-&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\phi'^3 -24 \phi' /\pi^2}
- d\phi' \\ \notag
-=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \\ \notag
-\leq& \frac{1}{\pi^2} \log \frac{L}{N}
-\end{align}
-Here, the integral in the first line is immediate.
-The second term in the bracket is smaller than 0 and is dropped in the last inequality.
-}
-
-The bound is satisfying enough, though refinement is surely possible.
-Indeed, \(\log L/N \to 0\) as \(N \to \infty\) and limited by the number of paths \(L\).
-
-The rest follows ``The Dantzig Selector'' very closely.
-
-\Result
-{Proposition}
-{
-Let \(h \in \mathbb{R}^n\) and \(\eta \in \mathbb{R}^p\) are defined as in ().
-Then
-\begin{align}
-\|d_{BC}\|_1
-\leq \|d_A\|_1 +\|g_{BC}\|_1
-\end{align}
-}
-To show this, observe
-\begin{align}
-\|g\|_1 -\|d_A\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1
-\leq& \|g +d\|_1 \\ \notag
-\leq& \|g\|_1
-\end{align}
-In the first line, we recall \(g =g_A\).
-
-\Result
-{Lemma}
-{
-\begin{align}
-|\langle e, P_{:,j} \rangle| \leq \sqrt{2 \log p}
-\end{align}
-}
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|P^\dagger P d\|_\infty
-\leq& 2 \sqrt{2 \log p}.
-\end{align}
-}
-To show this, start with
-\begin{align}
-\langle e -r, P_{:,j} \rangle
-=\langle P \hat{g} -P g, P_{:,j} \rangle
-=\langle P g, P_{:,j} \rangle
-\end{align}
-Result follows from triangle inequality, and Lemma ().
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result below.
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|d_A\|_2
-\leq \frac{1}{1-\delta} \|P^\dagger_{AB} P \eta\|_2 +\frac{\theta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
-\end{align}
-}
-
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result below.
-
-\Result
-{Lemma}
-{
-\begin{align}
-\|d\|_2^2
-\leq \|d_{AB}\|_2^2 +\frac{1}{L} \|d_C\|_1^2
-\end{align}
-}
-
-We can formulate our main theorem:
-
-(To be done)
-
-\section{Simulation}
-
-With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
-
-As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\mathcal{R}(h)\).
-But it is not the end.
-In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-magic'' transforms DS into a linear program (LP), but that does not directly applies
-Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
-Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
-Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-magic''.
-
-\subsection{Transformation into Second Order Cone Problem}
-
-Since our setting is slightly different from ``\(\ell_1\)-Magic'', for completeness of exposition we write down derivation of the dual problem from the primal problem.
-Recapitulate that, as we explained in the above, DS involves a 
-We transform the \(\ell_1\)-minimization problem to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
-
-% % % % % % % % % % % % % % % %
-
-\section{Conclusion and Future Work}
-
-Firstly,
-Meanwhile, DS goes not without criticism for large complexity.
-Indeed it is clear, even from the primal-dual implementation above, that DS requires large dimensional vector
-
-Secondly
-And comparison of bounds of OMP and DS
-The author criticises the tendency of current literature to mix up results for DS and OMP without clear justification, since they are two quite different approaches to the compressed sensing problem.
-It is however not trivial to make meaningful comparison, since DS works with a RIP matrix, and OMP for Gaussian... the distinction is slight but definite...
-The author critizises In OMP we don't know whether the measurement matrix is the same as channel
-And OMP has stricter condition than DS
-Tao, however, specifies a noise relation
-
-Bounds of performance in different setting are often nontrivial to obtain, and one cannot think OMP, or indeed every algorithm, as a universal solution.
-OMP trades off precision for time complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
-All in all, different problems requires different technique and algorihm within the constraint at hand, as is probably true in every discipline of engineering.
-
-\section{References}
+\subsection{References}
 
@@
 
-\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.
-5.
+\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.\ 5.
 
@@
 
-\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.98, No.6.
+\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.\ 98, No.\ 6.
 
@@
 \end{enumerate}
-
-\end{document}

### 2019-01-06 ongoing/report/sec_1_introduction.tex
Revise Introduction

@@
 \(|a|\) denotes the magnitude for real or complex numbers \(a\).
-The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(a =\MF{Re}(a) +i \MF{Im}(a)\)
+The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(a =\MF{Re}(a) + i \MF{Im}(a)\)
 
@@
 
-To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p\) is much larger than the number of observations \(N_o\).
+To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p\) is much larger than the number of measurements \(N_m\).
 Here, we consider
+%
 \Disp{
-N_p \gg N_o
+N_p \gg N_m
 }
+In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \(N_p\) parameters?
+Of course, more assumption must be made to make the question meaningful.
+Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.
 
-In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?
-
-Of course, more assumption must be made to make the question meaningful.
-They showed frst that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
+Cand\`es and Tao showed frst that that in the noiseless case (``Decoding by Linear Programming'', 2006), it is possible to recover the sparse signal, under a \(\ell_1\) minimization program.
 The work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
 
-Later they established a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006), with another \(\ell_1\)-1 minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
-They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
+Later they established a stronger result that (``The Dantzig Selector'', 2007), with another \(\ell_1\) minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
+Such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
 Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
@@
 
-From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
-Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
+From the realistic perspective, the formulation as an \(\ell_1\) minimization problem, which is convex, made techniques from convex optimization usable.
+Indeed, relevent code has been put on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
 
-In this article we focuss on DS, and we introduce several notions before we describe their wok.
-To facilitate reader's understanding, in this section we will consistently use \(N_s\) and \(N_s\) to denote matrix dimensions.
+In this article we focuss on DS, and we introduce several notions before we describe their work.
+To facilitate reader's understanding, in this section we will consistently use \(N_p\) and \(N_m\) to denote matrix dimensions.
 Following Cand\`es and Tao, we borrow the term ``support'' from the context of analysis, where it denotes the set on which a function is nonzero.
@@
 {
-We say \(T (N) =\{1, \dotsc, N\}\), \(N \in \MB{N}\) is the support of vector space \(\MB{V}_{\MB{K}} (N)\).
+We say \(T (N_m) =\{1, \dotsc, N_m\}\), \(N_m \in \MB{N}\) is the support of vector space \(\MB{V}_{\MB{K}} (N_m)\).
 }
@@
 {
-Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_1, N_2)\).
-Let \(\MC{T} \subset T (N_2)\).
+Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)\).
+Let \(\MC{T} \subset T (N_p)\).
 Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
@@
 {
-\(x \in \MB{V}_{\MB{K}} (N)\) is called \(s\)-sparse with support \(\MC{A}\), \(s \in \MB{N}\), if there is \(\MC{A} \subset T (N)\) such that
+\(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s \in \MB{N_m}\), if there is \(\MC{A} \subset T (N_m)\) such that
 %
@@
 \Disp{
-y =Ax +z
+y =Ax + z
 }
@@
 \Disp{
-y[t] =(x[t] \star h[t]) +z[t]
+y[t] =(x[t] \star h[t]) + z[t]
 }
@@
 \begin{enumerate}
-\item
+\item To be done.
 \end{enumerate}
@@
 %
-Then Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
+Then OMP (Algorithm \_\_) recovers \(x\) completely, with overwhelming probability \(1-\delta\).
 }
 
-For the proof, see the technical report: Tropp and A C Gilbert (2007a).
+For the proof, see the technical report: Tropp and Gilbert (2007a).
 
@@
 
-\subsection{Contribution}
-
 We remark several observation on past literature, that has been, to the best of our knowledge, lacking or less than ideal.
@@
 \begin{enumerate}
-\item As said, previous work the favor on OMP rather than DS (let alone other sparse algorithm) is evident.
-\item In view of The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian, Tropp and Gilvert (2007) seems to be more restrictive than Cand\`es and Tao (2007).
-\item Previous work only takes the assumption on the bound of the norm of the channel matrix to be granted.
-\item Likewise, such probability bounds on the sparsity of the channel as involving, say, number of channel paths and vector of array response has not be explored.
+\item Previous work favors OMP rather than DS, let alone other sparse algorithm.
+\item Previous work simply assumes the bound of the norm of the channel matrix.
+\item The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian (Tropp and Gilvert 2007) seems to be more restrictive than RIP (Cand\`es and Tao 2007).
+\item No bounds is derived that explicitly depends on the sparsity of the channel parameters as, say, number of channel paths and array response.
 \end{enumerate}
+
+\subsection{Contribution}
 
@@
 We apply a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
-Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), the author gives such an asymptotic bound for the probability will be shown, that indicates our method is successful for overwhelming probability.
+Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), we give a bound that indicates our method is to be successful for overwhelming probability.
 

### 2019-01-06 ongoing/report/sec_2_problem_setting.tex
Revise Introduction

@@
 }
-
-\subsection{Proposed Method}
-
 \(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
@@
 \M{Y} (:,n_y)
-:=\M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \quad
-n_y =1, 2, \dotsc, N_y
+:=\M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \\
+\quad n_y &=1, 2, \dotsc, N_y \NT
 }
 %
-The crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), while \(\M{W}_R\), \(\M{W}_B\), \(\M{F}_R\), and \(\M{F}_B\) are in our control.
+Still, the crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), while \(\M{W}_R\), \(\M{W}_B\), \(\M{F}_R\), and \(\M{F}_B\) are in our control.
 
-Following previous work on CSS, we write
+\subsection{Vectorization}
+
+If we had followed the widely accepted approach of compressive channel sensing, we would have written
 %
@@
 := &\RM{vec} (\M{Y})
-\in \MB{M}_{\MB{C}} (N_y^2) \\
+\in \MB{V}_{\MB{C}} (N_y^2) \\
 \V{z}^\star
 := &\RM{vec} (\M{Z})
-\in \MB{M}_{\MB{C}} (N_y^2) \\
+\in \MB{V}_{\MB{C}} (N_y^2) \\
 \M{P}^\star
-:= &(\M{F}_R \M{F}_B) \otimes (\M{W}_B \M{W}_R)
-\in \MB{M}_{\MB{C}} (N_h, N_h).
+:= &(\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
+\in \MB{M}_{\MB{C}} (N_y^2, N_h^2).
 }
@@
 
+\subsection{Proposed Method}
+
 Introduce the discrete Fourier matrix \(\M{K}\) defined to be
@@
 \Disp{
-\M{K} \in &\MB{M}_{\MB{C}} (N_h, N_h) \notag \\
-\M{K} (n_1, n_2) =&\frac{1} {\sqrt{N}} \RM{e}^{2\pi i n_1 n_2 /N}, \\
-\quad n_1, n_2 =&0, 1, \dotsc, N_h-1 \notag
+\M{K} \in &\MB{M}_{\MB{C}} (N_h, N_h) \NT \\
+\M{K} (n_1, n_2) =&\frac{1} {\sqrt{N_h}} \RM{e}^{2\pi i n_1 n_2 /N_h}, \\
+\quad n_1, n_2 =&0, 1, \dotsc, N_h-1 \NT
 }
@@
 %
-which has the interpretation as the spatial frequency domain representation of \(\M{H}\), then
+which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
 %
@@
 If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.
-To the best of our knowledge, no work has explicitly considered the beamspace CSS.
 
@@
 \M{P}
-=(\M{F}_B^\H \M{F}_R^\H K) \otimes (\M{W}_B \M{W}_R \M{K})
+=(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
 \in \MB{M}_{\MB{C}} (N_y^2, N_h^2)
@@
 \Disp{
+\V{g}
+:= &\RM{vec} (\M{G})
+\in \MB{M}_{\MB{C}} (N_h^2) \\
 \V{z}
@@
 \hat{\V{g}}
-=\underset {\V{h}} {\RM{min}} \|\V{h}\|_1 \quad
-\RM{subject}\; \RM{to}\quad \|P^\H (y -P h)\|_\infty \leq \gamma
+=\min_{\V{g}'} \|\V{g}'\|_1 \quad
+\RM{subject}\; \RM{to}\quad \|\M{P}^\H (\V{y} -\M{P} \V{g}')\|_\infty \leq \gamma
 }
 %
-And convert \(\hat{g}\) back to the space domain as
+And convert \(\hat{\V{g}}\) back to the space domain as
 %
 \Disp{
-\hat{h}
-=K \hat{g}.
+\hat{G} =\RM{vec}^{-1} (\hat{g})
 }
@@
 \Disp{
-\hat{H} =\RM{vec}^{-1} (\hat{h})
+\hat{\M{H}} =\M{K} \hat{\M{G}} \M{K}^\H.
 }

### 2019-01-06 ongoing/report/sec_3_theorems_and_proofs.tex
Revise Introduction

@@
 The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_h^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
+To simplify the exposition, we will continue to use the variables \(\V{P}\), \(\V{g}\), \(\V{y}\), and \(\V{z}\) introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).
 
@@
 At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
+
+\subsection{Beamspace Channel is Almost Sparse}
 
@@
 \item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
-\item \(\MC{C} =\{1, \dotsc, N_h^2\} -( \MC{B} \cup \MC{C} )\), i.e., the complementary index set.
+\item \(\MC{C} =T(N_h^2) -\MC{B} -\MC{C}\), i.e., the complementary index set.
 \end{itemize}
@@
 \Disp{
-\MC{A}, \MC{B}, \MC{C} \subset \{1, \dotsc, N_h^2\} \\
+\MC{A}, \MC{B}, \MC{C} \subset T(N_h^2) \\
 \MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
-\MC{A} \cup \MC{B} \cup \MC{C} =\{1, \dotsc, N\}.
+\MC{A} \cup \MC{B} \cup \MC{C} =T(N_h^2).
 }
@@
 \Disp{
-S (x)(n_1) \geq S (x)(n_2),
-\quad n_1, n_2 \in T (N).
+|S (x)(n_1)| \geq &|S (x)(n_2)|, \\
+n_1 >&n_2,
+\quad n_1, n_2 \in T (N) \NT
 }
+}
+
 Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \(S\) throughout this article.
@@
 If still there is a tie for a certain component (for complex numbers), we compare the real part first, then the imaginary part.
-}
 
@@
 \Disp{
-x (n) <f (n),
+|S(x) (n)| <&f (n),
 \quad n \in T (N).
@@
 Let \(\varphi (\omega_h)\) be uniformly, independently distributed in \([0,2\pi)\), and array response \(\V{a} (\varphi)\) defined as in ().
+Then
 %
@@
 
+\subsection{Design of RIP Precoders and Combiners}
+
+\subsection{DS for Complex Vectors}
+
 The rest follows ``The Dantzig Selector'' very closely.
@@
 \Disp{
-|\IP{ e, P_{:,j} }| \leq \sqrt{2 \log p}
+|\IP{ d, P(:, n_h) }|
+\leq& 4 \sqrt{\log N_h},
+\quad n_h =1, \dotsc, N_h^2.
 }
@@
 \|P^\H P d\|_\infty
-\leq& 2 \sqrt{2 \log p}.
+\leq& 4 \sqrt{\log N_h},
+\quad n_h =1, \dotsc, N_h^2.
 }
@@
 \Disp{
-\IP{ z -(y -P h), P (:,n_y) }
-=\IP{ P \hat{g} -P g, P (:,n_y) }
-=\IP{ P g, P (:,n_y) }
+&\IP{ z -(y -P g), P (:,n_y) } \NT \\
+=&\IP{ P \hat{g} -P g, P (:,n_y) } \NT \\
+=&\IP{ P g, P (:,n_y) }
 }
@@
 \|d_{\MC{A}}\|_2
-\leq \frac{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P \eta\|_2 +\frac{\vartheta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
+\leq \frac{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P d\|_2 +\frac{\delta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
 }
@@
 
+\subsection{Putting Together}
+
 We can formulate our main theorem.

### 2019-01-07 ongoing/report/sec_1_introduction.tex
Shorten introduction

@@
 \(|a|\) denotes the magnitude for real or complex numbers \(a\).
-The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(a =\MF{Re}(a) + i \MF{Im}(a)\)
+The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re} (a)\) and \(\MF{Im} (a)\), respectively, thus \(a =\MF{Re} (a) + i \MF{Im} (a)\)
 
@@
 Not to avoid confusion, we call the Hilbert space \(\MB{K}^N\) over \(\MB{K}\) to be \(\MB{V}_{\MB{K}} (N)\).
-We also call the collection of \(M\) by \(N\) matrices to be \(\MB{M}_{\MB{K}}(M,N)\), and its role as linear transformation is understood.
+We also call the collection of \(M\) by \(N\) matrices to be \(\MB{M}_{\MB{K}} (M,N)\), and its role as linear transformation is understood.
 Inner product of \(\V{a}\) and \(\V{b}\) is denoted as \(\IP{ \V{a}, \V{b} }\).
-Slightly abusing notation, we denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
+Slightly abusing notation, we denote as \(\V{a} (n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A} (m,n)\) the \((m,n)\)-entry of \(\V{A}\)
 Particularly, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).
@@
 
-Denote as \(\MB{P}(X)\) the probability, and \(\MB{E}(X)\) the expectation.
+Denote as \(\MB{P} (X)\) the probability, and \(\MB{E} (X)\) the expectation.
 Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.
@@
 }
+%
 In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \(N_p\) parameters?
@@
 {
-\(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s \in \MB{N_m}\), if there is \(\MC{A} \subset T (N_m)\) such that
+\(h \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T (N_m)\) such that
 %
@@
 }
-%
 That is, only at most \(s\) components of vector \(x\) is nonzero.
@@
 {
-Let \(A,y\) be given.
-Find \(x\) with
+Let \(P \in \MB{M}_\MB{K} (N_m, N_p)\) and \(y \in \MB{V}_\MB{K} (N_p)\) be given.
+Find \(h \in \MB{V}_\MB{K} (N_p)\) with
 %
 \Disp{
-\min_{x' \in \MB{V}_\MB{K}(K)}
-\quad \|x'\|_1
-\quad \RM{s.t.} \quad A x' =y
+\min_{h'}
+\quad &\|h'\|_1 \\
+\quad \RM{subject}\; \RM{to}
+\quad &P h' =y
 }
-%
 }
 
-\Result
-{Theorem}
-{
-Let \(y =Ax\).
-Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
-That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
-%
-\Disp{
-\delta_{S} +\delta_{2S} +\delta_{3S} <1
-}
-%
-}
+Now let \(y =P h\).
+Suppose \(h\) is \(s\)-sparse, then the program () completely recovers \(h\).
+That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability.
 
@@
 {
-Let \(A\) be an \(n \times p\) matrix, with
+Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
+For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the RIP of order \(s\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq s\), for all \(\MC{T} \subset T(N_m)\) with \(|\MC{T}| \leq s\),
 %
 \Disp{
-\delta_{S} +\delta_{2S} +\delta_{3S} <1
+(1-\delta_s) \|h\|^2
+\leq \|P_{\MB{T}} h\|_2^2
+\leq (1+\delta_s) \|h\|^2
+}
+}
+
+RIP of order \(s\) is essentially saying that the matrix \(X\) is ``almost unitary'' up to ``relative error'' \(\delta_s\).
+
+Consider a linear transformation with noise corruption,
+%
+\Disp{
+\V{y} =\M{P} \V{h} + \V{z}
 }
 %
-
-having unit \(\ell_2\)-norm columns.
-For each integer \(S \in \MB{N}\), we say that \(A\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
-%
-\Disp{
-(1-\delta_S) \|x\|^2
-\leq \|A_T x\|_2^2
-\leq (1+\delta_S) \|x\|^2
-}
-%
-}
-
-RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\delta_S\).
-
-Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
-%
-\Disp{
-| \IP{ X_T c, X_{T'} c' } |
-\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
-}
-%
-
-For concreteness, consider a linear transformation with noise,
-%
-\Disp{
-y =Ax + z
-}
-%
-where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
+where (w.l.o.g.) \(z\) is an i.i.d.\ normalized Gaussian vector.
 How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
@@
 {
-Let \(A,y\) be given.
-Find \(x\) with
+Let \(\M{P} \in \MB{V}_\MB{R} (N_m, N_p)\) and \(\V{y} \in \MB{V}_\MB{R} (N_m)\) be given.
+Find \(\V{h} \in \MB{V}_\MB{R} (N_m)\) with
 %
 \Disp{
-\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \NT
-\RM{subject}\; \RM{to} \quad \|A^\H r\|_\infty \leq \lambda_p \sigma
+\min_{\V{h}'} \quad &\|\V{h}'\|_1 \\ \NT
+\RM{subject}\; \RM{to} \quad &\|\M{P}^\H (\M{P} \V{h} -\V{y})\|_\infty \leq \gamma
 }
-%
-where \(r =y -A \hat{x}\).
 }
-And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.
 
-\subsection{Condition of RIP Linear Transformation}
+And it can be shown that this \(\ell_1\)-minimization problem with \(\ell_\infty\)-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
+Note that they confined their discussion for real vectors.
+
+\subsection{Sufficient Conditions of RIP}
 
 The constant \(\delta\) in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(A\) is fully unitary.
+Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(P\) is fully unitary, rendering the RIP an important role.
+Here, it is not clear at first what matrices serves as the RIP condition.
 
-Here, it is not clear at first what matrices serves as the RIP condition.
 But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.
@@
 {
-Let each entry of random matrix \(A \in \MB{V}_\MB{K}(M \cdot N)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
+Let each entry of random matrix \(P \in \MB{M}_\MB{K} (N_m, N_p)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{N_m}\) (that is, Rademacher distribution).
 Then, with \(0 <\epsilon <1\),
@@
 \Disp{
-   \MB{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
-   \leq 2 \exp (-n c_0(\epsilon))
+   \MB{P} ( |\|P h\|_2^2 -\|h\|_2^2| \geq \epsilon \|h\|_2^2)
+   \leq 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) )
 }
-%
-where we have
-%
-\Disp{
-c_0(\epsilon)
-=\epsilon^2/4 -\epsilon^3/6.
-}
-%
 }
@@
 
-To explain the idea, consider a simplified scenario.
-Let \(x[t] \in \MB{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
-Consider a linear time-invariant channel with
-%
-\Disp{
-y[t] =(x[t] \star h[t]) + z[t]
-}
-%
-where \(h[t] \in \MB{R}^L\) is the channel's impulse response, \(x[t] \in \MB{R}^N\) as the input, \(y[t] \in \MB{R}^N\) as the output, and \(z[t] \in \MB{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
-Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
-%
-\Disp{
-y =X h
-}
-%
-where \(X\) takes the form
-%
-\Disp{
-X
-=\begin{bmatrix}
-x_1, &0, &\cdots, &0 \\
-x_2, &x_1, &\cdots, &0 \\
-\vdots, &\vdots, &\ddots, &0 \\
-x_N, &x_{N-1}, &\cdots, &x_1
-\end{bmatrix}
-}
-%
-We seek to get \(h\) in this undertermined system.
-
-Bajwa et.\ al.\ was able to show that \(X\) is RIP of overwhelmingly probability.
+To explain the idea, consider a linear time-invariant channel that \(y(t) =(x \star h)(t) + z(t)\), where \(x(t)\) is random instances of i.i.d.\ Rademacher distribution drawn in each time index, \(h(t)\) is the channel's impulse response, \(y(t)\) as the output, and \(z(t)\) is i.i.d.\ normalized AWGN
+Simply assuming \(h\) has sparse support, and let the convolution with \(x\) be expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that \(y =X h +z\).
+Then Bajwa et.\ al.\ was able to show that, \(X\) is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.
 
@@
 
-The setting here is \(y =Ax\), the noiseless, real-number case.
-Same as before, let \(y \in \MB{V}_\MB{K}(M)\), \(x \in \MB{V}_\MB{K}(N)\) which is \(s\)-sparse, while \(M \ll N\).
-We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).
+Same as before, consider \(\V{y} \in \MB{V}_\MB{K} (N_p)\), \(\V{h} \in \MB{V}_\MB{K} (N_s)\), where \(\V{h}\) is \(s\)-sparse, with \(N_p \gg N_s\).
+If
+\Disp{
+\V{y} =\M{P} \M{h},
+}
+that is, the noiseless, real-number case.
+We pick up the columns of \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\).
 
@@
 }
+
+From Tropp and Gilbert (2007a),
 
@@
 
-For the proof, see the technical report: Tropp and Gilbert (2007a).
+It is interesting to note that, ever since, scholars has applied OMP in favor of DS, due the simplicity of former's implementation, making OMP perhaps the most widely used channel estimation technique.
 
-It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
-Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
-To see this, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
-Let signal \(x\) be sent, and \(y\) be receiverd, that is
+For concreteness, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
+Let signal \(\V{x}\) be sent, and \(\V{y}\) be receiverd, that is
 %
@@
 {
-Define \(\RM{vec}(\M{A}) \in \MB{K}^{nm}\) to be the vectorization of \(\M{A} \in \MB{M}_{\MB{K}}(n,m)\).
+Define \(\RM{vec} (\M{A}) \in \MB{K}^{NM}\) to be the vectorization of \(\M{A} \in \MB{M}_{\MB{K}} (N,M)\).
 }
@@
 {
-For \(\RM{vec}(A) \in \MB{M}_{\MB{K}}(n,m)\) and \(\RM{vec}(A) \in \MB{M}_{\MB{K}}(n,m)\)
-Define the Kronecker product \(\RM{vec}(A) \in \MB{K}^{nm}\) 
+For \(\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)\) and \(\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)\)
+Define the Kronecker product \(\RM{vec} (A) \in \MB{K}^{nm}\) 
 }
@@
 \Disp{
-\RM{vec}(Y)
-=\big[ (F^\H) \otimes W \big] \RM{vec}(\M{H})
+\RM{vec} (Y)
+=\big[ (F^\H) \otimes W \big] \RM{vec} (\M{H})
 }
@@
 
-Our contribution include:
+Our contribution includes:
 
@@
 \item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
-\item We do not assume that the virtual channel model is naturally quantized in its angle of departure and of arrival, thus removes concern of the quantization error within the proof.
-\item Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
 \item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
+\item Accordingly, the concern of quantization error of the virtual channel's phase angle (which is inevitable when designing the OMP beambook) has already been considered in the proof of our main bound.
 \item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.

### 2019-01-07 ongoing/report/sec_3_theorems_and_proofs.tex
Shorten introduction

@@
 \| \V{a} (\varphi) \|_1
-\leq \frac{1}{\pi^2} \log \frac{L}{N}.
+\leq \F{1}{\pi^2} \log \F{L}{N}.
 }
@@
 \Disp{
-D (\varphi)
-:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi} \right| \\ \NT
-=&\frac{|\sin (N \varphi/2)|}{|\sin (\varphi /2)|},
-\quad 0 \leq \varphi \leq \pi
+D (\varphi')
+:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi'} \right| \\ \NT
+=&\F{|\sin (N \varphi'/2)|}{|\sin (\varphi' /2)|},
+\quad 0 \leq \varphi' \leq \pi
 }
@@
 
-By taking the first two term of the expansion
+Recall the Taylor expansion of sin for the first two terms with respect to zero
 %
 \Disp{
-\sin x =x -x^3/6 + \MC{O}(x^5), \quad x \ll 1
+\sin x =x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1
 }
 %
-and noting the monotony of the first two terms,
+Actually it can be shown that we have a inequality
 %
 \Disp{
-D (\varphi)
-\leq& \frac{1}{\varphi/2 -(\varphi/2)^3/6} \NT \\
-=& \frac{-48}{\varphi^3 -24\varphi} \\
-\quad 0 \leq \varphi \leq \pi,
+\left| x -\F{x^3}{6} \right| \leq \sin x, \quad -\pi \leq x \leq \pi
+}
+%
+Applying the above inequality to the denominator and bounding the nominator by 1, we have
+%
+\Disp{
+\left| D (\varphi') \right|
+= \F{48}{|\varphi'^2 -24| |\varphi'|}
+\quad 0 \leq \varphi' \leq \pi,
 }
@@
 
-By the same token, more generally,
+Particularly,
 %
 \Disp{
-\frac{1}{N} S (\pi \varphi')
-=&\left| \frac{1}{N} \sum_{n=0}^{N-1} \RM{e}^{-2\pi i k n/N} \RM{e}^{i n \varphi} \right| \NT \\
-\leq& \frac{48}{N \pi^3 (\varphi'^3 -24 \varphi' /\pi^2)}
+\F{1}{N} S \left( \varphi' -\F{2\pi k}{N} \right)
+=&\F{1}{N} \left| \sum_{n=0}^{N-1} \RM{e}^{-2\pi i k n/N} \RM{e}^{i n \varphi} \right| \NT \\
+\leq& \F{48}{N \pi^3 (\varphi'^3 -24 \varphi' /\pi^2)}
 }
@@
 \Disp{
-&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\varphi'^3 -24 \varphi' /\pi^2}
+&\F{N}{2\pi} \cdot \F{48}{N \pi^3} \int_{L/N}^1 \F{1}{\varphi'^3 -24 \varphi' /\pi^2}
  d\varphi' \NT \\
-=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \NT \\
-\leq& \frac{1}{\pi^2} \log \frac{L}{N}
+=&\F{1}{2\pi^2} \cdot \left( 2 \log \F{L}{N} +\log \F{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \NT \\
+\leq& \F{1}{\pi^2} \log \F{L}{N}
 }
@@
 
+\Result
+{Definition}
+{
+For \(\MC{T}, \MC{T}' \subset \{1, \dotsc, N_p\}\), define the \(s,s'\)-restricted orthogonality constant \(\tau_{s,s'} >0\) to be the smallest such that
+%
+\Disp{
+| \IP{ P_{\MC{T}} h, P_{\MC{T}'} h' } |
+\leq \tau_{s, s'} \cdot \| h \|_2 \|h'\|_2
+}
+}
+
+From ``Decoding from Linear Programming'',
+\Result
+{Lemma}
+{
+%
+\Disp{
+\leq 
+\tau_{s, s'}
+\leq \delta_s
+}
+}
+
 The rest follows ``The Dantzig Selector'' very closely.
-
 \Result
@@
 {
-Let \(h \in \MB{R}^n\) and \(\eta \in \MB{R}^p\) are defined as in ().
+Let \(g\) and \(d\) be defined as above.
 Then
@@
 }
-%
 }
@@
 {
+Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
 %
@@
 {
+Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with constant \(\delta\).
 %
@@
 \|d_{\MC{A}}\|_2
-\leq \frac{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P d\|_2 +\frac{\delta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
+\leq \F{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P d\|_2 +\F{\delta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
 }
@@
 {
+Let \(d\) be defined as above.
+Then
 %
@@
 \|d\|_2^2
-\leq \|d_{\MC{A}\MC{B}}\|_2^2 +\frac{1}{L} \|d_{\MC{C}}\|_1^2
+\leq \|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2
 }
@@
 
-\subsection{Putting Together}
+\subsection{The Main Bound}
 
-We can formulate our main theorem.
+We can now formulate and prove the main bound of ours.
 

### 2019-01-08 ongoing/report/sec_1_introduction.tex
Work on Main Bound

@@
 
+{ \color{red} (To be done) }
+
 \subsection{Compressed Channel Sensing}
@@
 
-To explain the idea, consider a linear time-invariant channel that \(y(t) =(x \star h)(t) + z(t)\), where \(x(t)\) is random instances of i.i.d.\ Rademacher distribution drawn in each time index, \(h(t)\) is the channel's impulse response, \(y(t)\) as the output, and \(z(t)\) is i.i.d.\ normalized AWGN
+To explain the idea, consider a linear time-invariant channel that \(y(t) =(x \star h)(t) + z(t)\), where \(h(t)\) is the channel's impulse response, \(y(t)\) is the output, and, for each time index, \(x(t)\) is i.i.d.\ Rademacher, and \(z(t)\) is i.i.d.\ Gaussian.
 Simply assuming \(h\) has sparse support, and let the convolution with \(x\) be expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that \(y =X h +z\).

### 2019-01-08 ongoing/report/sec_2_problem_setting.tex
Shorten introduction
Work on Main Bound

@@
 \Disp{
-\V{a} \in \MB{V}_\MB{K} (N_h) \\
+\V{a} \in \MB{V}_\MB{K} (N_H) \\
 \V{a} (\psi')
@@
 H
-=\sum_{l=1}^L \alpha_l \V{a} \left( \frac{d} {\lambda} \sin \varphi_l' \right) \V{a} \left( \frac{d_{\RM{arr}}} {\lambda} \sin \vartheta_l' \right)^\H
+=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \varphi_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \vartheta_l' \right)^\H
 }
@@
 \varphi_l
-=\frac{d_{\RM{arr}}} {\lambda} \sin \varphi_l' \\
+=\F{d_{\RM{arr}}} {\lambda} \sin \varphi_l' \\
 \vartheta_l
-=\frac{d_{\RM{arr}}} {\lambda} \sin \vartheta_l'
+=\F{d_{\RM{arr}}} {\lambda} \sin \vartheta_l'
 }
@@
 \Disp{
-\M{F}_B \in &\MB{M}_{\MB{C}} (N_r, N_y) \\
-\M{F}_R \in &\MB{M}_{\MB{C}} (N_h, N_r) \\
-\M{W}_R \in &\MB{M}_{\MB{C}} (N_r, N_h) \\
-\M{W}_B \in &\MB{M}_{\MB{C}} (N_y, N_r).
+\M{F}_B \in &\MB{M}_{\MB{C}} (N_R, N_Y) \\
+\M{F}_R \in &\MB{M}_{\MB{C}} (N_H, N_R) \\
+\M{W}_R \in &\MB{M}_{\MB{C}} (N_R, N_H) \\
+\M{W}_B \in &\MB{M}_{\MB{C}} (N_Y, N_R).
 }
@@
 |\M{W}_R (n_r, n_h)| =&1, \\
-n_h =&1, \dotsc N_h, \NT \\
-n_r =&1, \dotsc N_r \NT
+n_h =&1, \dotsc N_H, \NT \\
+n_r =&1, \dotsc N_R \NT
 }
@@
 \Disp{
-N_h \gg &N_r \\
-N_r \gg &N_s
+N_H \gg &N_R \\
+N_R \gg &N_s
 }
@@
 }
-\(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
+\(\M{Y}\) has \(N_Y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
 This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
@@
 :=\M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \\
-\quad n_y &=1, 2, \dotsc, N_y \NT
+\quad n_y &=1, 2, \dotsc, N_Y \NT
 }
@@
 := &\RM{vec} (\M{H})
-\in \MB{V}_{\MB{C}} (N_h^2) \\
+\in \MB{V}_{\MB{C}} (N_g) \\
 \V{y}
 := &\RM{vec} (\M{Y})
-\in \MB{V}_{\MB{C}} (N_y^2) \\
+\in \MB{V}_{\MB{C}} (N_y) \\
 \V{z}^\star
 := &\RM{vec} (\M{Z})
-\in \MB{V}_{\MB{C}} (N_y^2) \\
+\in \MB{V}_{\MB{C}} (N_y) \\
 \M{P}^\star
 := &(\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
-\in \MB{M}_{\MB{C}} (N_y^2, N_h^2).
+\in \MB{M}_{\MB{C}} (N_y, N_g).
 }
@@
 \Disp{
-\M{K} \in &\MB{M}_{\MB{C}} (N_h, N_h) \NT \\
-\M{K} (n_1, n_2) =&\frac{1} {\sqrt{N_h}} \RM{e}^{2\pi i n_1 n_2 /N_h}, \\
-\quad n_1, n_2 =&0, 1, \dotsc, N_h-1 \NT
+\M{K} \in &\MB{M}_{\MB{C}} (N_H, N_H) \NT \\
+\M{K} (n_1, n_2) =&\F{1} {\sqrt{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \\
+\quad n_1, n_2 =&0, 1, \dotsc, N_H-1 \NT
 }
@@
 =(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
-\in \MB{M}_{\MB{C}} (N_y^2, N_h^2)
+\in \MB{M}_{\MB{C}} (N_y, N_g)
 }
@@
 := &\RM{vec} (\M{G})
-\in \MB{M}_{\MB{C}} (N_h^2) \\
+\in \MB{M}_{\MB{C}} (N_g) \\
 \V{z}
 := &\RM{vec} (\M{K}^\H \M{Z})
-\in \MB{V}_{\MB{C}} (N_y^2)
+\in \MB{V}_{\MB{C}} (N_y)
+}
+where for short we set
+\Disp{
+N_g =&N_H^2 \\
+N_y =&N_Y^2
 }
@@
 \hat{\V{g}}
-=\min_{\V{g}'} \|\V{g}'\|_1 \quad
-\RM{subject}\; \RM{to}\quad \|\M{P}^\H (\V{y} -\M{P} \V{g}')\|_\infty \leq \gamma
+=\min_{\V{g}'} &\|\V{g}'\|_1 \quad
+\RM{subject}\; \RM{to}\quad &\|\M{P}^\H (\V{y} -\M{P} \V{g}')\|_\infty \leq \gamma
 }

### 2019-01-08 ongoing/report/sec_3_theorems_and_proofs.tex
Work on Main Bound

@@
 We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_h^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
+The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_g}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.
 To simplify the exposition, we will continue to use the variables \(\V{P}\), \(\V{g}\), \(\V{y}\), and \(\V{z}\) introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).
 
-We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\).
+We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(s\).
 At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
 
-\subsection{Beamspace Channel is Almost Sparse}
+\subsection{Almost-Sparsity of Beamspace Channel Matrix}
 
-Consider
+We apply DS to find \(\hat{g}\), setting
+\Disp{
+\gamma =\sqrt{2 \log N_g}
+}
+Other values are of course possible, but this is enough to illustrate our purpose.
+Also set for short
 %
 \Disp{
-d =g -\hat{g}
+d =\hat{g} -g
 }
 %
-And let
+And call
 \begin{itemize}
-\item \(\MC{A}\) be the largest \(L\) position of \(g\).
-\item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
-\item \(\MC{C} =T(N_h^2) -\MC{B} -\MC{C}\), i.e., the complementary index set.
+\item \(\MC{A}\) be the largest \(s\) position of \(g\).
+\item \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
+\item \(\MC{C} =T(N_g) -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
 \end{itemize}
-So \(\MC{A}, \MC{B}, \MC{C}\) are mutually exclusive index sets by construction:
-%
-\Disp{
-\MC{A}, \MC{B}, \MC{C} \subset T(N_h^2) \\
-\MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
-\MC{A} \cup \MC{B} \cup \MC{C} =T(N_h^2).
-}
 
@@
 \Result
-{Lemma}
+{Definition}
 {
-Let \(\varphi (\omega_h)\) be uniformly, independently distributed in \([0,2\pi)\), and array response \(\V{a} (\varphi)\) defined as in ().
-Then
+For \(x \in \MB{V}_{\MB{K}}(N)\), we say \(x\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
+\Disp{
+\sum_{n=s+1}^N |S(x) (n)|
+\leq R.
+}
+}
+
+\Result
+{Lemma (Tentative)}
+{
+Suppose \(0 \leq \varphi \leq 2\pi k /N_H\), \(k =0, \dotsc, N_H-1\).
+Let \(\varphi\) be given, and array response \(\V{a} (\varphi)\) defined as in ().
+Then \(\V{a} (\varphi)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R\)
 %
 \Disp{
-\| \V{a} (\varphi) \|_1
-\leq \F{1}{\pi^2} \log \F{L}{N}.
+R
+\leq 2 N_H \log \F{2\pi N_H}{L}.
 }
-%
 }
 
-To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
+The lemma is the key to estimating sparsity of \(h\), which we now show.
+Recall the identity for Dirichlet kernel
 %
@@
 D (\varphi')
-:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi'} \right| \\ \NT
-=&\F{|\sin (N \varphi'/2)|}{|\sin (\varphi' /2)|},
+:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \varphi'} \right| \NT \\
+=&\F{|\sin (N_H \varphi'/2)|}{|\sin (\varphi' /2)|},
 \quad 0 \leq \varphi' \leq \pi
@@
 %
-
-Recall the Taylor expansion of sin for the first two terms with respect to zero
+And recall the Taylor expansion of sin for the first two terms with respect to zero
 %
@@
 }
+
+Particularly, for arbitrary \(\varphi\), find \(k\) so that
+\Disp{
+\eta :=&\varphi -\F{2\pi k}{N_H}, \\
+\left| \eta \right|
+\leq &\F{2\pi}{N_H}.
+}
 %
-The fraction above can be bounded.
+Then observe
+\Disp{
+K^\H a(\varphi) (k)
+=D \left( \varphi -\F{2 \pi k} {N_H} \right)
+}
+So we need only bound
+\Disp{
+R(\eta) :=\sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
+}
+By the approximation of rectangle to integral,
+\Disp{
+R(\eta) -\F{2\pi} {N_H}
+\leq N_H \int_{\varphi'=2\pi L/N_H}^{2\pi} |D(\varphi')| d \varphi'
+}
+Bound \(D\) by above technique, meanwhile we notice \(\varphi' <24\).
+\Disp{
+R(\varphi)
+\leq &\F{N_H}{2\pi} \int_{\varphi'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\varphi'^2) \varphi'} d \varphi'
++\F{2\pi} {N_H} \\
+=&\F{N_H}{\pi} \log \F{2\pi N_H}{L} -\log \F{4\pi^2 -24} {L^2/N_H^2 -24}
++\F{2\pi} {N_H}
+}
+Notice the second log term \(<1\) and we drop that.
+Also drop \(2\pi /N_H\) since it is small.
+Furthermore the \(2\pi\) factor in log can be dropped too.
+\Disp{
+R(\varphi)
+\leq \F{N_H}{\pi} \log \F{N_H}{L}.
+}
 
-Particularly,
+\Result
+{Lemma (Tentative)}
+{
+Let \(\varphi\) and \(\vartheta\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
+Let \(g\) be defined as above.
+Then \(g\) is almost-\(L\)-sparse with \(\ell_1\)-residue
 %
 \Disp{
-\F{1}{N} S \left( \varphi' -\F{2\pi k}{N} \right)
-=&\F{1}{N} \left| \sum_{n=0}^{N-1} \RM{e}^{-2\pi i k n/N} \RM{e}^{i n \varphi} \right| \NT \\
-\leq& \F{48}{N \pi^3 (\varphi'^3 -24 \varphi' /\pi^2)}
+R
+\leq \F{L N_H^2}{\pi^2} \left( \log \F{N_H}{L} \right)
 }
-%
-where \(\varphi' =k/N -\varphi/2\pi\), and the cubic expression is split.
-We wish to bound the tail of \(S (\pi \varphi')\), and apply the na\"ive bound
-%
-\Disp{
-&\F{N}{2\pi} \cdot \F{48}{N \pi^3} \int_{L/N}^1 \F{1}{\varphi'^3 -24 \varphi' /\pi^2}
- d\varphi' \NT \\
-=&\F{1}{2\pi^2} \cdot \left( 2 \log \F{L}{N} +\log \F{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \NT \\
-\leq& \F{1}{\pi^2} \log \F{L}{N}
 }
-%
-Here, the integral in the first line is immediate.
-The second term in the bracket is smaller than 0 and is dropped in the last inequality.
-The proof of Lemma () is complete.
-
-The bound is satisfying enough, though refinement is surely possible.
-Indeed, \(\log L/N \to 0\) as \(N \to \infty\) and limited by the number of paths \(L\).
-Intuitively, this says that when there are few paths, but many antennas, we expect the spatial frequency domain of the virtual channel to be sparse too.
 
 \subsection{Design of RIP Precoders and Combiners}
-
-\subsection{DS for Complex Vectors}
 
@@
 
-From ``Decoding from Linear Programming'',
+From ``Decoding from Linear Programming'' (Cand\`es and Tao 2005), Lemma 1.1:
+
 \Result
@@
 {
-%
+Let \(P\) be given.
+Then \(\tau_{s, s'}\) is bounded in both direction as follows,
 \Disp{
-\leq 
-\tau_{s, s'}
-\leq \delta_s
+\delta_{s+s'} -\max (\{\delta_s, \delta_{s'}\})
+\leq \tau_{s, s'}
+\leq \delta_{s+s'}
 }
@@
 
+Thus \(\delta_s\), which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
+We may well keep track of \(\delta_s\) only.
+
+\Result
+{Lemma}
+{
+Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
+Then \(P\) is RIP according to \(\delta\) for at least probability
+\Disp{
+   1 -2 \left( \F{12}{\delta} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\delta}{2} N_p \right]
+}
+}
+
+{ \color{red} (To be done) }
+
+\subsection{DS for Complex Vectors}
+
 The rest follows ``The Dantzig Selector'' very closely.
+The generalization to complex vector is necessary (though we will ultimately do it in simulation involving real numbers only.
+We spell out the proof when such generalization is nontrivial.
+
 \Result
@@
 \Disp{
-\|d_{BC}\|_1
-\leq \|d_{\MC{A}}\|_1 +\|g_{BC}\|_1
+\|d_{\MC{C}}\|_1
+\leq \|d_{\MC{A}}\|_1 +2\|g_{C}\|_1
 }
@@
 
-To show this, observe
-%
+To show this, observe that with triangle inequality applied respectively on \(\MC{A}\) and \(\MC{C}\),
 \Disp{
-&\|g\|_1 -\|d_{\MC{A}}\|_1 +\|d_{BC}\|_1 -\|g_{BC}\|_1 \\
-\leq& \|g +d\|_1 \NT \\
-\leq& \|g\|_1
+\|g\|_1
+-\|d_{\MC{A}}\|_1
++\|d_{\MC{C}}\|_1
+-\|g_{\MC{C}}\|_1
+\leq \|g+d\|_1
 }
-%
 In the first line, we recall \(g =g_{\MC{A}}\).
+On the other hand, by construction that \(\hat{g}\) minimizes the \(\ell_1\)-norm,
+\Disp{
+\|g+d\|_1
+=\|\hat{g}\|_1
+\leq \|g\|_1
+}
+The result follows by combining.
 
@@
 {
-Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
+Let \(z\) and \(P\) be defined as above.
+Then
 %
 \Disp{
-|\IP{ d, P(:, n_h) }|
-\leq& 4 \sqrt{\log N_h},
-\quad n_h =1, \dotsc, N_h^2.
+|\IP{ z, P(:, n_g) }|
+\leq& 2 \sqrt{\log N_g},
+\quad n_g =1, \dotsc, N_g.
 }
 %
+with overwhelming probability.
 }
+
+This only depends on the fact that \(P(:, n_g)\) has unity \(\ell_2\)-norm, and on the randomness of \(z\).
+
+{ \color{red} (To be done) }
 
@@
 \|P^\H P d\|_\infty
-\leq& 4 \sqrt{\log N_h},
-\quad n_h =1, \dotsc, N_h^2.
+\leq& 4 \sqrt{\log N_g},
+\quad n_g =1, \dotsc, N_g.
 }
-%
 }
 
-To show this, start with
+To show this, by definition
 %
 \Disp{
-&\IP{ z -(y -P g), P (:,n_y) } \NT \\
+&\IP{ z -(y -P \hat{g}), P (:,n_y) } \NT \\
 =&\IP{ P \hat{g} -P g, P (:,n_y) } \NT \\
-=&\IP{ P g, P (:,n_y) }
+=&\IP{ P d, P (:,n_y) }
 }
-%
-Result follows from triangle inequality, and Lemma ().
+
+By construction
+\Disp{
+\| P (:,n_y)^\H (y -P \hat{g}) \|
+\leq &\| P^\H (y -P \hat{g}) \|_\infty \\
+\leq &2\sqrt{\log N_g}
+}
+By triangle inequality, together with lemma (), we have
+\Disp{
+\|P (:,n_y)^\H P d\|
+\leq &\|\IP{ z, P (:,n_y) }\| +\IP{ y -P \hat{g}, P (:,n_y) } \\
+\leq &2 \sqrt{\log N_g} +2 \sqrt{\log N_g}
+}
+which implies
+\Disp{
+\|P^\H P d\|_\infty
+\leq &4 \sqrt{\log N_g}.
+}
 
@@
 {
-Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with constant \(\delta\).
+Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with respect to \(\delta_s\).
 %
 \Disp{
-\|d_{\MC{A}}\|_2
-\leq \F{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P d\|_2 +\F{\delta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
+\|d_{\MC{AB}}\|_2
+\leq \F{1}{1-\delta_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\delta_{3s}}{(1-\delta_{2s}) \sqrt{L}} \|d_{C}\|_1
 }
@@
 
+\Result
+{Theorem}
+{
+Let \(y\), \(P\), \(g\), \(\hat{g}\), \(d\) be defined as above.
+Then, if \(g\) is almost-\(L\)-sparse with residue \(\epsilon(N,L)\), then
+\Disp{
+-\|g_{\MC{C}}\|_2
+\leq C 4 (\log N_g) \cdot \left( L +\F{1}{L} \epsilon(N,L) \right)
+}
+with overwhelming probability.
+}
+
+\Disp{
+\| d \|_2^2
+\leq &\|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2 \\
+\leq \F{1}{(1-\delta_{2s})^2}
+\left(
+\|P_{\MC{A}\MC{B}}^\Tr P d\|_2^2
++\F{\delta_{3s}^2} {(1-\delta_{2s})^2 L} \|d_{C}\|_1^2
+\right)
++\F{1}{L} \|d_{\MC{C}}\|_1^2
+}
+
 { \color{red} (To be done) }

### 2019-01-08 ongoing/report/sec_1_introduction.tex
Finish the Main Bound

@@
 Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
-For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the RIP of order \(s\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq s\), for all \(\MC{T} \subset T(N_m)\) with \(|\MC{T}| \leq s\),
+For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the RIP of order \(s\) with respect to parameter \(0 \leq \d_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq s\), for all \(\MC{T} \subset T(N_m)\) with \(|\MC{T}| \leq s\),
 %
 \Disp{
-(1-\delta_s) \|h\|^2
+(1-\d_s) \|h\|^2
 \leq \|P_{\MB{T}} h\|_2^2
-\leq (1+\delta_s) \|h\|^2
+\leq (1+\d_s) \|h\|^2
 }
@@
 
-RIP of order \(s\) is essentially saying that the matrix \(X\) is ``almost unitary'' up to ``relative error'' \(\delta_s\).
+RIP of order \(s\) is essentially saying that the matrix \(X\) is ``almost unitary'' up to ``relative error'' \(\d_s\).
 
@@
 
-The constant \(\delta\) in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(P\) is fully unitary, rendering the RIP an important role.
+The constant \(\d\) in the proof of DS is significant.
+Indeed, we may observe that in theorem (), the bound is not tightest when \(\d=0\), i.e., that \(P\) is fully unitary, rendering the RIP an important role.
 Here, it is not clear at first what matrices serves as the RIP condition.
@@
 {
-Let each entry of random matrix \(P \in \MB{M}_\MB{K} (N_m, N_p)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{N_m}\) (that is, Rademacher distribution).
+Let each entry of random matrix \(P \in \MB{M}_\MB{K} (N_m, N_p)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\R{N_m}\) (that is, Rademacher distribution).
 Then, with \(0 <\epsilon <1\),
@@
 {
-Following the setting described above, suppose, for \(0 <\delta <1\),
+Following the setting described above, suppose, for \(0 <\d <1\),
 %
 \Disp{
-M \geq 16s \log (N/\delta)
+M \geq 16s \log (N/\d)
 }
 %
-Then OMP (Algorithm \_\_) recovers \(x\) completely, with overwhelming probability \(1-\delta\).
+Then OMP (Algorithm \_\_) recovers \(x\) completely, with overwhelming probability \(1-\d\).
 }

### 2019-01-08 ongoing/report/sec_2_problem_setting.tex
Finish the Main Bound

@@
 H
-=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \varphi_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \vartheta_l' \right)^\H
+=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \f_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \th_l' \right)^\H
 }
 %
-The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
+The physical meaning of \(\th_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\th_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
 For our purpose, we may absorb the argument of \(\V{a}\) as
@@
 \Disp{
-\varphi_l
-=\F{d_{\RM{arr}}} {\lambda} \sin \varphi_l' \\
-\vartheta_l
-=\F{d_{\RM{arr}}} {\lambda} \sin \vartheta_l'
+\f_l
+=\F{d_{\RM{arr}}} {\lambda} \sin \f_l' \\
+\th_l
+=\F{d_{\RM{arr}}} {\lambda} \sin \th_l'
 }
@@
 H
-=\sum_{l=0}^L \alpha_l \V{a} (\varphi_l) \V{a} (\vartheta_l)^\H
+=\sum_{l=0}^L \alpha_l \V{a} (\f_l) \V{a} (\th_l)^\H
 }
@@
 \M{K} \in &\MB{M}_{\MB{C}} (N_H, N_H) \NT \\
-\M{K} (n_1, n_2) =&\F{1} {\sqrt{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \\
+\M{K} (n_1, n_2) =&\F{1} {\R{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \\
 \quad n_1, n_2 =&0, 1, \dotsc, N_H-1 \NT

### 2019-01-08 ongoing/report/sec_3_theorems_and_proofs.tex
Finish the Main Bound

@@
 \Disp{
-\gamma =\sqrt{2 \log N_g}
+\gamma =\R{2 \log N_g}
 }
@@
 {
-Suppose \(0 \leq \varphi \leq 2\pi k /N_H\), \(k =0, \dotsc, N_H-1\).
-Let \(\varphi\) be given, and array response \(\V{a} (\varphi)\) defined as in ().
-Then \(\V{a} (\varphi)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R\)
+Suppose \(0 \leq \f \leq 2\pi k /N_H\), \(k =0, \dotsc, N_H-1\).
+Let \(\f\) be given, and array response \(\V{a} (\f)\) defined as in ().
+Then \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
 %
@@
 \Disp{
-D (\varphi')
-:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \varphi'} \right| \NT \\
-=&\F{|\sin (N_H \varphi'/2)|}{|\sin (\varphi' /2)|},
-\quad 0 \leq \varphi' \leq \pi
+D (\f')
+:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} \right| \NT \\
+=&\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|},
+\quad 0 \leq \f' \leq \pi
 }
@@
 \Disp{
-\left| D (\varphi') \right|
-= \F{48}{|\varphi'^2 -24| |\varphi'|}
-\quad 0 \leq \varphi' \leq \pi,
+\left| D (\f') \right|
+= \F{48}{|\f'^2 -24| |\f'|}
+\quad 0 \leq \f' \leq \pi,
 }
 
-Particularly, for arbitrary \(\varphi\), find \(k\) so that
+Particularly, for arbitrary \(\f\), find \(k\) so that
 \Disp{
-\eta :=&\varphi -\F{2\pi k}{N_H}, \\
+\eta :=&\f -\F{2\pi k}{N_H}, \\
 \left| \eta \right|
@@
 \Disp{
-K^\H a(\varphi) (k)
-=D \left( \varphi -\F{2 \pi k} {N_H} \right)
+K^\H a(\f) (k)
+=\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right)
 }
@@
 \Disp{
-R(\eta) :=\sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
+R(\eta)
+:=\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
 }
@@
 R(\eta) -\F{2\pi} {N_H}
-\leq N_H \int_{\varphi'=2\pi L/N_H}^{2\pi} |D(\varphi')| d \varphi'
+\leq \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
 }
-Bound \(D\) by above technique, meanwhile we notice \(\varphi' <24\).
+Bound \(D\) by above technique, meanwhile we notice \(\f' <24\).
 \Disp{
-R(\varphi)
-\leq &\F{N_H}{2\pi} \int_{\varphi'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\varphi'^2) \varphi'} d \varphi'
+R(\f)
+\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
 +\F{2\pi} {N_H} \\
-=&\F{N_H}{\pi} \log \F{2\pi N_H}{L} -\log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+=&\F{1}{\pi} \log \F{2\pi N_H}{L}
+-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
 +\F{2\pi} {N_H}
 }
-Notice the second log term \(<1\) and we drop that.
+Notice the argument of log in the second term \(<1\), and we drop that.
 Also drop \(2\pi /N_H\) since it is small.
@@
 \Disp{
-R(\varphi)
-\leq \F{N_H}{\pi} \log \F{N_H}{L}.
+R(\f)
+\leq \F{1}{\pi} \log \F{N_H}{L}.
 }
@@
 {
-Let \(\varphi\) and \(\vartheta\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
+Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
 Let \(g\) be defined as above.
-Then \(g\) is almost-\(L\)-sparse with \(\ell_1\)-residue
+Then \(g\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
 %
@@
 R
-\leq \F{L N_H^2}{\pi^2} \left( \log \F{N_H}{L} \right)
+\leq \F{L}{\pi^2} \left( \log \F{N_H}{L} \right)^2
 }
@@
 \Disp{
-\delta_{s+s'} -\max (\{\delta_s, \delta_{s'}\})
+\d_{s+s'} -\max (\{\d_s, \d_{s'}\})
 \leq \tau_{s, s'}
-\leq \delta_{s+s'}
+\leq \d_{s+s'}
 }
@@
 
-Thus \(\delta_s\), which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
-We may well keep track of \(\delta_s\) only.
+Thus \(\d_s\), which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
+We may well keep track of \(\d_s\) only.
 
@@
 Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
-Then \(P\) is RIP according to \(\delta\) for at least probability
+Then \(P\) is RIP according to \(\d\) for at least probability
 \Disp{
-   1 -2 \left( \F{12}{\delta} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\delta}{2} N_p \right]
+   1 -2 \left( \F{12}{\d} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\d}{2} N_p \right]
 }
@@
 |\IP{ z, P(:, n_g) }|
-\leq& 2 \sqrt{\log N_g},
+\leq& 2 \R{\log N_g},
 \quad n_g =1, \dotsc, N_g.
@@
 \|P^\H P d\|_\infty
-\leq& 4 \sqrt{\log N_g},
+\leq& 4 \R{\log N_g},
 \quad n_g =1, \dotsc, N_g.
@@
 \leq &\| P^\H (y -P \hat{g}) \|_\infty \\
-\leq &2\sqrt{\log N_g}
+\leq &2\R{\log N_g}
 }
@@
 \leq &\|\IP{ z, P (:,n_y) }\| +\IP{ y -P \hat{g}, P (:,n_y) } \\
-\leq &2 \sqrt{\log N_g} +2 \sqrt{\log N_g}
+\leq &2 \R{\log N_g} +2 \R{\log N_g}
 }
@@
 \|P^\H P d\|_\infty
-\leq &4 \sqrt{\log N_g}.
+\leq &4 \R{\log N_g}.
 }
@@
 {
-Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with respect to \(\delta_s\).
+Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with respect to \(\d_s\).
 %
@@
 \|d_{\MC{AB}}\|_2
-\leq \F{1}{1-\delta_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\delta_{3s}}{(1-\delta_{2s}) \sqrt{L}} \|d_{C}\|_1
+\leq \F{1}{1-\d_{2L}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\d_{3L}}{(1-\d_{2L}) \R{L}} \|d_{C}\|_1
 }
@@
 Let \(y\), \(P\), \(g\), \(\hat{g}\), \(d\) be defined as above.
-Then, if \(g\) is almost-\(L\)-sparse with residue \(\epsilon(N,L)\), then
+Then
 \Disp{
--\|g_{\MC{C}}\|_2
-\leq C 4 (\log N_g) \cdot \left( L +\F{1}{L} \epsilon(N,L) \right)
+\|d\|_2
+\leq \F{4 L^4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) ( \log N_H )^4
 }
@@
 
+We are ready to combine previous lemmata.
+The first quantity we want to bound away is
+\Disp{
+\|P_{\MC{A}\MC{B}}^\Tr P d\|_2
+\leq &\|P^\Tr P d\|_2 \NT \\
+\leq &\R{N_g} \|P^\Tr P d\|_\infty \NT \\
+\leq &4 \R{ N_g \log N_g }
+}
+Thus, by virtue of Lemma (),
+\Disp{
+\| d_{A} \|_1
+\leq &\R{L} \| d_{A} \|_2 \NT \\
+\leq &\R{L} \| d_{\MC{AB}} \|_2 \NT \\
+\leq &\F {\d_{3L}} {1-\d_{2L}} \| d_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
+}
+
+As the next step, we must eliminate \(\|d_{\MC{A}}\|_1\) in rhs of Lemma ().
+\Disp{
+\| d_{\MC{C}} \|_1
+\leq &\| d_{\MC{A}} \|_1 +2 \| g_{\MC{C}} \|_1 \NT \\
+\leq &\F {\d_{3L}} {1-\d_{2L}} \| d_{\MC{C}} \|_1
++2 \| g_{\MC{C}} \|_1
++\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
+}
+Or,
+\Disp{
+\| d_{\MC{C}} \|_1
+\leq &2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| g_{\MC{C}} \|_1
++\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
+}
+
+We are ready to bound \(\| d \|_2^2\).
+Using Lemma () again, we have
 \Disp{
 \| d \|_2^2
-\leq &\|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2 \\
-\leq \F{1}{(1-\delta_{2s})^2}
-\left(
-\|P_{\MC{A}\MC{B}}^\Tr P d\|_2^2
-+\F{\delta_{3s}^2} {(1-\delta_{2s})^2 L} \|d_{C}\|_1^2
-\right)
-+\F{1}{L} \|d_{\MC{C}}\|_1^2
+\leq &\|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2 \NT \\
+\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|d_{\MC{C}}\|_1^2
++\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|d_{\MC{C}}\|_1 \NT \\
+&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g
+}
+Finally, plug in the bound for \(\|d_{\MC{C}}\|_1\), the last unknown, and we make use of the almost-sparsity condition of \(\|d_{\MC{C}}\|_1\).
+There are several dozens of terms if we expand all.
+but for simplicity, we keep only the leading term under the approximation
+\Disp{
+1 \ll L \ll N_g
+}
+And expand to the first order expressions containing \(\d_{2L}\) or \(\d_{3L}\) in the denominator using
+\Disp{
+\d_{2L} <\d_{3L} \ll 1.
+}
+Then
+\Disp{
+\|d\|_2^2
+\leq \F{4 L^4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) ( \log N_H )^4
 }

### 2019-01-08 ongoing/presentation/slides.tex
Create slides

\documentclass{beamer}

\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{stackengine}

\setcounter{section}{-1}

\newcommand{\Disp}[1]{\begin{align} #1 \end{align}}

\renewcommand{\H}{\dagger}
\newcommand{\Tr}{\intercal}
\newcommand{\NT}{\notag}
\renewcommand{\d}{\delta}
\newcommand{\f}{\varphi}
\renewcommand{\th}{\vartheta}
\newcommand{\I}{\item}

\newcommand{\MB}[1]{\mathbb{#1}}
\newcommand{\MC}[1]{\mathcal{#1}}
\newcommand{\MF}[1]{\mathfrak{#1}}
\newcommand{\RM}[1]{\mathrm{#1}}
\newcommand{\R}[1]{\sqrt{#1}}
\newcommand{\F}[1]{\frac{#1}}
\newcommand{\V}[1]{\stackunder[1.2pt]{$#1$}{\rule{.9ex}{.075ex}}}
\newcommand{\M}[1]{\V{\V{#1}}}
\newcommand{\T}[1]{\tilde{#1}}
\newcommand{\IP}[1]{\langle #1 \rangle}

\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
\author{Presenter: Tzu-Yu Jeng \\ Advisor: Prof.\ H.J.\ Su}
\date{Jan.\ 9, 2019}
\institute{Graduate Instute of Commnication Engineering, NTU}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{Sample frame title}
This is a text in the first frame. This is a text in the first frame. This is a text in the first frame.
\end{frame}

\begin{frame}
\frametitle{Notation}
\begin{itemize}
\I \(\V{a}\) denotes vectors
\I \(\M{A}\) denotes matrices
\I \(\MB{K}\) refers to either \(\MB{R}\) or \(\MB{C}\).
\I \(\MB{V}_{\MB{K}} (N)\) is the Hilbert space \(\MB{K}^N\) over \(\MB{K}\)
\I \(\MB{M}_{\MB{K}} (M,N)\) is the collection of \(M\) by \(N\) matrices.
\I \(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm \(\V{a}\)
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Channel Model}
\begin{itemize}
\I The response of uniform linear array is
\Disp{
\V{a} (\psi')
=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
\in \MB{V}_\MB{C} (N_H)
}
\I Let the angle of departure and arrival absorb the factor
\Disp{
\f_l =\dfrac{d_{\RM{arr}}} {\lambda} \sin \f_l', \quad \th_l =\dfrac{d_{\RM{arr}}} {\lambda} \sin \th_l'
}
\I The channel matrix is
\Disp{
=\sum_{l=0}^L \alpha_l \V{a} (\f_l) \V{a} (\th_l)^\H
\in \MB{M}_\MB{C} (N_H, N_H)
}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Precoders Model}
\begin{itemize}
\I We consider the hybrid configuration at both transmitter and receiver end.
In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
In the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
\Disp{
\M{F}_B \in &\MB{M}_{\MB{C}} (N_R, N_Y) \\
\M{F}_R \in &\MB{M}_{\MB{C}} (N_H, N_R) \\
\M{W}_R \in &\MB{M}_{\MB{C}} (N_R, N_H) \\
\M{W}_B \in &\MB{M}_{\MB{C}} (N_Y, N_R)
}
\I Recall the constraint of magnitude for analog precoders:
\Disp{
|\M{F}_R (n_h, n_r)| =&1, \quad |\M{W}_R (n_r, n_h)| =1, \\
n_h =&1, \dotsc N_H, \quad n_r =1, \dotsc N_R \NT
}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Effective Channel}
\begin{itemize}
\I We have the effective channel \(Y =W_B W_R ( H F_R F_B +Z ) \in \MB{M}_{\MB{C}} (N_Y, N_R)\)
\I We may estimate \(\M{Y} (:,n_y)\) with \(\M{W}_B \M{W}_R [ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} ]\), \(n_y =1, 2, \dotsc, N_Y\), using pilog signal as unit vectors \(\V{u}_{n_y}\).
\I It remains to recover \(\M{H}\) with knowledge of \(\M{Y}\), while \(\M{W}_R\), \(\M{W}_B\), \(\M{F}_R\), and \(\M{F}_B\) are in our control
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Vectorization}
Previous literature usually approaches the problem as
\Disp{
\V{h}
:= &\RM{vec} (\M{H})
\in \MB{V}_{\MB{C}} (N_g) \\
\V{y}
:= &\RM{vec} (\M{Y})
\in \MB{V}_{\MB{C}} (N_y) \\
\V{z}^\star
:= &\RM{vec} (\M{Z})
\in \MB{V}_{\MB{C}} (N_y) \\
\M{P}^\star
:= &(\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
\in \MB{M}_{\MB{C}} (N_y, N_g).
}
So that \(\V{y} =\M{P}^\star \V{h} +\V{z}^\star\)
\end{frame}

\begin{frame}
\frametitle{Vectorization}
But if we write \( \M{G} =\M{K}^\H \M{H} \M{K} \), i.e.\ the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
\Disp{
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
\in \MB{M}_{\MB{C}} (N_Y, N_Y) \\
\M{P}
:=(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
\in \MB{M}_{\MB{C}} (N_Y^2, N_H^2)
}
where accordingly \(\V{g} := \RM{vec} (\M{G}) \in \MB{M}_{\MB{C}} (N_g)\), \(\V{z} := \RM{vec} (\M{K}^\H \M{Z}) \in \MB{V}_{\MB{C}} (N_y)\),
and for short we set \(N_g =N_H^2\) and \(N_y =N_Y^2\),
so that
\Disp{
\V{y}
=\M{P} \V{g} +\V{z}
}

\end{frame}

\begin{frame}
\frametitle{Lemma: \(g\) is Almost Sparse}
\(\forall \f\), \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
\Disp{
R
\leq 2 N_H \log \F{2\pi N_H}{L}.
}
\end{frame}

\begin{frame}
\frametitle{Proof (1/3)}
\Disp{
D (\f')
:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} \right|
=\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|} \\
\left| x -\F{x^3}{6} \right|
\leq &\sin x, \quad -\pi \leq x \leq \pi \\
\left| D (\f') \right|
= &\F{48}{|\f'^2 -24| |\f'|}
}
\begin{enumerate}
\I Definition and arrangement
\I Can be shown with basic calculus
\I Plug into \(D\)
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof (2/3)}
\Disp{
\M{K}^\H \V{a}(\f) (k)
=&\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right) \\
R(\eta)
:=&\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right) \\
R(\eta) -\F{2\pi} {N_H}
\leq &\F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
}
\begin{enumerate}
\I Straightforward
\I Definition
\I Approximation of rectangle to integral
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof (3/3)}
\Disp{
R(\f)
\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \NT \\
=&\F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H} \\
\leq &\F{1}{\pi} \log \F{N_H}{L}.
}
\begin{enumerate}
\I Plugging in
\I Calculation
\I Dropping terms
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Lemma (Tentative): \(\V{g}\) is Almost-\(L\)-Sparse}
Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\).
Then \(\V{g}\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
\Disp{
R
\leq \F{L}{\pi^2} \left( \log \F{N_H}{L} \right)^2
}
\end{frame}

\begin{frame}
\frametitle{Lemma}
Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
Then \(P\) is RIP according to \(\d\) for at least probability
\Disp{
1 -2 \left( \F{12}{\d} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\d}{2} N_p \right]
}
{\small Source: R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263 }
\end{frame}

\begin{frame}
\frametitle{Definitions}
\begin{itemize}
\I Denote \(d =\hat{g} -g\)
\I \(\MC{A}\) be the largest \(s\) position of \(g\).
\I \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
\I \(\MC{C} =T(N_g) -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
\I Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
\I we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Lemmata}
\begin{itemize}
\I \( \|\V{d}_{\MC{C}}\|_1 \leq \|\V{d}_{\MC{A}}\|_1 +2\|\V{g}_{C}\|_1 \)
\I \( |\IP{ \V{z}, \M{P}(:, n_g) }| \leq 2 \R{\log N_g}, \quad n_g =1, \dotsc, N_g. \) for overwhelming probability
\I \( \|\M{P}^\H \M{P} \V{d}\|_\infty \leq 4 \R{\log N_g}, \quad n_g =1, \dotsc, N_g \) for overwhelming probability
\end{itemize}
{\small Source: E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6}
\end{frame}

\begin{frame}
\frametitle{Lemmata}
\begin{itemize}
\I \( \|\V{d}_{\MC{AB}}\|_2 \leq \dfrac{1}{1-\d_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\dfrac{\d_{3s}}{(1-\d_{2s}) \R{s}} \|d_{C}\|_1 \) for overwhelming probability
\I \( \|\V{d}\|_2^2 \leq \|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\dfrac{1}{s} \|\V{d}_{\MC{C}}\|_1^2 \)
\end{itemize}
{\small Source: E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6}
\end{frame}

\begin{frame}
\frametitle{The Main Bound}
Let \(\V{y}\), \(\M{P}\), \(\V{g}\), \(\hat{\V{g}}\), \(\V{d}\) be defined as above, and set \(s=L\), then
\Disp{
\|\V{d}\|_2
\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
}
\end{frame}

\begin{frame}
\frametitle{Proof (1/4)}
\Disp{
\|\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}\|_2
\leq &\|\M{P}^\Tr \M{P} \V{d}\|_2 \NT \\
\leq &\R{N_g} \|\M{P}^\Tr \M{P} \V{d}\|_\infty \NT \\
\leq &4 \R{ N_g \log N_g }
}
\begin{enumerate}
\I Inclusion of larger support
\I \(\ell_p\) norm inequality
\I Plug in the Lemma for \(\|\M{P}^\Tr \M{P} \V{d}\|_2\)
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof (2/4)}
\Disp{
\| \V{d}_{A} \|_1
\leq &\R{L} \| \V{d}_{A} \|_2 \NT \\
\leq &\R{L} \| \V{d}_{\MC{AB}} \|_2 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
}
\begin{enumerate}
\I \(\ell_p\) norm inequality
\I Inclusion of larger support
\I Plug in the Lemma for \(\|\V{d}_{\MC{A}\MC{B}}\|_2\)
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof (3/4)}
\Disp{
\| \V{d}_{\MC{C}} \|_1
\leq &\| \V{d}_{\MC{A}} \|_1 +2 \| \V{g}_{\MC{C}} \|_1 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1
+2 \| \V{g}_{\MC{C}} \|_1
+\F {4} {1-\d_{2L}} \R{L N_g \log N_g} \\
\| \V{d}_{\MC{C}} \|_1
\leq &2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| \V{g}_{\MC{C}} \|_1
+\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
}
\begin{enumerate}
\I Copy the Lemma for \(\| \V{d}_{\MC{C}} \|_1\)
\I Plug in the previous eqn.\ for \(\| \V{d}_{\MC{A}} \|_1\)
\I Cancellation, simplification
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof (4/4)}
\Disp{
\| \V{d} \|_2^2
\leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|\V{d}_{\MC{C}}\|_1^2 \NT \\
&\quad +\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\
&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g \\
\|\V{d}\|_2^2
\leq &\F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
}
\begin{enumerate}
\I Copy the Lemma for \(\| \V{d} \|_2^2\)
\I Plug in the Lemma for \(\|\V{d}_{\MC{A}\MC{B}}\|_2\)
\I Approximation with \(1 \ll L \ll N_g\), and \(\d_{2L} <\d_{3L} \ll 1\)
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof}
\Disp{
}
\begin{enumerate}
\I 
\I 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof}
\Disp{
}
\begin{enumerate}
\I 
\I 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof}
\Disp{
}
\begin{enumerate}
\I 
\I 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof}
\Disp{
}
\begin{enumerate}
\I 
\I 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof}
\Disp{
}
\begin{enumerate}
\I 
\I 
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Conclusion}
\begin{enumerate}
\I We are concerned with the problem of effective and estimation of the millimeter wave channel by exploiting its sparsity
\I We adopt The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
\I We have derived the generalization of DS for complex vectors
\I We proceed the estimation algorithm in the spatial frequency domain, assuming the virtual channel model according to uniform linear array response, 
\I We proved explicitly that the probability that the expected square error is bounded is overwhelming, where the bounding constant is an explicit function of the number of path
\I It remains to transform DS into Second Order Cone Problem, and finding the Lagrangian and dual problem, do the simulation and compare the theoretical bound
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{References}
\begin{enumerate}
{ \small
\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
}
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Proof}
\Disp{
}
\begin{enumerate}
\I 
\I 
\end{enumerate}
\end{frame}

% % % % % % % % % % % % % % % % % % % %

\end{document}

\begin{frame}
\frametitle{Definition}
For \(\MC{T}, \MC{T}' \subset \{1, \dotsc, N_p\}\), define the \(s, s'\)-restricted orthogonality constant \(\tau_{s,s'} >0\) to be the smallest such that
%
\Disp{
| \IP{ P_{\MC{T}} h, P_{\MC{T}'} h' } |
\leq \tau_{s, s'} \cdot \| h \|_2 \|h'\|_2
}
\end{frame}

\begin{frame}
\frametitle{Lemma: \(\d_{s+s'}\) Can Bound \(\tau_{s, s'}\)}
Let \(P\) be given.
Then \(\tau_{s, s'}\) is bounded in both direction as follows,
\Disp{
\d_{s+s'} -\max (\{\d_s, \d_{s'}\})
\leq &\tau_{s, s'} \\
\leq &\d_{s+s'}
}
{\small Source: E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12. }
\end{frame}

### 2019-01-08 ongoing/report/sec_3_theorems_and_proofs.tex
Create slides

@@
 
-We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(s\).
-At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.
+We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\), which guarantees, at the heart of the argument, that \(g\) is almost-sparse
 
@@
 {
-For \(x \in \MB{V}_{\MB{K}}(N)\), we say \(x\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
+For \(\V{x} \in \MB{V}_{\MB{K}}(N)\), we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
 \Disp{
-\sum_{n=s+1}^N |S(x) (n)|
+\sum_{n=s+1}^N |S(\V{x}) (n)|
 \leq R.
@@
 \Disp{
-K^\H a(\f) (k)
+\M{K}^\H \V{a}(\f) (k)
 =\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right)
@@
 \leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
-+\F{2\pi} {N_H} \\
++\F{2\pi} {N_H} \NT \\
 =&\F{1}{\pi} \log \F{2\pi N_H}{L}
@@
 Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
-Let \(g\) be defined as above.
-Then \(g\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
+Let \(\V{g}\) be defined as above.
+Then \(\V{g}\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
 %
@@
 {
-For \(\MC{T}, \MC{T}' \subset \{1, \dotsc, N_p\}\), define the \(s,s'\)-restricted orthogonality constant \(\tau_{s,s'} >0\) to be the smallest such that
+For \(\MC{T}, \MC{T}' \subset \{1, \dotsc, N_p\}\), define the \(s, s'\)-restricted orthogonality constant \(\tau_{s,s'} >0\) to be the smallest such that
 %
@@
 {
-Let \(g\) and \(d\) be defined as above.
+Let \(\V{g}\) and \(\V{d}\) be defined as above.
 Then
@@
 \Disp{
-\|d_{\MC{C}}\|_1
-\leq \|d_{\MC{A}}\|_1 +2\|g_{C}\|_1
+\|\V{d}_{\MC{C}}\|_1
+\leq \|\V{d}_{\MC{A}}\|_1 +2\|\V{g}_{C}\|_1
 }
@@
 \Disp{
-\|g\|_1
--\|d_{\MC{A}}\|_1
-+\|d_{\MC{C}}\|_1
--\|g_{\MC{C}}\|_1
-\leq \|g+d\|_1
+\|\V{g}\|_1
+-\|\V{d}_{\MC{A}}\|_1
++\|\V{d}_{\MC{C}}\|_1
+-\|\V{g}_{\MC{C}}\|_1
+\leq \|\V{g} +\V{d}\|_1
 }
-In the first line, we recall \(g =g_{\MC{A}}\).
+In the first line, we recall \(\V{g} =\V{g}_{\MC{A}}\).
 On the other hand, by construction that \(\hat{g}\) minimizes the \(\ell_1\)-norm,
 \Disp{
-\|g+d\|_1
-=\|\hat{g}\|_1
-\leq \|g\|_1
+\|\V{g} +\V{d}\|_1
+=\|\hat{\V{g}}\|_1
+\leq \|\V{g}\|_1
 }
@@
 {
-Let \(z\) and \(P\) be defined as above.
+Let \(\V{z}\) and \(\M{P}\) be defined as above.
 Then
@@
 \Disp{
-|\IP{ z, P(:, n_g) }|
+|\IP{ \V{z}, \M{P}(:, n_g) }|
 \leq& 2 \R{\log N_g},
@@
 
-This only depends on the fact that \(P(:, n_g)\) has unity \(\ell_2\)-norm, and on the randomness of \(z\).
+This only depends on the fact that \(\M{P}(:, n_g)\) has unity \(\ell_2\)-norm, and on the randomness of \(\V{z}\).
+
+Recall the following bound for \(Q\) function
+\Disp{
+Q(x)
+\leq \F{1}{2} \RM{e}^{-x^2/2}
+}
+Particularly, for \(x =\R{2 \log N_g}\), according to CLT,
+\Disp{
+Q(\R{2 \log N_g})
+=\F{1}{N_g}.
+}
 
@@
 {
-Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
+Let \(\V{d}\) and \(\M{P}\) be defined as above, and \(\M{P}\) satisfies RIP as in ().
 %
 \Disp{
-\|P^\H P d\|_\infty
+\|\M{P}^\H \M{P} \V{d}\|_\infty
 \leq& 4 \R{\log N_g},
@@
 \Disp{
-&\IP{ z -(y -P \hat{g}), P (:,n_y) } \NT \\
-=&\IP{ P \hat{g} -P g, P (:,n_y) } \NT \\
-=&\IP{ P d, P (:,n_y) }
+&\IP{ \V{z} -(\V{y} -\M{P} \hat{\V{g}}), \M{P} (:,n_y) } \NT \\
+=&\IP{ \M{P} \hat{\V{g}} -\M{P} \V{g}, \M{P} (:,n_y) } \NT \\
+=&\IP{ \M{P} \V{d}, \M{P} (:,n_y) }
 }
@@
 \Disp{
-\| P (:,n_y)^\H (y -P \hat{g}) \|
-\leq &\| P^\H (y -P \hat{g}) \|_\infty \\
+\| \M{P} (:,n_y)^\H (\V{y} -\M{P} \hat{\V{g}}) \|
+\leq &\| \M{P}^\H (\V{y} -\M{P} \hat{\V{g}}) \|_\infty \NT \\
 \leq &2\R{\log N_g}
 }
-By triangle inequality, together with lemma (), we have
+By triangle inequality, together with Lemma (), we have
 \Disp{
-\|P (:,n_y)^\H P d\|
-\leq &\|\IP{ z, P (:,n_y) }\| +\IP{ y -P \hat{g}, P (:,n_y) } \\
+\|\M{P} (:,n_y)^\H \M{P} \V{d}\|
+\leq &\|\IP{ \V{z}, \M{P} (:,n_y) }\| +\IP{ \V{y} -\M{P} \hat{\V{g}}, \M{P} (:,n_y) } \NT \\
 \leq &2 \R{\log N_g} +2 \R{\log N_g}
@@
 \Disp{
-\|P^\H P d\|_\infty
+\|\M{P}^\H \M{P} \V{d}\|_\infty
 \leq &4 \R{\log N_g}.
@@
 {
-Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with respect to \(\d_s\).
+Let \(\V{d}\) and \(\M{P}\) be defined as above, and \(\M{P}\) satisfies RIP as in () with respect to \(\d_s\).
 %
 \Disp{
-\|d_{\MC{AB}}\|_2
-\leq \F{1}{1-\d_{2L}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\d_{3L}}{(1-\d_{2L}) \R{L}} \|d_{C}\|_1
+\|\V{d}_{\MC{AB}}\|_2
+\leq \F{1}{1-\d_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\d_{3s}}{(1-\d_{2s}) \R{s}} \|d_{C}\|_1
 }
@@
 {
-Let \(d\) be defined as above.
+Let \(\V{d}\) be defined as above.
 Then
@@
 \Disp{
-\|d\|_2^2
-\leq \|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2
+\|\V{d}\|_2^2
+\leq \|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{s} \|\V{d}_{\MC{C}}\|_1^2
 }
@@
 We can now formulate and prove the main bound of ours.
+Here, we use \(s=L\) as the sparsity threshold.
 
@@
 {
-Let \(y\), \(P\), \(g\), \(\hat{g}\), \(d\) be defined as above.
+Let \(\V{y}\), \(\M{P}\), \(\V{g}\), \(\hat{\V{g}}\), \(\V{d}\) be defined as above.
 Then
 \Disp{
-\|d\|_2
-\leq \F{4 L^4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) ( \log N_H )^4
+\|\V{d}\|_2
+\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
 }
@@
 \Disp{
-\|P_{\MC{A}\MC{B}}^\Tr P d\|_2
-\leq &\|P^\Tr P d\|_2 \NT \\
-\leq &\R{N_g} \|P^\Tr P d\|_\infty \NT \\
+\|\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}\|_2
+\leq &\|\M{P}^\Tr \M{P} \V{d}\|_2 \NT \\
+\leq &\R{N_g} \|\M{P}^\Tr \M{P} \V{d}\|_\infty \NT \\
 \leq &4 \R{ N_g \log N_g }
@@
 \Disp{
-\| d_{A} \|_1
-\leq &\R{L} \| d_{A} \|_2 \NT \\
-\leq &\R{L} \| d_{\MC{AB}} \|_2 \NT \\
-\leq &\F {\d_{3L}} {1-\d_{2L}} \| d_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
+\| \V{d}_{A} \|_1
+\leq &\R{L} \| \V{d}_{A} \|_2 \NT \\
+\leq &\R{L} \| \V{d}_{\MC{AB}} \|_2 \NT \\
+\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
 }
@@
 \Disp{
-\| d_{\MC{C}} \|_1
-\leq &\| d_{\MC{A}} \|_1 +2 \| g_{\MC{C}} \|_1 \NT \\
-\leq &\F {\d_{3L}} {1-\d_{2L}} \| d_{\MC{C}} \|_1
-+2 \| g_{\MC{C}} \|_1
+\| \V{d}_{\MC{C}} \|_1
+\leq &\| \V{d}_{\MC{A}} \|_1 +2 \| \V{g}_{\MC{C}} \|_1 \NT \\
+\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1
++2 \| \V{g}_{\MC{C}} \|_1
 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
@@
 \Disp{
-\| d_{\MC{C}} \|_1
-\leq &2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| g_{\MC{C}} \|_1
+\| \V{d}_{\MC{C}} \|_1
+\leq &2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| \V{g}_{\MC{C}} \|_1
 +\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
@@
 \Disp{
-\| d \|_2^2
-\leq &\|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2 \NT \\
-\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|d_{\MC{C}}\|_1^2
-+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|d_{\MC{C}}\|_1 \NT \\
+\| \V{d} \|_2^2
+\leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
+\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|\V{d}_{\MC{C}}\|_1^2
++\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\
 &\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g
 }
-Finally, plug in the bound for \(\|d_{\MC{C}}\|_1\), the last unknown, and we make use of the almost-sparsity condition of \(\|d_{\MC{C}}\|_1\).
+Finally, plug in the bound for \(\|\V{d}_{\MC{C}}\|_1\), the last unknown, and we make use of the almost-sparsity condition of \(\|\V{d}_{\MC{C}}\|_1\).
 There are several dozens of terms if we expand all.
@@
 \Disp{
-\|d\|_2^2
-\leq \F{4 L^4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) ( \log N_H )^4
+\|\V{d}\|_2^2
+\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
 }

### 2019-01-08 ongoing/report/sec_5_back_matter.tex
Create slides

@@
 This article adopts The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
-Beside exploiting the sparsity of space domain representation as existing literature does, we proceed the estimation algorithm in the spatial frequency domain.
+Rather than exploiting the sparsity of space domain representation as existing literature does, we proceed the estimation algorithm in the spatial frequency domain.
 The technique is surely inspiring to future work, as many bounds are ready to be obtained once we change the physical model of the channel.

### 2019-01-08 ongoing/presentation/slides.tex
Finish Slides

@@
 \begin{frame}
-\frametitle{Sample frame title}
-This is a text in the first frame. This is a text in the first frame. This is a text in the first frame.
+\frametitle{Overview}
+\begin{itemize}
+\I Motivation and Background 
+\I Configuration and Problem Formulation
+\I Theorems and Proofs
+\I Conclusion and Future Work
+\I References
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Motivation (1/2)}
+\begin{itemize}
+\I Multiple-input-multiple-output (MIMO) wireless communication is widely expected to be the next-generation communication scheme.
+\I Recall that reliable communication requires that the channel response be known at the receiver, to facilitate beamforming algorithm and channel calibration
+\I And in the MIMO system, it is a non-trivial problem to estimate wireless channels.
+Meanwhile, in the millimeter wave r\`egime, which is often used together with MIMO, channel often exhibits sparse properties.
+\I If the sparsity is exploited, few observations may suffice to estimate the channel
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Motivation (2/2)}
+\begin{itemize}
+\I Recent developement on channel estimation is facilitated by advances of so-called compressed sensing (CS)
+\I CS addresses the common situation in statsitical applications that the number of model parameters \(N_p \gg\) the number of measurements \(N_m\).
+\I With insufficient (possibly noisy) measurements, how well can we recover all \(N_p\) parameters?
+Of course, more assumption must be made.
+\I The work reveals that few observations of the signal may be sufficient for us to resonstruct the signal when it is sparse.
+\I Cand\`es and Tao (2006) proposes the Dantzig Selector (DS), which was first applied in channel estimation context
+\end{itemize}
 \end{frame}
@@
 \I \(\MB{M}_{\MB{K}} (M,N)\) is the collection of \(M\) by \(N\) matrices.
-\I \(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm \(\V{a}\)
+\I \(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm of \(\V{a}\)
 \end{itemize}
+\end{frame}
 
+\begin{frame}
+\frametitle{Definitions: Sparsity}
+\begin{itemize}
+\I \(T (N_m) =\{1, \dotsc, N_m\}\) is the support of \(\MB{V}_{\MB{K}} (N_m)\).
+\I Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)\).
+Let \(\MC{T} \subset T (N_p)\).
+Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
+\I \(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if only at most \(s\) components of \(x\) is nonzero.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Program: The Dantzig Selector}
+Let \(\M{P} \in \MB{V}_\MB{R} (N_m, N_p)\) and \(\V{y} \in \MB{V}_\MB{R} (N_m)\) be given.
+Find \(\hat{\V{h}} \in \MB{V}_\MB{R} (N_m)\) with
+\Disp{
+\hat{\V{h}} =\min_{\V{h}'} \quad &\|\V{h}'\|_1 \\ \NT
+\RM{subject}\; \RM{to} \quad &\|\M{P}^\H (\M{P} \V{h} -\V{y})\|_\infty \leq \gamma
+}
+\end{frame}
+
+\begin{frame}
+\frametitle{Performance Guarantee of DS}
+\begin{itemize}
+\I Now, consider a linear transformation with noise corruption,
+\Disp{
+\V{y} =\M{P} \V{h} + \V{z}
+}
+where \(\V{z}\) is i.i.d.\ standard Gaussian.
+
+\I They showed that the mean square error \(\MB{E}(\| \V{h} -\hat{\V{h}} \|^2)\) is bounded with overwhelming probability.
+
+\I Furthermore, this \(\ell_1\)-minimization problem with \(\ell_\infty\)-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Definition: Restricted Isometry Property}
+\begin{itemize}
+\I Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
+For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the restricted isometry property (RIP) of sparsity \(s\) with respect to \(0 \leq \d_s \leq 1\), if, for all \(s\)-sparse \(\V{x} \in \MB{V}_{\MB{K}} (N_p)\), for all \(\MC{T} \subset T(N_m)\) with \(\#\{\MC{T}\} \leq s\),
+%
+\Disp{
+(1-\d_s) \|\V{x}\|^2
+\leq \|P_{\MC{T}} \V{x}\|_2^2
+\leq (1+\d_s) \|\V{x}\|_2^2
+}
+\I RIP is essentially saying that \(P\) is ``almost unitary'' up to ``relative error'' \(\d_s\).
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Orthogonal Matching Pursuit}
+\begin{itemize}
+\I Afterwards, scholars (Tropp and A C Gilbert 2007b) proposed a greedy algorithm called Orthogonal Matching Pursuit (OMP)
+\I Here, we pick up the columns of the sensing matrix \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\), thus recovering the original signal.
+\I An i.i.d.\ random sensing matrix may perform sufficiently well, and may even recover the original signal in an overwhemingly probability too.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Recent Literature on Compressive Channel Sensing}
+\begin{itemize}
+\I Scholars has since favored OMP rather than DS, let alone other sparse algorithm, without clear justification
+\I OMP's requirement on the sensing matrix (elementwise i.i.d.\ Gaussian) seems to be more restrictive than DS's (RIP)
+\I The quantization of angle in generating may be a problem, and that is difficult to analyze in OMP's setting
+\I Previous work simply assumes the norm of the channel matrix is bounded in some way, and dependency on the sparsity of the channel parameters is unknown
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Our Work}
+\begin{itemize}
+\I We will use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
+\I We will show an explicit bound, where the sparsity of the virtual channel matrix is depends explicitly on the number of paths of the channel.
+\I Bounding the beamspace sparsity, accordingly the concern of quantization error of the virtual channel's phase angle has been incorporated in our proof of the bound.
+\I We will derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
+\end{itemize}
 \end{frame}
@@
 }
-\I Let the angle of departure and arrival absorb the factor
+\I Let the virtual angle of departure and arrival be defined as thus to simplify expression
 \Disp{
@@
 }
-\I The channel matrix is
+\I Let there be \(L\) paths.
+The channel matrix is, then,
 \Disp{
+H
 =\sum_{l=0}^L \alpha_l \V{a} (\f_l) \V{a} (\th_l)^\H
@@
 \begin{frame}
-\frametitle{Precoders Model}
+\frametitle{Precoder Setting}
 \begin{itemize}
@@
 \Disp{
-|\M{F}_R (n_h, n_r)| =&1, \quad |\M{W}_R (n_r, n_h)| =1, \\
-n_h =&1, \dotsc N_H, \quad n_r =1, \dotsc N_R \NT
+|\M{F}_R (n_h, n_r)| =1, \quad |\M{W}_R (n_r, n_h)| =1, \\
+n_h =1, \dotsc N_H, \quad n_r =1, \dotsc N_R \NT
+}
+\I We also assume
+\Disp{
+N_Y \ll N_R \ll N_H
 }
@@
 }
-So that \(\V{y} =\M{P}^\star \V{h} +\V{z}^\star\)
+and for short we set \(N_g =N_H^2\) and \(N_y =N_Y^2\),
+so that
+\Disp{
+\V{y} =\M{P}^\star \V{h} +\V{z}^\star
+}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Vectorization}
+\frametitle{Beamspace Channel Representation}
 But if we write \( \M{G} =\M{K}^\H \M{H} \M{K} \), i.e.\ the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
@@
 \M{Y}
-:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
+:=&\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
 \in \MB{M}_{\MB{C}} (N_Y, N_Y) \\
 \M{P}
-:=(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
-\in \MB{M}_{\MB{C}} (N_Y^2, N_H^2)
+:=&(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
+\in \MB{M}_{\MB{C}} (N_y, N_g)
 }
-where accordingly \(\V{g} := \RM{vec} (\M{G}) \in \MB{M}_{\MB{C}} (N_g)\), \(\V{z} := \RM{vec} (\M{K}^\H \M{Z}) \in \MB{V}_{\MB{C}} (N_y)\),
-and for short we set \(N_g =N_H^2\) and \(N_y =N_Y^2\),
+where accordingly
+\Disp{
+\V{g} := &\RM{vec} (\M{G}) \in \MB{M}_{\MB{C}} (N_g) \\
+\V{z} := &\RM{vec} (\M{K}^\H \M{Z}) \in \MB{V}_{\MB{C}} (N_y)
+}
 so that
@@
 \begin{frame}
-\frametitle{Lemma: \(g\) is Almost Sparse}
+\frametitle{Lemma: \(\V{a}\) is Almost Sparse}
 \(\forall \f\), \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
@@
 \I Can be shown with basic calculus
-\I Plug into \(D\)
+\I Plug the previous eqn.\ into \(D\)
 \end{enumerate}
@@
 \begin{enumerate}
-\I Straightforward
+\I Straightforward by definition
 \I Definition
@@
 \begin{enumerate}
-\I Plugging in
+\I Plug in above bound for \(D\)
 \I Calculation
-\I Dropping terms
+\I Drop the middle term (\(<0\)) and last term (small)
 \end{enumerate}
@@
 \begin{frame}
-\frametitle{Lemma (Tentative): \(\V{g}\) is Almost-\(L\)-Sparse}
+\frametitle{Lemma (Tentative): \(\V{g}\) is Almost Sparse}
 Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\).
@@
 \begin{frame}
-\frametitle{Lemma}
+\frametitle{Lemma: RIP Probability w.r.t.\ \(\d\)}
 Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
@@
 }
-{\small Source: R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263 }
+{\small Source: Baraniuk, Davenport, DeVore, and Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices''}
 \end{frame}
@@
 \begin{itemize}
+\I Let \(\MC{A}\) be the largest \(s\) position of \(g\), \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\), and \(\MC{C} =T(N_g) -\MC{A}\)
+\I Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
+\I we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), if \( \sum_{n=s+1}^N |S(\V{x}) (n)| \leq R \)
 \I Denote \(d =\hat{g} -g\)
-\I \(\MC{A}\) be the largest \(s\) position of \(g\).
-\I \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
-\I \(\MC{C} =T(N_g) -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
-\I Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
-\I we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
+where \(S(x)\) is sorted in magnitude.
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Lemmata}
+\frametitle{Lemmata on RIP Matrix}
+For overwhelming probability,
 \begin{itemize}
-\I \( \|\V{d}_{\MC{C}}\|_1 \leq \|\V{d}_{\MC{A}}\|_1 +2\|\V{g}_{C}\|_1 \)
-\I \( |\IP{ \V{z}, \M{P}(:, n_g) }| \leq 2 \R{\log N_g}, \quad n_g =1, \dotsc, N_g. \) for overwhelming probability
-\I \( \|\M{P}^\H \M{P} \V{d}\|_\infty \leq 4 \R{\log N_g}, \quad n_g =1, \dotsc, N_g \) for overwhelming probability
+\I \( |\IP{ \V{z}, \M{P}(:, n_g) }| \leq 2 \R{\log N_g}, \quad n_g =1, \dotsc, N_g. \)  (generalized from real case)
+\I \( \|\M{P}^\H \M{P} \V{d}\|_\infty \leq 4 \R{\log N_g}, \quad n_g =1, \dotsc, N_g \) (generalized from real case)
+\I \( \|\V{d}_{\MC{AB}}\|_2 \leq \dfrac{1}{1-\d_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\dfrac{\d_{3s}}{(1-\d_{2s}) \R{s}} \|d_{C}\|_1 \)
 \end{itemize}
-{\small Source: E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6}
+{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Lemmata}
+\frametitle{Lemmata on Vector Supports}
 \begin{itemize}
-\I \( \|\V{d}_{\MC{AB}}\|_2 \leq \dfrac{1}{1-\d_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\dfrac{\d_{3s}}{(1-\d_{2s}) \R{s}} \|d_{C}\|_1 \) for overwhelming probability
+\I \( \|\V{d}_{\MC{C}}\|_1 \leq \|\V{d}_{\MC{A}}\|_1 +2\|\V{g}_{C}\|_1 \)
 \I \( \|\V{d}\|_2^2 \leq \|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\dfrac{1}{s} \|\V{d}_{\MC{C}}\|_1^2 \)
 \end{itemize}
-{\small Source: E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6}
+{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
 \end{frame}
@@
 \frametitle{The Main Bound}
-Let \(\V{y}\), \(\M{P}\), \(\V{g}\), \(\hat{\V{g}}\), \(\V{d}\) be defined as above, and set \(s=L\), then
+Let \(\V{d}\) be defined as above, and set \(s=L\), then
 \Disp{
@@
 \leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1
-+2 \| \V{g}_{\MC{C}} \|_1
-+\F {4} {1-\d_{2L}} \R{L N_g \log N_g} \\
++\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
++2 \| \V{g}_{\MC{C}} \|_1 \\
 \| \V{d}_{\MC{C}} \|_1
-\leq &2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| \V{g}_{\MC{C}} \|_1
-+\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
+\leq &\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
++2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| \V{g}_{\MC{C}} \|_1
 }
@@
 \I Plug in the Lemma for \(\|\V{d}_{\MC{A}\MC{B}}\|_2\)
-\I Approximation with \(1 \ll L \ll N_g\), and \(\d_{2L} <\d_{3L} \ll 1\)
-\end{enumerate}
-\end{frame}
-
-\begin{frame}
-\frametitle{Proof}
-\Disp{
-}
-\begin{enumerate}
-\I 
-\I 
-\end{enumerate}
-\end{frame}
-
-\begin{frame}
-\frametitle{Proof}
-\Disp{
-}
-\begin{enumerate}
-\I 
-\I 
-\end{enumerate}
-\end{frame}
-
-\begin{frame}
-\frametitle{Proof}
-\Disp{
-}
-\begin{enumerate}
-\I 
-\I 
-\end{enumerate}
-\end{frame}
-
-\begin{frame}
-\frametitle{Proof}
-\Disp{
-}
-\begin{enumerate}
-\I 
-\I 
-\end{enumerate}
-\end{frame}
-
-\begin{frame}
-\frametitle{Proof}
-\Disp{
-}
-\begin{enumerate}
-\I 
-\I 
+\I Plug in the Lemma for \(\|\V{d}_{\MC{C}}\|_1\), approximate using \(1 \ll L \ll N_g\), and \(\d_{2L} <\d_{3L} \ll 1\)
 \end{enumerate}
@@
 \begin{enumerate}
-\I We are concerned with the problem of effective and estimation of the millimeter wave channel by exploiting its sparsity
-\I We adopt The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
-\I We have derived the generalization of DS for complex vectors
-\I We proceed the estimation algorithm in the spatial frequency domain, assuming the virtual channel model according to uniform linear array response, 
-\I We proved explicitly that the probability that the expected square error is bounded is overwhelming, where the bounding constant is an explicit function of the number of path
-\I It remains to transform DS into Second Order Cone Problem, and finding the Lagrangian and dual problem, do the simulation and compare the theoretical bound
+\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity
+\I We adopt The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm
+\I We generalized DS for complex vectors, and we carried it out in the spatial frequency domain \(g\)
+\I Analogous to original DS proof, we proved explicitly that the probability that the expected square error is bounded is overwhelming, where the bounding constant is an explicit function of \(L\), the number of path
+\end{enumerate}
+\end{frame}
+
+\begin{frame}
+\frametitle{Future Work}
+It remains to
+\begin{enumerate}
+\I Transform DS into Second Order Cone Problem
+\I Find the Lagrangian and dual problem
+\I Complete the simulation
+\I Compare the theoretical bound
 \end{enumerate}
@@
 { \small
-\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
-\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
-\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
-\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
+\I W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
+\I R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
+\I S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
+\I E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
 }
@@
 \begin{frame}
-\frametitle{Proof}
-\Disp{
+\frametitle{References}
+\begin{enumerate}
+{ \small
+\I E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
+\I E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
+\I J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
+Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
+\I J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
 }
-\begin{enumerate}
-\I 
-\I 
 \end{enumerate}
@@
 }
-{\small Source: E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12. }
+{\small Source: Cand\`es and Tao (2005), ``Decoding by Linear Programming''}
 \end{frame}

### 2019-01-08 ongoing/report/sec_0_front_matter.tex
Finish Slides

@@
 Multiple-input-multiple-output (MIMO) communication is widely expected to be the next-generation wireless communication scheme.
-However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
+However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibration.
 It is then a non-trivial problem to estimate real-world wireless channels.

### 2019-01-08 ongoing/report/sec_1_introduction.tex
Finish Slides

@@
 
-To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p\) is much larger than the number of measurements \(N_m\).
-Here, we consider
+To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p \in \MB{N}\) is much larger than the number of measurements \(N_m \in \MB{N}\), namely,
 %
@@
 
-\Result
-{Definition}
-{
-We say \(T (N_m) =\{1, \dotsc, N_m\}\), \(N_m \in \MB{N}\) is the support of vector space \(\MB{V}_{\MB{K}} (N_m)\).
-}
+We will use \(T (N_m) =\{1, \dotsc, N_m\}\) to denote the support of \(\MB{V}_{\MB{K}} (N_m)\).
 
@@
 {
-\(h \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T (N_m)\) such that
+\(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T (N_m)\) such that
 %
@@
 }
-That is, only at most \(s\) components of vector \(x\) is nonzero.
+That is, only at most \(s\) components of \(x\) is nonzero.
 }
@@
 Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
-For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the RIP of order \(s\) with respect to parameter \(0 \leq \d_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq s\), for all \(\MC{T} \subset T(N_m)\) with \(|\MC{T}| \leq s\),
+For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the restricted isometry property (RIP) of sparsity \(s\) with respect to \(0 \leq \d_s \leq 1\), if, for all \(s\)-sparse \(\V{x} \in \MB{V}_{\MB{K}} (N_p)\), for all \(\MC{T} \subset T(N_m)\) with \(\#\{\MC{T}\} \leq s\),
 %
 \Disp{
-(1-\d_s) \|h\|^2
-\leq \|P_{\MB{T}} h\|_2^2
-\leq (1+\d_s) \|h\|^2
+(1-\d_s) \|\V{x}\|^2
+\leq \|P_{\MC{T}} \V{x}\|_2^2
+\leq (1+\d_s) \|\V{x}\|_2^2
 }
@@
 
-RIP of order \(s\) is essentially saying that the matrix \(X\) is ``almost unitary'' up to ``relative error'' \(\d_s\).
+RIP is essentially saying that \(P\) is ``almost unitary'' up to ``relative error'' \(\d_s\).
 
-Consider a linear transformation with noise corruption,
+Now, consider a linear transformation with noise corruption,
 %
@@
 
+They was able to show that, with Program (), the mean square error is bounded with overwhelming probability.
 And it can be shown that this \(\ell_1\)-minimization problem with \(\ell_\infty\)-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
@@
 
-Around that time, Tropp and A C Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit, that a i.i.d.\ matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.
+Around that time, Tropp and Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit (OMP), that an i.i.d.\ random matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.
 
@@
 that is, the noiseless, real-number case.
-We pick up the columns of \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\).
+We pick up the columns of \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\), thus recovering the original signal.
 
@@
 \item The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian (Tropp and Gilvert 2007) seems to be more restrictive than RIP (Cand\`es and Tao 2007).
+\item The quantization of angle in generating may be a problem, and that is difficult to analyze in OMP's setting
 \item No bounds is derived that explicitly depends on the sparsity of the channel parameters as, say, number of channel paths and array response.

### 2019-02-01 ongoing/presentation/slides.tex
Slightly fix notation

@@
 \setcounter{section}{-1}
+\newcounter{countRef}
 
@@
 \I Recall that reliable communication requires that the channel response be known at the receiver, to facilitate beamforming algorithm and channel calibration
-\I And in the MIMO system, it is a non-trivial problem to estimate wireless channels.
-Meanwhile, in the millimeter wave r\`egime, which is often used together with MIMO, channel often exhibits sparse properties.
+\I And in the MIMO system, it is a non-trivial problem to estimate wireless channels due to high complexity
+\I Meanwhile, in the millimeter wave r\`egime, which is often used together with MIMO, channel often exhibits sparse properties.
 \I If the sparsity is exploited, few observations may suffice to estimate the channel
@@
 Of course, more assumption must be made.
-\I The work reveals that few observations of the signal may be sufficient for us to resonstruct the signal when it is sparse.
-\I Cand\`es and Tao (2006) proposes the Dantzig Selector (DS), which was first applied in channel estimation context
+\I Work on CS reveals that few observations of the signal may be sufficient for us to resonstruct the signal when it is sparse.
+\I In the advent, Cand\`es and Tao (2006) proposes the Dantzig Selector (DS).
+It was first applied in channel estimation context
 \end{itemize}
@@
 \begin{itemize}
-\I \(T (N_m) =\{1, \dotsc, N_m\}\) is the support of \(\MB{V}_{\MB{K}} (N_m)\).
 \I Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)\).
-Let \(\MC{T} \subset T (N_p)\).
+Let \(\MC{T} \subset \{1, \dotsc, N_m\}\).
 Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
-\I \(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if only at most \(s\) components of \(x\) is nonzero.
+\I \(\V{x} \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if only at most \(s\) components of \(\V{x}\) is nonzero.
+\I (New def.) We say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), if \( \sum_{n=s+1}^N |S(\V{x}) (n)| \leq R \) where \(S(\V{x})\) is sorted in magnitude.
 \end{itemize}
@@
 \frametitle{Program: The Dantzig Selector}
-Let \(\M{P} \in \MB{V}_\MB{R} (N_m, N_p)\) and \(\V{y} \in \MB{V}_\MB{R} (N_m)\) be given.
+Let \(\M{P} \in \MB{V}_\MB{R} (N_m, N_p)\) and \(\V{y} \in \MB{V}_\MB{R} (N_m)\) be given, and \(\gamma\) be fixed.
 Find \(\hat{\V{h}} \in \MB{V}_\MB{R} (N_m)\) with
@@
 \hat{\V{h}} =\min_{\V{h}'} \quad &\|\V{h}'\|_1 \\ \NT
-\RM{subject}\; \RM{to} \quad &\|\M{P}^\H (\M{P} \V{h} -\V{y})\|_\infty \leq \gamma
+\RM{subject}\; \RM{to} \quad &\|\M{P}^\H (\M{P} \V{h'} -\V{y})\|_\infty \leq \gamma
 }
@@
 \I Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
-For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the restricted isometry property (RIP) of sparsity \(s\) with respect to \(0 \leq \d_s \leq 1\), if, for all \(s\)-sparse \(\V{x} \in \MB{V}_{\MB{K}} (N_p)\), for all \(\MC{T} \subset T(N_m)\) with \(\#\{\MC{T}\} \leq s\),
+For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the restricted isometry property (RIP) of sparsity \(s\) with respect to \(0 \leq \d_s \leq 1\), if, for all \(s\)-sparse \(\V{x} \in \MB{V}_{\MB{K}} (N_p)\), for all \(\MC{T} \subset \{1, \dotsc, N_p\}\) with \(\#\{\MC{T}\} \leq s\),
 %
@@
 \begin{itemize}
-\I Afterwards, scholars (Tropp and A C Gilbert 2007b) proposed a greedy algorithm called Orthogonal Matching Pursuit (OMP)
+\I Afterwards, scholars (Tropp and Gilbert 2007b) proposed a greedy algorithm called Orthogonal Matching Pursuit (OMP)
 \I Here, we pick up the columns of the sensing matrix \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\), thus recovering the original signal.
@@
 \I Scholars has since favored OMP rather than DS, let alone other sparse algorithm, without clear justification
+\I Previous work simply assumes the norm of the channel matrix is bounded in some way, and dependency on the sparsity of the channel parameters is unknown
 \I OMP's requirement on the sensing matrix (elementwise i.i.d.\ Gaussian) seems to be more restrictive than DS's (RIP)
 \I The quantization of angle in generating may be a problem, and that is difficult to analyze in OMP's setting
-\I Previous work simply assumes the norm of the channel matrix is bounded in some way, and dependency on the sparsity of the channel parameters is unknown
 \end{itemize}
@@
 \V{a} (\psi')
-=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
+=\F{1}{\R{N_H}} \sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
 \in \MB{V}_\MB{C} (N_H)
@@
 \frametitle{Beamspace Channel Representation}
-But if we write \( \M{G} =\M{K}^\H \M{H} \M{K} \), i.e.\ the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
+Let \(\M{K}\) be the DFT matrix.
+If we write \( \M{G} =\M{K}^\H \M{H} \M{K} \), i.e.\ the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
 \Disp{
@@
 \M{P}
-:=&(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
+:=&(\M{F}_B^\Tr \M{F}_R^\Tr \M{K}^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
 \in \MB{M}_{\MB{C}} (N_y, N_g)
@@
 }
+\end{frame}
 
+\begin{frame}
+\frametitle{Proposed Program}
+\begin{itemize}
+\I Let \(\M{P}, \V{y}\) be given.
+Then, with parameter \(\gamma\) specified, find
+%
+\Disp{
+\hat{\V{g}}
+=\min_{\V{g}'} &\|\V{g}'\|_1 \quad \\
+\RM{subject}\; \RM{to}\quad
+&\|\M{P}^\H (\V{y} -\M{P} \V{g}')\|_\infty \leq \gamma
+}
+\I And convert \(\hat{\V{g}}\) back to matrix form as
+\Disp{
+\hat{G} =\RM{vec}^{-1} (\hat{g})
+}
+\I And finally recover the estimated \(H\) in the space domain as
+\Disp{
+\hat{\M{H}} =\M{K} \hat{\M{G}} \M{K}^\H.
+}
+\end{itemize}
 \end{frame}
@@
 \frametitle{Lemma: \(\V{a}\) is Almost Sparse}
-\(\forall \f\), \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
+For arbitrary \(\f\), for \(N_H \gg 1\), \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
 \Disp{
 R
-\leq 2 N_H \log \F{2\pi N_H}{L}.
+   \leq \F{1}{\pi} \log \F{N_H}{L}.
 }
@@
 \begin{frame}
-\frametitle{Definitions}
+\frametitle{The Main Bound}
+Let \(\V{d}\) be defined as above, then, for overwhelming probability
+\Disp{
+\|\V{d}\|_2
+\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
+}
+\end{frame}
+
+\begin{frame}
+\frametitle{Preparation for the Proof}
 \begin{itemize}
-\I Let \(\MC{A}\) be the largest \(s\) position of \(g\), \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\), and \(\MC{C} =T(N_g) -\MC{A}\)
+\I Use \(s=L\) in our case
+\I Let \(\MC{A}\) be the index set of the largest \(L\) components of \(g\), \(\MC{B}\) be the index set of the largest \(L\) position of \(d\) except \(\MC{A}\), and \(\MC{C} =\{1, \dotsc, N_g\} -\MC{A}\)
 \I Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
-\I we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), if \( \sum_{n=s+1}^N |S(\V{x}) (n)| \leq R \)
-\I Denote \(d =\hat{g} -g\)
-where \(S(x)\) is sorted in magnitude.
+\I Denote \(\V{d} =\hat{\V{g}} -\V{g}\)
 \end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Lemmata on Vector Supports}
+\begin{itemize}
+\I \( \|\V{d}\|_2^2 \leq \|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\dfrac{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \)
+\I \( \|\V{d}_{\MC{C}}\|_1 \leq \|\V{d}_{\MC{A}}\|_1 +2\|\V{g}_{C}\|_1 \)
+\begin{itemize}
+\item (modified to account nonzero \(\|\V{g}_{C}\|_1\))
+\end{itemize}
+\end{itemize}
+{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
 \end{frame}
@@
 \begin{itemize}
-\I \( |\IP{ \V{z}, \M{P}(:, n_g) }| \leq 2 \R{\log N_g}, \quad n_g =1, \dotsc, N_g. \)  (generalized from real case)
-\I \( \|\M{P}^\H \M{P} \V{d}\|_\infty \leq 4 \R{\log N_g}, \quad n_g =1, \dotsc, N_g \) (generalized from real case)
-\I \( \|\V{d}_{\MC{AB}}\|_2 \leq \dfrac{1}{1-\d_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\dfrac{\d_{3s}}{(1-\d_{2s}) \R{s}} \|d_{C}\|_1 \)
+\I \( \|\V{d}_{\MC{AB}}\|_2 \leq \dfrac{1}{1-\d_{2L}} \left( \|\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}\|_2 +\dfrac{\d_{3L}}{\R{L}} \|\V{d}_{C}\|_1 \right) \)
+\I \( |\IP{ \V{z}, \M{P}(:, n_g) }| \leq 2 \R{\log N_g}, \quad n_g =1, \dotsc, N_g. \)
+\begin{itemize}
+\item (generalized from real case)
+\end{itemize}
+\I \( \|\M{P}^\H \M{P} \V{d}\|_\infty \leq 4 \R{\log N_g}, \quad n_g =1, \dotsc, N_g \)
+\begin{itemize}
+\item (generalized from real case)
+\end{itemize}
 \end{itemize}
 {\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
-\end{frame}
-
-\begin{frame}
-\frametitle{Lemmata on Vector Supports}
-\begin{itemize}
-\I \( \|\V{d}_{\MC{C}}\|_1 \leq \|\V{d}_{\MC{A}}\|_1 +2\|\V{g}_{C}\|_1 \)
-\I \( \|\V{d}\|_2^2 \leq \|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\dfrac{1}{s} \|\V{d}_{\MC{C}}\|_1^2 \)
-\end{itemize}
-{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
-\end{frame}
-
-\begin{frame}
-\frametitle{The Main Bound}
-Let \(\V{d}\) be defined as above, and set \(s=L\), then
-\Disp{
-\|\V{d}\|_2
-\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
-}
 \end{frame}
@@
 \|\V{d}\|_2^2
-\leq &\F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
+\leq &\F{1}{4 \pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_g )^4
 }
@@
 \begin{enumerate}
+\I Find the explicit ``overwhelming'' probability
 \I Transform DS into Second Order Cone Problem
 \I Find the Lagrangian and dual problem
-\I Complete the simulation
-\I Compare the theoretical bound
+\I Write the simulation, using Newton method
+\I Compare the probability bound with the simulation result
 \end{enumerate}
@@
 }
+\setcounter{countRef}{\value{enumi}}
 \end{enumerate}
@@
 \begin{enumerate}
-{ \small
+\setcounter{enumi}{\value{countRef}} { \small
 \I E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.

### 2019-02-01 ongoing/report/sec_3_theorems_and_proofs.tex
Finish Slides
Slightly fix notation

@@
 
-We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\), which guarantees, at the heart of the argument, that \(g\) is almost-sparse
+We first establish a technical lemma that shows \(\RM{supp}(\V{g})\) has roughly cardinal \(L\), which guarantees, at the heart of the argument, that \(\V{g}\) is almost-sparse
 
@@
 
-We apply DS to find \(\hat{g}\), setting
+We apply DS to find \(\hat{\V{g}}\), setting
 \Disp{
@@
 \Disp{
-d =\hat{g} -g
+\V{d} =\hat{\V{g}} -\V{g}
 }
@@
 \item \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
-\item \(\MC{C} =T(N_g) -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
+\item \(\MC{C} =T \RB{ N_g } -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
 \end{itemize}
 
-Recall the definition () in section 1.
-
-\Result
-{Definition}
-{
-Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_1, N_2)\).
-Let \(\MC{T} \subset T (N_2)\).
+Suppose \(\M{A} \in \MB{M}_{\MB{K}} \RB{ N_1, N_2 }\).
+For brevity, let \(\MC{T} \subset T \RB{ N_2 }\).
 Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
+Let \(S:\; \MB{V}_{\MB{K}}(N) \mapsto \MB{V}_{\MB{K}}(N)\), \(N \in \MB{N}\), be the sorting function for \(x \in \MB{V}_{\MB{K}}(N))\), so that
+\Disp{
+|S \RB{x} \DB{n_1}| \geq &|S \RB{x} \DB{n_2}|, \\
+n_1 >&n_2,
+\quad n_1, n_2 \in T\RB{N} \NT
 }
-
-\Result
-{Definition}
-{
-The function \(S:\; \MB{V}_{\MB{K}}(N) \mapsto \MB{V}_{\MB{K}}(N)\), \(N \in \MB{N}\), sorts the vector \(x \in \MB{V}_{\MB{K}}(N))\), so that
-\Disp{
-|S (x)(n_1)| \geq &|S (x)(n_2)|, \\
-n_1 >&n_2,
-\quad n_1, n_2 \in T (N) \NT
-}
-}
-
 Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \(S\) throughout this article.
@@
 {
-Let function \(f:\; T (N) \mapsto \MB{R}_+\), \(N \in \MB{N}\), be given.
+Let function \(f:\; T\RB{N} \mapsto \MB{R}_+\), \(N \in \MB{N}\), be given.
 For \(x \in \MB{V}_{\MB{K}}(N)\), we say \(x\) is confined in sorted magnitude according to \(f\), if
 \Disp{
-|S(x) (n)| <&f (n),
-\quad n \in T (N).
+|S(x) \DB{ n } | <&f (n),
+\quad n \in T\RB{N}.
 }
@@
 {
-For \(\V{x} \in \MB{V}_{\MB{K}}(N)\), we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), where \(s \ll N\), if
+For \(\V{x} \in \MB{V}_{\MB{K}}(N)\), we say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), if
 \Disp{
@@
 R
-\leq 2 N_H \log \F{2\pi N_H}{L}.
+\leq \F{1}{\pi} \log \F{N_H}{L}.
 }
@@
 
-The lemma is the key to estimating sparsity of \(h\), which we now show.
+We show the lemma, which is the key to bounding the sparsity of \(h\).
 Recall the identity for Dirichlet kernel
@@
 D (\f')
-:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} \right| \NT \\
-=&\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|},
-\quad 0 \leq \f' \leq \pi
+:=&\Nm{ \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} } \NT \\
+=&\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|}, \\
+\quad 0 \leq& \f' \leq \pi \NT
 }
@@
 \Disp{
-\left| x -\F{x^3}{6} \right| \leq \sin x, \quad -\pi \leq x \leq \pi
+\Nm{ x -\F{x^3}{6} } \leq \Nm{ \sin x }, \\
+-\pi \leq &x \leq \pi \NT
 }
@@
 \Disp{
-\left| D (\f') \right|
+\Nm{ D (\f') }
 = \F{48}{|\f'^2 -24| |\f'|}
-\quad 0 \leq \f' \leq \pi,
+\quad 0 \leq \f' \leq \pi. \NT
 }
@@
 \eta :=&\f -\F{2\pi k}{N_H}, \\
-\left| \eta \right|
+\Nm{ \eta }
 \leq &\F{2\pi}{N_H}.
@@
 \Disp{
-\M{K}^\H \V{a}(\f) (k)
-=\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right)
+\RB{ \M{K}^\H \V{a}(\f) } \DB{ k }
+=\F{1}{N_H} D \RB{ \f -\F{2 \pi k} {N_H} }
 }
@@
 R(\eta)
-:=\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
+:=\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB{ \eta +\F{2 \pi n_H} {N_H} }
 }
@@
 R
-\leq \F{L}{\pi^2} \left( \log \F{N_H}{L} \right)^2
+\leq \F{L}{\pi^2} \RB{ \log \F{N_H}{L} }^2
 }
@@
 \Disp{
-1 -2 \left( \F{12}{\d} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\d}{2} N_p \right]
+1 -2 \RB{ \F{12}{\d} }^s \exp \left[ - \RB{ \F{\epsilon^2}{4} -\F{\epsilon^3}{6} } \F{\d}{2} N_p \right]
 }
@@
 \leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
-\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|\V{d}_{\MC{C}}\|_1^2
+\leq & \RB{ \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} } \|\V{d}_{\MC{C}}\|_1^2
 +\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\

### 2019-02-01 ongoing/report/make.sh

@@ -1,0 +1,3 @@
+#!/usr/bin/env bash
+
+lualatex main.tex

### 2019-02-19 ongoing/report/1_introduction.tex
Change fonts

--- 2019-01-08 ongoing/report/sec_1_introduction.tex
@@
 
-We will use \(T (N_m) =\{1, \dotsc, N_m\}\) to denote the support of \(\MB{V}_{\MB{K}} (N_m)\).
+We will use \(T \RB{N_m} =\{1, \dotsc, N_m\}\) to denote the support of \(\MB{V}_{\MB{K}} (N_m)\).
 
@@
 Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)\).
-Let \(\MC{T} \subset T (N_p)\).
+Let \(\MC{T} \subset T \RB{N_p}\).
 Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
@@
 {
-\(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T (N_m)\) such that
+   \(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T \RB{N_m}\) such that
 %
 \Disp{ 
-x_{T (N) -\MC{A}} =\V{0}
+x_{T\RB{N} -\MC{A}} =\V{0}
 }
@@
 Let \(\M{P} \in \MB{V}_\MB{R} (N_m, N_p)\) and \(\V{y} \in \MB{V}_\MB{R} (N_m)\) be given.
-Find \(\V{h} \in \MB{V}_\MB{R} (N_m)\) with
+Find \(\V{h} \in \MB{V}_\MB{R} (N_m)\) by
 %
 \Disp{
-\min_{\V{h}'} \quad &\|\V{h}'\|_1 \\ \NT
+\V{h}
+=\begin{cases}
+\min_{\V{h}'} \quad &\|\V{h}'\|_1 \NT \\
 \RM{subject}\; \RM{to} \quad &\|\M{P}^\H (\M{P} \V{h} -\V{y})\|_\infty \leq \gamma
+\end{cases}
 }
@@
 \Disp{
-\V{y} =\M{P} \M{h},
+\V{y} =\M{P} \V{h},
 }

### 2019-03-02 ongoing/report/1_introduction.tex
Compilation passed

--- 2019-01-08 ongoing/report/sec_1_introduction.tex
@@
+\startchapter [title={Introduction}]
+
 This section is organized as follows.
@@
 
-\subsection{Notation}
+\startsection [title={Notation}]
 
@@
 
-\(|a|\) denotes the magnitude for real or complex numbers \(a\).
-The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re} (a)\) and \(\MF{Im} (a)\), respectively, thus \(a =\MF{Re} (a) + i \MF{Im} (a)\)
+\m{\Nm{a}} denotes the magnitude for real or complex numbers \m{a}.
+The real and imaginary part of \m{a} will be denoted respectively as \m{\MF{Re} (a)} and \m{\MF{Im} (a)}, respectively, thus \m{a =\MF{Re} (a) + i \MF{Im} (a)}
 
-We restrict our discussion to \(\MB{R}^N\) or \(\MB{C}^N\) seen as the Hilbert space , equipped with standard inner product.
-Lower case Latin alphabets with single underline, like \(\V{a}\), denote vectors, and upper case Latin alphabets with double underlines, like \(\M{A}\), denote matrices.
-Particularly, define \(\V{1} =\IP{ 1, \dotsc, 1 }\) and \(\V{1} =\IP{ 1, \dotsc, 1 }\).
+We restrict our discussion to \m{\MB{R}^N} or \m{\MB{C}^N} seen as the Hilbert space , equipped with standard inner product.
+Lower case Latin alphabets with single underline, like \m{\V{a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m{\M{A}}, denote matrices.
+Particularly, define \m{\V{1} =\IP {1, \dots, 1}} and \m{\V{1} =\IP {1, \dots, 1}}.
 
 In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
-Of course, scalar operation on \(\MB{R}^N\) is over field \(\MB{R}\), and that on \(\MB{C}^N\) is over field \(\MB{C}\).
-We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
-Not to avoid confusion, we call the Hilbert space \(\MB{K}^N\) over \(\MB{K}\) to be \(\MB{V}_{\MB{K}} (N)\).
-We also call the collection of \(M\) by \(N\) matrices to be \(\MB{M}_{\MB{K}} (M,N)\), and its role as linear transformation is understood.
-Inner product of \(\V{a}\) and \(\V{b}\) is denoted as \(\IP{ \V{a}, \V{b} }\).
-Slightly abusing notation, we denote as \(\V{a} (n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A} (m,n)\) the \((m,n)\)-entry of \(\V{A}\)
-Particularly, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).
-\(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm of vector \(\V{a}\).
-Recall that \(\ell_\infty\)-norm is the maximum-magnitude norm.
+Of course, scalar operation on \m{\MB{R}^N} is over field \m{\MB{R}}, and that on \m{\MB{C}^N} is over field \m{\MB{C}}.
+We use \m{\MB{K}} to refer to either \m{\MB{R}} or \m{\MB{C}}.
+Not to avoid confusion, we call the Hilbert space \m{\MB{K}^N} over \m{\MB{K}} to be \m{\MB{V}_{\MB{K}} (N)}.
+We also call the collection of \m{M} by \m{N} matrices to be \m{\MB{M}_{\MB{K}} (M,N)}, and its role as linear transformation is understood.
+Inner product of \m{\V{a}} and \m{\V{b}} is denoted as \m{\IP{ \V{a}, \V{b} }}.
+Slightly abusing notation, we denote as \m{\V{a} (n)} the \m{n}-th component of \m{\V{a}}, and denote as \m{\V{A} (m,n)} the \m{(m,n)}-entry of \m{\V{A}}
+Particularly, \m{\V{u}_n} is the \m{n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
+\m{\VNm {\V{a}} _p} denotes the \m{\ell_p}-norm of vector \m{\V{a}}.
+Recall that \m{\ell_\infty}-norm is the maximum-magnitude norm.
 
-Denote as \(\MB{P} (X)\) the probability, and \(\MB{E} (X)\) the expectation.
+Denote as \m{\MB{P} (X)} the probability, and \m{\MB{E} (X)} the expectation.
 Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.
 
-\subsection{Background}
+\stopsection
+\startsection [title={Background}]
 
@@
 The figure of merit of a MIMO system is usually considered to be the channel capacity.
-In vague terms, the capacity \(C\) of a MIMO channel \(\M{H}\) at perfect channel state information is well-known to be roughly in the form \(\log \det (I +\RM{SNR})\), but that knowledge is hardly always available.
-What makes things more difficult is the case that \(\M{H}\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
+In vague terms, the capacity \m{C} of a MIMO channel \m{\M{H}} at perfect channel state information is well-known to be roughly in the form \m{\log \det (I +\RM{SNR})}, but that knowledge is hardly always available.
+What makes things more difficult is the case that \m{\M{H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
 It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
 Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\RM{SNR})\).
+Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m{\log \det (I +\RM{SNR})}.
 
-Therefore the real-time estimation, \(\hat{\M{H}}\), of \(\M{H}\) is of paramount importance.
-Needless to say, when the \(\hat{\M{H}}\) is imprecise, resulting analysis is also undermined.
+Therefore the real-time estimation, \m{\hat{\M{H}}}, of \m{\M{H}} is of paramount importance.
+Needless to say, when the \m{\hat{\M{H}}} is imprecise, resulting analysis is also undermined.
 With more antennae present, conventional training-based algorithms also increase in complexity and storage.
@@
 
-\subsection{The Dantzig Selector}
+\stopsection
+\startsection [title={The Dantzig Selector}]
 
@@
 
-To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p \in \MB{N}\) is much larger than the number of measurements \(N_m \in \MB{N}\), namely,
+To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m{N_p \in \MB{N}} is much larger than the number of measurements \m{N_m \in \MB{N}}, namely,
 %
 \Disp{
-N_p \gg N_m
+\NC N_p \gg N_m \NR
 }
 %
-In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \(N_p\) parameters?
+In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m{N_p} parameters?
 Of course, more assumption must be made to make the question meaningful.
@@
 
-Cand\`es and Tao showed frst that that in the noiseless case (``Decoding by Linear Programming'', 2006), it is possible to recover the sparse signal, under a \(\ell_1\) minimization program.
+Cand\`es and Tao showed frst that that in the noiseless case (``Decoding by Linear Programming'', 2006), it is possible to recover the sparse signal, under a \m{\ell_1} minimization program.
 The work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
 
-Later they established a stronger result that (``The Dantzig Selector'', 2007), with another \(\ell_1\) minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
+Later they established a stronger result that (``The Dantzig Selector'', 2007), with another \m{\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
 Such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
@@
 
-From the realistic perspective, the formulation as an \(\ell_1\) minimization problem, which is convex, made techniques from convex optimization usable.
+From the realistic perspective, the formulation as an \m{\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
 Indeed, relevent code has been put on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
@@
 In this article we focuss on DS, and we introduce several notions before we describe their work.
-To facilitate reader's understanding, in this section we will consistently use \(N_p\) and \(N_m\) to denote matrix dimensions.
+To facilitate reader's understanding, in this section we will consistently use \m{N_p} and \m{N_m} to denote matrix dimensions.
 Following Cand\`es and Tao, we borrow the term ``support'' from the context of analysis, where it denotes the set on which a function is nonzero.
 
-We will use \(T (N_m) =\{1, \dotsc, N_m\}\) to denote the support of \(\MB{V}_{\MB{K}} (N_m)\).
+We will use \m{T \RB{N_m} =\{1, \dots, N_m\}} to denote the support of \m{\MB{V}_{\MB{K}} (N_m)}.
 
@@
 {
-Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)\).
-Let \(\MC{T} \subset T (N_p)\).
-Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
+Suppose \m{\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)}.
+Let \m{\MC{T} \subset T \RB{N_p}}.
+Denote as \m{\M{A}_{\MC{T}}} the columns of \m{\M{A}} having indices in \m{\MC{T}}.
 }
@@
 {
-\(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T (N_m)\) such that
+\m{x \in \MB{V}_{\MB{K}} (N_m)} is called \m{s}-sparse with support \m{\MC{A}}, \m{s <N_m}, if there is \m{\MC{A} \subset T \RB{N_m}} such that
 %
 \Disp{ 
-x_{T (N) -\MC{A}} =\V{0}
+\NC x_{T(N) -\MC{A}}
+=\NC \V{0} \NR
 }
@@
 \Disp{ 
-\# \MC{A} \leq s.
+\NC \# \MC{A} \leq s. \NR
 }
-That is, only at most \(s\) components of \(x\) is nonzero.
+That is, only at most \m{s} components of \m{x} is nonzero.
 }
@@
 {
-Let \(P \in \MB{M}_\MB{K} (N_m, N_p)\) and \(y \in \MB{V}_\MB{K} (N_p)\) be given.
-Find \(h \in \MB{V}_\MB{K} (N_p)\) with
+Let \m{P \in \MB{M}_\MB{K} (N_m, N_p)} and \m{y \in \MB{V}_\MB{K} (N_p)} be given.
+Find \m{h \in \MB{V}_\MB{K} (N_p)} with
 %
 \Disp{
-\min_{h'}
-\quad &\|h'\|_1 \\
-\quad \RM{subject}\; \RM{to}
-\quad &P h' =y
+\NC
+h
+= \NC \startcases
+\NC \Min {h'}
+\quad \MC \VNm {h'} _1 \NR[+]
+\NC \RM{subject}\; \RM{to}
+\quad \MC P h' =y \NR
+\stopcases \NR
 }
@@
 
-Now let \(y =P h\).
-Suppose \(h\) is \(s\)-sparse, then the program () completely recovers \(h\).
-That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability.
+Now let \m{y =P h}.
+Suppose \m{h} is \m{s}-sparse, then the program () completely recovers \m{h}.
+That is, a noiseless linear transformation of a sparse vector is completely recovered by a \m{\ell_1}-minimization program with an overwhelming probability.
 
@@
 {
-Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
-For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the restricted isometry property (RIP) of sparsity \(s\) with respect to \(0 \leq \d_s \leq 1\), if, for all \(s\)-sparse \(\V{x} \in \MB{V}_{\MB{K}} (N_p)\), for all \(\MC{T} \subset T(N_m)\) with \(\#\{\MC{T}\} \leq s\),
+Consider \m{P \in \MB{M}_{\MB{K}} (N_m, N_p)}, with unity-\m{\ell_2}-norm columns.
+For \m{s =1, \dots N_p}, we say that \m{P} satisfies the restricted isometry property (RIP) of sparsity \m{s} with respect to \m{0 \leq \d_s \leq 1}, if, for all \m{s}-sparse \m{\V{x} \in \MB{V}_{\MB{K}} (N_p)}, for all \m{\MC{T} \subset T(N_m)} with \m{\#\{\MC{T}\} \leq s},
 %
 \Disp{
-(1-\d_s) \|\V{x}\|^2
-\leq \|P_{\MC{T}} \V{x}\|_2^2
-\leq (1+\d_s) \|\V{x}\|_2^2
+\NC \NC (1-\d_s) \VNm {V{x}}^2 \NR
+\NC \leq \NC \VNm {P_{\MC{T}} \V{x}} _2^2 \NR
+\NC \leq \NC (1+\d_s) \VNm {\V{x}} _2^2 \NR[+]
 }
@@
 
-RIP is essentially saying that \(P\) is ``almost unitary'' up to ``relative error'' \(\d_s\).
+RIP is essentially saying that \m{P} is ``almost unitary'' up to ``relative error'' \m{\d_s}.
 
@@
 \Disp{
-\V{y} =\M{P} \V{h} + \V{z}
+\NC \V{y} =\M{P} \V{h} + \V{z} \NR
 }
 %
-where (w.l.o.g.) \(z\) is an i.i.d.\ normalized Gaussian vector.
-How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?
+where (w.l.o.g.) \m{z} is an i.i.d.\ normalized Gaussian vector.
+How can we hope to estimate \m{h} when, in addition to insufficient observations, there are too few observations?
 
@@
 {
-Let \(\M{P} \in \MB{V}_\MB{R} (N_m, N_p)\) and \(\V{y} \in \MB{V}_\MB{R} (N_m)\) be given.
-Find \(\V{h} \in \MB{V}_\MB{R} (N_m)\) with
+Let \m{\M{P} \in \MB{V}_\MB{R} (N_m, N_p)} and \m{\V{y} \in \MB{V}_\MB{R} (N_m)} be given.
+Find \m{\V{h} \in \MB{V}_\MB{R} (N_m)} by
 %
+
 \Disp{
-\min_{\V{h}'} \quad &\|\V{h}'\|_1 \\ \NT
-\RM{subject}\; \RM{to} \quad &\|\M{P}^\H (\M{P} \V{h} -\V{y})\|_\infty \leq \gamma
+\NC \V{h}
+=
+\NC \startcases
+\NC \Min {\V{h}'} \quad \MC \VNm {\V{h}'} _1 \NR
+\NC \RM{subject}\; \RM{to} \quad \MC \VNm {\M{P}^\H (\M{P} \V{h} -\V{y})} _\infty \leq \gamma \NR
+\stopcases \NR
 }
@@
 They was able to show that, with Program (), the mean square error is bounded with overwhelming probability.
-And it can be shown that this \(\ell_1\)-minimization problem with \(\ell_\infty\)-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
+And it can be shown that this \m{\ell_1}-minimization problem with \m{\ell_\infty}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
 Note that they confined their discussion for real vectors.
 
-\subsection{Sufficient Conditions of RIP}
+\stopsection
+\startsection [title={Sufficient Conditions of RIP}]
 
-The constant \(\d\) in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \(\d=0\), i.e., that \(P\) is fully unitary, rendering the RIP an important role.
+The constant \m{\d} in the proof of DS is significant.
+Indeed, we may observe that in theorem (), the bound is not tightest when \m{\d=0}, i.e., that \m{P} is fully unitary, rendering the RIP an important role.
 Here, it is not clear at first what matrices serves as the RIP condition.
@@
 {
-Let each entry of random matrix \(P \in \MB{M}_\MB{K} (N_m, N_p)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\R{N_m}\) (that is, Rademacher distribution).
-Then, with \(0 <\epsilon <1\),
+Let each entry of random matrix \m{P \in \MB{M}_\MB{K} (N_m, N_p)} be defined as i.i.d.\ Bernoulli with value \m{\pm 1/\R{N_m}} (that is, Rademacher distribution).
+Then, with \m{0 <\epsilon <1},
 %
 \Disp{
-\MB{P} ( |\|P h\|_2^2 -\|h\|_2^2| \geq \epsilon \|h\|_2^2)
-\leq 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) )
+\NC \NC \MB{P} ( \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm{h} _2^2) \NR
+\NC \leq \NC 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) ) \NR
 }
@@
 
-{ \color{red} (To be done) }
+\color[red] {(To be done)}
 
-\subsection{Compressed Channel Sensing}
+\stopsection
+\startsection [title={Compressed Channel Sensing}]
 
@@
 
-One of the first papers, Bajwa et.\ al.\ (2010) argues the \(\ell_0\)-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
+One of the first papers, Bajwa et.\ al.\ (2010) argues the \m{\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
 What they explored was the estimation of single-antenna channel response with respect to time.
-Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \(X\) is RIP for overwhelming probability, providing the ground for the former paper.
+Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \m{X} is RIP for overwhelming probability, providing the ground for the former paper.
 
-To explain the idea, consider a linear time-invariant channel that \(y(t) =(x \star h)(t) + z(t)\), where \(h(t)\) is the channel's impulse response, \(y(t)\) is the output, and, for each time index, \(x(t)\) is i.i.d.\ Rademacher, and \(z(t)\) is i.i.d.\ Gaussian.
-Simply assuming \(h\) has sparse support, and let the convolution with \(x\) be expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that \(y =X h +z\).
-Then Bajwa et.\ al.\ was able to show that, \(X\) is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.
+To explain the idea, consider a linear time-invariant channel that \m{y(t) =(x \star h)(t) + z(t)}, where \m{h(t)} is the channel's impulse response, \m{y(t)} is the output, and, for each time index, \m{x(t)} is i.i.d.\ Rademacher, and \m{z(t)} is i.i.d.\ Gaussian.
+Simply assuming \m{h} has sparse support, and let the convolution with \m{x} be expressed by a matrix \m{X}, \m{X} is a Toeplitz matrix, so that \m{y =X h +z}.
+Then Bajwa et.\ al.\ was able to show that, \m{X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.
 
-\subsection{Orthogonal Matching Pursuit}
+\stopsection
+\startsection [title={Orthogonal Matching Pursuit}]
 
@@
 
-Same as before, consider \(\V{y} \in \MB{V}_\MB{K} (N_p)\), \(\V{h} \in \MB{V}_\MB{K} (N_s)\), where \(\V{h}\) is \(s\)-sparse, with \(N_p \gg N_s\).
+Same as before, consider \m{\V{y} \in \MB{V}_\MB{K} (N_p)}, \m{\V{h} \in \MB{V}_\MB{K} (N_s)}, where \m{\V{h}} is \m{s}-sparse, with \m{N_p \gg N_s}.
 If
 \Disp{
-\V{y} =\M{P} \M{h},
+\NC \V{y} =\M{P} \V{h}, \NR
 }
 that is, the noiseless, real-number case.
-We pick up the columns of \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\), thus recovering the original signal.
+We pick up the columns of \m{\M{P}} greedily, hoping to correspond to the support of \m{\V{h}}, thus recovering the original signal.
 
@@
 {
-\begin{enumerate}
+\startitemize[n]
 \item To be done.
-\end{enumerate}
+\stopitemize
 }
@@
 {
-Following the setting described above, suppose, for \(0 <\d <1\),
+Following the setting described above, suppose, for \m{0 <\d <1},
 %
 \Disp{
-M \geq 16s \log (N/\d)
+\NC M \geq 16s \log (N/\d) \NR
 }
 %
-Then OMP (Algorithm \_\_) recovers \(x\) completely, with overwhelming probability \(1-\d\).
+Then OMP (Algorithm \_\_) recovers \m{x} completely, with overwhelming probability \m{1-\d}.
 }
@@
 
-For concreteness, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
-Let signal \(\V{x}\) be sent, and \(\V{y}\) be receiverd, that is
+For concreteness, let \m{\M{F}} be the precoder and \m{\M{W}} the combiner, and \m{\M{H}} the channel, and consider the noiseless case.
+Let signal \m{\V{x}} be sent, and \m{\V{y}} be receiverd, that is
 %
 \Disp{
-\V{y} =\M{W} \M{H} \M{F} \V{x}
+\NC \V{y} =\M{W} \M{H} \M{F} \V{x} \NR
 }
@@
 {
-Define \(\RM{vec} (\M{A}) \in \MB{K}^{NM}\) to be the vectorization of \(\M{A} \in \MB{M}_{\MB{K}} (N,M)\).
+Define \m{\RM{vec} (\M{A}) \in \MB{K}^{NM}} to be the vectorization of \m{\M{A} \in \MB{M}_{\MB{K}} (N,M)}.
 }
@@
 {
-For \(\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)\) and \(\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)\)
-Define the Kronecker product \(\RM{vec} (A) \in \MB{K}^{nm}\) 
+For \m{\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)} and \m{\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)}
+Define the Kronecker product \m{\RM{vec} (A) \in \MB{K}^{nm}} 
 }
@@
 \Disp{
-\RM{vec} (Y)
-=\big[ (F^\H) \otimes W \big] \RM{vec} (\M{H})
+\NC \RM{vec} (Y)
+=\big[ (F^\H) \otimes W \big] \RM{vec} (\M{H}) \NR
 }
@@
 
-\subsection{Further Development on Compressive Channel Sensing}
+\stopsection
+\startsection [title={Further Development on Compressive Channel Sensing}]
 
@@
 
-\begin{enumerate}
+\startitemize
 \item Previous work favors OMP rather than DS, let alone other sparse algorithm.
@@
 \item No bounds is derived that explicitly depends on the sparsity of the channel parameters as, say, number of channel paths and array response.
-\end{enumerate}
+\stopitemize
 
-\subsection{Contribution}
+\startsection [title={Contribution}]
 
@@
 
-\begin{enumerate}
-\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
+\startitemize
+\item As a {\it prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
 \item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
@@
 \item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
-\end{enumerate}
+\stopitemize
+
+\stopsection
+
+\stopchapter

### 2019-03-02 ongoing/report/2_problem_setting.tex
Change fonts
Compilation passed

--- 2019-01-08 ongoing/report/sec_2_problem_setting.tex
@@
-\subsection{Channel Model}
+\startchapter [title={Problem Setting}]
 
-Since expression involving probability will get very complecated, sometimes we will explicit mark the independence on event space index.
+\startsection [title={Channel Model}]
+
+Since expression involving probability will get complicated, sometimes we explicitly mark the independence on event space index.
 Introduce the direct product
 %
+
 \Disp{
-\Omega
-=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
+\NC \Omega
+= \NC \Omega_t \times \Omega_h \times \Omega_n \times \Omega_r \NR
 }
@@
 
-\begin{itemize}
-\item \(\Omega_t\) denotes the event space of the transmitter end,
-\item \(\Omega_h\) denotes the event space of the communication channel itself,
-\item \(\Omega_z\) denotes the event space of the noise arising in the communication channel,
-\item \(\Omega_r\) denotes the event space of the receiver end.
-\end{itemize}
+\startitemize
+\item \m{\Omega_t} denotes the event space of the transmitter end,
+\item \m{\Omega_h} denotes the event space of the communication channel itself,
+\item \m{\Omega_z} denotes the event space of the noise arising in the communication channel,
+\item \m{\Omega_r} denotes the event space of the receiver end.
+\stopitemize
 %
@@
 \Disp{
-\V{a} \in \MB{V}_\MB{K} (N_H) \\
-\V{a} (\psi')
-=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
+\NC \V{a} (\psi')
+= \NC \F{1}{\R{N_H}} \sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
+\in \MB{V}_\MB{C} (N_H) \NR
 }
 %
-where \(\RM{e}\) is the base of natural logarithm, and \(i\) the imaginary unit.
+where \m{\RM{e}} is the base of natural logarithm, and \m{i} the imaginary unit.
 
@@
 \Disp{
-H
-=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \f_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \th_l' \right)^\H
+\NC H
+=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \f_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \th_l' \right)^\H \NR
 }
 %
-The physical meaning of \(\th_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\th_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
-For our purpose, we may absorb the argument of \(\V{a}\) as
+The physical meaning of \m{\th_l} is the \m{l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m{\th_l}, the \m{l}-th that of arrival wave, while \m{d_{\RM{arr}}} is the distance between two adjacent antennae.
+For our purpose, we may absorb the argument of \m{\V{a}} as
 %
 \Disp{
-\f_l
-=\F{d_{\RM{arr}}} {\lambda} \sin \f_l' \\
-\th_l
-=\F{d_{\RM{arr}}} {\lambda} \sin \th_l'
+\NC \f_l
+=\NC \F{d_{\RM{arr}}} {\lambda} \sin \f_l' \NR[+]
+\NC \th_l
+=\NC \F{d_{\RM{arr}}} {\lambda} \sin \th_l' \NR[+]
 }
@@
 \Disp{
-H
+\NC H
 =\sum_{l=0}^L \alpha_l \V{a} (\f_l) \V{a} (\th_l)^\H
+\in \MB{M}_\MB{C} (N_H) \NR
 }
@@
 
-\subsection{System Model}
+\stopsection
+
+\startsection [title={System Model}]
 
@@
 That is to say, each end consists of both digital and analog percoders and combiners, as follows.
-In the transmitter end, there are, in order seeing from the end, digital precoder \(F_B\) and analog precoder \(F_R\).
-Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \(W_B\) and analog combiner \(W_R\).
+In the transmitter end, there are, in order seeing from the end, digital precoder \m{F_B} and analog precoder \m{F_R}.
+Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m{W_B} and analog combiner \m{W_R}.
 To set up notation, we list them as below.
@@
 \Disp{
-\M{F}_B \in &\MB{M}_{\MB{C}} (N_R, N_Y) \\
-\M{F}_R \in &\MB{M}_{\MB{C}} (N_H, N_R) \\
-\M{W}_R \in &\MB{M}_{\MB{C}} (N_R, N_H) \\
-\M{W}_B \in &\MB{M}_{\MB{C}} (N_Y, N_R).
+\NC \M{F}_B \in  \NC \MB{M}_{\MB{C}} (N_R, N_Y) \NR[+]
+\NC \M{F}_R \in  \NC \MB{M}_{\MB{C}} (N_H, N_R) \NR[+]
+\NC \M{W}_R \in  \NC \MB{M}_{\MB{C}} (N_R, N_H) \NR[+]
+\NC \M{W}_B \in  \NC \MB{M}_{\MB{C}} (N_Y, N_R) \NR
 }
@@
 \Disp{
-|\M{F}_R (n_h, n_r)| =&1, \\
-|\M{W}_R (n_r, n_h)| =&1, \\
-n_h =&1, \dotsc N_H, \NT \\
-n_r =&1, \dotsc N_R \NT
+\NC \Nm{\M{F}_R (n_h, n_r)} = \NC 1, \NR[+]
+\NC \Nm{\M{W}_R (n_r, n_h)} = \NC 1, \NR[+]
+\NC n_h = \NC 1, \dots N_H, \NR
+\NC n_r = \NC 1, \dots N_R \NR
 }
@@
 \Disp{
-N_H \gg &N_R \\
-N_R \gg &N_s
+\NC N_H \gg  \NC N_R \NR[+]
+\NC N_R \gg  \NC N_s \NR[+]
 }
@@
 
-We consider zero-mean, unity-variance additive white Gaussian noise \(z\).
-Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.
+We consider zero-mean, unity-variance additive white Gaussian noise \m{z}.
+Since we restrict our discussion to a specific slice of time, the signal \m{z} degrades as a entrywise i.i.d.\ standard normal distribution vector.
 
@@
 \Disp{
-Y (\omega_h, \omega_e)
-:=W_B (\omega_r) W_R (\omega_r) \Big[ H (\omega_h) F_R (\omega_t) F_B (\omega_t) +Z (\omega_z) \Big]
+\NC Y (\omega_h, \omega_e)
+:= \NC W_B (\omega_r) W_R (\omega_r) \Big[ H (\omega_h) F_R (\omega_t) F_B (\omega_t) +Z (\omega_z) \Big] \NR
 }
@@
 \Disp{
-Y
-:=W_B W_R ( H F_R F_B +z )
+\NC Y
+:=W_B W_R ( H F_R F_B +Z ) \NR
 }
-\(\M{Y}\) has \(N_Y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
-This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
+\m{\M{Y}} has \m{N_Y} columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \m{\V{u}_n}.
+This way, we may denote the acquired effective channel matrix \m{\M{Y}} under noisy observation as (borrowing Matlab's colon notation to denote columns)
 %
 \Disp{
-\M{Y} (:,n_y)
-:=\M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \\
-\quad n_y &=1, 2, \dotsc, N_Y \NT
+\NC \M{Y} (:,n_y)
+:= \NC \M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \NR[+]
+\NC \quad n_y = \NC 1, 2, \dots, N_Y \NR
 }
 %
-Still, the crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), while \(\M{W}_R\), \(\M{W}_B\), \(\M{F}_R\), and \(\M{F}_B\) are in our control.
+Still, the crux of the matter is the recovery of \m{\M{H}} with knowledge of \m{\M{Y}}, while \m{\M{W}_R}, \m{\M{W}_B}, \m{\M{F}_R}, and \m{\M{F}_B} are in our control.
 
-\subsection{Vectorization}
+\stopsection
+\startsection [title={Vectorization}]
 
@@
 \Disp{
-\V{h}
-:= &\RM{vec} (\M{H})
-\in \MB{V}_{\MB{C}} (N_g) \\
-\V{y}
-:= &\RM{vec} (\M{Y})
-\in \MB{V}_{\MB{C}} (N_y) \\
-\V{z}^\star
-:= &\RM{vec} (\M{Z})
-\in \MB{V}_{\MB{C}} (N_y) \\
-\M{P}^\star
-:= &(\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
-\in \MB{M}_{\MB{C}} (N_y, N_g).
+\NC \V{h}
+:= \NC \RM{vec} (\M{H})
+\in \MB{V}_{\MB{C}} (N_g) \NR[+]
+\NC \V{y}
+:= \NC \RM{vec} (\M{Y})
+\in \MB{V}_{\MB{C}} (N_y) \NR[+]
+\NC \V{z}^\star
+:= \NC \RM{vec} (\M{Z})
+\in \MB{V}_{\MB{C}} (N_y) \NR[+]
+\NC \M{P}^\star
+:= \NC (\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
+\in \MB{M}_{\MB{C}} (N_y, N_g) \NR
 }
 %
-to formulate our goal as sparse recovery problem of \(\RM{vec} (H)\) to be
+to formulate our goal as sparse recovery problem of \m{\RM{vec} (H)} to be
 %
 \Disp{
-\V{y} =\M{P}^\star \V{h} +\V{z}^\star
+\NC \V{y} =\M{P}^\star \V{h} +\V{z}^\star \NR
 }
@@
 
-\subsection{Proposed Method}
+\stopsection
 
-Introduce the discrete Fourier matrix \(\M{K}\) defined to be
+\startsection [title={Proposed Method}]
+
+Introduce the discrete Fourier matrix \m{\M{K}} defined to be
 %
 \Disp{
-\M{K} \in &\MB{M}_{\MB{C}} (N_H, N_H) \NT \\
-\M{K} (n_1, n_2) =&\F{1} {\R{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \\
-\quad n_1, n_2 =&0, 1, \dotsc, N_H-1 \NT
+\NC \M{K} \in  \NC \MB{M}_{\MB{C}} (N_H, N_H) \NR
+\NC \M{K} (n_1, n_2) = \NC \F{1} {\R{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \NR[+]
+\NC \quad n_1, n_2 = \NC 0, 1, \dots, N_H-1 \NR
 }
@@
 \Disp{
-\M{G}
-=\M{K}^\H \M{H} \M{K}
+\NC \M{G}
+=\M{K}^\H \M{H} \M{K} \NR
 }
 %
-which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
+which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \m{\M{H}}, then
 %
 \Disp{
-\M{Y}
+\NC \M{Y}
 :=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
+\in \MB{M}_{\MB{C}} (N_Y, N_Y) \NR
 }
 %
-If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.
+If at the end of day, \m{\M{G}} is sparse, then we recover \m{\M{G}} instead, and our use of DS is fully justified.
 
-That is to say, \(\M{K}^\H \V{z}\) may be absorbed, and a similar Kronecker product may be used.
+That is to say, \m{\M{K}^\H \V{z}} may be absorbed, and a similar Kronecker product may be used.
 To simplify notation, set
@@
 \Disp{
-\M{P}
-=(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
-\in \MB{M}_{\MB{C}} (N_y, N_g)
+\NC \M{P}
+:=(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
+\in \MB{M}_{\MB{C}} (N_y, N_g) \NR
 }
@@
 \Disp{
-\V{g}
-:= &\RM{vec} (\M{G})
-\in \MB{M}_{\MB{C}} (N_g) \\
-\V{z}
-:= &\RM{vec} (\M{K}^\H \M{Z})
-\in \MB{V}_{\MB{C}} (N_y)
+\NC \V{g}
+:= \NC \RM{vec} (\M{G})
+\in \MB{M}_{\MB{C}} (N_g) \NR[+]
+\NC \V{z}
+:= \NC \RM{vec} (\M{K}^\H \M{Z})
+\in \MB{V}_{\MB{C}} (N_y) \NR
 }
@@
 \Disp{
-N_g =&N_H^2 \\
-N_y =&N_Y^2
+\NC N_g = \NC N_H^2 \NR[+]
+\NC N_y = \NC N_Y^2 \NR
 }
@@
 \Disp{
-\V{y}
-=\M{P} \V{g} +\V{z}
+\NC \V{y}
+=\M{P} \V{g} +\V{z} \NR
 }
@@
 {
-Let \(\M{P}, \V{y}\) be defined just above in ().
-Then, with parameter \(\gamma\) specified, define the following program
+Let \m{\M{P}, \V{y}} be defined just above in ().
+Then, with parameter \m{\gamma} specified, define the following program
 %
 \Disp{
-\hat{\V{g}}
-=\min_{\V{g}'} &\|\V{g}'\|_1 \quad
-\RM{subject}\; \RM{to}\quad &\|\M{P}^\H (\V{y} -\M{P} \V{g}')\|_\infty \leq \gamma
+\NC \hat{\V{g}}
+=\NC \startcases
+\Min {\V{g}'}  \MC \VNm {\V{g}'} _1 \NR[+]
+\RM{subject}\; \RM{to} \quad  \MC \VNm {\M{P}^\H (\V{y} -\M{P} \V{g}')} _\infty \leq \gamma \NR
+\stopcases \NR
 }
 %
-And convert \(\hat{\V{g}}\) back to the space domain as
+And convert \m{\hat{\V{g}}} back to the space domain as
 %
 \Disp{
-\hat{G} =\RM{vec}^{-1} (\hat{g})
+\NC \hat{G} =\RM{vec}^{-1} (\hat{g}) \NR
 }
 %
-And finally recover the estimated \(H\) as
+And finally recover the estimated \m{H} as
 %
 \Disp{
-\hat{\M{H}} =\M{K} \hat{\M{G}} \M{K}^\H.
+\NC \hat{\M{H}} =\M{K} \hat{\M{G}} \M{K}^\H \NR
 }
@@
 It, then, will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
+
+\stopsection
+
+\stopchapter

### 2019-03-02 ongoing/report/3_theorems_and_proofs.tex
Compilation passed

\startchapter [title={Theorems and Proofs}]

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \m{g \in \MB{C}^{N_g}}, and we continue to use \m{\hat{g}} to denote the Dantzig Selector.
To simplify the exposition, we will continue to use the variables \m{\V{P}}, \m{\V{g}}, \m{\V{y}}, and \m{\V{z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).

We first establish a technical lemma that shows \m{\RM{supp}(\V{g})} has roughly cardinal \m{L}, which guarantees, at the heart of the argument, that \m{\V{g}} is almost-sparse

\startsection [title={Almost-Sparsity of Beamspace Channel Matrix}]

We apply DS to find \m{\hat{\V{g}}}, setting
\Disp{
\NC \gamma = \NC \R{2 \log N_g} \NR[+]
}

Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp{
\NC \V{d} = \NC \hat{\V{g}} -\V{g} \NR[+]
}
%
And call
\startitemize
\item \m{\MC{A}} be the largest \m{s} position of \m{g}.
\item \m{\MC{B}} be the largest \m{s} position of \m{d_{T(N_g) -\MC{A}}}.
\item \m{\MC{C} =T \RB{ N_g } -\MC{A}}, i.e., the complementary index set of \m{\MC{A}}.
\stopitemize

Suppose \m{\M{A} \in \MB{M}_{\MB{K}} \RB{ N_1, N_2 }}.
For brevity, let \m{\MC{T} \subset T \RB{ N_2 }}.
Denote as \m{\M{A}_{\MC{T}}} the columns of \m{\M{A}} having indices in \m{\MC{T}}.
Let \m{S:\; \MB{V}_{\MB{K}}(N) \mapsto \MB{V}_{\MB{K}}(N)}, \m{N \in \MB{N}}, be the sorting function for \m{x \in \MB{V}_{\MB{K}}(N))}, so that
\Disp{
\NC \Nm{S \RB{x} \DB{n_1}} \geq  \NC \Nm {S \RB{x} \DB{n_2}}, \NR[+]
\NC n_1 > \NC n_2,
\quad n_1, n_2 \in T\RB{N} \NR
}
Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \m{S} throughout this article.
For definiteness, we may compare the first component first, and the second, and so on.
If still there is a tie for a certain component (for complex numbers), we compare the real part first, then the imaginary part.

\Result
{Definition}
{
Let function \m{f:\; T\RB{N} \mapsto \MB{R}_+}, \m{N \in \MB{N}}, be given.
For \m{x \in \MB{V}_{\MB{K}}(N)}, we say \m{x} is confined in sorted magnitude according to \m{f}, if
\Disp{
\NC \Nm {S(x) \DB{ n } } < \NC f (n),
\quad n \in T\RB{N}. \NR
}
}

\Result
{Definition}
{
For \m{\V{x} \in \MB{V}_{\MB{K}}(N)}, we say \m{\V{x}} is almost-\m{s}-sparse with \m{\ell_1}-residue \m{R}, if
\Disp{
\NC \sum_{n=s+1}^N \Nm {S(\V{x}) (n)}
\leq \NC R. \NR
}
}

\Result
{Lemma (Tentative)}
{
Suppose \m{0 \leq \f \leq 2\pi k /N_H}, \m{k =0, \dots, N_H-1}.
Let \m{\f} be given, and array response \m{\V{a} (\f)} defined as in ().
Then \m{\V{a} (\f)} is almost-\m{L}-sparse with \m{\ell_1}-residue \m{R(N_H, L)} to be
%
\Disp{
\NC R
\leq \NC \F{1}{\pi} \log \F{N_H}{L}. \NR
}
}

We show the lemma, which is the key to bounding the sparsity of \m{h}.
Recall the identity for Dirichlet kernel
%
\Disp{
\NC D (\f')
:= \NC \Nm{ \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} } \NR
\NC = \NC \F{\Nm {\sin (N_H \f'/2)}}{\Nm {\sin (\f' /2)}}, \NR[+]
\NC \quad 0 \leq \NC  \f' \leq \pi \NR
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\NC \sin x = \NC x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1 \NR
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\NC \Nm{x - \F{x^3}{6}} \leq \NC \Nm{\sin x}, \NR[+]
\NC -\pi \leq \NC x \leq \pi \NR
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\NC \Nm{ D (\f') }
= \NC \F{48}{\Nm {\f'^2 -24} \Nm {\f'}}
\quad 0 \leq \f' \leq \pi. \NR
}

Particularly, for arbitrary \m{\f}, find \m{k} so that
\Disp{
\NC \eta := \NC \f -\F{2\pi k}{N_H}, \NR[+]
\NC \Nm {\eta}
\leq \NC \F{2\pi}{N_H}. \NR
}
%
Then observe
\Disp{
\NC \RB {\M{K}^\H \V{a}(\f)} \DB {k}
=\NC \F{1}{N_H} D \RB{\f -\F{2 \pi k} {N_H}} \NR
}
So we need only bound
\Disp{
\NC R(\eta)
:=\NC \F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB{ \eta +\F{2 \pi n_H} {N_H} } \NR
}
By the approximation of rectangle to integral,
\Disp{
\NC R(\eta) -\F{2\pi} {N_H}
\leq \NC \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D(\f')} d \f' \NR
}
Bound \m{D} by above technique, meanwhile we notice \m{\f' <24}.
\Disp{
\NC R(\f)
\leq \NC \F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \NR
\NC = \NC \F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the argument of log in the second term \m{<1}, and we drop that.
Also drop \m{2\pi /N_H} since it is small.
Furthermore the \m{2\pi} factor in log can be dropped too.
\Disp{
\NC R(\f)
\leq \NC \F{1}{\pi} \log \F{N_H}{L}. \NR
}

\Result
{Lemma (Tentative)}
{
Let \m{\f} and \m{\th} be uniformly, independently distributed in \m{[0,2\pi)}, and linear array response \m{\V{a}} defined as in ().
Let \m{\V{g}} be defined as above.
Then \m{\V{g}} is almost-\m{L}-sparse with \m{\ell_1}-residue \m{R(N_H, L)} to be
%
\Disp{
\NC R
\leq \NC \F{L}{\pi^2} \RB{ \log \F{N_H}{L} }^2 \NR
}
}

\startsection [title={Design of RIP Precoders and Combiners}]

\Result
{Definition}
{
For \m{\MC{T}, \MC{T}' \subset \{1, \dots, N_p\}}, define the \m{s, s'}-restricted orthogonality constant \m{\tau_{s,s'} >0} to be the smallest such that
%
\Disp{
\NC \Nm {\IP {P_{\MC{T}} h, P_{\MC{T}'} h'}}
\leq \NC \tau_{s, s'} \cdot \VNm { h } _2 \VNm {h'} _2 \NR
}
}

From ``Decoding from Linear Programming'' (Cand\`es and Tao 2005), Lemma 1.1:

\Result
{Lemma}
{
Let \m{P} be given.
Then \m{\tau_{s, s'}} is bounded in both direction as follows,
\Disp{
\NC \d_{s+s'} -\max (\{\d_s, \d_{s'}\})
\leq \NC \tau_{s, s'} \NR
\NC \leq \NC \d_{s+s'}
}
}

Thus \m{\d_s}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
We may well keep track of \m{\d_s} only.

\Result
{Lemma}
{
Let \m{P} be i.i.d.\ Radmacher, as defined in Lemma ().
Then \m{P} is RIP according to \m{\d} for at least probability
\Disp{
\NC 1 -2 \RB{ \F{12}{\d} }^s \exp \left[ - \RB{ \F{\epsilon^2}{4} -\F{\epsilon^3}{6} } \F{\d}{2} N_p \right] \NR
}
}

\color[red]{(To be done)}

\startsection [title={DS for Complex Vectors}]

The rest follows ``The Dantzig Selector'' very closely.
The generalization to complex vector is necessary (though we will ultimately do it in simulation involving real numbers only.
We spell out the proof when such generalization is nontrivial.

\Result
{Proposition}
{
Let \m{\V{g}} and \m{\V{d}} be defined as above.
Then
%
\Disp{
\NC \VNm {\V{d}_{\MC{C}}} _1
\leq \NC \VNm {\V{d}_{\MC{A}}} _1 +2\VNm {\V{g}_{C}} _1 \NR
}
}

To show this, observe that with triangle inequality applied respectively on \m{\MC{A}} and \m{\MC{C}},
\Disp{
\NC \VNm {\V{g}} _1
-\VNm {\V{d}_{\MC{A}}} _1
+\VNm {\V{d}_{\MC{C}}} _1
-\VNm {\V{g}_{\MC{C}}} _1
\leq \NC \VNm {\V{g} +\V{d}} _1 \NR
}
In the first line, we recall \m{\V{g} =\V{g}_{\MC{A}}}.
On the other hand, by construction that \m{\hat{g}} minimizes the \m{\ell_1}-norm,
\Disp{
\NC \VNm {\V{g} +\V{d}} _1
=\NC \VNm {\hat{\V{g}}} _1 \NR
\NC \leq \NC \VNm {\V{g}} _1 \NR
}
The result follows by combining.

\Result
{Lemma}
{
Let \m{\V{z}} and \m{\M{P}} be defined as above.
Then
%
\Disp{
\NC \Nm {\IP{ \V{z}, \M{P}(:, n_g) }}
\leq \NC  2 \R{\log N_g},
\quad n_g =1, \dots, N_g. \NR
}
%
with overwhelming probability.
}

This only depends on the fact that \m{\M{P}(:, n_g)} has unity \m{\ell_2}-norm, and on the randomness of \m{\V{z}}.

Recall the following bound for \m{Q} function
\Disp{
\NC Q(x)
\leq \NC \F{1}{2} \RM{e}^{-x^2/2} \NR
}
Particularly, for \m{x =\R{2 \log N_g}}, according to CLT,
\Disp{
\NC Q(\R{2 \log N_g})
=\NC \F{1}{N_g}. \NR
}

\color[red]{(To be done)}

\Result
{Lemma}
{
Let \m{\V{d}} and \m{\M{P}} be defined as above, and \m{\M{P}} satisfies RIP as in ().
%
\Disp{
\NC \VNm {\M{P}^\H \M{P} \V{d}} _\infty
\leq \NC  4 \R{\log N_g},
\quad n_g =1, \dots, N_g. \NR
}
}

To show this, by definition
%
\Disp{
\NC \IP{ \V{z} -(\V{y} -\M{P} \hat{\V{g}}), \M{P} (:,n_y) }
= \NC \IP{ \M{P} \hat{\V{g}} -\M{P} \V{g}, \M{P} (:,n_y) } \NR
\NC = \NC \IP{ \M{P} \V{d}, \M{P} (:,n_y) } \NR
}

By construction
\Disp{
\NC \VNm { \M{P} (:,n_y)^\H (\V{y} -\M{P} \hat{\V{g}}) } 
\leq \NC \VNm { \M{P}^\H (\V{y} -\M{P} \hat{\V{g}}) } _\infty \NR
\NC \leq \NC 2\R{\log N_g} \NR
}
By triangle inequality, together with Lemma (), we have
\Disp{
\NC \VNm {\M{P} (:,n_y)^\H \M{P} \V{d}} 
\leq \NC \VNm {\IP{ \V{z}, \M{P} (:,n_y) }}  +\IP{ \V{y} -\M{P} \hat{\V{g}}, \M{P} (:,n_y) } \NR
\NC \leq \NC 2 \R{\log N_g} +2 \R{\log N_g} \NR
}
which implies
\Disp{
\NC \VNm {\M{P}^\H \M{P} \V{d}} _\infty
\leq \NC 4 \R{\log N_g}. \NR
}

From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result as below.
The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
Of course the interpretation of modulus and the inner product changes accordingly.

\Result
{Lemma}
{
Let \m{\V{d}} and \m{\M{P}} be defined as above, and \m{\M{P}} satisfies RIP as in () with respect to \m{\d_s}.
%
\Disp{
\NC \VNm {\V{d}_{\MC{AB}}} _2
\leq \NC \F{1}{1-\d_{2s}} \VNm {P_{\MC{A}\MC{B}}^\Tr P d} _2 +\F{\d_{3s}}{(1-\d_{2s}) \R{s}} \VNm {d_{C}} _1 \NR
}
%
}

From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result as below.
Again, their proof works with complex vector spaces in place of real ones too.

\Result
{Lemma}
{
Let \m{\V{d}} be defined as above.
Then
%
\Disp{
\NC \VNm {\V{d}} _2^2
\leq \NC \VNm {\V{d}_{\MC{A}\MC{B}}} _2^2 +\F{1}{s} \VNm {\V{d}_{\MC{C}}} _1^2 \NR
}
%
}

\startsection [title={The Main Bound}]

We can now formulate and prove the main bound of ours.
Here, we use \m{s=L} as the sparsity threshold.

\Result
{Theorem}
{
Let \m{\V{y}}, \m{\M{P}}, \m{\V{g}}, \m{\hat{\V{g}}}, \m{\V{d}} be defined as above.
Then
\Disp{
\NC \VNm {\V{d}} _2
\leq \NC \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
}
with overwhelming probability.
}

We are ready to combine previous lemmata.
The first quantity we want to bound away is
\Disp{
\NC \VNm {\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}} _2
\leq \NC \VNm {\M{P}^\Tr \M{P} \V{d}} _2 \NR
\NC \leq \NC \R{N_g} \VNm {\M{P}^\Tr \M{P} \V{d}} _\infty \NR
\NC \leq \NC 4 \R{ N_g \log N_g } \NR
}
Thus, by virtue of Lemma (),
\Disp{
\NC \VNm { \V{d}_{A} } _1
\leq \NC \R{L} \VNm { \V{d}_{A} } _2 \NR
\NC \leq \NC \R{L} \VNm { \V{d}_{\MC{AB}} } _2 \NR
\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V{d}_{\MC{C}} } _1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} \NR
}

As the next step, we must eliminate \m{\VNm {d_{\MC{A}}} _1} in rhs of Lemma ().
\Disp{
\NC \VNm { \V{d}_{\MC{C}} } _1
\leq \NC \VNm { \V{d}_{\MC{A}} } _1 +2 \VNm { \V{g}_{\MC{C}} } _1 \NR
\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V{d}_{\MC{C}} } _1
+2 \VNm { \V{g}_{\MC{C}} } _1
+\F {4} {1-\d_{2L}} \R{L N_g \log N_g} \NR
}
Or,
\Disp{
\NC \VNm { \V{d}_{\MC{C}} } _1
\leq \NC 2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V{g}_{\MC{C}} } _1
+\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g} \NR
}

We are ready to bound \m{\VNm { d } _2^2}.
Using Lemma () again, we have
\Disp{
\NC \VNm { \V{d} } _2^2
\leq \NC \VNm {\V{d}_{\MC{A}\MC{B}}} _2^2 +\F{1}{L} \VNm {\V{d}_{\MC{C}}} _1^2 \NR
\NC \leq \NC  \RB{ \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} } \VNm {\V{d}_{\MC{C}}} _1^2
+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \VNm {\V{d}_{\MC{C}}} _1 \NR
\NC \NC \quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g \NR
}
Finally, plug in the bound for \m{\VNm {\V{d}_{\MC{C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m{\VNm {\V{d}_{\MC{C}}} _1}.
There are several dozens of terms if we expand all.
but for simplicity, we keep only the leading term under the approximation
\Disp{
\NC 1 \ll \NC L \NR
\NC \ll \NC N_g \NR
}
And expand to the first order expressions containing \m{\d_{2L}} or \m{\d_{3L}} in the denominator using
\Disp{
\NC \d_{2L} <\NC \d_{3L} \ll 1. \NR
}
Then
\Disp{
\NC \VNm {\V{d}} _2^2
\leq \NC \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
}

\color[red]{(To be done)}

\stopchapter

### 2019-03-02 ongoing/report/4_simulation.tex
Compilation passed

--- 2019-01-05 ongoing/report/sec_4_simulation.tex
@@
+\startchapter [title={Simulation}]
+
 With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
@@
 
-\subsection{Transformation into Second Order Cone Problem}
+\startsection [title={Transformation into Second Order Cone Problem}]
 
@@
 \Disp{
-\MC{R}(x) \in &\MB{V}(2M) \NT \\
+\MC{R}(x) \in \NC \MB{V}(2M) \NR
 \MC{R}(x)(m) =
-&\begin{cases}
-\MF{Re}(\MC{R}(x)(m)), &m =2m' \\
-\MF{Im}(\MC{R}(x)(m)), &m =2m'+1
-\end{cases} \\
-m' =& 1, \dotsc, M \NT
+\NC \begin{cases}
+\MF{Re}(\MC{R}(x)(m)), \NC m =2m' \NR[+]
+\MF{Im}(\MC{R}(x)(m)), \NC m =2m'+1
+\end{cases} \NR[+]
+m' =\NC  1, \dots, M \NT
 }
@@
 \Disp{
-A \in &\MB{V}_{\MB{R}} (2M_1, 2M_2) \NT \\
+A \in \NC \MB{V}_{\MB{R}} (2M_1, 2M_2) \NR
 A (m_1,m_2) =
-&\begin{cases}
-\MF{Re}(A (m_1,m_2)), &m_1 =2m_1'-1,\; m_2 =2m_2'-1  \\
-\MF{Im}(A (m_1,m_2)), &m_1 =2m_1',\; m_2 =2m_2'-1  \\
--\MF{Im}(A (m_1,m_2)), &m_1 =2m_1'-1,\; m_2 =2m_2'  \\
-\MF{Re}(A (m_1,m_2)), &m_1 =2m_1',\; m_2 =2m_2'  \\
-\end{cases} \\
-m_1' = &1, \dotsc, m_1 \NT \\
-m_2' = &1, \dotsc, m_2 \NT
+\NC \begin{cases}
+\MF{Re}(A (m_1,m_2)), \NC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR[+]
+\MF{Im}(A (m_1,m_2)), \NC m_1 =2m_1',\; m_2 =2m_2'-1  \NR[+]
+-\MF{Im}(A (m_1,m_2)), \NC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR[+]
+\MF{Re}(A (m_1,m_2)), \NC m_1 =2m_1',\; m_2 =2m_2'  \NR[+]
+\end{cases} \NR[+]
+m_1' = \NC 1, \dots, m_1 \NR
+m_2' = \NC 1, \dots, m_2 \NT
 }
@@
 \V{\T{y}}
-=\MC{R}(y) \in \MB{V}(N_h) \\
+=\NC \MC{R}(y)
+\in \MB{V}(N_h) \NR[+]
 \V{\T{g}}
-=\MC{R}(g) \in \MB{V}(N_h) \\
+=\NC \MC{R}(g)
+\in \MB{V}(N_h) \NR[+]
 \M{\T{P}}
-=\MC{R}(\M{P}) \in \MB{M}_{\MB{C}} (2 N_y^2, 2 N_h^2)
+=\NC \MC{R}(\M{P})
+\in \MB{M}_{\MB{C}} (2 N_y^2, 2 N_h^2)
 }
@@
 \Disp{
-I_{n_y}^{(y)} \in &\MB{M}_{\MB{C}} (N_y, N_y) \NT \\
-I_{n_y}^{(y)}(n_y')
-=&\begin{cases}
-1, &n_y' =2n_y \\
-1, &n_y' =2n_y +1 \\
-0, &\RM{otherwise}
-\end{cases} \\
-I_{n_h}^{(h)} \in &\MB{M}_{\MB{C}} (N_h, N_h) \NT \\
-I_{n_h}^{(h)}(n_h')
-=&\begin{cases}
-1, &n_h' =2n_h \\
-1, &n_h' =2n_h +1 \\
-0, &\RM{otherwise}
-\end{cases} \\
-n_y =&1, \dotsc, N_y \NT \\
-n_h =&1, \dotsc, N_h \NT
+\M{I}_{n_y}^{(y)} \in \NC \MB{M}_{\MB{R}} (2N_y^2, 2N_y^2) \NR
+\M{I}_{n_y}^{(y)}(n_y')
+=\NC \begin{cases}
+1, \NC n_y' =2n_y \NR[+]
+1, \NC n_y' =2n_y +1 \NR[+]
+0, \NC \RM{otherwise}
+\end{cases} \NR[+]
+\M{I}_{n_h}^{(h)} \in \NC \MB{M}_{\MB{R}} (2N_h^2, 2N_h^2) \NR
+\M{I}_{n_h}^{(h)}(n_h')
+=\NC \begin{cases}
+1, \NC n_h' =2n_h \NR[+]
+1, \NC n_h' =2n_h +1 \NR[+]
+0, \NC \RM{otherwise}
+\end{cases} \NR[+]
+n_y =\NC 1, \dots, N_y \NR
+n_h =\NC 1, \dots, N_h \NT
 }
@@
 \Disp{
-&\min_{\T{\V{g}}, \V{m}} \IP{ \V{1}, \V{m} } \NT \\
-\RM{s.t.}
-&\begin{cases}
-\| I_{n_h}^{(h)} \T{\V{g}} \|_2
-\leq \IP{ \V{y}_{n_h}, \V{m} } \\
-\| I_{n_y}^{(y)} \T{\M{P}}^\H ( \T{\M{P}} \T{\V{g}} -\T{\V{y}} ) \|_2
-\leq \gamma  \\
+\min_{\T{\V{g}}, \V{m}} \quad
+\NC \IP{ \V{1}, \V{m} } \NR
+\RM{subject}\; \RM{to} \quad
+\NC \begin{cases}
+\| \M{I}_{n_h}^{(h)} \T{\V{g}} \|_2
+\leq \IP{ \V{y}_{n_h}, \V{m} } \NR[+]
+\| \M{I}_{n_y}^{(y)} \T{\M{P}}^\H ( \T{\M{P}} \T{\V{g}} -\T{\V{y}} ) \|_2
+\leq \gamma  \NR[+]
 \end{cases}
@@
 
-{ \color{red} (To be done) }
+\color[red]{(To be done)}
 
-\subsection{Primal-Dual Interior Point Algorithm}
+\startsection [title={Primal-Dual Interior Point Algorithm}]
 
@@
 Of course it is not the only way to do this.
-We mention, again, Boyd and Vandenberghe (2004), \textit{Convex Optimization} chap.11 as a standard reference, and ``\(\ell_1\)-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.
+We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.11 as a standard reference, and ``\(\ell_1\)-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.
 
@@
 \Disp{
-&\MC{L}(\V{m}, \T{g}, \mu^{(h)}, \mu^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NT \\
-=& \IP{ \V{1}, m } 
-+\sum_{n_h} \big[ \IP{ \mu^{(h)}, I_{n_h}^{(h)} \T{g} } -\lambda^{(h)} \IP{ \V{y}_{n_h}, \V{m} } \big] \NT \\
-\quad & +\sum_{n_y} \big[ \IP{ \mu^{(h)}, I_{n_y}^{(y)} \T{P}^\H ( \T{P} \T{g} -\T{u} ) } -\lambda^{(h)} \gamma \big]
+\NC \NC \MC{L}(\V{m}, \T{\V{g}}, \V{\mu}^{(h)}, \V{\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NR
+\NC =\NC \IP{\V{1}, \V{m}}
++\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M{g}}} -\lambda^{(h)} \IP {\V{y}_{n_h}, \V{m}}} \NR
+\NC \quad \NC  +\sum_{n_y} \SB{ \IP{ \V{\mu}^{(h)}, \M{I}_{n_y}^{(y)} \T{\M{P}}^\H ( \T{\M{P}} \T{\V{g}} -\T{\V{y}} ) } -\lambda^{(h)} \gamma} \NR[+]
 }
@@
 
-\subsection{Discussion}
+\startsection [title={Discussion}]
 
@@
 On the other hand, as of OMP, besides the original justification of entrywise i.i.d.\ Gaussian sensing matrix (Tropp and Gilbert 2007a), and existent attempt to characterize MIP condition, there is much to be done OMP for Gaussian.
+
+\stopchapter

### 2019-03-05 ongoing/report/1_introduction.tex
Reformatting source

@@
 
-\m{\Nm{a}} denotes the magnitude for real or complex numbers \m{a}.
-The real and imaginary part of \m{a} will be denoted respectively as \m{\MF{Re} (a)} and \m{\MF{Im} (a)}, respectively, thus \m{a =\MF{Re} (a) + i \MF{Im} (a)}
+\m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
+The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} (a)} and \m {\MF {Im} (a)}, respectively, thus \m {a =\MF {Re} (a) + i \MF {Im} (a)}
 
-We restrict our discussion to \m{\MB{R}^N} or \m{\MB{C}^N} seen as the Hilbert space , equipped with standard inner product.
-Lower case Latin alphabets with single underline, like \m{\V{a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m{\M{A}}, denote matrices.
-Particularly, define \m{\V{1} =\IP {1, \dots, 1}} and \m{\V{1} =\IP {1, \dots, 1}}.
+We restrict our discussion to \m {\MB {R}^N} or \m {\MB {C}^N} seen as the Hilbert space , equipped with standard inner product.
+Lower case Latin alphabets with single underline, like \m {\V {a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m {\M {A}}, denote matrices.
+Particularly, define \m {\V {1} =\IP {1, \dots, 1}}.
+Denote \m {\V {a} \DB {n}} to be the \m {n}-th component of \m {\V {a}}, and similarly \m {\M {A} \DB {m,n}} to be the \m {(m,n)}-th entry of \m {\M {A}}.
 
 In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
-Of course, scalar operation on \m{\MB{R}^N} is over field \m{\MB{R}}, and that on \m{\MB{C}^N} is over field \m{\MB{C}}.
-We use \m{\MB{K}} to refer to either \m{\MB{R}} or \m{\MB{C}}.
-Not to avoid confusion, we call the Hilbert space \m{\MB{K}^N} over \m{\MB{K}} to be \m{\MB{V}_{\MB{K}} (N)}.
-We also call the collection of \m{M} by \m{N} matrices to be \m{\MB{M}_{\MB{K}} (M,N)}, and its role as linear transformation is understood.
-Inner product of \m{\V{a}} and \m{\V{b}} is denoted as \m{\IP{ \V{a}, \V{b} }}.
-Slightly abusing notation, we denote as \m{\V{a} (n)} the \m{n}-th component of \m{\V{a}}, and denote as \m{\V{A} (m,n)} the \m{(m,n)}-entry of \m{\V{A}}
-Particularly, \m{\V{u}_n} is the \m{n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
-\m{\VNm {\V{a}} _p} denotes the \m{\ell_p}-norm of vector \m{\V{a}}.
-Recall that \m{\ell_\infty}-norm is the maximum-magnitude norm.
+Of course, scalar operation on \m {\MB {R}^N} is over field \m {\MB {R}}, and that on \m {\MB {C}^N} is over field \m {\MB {C}}.
+We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
+Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} (N)}.
+We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} (M,N)}, and its role as linear transformation is understood.
+Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
+Slightly abusing notation, we denote as \m {\V {a} (n)} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} (m,n)} the \m {(m,n)}-entry of \m {\V {A}}
+Particularly, \m {\V {u}_n} is the \m {n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
+\m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
+Recall that \m {\ell_\infty}-norm is the maximum-magnitude norm.
 
-Denote as \m{\MB{P} (X)} the probability, and \m{\MB{E} (X)} the expectation.
+Denote as \m {\MB {P} (X)} the probability, and \m {\MB {E} (X)} the expectation.
 Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.
+
+Round brackets \m {\RB {\cdot}} are used purely for precedence of , and \m {\SB {\cdot}} exclusively for function arguments.
 
@@
 The figure of merit of a MIMO system is usually considered to be the channel capacity.
-In vague terms, the capacity \m{C} of a MIMO channel \m{\M{H}} at perfect channel state information is well-known to be roughly in the form \m{\log \det (I +\RM{SNR})}, but that knowledge is hardly always available.
-What makes things more difficult is the case that \m{\M{H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
+In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det (I +\RM {SNR})}, but that knowledge is hardly always available.
+What makes things more difficult is the case that \m {\M {H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
 It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
 Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m{\log \det (I +\RM{SNR})}.
+Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det (I +\RM {SNR})}.
 
-Therefore the real-time estimation, \m{\hat{\M{H}}}, of \m{\M{H}} is of paramount importance.
-Needless to say, when the \m{\hat{\M{H}}} is imprecise, resulting analysis is also undermined.
+Therefore the real-time estimation, \m {\hat {\M {H}}}, of \m {\M {H}} is of paramount importance.
+Needless to say, when the \m {\hat {\M {H}}} is imprecise, resulting analysis is also undermined.
 With more antennae present, conventional training-based algorithms also increase in complexity and storage.
@@
 
-To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m{N_p \in \MB{N}} is much larger than the number of measurements \m{N_m \in \MB{N}}, namely,
+To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
 %
-\Disp{
+\Disp {
 \NC N_p \gg N_m \NR
@@
 %
-In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m{N_p} parameters?
+In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
 Of course, more assumption must be made to make the question meaningful.
@@
 
-Cand\`es and Tao showed frst that that in the noiseless case (``Decoding by Linear Programming'', 2006), it is possible to recover the sparse signal, under a \m{\ell_1} minimization program.
+Cand\`es and Tao showed frst that that in the noiseless case (``Decoding by Linear Programming'', 2006), it is possible to recover the sparse signal, under a \m {\ell_1} minimization program.
 The work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
 
-Later they established a stronger result that (``The Dantzig Selector'', 2007), with another \m{\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
+Later they established a stronger result that (``The Dantzig Selector'', 2007), with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
 Such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
@@
 
-From the realistic perspective, the formulation as an \m{\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
+From the realistic perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
 Indeed, relevent code has been put on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
@@
 In this article we focuss on DS, and we introduce several notions before we describe their work.
-To facilitate reader's understanding, in this section we will consistently use \m{N_p} and \m{N_m} to denote matrix dimensions.
+To facilitate reader's understanding, in this section we will consistently use \m {N_p} and \m {N_m} to denote matrix dimensions.
 Following Cand\`es and Tao, we borrow the term ``support'' from the context of analysis, where it denotes the set on which a function is nonzero.
 
-We will use \m{T \RB{N_m} =\{1, \dots, N_m\}} to denote the support of \m{\MB{V}_{\MB{K}} (N_m)}.
+We will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} (N_m)}.
 
@@
 {
-Suppose \m{\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)}.
-Let \m{\MC{T} \subset T \RB{N_p}}.
-Denote as \m{\M{A}_{\MC{T}}} the columns of \m{\M{A}} having indices in \m{\MC{T}}.
+Suppose \m {\M {A} \in \MB {M}_{\MB {K}} (N_m, N_p)}.
+Let \m {\MC {T} \subset T \RB {N_p}}.
+Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
 }
@@
 {
-\m{x \in \MB{V}_{\MB{K}} (N_m)} is called \m{s}-sparse with support \m{\MC{A}}, \m{s <N_m}, if there is \m{\MC{A} \subset T \RB{N_m}} such that
+\m {x \in \MB {V}_{\MB {K}} (N_m)} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
 %
-\Disp{ 
-\NC x_{T(N) -\MC{A}}
-=\NC \V{0} \NR
+\Disp { 
+\NC x_{T(N) -\MC {A}}
+=\NC \V {0} \NR
 }
 with
-\Disp{ 
-\NC \# \MC{A} \leq s. \NR
+\Disp { 
+\NC \# \MC {A} \leq s. \NR
 }
-That is, only at most \m{s} components of \m{x} is nonzero.
+That is, only at most \m {s} components of \m {x} is nonzero.
 }
@@
 {
-Let \m{P \in \MB{M}_\MB{K} (N_m, N_p)} and \m{y \in \MB{V}_\MB{K} (N_p)} be given.
-Find \m{h \in \MB{V}_\MB{K} (N_p)} with
+Let \m {P \in \MB {M}_\MB {K} (N_m, N_p)} and \m {y \in \MB {V}_\MB {K} (N_p)} be given.
+Find \m {h \in \MB {V}_\MB {K} (N_p)} with
 %
-\Disp{
+\Disp {
 \NC
@@
 \quad \MC \VNm {h'} _1 \NR[+]
-\NC \RM{subject}\; \RM{to}
+\NC \RM {subject} \; \RM {to}
 \quad \MC P h' =y \NR
@@
 
-Now let \m{y =P h}.
-Suppose \m{h} is \m{s}-sparse, then the program () completely recovers \m{h}.
-That is, a noiseless linear transformation of a sparse vector is completely recovered by a \m{\ell_1}-minimization program with an overwhelming probability.
+Now let \m {y =P h}.
+Suppose \m {h} is \m {s}-sparse, then the program () completely recovers \m {h}.
+That is, a noiseless linear transformation of a sparse vector is completely recovered by a \m {\ell_1}-minimization program with an overwhelming probability.
 
@@
 {
-Consider \m{P \in \MB{M}_{\MB{K}} (N_m, N_p)}, with unity-\m{\ell_2}-norm columns.
-For \m{s =1, \dots N_p}, we say that \m{P} satisfies the restricted isometry property (RIP) of sparsity \m{s} with respect to \m{0 \leq \d_s \leq 1}, if, for all \m{s}-sparse \m{\V{x} \in \MB{V}_{\MB{K}} (N_p)}, for all \m{\MC{T} \subset T(N_m)} with \m{\#\{\MC{T}\} \leq s},
+Consider \m {P \in \MB {M}_{\MB {K}} (N_m, N_p)}, with unity-\m {\ell_2}-norm columns.
+For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} (N_p)}, for all \m {\MC {T} \subset T(N_m)} with \m {\#\{\MC {T} \} \leq s},
 %
-\Disp{
-\NC \NC (1-\d_s) \VNm {V{x}}^2 \NR
-\NC \leq \NC \VNm {P_{\MC{T}} \V{x}} _2^2 \NR
-\NC \leq \NC (1+\d_s) \VNm {\V{x}} _2^2 \NR[+]
+\Disp {
+\NC \NC (1-\d_s) \VNm {V {x}}^2 \NR
+\NC \leq \NC \VNm {P_{\MC {T}} \V {x}} _2^2 \NR
+\NC \leq \NC (1+\d_s) \VNm {\V {x}} _2^2 \NR[+]
 }
@@
 
-RIP is essentially saying that \m{P} is ``almost unitary'' up to ``relative error'' \m{\d_s}.
+RIP is essentially saying that \m {P} is ``almost unitary'' up to ``relative error'' \m {\d_s}.
 
@@
 %
-\Disp{
-\NC \V{y} =\M{P} \V{h} + \V{z} \NR
+\Disp {
+\NC \V {y} =\M {P} \V {h} + \V {z} \NR
 }
 %
-where (w.l.o.g.) \m{z} is an i.i.d.\ normalized Gaussian vector.
-How can we hope to estimate \m{h} when, in addition to insufficient observations, there are too few observations?
+where (w.l.o.g.) \m {z} is an i.i.d.\ normalized Gaussian vector.
+How can we hope to estimate \m {h} when, in addition to insufficient observations, there are too few observations?
 
@@
 {
-Let \m{\M{P} \in \MB{V}_\MB{R} (N_m, N_p)} and \m{\V{y} \in \MB{V}_\MB{R} (N_m)} be given.
-Find \m{\V{h} \in \MB{V}_\MB{R} (N_m)} by
+Let \m {\M {P} \in \MB {V}_\MB {R} (N_m, N_p)} and \m {\V {y} \in \MB {V}_\MB {R} (N_m)} be given.
+Find \m {\V {h} \in \MB {V}_\MB {R} (N_m)} by
 %
 
-\Disp{
-\NC \V{h}
-=
-\NC \startcases
-\NC \Min {\V{h}'} \quad \MC \VNm {\V{h}'} _1 \NR
-\NC \RM{subject}\; \RM{to} \quad \MC \VNm {\M{P}^\H (\M{P} \V{h} -\V{y})} _\infty \leq \gamma \NR
+\Disp {
+\NC \V {h}
+= \NC \startcases
+\NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
+\NC \RM {subject} \; \RM {to} \quad \MC \VNm {\M {P}^\H (\M {P} \V {h} -\V {y})} _\infty \leq \gamma \NR
 \stopcases \NR
@@
 They was able to show that, with Program (), the mean square error is bounded with overwhelming probability.
-And it can be shown that this \m{\ell_1}-minimization problem with \m{\ell_\infty}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
+And it can be shown that this \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
 Note that they confined their discussion for real vectors.
@@
 
-The constant \m{\d} in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \m{\d=0}, i.e., that \m{P} is fully unitary, rendering the RIP an important role.
+The constant \m {\d} in the proof of DS is significant.
+Indeed, we may observe that in theorem (), the bound is not tightest when \m {\d=0}, i.e., that \m {P} is fully unitary, rendering the RIP an important role.
 Here, it is not clear at first what matrices serves as the RIP condition.
@@
 {
-Let each entry of random matrix \m{P \in \MB{M}_\MB{K} (N_m, N_p)} be defined as i.i.d.\ Bernoulli with value \m{\pm 1/\R{N_m}} (that is, Rademacher distribution).
-Then, with \m{0 <\epsilon <1},
+Let each entry of random matrix \m {P \in \MB {M}_\MB {K} (N_m, N_p)} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
+Then, with \m {0 <\epsilon <1},
 %
-\Disp{
-\NC \NC \MB{P} ( \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm{h} _2^2) \NR
+\Disp {
+\NC \NC \MB {P} ( \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2) \NR
 \NC \leq \NC 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) ) \NR
@@
 
-One of the first papers, Bajwa et.\ al.\ (2010) argues the \m{\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
+One of the first papers, Bajwa et.\ al.\ (2010) argues the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
 What they explored was the estimation of single-antenna channel response with respect to time.
-Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \m{X} is RIP for overwhelming probability, providing the ground for the former paper.
+Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \m {X} is RIP for overwhelming probability, providing the ground for the former paper.
 
-To explain the idea, consider a linear time-invariant channel that \m{y(t) =(x \star h)(t) + z(t)}, where \m{h(t)} is the channel's impulse response, \m{y(t)} is the output, and, for each time index, \m{x(t)} is i.i.d.\ Rademacher, and \m{z(t)} is i.i.d.\ Gaussian.
-Simply assuming \m{h} has sparse support, and let the convolution with \m{x} be expressed by a matrix \m{X}, \m{X} is a Toeplitz matrix, so that \m{y =X h +z}.
-Then Bajwa et.\ al.\ was able to show that, \m{X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.
+To explain the idea, consider a linear time-invariant channel that \m {y(t) =(x \star h)(t) + z(t)}, where \m {h(t)} is the channel's impulse response, \m {y(t)} is the output, and, for each time index, \m {x(t)} is i.i.d.\ Rademacher, and \m {z(t)} is i.i.d.\ Gaussian.
+Simply assuming \m {h} has sparse support, and let the convolution with \m {x} be expressed by a matrix \m {X}, \m {X} is a Toeplitz matrix, so that \m {y =X h +z}.
+Then Bajwa et.\ al.\ was able to show that, \m {X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.
 
@@
 
-Same as before, consider \m{\V{y} \in \MB{V}_\MB{K} (N_p)}, \m{\V{h} \in \MB{V}_\MB{K} (N_s)}, where \m{\V{h}} is \m{s}-sparse, with \m{N_p \gg N_s}.
+Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} (N_p)}, \m {\V {h} \in \MB {V}_\MB {K} (N_s)}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
 If
-\Disp{
-\NC \V{y} =\M{P} \V{h}, \NR
+\Disp {
+\NC \V {y} =\M {P} \V {h}, \NR
 }
 that is, the noiseless, real-number case.
-We pick up the columns of \m{\M{P}} greedily, hoping to correspond to the support of \m{\V{h}}, thus recovering the original signal.
+We pick up the columns of \m {\M {P}} greedily, hoping to correspond to the support of \m {\V {h}}, thus recovering the original signal.
 
@@
 {
-Following the setting described above, suppose, for \m{0 <\d <1},
+Following the setting described above, suppose, for \m {0 <\d <1},
 %
-\Disp{
+\Disp {
 \NC M \geq 16s \log (N/\d) \NR
@@
 %
-Then OMP (Algorithm \_\_) recovers \m{x} completely, with overwhelming probability \m{1-\d}.
+Then OMP (Algorithm \_\_) recovers \m {x} completely, with overwhelming probability \m {1-\d}.
 }
@@
 
-For concreteness, let \m{\M{F}} be the precoder and \m{\M{W}} the combiner, and \m{\M{H}} the channel, and consider the noiseless case.
-Let signal \m{\V{x}} be sent, and \m{\V{y}} be receiverd, that is
+For concreteness, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
+Let signal \m {\V {x}} be sent, and \m {\V {y}} be receiverd, that is
 %
-\Disp{
-\NC \V{y} =\M{W} \M{H} \M{F} \V{x} \NR
+\Disp {
+\NC \V {y} =\M {W} \M {H} \M {F} \V {x} \NR
 }
@@
 {
-Define \m{\RM{vec} (\M{A}) \in \MB{K}^{NM}} to be the vectorization of \m{\M{A} \in \MB{M}_{\MB{K}} (N,M)}.
+Define \m {\RM {vec} (\M {A}) \in \MB {K}^{NM}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} (N,M)}.
 }
@@
 {
-For \m{\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)} and \m{\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)}
-Define the Kronecker product \m{\RM{vec} (A) \in \MB{K}^{nm}} 
+For \m {\RM {vec} (A) \in \MB {M}_{\MB {K}} (N,M)} and \m {\RM {vec} (A) \in \MB {M}_{\MB {K}} (N,M)}
+Define the Kronecker product \m {\RM {vec} (A) \in \MB {K}^{nm}} 
 }
@@
 %
-\Disp{
-\NC \RM{vec} (Y)
-=\big[ (F^\H) \otimes W \big] \RM{vec} (\M{H}) \NR
+\Disp {
+\NC \RM {vec} (Y)
+=\big[ (F^\H) \otimes W \big] \RM {vec} (\M {H}) \NR
 }

### 2019-03-05 ongoing/report/2_problem_setting.tex
Reformatting source

@@
 
-\Disp{
+\Disp {
 \NC \Omega
@@
 \startitemize
-\item \m{\Omega_t} denotes the event space of the transmitter end,
-\item \m{\Omega_h} denotes the event space of the communication channel itself,
-\item \m{\Omega_z} denotes the event space of the noise arising in the communication channel,
-\item \m{\Omega_r} denotes the event space of the receiver end.
+\item \m {\Omega_t} denotes the event space of the transmitter end,
+\item \m {\Omega_h} denotes the event space of the communication channel itself,
+\item \m {\Omega_z} denotes the event space of the noise arising in the communication channel,
+\item \m {\Omega_r} denotes the event space of the receiver end.
 \stopitemize
@@
 %
-\Disp{
-\NC \V{a} (\psi')
-= \NC \F{1}{\R{N_H}} \sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
-\in \MB{V}_\MB{C} (N_H) \NR
+\Disp {
+\NC \V {a} (\psi')
+= \NC \F {1}{\R {N_H}} \sum_{n=1}^{N} \RM {e}^{n \psi' i} \V {u}_n
+\in \MB {V}_\MB {C} (N_H) \NR
 }
 %
-where \m{\RM{e}} is the base of natural logarithm, and \m{i} the imaginary unit.
+where \m {\RM {e}} is the base of natural logarithm, and \m {i} the imaginary unit.
 
@@
 %
-\Disp{
+\Disp {
 \NC H
-=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \f_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \th_l' \right)^\H \NR
+=\sum_{l=1}^L \alpha_l \V {a} \left( \F {d} {\lambda} \sin \f_l' \right) \V {a} \left( \F {d_{\RM {arr}}} {\lambda} \sin \th_l' \right)^\H \NR
 }
 %
-The physical meaning of \m{\th_l} is the \m{l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m{\th_l}, the \m{l}-th that of arrival wave, while \m{d_{\RM{arr}}} is the distance between two adjacent antennae.
-For our purpose, we may absorb the argument of \m{\V{a}} as
+The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\RM {arr}}} is the distance between two adjacent antennae.
+For our purpose, we may absorb the argument of \m {\V {a}} as
 %
-\Disp{
+\Disp {
 \NC \f_l
-=\NC \F{d_{\RM{arr}}} {\lambda} \sin \f_l' \NR[+]
+=\NC \F {d_{\RM {arr}}} {\lambda} \sin \f_l' \NR[+]
 \NC \th_l
-=\NC \F{d_{\RM{arr}}} {\lambda} \sin \th_l' \NR[+]
+=\NC \F {d_{\RM {arr}}} {\lambda} \sin \th_l' \NR[+]
 }
@@
 %
-\Disp{
+\Disp {
 \NC H
-=\sum_{l=0}^L \alpha_l \V{a} (\f_l) \V{a} (\th_l)^\H
-\in \MB{M}_\MB{C} (N_H) \NR
+=\sum_{l=0}^L \alpha_l \V {a} (\f_l) \V {a} (\th_l)^\H
+\in \MB {M}_\MB {C} (N_H) \NR
 }
@@
 That is to say, each end consists of both digital and analog percoders and combiners, as follows.
-In the transmitter end, there are, in order seeing from the end, digital precoder \m{F_B} and analog precoder \m{F_R}.
-Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m{W_B} and analog combiner \m{W_R}.
+In the transmitter end, there are, in order seeing from the end, digital precoder \m {F_B} and analog precoder \m {F_R}.
+Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m {W_B} and analog combiner \m {W_R}.
 To set up notation, we list them as below.
 %
-\Disp{
-\NC \M{F}_B \in  \NC \MB{M}_{\MB{C}} (N_R, N_Y) \NR[+]
-\NC \M{F}_R \in  \NC \MB{M}_{\MB{C}} (N_H, N_R) \NR[+]
-\NC \M{W}_R \in  \NC \MB{M}_{\MB{C}} (N_R, N_H) \NR[+]
-\NC \M{W}_B \in  \NC \MB{M}_{\MB{C}} (N_Y, N_R) \NR
+\Disp {
+\NC \M {F}_B \in  \NC \MB {M}_{\MB {C}} (N_R, N_Y) \NR[+]
+\NC \M {F}_R \in  \NC \MB {M}_{\MB {C}} (N_H, N_R) \NR[+]
+\NC \M {W}_R \in  \NC \MB {M}_{\MB {C}} (N_R, N_H) \NR[+]
+\NC \M {W}_B \in  \NC \MB {M}_{\MB {C}} (N_Y, N_R) \NR
 }
@@
 %
-\Disp{
-\NC \Nm{\M{F}_R (n_h, n_r)} = \NC 1, \NR[+]
-\NC \Nm{\M{W}_R (n_r, n_h)} = \NC 1, \NR[+]
+\Disp {
+\NC \Nm {\M {F}_R (n_h, n_r)} = \NC 1, \NR[+]
+\NC \Nm {\M {W}_R (n_r, n_h)} = \NC 1, \NR[+]
 \NC n_h = \NC 1, \dots N_H, \NR
@@
 And we assume
-\Disp{
+\Disp {
 \NC N_H \gg  \NC N_R \NR[+]
@@
 
-We consider zero-mean, unity-variance additive white Gaussian noise \m{z}.
-Since we restrict our discussion to a specific slice of time, the signal \m{z} degrades as a entrywise i.i.d.\ standard normal distribution vector.
+We consider zero-mean, unity-variance additive white Gaussian noise \m {z}.
+Since we restrict our discussion to a specific slice of time, the signal \m {z} degrades as a entrywise i.i.d.\ standard normal distribution vector.
 
@@
 %
-\Disp{
+\Disp {
 \NC Y (\omega_h, \omega_e)
@@
 %
-\Disp{
+\Disp {
 \NC Y
@@
 }
-\m{\M{Y}} has \m{N_Y} columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \m{\V{u}_n}.
-This way, we may denote the acquired effective channel matrix \m{\M{Y}} under noisy observation as (borrowing Matlab's colon notation to denote columns)
+\m {\M {Y}} has \m {N_Y} columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \m {\V {u}_n}.
+This way, we may denote the acquired effective channel matrix \m {\M {Y}} under noisy observation as (borrowing Matlab's colon notation to denote columns)
 %
-\Disp{
-\NC \M{Y} (:,n_y)
-:= \NC \M{W}_B \M{W}_R \Big[ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} \Big], \NR[+]
+\Disp {
+\NC \M {Y} (:,n_y)
+:= \NC \M {W}_B \M {W}_R \Big[ \M {H} \M {F}_R \M {F}_B \V {u}_{n_y} +\V {z} \Big], \NR[+]
 \NC \quad n_y = \NC 1, 2, \dots, N_Y \NR
@@
 %
-Still, the crux of the matter is the recovery of \m{\M{H}} with knowledge of \m{\M{Y}}, while \m{\M{W}_R}, \m{\M{W}_B}, \m{\M{F}_R}, and \m{\M{F}_B} are in our control.
+Still, the crux of the matter is the recovery of \m {\M {H}} with knowledge of \m {\M {Y}}, while \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B} are in our control.
 
@@
 %
-\Disp{
-\NC \V{h}
-:= \NC \RM{vec} (\M{H})
-\in \MB{V}_{\MB{C}} (N_g) \NR[+]
-\NC \V{y}
-:= \NC \RM{vec} (\M{Y})
-\in \MB{V}_{\MB{C}} (N_y) \NR[+]
-\NC \V{z}^\star
-:= \NC \RM{vec} (\M{Z})
-\in \MB{V}_{\MB{C}} (N_y) \NR[+]
-\NC \M{P}^\star
-:= \NC (\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
-\in \MB{M}_{\MB{C}} (N_y, N_g) \NR
+\Disp {
+\NC \V {h}
+:= \NC \RM {vec} (\M {H})
+\in \MB {V}_{\MB {C}} (N_g) \NR[+]
+\NC \V {y}
+:= \NC \RM {vec} (\M {Y})
+\in \MB {V}_{\MB {C}} (N_y) \NR[+]
+\NC \V {z}^\star
+:= \NC \RM {vec} (\M {Z})
+\in \MB {V}_{\MB {C}} (N_y) \NR[+]
+\NC \M {P}^\star
+:= \NC (\M {F}_R^\Tr \M {F}_B^\Tr) \otimes (\M {W}_B \M {W}_R)
+\in \MB {M}_{\MB {C}} (N_y, N_g) \NR
 }
 %
-to formulate our goal as sparse recovery problem of \m{\RM{vec} (H)} to be
+to formulate our goal as sparse recovery problem of \m {\RM {vec} (H)} to be
 %
-\Disp{
-\NC \V{y} =\M{P}^\star \V{h} +\V{z}^\star \NR
+\Disp {
+\NC \V {y} =\M {P}^\star \V {h} +\V {z}^\star \NR
 }
@@
 
-Introduce the discrete Fourier matrix \m{\M{K}} defined to be
+Introduce the discrete Fourier matrix \m {\M {K}} defined to be
 %
-\Disp{
-\NC \M{K} \in  \NC \MB{M}_{\MB{C}} (N_H, N_H) \NR
-\NC \M{K} (n_1, n_2) = \NC \F{1} {\R{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \NR[+]
+\Disp {
+\NC \M {K} \in  \NC \MB {M}_{\MB {C}} (N_H, N_H) \NR
+\NC \M {K} (n_1, n_2) = \NC \F {1} {\R {N_H}} \RM {e}^{2\pi i n_1 n_2 /N_H}, \NR[+]
 \NC \quad n_1, n_2 = \NC 0, 1, \dots, N_H-1 \NR
@@
 %
-\Disp{
-\NC \M{G}
-=\M{K}^\H \M{H} \M{K} \NR
+\Disp {
+\NC \M {G}
+=\M {K}^\H \M {H} \M {K} \NR
 }
 %
-which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \m{\M{H}}, then
+which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \m {\M {H}}, then
 %
-\Disp{
-\NC \M{Y}
-:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
-\in \MB{M}_{\MB{C}} (N_Y, N_Y) \NR
+\Disp {
+\NC \M {Y}
+:=\M {W}_B \M {W}_R \M {K} ( \M {G} \M {K}^\H \M {F}_R \M {F}_B +\M {K}^\H \M {Z} )
+\in \MB {M}_{\MB {C}} (N_Y, N_Y) \NR
 }
 %
-If at the end of day, \m{\M{G}} is sparse, then we recover \m{\M{G}} instead, and our use of DS is fully justified.
+If at the end of day, \m {\M {G}} is sparse, then we recover \m {\M {G}} instead, and our use of DS is fully justified.
 
-That is to say, \m{\M{K}^\H \V{z}} may be absorbed, and a similar Kronecker product may be used.
+That is to say, \m {\M {K}^\H \V {z}} may be absorbed, and a similar Kronecker product may be used.
 To simplify notation, set
 %
-\Disp{
-\NC \M{P}
-:=(\M{F}_B^\Tr \M{F}_R^\Tr K^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
-\in \MB{M}_{\MB{C}} (N_y, N_g) \NR
+\Disp {
+\NC \M {P}
+:=(\M {F}_B^\Tr \M {F}_R^\Tr K^\ast) \otimes (\M {W}_B \M {W}_R \M {K})
+\in \MB {M}_{\MB {C}} (N_y, N_g) \NR
 }
@@
 And accordingly
-\Disp{
-\NC \V{g}
-:= \NC \RM{vec} (\M{G})
-\in \MB{M}_{\MB{C}} (N_g) \NR[+]
-\NC \V{z}
-:= \NC \RM{vec} (\M{K}^\H \M{Z})
-\in \MB{V}_{\MB{C}} (N_y) \NR
+\Disp {
+\NC \V {g}
+:= \NC \RM {vec} (\M {G})
+\in \MB {M}_{\MB {C}} (N_g) \NR[+]
+\NC \V {z}
+:= \NC \RM {vec} (\M {K}^\H \M {Z})
+\in \MB {V}_{\MB {C}} (N_y) \NR
 }
 where for short we set
-\Disp{
+\Disp {
 \NC N_g = \NC N_H^2 \NR[+]
@@
 %
-\Disp{
-\NC \V{y}
-=\M{P} \V{g} +\V{z} \NR
+\Disp {
+\NC \V {y}
+=\M {P} \V {g} +\V {z} \NR
 }
@@
 {
-Let \m{\M{P}, \V{y}} be defined just above in ().
-Then, with parameter \m{\gamma} specified, define the following program
+Let \m {\M {P}, \V {y}} be defined just above in ().
+Then, with parameter \m {\gamma} specified, define the following program
 %
-\Disp{
-\NC \hat{\V{g}}
+\Disp {
+\NC \hat {\V {g}}
 =\NC \startcases
-\Min {\V{g}'}  \MC \VNm {\V{g}'} _1 \NR[+]
-\RM{subject}\; \RM{to} \quad  \MC \VNm {\M{P}^\H (\V{y} -\M{P} \V{g}')} _\infty \leq \gamma \NR
+\Min {\V {g}'}  \MC \VNm {\V {g}'} _1 \NR[+]
+\RM {subject} \; \RM {to} \quad  \MC \VNm {\M {P}^\H (\V {y} -\M {P} \V {g}')} _\infty \leq \gamma \NR
 \stopcases \NR
@@
 %
-And convert \m{\hat{\V{g}}} back to the space domain as
+And convert \m {\hat {\V {g}}} back to the space domain as
 %
-\Disp{
-\NC \hat{G} =\RM{vec}^{-1} (\hat{g}) \NR
+\Disp {
+\NC \hat {G} =\RM {vec}^{-1} (\hat {g}) \NR
 }
 %
-And finally recover the estimated \m{H} as
+And finally recover the estimated \m {H} as
 %
-\Disp{
-\NC \hat{\M{H}} =\M{K} \hat{\M{G}} \M{K}^\H \NR
+\Disp {
+\NC \hat {\M {H}} =\M {K} \hat {\M {G}} \M {K}^\H \NR
 }

### 2019-03-05 ongoing/report/3_theorems_and_proofs.tex
Reformatting source

@@
 We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \m{g \in \MB{C}^{N_g}}, and we continue to use \m{\hat{g}} to denote the Dantzig Selector.
-To simplify the exposition, we will continue to use the variables \m{\V{P}}, \m{\V{g}}, \m{\V{y}}, and \m{\V{z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).
+The sparse vector to be recovered of our investigation is \m {g \in \MB {C}^{N_g}}, and we continue to use \m {\hat {g}} to denote the Dantzig Selector.
+To simplify the exposition, we will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).
 
-We first establish a technical lemma that shows \m{\RM{supp}(\V{g})} has roughly cardinal \m{L}, which guarantees, at the heart of the argument, that \m{\V{g}} is almost-sparse
+We first establish a technical lemma that shows \m {\RM {supp} (\V {g})} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse
 
@@
 
-We apply DS to find \m{\hat{\V{g}}}, setting
-\Disp{
-\NC \gamma = \NC \R{2 \log N_g} \NR[+]
+We apply DS to find \m {\hat {\V {g}}}, setting
+\Disp {
+\NC \gamma = \NC \R {2 \log N_g} \NR[+]
 }
@@
 %
-\Disp{
-\NC \V{d} = \NC \hat{\V{g}} -\V{g} \NR[+]
+\Disp {
+\NC \V {d} = \NC \hat {\V {g}} -\V {g} \NR[+]
 }
@@
 \startitemize
-\item \m{\MC{A}} be the largest \m{s} position of \m{g}.
-\item \m{\MC{B}} be the largest \m{s} position of \m{d_{T(N_g) -\MC{A}}}.
-\item \m{\MC{C} =T \RB{ N_g } -\MC{A}}, i.e., the complementary index set of \m{\MC{A}}.
+\item \m {\MC {A}} be the largest \m {s} position of \m {g}.
+\item \m {\MC {B}} be the largest \m {s} position of \m {d_{T(N_g) -\MC {A}}}.
+\item \m {\MC {C} =T \RB {N_g} -\MC {A}}, i.e., the complementary index set of \m {\MC {A}}.
 \stopitemize
 
-Suppose \m{\M{A} \in \MB{M}_{\MB{K}} \RB{ N_1, N_2 }}.
-For brevity, let \m{\MC{T} \subset T \RB{ N_2 }}.
-Denote as \m{\M{A}_{\MC{T}}} the columns of \m{\M{A}} having indices in \m{\MC{T}}.
-Let \m{S:\; \MB{V}_{\MB{K}}(N) \mapsto \MB{V}_{\MB{K}}(N)}, \m{N \in \MB{N}}, be the sorting function for \m{x \in \MB{V}_{\MB{K}}(N))}, so that
-\Disp{
-\NC \Nm{S \RB{x} \DB{n_1}} \geq  \NC \Nm {S \RB{x} \DB{n_2}}, \NR[+]
+Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \RB {N_1, N_2 }}.
+For brevity, let \m {\MC {T} \subset T \RB {N_2 }}.
+Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
+Let \m {S:\; \MB {V}_{\MB {K}} (N) \mapsto \MB {V}_{\MB {K}} (N)}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} (N))}, so that
+\Disp {
+\NC \Nm {S \RB {x} \DB {n_1}} \geq  \NC \Nm {S \RB {x} \DB {n_2}}, \NR[+]
 \NC n_1 > \NC n_2,
-\quad n_1, n_2 \in T\RB{N} \NR
+\quad n_1, n_2 \in T\RB {N} \NR
 }
-Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \m{S} throughout this article.
+Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \m {S} throughout this article.
 For definiteness, we may compare the first component first, and the second, and so on.
@@
 {
-Let function \m{f:\; T\RB{N} \mapsto \MB{R}_+}, \m{N \in \MB{N}}, be given.
-For \m{x \in \MB{V}_{\MB{K}}(N)}, we say \m{x} is confined in sorted magnitude according to \m{f}, if
-\Disp{
-\NC \Nm {S(x) \DB{ n } } < \NC f (n),
-\quad n \in T\RB{N}. \NR
+Let function \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}, be given.
+For \m {x \in \MB {V}_{\MB {K}} (N)}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
+\Disp {
+\NC \Nm {S(x) \DB {n} } < \NC f (n),
+\quad n \in T\RB {N}. \NR
 }
@@
 {
-For \m{\V{x} \in \MB{V}_{\MB{K}}(N)}, we say \m{\V{x}} is almost-\m{s}-sparse with \m{\ell_1}-residue \m{R}, if
-\Disp{
-\NC \sum_{n=s+1}^N \Nm {S(\V{x}) (n)}
+For \m {\V {x} \in \MB {V}_{\MB {K}} (N)}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
+\Disp {
+\NC \sum_{n=s+1}^N \Nm {S(\V {x}) (n)}
 \leq \NC R. \NR
@@
 {
-Suppose \m{0 \leq \f \leq 2\pi k /N_H}, \m{k =0, \dots, N_H-1}.
-Let \m{\f} be given, and array response \m{\V{a} (\f)} defined as in ().
-Then \m{\V{a} (\f)} is almost-\m{L}-sparse with \m{\ell_1}-residue \m{R(N_H, L)} to be
+Suppose \m {0 \leq \f \leq 2\pi k /N_H}, \m {k =0, \dots, N_H-1}.
+Let \m {\f} be given, and array response \m {\V {a} (\f)} defined as in ().
+Then \m {\V {a} (\f)} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R(N_H, L)} to be
 %
-\Disp{
+\Disp {
 \NC R
-\leq \NC \F{1}{\pi} \log \F{N_H}{L}. \NR
+\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
 }
@@
 
-We show the lemma, which is the key to bounding the sparsity of \m{h}.
+We show the lemma, which is the key to bounding the sparsity of \m {h}.
 Recall the identity for Dirichlet kernel
 %
-\Disp{
+\Disp {
 \NC D (\f')
-:= \NC \Nm{ \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} } \NR
-\NC = \NC \F{\Nm {\sin (N_H \f'/2)}}{\Nm {\sin (\f' /2)}}, \NR[+]
+:= \NC \Nm { \sum_{n=0}^{N_H-1} \RM {e}^{i n \f'} } \NR
+\NC = \NC \F {\Nm {\sin (N_H \f'/2)}}{\Nm {\sin (\f' /2)}}, \NR[+]
 \NC \quad 0 \leq \NC  \f' \leq \pi \NR
@@
 %
-\Disp{
-\NC \sin x = \NC x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1 \NR
+\Disp {
+\NC \sin x = \NC x -\F {x^3}{6} + \MC {O} (x^5), \quad x \ll 1 \NR
 }
@@
 %
-\Disp{
-\NC \Nm{x - \F{x^3}{6}} \leq \NC \Nm{\sin x}, \NR[+]
+\Disp {
+\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}, \NR[+]
 \NC -\pi \leq \NC x \leq \pi \NR
@@
 %
-\Disp{
-\NC \Nm{ D (\f') }
-= \NC \F{48}{\Nm {\f'^2 -24} \Nm {\f'}}
+\Disp {
+\NC \Nm {D (\f') }
+= \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}}
 \quad 0 \leq \f' \leq \pi. \NR
@@
 
-Particularly, for arbitrary \m{\f}, find \m{k} so that
-\Disp{
-\NC \eta := \NC \f -\F{2\pi k}{N_H}, \NR[+]
+Particularly, for arbitrary \m {\f}, find \m {k} so that
+\Disp {
+\NC \eta := \NC \f -\F {2\pi k}{N_H}, \NR[+]
 \NC \Nm {\eta}
-\leq \NC \F{2\pi}{N_H}. \NR
+\leq \NC \F {2\pi}{N_H}. \NR
 }
@@
 Then observe
-\Disp{
-\NC \RB {\M{K}^\H \V{a}(\f)} \DB {k}
-=\NC \F{1}{N_H} D \RB{\f -\F{2 \pi k} {N_H}} \NR
+\Disp {
+\NC \RB {\M {K}^\H \V {a} (\f)} \DB {k}
+=\NC \F {1}{N_H} D \RB {\f -\F {2 \pi k} {N_H}} \NR
 }
 So we need only bound
-\Disp{
+\Disp {
 \NC R(\eta)
-:=\NC \F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB{ \eta +\F{2 \pi n_H} {N_H} } \NR
+:=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB { \eta +\F {2 \pi n_H} {N_H} } \NR
 }
 By the approximation of rectangle to integral,
-\Disp{
-\NC R(\eta) -\F{2\pi} {N_H}
-\leq \NC \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D(\f')} d \f' \NR
+\Disp {
+\NC R(\eta) -\F {2\pi} {N_H}
+\leq \NC \F {1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D(\f')} d \f' \NR
 }
-Bound \m{D} by above technique, meanwhile we notice \m{\f' <24}.
-\Disp{
+Bound \m {D} by above technique, meanwhile we notice \m {\f' <24}.
+\Disp {
 \NC R(\f)
-\leq \NC \F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
-+\F{2\pi} {N_H} \NR
-\NC = \NC \F{1}{\pi} \log \F{2\pi N_H}{L}
--\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
-+\F{2\pi} {N_H}
+\leq \NC \F {1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F {48}{(24 -\f'^2) \f'} d \f'
++\F {2\pi} {N_H} \NR
+\NC = \NC \F {1}{\pi} \log \F {2\pi N_H}{L}
+-\F {1}{N_H} \log \F {4\pi^2 -24} {L^2/N_H^2 -24}
++\F {2\pi} {N_H}
 }
-Notice the argument of log in the second term \m{<1}, and we drop that.
-Also drop \m{2\pi /N_H} since it is small.
-Furthermore the \m{2\pi} factor in log can be dropped too.
-\Disp{
+Notice the argument of log in the second term \m {<1}, and we drop that.
+Also drop \m {2\pi /N_H} since it is small.
+Furthermore the \m {2\pi} factor in log can be dropped too.
+\Disp {
 \NC R(\f)
-\leq \NC \F{1}{\pi} \log \F{N_H}{L}. \NR
+\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
 }
@@
 {
-Let \m{\f} and \m{\th} be uniformly, independently distributed in \m{[0,2\pi)}, and linear array response \m{\V{a}} defined as in ().
-Let \m{\V{g}} be defined as above.
-Then \m{\V{g}} is almost-\m{L}-sparse with \m{\ell_1}-residue \m{R(N_H, L)} to be
+Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)}, and linear array response \m {\V {a}} defined as in ().
+Let \m {\V {g}} be defined as above.
+Then \m {\V {g}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R(N_H, L)} to be
 %
-\Disp{
+\Disp {
 \NC R
-\leq \NC \F{L}{\pi^2} \RB{ \log \F{N_H}{L} }^2 \NR
+\leq \NC \F {L}{\pi^2} \RB { \log \F {N_H}{L} }^2 \NR
 }
@@
 {
-For \m{\MC{T}, \MC{T}' \subset \{1, \dots, N_p\}}, define the \m{s, s'}-restricted orthogonality constant \m{\tau_{s,s'} >0} to be the smallest such that
+For \m {\MC {T}, \MC {T}' \subset \{1, \dots, N_p\}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} >0} to be the smallest such that
 %
-\Disp{
-\NC \Nm {\IP {P_{\MC{T}} h, P_{\MC{T}'} h'}}
-\leq \NC \tau_{s, s'} \cdot \VNm { h } _2 \VNm {h'} _2 \NR
+\Disp {
+\NC \Nm {\IP {P_{\MC {T}} h, P_{\MC {T}'} h'}}
+\leq \NC \tau_{s, s'} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
 }
@@
 {
-Let \m{P} be given.
-Then \m{\tau_{s, s'}} is bounded in both direction as follows,
-\Disp{
-\NC \d_{s+s'} -\max (\{\d_s, \d_{s'}\})
+Let \m {P} be given.
+Then \m {\tau_{s, s'}} is bounded in both direction as follows,
+\Disp {
+\NC \d_{s+s'} -\max (\{\d_s, \d_{s'} \})
 \leq \NC \tau_{s, s'} \NR
@@
 
-Thus \m{\d_s}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
-We may well keep track of \m{\d_s} only.
+Thus \m {\d_s}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
+We may well keep track of \m {\d_s} only.
 
@@
 {
-Let \m{P} be i.i.d.\ Radmacher, as defined in Lemma ().
-Then \m{P} is RIP according to \m{\d} for at least probability
-\Disp{
-\NC 1 -2 \RB{ \F{12}{\d} }^s \exp \left[ - \RB{ \F{\epsilon^2}{4} -\F{\epsilon^3}{6} } \F{\d}{2} N_p \right] \NR
+Let \m {P} be i.i.d.\ Radmacher, as defined in Lemma ().
+Then \m {P} is RIP according to \m {\d} for at least probability
+\Disp {
+\NC 1 -2 \RB { \F {12}{\d} }^s \exp \left[ - \RB { \F {\epsilon^2}{4} -\F {\epsilon^3}{6} } \F {\d}{2} N_p \right] \NR
 }
@@
 {
-Let \m{\V{g}} and \m{\V{d}} be defined as above.
+Let \m {\V {g}} and \m {\V {d}} be defined as above.
 Then
 %
-\Disp{
-\NC \VNm {\V{d}_{\MC{C}}} _1
-\leq \NC \VNm {\V{d}_{\MC{A}}} _1 +2\VNm {\V{g}_{C}} _1 \NR
+\Disp {
+\NC \VNm {\V {d}_{\MC {C}}} _1
+\leq \NC \VNm {\V {d}_{\MC {A}}} _1 +2\VNm {\V {g}_{\MC {C}}} _1 \NR
 }
@@
 
-To show this, observe that with triangle inequality applied respectively on \m{\MC{A}} and \m{\MC{C}},
-\Disp{
-\NC \VNm {\V{g}} _1
--\VNm {\V{d}_{\MC{A}}} _1
-+\VNm {\V{d}_{\MC{C}}} _1
--\VNm {\V{g}_{\MC{C}}} _1
-\leq \NC \VNm {\V{g} +\V{d}} _1 \NR
+To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}},
+\Disp {
+\NC \VNm {\V {g}} _1
+-\VNm {\V {d}_{\MC {A}}} _1
++\VNm {\V {d}_{\MC {C}}} _1
+-\VNm {\V {g}_{\MC {C}}} _1
+\leq \NC \VNm {\V {g} +\V {d}} _1 \NR
 }
-In the first line, we recall \m{\V{g} =\V{g}_{\MC{A}}}.
-On the other hand, by construction that \m{\hat{g}} minimizes the \m{\ell_1}-norm,
-\Disp{
-\NC \VNm {\V{g} +\V{d}} _1
-=\NC \VNm {\hat{\V{g}}} _1 \NR
-\NC \leq \NC \VNm {\V{g}} _1 \NR
+In the first line, we recall \m {\V {g} =\V {g}_{\MC {A}}}.
+On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
+\Disp {
+\NC \VNm {\V {g} +\V {d}} _1
+=\NC \VNm {\hat {\V {g}}} _1 \NR
+\NC \leq \NC \VNm {\V {g}} _1 \NR
 }
@@
 {
-Let \m{\V{z}} and \m{\M{P}} be defined as above.
+Let \m {\V {z}} and \m {\M {P}} be defined as above.
 Then
 %
-\Disp{
-\NC \Nm {\IP{ \V{z}, \M{P}(:, n_g) }}
-\leq \NC  2 \R{\log N_g},
+\Disp {
+\NC \Nm {\IP { \V {z}, \M {P} (:, n_g) }}
+\leq \NC  2 \R {\log N_g},
 \quad n_g =1, \dots, N_g. \NR
@@
 
-This only depends on the fact that \m{\M{P}(:, n_g)} has unity \m{\ell_2}-norm, and on the randomness of \m{\V{z}}.
+This only depends on the fact that \m {\M {P} (:, n_g)} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
 
-Recall the following bound for \m{Q} function
-\Disp{
+Recall the following bound for \m {Q} function
+\Disp {
 \NC Q(x)
-\leq \NC \F{1}{2} \RM{e}^{-x^2/2} \NR
+\leq \NC \F {1}{2} \RM {e}^{-x^2/2} \NR
 }
-Particularly, for \m{x =\R{2 \log N_g}}, according to CLT,
-\Disp{
-\NC Q(\R{2 \log N_g})
-=\NC \F{1}{N_g}. \NR
+Particularly, for \m {x =\R {2 \log N_g}}, according to CLT,
+\Disp {
+\NC Q(\R {2 \log N_g})
+=\NC \F {1}{N_g}. \NR
 }
@@
 {
-Let \m{\V{d}} and \m{\M{P}} be defined as above, and \m{\M{P}} satisfies RIP as in ().
+Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in ().
 %
-\Disp{
-\NC \VNm {\M{P}^\H \M{P} \V{d}} _\infty
-\leq \NC  4 \R{\log N_g},
+\Disp {
+\NC \VNm {\M {P}^\H \M {P} \V {d}} _\infty
+\leq \NC  4 \R {\log N_g},
 \quad n_g =1, \dots, N_g. \NR
@@
 %
-\Disp{
-\NC \IP{ \V{z} -(\V{y} -\M{P} \hat{\V{g}}), \M{P} (:,n_y) }
-= \NC \IP{ \M{P} \hat{\V{g}} -\M{P} \V{g}, \M{P} (:,n_y) } \NR
-\NC = \NC \IP{ \M{P} \V{d}, \M{P} (:,n_y) } \NR
+\Disp {
+\NC \IP { \V {z} -(\V {y} -\M {P} \hat {\V {g}}), \M {P} (:,n_y) }
+= \NC \IP { \M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} (:,n_y) } \NR
+\NC = \NC \IP { \M {P} \V {d}, \M {P} (:,n_y) } \NR
 }
@@
 By construction
-\Disp{
-\NC \VNm { \M{P} (:,n_y)^\H (\V{y} -\M{P} \hat{\V{g}}) } 
-\leq \NC \VNm { \M{P}^\H (\V{y} -\M{P} \hat{\V{g}}) } _\infty \NR
-\NC \leq \NC 2\R{\log N_g} \NR
+\Disp {
+\NC \VNm { \M {P} (:,n_y)^\H (\V {y} -\M {P} \hat {\V {g}}) } 
+\leq \NC \VNm { \M {P}^\H (\V {y} -\M {P} \hat {\V {g}}) } _\infty \NR
+\NC \leq \NC 2\R {\log N_g} \NR
 }
 By triangle inequality, together with Lemma (), we have
-\Disp{
-\NC \VNm {\M{P} (:,n_y)^\H \M{P} \V{d}} 
-\leq \NC \VNm {\IP{ \V{z}, \M{P} (:,n_y) }}  +\IP{ \V{y} -\M{P} \hat{\V{g}}, \M{P} (:,n_y) } \NR
-\NC \leq \NC 2 \R{\log N_g} +2 \R{\log N_g} \NR
+\Disp {
+\NC \VNm {\M {P} (:,n_y)^\H \M {P} \V {d}} 
+\leq \NC \VNm {\IP { \V {z}, \M {P} (:,n_y) }}  +\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} (:,n_y) } \NR
+\NC \leq \NC 2 \R {\log N_g} +2 \R {\log N_g} \NR
 }
 which implies
-\Disp{
-\NC \VNm {\M{P}^\H \M{P} \V{d}} _\infty
-\leq \NC 4 \R{\log N_g}. \NR
+\Disp {
+\NC \VNm {\M {P}^\H \M {P} \V {d}} _\infty
+\leq \NC 4 \R {\log N_g}. \NR
 }
@@
 {
-Let \m{\V{d}} and \m{\M{P}} be defined as above, and \m{\M{P}} satisfies RIP as in () with respect to \m{\d_s}.
+Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in () with respect to \m {\d_s}.
 %
-\Disp{
-\NC \VNm {\V{d}_{\MC{AB}}} _2
-\leq \NC \F{1}{1-\d_{2s}} \VNm {P_{\MC{A}\MC{B}}^\Tr P d} _2 +\F{\d_{3s}}{(1-\d_{2s}) \R{s}} \VNm {d_{C}} _1 \NR
+\Disp {
+\NC \VNm {\V {d}_{\MC {AB}}} _2
+\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{(1-\d_{2s}) \R {s}} \VNm {d_{C}} _1 \NR
 }
@@
 {
-Let \m{\V{d}} be defined as above.
+Let \m {\V {d}} be defined as above.
 Then
 %
-\Disp{
-\NC \VNm {\V{d}} _2^2
-\leq \NC \VNm {\V{d}_{\MC{A}\MC{B}}} _2^2 +\F{1}{s} \VNm {\V{d}_{\MC{C}}} _1^2 \NR
+\Disp {
+\NC \VNm {\V {d}} _2^2
+\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
 }
@@
 We can now formulate and prove the main bound of ours.
-Here, we use \m{s=L} as the sparsity threshold.
+Here, we use \m {s=L} as the sparsity threshold.
 
@@
 {
-Let \m{\V{y}}, \m{\M{P}}, \m{\V{g}}, \m{\hat{\V{g}}}, \m{\V{d}} be defined as above.
+Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
 Then
-\Disp{
-\NC \VNm {\V{d}} _2
-\leq \NC \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
+\Disp {
+\NC \VNm {\V {d}} _2
+\leq \NC \F {4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
 }
@@
 The first quantity we want to bound away is
-\Disp{
-\NC \VNm {\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}} _2
-\leq \NC \VNm {\M{P}^\Tr \M{P} \V{d}} _2 \NR
-\NC \leq \NC \R{N_g} \VNm {\M{P}^\Tr \M{P} \V{d}} _\infty \NR
-\NC \leq \NC 4 \R{ N_g \log N_g } \NR
+\Disp {
+\NC \VNm {\M {P}_{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
+\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
+\NC \leq \NC \R {N_g} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
+\NC \leq \NC 4 \R {N_g \log N_g} \NR
 }
 Thus, by virtue of Lemma (),
-\Disp{
-\NC \VNm { \V{d}_{A} } _1
-\leq \NC \R{L} \VNm { \V{d}_{A} } _2 \NR
-\NC \leq \NC \R{L} \VNm { \V{d}_{\MC{AB}} } _2 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V{d}_{\MC{C}} } _1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} \NR
+\Disp {
+\NC \VNm { \V {d}_{A} } _1
+\leq \NC \R {L} \VNm { \V {d}_{A} } _2 \NR
+\NC \leq \NC \R {L} \VNm { \V {d}_{\MC {AB}} } _2 \NR
+\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1 +\F {4} {1-\d_{2L}} \R {L N_g \log N_g} \NR
 }
 
-As the next step, we must eliminate \m{\VNm {d_{\MC{A}}} _1} in rhs of Lemma ().
-\Disp{
-\NC \VNm { \V{d}_{\MC{C}} } _1
-\leq \NC \VNm { \V{d}_{\MC{A}} } _1 +2 \VNm { \V{g}_{\MC{C}} } _1 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V{d}_{\MC{C}} } _1
-+2 \VNm { \V{g}_{\MC{C}} } _1
-+\F {4} {1-\d_{2L}} \R{L N_g \log N_g} \NR
+As the next step, we must eliminate \m {\VNm {d_{\MC {A}}} _1} in rhs of Lemma ().
+\Disp {
+\NC \VNm { \V {d}_{\MC {C}} } _1
+\leq \NC \VNm { \V {d}_{\MC {A}} } _1 +2 \VNm { \V {g}_{\MC {C}} } _1 \NR
+\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1
++2 \VNm { \V {g}_{\MC {C}} } _1
++\F {4} {1-\d_{2L}} \R {L N_g \log N_g} \NR
 }
 Or,
-\Disp{
-\NC \VNm { \V{d}_{\MC{C}} } _1
-\leq \NC 2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V{g}_{\MC{C}} } _1
-+\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g} \NR
+\Disp {
+\NC \VNm { \V {d}_{\MC {C}} } _1
+\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g}_{\MC {C}} } _1
++\F {4} {1-\d_{2L} -\d_{3L}} \R {L N_g \log N_g} \NR
 }
 
-We are ready to bound \m{\VNm { d } _2^2}.
+We are ready to bound \m {\VNm {d} _2^2}.
 Using Lemma () again, we have
-\Disp{
-\NC \VNm { \V{d} } _2^2
-\leq \NC \VNm {\V{d}_{\MC{A}\MC{B}}} _2^2 +\F{1}{L} \VNm {\V{d}_{\MC{C}}} _1^2 \NR
-\NC \leq \NC  \RB{ \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} } \VNm {\V{d}_{\MC{C}}} _1^2
-+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \VNm {\V{d}_{\MC{C}}} _1 \NR
-\NC \NC \quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g \NR
+\Disp {
+\NC \VNm { \V {d} } _2^2
+\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
+\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F {1}{L} } \VNm {\V {d}_{\MC {C}}} _1^2
++\F {8 \d_{3L}} {L (1-\d_{2L})^2} \R {N_g \log N_g} \VNm {\V {d}_{\MC {C}}} _1 \NR
+\NC \NC \quad +\F {16}{(1-\d_{2L})^2} N_g \log N_g \NR
 }
-Finally, plug in the bound for \m{\VNm {\V{d}_{\MC{C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m{\VNm {\V{d}_{\MC{C}}} _1}.
+Finally, plug in the bound for \m {\VNm {\V {d}_{\MC {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d}_{\MC {C}}} _1}.
 There are several dozens of terms if we expand all.
 but for simplicity, we keep only the leading term under the approximation
-\Disp{
+\Disp {
 \NC 1 \ll \NC L \NR
@@
 }
-And expand to the first order expressions containing \m{\d_{2L}} or \m{\d_{3L}} in the denominator using
-\Disp{
+And expand to the first order expressions containing \m {\d_{2L}} or \m {\d_{3L}} in the denominator using
+\Disp {
 \NC \d_{2L} <\NC \d_{3L} \ll 1. \NR
@@
 Then
-\Disp{
-\NC \VNm {\V{d}} _2^2
-\leq \NC \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
+\Disp {
+\NC \VNm {\V {d}} _2^2
+\leq \NC \F {4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
 }

### 2019-03-05 ongoing/report/4_simulation.tex
Reformatting source

@@
 
-As of now, we have transformed the sparse-recovery problem of complex matrix \(H\) to complex vector \(h\), and finally to real vector \(\MC{R}(h)\).
+As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} (h)}.
 But it is not the end.
-In fact, Cand\`es and Tao's analysis in ``\(\ell_1\)-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
+In fact, Cand\`es and Tao's analysis in ``\m {\ell_1}-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
 Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
 Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
-Thus our proposed algorithm is not a corollary of the DS program outlines in ``\(\ell_1\)-MAGIC''.
+Thus our proposed algorithm is not a corollary of the DS program outlines in ``\m {\ell_1}-MAGIC''.
 
@@
 
-Since our setting is slightly different from ``\(\ell_1\)-MAGIC'', for completeness of exposition we write down derivation of the dual problem from the primal problem, as follows.
-Recapitulate that, as we explained in the above, DS involves the calculation of \(\ell_1\)-1 norm.
+Since our setting is slightly different from ``\m {\ell_1}-MAGIC'', for completeness of exposition we write down derivation of the dual problem from the primal problem, as follows.
+Recapitulate that, as we explained in the above, DS involves the calculation of \m {\ell_1}-1 norm.
 This, for real vectors, can be transformed into a linear program (LP).
 But in the complex case, that becomes a quadratic expression of the real and imaginary part of the vector, and is no longer equivalent to an LP.
-Still, the comparison arising from primal-dual problem is not easily done in complex numbers, and we cast it into a real \(\ell_1\)-1 norm problem.
+Still, the comparison arising from primal-dual problem is not easily done in complex numbers, and we cast it into a real \m {\ell_1}-1 norm problem.
 Afterwards we will further transform the SOCP to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
@@
 {
-For \(x \in \MB{V}(M)\), we say \(\MC{R}(x)\) is the real representation of \(x\), defined by
+For \m {x \in \MB {V} (M)}, we say \m {\MC {R} (x)} is the real representation of \m {x}, defined by
 %
-\Disp{
-\MC{R}(x) \in \NC \MB{V}(2M) \NR
-\MC{R}(x)(m) =
-\NC \begin{cases}
-\MF{Re}(\MC{R}(x)(m)), \NC m =2m' \NR[+]
-\MF{Im}(\MC{R}(x)(m)), \NC m =2m'+1
-\end{cases} \NR[+]
-m' =\NC  1, \dots, M \NT
+\Disp {
+\NC \MC {R} (x) \in \NC \MB {V} (2M) \NR[+]
+\NC \MC {R} (x) \DB {m} =
+\NC \startcases
+\MF {Re} (\MC {R} (x)\DB {m}), \quad \MC m =2m' \NR
+\MF {Im} (\MC {R} (x)\DB {m}), \quad \MC m =2m'+1 \NR
+\stopcases \NR[+]
+\NC m' \NC =  1, \dots, M \NR
 }
@@
 {
-For \(A \in \MB{M}_{\MB{C}} (M_1, M_2)\), we say \(\MC{R}(A)\) is the real representation of \(A\), defined by
+For \m {A \in \MB {M}_{\MB {C}} (M_1, M_2)}, we say \m {\MC {R} (A)} is the real representation of \m {A}, defined by
 %
-\Disp{
-A \in \NC \MB{V}_{\MB{R}} (2M_1, 2M_2) \NR
-A (m_1,m_2) =
-\NC \begin{cases}
-\MF{Re}(A (m_1,m_2)), \NC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR[+]
-\MF{Im}(A (m_1,m_2)), \NC m_1 =2m_1',\; m_2 =2m_2'-1  \NR[+]
--\MF{Im}(A (m_1,m_2)), \NC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR[+]
-\MF{Re}(A (m_1,m_2)), \NC m_1 =2m_1',\; m_2 =2m_2'  \NR[+]
-\end{cases} \NR[+]
-m_1' = \NC 1, \dots, m_1 \NR
-m_2' = \NC 1, \dots, m_2 \NT
+\Disp {
+\NC A \in \NC \MB {V}_{\MB {R}} (2M_1, 2M_2) \NR[+]
+\NC A (m_1,m_2) =
+\NC \startcases
+\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR
+\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'-1  \NR
+-\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR
+\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'  \NR
+\stopcases \NR[+]
+\NC m_1' \NC = 1, \dots, m_1 \NR[+]
+\NC m_2' \NC = 1, \dots, m_2 \NR
 }
@@
 %
-\Disp{
-\V{\T{y}}
-=\NC \MC{R}(y)
-\in \MB{V}(N_h) \NR[+]
-\V{\T{g}}
-=\NC \MC{R}(g)
-\in \MB{V}(N_h) \NR[+]
-\M{\T{P}}
-=\NC \MC{R}(\M{P})
-\in \MB{M}_{\MB{C}} (2 N_y^2, 2 N_h^2)
+\Disp {
+\NC \V {\T {y}}
+\NC = \MC {R} (y)
+\in \MB {V} (N_h) \NR[+]
+\NC \V {\T {g}}
+\NC = \MC {R} (g)
+\in \MB {V} (N_h) \NR[+]
+\NC \M {\T {P}}
+\NC = \MC {R} (\M {P})
+\in \MB {M}_{\MB {C}} (2 N_y^2, 2 N_h^2) \NR
 }
@@
 %
-\Disp{
-\V{\T{y}} =\M{\T{P}} \V{\T{g}} +\V{\T{z}}
+\Disp {
+\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
 }
@@
 %
-\Disp{
-\V{\T{z}}
-=\MC{R}(\V{z}) \in \MB{V}(N_y)
+\Disp {
+\NC \V {\T {z}}
+\NC = \MC {R} (\V {z}) \in \MB {V} (N_y) \NR
 }
@@
 
-Finally, introduce these indicator matrices to identify the place where we want to take \(\ell_2\)-norm.
+Finally, introduce the following matrices to identify the components where we want to take \m {\ell_2}-norm, in the manner similar to an indicator function.
 
 %
-\Disp{
-\M{I}_{n_y}^{(y)} \in \NC \MB{M}_{\MB{R}} (2N_y^2, 2N_y^2) \NR
-\M{I}_{n_y}^{(y)}(n_y')
-=\NC \begin{cases}
-1, \NC n_y' =2n_y \NR[+]
-1, \NC n_y' =2n_y +1 \NR[+]
-0, \NC \RM{otherwise}
-\end{cases} \NR[+]
-\M{I}_{n_h}^{(h)} \in \NC \MB{M}_{\MB{R}} (2N_h^2, 2N_h^2) \NR
-\M{I}_{n_h}^{(h)}(n_h')
-=\NC \begin{cases}
-1, \NC n_h' =2n_h \NR[+]
-1, \NC n_h' =2n_h +1 \NR[+]
-0, \NC \RM{otherwise}
-\end{cases} \NR[+]
-n_y =\NC 1, \dots, N_y \NR
-n_h =\NC 1, \dots, N_h \NT
+\Disp {
+\NC \M {I}_{n_y}^{(y)} \in \NC \MB {M}_{\MB {R}} (2N_y^2, 2N_y^2) \NR[+]
+\NC \M {I}_{n_y}^{(y)} (n_y')
+\NC =
+\startcases
+1, \quad \MC n_y' =2n_y \NR[+]
+1, \quad \MC n_y' =2n_y +1 \NR[+]
+0, \quad \NC otherwise
+\stopcases \NR[+]
+\NC \M {I}_{n_h}^{(h)} \in \NC \MB {M}_{\MB {R}} (2N_h^2, 2N_h^2) \NR[+]
+\NC \M {I}_{n_h}^{(h)} (n_h')
+\NC =
+\startcases
+1, \quad \MC n_h' =2n_h \NR[+]
+1, \quad \MC n_h' =2n_h +1 \NR[+]
+0, \NC otherwise
+\stopcases \NR[+]
+\NC n_y \NC = 1, \dots, N_y \NR[+]
+\NC n_h \NC = 1, \dots, N_h \NR
 }
@@
 
-If we introduce vector \(\V{m}\) to denote the entrywise complex modulus, we see that Program () now take the form
+If we introduce vector \m {\V {m}} to denote the entrywise complex modulus, we see that Program () now take the form
 
@@
 {
-   Given are \(\T{\M{P}}, \T{\V{y}}, \gamma\).
-Find \(\T{\V{g}}\) with
+Given are \m {\T {\M {P}}, \T {\V {y}}, \gamma}.
+Find \m {\T {\V {g}}} with
 %
-\Disp{
-\min_{\T{\V{g}}, \V{m}} \quad
-\NC \IP{ \V{1}, \V{m} } \NR
-\RM{subject}\; \RM{to} \quad
-\NC \begin{cases}
-\| \M{I}_{n_h}^{(h)} \T{\V{g}} \|_2
-\leq \IP{ \V{y}_{n_h}, \V{m} } \NR[+]
-\| \M{I}_{n_y}^{(y)} \T{\M{P}}^\H ( \T{\M{P}} \T{\V{g}} -\T{\V{y}} ) \|_2
-\leq \gamma  \NR[+]
-\end{cases}
+\Disp {
+\NC \T {\V {g}}
+\NC = \startcases
+\NC \Min {\T {\V {g}}, \V {m}} \quad
+\MC \IP { \V {1}, \V {m} } \NR
+\NC \RM {subject} \; \RM {to} \quad
+\MC \VNm { \M {I}_{n_h}^{(h)} \T {\V {g}} }_2
+\leq \IP { \V {y}_{n_h}, \V {m} } \NR
+\NC \MC \VNm { \M {I}_{n_y}^{(y)} \T {\M {P}}^\H \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } }_2
+\leq \gamma \NR
+\stopcases \NR
 }
 %
-where \(\V{1}\) is the all-1 vector.
+where \m {\V {1}} is the all-1 vector.
 }
@@
 Of course it is not the only way to do this.
-We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.11 as a standard reference, and ``\(\ell_1\)-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.
+We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.11 as a standard reference, and ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.
 
 To clarify notation and for complentess of exposition, we derive the dual problem here.
-Start with the Lagrangian \(\MC{L}\), where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \(\ell_2\)-norm constraint.
+Start with the Lagrangian \m {\MC {L}}, where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \m {\ell_2}-norm constraint.
 
 %
-\Disp{
-\NC \NC \MC{L}(\V{m}, \T{\V{g}}, \V{\mu}^{(h)}, \V{\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NR
-\NC =\NC \IP{\V{1}, \V{m}}
-+\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M{g}}} -\lambda^{(h)} \IP {\V{y}_{n_h}, \V{m}}} \NR
-\NC \quad \NC  +\sum_{n_y} \SB{ \IP{ \V{\mu}^{(h)}, \M{I}_{n_y}^{(y)} \T{\M{P}}^\H ( \T{\M{P}} \T{\V{g}} -\T{\V{y}} ) } -\lambda^{(h)} \gamma} \NR[+]
+\Disp {
+\NC \NC \MC {L} (\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NR[+]
+\NC \NC = \IP {\V {1}, \V {m}}
++\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M {g}}} -\lambda^{(h)} \IP {\V {y}_{n_h}, \V {m}}} \NR[+]
+\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\H ( \T {\M {P}} \T {\V {g}} -\T {\V {y}} ) } -\lambda^{(h)} \gamma} \NR[+]
 }

### 2019-03-05 ongoing/report/5_conclusion.tex
Reformatting source

--- 2019-01-08 ongoing/report/sec_5_back_matter.tex
@@
-\subsection{Conclusion}
+\startchapter [title={Conclusion}]
 
@@
 Simulation is done, and DS's performance is compared to OMP.
-{ \color{red} (To be done) }
+\color[red]{(To be done)}
 
@@
 
-\subsection{References}
-
-References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.
-
-\begin{enumerate}
-
-\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6
-
-\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.\ 5.
-
-\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}
-
-\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.\ 98, No.\ 6.
-
-\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
-
-\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
-
-\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.
-
-\item S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-
-\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.2.
-
-\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
-
-\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-
-\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' \textit{IEEE Transactions on Information Theory}, Vol.52, No.12.
-
-\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
-
-\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', \textit{IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.
-
-\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', \textit{IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.
-
-\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.\ 35, No.\ 6.
-
-\item Z Gao, L Dai, Z Wang, and S Chen (2015).
-``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.
-
-\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', \textit{IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.
-
-\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', \textit{IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.
-
-\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', \textit{IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.
-
-\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \textit{2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.
-
-\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', \textit{IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.
-
-\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
-Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
-
-\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
-
-\end{enumerate}
+\stopchapter

### 2019-03-05 ongoing/report/references.tex
Reformatting source

\starttitle [title={References}]

References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.

\startitemize[n]

\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', {\it IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6

\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', {\it IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.\ 5.

\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' {\it IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}

\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.\ 98, No.\ 6.

\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.

\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', {\it Constructive Approximation} {\bf 28}: 253–263

\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', {\it IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.

\item S Boyd, L Vandenberghe (2004), {\it Convex Optimization}. Cambridge U.\ Press.

\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' {\it IEEE Transactions on Information Theory}, Vol.52, No.2.

\item E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \type{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.

\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', {\it IEEE Transactions on Information Theory}, Vol.51, No.12.

\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' {\it IEEE Transactions on Information Theory}, Vol.52, No.12.

\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', {\it The Annals of Statistics}, Vol.35, No.6.

\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', {\it IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.

\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', {\it IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.

\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', {\it The Annals of Statistics}, Vol.\ 35, No.\ 6.

\item Z Gao, L Dai, Z Wang, and S Chen (2015). ``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', {\it IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.

\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', {\it IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.

\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', {\it IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.

\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', {\it IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.

\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', {\it 2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.

\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', {\it IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.

\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep. Retrieved from: \type{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}

\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', {\it IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.

\stopitemize

\stoptitle

### 2019-03-06 ongoing/report/1_introduction.tex
Correct delimiters usage

@@
 
+First of all, round brackets \m {\RB {\cdot}} are used purely for precedence of , and \m {\SB {\cdot}} exclusively for function arguments, for better clarity.
+
 \m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
-The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} (a)} and \m {\MF {Im} (a)}, respectively, thus \m {a =\MF {Re} (a) + i \MF {Im} (a)}
+The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} \SB {a}} and \m {\MF {Im} \SB {a}}, respectively, thus \m {a =\MF {Re} \SB {a} + i \MF {Im} \SB {a}}
 
@@
 We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
-Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} (N)}.
-We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} (M,N)}, and its role as linear transformation is understood.
+Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} \SB {N}}.
+We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} \SB {M,N}}, and its role as linear transformation is understood.
 Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
-Slightly abusing notation, we denote as \m {\V {a} (n)} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} (m,n)} the \m {(m,n)}-entry of \m {\V {A}}
+Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {\DB {m,n}}-entry of \m {\V {A}}
 Particularly, \m {\V {u}_n} is the \m {n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
@@
 
-Denote as \m {\MB {P} (X)} the probability, and \m {\MB {E} (X)} the expectation.
+Denote as \m {\MB {P} \SB {X}} the probability, and \m {\MB {E} \SB {X}} the expectation.
 Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.
-
-Round brackets \m {\RB {\cdot}} are used purely for precedence of , and \m {\SB {\cdot}} exclusively for function arguments.
 
@@
 The figure of merit of a MIMO system is usually considered to be the channel capacity.
-In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det (I +\RM {SNR})}, but that knowledge is hardly always available.
+In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det \RB {I +\RM {SNR}}}, but that knowledge is hardly always available.
 What makes things more difficult is the case that \m {\M {H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
@@
 Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det (I +\RM {SNR})}.
+Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det \RB {I +\RM {SNR}}}.
 
@@
 
-We will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} (N_m)}.
+We will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} \SB {N_m}}.
 
@@
 {
-Suppose \m {\M {A} \in \MB {M}_{\MB {K}} (N_m, N_p)}.
+Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
 Let \m {\MC {T} \subset T \RB {N_p}}.
@@
 {
-\m {x \in \MB {V}_{\MB {K}} (N_m)} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
+\m {x \in \MB {V}_{\MB {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
 %
 \Disp { 
-\NC x_{T(N) -\MC {A}}
+\NC x_{T\SB {N} -\MC {A}}
 =\NC \V {0} \NR
@@
 {
-Let \m {P \in \MB {M}_\MB {K} (N_m, N_p)} and \m {y \in \MB {V}_\MB {K} (N_p)} be given.
-Find \m {h \in \MB {V}_\MB {K} (N_p)} with
+Let \m {P \in \MB {M}_\MB {K} \SB {N_m, N_p}} and \m {y \in \MB {V}_\MB {K} \SB {N_p}} be given.
+Find \m {h \in \MB {V}_\MB {K} \SB {N_p}} with
 %
@@
 {
-Consider \m {P \in \MB {M}_{\MB {K}} (N_m, N_p)}, with unity-\m {\ell_2}-norm columns.
-For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} (N_p)}, for all \m {\MC {T} \subset T(N_m)} with \m {\#\{\MC {T} \} \leq s},
+Consider \m {P \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
+For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N_p}}, for all \m {\MC {T} \subset T\SB {N_m}} with \m {\#\{\MC {T} \} \leq s},
 %
 \Disp {
-\NC \NC (1-\d_s) \VNm {V {x}}^2 \NR
+\NC \NC \RB {1-\d_s} \VNm {V {x}}^2 \NR
 \NC \leq \NC \VNm {P_{\MC {T}} \V {x}} _2^2 \NR
-\NC \leq \NC (1+\d_s) \VNm {\V {x}} _2^2 \NR[+]
+\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
 }
@@
 {
-Let \m {\M {P} \in \MB {V}_\MB {R} (N_m, N_p)} and \m {\V {y} \in \MB {V}_\MB {R} (N_m)} be given.
-Find \m {\V {h} \in \MB {V}_\MB {R} (N_m)} by
+Let \m {\M {P} \in \MB {V}_\MB {R} \SB {N_m, N_p}} and \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}} be given.
+Find \m {\V {h} \in \MB {V}_\MB {R} \SB {N_m}} by
 %
@@
 \NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
-\NC \RM {subject} \; \RM {to} \quad \MC \VNm {\M {P}^\H (\M {P} \V {h} -\V {y})} _\infty \leq \gamma \NR
+\NC \RM {subject} \; \RM {to} \quad \MC \VNm {\M {P}^\H \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \gamma \NR
 \stopcases \NR
@@
 {
-Let each entry of random matrix \m {P \in \MB {M}_\MB {K} (N_m, N_p)} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
+Let each entry of random matrix \m {P \in \MB {M}_\MB {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
 Then, with \m {0 <\epsilon <1},
@@
 \Disp {
-\NC \NC \MB {P} ( \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2) \NR
-\NC \leq \NC 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) ) \NR
+\NC \NC \MB {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2} \NR
+\NC \leq \NC 2 \exp \SB {-n \RB {\epsilon^2/4 -\epsilon^3/6} } \NR
 }
@@
 
-To explain the idea, consider a linear time-invariant channel that \m {y(t) =(x \star h)(t) + z(t)}, where \m {h(t)} is the channel's impulse response, \m {y(t)} is the output, and, for each time index, \m {x(t)} is i.i.d.\ Rademacher, and \m {z(t)} is i.i.d.\ Gaussian.
+To explain the idea, consider a linear time-invariant channel that \m {y\SB {t} =\RB {x \star h} \SB {t} + z\SB {t}}, where \m {h\SB {t}} is the channel's impulse response, \m {y\SB {t}} is the output, and, for each time index, \m {x\SB {t}} is i.i.d.\ Rademacher, and \m {z\SB {t}} is i.i.d.\ Gaussian.
 Simply assuming \m {h} has sparse support, and let the convolution with \m {x} be expressed by a matrix \m {X}, \m {X} is a Toeplitz matrix, so that \m {y =X h +z}.
@@
 
-Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} (N_p)}, \m {\V {h} \in \MB {V}_\MB {K} (N_s)}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
+Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} \SB {N_p}}, \m {\V {h} \in \MB {V}_\MB {K} \SB {N_s}}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
 If
@@
 \Disp {
-\NC M \geq 16s \log (N/\d) \NR
+\NC M \geq 16s \log \RB {N/\d} \NR
 }
@@
 {
-Define \m {\RM {vec} (\M {A}) \in \MB {K}^{NM}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} (N,M)}.
+Define \m {\RM {vec} \SB {\M {A}} \in \MB {K}^{NM}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N,M}}.
 }
@@
 {
-For \m {\RM {vec} (A) \in \MB {M}_{\MB {K}} (N,M)} and \m {\RM {vec} (A) \in \MB {M}_{\MB {K}} (N,M)}
-Define the Kronecker product \m {\RM {vec} (A) \in \MB {K}^{nm}} 
+For \m {\RM {vec} \SB {A} \in \MB {M}_{\MB {K}} \SB {N,M}} and \m {\RM {vec} \SB {A} \in \MB {M}_{\MB {K}} \SB {N,M}}
+Define the Kronecker product \m {\RM {vec} \SB {A} \in \MB {K}^{nm}} 
 }
@@
 \Disp {
-\NC \RM {vec} (Y)
-=\big[ (F^\H) \otimes W \big] \RM {vec} (\M {H}) \NR
+\NC \RM {vec} \SB {Y}
+=\big[ \RB {F^\H} \otimes W \big] \RM {vec} \RB {\M {H}} \NR
 }

### 2019-03-06 ongoing/report/3_theorems_and_proofs.tex
Correct delimiters usage

@@
 
-We first establish a technical lemma that shows \m {\RM {supp} (\V {g})} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse
+We first establish a technical lemma that shows \m {\RM {supp} \SB {\V {g}}} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse
 
@@
 \item \m {\MC {A}} be the largest \m {s} position of \m {g}.
-\item \m {\MC {B}} be the largest \m {s} position of \m {d_{T(N_g) -\MC {A}}}.
+\item \m {\MC {B}} be the largest \m {s} position of \m {d_{T\SB {N_g} -\MC {A}}}.
 \item \m {\MC {C} =T \RB {N_g} -\MC {A}}, i.e., the complementary index set of \m {\MC {A}}.
@@
 Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
-Let \m {S:\; \MB {V}_{\MB {K}} (N) \mapsto \MB {V}_{\MB {K}} (N)}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} (N))}, so that
+Let \m {S:\; \MB {V}_{\MB {K}} \SB {N} \mapsto \MB {V}_{\MB {K}} \SB {N}}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} \SB {N})}, so that
 \Disp {
@@
 Let function \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}, be given.
-For \m {x \in \MB {V}_{\MB {K}} (N)}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
+For \m {x \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
 \Disp {
-\NC \Nm {S(x) \DB {n} } < \NC f (n),
+\NC \Nm {S\SB {x} \DB {n} } < \NC f \SB {n},
 \quad n \in T\RB {N}. \NR
@@
 {
-For \m {\V {x} \in \MB {V}_{\MB {K}} (N)}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
+For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
 \Disp {
-\NC \sum_{n=s+1}^N \Nm {S(\V {x}) (n)}
+\NC \sum_{n=s+1}^N \Nm {S\SB {\V {x}} \SB {n}}
 \leq \NC R. \NR
@@
 Suppose \m {0 \leq \f \leq 2\pi k /N_H}, \m {k =0, \dots, N_H-1}.
-Let \m {\f} be given, and array response \m {\V {a} (\f)} defined as in ().
-Then \m {\V {a} (\f)} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R(N_H, L)} to be
+Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
+Then \m {\V {a} \SB {\f}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
 %
@@
 \Disp {
-\NC D (\f')
+\NC D \SB {\f'}
 := \NC \Nm { \sum_{n=0}^{N_H-1} \RM {e}^{i n \f'} } \NR
-\NC = \NC \F {\Nm {\sin (N_H \f'/2)}}{\Nm {\sin (\f' /2)}}, \NR[+]
+\NC = \NC \F {\Nm {\sin \SB {N_H \f'/2}}}{\Nm {\sin \SB {\f' /2}}}, \NR[+]
 \NC \quad 0 \leq \NC  \f' \leq \pi \NR
@@
 \Disp {
-\NC \sin x = \NC x -\F {x^3}{6} + \MC {O} (x^5), \quad x \ll 1 \NR
+\NC \sin x = \NC x -\F {x^3}{6} + \MC {O} \SB {x^5}, \quad x \ll 1 \NR
 }
@@
 \Disp {
-\NC \Nm {D (\f') }
+\NC \Nm {D \SB {\f'} }
 = \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}}
@@
 \Disp {
-\NC \RB {\M {K}^\H \V {a} (\f)} \DB {k}
+\NC \RB {\M {K}^\H \V {a} \SB {\f}} \DB {k}
 =\NC \F {1}{N_H} D \RB {\f -\F {2 \pi k} {N_H}} \NR
@@
 \Disp {
-\NC R(\eta)
+\NC R\SB {\eta}
 :=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB { \eta +\F {2 \pi n_H} {N_H} } \NR
@@
 \Disp {
-\NC R(\eta) -\F {2\pi} {N_H}
-\leq \NC \F {1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D(\f')} d \f' \NR
+\NC R\SB {\eta} -\F {2\pi} {N_H}
+\leq \NC \F {1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D\SB {\f'}} d \f' \NR
 }
@@
 \Disp {
-\NC R(\f)
-\leq \NC \F {1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F {48}{(24 -\f'^2) \f'} d \f'
+\NC R\SB {\f}
+\leq \NC \F {1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F {48}{\RB {24 -\f'^2} \f'} d \f'
 +\F {2\pi} {N_H} \NR
@@
 \Disp {
-\NC R(\f)
+\NC R\SB {\f}
 \leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
@@
 Let \m {\V {g}} be defined as above.
-Then \m {\V {g}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R(N_H, L)} to be
+Then \m {\V {g}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
 %
@@
 \Disp {
-\NC \d_{s+s'} -\max (\{\d_s, \d_{s'} \})
+\NC \d_{s+s'} -\max \SB {\{\d_s, \d_{s'} \}}
 \leq \NC \tau_{s, s'} \NR
@@
 \Disp {
-\NC \Nm {\IP { \V {z}, \M {P} (:, n_g) }}
+\NC \Nm {\IP { \V {z}, \M {P} \DB {:, n_g} }}
 \leq \NC  2 \R {\log N_g},
@@
 
-This only depends on the fact that \m {\M {P} (:, n_g)} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
+This only depends on the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
 
@@
 \Disp {
-\NC Q(x)
+\NC Q\SB {x}
 \leq \NC \F {1}{2} \RM {e}^{-x^2/2} \NR
@@
 \Disp {
-\NC Q(\R {2 \log N_g})
+\NC Q\SB {\R {2 \log N_g}}
 =\NC \F {1}{N_g}. \NR
@@
 \Disp {
-\NC \IP { \V {z} -(\V {y} -\M {P} \hat {\V {g}}), \M {P} (:,n_y) }
-= \NC \IP { \M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} (:,n_y) } \NR
-\NC = \NC \IP { \M {P} \V {d}, \M {P} (:,n_y) } \NR
+\NC \IP { \V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y} }
+= \NC \IP { \M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y} } \NR
+\NC = \NC \IP { \M {P} \V {d}, \M {P} \DB {:,n_y} } \NR
 }
@@
 \Disp {
-\NC \VNm { \M {P} (:,n_y)^\H (\V {y} -\M {P} \hat {\V {g}}) } 
-\leq \NC \VNm { \M {P}^\H (\V {y} -\M {P} \hat {\V {g}}) } _\infty \NR
+\NC \VNm { \M {P} \DB {:,n_y}^\H \RB {\V {y} -\M {P} \hat {\V {g}}} } 
+\leq \NC \VNm { \M {P}^\H \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty \NR
 \NC \leq \NC 2\R {\log N_g} \NR
@@
 \Disp {
-\NC \VNm {\M {P} (:,n_y)^\H \M {P} \V {d}} 
-\leq \NC \VNm {\IP { \V {z}, \M {P} (:,n_y) }}  +\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} (:,n_y) } \NR
+\NC \VNm {\M {P} \DB {:,n_y}^\H \M {P} \V {d}} 
+\leq \NC \VNm {\IP { \V {z}, \M {P} \DB {:,n_y} }}  +\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y} } \NR
 \NC \leq \NC 2 \R {\log N_g} +2 \R {\log N_g} \NR
@@
 \NC \VNm {\V {d}_{\MC {AB}}} _2
-\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{(1-\d_{2s}) \R {s}} \VNm {d_{C}} _1 \NR
+\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{C}} _1 \NR
 }
@@
 \NC \VNm {\V {d}} _2
-\leq \NC \F {4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
+\leq \NC \F {4}{\pi^4} \d_{3L}^4 \RB {1-2\d_{2L}} L^4 \RB { \log N_H}^4 \NR
 }
@@
 \leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
-\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F {1}{L} } \VNm {\V {d}_{\MC {C}}} _1^2
-+\F {8 \d_{3L}} {L (1-\d_{2L})^2} \R {N_g \log N_g} \VNm {\V {d}_{\MC {C}}} _1 \NR
-\NC \NC \quad +\F {16}{(1-\d_{2L})^2} N_g \log N_g \NR
+\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d}_{\MC {C}}} _1^2
++\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_g \log N_g} \VNm {\V {d}_{\MC {C}}} _1 \NR
+\NC \NC \quad +\F {16}{\RB {1-\d_{2L}}^2} N_g \log N_g \NR
 }
@@
 \NC \VNm {\V {d}} _2^2
-\leq \NC \F {4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4 \NR
+\leq \NC \F {4}{\pi^4} \d_{3L}^4 \RB {1-2\d_{2L}} L^4 \RB { \log N_H}^4 \NR
 }

### 2019-03-06 ongoing/report/4_simulation.tex
Correct delimiters usage

@@
 
-As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} (h)}.
+As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} \SB {h}}.
 But it is not the end.
@@
 {
-For \m {x \in \MB {V} (M)}, we say \m {\MC {R} (x)} is the real representation of \m {x}, defined by
+For \m {x \in \MB {V} \SB {M}}, we say \m {\MC {R} \SB {x}} is the real representation of \m {x}, defined by
 %
 \Disp {
-\NC \MC {R} (x) \in \NC \MB {V} (2M) \NR[+]
-\NC \MC {R} (x) \DB {m} =
+\NC \MC {R} \SB {x} \in \NC \MB {V} \SB {2M} \NR[+]
+\NC \MC {R} \SB {x} \DB {m} =
 \NC \startcases
-\MF {Re} (\MC {R} (x)\DB {m}), \quad \MC m =2m' \NR
-\MF {Im} (\MC {R} (x)\DB {m}), \quad \MC m =2m'+1 \NR
+\MF {Re} \SB {\MC {R} \SB {x} \DB {m}}, \quad \MC m =2m' \NR
+\MF {Im} \SB {\MC {R} \SB {x} \DB {m}}, \quad \MC m =2m'+1 \NR
 \stopcases \NR[+]
@@
 {
-For \m {A \in \MB {M}_{\MB {C}} (M_1, M_2)}, we say \m {\MC {R} (A)} is the real representation of \m {A}, defined by
+For \m {A \in \MB {M}_{\MB {C}} \SB {M_1, M_2}}, we say \m {\MC {R} \SB {A}} is the real representation of \m {A}, defined by
 %
 \Disp {
-\NC A \in \NC \MB {V}_{\MB {R}} (2M_1, 2M_2) \NR[+]
-\NC A (m_1,m_2) =
+\NC A \in \NC \MB {V}_{\MB {R}} \SB {2M_1, 2M_2} \NR[+]
+\NC A \SB {m_1,m_2} =
 \NC \startcases
-\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR
-\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'-1  \NR
--\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR
-\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'  \NR
+\MF {Re} \SB {A \SB {m_1,m_2}}, \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR
+\MF {Im} \SB {A \SB {m_1,m_2}}, \quad \MC m_1 =2m_1',\; m_2 =2m_2'-1  \NR
+-\MF {Im} \SB {A \SB {m_1,m_2}}, \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR
+\MF {Re} \SB {A \SB {m_1,m_2}}, \quad \MC m_1 =2m_1',\; m_2 =2m_2'  \NR
 \stopcases \NR[+]
@@
 \NC \V {\T {y}}
-\NC = \MC {R} (y)
-\in \MB {V} (N_h) \NR[+]
+\NC = \MC {R} \SB {y}
+\in \MB {V} \SB {N_h} \NR[+]
 \NC \V {\T {g}}
-\NC = \MC {R} (g)
-\in \MB {V} (N_h) \NR[+]
+\NC = \MC {R} \SB {g}
+\in \MB {V} \SB {N_h} \NR[+]
 \NC \M {\T {P}}
-\NC = \MC {R} (\M {P})
-\in \MB {M}_{\MB {C}} (2 N_y^2, 2 N_h^2) \NR
+\NC = \MC {R} \SB {\M {P}}
+\in \MB {M}_{\MB {C}} \SB {2 N_y^2, 2 N_h^2} \NR
 }
@@
 \NC \V {\T {z}}
-\NC = \MC {R} (\V {z}) \in \MB {V} (N_y) \NR
+\NC = \MC {R} \SB {\V {z}} \in \MB {V} \SB {N_y} \NR
 }
@@
 \Disp {
-\NC \M {I}_{n_y}^{(y)} \in \NC \MB {M}_{\MB {R}} (2N_y^2, 2N_y^2) \NR[+]
-\NC \M {I}_{n_y}^{(y)} (n_y')
+\NC \M {I}_{n_y}^{(y)} \in \NC \MB {M}_{\MB {R}} \SB {2N_y^2, 2N_y^2} \NR[+]
+\NC \M {I}_{n_y}^{(y)} \SB {n_y'}
 \NC =
@@
 \stopcases \NR[+]
-\NC \M {I}_{n_h}^{(h)} \in \NC \MB {M}_{\MB {R}} (2N_h^2, 2N_h^2) \NR[+]
-\NC \M {I}_{n_h}^{(h)} (n_h')
+\NC \M {I}_{n_h}^{(h)} \in \NC \MB {M}_{\MB {R}} \SB {2N_h^2, 2N_h^2} \NR[+]
+\NC \M {I}_{n_h}^{(h)} \SB {n_h'}
 \NC =
@@
 \Disp {
-\NC \NC \MC {L} (\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NR[+]
+\NC \NC \MC {L} \SB {\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}} \NR[+]
 \NC \NC = \IP {\V {1}, \V {m}}
 +\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M {g}}} -\lambda^{(h)} \IP {\V {y}_{n_h}, \V {m}}} \NR[+]
-\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\H ( \T {\M {P}} \T {\V {g}} -\T {\V {y}} ) } -\lambda^{(h)} \gamma} \NR[+]
+\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\H \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } } -\lambda^{(h)} \gamma} \NR[+]
 }

### 2019-03-06 ongoing/code/src/Classes.py

@@ -1,0 +1,20 @@
+class Ddss:
+
+    def __init__(self, pp, y, gG):
+        self.pp = pp
+        self.y = y
+        self.gG = gG
+
+def run(self):
+g = cp.Variable(n)
+m = cp.Variable(n)
+i = np.ones()
+socp_constr = (cvx.norm(A*x + b, 2) <= c.T*x + d)
+objective = cp.Minimize (i*m)
+constraints = [0 <= x, x <= 1]
+prob = cp.Problem(objective, constraints)
+
+
+
+self.sol = prob.solve())
+

### 2019-03-06 ongoing/code/src/Constants.py

@@ -1,0 +1,5 @@
+n_y
+n_h
+nn_y
+nn_h
+

### 2019-03-06 ongoing/code/src/main.py

@@ -1,0 +1,9 @@
+import numpy as np
+import cvxpy as cp
+import matplotlib.pyplot as plt
+
+import Constants
+import Classes
+import Functions
+import Drawing
+

### 2019-03-06 ongoing/deprecated_one/code/run.sh

@@ -1,7 +1,0 @@
-#!/usr/bin/env bash
-
-#lldb ./bin/main.o ./dat/table.txt
-rm -f ./dat/table.txt ./plt/fig.png
-./bin/main.o ./dat/table.txt
-./src/read_and_draw.py ./dat/table.txt 
-

### 2019-03-06 ongoing/deprecated_one/code/src/constants.cpp

@@ -1,32 +1,0 @@
-#include <map>
-#include <complex>
-#include <boost/numeric/ublas/matrix.hpp>
-#include <boost/numeric/ublas/io.hpp>
-#include "constants.h"
-
-namespace cst
-{
-   extern const double pi =3.14159265358979;
-   extern const std::complex<double> ii =std::sqrt( static_cast<Comp>(-1) );
-   extern const double a_t_phase =0.5; // a phase factor in uniform linear array of Tx
-   extern const double a_r_phase =0.6; // a phase factor in uniform linear array of Rx
-   extern const double spread =0.1; // relative spread of cluster
-   extern const std::size_t nn =7; // # of antennae, assumed same in Tx and Rx
-   extern const std::size_t kk =4; // # of subcarrier
-   extern const std::size_t s_blk_kk  =2; // # of subcarriers that share a precoder
-   extern const std::size_t nn_blk_kk  =kk /s_blk_kk;
-   extern const std::size_t uu =6; // # of user
-   extern const std::size_t s_blk_uu  =2; // # of users that share a precoder
-   extern const std::size_t nn_blk_uu  =kk /s_blk_uu;
-   extern const std::size_t ff =(kk/s_blk_kk) *(uu/s_blk_uu); // # of different precoders
-   extern const std::size_t nn_c =6; // # of cluster
-   extern const std::size_t nn_s =6; // # of scatterer
-   extern const double pp =1e5; // maximum power
-   extern const std::size_t t_record =100; // interval between subsequent record
-   extern const std::size_t t_change_temp =10; // interval between subsequent record
-   extern const double max_iter =800;
-   extern const double step_size =1.3;
-   extern const double delta =0.3; // simulation step
-   extern const double temp_init =1; // initial temperature
-   extern const double arr_cooling_param[] ={0.97, 0.96, 0.95, 0.94};
-}

### 2019-03-06 ongoing/deprecated_one/code/src/constants.h

@@ -1,41 +1,0 @@
-#ifndef CONSTANTS_H
-#define CONSTANTS_H
-
-#include <map>
-#include <complex>
-#include <boost/numeric/ublas/matrix.hpp>
-#include <boost/numeric/ublas/io.hpp>
-
-namespace ublas = boost::numeric::ublas;
-typedef std::complex<double> Comp;
-typedef ublas::matrix <Comp> Mat;
-typedef std::map< std::size_t, Mat> Map_mat;
-
-namespace cst
-{
-   extern const double pi;
-   extern const Comp ii;
-   extern const double a_t_phase;
-   extern const double a_r_phase;
-   extern const double spread;
-   extern const std::size_t nn;
-   extern const std::size_t kk;
-   extern const std::size_t s_blk_kk;
-   extern const std::size_t nn_blk_kk;
-   extern const std::size_t uu;
-   extern const std::size_t s_blk_uu;
-   extern const std::size_t nn_blk_uu;
-   extern const std::size_t ff;
-   extern const std::size_t nn_c;
-   extern const std::size_t nn_s;
-   extern const double pp;
-   extern const std::size_t t_record;
-   extern const std::size_t t_change_temp;
-   extern const double max_iter;
-   extern const double step_size;
-   extern const double delta;
-   extern const double temp_init;
-   extern const double arr_cooling_param[4];
-}
-
-#endif

### 2019-03-06 ongoing/deprecated_one/code/src/functions.cpp

@@ -1,167 +1,0 @@
-#include <iostream>
-#include <cstdio>      /* printf, scanf, puts, NULL */
-#include <cstdlib>     /* srand, rand */
-#include <ctime>       /* time */
-
-#include <boost/numeric/ublas/matrix.hpp>
-#include <boost/numeric/ublas/io.hpp>
-#include <boost/numeric/ublas/matrix_proxy.hpp>
-#include <boost/numeric/ublas/lu.hpp>
-
-#include "constants.h"
-
-// stackoverflow.com/questions/29877760/boostublas-how-to-get-determinant-of-int-matrix?rq=1
-Comp determinant(const Mat& mm)
-{
-    Mat m =mm;
-    ublas::permutation_matrix<std::size_t> pivots( m.size1() );
-    auto be_singular = ublas::lu_factorize(m, pivots);
-    if (be_singular) {return 0;}
-
-    Comp det = 1;
-    for (std::size_t i = 0; i < pivots.size(); ++i) 
-    {
-        if (pivots(i) != i) {det *= -1;}
-        det *= m(i,i);
-    //std::cout << "det= " << det << std::endl; //XXX
-    }
-
-    return det;
-}
-
-double frob_norm(const Mat& m)
-{
-   double ret =0;
-   for(std::size_t i=0; i<=cst::nn-1; i++)
-      for(std::size_t j=0; j<=cst::nn-1; j++)
-      {
-         double hold_abs =std::abs( m(i,j) );
-         ret =ret +hold_abs *hold_abs; // hold
-      }
-   ret =std::sqrt(ret);
-   return ret;
-}
-
-Mat get_array_response(double psi, std::size_t len)
-{
-   Mat ret(len,1);
-   for(std::size_t n=0; n <=len -1; n++)
-   {
-      ret(n,0) =std::exp(cst::ii *static_cast<double>(n) *psi);
-   }
-   return ret;
-}
-
-void set_rand_channel( Mat& h )
-{
-   h =ublas::zero_matrix <Comp> (cst::nn, cst::nn);
-   for(std::size_t n_c=0; n_c <cst::nn_c-1; n_c++)
-   {
-      double mu =static_cast<double> (rand()) /RAND_MAX;
-      mu =2*mu -1;// [-1,1]
-      for(std::size_t n_s=0; n_s <cst::nn_s-1; n_s++)
-      {
[…]

### 2019-03-06 ongoing/deprecated_one/code/src/read_and_draw.py

@@ -1,74 +1,0 @@
-#!/usr/bin/env python
-# the shebang line indicates this file be passed as a python3 script
-
-import matplotlib.pyplot as plt # plotting functions
-import os # getcwd
-
-# to set input & output paths
-top_dir = os.getcwd() # current working directory
-out_data_path =top_dir +"/dat/table.txt"
-out_fig_path =top_dir +"/plt/fig.png"
-#print(out_fig_path)
-
-# to retrieve line by line
-handle_text =open(out_data_path)
-content =handle_text.read()
-list_line =content.split('\n') # newline as delimiter
-
-# to set axis & title
-#plt.close("all")
-fig =plt.figure()
-plt.title( "Simulated Annealing", fontsize =15 )
-plt.xlabel( "Time", fontsize =12 )
-plt.ylabel( "Rate", fontsize =12 )
-
-# to set plot style
-num_line_style =4
-list_line_style =['-', '--', '-.', ':'] # the larger, the thicker
-num_color =5
-list_color =['r', 'g', 'c', 'b', 'k'] # red, green, cyan, blue, black
-num_marker =6
-list_marker =['v', '^', 'o', 's', '*', 'D'] # triangle down, triangle up, circle, square, star, diamond
-size_width =3 # fixed line width
-size_marker =7 # fixed marker size
-
-vec_x =[] # to set empty list to enlarge its scope
-# split w/o arguments parses any number of spaces and tabs
-list_str =list_line[0]. split()
-for tmp_str in list_str:
-    # strip decimal mark to determine, whether a decimal number
-    if not tmp_str. replace('-',''). replace('.',''). isdigit():
-        continue
-    else:
-        vec_x.append(float(tmp_str))
-# end for
-list_line.pop(0)
-
-for idx, line in enumerate(list_line):
-    list_str =line.split()
-    if not list_str: # "list_str" is empty
-        continue
-    # end if empty
-
-    vec_y =[] # to create list to enlarge its scope
-    
-    for tmp_str in list_str:
-        # to strip decimal mark & minus sign to check whether a decimal number
-        if not (tmp_str. replace('-',''). replace('.',''). isdigit()):
-            continue
-        else:
-            vec_y.append(float(tmp_str))
-    # end for each word
-
-    plt.plot( vec_x, vec_y,
-            markersize =size_marker,
-            linewidth =size_width,
-            linestyle =list_line_style[ int( idx % num_line_style ) ],
[…]

### 2019-03-06 ongoing/deprecated_two/src/class.cpp

@@ -1,33 +1,0 @@
-
-void Parameters::Parameters(int num_path) :
-      num_path(num_path),
-      list_ang_dep(cst::nn, 0),
-      list_ang_arr(cst::nn, 0),
-      list_amp(cst::nn, 0)
-{
-}
-
-void Parameters::generate_new_instance()
-{
-   for(int i=0; i<=this->cst::nn-1; i++)
-   {
-      this ->list_ang_dep[i] =2 *cst::pi *get_normalized_uniform();
-      this ->list_ang_arr[i] =2 *cst::pi *get_normalized_uniform();
-      this ->list_amp.[i] +=get_normalized_gausian() +cst::ii *get_normalized_gausian();
-   }
-}
-
-Mat Parameters::get_channel()
-{
-   Mat ret;
-   ret =ublas::zero_matrix <Comp> (this->cst::nn, this->cst::nn);
-   for(std::int i_path=0; i_path <num_path-1; i_path++)
-   {
-      Mat a_t =get_array_response(cst::a_t_phase *psi);
-      Mat tr_a_r =ublas::trans(get_array_response(cst::a_r_phase *psi));
-      ret =ret +ublas::prod( a_t, tr_a_r );
-   }
-   return ret;
-}
-
-

### 2019-03-06 ongoing/deprecated_two/src/class.h

@@ -1,17 +1,0 @@
-
-class Parameters
-{
-public:
-   Parameters();
-   Parameters(int, int);
-   ~Parameters();
-   void generate_new_instance();
-   Mat get_channel();
-   
-private:
-   int nn_path;
-   std::vector<double> list_ang_dep;
-   std::vector<double> list_ang_arr;
-   std::vector<Comp> list_amp;
-   
-}

### 2019-03-06 ongoing/deprecated_two/src/constants.cpp

@@ -1,19 +1,0 @@
-#include <map>
-#include <complex>
-#include <boost/numeric/ublas/matrix.hpp>
-#include <boost/numeric/ublas/io.hpp>
-#include "constants.h"
-
-namespace cst
-{
-   extern const double pi =3.14159265358979;
-   extern const std::complex<double> ii =std::sqrt( static_cast<Comp>(-1) );
-   extern const double a_t_phase =0.5; // a phase factor in uniform linear array of Tx
-   extern const double a_r_phase =0.6; // a phase factor in uniform linear array of Rx
-   extern const double spread_cluster =0.1; // relative spread of cluster
-   extern const std::size_t nn =7; // # of antennae, assumed same in Tx and Rx
-   extern const std::size_t nn_c =6; // # of cluster
-   extern const std::size_t nn_s =6; // # of scatterer
-   extern const double max_iter =800;
-   extern const double step_size =1.3;
-}

### 2019-03-06 ongoing/deprecated_two/src/functions.cpp

@@ -1,83 +1,0 @@
-#include <iostream>
-#include <cstdio>
-#include <cstdlib>
-#include <ctime>
-#include <random>
-
-#include <boost/numeric/ublas/matrix.hpp>
-#include <boost/numeric/ublas/io.hpp>
-#include <boost/numeric/ublas/matrix_proxy.hpp>
-#include <boost/numeric/ublas/lu.hpp>
-#include "constants.h"
-
-
-
-void newton_method(std::vector<double> list_ang_dep, std::vector<double> list_ang_arr, std::vector<Comp> list_amp)
-{
-   
-}
-
-void walk_one_step(Parameters& param)
-{
-   
-}
-
-void write_idx( std::ostream* p_ios )
-{
-   for(std::size_t idx=0; idx <=cst::max_iter-1; idx++)
-   {
-      if( idx %cst::t_record ==0 ){ (*p_ios) << idx << ' '; }
-   }
-   (*p_ios) << std::endl;
-}
-
-double infty_norm(const Mat& m)
-{
-   double ret =0;
-   for(std::size_t i=0; i<=cst::nn-1; i++)
-      for(std::size_t j=0; j<=cst::nn-1; j++)
-      {
-         double hold_abs =std::abs( m(i,j) );
-         if(hold_abs >ret){ ret =hold_abs; }
-      }
-   return ret;
-}
-
-double get_normalized_uniform()
-{
-   std::random_device dev;
-   std::mt19937 gen(dev());
-   std::uniform_real_distribution<> dist(0.0, 1.0);
-   return dist(gen);
-}
-
-double get_normalized_gaussian()
-{
-   std::default_random_engine gen;
-   std::normal_distribution<double> dist(0,1);
-   return x+dist(gen);
-}
-
-double mod_2_pi(double x)
-{
-   double ret =0;
-   bool sgn =false;
-
-   if(x>0){sgn =true;}
-   else{sgn =false;}
-   if(!sgn){ x =-x; }
-
-   ret =x -2 *cst::pi *static_cast<int>(x/2/cst::pi);
-   if(!sgn){ ret =-ret; }
-   return ret;
-}
-
-Mat get_array_response(double psi)
-{
-   Mat ret(len,1);
-   for(std::size_t n=0; n <=cst::nn -1; n++)
-   {
-      ret(n,0) =std::exp(cst::ii *static_cast<double>(n) *psi);
-   }
-   return ret;
-}

### 2019-03-06 ongoing/deprecated_two/src/functions.h

@@ -1,17 +1,0 @@
-#ifndef FUNCION_H
-#define FUNCION_H
-
-#include "constants.h"
-//extern typedef Vec;
-
-Comp determinant(const Mat&);
-double frob_norm(const Mat&);
-Mat get_array_response(double, std::size_t);
-void set_rand_channel( Mat& );
-void accept_random_step(Map_mat*, Map_mat*);
-void set_random_step(Map_mat*);
-double find_new_sum_rate(Map_mat*, Map_mat*, Map_mat*);
-void write_idx( std::ostream* );
-void simulated_annealing( double, std::ostream* );
-
-#endif

### 2019-03-06 ongoing/deprecated_two/src/main.cpp

@@ -1,27 +1,0 @@
-#include <cmath>
-#include <cstdio>
-#include <ctime>
-#include <cstdlib>     /* srand, rand */
-#include <sstream> // stringstream
-#include <fstream> // ofstream
-#include <string> // string
-#include <boost/numeric/ublas/matrix.hpp>
-#include <boost/numeric/ublas/io.hpp>
-#include "functions.h"
-#include "constants.h"
-
-int main( int argc, char** argv )
-{
-   srand(time(NULL));
-   std::ofstream* p_file =new std::ofstream;
-   p_file -> open (argv[1]);
-
-   write_idx(p_file);
-   for(std::size_t i=0; i<=3; i++)
-   {
-      simulated_annealing( cst::arr_cooling_param[i], p_file );
-      (*p_file) << std::endl;
-   }
-
-   delete p_file;
-}

### 2019-03-14 ongoing/report/1_introduction.tex
Simulation: Rev block matrix notation

@@
 \m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
-The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} \SB {a}} and \m {\MF {Im} \SB {a}}, respectively, thus \m {a =\MF {Re} \SB {a} + i \MF {Im} \SB {a}}
+The real and imaginary part of \m {a} will be denoted respectively as \m {\Mf {Re} \SB {a}} and \m {\Mf {Im} \SB {a}}, respectively, thus \m {a =\Mf {Re} \SB {a} + i \Mf {Im} \SB {a}}
 
-We restrict our discussion to \m {\MB {R}^N} or \m {\MB {C}^N} seen as the Hilbert space , equipped with standard inner product.
+We restrict our discussion to \m {\Mb {R}^N} or \m {\Mb {C}^N} seen as the Hilbert space , equipped with standard inner product.
 Lower case Latin alphabets with single underline, like \m {\V {a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m {\M {A}}, denote matrices.
@@
 In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
-Of course, scalar operation on \m {\MB {R}^N} is over field \m {\MB {R}}, and that on \m {\MB {C}^N} is over field \m {\MB {C}}.
-We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
-Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} \SB {N}}.
-We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} \SB {M,N}}, and its role as linear transformation is understood.
+Of course, scalar operation on \m {\Mb {R}^N} is over field \m {\Mb {R}}, and that on \m {\Mb {C}^N} is over field \m {\Mb {C}}.
+We use \m {\Mb {K}} to refer to either \m {\Mb {R}} or \m {\Mb {C}}.
+Not to avoid confusion, we call the Hilbert space \m {\Mb {K}^N} over \m {\Mb {K}} to be \m {\Mb {V}_{\Mb {K}} \SB {N}}.
+We also call the collection of \m {M} by \m {N} matrices to be \m {\Mb {M}_{\Mb {K}} \SB {M,N}}, and its role as linear transformation is understood.
 Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
@@
 
-Denote as \m {\MB {P} \SB {X}} the probability, and \m {\MB {E} \SB {X}} the expectation.
+Denote as \m {\Mb {P} \SB {X}} the probability, and \m {\Mb {E} \SB {X}} the expectation.
 Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.
@@
 The figure of merit of a MIMO system is usually considered to be the channel capacity.
-In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det \RB {I +\RM {SNR}}}, but that knowledge is hardly always available.
+In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det \RB {I +\Mr {SNR}}}, but that knowledge is hardly always available.
 What makes things more difficult is the case that \m {\M {H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
@@
 Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det \RB {I +\RM {SNR}}}.
+Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det \RB {I +\Mr {SNR}}}.
 
@@
 
-To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
+To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \Mb {N}} is much larger than the number of measurements \m {N_m \in \Mb {N}}, namely,
 %
@@
 
-We will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} \SB {N_m}}.
+For brevity, we will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\Mb {V}_{\Mb {K}} \SB {N_m}}.
+Also, suppose \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N_m, N_p}}.
+Let \m {\Mc {T} \subset T \RB {N_p}}.
+Denote as \m {\M {A}_{\Mc {T}}} the columns of \m {\M {A}} having indices in \m {\Mc {T}}.
 
@@
 {
-Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
-Let \m {\MC {T} \subset T \RB {N_p}}.
-Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
+\m {x \in \Mb {V}_{\Mb {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\Mc {A}}, \m {s <N_m}, if there is \m {\Mc {A} \subset T \RB {N_m}} such that
+%
+\Disp { 
+\NC x_{T\SB {N} -\Mc {A}}
+=\NC \V {0} \NR
+}
+with
+\Disp { 
+\NC \# \Mc {A} \leq s. \NR
+}
+That is, only at most \m {s} components of \m {x} is nonzero.
 }
@@
 {
-\m {x \in \MB {V}_{\MB {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
-%
-\Disp { 
-\NC x_{T\SB {N} -\MC {A}}
-=\NC \V {0} \NR
-}
-with
-\Disp { 
-\NC \# \MC {A} \leq s. \NR
-}
-That is, only at most \m {s} components of \m {x} is nonzero.
-}
-
-\Result
-{Program}
-{
-Let \m {P \in \MB {M}_\MB {K} \SB {N_m, N_p}} and \m {y \in \MB {V}_\MB {K} \SB {N_p}} be given.
-Find \m {h \in \MB {V}_\MB {K} \SB {N_p}} with
-%
-\Disp {
-\NC
-h
-= \NC \startcases
-\NC \Min {h'}
-\quad \MC \VNm {h'} _1 \NR[+]
-\NC \RM {subject} \; \RM {to}
-\quad \MC P h' =y \NR
-\stopcases \NR
-}
-}
-
-Now let \m {y =P h}.
-Suppose \m {h} is \m {s}-sparse, then the program () completely recovers \m {h}.
-That is, a noiseless linear transformation of a sparse vector is completely recovered by a \m {\ell_1}-minimization program with an overwhelming probability.
-
-\Result
-{Definition}
-{
-Consider \m {P \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
-For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N_p}}, for all \m {\MC {T} \subset T\SB {N_m}} with \m {\#\{\MC {T} \} \leq s},
+Consider \m {P \in \Mb {M}_{\Mb {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
+For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \Mb {V}_{\Mb {K}} \SB {N_p}}, for all \m {\Mc {T} \subset T\SB {N_m}} with \m {\#\{\Mc {T} \} \leq s},
 %
@@
 \NC \NC \RB {1-\d_s} \VNm {V {x}}^2 \NR
-\NC \leq \NC \VNm {P_{\MC {T}} \V {x}} _2^2 \NR
+\NC \leq \NC \VNm {P_{\Mc {T}} \V {x}} _2^2 \NR
 \NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
@@
 \Result
-{Program}
+{Algorithm}
 {
-Let \m {\M {P} \in \MB {V}_\MB {R} \SB {N_m, N_p}} and \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}} be given.
-Find \m {\V {h} \in \MB {V}_\MB {R} \SB {N_m}} by
-%
-
+\startitemize[n]
+\item Input \m {\M {P} \in \Mb {V}_\Mb {R} \SB {N_m, N_p}}, \m {\V {y} \in \Mb {V}_\Mb {R} \SB {N_m}}.
+\item Find \m {\V {h} \in \Mb {V}_\Mb {R} \SB {N_m}} by
 \Disp {
@@
 \NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
-\NC \RM {subject} \; \RM {to} \quad \MC \VNm {\M {P}^\H \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \gamma \NR
+\NC \Mr {subject} \; \Mr {to} \quad \MC \VNm {\M {P}^\Adj \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \gamma \NR
 \stopcases \NR
 }
+\item Output \m {\V {h}}.
 }
 
-They was able to show that, with Program (), the mean square error is bounded with overwhelming probability.
+They was able to show that, with Algorithm (), the mean square error is bounded with overwhelming probability.
 And it can be shown that this \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
@@
 {
-Let each entry of random matrix \m {P \in \MB {M}_\MB {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
+Let each entry of random matrix \m {P \in \Mb {M}_\Mb {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
 Then, with \m {0 <\epsilon <1},
@@
 \Disp {
-\NC \NC \MB {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2} \NR
+\NC \NC \Mb {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2} \NR
 \NC \leq \NC 2 \exp \SB {-n \RB {\epsilon^2/4 -\epsilon^3/6} } \NR
@@
 
-Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} \SB {N_p}}, \m {\V {h} \in \MB {V}_\MB {K} \SB {N_s}}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
+Same as before, consider \m {\V {y} \in \Mb {V}_\Mb {K} \SB {N_p}}, \m {\V {h} \in \Mb {V}_\Mb {K} \SB {N_s}}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
 If
@@
 {
-Define \m {\RM {vec} \SB {\M {A}} \in \MB {K}^{NM}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N,M}}.
+Define \m {\Mr {vec} \SB {\M {A}} \in \Mb {K}^{NM}} to be the vectorization of \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}}.
 }
@@
 {
-For \m {\RM {vec} \SB {A} \in \MB {M}_{\MB {K}} \SB {N,M}} and \m {\RM {vec} \SB {A} \in \MB {M}_{\MB {K}} \SB {N,M}}
-Define the Kronecker product \m {\RM {vec} \SB {A} \in \MB {K}^{nm}} 
+For \m {\Mr {vec} \SB {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}} and \m {\Mr {vec} \SB {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}}
+Define the Kronecker product \m {\Mr {vec} \SB {A} \in \Mb {K}^{nm}} 
 }
@@
 \Disp {
-\NC \RM {vec} \SB {Y}
-=\big[ \RB {F^\H} \otimes W \big] \RM {vec} \RB {\M {H}} \NR
+\NC \Mr {vec} \SB {Y}
+=\SB {\RB {F^\Adj} \otimes W} \Mr {vec} \RB {\M {H}} \NR
 }

### 2019-03-14 ongoing/report/2_problem_setting.tex
Correct delimiters usage
Simulation: Rev block matrix notation

@@
 Since expression involving probability will get complicated, sometimes we explicitly mark the independence on event space index.
-Introduce the direct product
-%
 
-\Disp {
-\NC \Omega
-= \NC \Omega_t \times \Omega_h \times \Omega_n \times \Omega_r \NR
-}
-%
-to denote the overall event space, where
-
-\startitemize
-\item \m {\Omega_t} denotes the event space of the transmitter end,
-\item \m {\Omega_h} denotes the event space of the communication channel itself,
-\item \m {\Omega_z} denotes the event space of the noise arising in the communication channel,
-\item \m {\Omega_r} denotes the event space of the receiver end.
-\stopitemize
-%
+For clarity, we use \m {\O_t} to denote the event space of the transmitter end, \m {\O_h} to denote that of the communication channel itself, \m {\O_z} to denote that of the noise arising in the communication channel, and \m {\O_r} to denote that of the receiver end.
+It helps to think \m {\NC \O = \NC \O_t \times \O_h \times \O_n \times \O_r \NR} as the overall event space, though we will not really calculate Lebesgue integrals.
 
 We restrict our consideration to the uniform linear array, which can be modeled as
-%
 \Disp {
-\NC \V {a} (\psi')
-= \NC \F {1}{\R {N_H}} \sum_{n=1}^{N} \RM {e}^{n \psi' i} \V {u}_n
-\in \MB {V}_\MB {C} (N_H) \NR
+\NC \V {a} \SB {\psi'}
+= \NC \F {1}{\R {N_H}} \sum_{n=1}^{N} \Mr {e}^{n \psi' i} \V {u}_n
+\in \Mb {V}_\Mb {C} \SB {N_H} \NR
 }
-%
-where \m {\RM {e}} is the base of natural logarithm, and \m {i} the imaginary unit.
+where \m {\Mr {e}} is the base of natural logarithm, and \m {i} the imaginary unit.
 
 And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
-%
 \Disp {
 \NC H
-=\sum_{l=1}^L \alpha_l \V {a} \left( \F {d} {\lambda} \sin \f_l' \right) \V {a} \left( \F {d_{\RM {arr}}} {\lambda} \sin \th_l' \right)^\H \NR
+=\sum_{l=1}^L \alpha_l \V {a} \SB { \F {d} {\lambda} \sin \f_l' } \V {a} \SB { \F {d_{\Mr {arr}}} {\lambda} \sin \th_l' }^\Adj \NR
 }
-%
-The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\RM {arr}}} is the distance between two adjacent antennae.
+The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Mr {arr}}} is the distance between two adjacent antennae.
 For our purpose, we may absorb the argument of \m {\V {a}} as
-%
 \Disp {
 \NC \f_l
-=\NC \F {d_{\RM {arr}}} {\lambda} \sin \f_l' \NR[+]
+= \NC \F {d_{\Mr {arr}}} {\lambda} \sin \f_l' \NR[+]
 \NC \th_l
-=\NC \F {d_{\RM {arr}}} {\lambda} \sin \th_l' \NR[+]
+= \NC \F {d_{\Mr {arr}}} {\lambda} \sin \th_l' \NR[+]
 }
-%
 to get a simpler form
-%
 \Disp {
 \NC H
-=\sum_{l=0}^L \alpha_l \V {a} (\f_l) \V {a} (\th_l)^\H
-\in \MB {M}_\MB {C} (N_H) \NR
+=\sum_{l=0}^L \alpha_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
+\in \Mb {M}_\Mb {C} \SB {N_H} \NR
 }
-%
 
@@
 To set up notation, we list them as below.
-%
 \Disp {
-\NC \M {F}_B \in  \NC \MB {M}_{\MB {C}} (N_R, N_Y) \NR[+]
-\NC \M {F}_R \in  \NC \MB {M}_{\MB {C}} (N_H, N_R) \NR[+]
-\NC \M {W}_R \in  \NC \MB {M}_{\MB {C}} (N_R, N_H) \NR[+]
-\NC \M {W}_B \in  \NC \MB {M}_{\MB {C}} (N_Y, N_R) \NR
+\NC \M {F}_B \in  \NC \Mb {M}_{\Mb {C}} \SB {N_R, N_Y} \NR[+]
+\NC \M {F}_R \in  \NC \Mb {M}_{\Mb {C}} \SB {N_H, N_R} \NR[+]
+\NC \M {W}_R \in  \NC \Mb {M}_{\Mb {C}} \SB {N_R, N_H} \NR[+]
+\NC \M {W}_B \in  \NC \Mb {M}_{\Mb {C}} \SB {N_Y, N_R} \NR[+]
 }
-%
 Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
-%
 \Disp {
-\NC \Nm {\M {F}_R (n_h, n_r)} = \NC 1, \NR[+]
-\NC \Nm {\M {W}_R (n_r, n_h)} = \NC 1, \NR[+]
-\NC n_h = \NC 1, \dots N_H, \NR
-\NC n_r = \NC 1, \dots N_R \NR
+\NC \Nm {\M {F}_R \DB {n_H, n_R}} = \NC 1, \NR[+]
+\NC \Nm {\M {W}_R \DB {n_R, n_H}} = \NC 1, \NR[+]
+\NC n_H = \NC 1, \dots N_H, \NR
+\NC n_R = \NC 1, \dots N_R \NR
 }
-%
 And we assume
@@
 \NC N_H \gg  \NC N_R \NR[+]
-\NC N_R \gg  \NC N_s \NR[+]
+\NC N_R \gg  \NC N_Y \NR[+]
 }
@@
 We may introduce the effective channel
-%
 \Disp {
-\NC Y (\omega_h, \omega_e)
-:= \NC W_B (\omega_r) W_R (\omega_r) \Big[ H (\omega_h) F_R (\omega_t) F_B (\omega_t) +Z (\omega_z) \Big] \NR
+\NC \NC \M{Y} \SB {\o_t, \o_h, \o_z, \o_r} \NR
+\NC := \NC \M{W}_B \SB {\o_r} \M{W}_R \SB {\o_r} \RB {\M{H} \SB {\o_h} \M{F}_R \SB {\o_t} \M{F}_B \SB {\o_t} +\M{Z} \SB {\o_z} } \NR
 }
-%
 Supress the event space index for brevity, we restate the same equation as
-%
 \Disp {
-\NC Y
-:=W_B W_R ( H F_R F_B +Z ) \NR
+\NC \M{Y}
+:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
 }
-\m {\M {Y}} has \m {N_Y} columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \m {\V {u}_n}.
-This way, we may denote the acquired effective channel matrix \m {\M {Y}} under noisy observation as (borrowing Matlab's colon notation to denote columns)
-%
-\Disp {
-\NC \M {Y} (:,n_y)
-:= \NC \M {W}_B \M {W}_R \Big[ \M {H} \M {F}_R \M {F}_B \V {u}_{n_y} +\V {z} \Big], \NR[+]
-\NC \quad n_y = \NC 1, 2, \dots, N_Y \NR
-}
-%
 Still, the crux of the matter is the recovery of \m {\M {H}} with knowledge of \m {\M {Y}}, while \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B} are in our control.
@@
 \stopsection
-\startsection [title={Vectorization}]
+\startsection [title={Proposed Method}]
+\startsubsection [title={Vectorization}]
 
+First, for short we set
+\Disp {
+\NC N_h = \NC N_H^2 \NR[+]
+\NC N_y = \NC N_Y^2 \NR[+]
+}
 If we had followed the widely accepted approach of compressive channel sensing, we would have written
-%
 \Disp {
 \NC \V {h}
-:= \NC \RM {vec} (\M {H})
-\in \MB {V}_{\MB {C}} (N_g) \NR[+]
+:= \NC \Mr {vec} \SB {\M {H}}
+\in \Mb {V}_{\Mb {C}} \SB {N_h} \NR[+]
 \NC \V {y}
-:= \NC \RM {vec} (\M {Y})
-\in \MB {V}_{\MB {C}} (N_y) \NR[+]
-\NC \V {z}^\star
-:= \NC \RM {vec} (\M {Z})
-\in \MB {V}_{\MB {C}} (N_y) \NR[+]
+:= \NC \Mr {vec} \SB {\M {Y}}
+\in \Mb {V}_{\Mb {C}} \SB {N_y} \NR[+]
+\NC \V {z}
+:= \NC \Mr {vec} \SB {\M{W}_B \M{W}_R \M {Z}}
+\in \Mb {V}_{\Mb {C}} \SB {N_y} \NR[+]
 \NC \M {P}^\star
-:= \NC (\M {F}_R^\Tr \M {F}_B^\Tr) \otimes (\M {W}_B \M {W}_R)
-\in \MB {M}_{\MB {C}} (N_y, N_g) \NR
+:= \NC \RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R}
+\in \Mb {M}_{\Mb {C}} \SB {N_y, N_h} \NR[+]
 }
-%
-to formulate our goal as sparse recovery problem of \m {\RM {vec} (H)} to be
-%
+to formulate our goal as sparse recovery problem of \m {\Mr {vec} \SB {H}} to be
 \Disp {
-\NC \V {y} =\M {P}^\star \V {h} +\V {z}^\star \NR
+\NC \V {y} =\M {P}^\star \V {h} +\V {z} \NR
 }
-%
-But, as we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
-What shall we do?
+As we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
+However, there is no guarantee, though, that \m {\V {h}} will be sparse.
 
-\stopsection
+\stopsubsection
 
-\startsection [title={Proposed Method}]
+\startsubsection [title={Expression for the Angular Space}]
 
 Introduce the discrete Fourier matrix \m {\M {K}} defined to be
-%
 \Disp {
-\NC \M {K} \in  \NC \MB {M}_{\MB {C}} (N_H, N_H) \NR
-\NC \M {K} (n_1, n_2) = \NC \F {1} {\R {N_H}} \RM {e}^{2\pi i n_1 n_2 /N_H}, \NR[+]
+\NC \M {K} \in  \NC \Mb {M}_{\Mb {C}} \SB {N_H, N_H} \NR
+\NC \M {K} \DB {n_1, n_2} = \NC \F {1} {\R {N_H}} \Mr {e}^{2\pi i n_1 n_2 /N_H}, \NR[+]
 \NC \quad n_1, n_2 = \NC 0, 1, \dots, N_H-1 \NR
 }
-%
+where recall that we have
+\Disp{
+\NC \M {K}^\Adj \M {K}
+= \NC \M {I} \NR
+}
 Observe that, if we write
-%
 \Disp {
 \NC \M {G}
-=\M {K}^\H \M {H} \M {K} \NR
+=\M {K}^\Adj \M {H} \M {K} \NR
 }
-%
-which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \m {\M {H}}, then
-%
+which has the interpretation as the angular space (i.e., spatial frequency domain) representation of \m {\M {H}}, then
 \Disp {
 \NC \M {Y}
-:=\M {W}_B \M {W}_R \M {K} ( \M {G} \M {K}^\H \M {F}_R \M {F}_B +\M {K}^\H \M {Z} )
-\in \MB {M}_{\MB {C}} (N_Y, N_Y) \NR
+=\M {W}_B \M {W}_R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F}_R \M {F}_B
++\M {W}_B \M {W}_R \M {Z}
+\in \Mb {M}_{\Mb {C}} \SB {N_Y, N_Y} \NR
 }
-%
 If at the end of day, \m {\M {G}} is sparse, then we recover \m {\M {G}} instead, and our use of DS is fully justified.
 
-That is to say, \m {\M {K}^\H \V {z}} may be absorbed, and a similar Kronecker product may be used.
+That is to say, a similar Kronecker product may be used.
 To simplify notation, set
-%
 \Disp {
 \NC \M {P}
-:=(\M {F}_B^\Tr \M {F}_R^\Tr K^\ast) \otimes (\M {W}_B \M {W}_R \M {K})
-\in \MB {M}_{\MB {C}} (N_y, N_g) \NR
+:=\RB {\M {F}_B^\Tr \M {F}_R^\Tr K^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}
+\in \Mb {M}_{\Mb {C}} \SB {N_y, N_h} \NR
 }
-%
 And accordingly
@@
 \NC \V {g}
-:= \NC \RM {vec} (\M {G})
-\in \MB {M}_{\MB {C}} (N_g) \NR[+]
-\NC \V {z}
-:= \NC \RM {vec} (\M {K}^\H \M {Z})
-\in \MB {V}_{\MB {C}} (N_y) \NR
+:= \NC \Mr {vec} \SB {\M {G}}
+\in \Mb {M}_{\Mb {C}} \SB {N_h} \NR[+]
 }
-where for short we set
-\Disp {
-\NC N_g = \NC N_H^2 \NR[+]
-\NC N_y = \NC N_Y^2 \NR
-}
-%
 Then
-%
 \Disp {
@@
 }
-%
 If so, our program reads
@@
 \Result
-{Program}
+{Algorithm}
 {
-Let \m {\M {P}, \V {y}} be defined just above in ().
-Then, with parameter \m {\gamma} specified, define the following program
-%
+\startitemize[n]
+\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_h}}, \m{\gamma \geq 0}.
+\item Calculate
 \Disp {
-\NC \hat {\V {g}}
-=\NC \startcases
-\Min {\V {g}'}  \MC \VNm {\V {g}'} _1 \NR[+]
-\RM {subject} \; \RM {to} \quad  \MC \VNm {\M {P}^\H (\V {y} -\M {P} \V {g}')} _\infty \leq \gamma \NR
+\NC \Hat {\V {g}}
+= \NC \startcases
+\NC \Min {\V {g}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR[+]
+\NC \Mr {subject} \; \Mr {to} \quad  \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \gamma \NR
 \stopcases \NR
 }
-%
-And convert \m {\hat {\V {g}}} back to the space domain as
-%
+\item Convert \m {\Hat {\V {g}}} back to the space domain, namely
 \Disp {
-\NC \hat {G} =\RM {vec}^{-1} (\hat {g}) \NR
+\NC \Hat {G} =\Mr {vec}^{-1} \SB {\Hat {g}} \NR
 }
-%
-And finally recover the estimated \m {H} as
-%
+\item Recover the estimated \m {\Hat {\M {H}}}, as
 \Disp {
-\NC \hat {\M {H}} =\M {K} \hat {\M {G}} \M {K}^\H \NR
+\NC \Hat {\M {H}} =\M {K} \Hat {\M {G}} \M {K}^\Adj \NR
 }
-%
+\item Output \m {\Hat {\M {H}}}.
+\stopitemize
 }
@@
 
+\stopsubsection
 \stopsection

### 2019-03-14 ongoing/report/3_theorems_and_proofs.tex
Simulation: Rev block matrix notation

@@
 We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \m {g \in \MB {C}^{N_g}}, and we continue to use \m {\hat {g}} to denote the Dantzig Selector.
+The sparse vector to be recovered of our investigation is \m {g \in \Mb {C}^{N_h}}, and we continue to use \m {\hat {g}} to denote the Dantzig Selector.
 To simplify the exposition, we will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).
 
-We first establish a technical lemma that shows \m {\RM {supp} \SB {\V {g}}} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse
+We first establish a technical lemma that shows \m {\Mr {supp} \SB {\V {g}}} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse
 
-\startsection [title={Almost-Sparsity of Beamspace Channel Matrix}]
+\startsection [title={Almost-Sparsity of Angular Channel}]
 
@@
 \Disp {
-\NC \gamma = \NC \R {2 \log N_g} \NR[+]
+\NC \gamma = \NC \R {2 \log N_h} \NR[+]
 }
@@
 And call
-\startitemize
-\item \m {\MC {A}} be the largest \m {s} position of \m {g}.
-\item \m {\MC {B}} be the largest \m {s} position of \m {d_{T\SB {N_g} -\MC {A}}}.
-\item \m {\MC {C} =T \RB {N_g} -\MC {A}}, i.e., the complementary index set of \m {\MC {A}}.
+\startitemize [1]
+\item \m {\Mc {A}} be the largest \m {s} position of \m {g}.
+\item \m {\Mc {B}} be the largest \m {s} position of \m {d_{T\SB {N_h} -\Mc {A}}}.
+\item \m {\Mc {C} =T \RB {N_h} -\Mc {A}}, i.e., the complementary index set of \m {\Mc {A}}.
 \stopitemize
 
-Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \RB {N_1, N_2 }}.
-For brevity, let \m {\MC {T} \subset T \RB {N_2 }}.
-Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
-Let \m {S:\; \MB {V}_{\MB {K}} \SB {N} \mapsto \MB {V}_{\MB {K}} \SB {N}}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} \SB {N})}, so that
+Suppose \m {\M {A} \in \Mb {M}_{\Mb {K}} \RB {N_1, N_2 }}.
+For brevity, let \m {\Mc {T} \subset T \RB {N_2 }}.
+Denote as \m {\M {A}_{\Mc {T}}} the columns of \m {\M {A}} having indices in \m {\Mc {T}}.
+Let \m {S:\; \Mb {V}_{\Mb {K}} \SB {N} \mapsto \Mb {V}_{\Mb {K}} \SB {N}}, \m {N \in \Mb {N}}, be the sorting function for \m {x \in \Mb {V}_{\Mb {K}} \SB {N})}, so that
 \Disp {
@@
 {
-Let function \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}, be given.
-For \m {x \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
+Let function \m {f:\; T\RB {N} \mapsto \Mb {R}_+}, \m {N \in \Mb {N}}, be given.
+For \m {x \in \Mb {V}_{\Mb {K}} \SB {N}}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
 \Disp {
@@
 {
-For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
+For \m {\V {x} \in \Mb {V}_{\Mb {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
 \Disp {
@@
 \NC D \SB {\f'}
-:= \NC \Nm { \sum_{n=0}^{N_H-1} \RM {e}^{i n \f'} } \NR
+:= \NC \Nm { \sum_{n=0}^{N_H-1} \Mr {e}^{i n \f'} } \NR
 \NC = \NC \F {\Nm {\sin \SB {N_H \f'/2}}}{\Nm {\sin \SB {\f' /2}}}, \NR[+]
@@
 \Disp {
-\NC \sin x = \NC x -\F {x^3}{6} + \MC {O} \SB {x^5}, \quad x \ll 1 \NR
+\NC \sin x = \NC x -\F {x^3}{6} + \Mc {O} \SB {x^5}, \quad x \ll 1 \NR
 }
@@
 \Disp {
-\NC \RB {\M {K}^\H \V {a} \SB {\f}} \DB {k}
+\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {k}
 =\NC \F {1}{N_H} D \RB {\f -\F {2 \pi k} {N_H}} \NR
@@
 {
-For \m {\MC {T}, \MC {T}' \subset \{1, \dots, N_p\}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} >0} to be the smallest such that
+For \m {\Mc {T}, \Mc {T}' \subset \{1, \dots, N_p\}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} >0} to be the smallest such that
 %
 \Disp {
-\NC \Nm {\IP {P_{\MC {T}} h, P_{\MC {T}'} h'}}
+\NC \Nm {\IP {P_{\Mc {T}} h, P_{\Mc {T}'} h'}}
 \leq \NC \tau_{s, s'} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
@@
 \Disp {
-\NC \VNm {\V {d}_{\MC {C}}} _1
-\leq \NC \VNm {\V {d}_{\MC {A}}} _1 +2\VNm {\V {g}_{\MC {C}}} _1 \NR
+\NC \VNm {\V {d}_{\Mc {C}}} _1
+\leq \NC \VNm {\V {d}_{\Mc {A}}} _1 +2\VNm {\V {g}_{\Mc {C}}} _1 \NR
 }
@@
 
-To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}},
+To show this, observe that with triangle inequality applied respectively on \m {\Mc {A}} and \m {\Mc {C}},
 \Disp {
 \NC \VNm {\V {g}} _1
--\VNm {\V {d}_{\MC {A}}} _1
-+\VNm {\V {d}_{\MC {C}}} _1
--\VNm {\V {g}_{\MC {C}}} _1
+-\VNm {\V {d}_{\Mc {A}}} _1
++\VNm {\V {d}_{\Mc {C}}} _1
+-\VNm {\V {g}_{\Mc {C}}} _1
 \leq \NC \VNm {\V {g} +\V {d}} _1 \NR
 }
-In the first line, we recall \m {\V {g} =\V {g}_{\MC {A}}}.
+In the first line, we recall \m {\V {g} =\V {g}_{\Mc {A}}}.
 On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
@@
 \NC \Nm {\IP { \V {z}, \M {P} \DB {:, n_g} }}
-\leq \NC  2 \R {\log N_g},
-\quad n_g =1, \dots, N_g. \NR
+\leq \NC  2 \R {\log N_h},
+\quad n_g =1, \dots, N_h. \NR
 }
@@
 \NC Q\SB {x}
-\leq \NC \F {1}{2} \RM {e}^{-x^2/2} \NR
+\leq \NC \F {1}{2} \Mr {e}^{-x^2/2} \NR
 }
-Particularly, for \m {x =\R {2 \log N_g}}, according to CLT,
+Particularly, for \m {x =\R {2 \log N_h}}, according to CLT,
 \Disp {
-\NC Q\SB {\R {2 \log N_g}}
-=\NC \F {1}{N_g}. \NR
+\NC Q\SB {\R {2 \log N_h}}
+=\NC \F {1}{N_h}. \NR
 }
@@
 \Disp {
-\NC \VNm {\M {P}^\H \M {P} \V {d}} _\infty
-\leq \NC  4 \R {\log N_g},
-\quad n_g =1, \dots, N_g. \NR
+\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
+\leq \NC  4 \R {\log N_h},
+\quad n_g =1, \dots, N_h. \NR
 }
@@
 \Disp {
-\NC \VNm { \M {P} \DB {:,n_y}^\H \RB {\V {y} -\M {P} \hat {\V {g}}} } 
-\leq \NC \VNm { \M {P}^\H \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty \NR
-\NC \leq \NC 2\R {\log N_g} \NR
+\NC \VNm { \M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } 
+\leq \NC \VNm { \M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty \NR
+\NC \leq \NC 2\R {\log N_h} \NR
 }
@@
 \Disp {
-\NC \VNm {\M {P} \DB {:,n_y}^\H \M {P} \V {d}} 
+\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} 
 \leq \NC \VNm {\IP { \V {z}, \M {P} \DB {:,n_y} }}  +\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y} } \NR
-\NC \leq \NC 2 \R {\log N_g} +2 \R {\log N_g} \NR
+\NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
 }
@@
 \Disp {
-\NC \VNm {\M {P}^\H \M {P} \V {d}} _\infty
-\leq \NC 4 \R {\log N_g}. \NR
+\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
+\leq \NC 4 \R {\log N_h}. \NR
 }
@@
 \Disp {
-\NC \VNm {\V {d}_{\MC {AB}}} _2
-\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{C}} _1 \NR
+\NC \VNm {\V {d}_{\Mc {AB}}} _2
+\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\Mc {A} \Mc {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{C}} _1 \NR
 }
@@
 \NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
+\leq \NC \VNm {\V {d}_{\Mc {A} \Mc {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\Mc {C}}} _1^2 \NR
 }
@@
 \Disp {
-\NC \VNm {\M {P}_{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
+\NC \VNm {\M {P}_{\Mc {A} \Mc {B}}^\Tr \M {P} \V {d}} _2
 \leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
-\NC \leq \NC \R {N_g} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
-\NC \leq \NC 4 \R {N_g \log N_g} \NR
+\NC \leq \NC \R {N_h} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
+\NC \leq \NC 4 \R {N_h \log N_h} \NR
 }
@@
 \leq \NC \R {L} \VNm { \V {d}_{A} } _2 \NR
-\NC \leq \NC \R {L} \VNm { \V {d}_{\MC {AB}} } _2 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1 +\F {4} {1-\d_{2L}} \R {L N_g \log N_g} \NR
+\NC \leq \NC \R {L} \VNm { \V {d}_{\Mc {AB}} } _2 \NR
+\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\Mc {C}} } _1 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
 }
 
-As the next step, we must eliminate \m {\VNm {d_{\MC {A}}} _1} in rhs of Lemma ().
+As the next step, we must eliminate \m {\VNm {d_{\Mc {A}}} _1} in rhs of Lemma ().
 \Disp {
-\NC \VNm { \V {d}_{\MC {C}} } _1
-\leq \NC \VNm { \V {d}_{\MC {A}} } _1 +2 \VNm { \V {g}_{\MC {C}} } _1 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1
-+2 \VNm { \V {g}_{\MC {C}} } _1
-+\F {4} {1-\d_{2L}} \R {L N_g \log N_g} \NR
+\NC \VNm { \V {d}_{\Mc {C}} } _1
+\leq \NC \VNm { \V {d}_{\Mc {A}} } _1 +2 \VNm { \V {g}_{\Mc {C}} } _1 \NR
+\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\Mc {C}} } _1
++2 \VNm { \V {g}_{\Mc {C}} } _1
++\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
 }
@@
 \Disp {
-\NC \VNm { \V {d}_{\MC {C}} } _1
-\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g}_{\MC {C}} } _1
-+\F {4} {1-\d_{2L} -\d_{3L}} \R {L N_g \log N_g} \NR
+\NC \VNm { \V {d}_{\Mc {C}} } _1
+\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g}_{\Mc {C}} } _1
++\F {4} {1-\d_{2L} -\d_{3L}} \R {L N_h \log N_h} \NR
 }
@@
 \NC \VNm { \V {d} } _2^2
-\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
-\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d}_{\MC {C}}} _1^2
-+\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_g \log N_g} \VNm {\V {d}_{\MC {C}}} _1 \NR
-\NC \NC \quad +\F {16}{\RB {1-\d_{2L}}^2} N_g \log N_g \NR
+\leq \NC \VNm {\V {d}_{\Mc {A} \Mc {B}}} _2^2 +\F {1}{L} \VNm {\V {d}_{\Mc {C}}} _1^2 \NR
+\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d}_{\Mc {C}}} _1^2
++\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_h \log N_h} \VNm {\V {d}_{\Mc {C}}} _1 \NR
+\NC \NC \quad +\F {16}{\RB {1-\d_{2L}}^2} N_h \log N_h \NR
 }
-Finally, plug in the bound for \m {\VNm {\V {d}_{\MC {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d}_{\MC {C}}} _1}.
+Finally, plug in the bound for \m {\VNm {\V {d}_{\Mc {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d}_{\Mc {C}}} _1}.
 There are several dozens of terms if we expand all.
@@
 \NC 1 \ll \NC L \NR
-\NC \ll \NC N_g \NR
+\NC \ll \NC N_h \NR
 }

### 2019-03-14 ongoing/report/4_simulation.tex
Simulation: Rev block matrix notation

--- 2019-03-05 ongoing/report/4_simulation.tex
@@
 
-As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} (h)}.
+As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\Mc {R} \SB {h}}.
 But it is not the end.
@@
 
-\startsection [title={Transformation into Second Order Cone Problem}]
+\startsection [title={Transformation of the Problem}]
+
+\startsubsection [title={Representation by Real Matrices}]
 
@@
 {
-For \m {x \in \MB {V} (M)}, we say \m {\MC {R} (x)} is the real representation of \m {x}, defined by
+For \m {x \in \Mb {V} \SB {M}}, we say that \m {\Mc {R} \SB {x}} is the real representation of \m {x}, defined by
 %
 \Disp {
-\NC \MC {R} (x) \in \NC \MB {V} (2M) \NR[+]
-\NC \MC {R} (x) \DB {m} =
+\NC \Mc {R} \SB {x} \in \NC \Mb {V} \SB {2M} \NR[+]
+\NC \Mc {R} \SB {x} \DB {m} =
 \NC \startcases
-\MF {Re} (\MC {R} (x)\DB {m}), \quad \MC m =2m' \NR
-\MF {Im} (\MC {R} (x)\DB {m}), \quad \MC m =2m'+1 \NR
+\NC \Mf {Re} \SB {\Mc {R} \SB {x} \DB {m'}}, \MC m =2m' \NR
+\NC \Mf {Im} \SB {\Mc {R} \SB {x} \DB {m'}}, \MC m =2m'+1 \NR
 \stopcases \NR[+]
-\NC m' \NC =  1, \dots, M \NR
+\NC m' = \NC  1, \dots, M \NR
 }
@@
 {
-For \m {A \in \MB {M}_{\MB {C}} (M_1, M_2)}, we say \m {\MC {R} (A)} is the real representation of \m {A}, defined by
+For \m {A \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {A}} is the real representation of \m {A}, defined by
 %
 \Disp {
-\NC A \in \NC \MB {V}_{\MB {R}} (2M_1, 2M_2) \NR[+]
-\NC A (m_1,m_2) =
+\NC A \in \NC \Mb {V}_{\Mb {R}} \SB {2M_1, 2M_2} \NR[+]
+\NC A \DB {m_1,m_2} =
 \NC \startcases
-\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR
-\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'-1  \NR
--\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR
-\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'  \NR
+\NC \Mf {Re} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
+\NC \Mf {Im} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
+\NC -\Mf {Im} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
+\NC \Mf {Re} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
 \stopcases \NR[+]
-\NC m_1' \NC = 1, \dots, m_1 \NR[+]
-\NC m_2' \NC = 1, \dots, m_2 \NR
+\NC m_1' = \NC 1, \dots, m_1 \NR[+]
+\NC m_2' = \NC 1, \dots, m_2 \NR
 }
@@
 \NC \V {\T {y}}
-\NC = \MC {R} (y)
-\in \MB {V} (N_h) \NR[+]
+= \NC \Mc {R} \SB {y}
+\in \Mb {V} \SB {2N_y} \NR[+]
 \NC \V {\T {g}}
-\NC = \MC {R} (g)
-\in \MB {V} (N_h) \NR[+]
+= \NC \Mc {R} \SB {g}
+\in \Mb {V} \SB {2N_h} \NR[+]
 \NC \M {\T {P}}
-\NC = \MC {R} (\M {P})
-\in \MB {M}_{\MB {C}} (2 N_y^2, 2 N_h^2) \NR
+= \NC \Mc {R} \SB {\M {P}}
+\in \Mb {M}_{\Mb {C}} \SB {2N_y, 2N_h} \NR[+]
+\NC \V {\T {z}}
+= \NC \Mc {R} \SB {\V {z}} \in \Mb {V} \SB {2N_y} \NR[+]
 }
 %
-such that
+such that, by construction,
 %
 \Disp {
-\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
-}
-%
-where by construction
-%
-\Disp {
-\NC \V {\T {z}}
-\NC = \MC {R} (\V {z}) \in \MB {V} (N_y) \NR
+\NC \V {\T {y}} = \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}}
 }
@@
 \Disp {
-\NC \M {I}_{n_y}^{(y)} \in \NC \MB {M}_{\MB {R}} (2N_y^2, 2N_y^2) \NR[+]
-\NC \M {I}_{n_y}^{(y)} (n_y')
-\NC =
+\NC {\T {\M {u}}}_{n_y}^{(y)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_y} \NR
+\NC {\T {\M {u}}}_{n_y}^{(y)} \DB {m_y}
+= \NC
 \startcases
-1, \quad \MC n_y' =2n_y \NR[+]
-1, \quad \MC n_y' =2n_y +1 \NR[+]
-0, \quad \NC otherwise
+1, \quad \MC m_y =2n_y \NR
+1, \quad \MC m_y =2n_y +1 \NR
+0, \quad \NC {\rm otherwise}
 \stopcases \NR[+]
-\NC \M {I}_{n_h}^{(h)} \in \NC \MB {M}_{\MB {R}} (2N_h^2, 2N_h^2) \NR[+]
-\NC \M {I}_{n_h}^{(h)} (n_h')
-\NC =
+\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
+\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {m_h, m_h'}
+= \NC
 \startcases
-1, \quad \MC n_h' =2n_h \NR[+]
-1, \quad \MC n_h' =2n_h +1 \NR[+]
-0, \NC otherwise
+1, \quad \MC m_h =2n_h,\; m_h' =2n_h \NR
+1, \quad \MC m_h =2n_h +1,\; m_h' =2n_h \NR
+1, \quad \MC m_h =2n_h,\; m_h' =2n_h +1\NR
+1, \quad \MC m_h =2n_h +1,\; m_h' =2n_h +1 \NR
+0, \quad \NC {\rm otherwise}
 \stopcases \NR[+]
-\NC n_y \NC = 1, \dots, N_y \NR[+]
-\NC n_h \NC = 1, \dots, N_h \NR
+\NC n_y, m_y = \NC 1, \dots, N_y \NR
+\NC n_h, m_h, m_h' = \NC 1, \dots, N_h \NR
 }
@@
 
-If we introduce vector \m {\V {m}} to denote the entrywise complex modulus, we see that Program () now take the form
-
-\Result
-{Program}
-{
-Given are \m {\T {\M {P}}, \T {\V {y}}, \gamma}.
-Find \m {\T {\V {g}}} with
-%
+If we introduce vector \m {\V {m} \in \Mb {M}_{\Mb {V}} \SB {N_y}} to denote the entrywise complex modulus, we see that the convex optimization now take the form
 \Disp {
 \NC \T {\V {g}}
-\NC = \startcases
+= \NC \startcases
 \NC \Min {\T {\V {g}}, \V {m}} \quad
 \MC \IP { \V {1}, \V {m} } \NR
-\NC \RM {subject} \; \RM {to} \quad
-\MC \VNm { \M {I}_{n_h}^{(h)} \T {\V {g}} }_2
-\leq \IP { \V {y}_{n_h}, \V {m} } \NR
-\NC \MC \VNm { \M {I}_{n_y}^{(y)} \T {\M {P}}^\H \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } }_2
+\NC \Mr {subject} \; \Mr {to} \quad
+\MC \VNm { \M {U}_{n_h}^{(h)} \T {\V {g}} }_2
+\leq \IP { \V {u}_{n_h}, \V {m} } \NR
+\NC \MC \VNm { \M {U}_{n_y}^{(y)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } }_2
 \leq \gamma \NR
@@
 }
-%
-where \m {\V {1}} is the all-1 vector.
+where \m {\V {1} \in \Mb {M}_{\Mb {V}} \SB {N_y}} is the all-1 vector.
+
+\stopsubsection
+
+\startsubsection [title={Second Order Cone Problem}]
+
+We shall see furthermore that the program can be cast into an SOCP.
+To make the point clearer, we rewrite Program () into a stricter, extended block matrix form
+\Result
+{Algorithm}
+{
+\startitemize[n]
+\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_h}}, \m{\gamma \geq 0}.
+\item Input \m{\hat {\M {P}} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\hat {\V {y}} \in \Mb {V}_{\Mb {C}} \SB {N_h}}.
+\item Calculate
+\item Output \m {\hat {\M {H}}}.
+\stopitemize
 }
-
-The program, we see, is an SOCP.
-
-We further rewrite Program () into a stricter, extended block matrix form to make the point clearer.
-
-\color[red]{(To be done)}
 
@@
 To clarify notation and for complentess of exposition, we derive the dual problem here.
-Start with the Lagrangian \m {\MC {L}}, where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \m {\ell_2}-norm constraint.
+Start with the Lagrangian \m {\Mc {L}}, where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \m {\ell_2}-norm constraint.
 
@@
 \Disp {
-\NC \NC \MC {L} (\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NR[+]
-\NC \NC = \IP {\V {1}, \V {m}}
+\NC \NC \Mc {L} \SB {\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}} \NR[+]
+\NC = \NC \IP {\V {1}, \V {m}}
 +\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M {g}}} -\lambda^{(h)} \IP {\V {y}_{n_h}, \V {m}}} \NR[+]
-\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\H ( \T {\M {P}} \T {\V {g}} -\T {\V {y}} ) } -\lambda^{(h)} \gamma} \NR[+]
+\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } } -\lambda^{(h)} \gamma} \NR[+]
 }

### 2019-03-14 ongoing/code/src/Classes.py

@@ -1,20 +1,40 @@
-class Ddss:
+import numpy as np
+import Constants as cst
 
+class Ddss:
     def __init__(self, pp, y, gG):
         self.pp = pp
         self.y = y
         self.gG = gG
 
-def run(self):
-g = cp.Variable(n)
-m = cp.Variable(n)
-i = np.ones()
-socp_constr = (cvx.norm(A*x + b, 2) <= c.T*x + d)
-objective = cp.Minimize (i*m)
-constraints = [0 <= x, x <= 1]
-prob = cp.Problem(objective, constraints)
+    def run(self):
+        g = cp.Variable(n)
+        m = cp.Variable(n)
+        i = np.ones()
+        socp_constr = (cvx.norm(A*x + b, 2) <= c.T*x + d)
+        objective = cp.Minimize (i*m)
+        constraints = [0 <= x, x <= 1]
+        prob = cp.Problem(objective, constraints)
+        self.sol = prob.solve()
 
+class Oommpp:
+    def __init__(self):
+        pass
 
+class Hh:
+    def __init__(self):
+        
 
-self.sol = prob.solve())
+class Ff_b:
+    def __init__(self):
+        np.random.normal();
 
+class Ff_r:
+    def __init__(self, len1, len2):
+        
+class Ww_b:
+    def __init__(self, len1, len2):
+
+class Ww_r:
+    def __init__(self, len1, len2):
+        

### 2019-03-14 ongoing/code/src/Functions.py

@@ -1,1 +1,9 @@
+def a1():
+    print(1)
 
+
+def a2():
+    print(2)
+
+def a3():
+    print(3)

### 2019-03-14 ongoing/report/make.sh

@@ -1,3 +1,5 @@
 #!/usr/bin/env bash
 
 context main.tex
+cp -f main.pdf main_1.pdf
+cp -f main.pdf main_2.pdf

### 2019-03-22 dantzig_selector/report/4_simulation.tex
Set & correct simulation variables

--- 2019-03-14 ongoing/report/4_simulation.tex
@@
 
-\startsection [title={Transformation of the Problem}]
-
-\startsubsection [title={Representation by Real Matrices}]
+\startsection [title={Representation by Real Matrices}]
 
@@
 \NC \startcases
-\NC \Mf {Re} \SB {\Mc {R} \SB {x} \DB {m'}}, \MC m =2m' \NR
-\NC \Mf {Im} \SB {\Mc {R} \SB {x} \DB {m'}}, \MC m =2m'+1 \NR
+\NC \Mf {Re} \SB {x \DB {m'}}, \MC m =2m' \NR
+\NC \Mf {Im} \SB {x \DB {m'}}, \MC m =2m'+1 \NR
 \stopcases \NR[+]
-\NC m' = \NC  1, \dots, M \NR
+\NC m' \NC =  1, \dots, M \NR
 }
@@
 \Disp {
-\NC A \in \NC \Mb {V}_{\Mb {R}} \SB {2M_1, 2M_2} \NR[+]
-\NC A \DB {m_1,m_2} =
+\NC \Mc {R} \SB {A} \in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR[+]
+\NC \Mc {R} \SB {A} \DB {m_1,m_2} =
 \NC \startcases
-\NC \Mf {Re} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
-\NC \Mf {Im} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
-\NC -\Mf {Im} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
-\NC \Mf {Re} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
+\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
+\NC \Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
+\NC -\Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
+\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
 \stopcases \NR[+]
-\NC m_1' = \NC 1, \dots, m_1 \NR[+]
-\NC m_2' = \NC 1, \dots, m_2 \NR
+\NC m_1' \NC = 1, \dots, M_1 \NR
+\NC m_2' \NC = 1, \dots, M_2 \NR
 }
@@
 \Disp {
-\NC \V {\T {y}}
-= \NC \Mc {R} \SB {y}
-\in \Mb {V} \SB {2N_y} \NR[+]
-\NC \V {\T {g}}
-= \NC \Mc {R} \SB {g}
-\in \Mb {V} \SB {2N_h} \NR[+]
-\NC \M {\T {P}}
-= \NC \Mc {R} \SB {\M {P}}
-\in \Mb {M}_{\Mb {C}} \SB {2N_y, 2N_h} \NR[+]
-\NC \V {\T {z}}
-= \NC \Mc {R} \SB {\V {z}} \in \Mb {V} \SB {2N_y} \NR[+]
+\NC \T {\V {y}}
+\NC = \Mc {R} \SB {\V {y}}
+\in \Mb {V}_{\Mb {R}} \SB {2N_y} \NR[+]
+\NC \T {\V {g}}
+\NC = \Mc {R} \SB {\V {g}}
+\in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR[+]
+\NC \T {\M {P}}
+\NC = \Mc {R} \SB {\M {P}}
+\in \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_h} \NR[+]
+\NC \T {\V {z}}
+\NC = \Mc {R} \SB {\V {z}} \in \Mb {V}_{\Mb {R}} \SB {2N_y} \NR[+]
 }
@@
 \Disp {
-\NC \V {\T {y}} = \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}}
+\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
 }
@@
 \Disp {
-\NC {\T {\M {u}}}_{n_y}^{(y)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_y} \NR
-\NC {\T {\M {u}}}_{n_y}^{(y)} \DB {m_y}
-= \NC
+\NC {\V {u}}_{n_h}^{(h)} \in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR[+]
+\NC {\V {u}}_{n_h}^{(h)} \DB {n_h'}
+\NC =
 \startcases
-1, \quad \MC m_y =2n_y \NR
-1, \quad \MC m_y =2n_y +1 \NR
+1, \quad \MC n_h' =n_h \NR
 0, \quad \NC {\rm otherwise}
 \stopcases \NR[+]
-\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
-\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {m_h, m_h'}
-= \NC
+\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR[+]
+\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {n_h', n_h''}
+\NC =
 \startcases
-1, \quad \MC m_h =2n_h,\; m_h' =2n_h \NR
-1, \quad \MC m_h =2n_h +1,\; m_h' =2n_h \NR
-1, \quad \MC m_h =2n_h,\; m_h' =2n_h +1\NR
-1, \quad \MC m_h =2n_h +1,\; m_h' =2n_h +1 \NR
+1, \quad \MC n_h' =2n_h -1,\; n_h'' =2n_h -1 \NR
+1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h -1 \NR
+1, \quad \MC n_h' =2n_h -1,\; n_h'' =2n_h \NR
+1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
 0, \quad \NC {\rm otherwise}
 \stopcases \NR[+]
-\NC n_y, m_y = \NC 1, \dots, N_y \NR
-\NC n_h, m_h, m_h' = \NC 1, \dots, N_h \NR
+\NC n_h, n_h', n_h'' \NC = 1, \dots, N_h \NR
 }
-%
+Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
+Now, if we introduce vector \m{\V{m}}
 
-If we introduce vector \m {\V {m} \in \Mb {M}_{\Mb {V}} \SB {N_y}} to denote the entrywise complex modulus, we see that the convex optimization now take the form
+\Disp{
+\NC \V {m} \NC \in \Mb {V}_{\Mb {R}} \SB {N_h} \NR[+]
+\NC \V{m} \DB{n_h}
+\NC =\Nm{\V{g} \DB{n_h}} \NR[+]
+\NC n_h, n_h', n_h'' \NC = 1, \dots, N_h \NR
+}
+
+to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now take the form
 \Disp {
-\NC \T {\V {g}}
-= \NC \startcases
-\NC \Min {\T {\V {g}}, \V {m}} \quad
+\NC \Hat {\T {\V {g}}}
+\NC = \startcases
+\NC \Min {\T {\V {g}}', \V {m}} \quad
 \MC \IP { \V {1}, \V {m} } \NR
 \NC \Mr {subject} \; \Mr {to} \quad
-\MC \VNm { \M {U}_{n_h}^{(h)} \T {\V {g}} }_2
+\MC \VNm { \T {\M {U}}_{n_h}^{(h)} \T {\V {g}}' }_2
 \leq \IP { \V {u}_{n_h}, \V {m} } \NR
-\NC \MC \VNm { \M {U}_{n_y}^{(y)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } }_2
-\leq \gamma \NR
-\stopcases \NR
+\NC \MC \VNm { \T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
+\leq \g \NR
+\stopcases \NR[+]
+\NC n_h \NC = 1, \dots, N_h \NR
 }
-where \m {\V {1} \in \Mb {M}_{\Mb {V}} \SB {N_y}} is the all-1 vector.
 
-\stopsubsection
+\stopsection
 
-\startsubsection [title={Second Order Cone Problem}]
+\startsection [title={Second Order Cone Programming}]
 
 We shall see furthermore that the program can be cast into an SOCP.
-To make the point clearer, we rewrite Program () into a stricter, extended block matrix form
+To make the point clearer, we rewrite Program () into a stricter, extended block matrix form, by defining auxiliary variables with dimension
+
+\Disp{
+\NC \V{t}_i
+\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
+\NC \V{x}_i
+\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
+\NC \M{A}_i
+\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_y +N_h} \NR[+]
+\NC \V{b}_i
+\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
+\NC \V{c}_i
+\NC \in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR[+]
+\NC d_i
+\NC \in \Mb {R} \NR[+]
+}
+
+defined below to be
+
+\Disp{
+\NC \V{t}
+\NC =\startthematrix
+\NC \V{0} \NR
+\NC \V{1} \NR
+\stopthematrix \NR[+]
+\NC \V{x}'
+\NC =\startthematrix
+\NC \T {\V {g}}' \NR
+\NC \V{m} \NR
+\stopthematrix \NR[+]
+}
+
+with
+
+\Disp{
+\NC \M{A}_i
+\NC =\startthematrix
+\NC \T {\M {U}}_{n_h}^{(h)}, \NC \M{0} \NR
+\stopthematrix \NR[+]
+\NC \V{b}_i
+\NC =\startthematrix
+\NC \V{0} \NR
+\NC \V{0} \NR
+\stopthematrix \NR[+]
+\NC \V{c}_i
+\NC =\startthematrix
+\NC \V{0} \NR
+\NC \V {u}_{n_h} \NR
+\stopthematrix \NR[+]
+\NC d_i
+\NC =0 \NR[+]
+\NC i \NC =1, 2, \dots, N_h \NR
+}
+
+And
+
+\Disp{
+\NC \M{A}_i
+\NC =\startthematrix
+\NC \T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
+\stopthematrix \NR[+]
+\NC \V{b}_i
+\NC =\startthematrix
+\NC -\T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \T {\V {y}} \NR
+\NC \V{0} \NR
+\stopthematrix \NR[+]
+\NC \V{c}_i
+\NC =\startthematrix
+\NC \V{0} \NR
+\NC \V{0} \NR
+\stopthematrix \NR[+]
+\NC d_i
+\NC =\g \NR[+]
+\NC i \NC =N_h +1, N_h +2, \dots, N_h +N_y \NR
+}
+
+The step that we convert \m {\Hat {\V {g}}} back is same as Algorithm () is same as before, but this is listed for sake of completeness.
+
 \Result
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_h}}, \m{\gamma \geq 0}.
-\item Input \m{\hat {\M {P}} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\hat {\V {y}} \in \Mb {V}_{\Mb {C}} \SB {N_h}}.
+\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_y}}, \m{\g \geq 0}.
+\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
 \item Calculate
-\item Output \m {\hat {\M {H}}}.
+\Disp{
+\NC \Hat {\V {x}}
+\NC = \startcases
+\NC \Min {\V {x}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}
+\MC \IP {\V {t}, \V {x}'} \NR[+]
+\NC \Mr {subject} \; \Mr {to}
+\quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
+\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
+\NC \MC i =1, 2, \dots, N_y +N_h \NR
+\stopcases \NR[+]
+}
+\item Extract
+\Disp{
+\NC \Hat{\T{\V{g}}} =\NC \Hat{\V{x}} \DB {1 : 2N_h} \NR[+]
+}
+\item Convert 
+\Disp{
+\NC \Hat{\V{g}} =\NC \Mc{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
+}
+\item Calculate
+\Disp {
+\NC \Hat {G} =\Mr {vec}^{-1} \SB {\Hat {g}} \NR[+]
+}
+\item Calculate
+\Disp {
+\NC \Hat {\M {H}} =\M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
+}
+\item Output \m {\Hat {\M {H}}}.
 \stopitemize
@@
 
-\startsection [title={Primal-Dual Interior Point Algorithm}]
+\stopsection
 
-It remains to convert primal-dual interior point algorithm to make the SOCP easier to calculate.
-Of course it is not the only way to do this.
-We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.11 as a standard reference, and ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of application to DS.
+\startsection [title={Simulation}]
 
-To clarify notation and for complentess of exposition, we derive the dual problem here.
-Start with the Lagrangian \m {\Mc {L}}, where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \m {\ell_2}-norm constraint.
+One can convert primal-dual interior point algorithm to make the SOCP easier to calculate.
+We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.\ 11 as a standard reference, and ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of SOCP applied to DS.
 
-%
-\Disp {
-\NC \NC \Mc {L} \SB {\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}} \NR[+]
-\NC = \NC \IP {\V {1}, \V {m}}
-+\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M {g}}} -\lambda^{(h)} \IP {\V {y}_{n_h}, \V {m}}} \NR[+]
-\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } } -\lambda^{(h)} \gamma} \NR[+]
-}
-%
+However, for brevity we use Python Library CVXPY to solve the SOCP.
+
+\stopsection
 
@@
 
-On the other hand, DS goes not without criticism for large complexity of it (Friedlander and Saunders 2007).
+On the other hand, DS goes not without criticism for its large complexity (Friedlander and Saunders 2007).
 Indeed it is clear, even from the primal-dual implementation above, that DS requires memory for large dimensional vector, but OMP does not.
@@
 
+\stopsection
+
 \stopchapter

### 2019-03-22 dantzig_selector/code/src/Classes.py

@@ -17,6 +17,8 @@ class Ddss:
         prob = cp.Problem(objective, constraints)
         self.sol = prob.solve()
 
+
+
 class Oommpp:
     def __init__(self):
         pass

### 2019-03-22 dantzig_selector/report/make.sh

@@ -1,5 +1,6 @@
 #!/usr/bin/env bash
 
+clear
 context main.tex
 cp -f main.pdf main_1.pdf
 cp -f main.pdf main_2.pdf

### 2019-04-22 dantzig_selector/report/1_introduction.tex
Set & correct simulation variables
Kronecker product identity proof

--- 2019-03-14 ongoing/report/1_introduction.tex
@@
 Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {\DB {m,n}}-entry of \m {\V {A}}
-Particularly, \m {\V {u}_n} is the \m {n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
+To better correspond to the pseudo code, the numbering of both vector and matrix entries are zero-based, that is, numbered from \m {0,1,2,\dots}.
+Especially when manipulating the indices, but also in the main proof of DS bound, we will encounter the modulo as operation, namely the remainder of \m {m} divided by \m {n}, with \m {m, n \geq 0}, and we use the capital \m {m\; \rm{Mod}\; n} to denote that number.
+And we denote \m {\V {u}_n} to be the \m {n}-th unit vector in the Cartesian coordinates, whose numbering is also zero-based.
 \m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
@@
 To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \Mb {N}} is much larger than the number of measurements \m {N_m \in \Mb {N}}, namely,
-%
+
 \Disp {
@@
 }
-%
+
 In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
@@
 \m {x \in \Mb {V}_{\Mb {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\Mc {A}}, \m {s <N_m}, if there is \m {\Mc {A} \subset T \RB {N_m}} such that
-%
+
 \Disp { 
@@
 For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \Mb {V}_{\Mb {K}} \SB {N_p}}, for all \m {\Mc {T} \subset T\SB {N_m}} with \m {\#\{\Mc {T} \} \leq s},
-%
+
 \Disp {
@@
 Now, consider a linear transformation with noise corruption,
-%
+
 \Disp {
@@
 }
-%
+
 where (w.l.o.g.) \m {z} is an i.i.d.\ normalized Gaussian vector.
@@
 \NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
-\NC \Mr {subject} \; \Mr {to} \quad \MC \VNm {\M {P}^\Adj \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \gamma \NR
+\NC \Mr {subject} \; \Mr {to} \quad \MC \VNm {\M {P}^\Adj \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \g \NR
 \stopcases \NR
@@
 Let each entry of random matrix \m {P \in \Mb {M}_\Mb {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
-Then, with \m {0 <\epsilon <1},
-%
+Then, with \m {0 <\e <1},
+
 \Disp {
-\NC \NC \Mb {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2} \NR
-\NC \leq \NC 2 \exp \SB {-n \RB {\epsilon^2/4 -\epsilon^3/6} } \NR
+\NC \NC \Mb {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \e \VNm {h} _2^2} \NR
+\NC \leq \NC 2 \exp \SB {-n \RB {\F {\e ^2} {4} -\F {\e ^3} {6}} } \NR
 }
@@
 Following the setting described above, suppose, for \m {0 <\d <1},
-%
+
 \Disp {
@@
 }
-%
+
 Then OMP (Algorithm \_\_) recovers \m {x} completely, with overwhelming probability \m {1-\d}.
@@
 
+\stopsection
+\startsection [title={OMP used in Channel Sensing}]
+
 For concreteness, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
 Let signal \m {\V {x}} be sent, and \m {\V {y}} be receiverd, that is
-%
+
 \Disp {
@@
 }
+
+% % % % % % % % % % % % % % % % % % % %
+
+%I want to show the Kronecker Product identity listed on [Wikipedia](https://en.wikipedia.org/wiki/Kronecker_product):
+%$$\begin{align}
+%\mathrm{vec}(AXB)
+%=(B^T \otimes A) \mathrm{vec}(X) \\ \tag{1}
+%\end{align}$$
+%Wikipedia does not cite references for the proof for (1), and I want to verify.
+%Before the calculation, agree with some convention.
+%Let us denote $a\; \mathrm{mod}\; b$ for the remainder of $a$ modulo $b$ (so that $9\; \mathrm{mod}\; 4 =1$).
+%This is unlike the usual practice, but otherwise the expression gets too verbose.
+%Moreover let us denote the $(i,j)$-th entry of $A$ to be $A_{i,j}$, and $i$-th entry of $v$ to be $v_{i}$.
+%Also say that $A \in \mathbb{R}^{M \cdot N}$ if it is a $M$ by $N$ matrix, by slightly abusing the meaning of $\mathbb{R}$.
+%If we stick to only addition and multiplication, once the proof works, it works for any field.
 %
+%Firstly, restate the formal definition of Kronecker product and vectorization, for later use.
+%For $X' \in \mathbb{R}^{N_2 \cdot N_3}$
+%$$\begin{align}
+%(\mathrm{vec}(X'))_{m_1}
+%=X'_{m_1\; \mathrm{mod}\; N_1, \lceil m_1/N_1 \rceil} \\ \tag{2}
+%\end{align}$$
+%
+%For $A' \in \mathbb{R}^{N_1 \cdot N_2}, B' \in \mathbb{R}^{N_3 \cdot N_4}$,
+%$$\begin{align}
+%(A' \otimes B')_{m_1, m_2}
+%=A'_{\lceil m_1/N_3 \rceil, \lceil m_2/N_4 \rceil}
+%B'_{m_1\; \mathrm{mod}\; N_3, m_2\; \mathrm{mod}\; N_4} \\ \tag{3}
+%\end{align}$$ 
+%
+%Now, let $A \in \mathbb{R}^{N_1 \cdot N_2},\; X \in \mathbb{R}^{N_2 \cdot N_3},\; B \in \mathbb{R}^{N_3 \cdot N_4},$,
+%We try to evaluate lhs and rhs of (1).
+%
+%$$\begin{align}
+%&(\mathrm{vec}(AXB))_{m_1} \\
+%=&(AXB)_{m_1\; \mathrm{mod}\; N_1, \lceil m_1/N_1 \rceil} \\
+%=&\sum_{n_2=1}^{N_2} \sum_{n_3=1}^{N_3}
+%A_{m_1\; \mathrm{mod}\; N_1, n_2} X_{n_2, n_3} B_{n_3, \lceil m_1/N_1 \rceil} \\ \tag{4}
+%\end{align}$$
+%
+%$$\begin{align}
+%&((B^T \otimes A) \mathrm{vec}(X) )_{m_1} \\
+%=&\sum_{m_2=1}^{N_2 N_3} (B^T \otimes A)_{m_1, m_2} \mathrm{vec}(X)_{m_2} \\
+%=&\sum_{m_2=1}^{N_2 N_3} (B^T)_{\lceil m_1/N_1 \rceil, \lceil m_2/N_2 \rceil}
+%A_{m_1\; \mathrm{mod}\; N_1, m_2\; \mathrm{mod}\; N_2} \mathrm{vec}(X)_{m_2} \\ 
+%=&\sum_{m_2=1}^{N_2 N_3} B_{\lceil m_2/N_2 \rceil, \lceil m_1/N_1 \rceil}
+%A_{m_1\; \mathrm{mod}\; N_1, m_2\; \mathrm{mod}\; N_2} X_{m_2\; \mathrm{mod}\; N_2, \lceil m_2/N_2 \rceil} \\ \tag{5}
+%\end{align}$$ 
+%
+%It would seem that we are close, but it is not obvious that (4) and (5) are equal.
+%Although $A$'s row index $m_1\; \mathrm{mod}\; N_1$ and $B$'s column index $\lceil m_1/N_1 \rceil$ agree, the other do not.
+%It is suggestive that maybe if we "sum away" $n_2, n_3$, we might find them to agree, but $A,X,B$ are all free, and we have nothing to exploit to carry out that summation.
+
+% % % % % % % % % % % % % % % % % % % %
 
 \Result
-{Definition}
+{Definition.}
 {
-Define \m {\Mr {vec} \SB {\M {A}} \in \Mb {K}^{NM}} to be the vectorization of \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}}.
+Define \m {\Mr {vec} \SB {\M {A}} \in \Mb {V}_{\Mb {K}} \SB {N_1, N_2}} to be the vectorization of \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}}.
+Formally,
+\Disp{
+\NC \RB {\Mr{vec} \SB {\M{A}}} \DB {m_1}
+=\NC \M{A} \DB {m_1\; \Mr{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR[+]
+}
 }
@@
 {
-For \m {\Mr {vec} \SB {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}} and \m {\Mr {vec} \SB {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}}
-Define the Kronecker product \m {\Mr {vec} \SB {A} \in \Mb {K}^{nm}} 
+For \m {\M{A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}} and \m {\M{B} \in \Mb {M}_{\Mb {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \Mb {M}_{\Mb {K}} \SB {N_1 N_3, N_2 N_4}} by
+\Disp{
+\NC \NC \RB {\M{A} \otimes \M{B}} \DB {m_1, m_2} \NR
+\NC =\NC \M{A} \DB {\Fl{ m_1/N_3 }, \Fl{ m_2/N_4 }}
+\M{B} \DB {m_1\; \Mr{Mod}\; N_3, m_2\; \Mr{Mod}\; N_4} \NR[+]
+}
 }
@@
 With (), scholars often exploit the relation
-%
+
+\Result
+{Lemma.}
+{
+Suppose \m {\M{A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}, \M{X} \in \Mb {M}_{\Mb {K}} \SB {N_2, N_3}, \M{B} \in \Mb {M}_{\Mb {K}} \SB {N_3, N_4}},
+Then
 \Disp {
-\NC \Mr {vec} \SB {Y}
-=\SB {\RB {F^\Adj} \otimes W} \Mr {vec} \RB {\M {H}} \NR
+\NC \mathrm{vec} \RB {\M{A}\M{X}\M{B}}
+= \NC \RB {\M{B}^\Tr \otimes \M{A}} \mathrm{vec} \SB {X} \NR
 }
-%
+}
+
+The proof is not particularly easy to find, and we show it here.
+We thus verify that arbitrary components of lhs and rhs agree.
+On one hand,
+
+\Disp{
+\NC \NC \RB {\Mr{vec} \SB {\M{A}\M{X}\M{B}}} \DB {m_1} \NR
+\NC = \NC \RB {\M{A}\M{X}\M{B}} \DB {m_1\; \Mr{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
+\NC = \NC \sum _{n_2=1} ^{N_2} \sum _{n_3=1} ^{N_3}
+\M{A} \DB {m_1\; \Mr{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR[+]
+}
+
+On the other hand,
+
+\Disp{
+\NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Mr{vec} \SB{\M{X}} } \DB {m_1} \NR
+\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Mr{vec} \SB {\M{X}} \DB {m_2} \NR
+\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
+\M{A} \DB {m_1\; \Mr{Mod}\; N_1, m_2\; \Mr{Mod}\; N_2} \Mr{vec} \SB {\M{X}} \DB {m_2} \NR 
+\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
+\M{A} \DB {m_1\; \Mr{Mod}\; N_1, m_2\; \Mr{Mod}\; N_2} \M{X} \DB {m_2\; \Mr{Mod}\; N_2, \Fl{ m_2/N_2 }} \NR[+]
+}
+
+In () and (), the row index of \m {\M{A}} and \m {\M{B}} already agree.
+The key observation is that when \m {n_2} runs through \m {0, \dots, N_2-1} and \m {n_3} runs through \m {0, \dots, N_3-1}, it follows \m {n_2 n_3} runs through \m {0, \dots, N_2 N_3-1}.
+We see two expressions are exactly the same, and we are done.
 

### 2019-04-22 dantzig_selector/report/2_problem_setting.tex
Set & correct simulation variables
Kronecker product identity proof

--- 2019-03-14 ongoing/report/2_problem_setting.tex
@@
 
-For clarity, we use \m {\O_t} to denote the event space of the transmitter end, \m {\O_h} to denote that of the communication channel itself, \m {\O_z} to denote that of the noise arising in the communication channel, and \m {\O_r} to denote that of the receiver end.
-It helps to think \m {\NC \O = \NC \O_t \times \O_h \times \O_n \times \O_r \NR} as the overall event space, though we will not really calculate Lebesgue integrals.
+Conceptually, we use \m {\O_t} to denote the event space of the transmitter end, \m {\O_h} to denote that of the communication channel itself, \m {\O_z} to denote that of the noise arising in the communication channel, and \m {\O_r} to denote that of the receiver end.
+It helps to think \m {\NC \O = \NC \O_t \times \O_h \times \O_n \times \O_r \NR} as the overall event space.
 
@@
 \NC \V {a} \SB {\psi'}
-= \NC \F {1}{\R {N_H}} \sum_{n=1}^{N} \Mr {e}^{n \psi' i} \V {u}_n
-\in \Mb {V}_\Mb {C} \SB {N_H} \NR
+\in \NC \Mb {V}_\Mb {C} \SB {N_H} \NR
+\NC \V {a} \SB {\psi'}
+= \NC \F {1}{\R {N_H}} \sum_{n=0}^{N-1} \Mr {e}^{n \psi' \Mr {i}} \V {u}_n \NR
 }
-where \m {\Mr {e}} is the base of natural logarithm, and \m {i} the imaginary unit.
+where \m {\Mr {e}} is the base of natural logarithm, and \m {\Mr {i}} the imaginary unit.
 
@@
 \Disp {
-\NC H
-=\sum_{l=1}^L \alpha_l \V {a} \SB { \F {d} {\lambda} \sin \f_l' } \V {a} \SB { \F {d_{\Mr {arr}}} {\lambda} \sin \th_l' }^\Adj \NR
+\NC \M{H}
+=\sum_{l=1}^L \alpha_l \V {a} \SB { \F {d_{\Mr {arr}}} {\lambda} \sin \f_l' } \V {a} \SB { \F {d_{\Mr {arr}}} {\lambda} \sin \th_l' }^\Adj \NR
 }
@@
 \NC \f_l
-= \NC \F {d_{\Mr {arr}}} {\lambda} \sin \f_l' \NR[+]
+= \NC \F {d_{\Mr {arr}}} {\lambda} \sin \f_l' \quad \rm{Mod}\; (2\pi) \NR[+]
 \NC \th_l
-= \NC \F {d_{\Mr {arr}}} {\lambda} \sin \th_l' \NR[+]
+= \NC \F {d_{\Mr {arr}}} {\lambda} \sin \th_l' \quad \rm{Mod}\; (2\pi) \NR[+]
 }
@@
 \Disp {
-\NC H
-=\sum_{l=0}^L \alpha_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
-\in \Mb {M}_\Mb {C} \SB {N_H} \NR
+\NC \M{H}
+\in \NC \Mb {M}_\Mb {C} \SB {N_H} \NR
+\NC \M{H}
+=\NC \sum_{l=1}^L \alpha_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
 }
@@
 \Disp {
-\NC \M {F}_B \in  \NC \Mb {M}_{\Mb {C}} \SB {N_R, N_Y} \NR[+]
-\NC \M {F}_R \in  \NC \Mb {M}_{\Mb {C}} \SB {N_H, N_R} \NR[+]
-\NC \M {W}_R \in  \NC \Mb {M}_{\Mb {C}} \SB {N_R, N_H} \NR[+]
+\NC \M {F}_B \in \NC \Mb {M}_{\Mb {C}} \SB {N_R, N_Y} \NR
+\NC \M {F}_R \in \NC \Mb {M}_{\Mb {C}} \SB {N_H, N_R} \NR
+\NC \M {W}_R \in \NC \Mb {M}_{\Mb {C}} \SB {N_R, N_H} \NR
 \NC \M {W}_B \in \NC \Mb {M}_{\Mb {C}} \SB {N_Y, N_R} \NR[+]
@@
 \NC \Nm {\M {W}_R \DB {n_R, n_H}} = \NC 1, \NR[+]
-\NC n_H = \NC 1, \dots N_H, \NR
-\NC n_R = \NC 1, \dots N_R \NR
+\NC n_H = \NC 0, \dots N_H-1, \NR
+\NC n_R = \NC 0, \dots N_R-1 \NR
 }
@@
 \NC \V {h}
-:= \NC \Mr {vec} \SB {\M {H}}
-\in \Mb {V}_{\Mb {C}} \SB {N_h} \NR[+]
+\in \NC \Mb {V}_{\Mb {C}} \SB {N_h} \NR
+\NC \V {h}
+:= \NC \Mr {vec} \SB {\M {H}} \NR[+]
 \NC \V {y}
-:= \NC \Mr {vec} \SB {\M {Y}}
-\in \Mb {V}_{\Mb {C}} \SB {N_y} \NR[+]
+\in \NC \Mb {V}_{\Mb {C}} \SB {N_y} \NR
+\NC \V {y}
+:= \NC \Mr {vec} \SB {\M {Y}} \NR[+]
 \NC \V {z}
-:= \NC \Mr {vec} \SB {\M{W}_B \M{W}_R \M {Z}}
-\in \Mb {V}_{\Mb {C}} \SB {N_y} \NR[+]
+\in \NC \Mb {V}_{\Mb {C}} \SB {N_y} \NR
+\NC \V {z}
+:= \NC \Mr {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR[+]
 \NC \M {P}^\star
-:= \NC \RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R}
-\in \Mb {M}_{\Mb {C}} \SB {N_y, N_h} \NR[+]
+\in \NC \Mb {M}_{\Mb {C}} \SB {N_y, N_h} \NR
+\NC \M {P}^\star
+:= \NC \RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR[+]
 }
@@
 \NC \M {K} \in  \NC \Mb {M}_{\Mb {C}} \SB {N_H, N_H} \NR
-\NC \M {K} \DB {n_1, n_2} = \NC \F {1} {\R {N_H}} \Mr {e}^{2\pi i n_1 n_2 /N_H}, \NR[+]
+\NC \M {K} \DB {n_1, n_2} = \NC \F {1} {\R {N_H}} \Mr {e}^{2\pi \Mr{i} n_1 n_2 /N_H}, \NR[+]
 \NC \quad n_1, n_2 = \NC 0, 1, \dots, N_H-1 \NR
 }
-where recall that we have
+Roman \m{\Mr{e}} and \m{\Mr{i}} denote the natural base and imaginary unit, respectively.
+Here recall that we have
 \Disp{
 \NC \M {K}^\Adj \M {K}
-= \NC \M {I} \NR
+= \NC \M {I} \NR[+]
 }
@@
 \NC \M {G}
-=\M {K}^\Adj \M {H} \M {K} \NR
+=\NC \M {K}^\Adj \M {H} \M {K} \NR[+]
 }
@@
 \NC \M {Y}
-=\M {W}_B \M {W}_R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F}_R \M {F}_B
-+\M {W}_B \M {W}_R \M {Z}
-\in \Mb {M}_{\Mb {C}} \SB {N_Y, N_Y} \NR
+\in \NC \Mb {M}_{\Mb {C}} \SB {N_Y, N_Y} \NR
+\NC \M {Y}
+=\NC \M {W}_B \M {W}_R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F}_R \M {F}_B
++\M {W}_B \M {W}_R \M {Z} \NR[+]
 }
@@
 \NC \M {P}
-:=\RB {\M {F}_B^\Tr \M {F}_R^\Tr K^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}
-\in \Mb {M}_{\Mb {C}} \SB {N_y, N_h} \NR
+\in \NC \Mb {M}_{\Mb {C}} \SB {N_y, N_h} \NR
+\NC \M {P}
+:=\NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr K^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}} \NR[+]
 }
@@
 \NC \V {g}
-:= \NC \Mr {vec} \SB {\M {G}}
-\in \Mb {M}_{\Mb {C}} \SB {N_h} \NR[+]
+\in \NC \Mb {M}_{\Mb {C}} \SB {N_h} \NR
+\NC \V {g}
+:= \NC \Mr {vec} \SB {\M {G}} \NR[+]
 }
@@
 \NC \V {y}
-=\M {P} \V {g} +\V {z} \NR
+=\NC \M {P} \V {g} +\V {z} \NR[+]
 }
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_h}}, \m{\gamma \geq 0}.
+\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_h}}, \m{\g \geq 0}.
 \item Calculate
@@
 \NC \Min {\V {g}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR[+]
-\NC \Mr {subject} \; \Mr {to} \quad  \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \gamma \NR
+\NC \Mr {subject} \; \Mr {to} \quad  \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
 \stopcases \NR

### 2019-04-22 dantzig_selector/report/abstract.tex
Kronecker product identity proof

\starttitle [title={Abstract}]

Multiple-input-multiple-output (MIMO) is widely expected to be used in the next-generation wireless communication.
However, reliable communication in such r\`egime often desires that the channel state information be known at the receiver, necessary for example in beamforming algorithm and channel calibration, but it is usually not easy to estimate real-world wireless channel.

Meanwhile, the millimeter wave channel, which is usually used in tandem with MIMO, often exhibits sparse properties, if the sparsity is exploited, few observations may suffice to estimate the channel.
Such algorithm falls under the study of Compressive Sensing, an active area that has recently emerged.
A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context, and as originally perceived, it ideal in certain senses.
However, Orthogonal Matching Pursuit (OMP) later emerges as a solution with lower complexity, and following-up literature, as a result, usually used OMP rather than DS.
In this article, we consider a hybrid structure at both the transmitter and receiver end, each of them having both digital and analog percoders and combiners.
We argue in favor of DS, since DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, as well as in its tolerance of noise corruption.
Indeed, we shall refine Tao and Cand\'es's bound, and generalize under current settings, thus giving a viable solution for the estimation of millimeter wave channel.
Moreover, we show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.

\stoptitle

### 2019-04-22 dantzig_selector/code/src/Classes.py

@@ -1,42 +1,0 @@
-import numpy as np
-import Constants as cst
-
-class Ddss:
-    def __init__(self, pp, y, gG):
-        self.pp = pp
-        self.y = y
-        self.gG = gG
-
-    def run(self):
-        g = cp.Variable(n)
-        m = cp.Variable(n)
-        i = np.ones()
-        socp_constr = (cvx.norm(A*x + b, 2) <= c.T*x + d)
-        objective = cp.Minimize (i*m)
-        constraints = [0 <= x, x <= 1]
-        prob = cp.Problem(objective, constraints)
-        self.sol = prob.solve()
-
-
-
-class Oommpp:
-    def __init__(self):
-        pass
-
-class Hh:
-    def __init__(self):
-        
-
-class Ff_b:
-    def __init__(self):
-        np.random.normal();
-
-class Ff_r:
-    def __init__(self, len1, len2):
-        
-class Ww_b:
-    def __init__(self, len1, len2):
-
-class Ww_r:
-    def __init__(self, len1, len2):
-        

### 2019-04-22 dantzig_selector/code/src/Drawing.py

@@ -1,61 +1,0 @@
-import matplotlib.pyplot as plt # plotting functions
-import os # getcwd
-
-
-# to set axis & title
-#plt.close("all")
-fig =plt.figure()
-plt.title( "Simulated Annealing", fontsize =15 )
-plt.xlabel( "Time", fontsize =12 )
-plt.ylabel( "Rate", fontsize =12 )
-
-# to set plot style
-num_line_style =4
-list_line_style =['-', '--', '-.', ':'] # the larger, the thicker
-num_color =5
-list_color =['r', 'g', 'c', 'b', 'k'] # red, green, cyan, blue, black
-num_marker =6
-list_marker =['v', '^', 'o', 's', '*', 'D'] # triangle down, triangle up, circle, square, star, diamond
-size_width =3 # fixed line width
-size_marker =7 # fixed marker size
-
-vec_x =[] # to set empty list to enlarge its scope
-# split w/o arguments parses any number of spaces and tabs
-list_str =list_line[0]. split()
-for tmp_str in list_str:
-    # strip decimal mark to determine, whether a decimal number
-    if not tmp_str. replace('-',''). replace('.',''). isdigit():
-        continue
-    else:
-        vec_x.append(float(tmp_str))
-# end for
-list_line.pop(0)
-
-for idx, line in enumerate(list_line):
-    list_str =line.split()
-    if not list_str: # "list_str" is empty
-        continue
-    # end if empty
-
-    vec_y =[] # to create list to enlarge its scope
-    
-    for tmp_str in list_str:
-        # to strip decimal mark & minus sign to check whether a decimal number
-        if not (tmp_str. replace('-',''). replace('.',''). isdigit()):
-            continue
-        else:
-            vec_y.append(float(tmp_str))
-    # end for each word
-
-    plt.plot( vec_x, vec_y,
-            markersize =size_marker,
-            linewidth =size_width,
-            linestyle =list_line_style[ int( idx % num_line_style ) ],
-            color =list_color[ int( idx % num_color ) ],
-            marker =list_marker[ int( idx % num_marker ) ],
-            )
-# end for each line
-
-# to set legend and save figure
-fig.savefig( out_fig_path, bbox_inches ="tight" )
-

### 2019-04-22 dantzig_selector/code/src/algorithms.py

@@ -1,0 +1,57 @@
+import numpy as np
+import cvxpy as cp
+import constants as cst
+
+class Ddss(cst):
+    def __init__(self):
+        self.pp = np.ones ((cst.nn_y, cst.nn_h))
+        self.y = np.zeros ((cst.nn_y))
+        self.gG = float('inf')
+        self.g_h = np.zeros ((cst.nn_h))
+        self.hh_h = np.zeros ((cst.nn_hh, cst.nn_hh))
+
+    def set(self, pp, y, gG):
+        self.pp = pp
+        self.y = y
+        self.gG = gG
+
+    def run(self):
+
+t =np.zeros ((2*cst.nn_y)) +np.zeros ((cst.nn_h))
+
+for i in range(nn_h):
+    A.append ()
+    b.append ()
+    c.append ()
+    d.append ()
+
+for i in range(nn_h):
+    A.append ()
+    b.append ()
+    c.append ()
+    d.append ()
+
+# Define and solve the CVXPY problem.
+x = cp.Variable(n)
+# We use cp.SOC(t, x) to create the SOC constraint ||x||_2 <= t.
+soc_constraints = [cp.SOC (c[i].T @ x + d[i], A[i] @ x + b[i]) for i in range (nn_h+nn_y)]
+prob = cp.Problem(cp.Minimize(f.T@x),
+                  soc_constraints + [F@x == g])
+prob.solve()
+
+
+# Print result.
+print("The optimal value is", prob.value)
+print("A solution x is")
+print(x.value)
+for i in range(m):
+    print("SOC constraint %i dual variable solution" % i)
+    print(soc_constraints[i].dual_value)
+
+
+# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
+
+#class Oommpp:
+#    def __init__(self):
+#        pass
+

### 2019-04-22 dantzig_selector/code/src/helpers.py

@@ -1,0 +1,22 @@
+import numpy as np
+import constants as cst
+
+def arr_resp(pG, l)
+return [np.exp(1J*i*pG) for i in range(l)]
+
+def real_rep (v)
+    ret =np.zero (2*len(v))
+    for i in range(len(v))
+        ret[2*i] ==np.real(v[i])
+        ret[2*i+1] ==np.imag(v[i])
+    return ret
+
+def inv_real_rep (v)
+assert (len(v)%2==0)
+    for i in range (int (len(v)/2))
+
+
+def vec ()
+
+def inv_vec ()
+

### 2019-04-22 dantzig_selector/code/src/test.py

@@ -1,0 +1,50 @@
+import matplotlib.pyplot as plt # plotting functions
+import numpy as np
+import constants as cst
+#import os # getcwd
+#import cvxpy as cp
+
+a=[[1,2,3,4],[5,6,7,8]]
+#b=[[1,-1],[0,1]]
+#print(np.reshape(np.kron(a,b), (1,-1)))
+
+c=[1,2,3,4,5,6]
+#print (np.reshape(c, (2,-1))[0] +1J *np.reshape(c, (2,-1))[1])
+c1=a[:,0]
+#print (((np.reshape(c, (-1,2))).T)[0] +1J *((np.reshape(c, (-1.2))).T)[1])
+
+#y=[1+2j,2,3,4]
+#z1=[(y[2*i]) for i in range(2)]
+#z2=[(y[2*i+1]) for i in range(2)]
+#print(z1)
+#print(z2)
+
+#A=np.array ([[1,2],[3,4],[5,6]])
+#B=np.array ([[1,2],[4,5]])
+#b=np.array ([1,2])
+#c=np.array ([[1],[2]])
+#d=b.T
+#
+#print(A@b)
+#print(A@c)
+#print(A@d)
+#print(A@b.T)
+
+#
+# # # # # # # # # # # # # # # # # # # #
+#
+#lst_x =[1, 2, 4]
+#lst_lst_y =[[3.5, 6.2, 7], [2.1, 2.2, 2.3], [-0.2, 1, 3]]
+#
+#len_line =len(lst_lst_y)
+#arr_x =np.array (lst_x)
+#
+#for i in range (len_line):
+#    arr_y_i =np.array(lst_lst_y[i])
+#    plt.plot (arr_x, arr_y_i)
+#
+#out_fig_path =os.path.abspath(os.path.join(os.getcwd(), os.path.pardir)) +"/plt/test.png"
+##print (out_fig_path)
+#plt.savefig (out_fig_path, bbox_inches ="tight")
+
+

### 2019-04-22 dantzig_selector/report/4_simulation.tex
Kronecker product identity proof
Helper functions

@@
 \Disp {
-\NC \Mc {R} \SB {x} \in \NC \Mb {V} \SB {2M} \NR[+]
+\NC \Mc {R} \SB {x}
+\in \NC \Mb {V} \SB {2M} \NR
 \NC \Mc {R} \SB {x} \DB {m} =
@@
 \Disp {
-\NC \Mc {R} \SB {A} \in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR[+]
+\NC \Mc {R} \SB {A}
+\in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR
 \NC \Mc {R} \SB {A} \DB {m_1,m_2} =
@@
 \NC \T {\V {y}}
-\NC = \Mc {R} \SB {\V {y}}
-\in \Mb {V}_{\Mb {R}} \SB {2N_y} \NR[+]
+\in \NC \Mb {V}_{\Mb {R}} \SB {2N_y} \NR
+\NC \T {\V {y}}
+\NC = \Mc {R} \SB {\V {y}} \NR[+]
 \NC \T {\V {g}}
-\NC = \Mc {R} \SB {\V {g}}
-\in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR[+]
+\in \NC \Mb {V}_{\Mb {R}} \SB {2N_h} \NR
+\NC \T {\V {g}}
+\NC = \Mc {R} \SB {\V {g}} \NR[+]
 \NC \T {\M {P}}
-\NC = \Mc {R} \SB {\M {P}}
-\in \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_h} \NR[+]
+\in \NC \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_h} \NR
+\NC \T {\M {P}}
+\NC = \Mc {R} \SB {\M {P}} \NR[+]
 \NC \T {\V {z}}
-\NC = \Mc {R} \SB {\V {z}} \in \Mb {V}_{\Mb {R}} \SB {2N_y} \NR[+]
+\in \NC \Mb {V}_{\Mb {R}} \SB {2N_y} \NR
+\NC \T {\V {z}}
+\NC = \Mc {R} \SB {\V {z}} \NR[+]
 }
@@
 \Disp {
-\NC {\V {u}}_{n_h}^{(h)} \in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR[+]
+\NC {\V {u}}_{n_h}^{(h)} \in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR
 \NC {\V {u}}_{n_h}^{(h)} \DB {n_h'}
@@
 \stopcases \NR[+]
-\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR[+]
+\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
 \NC {\T {\M {U}}}_{n_h}^{(h)} \DB {n_h', n_h''}
@@
 \startcases
-1, \quad \MC n_h' =2n_h -1,\; n_h'' =2n_h -1 \NR
-1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h -1 \NR
-1, \quad \MC n_h' =2n_h -1,\; n_h'' =2n_h \NR
 1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
+1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h \NR
+1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h +1 \NR
+1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
 0, \quad \NC {\rm otherwise}
 \stopcases \NR[+]
-\NC n_h, n_h', n_h'' \NC = 1, \dots, N_h \NR
+\NC n_h, n_h', n_h'' \NC = 0, \dots, N_h -1 \NR
 }
@@
 \Disp{
-\NC \V {m} \NC \in \Mb {V}_{\Mb {R}} \SB {N_h} \NR[+]
+\NC \V {m} \NC \in \Mb {V}_{\Mb {R}} \SB {N_h} \NR
 \NC \V{m} \DB{n_h}
 \NC =\Nm{\V{g} \DB{n_h}} \NR[+]
-\NC n_h, n_h', n_h'' \NC = 1, \dots, N_h \NR
+\NC n_h, n_h', n_h'' \NC = 0, \dots, N_h -1 \NR
 }
@@
 \NC \V{t}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
+\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
 \NC \V{x}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
+\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
 \NC \M{A}_i
-\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_y +N_h} \NR[+]
+\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_y +N_h} \NR
 \NC \V{b}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR[+]
+\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
 \NC \V{c}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR[+]
+\NC \in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR
 \NC d_i
-\NC \in \Mb {R} \NR[+]
+\NC \in \Mb {R} \NR
 }
@@
 \Disp {
-\NC \Hat {G} =\Mr {vec}^{-1} \SB {\Hat {g}} \NR[+]
+\NC \Hat {G} =\NC \Mr {vec}^{-1} \SB {\Hat {g}} \NR[+]
 }
@@
 \Disp {
-\NC \Hat {\M {H}} =\M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
+\NC \Hat {\M {H}} =\NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
 }

### 2019-04-22 dantzig_selector/code/src/helpers.py

@@ -2,21 +2,39 @@ import numpy as np
 import constants as cst
 
 def arr_resp(pG, l)
-return [np.exp(1J*i*pG) for i in range(l)]
+    return np.array ([np.exp(1J*i*pG) for i in range(l)])
 
-def real_rep (v)
-    ret =np.zero (2*len(v))
+def repr (v)
+    ret =np.zeros (2*len(v))
     for i in range(len(v))
-        ret[2*i] ==np.real(v[i])
-        ret[2*i+1] ==np.imag(v[i])
+        ret [2*i] ==np.real (v[i])
+        ret [2*i+1] ==np.imag (v[i])
     return ret
 
-def inv_real_rep (v)
-assert (len(v)%2==0)
-    for i in range (int (len(v)/2))
+def inv_repr (v)
+    assert (len(v)%2==0)
+    v_re =np.array ([v[2*i] for i in range (int (len(v)/2))])
+    v_im =np.array ([v[2*i+1] for i in range (int (len(v)/2))])
+    return v_re +1J *v_im
 
+def vec (v)
+    return np.reshape(v, (1,-1))[0]
 
-def vec ()
+def inv_vec (v, nn_1, nn_2)
+    assert (len(v) ==nn_1 *nn_2)
+    return np.reshape(v, (nn_2, -1)).T
 
-def inv_vec ()
+def ind_vec (n_h)
+    ret =np.zeros (cst.nn_h)
+    ret[n_h] =1
+    return ret
+
+def ind_mat_repr (n_h_1, n_h_2)
+    ret =np.zeros (2*cst.nn_h, 2*cst.nn_h)
+    ret [2*n_h_1, 2*n_h_2] =1
+    ret [2*n_h_1 +1, 2*n_h_2] =1
+    ret [2*n_h_1, 2*n_h_2 +1] =1
+    ret [2*n_h_1 +1, 2*n_h_2 +1] =1
+    return ret
+
 

### 2019-04-26 dantzig_selector/report/4_simulation.tex
Draft: DS main algorithm

@@
 {
-For \m {x \in \Mb {V} \SB {M}}, we say that \m {\Mc {R} \SB {x}} is the real representation of \m {x}, defined by
+For \m {\V{x} \in \Mb {V}_{\Mb {C}} \SB {M}}, we say that \m {\Mc {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
 %
 \Disp {
-\NC \Mc {R} \SB {x}
-\in \NC \Mb {V} \SB {2M} \NR
-\NC \Mc {R} \SB {x} \DB {m} =
+\NC \Mc {R} \SB {\V{x}}
+\in \NC \Mb {V}_{\Mb {R}} \SB {2M} \NR
+\NC \Mc {R} \SB {\V{x}} \DB {m} =
 \NC \startcases
-\NC \Mf {Re} \SB {x \DB {m'}}, \MC m =2m' \NR
-\NC \Mf {Im} \SB {x \DB {m'}}, \MC m =2m'+1 \NR
+\NC \Mf {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
+\NC \Mf {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
 \stopcases \NR[+]
-\NC m' \NC =  1, \dots, M \NR
+\NC m' 
+= \NC  0, 1, 2, \dots, M-1 \NR
 }
-%
+The bijectivity is obvious, and we define \m {\Mc {R} ^{-1}} so that
+\Disp {
+\NC \Mc {R} ^{-1} \SB {\Mc {R} \SB {\V{x}}}
+=\NC \V{x} \NR[+]
+}
 }
 
-A moment's reflection reveals the corresponding definition of real representation of matrices.
+By the same token, a moment's reflection reveals the corresponding definition of real representation of matrices.
 
@@
 {
-For \m {A \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {A}} is the real representation of \m {A}, defined by
+For \m {\M{A} \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
 %
 \Disp {
-\NC \Mc {R} \SB {A}
+\NC \Mc {R} \SB {\M{A}}
 \in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR
-\NC \Mc {R} \SB {A} \DB {m_1,m_2} =
+\NC \Mc {R} \SB {\M{A}} \DB {m_1,m_2} =
 \NC \startcases
-\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
-\NC \Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
-\NC -\Mf {Im} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
-\NC \Mf {Re} \SB {A \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
+\NC \Mf {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
+\NC \Mf {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
+\NC -\Mf {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
+\NC \Mf {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
 \stopcases \NR[+]
-\NC m_1' \NC = 1, \dots, M_1 \NR
-\NC m_2' \NC = 1, \dots, M_2 \NR
+\NC m_1 
+= \NC 0, 1, 2, \dots, M_1 -1 \NR
+\NC m_2 
+= \NC 0, 1, 2, \dots, M_2 -1 \NR
 }
-%
+Notice that Here not all matrices in \m {\Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
 }
@@
 
-%
 \Disp {
@@
 \NC \T {\V {y}}
-\NC = \Mc {R} \SB {\V {y}} \NR[+]
+= \NC \Mc {R} \SB {\V {y}} \NR[+]
 \NC \T {\V {g}}
@@
 \NC \T {\V {g}}
-\NC = \Mc {R} \SB {\V {g}} \NR[+]
+= \NC \Mc {R} \SB {\V {g}} \NR[+]
 \NC \T {\M {P}}
@@
 \NC \T {\M {P}}
-\NC = \Mc {R} \SB {\M {P}} \NR[+]
+= \NC \Mc {R} \SB {\M {P}} \NR[+]
 \NC \T {\V {z}}
@@
 \NC \T {\V {z}}
-\NC = \Mc {R} \SB {\V {z}} \NR[+]
+= \NC \Mc {R} \SB {\V {z}} \NR[+]
 }
@@
 \Disp {
-\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
+\NC \V {\T {y}}
+= \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}}
 }
@@
 \Disp {
-\NC {\V {u}}_{n_h}^{(h)} \in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR
-\NC {\V {u}}_{n_h}^{(h)} \DB {n_h'}
-\NC =
+\NC {\V {u}}_{n_h}
+\in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR
+\NC {\V {u}}_{n_h} \DB {n_h'}
+= \NC
 \startcases
@@
 \stopcases \NR[+]
-\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
-\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {n_h', n_h''}
-\NC =
+\NC {\T {\M {U}}}_{n_h} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
+\NC {\T {\M {U}}}_{n_h} \DB {n_h', n_h''}
+= \NC
 \startcases
@@
 \stopcases \NR[+]
-\NC n_h, n_h', n_h'' \NC = 0, \dots, N_h -1 \NR
+\NC n_h, n_h', n_h'' 
+= \NC 0, 1, 2, \dots, N_h -1 \NR
 }
@@
 \NC \V{m} \DB{n_h}
-\NC =\Nm{\V{g} \DB{n_h}} \NR[+]
-\NC n_h, n_h', n_h'' \NC = 0, \dots, N_h -1 \NR
+= \NC \Nm{\V{g} \DB{n_h}} \NR[+]
+\NC n_h, n_h', n_h'' 
+= \NC 0, 1, 2, \dots, N_h -1 \NR
 }
@@
 \NC \Hat {\T {\V {g}}}
-\NC = \startcases
+= \NC \startcases
 \NC \Min {\T {\V {g}}', \V {m}} \quad
@@
 \NC \Mr {subject} \; \Mr {to} \quad
-\MC \VNm { \T {\M {U}}_{n_h}^{(h)} \T {\V {g}}' }_2
+\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
 \leq \IP { \V {u}_{n_h}, \V {m} } \NR
-\NC \MC \VNm { \T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
+\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
 \leq \g \NR
 \stopcases \NR[+]
-\NC n_h \NC = 1, \dots, N_h \NR
+\NC n_h 
+= \NC 0, 1, 2, \dots, N_h-1 \NR
 }
@@
 \NC \V{t}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
+\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
 \NC \V{x}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
+\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
 \NC \M{A}_i
-\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_y +N_h} \NR
+\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 3N_h} \NR
 \NC \V{b}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {2N_y +N_h} \NR
+\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
 \NC \V{c}_i
@@
 \NC \V{t}
-\NC =\startthematrix
+= \NC \startthematrix
 \NC \V{0} \NR
@@
 \NC \V{x}'
-\NC =\startthematrix
+= \NC \startthematrix
 \NC \T {\V {g}}' \NR
@@
 \NC \M{A}_i
-\NC =\startthematrix
-\NC \T {\M {U}}_{n_h}^{(h)}, \NC \M{0} \NR
+= \NC \startthematrix
+\NC \T {\M {U}}_{i}, \NC \M{0} \NR
 \stopthematrix \NR[+]
 \NC \V{b}_i
-\NC =\startthematrix
+= \NC \V{0} \NR[+]
+\NC \V{c}_i
+= \NC \startthematrix
 \NC \V{0} \NR
-\NC \V{0} \NR
-\stopthematrix \NR[+]
-\NC \V{c}_i
-\NC =\startthematrix
-\NC \V{0} \NR
-\NC \V {u}_{n_h} \NR
+\NC \V {u}_{i} \NR
 \stopthematrix \NR[+]
 \NC d_i
-\NC =0 \NR[+]
-\NC i \NC =1, 2, \dots, N_h \NR
+= \NC 0 \NR[+]
+\NC i 
+= \NC 0, 1, 2, \dots, N_h -1 \NR
 }
@@
 \NC \M{A}_i
-\NC =\startthematrix
-\NC \T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
+= \NC \startthematrix
+\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
 \stopthematrix \NR[+]
 \NC \V{b}_i
-\NC =\startthematrix
-\NC -\T {\M {U}}_{n_h}^{(h)} \T {\M {P}}^\Adj \T {\V {y}} \NR
-\NC \V{0} \NR
-\stopthematrix \NR[+]
+=\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
 \NC \V{c}_i
-\NC =\startthematrix
+= \NC \startthematrix
 \NC \V{0} \NR
@@
 \NC d_i
-\NC =\g \NR[+]
-\NC i \NC =N_h +1, N_h +2, \dots, N_h +N_y \NR
+= \NC \g \NR[+]
+\NC i 
+= \NC N_h, N_h +1, N_h +2, \dots, 2N_h -1 \NR
 }
@@
 \NC \Hat {\V {x}}
-\NC = \startcases
+= \NC \startcases
 \NC \Min {\V {x}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}
@@
 \leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
-\NC \MC i =1, 2, \dots, N_y +N_h \NR
+\NC \MC i =0, 1, 2, \dots, 2N_h -1 \NR
 \stopcases \NR[+]
@@
 \Disp{
-\NC \Hat{\T{\V{g}}} =\NC \Hat{\V{x}} \DB {1 : 2N_h} \NR[+]
+\NC \Hat{\T{\V{g}}} =\NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
 }

### 2019-04-26 dantzig_selector/code/src/algorithms.py

@@ -17,27 +17,35 @@ class Ddss(cst):
 
     def run(self):
 
-t =np.zeros ((2*cst.nn_y)) +np.zeros ((cst.nn_h))
+    t =np.concatenate ([np.zeros ((2*cst.nn_h)), np.ones ((cst.nn_h))])
 
-for i in range(nn_h):
-    A.append ()
-    b.append ()
-    c.append ()
-    d.append ()
+for i in range(cst.nn_h):
+    A.append (np.concatenate ([ind_mat_repr (i), +np.zeros ((cst.nn_h))]))
+    b.append (np.zeros ((2*cst.nn_h)))
+    c.append (np.concatenate ([np.zeros ((2*cst.nn_h)), ind_vec (i)]))
+    d.append (0)
 
-for i in range(nn_h):
-    A.append ()
-    b.append ()
-    c.append ()
-    d.append ()
+for i in range(cst.nn_h, 2*cst.nn_h):
+    A.append (np.concatenate ([ind_mat_repr (i -cst.nn_h)
+                                   @ mat_repr (self.pp) .H
+                                   @ mat_repr (self.pp),
+                               np.zeros ((cst.nn_h))]), axis=1)
+    A.append (ind_mat_repr (i -cst.nn_h)
+                  @ mat_repr (self.pp) .H
+                  @ mat_repr (self.y))
+    c.append (np.concatenate (np.zeros ((3*cst.nn_h))))
+    d.append (cst.gG)
 
-# Define and solve the CVXPY problem.
-x = cp.Variable(n)
-# We use cp.SOC(t, x) to create the SOC constraint ||x||_2 <= t.
-soc_constraints = [cp.SOC (c[i].T @ x + d[i], A[i] @ x + b[i]) for i in range (nn_h+nn_y)]
-prob = cp.Problem(cp.Minimize(f.T@x),
-                  soc_constraints + [F@x == g])
+x = cp.Variable (3*cst.nn_h)
+constr = [cp.SOC (c[i].T @ x + d[i], A[i] @ x + b[i]) for i in range (2*cst.nn_h)]
+prob = cp.Problem (cp.Minimize(f.T@x), constr)
 prob.solve()
+
+x_hat =x.value
+g_repr_hat =x_hat [0:2*cst.nn_h -1]
+g_hat =inv_vec_repr (g_repr_hat)
+gg_hat =inv_vec (g_hat)
+hh_hat =cst.kk @ gg_hat @ cst.kk.H
 
 
 # Print result.

### 2019-04-26 dantzig_selector/code/src/constants.py

@@ -1,3 +1,6 @@
+import numpy as np
+
+
 lG =3
 ll =5
 d_arr =5
@@ -7,4 +10,9 @@ nn_hh =7
 nn_y =nn_yy *nn_yy
 nn_h =nn_hh *nn_hh
 gG =1
+
+kk =np.zeros(nn_hh, nn_hh)
+for i in range(nn_h):
+    for j in range(nn_h):
+        kk[i,j] =() *np.exp(2 *np.pi *1J *i *j /nn_hh)
 

### 2019-04-26 dantzig_selector/code/src/draw.py

@@ -40,7 +40,6 @@ for i in range (len_line):
 
 out_fig_path =os.path.abspath(os.path.join(os.getcwd(), os.path.pardir))
               +"/plt/" +str_title +".png"
-#print (out_fig_path)
 plt.savefig (out_fig_path, bbox_inches ="tight")
 
 

### 2019-04-26 dantzig_selector/code/src/helpers.py

@@ -1,40 +1,53 @@
 import numpy as np
 import constants as cst
 
-def arr_resp(pG, l)
+def arr_resp (pG, l):
     return np.array ([np.exp(1J*i*pG) for i in range(l)])
 
-def repr (v)
+def vec_repr (v):
     ret =np.zeros (2*len(v))
-    for i in range(len(v))
+    for i in range(len(v)):
         ret [2*i] ==np.real (v[i])
         ret [2*i+1] ==np.imag (v[i])
     return ret
 
-def inv_repr (v)
+def inv_vec_repr (v):
     assert (len(v)%2==0)
-    v_re =np.array ([v[2*i] for i in range (int (len(v)/2))])
-    v_im =np.array ([v[2*i+1] for i in range (int (len(v)/2))])
+    len_v =int (len(v)/2)
+    v_re =np.array ([v[2*i] for i in range (len_v)])
+    v_im =np.array ([v[2*i+1] for i in range (len_v)])
     return v_re +1J *v_im
 
-def vec (v)
+def mat_repr (aa):
+    len_ret_1 =2 *len(aa)[0]
+    len_ret_2 =2 *len(aa)[1]
+    ret =np.zeros(len_ret_1, len_ret_2)
+    for i in range(len_ret_1):
+        for j in range(len_ret_2):
+            ret [2*i, 2*j] ==np.real (aa[i,j])
+            ret [2*i+1, 2*j] ==np.imag (aa[i,j])
+            ret [2*i, 2*j+1] ==np.real (aa[i,j])
+            ret [2*i+1, 2*j+1] ==np.imag (aa[i,j])
+    return ret
+
+def make_vec (v):
     return np.reshape(v, (1,-1))[0]
 
-def inv_vec (v, nn_1, nn_2)
+def inv_make_vec (v, nn_1, nn_2):
     assert (len(v) ==nn_1 *nn_2)
     return np.reshape(v, (nn_2, -1)).T
 
-def ind_vec (n_h)
+def ind_vec (n_h):
     ret =np.zeros (cst.nn_h)
     ret[n_h] =1
     return ret
 
-def ind_mat_repr (n_h_1, n_h_2)
+def ind_mat_repr (n_h):
     ret =np.zeros (2*cst.nn_h, 2*cst.nn_h)
-    ret [2*n_h_1, 2*n_h_2] =1
[…]

### 2019-04-30 dantzig_selector/report/3_theorems_and_proofs.tex
Set & correct simulation variables
Kronecker product identity proof
Correct vectorize convention

--- 2019-03-14 ongoing/report/3_theorems_and_proofs.tex
@@
 \Disp {
-\NC \gamma = \NC \R {2 \log N_h} \NR[+]
+\NC \g = \NC \R {2 \log N_h} \NR[+]
 }
@@
 Also set for short
-%
 \Disp {
@@
 }
-%
 And call
@@
 Then \m {\V {a} \SB {\f}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
-%
 \Disp {
@@
 Recall the identity for Dirichlet kernel
-%
 \Disp {
@@
 }
-%
 And recall the Taylor expansion of sin for the first two terms with respect to zero
-%
 \Disp {
@@
 }
-%
 Actually it can be shown that we have a inequality
-%
 \Disp {
@@
 }
-%
 Applying the above inequality to the denominator and bounding the nominator by 1, we have
-%
 \Disp {
@@
 
-Particularly, for arbitrary \m {\f}, find \m {k} so that
+Particularly, for arbitrary \m {\f}, find \m {k} by
 \Disp {
-\NC \eta := \NC \f -\F {2\pi k}{N_H}, \NR[+]
-\NC \Nm {\eta}
-\leq \NC \F {2\pi}{N_H}. \NR
+\NC \eta := \NC \f \quad \rm{mod}\; (2\pi) \NR[+]
+\NC k := \NC \F {N_H} {2\pi} (\f -\eta) \NR[+]
 }
-%
 Then observe
@@
 Then \m {\V {g}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
-%
 \Disp {
@@
 For \m {\Mc {T}, \Mc {T}' \subset \{1, \dots, N_p\}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} >0} to be the smallest such that
-%
 \Disp {
@@
 Then
-%
 \Disp {
@@
 }
-%
 with overwhelming probability.
@@
 Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in ().
-%
 \Disp {
@@
 To show this, by definition
-%
 \Disp {
@@
 Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in () with respect to \m {\d_s}.
-%
 \Disp {

### 2019-04-30 dantzig_selector/code/src/algorithms.py

@@ -17,17 +17,17 @@ class Ddss(cst):
     def run(self):
         t = np.concatenate ([np.zeros ((2 * cst.nn_h)), np.ones ((cst.nn_h))])
         for i in range(cst.nn_h):
-            A.append (np.concatenate ([ind_repr_mat (i), + np.zeros ((cst.nn_h, cst.nn_h))], axis= 1))
+            A.append (np.concatenate ([indic_repr_mat (i), + np.zeros ((cst.nn_h, cst.nn_h))], axis= 1))
             b.append (np.zeros ((cst.nn_h)))
-            c.append (np.concatenate ([np.zeros ((2 * cst.nn_h)), ind_vec (i)]))
+            c.append (np.concatenate ([np.zeros ((2 * cst.nn_h)), indic_vec (i)]))
             d.append (0)
         for i in range(cst.nn_h, 2 * cst.nn_h):
             A.append (-np.concatenate ([ind_repr_mat (i -cst.nn_h)
-                                           @ find_repr_mat (self.pp).H
+                                           @ find_repr_mat (self.pp.H)
                                            @ find_repr_mat (self.pp),
                                        np.zeros ((cst.nn_h))]), axis= 1)
             A.append (ind_repr_mat (i -cst.nn_h)
-                          @ find_repr_mat (self.pp).H
+                          @ find_repr_mat (self.pp.H)
                           @ find_repr_mat (self.y))
             c.append (np.zeros ((3 * cst.nn_h)))
             d.append (self.gG)

### 2019-04-30 dantzig_selector/code/src/helpers.py

@@ -42,16 +42,14 @@ def inv_vectorize (v, nn_1, nn_2):
     assert (len(v) ==nn_1 *nn_2)
     return np.reshape(v, (nn_2, -1)).T
 
-def ind_vec (n_h):
+def indic_vec (n_h):
     ret =np.zeros (cst.nn_h)
     ret[n_h] =1
     return ret
 
-def ind_repr_mat (n_h):
+def indic_repr_mat (n_h):
     ret =np.zeros (2*cst.nn_h, 2*cst.nn_h)
     ret [2*n_h] [2*n_h] =1
-    ret [2*n_h +1] [2*n_h] =1
-    ret [2*n_h] [2*n_h +1] =1
     ret [2*n_h +1] [2*n_h +1] =1
     return ret
 

### 2019-05-01 dantzig_selector/report/1_introduction.tex
Helper functions
Draft: DS main algorithm
Draft: Matrices generation

--- 2019-03-14 ongoing/report/1_introduction.tex
@@
 The figure of merit of a MIMO system is usually considered to be the channel capacity.
-In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det \RB {I +\Mr {SNR}}}, but that knowledge is hardly always available.
+In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det \RB {I +\Rm {SNR}}}, but that knowledge is hardly always available.
 What makes things more difficult is the case that \m {\M {H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
@@
 Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det \RB {I +\Mr {SNR}}}.
+Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det \RB {I +\Rm {SNR}}}.
 
@@
 \NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
-\NC \Mr {subject} \; \Mr {to} \quad \MC \VNm {\M {P}^\Adj \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \gamma \NR
+\NC \Rm {subject} \; \Rm {to} \quad \MC \VNm {\M {P}^\Adj \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \g \NR
 \stopcases \NR
@@
 
+\stopsection
+\startsection [title={OMP used in Channel Sensing}]
+
 For concreteness, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
 Let signal \m {\V {x}} be sent, and \m {\V {y}} be receiverd, that is
-%
+
 \Disp {
 \NC \V {y} =\M {W} \M {H} \M {F} \V {x} \NR
-}
-%
-
-\Result
-{Definition}
-{
-Define \m {\Mr {vec} \SB {\M {A}} \in \Mb {K}^{NM}} to be the vectorization of \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}}.
 }
@@
 {
-For \m {\Mr {vec} \SB {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}} and \m {\Mr {vec} \SB {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}}
-Define the Kronecker product \m {\Mr {vec} \SB {A} \in \Mb {K}^{nm}} 
+Define \m {\Rm {vec} \SB {\M {A}} \in \Mb {V}_{\Mb {K}} \SB {N_1, N_2}} to be the vectorization of \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}}.
+Formally,
+\Disp{
+\NC \RB {\Rm{vec} \SB {\M{A}}} \DB {m_1}
+=\NC \M{A} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR[+]
+}
+The bijectivity is obvious, and we define \m {\Rm {vec} ^{-1}} so that
+\Disp {
+\NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
+=\NC x \NR[+]
+}
+}
+
+\Result
+{Definition.}
+{
+For \m {\M{A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}} and \m {\M{B} \in \Mb {M}_{\Mb {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \Mb {M}_{\Mb {K}} \SB {N_1 N_3, N_2 N_4}} by
+\Disp{
+\NC \NC \RB {\M{A} \otimes \M{B}} \DB {m_1, m_2} \NR
+\NC =\NC \M{A} \DB {\Fl{ m_1/N_3 }, \Fl{ m_2/N_4 }}
+\M{B} \DB {m_1\; \Rm{Mod}\; N_3, m_2\; \Rm{Mod}\; N_4} \NR[+]
+}
 }
@@
 With (), scholars often exploit the relation
-%
+
+\Result
+{Lemma.}
+{
+Suppose \m {\M{A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}, \M{X} \in \Mb {M}_{\Mb {K}} \SB {N_2, N_3}, \M{B} \in \Mb {M}_{\Mb {K}} \SB {N_3, N_4}},
+Then
 \Disp {
-\NC \Mr {vec} \SB {Y}
-=\SB {\RB {F^\Adj} \otimes W} \Mr {vec} \RB {\M {H}} \NR
+\NC \mathrm{vec} \RB {\M{A}\M{X}\M{B}}
+= \NC \RB {\M{B}^\Tr \otimes \M{A}} \mathrm{vec} \SB {\M{X}} \NR
 }
-%
+}
+
+The proof is not particularly easy to find, and we show it here.
+We thus verify that arbitrary components of lhs and rhs agree.
+On one hand,
+
+\Disp{
+\NC \NC \RB {\Rm{vec} \SB {\M{A}\M{X}\M{B}}} \DB {m_1} \NR
+\NC = \NC \RB {\M{A}\M{X}\M{B}} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
+\NC = \NC \sum _{n_2=1} ^{N_2} \sum _{n_3=1} ^{N_3}
+\M{A} \DB {m_1\; \Rm{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR[+]
+}
+
+On the other hand,
+
+\Disp{
+\NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB{\M{X}} } \DB {m_1} \NR
+\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR
+\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
+\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR 
+\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
+\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }} \NR[+]
+}
+
+In () and (), the row index of \m {\M{A}} and \m {\M{B}} already agree.
+The key observation is that when \m {n_2} runs through \m {0, \dots, N_2-1} and \m {n_3} runs through \m {0, \dots, N_3-1}, it follows \m {n_2 n_3} runs through \m {0, \dots, N_2 N_3-1}.
+We see two expressions are exactly the same, and we are done.
 

### 2019-05-01 dantzig_selector/report/2_problem_setting.tex
Draft: Matrices generation

@@
 \NC \V {a} \SB {\psi'}
-= \NC \F {1}{\R {N_H}} \sum_{n=0}^{N-1} \Mr {e}^{n \psi' \Mr {i}} \V {u}_n \NR
+= \NC \F {1}{\R {N_H}} \sum_{n=0}^{N-1} \Ss {e}^{n \psi' \Ss {i}} \V {u}_n \NR
 }
-where \m {\Mr {e}} is the base of natural logarithm, and \m {\Mr {i}} the imaginary unit.
+where \m {\Ss {e}} is the base of natural logarithm, and \m {\Ss {i}} the imaginary unit.
 
@@
 \NC \M{H}
-=\sum_{l=1}^L \alpha_l \V {a} \SB { \F {d_{\Mr {arr}}} {\lambda} \sin \f_l' } \V {a} \SB { \F {d_{\Mr {arr}}} {\lambda} \sin \th_l' }^\Adj \NR
+=\sum_{l=1}^L \alpha_l \V {a} \SB { \F {d_{\Rm {arr}}} {\lambda} \sin \f_l' } \V {a} \SB { \F {d_{\Rm {arr}}} {\lambda} \sin \th_l' }^\Adj \NR
 }
-The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Mr {arr}}} is the distance between two adjacent antennae.
+The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
 For our purpose, we may absorb the argument of \m {\V {a}} as
@@
 \NC \f_l
-= \NC \F {d_{\Mr {arr}}} {\lambda} \sin \f_l' \quad \rm{Mod}\; (2\pi) \NR[+]
+= \NC \F {d_{\Rm {arr}}} {\lambda} \sin \f_l' \quad \Rm{Mod}\; (2\pi) \NR[+]
 \NC \th_l
-= \NC \F {d_{\Mr {arr}}} {\lambda} \sin \th_l' \quad \rm{Mod}\; (2\pi) \NR[+]
+= \NC \F {d_{\Rm {arr}}} {\lambda} \sin \th_l' \quad \Rm{Mod}\; (2\pi) \NR[+]
 }
@@
 
-We consider zero-mean, unity-variance additive white Gaussian noise \m {z}.
-Since we restrict our discussion to a specific slice of time, the signal \m {z} degrades as a entrywise i.i.d.\ standard normal distribution vector.
-
+We consider zero-mean, unity-variance additive white Gaussian noise (AWGN).
+Since we restrict our discussion to a specific slice of time, this random process may be simply taken to be a matrix \m {\M{Z}} with each entry being i.i.d.\ standard Gaussian.
+\Disp{
+\NC \M {Z} \in \NC \Mb {M}_{\Mb {C}} \SB {N_Y, N_Y} \NR[+]
+}
 We may introduce the effective channel
@@
 \NC \V {h}
-:= \NC \Mr {vec} \SB {\M {H}} \NR[+]
+:= \NC \Rm {vec} \SB {\M {H}} \NR[+]
 \NC \V {y}
@@
 \NC \V {y}
-:= \NC \Mr {vec} \SB {\M {Y}} \NR[+]
+:= \NC \Rm {vec} \SB {\M {Y}} \NR[+]
 \NC \V {z}
@@
 \NC \V {z}
-:= \NC \Mr {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR[+]
+:= \NC \Rm {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR[+]
 \NC \M {P}^\star
@@
 }
-to formulate our goal as sparse recovery problem of \m {\Mr {vec} \SB {H}} to be
+to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {H}} to be
 \Disp {
@@
 \NC \M {K} \in  \NC \Mb {M}_{\Mb {C}} \SB {N_H, N_H} \NR
-\NC \M {K} \DB {n_1, n_2} = \NC \F {1} {\R {N_H}} \Mr {e}^{2\pi \Mr{i} n_1 n_2 /N_H}, \NR[+]
+\NC \M {K} \DB {n_1, n_2} = \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR[+]
 \NC \quad n_1, n_2 = \NC 0, 1, \dots, N_H-1 \NR
 }
-Roman \m{\Mr{e}} and \m{\Mr{i}} denote the natural base and imaginary unit, respectively.
+Roman \m{\Ss{e}} and \m{\Ss{i}} denote the natural base and imaginary unit, respectively.
 Here recall that we have
@@
 \NC \V {g}
-:= \NC \Mr {vec} \SB {\M {G}} \NR[+]
+:= \NC \Rm {vec} \SB {\M {G}} \NR[+]
 }
@@
 \NC \Min {\V {g}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR[+]
-\NC \Mr {subject} \; \Mr {to} \quad  \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
+\NC \Rm {subject} \; \Rm {to} \quad  \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
 \stopcases \NR
@@
 \Disp {
-\NC \Hat {G} =\Mr {vec}^{-1} \SB {\Hat {g}} \NR
+\NC \Hat {G} =\Rm {vec}^{-1} \SB {\Hat {g}} \NR
 }
@@
 \stopsection
-
 \stopchapter

### 2019-05-01 dantzig_selector/report/3_theorems_and_proofs.tex
Draft: Matrices generation

@@
 
-We first establish a technical lemma that shows \m {\Mr {supp} \SB {\V {g}}} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse
+We first establish a technical lemma that shows \m {\Rm {supp} \SB {\V {g}}} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse
 
@@
 \NC D \SB {\f'}
-:= \NC \Nm { \sum_{n=0}^{N_H-1} \Mr {e}^{i n \f'} } \NR
+:= \NC \Nm { \sum_{n=0}^{N_H-1} \Rm {e}^{i n \f'} } \NR
 \NC = \NC \F {\Nm {\sin \SB {N_H \f'/2}}}{\Nm {\sin \SB {\f' /2}}}, \NR[+]
@@
 \NC Q\SB {x}
-\leq \NC \F {1}{2} \Mr {e}^{-x^2/2} \NR
+\leq \NC \F {1}{2} \Rm {e}^{-x^2/2} \NR
 }

### 2019-05-01 dantzig_selector/code/src/algorithms.py

@@ -2,43 +2,46 @@ import numpy as np
 import cvxpy as cp
 import constants as cst
 
-class Ddss(cst):
+class Ddss (cst):
     def __init__(self):
         self.pp = np.ones ((cst.nn_y, cst.nn_h))
         self.y = np.zeros ((cst.nn_y))
-        self.gG = float('inf')
+        self.gG = float ('inf')
         self.hh_hat = np.zeros ((cst.nn_hh, cst.nn_hh))
 
-    def set(self, pp, y, gG):
+    def set (self, pp, y, gG):
         self.pp = pp
         self.y = y
         self.gG = gG
 
-    def run(self):
-        t = np.concatenate ([np.zeros ((2 * cst.nn_h)), np.ones ((cst.nn_h))])
-        for i in range(cst.nn_h):
-            A.append (np.concatenate ([indic_repr_mat (i), + np.zeros ((cst.nn_h, cst.nn_h))], axis= 1))
+    def run (self):
+        for i in range (cst.nn_h):
+            A.append (np.concatenate ([indication_repr_mat (i),
+                                       np.zeros ((cst.nn_h, cst.nn_h))],
+                                      axis= 1))
             b.append (np.zeros ((cst.nn_h)))
-            c.append (np.concatenate ([np.zeros ((2 * cst.nn_h)), indic_vec (i)]))
+            c.append (np.concatenate ([np.zeros ((2 * cst.nn_h)), indication_vec (i)]))
             d.append (0)
-        for i in range(cst.nn_h, 2 * cst.nn_h):
-            A.append (-np.concatenate ([ind_repr_mat (i -cst.nn_h)
-                                           @ find_repr_mat (self.pp.H)
-                                           @ find_repr_mat (self.pp),
-                                       np.zeros ((cst.nn_h))]), axis= 1)
-            A.append (ind_repr_mat (i -cst.nn_h)
-                          @ find_repr_mat (self.pp.H)
-                          @ find_repr_mat (self.y))
+        for i in range (cst.nn_h, 2 * cst.nn_h):
+            A.append (np.concatenate ([-indication_repr_mat (i -cst.nn_h)
+                                        @ find_repr_mat (self.pp.H)
+                                        @ find_repr_mat (self.pp),
+                                        np.zeros ((cst.nn_h, cst.nn_h))],
[…]

### 2019-05-01 dantzig_selector/code/src/constants.py

@@ -1,21 +1,23 @@
 import numpy as np
 
-d_array =1
-ll_path =10
+d_arr = 1
+ll_path = 10
 
-lG =3
-ll =5
-d_arr =5
-nn_yy =3
-nn_rr =5
-nn_hh =7
-nn_y =nn_yy *nn_yy
-nn_h =nn_hh *nn_hh
+lG = 3
+d_arr = 5
+nn_yy = 3
+nn_rr = 5
+nn_hh = 7
+nn_y = nn_yy *nn_yy
+nn_h = nn_hh *nn_hh
 
-num_quantization =8
-normal_mean =3
-normal_std =1
-power_constr =nn_rr *nn_yy *10
+num_grid_phase = 8
+amp_mean_hh = 3
+amp_std_hh = 1
+part_mean_bb = 1
+part_std_bb = 0.1
+
+power_constr = nn_rr *nn_yy *10
 
 
 

### 2019-05-01 dantzig_selector/code/src/helpers.py

@@ -1,34 +1,34 @@
 import numpy as np
 import constants as cst
 
-def arr_response (pG):
-    return np.array ([np.exp (1J *i *pG) for i in range(cst.nn_hh)])
+def array_response (pG):
+    return np.array ([np.exp (1J *i *pG) for i in range (cst.nn_hh)])
 
 def kk ():
-    ret =np.zeros(nn_hh, nn_hh)
-    for i in range(nn_h):
-        for j in range(nn_h):
-            ret[i] [j] =(1 /np.sqrt(nn_h)) *np.exp(2 *np.pi *1J *i *j /nn_hh)
+    ret =np.zeros (nn_hh, nn_hh)
+    for i in range (nn_h):
+        for j in range (nn_h):
+            ret[i] [j] =(1 /np.sqrt (nn_h)) *np.exp (2 *np.pi *1J *i *j /nn_hh)
     return ret
 
 def find_repr_vec (v):
-    ret =np.zeros (2*len(v))
-    for i in range(len(v)):
+    ret =np.zeros (2*len (v))
+    for i in range (len (v)):
         ret [2*i] ==np.real (v[i])
         ret [2*i+1] ==np.imag (v[i])
     return ret
 
 def inv_find_repr_vec (v):
-    assert (len(v)%2==0)
-    len_v =int (len(v)/2)
+    assert (len (v)%2==0)
+    len_v =int (len (v)/2)
     v_re =np.array ([v[2*i] for i in range (len_v)])
     v_im =np.array ([v[2*i+1] for i in range (len_v)])
     return v_re +1J *v_im
 
 def find_repr_mat (aa):
-    ret =np.zeros (2 *len(aa)[0], 2 *len(aa)[1])
-    for i in range (len(aa)[0]):
-        for j in range (len(aa)[1]):
+    ret =np.zeros (2 *len (aa)[0], 2 *len (aa)[1])
+    for i in range (len (aa)[0]):
+        for j in range (len (aa)[1]):
             ret [2*i] [2*j] ==np.real (aa[i,j])
             ret [2*i+1] [2*j] ==np.imag (aa[i,j])
             ret [2*i] [2*j+1] ==np.real (aa[i,j])
@@ -36,18 +36,18 @@ def find_repr_mat (aa):
     return ret
 
 def vectorize (v):
-    return np.reshape(v, (1,-1))[0]
[…]

### 2019-05-01 dantzig_selector/code/src/matrices.py

@@ -3,40 +3,71 @@ import constants as cst
 
 
 class Hh:
-    def __init__(self):
-        val =np.zeros((self.cst.nn_h, self.cst.nn_h))
+    def __init__ (self):
+        self.val = np.zeros ((cst.nn_h, cst.nn_h))
     
-    def refresh(self):
-        for l in range (self.cst.ll)
-            pG_l =(d_array /cst.lG) * np.sin (np.random.uniform(0, 2 * np.pi))
-            tG_l =(d_array /cst.lG) * np.sin (np.random.uniform(0, 2 * np.pi))
-            (arr_response (pG_l)).H @ arr_response (pG_l)
+    def generate (self):
+        self.val = np.zeros ((cst.nn_h, cst.nn_h))
+        for l in range (cst.ll_path)
+            aG_l = np.random.normal (cst.amp_mean_hh, cst.amp_std_hh)
+            pG_l = (d_arr /cst.lG) * np.sin (np.random.uniform (0, 2 * np.pi))
+            tG_l = (d_arr /cst.lG) * np.sin (np.random.uniform (0, 2 * np.pi))
+            self.val += aG_l * (array_response (pG_l)) @ array_response (pG_l).H
+
+class Zz:
+    def __init__ (self):
+        self.val = np.zeros ((cst.nn_yy, cst.nn_yy))
+    
+    def generate (self):
+        self.val = np.zeros ((cst.nn_yy, cst.nn_yy))
+        for i in range (cst.nn_yy)
+            for j in range (cst.nn_yy)
+                self.val [i] [j] =
+                        np.random.normal (0, 1) + 1J * np.random.normal (0, 1)
+
+class Ff_bb:
+    def __init__ (self):
+        self.val = np.zeros ((cst.nn_rr, cst.nn_yy))
+
+    def generate (self):
+        self.val = np.zeros ((cst.nn_rr, cst.nn_yy))
+        for i in range (cst.nn_rr)
+            for j in range (cst.nn_yy)
+                self.val [i] [j] =
+                        np.random.normal (cst.part_mean_bb, cst.part_std_bb)
+                        + 1J * np.random.normal (cst.part_mean_bb, cst.part_std_bb)
+        self.val /= power_constr
+
+class Ff_rr:
+    def __init__ (self):
+        self.val = np.zeros ((cst.nn_hh, self.cst.nn_rr))
+
+    def generate (self):
+        for i in range (cst.nn_hh)
+            for j in range (cst.nn_rr)
[…]

### 2019-05-01 dantzig_selector/code/src/test.py

@@ -9,11 +9,12 @@ import helpers
 #print (np.random.randint(7, size=10))
 #print (np.sin (1J *np.pi)/ np.pi)
 
-a=[[1,2,3,4],[5,6,7,8]]
-b=[[1,-1],[0,1]]
-c=[1,2,3,4,5,6]
+a =np.array ([[1,2,3,4],[5,6,7,8]])
+b =np.array ([[1,-1],[0,1]])
+c =np.array ([1,2,3,4,5,6])
 #print (helpers.kk())
-print (-np.ones ((cst.nn_hh)))
+a +=1
+print (a)
 #print(np.kron(a,b))
 #print (type (np.reshape (a, (1,-1))[0]))
 #print(np.reshape(np.kron(a,b), (1,-1)))

### 2019-05-04 dantzig_selector/code/src/algorithms.py
Reorganize source files

@@ -1,53 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import constants as cst
-
-class Dd_ss:
-    def __init__(self, pp, y, gG):
-        self.pp = pp
-        self.y = y
-        self.gG = gG
-        self.g_hat = np.zeros ((cst.nn_hh))
-
-    def run (self):
-        for i in range (cst.nn_h):
-            A.append (np.concatenate ([indication_repr_mat (i),
-                                       np.zeros ((cst.nn_h, cst.nn_h))],
-                                      axis= 1))
-            b.append (np.zeros ((cst.nn_h)))
-            c.append (np.concatenate ([np.zeros ((2 * cst.nn_h)), indication_vec (i)]))
-            d.append (0)
-        for i in range (cst.nn_h, 2 * cst.nn_h):
-            A.append (np.concatenate ([-indication_repr_mat (i -cst.nn_h)
-                                        @ find_repr_mat (self.pp.H)
-                                        @ find_repr_mat (self.pp),
-                                        np.zeros ((cst.nn_h, cst.nn_h))],
-                                       axis= 1))
-            b.append (indication_repr_mat (i -cst.nn_h)
-                      @ find_repr_mat (self.pp.H)
-                      @ find_repr_vec (self.y))
-            c.append (np.zeros ((3 * cst.nn_h)))
-            d.append (self.gG)
-        t = np.concatenate ([np.zeros ((2 * cst.nn_h)), np.ones ((cst.nn_h))])
-        x = cp.Variable (3 * cst.nn_h)
-
-        constr = [cp.SOC (c[i].T @ x + d[i], A[i] @ x + b[i]) for i in range (2 * cst.nn_h)]
-        prob = cp.Problem (cp.Minimize (f.T@x), constr)
-        prob.solve ()
-
-        x_hat = x.value
-        g_repr_hat = x_hat [0 : 2 * cst.nn_h -1]
-        self.g_hat = inv_find_repr_vec (g_repr_hat)
-
-# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
-
-class Oo_mm_pp:
-    def __init__(self):
-        
-
-class Ll_ss:
-    def __init__(self, pp, y):
-
-
-
-

### 2019-05-04 dantzig_selector/code/src/functions.py

@@ -1,8 +1,9 @@
 import numpy as np
-import matplotlib.pyplot as plt # plotting functions
-import os # getcwd
+import matplotlib.pyplot as plt
+import os
 
 import constants as cst
+import classes as cls
 
 def array_response (pG):
     return np.array ([np.exp (1J *i *pG) for i in range (cst.nn_hh)])
@@ -58,10 +59,6 @@ def indication_repr_mat (n_h):
 
 # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
 
-class Data:
-    def __init__ (self, arr, legend):
-        self.arr =arr
-        self.legend =legend
 
 def draw (arr_x, list_dat, label_x, label_y, title):
     plt.close ("all")

### 2019-05-04 dantzig_selector/code/src/main.py

@@ -3,16 +3,17 @@ import cvxpy as cp
 import matplotlib.pyplot as plt
 
 import constants as cst
-import algorithms as agr
-import Functions as f
-#import Drawing as d
+import classes as cls
+import functions as fct
 
 list_ss_nn_rr = range()
 
 for ss_nn_rr in list_ss_nn_rr:
-    dd_ss = dd_ss (pp, y, gG);
-    gg_hat = inv_vectorize (dd_ss.g_hat)
-    self.hh_hat = cst.kk @ gg_hat @ cst.kk.H
+    hh =Hh()
+    yy =hh
+    dd_ss = Dd_ss (pp, y, gG);
+    hh_hat = cst.kk @ inv_vectorize (dd_ss.g_hat) @ cst.kk.conj().T
 
+    oo_mm_pp = Oo_mm_pp (pp, y);
 
 

### 2019-05-04 dantzig_selector/code/src/matrices.py

@@ -1,73 +1,0 @@
-import numpy as np
-import constants as cst
-
-class Hh:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_h, cst.nn_h))
-    
-    def generate (self):
-        self.val = np.zeros ((cst.nn_h, cst.nn_h))
-        for l in range (cst.ll_path):
-            aG_l = np.random.normal (cst.amp_mean_hh, cst.amp_std_hh)
-            pG_l = (dist_antenna /cst.lG) * np.sin (np.random.uniform (0, 2 * np.pi))
-            tG_l = (dist_antenna /cst.lG) * np.sin (np.random.uniform (0, 2 * np.pi))
-            self.val += aG_l * (array_response (pG_l)) @ array_response (pG_l).H
-
-class Zz:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_yy, cst.nn_yy))
-    
-    def generate (self):
-        self.val = np.zeros ((cst.nn_yy, cst.nn_yy))
-        for i in range (cst.nn_yy):
-            for j in range (cst.nn_yy):
-                self.val [i] [j] = (
-                    np.random.normal (0, 1)
-                    + 1J * np.random.normal (0, 1))
-
-class Ff_bb:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_rr, cst.nn_yy))
-
-    def generate (self):
-        self.val = np.zeros ((cst.nn_rr, cst.nn_yy))
-        for i in range (cst.nn_rr):
-            for j in range (cst.nn_yy):
-                self.val [i] [j] = (
-                    np.random.normal (cst.part_mean_bb, cst.part_std_bb)
-                    + 1J * np.random.normal (cst.part_mean_bb, cst.part_std_bb))
-        self.val /= power_constr
-
-class Ff_rr:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_hh, self.cst.nn_rr))
-
-    def generate (self):
-        for i in range (cst.nn_hh):
-            for j in range (cst.nn_rr):
-                idx_phase = np.random.randint (cst.num_grid_phase)
-                self.val[i][j] = np.exp (2 * np.pi * 1J * idx_phase /num_grid_phase)
-        
-class Ww_bb:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_yy, cst.nn_rr))
-
-    def generate (self):
-        self.val = np.zeros ((cst.nn_yy, cst.nn_rr))
[…]

### 2019-05-04 dantzig_selector/code/src/test.py

@@ -4,22 +4,34 @@ import constants as cst
 #import os # getcwd
 #import cvxpy as cp
 
-import helpers as hp
+import functions as fct
 import matrices as mt
 
 #print (np.random.randint(7, size=10))
 #print (np.sin (1J *np.pi)/ np.pi)
 
-a =np.array ([1,2,4,5,7,8])
-b1 =np.array ([1,-1,0,1,3,6])
-b2 =np.array ([2,3,4,4.5,1,1])
-b3 =np.array ([1,3,5,7,5,3])
-#d_b1 =hp.Data(b1,"1st")
-#d_b2 =hp.Data(b1,"2nd")
-#d_b3 =hp.Data(b1,"3rd")
-list_dat =[hp.Data(b1,"1st"), hp.Data(b2,"2nd"), hp.Data(b3,"3rd")]
+#zz =mt.Zz()
+#zz.generate()
+#hh =mt.Hh()
+#hh.generate()
 
-hp.draw (a, list_dat, "Number", "Value", "Test")
+#a =np.array ([[1+2J, 3+4.4J], [-1J, -2.3+3J]])
+#print (a.conj().T)
+
+#a = np.array ([ [(i+j^2) for i in range(5)] for j in range(5)])
+#a = [ [(i+j^2) for i in range(5)] for j in range(5)]
+#print (a)
+#s =set([0,2,4])
+#b =a [:, list(s)]
+#print (b)
+
+
+#a =np.array ([1,2,4,5,7,8])
+#b1 =np.array ([1,-1,0,1,3,6])
+#b2 =np.array ([2,3,4,4.5,1,1])
+#b3 =np.array ([1,3,5,7,5,3])
+#list_dat =[hp.Data(b1,"1st"), hp.Data(b2,"2nd"), hp.Data(b3,"3rd")]
+#hp.draw (a, list_dat, "Number", "Value", "Test")
 
 #print (np.linalg.norm (b, ord='fro'))
 #print(np.kron(a,b))

### 2019-05-15 dantzig_selector/report/1_introduction.tex
Reorganize source files
Proof: Concentration ineq. of

@@
 \m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
-The real and imaginary part of \m {a} will be denoted respectively as \m {\Mf {Re} \SB {a}} and \m {\Mf {Im} \SB {a}}, respectively, thus \m {a =\Mf {Re} \SB {a} + i \Mf {Im} \SB {a}}
+The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} \SB {a}} and \m {\MF {Im} \SB {a}}, respectively, thus \m {a =\MF {Re} \SB {a} + \Ss{i} \MF {Im} \SB {a}}
 
-We restrict our discussion to \m {\Mb {R}^N} or \m {\Mb {C}^N} seen as the Hilbert space , equipped with standard inner product.
+We restrict our discussion to \m {\MB {R}^N} or \m {\MB {C}^N} seen as the Hilbert space , equipped with standard inner product.
 Lower case Latin alphabets with single underline, like \m {\V {a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m {\M {A}}, denote matrices.
 Particularly, define \m {\V {1} =\IP {1, \dots, 1}}.
-Denote \m {\V {a} \DB {n}} to be the \m {n}-th component of \m {\V {a}}, and similarly \m {\M {A} \DB {m,n}} to be the \m {(m,n)}-th entry of \m {\M {A}}.
+Denote \m {\V {a} \DB {n}} to be the \m {n}-th component of \m {\V {a}}, and similarly \m {\M {A} \DB {m,n}} to be the \m {m,n}-th entry of \m {\M {A}}.
 
 In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
-Of course, scalar operation on \m {\Mb {R}^N} is over field \m {\Mb {R}}, and that on \m {\Mb {C}^N} is over field \m {\Mb {C}}.
-We use \m {\Mb {K}} to refer to either \m {\Mb {R}} or \m {\Mb {C}}.
-Not to avoid confusion, we call the Hilbert space \m {\Mb {K}^N} over \m {\Mb {K}} to be \m {\Mb {V}_{\Mb {K}} \SB {N}}.
-We also call the collection of \m {M} by \m {N} matrices to be \m {\Mb {M}_{\Mb {K}} \SB {M,N}}, and its role as linear transformation is understood.
+Of course, scalar operation on \m {\MB {R}^N} is over field \m {\MB {R}}, and that on \m {\MB {C}^N} is over field \m {\MB {C}}.
+We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
+Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} \SB {N}}.
+We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} \SB {M,N}}, and its role as linear transformation is understood.
 Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
-Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {\DB {m,n}}-entry of \m {\V {A}}
+Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {m,n}-entry of \m {\V {A}}
 To better correspond to the pseudo code, the numbering of both vector and matrix entries are zero-based, that is, numbered from \m {0,1,2,\dots}.
-Especially when manipulating the indices, but also in the main proof of DS bound, we will encounter the modulo as operation, namely the remainder of \m {m} divided by \m {n}, with \m {m, n \geq 0}, and we use the capital \m {m\; \rm{Mod}\; n} to denote that number.
+Especially when manipulating the indices, but also in the main proof of DS bound, we will encounter the modulo as operation, namely the remainder of \m {m} divided by \m {n}, with \m {m, n \geq 0}, and we use the capital \m {m\; \Rm{Mod}\; n} to denote that number.
 And we denote \m {\V {u}_n} to be the \m {n}-th unit vector in the Cartesian coordinates, whose numbering is also zero-based.
@@
 
-Denote as \m {\Mb {P} \SB {X}} the probability, and \m {\Mb {E} \SB {X}} the expectation.
-Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.
+Denote as \m {\MB {P} \SB {X}} the probability, \m {\MB {E} \SB {X}} the expectation, and \m {\MB {Var} \SB {X}} the variance.
+Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables like \m {\MB {P} _\o \SB {X \SB {\o}}}.
 
@@
 
-To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \Mb {N}} is much larger than the number of measurements \m {N_m \in \Mb {N}}, namely,
+To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
 
@@
 
-In this article we focuss on DS, and we introduce several notions before we describe their work.
-To facilitate reader's understanding, in this section we will consistently use \m {N_p} and \m {N_m} to denote matrix dimensions.
-Following Cand\`es and Tao, we borrow the term ``support'' from the context of analysis, where it denotes the set on which a function is nonzero.
+In this article we focus on DS, and we introduce several notions before we describe their work.
+For simpliciy, in this section we will consistently use \m {N_p} and \m {N_m} to denote matrix dimensions.
+And, following their presentation, with slight abuse of notation we borrow the term ``support'' to denote the index set on which a vector's components are nonzero.
 
-For brevity, we will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\Mb {V}_{\Mb {K}} \SB {N_m}}.
-Also, suppose \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N_m, N_p}}.
-Let \m {\Mc {T} \subset T \RB {N_p}}.
-Denote as \m {\M {A}_{\Mc {T}}} the columns of \m {\M {A}} having indices in \m {\Mc {T}}.
+For brevity, we will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} \SB {N_m}}.
+Also, suppose \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
+Let \m {\MC {T} \subset T \RB {N_p}}.
+Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
 
@@
 {
-\m {x \in \Mb {V}_{\Mb {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\Mc {A}}, \m {s <N_m}, if there is \m {\Mc {A} \subset T \RB {N_m}} such that
+\m {x \in \MB {V}_{\MB {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
 
 \Disp { 
-\NC x_{T\SB {N} -\Mc {A}}
+\NC x_{T\SB {N} -\MC {A}}
 =\NC \V {0} \NR
@@
 \Disp { 
-\NC \# \Mc {A} \leq s. \NR
+\NC \# \MC {A} \leq s. \NR
 }
@@
 {
-Consider \m {P \in \Mb {M}_{\Mb {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
-For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \Mb {V}_{\Mb {K}} \SB {N_p}}, for all \m {\Mc {T} \subset T\SB {N_m}} with \m {\#\{\Mc {T} \} \leq s},
+Consider \m {P \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
+For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N_p}}, for all \m {\MC {T} \subset T\SB {N_m}} with \m {\#\{\MC {T} \} \leq s},
 
@@
 \NC \NC \RB {1-\d_s} \VNm {V {x}}^2 \NR
-\NC \leq \NC \VNm {P_{\Mc {T}} \V {x}} _2^2 \NR
+\NC \leq \NC \VNm {P_{\MC {T}} \V {x}} _2^2 \NR
 \NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
@@
 \Disp {
-\NC \V {y} =\M {P} \V {h} + \V {z} \NR
+\NC \V {y}
+=\NC \M {P} \V {h} + \V {z} \NR
 }
@@
 \startitemize[n]
-\item Input \m {\M {P} \in \Mb {V}_\Mb {R} \SB {N_m, N_p}}, \m {\V {y} \in \Mb {V}_\Mb {R} \SB {N_m}}.
-\item Find \m {\V {h} \in \Mb {V}_\Mb {R} \SB {N_m}} by
+\item Input \m {\M {P} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
+\item Calculate
 \Disp {
 \NC \V {h}
-= \NC \startcases
+\LA \NC \startcases
 \NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
@@
 {
-Let each entry of random matrix \m {P \in \Mb {M}_\Mb {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
+Let each entry of random matrix \m {P \in \MB {M}_\MB {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
 Then, with \m {0 <\e <1},
@@
 \Disp {
-\NC \NC \Mb {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \e \VNm {h} _2^2} \NR
+\NC \NC \MB {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \e \VNm {h} _2^2} \NR
 \NC \leq \NC 2 \exp \SB {-n \RB {\F {\e ^2} {4} -\F {\e ^3} {6}} } \NR
@@
 
-Same as before, consider \m {\V {y} \in \Mb {V}_\Mb {K} \SB {N_p}}, \m {\V {h} \in \Mb {V}_\Mb {K} \SB {N_s}}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
+Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} \SB {N_p}}, \m {\V {h} \in \MB {V}_\MB {K} \SB {N_s}}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
 If
 \Disp {
-\NC \V {y} =\M {P} \V {h}, \NR
+\NC \V {y}
+=\NC \M {P} \V {h}, \NR
 }
@@
 \Disp {
-\NC \V {y} =\M {W} \M {H} \M {F} \V {x} \NR
+\NC \V {y}
+=\NC \M {W} \M {H} \M {F} \V {x} \NR
 }
@@
 {
-Define \m {\Rm {vec} \SB {\M {A}} \in \Mb {V}_{\Mb {K}} \SB {N_1, N_2}} to be the vectorization of \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}}.
+Define \m {\Rm {vec} \SB {\M {A}} \in \MB {V}_{\MB {K}} \SB {N_1, N_2}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}}.
 Formally,
@@
 {
-For \m {\M{A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}} and \m {\M{B} \in \Mb {M}_{\Mb {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \Mb {M}_{\Mb {K}} \SB {N_1 N_3, N_2 N_4}} by
+For \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}} and \m {\M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \MB {M}_{\MB {K}} \SB {N_1 N_3, N_2 N_4}} by
 \Disp{
@@
 {
-Suppose \m {\M{A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}, \M{X} \in \Mb {M}_{\Mb {K}} \SB {N_2, N_3}, \M{B} \in \Mb {M}_{\Mb {K}} \SB {N_3, N_4}},
+Suppose \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}, \M{X} \in \MB {M}_{\MB {K}} \SB {N_2, N_3}, \M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}},
 Then

### 2019-05-15 dantzig_selector/report/2_problem_setting.tex
Reorganize source files
Proof: Concentration ineq. of

@@
 \NC \V {a} \SB {\psi'}
-\in \NC \Mb {V}_\Mb {C} \SB {N_H} \NR
+\in \NC \MB {V}_\MB {C} \SB {N_H} \NR
 \NC \V {a} \SB {\psi'}
@@
 \NC \M{H}
-\in \NC \Mb {M}_\Mb {C} \SB {N_H} \NR
+\in \NC \MB {M}_\MB {C} \SB {N_H} \NR
 \NC \M{H}
@@
 \Disp {
-\NC \M {F}_B \in \NC \Mb {M}_{\Mb {C}} \SB {N_R, N_Y} \NR
-\NC \M {F}_R \in \NC \Mb {M}_{\Mb {C}} \SB {N_H, N_R} \NR
-\NC \M {W}_R \in \NC \Mb {M}_{\Mb {C}} \SB {N_R, N_H} \NR
-\NC \M {W}_B \in \NC \Mb {M}_{\Mb {C}} \SB {N_Y, N_R} \NR[+]
+\NC \M {F}_B \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_Y} \NR
+\NC \M {F}_R \in \NC \MB {M}_{\MB {C}} \SB {N_H, N_R} \NR
+\NC \M {W}_R \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_H} \NR
+\NC \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R} \NR[+]
 }
@@
 \Disp {
-\NC \Nm {\M {F}_R \DB {n_H, n_R}} = \NC 1, \NR[+]
-\NC \Nm {\M {W}_R \DB {n_R, n_H}} = \NC 1, \NR[+]
-\NC n_H = \NC 0, \dots N_H-1, \NR
-\NC n_R = \NC 0, \dots N_R-1 \NR
+\NC \Nm {\M {F}_R \DB {n_H, n_R}}
+= \NC 1, \NR[+]
+\NC \Nm {\M {W}_R \DB {n_R, n_H}}
+= \NC 1, \NR[+]
+\NC n_H
+= \NC 0, \dots N_H-1, \NR
+\NC n_R
+= \NC 0, \dots N_R-1 \NR
 }
@@
 \Disp{
-\NC \M {Z} \in \NC \Mb {M}_{\Mb {C}} \SB {N_Y, N_Y} \NR[+]
+\NC \M {Z} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR[+]
 }
@@
 \stopsection
-\startsection [title={Proposed Method}]
 \startsubsection [title={Vectorization}]
@@
 \Disp {
-\NC N_h = \NC N_H^2 \NR[+]
-\NC N_y = \NC N_Y^2 \NR[+]
+\NC N_h
+= \NC N_H^2 \NR[+]
+\NC N_y
+= \NC N_Y^2 \NR[+]
 }
@@
 \NC \V {h}
-\in \NC \Mb {V}_{\Mb {C}} \SB {N_h} \NR
+\in \NC \MB {V}_{\MB {C}} \SB {N_h} \NR
 \NC \V {h}
@@
 \NC \V {y}
-\in \NC \Mb {V}_{\Mb {C}} \SB {N_y} \NR
+\in \NC \MB {V}_{\MB {C}} \SB {N_y} \NR
 \NC \V {y}
@@
 \NC \V {z}
-\in \NC \Mb {V}_{\Mb {C}} \SB {N_y} \NR
+\in \NC \MB {V}_{\MB {C}} \SB {N_y} \NR
 \NC \V {z}
@@
 \NC \M {P}^\star
-\in \NC \Mb {M}_{\Mb {C}} \SB {N_y, N_h} \NR
+\in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
 \NC \M {P}^\star
@@
 \Disp {
-\NC \V {y} =\M {P}^\star \V {h} +\V {z} \NR
+\NC \V {y}
+=\M {P}^\star \V {h} +\V {z} \NR
 }
@@
 
-\stopsubsection
-
-\startsubsection [title={Expression for the Angular Space}]
+\stopsection
+\startsection [title={Expression for the Angular Space}]
 
@@
 \Disp {
-\NC \M {K} \in  \NC \Mb {M}_{\Mb {C}} \SB {N_H, N_H} \NR
-\NC \M {K} \DB {n_1, n_2} = \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR[+]
-\NC \quad n_1, n_2 = \NC 0, 1, \dots, N_H-1 \NR
+\NC \M {K} \in  \NC \MB {M}_{\MB {C}} \SB {N_H, N_H} \NR
+\NC \M {K} \DB {n_1, n_2}
+= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR[+]
+\NC \quad n_1, n_2
+= \NC 0, 1, \dots, N_H-1 \NR
 }
@@
 \NC \M {Y}
-\in \NC \Mb {M}_{\Mb {C}} \SB {N_Y, N_Y} \NR
+\in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR
 \NC \M {Y}
@@
 \NC \M {P}
-\in \NC \Mb {M}_{\Mb {C}} \SB {N_y, N_h} \NR
+\in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
 \NC \M {P}
@@
 \NC \V {g}
-\in \NC \Mb {M}_{\Mb {C}} \SB {N_h} \NR
+\in \NC \MB {M}_{\MB {C}} \SB {N_h} \NR
 \NC \V {g}
@@
 }
+
+\stopsection
+\startsection [title={Proposed Method}]
+
 If so, our program reads
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_h}}, \m{\g \geq 0}.
+\item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_h}}, \m{\g \geq 0}.
 \item Calculate
@@
 \NC \Hat {\V {g}}
-= \NC \startcases
-\NC \Min {\V {g}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR[+]
+\LA \NC \startcases
+\NC \Min {\V {g}' \in \MB {V}_{\MB {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR[+]
 \NC \Rm {subject} \; \Rm {to} \quad \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
@@
 \Disp {
-\NC \Hat {G} =\Rm {vec}^{-1} \SB {\Hat {g}} \NR
+\NC \Hat {G}
+\LA \Rm {vec}^{-1} \SB {\Hat {g}} \NR
 }
@@
 \Disp {
-\NC \Hat {\M {H}} =\M {K} \Hat {\M {G}} \M {K}^\Adj \NR
+\NC \Hat {\M {H}}
+\LA \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
 }
@@
 
-\stopsubsection
 \stopsection

### 2019-05-15 dantzig_selector/report/3_theorems_and_proofs.tex
Reorganize source files
Proof: Concentration ineq. of

@@
 We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \m {g \in \Mb {C}^{N_h}}, and we continue to use \m {\hat {g}} to denote the Dantzig Selector.
+The sparse vector to be recovered of our investigation is \m {g \in \MB {C}^{N_h}}, and we continue to use \m {\hat {g}} to denote the Dantzig Selector.
 To simplify the exposition, we will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).
@@
 \Disp {
-\NC \g = \NC \R {2 \log N_h} \NR[+]
+\NC \g 
+= \NC \R {2 \log N_h} \NR[+]
 }
@@
 \Disp {
-\NC \V {d} = \NC \hat {\V {g}} -\V {g} \NR[+]
+\NC \V {d} 
+= \NC \hat {\V {g}} -\V {g} \NR[+]
 }
@@
 \startitemize [1]
-\item \m {\Mc {A}} be the largest \m {s} position of \m {g}.
-\item \m {\Mc {B}} be the largest \m {s} position of \m {d_{T\SB {N_h} -\Mc {A}}}.
-\item \m {\Mc {C} =T \RB {N_h} -\Mc {A}}, i.e., the complementary index set of \m {\Mc {A}}.
+\item \m {\MC {A}} be the largest \m {s} position of \m {g}.
+\item \m {\MC {B}} be the largest \m {s} position of \m {d_{T\SB {N_h} -\MC {A}}}.
+\item \m {\MC {C} =T \RB {N_h} -\MC {A}}, i.e., the complementary index set of \m {\MC {A}}.
 \stopitemize
 
-Suppose \m {\M {A} \in \Mb {M}_{\Mb {K}} \RB {N_1, N_2 }}.
-For brevity, let \m {\Mc {T} \subset T \RB {N_2 }}.
-Denote as \m {\M {A}_{\Mc {T}}} the columns of \m {\M {A}} having indices in \m {\Mc {T}}.
-Let \m {S:\; \Mb {V}_{\Mb {K}} \SB {N} \mapsto \Mb {V}_{\Mb {K}} \SB {N}}, \m {N \in \Mb {N}}, be the sorting function for \m {x \in \Mb {V}_{\Mb {K}} \SB {N})}, so that
+Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \RB {N_1, N_2 }}.
+For brevity, let \m {\MC {T} \subset T \RB {N_2 }}.
+Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
+Let \m {S:\; \MB {V}_{\MB {K}} \SB {N} \mapsto \MB {V}_{\MB {K}} \SB {N}}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} \SB {N})}, so that
 \Disp {
@@
 {
-Let function \m {f:\; T\RB {N} \mapsto \Mb {R}_+}, \m {N \in \Mb {N}}, be given.
-For \m {x \in \Mb {V}_{\Mb {K}} \SB {N}}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
+Let function \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}, be given.
+For \m {x \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
 \Disp {
@@
 {
-For \m {\V {x} \in \Mb {V}_{\Mb {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
+For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
 \Disp {
@@
 \Disp {
-\NC \sin x = \NC x -\F {x^3}{6} + \Mc {O} \SB {x^5}, \quad x \ll 1 \NR
+\NC \sin x 
+= \NC x -\F {x^3}{6} + \MC {O} \SB {x^5}, \quad x \ll 1 \NR
 }
@@
 \Disp {
-\NC \eta := \NC \f \quad \rm{mod}\; (2\pi) \NR[+]
-\NC k := \NC \F {N_H} {2\pi} (\f -\eta) \NR[+]
+\NC \eta :
+= \NC \f \quad \rm{mod}\; (2\pi) \NR[+]
+\NC k :
+= \NC \F {N_H} {2\pi} (\f -\eta) \NR[+]
 }
@@
 {
-For \m {\Mc {T}, \Mc {T}' \subset \{1, \dots, N_p\}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} >0} to be the smallest such that
+Let \m {P} be fixed.
+For \m {\MC {T}, \MC {T}' \subset T \RB {N_p}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} \SB {P} >0} to be the smallest number such that
 \Disp {
-\NC \Nm {\IP {P_{\Mc {T}} h, P_{\Mc {T}'} h'}}
-\leq \NC \tau_{s, s'} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
+\NC \Nm {\IP {P_{\MC {T}} h, P_{\MC {T}'} h'}}
+\leq \NC \tau_{s, s'} \SB {P} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
 }
@@
 {
-Let \m {P} be given.
-Then \m {\tau_{s, s'}} is bounded in both direction as follows,
+Let \m {\M{P}} be fixed.
+Then \m {\tau_{s, s'} \SB {\M{P}}} is bounded in both direction as follows,
 \Disp {
-\NC \d_{s+s'} -\max \SB {\{\d_s, \d_{s'} \}}
-\leq \NC \tau_{s, s'} \NR
-\NC \leq \NC \d_{s+s'}
+\NC \d_{s+s'} \SB {\M{P}} -\max \SB {\CB {\d_s \SB {\M{P}}, \d_{s'} \SB {\M{P}} }}
+\leq \NC \tau_{s, s'} \SB {\M{P}} \NR
+\NC \leq \NC \d_{s+s'} \SB {\M{P}} \NR[+]
 }
@@
 
-Thus \m {\d_s}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
-We may well keep track of \m {\d_s} only.
+Thus \m {\d_s \SB {\M{P}}}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
+We may well keep track of \m {\d_s \SB {\M{P}}} only.
+When \m {\SB {\M{P}}} is clear, we may suppress it.
+
+We seek to find \m {\d_s \SB {\M{F}_B} \SB {\o_t}}, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
+Start with the density of each entry of \m {\M{F}_B}, namely i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}.
+They are (with a slight of abuse of meaning of \m {\o_t} and so on)
+\Disp{
+\NC d \o_t
+=\NC \F {1} {\R {\pi}} \exp
+  \RB {-\MF{Re} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
+d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
+\NC d \o_t
+=\NC \F {1} {\R {\pi}} \exp
+  \RB {-\MF{Im} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
+d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
+\NC n_R
+= \NC 0, 1, 2, \dots, N_R -1 \NR
+\NC n_Y
+= \NC 0, 1, 2, \dots, N_Y -1 \NR
+}
+We know that the magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
+\Disp{
+\NC \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}
+=\NC 0 \NR
+\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2}
+=\NC 1 -\F {\pi}{4} \NR
+}
+Fix test vector \m {\V{u} \in \MB{M}_\MB{C} \SB{N_Y}}, we have to study \m {\VNm {\M{F}_B \V{u}}_2}.
+\Disp{
+\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \V{u}} _2 ^2} \NR
+\NC = \NC \MB{E}
+\SB {
+  \sum_{n_R=0}^{N_R-1}
+  \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}}^2
+} \NR
+\NC = \NC \sum_{n_R=0}^{N_R-1}
+  \MB{E} _{\o_t} \SB {\Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}}^2}
+\NR
+\NC = \NC
+\sum_{n_R=0}^{N_R-1}
+  \MB{E} _{\o_t} \SB {
+      2 \sum_{n_Y, n_Y'=0}^{N_Y-1}
+         \MF {Re} \SB{
+            \M{F}_B \DB {n_R, n_Y} \M{F}_B \DB {n_R, n_Y'}
+            \V{u} \DB{n_Y} ^* \V{u} \DB{n_Y'} ^*
+         }
+   } \NR
+\NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
+  \MB{E} _{\o_t}
+     \SB {\sum_{n_Y=0}^{N_Y-1} \Nm {\M{F}_B \DB {n_R, n_Y}}^2 \Nm {\V{u} \DB{n_Y}}^2}
+\NR
+\NC = \NC
+\sum_{n_R=0}^{N_R-1}
+2 \sum_{n_Y, n_Y'=0}^{N_Y-1}
+\MF {Re} \SB{
+   \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y}}
+   \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y'}}
+}
+\V{u} \DB{n_Y} ^* \V{u} \DB{n_Y'} ^*
+\NR
+\NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
+   \sum_{n_Y=0}^{N_Y-1} \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2} \Nm {\V{u} \DB{n_Y}}^2
+\NR
+\NC = \NC \RB {1 -\F{\pi}{4}} N_Y N_R \VNm {\V{u}} _2 ^2 \NR[+]
+}
+
+Thus, by Chebyshev bound,
+\Disp{
+\NC \MB{P} _{\o_t} \SB {
+   \Nm {\VNm {\M{F}_B \V{u}} _2 -\VNm {\V{u}} _2}
+   \geq \e \VNm {\V{u}}
+}
+\leq \NC \RB {1 -\F{\pi}{4}} \F {N_Y N_R} {\e} \NR
+}
 
@@
 {
-Let \m {P} be i.i.d.\ Radmacher, as defined in Lemma ().
-Then \m {P} is RIP according to \m {\d} for at least probability
-\Disp {
-\NC 1 -2 \RB { \F {12}{\d} }^s \exp \left[ - \RB { \F {\epsilon^2}{4} -\F {\epsilon^3}{6} } \F {\d}{2} N_p \right] \NR
-}
 }
 
-\color[red]{(To be done)}
+\stoptext
 
@@
 The rest follows ``The Dantzig Selector'' very closely.
-The generalization to complex vector is necessary (though we will ultimately do it in simulation involving real numbers only.
+The generalization to complex vector is necessary in our setting.
 We spell out the proof when such generalization is nontrivial.
@@
 \Disp {
-\NC \VNm {\V {d}_{\Mc {C}}} _1
-\leq \NC \VNm {\V {d}_{\Mc {A}}} _1 +2\VNm {\V {g}_{\Mc {C}}} _1 \NR
+\NC \VNm {\V {d}_{\MC {C}}} _1
+\leq \NC \VNm {\V {d}_{\MC {A}}} _1 +2\VNm {\V {g}_{\MC {C}}} _1 \NR
 }
@@
 
-To show this, observe that with triangle inequality applied respectively on \m {\Mc {A}} and \m {\Mc {C}},
+To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}},
 \Disp {
 \NC \VNm {\V {g}} _1
--\VNm {\V {d}_{\Mc {A}}} _1
-+\VNm {\V {d}_{\Mc {C}}} _1
--\VNm {\V {g}_{\Mc {C}}} _1
+-\VNm {\V {d}_{\MC {A}}} _1
++\VNm {\V {d}_{\MC {C}}} _1
+-\VNm {\V {g}_{\MC {C}}} _1
 \leq \NC \VNm {\V {g} +\V {d}} _1 \NR
 }
-In the first line, we recall \m {\V {g} =\V {g}_{\Mc {A}}}.
+In the first line, we recall \m {\V {g} =\V {g}_{\MC {A}}}.
 On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
@@
 \leq \NC  2 \R {\log N_h},
-\quad n_g =1, \dots, N_h. \NR
+\quad n_g 
+=1, \dots, N_h. \NR
 }
@@
 \NC Q\SB {x}
-\leq \NC \F {1}{2} \Rm {e}^{-x^2/2} \NR
+\leq \NC \F {1}{2} \Ss {e}^{-x^2/2} \NR
 }
@@
 \leq \NC  4 \R {\log N_h},
-\quad n_g =1, \dots, N_h. \NR
+\quad n_g 
+=1, \dots, N_h. \NR
 }
@@
 \Disp {
-\NC \VNm {\V {d}_{\Mc {AB}}} _2
-\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\Mc {A} \Mc {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{C}} _1 \NR
+\NC \VNm {\V {d}_{\MC {AB}}} _2
+\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{C}} _1 \NR
 }
@@
 \NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d}_{\Mc {A} \Mc {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\Mc {C}}} _1^2 \NR
+\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
 }
@@
 \Disp {
-\NC \VNm {\M {P}_{\Mc {A} \Mc {B}}^\Tr \M {P} \V {d}} _2
+\NC \VNm {\M {P}_{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
 \leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
@@
 \leq \NC \R {L} \VNm { \V {d}_{A} } _2 \NR
-\NC \leq \NC \R {L} \VNm { \V {d}_{\Mc {AB}} } _2 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\Mc {C}} } _1 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
+\NC \leq \NC \R {L} \VNm { \V {d}_{\MC {AB}} } _2 \NR
+\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
 }
 
-As the next step, we must eliminate \m {\VNm {d_{\Mc {A}}} _1} in rhs of Lemma ().
+As the next step, we must eliminate \m {\VNm {d_{\MC {A}}} _1} in rhs of Lemma ().
 \Disp {
-\NC \VNm { \V {d}_{\Mc {C}} } _1
-\leq \NC \VNm { \V {d}_{\Mc {A}} } _1 +2 \VNm { \V {g}_{\Mc {C}} } _1 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\Mc {C}} } _1
-+2 \VNm { \V {g}_{\Mc {C}} } _1
+\NC \VNm { \V {d}_{\MC {C}} } _1
+\leq \NC \VNm { \V {d}_{\MC {A}} } _1 +2 \VNm { \V {g}_{\MC {C}} } _1 \NR
+\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1
++2 \VNm { \V {g}_{\MC {C}} } _1
 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
@@
 \Disp {
-\NC \VNm { \V {d}_{\Mc {C}} } _1
-\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g}_{\Mc {C}} } _1
+\NC \VNm { \V {d}_{\MC {C}} } _1
+\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g}_{\MC {C}} } _1
 +\F {4} {1-\d_{2L} -\d_{3L}} \R {L N_h \log N_h} \NR
@@
 \NC \VNm { \V {d} } _2^2
-\leq \NC \VNm {\V {d}_{\Mc {A} \Mc {B}}} _2^2 +\F {1}{L} \VNm {\V {d}_{\Mc {C}}} _1^2 \NR
-\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d}_{\Mc {C}}} _1^2
-+\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_h \log N_h} \VNm {\V {d}_{\Mc {C}}} _1 \NR
+\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
+\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d}_{\MC {C}}} _1^2
++\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_h \log N_h} \VNm {\V {d}_{\MC {C}}} _1 \NR
 \NC \NC \quad +\F {16}{\RB {1-\d_{2L}}^2} N_h \log N_h \NR
 }
-Finally, plug in the bound for \m {\VNm {\V {d}_{\Mc {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d}_{\Mc {C}}} _1}.
+Finally, plug in the bound for \m {\VNm {\V {d}_{\MC {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d}_{\MC {C}}} _1}.
 There are several dozens of terms if we expand all.

### 2019-05-15 dantzig_selector/report/4_simulation.tex
Correct vectorize convention
Draft: Matrices generation
Reorganize source files
Proof: Concentration ineq. of

@@
 
-As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\Mc {R} \SB {h}}.
+As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} \SB {h}}.
 But it is not the end.
@@
 {
-For \m {\V{x} \in \Mb {V}_{\Mb {C}} \SB {M}}, we say that \m {\Mc {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
-%
+For \m {\V{x} \in \MB {V}_{\MB {C}} \SB {M}}, we say that \m {\MC {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
 \Disp {
-\NC \Mc {R} \SB {\V{x}}
-\in \NC \Mb {V}_{\Mb {R}} \SB {2M} \NR
-\NC \Mc {R} \SB {\V{x}} \DB {m} =
-\NC \startcases
-\NC \Mf {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
-\NC \Mf {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
+\NC \MC {R} \SB {\V{x}}
+\in \NC \MB {V}_{\MB {R}} \SB {2M} \NR
+\NC \MC {R} \SB {\V{x}} \DB {m}
+= \NC \startcases
+\NC \MF {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
+\NC \MF {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
 \stopcases \NR[+]
@@
 }
-The bijectivity is obvious, and we define \m {\Mc {R} ^{-1}} so that
+The bijectivity is obvious, and we define \m {\MC {R} ^{-1}} so that
 \Disp {
-\NC \Mc {R} ^{-1} \SB {\Mc {R} \SB {\V{x}}}
+\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V{x}}}
 =\NC \V{x} \NR[+]
@@
 {
-For \m {\M{A} \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
-%
+For \m {\M{A} \in \MB {M}_{\MB {C}} \SB {M_1, M_2}}, we say that \m {\MC {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
 \Disp {
-\NC \Mc {R} \SB {\M{A}}
-\in \NC \Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2} \NR
-\NC \Mc {R} \SB {\M{A}} \DB {m_1,m_2} =
+\NC \MC {R} \SB {\M{A}}
+\in \NC \MB {M}_{\MB {R}} \SB {2M_1, 2M_2} \NR
+\NC \MC {R} \SB {\M{A}} \DB {m_1,m_2} =
 \NC \startcases
-\NC \Mf {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
-\NC \Mf {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
-\NC -\Mf {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
-\NC \Mf {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
+\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
+\NC \MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
+\NC -\MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
+\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
 \stopcases \NR[+]
@@
 }
-Notice that Here not all matrices in \m {\Mb {M}_{\Mb {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
+Notice that Here not all matrices in \m {\MB {M}_{\MB {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
 }
@@
 \NC \T {\V {y}}
-\in \NC \Mb {V}_{\Mb {R}} \SB {2N_y} \NR
+\in \NC \MB {V}_{\MB {R}} \SB {2N_y} \NR
 \NC \T {\V {y}}
-= \NC \Mc {R} \SB {\V {y}} \NR[+]
+= \NC \MC {R} \SB {\V {y}} \NR[+]
 \NC \T {\V {g}}
-\in \NC \Mb {V}_{\Mb {R}} \SB {2N_h} \NR
+\in \NC \MB {V}_{\MB {R}} \SB {2N_h} \NR
 \NC \T {\V {g}}
-= \NC \Mc {R} \SB {\V {g}} \NR[+]
+= \NC \MC {R} \SB {\V {g}} \NR[+]
 \NC \T {\M {P}}
-\in \NC \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_h} \NR
+\in \NC \MB {M}_{\MB {R}} \SB {2N_y, 2N_h} \NR
 \NC \T {\M {P}}
-= \NC \Mc {R} \SB {\M {P}} \NR[+]
+= \NC \MC {R} \SB {\M {P}} \NR[+]
+\NC \T {\M {P}} ^\Adj
+\in \NC \MB {M}_{\MB {R}} \SB {2N_y, 2N_h} \NR
+\NC \T {\M {P}} ^\Adj
+= \NC \MC {R} \SB {\M {P} ^\Adj} \NR[+]
 \NC \T {\V {z}}
-\in \NC \Mb {V}_{\Mb {R}} \SB {2N_y} \NR
+\in \NC \MB {V}_{\MB {R}} \SB {2N_y} \NR
 \NC \T {\V {z}}
-= \NC \Mc {R} \SB {\V {z}} \NR[+]
+= \NC \MC {R} \SB {\V {z}} \NR[+]
 }
-%
 such that, by construction,
-%
 \Disp {
@@
 }
-%
 
@@
 
-%
 \Disp {
 \NC {\V {u}}_{n_h}
-\in \NC \Mb {V}_{\Mb {R}} \SB {N_h} \NR
+\in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
 \NC {\V {u}}_{n_h} \DB {n_h'}
@@
 \stopcases \NR[+]
-\NC {\T {\M {U}}}_{n_h} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
+\NC {\T {\M {U}}}_{n_h} \in \NC \MB {M}_{\MB {R}} \SB {2N_h, 2N_h} \NR
 \NC {\T {\M {U}}}_{n_h} \DB {n_h', n_h''}
@@
 1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
-1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h \NR
-1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h +1 \NR
 1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
@@
 \Disp{
-\NC \V {m} \NC \in \Mb {V}_{\Mb {R}} \SB {N_h} \NR
+\NC \V {m} \NC \in \MB {V}_{\MB {R}} \SB {N_h} \NR
 \NC \V{m} \DB{n_h}
@@
 \MC \IP { \V {1}, \V {m} } \NR
-\NC \Mr {subject} \; \Mr {to} \quad
+\NC \Rm {subject} \; \Rm {to} \quad
 \MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
@@
 \NC \V{t}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
+\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
 \NC \V{x}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
+\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
 \NC \M{A}_i
-\NC \in \Mb {M}_{\Mb {R}} \SB {2N_h, 3N_h} \NR
+\NC \in \MB {M}_{\MB {R}} \SB {2N_h, 3N_h} \NR
 \NC \V{b}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {3N_h} \NR
+\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
 \NC \V{c}_i
-\NC \in \Mb {V}_{\Mb {R}} \SB {2N_h} \NR
+\NC \in \MB {V}_{\MB {R}} \SB {2N_h} \NR
 \NC d_i
-\NC \in \Mb {R} \NR
+\NC \in \MB {R} ^+ \NR
 }
@@
 \NC \V{t}
-= \NC \startthematrix
+= \NC \startTheMatrix
 \NC \V{0} \NR
 \NC \V{1} \NR
-\stopthematrix \NR[+]
+\stopTheMatrix \NR[+]
 \NC \V{x}'
-= \NC \startthematrix
+= \NC \startTheMatrix
 \NC \T {\V {g}}' \NR
 \NC \V{m} \NR
-\stopthematrix \NR[+]
+\stopTheMatrix \NR[+]
 }
@@
 \NC \M{A}_i
-= \NC \startthematrix
+= \NC \startTheMatrix
 \NC \T {\M {U}}_{i}, \NC \M{0} \NR
-\stopthematrix \NR[+]
+\stopTheMatrix \NR[+]
 \NC \V{b}_i
@@
 \NC \V{c}_i
-= \NC \startthematrix
+= \NC \startTheMatrix
 \NC \V{0} \NR
 \NC \V {u}_{i} \NR
-\stopthematrix \NR[+]
+\stopTheMatrix \NR[+]
 \NC d_i
@@
 \NC \M{A}_i
-= \NC \startthematrix
-\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
-\stopthematrix \NR[+]
+= \NC \startTheMatrix
+\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
+\stopTheMatrix \NR[+]
 \NC \V{b}_i
-=\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
+=\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
 \NC \V{c}_i
-= \NC \startthematrix
-\NC \V{0} \NR
-\NC \V{0} \NR
-\stopthematrix \NR[+]
+= \NC \V{0} \NR[+]
 \NC d_i
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_y}}, \m{\g \geq 0}.
+\item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_y}}, \m{\g > 0}.
 \item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
@@
 \NC \Hat {\V {x}}
-= \NC \startcases
-\NC \Min {\V {x}' \in \Mb {V}_{\Mb {C}} \SB {N_h}}
+\LA \NC \startcases
+\NC \Min {\V {x}' \in \MB {V}_{\MB {C}} \SB {N_h}}
 \MC \IP {\V {t}, \V {x}'} \NR[+]
-\NC \Mr {subject} \; \Mr {to}
+\NC \Rm {subject} \; \Rm {to}
 \quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
 \leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
-\NC \MC i =0, 1, 2, \dots, 2N_h -1 \NR
+\NC \MC i 
+=0, 1, 2, \dots, 2N_h -1 \NR
 \stopcases \NR[+]
@@
 \Disp{
-\NC \Hat{\T{\V{g}}} =\NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
+\NC \Hat{\T{\V{g}}}
+\LA \NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
 }
@@
 \Disp{
-\NC \Hat{\V{g}} =\NC \Mc{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
+\NC \Hat{\V{g}}
+\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
 }
@@
 \Disp {
-\NC \Hat {G} =\NC \Mr {vec}^{-1} \SB {\Hat {g}} \NR[+]
+\NC \Hat {G}
+\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR[+]
 }
@@
 \Disp {
-\NC \Hat {\M {H}} =\NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
+\NC \Hat {\M {H}}
+\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
 }

### 2019-05-15 dantzig_selector/code/src/classes.py

@@ -115,8 +115,6 @@ class Dd_ss:
         g_repr_hat = x_hat [0 : 2 * cst.nn_h -1]
         self.g_hat = inv_find_repr_vec (g_repr_hat)
 
-# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
-
 class Oo_mm_pp:
     def __init__(self):
         self.pp = pp
@@ -124,7 +122,6 @@ class Oo_mm_pp:
         self.g_hat = np.zeros ((cst.nn_hh))
     def run (self):
         
-# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
 
 class Ll_ss:
     def __init__(self, pp, y):
@@ -133,8 +130,6 @@ class Ll_ss:
         self.g_hat = np.zeros ((cst.nn_hh))
     def run (self):
         g_hat =pp.conj().T @ numpy.linalg.inv (self.pp @ self.pp.conj().T).inv @ self.y
-
-# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
 
 class Data:
     def __init__ (self, arr, legend):

### 2019-05-18 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Concentration of F_B

@@
 
-\startsection [title={Design of RIP Precoders and Combiners}]
+\startsection [title={Design of \m {\M{F}_B}}]
 
@@
 We seek to find \m {\d_s \SB {\M{F}_B} \SB {\o_t}}, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
-Start with the density of each entry of \m {\M{F}_B}, namely i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}.
+Try to set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\a >0}.
 They are (with a slight of abuse of meaning of \m {\o_t} and so on)
@@
 \NC d \o_t
-=\NC \F {1} {\R {\pi}} \exp
-  \RB {-\MF{Re} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
+=\NC \F {1} {\R {\pi} \a} \exp
+  \RB {-\F{1}{\a^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
 d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
 \NC d \o_t
-=\NC \F {1} {\R {\pi}} \exp
-  \RB {-\MF{Im} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
+=\NC \F {1} {\R {\pi} \a} \exp
+  \RB {-\F{1}{\a^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
 d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
@@
 \Disp{
-\NC \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}
-=\NC 0 \NR
-\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2}
-=\NC 1 -\F {\pi}{4} \NR
+\NC \NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}} \NR
+\NC =\NC \F{\R{\pi}}{2} \a \NR[+]
+\NC M_2
+:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
+\NC =\NC \a^2 \NR[+]
+\NC M_4
+:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
+\NC =\NC 2 \a^4 \NR[+]
 }
-Fix test vector \m {\V{u} \in \MB{M}_\MB{C} \SB{N_Y}}, we have to study \m {\VNm {\M{F}_B \V{u}}_2}.
+Fix test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we have to study the concentration of \m {\VNm {\M{F}_B \V{u}}_2} in probability mass.
+We shall exploit Chebyshev bound, which required the first and second moment to be found.
 \Disp{
-\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \V{u}} _2 ^2} \NR
+\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2} \NR
 \NC = \NC \MB{E}
@@
   \sum_{n_R=0}^{N_R-1}
-  \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}}^2
+  \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
 } \NR
 \NC = \NC \sum_{n_R=0}^{N_R-1}
-  \MB{E} _{\o_t} \SB {\Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}}^2}
+  \MB{E} \SB {\Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2}
 \NR
@@
 \sum_{n_R=0}^{N_R-1}
-  \MB{E} _{\o_t} \SB {
-      2 \sum_{n_Y, n_Y'=0}^{N_Y-1}
+  \MB{E} \SB {
+     2 \sum_{\startsubstack n_Y, n_Y'=0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
        \MF {Re} \SB{
-            \M{F}_B \DB {n_R, n_Y} \M{F}_B \DB {n_R, n_Y'}
-            \V{u} \DB{n_Y} ^* \V{u} \DB{n_Y'} ^*
+         \M{F}_B \DB {n_R, n_Y} ^* \M{F}_B \DB {n_R, n_Y'}
+         \V{u} \DB{n_Y} \V{u} \DB{n_Y'} ^*
        }
@@
 \NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
-  \MB{E} _{\o_t}
+  \MB{E}
      \SB {\sum_{n_Y=0}^{N_Y-1} \Nm {\M{F}_B \DB {n_R, n_Y}}^2 \Nm {\V{u} \DB{n_Y}}^2}
@@
 \NC = \NC
-\sum_{n_R=0}^{N_R-1}
-2 \sum_{n_Y, n_Y'=0}^{N_Y-1}
+2 \sum_{n_R=0}^{N_R-1}
+\sum_{\startsubstack n_Y, n_Y'=0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
 \MF {Re} \SB{
-   \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y}}
-   \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y'}}
+   \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^*}
+   \MB{E} \SB {\M{F}_B \DB {n_R, n_Y'}}
 }
-\V{u} \DB{n_Y} ^* \V{u} \DB{n_Y'} ^*
+\V{u} \DB{n_Y} \V{u} \DB{n_Y'} ^*
 \NR
 \NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
-   \sum_{n_Y=0}^{N_Y-1} \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2} \Nm {\V{u} \DB{n_Y}}^2
+   \sum_{n_Y=0}^{N_Y-1} \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2} \Nm {\V{u} \DB{n_Y}}^2
 \NR
-\NC = \NC \RB {1 -\F{\pi}{4}} N_Y N_R \VNm {\V{u}} _2 ^2 \NR[+]
+\NC = \NC \a^2 N_R \VNm {\V{u}} _2 ^2 \NR[+]
+}
+Thus, we may set
+\Disp{
+\NC \a
+=\NC \F {1} {\R{N_R}} \NR[+]
+}
+To make
+\Disp{
+\NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2}
+=\NC \VNm {\V{u}} _2 ^2
 }
 
+Similarly, we have to find, in advance, the second moment.
+\Disp{
+\NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4}
+=\NC \SB {
+  \RB {
+    \sum_{n_R=0}^{N_R-1}
+    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
+  } ^2
+}
+\NR[+]
+}
+Without spelling out everything, we notice that as long as a term has a single \m {\M{F}_B \DB {n_R, n_Y}} factor, it's expectation is zero.
+Also notice that
+\Disp{
+\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
+\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
+   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
+\NC \NC \quad \quad +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
+      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
+\NC = \NC 0 \NR[+]
+}
+Having said that, with straightforward calculation, we see that the remaining terms are
+\Disp{
+\NC \NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4} \NR
+\NC = \NC
+\sum_{n_R=0}^{N_R-1} \sum_{n_Y=0}^{N_Y-1}
+\Nm {\M{F}_B \DB {n_R, n_Y}} ^4
+\Nm {\V{u} \DB{n_Y}} ^4 \NR
+\NC \NC \quad \quad
++\sum _{\startsubstack n_R, n_R' =0 \NR n_R <n_R' \stopsubstack}^{N_R-1}
+\sum _{n_Y =0}^{N_Y-1}
+\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
+\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
+\Nm {\V{u} \DB{n_Y}} ^2
+\Nm {\V{u} \DB{n_Y'}} ^2 \NR
+\NC \NC \quad \quad
++\sum _{n_R, n_R' =0}^{N_R-1}
+\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
+\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
+\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
+\Nm {\V{u} \DB{n_Y}} ^2
+\Nm {\V{u} \DB{n_Y'}} ^2 \NR
+\NC \NC \quad \quad
++\sum _{n_R =0}^{N_R-1}
+\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
+\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
+\Nm {\M{F}_B \DB {n_R, n_Y'}} ^2
+\Nm {\V{u} \DB{n_Y}} ^2
+\Nm {\V{u} \DB{n_Y'}} ^2 \NR
+\NC =\NC N_R \D M_4 \D \VNm {\V{u}} _4 ^4
+   +\F {1} {2} N_R \RB {N_R-1} \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
+\NC \NC \quad \quad + N_R^2 \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}
+   + N_R \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
+\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
++\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
+}
+Plugging in the moments, we have
+\Disp{
+\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
++\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
+}
+Use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, and we have simply
+\Disp{
+\NC \NC \leq \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
+}
+In conclusion,
+\Disp{
+\NC \Ss{Var} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2}
+\leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
+}
 Thus, by Chebyshev bound,
-\Disp{
-\NC \MB{P} _{\o_t} \SB {
-   \Nm {\VNm {\M{F}_B \V{u}} _2 -\VNm {\V{u}} _2}
-   \geq \e \VNm {\V{u}}
-}
-\leq \NC \RB {1 -\F{\pi}{4}} \F {N_Y N_R} {\e} \NR
-}
-
 \Result
@@
 {
+Let \m {\M{F}_B \in \MB {M}_{\MB {C}} \SB {N_R, N_Y}} be generated randomly according to ().
+Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_Y}}, and for any \m {\e >0},
+\Disp{
+\NC \MB{P} _{\o_t}
+\SB {
+  \Nm {\VNm {\M{F}_B \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
+  \geq \e \VNm {\V{u}} _2 ^2
+}
+\leq \NC \F {1} {2\e^2} \NR[+]
+}
 }
 
-\stoptext
+\stopsection
 
-\startsection [title={DS for Complex Vectors}]
+\startsection [title={Design of \m {\M{F}_R}}]
+
+Let \m {\M{F}_B \DB {n_R, n_Y}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
+
+\Disp{
+\NC d \o_t
+= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_R, n_Y} \SB {\o_t}}} ^2}^{-1/2}
+d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
+\NC d \o_t
+= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_R, n_Y} \SB {\o_t}}} ^2}^{-1/2}
+d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
+}
+
+\Disp{
+\NC \NC \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} \NR
+\NC =\NC \a \NR[+]
+\NC M_2
+:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
+\NC =\NC \a^2 \NR[+]
+\NC M_4
+:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
+\NC =\NC \a^4 \NR[+]
+}
+
+\stopsection
+
+\startsection [title={Mean Square Error Analysis for Complex DS}]
 

### 2019-05-19 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Concentration of F_R

@@
 }
-Fix test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we have to study the concentration of \m {\VNm {\M{F}_B \V{u}}_2} in probability mass.
+Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we have to study the concentration of \m {\VNm {\M{F}_B \V{u}}_2} in probability mass.
 We shall exploit Chebyshev bound, which required the first and second moment to be found.
@@
 \Disp{
-\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
-+\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
+\NC =\NC -\F{3}{2} \RB {1 -\F{1}{N_R}} \VNm {\V{u}} _4 ^4
++\F{1}{2} \RB {3 +\F{1}{N_R}} \VNm {\V{u}} _2 ^4 \NR[+]
 }
@@
 }
+
 In conclusion,
@@
 
-Let \m {\M{F}_B \DB {n_R, n_Y}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
-
+Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
 \Disp{
 \NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_R, n_Y} \SB {\o_t}}} ^2}^{-1/2}
-d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
+= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} ^2}^{-1/2}
+d \MF{Re} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
 \NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_R, n_Y} \SB {\o_t}}} ^2}^{-1/2}
-d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
+= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} ^2}^{-1/2}
+d \MF{Im} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
+}
+As a result,
+\Disp{
+\NC \NC \MB{E} _{\o_t} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}} \NR
+\NC =\NC \a \NR[+]
+\NC M_2
+:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^2} \NR
+\NC =\NC \a^2 \NR[+]
+\NC M_4
+:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^4} \NR
+\NC =\NC \a^4 \NR[+]
 }
 
+Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_H}}, 
+By a similar argument, we may set
 \Disp{
-\NC \NC \MB{E} _{\o_t} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} \NR
-\NC =\NC \a \NR[+]
-\NC M_2
-:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
-\NC =\NC \a^2 \NR[+]
-\NC M_4
-:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
-\NC =\NC \a^4 \NR[+]
+\NC \a
+=\NC \F {1} {\R{N_H}} \NR[+]
+}
+to make
+\Disp{
+\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_R \SB {\o_t} \V{u}} _2 ^2} \NR
+\NC = \NC \VNm {\V{u}} _2 ^2 \NR[+]
+}
+Furthermore, if we plug in the moments and use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, we have simply
+\Disp{
+\NC \NC \MB{E} \SB {\VNm {\M{F}_R \V{u}} _2 ^4} \NR
+\NC =\NC \RB {N_H M_4 -\F{1}{2} \RB {3N_H^2 +N_H} M_2^2} \VNm {\V{u}} _4 ^4
++\F{1}{2} \RB {3N_H^2 +N_H} M_2^2 \VNm {\V{u}} _2 ^4 \NR
+\NC =\NC -\F{1}{2} \RB {3 -\F{1}{N_H}} \VNm {\V{u}} _4 ^4
++\F{1}{2} \RB {3 +\F{1}{N_H}} \VNm {\V{u}} _2 ^4 \NR
+\NC \leq \NC \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
+}
+
+In conclusion,
+\Disp{
+\NC \Ss{Var} _{\o_t} \SB {\VNm {\M{F}_R \SB {\o_t} \V{u}} _2 ^2}
+\leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
+}
+Thus, by Chebyshev bound, we obtain an identical expression,
+\Result
+{Lemma}
+{
+Let \m {\M{F}_R \in \MB {M}_{\MB {C}} \SB {N_H, N_R}} be generated randomly according to ().
+Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_R}}, and for any \m {\e >0},
+\Disp{
+\NC \MB{P} _{\o_t}
+\SB {
+  \Nm {\VNm {\M{F}_R \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
+  \geq \e \VNm {\V{u}} _2 ^2
+}
+\leq \NC \F {1} {2\e^2} \NR[+]
+}
 }

### 2019-05-20 dantzig_selector/report/1_introduction.tex
Proof: Rev. almost sparsity of g

@@
 This section is organized as follows.
-Before we start, we introduce our notation in the very beginning, since the literature survery quickly goes into technical details.
-And we first provide the motivation, and then overview the existent literature on channel estimation.
+We first provide the motivation, and then overview the existent literature on channel estimation.
 Particularly, we will summerize present results on DS and OMP, and argue that DS is a viable solution that has been ignored, and then claim our contribution in this article that will be shown in the later sections.
 
-\startsection [title={Notation}]
+\stopsection
 
-Before we start, let us remind that, in this article, to avoid confusion all results other than the major theorems to be proved are called lemmata, so the classification may be different from its source.
-
-First of all, round brackets \m {\RB {\cdot}} are used purely for precedence of , and \m {\SB {\cdot}} exclusively for function arguments, for better clarity.
-
-\m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
-The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} \SB {a}} and \m {\MF {Im} \SB {a}}, respectively, thus \m {a =\MF {Re} \SB {a} + \Ss{i} \MF {Im} \SB {a}}
-
-We restrict our discussion to \m {\MB {R}^N} or \m {\MB {C}^N} seen as the Hilbert space , equipped with standard inner product.
-Lower case Latin alphabets with single underline, like \m {\V {a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m {\M {A}}, denote matrices.
-Particularly, define \m {\V {1} =\IP {1, \dots, 1}}.
-Denote \m {\V {a} \DB {n}} to be the \m {n}-th component of \m {\V {a}}, and similarly \m {\M {A} \DB {m,n}} to be the \m {m,n}-th entry of \m {\M {A}}.
-
-In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
-Of course, scalar operation on \m {\MB {R}^N} is over field \m {\MB {R}}, and that on \m {\MB {C}^N} is over field \m {\MB {C}}.
-We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
-Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} \SB {N}}.
-We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} \SB {M,N}}, and its role as linear transformation is understood.
-Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
-Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {m,n}-entry of \m {\V {A}}
-To better correspond to the pseudo code, the numbering of both vector and matrix entries are zero-based, that is, numbered from \m {0,1,2,\dots}.
-Especially when manipulating the indices, but also in the main proof of DS bound, we will encounter the modulo as operation, namely the remainder of \m {m} divided by \m {n}, with \m {m, n \geq 0}, and we use the capital \m {m\; \Rm{Mod}\; n} to denote that number.
-And we denote \m {\V {u}_n} to be the \m {n}-th unit vector in the Cartesian coordinates, whose numbering is also zero-based.
-\m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
-Recall that \m {\ell_\infty}-norm is the maximum-magnitude norm.
-
-Denote as \m {\MB {P} \SB {X}} the probability, \m {\MB {E} \SB {X}} the expectation, and \m {\MB {Var} \SB {X}} the variance.
-Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables like \m {\MB {P} _\o \SB {X \SB {\o}}}.
-
-\stopsection
 \startsection [title={Background}]
@@
 {
-Consider \m {P \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
+Consider \m {\Phi \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
 For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N_p}}, for all \m {\MC {T} \subset T\SB {N_m}} with \m {\#\{\MC {T} \} \leq s},
-
 \Disp {
-\NC \NC \RB {1-\d_s} \VNm {V {x}}^2 \NR
-\NC \leq \NC \VNm {P_{\MC {T}} \V {x}} _2^2 \NR
+\NC \NC \RB {1-\d_s} \VNm {\V {x}}^2 \NR
+\NC \leq \NC \VNm {\Phi_{\MC {T}} \V {x}} _2^2 \NR
 \NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]

### 2019-05-20 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Rev. almost sparsity of g

@@
 }
-Note that there are infinitely many sorting functions depending on how to break the tie, but we fix any \m {S} throughout this article.
+
+Denote the sorting function to be \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}.
+That is, for \m {x \in \MB {V}_{\MB {K}} \SB {N}}, \m {x} is confined in sorted magnitude according to \m {f}.
 For definiteness, we may compare the first component first, and the second, and so on.
-If still there is a tie for a certain component (for complex numbers), we compare the real part first, then the imaginary part.
-
-\Result
-{Definition}
-{
-Let function \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}, be given.
-For \m {x \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {x} is confined in sorted magnitude according to \m {f}, if
+If still there is a tie for a certain component (for complex numbers), the order is irrelevent.
+Formally,
 \Disp {
-\NC \Nm {S\SB {x} \DB {n} } < \NC f \SB {n},
-\quad n \in T\RB {N}. \NR
-}
+\NC \Nm {\MC{S} \SB {x} \DB {n} }
+\leq \NC f \SB {n},
+\quad n \in T \RB {N}. \NR
 }
@@
 {
-For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse with \m {\ell_1}-residue \m {R}, if
+For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse according to the \m {\ell_p}-norm with remainder \m {R}, if
 \Disp {
-\NC \sum_{n=s+1}^N \Nm {S\SB {\V {x}} \SB {n}}
+\NC \sum_{n=s}^N \Nm {\MC{S} \SB {\V {x}} \SB {n}}
 \leq \NC R. \NR
@@
 \Result
-{Lemma (Tentative)}
+{Lemma}
 {
@@
 Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
-Then \m {\V {a} \SB {\f}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
+Then \m {\V {a} \SB {\f}} is almost-\m {L}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
 \Disp {
 \NC R
-\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
+= \NC \F {1}{\pi} \log \F {N_H}{L-1}. \NR
 }
@@
 
-We show the lemma, which is the key to bounding the sparsity of \m {h}.
-Recall the identity for Dirichlet kernel
+We now show the lemma, which is the key to bounding the sparsity of \m {h}.
+Let \m {\f'} be fixed.
+What we have to bound is
+\Disp {
+\NC R \SB {\f'}
+=\NC \sum_{n_H =s}^{N_H -1}
+   \RB {\MC{S} \SB {\M {K}^\Adj \V {a} \SB {\f}}} \DB {n_H} \NR[+]
+}
+Observe
+\Disp {
+\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {n_H}
+=\NC \F {1}{N_H} D \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H} {N_H}} \NR
+}
+where \m {D} is the Dirichlet kernel
 \Disp {
 \NC D \SB {\f'}
-:= \NC \Nm { \sum_{n=0}^{N_H-1} \Rm {e}^{i n \f'} } \NR
+:= \NC \Nm { \sum_{n_H=0}^{N_H-1} \Rm {e}^{i n_H \f'} } \NR
 \NC = \NC \F {\Nm {\sin \SB {N_H \f'/2}}}{\Nm {\sin \SB {\f' /2}}}, \NR[+]
@@
 }
-And recall the Taylor expansion of sin for the first two terms with respect to zero
+Now, it can be verified that
+\Result
+{Lemma}
+{
+For \m {-\pi \leq x < \pi}, we have
 \Disp {
-\NC \sin x 
-= \NC x -\F {x^3}{6} + \MC {O} \SB {x^5}, \quad x \ll 1 \NR
+\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}. \NR[+]
 }
-Actually it can be shown that we have a inequality
-\Disp {
-\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}, \NR[+]
-\NC -\pi \leq \NC x \leq \pi \NR
 }
-Applying the above inequality to the denominator and bounding the nominator by 1, we have
+Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
 \Disp {
 \NC \Nm {D \SB {\f'} }
-= \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}}
-\quad 0 \leq \f' \leq \pi. \NR
+\leq \NC B \SB {\f'} \NR
+\NC := \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}} \NR[+]
+\NC -\pi \leq \NC \f' < \pi. \NR
+}
+Thus,
+\Disp {
+\NC R \SB {\f'}
+=\NC \sum_{n_H =s}^{N_H -1}
+   \F {1}{N_H}
+   \MC{S}
+   \SB {
+      \sum_{n_H' =s}^{N_H -1}
+      B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H'} {N_H}}
+      \V {u}_{n_H'}
+   }
+   \DB {n_H}
+\NR[+]
+}
+Notice that \m {\Nm {B \SB {\phi'}}} is monotone, and then
+\Disp{
+\NC \NC \MC{S}
+\SB {
+   \sum_{n_H' =s}^{N_H' -1}
+   B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H'} {N_H}}
+   \V {u}_{n_H'}
+}
+\DB {n_H} \NR
+\NC =\NC B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H} {N_H}} \NR
+\NC \leq \NC B \SB {\F {2 \pi n_H} {N_H}} \NR[+]
+}
+What we saw gives
+\Disp{
+\NC R \SB {\f'}
+=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1}
+   B \SB {\F {2 \pi n_H} {N_H}} \NR
 }
 
-Particularly, for arbitrary \m {\f}, find \m {k} by
-\Disp {
-\NC \eta :
-= \NC \f \quad \rm{mod}\; (2\pi) \NR[+]
-\NC k :
-= \NC \F {N_H} {2\pi} (\f -\eta) \NR[+]
-}
-Then observe
-\Disp {
-\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {k}
-=\NC \F {1}{N_H} D \RB {\f -\F {2 \pi k} {N_H}} \NR
-}
-So we need only bound
-\Disp {
-\NC R\SB {\eta}
-:=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1} D \RB { \eta +\F {2 \pi n_H} {N_H} } \NR
-}
 By the approximation of rectangle to integral,
@@
 
-\startsection [title={Design of \m {\M{F}_B}}]
+\startsection [title={Concentration Inequality of \m {\M{F}_B, \M{W}_B}}]
 
@@
 }
+According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), substitution of relevent quantities yields
+\Result
+{Lemma}
+{
+Let \m {\M{F}_B ^\Tr} be found as above.
+Suppose the probability that RIP holds for \m {\M{F}_B} w.r.t.\ \m {\d_s} is \m {P}, then
+\Disp{
+\NC 1 -P
+\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} \NR[+]
+}
+Same can be said of \m {\M{W}_B}.
+}
 
@@
 
-\startsection [title={Design of \m {\M{F}_R}}]
+\startsection [title={Concentration Inequality of Precoders and Combiners}]
 
@@
 }
-Thus, by Chebyshev bound, we obtain an identical expression,
+
+\stopsection
+
+\startsection [title={RIP of Precoders and Combiners}]
+
+The relevent expressions for \m {\M{F}_B ^\Tr} and \m {\M{F}_R ^\Tr} are identical, and same can be said of \m {\M{W}_B} and \m {\M{W}_R}.
+Let \m {\Phi} be either of \m {\M{R}_B ^\Tr}, \m {\M{R}_R ^\Tr}, \m {\M{W}_B}, or \m {\M{W}_B}.
+By Chebyshev bound, we obtain an identical expression,
 \Result
@@
 {
-Let \m {\M{F}_R \in \MB {M}_{\MB {C}} \SB {N_H, N_R}} be generated randomly according to ().
-Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_R}}, and for any \m {\e >0},
+Let \m {\Phi} be generated randomly as above.
+Then, for any fixed complex \m {\V{u}} (with corresponding dimension), and for any \m {\e >0},
 \Disp{
@@
 \SB {
-  \Nm {\VNm {\M{F}_R \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
+  \Nm {\VNm {\Phi \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
   \geq \e \VNm {\V{u}} _2 ^2
@@
 }
+According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), substitution of relevent quantities yields
+\Result
+{Lemma}
+{
+Suppose the probability that RIP holds for \m {\Phi} w.r.t.\ \m {\d_s} is \m {P}, then
+\Disp{
+\NC 1 -P
+\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} \NR[+]
+}
+Same can be said of \m {\M{W}_B}.
+}
+
+We may bound \m {\RB {1 +\d_s}^2} by \m {1 +3\d_s}.
+A moment of reflection shows that
 

### 2019-05-20 dantzig_selector/report/notation.tex
Proof: Rev. almost sparsity of g

\starttitle [title={Notation}]

To avoid confusion, round brackets \m {\RB {\cdot}} are used purely for precedence of , and \m {\SB {\cdot}} exclusively for function arguments, for better clarity.

\m {\Nm {a}} denotes the magnitude for real or complex numbers \m {a}.
The real and imaginary part of \m {a} will be denoted respectively as \m {\MF {Re} \SB {a}} and \m {\MF {Im} \SB {a}}, respectively, thus \m {a =\MF {Re} \SB {a} + \Ss{i} \MF {Im} \SB {a}}

We restrict our discussion to \m {\MB {R}^N} or \m {\MB {C}^N} seen as the Hilbert space , equipped with standard inner product.
Lower case Latin alphabets with single underline, like \m {\V {a}}, denote vectors, and upper case Latin alphabets with double underlines, like \m {\M {A}}, denote matrices.
Particularly, define \m {\V {1} =\IP {1, \dots, 1}}.
Denote \m {\V {a} \DB {n}} to be the \m {n}-th component of \m {\V {a}}, and similarly \m {\M {A} \DB {m,n}} to be the \m {m,n}-th entry of \m {\M {A}}.

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \m {\MB {R}^N} is over field \m {\MB {R}}, and that on \m {\MB {C}^N} is over field \m {\MB {C}}.
We use \m {\MB {K}} to refer to either \m {\MB {R}} or \m {\MB {C}}.
Not to avoid confusion, we call the Hilbert space \m {\MB {K}^N} over \m {\MB {K}} to be \m {\MB {V}_{\MB {K}} \SB {N}}.
We also call the collection of \m {M} by \m {N} matrices to be \m {\MB {M}_{\MB {K}} \SB {M,N}}, and its role as linear transformation is understood.
Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {m,n}-entry of \m {\V {A}}
To better correspond to the pseudo code, the numbering of both vector and matrix entries are zero-based, that is, numbered from \m {0,1,2,\dots}.
Especially when manipulating the indices, but also in the main proof of DS bound, we will encounter the modulo as operation, namely the remainder of \m {m} divided by \m {n}, with \m {m, n \geq 0}, and we use the capital \m {m\; \Rm{Mod}\; n} to denote that number.
And we denote \m {\V {u}_n} to be the \m {n}-th unit vector in the Cartesian coordinates, whose numbering is also zero-based.
\m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
Recall that \m {\ell_\infty}-norm is the maximum-magnitude norm.

Denote as \m {\MB {P} \SB {X}} the probability, \m {\MB {E} \SB {X}} the expectation, and \m {\MB {Var} \SB {X}} the variance.
Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables like \m {\MB {P} _\o \SB {X \SB {\o}}}.

\stopchapter

### 2019-05-21 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Complete:  is almost sparse

@@
 
-We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
-The sparse vector to be recovered of our investigation is \m {g \in \MB {C}^{N_h}}, and we continue to use \m {\hat {g}} to denote the Dantzig Selector.
-To simplify the exposition, we will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections, without defining them over and over (by which one would make each statement completely self-containing but considerably more verbose).
-
-We first establish a technical lemma that shows \m {\Rm {supp} \SB {\V {g}}} has roughly cardinal \m {L}, which guarantees, at the heart of the argument, that \m {\V {g}} is almost-sparse
+Our plan is first to show that \m {\SB {\V {g}}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
+We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections.
 
@@
 
-We apply DS to find \m {\hat {\V {g}}}, setting
+Let \m {\hat {\V {g}}} be the Dantzig Selector.
+For concreteness, we set
 \Disp {
@@
 Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
-Let \m {S:\; \MB {V}_{\MB {K}} \SB {N} \mapsto \MB {V}_{\MB {K}} \SB {N}}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} \SB {N})}, so that
+
+And Denote the sorting function to be \m {\MC {S}:\; \MB {V}_{\MB {K}} \SB {N} \mapsto \MB {V}_{\MB {K}} \SB {N}}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} \SB {N})}, so that
 \Disp {
-\NC \Nm {S \RB {x} \DB {n_1}} \geq  \NC \Nm {S \RB {x} \DB {n_2}}, \NR[+]
-\NC n_1 > \NC n_2,
+\NC \Nm {\MC {S} \SB {\V{x}} \DB {n_1}} \geq \NC \Nm {\MC {S} \SB {\V{x}} \DB {n_2}}, \NR[+]
+\NC n_1 \leq \NC n_2,
 \quad n_1, n_2 \in T\RB {N} \NR
 }
-
-Denote the sorting function to be \m {f:\; T\RB {N} \mapsto \MB {R}_+}, \m {N \in \MB {N}}.
-That is, for \m {x \in \MB {V}_{\MB {K}} \SB {N}}, \m {x} is confined in sorted magnitude according to \m {f}.
+That is, \m {\V{x}} is sorted in magnitude.
 For definiteness, we may compare the first component first, and the second, and so on.
 If still there is a tie for a certain component (for complex numbers), the order is irrelevent.
-Formally,
-\Disp {
-\NC \Nm {\MC{S} \SB {x} \DB {n} }
-\leq \NC f \SB {n},
-\quad n \in T \RB {N}. \NR
-}
 
@@
 \Disp {
-\NC \sum_{n=s}^N \Nm {\MC{S} \SB {\V {x}} \SB {n}}
-\leq \NC R. \NR
+\NC \Nm {\RB {\MC{S} \SB {\V {x}} \SB {n}} \DB {s:N}}_p
+\leq \NC R. \NR[+]
 }
@@
 
-\Result
-{Lemma}
-{
-Suppose \m {0 \leq \f \leq 2\pi k /N_H}, \m {k =0, \dots, N_H-1}.
-Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
-Then \m {\V {a} \SB {\f}} is almost-\m {L}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
+Let \m {\f} be fixed.
+What we have to bound is
 \Disp {
-\NC R
-= \NC \F {1}{\pi} \log \F {N_H}{L-1}. \NR
-}
+\NC R^2
+=\NC \sum_{n_H =s}^{N_H -1}
+   \RB {\MC{S} \SB {\M {K}^\Adj \V {a} \SB {\f}}} \DB {n_H} ^2 \NR[+]
 }
 
-We now show the lemma, which is the key to bounding the sparsity of \m {h}.
-Let \m {\f'} be fixed.
-What we have to bound is
+Introduce
 \Disp {
-\NC R \SB {\f'}
-=\NC \sum_{n_H =s}^{N_H -1}
-   \RB {\MC{S} \SB {\M {K}^\Adj \V {a} \SB {\f}}} \DB {n_H} \NR[+]
+\NC \psi \SB {\f, n_H}
+:=\NC \RB {
+   \RB {
+      \RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}}
+      +\F {2 \pi n_H} {N_H}
+      +\pi
+   } \;
+   \Rm{mod}\; \RB {2\pi}
 }
-Observe
+-\pi
+}
+so that
+\Disp{
+\NC \Nm {\psi \SB {\f, n_H}}
+\leq \NC \pi
+}
+And define \m {D} to be the Dirichlet kernel
+\Disp {
+\NC D \SB {\psi'}
+:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
+\NC \quad 0 \leq \NC  \psi' \leq \pi \NR
+}
+Then observe
 \Disp {
 \NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {n_H}
-=\NC \F {1}{N_H} D \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H} {N_H}} \NR
+=\NC \F {1}{N_H} D \SB {\psi \SB {\f, n_H}} \NR
 }
-where \m {D} is the Dirichlet kernel
-\Disp {
-\NC D \SB {\f'}
-:= \NC \Nm { \sum_{n_H=0}^{N_H-1} \Rm {e}^{i n_H \f'} } \NR
-\NC = \NC \F {\Nm {\sin \SB {N_H \f'/2}}}{\Nm {\sin \SB {\f' /2}}}, \NR[+]
-\NC \quad 0 \leq \NC  \f' \leq \pi \NR
-}
+
 Now, it can be verified that
@@
 \Disp {
-\NC \Nm {D \SB {\f'} }
-\leq \NC B \SB {\f'} \NR
-\NC := \NC \F {48}{\Nm {\f'^2 -24} \Nm {\f'}} \NR[+]
-\NC -\pi \leq \NC \f' < \pi. \NR
+\NC \Nm {D \SB {\psi'} }
+= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}}{\Nm {\sin \SB {\psi' /2}}} \NR
+\NC \leq \NC B \SB {\psi'} \NR
+\NC := \NC \F {48}{\Nm {\psi'^2 -24} \Nm {\psi'}} \NR[+]
+\NC -\pi \leq \NC \psi' < \pi. \NR
 }
@@
 \Disp {
-\NC R \SB {\f'}
-=\NC \sum_{n_H =s}^{N_H -1}
-   \F {1}{N_H}
-   \MC{S}
-   \SB {
-      \sum_{n_H' =s}^{N_H -1}
-      B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H'} {N_H}}
+\NC R^2
+=\NC \F {1}{N_H^2}
+\sum_{n_H =s}^{N_H -1}
+\MC{S} \SB {
+   \sum_{n_H' =0}^{N_H -1}
+   B \SB {\psi \SB {\f, n_H'}}
    \V {u}_{n_H'}
 }
-   \DB {n_H}
-\NR[+]
+\DB {n_H} ^2 \NR[+]
 }
-Notice that \m {\Nm {B \SB {\phi'}}} is monotone, and then
-\Disp{
-\NC \NC \MC{S}
-\SB {
-   \sum_{n_H' =s}^{N_H' -1}
-   B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H'} {N_H}}
-   \V {u}_{n_H'}
+Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
+We seek to bound the ``rectangulars'' with an integral, and we have to split the cases that \m {N_H} is odd and even.
+Anyway, a moment's reflection shows
+\Disp {
+\NC R^2
+\leq \NC \F {1}{N_H^2} \D \F {N_H}{2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
+\NC = \NC \F {2304} {N_H \pi^6}
+\int _{s /N_H} ^1 \F{1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
+\NC =\NC \F{1} {2\pi^2}
+\RB {
+  -\F {8} {u}
++\F {4\pi^2 u} {24 -\pi^2 u^2}
++\R{6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R{6}}}
 }
-\DB {n_H} \NR
-\NC =\NC B \SB {\RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}} +\F {2 \pi n_H} {N_H}} \NR
-\NC \leq \NC B \SB {\F {2 \pi n_H} {N_H}} \NR[+]
+\Bigg \| _{s/N_H} ^1 \NR
+\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +0.032670 \NR[+]
 }
-What we saw gives
-\Disp{
-\NC R \SB {\f'}
-=\NC \F {1}{N_H} \sum_{n_H =s}^{N_H -1}
-   B \SB {\F {2 \pi n_H} {N_H}} \NR
+In the last step we bound the lower limit of the second and third term with \m {x' =0}, and leave the dominating \m {1/x'}.
+
+In summary,
+
+\Result
+{Lemma}
+{
+Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
+Then \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
+\Disp {
+\NC R
+= \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {1} {62}. \NR[+]
+}
 }
 
-By the approximation of rectangle to integral,
-\Disp {
-\NC R\SB {\eta} -\F {2\pi} {N_H}
-\leq \NC \F {1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} \Nm {D\SB {\f'}} d \f' \NR
-}
-Bound \m {D} by above technique, meanwhile we notice \m {\f' <24}.
-\Disp {
-\NC R\SB {\f}
-\leq \NC \F {1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F {48}{\RB {24 -\f'^2} \f'} d \f'
-+\F {2\pi} {N_H} \NR
-\NC = \NC \F {1}{\pi} \log \F {2\pi N_H}{L}
--\F {1}{N_H} \log \F {4\pi^2 -24} {L^2/N_H^2 -24}
-+\F {2\pi} {N_H}
-}
-Notice the argument of log in the second term \m {<1}, and we drop that.
-Also drop \m {2\pi /N_H} since it is small.
-Furthermore the \m {2\pi} factor in log can be dropped too.
-\Disp {
-\NC R\SB {\f}
-\leq \NC \F {1}{\pi} \log \F {N_H}{L}. \NR
-}
+\stoptext
 
@@
 \NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2} \NR
-\NC = \NC \MB{E}
-\SB {
+\NC = \NC \MB{E} \SB {
   \sum_{n_R=0}^{N_R-1}
@@
 \NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4}
-=\NC \SB {
+=\NC \MB{E} \SB {
   \RB {
@@
 
-\startsection [title={Mean Square Error Analysis for Complex DS}]
+\startsection [title={Expected Square Error for Complex-Case DS}]
 

### 2019-05-22 dantzig_selector/report/2_problem_setting.tex
Proof: Ongoing: Almost sparsity of

@@
 \NC \M{H}
-=\sum_{l=1}^L \alpha_l \V {a} \SB { \F {d_{\Rm {arr}}} {\lambda} \sin \f_l' } \V {a} \SB { \F {d_{\Rm {arr}}} {\lambda} \sin \th_l' }^\Adj \NR
+=\NC \sum_{l=0} ^{L-1}
+\a_l
+\V {a} \SB { \F {d_{\Rm {arr}}} {\l _{\Rm {arr}} \sin \f_l' }}
+\V {a} \SB { \F {d_{\Rm {arr}}} {\l _{\Rm {arr}} \sin \th_l' }}^\Adj \NR[+]
 }
@@
 \NC \f_l
-= \NC \F {d_{\Rm {arr}}} {\lambda} \sin \f_l' \quad \Rm{Mod}\; (2\pi) \NR[+]
+= \NC \RB {
+\F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
+\; \Rm{Mod}\; \RB {2\pi}
+} \NR[+]
 \NC \th_l
-= \NC \F {d_{\Rm {arr}}} {\lambda} \sin \th_l' \quad \Rm{Mod}\; (2\pi) \NR[+]
+= \NC \RB {
+\F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
+\; \Rm{Mod}\; \RB {2\pi}
+} \NR[+]
 }
@@
 \NC \M{H}
-=\NC \sum_{l=1}^L \alpha_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
-}
-
-\Result
-{Definition.}
-{
+=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
 }

### 2019-05-22 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Ongoing: Almost sparsity of

@@
 \int _{s /N_H} ^1 \F{1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
-\NC =\NC \F{1} {2\pi^2}
+\NC =\NC \F{1} {2\pi^2 N_H}
 \RB {
@@
 \Bigg \| _{s/N_H} ^1 \NR
-\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +0.032670 \NR[+]
+\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR[+]
 }
@@
 
-In summary,
+Expanding \m {R} gives
+\Disp {
+\NC R
+\leq \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {\R {s}} {38 N_H}. \NR[+]
+}
+Futhermore, finding the \m {s} that minimizes the function gives us a upper bound.
+And it is easy to see the function to be strictly decreasing in \m {N_H}.
+To keep it simple, let us plug in \m {N_H =4} for the upper bound.
 
@@
 {
-Let \m {\f} be given, and array response \m {\V {a} \SB {\f}} defined as in ().
-Then \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
-\Disp {
-\NC R
-= \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {1} {62}. \NR[+]
+Let \m {\f \SB {\o_h}} be given, and linear array response \m {\V {a} \SB {\f}} defined as in ().
+Suppose \m {N_H \geq 4}.
+Then, for all instances of \m {\f}, \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
+
+with
+\Disp{
+\NC s
+\leq 5
 }
@@
 
-\stoptext
+It remains to bound \m {\VNm {\M {G}}}.
+Note that
+\Disp{
+\NC \VNm {\M {G}}_F
+=\NC \VNm {\M {H}}_F \NR[+]
+}
+So it suffices to consider \m {\VNm {\M {H}}}.
+
+\Disp{
+\NC \VNm {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F
+\leq \NC \sum _{l=0} ^{L-1} \Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
+\NC \leq \NC
+\sum _{l=0} ^{L-1}
+\Nm {\a_l} \VNm {\V {a} \SB {\f_l}} _2
+\D \VNm {\V {a} \SB {\th_l}} _2 \NR[+]
+}
+
+Lastly, we know \m {\ell_1}-norm is larger than \m {\ell_2}-norm.
+Since \m {\ell_1}-norm will be used in later proof, we display the statement about \m {\ell_1}-norm.
 
@@
 {
-Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)}, and linear array response \m {\V {a}} defined as in ().
-Let \m {\V {g}} be defined as above.
-Then \m {\V {g}} is almost-\m {L}-sparse with \m {\ell_1}-residue \m {R\SB {N_H, L}} to be
+Let \m {\f \SB {\o_h}} and \m {\th \SB {\o_h}} be uniformly, independently distributed in \m {[0,2\pi)}, and let \m {\V {g} \in \MB{V}_\MB{C} \SB{N_h}} be defined as in ().
+If \m {N_h \geq 4^2 =16}, then \m {\V {g}} is almost-\m {s^2 L}-sparse with \m {\ell_1}-residue \m {R} to be
 \Disp {
 \NC R
-\leq \NC \F {L}{\pi^2} \RB { \log \F {N_H}{L} }^2 \NR
+\leq \NC 2L \NR
 }

### 2019-05-22 dantzig_selector/report/1_introduction.tex
Proof: Def. of sorting function

@@
 
-\startsection [title={Background}]
+\startsection [title={Motivation of Compressed Channel Sensing}]
 
@@
 Indeed, relevent code has been put on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
+In this article we focus on DS, and we introduce several notions before we describe their work.
 
-In this article we focus on DS, and we introduce several notions before we describe their work.
-For simpliciy, in this section we will consistently use \m {N_p} and \m {N_m} to denote matrix dimensions.
-And, following their presentation, with slight abuse of notation we borrow the term ``support'' to denote the index set on which a vector's components are nonzero.
+In this section, consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}} and \m {\V{\Phi} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
+Set \m {\MC {T} \RB {N_p} =\CB {0, \dots, N_p-1}} for short.
+For \m {\MC {A} \subseteq \MC {T} \SB {N_p}}, denote
+\Disp{
+\NC \V {x} _{\MC {A}}
+=\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR[+]
+\NC \M {\Phi} _{\MC {A}}
+=\NC \sum _{i \in \MC {A}} \M {\Phi} \DB {:,i} \NR[+]
+}
+That is, respectfully, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MC {A}}.
 
-For brevity, we will use \m {T \RB {N_m} =\{1, \dots, N_m\}} to denote the support of \m {\MB {V}_{\MB {K}} \SB {N_m}}.
-Also, suppose \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
-Let \m {\MC {T} \subset T \RB {N_p}}.
-Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
-
+We say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
+Formally,
 \Result
-{Definition}
+{Definition: Sparsity}
 {
-\m {x \in \MB {V}_{\MB {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\MC {A}}, \m {s <N_m}, if there is \m {\MC {A} \subset T \RB {N_m}} such that
-
+\m {\V {x}} is called \m {s}-sparse, if there is \m {\MC {A} \subseteq \MC {T} \SB {N_p}} such that
 \Disp { 
-\NC x_{T\SB {N} -\MC {A}}
-=\NC \V {0} \NR
+\NC \V{x}_{\MC {A}}
+=\NC \V{x} \NR
 }
@@
 }
-That is, only at most \m {s} components of \m {x} is nonzero.
 }
@@
 \Result
-{Definition}
+{Definition: Restricted Isometry Property}
 {
-Consider \m {\Phi \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
-For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N_p}}, for all \m {\MC {T} \subset T\SB {N_m}} with \m {\#\{\MC {T} \} \leq s},
+For fixed \m {s =0, \dots N_p -1}, we say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {\V {x}}, and for all \m {\MC {A} \subset \MC {T} \SB {N_m}} with \m {\# \MC {A} \leq s},
 \Disp {
-\NC \NC \RB {1-\d_s} \VNm {\V {x}}^2 \NR
-\NC \leq \NC \VNm {\Phi_{\MC {T}} \V {x}} _2^2 \NR
-\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
+\NC \NC \RB {1-\d_s} \VNm {\V {x}_{\MC {A}}}^2 \NR
+\NC \leq \NC \VNm {\M{\Phi} \V {x}_{\MC {A}}} _2^2 \NR
+\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}_{\MC {A}}} _2^2 \NR[+]
 }
 }
-
-RIP is essentially saying that \m {P} is ``almost unitary'' up to ``relative error'' \m {\d_s}.
+That is, \m {\Phi} is ``almost unitary'' up to ``relative error'' \m {\d_s}.
 
@@
 \NC \V {y}
-=\NC \M {P} \V {h} + \V {z} \NR
+=\NC \M {\Phi} \V {x} + \V {z} \NR
 }
 
-where (w.l.o.g.) \m {z} is an i.i.d.\ normalized Gaussian vector.
-How can we hope to estimate \m {h} when, in addition to insufficient observations, there are too few observations?
+where (w.l.o.g.) \m {\V{z}} is an i.i.d.\ normalized Gaussian vector.
+How can we hope to estimate \m {\V{x}} when, in addition to insufficient observations, there are too few observations?
 
 \Result
-{Algorithm}
+{Algorithm: Dantzig Selector}
 {
 \startitemize[n]
-\item Input \m {\M {P} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
+\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
 \item Calculate
@@
 \NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
-\NC \Rm {subject} \; \Rm {to} \quad \MC \VNm {\M {P}^\Adj \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \g \NR
+\NC \Rm {subject} \; \Rm {to} \quad \MC \VNm {\M {\Phi}^\Adj \RB {\M {\Phi} \V {h}' -\V {y}}} _\infty \leq \g \NR
 \stopcases \NR
@@
 
-\stopsection
-\startsection [title={Sufficient Conditions of RIP}]
-
 The constant \m {\d} in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \m {\d=0}, i.e., that \m {P} is fully unitary, rendering the RIP an important role.
+Indeed, we may observe that in theorem (), the bound is not tightest when \m {\d=0}, i.e., that \m {\Phi} is fully unitary, rendering the RIP an important role.
 Here, it is not clear at first what matrices serves as the RIP condition.
@@
 But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.
-
-\Result
-{Theorem}
-{
-Let each entry of random matrix \m {P \in \MB {M}_\MB {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
-Then, with \m {0 <\e <1},
-
-\Disp {
-\NC \NC \MB {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \e \VNm {h} _2^2} \NR
-\NC \leq \NC 2 \exp \SB {-n \RB {\F {\e ^2} {4} -\F {\e ^3} {6}} } \NR
-}
-}
-
-\color[red] {(To be done)}
-
-\stopsection
-\startsection [title={Compressed Channel Sensing}]
 
@@
 To explain the idea, consider a linear time-invariant channel that \m {y\SB {t} =\RB {x \star h} \SB {t} + z\SB {t}}, where \m {h\SB {t}} is the channel's impulse response, \m {y\SB {t}} is the output, and, for each time index, \m {x\SB {t}} is i.i.d.\ Rademacher, and \m {z\SB {t}} is i.i.d.\ Gaussian.
-Simply assuming \m {h} has sparse support, and let the convolution with \m {x} be expressed by a matrix \m {X}, \m {X} is a Toeplitz matrix, so that \m {y =X h +z}.
+Simply assuming \m {h} is sparse, and let the convolution with \m {x} be expressed by a matrix \m {X}, \m {X} is a Toeplitz matrix, so that \m {y =X h +z}.
 Then Bajwa et.\ al.\ was able to show that, \m {X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.
@@
 
-Same as before, consider \m {\V {y} \in \MB {V}_\MB {K} \SB {N_p}}, \m {\V {h} \in \MB {V}_\MB {K} \SB {N_s}}, where \m {\V {h}} is \m {s}-sparse, with \m {N_p \gg N_s}.
-If
+Same as before, consider an \m {s}-sparse \m {\V {x}}, with \m {N_p \gg N_s}.
+For the noiseless, real-number case,
 \Disp {
 \NC \V {y}
-=\NC \M {P} \V {h}, \NR
+=\NC \M {\Phi} \V {x}, \NR
 }
-that is, the noiseless, real-number case.
-We pick up the columns of \m {\M {P}} greedily, hoping to correspond to the support of \m {\V {h}}, thus recovering the original signal.
+We pick up the columns of \m {\M {\Phi}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.
 
@@
 \startitemize[n]
-\item To be done.
+\item \color[red]{(To be done)}
 \stopitemize
 }
-
-From Tropp and Gilbert (2007a),
-
-\Result
-{Theorem}
-{
-Following the setting described above, suppose, for \m {0 <\d <1},
-
-\Disp {
-\NC M \geq 16s \log \RB {N/\d} \NR
-}
-
-Then OMP (Algorithm \_\_) recovers \m {x} completely, with overwhelming probability \m {1-\d}.
-}
+From Tropp and Gilbert (2007a), OMP recovers \m {x} completely, with overwhelming probability.
 
@@
 
-\stopsection
-\startsection [title={OMP used in Channel Sensing}]
-
-For concreteness, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
+For our purposes, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
 Let signal \m {\V {x}} be sent, and \m {\V {y}} be receiverd, that is
@@
 \NC = \NC \RB {\M{A}\M{X}\M{B}} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
-\NC = \NC \sum _{n_2=1} ^{N_2} \sum _{n_3=1} ^{N_3}
+\NC = \NC \sum _{n_2 =0} ^{N_2 -1} \sum _{n_3 =0} ^{N_3 -1}
 \M{A} \DB {m_1\; \Rm{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR[+]
@@
 \NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB{\M{X}} } \DB {m_1} \NR
-\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR
-\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
+\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR
+\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
 \M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR 
-\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
-\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }} \NR[+]
+\NC = \NC
+\sum _{m_2 =0} ^{N_2 N_3 -1}
+\M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
+\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \NR
+\NC \NC \quad \quad \quad \quad \quad \quad
+\M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}
+\NR[+]
 }
 
-In () and (), the row index of \m {\M{A}} and \m {\M{B}} already agree.
+In () and (), the row indices of \m {\M{A}} and \m {\M{B}} already agree.
 The key observation is that when \m {n_2} runs through \m {0, \dots, N_2-1} and \m {n_3} runs through \m {0, \dots, N_3-1}, it follows \m {n_2 n_3} runs through \m {0, \dots, N_2 N_3-1}.
@@
 \stopsection
-\startsection [title={Further Development on Compressive Channel Sensing}]
+
+\startsection [title={Further Development}]
 
@@
 
-Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same support.
+Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same positions of nonzero components.
 
@@
 
-Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same support, using different measurement matrices in a modified basis pursuit problem.
+Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same positions of nonzero components, using different measurement matrices in a modified basis pursuit problem.
 
@@
 
-\startsection [title={Contribution}]
+\startsection [title={Our Contribution}]
 

### 2019-05-22 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Def. of sorting function

@@
 \startsection [title={Almost-Sparsity of Angular Channel}]
+
+Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {s} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {s} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {C}} are the positions complement to \m {\V {g} _\MC {A}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {s=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
+We rephrase it formally.
+
+\Result
+{Definition}
+{
+Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
+Let bijection \m {\sigma: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
+\Disp{
+\NC \V{v} \DB {\sigma \SB {n}}
+\leq \NC \V{v} \DB {\sigma \SB {n-1}} \NR[+]
+\NC n =\NC 1, \dots, N_p-1 \NR
+}
+Its existence is evident.
+Then define
+\Disp{
+\NC \MC {S} \SB {\V{x}, s}
+=\NC \CB {\sigma \SB{i}:\; i =0, \dots, s-1} \NR[+]
+}
+}
+Now set
+\Disp{
+\NC \MC {A}
+=\NC \MC {S} {\V{g}, s} \NR
+\NC \MC {C}
+=\NC \MC {T} \SB {N_p} -\MC{A} \NR
+\NC \MC {B}
+=\NC \MC {S} {\V{g} _\MC{C}, s} \NR
+}
 
@@
 }
-And call
-\startitemize [1]
-\item \m {\MC {A}} be the largest \m {s} position of \m {g}.
-\item \m {\MC {B}} be the largest \m {s} position of \m {d_{T\SB {N_h} -\MC {A}}}.
-\item \m {\MC {C} =T \RB {N_h} -\MC {A}}, i.e., the complementary index set of \m {\MC {A}}.
-\stopitemize
-
-Suppose \m {\M {A} \in \MB {M}_{\MB {K}} \RB {N_1, N_2 }}.
-For brevity, let \m {\MC {T} \subset T \RB {N_2 }}.
-Denote as \m {\M {A}_{\MC {T}}} the columns of \m {\M {A}} having indices in \m {\MC {T}}.
-
-And Denote the sorting function to be \m {\MC {S}:\; \MB {V}_{\MB {K}} \SB {N} \mapsto \MB {V}_{\MB {K}} \SB {N}}, \m {N \in \MB {N}}, be the sorting function for \m {x \in \MB {V}_{\MB {K}} \SB {N})}, so that
-\Disp {
-\NC \Nm {\MC {S} \SB {\V{x}} \DB {n_1}} \geq \NC \Nm {\MC {S} \SB {\V{x}} \DB {n_2}}, \NR[+]
-\NC n_1 \leq \NC n_2,
-\quad n_1, n_2 \in T\RB {N} \NR
-}
-That is, \m {\V{x}} is sorted in magnitude.
-For definiteness, we may compare the first component first, and the second, and so on.
-If still there is a tie for a certain component (for complex numbers), the order is irrelevent.
 
@@
 \NC \Nm {\RB {\MC{S} \SB {\V {x}} \SB {n}} \DB {s:N}}_p
+\V {x} _{\MC {T} \SB {N_p} -\MC {S} \SB{\V {x}, s}}
 \leq \NC R. \NR[+]
@@
 Let \m {P} be fixed.
-For \m {\MC {T}, \MC {T}' \subset T \RB {N_p}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} \SB {P} >0} to be the smallest number such that
+For \m {\MC {T}, \MC {T}' \subset \MC {T} \RB {N_p}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} \SB {P} >0} to be the smallest number such that
 \Disp {
@@
 We can now formulate and prove the main bound of ours.
-Here, we use \m {s=L} as the sparsity threshold.
 

### 2019-05-27 dantzig_selector/report/1_introduction.tex
Proof: Expectation of

@@
 \Disp{
-\NC \V {x} _{\MC {A}}
+\NC \V {x}  \DB {\MC {A}}
 =\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR[+]
-\NC \M {\Phi} _{\MC {A}}
+\NC \M {\Phi}  \DB {\MC {A}}
 =\NC \sum _{i \in \MC {A}} \M {\Phi} \DB {:,i} \NR[+]
@@
 \Disp { 
-\NC \V{x}_{\MC {A}}
+\NC \V{x} \DB {\MC {A}}
 =\NC \V{x} \NR
@@
 \Disp {
-\NC \NC \RB {1-\d_s} \VNm {\V {x}_{\MC {A}}}^2 \NR
-\NC \leq \NC \VNm {\M{\Phi} \V {x}_{\MC {A}}} _2^2 \NR
-\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}_{\MC {A}}} _2^2 \NR[+]
+\NC \NC \RB {1-\d_s} \VNm {\V {x} \DB {\MC {A}}}^2 \NR
+\NC \leq \NC \VNm {\M{\Phi} \V {x} \DB {\MC {A}}} _2^2 \NR
+\NC \leq \NC \RB {1+\d_s} \VNm {\V {x} \DB {\MC {A}}} _2^2 \NR[+]
 }
@@
 \LA \NC \startcases
-\NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
-\NC \Rm {subject} \; \Rm {to} \quad \MC \VNm {\M {\Phi}^\Adj \RB {\M {\Phi} \V {h}' -\V {y}}} _\infty \leq \g \NR
+\NC \Min {\V {h}'} \Q \MC \VNm {\V {h}'} _1 \NR
+\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {\Phi}^\Adj \RB {\M {\Phi} \V {h}' -\V {y}}} _\infty \leq \g \NR
 \stopcases \NR
@@
 \M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \NR
-\NC \NC \quad \quad \quad \quad \quad \quad
+\NC \NC \Q \Q \Q \Q \Q \Q
 \M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}

### 2019-05-27 dantzig_selector/report/2_problem_setting.tex
Proof: Expectation of

@@
-\startchapter [title={Problem Setting}]
+quad\startchapter [title={Problem Setting}]
 
@@
 \NC \M {W}_R \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_H} \NR
-\NC \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R} \NR[+]
+\NC \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R} \NR
 }
@@
 := \NC \Rm {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR[+]
-\NC \M {P}^\star
+\NC \M {Q}
 \in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
-\NC \M {P}^\star
+\NC \M {Q}
 := \NC \RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR[+]
 }
-to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {H}} to be
+to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M{H}}} to be
 \Disp {
 \NC \V {y}
-=\M {P}^\star \V {h} +\V {z} \NR
+=\M {Q} \V {h} +\V {z} \NR
 }
@@
 \stopsection
-\startsection [title={Expression for the Angular Space}]
+\startsection [title={Working in the Angular Space}]
 
@@
 = \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR[+]
-\NC \quad n_1, n_2
+\NC \Q n_1, n_2
 = \NC 0, 1, \dots, N_H-1 \NR
@@
 \NC \M {P}
-:=\NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr K^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}} \NR[+]
+:=\NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}} \NR[+]
 }
@@
 \NC \Min {\V {g}' \in \MB {V}_{\MB {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR[+]
-\NC \Rm {subject} \; \Rm {to} \quad \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
+\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
 \stopcases \NR

### 2019-05-27 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Expectation of

@@
 
-\startsection [title={Almost-Sparsity of Angular Channel}]
-
-Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {s} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {s} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {C}} are the positions complement to \m {\V {g} _\MC {A}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {s=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
-We rephrase it formally.
-
-\Result
-{Definition}
-{
-Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
-Let bijection \m {\sigma: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
-\Disp{
-\NC \V{v} \DB {\sigma \SB {n}}
-\leq \NC \V{v} \DB {\sigma \SB {n-1}} \NR[+]
-\NC n =\NC 1, \dots, N_p-1 \NR
-}
-Its existence is evident.
-Then define
-\Disp{
-\NC \MC {S} \SB {\V{x}, s}
-=\NC \CB {\sigma \SB{i}:\; i =0, \dots, s-1} \NR[+]
-}
-}
-Now set
-\Disp{
-\NC \MC {A}
-=\NC \MC {S} {\V{g}, s} \NR
-\NC \MC {C}
-=\NC \MC {T} \SB {N_p} -\MC{A} \NR
-\NC \MC {B}
-=\NC \MC {S} {\V{g} _\MC{C}, s} \NR
-}
-
-Let \m {\hat {\V {g}}} be the Dantzig Selector.
-For concreteness, we set
-\Disp {
-\NC \g 
-= \NC \R {2 \log N_h} \NR[+]
-}
-
-Other values are of course possible, but this is enough to illustrate our purpose.
-Also set for short
-\Disp {
-\NC \V {d} 
-= \NC \hat {\V {g}} -\V {g} \NR[+]
-}
+\startsection [title={Almost-Sparsity of Array Response \m {\V{a}}}]
 
@@
 \Disp {
-\NC \Nm {\RB {\MC{S} \SB {\V {x}} \SB {n}} \DB {s:N}}_p
-\V {x} _{\MC {T} \SB {N_p} -\MC {S} \SB{\V {x}, s}}
+\NC \VNm {\MC {C} \SB{\V {x}, s}} _p
 \leq \NC R. \NR[+]
@@
 Let \m {\f} be fixed.
-What we have to bound is
+It suffices to bound
 \Disp {
-\NC R^2
-=\NC \sum_{n_H =s}^{N_H -1}
-   \RB {\MC{S} \SB {\M {K}^\Adj \V {a} \SB {\f}}} \DB {n_H} ^2 \NR[+]
+\NC \NC
+\VNm {
+\MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}
+} _2 ^2 \NR[+]
 }
 
-Introduce
+Towards that end, introduce
 \Disp {
@@
    \RB {
-      \RB {\f \; \Rm{mod}\; \F{2\pi}{N_H}}
+      \RB {\f \; \Rm{Mod}\; \F{2\pi}{N_H}}
       +\F {2 \pi n_H} {N_H}
@@
    } \;
-   \Rm{mod}\; \RB {2\pi}
+   \Rm{Mod}\; \RB {2\pi}
 }
--\pi
+-\pi \NR
 }
-so that
+Note that by construction
 \Disp{
 \NC \Nm {\psi \SB {\f, n_H}}
-\leq \NC \pi
+\leq \NC \pi \NR
 }
-And define \m {D} to be the Dirichlet kernel
+And define the so-called Dirichlet kernel
 \Disp {
@@
 := \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
-\NC \quad 0 \leq \NC  \psi' \leq \pi \NR
+\NC 0 \leq \NC  \psi' \leq \pi \NR
 }
@@
 =\NC \F {1}{N_H^2}
-\sum_{n_H =s}^{N_H -1}
-\MC{S} \SB {
+\VNm {
+\MC {C}
+\SB{
    \sum_{n_H' =0}^{N_H -1}
    B \SB {\psi \SB {\f, n_H'}}
-   \V {u}_{n_H'}
+   \V {u}_{n_H'},
+   s
 }
-\DB {n_H} ^2 \NR[+]
+} _2^2
+\NR[+]
 }
@@
 }
-Futhermore, finding the \m {s} that minimizes the function gives us a upper bound.
-And it is easy to see the function to be strictly decreasing in \m {N_H}.
-To keep it simple, let us plug in \m {N_H =4} for the upper bound.
+
+Fixing \m {N_H}, it shall be easy to see that rhs is strictly decreasing in \m {N_H}, and the value of \m {s} that minimizes it is about \m {s =5N_H}.
+In the range that we care, rhs is thus strictly decreasing in \m {s}.
+\m {N_H}.
 
@@
 Then, for all instances of \m {\f}, \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
-
-with
 \Disp{
-\NC s
-\leq 5
+\NC R
+\leq \NC \m {\F{1}{3 \R{N_H}}} \NR[+]
 }
@@
 
-It remains to bound \m {\VNm {\M {G}}}.
+Since the bound is also decreasing in \m {N_H}, for concreteness, let us plug in \m {N_H =4} for the upper bound, giving
+\Disp{
+\NC R
+\leq \NC \F {1} {6} \NR[+]
+}
+
+\stopsection
+
+\startsection [title={Almost-Sparsity of Channel Response \m {\M{H}}}]
+
+It remains to bound \m {\VNm {\M {G}} _F}.
 Note that
@@
 }
-So it suffices to consider \m {\VNm {\M {H}}}.
+So it suffices to consider \m {\VNm {\M {H}} _F}.
 
@@
 
-\startsection [title={Concentration Inequality of \m {\M{F}_B, \M{W}_B}}]
+\stopsection
+
+\startsection [title={Moments of Precoders' and Combiners' entries}]
+
+Our plan is setting the four precoder matrices to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
+Indeed, \m {\d_s \SB {\M{F}_B} \SB {\o_t}} may be found, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
+We prove a concentration inequality, as explained below, and invoke Chebyshev inequality.
+But before that, we have to investigate the moments of each entry of \m {\M{F}_B \SB {\o_t}} (resp.\ \m {\M{W}_B \SB {\o_t}}) and that of \m {\M{F}_R \SB {\o_t}} (resp.\ \m {\M{W}_R \SB {\o_t}}).
+
+Let us call it a day and set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l >0}.
+They are (with a slight of abuse of meaning of \m {\o_t} and so on)
+\Disp{
+\NC d \o_t
+=\NC \F {1} {\R {\pi} \l} \exp
+  \RB {-\F{1}{\l^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
+d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
+\NC d \o_t
+=\NC \F {1} {\R {\pi} \l} \exp
+  \RB {-\F{1}{\l^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
+d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
+\NC n_R
+= \NC 0, 1, 2, \dots, N_R -1 \NR
+\NC n_Y
+= \NC 0, 1, 2, \dots, N_Y -1 \NR
+}
+
+We know that the magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
+\Disp{
+\NC \NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}} \NR
+\NC =\NC \F{\R{\pi}}{2} \l_B \NR[+]
+\NC M_{B,2}
+:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
+\NC =\NC \l_R^2 \NR[+]
+\NC M_{B,4}
+:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
+\NC =\NC 2 \l_R^4 \NR[+]
+}
+Also notice that
+\Disp{
+\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
+\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
+   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
+\NC \NC \Q \Q +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
+      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
+\NC = \NC 0 \NR[+]
+}
+
+Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
+\Disp{
+\NC d \o_t
+= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_H, n_R}}} ^2}^{-1/2}
+d \MF{Re} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
+\NC d \o_t
+= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_H, n_R}}} ^2}^{-1/2}
+d \MF{Im} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
+}
+As a result,
+\Disp{
+\NC \NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} \NR
+\NC =\NC \l_R \NR[+]
+\NC M_{R,2}
+:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^2} \NR
+\NC =\NC \l_R^2 \NR[+]
+\NC M_{R,4}
+:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^4} \NR
+\NC =\NC \l_R^4 \NR[+]
+}
+And again
+\Disp{
+\NC \MB{E} \SB {\M{F}_R \DB {n_R, n_Y}^2}
+= \NC 0 \NR[+]
+}
+
+\startsection [title={Restricted Isometry of \m {P}}]
 
@@
 \Disp {
-\NC \Nm {\IP {P_{\MC {T}} h, P_{\MC {T}'} h'}}
+\NC \Nm {\IP {P _{\MC {T}} h, P _{\MC {T}'} h'}}
 \leq \NC \tau_{s, s'} \SB {P} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
@@
 We may well keep track of \m {\d_s \SB {\M{P}}} only.
-When \m {\SB {\M{P}}} is clear, we may suppress it.
+When \m {\M{P}} is clear, we may suppress it.
 
-We seek to find \m {\d_s \SB {\M{F}_B} \SB {\o_t}}, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
-Try to set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\a >0}.
-They are (with a slight of abuse of meaning of \m {\o_t} and so on)
+Similar is true of \m {\d_s \SB {\M{F}_B} \SB {\o_t}}.
+But each entry of \m {P} is a linear combination of products, and such reasoning does not work.
+If only \m {P} were also an i.i.d.\ random matrix, the resulting proof would be easier.
+Is the approach all but lost?
+
+Start with the observtion
+\Result
+{Lemma}
+{
+\Disp {
+\NC \NC \MB{E} \SB {\M{P} \DB {n_y, n_h} \M{P} \DB {n_y', n_h'}} \NR
+\NC = \NC \startcases
+\l_R^4 \l_B^4, \Q \MC n_y =n_y', n_h =n_h' \NR
+0, \Q \NC \Rm {otherwise} \NR
+\stopcases \NR
+}
+}
+
+Notice
+\Disp {
+\NC \M{P} ^\Adj \M{P}
+=\NC
+\RB {
+   \RB {\M{K} ^\Tr \M {F}_R^\ast \M {F}_B^\ast}
+   \otimes \RB {\M {K} \M {W}_R \M {W}_B}
+}
+\RB {
+   \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast}
+   \otimes \RB {\M {W}_B \M {W}_R \M {K}}
+} \NR
+\NC =\NC
+\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast \M{K}^\Tr \M {F}_R^\ast \M {F}_B^\ast}
+\otimes \RB {\M {W}_B \M {W}_R \M{K} \M{K}^\Adj \M {W}_R^\Adj \M {W}_B^\Adj} \NR
+\NC =\NC
+\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M {F}_R^\ast \M {F}_B^\ast}
+\otimes \RB {\M {W}_B \M {W}_R \M {W}_R^\Adj \M {W}_B^\Adj} \NR[+]
+}
+where, restating (), \m {\M {Q} :=\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R}}.
+
+This implies
+\Disp {
+\NC \V{u} ^\Adj \M{P} ^\Adj \M{P} \V{u}
+= \NC \V{u} ^\Adj \M{Q} ^\Adj \M{Q} \V{u} \NR[+]
+}
+or
+\Result
+{Lemma}
+{
+For any instance of \m {\M{P} \SB {\o_t, \o_r}} and \m {\M{Q} \SB {\o_t, \o_r}},
 \Disp{
-\NC d \o_t
-=\NC \F {1} {\R {\pi} \a} \exp
-  \RB {-\F{1}{\a^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
-d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
-\NC d \o_t
-=\NC \F {1} {\R {\pi} \a} \exp
-  \RB {-\F{1}{\a^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}} ^2}
-d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
-\NC n_R
-= \NC 0, 1, 2, \dots, N_R -1 \NR
-\NC n_Y
-= \NC 0, 1, 2, \dots, N_Y -1 \NR
+\NC \VNm {\M{P} \V{u}} _2
+= \NC \VNm {\M{Q} \V{u}} _2 \NR[+]
 }
-We know that the magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
+}
+
+And it will turn out that any two distinct entries of \m {\M{Q}} are not correlated.
+
+To make expressions more compact, introduce
+\Disp {
+\NC \i_2 \SB {x_0, x_1}
+=\NC \startcases
+\NC 1, \MC \Q x_0 =x_1 \NR
+\NC 0, \NC \Q \Rm {otherwise} \NR
+\stopcases \NR
+\NC \i_4 \SB {x_0, x_1, x_2, x_3}
+=\NC \startcases
+\NC 1, \MC \Q x_0 =x_1 =x_2 =x_3 \NR
+\NC 0, \NC \Q \Rm {otherwise} \NR
+\stopcases \NR
+}
+And, for any permutation \m {\s} on \m {\CB {1, 2, 3, 4}},
+\Disp {
+\NC \i_{2,2} \SB {x_0, x_1, x_2, x_3}
+=\NC \startcases
+\NC 1, \MC \Q x_{\s \RB{0}} =x_{\s \RB{1}} \neq x_{\s \RB{2}} =x_{\s \RB{3}} \NR
+\NC 0, \NC \Q \Rm {otherwise} \NR
+\stopcases \NR
+}
+
+\Result
+{Lemma}
+{
+\Disp {
+\NC \NC \MB{E} \SB {\RB {\M{F}_R \M{F}_B} \DB {n_H, n_Y} \RB {\M{F}_R \M{F}_B} \DB {n_H', n_Y'}} \NR
+\NC = \NC \MB{E} \SB {\RB {\M{W}_R \M{W}_B} \DB {n_Y, n_H} \RB {\M{W}_R \M{W}_B} \DB {n_Y', n_H'}} \NR
+\NC = \NC N_R \D \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D \RB {\l_R^2 +\l_B^2} \NR
+}
+}
+
+To see this, expanding the definition
+\Disp {
+\NC \NC \RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y, n_H} \RB {\M{F}_R \M{F}_B} \DB {n_Y', n_H'} \NR
+\NC =\NC
+\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H, n_R} \M{F}_B \DB {n_R, n_Y}}
+\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H', n_R} \M{F}_B \DB {n_R, n_Y'}} \NR
+}
+When either \m {n_y \neq n_y'} or \m {n_h \neq n_h'}, no term is an all-square product.
+After taking expectation, the expectation sign is distributed, and every term vanishes.
+But when \m {n_y =n_y'} or \m {n_h =n_h'}, the only terms that remains are
+\Disp {
+\NC \NC \sum_{n_R=0}^{N_R-1}
+\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
+\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
+\NC = \NC N_R \D \RB {M_{R,2} +M_{B,2}} \NR
+}
+
+Having this in mind, a moment's reflection shows
+\Result
+{Lemma}
+{
+\Disp {
+\NC \NC \MB{E} \SB {\M{Q} \DB {n_Y, n_H} \M{Q} \DB {n_Y', n_H'}} \NR
+\NC = \NC \startcases
+N_R \l_R^2 \l_B^2, \Q \MC n_Y =n_Y', n_H =n_H' \NR
+0, \Q \NC \Rm {otherwise} \NR
+\stopcases \NR
+}
+}
+
+Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we shall study the probability concentration of \m {\VNm {\M{F}_B \V{u}}_2^2} and \m {\VNm {\M{F}_B \V{u}}_2^4}.
+The two moments are present in Chebyshev bound.
 \Disp{
-\NC \NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}} \NR
-\NC =\NC \F{\R{\pi}}{2} \a \NR[+]
-\NC M_2
-:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
-\NC =\NC \a^2 \NR[+]
-\NC M_4
-:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
-\NC =\NC 2 \a^4 \NR[+]
-}
-Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we have to study the concentration of \m {\VNm {\M{F}_B \V{u}}_2} in probability mass.
-We shall exploit Chebyshev bound, which required the first and second moment to be found.
-\Disp{
-\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2} \NR
+\NC \NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2} \NR
 \NC = \NC \MB{E} \SB {
-  \sum_{n_R=0}^{N_R-1}
-  \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
+  \sum_{n_y=0}^{N_y-1}
+  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
 } \NR
-\NC = \NC \sum_{n_R=0}^{N_R-1}
-  \MB{E} \SB {\Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2}
+\NC = \NC \sum_{n_y=0}^{N_y-1}
+  \MB{E} \SB {\Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2}
 \NR
 \NC = \NC
-\sum_{n_R=0}^{N_R-1}
+\sum_{n_y=0}^{N_y-1}
   \MB{E} \SB {
-     2 \sum_{\startsubstack n_Y, n_Y'=0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
+     2 \sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
        \MF {Re} \SB{
-         \M{F}_B \DB {n_R, n_Y} ^* \M{F}_B \DB {n_R, n_Y'}
-         \V{u} \DB{n_Y} \V{u} \DB{n_Y'} ^*
+         \M{Q} \DB {n_y, n_h} ^\ast \M{Q} \DB {n_y, n_h'}
+         \V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
        }
    } \NR
-\NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
+\NC \NC \Q \Q +\sum_{n_y=0}^{N_y-1}
   \MB{E}
-     \SB {\sum_{n_Y=0}^{N_Y-1} \Nm {\M{F}_B \DB {n_R, n_Y}}^2 \Nm {\V{u} \DB{n_Y}}^2}
+     \SB {\sum_{n_h=0}^{N_h-1} \Nm {\M{Q} \DB {n_y, n_h}}^2 \Nm {\V{u} \DB{n_h}}^2}
 \NR
 \NC = \NC
-2 \sum_{n_R=0}^{N_R-1}
-\sum_{\startsubstack n_Y, n_Y'=0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
+2 \sum_{n_y=0}^{N_y-1}
+\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
 \MF {Re} \SB{
-   \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^*}
-   \MB{E} \SB {\M{F}_B \DB {n_R, n_Y'}}
+   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
+   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
 }
-\V{u} \DB{n_Y} \V{u} \DB{n_Y'} ^*
+\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
 \NR
-\NC \NC \quad \quad +\sum_{n_R=0}^{N_R-1}
-   \sum_{n_Y=0}^{N_Y-1} \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2} \Nm {\V{u} \DB{n_Y}}^2
+\NC \NC \Q \Q +\sum_{n_y=0}^{N_y-1}
+   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
 \NR
-\NC = \NC \a^2 N_R \VNm {\V{u}} _2 ^2 \NR[+]
+\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR[+]
 }
@@
 \Disp{
-\NC \a
-=\NC \F {1} {\R{N_R}} \NR[+]
+\NC \l_B
+=\NC \l_R \NR
+\NC =\NC \F {1} {\R {N_Y N_R}} \NR[+]
 }
@@
 \Disp{
-\NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2}
+\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2}
 =\NC \VNm {\V{u}} _2 ^2
@@
 \Disp{
-\NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4}
+\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^4}
 =\NC \MB{E} \SB {
@@
     \sum_{n_R=0}^{N_R-1}
-    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{F}_B \DB {n_R, n_Y} ^* \V{u} \DB{n_Y}} ^2
+    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{Q} \DB {n_R, n_Y} ^\ast \V{u} \DB{n_Y}} ^2
   } ^2
+} \NR
+\NC = \NC E_1 +E_2 +E_3 +E_4 +E_5 \NR[+]
 }
-\NR[+]
+These terms are discussed as immediately follows.
+Without spelling out everything, we notice that as long as a term has a single \m {\M{Q} \DB {n_R, n_Y}} factor, it's expectation is zero.
+The terms that does not vanish is a product of three numbers: How many terms, the moment involving \m {\M{Q} \DB {n_y, n_h}}, the norm of \m {\V{u}}.
+We will repeatedly bound \m {N_R \D (N_R-1) /2} by \m {N_R^2 /2}, and bound \m {\Nm {\V{u}} _2} by \m {\Nm {\V{u}} _2}, and so on.
+\Disp {
+\NC E_1
+=\NC \sum_{n_y=0}^{N_y-1} \sum_{n_h=0}^{N_h-1}
+\Nm {\M{Q} \DB {n_y, n_h}} ^4
+\Nm {\V{u} \DB{n_h}} ^4 \NR
+\NC =\NC N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \D \Nm {\V{u}} _4 ^4 \NR
+\NC \leq \NC 4 N_Y ^{-2} N_R ^{-2} \Nm {\V{u}} _2 ^4 \NR[+]
 }
-Without spelling out everything, we notice that as long as a term has a single \m {\M{F}_B \DB {n_R, n_Y}} factor, it's expectation is zero.
-Also notice that
-\Disp{
-\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
-\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
-   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
-\NC \NC \quad \quad +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
-      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
-\NC = \NC 0 \NR[+]
+\Disp {
+\NC E_2
+= \NC \sum _{\Stack { n_y, n_y' =0 \NR n_y <n_y' }}^{N_y-1}
+\sum _{n_h =0}^{N_h-1}
+\Nm {\M{Q} \DB {n_y, n_h}} ^2
+\Nm {\M{Q} \DB {n_y', n_h}} ^2
+\Nm {\V{u} \DB{n_h}} ^4 \NR
+\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D 8 N_R ^{-2} N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
+\NC \NC \Q \Q + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
+\NC \leq \NC 4 N_R ^{-2} \VNm {\V{u}} _2 ^4 \NR[+]
 }
-Having said that, with straightforward calculation, we see that the remaining terms are
-\Disp{
-\NC \NC \MB{E} \SB {\VNm {\M{F}_B \V{u}} _2 ^4} \NR
-\NC = \NC
-\sum_{n_R=0}^{N_R-1} \sum_{n_Y=0}^{N_Y-1}
-\Nm {\M{F}_B \DB {n_R, n_Y}} ^4
-\Nm {\V{u} \DB{n_Y}} ^4 \NR
-\NC \NC \quad \quad
-+\sum _{\startsubstack n_R, n_R' =0 \NR n_R <n_R' \stopsubstack}^{N_R-1}
-\sum _{n_Y =0}^{N_Y-1}
-\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
-\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
-\Nm {\V{u} \DB{n_Y}} ^2
-\Nm {\V{u} \DB{n_Y'}} ^2 \NR
-\NC \NC \quad \quad
-+\sum _{n_R, n_R' =0}^{N_R-1}
-\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
-\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
-\Nm {\M{F}_B \DB {n_R', n_Y'}} ^2
-\Nm {\V{u} \DB{n_Y}} ^2
-\Nm {\V{u} \DB{n_Y'}} ^2 \NR
-\NC \NC \quad \quad
-+\sum _{n_R =0}^{N_R-1}
-\sum _{\startsubstack n_Y, n_Y' =0 \NR n_Y <n_Y' \stopsubstack}^{N_Y-1}
-\Nm {\M{F}_B \DB {n_R, n_Y}} ^2
-\Nm {\M{F}_B \DB {n_R, n_Y'}} ^2
-\Nm {\V{u} \DB{n_Y}} ^2
-\Nm {\V{u} \DB{n_Y'}} ^2 \NR
-\NC =\NC N_R \D M_4 \D \VNm {\V{u}} _4 ^4
-   +\F {1} {2} N_R \RB {N_R-1} \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \NC \quad \quad + N_R^2 \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}
-   + N_R \D M_2^2 \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC =\NC \RB {N_R M_4 -\F{1}{2} \RB {3N_R^2 +N_R} M_2^2} \VNm {\V{u}} _4 ^4
-+\F{1}{2} \RB {3N_R^2 +N_R} M_2^2 \VNm {\V{u}} _2 ^4 \NR[+]
+\Disp {
+\NC E_3
+=\NC \sum _{n_y, n_y' =0}^{N_y-1}
+\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
+\Nm {\M{Q} \DB {n_y, n_h}} ^2
+\Nm {\M{Q} \DB {n_y', n_h'}} ^2
+\Nm {\V{u} \DB{n_h}} ^2
+\Nm {\V{u} \DB{n_h'}} ^2 \NR
+\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D 8 N_R ^{-2} N_Y ^{-4} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
+\NC \leq \NC 4 N_R ^{-2} N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
 }
-Plugging in the moments, we have
-\Disp{
-\NC =\NC -\F{3}{2} \RB {1 -\F{1}{N_R}} \VNm {\V{u}} _4 ^4
-+\F{1}{2} \RB {3 +\F{1}{N_R}} \VNm {\V{u}} _2 ^4 \NR[+]
+\Disp {
+\NC E_4
+=\NC \sum _{n_y =0}^{N_y-1}
+\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
+\Nm {\M{Q} \DB {n_y, n_h}} ^2
+\Nm {\M{Q} \DB {n_y, n_h'}} ^2
+\Nm {\V{u} \DB{n_h}} ^2
+\Nm {\V{u} \DB{n_h'}} ^2 \NR
+\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D 8 N_R ^{-2} N_Y ^{-4} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
+\NC \leq \NC 4 N_H ^2 N_R ^{-2} N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
 }
-Use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, and we have simply
-\Disp{
-\NC \NC \leq \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
+The last one is more difficult.
+In the end we used Muirhead inequality to get \m {\i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \leq \RB {1/6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}}.
+\Disp {
+\NC E_5
+\NC = \sum _{
+    \Stack {
+      0 =n_h <n_h' \NR
+      0 =m_h <m_h' \NR
+      n_h +m_h' =n_h' +m_h \NR
+      \Fl {n_h/N_H} =\Fl {n_h'/N_H} \NR
+      \Fl {m_h/N_H} =\Fl {m_h'/N_H}
+    }
+  } ^{N_H-1}
+  \sum _{\Stack { 0 =n_y <n_y' \NR \Fl {n_y/N_Y} =\Fl {n_y'/N_Y} }} ^{N_y-1} \NR
+  \NC \NC \Q \Q \Q \Q
+  \Nm {\M{Q} \DB {n_y, n_h}}
+  \Nm {\M{Q} \DB {n_y, n_h'}}
+  \Nm {\M{Q} \DB {n_y, m_h}}
+  \Nm {\M{Q} \DB {n_y, m_h'}} \NR
+  \NC \NC \Q \Q \Q \Q
+  \VNm {\V{u} \DB{n_h}} ^2
+  \VNm {\V{u} \DB{n_h'}} ^2
+  \VNm {\V{u} \DB{m_h}} ^2
+  \VNm {\V{u} \DB{m_h'}} ^2 \NR
+\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \NR
+\NC \NC \Q \Q \Q \Q
+\D 8 N_R ^{-2} N_Y ^{-4} \NR
+\NC \NC \Q \Q \Q \Q
+\D \sum_{\Stack {n_h, n_h' =0}} ^{N_H-1}
+\sum_{\Stack {m_h, m_h' =0}} ^{N_H-1}
+\i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \NR
+\NC \NC \Q \Q \Q \Q
+\VNm {\V{u} \DB{n_h}} \VNm {\V{u} \DB{n_h'}}
+\VNm {\V{u} \DB{m_h}} \VNm {\V{u} \DB{m_h'}} \NR
+\NC \leq \NC \F{1}{3} N_Y ^{-1} N_H ^4 N_R ^{-2} \VNm {\V{u}} _2 ^4. \NR[+]
 }
@@
 \Disp{
-\NC \Ss{Var} _{\o_t} \SB {\VNm {\M{F}_B \SB {\o_t} \V{u}} _2 ^2}
+\NC \Ss{Var} \SB {\VNm {\M{P} \SB {\o_t, \o_r} \V{u}} _2 ^2}
 \leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
@@
 {
-Let \m {\M{F}_B \in \MB {M}_{\MB {C}} \SB {N_R, N_Y}} be generated randomly according to ().
+Let \m {\M{P} \in \MB {M}_{\MB {C}} \SB {N_R, N_Y}} be generated randomly according to ().
 Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_Y}}, and for any \m {\e >0},
 \Disp{
-\NC \MB{P} _{\o_t}
+\NC \MB{P}
 \SB {
-  \Nm {\VNm {\M{F}_B \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
+  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
   \geq \e \VNm {\V{u}} _2 ^2
@@
 }
+
 According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), substitution of relevent quantities yields
@@
 }
-Same can be said of \m {\M{W}_B}.
 }
@@
 
-\startsection [title={Concentration Inequality of Precoders and Combiners}]
-
-Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
-\Disp{
-\NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} ^2}^{-1/2}
-d \MF{Re} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
-\NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} ^2}^{-1/2}
-d \MF{Im} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
-}
-As a result,
-\Disp{
-\NC \NC \MB{E} _{\o_t} \SB {\M{F}_R \DB {n_H, n_R} \SB {\o_t}} \NR
-\NC =\NC \a \NR[+]
-\NC M_2
-:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^2} \NR
-\NC =\NC \a^2 \NR[+]
-\NC M_4
-:=\NC \MB{E} _{\o_t} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^4} \NR
-\NC =\NC \a^4 \NR[+]
-}
-
-Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_H}}, 
-By a similar argument, we may set
-\Disp{
-\NC \a
-=\NC \F {1} {\R{N_H}} \NR[+]
-}
-to make
-\Disp{
-\NC \NC \MB{E} _{\o_t} \SB {\VNm {\M{F}_R \SB {\o_t} \V{u}} _2 ^2} \NR
-\NC = \NC \VNm {\V{u}} _2 ^2 \NR[+]
-}
-Furthermore, if we plug in the moments and use \m {\VNm {\V{u}} _2 \leq N_y \VNm {\V{u}} _4} and drop the rest of \m {\VNm {\V{u}} _4 ^4} term, we have simply
-\Disp{
-\NC \NC \MB{E} \SB {\VNm {\M{F}_R \V{u}} _2 ^4} \NR
-\NC =\NC \RB {N_H M_4 -\F{1}{2} \RB {3N_H^2 +N_H} M_2^2} \VNm {\V{u}} _4 ^4
-+\F{1}{2} \RB {3N_H^2 +N_H} M_2^2 \VNm {\V{u}} _2 ^4 \NR
-\NC =\NC -\F{1}{2} \RB {3 -\F{1}{N_H}} \VNm {\V{u}} _4 ^4
-+\F{1}{2} \RB {3 +\F{1}{N_H}} \VNm {\V{u}} _2 ^4 \NR
-\NC \leq \NC \F{3}{2} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-
-In conclusion,
-\Disp{
-\NC \Ss{Var} _{\o_t} \SB {\VNm {\M{F}_R \SB {\o_t} \V{u}} _2 ^2}
-\leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-
-\stopsection
-
-\startsection [title={RIP of Precoders and Combiners}]
+\startsection [title={Restricted Isometry of \m {P}}]
 
@@
 \Disp{
-\NC \MB{P} _{\o_t}
+\NC \MB{P}
 \SB {
@@
 {
-Suppose the probability that RIP holds for \m {\Phi} w.r.t.\ \m {\d_s} is \m {P}, then
+Suppose the probability that RIP holds for \m {\V{P}} w.r.t.\ \m {\d_s} is \m {p}, then
 \Disp{
-\NC 1 -P
+\NC 1 -p
 \leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} \NR[+]
 }
-Same can be said of \m {\M{W}_B}.
 }
-
-We may bound \m {\RB {1 +\d_s}^2} by \m {1 +3\d_s}.
-A moment of reflection shows that
 
@@
 
-\startsection [title={Expected Square Error for Complex-Case DS}]
+\startsection [title={Expected Error for Complex-Case Dantzig Selector}]
+
+Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {s} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {s} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {s=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
+We rephrase it formally.
+
+\Result
+{Definition}
+{
+Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
+Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
+\Disp{
+\NC \V{v} \DB {\s \SB {n}}
+\leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
+\NC n =\NC 1, \dots, N_p-1 \NR
+}
+Its existence is evident.
+
+Let \m {s \leq N_p/2} be fixed.
+Define
+\Disp{
+\NC \MC {S} \SB {\V{x}, s}
+=\NC \sum_{i=0} ^{s-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
+\NC \MC {C} \SB {\V{x}, s}
+=\NC \sum_{i=s} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
+}
+}
+
+Now set
+\Disp{
+\NC \V{g} _\MC {A}
+=\NC \MC {S} \SB {\V{g}, s} \NR[+]
+\NC \V{g} _\MC {K}
+=\NC \MC {C} \SB {\V{g}, s} \NR[+]
+\NC \V{g} _\MC {B}
+=\NC \MC {S} \SB {\V{g} _\MC {K}, s} \NR[+]
+}
+
+Let \m {\hat {\V {g}}} be the Dantzig Selector.
+For concreteness, we set
+\Disp {
+\NC \g 
+= \NC \R {2 \log N_h} \NR[+]
+}
+
+Other values are of course possible, but this is enough to illustrate our purpose.
+Also set for short
+\Disp {
+\NC \V {d} 
+= \NC \Hat {\V {g}} -\V {g} \NR[+]
+}
 
@@
 \Result
-{Proposition}
+{Lemma}
 {
@@
 \Disp {
-\NC \VNm {\V {d}_{\MC {C}}} _1
-\leq \NC \VNm {\V {d}_{\MC {A}}} _1 +2\VNm {\V {g}_{\MC {C}}} _1 \NR
+\NC \VNm {\V {d} _{\MC {K}}} _1
+\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {K}}} _1 \NR
 }
@@
 
-To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}},
+To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {K}},
 \Disp {
 \NC \VNm {\V {g}} _1
--\VNm {\V {d}_{\MC {A}}} _1
-+\VNm {\V {d}_{\MC {C}}} _1
--\VNm {\V {g}_{\MC {C}}} _1
+-\VNm {\V {d} _{\MC {A}}} _1
++\VNm {\V {d} _{\MC {K}}} _1
+-\VNm {\V {g} _{\MC {K}}} _1
 \leq \NC \VNm {\V {g} +\V {d}} _1 \NR
 }
-In the first line, we recall \m {\V {g} =\V {g}_{\MC {A}}}.
+In the first line, we recall \m {\V {g} =\V {g} _{\MC {A}}}.
 On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
@@
 {
-Let \m {\V {z}} and \m {\M {P}} be defined as above.
-Then
 \Disp {
-\NC \Nm {\IP { \V {z}, \M {P} \DB {:, n_g} }}
-\leq \NC  2 \R {\log N_h},
-\quad n_g 
-=1, \dots, N_h. \NR
+\NC \Nm {\IP { \V {z} \SB {\o_z}, \M {P} \DB {:, n_g} }}
+\leq \NC  2 \R {\log N_h} \NR
+\NC n_g 
+=\NC 1, \dots, N_h. \NR
 }
-with overwhelming probability.
+with probability \m {\geq 1 -N_h}.
 }
@@
 }
-Particularly, for \m {x =\R {2 \log N_h}}, according to CLT,
+Particularly, for \m {x =\R {2 \log N_h}},
 \Disp {
@@
 
-\color[red]{(To be done)}
-
 \Result
@@
 {
-Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in ().
+With the condition that \m {\M {P}} satisfies RIP for \m {\d_s \SB {\M{P}}},
 \Disp {
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC  4 \R {\log N_h},
-\quad n_g 
-=1, \dots, N_h. \NR
+\leq \NC  4 \R {\log N_h} \NR
+\NC n_g 
+=\NC 1, \dots, N_h. \NR
 }
+with probability \m {\geq 1 -N_h}.
 }
@@
 }
-
 By construction
 \Disp {
-\NC \VNm { \M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } 
+\NC \VNm { \M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty
 \leq \NC \VNm { \M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty \NR
@@
 \Disp {
-\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} 
-\leq \NC \VNm {\IP { \V {z}, \M {P} \DB {:,n_y} }}  +\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y} } \NR
+\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
+\leq \NC \VNm {\IP { \V {z}, \M {P} \DB {:,n_y} }} _\infty
++\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y} } \NR
 \NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
@@
 
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, first equation, we have the result as below.
+From ``Dantzig Selector'' Lemma 1, first equation, we have the result as below.
 The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
-Of course the interpretation of modulus and the inner product changes accordingly.
+The only thing that has to change accordingly is the interpretation of magnitude and the inner product, which are evident.
 
@@
 {
-Let \m {\V {d}} and \m {\M {P}} be defined as above, and \m {\M {P}} satisfies RIP as in () with respect to \m {\d_s}.
+With the condition that \m {\M {P}} satisfies RIP for \m {\d_s \SB {\M{P}}},
 \Disp {
-\NC \VNm {\V {d}_{\MC {AB}}} _2
-\leq \NC \F {1}{1-\d_{2s}} \VNm {P_{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{C}} _1 \NR
+\NC \VNm {\V {d} _{\MC {AB}}} _2
+\leq \NC \F {1}{1-\d_{2s}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{\MC {K}}} _1 \NR
 }
@@
 
-From ``Dantzig Selector'' (Cand\`es and Tao 2007), Lemma 1, second equation, we have the result as below.
+From ``Dantzig Selector'', Lemma 1, second equation, we have the result as below.
 Again, their proof works with complex vector spaces in place of real ones too.
@@
 {
-Let \m {\V {d}} be defined as above.
-Then
 \Disp {
 \NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{s} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
+\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{s} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
 }
 }
+
+\stopsection
 
@@
 }
-with overwhelming probability.
+with probability \m {\geq 1 -N_h}.
 }
@@
 \Disp {
-\NC \VNm {\M {P}_{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
+\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
 \leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
@@
 \leq \NC \R {L} \VNm { \V {d}_{A} } _2 \NR
-\NC \leq \NC \R {L} \VNm { \V {d}_{\MC {AB}} } _2 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
+\NC \leq \NC \R {L} \VNm { \V {d} _{\MC {AB}} } _2 \NR
+\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d} _{\MC {K}} } _1 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
 }
 
-As the next step, we must eliminate \m {\VNm {d_{\MC {A}}} _1} in rhs of Lemma ().
+As the next step, we must eliminate \m {\VNm {d _{\MC {A}}} _1} in rhs of Lemma ().
 \Disp {
-\NC \VNm { \V {d}_{\MC {C}} } _1
-\leq \NC \VNm { \V {d}_{\MC {A}} } _1 +2 \VNm { \V {g}_{\MC {C}} } _1 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d}_{\MC {C}} } _1
-+2 \VNm { \V {g}_{\MC {C}} } _1
+\NC \VNm { \V {d} _{\MC {K}} } _1
+\leq \NC \VNm { \V {d} _{\MC {A}} } _1 +2 \VNm { \V {g} _{\MC {K}} } _1 \NR
+\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d} _{\MC {K}} } _1
++2 \VNm { \V {g} _{\MC {K}} } _1
 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
@@
 \Disp {
-\NC \VNm { \V {d}_{\MC {C}} } _1
-\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g}_{\MC {C}} } _1
+\NC \VNm { \V {d} _{\MC {K}} } _1
+\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g} _{\MC {K}} } _1
 +\F {4} {1-\d_{2L} -\d_{3L}} \R {L N_h \log N_h} \NR
@@
 \NC \VNm { \V {d} } _2^2
-\leq \NC \VNm {\V {d}_{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d}_{\MC {C}}} _1^2 \NR
-\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d}_{\MC {C}}} _1^2
-+\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_h \log N_h} \VNm {\V {d}_{\MC {C}}} _1 \NR
-\NC \NC \quad +\F {16}{\RB {1-\d_{2L}}^2} N_h \log N_h \NR
+\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
+\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d} _{\MC {K}}} _1^2
++\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_h \log N_h} \VNm {\V {d} _{\MC {K}}} _1 \NR
+\NC \NC \Q +\F {16}{\RB {1-\d_{2L}}^2} N_h \log N_h \NR
 }
-Finally, plug in the bound for \m {\VNm {\V {d}_{\MC {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d}_{\MC {C}}} _1}.
+Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {K}}} _1}.
 There are several dozens of terms if we expand all.

### 2019-05-27 dantzig_selector/report/notation.tex
Proof: Expectation of

@@
 
-Denote as \m {\MB {P} \SB {X}} the probability, \m {\MB {E} \SB {X}} the expectation, and \m {\MB {Var} \SB {X}} the variance.
-Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables like \m {\MB {P} _\o \SB {X \SB {\o}}}.
+Denote as \m {\MB {P} \SB {X}} the probability, \m {\MB {E} \SB {X}} the expectation, and \m {\Ss {Var} \SB {X}} the variance.
+We may spell out the random variables' dependence of event space index when confusion might arise, as in \m {X \SB {\o}}.
 

### 2019-05-28 dantzig_selector/report/3_theorems_and_proofs.tex
Create ConTeXt slides

@@
 \NC n_R
-= \NC 0, 1, 2, \dots, N_R -1 \NR
+= \NC 0, 1, 2, \ldots, N_R -1 \NR
 \NC n_Y
-= \NC 0, 1, 2, \dots, N_Y -1 \NR
+= \NC 0, 1, 2, \ldots, N_Y -1 \NR
 }
@@
 
-Start with the observtion
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E} \SB {\M{P} \DB {n_y, n_h} \M{P} \DB {n_y', n_h'}} \NR
-\NC = \NC \startcases
-\l_R^4 \l_B^4, \Q \MC n_y =n_y', n_h =n_h' \NR
-0, \Q \NC \Rm {otherwise} \NR
-\stopcases \NR
-}
-}
-
-Notice
+Observe
 \Disp {
@@
 \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-\otimes \RB {\M {W}_B \M {W}_R \M {W}_R^\Adj \M {W}_B^\Adj} \NR[+]
+\otimes \RB {\M {W}_B \M {W}_R \M {W}_R^\Adj \M {W}_B^\Adj}
+\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR
+\NC := \NC \M{Q} \NR[+]
 }
-where, restating (), \m {\M {Q} :=\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R}}.
 
@@
 
-To make expressions more compact, introduce
+\Result
+{Definition}
+{
+To make expressions more compact, introduce the indication function \m {\i}, so that, for some injective \m {\s:\; \CB {0, \ldots, M-1} \CB {0, \ldots, N-1}},
 \Disp {
-\NC \i_2 \SB {x_0, x_1}
+\NC \i_{a_0, \ldots, a_{M-1}} \SB {x_0, \ldots, x_{N-1}}
 =\NC \startcases
-\NC 1, \MC \Q x_0 =x_1 \NR
-\NC 0, \NC \Q \Rm {otherwise} \NR
-\stopcases \NR
-\NC \i_4 \SB {x_0, x_1, x_2, x_3}
-=\NC \startcases
-\NC 1, \MC \Q x_0 =x_1 =x_2 =x_3 \NR
+\NC 1, \MC \Q \exists \s:\; x_0 \cdots x_{N-1}
+=x_{\s \SB {0}} ^{a_0} \cdots x_{\s \SB {M-1}} ^{a_{M-1}} \NR
 \NC 0, \NC \Q \Rm {otherwise} \NR
@@
 }
-And, for any permutation \m {\s} on \m {\CB {1, 2, 3, 4}},
-\Disp {
-\NC \i_{2,2} \SB {x_0, x_1, x_2, x_3}
-=\NC \startcases
-\NC 1, \MC \Q x_{\s \RB{0}} =x_{\s \RB{1}} \neq x_{\s \RB{2}} =x_{\s \RB{3}} \NR
-\NC 0, \NC \Q \Rm {otherwise} \NR
-\stopcases \NR
 }
 
+For short, denote
+\Disp {
+\NC F :=\NC \M {F}_B \M {F}_R \NR
+\NC W :=\NC \M {W}_R \M {W}_B \NR
+}
 \Result
@@
 \Disp {
-\NC \NC \MB{E} \SB {\RB {\M{F}_R \M{F}_B} \DB {n_H, n_Y} \RB {\M{F}_R \M{F}_B} \DB {n_H', n_Y'}} \NR
-\NC = \NC \MB{E} \SB {\RB {\M{W}_R \M{W}_B} \DB {n_Y, n_H} \RB {\M{W}_R \M{W}_B} \DB {n_Y', n_H'}} \NR
-\NC = \NC N_R \D \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D \RB {\l_R^2 +\l_B^2} \NR
+\NC \NC \MB{E} \SB {\M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'}} \NR
+\NC = \NC \MB{E} \SB {\M{W}^\Adj \DB {n_Y, n_H} \M{W}^\Adj \DB {n_Y', n_H'}} \NR
+\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR
 }
@@
 \Disp {
-\NC \NC \RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y, n_H} \RB {\M{F}_R \M{F}_B} \DB {n_Y', n_H'} \NR
+\NC \NC \M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'} \NR
 \NC =\NC
@@
 }
-When either \m {n_y \neq n_y'} or \m {n_h \neq n_h'}, no term is an all-square product.
+Examine the \m {\i_{1,1} \SB {n_H, n_H'}} factor and \m {\i_{1,1} \SB {n_Y, n_Y'}} factors.
 After taking expectation, the expectation sign is distributed, and every term vanishes.
-But when \m {n_y =n_y'} or \m {n_h =n_h'}, the only terms that remains are
+Other terms that remains are \m {\i_{2} \SB {n_H, n_H'}} and \m {\i_{2} \SB {n_Y, n_Y'}}, namely
 \Disp {
@@
 \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
-\NC = \NC N_R \D \RB {M_{R,2} +M_{B,2}} \NR
+\NC = \NC N_R \D M_{R,2} M_{B,2} \NR
+}
+
+By the same token,
+\Result
+{Lemma}
+{
+\Disp {
+\NC \NC \MB{E} \SB {\M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'} \M{F} \DB {n_H, n_Y} \M{F} \DB {n_H, n_Y}} \NR
+\NC = \NC \MB{E} \SB {\RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y, n_H} \RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y', n_H'}} \NR
+\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR
+}
 }
@@
 
-Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we shall study the probability concentration of \m {\VNm {\M{F}_B \V{u}}_2^2} and \m {\VNm {\M{F}_B \V{u}}_2^4}.
+\Result
+{Lemma}
+{
+\Disp {
+\NC \NC \MB{E} \SB {\M{Q} \DB {n_Y, n_H} \M{Q} \DB {n_Y', n_H'}} \NR
+\NC = \NC \startcases
+N_R^2 \l_R^4 \l_B^4, \Q \MC n_Y =n_Y', n_H =n_H' \NR
+0, \Q \NC \Rm {otherwise} \NR
+\stopcases \NR
+}
+}
+
+Now, fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we shall study the probability concentration of \m {\VNm {\M{F}_B \V{u}}_2^2} and \m {\VNm {\M{F}_B \V{u}}_2^4}.
 The two moments are present in Chebyshev bound.
@@
 \Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC =\NC N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \D \Nm {\V{u}} _4 ^4 \NR
-\NC \leq \NC 4 N_Y ^{-2} N_R ^{-2} \Nm {\V{u}} _2 ^4 \NR[+]
+\NC =\NC N_Y^2 \D 4 N_Y ^{-4} \D \VNm {\V{u}} _4 ^4 \NR
+\NC \leq \NC 4 N_Y ^{-2} \VNm {\V{u}} _2 ^4 \NR[+]
 }
+Now we have to bound \m {\i_{1,1} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,2}^2} and \m {\i_{2} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,4}} by \m {M_{B,4}} to simplifying matters, and similar for \m {E_3} and \m {E_4}.
 \Disp {
@@
 \Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D 8 N_R ^{-2} N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
+\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D 4 N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
 \NC \NC \Q \Q + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
-\NC \leq \NC 4 N_R ^{-2} \VNm {\V{u}} _2 ^4 \NR[+]
+\NC \leq \NC 4 \VNm {\V{u}} _2 ^4 \NR[+]
 }
@@
 \Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D 8 N_R ^{-2} N_Y ^{-4} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \leq \NC 4 N_R ^{-2} N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
+\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D 4 N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
+\NC \leq \NC 4 N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
 }
@@
 \Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D 8 N_R ^{-2} N_Y ^{-4} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \leq \NC 4 N_H ^2 N_R ^{-2} N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
+\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D 4 N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
+\NC \leq \NC 4 N_H ^2 N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
 }
-The last one is more difficult.
-In the end we used Muirhead inequality to get \m {\i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \leq \RB {1/6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}}.
+
+The last one is more complicated.
+We need a corollary that follows from ``Muirhead inequality''.
+\Result
+{Lemma}
+{
+If every component of \m {\V{u} \in \MB {M}_{\MB {C}} \SB {N_h}} is considered as a free variable taking complex values, then
+\Disp {
+\NC \NC \sum \i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'}
+\V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \NR
+\NC \leq \NC \RB {1/6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
+}
+}
+
+Now,
 \Disp {
@@
   \sum _{\Stack { 0 =n_y <n_y' \NR \Fl {n_y/N_Y} =\Fl {n_y'/N_Y} }} ^{N_y-1} \NR
-  \NC \NC \Q \Q \Q \Q
-  \Nm {\M{Q} \DB {n_y, n_h}}
-  \Nm {\M{Q} \DB {n_y, n_h'}}
-  \Nm {\M{Q} \DB {n_y, m_h}}
-  \Nm {\M{Q} \DB {n_y, m_h'}} \NR
-  \NC \NC \Q \Q \Q \Q
-  \VNm {\V{u} \DB{n_h}} ^2
-  \VNm {\V{u} \DB{n_h'}} ^2
-  \VNm {\V{u} \DB{m_h}} ^2
-  \VNm {\V{u} \DB{m_h'}} ^2 \NR
-\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \NR
-\NC \NC \Q \Q \Q \Q
-\D 8 N_R ^{-2} N_Y ^{-4} \NR
-\NC \NC \Q \Q \Q \Q
-\D \sum_{\Stack {n_h, n_h' =0}} ^{N_H-1}
-\sum_{\Stack {m_h, m_h' =0}} ^{N_H-1}
+  \NC \NC \SixQ
+  \M{Q} \DB {n_y, n_h}
+  \M{Q} \DB {n_y, n_h'}
+  \M{Q} \DB {n_y', m_h}
+  \M{Q} \DB {n_y', m_h'} \NR
+  \NC \NC \SixQ
+  \V{u} \DB{n_h}
+  \V{u} \DB{n_h'}
+  \V{u} \DB{m_h}
+  \V{u} \DB{m_h'} \NR
+\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \D 4 N_Y ^{-4} \NR
+\NC \NC \SixQ
+\D \sum_{n_h, n_h' =0} ^{N_H-1}
+\sum_{m_h, m_h' =0} ^{N_H-1}
 \i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \NR
-\NC \NC \Q \Q \Q \Q
-\VNm {\V{u} \DB{n_h}} \VNm {\V{u} \DB{n_h'}}
-\VNm {\V{u} \DB{m_h}} \VNm {\V{u} \DB{m_h'}} \NR
-\NC \leq \NC \F{1}{3} N_Y ^{-1} N_H ^4 N_R ^{-2} \VNm {\V{u}} _2 ^4. \NR[+]
+\NC \NC \SixQ
+\Nm {\V{u} \DB{n_h}}
+\Nm {\V{u} \DB{n_h'}}
+\Nm {\V{u} \DB{m_h}}
+\Nm {\V{u} \DB{m_h'}} \NR
+\NC \leq \NC \F{1}{3} N_Y ^{-1} N_H ^4 \VNm {\V{u}} _2 ^4. \NR[+]
 }
@@
 \leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
-\NC n =\NC 1, \dots, N_p-1 \NR
+\NC n =\NC 1, \ldots, N_p-1 \NR
 }
@@
 \NC n_g 
-=\NC 1, \dots, N_h. \NR
+=\NC 1, \ldots, N_h. \NR
 }

### 2019-05-28 dantzig_selector/report/4_simulation.tex
Proof: Expectation of
Create ConTeXt slides

@@
 \NC m' 
-= \NC  0, 1, 2, \dots, M-1 \NR
+= \NC  0, 1, 2, \ldots, M-1 \NR
 }
@@
 \NC m_1 
-= \NC 0, 1, 2, \dots, M_1 -1 \NR
+= \NC 0, 1, 2, \ldots, M_1 -1 \NR
 \NC m_2 
-= \NC 0, 1, 2, \dots, M_2 -1 \NR
+= \NC 0, 1, 2, \ldots, M_2 -1 \NR
 }
@@
 \startcases
-1, \quad \MC n_h' =n_h \NR
-0, \quad \NC {\rm otherwise}
+1, \Q \MC n_h' =n_h \NR
+0, \Q \NC \Rm {otherwise} \NR
 \stopcases \NR[+]
@@
 \startcases
-1, \quad \MC n_h' =2n_h,\; n_h'' =2n_h \NR
-1, \quad \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
-0, \quad \NC {\rm otherwise}
+1, \Q \MC n_h' =2n_h,\; n_h'' =2n_h \NR
+1, \Q \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
+0, \Q \NC \Rm {otherwise} \NR
 \stopcases \NR[+]
 \NC n_h, n_h', n_h'' 
-= \NC 0, 1, 2, \dots, N_h -1 \NR
+= \NC 0, 1, 2, \ldots, N_h -1 \NR
 }
@@
 \Disp{
-\NC \V {m} \NC \in \MB {V}_{\MB {R}} \SB {N_h} \NR
+\NC \V {m} \in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
 \NC \V{m} \DB{n_h}
@@
 \NC n_h, n_h', n_h'' 
-= \NC 0, 1, 2, \dots, N_h -1 \NR
+= \NC 0, 1, 2, \ldots, N_h -1 \NR
 }
-
-to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now take the form
+to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now takes the form
 \Disp {
@@
 = \NC \startcases
-\NC \Min {\T {\V {g}}', \V {m}} \quad
+\NC \Min {\T {\V {g}}', \V {m}} \Q
 \MC \IP { \V {1}, \V {m} } \NR
-\NC \Rm {subject} \; \Rm {to} \quad
+\NC \Rm {subject} \; \Rm {to} \Q
 \MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
@@
 \NC n_h 
-= \NC 0, 1, 2, \dots, N_h-1 \NR
+= \NC 0, 1, 2, \ldots, N_h-1 \NR
 }
@@
 \NC i 
-= \NC 0, 1, 2, \dots, N_h -1 \NR
+= \NC 0, 1, 2, \ldots, N_h -1 \NR
 }
@@
 \NC i 
-= \NC N_h, N_h +1, N_h +2, \dots, 2N_h -1 \NR
+= \NC N_h, N_h +1, N_h +2, \ldots, 2N_h -1 \NR
 }
@@
 \NC \Rm {subject} \; \Rm {to}
-\quad  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
+\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
 \leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
 \NC \MC i 
-=0, 1, 2, \dots, 2N_h -1 \NR
+=0, 1, 2, \ldots, 2N_h -1 \NR
 \stopcases \NR[+]

### 2019-05-28 dantzig_selector/presentation/main.tex
Create ConTeXt slides
Proof: Finish: Almost-sparsity of

--- 2019-02-01 ongoing/presentation/slides.tex
@@
-\documentclass{beamer}
+\input {./preamble.tex}
 
-\usepackage{mathtools}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{stackengine}
+\starttext
 
-\setcounter{section}{-1}
-\newcounter{countRef}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\newcommand{\Disp}[1]{\begin{align} #1 \end{align}}
+\blank [big, force]
+\Title {Dantzig Selector \\ Applied on mm-Wave MIMO: \\ Part I. Expected Error Analysis}
+\blank [big]
+\Subtitle {Presenter: Tzu-Yu Jeng \\ Advisor: Prof.\ H.J.\ Su}
+\blank [big]
+\Subsubtitle{May 30, 2019}
+\Subsubtitle{Graduate Instute of Commnication Engineering, \\ National Taiwan University}
 
-\renewcommand{\H}{\dagger}
-\newcommand{\Tr}{\intercal}
-\newcommand{\NT}{\notag}
-\renewcommand{\d}{\delta}
-\newcommand{\f}{\varphi}
-\renewcommand{\th}{\vartheta}
-\newcommand{\I}{\item}
+\page[yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\newcommand{\MB}[1]{\mathbb{#1}}
-\newcommand{\MC}[1]{\mathcal{#1}}
-\newcommand{\MF}[1]{\mathfrak{#1}}
-\newcommand{\RM}[1]{\mathrm{#1}}
-\newcommand{\R}[1]{\sqrt{#1}}
-\newcommand{\F}[1]{\frac{#1}}
-\newcommand{\V}[1]{\stackunder[1.2pt]{$#1$}{\rule{.9ex}{.075ex}}}
-\newcommand{\M}[1]{\V{\V{#1}}}
-\newcommand{\T}[1]{\tilde{#1}}
-\newcommand{\IP}[1]{\langle #1 \rangle}
+\Frametitle {Organization}
 
-\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}
-\author{Presenter: Tzu-Yu Jeng \\ Advisor: Prof.\ H.J.\ Su}
-\date{Jan.\ 9, 2019}
-\institute{Graduate Instute of Commnication Engineering, NTU}
-
-\begin{document}
-
-\frame{\titlepage}
-
-\begin{frame}
-\frametitle{Overview}
-\begin{itemize}
-\I Motivation and Background 
-\I Configuration and Problem Formulation
-\I Theorems and Proofs
+\startitemize
+\I Problem Configuration Proposed Method
+\I Sparsity of Angular Channel Matrix
+\I Concentration Inequality of \m {\M{P}}
+\I Restricted Isometry of \m {\M{P}}
+\I Expected Error of Dantzig Selector
 \I Conclusion and Future Work
 \I References
-\end{itemize}
-\end{frame}
+\stopitemize
 
-\begin{frame}
-\frametitle{Motivation (1/2)}
-\begin{itemize}
-\I Multiple-input-multiple-output (MIMO) wireless communication is widely expected to be the next-generation communication scheme.
-\I Recall that reliable communication requires that the channel response be known at the receiver, to facilitate beamforming algorithm and channel calibration
-\I And in the MIMO system, it is a non-trivial problem to estimate wireless channels due to high complexity
-\I Meanwhile, in the millimeter wave r\`egime, which is often used together with MIMO, channel often exhibits sparse properties.
-\I If the sparsity is exploited, few observations may suffice to estimate the channel
-\end{itemize}
-\end{frame}
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\begin{frame}
-\frametitle{Motivation (2/2)}
-\begin{itemize}
+\stoptext
+
+\Frametitle {Background}
+\startitemize
+
+\I Multiple-input-multiple-output (MIMO) wireless communication is widely expected to be the next-generation communication scheme
+\I But reliable communication requires that the channel response be known at the receiver to facilitate, say, beamforming algorithm and channel calibration
+\I And in the MIMO system, estimating wireless channels calls for high complexity
+\I Meanwhile, in the millimeter wave r\`egime, which is often used together with MIMO, channel often exhibits sparse properties
+\I If the sparsity is exploited, can few observations suffice to estimate the channel?
+
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Compressive Sensing}
+\startitemize
+
 \I Recent developement on channel estimation is facilitated by advances of so-called compressed sensing (CS)
-\I CS addresses the common situation in statsitical applications that the number of model parameters \(N_p \gg\) the number of measurements \(N_m\).
-\I With insufficient (possibly noisy) measurements, how well can we recover all \(N_p\) parameters?
+\I CS addresses the common situation in statsitical applications that the number of model parameters \m {} the number of measurements \m {}.
+\I With insufficient (possibly noisy) measurements, how well can we recover all \m {} parameters?
 Of course, more assumption must be made.
@@
 It was first applied in channel estimation context
-\end{itemize}
-\end{frame}
 
-\begin{frame}
-\frametitle{Notation}
-\begin{itemize}
-\I \(\V{a}\) denotes vectors
-\I \(\M{A}\) denotes matrices
-\I \(\MB{K}\) refers to either \(\MB{R}\) or \(\MB{C}\).
-\I \(\MB{V}_{\MB{K}} (N)\) is the Hilbert space \(\MB{K}^N\) over \(\MB{K}\)
-\I \(\MB{M}_{\MB{K}} (M,N)\) is the collection of \(M\) by \(N\) matrices.
-\I \(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm of \(\V{a}\)
-\end{itemize}
-\end{frame}
+\stopitemize
 
-\begin{frame}
-\frametitle{Definitions: Sparsity}
-\begin{itemize}
-\I Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_m, N_p)\).
-Let \(\MC{T} \subset \{1, \dotsc, N_m\}\).
-Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
-\I \(\V{x} \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if only at most \(s\) components of \(\V{x}\) is nonzero.
-\I (New def.) We say \(\V{x}\) is almost-\(s\)-sparse with \(\ell_1\)-residue \(R\), if \( \sum_{n=s+1}^N |S(\V{x}) (n)| \leq R \) where \(S(\V{x})\) is sorted in magnitude.
-\end{itemize}
-\end{frame}
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\begin{frame}
-\frametitle{Program: The Dantzig Selector}
-Let \(\M{P} \in \MB{V}_\MB{R} (N_m, N_p)\) and \(\V{y} \in \MB{V}_\MB{R} (N_m)\) be given, and \(\gamma\) be fixed.
-Find \(\hat{\V{h}} \in \MB{V}_\MB{R} (N_m)\) with
+\Frametitle {Notation}
+\startitemize
+
+\I \m {} denotes vectors
+\I \m {} denotes matrices
+\I \m {} refers to either \m {} or \m {}.
+\I \m {} is the Hilbert space \m {} over \m {}
+\I \m {} is the collection of \m {} by \m {} matrices.
+\I \m {} denotes the \m {}-norm of \m {}
+
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Definitions: Sparsity}
+\startitemize
+
+\I Suppose \m {}.
+Let \m {}.
+Denote as \m {} the columns of \m {} having indices in \m {}.
+\I \m {} is called \m {}-sparse with support \m {}, \m {}, if only at most \m {} components of \m {} is nonzero.
+\I (New def.) We say \m {} is almost-\m {}-sparse with \m {}-residue \m {}, if \m {} where \m {} is sorted in magnitude.
+
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Program: The Dantzig Selector}
+Let \m {} and \m {} be given, and \m {} be fixed.
+Find \m {} with
 \Disp{
@@
 }
-\end{frame}
 
-\begin{frame}
-\frametitle{Performance Guarantee of DS}
-\begin{itemize}
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Performance Guarantee of DS}
+\startitemize
+
 \I Now, consider a linear transformation with noise corruption,
@@
 }
-where \(\V{z}\) is i.i.d.\ standard Gaussian.
+where \m {} is i.i.d.\ standard Gaussian.
 
-\I They showed that the mean square error \(\MB{E}(\| \V{h} -\hat{\V{h}} \|^2)\) is bounded with overwhelming probability.
+\I They showed that the mean square error \m {} is bounded with overwhelming probability.
 
-\I Furthermore, this \(\ell_1\)-minimization problem with \(\ell_\infty\)-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
-\end{itemize}
-\end{frame}
+\I Furthermore, this \m {}-minimization problem with \m {}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
 
-\begin{frame}
-\frametitle{Definition: Restricted Isometry Property}
-\begin{itemize}
-\I Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
-For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the restricted isometry property (RIP) of sparsity \(s\) with respect to \(0 \leq \d_s \leq 1\), if, for all \(s\)-sparse \(\V{x} \in \MB{V}_{\MB{K}} (N_p)\), for all \(\MC{T} \subset \{1, \dotsc, N_p\}\) with \(\#\{\MC{T}\} \leq s\),
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Definition: Restricted Isometry Property}
+\startitemize
+
+\I Consider \m {}, with unity-\m {}-norm columns.
+For \m {}, we say that \m {} satisfies the restricted isometry property (RIP) of sparsity \m {} with respect to \m {}, if, for all \m {}-sparse \m {}, for all \m {} with \m {},
 %
@@
 }
-\I RIP is essentially saying that \(P\) is ``almost unitary'' up to ``relative error'' \(\d_s\).
-\end{itemize}
-\end{frame}
+\I RIP is essentially saying that \m {} is ``almost unitary'' up to ``relative error'' \m {}.
 
-\begin{frame}
-\frametitle{Orthogonal Matching Pursuit}
-\begin{itemize}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Orthogonal Matching Pursuit}
+\startitemize
+
 \I Afterwards, scholars (Tropp and Gilbert 2007b) proposed a greedy algorithm called Orthogonal Matching Pursuit (OMP)
-\I Here, we pick up the columns of the sensing matrix \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\), thus recovering the original signal.
+\I Here, we pick up the columns of the sensing matrix \m {} greedily, hoping to correspond to the support of \m {}, thus recovering the original signal.
 \I An i.i.d.\ random sensing matrix may perform sufficiently well, and may even recover the original signal in an overwhemingly probability too.
-\end{itemize}
-\end{frame}
 
-\begin{frame}
-\frametitle{Recent Literature on Compressive Channel Sensing}
-\begin{itemize}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Recent Literature on Compressive Channel Sensing}
+\startitemize
+
 \I Scholars has since favored OMP rather than DS, let alone other sparse algorithm, without clear justification
@@
 \I The quantization of angle in generating may be a problem, and that is difficult to analyze in OMP's setting
-\end{itemize}
-\end{frame}
 
-\begin{frame}
-\frametitle{Our Work}
-\begin{itemize}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Our Work}
+\startitemize
+
 \I We will use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
@@
 \I We will derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
-\end{itemize}
-\end{frame}
 
-\begin{frame}
-\frametitle{Channel Model}
-\begin{itemize}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Channel Model}
+\startitemize
+
 \I The response of uniform linear array is
@@
 }
-\I Let there be \(L\) paths.
+\I Let there be \m {} paths.
 The channel matrix is, then,
@@
 }
-\end{itemize}
-\end{frame}
 
-\begin{frame}
-\frametitle{Precoder Setting}
-\begin{itemize}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Precoder Setting}
+\startitemize
+
 \I We consider the hybrid configuration at both transmitter and receiver end.
-In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
-In the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
+In the transmitter end, there are digital precoder \m {} and analog precoder \m {}.
+In the receiver end, there are digital combiner \m {} and analog combiner \m {}.
 \Disp{
@@
 }
-\end{itemize}
-\end{frame}
 
-\begin{frame}
-\frametitle{Effective Channel}
-\begin{itemize}
-\I We have the effective channel \(Y =W_B W_R ( H F_R F_B +Z ) \in \MB{M}_{\MB{C}} (N_Y, N_R)\)
-\I We may estimate \(\M{Y} (:,n_y)\) with \(\M{W}_B \M{W}_R [ \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} ]\), \(n_y =1, 2, \dotsc, N_Y\), using pilog signal as unit vectors \(\V{u}_{n_y}\).
-\I It remains to recover \(\M{H}\) with knowledge of \(\M{Y}\), while \(\M{W}_R\), \(\M{W}_B\), \(\M{F}_R\), and \(\M{F}_B\) are in our control
-\end{itemize}
-\end{frame}
+\stopitemize
 
-\begin{frame}
-\frametitle{Vectorization}
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Effective Channel}
+\startitemize
+
+\I We have the effective channel \m {}
+\I We may estimate \m {} with \m {}, \m {}, using pilog signal as unit vectors \m {}.
+\I It remains to recover \m {} with knowledge of \m {}, while \m {}, \m {}, \m {}, and \m {} are in our control
+
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Vectorization}
 Previous literature usually approaches the problem as
@@
 }
-and for short we set \(N_g =N_H^2\) and \(N_y =N_Y^2\),
+and for short we set \m {} and \m {},
 so that
@@
 }
-\end{frame}
 
-\begin{frame}
-\frametitle{Beamspace Channel Representation}
-Let \(\M{K}\) be the DFT matrix.
-If we write \( \M{G} =\M{K}^\H \M{H} \M{K} \), i.e.\ the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Beamspace Channel Representation}
+Let \m {} be the DFT matrix.
+If we write \m {}, i.e.\ the beamspace (i.e., spatial frequency domain) representation of \m {}, then
 \Disp{
@@
 }
-\end{frame}
 
-\begin{frame}
-\frametitle{Proposed Program}
-\begin{itemize}
-\I Let \(\M{P}, \V{y}\) be given.
-Then, with parameter \(\gamma\) specified, find
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Proposed Program}
+\startitemize
+
+\I Let \m {} be given.
+Then, with parameter \m {} specified, find
 %
@@
 }
-\I And convert \(\hat{\V{g}}\) back to matrix form as
+\I And convert \m {} back to matrix form as
 \Disp{
@@
 }
-\I And finally recover the estimated \(H\) in the space domain as
+\I And finally recover the estimated \m {} in the space domain as
 \Disp{
@@
 }
-\end{itemize}
-\end{frame}
 
-\begin{frame}
-\frametitle{Lemma: \(\V{a}\) is Almost Sparse}
-For arbitrary \(\f\), for \(N_H \gg 1\), \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Lemma: \m {} is Almost Sparse}
+For arbitrary \m {}, for \m {}, \m {} is almost-\m {}-sparse with \m {}-residue \m {} to be
 \Disp{
@@
 }
-\end{frame}
 
-\begin{frame}
-\frametitle{Proof (1/3)}
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Proof (1/3)}
 \Disp{
@@
 }
-\begin{enumerate}
+\startitemize[n]
+
 \I Definition and arrangement
 \I Can be shown with basic calculus
-\I Plug the previous eqn.\ into \(D\)
-\end{enumerate}
-\end{frame}
+\I Plug the previous eqn.\ into \m {}
 
-\begin{frame}
-\frametitle{Proof (2/3)}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Proof (2/3)}
 \Disp{
@@
 }
-\begin{enumerate}
+\startitemize[n]
+
 \I Straightforward by definition
@@
 \I Approximation of rectangle to integral
-\end{enumerate}
-\end{frame}
 
-\begin{frame}
-\frametitle{Proof (3/3)}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Proof (3/3)}
 \Disp{
@@
 }
-\begin{enumerate}
-\I Plug in above bound for \(D\)
+\startitemize[n]
+
+\I Plug in above bound for \m {}
 \I Calculation
-\I Drop the middle term (\(<0\)) and last term (small)
-\end{enumerate}
-\end{frame}
+\I Drop the middle term (\m {}) and last term (small)
 
-\begin{frame}
-\frametitle{Lemma (Tentative): \(\V{g}\) is Almost Sparse}
-Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\).
-Then \(\V{g}\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Lemma (Tentative): \m {} is Almost Sparse}
+Let \m {} and \m {} be uniformly, independently distributed in \m {}.
+Then \m {} is almost-\m {}-sparse with \m {}-residue \m {} to be
 \Disp{
@@
 }
-\end{frame}
 
-\begin{frame}
-\frametitle{Lemma: RIP Probability w.r.t.\ \(\d\)}
-Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
-Then \(P\) is RIP according to \(\d\) for at least probability
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Lemma: RIP Probability w.r.t.\ \m {}}
+Let \m {} be i.i.d.\ Radmacher, as defined in Lemma ().
+Then \m {} is RIP according to \m {} for at least probability
 \Disp{
@@
 {\small Source: Baraniuk, Davenport, DeVore, and Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices''}
-\end{frame}
 
-\begin{frame}
-\frametitle{The Main Bound}
-Let \(\V{d}\) be defined as above, then, for overwhelming probability
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {The Main Bound}
+Let \m {} be defined as above, then, for overwhelming probability
 \Disp{
@@
 }
-\end{frame}
 
-\begin{frame}
-\frametitle{Preparation for the Proof}
-\begin{itemize}
-\I Use \(s=L\) in our case
-\I Let \(\MC{A}\) be the index set of the largest \(L\) components of \(g\), \(\MC{B}\) be the index set of the largest \(L\) position of \(d\) except \(\MC{A}\), and \(\MC{C} =\{1, \dotsc, N_g\} -\MC{A}\)
-\I Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
-\I Denote \(\V{d} =\hat{\V{g}} -\V{g}\)
-\end{itemize}
-\end{frame}
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\begin{frame}
-\frametitle{Lemmata on Vector Supports}
-\begin{itemize}
-\I \( \|\V{d}\|_2^2 \leq \|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\dfrac{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \)
-\I \( \|\V{d}_{\MC{C}}\|_1 \leq \|\V{d}_{\MC{A}}\|_1 +2\|\V{g}_{C}\|_1 \)
-\begin{itemize}
-\item (modified to account nonzero \(\|\V{g}_{C}\|_1\))
-\end{itemize}
-\end{itemize}
+\Frametitle {Preparation for the Proof}
+\startitemize
+
+\I Use \m {} in our case
+\I Let \m {} be the index set of the largest \m {} components of \m {}, \m {} be the index set of the largest \m {} position of \m {} except \m {}, and \m {}
+\I Denote as \m {} the columns of \m {} having indices in \m {}.
+\I Denote \m {}
+
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Lemmata on Vector Supports}
+\startitemize
+
+\I \m {}
+\I \m {}
+\startitemize
+
+\I (modified to account nonzero \m {})
+
+\stopitemize
+
+\stopitemize
 {\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
-\end{frame}
 
-\begin{frame}
-\frametitle{Lemmata on RIP Matrix}
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Lemmata on RIP Matrix}
 For overwhelming probability,
-\begin{itemize}
-\I \( \|\V{d}_{\MC{AB}}\|_2 \leq \dfrac{1}{1-\d_{2L}} \left( \|\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}\|_2 +\dfrac{\d_{3L}}{\R{L}} \|\V{d}_{C}\|_1 \right) \)
-\I \( |\IP{ \V{z}, \M{P}(:, n_g) }| \leq 2 \R{\log N_g}, \quad n_g =1, \dotsc, N_g. \)
-\begin{itemize}
-\item (generalized from real case)
-\end{itemize}
-\I \( \|\M{P}^\H \M{P} \V{d}\|_\infty \leq 4 \R{\log N_g}, \quad n_g =1, \dotsc, N_g \)
-\begin{itemize}
-\item (generalized from real case)
-\end{itemize}
-\end{itemize}
+\startitemize
+
+\I \m {}
+\I \m {}
+\startitemize
+
+\I (generalized from real case)
+
+\stopitemize
+\I \m {}
+\startitemize
+
+\I (generalized from real case)
+
+\stopitemize
+
+\stopitemize
 {\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
-\end{frame}
 
-\begin{frame}
-\frametitle{Proof (1/4)}
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Proof (1/4)}
 \Disp{
@@
 }
-\begin{enumerate}
+\startitemize[n]
+
 \I Inclusion of larger support
-\I \(\ell_p\) norm inequality
-\I Plug in the Lemma for \(\|\M{P}^\Tr \M{P} \V{d}\|_2\)
-\end{enumerate}
-\end{frame}
+\I \m {} norm inequality
+\I Plug in the Lemma for \m {}
 
-\begin{frame}
-\frametitle{Proof (2/4)}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Proof (2/4)}
 \Disp{
@@
 }
-\begin{enumerate}
-\I \(\ell_p\) norm inequality
+\startitemize[n]
+
+\I \m {} norm inequality
 \I Inclusion of larger support
-\I Plug in the Lemma for \(\|\V{d}_{\MC{A}\MC{B}}\|_2\)
-\end{enumerate}
-\end{frame}
+\I Plug in the Lemma for \m {}
 
-\begin{frame}
-\frametitle{Proof (3/4)}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Proof (3/4)}
 \Disp{
@@
 }
-\begin{enumerate}
-\I Copy the Lemma for \(\| \V{d}_{\MC{C}} \|_1\)
-\I Plug in the previous eqn.\ for \(\| \V{d}_{\MC{A}} \|_1\)
+\startitemize[n]
+
+\I Copy the Lemma for \m {}
+\I Plug in the previous eqn.\ for \m {}
 \I Cancellation, simplification
-\end{enumerate}
-\end{frame}
 
-\begin{frame}
-\frametitle{Proof (4/4)}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Proof (4/4)}
 \Disp{
@@
 }
-\begin{enumerate}
-\I Copy the Lemma for \(\| \V{d} \|_2^2\)
-\I Plug in the Lemma for \(\|\V{d}_{\MC{A}\MC{B}}\|_2\)
-\I Plug in the Lemma for \(\|\V{d}_{\MC{C}}\|_1\), approximate using \(1 \ll L \ll N_g\), and \(\d_{2L} <\d_{3L} \ll 1\)
-\end{enumerate}
-\end{frame}
+\startitemize[n]
 
-\begin{frame}
-\frametitle{Conclusion}
-\begin{enumerate}
+\I Copy the Lemma for \m {}
+\I Plug in the Lemma for \m {}
+\I Plug in the Lemma for \m {}, approximate using \m {}, and \m {}
+
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Conclusion}
+\startitemize[n]
+
 \I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity
 \I We adopt The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm
-\I We generalized DS for complex vectors, and we carried it out in the spatial frequency domain \(g\)
-\I Analogous to original DS proof, we proved explicitly that the probability that the expected square error is bounded is overwhelming, where the bounding constant is an explicit function of \(L\), the number of path
-\end{enumerate}
-\end{frame}
+\I We generalized DS for complex vectors, and we carried it out in the spatial frequency domain \m {}
+\I Analogous to original DS proof, we proved explicitly that the probability that the expected square error is bounded is overwhelming, where the bounding constant is an explicit function of \m {}, the number of path
 
-\begin{frame}
-\frametitle{Future Work}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {Future Work}
 It remains to
-\begin{enumerate}
+\startitemize[n]
+
 \I Find the explicit ``overwhelming'' probability
@@
 \I Compare the probability bound with the simulation result
-\end{enumerate}
-\end{frame}
 
-\begin{frame}
-\frametitle{References}
-\begin{enumerate}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {References}
+\startitemize[n]
+
 { \small
@@
 \I S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-\I E J Cand\`es and J Romberg (2005), ``\(\ell_1\)-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
+\I E J Cand\`es and J Romberg (2005), ``\m {}-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
 }
 \setcounter{countRef}{\value{enumi}}
-\end{enumerate}
-\end{frame}
 
-\begin{frame}
-\frametitle{References}
-\begin{enumerate}
+\stopitemize
+
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\Frametitle {References}
+\startitemize[n]
+
 \setcounter{enumi}{\value{countRef}} { \small
 \I E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-\I E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \(p\) is Much Larger than \(n\)'', \textit{The Annals of Statistics}, Vol.35, No.6.
+\I E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \m {} is Much Larger than \m {}'', \textit{The Annals of Statistics}, Vol.35, No.6.
 \I J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
@@
 }
-\end{enumerate}
-\end{frame}
 
-% % % % % % % % % % % % % % % % % % % %
+\stopitemize
 
-\end{document}
-
-\begin{frame}
-\frametitle{Definition}
-For \(\MC{T}, \MC{T}' \subset \{1, \dotsc, N_p\}\), define the \(s, s'\)-restricted orthogonality constant \(\tau_{s,s'} >0\) to be the smallest such that
-%
-\Disp{
-| \IP{ P_{\MC{T}} h, P_{\MC{T}'} h' } |
-\leq \tau_{s, s'} \cdot \| h \|_2 \|h'\|_2
-}
-\end{frame}
-
-\begin{frame}
-\frametitle{Lemma: \(\d_{s+s'}\) Can Bound \(\tau_{s, s'}\)}
-Let \(P\) be given.
-Then \(\tau_{s, s'}\) is bounded in both direction as follows,
-\Disp{
-\d_{s+s'} -\max (\{\d_s, \d_{s'}\})
-\leq &\tau_{s, s'} \\
-\leq &\d_{s+s'}
-}
-{\small Source: Cand\`es and Tao (2005), ``Decoding by Linear Programming''}
-\end{frame}
+\stoptext

### 2019-05-28 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Finish: Almost-sparsity of

@@
 Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
-We seek to bound the ``rectangulars'' with an integral, and we have to split the cases that \m {N_H} is odd and even.
+We seek to bound the \quotation {rectangulars} with an integral, and we have to split the cases that \m {N_H} is odd and even.
 Anyway, a moment's reflection shows
@@
 \Nm {\a_l} \VNm {\V {a} \SB {\f_l}} _2
-\D \VNm {\V {a} \SB {\th_l}} _2 \NR[+]
+\VNm {\V {a} \SB {\th_l}} _2 \NR[+]
+}
+Lastly, we know \m {\ell_1}-norm is larger than \m {\ell_2}-norm.
+Since \m {\ell_1}-norm will be used in later proof, we display the statement about \m {\ell_1}-norm.
+\Disp{
+\NC \NC \MB {E} \SB {\VNm {\MC {C} \SB {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj}} _F} \NR
+\NC \leq \NC \F {1} {9 \R{N_H}} \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}} \NR
+\NC \leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR[+]
 }
 
-Lastly, we know \m {\ell_1}-norm is larger than \m {\ell_2}-norm.
-Since \m {\ell_1}-norm will be used in later proof, we display the statement about \m {\ell_1}-norm.
-
 \Result
-{Lemma (Tentative)}
+{Lemma}
 {
@@
 \NC R
-\leq \NC 2L \NR
+\leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR
 }
@@
    -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
-\NC \NC \Q \Q +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
+\NC \NC \FourQ +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
       \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
@@
 
-From ``Decoding from Linear Programming'' (Cand\`es and Tao 2005), Lemma 1.1:
+From \quotation {Decoding from Linear Programming} (Cand\`es and Tao 2005), Lemma 1.1:
 
@@
 \NC = \NC \MB{E} \SB {\M{W}^\Adj \DB {n_Y, n_H} \M{W}^\Adj \DB {n_Y', n_H'}} \NR
-\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR
+\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR[+]
 }
@@
 \RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H, n_R} \M{F}_B \DB {n_R, n_Y}}
-\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H', n_R} \M{F}_B \DB {n_R, n_Y'}} \NR
+\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H', n_R} \M{F}_B \DB {n_R, n_Y'}} \NR[+]
 }
@@
 \Disp {
-\NC \NC \MB{E} \SB {\M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'} \M{F} \DB {n_H, n_Y} \M{F} \DB {n_H, n_Y}} \NR
-\NC = \NC \MB{E} \SB {\RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y, n_H} \RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y', n_H'}} \NR
-\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR
+\NC \NC \MB{E}
+\SB {
+\M{F} \DB {n_H, n_Y}
+\M{F} \DB {n_H', n_Y'}
+\M{F} \DB {n_H'', n_Y''}
+\M{F} \DB {n_H''', n_Y'''}
+} \NR
+\NC \NC =\MB{E}
+\SB {
+\M{W} \DB {n_Y, n_H}
+\M{W} \DB {n_Y', n_H'}
+\M{W} \DB {n_Y'', n_H''}
+\M{W} \DB {n_Y''', n_H'''}
+} \NR
+\NC = \NC
+\i_4 \SB {n_H, n_H', n_H'', n_H'''}
+\D \i_4 \SB {n_Y, n_Y', n_Y'', n_Y'''}
+\D 2 N_R^2 \l_R^4 \l_B^4 \NR
+\NC \NC \FourQ +\i_{2,2} \SB {n_H, n_H', n_H'', n_H'''}
+\D \i_{2,2} \SB {n_Y, n_Y', n_Y'', n_Y'''}
+\D N_R^2 \l_R^4 \l_B^4 \NR[+]
 }
@@
 
-Having this in mind, a moment's reflection shows
+A moment's reflection shows
 \Result
@@
 \Disp {
-\NC \NC \MB{E} \SB {\M{Q} \DB {n_Y, n_H} \M{Q} \DB {n_Y', n_H'}} \NR
-\NC = \NC \startcases
-N_R \l_R^2 \l_B^2, \Q \MC n_Y =n_Y', n_H =n_H' \NR
-0, \Q \NC \Rm {otherwise} \NR
-\stopcases \NR
+\NC \NC \MB{E} \SB {\M{P} \DB {n_h, n_y} \M{P} \DB {n_h', n_y'}} \NR
+\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR[+]
 }
@@
 
+More trickily, but by the same idea,
 \Result
@@
 \Disp {
-\NC \NC \MB{E} \SB {\M{Q} \DB {n_Y, n_H} \M{Q} \DB {n_Y', n_H'}} \NR
-\NC = \NC \startcases
-N_R^2 \l_R^4 \l_B^4, \Q \MC n_Y =n_Y', n_H =n_H' \NR
-0, \Q \NC \Rm {otherwise} \NR
-\stopcases \NR
+\NC \NC \M{F} \DB {n_h, n_y}
+\M{F} \DB {n_h', n_y'}
+\M{F} \DB {n_h'', n_y''}
+\M{F} \DB {n_h''', n_y'''} \NR
+\NC = \NC
+\i_4 \SB {n_H, n_H', n_H'', n_H'''}
+\D \i_4 \SB {n_Y, n_Y', n_Y'', n_Y'''}
+\D 4 N_R^4 \l_R^8 \l_B^8 \NR
+\NC \NC \FourQ +\i_{2,2} \SB {n_H, n_H', n_H'', n_H'''}
+\D \i_{2,2} \SB {n_Y, n_Y', n_Y'', n_Y'''}
+\D N_R^4 \l_R^8 \l_B^8 \NR[+]
 }
@@
    } \NR
-\NC \NC \Q \Q +\sum_{n_y=0}^{N_y-1}
+\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
   \MB{E}
@@
 \NR
-\NC \NC \Q \Q +\sum_{n_y=0}^{N_y-1}
+\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
    \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
@@
 \Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D 4 N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
-\NC \NC \Q \Q + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
+\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
+\NC \NC \FourQ + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
 \NC \leq \NC 4 \VNm {\V{u}} _2 ^4 \NR[+]
@@
 \Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D 4 N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
+\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
 \NC \leq \NC 4 N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
@@
 \Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D 4 N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
+\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
 \NC \leq \NC 4 N_H ^2 N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
@@
 The last one is more complicated.
-We need a corollary that follows from ``Muirhead inequality''.
+We need a corollary that follows from \quotation {Muirhead inequality}.
 \Result
@@
 \V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \NR
-\NC \leq \NC \RB {1/6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
+\NC \leq \NC \F{1}{6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
 }
@@
   \V{u} \DB{m_h'} \NR
-\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \D 4 N_Y ^{-4} \NR
+\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \D N_Y ^{-4} \NR
 \NC \NC \SixQ
@@
 \Nm {\V{u} \DB{m_h'}} \NR
-\NC \leq \NC \F{1}{3} N_Y ^{-1} N_H ^4 \VNm {\V{u}} _2 ^4. \NR[+]
+\NC \leq \NC \F{1}{6} N_Y ^{-1} N_H ^4 \VNm {\V{u}} _2 ^4. \NR[+]
 }
@@
 
-The rest follows ``The Dantzig Selector'' very closely.
+The rest follows \quotation {The Dantzig Selector} very closely.
 The generalization to complex vector is necessary in our setting.
@@
 
-From ``Dantzig Selector'' Lemma 1, first equation, we have the result as below.
+From \quotation {Dantzig Selector} Lemma 1, first equation, we have the result as below.
 The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
@@
 
-From ``Dantzig Selector'', Lemma 1, second equation, we have the result as below.
+From \quotation {Dantzig Selector}, Lemma 1, second equation, we have the result as below.
 Again, their proof works with complex vector spaces in place of real ones too.

### 2019-05-29 dantzig_selector/report/3_theorems_and_proofs.tex
Proof: Finish DS error bound

@@
 }
+
 Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
 \Disp {
-\NC \Nm {D \SB {\psi'} }
+\NC \Nm {D \SB {\psi'}}
 = \NC \F {\Nm {\sin \SB {N_H \psi'/2}}}{\Nm {\sin \SB {\psi' /2}}} \NR
@@
 
-\startsection [title={Restricted Isometry of \m {P}}]
+\startsection [title={Confirming the Restricted Isometry of \m {P}}]
 
@@
 \Disp {
-\NC \d_{s+s'} \SB {\M{P}} -\max \SB {\CB {\d_s \SB {\M{P}}, \d_{s'} \SB {\M{P}} }}
+\NC \d_{s+s'} \SB {\M{P}} -\max \SB {\CB {\d_s \SB {\M{P}}, \d_{s'} \SB {\M{P}}}}
 \leq \NC \tau_{s, s'} \SB {\M{P}} \NR
@@
 The last one is more complicated.
-We need a corollary that follows from \quotation {Muirhead inequality}.
-\Result
-{Lemma}
-{
-If every component of \m {\V{u} \in \MB {M}_{\MB {C}} \SB {N_h}} is considered as a free variable taking complex values, then
+Use the shorthand
 \Disp {
-\NC \NC \sum \i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'}
-\V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \NR
-\NC \leq \NC \F{1}{6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
-}
-}
-
-Now,
-\Disp {
-\NC E_5
-\NC = \sum _{
+\NC \sum _{n_h, n_h', m_h, m_h'} ^\star
+:= \NC \sum _{
    \Stack {
@@
 } ^{N_H-1}
-  \sum _{\Stack { 0 =n_y <n_y' \NR \Fl {n_y/N_Y} =\Fl {n_y'/N_Y} }} ^{N_y-1} \NR
-  \NC \NC \SixQ
+\sum _{
+  \Stack {
+     0 =n_y <n_y' \NR
+     \Fl {n_y/N_Y} =\Fl {n_y'/N_Y}
+  }
+} ^{N_y-1} \NR
+\NC \V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'}
+:=\NC \i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'}
+\V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \NR
+}
+Then observe
+\Disp {
+\NC \NC \sum _{n_h, n_h', m_h, m_h'} ^\star
+\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
+\NC \leq \NC N_h^{-2}
+\sum_{n_h, n_h' =0} ^{N_h-1}
+\sum_{m_h, m_h' =0} ^{N_h-1}
+\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
+}
+This is because one of \m {n_h, n_h'} and one of \m {m_h, m_h'} may both choose to lie in other \m {\RB {N_H-1} \RB {N_H-2}} blocks (of length \m {N_H}).
+Then we need a corollary that follows from \quotation {Muirhead inequality}.
+\Result
+{Lemma}
+{
+If every component of \m {\V{u} \in \MB {M}_{\MB {C}} \SB {N_h}} is considered as a free variable taking complex values, then
+\Disp {
+\NC \NC \sum_{n_h, n_h' =0} ^{N_h-1}
+\sum_{m_h, m_h' =0} ^{N_h-1}
+\Nm {\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'}} \NR
+\NC \leq \NC \F{1}{6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
+}
+}
+
+Now,
+\Disp {
+\NC E_5
+= \NC \sum _{n_h, n_h', m_h, m_h'} ^\star
   \M{Q} \DB {n_y, n_h}
@@
 \NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \D N_Y ^{-4} \NR
-\NC \NC \SixQ
-\D \sum_{n_h, n_h' =0} ^{N_H-1}
-\sum_{m_h, m_h' =0} ^{N_H-1}
-\i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \NR
-\NC \NC \SixQ
-\Nm {\V{u} \DB{n_h}}
-\Nm {\V{u} \DB{n_h'}}
-\Nm {\V{u} \DB{m_h}}
-\Nm {\V{u} \DB{m_h'}} \NR
-\NC \leq \NC \F{1}{6} N_Y ^{-1} N_H ^4 \VNm {\V{u}} _2 ^4. \NR[+]
+\NC \NC \FourQ
+\D N_H^{-2} \sum_{n_h, n_h' =0} ^{N_h-1} \sum_{m_h, m_h' =0} ^{N_h-1}
+\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
+\NC \leq \NC \F{1}{6} N_Y ^{-1} \VNm {\V{u}} _2 ^4. \NR[+]
 }
 
-In conclusion,
+In conclusion, \m {E_4} dominates.
 \Disp{
 \NC \Ss{Var} \SB {\VNm {\M{P} \SB {\o_t, \o_r} \V{u}} _2 ^2}
-\leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
+\leq \NC 4 N_H^2 N_Y^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
 }
@@
 \Result
-{Lemma}
+{Theorem}
 {
@@
 }
-\leq \NC \F {1} {2\e^2} \NR[+]
+\leq \NC \F {1} {\e^2} N_H^2 N_Y^{-3} \NR[+]
 }
@@
 {
-Let \m {\M{F}_B ^\Tr} be found as above.
-Suppose the probability that RIP holds for \m {\M{F}_B} w.r.t.\ \m {\d_s} is \m {P}, then
+Suppose the probability, according to event space \m {\o_t, \o_r}, that RIP holds for \m {\M{P}} w.r.t.\ \m {\d_s} is \m {p}, then
 \Disp{
-\NC 1 -P
-\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} \NR[+]
+\NC 1 -p
+\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} N_H^2 N_Y^{-3} \NR[+]
 }
@@
 
-\startsection [title={Restricted Isometry of \m {P}}]
+\startsection [title={Expected Error Analysis for Complex-Case Dantzig Selector}]
 
-The relevent expressions for \m {\M{F}_B ^\Tr} and \m {\M{F}_R ^\Tr} are identical, and same can be said of \m {\M{W}_B} and \m {\M{W}_R}.
-Let \m {\Phi} be either of \m {\M{R}_B ^\Tr}, \m {\M{R}_R ^\Tr}, \m {\M{W}_B}, or \m {\M{W}_B}.
-By Chebyshev bound, we obtain an identical expression,
-\Result
-{Lemma}
-{
-Let \m {\Phi} be generated randomly as above.
-Then, for any fixed complex \m {\V{u}} (with corresponding dimension), and for any \m {\e >0},
-\Disp{
-\NC \MB{P}
-\SB {
-  \Nm {\VNm {\Phi \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
-  \geq \e \VNm {\V{u}} _2 ^2
-}
-\leq \NC \F {1} {2\e^2} \NR[+]
-}
-}
-
-According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), substitution of relevent quantities yields
-\Result
-{Lemma}
-{
-Suppose the probability that RIP holds for \m {\V{P}} w.r.t.\ \m {\d_s} is \m {p}, then
-\Disp{
-\NC 1 -p
-\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} \NR[+]
-}
-}
-
-\stopsection
-
-\startsection [title={Expected Error for Complex-Case Dantzig Selector}]
-
-Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {s} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {s} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {s=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
+Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {S} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {S} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
 We rephrase it formally.
@@
 
-Let \m {s \leq N_p/2} be fixed.
+Let \m {S \leq N_p/2} be fixed.
 Define
 \Disp{
-\NC \MC {S} \SB {\V{x}, s}
-=\NC \sum_{i=0} ^{s-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
-\NC \MC {C} \SB {\V{x}, s}
-=\NC \sum_{i=s} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
+\NC \MC {S} \SB {\V{x}, S}
+=\NC \sum_{i=0} ^{S-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
+\NC \MC {C} \SB {\V{x}, S}
+=\NC \sum_{i=S} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
 }
@@
 \NC \V{g} _\MC {A}
-=\NC \MC {S} \SB {\V{g}, s} \NR[+]
+=\NC \MC {S} \SB {\V{g}, S} \NR[+]
 \NC \V{g} _\MC {K}
-=\NC \MC {C} \SB {\V{g}, s} \NR[+]
+=\NC \MC {C} \SB {\V{g}, S} \NR[+]
 \NC \V{g} _\MC {B}
-=\NC \MC {S} \SB {\V{g} _\MC {K}, s} \NR[+]
+=\NC \MC {S} \SB {\V{g} _\MC {K}, S} \NR[+]
 }
@@
 \Disp {
-\NC \Nm {\IP { \V {z} \SB {\o_z}, \M {P} \DB {:, n_g} }}
+\NC \MB {E} \SB {\Nm {\IP {\V {z} \SB {\o_z}, \M {P} \DB {:, n_h}}}}
 \leq \NC  2 \R {\log N_h} \NR
-\NC n_g 
+\NC n_h 
 =\NC 1, \ldots, N_h. \NR
 }
-with probability \m {\geq 1 -N_h}.
+with probability \m {\geq 1 -N_h^{-1}}.
 }
 
-This only depends on the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
+Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
 
@@
 {
-With the condition that \m {\M {P}} satisfies RIP for \m {\d_s \SB {\M{P}}},
+With the condition that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M{P}}},
 \Disp {
@@
 }
-with probability \m {\geq 1 -N_h}.
+with probability \m {\geq 1 -N_h^{-1}}.
 }
@@
 \Disp {
-\NC \IP { \V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y} }
-= \NC \IP { \M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y} } \NR
-\NC = \NC \IP { \M {P} \V {d}, \M {P} \DB {:,n_y} } \NR
+\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
+= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y}} \NR
+\NC = \NC \IP {\M {P} \V {d}, \M {P} \DB {:,n_y}} \NR
 }
@@
 \Disp {
-\NC \VNm { \M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty
-\leq \NC \VNm { \M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty \NR
+\NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
+\leq \NC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty \NR
 \NC \leq \NC 2\R {\log N_h} \NR
@@
 \NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
-\leq \NC \VNm {\IP { \V {z}, \M {P} \DB {:,n_y} }} _\infty
-+\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y} } \NR
+\leq \NC \VNm {\IP {\V {z}, \M {P} \DB {:,n_y}}} _\infty
++\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y}} \NR
 \NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
@@
 {
-With the condition that \m {\M {P}} satisfies RIP for \m {\d_s \SB {\M{P}}},
+With the condition that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M{P}}},
 \Disp {
 \NC \VNm {\V {d} _{\MC {AB}}} _2
-\leq \NC \F {1}{1-\d_{2s}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{\MC {K}}} _1 \NR
+\leq \NC \F {1}{1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}}{\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {K}}} _1 \NR
 }
@@
 \NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{s} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
+\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{S} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
 }
@@
 
-\startsection [title={The Main Bound}]
+\startsection [title={The Main Result}]
 
-We can now formulate and prove the main bound of ours.
+We are going to put things together and show the main result.
+In accordance with (), set
+\Disp{
+\NC S
+=\NC s^2 L \NR
+}
 
@@
 Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
-Then
+Then, with \m {S =s^2 L}, as \m {N_H \to \infty},
 \Disp {
 \NC \VNm {\V {d}} _2
-\leq \NC \F {4}{\pi^4} \d_{3L}^4 \RB {1-2\d_{2L}} L^4 \RB { \log N_H}^4 \NR
+\leq \NC \F {4}{\pi^4} \d_{3S}^4 \RB {1-2\d_{2S}} S^4 \RB {\log N_H}^4 \NR
 }
-with probability \m {\geq 1 -N_h}.
 }
@@
 \leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
-\NC \leq \NC \R {N_h} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
-\NC \leq \NC 4 \R {N_h \log N_h} \NR
+\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
+\NC \leq \NC 4 \R {S \log N_h} \NR
 }
-Thus, by virtue of Lemma (),
+Thus, by virtue of Lemma (), and approximating \m {1 /(1 -\d_{2S}) =1 +\d_{2S}} and so on,
 \Disp {
-\NC \VNm { \V {d}_{A} } _1
-\leq \NC \R {L} \VNm { \V {d}_{A} } _2 \NR
-\NC \leq \NC \R {L} \VNm { \V {d} _{\MC {AB}} } _2 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d} _{\MC {K}} } _1 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
+\NC \VNm {\V {d}_{\MC {A}}} _1
+\leq \NC \R {S} \VNm {\V {d}_{\MC {A}}} _2 \NR
+\NC \leq \NC \R {S} \VNm {\V {d} _{\MC {AB}}} _2 \NR
+\NC \leq \NC \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
++4 \RB {1+\d_{2S}} S \R {\log N_h} \NR
 }
 
-As the next step, we must eliminate \m {\VNm {d _{\MC {A}}} _1} in rhs of Lemma ().
+Next, we must eliminate \m {\VNm {d _{\MC {A}}} _1} in rhs of Lemma ().
 \Disp {
-\NC \VNm { \V {d} _{\MC {K}} } _1
-\leq \NC \VNm { \V {d} _{\MC {A}} } _1 +2 \VNm { \V {g} _{\MC {K}} } _1 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d} _{\MC {K}} } _1
-+2 \VNm { \V {g} _{\MC {K}} } _1
-+\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
+\NC \VNm {\V {d} _{\MC {K}}} _1
+\NC \leq \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
++4 \RB {1+\d_{2S}} S \R {\log N_h}
++2 \VNm {\V {g} _{\MC {K}}} _1 \NR
 }
-Or,
+Arranging and drop second order small terms like \m {\d_{2S} \d_{3S}}, that is,
 \Disp {
-\NC \VNm { \V {d} _{\MC {K}} } _1
-\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g} _{\MC {K}} } _1
-+\F {4} {1-\d_{2L} -\d_{3L}} \R {L N_h \log N_h} \NR
+\NC 1 \ll \NC S \NR
+\NC \ll \NC N_h \NR
+}
+doing this we have
+\Disp {
+\NC \VNm {\V {d} _{\MC {K}}} _1
+\leq \NC 2 \RB {1+\d_{3S}} \VNm {\V {g} _{\MC {K}}} _1
++4 \RB {1+2\d_{3S}} S \R {\log N_h} \NR
 }
 
-We are ready to bound \m {\VNm {d} _2^2}.
-Using Lemma () again, we have
+We are now in a position to bound \m {\VNm {d} _2^2}.
+Using Lemma () again, and only keeping to first order, we have
 \Disp {
-\NC \VNm { \V {d} } _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
-\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d} _{\MC {K}}} _1^2
-+\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_h \log N_h} \VNm {\V {d} _{\MC {K}}} _1 \NR
-\NC \NC \Q +\F {16}{\RB {1-\d_{2L}}^2} N_h \log N_h \NR
+\NC \VNm {\V {d}} _2^2
+\leq \NC 16 S \log N_h
++8 \d_{3S} \R {\log N_h} 
++\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {K}}} _1 \NR
 }
 Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {K}}} _1}.
-There are several dozens of terms if we expand all.
-but for simplicity, we keep only the leading term under the approximation
-\Disp {
-\NC 1 \ll \NC L \NR
-\NC \ll \NC N_h \NR
-}
-And expand to the first order expressions containing \m {\d_{2L}} or \m {\d_{3L}} in the denominator using
-\Disp {
-\NC \d_{2L} <\NC \d_{3L} \ll 1. \NR
-}
-Then
+Again for simplicity, we keep only the first order small terms.
+Plug in \m {S =s^2 L} and \m {N_h =N_H^2} we get, finally,
 \Disp {
 \NC \VNm {\V {d}} _2^2
-\leq \NC \F {4}{\pi^4} \d_{3L}^4 \RB {1-2\d_{2L}} L^4 \RB { \log N_H}^4 \NR
+\leq \NC 32 s^2 L \log N_H
++\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
++\F {\pi} {9} \F {L} {s^2 N_H} \NR
+}
+In particular for asymptotic \m {N_H \gg 1}, keep only the dominating term.
+\Disp {
+\NC \VNm {\V {d}} _2^2
+\leq \NC 32 s^2 L \log N_H \NR
 }
 
-\color[red]{(To be done)}
+The probability that it is true may be bounded by the number in Lemma () and Lemma ().
+Bounding generously with \m {\d_s \leq 1} yields
+\Disp {
+\NC 1 -p
+\leq \NC 4 \D 12^S N_H^2 N_Y^{-3} +N_H^{-2} \NR[+]
+}
+If \m {N_Y \leq N_H}, there is a condition imposed on the size of \m {N_H}.
+Arranging gives
+\Disp {
+\NC \log N_H
+\geq \NC s^2 L \log 12 + \log 4 \NR[+]
+}
+
+\Result
+{Theorem}
+{
+Theorem is meaningful only when
+\Disp {
+\NC N_H
+\geq \NC 4 \D {12}^{s^2 L} \NR[+]
+}
+}
+
+\stopsection
 

### 2019-05-29 dantzig_selector/presentation/1_slide.tex
Slides: Finish: Problem setting

--- 2019-05-28 dantzig_selector/presentation/main.tex
@@
-\input {./preamble.tex}
+\blank [big, force]
 
-\starttext
-
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\blank [big, force]
 \Title {Dantzig Selector \\ Applied on mm-Wave MIMO: \\ Part I. Expected Error Analysis}
 \blank [big]
+
 \Subtitle {Presenter: Tzu-Yu Jeng \\ Advisor: Prof.\ H.J.\ Su}
 \blank [big]
+
 \Subsubtitle{May 30, 2019}
@@
 
-\page[yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
 
-\Frametitle {Organization}
+\Frame {Organization}
+{
+\I Problem Configuration Proposed Method
 
-\startitemize
-\I Problem Configuration Proposed Method
 \I Sparsity of Angular Channel Matrix
+
 \I Concentration Inequality of \m {\M{P}}
+
 \I Restricted Isometry of \m {\M{P}}
+
 \I Expected Error of Dantzig Selector
+
 \I Conclusion and Future Work
+
 \I References
-\stopitemize
+}
 
@@
 
-\stoptext
+\Frame {Background}
+{
+\I Multiple-input-multiple-output (MIMO) wireless communication is expected to be the next-generation r\'egime
 
-\Frametitle {Background}
-\startitemize
+\I But channel response has to be known at the receiver to facilitate applications like beamforming and channel calibration
 
-\I Multiple-input-multiple-output (MIMO) wireless communication is widely expected to be the next-generation communication scheme
-\I But reliable communication requires that the channel response be known at the receiver to facilitate, say, beamforming algorithm and channel calibration
 \I And in the MIMO system, estimating wireless channels calls for high complexity
+
 \I Meanwhile, in the millimeter wave r\`egime, which is often used together with MIMO, channel often exhibits sparse properties
+
 \I If the sparsity is exploited, can few observations suffice to estimate the channel?
-
-\stopitemize
+}
 
@@
 
-\Frametitle {Compressive Sensing}
-\startitemize
+\Frame {Compressive Sensing}
+{
+\I Such case of channel estimation is facilitated by advances of so-called compressed sensing (CS)
 
-\I Recent developement on channel estimation is facilitated by advances of so-called compressed sensing (CS)
-\I CS addresses the common situation in statsitical applications that the number of model parameters \m {} the number of measurements \m {}.
-\I With insufficient (possibly noisy) measurements, how well can we recover all \m {} parameters?
-Of course, more assumption must be made.
+\I CS addresses the situation that the number of model parameters \m {N_p} the number of measurements \m {N_m}.
+
+\I With insufficient (possibly noisy) measurements, under what circumstances can we recover all \m {N_p} parameters?
+
 \I Work on CS reveals that few observations of the signal may be sufficient for us to resonstruct the signal when it is sparse.
-\I In the advent, Cand\`es and Tao (2006) proposes the Dantzig Selector (DS).
-It was first applied in channel estimation context
 
-\stopitemize
+\I In the advent, Cand\`es and Tao (2006) proposes the Dantzig Selector (DS) as an possible answer.
+}
 
@@
 \Frametitle {Notation}
-\startitemize
 
-\I \m {} denotes vectors
-\I \m {} denotes matrices
-\I \m {} refers to either \m {} or \m {}.
-\I \m {} is the Hilbert space \m {} over \m {}
-\I \m {} is the collection of \m {} by \m {} matrices.
-\I \m {} denotes the \m {}-norm of \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Definitions: Sparsity}
-\startitemize
-
-\I Suppose \m {}.
-Let \m {}.
-Denote as \m {} the columns of \m {} having indices in \m {}.
-\I \m {} is called \m {}-sparse with support \m {}, \m {}, if only at most \m {} components of \m {} is nonzero.
-\I (New def.) We say \m {} is almost-\m {}-sparse with \m {}-residue \m {}, if \m {} where \m {} is sorted in magnitude.
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Program: The Dantzig Selector}
-Let \m {} and \m {} be given, and \m {} be fixed.
-Find \m {} with
-\Disp{
-\hat{\V{h}} =\min_{\V{h}'} \quad &\|\V{h}'\|_1 \\ \NT
-\RM{subject}\; \RM{to} \quad &\|\M{P}^\H (\M{P} \V{h'} -\V{y})\|_\infty \leq \gamma
+{\tfx
+\starttable[|l|l|l|] \HL
+\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
+\NC \m {f \SB {x}} \VL square brackets \VL only for arguments \AR \HL
+\NC \m {\V {a}} \VL vector \VL  \AR \HL
+\NC \m {\M {A}} \VL matrix \VL  \AR \HL
+\NC \m {\V {a} \DB {n}} \VL \m {n}-th component of \m {\V {a}} \VL  \AR \HL
+\NC \m {\M {A} \DB {m,n}} \VL \m {m,n}-th entry of \m {\M {A}} \VL  \AR \HL
+\NC \m {\MB {V}_{\MB {K}} \SB {N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL \m {\MB {K} =\MB {R}} or \m {\MB {C}} \AR \HL
+\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
+\NC \m {\MB {M}_{\MB {K}} \SB {M,N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
+\stoptable
 }
 
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Performance Guarantee of DS}
-\startitemize
-
-\I Now, consider a linear transformation with noise corruption,
-\Disp{
-\V{y} =\M{P} \V{h} + \V{z}
-}
-where \m {} is i.i.d.\ standard Gaussian.
-
-\I They showed that the mean square error \m {} is bounded with overwhelming probability.
-
-\I Furthermore, this \m {}-minimization problem with \m {}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Definition: Restricted Isometry Property}
-\startitemize
-
-\I Consider \m {}, with unity-\m {}-norm columns.
-For \m {}, we say that \m {} satisfies the restricted isometry property (RIP) of sparsity \m {} with respect to \m {}, if, for all \m {}-sparse \m {}, for all \m {} with \m {},
-%
-\Disp{
-(1-\d_s) \|\V{x}\|^2
-\leq \|P_{\MC{T}} \V{x}\|_2^2
-\leq (1+\d_s) \|\V{x}\|_2^2
-}
-\I RIP is essentially saying that \m {} is ``almost unitary'' up to ``relative error'' \m {}.
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Orthogonal Matching Pursuit}
-\startitemize
-
-\I Afterwards, scholars (Tropp and Gilbert 2007b) proposed a greedy algorithm called Orthogonal Matching Pursuit (OMP)
-\I Here, we pick up the columns of the sensing matrix \m {} greedily, hoping to correspond to the support of \m {}, thus recovering the original signal.
-\I An i.i.d.\ random sensing matrix may perform sufficiently well, and may even recover the original signal in an overwhemingly probability too.
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Recent Literature on Compressive Channel Sensing}
-\startitemize
-
-\I Scholars has since favored OMP rather than DS, let alone other sparse algorithm, without clear justification
-\I Previous work simply assumes the norm of the channel matrix is bounded in some way, and dependency on the sparsity of the channel parameters is unknown
-\I OMP's requirement on the sensing matrix (elementwise i.i.d.\ Gaussian) seems to be more restrictive than DS's (RIP)
-\I The quantization of angle in generating may be a problem, and that is difficult to analyze in OMP's setting
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Our Work}
-\startitemize
-
-\I We will use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
-\I We will show an explicit bound, where the sparsity of the virtual channel matrix is depends explicitly on the number of paths of the channel.
-\I Bounding the beamspace sparsity, accordingly the concern of quantization error of the virtual channel's phase angle has been incorporated in our proof of the bound.
-\I We will derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Channel Model}
-\startitemize
-
-\I The response of uniform linear array is
-\Disp{
-\V{a} (\psi')
-=\F{1}{\R{N_H}} \sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
-\in \MB{V}_\MB{C} (N_H)
-}
-\I Let the virtual angle of departure and arrival be defined as thus to simplify expression
-\Disp{
-\f_l =\dfrac{d_{\RM{arr}}} {\lambda} \sin \f_l', \quad \th_l =\dfrac{d_{\RM{arr}}} {\lambda} \sin \th_l'
-}
-\I Let there be \m {} paths.
-The channel matrix is, then,
-\Disp{
-H
-=\sum_{l=0}^L \alpha_l \V{a} (\f_l) \V{a} (\th_l)^\H
-\in \MB{M}_\MB{C} (N_H, N_H)
-}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Precoder Setting}
-\startitemize
-
-\I We consider the hybrid configuration at both transmitter and receiver end.
-In the transmitter end, there are digital precoder \m {} and analog precoder \m {}.
-In the receiver end, there are digital combiner \m {} and analog combiner \m {}.
-\Disp{
-\M{F}_B \in &\MB{M}_{\MB{C}} (N_R, N_Y) \\
-\M{F}_R \in &\MB{M}_{\MB{C}} (N_H, N_R) \\
-\M{W}_R \in &\MB{M}_{\MB{C}} (N_R, N_H) \\
-\M{W}_B \in &\MB{M}_{\MB{C}} (N_Y, N_R)
-}
-\I Recall the constraint of magnitude for analog precoders:
-\Disp{
-|\M{F}_R (n_h, n_r)| =1, \quad |\M{W}_R (n_r, n_h)| =1, \\
-n_h =1, \dotsc N_H, \quad n_r =1, \dotsc N_R \NT
-}
-\I We also assume
-\Disp{
-N_Y \ll N_R \ll N_H
-}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Effective Channel}
-\startitemize
-
-\I We have the effective channel \m {}
-\I We may estimate \m {} with \m {}, \m {}, using pilog signal as unit vectors \m {}.
-\I It remains to recover \m {} with knowledge of \m {}, while \m {}, \m {}, \m {}, and \m {} are in our control
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Vectorization}
-Previous literature usually approaches the problem as
-\Disp{
-\V{h}
-:= &\RM{vec} (\M{H})
-\in \MB{V}_{\MB{C}} (N_g) \\
-\V{y}
-:= &\RM{vec} (\M{Y})
-\in \MB{V}_{\MB{C}} (N_y) \\
-\V{z}^\star
-:= &\RM{vec} (\M{Z})
-\in \MB{V}_{\MB{C}} (N_y) \\
-\M{P}^\star
-:= &(\M{F}_R^\Tr \M{F}_B^\Tr) \otimes (\M{W}_B \M{W}_R)
-\in \MB{M}_{\MB{C}} (N_y, N_g).
-}
-and for short we set \m {} and \m {},
-so that
-\Disp{
-\V{y} =\M{P}^\star \V{h} +\V{z}^\star
-}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Beamspace Channel Representation}
-Let \m {} be the DFT matrix.
-If we write \m {}, i.e.\ the beamspace (i.e., spatial frequency domain) representation of \m {}, then
-\Disp{
-\M{Y}
-:=&\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
-\in \MB{M}_{\MB{C}} (N_Y, N_Y) \\
-\M{P}
-:=&(\M{F}_B^\Tr \M{F}_R^\Tr \M{K}^\ast) \otimes (\M{W}_B \M{W}_R \M{K})
-\in \MB{M}_{\MB{C}} (N_y, N_g)
-}
-where accordingly
-\Disp{
-\V{g} := &\RM{vec} (\M{G}) \in \MB{M}_{\MB{C}} (N_g) \\
-\V{z} := &\RM{vec} (\M{K}^\H \M{Z}) \in \MB{V}_{\MB{C}} (N_y)
-}
-so that
-\Disp{
-\V{y}
-=\M{P} \V{g} +\V{z}
-}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proposed Program}
-\startitemize
-
-\I Let \m {} be given.
-Then, with parameter \m {} specified, find
-%
-\Disp{
-\hat{\V{g}}
-=\min_{\V{g}'} &\|\V{g}'\|_1 \quad \\
-\RM{subject}\; \RM{to}\quad
-&\|\M{P}^\H (\V{y} -\M{P} \V{g}')\|_\infty \leq \gamma
-}
-\I And convert \m {} back to matrix form as
-\Disp{
-\hat{G} =\RM{vec}^{-1} (\hat{g})
-}
-\I And finally recover the estimated \m {} in the space domain as
-\Disp{
-\hat{\M{H}} =\M{K} \hat{\M{G}} \M{K}^\H.
-}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Lemma: \m {} is Almost Sparse}
-For arbitrary \m {}, for \m {}, \m {} is almost-\m {}-sparse with \m {}-residue \m {} to be
-\Disp{
-R
-   \leq \F{1}{\pi} \log \F{N_H}{L}.
-}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (1/3)}
-\Disp{
-D (\f')
-:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} \right|
-=\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|} \\
-\left| x -\F{x^3}{6} \right|
-\leq &\sin x, \quad -\pi \leq x \leq \pi \\
-\left| D (\f') \right|
-= &\F{48}{|\f'^2 -24| |\f'|}
-}
-\startitemize[n]
-
-\I Definition and arrangement
-\I Can be shown with basic calculus
-\I Plug the previous eqn.\ into \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (2/3)}
-\Disp{
-\M{K}^\H \V{a}(\f) (k)
-=&\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right) \\
-R(\eta)
-:=&\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right) \\
-R(\eta) -\F{2\pi} {N_H}
-\leq &\F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
-}
-\startitemize[n]
-
-\I Straightforward by definition
-\I Definition
-\I Approximation of rectangle to integral
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (3/3)}
-\Disp{
-R(\f)
-\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
-+\F{2\pi} {N_H} \NT \\
-=&\F{1}{\pi} \log \F{2\pi N_H}{L}
--\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
-+\F{2\pi} {N_H} \\
-\leq &\F{1}{\pi} \log \F{N_H}{L}.
-}
-\startitemize[n]
-
-\I Plug in above bound for \m {}
-\I Calculation
-\I Drop the middle term (\m {}) and last term (small)
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Lemma (Tentative): \m {} is Almost Sparse}
-Let \m {} and \m {} be uniformly, independently distributed in \m {}.
-Then \m {} is almost-\m {}-sparse with \m {}-residue \m {} to be
-\Disp{
-R
-\leq \F{L}{\pi^2} \left( \log \F{N_H}{L} \right)^2
-}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Lemma: RIP Probability w.r.t.\ \m {}}
-Let \m {} be i.i.d.\ Radmacher, as defined in Lemma ().
-Then \m {} is RIP according to \m {} for at least probability
-\Disp{
-1 -2 \left( \F{12}{\d} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\d}{2} N_p \right]
-}
-{\small Source: Baraniuk, Davenport, DeVore, and Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices''}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {The Main Bound}
-Let \m {} be defined as above, then, for overwhelming probability
-\Disp{
-\|\V{d}\|_2
-\leq \F{4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_H )^4
-}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Preparation for the Proof}
-\startitemize
-
-\I Use \m {} in our case
-\I Let \m {} be the index set of the largest \m {} components of \m {}, \m {} be the index set of the largest \m {} position of \m {} except \m {}, and \m {}
-\I Denote as \m {} the columns of \m {} having indices in \m {}.
-\I Denote \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Lemmata on Vector Supports}
-\startitemize
-
-\I \m {}
-\I \m {}
-\startitemize
-
-\I (modified to account nonzero \m {})
-
-\stopitemize
-
-\stopitemize
-{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Lemmata on RIP Matrix}
-For overwhelming probability,
-\startitemize
-
-\I \m {}
-\I \m {}
-\startitemize
-
-\I (generalized from real case)
-
-\stopitemize
-\I \m {}
-\startitemize
-
-\I (generalized from real case)
-
-\stopitemize
-
-\stopitemize
-{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (1/4)}
-\Disp{
-\|\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}\|_2
-\leq &\|\M{P}^\Tr \M{P} \V{d}\|_2 \NT \\
-\leq &\R{N_g} \|\M{P}^\Tr \M{P} \V{d}\|_\infty \NT \\
-\leq &4 \R{ N_g \log N_g }
-}
-\startitemize[n]
-
-\I Inclusion of larger support
-\I \m {} norm inequality
-\I Plug in the Lemma for \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (2/4)}
-\Disp{
-\| \V{d}_{A} \|_1
-\leq &\R{L} \| \V{d}_{A} \|_2 \NT \\
-\leq &\R{L} \| \V{d}_{\MC{AB}} \|_2 \NT \\
-\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
-}
-\startitemize[n]
-
-\I \m {} norm inequality
-\I Inclusion of larger support
-\I Plug in the Lemma for \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (3/4)}
-\Disp{
-\| \V{d}_{\MC{C}} \|_1
-\leq &\| \V{d}_{\MC{A}} \|_1 +2 \| \V{g}_{\MC{C}} \|_1 \NT \\
-\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1
-+\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
-+2 \| \V{g}_{\MC{C}} \|_1 \\
-\| \V{d}_{\MC{C}} \|_1
-\leq &\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
-+2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| \V{g}_{\MC{C}} \|_1
-}
-\startitemize[n]
-
-\I Copy the Lemma for \m {}
-\I Plug in the previous eqn.\ for \m {}
-\I Cancellation, simplification
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (4/4)}
-\Disp{
-\| \V{d} \|_2^2
-\leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
-\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|\V{d}_{\MC{C}}\|_1^2 \NT \\
-&\quad +\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\
-&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g \\
-\|\V{d}\|_2^2
-\leq &\F{1}{4 \pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_g )^4
-}
-\startitemize[n]
-
-\I Copy the Lemma for \m {}
-\I Plug in the Lemma for \m {}
-\I Plug in the Lemma for \m {}, approximate using \m {}, and \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Conclusion}
-\startitemize[n]
-
-\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity
-\I We adopt The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm
-\I We generalized DS for complex vectors, and we carried it out in the spatial frequency domain \m {}
-\I Analogous to original DS proof, we proved explicitly that the probability that the expected square error is bounded is overwhelming, where the bounding constant is an explicit function of \m {}, the number of path
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Future Work}
-It remains to
-\startitemize[n]
-
-\I Find the explicit ``overwhelming'' probability
-\I Transform DS into Second Order Cone Problem
-\I Find the Lagrangian and dual problem
-\I Write the simulation, using Newton method
-\I Compare the probability bound with the simulation result
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {References}
-\startitemize[n]
-
-{ \small
-\I W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
-\I R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
-\I S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-\I E J Cand\`es and J Romberg (2005), ``\m {}-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
-}
-\setcounter{countRef}{\value{enumi}}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {References}
-\startitemize[n]
-
-\setcounter{enumi}{\value{countRef}} { \small
-\I E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-\I E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \m {} is Much Larger than \m {}'', \textit{The Annals of Statistics}, Vol.35, No.6.
-\I J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
-Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
-\I J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
-}
-
-\stopitemize
-
-\stoptext
+\page[yes] % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2019-05-29 dantzig_selector/presentation/5_slide.tex
Slides: Finish: Problem setting

\Frame {Conclusion}
{
\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity

\I Towards that end, We adopt The Dantzig Selector (DS) rather than the popular Orthogonal Matching Pursuit (OMP)

\I We generalized DS for complex vectors, and carried it out in the angular domain

\I Analogous to original DS proof, we bound the expected square error, and the successful probability is also bounded by a explicit constant
}

\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %

\Frame {Future Work}
{
\I Check the proof carefullly, especially approximation

\I Finish the simulation program

\I Compare the probability bound with simulation result

\I Also implement OMP and compare they two
}

\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %

\Frame {References}
{
{\tfxx
\I D Achlioptas (2001). Database-friendly random projections. In Proceedings of the twentieth ACM SIGMOD-SIGACT-SIGART symposium on Principles of database systems (pp. 274-281). ACM.

\I W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.

\I R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \It{Constructive Approximation} \Bf{28}: 253–263

\I E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \It{IEEE Transactions on Information Theory}, Vol.51, No.12.

\I E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \m {p} is Much Larger than \m {n}'', \It{The Annals of Statistics}, Vol.35, No.6.
}
}

### 2019-05-29 dantzig_selector/report/2_problem_setting.tex
Slides: Finish: Problem setting

@@
 \Disp {
+\NC \M{Y}
+:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
+}
+We restate the equation with event space index for greater clarity,
+\Disp {
 \NC \NC \M{Y} \SB {\o_t, \o_h, \o_z, \o_r} \NR
@@
 }
-Supress the event space index for brevity, we restate the same equation as
-\Disp {
-\NC \M{Y}
-:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
-}
-Still, the crux of the matter is the recovery of \m {\M {H}} with knowledge of \m {\M {Y}}, while \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B} are in our control.
+
+Our task, then, is the recovery of \m {\M {H}}, and the design of \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}.
 
@@
 
-Introduce the discrete Fourier matrix \m {\M {K}} defined to be
+Introduce the discrete Fourier transform matrix \m {\M {K}} defined to be
 \Disp {

### 2019-05-29 dantzig_selector/report/3_theorems_and_proofs.tex
Slides: Finish: Problem setting

@@
 \startsection [title={Almost-Sparsity of Array Response \m {\V{a}}}]
+
+Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {S} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {S} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
+We rephrase it formally.
+
+\Result
+{Definition}
+{
+Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
+Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
+\Disp{
+\NC \V{v} \DB {\s \SB {n}}
+\leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
+\NC n =\NC 1, \ldots, N_p-1 \NR
+}
+Its existence is evident.
+
+For fixed \m {S}, define
+\Disp{
+\NC \MC {S} \SB {\V{x}, S}
+=\NC \sum_{i=0} ^{S-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
+\NC \MC {C} \SB {\V{x}, S}
+=\NC \sum_{i=S} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
+}
+}
+
+Now set
+\Disp{
+\NC \V{g} _{\MC {A}}
+=\NC \MC {S} \SB {\V{g}, S} \NR[+]
+\NC \V{g} _{\MC {K}}
+=\NC \MC {C} \SB {\V{g}, S} \NR[+]
+\NC \V{g} _{\MC {B}}
+=\NC \MC {S} \SB {\V{g} _\MC {K}, S} \NR[+]
+}
+We hope that \m {\VNm {\V{g} _\MC {K}}_1} is small.
 
@@
 \Disp {
-\NC \NC
-\VNm {
+\NC \NC \VNm {
    \MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}
@@
 := \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
-\NC 0 \leq \NC  \psi' \leq \pi \NR
 }
@@
 
-\startsection [title={Almost-Sparsity of Channel Response \m {\M{H}}}]
+\startsection [title={Almost-Sparsity of \m {\M{G}}}]
 
@@
 
-Let us call it a day and set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l >0}.
+Let us call it a day and set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
 They are (with a slight of abuse of meaning of \m {\o_t} and so on)
@@
 \Disp{
-\NC \MB{E} \SB {\M{F}_R \DB {n_R, n_Y}^2}
+\NC \MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
 = \NC 0 \NR[+]
@@
 \NC \Ss{Var} \SB {\VNm {\M{P} \SB {\o_t, \o_r} \V{u}} _2 ^2}
-\leq \NC 4 N_H^2 N_Y^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
+\leq \NC \RB {4 N_H^2 N_Y^{-3} -1} \VNm {\V{u}} _2 ^4 \NR[+]
 }
@@
 }
-\leq \NC \F {1} {\e^2} N_H^2 N_Y^{-3} \NR[+]
+\leq \NC \F {1} {\e^2} \RB {4 N_H^2 N_Y^{-3} -1} \NR[+]
 }
@@
 \startsection [title={Expected Error Analysis for Complex-Case Dantzig Selector}]
-
-Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {S} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {S} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
-We rephrase it formally.
-
-\Result
-{Definition}
-{
-Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
-Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
-\Disp{
-\NC \V{v} \DB {\s \SB {n}}
-\leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
-\NC n =\NC 1, \ldots, N_p-1 \NR
-}
-Its existence is evident.
-
-Let \m {S \leq N_p/2} be fixed.
-Define
-\Disp{
-\NC \MC {S} \SB {\V{x}, S}
-=\NC \sum_{i=0} ^{S-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
-\NC \MC {C} \SB {\V{x}, S}
-=\NC \sum_{i=S} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
-}
-}
-
-Now set
-\Disp{
-\NC \V{g} _\MC {A}
-=\NC \MC {S} \SB {\V{g}, S} \NR[+]
-\NC \V{g} _\MC {K}
-=\NC \MC {C} \SB {\V{g}, S} \NR[+]
-\NC \V{g} _\MC {B}
-=\NC \MC {S} \SB {\V{g} _\MC {K}, S} \NR[+]
-}
 
@@
 
-We are going to put things together and show the main result.
+We are going to combine previous lemmata and show the main result.
 In accordance with (), set
@@
 \NC \VNm {\V {d}} _2
-\leq \NC \F {4}{\pi^4} \d_{3S}^4 \RB {1-2\d_{2S}} S^4 \RB {\log N_H}^4 \NR
+\leq \NC 32 s^2 L \log N_H \NR[+]
+}
+Under the design condition
+\Disp {
+\NC \RB {2 N_H}^2
+\approx \NC N_Y^3 \NR[+]
+}
+the bound is true for probability \m {p}, with
+\Disp {
+\NC 1 -p
+\leq \NC 16 \D {12}^S \d_{S}^{-S-2} N_H^2 N_Y^{-3} \NR[+]
 }
@@
 
-We are ready to combine previous lemmata.
 The first quantity we want to bound away is
@@
 
-The probability that it is true may be bounded by the number in Lemma () and Lemma ().
-Bounding generously with \m {\d_s \leq 1} yields
-\Disp {
-\NC 1 -p
-\leq \NC 4 \D 12^S N_H^2 N_Y^{-3} +N_H^{-2} \NR[+]
-}
-If \m {N_Y \leq N_H}, there is a condition imposed on the size of \m {N_H}.
-Arranging gives
-\Disp {
-\NC \log N_H
-\geq \NC s^2 L \log 12 + \log 4 \NR[+]
-}
-
-\Result
-{Theorem}
-{
-Theorem is meaningful only when
-\Disp {
-\NC N_H
-\geq \NC 4 \D {12}^{s^2 L} \NR[+]
-}
-}
+The probability that it is true may be bounded by plugging the probability in Lemma () and Lemma ().
 

### 2019-06-05 dantzig_selector/report/1_introduction.tex
Proof: Finish: Almost-sparsity of
Split chap 3 sources

@@
 {
-For fixed \m {s =0, \dots N_p -1}, we say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {\V {x}}, and for all \m {\MC {A} \subset \MC {T} \SB {N_m}} with \m {\# \MC {A} \leq s},
+For fixed \m {s =0, \dots N_p -1}, we say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
 \Disp {
-\NC \NC \RB {1-\d_s} \VNm {\V {x} \DB {\MC {A}}}^2 \NR
-\NC \leq \NC \VNm {\M{\Phi} \V {x} \DB {\MC {A}}} _2^2 \NR
-\NC \leq \NC \RB {1+\d_s} \VNm {\V {x} \DB {\MC {A}}} _2^2 \NR[+]
+\NC \RB {1-\d_s} \VNm {\V {x}}^2
+\leq \NC \VNm {\M{\Phi} \V {x}} _2^2 \NR
+\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
 }
@@
 \M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \NR
-\NC \NC \Q \Q \Q \Q \Q \Q
+\NC \NC \SixQ
 \M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}

### 2019-06-05 dantzig_selector/report/3_1_almost_sparsity.tex
Split chap 3 sources

--- 2019-05-29 dantzig_selector/report/3_theorems_and_proofs.tex
@@
-\startchapter [title={Theorems and Proofs}]
+\startsection [title={Almost-Sparsity of Angular Channel Response}]
+\startsubsection [title={Norm of Array Response}]
 
@@
 We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections.
-
-\startsection [title={Almost-Sparsity of Array Response \m {\V{a}}}]
 
@@
 
-\stopsection
+\stopsubsection
 
-\startsection [title={Almost-Sparsity of \m {\M{G}}}]
+\startsubsection [title={Norm of Angular Channel Response}]
 
@@
 
+\stopsubsection
 \stopsection
-
-\startsection [title={Moments of Precoders' and Combiners' entries}]
-
-Our plan is setting the four precoder matrices to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
-Indeed, \m {\d_s \SB {\M{F}_B} \SB {\o_t}} may be found, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
-We prove a concentration inequality, as explained below, and invoke Chebyshev inequality.
-But before that, we have to investigate the moments of each entry of \m {\M{F}_B \SB {\o_t}} (resp.\ \m {\M{W}_B \SB {\o_t}}) and that of \m {\M{F}_R \SB {\o_t}} (resp.\ \m {\M{W}_R \SB {\o_t}}).
-
-Let us call it a day and set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
-They are (with a slight of abuse of meaning of \m {\o_t} and so on)
-\Disp{
-\NC d \o_t
-=\NC \F {1} {\R {\pi} \l} \exp
-  \RB {-\F{1}{\l^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
-d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
-\NC d \o_t
-=\NC \F {1} {\R {\pi} \l} \exp
-  \RB {-\F{1}{\l^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
-d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
-\NC n_R
-= \NC 0, 1, 2, \ldots, N_R -1 \NR
-\NC n_Y
-= \NC 0, 1, 2, \ldots, N_Y -1 \NR
-}
-
-We know that the magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
-\Disp{
-\NC \NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}} \NR
-\NC =\NC \F{\R{\pi}}{2} \l_B \NR[+]
-\NC M_{B,2}
-:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
-\NC =\NC \l_R^2 \NR[+]
-\NC M_{B,4}
-:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
-\NC =\NC 2 \l_R^4 \NR[+]
-}
-Also notice that
-\Disp{
-\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
-\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
-   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
-\NC \NC \FourQ +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
-      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
-\NC = \NC 0 \NR[+]
-}
-
-Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
-\Disp{
-\NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_H, n_R}}} ^2}^{-1/2}
-d \MF{Re} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
-\NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_H, n_R}}} ^2}^{-1/2}
-d \MF{Im} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
-}
-As a result,
-\Disp{
-\NC \NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} \NR
-\NC =\NC \l_R \NR[+]
-\NC M_{R,2}
-:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^2} \NR
-\NC =\NC \l_R^2 \NR[+]
-\NC M_{R,4}
-:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^4} \NR
-\NC =\NC \l_R^4 \NR[+]
-}
-And again
-\Disp{
-\NC \MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
-= \NC 0 \NR[+]
-}
-
-\startsection [title={Confirming the Restricted Isometry of \m {P}}]
-
-\Result
-{Definition}
-{
-Let \m {P} be fixed.
-For \m {\MC {T}, \MC {T}' \subset \MC {T} \RB {N_p}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} \SB {P} >0} to be the smallest number such that
-\Disp {
-\NC \Nm {\IP {P _{\MC {T}} h, P _{\MC {T}'} h'}}
-\leq \NC \tau_{s, s'} \SB {P} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
-}
-}
-
-From \quotation {Decoding from Linear Programming} (Cand\`es and Tao 2005), Lemma 1.1:
-
-\Result
-{Lemma}
-{
-Let \m {\M{P}} be fixed.
-Then \m {\tau_{s, s'} \SB {\M{P}}} is bounded in both direction as follows,
-\Disp {
-\NC \d_{s+s'} \SB {\M{P}} -\max \SB {\CB {\d_s \SB {\M{P}}, \d_{s'} \SB {\M{P}}}}
-\leq \NC \tau_{s, s'} \SB {\M{P}} \NR
-\NC \leq \NC \d_{s+s'} \SB {\M{P}} \NR[+]
-}
-}
-
-Thus \m {\d_s \SB {\M{P}}}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
-We may well keep track of \m {\d_s \SB {\M{P}}} only.
-When \m {\M{P}} is clear, we may suppress it.
-
-Similar is true of \m {\d_s \SB {\M{F}_B} \SB {\o_t}}.
-But each entry of \m {P} is a linear combination of products, and such reasoning does not work.
-If only \m {P} were also an i.i.d.\ random matrix, the resulting proof would be easier.
-Is the approach all but lost?
-
-Observe
-\Disp {
-\NC \M{P} ^\Adj \M{P}
-=\NC
-\RB {
-   \RB {\M{K} ^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-   \otimes \RB {\M {K} \M {W}_R \M {W}_B}
-}
-\RB {
-   \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast}
-   \otimes \RB {\M {W}_B \M {W}_R \M {K}}
-} \NR
-\NC =\NC
-\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast \M{K}^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-\otimes \RB {\M {W}_B \M {W}_R \M{K} \M{K}^\Adj \M {W}_R^\Adj \M {W}_B^\Adj} \NR
-\NC =\NC
-\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-\otimes \RB {\M {W}_B \M {W}_R \M {W}_R^\Adj \M {W}_B^\Adj}
-\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR
-\NC := \NC \M{Q} \NR[+]
-}
-
-This implies
-\Disp {
-\NC \V{u} ^\Adj \M{P} ^\Adj \M{P} \V{u}
-= \NC \V{u} ^\Adj \M{Q} ^\Adj \M{Q} \V{u} \NR[+]
-}
-or
-\Result
-{Lemma}
-{
-For any instance of \m {\M{P} \SB {\o_t, \o_r}} and \m {\M{Q} \SB {\o_t, \o_r}},
-\Disp{
-\NC \VNm {\M{P} \V{u}} _2
-= \NC \VNm {\M{Q} \V{u}} _2 \NR[+]
-}
-}
-
-And it will turn out that any two distinct entries of \m {\M{Q}} are not correlated.
-
-\Result
-{Definition}
-{
-To make expressions more compact, introduce the indication function \m {\i}, so that, for some injective \m {\s:\; \CB {0, \ldots, M-1} \CB {0, \ldots, N-1}},
-\Disp {
-\NC \i_{a_0, \ldots, a_{M-1}} \SB {x_0, \ldots, x_{N-1}}
-=\NC \startcases
-\NC 1, \MC \Q \exists \s:\; x_0 \cdots x_{N-1}
-=x_{\s \SB {0}} ^{a_0} \cdots x_{\s \SB {M-1}} ^{a_{M-1}} \NR
-\NC 0, \NC \Q \Rm {otherwise} \NR
-\stopcases \NR
-}
-}
-
-For short, denote
-\Disp {
-\NC F :=\NC \M {F}_B \M {F}_R \NR
-\NC W :=\NC \M {W}_R \M {W}_B \NR
-}
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E} \SB {\M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'}} \NR
-\NC = \NC \MB{E} \SB {\M{W}^\Adj \DB {n_Y, n_H} \M{W}^\Adj \DB {n_Y', n_H'}} \NR
-\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR[+]
-}
-}
-
-To see this, expanding the definition
-\Disp {
-\NC \NC \M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'} \NR
-\NC =\NC
-\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H, n_R} \M{F}_B \DB {n_R, n_Y}}
-\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H', n_R} \M{F}_B \DB {n_R, n_Y'}} \NR[+]
-}
-Examine the \m {\i_{1,1} \SB {n_H, n_H'}} factor and \m {\i_{1,1} \SB {n_Y, n_Y'}} factors.
-After taking expectation, the expectation sign is distributed, and every term vanishes.
-Other terms that remains are \m {\i_{2} \SB {n_H, n_H'}} and \m {\i_{2} \SB {n_Y, n_Y'}}, namely
-\Disp {
-\NC \NC \sum_{n_R=0}^{N_R-1}
-\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
-\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
-\NC = \NC N_R \D M_{R,2} M_{B,2} \NR
-}
-
-By the same token,
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E}
-\SB {
-\M{F} \DB {n_H, n_Y}
-\M{F} \DB {n_H', n_Y'}
-\M{F} \DB {n_H'', n_Y''}
-\M{F} \DB {n_H''', n_Y'''}
-} \NR
-\NC \NC =\MB{E}
-\SB {
-\M{W} \DB {n_Y, n_H}
-\M{W} \DB {n_Y', n_H'}
-\M{W} \DB {n_Y'', n_H''}
-\M{W} \DB {n_Y''', n_H'''}
-} \NR
-\NC = \NC
-\i_4 \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_4 \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D 2 N_R^2 \l_R^4 \l_B^4 \NR
-\NC \NC \FourQ +\i_{2,2} \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_{2,2} \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D N_R^2 \l_R^4 \l_B^4 \NR[+]
-}
-}
-
-A moment's reflection shows
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E} \SB {\M{P} \DB {n_h, n_y} \M{P} \DB {n_h', n_y'}} \NR
-\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR[+]
-}
-}
-
-More trickily, but by the same idea,
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \M{F} \DB {n_h, n_y}
-\M{F} \DB {n_h', n_y'}
-\M{F} \DB {n_h'', n_y''}
-\M{F} \DB {n_h''', n_y'''} \NR
-\NC = \NC
-\i_4 \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_4 \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D 4 N_R^4 \l_R^8 \l_B^8 \NR
-\NC \NC \FourQ +\i_{2,2} \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_{2,2} \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D N_R^4 \l_R^8 \l_B^8 \NR[+]
-}
-}
-
-Now, fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we shall study the probability concentration of \m {\VNm {\M{F}_B \V{u}}_2^2} and \m {\VNm {\M{F}_B \V{u}}_2^4}.
-The two moments are present in Chebyshev bound.
-\Disp{
-\NC \NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2} \NR
-\NC = \NC \MB{E} \SB {
-  \sum_{n_y=0}^{N_y-1}
-  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
-} \NR
-\NC = \NC \sum_{n_y=0}^{N_y-1}
-  \MB{E} \SB {\Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2}
-\NR
-\NC = \NC
-\sum_{n_y=0}^{N_y-1}
-  \MB{E} \SB {
-     2 \sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
-       \MF {Re} \SB{
-         \M{Q} \DB {n_y, n_h} ^\ast \M{Q} \DB {n_y, n_h'}
-         \V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
-       }
-   } \NR
-\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
-  \MB{E}
-     \SB {\sum_{n_h=0}^{N_h-1} \Nm {\M{Q} \DB {n_y, n_h}}^2 \Nm {\V{u} \DB{n_h}}^2}
-\NR
-\NC = \NC
-2 \sum_{n_y=0}^{N_y-1}
-\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
-\MF {Re} \SB{
-   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
-   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
-}
-\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
-\NR
-\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
-   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
-\NR
-\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR[+]
-}
-Thus, we may set
-\Disp{
-\NC \l_B
-=\NC \l_R \NR
-\NC =\NC \F {1} {\R {N_Y N_R}} \NR[+]
-}
-To make
-\Disp{
-\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2}
-=\NC \VNm {\V{u}} _2 ^2
-}
-
-Similarly, we have to find, in advance, the second moment.
-\Disp{
-\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^4}
-=\NC \MB{E} \SB {
-  \RB {
-    \sum_{n_R=0}^{N_R-1}
-    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{Q} \DB {n_R, n_Y} ^\ast \V{u} \DB{n_Y}} ^2
-  } ^2
-} \NR
-\NC = \NC E_1 +E_2 +E_3 +E_4 +E_5 \NR[+]
-}
-These terms are discussed as immediately follows.
-Without spelling out everything, we notice that as long as a term has a single \m {\M{Q} \DB {n_R, n_Y}} factor, it's expectation is zero.
-The terms that does not vanish is a product of three numbers: How many terms, the moment involving \m {\M{Q} \DB {n_y, n_h}}, the norm of \m {\V{u}}.
-We will repeatedly bound \m {N_R \D (N_R-1) /2} by \m {N_R^2 /2}, and bound \m {\Nm {\V{u}} _2} by \m {\Nm {\V{u}} _2}, and so on.
-\Disp {
-\NC E_1
-=\NC \sum_{n_y=0}^{N_y-1} \sum_{n_h=0}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^4
-\Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC =\NC N_Y^2 \D 4 N_Y ^{-4} \D \VNm {\V{u}} _4 ^4 \NR
-\NC \leq \NC 4 N_Y ^{-2} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-Now we have to bound \m {\i_{1,1} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,2}^2} and \m {\i_{2} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,4}} by \m {M_{B,4}} to simplifying matters, and similar for \m {E_3} and \m {E_4}.
-\Disp {
-\NC E_2
-= \NC \sum _{\Stack { n_y, n_y' =0 \NR n_y <n_y' }}^{N_y-1}
-\sum _{n_h =0}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y', n_h}} ^2
-\Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
-\NC \NC \FourQ + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
-\NC \leq \NC 4 \VNm {\V{u}} _2 ^4 \NR[+]
-}
-\Disp {
-\NC E_3
-=\NC \sum _{n_y, n_y' =0}^{N_y-1}
-\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y', n_h'}} ^2
-\Nm {\V{u} \DB{n_h}} ^2
-\Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \leq \NC 4 N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-\Disp {
-\NC E_4
-=\NC \sum _{n_y =0}^{N_y-1}
-\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y, n_h'}} ^2
-\Nm {\V{u} \DB{n_h}} ^2
-\Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \leq \NC 4 N_H ^2 N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-
-The last one is more complicated.
-Use the shorthand
-\Disp {
-\NC \sum _{n_h, n_h', m_h, m_h'} ^\star
-:= \NC \sum _{
-   \Stack {
-     0 =n_h <n_h' \NR
-     0 =m_h <m_h' \NR
-     n_h +m_h' =n_h' +m_h \NR
-     \Fl {n_h/N_H} =\Fl {n_h'/N_H} \NR
-     \Fl {m_h/N_H} =\Fl {m_h'/N_H}
-   }
-} ^{N_H-1}
-\sum _{
-  \Stack {
-     0 =n_y <n_y' \NR
-     \Fl {n_y/N_Y} =\Fl {n_y'/N_Y}
-  }
-} ^{N_y-1} \NR
-\NC \V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'}
-:=\NC \i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'}
-\V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \NR
-}
-Then observe
-\Disp {
-\NC \NC \sum _{n_h, n_h', m_h, m_h'} ^\star
-\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
-\NC \leq \NC N_h^{-2}
-\sum_{n_h, n_h' =0} ^{N_h-1}
-\sum_{m_h, m_h' =0} ^{N_h-1}
-\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
-}
-This is because one of \m {n_h, n_h'} and one of \m {m_h, m_h'} may both choose to lie in other \m {\RB {N_H-1} \RB {N_H-2}} blocks (of length \m {N_H}).
-Then we need a corollary that follows from \quotation {Muirhead inequality}.
-\Result
-{Lemma}
-{
-If every component of \m {\V{u} \in \MB {M}_{\MB {C}} \SB {N_h}} is considered as a free variable taking complex values, then
-\Disp {
-\NC \NC \sum_{n_h, n_h' =0} ^{N_h-1}
-\sum_{m_h, m_h' =0} ^{N_h-1}
-\Nm {\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'}} \NR
-\NC \leq \NC \F{1}{6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
-}
-}
-
-Now,
-\Disp {
-\NC E_5
-= \NC \sum _{n_h, n_h', m_h, m_h'} ^\star
-  \M{Q} \DB {n_y, n_h}
-  \M{Q} \DB {n_y, n_h'}
-  \M{Q} \DB {n_y', m_h}
-  \M{Q} \DB {n_y', m_h'} \NR
-  \NC \NC \SixQ
-  \V{u} \DB{n_h}
-  \V{u} \DB{n_h'}
-  \V{u} \DB{m_h}
-  \V{u} \DB{m_h'} \NR
-\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \D N_Y ^{-4} \NR
-\NC \NC \FourQ
-\D N_H^{-2} \sum_{n_h, n_h' =0} ^{N_h-1} \sum_{m_h, m_h' =0} ^{N_h-1}
-\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
-\NC \leq \NC \F{1}{6} N_Y ^{-1} \VNm {\V{u}} _2 ^4. \NR[+]
-}
-
-In conclusion, \m {E_4} dominates.
-\Disp{
-\NC \Ss{Var} \SB {\VNm {\M{P} \SB {\o_t, \o_r} \V{u}} _2 ^2}
-\leq \NC \RB {4 N_H^2 N_Y^{-3} -1} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-Thus, by Chebyshev bound,
-\Result
-{Theorem}
-{
-Let \m {\M{P} \in \MB {M}_{\MB {C}} \SB {N_R, N_Y}} be generated randomly according to ().
-Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_Y}}, and for any \m {\e >0},
-\Disp{
-\NC \MB{P}
-\SB {
-  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
-  \geq \e \VNm {\V{u}} _2 ^2
-}
-\leq \NC \F {1} {\e^2} \RB {4 N_H^2 N_Y^{-3} -1} \NR[+]
-}
-}
-
-According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), substitution of relevent quantities yields
-\Result
-{Lemma}
-{
-Suppose the probability, according to event space \m {\o_t, \o_r}, that RIP holds for \m {\M{P}} w.r.t.\ \m {\d_s} is \m {p}, then
-\Disp{
-\NC 1 -p
-\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} N_H^2 N_Y^{-3} \NR[+]
-}
-}
-
-\stopsection
-
-\startsection [title={Expected Error Analysis for Complex-Case Dantzig Selector}]
-
-Let \m {\hat {\V {g}}} be the Dantzig Selector.
-For concreteness, we set
-\Disp {
-\NC \g 
-= \NC \R {2 \log N_h} \NR[+]
-}
-
-Other values are of course possible, but this is enough to illustrate our purpose.
-Also set for short
-\Disp {
-\NC \V {d} 
-= \NC \Hat {\V {g}} -\V {g} \NR[+]
-}
-
-The rest follows \quotation {The Dantzig Selector} very closely.
-The generalization to complex vector is necessary in our setting.
-We spell out the proof when such generalization is nontrivial.
-
-\Result
-{Lemma}
-{
-Let \m {\V {g}} and \m {\V {d}} be defined as above.
-Then
-\Disp {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {K}}} _1 \NR
-}
-}
-
-To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {K}},
-\Disp {
-\NC \VNm {\V {g}} _1
--\VNm {\V {d} _{\MC {A}}} _1
-+\VNm {\V {d} _{\MC {K}}} _1
--\VNm {\V {g} _{\MC {K}}} _1
-\leq \NC \VNm {\V {g} +\V {d}} _1 \NR
-}
-In the first line, we recall \m {\V {g} =\V {g} _{\MC {A}}}.
-On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
-\Disp {
-\NC \VNm {\V {g} +\V {d}} _1
-=\NC \VNm {\hat {\V {g}}} _1 \NR
-\NC \leq \NC \VNm {\V {g}} _1 \NR
-}
-The result follows by combining.
-
-\Result
-{Lemma}
-{
-\Disp {
-\NC \MB {E} \SB {\Nm {\IP {\V {z} \SB {\o_z}, \M {P} \DB {:, n_h}}}}
-\leq \NC  2 \R {\log N_h} \NR
-\NC n_h 
-=\NC 1, \ldots, N_h. \NR
-}
-with probability \m {\geq 1 -N_h^{-1}}.
-}
-
-Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
-
-Recall the following bound for \m {Q} function
-\Disp {
-\NC Q\SB {x}
-\leq \NC \F {1}{2} \Ss {e}^{-x^2/2} \NR
-}
-Particularly, for \m {x =\R {2 \log N_h}},
-\Disp {
-\NC Q\SB {\R {2 \log N_h}}
-=\NC \F {1}{N_h}. \NR
-}
-
-\Result
-{Lemma}
-{
-With the condition that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M{P}}},
-\Disp {
-\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC  4 \R {\log N_h} \NR
-\NC n_g 
-=\NC 1, \ldots, N_h. \NR
-}
-with probability \m {\geq 1 -N_h^{-1}}.
-}
-
-To show this, by definition
-\Disp {
-\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
-= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y}} \NR
-\NC = \NC \IP {\M {P} \V {d}, \M {P} \DB {:,n_y}} \NR
-}
-By construction
-\Disp {
-\NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
-\leq \NC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty \NR
-\NC \leq \NC 2\R {\log N_h} \NR
-}
-By triangle inequality, together with Lemma (), we have
-\Disp {
-\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
-\leq \NC \VNm {\IP {\V {z}, \M {P} \DB {:,n_y}}} _\infty
-+\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y}} \NR
-\NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
-}
-which implies
-\Disp {
-\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC 4 \R {\log N_h}. \NR
-}
-
-From \quotation {Dantzig Selector} Lemma 1, first equation, we have the result as below.
-The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
-The only thing that has to change accordingly is the interpretation of magnitude and the inner product, which are evident.
-
-\Result
-{Lemma}
-{
-With the condition that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M{P}}},
-\Disp {
-\NC \VNm {\V {d} _{\MC {AB}}} _2
-\leq \NC \F {1}{1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}}{\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {K}}} _1 \NR
-}
-}
-
-From \quotation {Dantzig Selector}, Lemma 1, second equation, we have the result as below.
-Again, their proof works with complex vector spaces in place of real ones too.
-
-\Result
-{Lemma}
-{
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{S} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
-}
-}
-
-\stopsection
-
-\startsection [title={The Main Result}]
-
-We are going to combine previous lemmata and show the main result.
-In accordance with (), set
-\Disp{
-\NC S
-=\NC s^2 L \NR
-}
-
-\Result
-{Theorem}
-{
-Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
-Then, with \m {S =s^2 L}, as \m {N_H \to \infty},
-\Disp {
-\NC \VNm {\V {d}} _2
-\leq \NC 32 s^2 L \log N_H \NR[+]
-}
-Under the design condition
-\Disp {
-\NC \RB {2 N_H}^2
-\approx \NC N_Y^3 \NR[+]
-}
-the bound is true for probability \m {p}, with
-\Disp {
-\NC 1 -p
-\leq \NC 16 \D {12}^S \d_{S}^{-S-2} N_H^2 N_Y^{-3} \NR[+]
-}
-}
-
-The first quantity we want to bound away is
-\Disp {
-\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
-\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
-\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
-\NC \leq \NC 4 \R {S \log N_h} \NR
-}
-Thus, by virtue of Lemma (), and approximating \m {1 /(1 -\d_{2S}) =1 +\d_{2S}} and so on,
-\Disp {
-\NC \VNm {\V {d}_{\MC {A}}} _1
-\leq \NC \R {S} \VNm {\V {d}_{\MC {A}}} _2 \NR
-\NC \leq \NC \R {S} \VNm {\V {d} _{\MC {AB}}} _2 \NR
-\NC \leq \NC \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
-+4 \RB {1+\d_{2S}} S \R {\log N_h} \NR
-}
-
-Next, we must eliminate \m {\VNm {d _{\MC {A}}} _1} in rhs of Lemma ().
-\Disp {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\NC \leq \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
-+4 \RB {1+\d_{2S}} S \R {\log N_h}
-+2 \VNm {\V {g} _{\MC {K}}} _1 \NR
-}
-Arranging and drop second order small terms like \m {\d_{2S} \d_{3S}}, that is,
-\Disp {
-\NC 1 \ll \NC S \NR
-\NC \ll \NC N_h \NR
-}
-doing this we have
-\Disp {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\leq \NC 2 \RB {1+\d_{3S}} \VNm {\V {g} _{\MC {K}}} _1
-+4 \RB {1+2\d_{3S}} S \R {\log N_h} \NR
-}
-
-We are now in a position to bound \m {\VNm {d} _2^2}.
-Using Lemma () again, and only keeping to first order, we have
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC 16 S \log N_h
-+8 \d_{3S} \R {\log N_h} 
-+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {K}}} _1 \NR
-}
-Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {K}}} _1}.
-Again for simplicity, we keep only the first order small terms.
-Plug in \m {S =s^2 L} and \m {N_h =N_H^2} we get, finally,
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC 32 s^2 L \log N_H
-+\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
-+\F {\pi} {9} \F {L} {s^2 N_H} \NR
-}
-In particular for asymptotic \m {N_H \gg 1}, keep only the dominating term.
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC 32 s^2 L \log N_H \NR
-}
-
-The probability that it is true may be bounded by plugging the probability in Lemma () and Lemma ().
-
-\stopsection
-
-\stopchapter

### 2019-06-05 dantzig_selector/report/3_3_expected_error_analysis.tex
Split chap 3 sources

--- 2019-05-29 dantzig_selector/report/3_theorems_and_proofs.tex
@@
-\startchapter [title={Theorems and Proofs}]
-
-Our plan is first to show that \m {\SB {\V {g}}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
-We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections.
-
-\startsection [title={Almost-Sparsity of Array Response \m {\V{a}}}]
-
-Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {S} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {S} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
-We rephrase it formally.
-
-\Result
-{Definition}
-{
-Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
-Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
-\Disp{
-\NC \V{v} \DB {\s \SB {n}}
-\leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
-\NC n =\NC 1, \ldots, N_p-1 \NR
-}
-Its existence is evident.
-
-For fixed \m {S}, define
-\Disp{
-\NC \MC {S} \SB {\V{x}, S}
-=\NC \sum_{i=0} ^{S-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
-\NC \MC {C} \SB {\V{x}, S}
-=\NC \sum_{i=S} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
-}
-}
-
-Now set
-\Disp{
-\NC \V{g} _{\MC {A}}
-=\NC \MC {S} \SB {\V{g}, S} \NR[+]
-\NC \V{g} _{\MC {K}}
-=\NC \MC {C} \SB {\V{g}, S} \NR[+]
-\NC \V{g} _{\MC {B}}
-=\NC \MC {S} \SB {\V{g} _\MC {K}, S} \NR[+]
-}
-We hope that \m {\VNm {\V{g} _\MC {K}}_1} is small.
-
-\Result
-{Definition}
-{
-For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse according to the \m {\ell_p}-norm with remainder \m {R}, if
-\Disp {
-\NC \VNm {\MC {C} \SB{\V {x}, s}} _p
-\leq \NC R. \NR[+]
-}
-}
-
-Let \m {\f} be fixed.
-It suffices to bound
-\Disp {
-\NC \NC \VNm {
-   \MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}
-} _2 ^2 \NR[+]
-}
-
-Towards that end, introduce
-\Disp {
-\NC \psi \SB {\f, n_H}
-:=\NC \RB {
-   \RB {
-      \RB {\f \; \Rm{Mod}\; \F{2\pi}{N_H}}
-      +\F {2 \pi n_H} {N_H}
-      +\pi
-   } \;
-   \Rm{Mod}\; \RB {2\pi}
-}
--\pi \NR
-}
-Note that by construction
-\Disp{
-\NC \Nm {\psi \SB {\f, n_H}}
-\leq \NC \pi \NR
-}
-And define the so-called Dirichlet kernel
-\Disp {
-\NC D \SB {\psi'}
-:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
-}
-Then observe
-\Disp {
-\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {n_H}
-=\NC \F {1}{N_H} D \SB {\psi \SB {\f, n_H}} \NR
-}
-
-Now, it can be verified that
-\Result
-{Lemma}
-{
-For \m {-\pi \leq x < \pi}, we have
-\Disp {
-\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}. \NR[+]
-}
-}
-
-Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
-\Disp {
-\NC \Nm {D \SB {\psi'}}
-= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}}{\Nm {\sin \SB {\psi' /2}}} \NR
-\NC \leq \NC B \SB {\psi'} \NR
-\NC := \NC \F {48}{\Nm {\psi'^2 -24} \Nm {\psi'}} \NR[+]
-\NC -\pi \leq \NC \psi' < \pi. \NR
-}
-Thus,
-\Disp {
-\NC R^2
-=\NC \F {1}{N_H^2}
-\VNm {
-\MC {C}
-\SB{
-   \sum_{n_H' =0}^{N_H -1}
-   B \SB {\psi \SB {\f, n_H'}}
-   \V {u}_{n_H'},
-   s
-}
-} _2^2
-\NR[+]
-}
-Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
-We seek to bound the \quotation {rectangulars} with an integral, and we have to split the cases that \m {N_H} is odd and even.
-Anyway, a moment's reflection shows
-\Disp {
-\NC R^2
-\leq \NC \F {1}{N_H^2} \D \F {N_H}{2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
-\NC = \NC \F {2304} {N_H \pi^6}
-\int _{s /N_H} ^1 \F{1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
-\NC =\NC \F{1} {2\pi^2 N_H}
-\RB {
-  -\F {8} {u}
-+\F {4\pi^2 u} {24 -\pi^2 u^2}
-+\R{6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R{6}}}
-}
-\Bigg \| _{s/N_H} ^1 \NR
-\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR[+]
-}
-In the last step we bound the lower limit of the second and third term with \m {x' =0}, and leave the dominating \m {1/x'}.
-
-Expanding \m {R} gives
-\Disp {
-\NC R
-\leq \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {\R {s}} {38 N_H}. \NR[+]
-}
-
-Fixing \m {N_H}, it shall be easy to see that rhs is strictly decreasing in \m {N_H}, and the value of \m {s} that minimizes it is about \m {s =5N_H}.
-In the range that we care, rhs is thus strictly decreasing in \m {s}.
-\m {N_H}.
-
-\Result
-{Lemma}
-{
-Let \m {\f \SB {\o_h}} be given, and linear array response \m {\V {a} \SB {\f}} defined as in ().
-Suppose \m {N_H \geq 4}.
-Then, for all instances of \m {\f}, \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
-\Disp{
-\NC R
-\leq \NC \m {\F{1}{3 \R{N_H}}} \NR[+]
-}
-}
-
-Since the bound is also decreasing in \m {N_H}, for concreteness, let us plug in \m {N_H =4} for the upper bound, giving
-\Disp{
-\NC R
-\leq \NC \F {1} {6} \NR[+]
-}
-
-\stopsection
-
-\startsection [title={Almost-Sparsity of \m {\M{G}}}]
-
-It remains to bound \m {\VNm {\M {G}} _F}.
-Note that
-\Disp{
-\NC \VNm {\M {G}}_F
-=\NC \VNm {\M {H}}_F \NR[+]
-}
-So it suffices to consider \m {\VNm {\M {H}} _F}.
-
-\Disp{
-\NC \VNm {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F
-\leq \NC \sum _{l=0} ^{L-1} \Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
-\NC \leq \NC
-\sum _{l=0} ^{L-1}
-\Nm {\a_l} \VNm {\V {a} \SB {\f_l}} _2
-\VNm {\V {a} \SB {\th_l}} _2 \NR[+]
-}
-Lastly, we know \m {\ell_1}-norm is larger than \m {\ell_2}-norm.
-Since \m {\ell_1}-norm will be used in later proof, we display the statement about \m {\ell_1}-norm.
-\Disp{
-\NC \NC \MB {E} \SB {\VNm {\MC {C} \SB {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj}} _F} \NR
-\NC \leq \NC \F {1} {9 \R{N_H}} \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}} \NR
-\NC \leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR[+]
-}
-
-\Result
-{Lemma}
-{
-Let \m {\f \SB {\o_h}} and \m {\th \SB {\o_h}} be uniformly, independently distributed in \m {[0,2\pi)}, and let \m {\V {g} \in \MB{V}_\MB{C} \SB{N_h}} be defined as in ().
-If \m {N_h \geq 4^2 =16}, then \m {\V {g}} is almost-\m {s^2 L}-sparse with \m {\ell_1}-residue \m {R} to be
-\Disp {
-\NC R
-\leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR
-}
-}
-
-\stopsection
-
-\startsection [title={Moments of Precoders' and Combiners' entries}]
-
-Our plan is setting the four precoder matrices to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
-Indeed, \m {\d_s \SB {\M{F}_B} \SB {\o_t}} may be found, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
-We prove a concentration inequality, as explained below, and invoke Chebyshev inequality.
-But before that, we have to investigate the moments of each entry of \m {\M{F}_B \SB {\o_t}} (resp.\ \m {\M{W}_B \SB {\o_t}}) and that of \m {\M{F}_R \SB {\o_t}} (resp.\ \m {\M{W}_R \SB {\o_t}}).
-
-Let us call it a day and set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
-They are (with a slight of abuse of meaning of \m {\o_t} and so on)
-\Disp{
-\NC d \o_t
-=\NC \F {1} {\R {\pi} \l} \exp
-  \RB {-\F{1}{\l^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
-d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
-\NC d \o_t
-=\NC \F {1} {\R {\pi} \l} \exp
-  \RB {-\F{1}{\l^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
-d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
-\NC n_R
-= \NC 0, 1, 2, \ldots, N_R -1 \NR
-\NC n_Y
-= \NC 0, 1, 2, \ldots, N_Y -1 \NR
-}
-
-We know that the magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
-\Disp{
-\NC \NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}} \NR
-\NC =\NC \F{\R{\pi}}{2} \l_B \NR[+]
-\NC M_{B,2}
-:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
-\NC =\NC \l_R^2 \NR[+]
-\NC M_{B,4}
-:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
-\NC =\NC 2 \l_R^4 \NR[+]
-}
-Also notice that
-\Disp{
-\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
-\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
-   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
-\NC \NC \FourQ +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
-      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
-\NC = \NC 0 \NR[+]
-}
-
-Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
-\Disp{
-\NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_H, n_R}}} ^2}^{-1/2}
-d \MF{Re} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
-\NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_H, n_R}}} ^2}^{-1/2}
-d \MF{Im} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
-}
-As a result,
-\Disp{
-\NC \NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} \NR
-\NC =\NC \l_R \NR[+]
-\NC M_{R,2}
-:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^2} \NR
-\NC =\NC \l_R^2 \NR[+]
-\NC M_{R,4}
-:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^4} \NR
-\NC =\NC \l_R^4 \NR[+]
-}
-And again
-\Disp{
-\NC \MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
-= \NC 0 \NR[+]
-}
-
-\startsection [title={Confirming the Restricted Isometry of \m {P}}]
-
-\Result
-{Definition}
-{
-Let \m {P} be fixed.
-For \m {\MC {T}, \MC {T}' \subset \MC {T} \RB {N_p}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} \SB {P} >0} to be the smallest number such that
-\Disp {
-\NC \Nm {\IP {P _{\MC {T}} h, P _{\MC {T}'} h'}}
-\leq \NC \tau_{s, s'} \SB {P} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
-}
-}
-
-From \quotation {Decoding from Linear Programming} (Cand\`es and Tao 2005), Lemma 1.1:
-
-\Result
-{Lemma}
-{
-Let \m {\M{P}} be fixed.
-Then \m {\tau_{s, s'} \SB {\M{P}}} is bounded in both direction as follows,
-\Disp {
-\NC \d_{s+s'} \SB {\M{P}} -\max \SB {\CB {\d_s \SB {\M{P}}, \d_{s'} \SB {\M{P}}}}
-\leq \NC \tau_{s, s'} \SB {\M{P}} \NR
-\NC \leq \NC \d_{s+s'} \SB {\M{P}} \NR[+]
-}
-}
-
-Thus \m {\d_s \SB {\M{P}}}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
-We may well keep track of \m {\d_s \SB {\M{P}}} only.
-When \m {\M{P}} is clear, we may suppress it.
-
-Similar is true of \m {\d_s \SB {\M{F}_B} \SB {\o_t}}.
-But each entry of \m {P} is a linear combination of products, and such reasoning does not work.
-If only \m {P} were also an i.i.d.\ random matrix, the resulting proof would be easier.
-Is the approach all but lost?
-
-Observe
-\Disp {
-\NC \M{P} ^\Adj \M{P}
-=\NC
-\RB {
-   \RB {\M{K} ^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-   \otimes \RB {\M {K} \M {W}_R \M {W}_B}
-}
-\RB {
-   \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast}
-   \otimes \RB {\M {W}_B \M {W}_R \M {K}}
-} \NR
-\NC =\NC
-\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast \M{K}^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-\otimes \RB {\M {W}_B \M {W}_R \M{K} \M{K}^\Adj \M {W}_R^\Adj \M {W}_B^\Adj} \NR
-\NC =\NC
-\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-\otimes \RB {\M {W}_B \M {W}_R \M {W}_R^\Adj \M {W}_B^\Adj}
-\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR
-\NC := \NC \M{Q} \NR[+]
-}
-
-This implies
-\Disp {
-\NC \V{u} ^\Adj \M{P} ^\Adj \M{P} \V{u}
-= \NC \V{u} ^\Adj \M{Q} ^\Adj \M{Q} \V{u} \NR[+]
-}
-or
-\Result
-{Lemma}
-{
-For any instance of \m {\M{P} \SB {\o_t, \o_r}} and \m {\M{Q} \SB {\o_t, \o_r}},
-\Disp{
-\NC \VNm {\M{P} \V{u}} _2
-= \NC \VNm {\M{Q} \V{u}} _2 \NR[+]
-}
-}
-
-And it will turn out that any two distinct entries of \m {\M{Q}} are not correlated.
-
-\Result
-{Definition}
-{
-To make expressions more compact, introduce the indication function \m {\i}, so that, for some injective \m {\s:\; \CB {0, \ldots, M-1} \CB {0, \ldots, N-1}},
-\Disp {
-\NC \i_{a_0, \ldots, a_{M-1}} \SB {x_0, \ldots, x_{N-1}}
-=\NC \startcases
-\NC 1, \MC \Q \exists \s:\; x_0 \cdots x_{N-1}
-=x_{\s \SB {0}} ^{a_0} \cdots x_{\s \SB {M-1}} ^{a_{M-1}} \NR
-\NC 0, \NC \Q \Rm {otherwise} \NR
-\stopcases \NR
-}
-}
-
-For short, denote
-\Disp {
-\NC F :=\NC \M {F}_B \M {F}_R \NR
-\NC W :=\NC \M {W}_R \M {W}_B \NR
-}
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E} \SB {\M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'}} \NR
-\NC = \NC \MB{E} \SB {\M{W}^\Adj \DB {n_Y, n_H} \M{W}^\Adj \DB {n_Y', n_H'}} \NR
-\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR[+]
-}
-}
-
-To see this, expanding the definition
-\Disp {
-\NC \NC \M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'} \NR
-\NC =\NC
-\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H, n_R} \M{F}_B \DB {n_R, n_Y}}
-\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H', n_R} \M{F}_B \DB {n_R, n_Y'}} \NR[+]
-}
-Examine the \m {\i_{1,1} \SB {n_H, n_H'}} factor and \m {\i_{1,1} \SB {n_Y, n_Y'}} factors.
-After taking expectation, the expectation sign is distributed, and every term vanishes.
-Other terms that remains are \m {\i_{2} \SB {n_H, n_H'}} and \m {\i_{2} \SB {n_Y, n_Y'}}, namely
-\Disp {
-\NC \NC \sum_{n_R=0}^{N_R-1}
-\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
-\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
-\NC = \NC N_R \D M_{R,2} M_{B,2} \NR
-}
-
-By the same token,
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E}
-\SB {
-\M{F} \DB {n_H, n_Y}
-\M{F} \DB {n_H', n_Y'}
-\M{F} \DB {n_H'', n_Y''}
-\M{F} \DB {n_H''', n_Y'''}
-} \NR
-\NC \NC =\MB{E}
-\SB {
-\M{W} \DB {n_Y, n_H}
-\M{W} \DB {n_Y', n_H'}
-\M{W} \DB {n_Y'', n_H''}
-\M{W} \DB {n_Y''', n_H'''}
-} \NR
-\NC = \NC
-\i_4 \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_4 \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D 2 N_R^2 \l_R^4 \l_B^4 \NR
-\NC \NC \FourQ +\i_{2,2} \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_{2,2} \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D N_R^2 \l_R^4 \l_B^4 \NR[+]
-}
-}
-
-A moment's reflection shows
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E} \SB {\M{P} \DB {n_h, n_y} \M{P} \DB {n_h', n_y'}} \NR
-\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR[+]
-}
-}
-
-More trickily, but by the same idea,
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \M{F} \DB {n_h, n_y}
-\M{F} \DB {n_h', n_y'}
-\M{F} \DB {n_h'', n_y''}
-\M{F} \DB {n_h''', n_y'''} \NR
-\NC = \NC
-\i_4 \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_4 \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D 4 N_R^4 \l_R^8 \l_B^8 \NR
-\NC \NC \FourQ +\i_{2,2} \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_{2,2} \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D N_R^4 \l_R^8 \l_B^8 \NR[+]
-}
-}
-
-Now, fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we shall study the probability concentration of \m {\VNm {\M{F}_B \V{u}}_2^2} and \m {\VNm {\M{F}_B \V{u}}_2^4}.
-The two moments are present in Chebyshev bound.
-\Disp{
-\NC \NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2} \NR
-\NC = \NC \MB{E} \SB {
-  \sum_{n_y=0}^{N_y-1}
-  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
-} \NR
-\NC = \NC \sum_{n_y=0}^{N_y-1}
-  \MB{E} \SB {\Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2}
-\NR
-\NC = \NC
-\sum_{n_y=0}^{N_y-1}
-  \MB{E} \SB {
-     2 \sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
-       \MF {Re} \SB{
-         \M{Q} \DB {n_y, n_h} ^\ast \M{Q} \DB {n_y, n_h'}
-         \V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
-       }
-   } \NR
-\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
-  \MB{E}
-     \SB {\sum_{n_h=0}^{N_h-1} \Nm {\M{Q} \DB {n_y, n_h}}^2 \Nm {\V{u} \DB{n_h}}^2}
-\NR
-\NC = \NC
-2 \sum_{n_y=0}^{N_y-1}
-\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
-\MF {Re} \SB{
-   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
-   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
-}
-\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
-\NR
-\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
-   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
-\NR
-\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR[+]
-}
-Thus, we may set
-\Disp{
-\NC \l_B
-=\NC \l_R \NR
-\NC =\NC \F {1} {\R {N_Y N_R}} \NR[+]
-}
-To make
-\Disp{
-\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2}
-=\NC \VNm {\V{u}} _2 ^2
-}
-
-Similarly, we have to find, in advance, the second moment.
-\Disp{
-\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^4}
-=\NC \MB{E} \SB {
-  \RB {
-    \sum_{n_R=0}^{N_R-1}
-    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{Q} \DB {n_R, n_Y} ^\ast \V{u} \DB{n_Y}} ^2
-  } ^2
-} \NR
-\NC = \NC E_1 +E_2 +E_3 +E_4 +E_5 \NR[+]
-}
-These terms are discussed as immediately follows.
-Without spelling out everything, we notice that as long as a term has a single \m {\M{Q} \DB {n_R, n_Y}} factor, it's expectation is zero.
-The terms that does not vanish is a product of three numbers: How many terms, the moment involving \m {\M{Q} \DB {n_y, n_h}}, the norm of \m {\V{u}}.
-We will repeatedly bound \m {N_R \D (N_R-1) /2} by \m {N_R^2 /2}, and bound \m {\Nm {\V{u}} _2} by \m {\Nm {\V{u}} _2}, and so on.
-\Disp {
-\NC E_1
-=\NC \sum_{n_y=0}^{N_y-1} \sum_{n_h=0}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^4
-\Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC =\NC N_Y^2 \D 4 N_Y ^{-4} \D \VNm {\V{u}} _4 ^4 \NR
-\NC \leq \NC 4 N_Y ^{-2} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-Now we have to bound \m {\i_{1,1} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,2}^2} and \m {\i_{2} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,4}} by \m {M_{B,4}} to simplifying matters, and similar for \m {E_3} and \m {E_4}.
-\Disp {
-\NC E_2
-= \NC \sum _{\Stack { n_y, n_y' =0 \NR n_y <n_y' }}^{N_y-1}
-\sum _{n_h =0}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y', n_h}} ^2
-\Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
-\NC \NC \FourQ + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
-\NC \leq \NC 4 \VNm {\V{u}} _2 ^4 \NR[+]
-}
-\Disp {
-\NC E_3
-=\NC \sum _{n_y, n_y' =0}^{N_y-1}
-\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y', n_h'}} ^2
-\Nm {\V{u} \DB{n_h}} ^2
-\Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \leq \NC 4 N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-\Disp {
-\NC E_4
-=\NC \sum _{n_y =0}^{N_y-1}
-\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y, n_h'}} ^2
-\Nm {\V{u} \DB{n_h}} ^2
-\Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \leq \NC 4 N_H ^2 N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-
-The last one is more complicated.
-Use the shorthand
-\Disp {
-\NC \sum _{n_h, n_h', m_h, m_h'} ^\star
-:= \NC \sum _{
-   \Stack {
-     0 =n_h <n_h' \NR
-     0 =m_h <m_h' \NR
-     n_h +m_h' =n_h' +m_h \NR
-     \Fl {n_h/N_H} =\Fl {n_h'/N_H} \NR
-     \Fl {m_h/N_H} =\Fl {m_h'/N_H}
-   }
-} ^{N_H-1}
-\sum _{
-  \Stack {
-     0 =n_y <n_y' \NR
-     \Fl {n_y/N_Y} =\Fl {n_y'/N_Y}
-  }
-} ^{N_y-1} \NR
-\NC \V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'}
-:=\NC \i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'}
-\V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \NR
-}
-Then observe
-\Disp {
-\NC \NC \sum _{n_h, n_h', m_h, m_h'} ^\star
-\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
-\NC \leq \NC N_h^{-2}
-\sum_{n_h, n_h' =0} ^{N_h-1}
-\sum_{m_h, m_h' =0} ^{N_h-1}
-\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
-}
-This is because one of \m {n_h, n_h'} and one of \m {m_h, m_h'} may both choose to lie in other \m {\RB {N_H-1} \RB {N_H-2}} blocks (of length \m {N_H}).
-Then we need a corollary that follows from \quotation {Muirhead inequality}.
-\Result
-{Lemma}
-{
-If every component of \m {\V{u} \in \MB {M}_{\MB {C}} \SB {N_h}} is considered as a free variable taking complex values, then
-\Disp {
-\NC \NC \sum_{n_h, n_h' =0} ^{N_h-1}
-\sum_{m_h, m_h' =0} ^{N_h-1}
-\Nm {\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'}} \NR
-\NC \leq \NC \F{1}{6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
-}
-}
-
-Now,
-\Disp {
-\NC E_5
-= \NC \sum _{n_h, n_h', m_h, m_h'} ^\star
-  \M{Q} \DB {n_y, n_h}
-  \M{Q} \DB {n_y, n_h'}
-  \M{Q} \DB {n_y', m_h}
-  \M{Q} \DB {n_y', m_h'} \NR
-  \NC \NC \SixQ
-  \V{u} \DB{n_h}
-  \V{u} \DB{n_h'}
-  \V{u} \DB{m_h}
-  \V{u} \DB{m_h'} \NR
-\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \D N_Y ^{-4} \NR
-\NC \NC \FourQ
-\D N_H^{-2} \sum_{n_h, n_h' =0} ^{N_h-1} \sum_{m_h, m_h' =0} ^{N_h-1}
-\V {u} ^{(1,1,1,1)} \SB {n_h, n_h', m_h, m_h'} \NR
-\NC \leq \NC \F{1}{6} N_Y ^{-1} \VNm {\V{u}} _2 ^4. \NR[+]
-}
-
-In conclusion, \m {E_4} dominates.
-\Disp{
-\NC \Ss{Var} \SB {\VNm {\M{P} \SB {\o_t, \o_r} \V{u}} _2 ^2}
-\leq \NC \RB {4 N_H^2 N_Y^{-3} -1} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-Thus, by Chebyshev bound,
-\Result
-{Theorem}
-{
-Let \m {\M{P} \in \MB {M}_{\MB {C}} \SB {N_R, N_Y}} be generated randomly according to ().
-Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_Y}}, and for any \m {\e >0},
-\Disp{
-\NC \MB{P}
-\SB {
-  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
-  \geq \e \VNm {\V{u}} _2 ^2
-}
-\leq \NC \F {1} {\e^2} \RB {4 N_H^2 N_Y^{-3} -1} \NR[+]
-}
-}
-
-According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), substitution of relevent quantities yields
-\Result
-{Lemma}
-{
-Suppose the probability, according to event space \m {\o_t, \o_r}, that RIP holds for \m {\M{P}} w.r.t.\ \m {\d_s} is \m {p}, then
-\Disp{
-\NC 1 -p
-\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} N_H^2 N_Y^{-3} \NR[+]
-}
-}
-
-\stopsection
-
-\startsection [title={Expected Error Analysis for Complex-Case Dantzig Selector}]
+\startsection [title={Expected Error Analysis for Dantzig Selector}]
+\startsubsection [title={Generalizing Technical Lemmata for Complex Case}]
 
@@
 \leq \NC  4 \R {\log N_h} \NR
-\NC n_g 
-=\NC 1, \ldots, N_h. \NR
 }
@@
 
-\stopsection
+\stopsubsection
 
-\startsection [title={The Main Result}]
+\startsubsection [title={Main Result}]
 
@@
 }
-the bound is true for probability \m {p}, with
+the bound holds for probability \m {p}, with
 \Disp {
@@
 
+\stopsubsection
 \stopsection
-
-\stopchapter

### 2019-06-05 dantzig_selector/report/3_theorems_and_proofs.tex
Slides: Complete Draft
Split chap 3 sources

--- 2019-05-28 dantzig_selector/report/3_theorems_and_proofs.tex
@@
 
-Our plan is first to show that \m {\SB {\V {g}}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
-We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections.
-
-\startsection [title={Almost-Sparsity of Array Response \m {\V{a}}}]
-
-\Result
-{Definition}
-{
-For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse according to the \m {\ell_p}-norm with remainder \m {R}, if
-\Disp {
-\NC \VNm {\MC {C} \SB{\V {x}, s}} _p
-\leq \NC R. \NR[+]
-}
-}
-
-Let \m {\f} be fixed.
-It suffices to bound
-\Disp {
-\NC \NC
-\VNm {
-\MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}
-} _2 ^2 \NR[+]
-}
-
-Towards that end, introduce
-\Disp {
-\NC \psi \SB {\f, n_H}
-:=\NC \RB {
-   \RB {
-      \RB {\f \; \Rm{Mod}\; \F{2\pi}{N_H}}
-      +\F {2 \pi n_H} {N_H}
-      +\pi
-   } \;
-   \Rm{Mod}\; \RB {2\pi}
-}
--\pi \NR
-}
-Note that by construction
-\Disp{
-\NC \Nm {\psi \SB {\f, n_H}}
-\leq \NC \pi \NR
-}
-And define the so-called Dirichlet kernel
-\Disp {
-\NC D \SB {\psi'}
-:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
-\NC 0 \leq \NC  \psi' \leq \pi \NR
-}
-Then observe
-\Disp {
-\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {n_H}
-=\NC \F {1}{N_H} D \SB {\psi \SB {\f, n_H}} \NR
-}
-
-Now, it can be verified that
-\Result
-{Lemma}
-{
-For \m {-\pi \leq x < \pi}, we have
-\Disp {
-\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}. \NR[+]
-}
-}
-Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
-\Disp {
-\NC \Nm {D \SB {\psi'} }
-= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}}{\Nm {\sin \SB {\psi' /2}}} \NR
-\NC \leq \NC B \SB {\psi'} \NR
-\NC := \NC \F {48}{\Nm {\psi'^2 -24} \Nm {\psi'}} \NR[+]
-\NC -\pi \leq \NC \psi' < \pi. \NR
-}
-Thus,
-\Disp {
-\NC R^2
-=\NC \F {1}{N_H^2}
-\VNm {
-\MC {C}
-\SB{
-   \sum_{n_H' =0}^{N_H -1}
-   B \SB {\psi \SB {\f, n_H'}}
-   \V {u}_{n_H'},
-   s
-}
-} _2^2
-\NR[+]
-}
-Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
-We seek to bound the \quotation {rectangulars} with an integral, and we have to split the cases that \m {N_H} is odd and even.
-Anyway, a moment's reflection shows
-\Disp {
-\NC R^2
-\leq \NC \F {1}{N_H^2} \D \F {N_H}{2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
-\NC = \NC \F {2304} {N_H \pi^6}
-\int _{s /N_H} ^1 \F{1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
-\NC =\NC \F{1} {2\pi^2 N_H}
-\RB {
-  -\F {8} {u}
-+\F {4\pi^2 u} {24 -\pi^2 u^2}
-+\R{6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R{6}}}
-}
-\Bigg \| _{s/N_H} ^1 \NR
-\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR[+]
-}
-In the last step we bound the lower limit of the second and third term with \m {x' =0}, and leave the dominating \m {1/x'}.
-
-Expanding \m {R} gives
-\Disp {
-\NC R
-\leq \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {\R {s}} {38 N_H}. \NR[+]
-}
-
-Fixing \m {N_H}, it shall be easy to see that rhs is strictly decreasing in \m {N_H}, and the value of \m {s} that minimizes it is about \m {s =5N_H}.
-In the range that we care, rhs is thus strictly decreasing in \m {s}.
-\m {N_H}.
-
-\Result
-{Lemma}
-{
-Let \m {\f \SB {\o_h}} be given, and linear array response \m {\V {a} \SB {\f}} defined as in ().
-Suppose \m {N_H \geq 4}.
-Then, for all instances of \m {\f}, \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
-\Disp{
-\NC R
-\leq \NC \m {\F{1}{3 \R{N_H}}} \NR[+]
-}
-}
-
-Since the bound is also decreasing in \m {N_H}, for concreteness, let us plug in \m {N_H =4} for the upper bound, giving
-\Disp{
-\NC R
-\leq \NC \F {1} {6} \NR[+]
-}
-
-\stopsection
-
-\startsection [title={Almost-Sparsity of Channel Response \m {\M{H}}}]
-
-It remains to bound \m {\VNm {\M {G}} _F}.
-Note that
-\Disp{
-\NC \VNm {\M {G}}_F
-=\NC \VNm {\M {H}}_F \NR[+]
-}
-So it suffices to consider \m {\VNm {\M {H}} _F}.
-
-\Disp{
-\NC \VNm {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F
-\leq \NC \sum _{l=0} ^{L-1} \Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
-\NC \leq \NC
-\sum _{l=0} ^{L-1}
-\Nm {\a_l} \VNm {\V {a} \SB {\f_l}} _2
-\VNm {\V {a} \SB {\th_l}} _2 \NR[+]
-}
-Lastly, we know \m {\ell_1}-norm is larger than \m {\ell_2}-norm.
-Since \m {\ell_1}-norm will be used in later proof, we display the statement about \m {\ell_1}-norm.
-\Disp{
-\NC \NC \MB {E} \SB {\VNm {\MC {C} \SB {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj}} _F} \NR
-\NC \leq \NC \F {1} {9 \R{N_H}} \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}} \NR
-\NC \leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR[+]
-}
-
-\Result
-{Lemma}
-{
-Let \m {\f \SB {\o_h}} and \m {\th \SB {\o_h}} be uniformly, independently distributed in \m {[0,2\pi)}, and let \m {\V {g} \in \MB{V}_\MB{C} \SB{N_h}} be defined as in ().
-If \m {N_h \geq 4^2 =16}, then \m {\V {g}} is almost-\m {s^2 L}-sparse with \m {\ell_1}-residue \m {R} to be
-\Disp {
-\NC R
-\leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR
-}
-}
-
-\stopsection
-
-\startsection [title={Moments of Precoders' and Combiners' entries}]
-
-Our plan is setting the four precoder matrices to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
-Indeed, \m {\d_s \SB {\M{F}_B} \SB {\o_t}} may be found, along similar lines with Achlioptas (2001) and Baraniuk et.\ al.\ (2008).
-We prove a concentration inequality, as explained below, and invoke Chebyshev inequality.
-But before that, we have to investigate the moments of each entry of \m {\M{F}_B \SB {\o_t}} (resp.\ \m {\M{W}_B \SB {\o_t}}) and that of \m {\M{F}_R \SB {\o_t}} (resp.\ \m {\M{W}_R \SB {\o_t}}).
-
-Let us call it a day and set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l >0}.
-They are (with a slight of abuse of meaning of \m {\o_t} and so on)
-\Disp{
-\NC d \o_t
-=\NC \F {1} {\R {\pi} \l} \exp
-  \RB {-\F{1}{\l^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
-d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
-\NC d \o_t
-=\NC \F {1} {\R {\pi} \l} \exp
-  \RB {-\F{1}{\l^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
-d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
-\NC n_R
-= \NC 0, 1, 2, \ldots, N_R -1 \NR
-\NC n_Y
-= \NC 0, 1, 2, \ldots, N_Y -1 \NR
-}
-
-We know that the magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
-\Disp{
-\NC \NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}} \NR
-\NC =\NC \F{\R{\pi}}{2} \l_B \NR[+]
-\NC M_{B,2}
-:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^2} \NR
-\NC =\NC \l_R^2 \NR[+]
-\NC M_{B,4}
-:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y} \SB {\o_t}}^4} \NR
-\NC =\NC 2 \l_R^4 \NR[+]
-}
-Also notice that
-\Disp{
-\NC \NC \MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
-\NC = \NC \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}^2}
-   -\MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}^2} \NR
-\NC \NC \FourQ +2 \Ss {i} \MB{E} \SB {\MF {Re} \SB {\M{F}_B \DB {n_R, n_Y}}}
-      \MB{E} \SB {\MF {Im} \SB {\M{F}_B \DB {n_R, n_Y}}} \NR
-\NC = \NC 0 \NR[+]
-}
-
-Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, which gives probability density
-\Disp{
-\NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Re} \SB {\M{F}_R \DB {n_H, n_R}}} ^2}^{-1/2}
-d \MF{Re} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
-\NC d \o_t
-= \NC \F {1} {\pi} \RB {1 -\RB {\MF{Im} \SB {\M{F}_R \DB {n_H, n_R}}} ^2}^{-1/2}
-d \MF{Im} \SB {\M{F}_R \DB {n_H, n_R}} \NR[+]
-}
-As a result,
-\Disp{
-\NC \NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}} \NR
-\NC =\NC \l_R \NR[+]
-\NC M_{R,2}
-:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^2} \NR
-\NC =\NC \l_R^2 \NR[+]
-\NC M_{R,4}
-:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R} \SB {\o_t}}^4} \NR
-\NC =\NC \l_R^4 \NR[+]
-}
-And again
-\Disp{
-\NC \MB{E} \SB {\M{F}_R \DB {n_R, n_Y}^2}
-= \NC 0 \NR[+]
-}
-
-\startsection [title={Restricted Isometry of \m {P}}]
-
-\Result
-{Definition}
-{
-Let \m {P} be fixed.
-For \m {\MC {T}, \MC {T}' \subset \MC {T} \RB {N_p}}, define the \m {s, s'}-restricted orthogonality constant \m {\tau_{s,s'} \SB {P} >0} to be the smallest number such that
-\Disp {
-\NC \Nm {\IP {P _{\MC {T}} h, P _{\MC {T}'} h'}}
-\leq \NC \tau_{s, s'} \SB {P} \cdot \VNm {h} _2 \VNm {h'} _2 \NR
-}
-}
-
-From \quotation {Decoding from Linear Programming} (Cand\`es and Tao 2005), Lemma 1.1:
-
-\Result
-{Lemma}
-{
-Let \m {\M{P}} be fixed.
-Then \m {\tau_{s, s'} \SB {\M{P}}} is bounded in both direction as follows,
-\Disp {
-\NC \d_{s+s'} \SB {\M{P}} -\max \SB {\CB {\d_s \SB {\M{P}}, \d_{s'} \SB {\M{P}} }}
-\leq \NC \tau_{s, s'} \SB {\M{P}} \NR
-\NC \leq \NC \d_{s+s'} \SB {\M{P}} \NR[+]
-}
-}
-
-Thus \m {\d_s \SB {\M{P}}}, which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
-We may well keep track of \m {\d_s \SB {\M{P}}} only.
-When \m {\M{P}} is clear, we may suppress it.
-
-Similar is true of \m {\d_s \SB {\M{F}_B} \SB {\o_t}}.
-But each entry of \m {P} is a linear combination of products, and such reasoning does not work.
-If only \m {P} were also an i.i.d.\ random matrix, the resulting proof would be easier.
-Is the approach all but lost?
-
-Observe
-\Disp {
-\NC \M{P} ^\Adj \M{P}
-=\NC
-\RB {
-   \RB {\M{K} ^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-   \otimes \RB {\M {K} \M {W}_R \M {W}_B}
-}
-\RB {
-   \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast}
-   \otimes \RB {\M {W}_B \M {W}_R \M {K}}
-} \NR
-\NC =\NC
-\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast \M{K}^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-\otimes \RB {\M {W}_B \M {W}_R \M{K} \M{K}^\Adj \M {W}_R^\Adj \M {W}_B^\Adj} \NR
-\NC =\NC
-\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M {F}_R^\ast \M {F}_B^\ast}
-\otimes \RB {\M {W}_B \M {W}_R \M {W}_R^\Adj \M {W}_B^\Adj}
-\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR
-\NC := \NC \M{Q} \NR[+]
-}
-
-This implies
-\Disp {
-\NC \V{u} ^\Adj \M{P} ^\Adj \M{P} \V{u}
-= \NC \V{u} ^\Adj \M{Q} ^\Adj \M{Q} \V{u} \NR[+]
-}
-or
-\Result
-{Lemma}
-{
-For any instance of \m {\M{P} \SB {\o_t, \o_r}} and \m {\M{Q} \SB {\o_t, \o_r}},
-\Disp{
-\NC \VNm {\M{P} \V{u}} _2
-= \NC \VNm {\M{Q} \V{u}} _2 \NR[+]
-}
-}
-
-And it will turn out that any two distinct entries of \m {\M{Q}} are not correlated.
-
-\Result
-{Definition}
-{
-To make expressions more compact, introduce the indication function \m {\i}, so that, for some injective \m {\s:\; \CB {0, \ldots, M-1} \CB {0, \ldots, N-1}},
-\Disp {
-\NC \i_{a_0, \ldots, a_{M-1}} \SB {x_0, \ldots, x_{N-1}}
-=\NC \startcases
-\NC 1, \MC \Q \exists \s:\; x_0 \cdots x_{N-1}
-=x_{\s \SB {0}} ^{a_0} \cdots x_{\s \SB {M-1}} ^{a_{M-1}} \NR
-\NC 0, \NC \Q \Rm {otherwise} \NR
-\stopcases \NR
-}
-}
-
-For short, denote
-\Disp {
-\NC F :=\NC \M {F}_B \M {F}_R \NR
-\NC W :=\NC \M {W}_R \M {W}_B \NR
-}
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E} \SB {\M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'}} \NR
-\NC = \NC \MB{E} \SB {\M{W}^\Adj \DB {n_Y, n_H} \M{W}^\Adj \DB {n_Y', n_H'}} \NR
-\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR[+]
-}
-}
-
-To see this, expanding the definition
-\Disp {
-\NC \NC \M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'} \NR
-\NC =\NC
-\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H, n_R} \M{F}_B \DB {n_R, n_Y}}
-\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H', n_R} \M{F}_B \DB {n_R, n_Y'}} \NR[+]
-}
-Examine the \m {\i_{1,1} \SB {n_H, n_H'}} factor and \m {\i_{1,1} \SB {n_Y, n_Y'}} factors.
-After taking expectation, the expectation sign is distributed, and every term vanishes.
-Other terms that remains are \m {\i_{2} \SB {n_H, n_H'}} and \m {\i_{2} \SB {n_Y, n_Y'}}, namely
-\Disp {
-\NC \NC \sum_{n_R=0}^{N_R-1}
-\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
-\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
-\NC = \NC N_R \D M_{R,2} M_{B,2} \NR
-}
-
-By the same token,
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E}
-\SB {
-\M{F} \DB {n_H, n_Y}
-\M{F} \DB {n_H', n_Y'}
-\M{F} \DB {n_H'', n_Y''}
-\M{F} \DB {n_H''', n_Y'''}
-} \NR
-\NC \NC =\MB{E}
-\SB {
-\M{W} \DB {n_Y, n_H}
-\M{W} \DB {n_Y', n_H'}
-\M{W} \DB {n_Y'', n_H''}
-\M{W} \DB {n_Y''', n_H'''}
-} \NR
-\NC = \NC
-\i_4 \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_4 \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D 2 N_R^2 \l_R^4 \l_B^4 \NR
-\NC \NC \FourQ +\i_{2,2} \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_{2,2} \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D N_R^2 \l_R^4 \l_B^4 \NR[+]
-}
-}
-
-A moment's reflection shows
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \MB{E} \SB {\M{P} \DB {n_h, n_y} \M{P} \DB {n_h', n_y'}} \NR
-\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR[+]
-}
-}
-
-More trickily, but by the same idea,
-\Result
-{Lemma}
-{
-\Disp {
-\NC \NC \M{F} \DB {n_h, n_y}
-\M{F} \DB {n_h', n_y'}
-\M{F} \DB {n_h'', n_y''}
-\M{F} \DB {n_h''', n_y'''} \NR
-\NC = \NC
-\i_4 \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_4 \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D 4 N_R^4 \l_R^8 \l_B^8 \NR
-\NC \NC \FourQ +\i_{2,2} \SB {n_H, n_H', n_H'', n_H'''}
-\D \i_{2,2} \SB {n_Y, n_Y', n_Y'', n_Y'''}
-\D N_R^4 \l_R^8 \l_B^8 \NR[+]
-}
-}
-
-Now, fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we shall study the probability concentration of \m {\VNm {\M{F}_B \V{u}}_2^2} and \m {\VNm {\M{F}_B \V{u}}_2^4}.
-The two moments are present in Chebyshev bound.
-\Disp{
-\NC \NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2} \NR
-\NC = \NC \MB{E} \SB {
-  \sum_{n_y=0}^{N_y-1}
-  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
-} \NR
-\NC = \NC \sum_{n_y=0}^{N_y-1}
-  \MB{E} \SB {\Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2}
-\NR
-\NC = \NC
-\sum_{n_y=0}^{N_y-1}
-  \MB{E} \SB {
-     2 \sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
-       \MF {Re} \SB{
-         \M{Q} \DB {n_y, n_h} ^\ast \M{Q} \DB {n_y, n_h'}
-         \V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
-       }
-   } \NR
-\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
-  \MB{E}
-     \SB {\sum_{n_h=0}^{N_h-1} \Nm {\M{Q} \DB {n_y, n_h}}^2 \Nm {\V{u} \DB{n_h}}^2}
-\NR
-\NC = \NC
-2 \sum_{n_y=0}^{N_y-1}
-\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
-\MF {Re} \SB{
-   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
-   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
-}
-\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
-\NR
-\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
-   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
-\NR
-\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR[+]
-}
-Thus, we may set
-\Disp{
-\NC \l_B
-=\NC \l_R \NR
-\NC =\NC \F {1} {\R {N_Y N_R}} \NR[+]
-}
-To make
-\Disp{
-\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2}
-=\NC \VNm {\V{u}} _2 ^2
-}
-
-Similarly, we have to find, in advance, the second moment.
-\Disp{
-\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^4}
-=\NC \MB{E} \SB {
-  \RB {
-    \sum_{n_R=0}^{N_R-1}
-    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{Q} \DB {n_R, n_Y} ^\ast \V{u} \DB{n_Y}} ^2
-  } ^2
-} \NR
-\NC = \NC E_1 +E_2 +E_3 +E_4 +E_5 \NR[+]
-}
-These terms are discussed as immediately follows.
-Without spelling out everything, we notice that as long as a term has a single \m {\M{Q} \DB {n_R, n_Y}} factor, it's expectation is zero.
-The terms that does not vanish is a product of three numbers: How many terms, the moment involving \m {\M{Q} \DB {n_y, n_h}}, the norm of \m {\V{u}}.
-We will repeatedly bound \m {N_R \D (N_R-1) /2} by \m {N_R^2 /2}, and bound \m {\Nm {\V{u}} _2} by \m {\Nm {\V{u}} _2}, and so on.
-\Disp {
-\NC E_1
-=\NC \sum_{n_y=0}^{N_y-1} \sum_{n_h=0}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^4
-\Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC =\NC N_Y^2 \D 4 N_Y ^{-4} \D \VNm {\V{u}} _4 ^4 \NR
-\NC \leq \NC 4 N_Y ^{-2} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-Now we have to bound \m {\i_{1,1} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,2}^2} and \m {\i_{2} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,4}} by \m {M_{B,4}} to simplifying matters, and similar for \m {E_3} and \m {E_4}.
-\Disp {
-\NC E_2
-= \NC \sum _{\Stack { n_y, n_y' =0 \NR n_y <n_y' }}^{N_y-1}
-\sum _{n_h =0}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y', n_h}} ^2
-\Nm {\V{u} \DB{n_h}} ^4 \NR
-\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
-\NC \NC \FourQ + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
-\NC \leq \NC 4 \VNm {\V{u}} _2 ^4 \NR[+]
-}
-\Disp {
-\NC E_3
-=\NC \sum _{n_y, n_y' =0}^{N_y-1}
-\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y', n_h'}} ^2
-\Nm {\V{u} \DB{n_h}} ^2
-\Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \leq \NC 4 N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-\Disp {
-\NC E_4
-=\NC \sum _{n_y =0}^{N_y-1}
-\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
-\Nm {\M{Q} \DB {n_y, n_h}} ^2
-\Nm {\M{Q} \DB {n_y, n_h'}} ^2
-\Nm {\V{u} \DB{n_h}} ^2
-\Nm {\V{u} \DB{n_h'}} ^2 \NR
-\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
-\NC \leq \NC 4 N_H ^2 N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-
-The last one is more complicated.
-We need a corollary that follows from \quotation {Muirhead inequality}.
-\Result
-{Lemma}
-{
-If every component of \m {\V{u} \in \MB {M}_{\MB {C}} \SB {N_h}} is considered as a free variable taking complex values, then
-\Disp {
-\NC \NC \sum \i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'}
-\V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \NR
-\NC \leq \NC \F{1}{6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
-}
-}
-
-Now,
-\Disp {
-\NC E_5
-\NC = \sum _{
-    \Stack {
-      0 =n_h <n_h' \NR
-      0 =m_h <m_h' \NR
-      n_h +m_h' =n_h' +m_h \NR
-      \Fl {n_h/N_H} =\Fl {n_h'/N_H} \NR
-      \Fl {m_h/N_H} =\Fl {m_h'/N_H}
-    }
-  } ^{N_H-1}
-  \sum _{\Stack { 0 =n_y <n_y' \NR \Fl {n_y/N_Y} =\Fl {n_y'/N_Y} }} ^{N_y-1} \NR
-  \NC \NC \SixQ
-  \M{Q} \DB {n_y, n_h}
-  \M{Q} \DB {n_y, n_h'}
-  \M{Q} \DB {n_y', m_h}
-  \M{Q} \DB {n_y', m_h'} \NR
-  \NC \NC \SixQ
-  \V{u} \DB{n_h}
-  \V{u} \DB{n_h'}
-  \V{u} \DB{m_h}
-  \V{u} \DB{m_h'} \NR
-\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \D N_Y ^{-4} \NR
-\NC \NC \SixQ
-\D \sum_{n_h, n_h' =0} ^{N_H-1}
-\sum_{m_h, m_h' =0} ^{N_H-1}
-\i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \NR
-\NC \NC \SixQ
-\Nm {\V{u} \DB{n_h}}
-\Nm {\V{u} \DB{n_h'}}
-\Nm {\V{u} \DB{m_h}}
-\Nm {\V{u} \DB{m_h'}} \NR
-\NC \leq \NC \F{1}{6} N_Y ^{-1} N_H ^4 \VNm {\V{u}} _2 ^4. \NR[+]
-}
-
-In conclusion,
-\Disp{
-\NC \Ss{Var} \SB {\VNm {\M{P} \SB {\o_t, \o_r} \V{u}} _2 ^2}
-\leq \NC \F{1}{2} \VNm {\V{u}} _2 ^4 \NR[+]
-}
-Thus, by Chebyshev bound,
-\Result
-{Lemma}
-{
-Let \m {\M{P} \in \MB {M}_{\MB {C}} \SB {N_R, N_Y}} be generated randomly according to ().
-Then, for any fixed \m {\V{u} \in \MB {V}_{\MB {C}} \SB {N_Y}}, and for any \m {\e >0},
-\Disp{
-\NC \MB{P}
-\SB {
-  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
-  \geq \e \VNm {\V{u}} _2 ^2
-}
-\leq \NC \F {1} {2\e^2} \NR[+]
-}
-}
-
-According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), substitution of relevent quantities yields
-\Result
-{Lemma}
-{
-Let \m {\M{F}_B ^\Tr} be found as above.
-Suppose the probability that RIP holds for \m {\M{F}_B} w.r.t.\ \m {\d_s} is \m {P}, then
-\Disp{
-\NC 1 -P
-\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} \NR[+]
-}
-}
-
-\stopsection
-
-\startsection [title={Restricted Isometry of \m {P}}]
-
-The relevent expressions for \m {\M{F}_B ^\Tr} and \m {\M{F}_R ^\Tr} are identical, and same can be said of \m {\M{W}_B} and \m {\M{W}_R}.
-Let \m {\Phi} be either of \m {\M{R}_B ^\Tr}, \m {\M{R}_R ^\Tr}, \m {\M{W}_B}, or \m {\M{W}_B}.
-By Chebyshev bound, we obtain an identical expression,
-\Result
-{Lemma}
-{
-Let \m {\Phi} be generated randomly as above.
-Then, for any fixed complex \m {\V{u}} (with corresponding dimension), and for any \m {\e >0},
-\Disp{
-\NC \MB{P}
-\SB {
-  \Nm {\VNm {\Phi \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
-  \geq \e \VNm {\V{u}} _2 ^2
-}
-\leq \NC \F {1} {2\e^2} \NR[+]
-}
-}
-
-According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), substitution of relevent quantities yields
-\Result
-{Lemma}
-{
-Suppose the probability that RIP holds for \m {\V{P}} w.r.t.\ \m {\d_s} is \m {p}, then
-\Disp{
-\NC 1 -p
-\leq \NC 4 \D 12^s \D \d_s^{-\RB {s+2}} \NR[+]
-}
-}
-
-\stopsection
-
-\startsection [title={Expected Error for Complex-Case Dantzig Selector}]
-
-Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {s} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {s} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {s=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
-We rephrase it formally.
-
-\Result
-{Definition}
-{
-Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
-Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
-\Disp{
-\NC \V{v} \DB {\s \SB {n}}
-\leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
-\NC n =\NC 1, \ldots, N_p-1 \NR
-}
-Its existence is evident.
-
-Let \m {s \leq N_p/2} be fixed.
-Define
-\Disp{
-\NC \MC {S} \SB {\V{x}, s}
-=\NC \sum_{i=0} ^{s-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
-\NC \MC {C} \SB {\V{x}, s}
-=\NC \sum_{i=s} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
-}
-}
-
-Now set
-\Disp{
-\NC \V{g} _\MC {A}
-=\NC \MC {S} \SB {\V{g}, s} \NR[+]
-\NC \V{g} _\MC {K}
-=\NC \MC {C} \SB {\V{g}, s} \NR[+]
-\NC \V{g} _\MC {B}
-=\NC \MC {S} \SB {\V{g} _\MC {K}, s} \NR[+]
-}
-
-Let \m {\hat {\V {g}}} be the Dantzig Selector.
-For concreteness, we set
-\Disp {
-\NC \g 
-= \NC \R {2 \log N_h} \NR[+]
-}
-
-Other values are of course possible, but this is enough to illustrate our purpose.
-Also set for short
-\Disp {
-\NC \V {d} 
-= \NC \Hat {\V {g}} -\V {g} \NR[+]
-}
-
-The rest follows \quotation {The Dantzig Selector} very closely.
-The generalization to complex vector is necessary in our setting.
-We spell out the proof when such generalization is nontrivial.
-
-\Result
-{Lemma}
-{
-Let \m {\V {g}} and \m {\V {d}} be defined as above.
-Then
-\Disp {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {K}}} _1 \NR
-}
-}
-
-To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {K}},
-\Disp {
-\NC \VNm {\V {g}} _1
--\VNm {\V {d} _{\MC {A}}} _1
-+\VNm {\V {d} _{\MC {K}}} _1
--\VNm {\V {g} _{\MC {K}}} _1
-\leq \NC \VNm {\V {g} +\V {d}} _1 \NR
-}
-In the first line, we recall \m {\V {g} =\V {g} _{\MC {A}}}.
-On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
-\Disp {
-\NC \VNm {\V {g} +\V {d}} _1
-=\NC \VNm {\hat {\V {g}}} _1 \NR
-\NC \leq \NC \VNm {\V {g}} _1 \NR
-}
-The result follows by combining.
-
-\Result
-{Lemma}
-{
-\Disp {
-\NC \Nm {\IP { \V {z} \SB {\o_z}, \M {P} \DB {:, n_g} }}
-\leq \NC  2 \R {\log N_h} \NR
-\NC n_g 
-=\NC 1, \ldots, N_h. \NR
-}
-with probability \m {\geq 1 -N_h}.
-}
-
-This only depends on the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
-
-Recall the following bound for \m {Q} function
-\Disp {
-\NC Q\SB {x}
-\leq \NC \F {1}{2} \Ss {e}^{-x^2/2} \NR
-}
-Particularly, for \m {x =\R {2 \log N_h}},
-\Disp {
-\NC Q\SB {\R {2 \log N_h}}
-=\NC \F {1}{N_h}. \NR
-}
-
-\Result
-{Lemma}
-{
-With the condition that \m {\M {P}} satisfies RIP for \m {\d_s \SB {\M{P}}},
-\Disp {
-\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC  4 \R {\log N_h} \NR
-\NC n_g 
-=\NC 1, \ldots, N_h. \NR
-}
-with probability \m {\geq 1 -N_h}.
-}
-
-To show this, by definition
-\Disp {
-\NC \IP { \V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y} }
-= \NC \IP { \M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y} } \NR
-\NC = \NC \IP { \M {P} \V {d}, \M {P} \DB {:,n_y} } \NR
-}
-By construction
-\Disp {
-\NC \VNm { \M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty
-\leq \NC \VNm { \M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}} } _\infty \NR
-\NC \leq \NC 2\R {\log N_h} \NR
-}
-By triangle inequality, together with Lemma (), we have
-\Disp {
-\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
-\leq \NC \VNm {\IP { \V {z}, \M {P} \DB {:,n_y} }} _\infty
-+\IP { \V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y} } \NR
-\NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
-}
-which implies
-\Disp {
-\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC 4 \R {\log N_h}. \NR
-}
-
-From \quotation {Dantzig Selector} Lemma 1, first equation, we have the result as below.
-The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
-The only thing that has to change accordingly is the interpretation of magnitude and the inner product, which are evident.
-
-\Result
-{Lemma}
-{
-With the condition that \m {\M {P}} satisfies RIP for \m {\d_s \SB {\M{P}}},
-\Disp {
-\NC \VNm {\V {d} _{\MC {AB}}} _2
-\leq \NC \F {1}{1-\d_{2s}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3s}}{\RB {1-\d_{2s}} \R {s}} \VNm {d_{\MC {K}}} _1 \NR
-}
-}
-
-From \quotation {Dantzig Selector}, Lemma 1, second equation, we have the result as below.
-Again, their proof works with complex vector spaces in place of real ones too.
-
-\Result
-{Lemma}
-{
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{s} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
-}
-}
-
-\stopsection
-
-\startsection [title={The Main Bound}]
-
-We can now formulate and prove the main bound of ours.
-
-\Result
-{Theorem}
-{
-Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
-Then
-\Disp {
-\NC \VNm {\V {d}} _2
-\leq \NC \F {4}{\pi^4} \d_{3L}^4 \RB {1-2\d_{2L}} L^4 \RB { \log N_H}^4 \NR
-}
-with probability \m {\geq 1 -N_h}.
-}
-
-We are ready to combine previous lemmata.
-The first quantity we want to bound away is
-\Disp {
-\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
-\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
-\NC \leq \NC \R {N_h} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
-\NC \leq \NC 4 \R {N_h \log N_h} \NR
-}
-Thus, by virtue of Lemma (),
-\Disp {
-\NC \VNm { \V {d}_{A} } _1
-\leq \NC \R {L} \VNm { \V {d}_{A} } _2 \NR
-\NC \leq \NC \R {L} \VNm { \V {d} _{\MC {AB}} } _2 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d} _{\MC {K}} } _1 +\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
-}
-
-As the next step, we must eliminate \m {\VNm {d _{\MC {A}}} _1} in rhs of Lemma ().
-\Disp {
-\NC \VNm { \V {d} _{\MC {K}} } _1
-\leq \NC \VNm { \V {d} _{\MC {A}} } _1 +2 \VNm { \V {g} _{\MC {K}} } _1 \NR
-\NC \leq \NC \F {\d_{3L}} {1-\d_{2L}} \VNm { \V {d} _{\MC {K}} } _1
-+2 \VNm { \V {g} _{\MC {K}} } _1
-+\F {4} {1-\d_{2L}} \R {L N_h \log N_h} \NR
-}
-Or,
-\Disp {
-\NC \VNm { \V {d} _{\MC {K}} } _1
-\leq \NC 2 \F {1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \VNm { \V {g} _{\MC {K}} } _1
-+\F {4} {1-\d_{2L} -\d_{3L}} \R {L N_h \log N_h} \NR
-}
-
-We are ready to bound \m {\VNm {d} _2^2}.
-Using Lemma () again, we have
-\Disp {
-\NC \VNm { \V {d} } _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{L} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
-\NC \leq \NC  \RB { \F {\d_{3L}^2} {L^2 \RB {1-\d_{2L}}^2} +\F {1}{L} } \VNm {\V {d} _{\MC {K}}} _1^2
-+\F {8 \d_{3L}} {L \RB {1-\d_{2L}}^2} \R {N_h \log N_h} \VNm {\V {d} _{\MC {K}}} _1 \NR
-\NC \NC \Q +\F {16}{\RB {1-\d_{2L}}^2} N_h \log N_h \NR
-}
-Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {K}}} _1}.
-There are several dozens of terms if we expand all.
-but for simplicity, we keep only the leading term under the approximation
-\Disp {
-\NC 1 \ll \NC L \NR
-\NC \ll \NC N_h \NR
-}
-And expand to the first order expressions containing \m {\d_{2L}} or \m {\d_{3L}} in the denominator using
-\Disp {
-\NC \d_{2L} <\NC \d_{3L} \ll 1. \NR
-}
-Then
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC \F {4}{\pi^4} \d_{3L}^4 \RB {1-2\d_{2L}} L^4 \RB { \log N_H}^4 \NR
-}
-
-\color[red]{(To be done)}
+\input {./3_1_almost_sparsity.tex}
+\input {./3_2_confirming_restricted_isometry.tex}
+\input {./3_3_expected_error_analysis.tex}
 

### 2019-06-12 dantzig_selector/report/2_problem_setting.tex
Proof: Concentration ineq.: Progress of

@@
 \NC \M {Q}
-:= \NC \RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR[+]
+:= \NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR[+]
 }

### 2019-06-17 dantzig_selector/report/1_introduction.tex
Proof: Concentration ineq.: Progress of
Introduction: Add OMP description

@@
 \Disp {
-\NC \V {h}
+\NC \Hat {\V {h}}
 \LA \NC \startcases
@@
 }
-\item Output \m {\V {h}}.
+\item Output \m {\Hat {\V {h}}}.
 }
@@
 \Result
-{Algorithm}
+{Algorithm: Orthogonal Matching Pursuit}
 {
 \startitemize[n]
-\item \color[red]{(To be done)}
+\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
+\item Initialize
+\Disp{
+\NC \V{r}
+\LA \NC \V{y} \NR[+]
+\NC S
+\LA \NC \varnothing \NR[+]
+}
+\item Start the loop with counter \m {i \LA 1}.
+\item Find
+\Disp{
+\NC c
+\LA \NC \underset {i =0, \dots, N_p-1} {\Rm{argmax}}
+\Nm {\M{\Phi} \DB {:,i} \V{r}} \NR[+]
+}
+and insert \m {S \LA S \cup {i}}.
+\item Compute
+\Disp{
+\NC \M{\Phi} ^\ddagger
+\LA \NC \RB {\M{\Phi} \DB {S} ^\Adj \M{\Phi} \DB {S}} ^{-1} \NR[+]
+\NC \V{r}
+\LA \NC \V{y} -\M{\Phi} ^\ddagger \V{y} \NR[+]
+}
+\item Break if
+\Disp{
+\NC \VNm {\M{\Phi} ^\ddagger} _1
+<\NC 1 \NR[+]
+}
+where \m {\VNm {\M{\Phi} ^\ddagger} _1} denotes the operator norm.
+\item Output 
+\Disp {
+\NC \Hat {\V {g}}
+\LA \NC \M{\Phi} ^\ddagger \V{y} \NR[+]
+}
 \stopitemize
 }
-From Tropp and Gilbert (2007a), OMP recovers \m {x} completely, with overwhelming probability.
+Here \m {\V{r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {h} is nonzero (where we have slightly abused the usage of double brackets).
 
-It is interesting to note that, ever since, scholars has applied OMP in favor of DS, due the simplicity of former's implementation, making OMP perhaps the most widely used channel estimation technique.
+From Tropp and Gilbert (2007a), the probability OMP recovers \m {h} completely is overwhelming.
+
+It is interesting to note that, ever since, the channel sensing scholars have applied OMP in favor of DS, due the simplicity of former's implementation, making OMP perhaps the most widely used channel estimation technique.
 
@@
 With (), scholars often exploit the relation
-
 \Result
@@
 \Disp {
-\NC \mathrm{vec} \RB {\M{A}\M{X}\M{B}}
-= \NC \RB {\M{B}^\Tr \otimes \M{A}} \mathrm{vec} \SB {\M{X}} \NR
+\NC \Rm{vec} \SB {\M{A}\M{X}\M{B}}
+= \NC \RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB {\M{X}} \NR
 }

### 2019-06-17 dantzig_selector/code/src/test.py

@@ -1,11 +1,33 @@
 import matplotlib.pyplot as plt # plotting functions
 import numpy as np
 import constants as cst
-#import os # getcwd
+import os # getcwd
 #import cvxpy as cp
 
 import functions as fct
-import matrices as mt
+
+
+tt =np.array (range(3))
+
+pp =np. array ([[4,5,6,3], [0,-2,7,4]])
+g =np. array ([4,4,5,5])
+y =pp @ g
+ss =set ([0,3])
+r =y
+
+t =np.argmin (abs (pp [:, tt].conj().T @ r))
+ss.add(t)
+print (np. array (list(ss))*2)
+
+#i =[1,2,4,5]
+#aa =np.array ([[5,8,-2,-3,0,9], [3,6,7,9,10,11]])
+#bb =aa [:, i]
+#print (bb)
+
+#a =[3,1,2]
+#print (a)
+#a.sort()
+#print (a)
 
 #print (np.random.randint(7, size=10))
 #print (np.sin (1J *np.pi)/ np.pi)
@@ -37,47 +59,5 @@ import matrices as mt
 #print(np.kron(a,b))
 #print (type (np.reshape (a, (1,-1))[0]))
 #print(np.reshape(np.kron(a,b), (1,-1)))
-
-#aa=np.array ([[1,2,3], [4,5,6]])
-#v=np.array ([1,2,3])
-#print (np.shape(aa)[0])
-#print (np.shape(v)[0])
-
-#a =np.array ([[1,2],[4,5]])
-#b =np.array ([1,-1])
-#a[1][1]=3
-#print (a @ b)
-#def fun(v):
-#    return 2*v
-#v =np.array([1,2,3])
-#print (fun(v))
-
-#c=np.array([1,2,3,4,5,6])
-#c=np.zeros(6)
-#c=[1.5*i for i in range(6)]
-#d=np.array([4,5,6,7,8,9])
-#print (np.add (c, 1J *d))
-#c_re =np.reshape(c, (2,-1))
-#print (c_re[1])
-#print (type(c_re[1]))
-#print (np.array (np.reshape(c, (2,-1))[1]))
-#print (c +1J *d)
-
-#
-# # # # # # # # # # # # # # # # # # # #
-#
-#list_x =[1, 2, 4]
-#list_list_y =[[3.5, 6.2, 7], [2.1, 2.2, 2.3], [-0.2, 1, 3]]
-#
-#len_line =len(list_list_y)
-#arr_x =np.array (list_x)
[…]

### 2019-07-02 dantzig_selector/code/src/test.py
Proof: Use Stirling's Approximation

@@ -7,17 +7,16 @@ import os # getcwd
 import functions as fct
 
 
-tt =np.array (range(3))
+#tt =np.array (range(3))
+#pp =np. array ([[4,5,6,3], [0,-2,7,4]])
+#g =np. array ([4,4,5,5])
+#y =pp @ g
+#ss =set ([0,3])
+#r =y
+#t =np.argmin (abs (pp [:, tt].conj().T @ r))
 
-pp =np. array ([[4,5,6,3], [0,-2,7,4]])
-g =np. array ([4,4,5,5])
-y =pp @ g
-ss =set ([0,3])
-r =y
-
-t =np.argmin (abs (pp [:, tt].conj().T @ r))
-ss.add(t)
-print (np. array (list(ss))*2)
+a =[3,4]
+print (np.linalg.norm(a, 2))
 
 #i =[1,2,4,5]
 #aa =np.array ([[5,8,-2,-3,0,9], [3,6,7,9,10,11]])

### 2019-08-13 dantzig_selector/report/3_3_expected_error_analysis.tex
Proof: Complete 3.2: Chebyshev bound
Introduction: Add OMP description
Complete baseline proof
Rid runtime error

@@
 We are going to combine previous lemmata and show the main result.
+
 In accordance with (), set
@@
 Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
-Then, with \m {S =s^2 L}, as \m {N_H \to \infty},
+Then the bound
 \Disp {
 \NC \VNm {\V {d}} _2
-\leq \NC 32 s^2 L \log N_H \NR[+]
+\leq \NC 32 S \log N_H \NR[+]
 }
-Under the design condition
-\Disp {
-\NC \RB {2 N_H}^2
-\approx \NC N_Y^3 \NR[+]
-}
-the bound holds for probability \m {p}, with
+holds for probability \m {p}, with
 \Disp {
 \NC 1 -p
-\leq \NC 16 \D {12}^S \d_{S}^{-S-2} N_H^2 N_Y^{-3} \NR[+]
+\leq \NC 2 \D 6^S \D \exp \SB {-\F{N_Y^2} {32}} \NR[+]
 }
@@
 \NC \VNm {\V {d}} _2^2
-\leq \NC 32 s^2 L \log N_H
+\leq \NC 32 S \log N_H
 +\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
@@
 }
-In particular for asymptotic \m {N_H \gg 1}, keep only the dominating term.
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC 32 s^2 L \log N_H \NR
-}
-
-The probability that it is true may be bounded by plugging the probability in Lemma () and Lemma ().
+Set \m {\d_S =1} for the worst situation, and we get the desired bound.
 

### 2019-08-13 dantzig_selector/report/4_simulation.tex
Rid runtime error

@@
 {
-For \m {\V{x} \in \MB {V}_{\MB {C}} \SB {M}}, we say that \m {\MC {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
+For \m {\V {x} \in \MB {V}_{\MB {C}} \SB {M}}, we say that \m {\MC {R} \SB {\V {x}}} is the real representation of \m {\V {x}}, defined by
 \Disp {
-\NC \MC {R} \SB {\V{x}}
+\NC \MC {R} \SB {\V {x}}
 \in \NC \MB {V}_{\MB {R}} \SB {2M} \NR
-\NC \MC {R} \SB {\V{x}} \DB {m}
+\NC \MC {R} \SB {\V {x}} \DB {m}
 = \NC \startcases
-\NC \MF {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
-\NC \MF {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
+\NC \MF {Re} \SB {\V {x} \DB {m'}}, \MC m =2m' \NR
+\NC \MF {Im} \SB {\V {x} \DB {m'}}, \MC m =2m'+1 \NR
 \stopcases \NR[+]
@@
 \Disp {
-\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V{x}}}
-=\NC \V{x} \NR[+]
+\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V {x}}}
+=\NC \V {x} \NR[+]
 }
@@
 
-By the same token, a moment's reflection reveals the corresponding definition of real representation of matrices.
+Accordingly, the corresponding definition of real representation of matrices is valid, once we call the ring representation of complex numbers.
 
@@
 {
-For \m {\M{A} \in \MB {M}_{\MB {C}} \SB {M_1, M_2}}, we say that \m {\MC {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
+For \m {\M {A} \in \MB {M}_{\MB {C}} \SB {M_1, M_2}}, we say that \m {\MC {R} \SB {\M {A}}} is the real representation of \m {\M {A}}, defined by
 \Disp {
-\NC \MC {R} \SB {\M{A}}
+\NC \MC {R} \SB {\M {A}}
 \in \NC \MB {M}_{\MB {R}} \SB {2M_1, 2M_2} \NR
-\NC \MC {R} \SB {\M{A}} \DB {m_1,m_2} =
+\NC \MC {R} \SB {\M {A}} \DB {m_1,m_2} =
 \NC \startcases
-\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
-\NC \MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
-\NC -\MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
-\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
+\NC \MF {Re} \SB {\M {A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
+\NC \MF {Im} \SB {\M {A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2') \NR
+\NC -\MF {Im} \SB {\M {A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'+1) \NR
+\NC \MF {Re} \SB {\M {A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2'+1) \NR
 \stopcases \NR[+]
@@
 }
-Notice that Here not all matrices in \m {\MB {M}_{\MB {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
+Not all matrices in \m {\MB {M}_{\MB {R}} \SB {2M_1, 2M_2}} are images, but we do not need the inverse function.
 }
@@
 Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
-Now, if we introduce vector \m{\V{m}}
+Now, if we introduce vector \m{\V {m}}
 
@@
 \NC \V {m} \in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
-\NC \V{m} \DB{n_h}
-= \NC \Nm{\V{g} \DB{n_h}} \NR[+]
+\NC \V {m} \DB{n_h}
+= \NC \Nm{\V {g} \DB{n_h}} \NR[+]
 \NC n_h, n_h', n_h'' 
@@
 \Disp{
-\NC \V{t}_i
+\NC \V {t}_i
 \NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
-\NC \V{x}_i
+\NC \V {x}_i
 \NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
-\NC \M{A}_i
+\NC \M {A}_i
 \NC \in \MB {M}_{\MB {R}} \SB {2N_h, 3N_h} \NR
-\NC \V{b}_i
+\NC \V {b}_i
+\NC \in \MB {V}_{\MB {R}} \SB {2N_h} \NR
+\NC \V {c}_i
 \NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
-\NC \V{c}_i
-\NC \in \MB {V}_{\MB {R}} \SB {2N_h} \NR
 \NC d_i
@@
 \Disp{
-\NC \V{t}
+\NC \V {t}
 = \NC \startTheMatrix
-\NC \V{0} \NR
-\NC \V{1} \NR
+\NC \V {0} \NR
+\NC \V {1} \NR
 \stopTheMatrix \NR[+]
-\NC \V{x}'
+\NC \V {x}'
 = \NC \startTheMatrix
 \NC \T {\V {g}}' \NR
-\NC \V{m} \NR
+\NC \V {m} \NR
 \stopTheMatrix \NR[+]
@@
 \Disp{
-\NC \M{A}_i
+\NC \M {A}_i
 = \NC \startTheMatrix
-\NC \T {\M {U}}_{i}, \NC \M{0} \NR
+\NC \T {\M {U}}_{i}, \NC \M {0} \NR
 \stopTheMatrix \NR[+]
-\NC \V{b}_i
-= \NC \V{0} \NR[+]
-\NC \V{c}_i
+\NC \V {b}_i
+= \NC \V {0} \NR[+]
+\NC \V {c}_i
 = \NC \startTheMatrix
-\NC \V{0} \NR
+\NC \V {0} \NR
 \NC \V {u}_{i} \NR
@@
 \Disp{
-\NC \M{A}_i
+\NC \M {A}_i
 = \NC \startTheMatrix
-\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
+\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
 \stopTheMatrix \NR[+]
-\NC \V{b}_i
+\NC \V {b}_i
 =\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
-\NC \V{c}_i
-= \NC \V{0} \NR[+]
+\NC \V {c}_i
+= \NC \V {0} \NR[+]
 \NC d_i
@@
 \item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_y}}, \m{\g > 0}.
-\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
+\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
 \item Calculate
@@
 \NC \Rm {subject} \; \Rm {to}
-\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
-\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
+\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
+\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
 \NC \MC i 
@@
 \Disp{
-\NC \Hat{\T{\V{g}}}
-\LA \NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
+\NC \Hat{\T{\V {g}}}
+\LA \NC \Hat{\V {x}} \DB {0 : 2N_h-1} \NR[+]
 }
@@
 \Disp{
-\NC \Hat{\V{g}}
-\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
+\NC \Hat{\V {g}}
+\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR[+]
 }

### 2019-08-13 dantzig_selector/code/src/classes.py

@@ -6,25 +6,20 @@ import functions as fct
 
 class Hh:
     def __init__ (self):
-        self.zero ()
-
-    def zero (self):
-        self.val = np.zeros ((cst.nn_h, cst.nn_h), dtype=complex)
+        self.val = np.zeros ((cst.nn_hh, cst.nn_hh), dtype=complex)
     
-    def generate (self):
-        self.val = np.zeros ((cst.nn_h, cst.nn_h), dtype=complex)
+    def gen (self):
         for l in range (cst.ll_path):
             aG_l = np.random.normal (cst.amp_mean_hh, cst.amp_std_hh)
             pG_l = (cst.dist_antenna /cst.lG) * np.sin (np.random.uniform (0, 2 * np.pi))
             tG_l = (cst.dist_antenna /cst.lG) * np.sin (np.random.uniform (0, 2 * np.pi))
-            self.val += aG_l * (fct.array_response (pG_l)) @ fct.array_response (pG_l).conj().T
+            self.val += aG_l * (fct.arr_resp (pG_l)) @ fct.arr_resp (pG_l).conj().T
 
 class Zz:
     def __init__ (self):
         self.val = np.zeros ((cst.nn_yy, cst.nn_yy), dtype=complex)
     
-    def generate (self):
-        self.val = np.zeros ((cst.nn_yy, cst.nn_yy), dtype=complex)
+    def gen (self):
         for i in range (cst.nn_yy):
             for j in range (cst.nn_yy):
                 self.val [i] [j] = (
@@ -33,50 +28,49 @@ class Zz:
 
 class Ff_bb:
     def __init__ (self):
-        self.val = np.zeros ((cst.nn_rr, cst.nn_yy))
+        self.val = np.zeros ((cst.nn_rr, cst.nn_yy), dtype=complex)
 
-    def generate (self):
-        self.val = np.zeros ((cst.nn_rr, cst.nn_yy))
+    def gen (self):
         for i in range (cst.nn_rr):
             for j in range (cst.nn_yy):
                 self.val [i] [j] = (
                     np.random.normal (cst.part_mean_bb, cst.part_std_bb)
                     + 1J * np.random.normal (cst.part_mean_bb, cst.part_std_bb))
-        self.val /= power_constr
+        self.val /= np.sqrt (cst.nn_yy)
 
 class Ff_rr:
     def __init__ (self):
[…]

### 2019-08-13 dantzig_selector/code/src/constants.py

@@ -12,11 +12,11 @@ nn_h = nn_hh *nn_hh
 
 num_grid_phase = 8
 amp_mean_hh = 3
-amp_std_hh = 0.5
+amp_std_hh = 1/np.sqrt(2)
 part_mean_bb = 1
 part_std_bb = 0.2
 
-power_constr = nn_rr *nn_yy *10
+#power_constr
 
 
 

### 2019-08-13 dantzig_selector/code/src/main.py

@@ -1,25 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import matplotlib.pyplot as plt
-
-import constants as cst
-import classes as cls
-import functions as fct
-
-list_ss_nn_rr = range()
-
-for ss_nn_rr in list_ss_nn_rr:
-    hh = cls.Hh()
-    ff_bb = cls.Ff_bb()
-    ff_rr = cls.Ff_rr()
-    ww_bb = cls.Ww_bb()
-    ww_rr = cls.Ww_rr()
-    pp = np.kron ()
-
-
-    dd_ss = cls.Dd_ss (pp, y, gG);
-    hh_hat = cst.kk @ inv_vectorize (dd_ss.g_hat) @ cst.kk.conj().T
-
-    oo_mm_pp = cls.Oo_mm_pp (pp, y);
-
-

### 2019-08-13 dantzig_selector/code/src/main_1.py

@@ -1,0 +1,50 @@
+import numpy as np
+import cvxpy as cp
+import matplotlib.pyplot as plt
+
+import constants as cst
+import classes as cls
+import functions as fct
+
+list_ss_nn_rr = [0.01 * 1.5 ** x for x in range (0,5)]
+kk = fct.kk()
+
+#for ss_nn_rr in list_ss_nn_rr:
+ff_bb = cls.Ff_bb()
+ff_rr = cls.Ff_rr()
+ww_bb = cls.Ww_bb()
+ww_rr = cls.Ww_rr()
+hh = cls.Hh()
+zz = cls.Zz()
+
+ff_bb.gen()
+ff_rr.gen()
+ww_bb.gen()
+ww_rr.gen()
+hh.gen()
+zz.gen()
+
+pp = np.kron (ff_bb.val.T @ ff_rr.val.T @ kk.conj(), ww_bb.val @ ww_rr.val @ kk)
+gg = kk.conj().T @ hh.val @ kk
+g = fct.vectorize(gg)
+z = fct.vectorize(zz.val)
+
+y = pp @ g + 2*z
+
+gG = np.sqrt (2*np.log (cst.nn_h))
+
+
+dd_ss = cls.Dd_ss (pp, y, gG);
+dd_ss.run()
+
+hh_hat = kk @ fct.inv_vectorize (dd_ss.g_hat, cst.nn_hh, cst.nn_hh) @ kk.conj().T
+
+print(np.linalg.norm (hh_hat, ord=1))
+
+#print(np.linalg.norm (ff_bb.val, ord=1))
+#print(np.linalg.norm (ff_rr.val, ord=1))
+#print(np.linalg.norm (ww_bb.val, ord=1))
+#print(np.linalg.norm (ww_rr.val, ord=1))
+#print(np.linalg.norm (hh.val, ord=1))
+#print(np.linalg.norm (zz.val, ord=1))
+#quit()

### 2019-08-13 dantzig_selector/code/src/test.py

@@ -15,8 +15,13 @@ import functions as fct
 #r =y
 #t =np.argmin (abs (pp [:, tt].conj().T @ r))
 
-a =[3,4]
-print (np.linalg.norm(a, 2))
+aa=[[1,2,3],[7,8,9]]
+
+#aa=[]
+#b=[[1,3],[2,4]]
+#c=[[5,6],[7,8]]
+#aa.append (np.concatenate ([b,c],axis=1))
+#aa.append (np.concatenate ([b,c],axis=1))
 
 #i =[1,2,4,5]
 #aa =np.array ([[5,8,-2,-3,0,9], [3,6,7,9,10,11]])
@@ -39,24 +44,5 @@ print (np.linalg.norm(a, 2))
 #a =np.array ([[1+2J, 3+4.4J], [-1J, -2.3+3J]])
 #print (a.conj().T)
 
-#a = np.array ([ [(i+j^2) for i in range(5)] for j in range(5)])
-#a = [ [(i+j^2) for i in range(5)] for j in range(5)]
-#print (a)
-#s =set([0,2,4])
-#b =a [:, list(s)]
-#print (b)
-
-
-#a =np.array ([1,2,4,5,7,8])
-#b1 =np.array ([1,-1,0,1,3,6])
-#b2 =np.array ([2,3,4,4.5,1,1])
-#b3 =np.array ([1,3,5,7,5,3])
-#list_dat =[hp.Data(b1,"1st"), hp.Data(b2,"2nd"), hp.Data(b3,"3rd")]
-#hp.draw (a, list_dat, "Number", "Value", "Test")
-
-#print (np.linalg.norm (b, ord='fro'))
-#print(np.kron(a,b))
-#print (type (np.reshape (a, (1,-1))[0]))
-#print(np.reshape(np.kron(a,b), (1,-1)))
 
 

### 2019-08-15 dantzig_selector/presentation_A/5_slide.tex
Code: Correct normalizing constants

--- 2019-05-29 dantzig_selector/presentation/5_slide.tex
@@
 
-\I Analogous to original DS proof, we bound the expected square error, and the successful probability is also bounded by a explicit constant
+\I Analogous to original DS proof, we bound the expected square error, and the successful probability is also bounded by a constant explicit depending on system parameters \m {s} and \m{L}
 }
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
+% % % % % % % % % % % % % % % % % % % % % % % % % %
 \Frame {Future Work}
 {
-\I Check the proof carefullly, especially approximation
+\I Check the proof carefullly, especially the approximation technique
 
@@
 }
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
+% % % % % % % % % % % % % % % % % % % % % % % % % %
 \Frame {References}
 {
-{\tfxx
+{\tfx
 \I D Achlioptas (2001). Database-friendly random projections. In Proceedings of the twentieth ACM SIGMOD-SIGACT-SIGART symposium on Principles of database systems (pp. 274-281). ACM.

### 2019-08-15 dantzig_selector/code/src/classes.py

@@ -4,63 +4,6 @@ import cvxpy as cp
 import constants as cst
 import functions as fct
 
-class Hh:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_hh, cst.nn_hh), dtype=complex)
-    
-    def gen (self):
-        for l in range (cst.ll_path):
-            aG_l = np.random.normal (cst.amp_mean_hh, cst.amp_std_hh)
-            pG_l = (cst.dist_antenna /cst.lG) * np.sin (np.random.uniform (0, 2 * np.pi))
-            tG_l = (cst.dist_antenna /cst.lG) * np.sin (np.random.uniform (0, 2 * np.pi))
-            self.val += aG_l * (fct.arr_resp (pG_l)) @ fct.arr_resp (pG_l).conj().T
-
-class Zz:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_yy, cst.nn_yy), dtype=complex)
-    
-    def gen (self):
-        for i in range (cst.nn_yy):
-            for j in range (cst.nn_yy):
-                self.val [i] [j] = (
-                    np.random.normal (0, 1)
-                    + 1J * np.random.normal (0, 1))
-
-class Ff_bb:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_rr, cst.nn_yy), dtype=complex)
-
-    def gen (self):
-        for i in range (cst.nn_rr):
-            for j in range (cst.nn_yy):
-                self.val [i] [j] = (
-                    np.random.normal (cst.part_mean_bb, cst.part_std_bb)
-                    + 1J * np.random.normal (cst.part_mean_bb, cst.part_std_bb))
-        self.val /= np.sqrt (cst.nn_yy)
-
-class Ff_rr:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_hh, cst.nn_rr), dtype=complex)
-
-    def gen (self):
-        for i in range (cst.nn_hh):
-            for j in range (cst.nn_rr):
-                idx_phase = np.random.randint (cst.num_grid_phase)
-                self.val[i][j] = np.exp (2 * np.pi * 1J * idx_phase /cst.num_grid_phase)
-        self.val /= np.sqrt (cst.nn_rr)
-        
-class Ww_bb:
-    def __init__ (self):
-        self.val = np.zeros ((cst.nn_yy, cst.nn_rr), dtype=complex)
-
-    def gen (self):
[…]

### 2019-08-15 dantzig_selector/code/src/constants.py

@@ -1,22 +1,65 @@
 import numpy as np
 
-dist_antenna = 2
-ll_path = 8
+# # Part 1
 
-lG = 3
+# precoder dimension
 nn_yy = 3
-nn_rr = 5
-nn_hh = 7
+nn_rr = 6
+nn_hh = 9
 nn_y = nn_yy *nn_yy
 nn_h = nn_hh *nn_hh
+num_grid_phase = 16
 
-num_grid_phase = 8
-amp_mean_hh = 3
-amp_std_hh = 1/np.sqrt(2)
-part_mean_bb = 1
-part_std_bb = 0.2
+# channel parameters
+lG_ant = 3
+d_ant = 2
+ll = 4
 
-#power_constr
+# simulation count
+num_scale_ssnnrr = 6
+num_try_gG = 2
+num_repeat = 8
 
+# # # # # # # # # # # # # # # #
+# # Part 2
+# # Uncomment the following to try different values:
 
+# # precoder dimension
+# nn_yy = 4
+# nn_rr = 8
+# nn_hh = 12
+# nn_y = nn_yy *nn_yy
+# nn_h = nn_hh *nn_hh
+# num_grid_phase = 16
 
+# # channel parameters
+# lG_ant = 3
+# d_ant = 2
+# ll = 4
+
+# # simulation count
+# num_scale_ssnnrr = 8
+# num_try_gG = 3
+# num_repeat = 12
+
+# # # # # # # # # # # # # # # #
+# # Part 3
+# # Uncomment the following to try different values:
+
+# # precoder dimension
+# nn_yy = 8
+# nn_rr = 12
+# nn_hh = 16
+# nn_y = nn_yy *nn_yy
+# nn_h = nn_hh *nn_hh
+# num_grid_phase = 16
+
+# # channel parameters
+# lG_ant = 3
+# d_ant = 2
+# ll = 4
+
+# # simulation count
+# num_scale_ssnnrr = 12
+# num_try_gG = 4
+# num_repeat = 16

### 2019-08-15 dantzig_selector/code/src/main_1.py

@@ -1,41 +1,74 @@
+#! /usr/bin/env python3
+
 import numpy as np
 import cvxpy as cp
 import matplotlib.pyplot as plt
+import time
 
 import constants as cst
 import classes as cls
 import functions as fct
 
-list_ss_nn_rr = [0.01 * 1.5 ** x for x in range (0,5)]
+
+# # # # # # # # # # # # # # # # 
+
+pow_low_gG = -int (cst.num_try_gG /2)
+pow_high_gG = cst.num_try_gG + pow_low_gG
+list_gG = [
+    np.sqrt (np.log (cst.nn_h)) * np.sqrt(2) ** x
+    for x in reversed (range (int(pow_high_gG), int(pow_low_gG), -1))]
+
+pow_low_ssnnrr = -int (cst.num_scale_ssnnrr /2)
+pow_high_ssnnrr = cst.num_scale_ssnnrr + pow_low_ssnnrr
+list_ssnnrr = [
+    np.sqrt(2) ** x
+    for x in reversed (range (int(pow_high_ssnnrr), int(pow_low_ssnnrr), -1))]
+
 kk =fct.kk()
-#for ss_nn_rr in list_ss_nn_rr:
+time_start = time.time()
 
-pp = np.kron (
-    fct.ff_bb().T @ fct.ff_rr().T @ kk.conj(),
-    fct.ww_bb() @ fct.ww_rr() @ kk)
-hh =fct.hh()
-gg = kk.conj().T @ hh @ kk
-g = fct.vectorize (gg)
-z = fct.vectorize (fct.zz())
+list_arr_e = []
+for gG in list_gG:
+    arr_e = np.array ([])
+    for ssnnrr in list_ssnnrr:
+        e = 0
+        for _ in range (cst.num_repeat):
+            ff_bb =fct.ff_bb()
+            ff_rr =fct.ff_rr()
+            ww_bb =fct.ww_bb()
+            ww_rr =fct.ww_rr()
+            hh =fct.hh()
+            zz =fct.zz()
+            gg = kk.conj().T @ hh @ kk
 
-#y = pp @ g + z
-y = pp @ g #XXX
+            pp = np.kron (
+                ff_bb.T @ ff_rr.T @ kk.conj(),
+                ww_bb @ ww_rr @ kk)
+            g = fct.vectorize (gg)
+            z = fct.vectorize (zz)
+            y = pp @ g + ssnnrr * z
 
[…]

### 2019-08-15 dantzig_selector/code/src/test.py

@@ -1,3 +1,5 @@
+#! /usr/bin/env python3
+
 import matplotlib.pyplot as plt # plotting functions
 import numpy as np
 import constants as cst
@@ -6,10 +8,18 @@ import os # getcwd
 
 import functions as fct
 
-x =np.random.randint (4, size=2)
-y =np.exp (x)
-print (x)
-print (y)
+#a =[x ** 3 for x in range (-(7/2), 4)]
+#print (a)
+
+#dat_x = np.array ([2,4,6,8])
+#dat_y1 =np.zeros (4)
+#dat_y2 =np.zeros (4)
+#for i in range(4):
+#    dat_y1 [i] = 3 * dat_x [i] + 0.1 * np.random.normal (0, 1)
+#    dat_y2 [i] = 5 * dat_x [i] + 0.1 * np.random.normal (0, 1)
+#list_dat_y =[dat_y1, dat_y2]
+#fct.draw(dat_x, list_dat_y, "foo", "bar", "Quux")
+
 
 #tt =np.array (range(3))
 #pp =np. array ([[4,5,6,3], [0,-2,7,4]])

### 2019-08-15 dantzig_selector/deprecated_src/channel.cpp

@@ -1,37 +1,0 @@
-#include <Eigen/Dense>
-
-#include "channel.h"
-#include "const.h"
-
-void Channel::Channel(int num_path) :
-      num_path(num_path),
-      list_ang_dep(cst::nn, 0),
-      list_ang_arr(cst::nn, 0),
-      list_amp(cst::nn, 0)
-{
-}
-
-void Channel::realize()
-{
-   for(int i=0; i<=this->Const::nn-1; i++)
-   {
-      this ->list_ang_dep[i] =2 *Const::pi *get_normalized_uniform();
-      this ->list_ang_arr[i] =2 *Const::pi *get_normalized_uniform();
-      this ->list_amp.[i] +=get_normalized_gausian() +Const::ii *get_normalized_gausian();
-   }
-}
-
-Mat Parameters::get_channel()
-{
-   Mat ret;
-   ret =ublas::zero_matrix <Comp> (this->Const::nn, this->Const::nn);
-   for(std::int i_path=0; i_path <num_path-1; i_path++)
-   {
-      Mat a_t =get_array_response(cst::a_t_phase *psi);
-      Mat tr_a_r =ublas::trans(get_array_response(cst::a_r_phase *psi));
-      ret =ret +ublas::prod( a_t, tr_a_r );
-   }
-   return ret;
-}
-
-*/

### 2019-08-15 dantzig_selector/deprecated_src/const.cpp

@@ -1,15 +1,0 @@
-#include <map>
-#include <complex>
-#include <Eigen/Dense>
-#include "const.h"
-
-
-const double Const::pi =3.14159265358979;
-const std::complex<double> Const::ii =std::sqrt( static_cast<Comp>(-1) );
-const double Const::array_t_phase =0.5;
-const double Const::array_r_phase =0.6;
-const int Const::nn_hh =24;
-const int Const::nn_rr =12;
-const int Const::nn_bb =4;
-const int Const::max_idx_ssnnrr =10;
-const double Const::step_ssnnrr =0.3;

### 2019-08-15 dantzig_selector/deprecated_src/ddss.h

@@ -1,7 +1,0 @@
-#ifndef DDSS_H
-#define DDSS_H
-
-#include "const.h"
-
-
-#endif

### 2019-08-15 dantzig_selector/deprecated_src/functions.cpp

@@ -1,46 +1,0 @@
-#include <iostream>
-#include <cstdio>
-#include <cstdlib>
-#include <ctime>
-#include <random>
-#include <cassert>
-
-#include <Eigen/Dense>
-
-#include "const.h"
-#include "functions.h"
-#include "channel.h"
-#include "ddss.h"
-#include "oommpp.h"
-
-void write_idx( std::ostream* p_ios )
-{
-   for(int ssnnrr=0; ssnnrr <=Const::max_idx_ssnnrr -1; ssnnrr++)
-      { (*p_ios) << ssnnrr << ' '; }
-
-   (*p_ios) << std::endl;
-}
-
-double get_uniform()
-{
-   std::random_device dev;
-   std::mt19937 gen(dev());
-   std::uniform_real_distribution<> distri(0.0, 1.0);
-   return distri(gen);
-}
-
-double get_normal()
-{
-   std::default_random_engine gen;
-   std::normal_distribution<double> distri(0,1);
-   return distri(gen);
-}
-
-Vec get_array_response(double ang, int nn)
-{
-   assert(nn >=0);
-   Vec ret(nn);
-   for(int n=0; n <=nn -1; n++)
-      { ret(n) =std::exp(Const::ii *static_cast<double>(n) *ang); }
-   return ret;
-}

### 2019-08-15 dantzig_selector/deprecated_src/oommpp.h

@@ -1,8 +1,0 @@
-#ifndef OOMMPP_H
-#define OOMMPP_H
-
-#include "const.h"
-
-
-
-#endif

### 2019-08-15 dantzig_selector/presentation/make.sh

@@ -1,6 +1,0 @@
-#!/usr/bin/env bash
-
-clear
-context main.tex
-cp -f main.pdf main_1.pdf
-cp -f main.pdf main_2.pdf

### 2019-08-15 dantzig_selector/presentation_A/make.sh

@@ -1,0 +1,6 @@
+#!/usr/bin/env bash
+
+clear
+context main.tex
+cp -f main.pdf main_1.pdf
+cp -f main.pdf main_2.pdf

### 2019-08-15 dantzig_selector/code/src/functions.py
Code: Correct several constants

@@ -106,9 +106,8 @@ def indication_repr_mat (n_h):
 
 # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
 
-def draw (dat_x, list_dat_y, label_x, label_y, title):
+def save_plot (data_x, list_data_y, label_x, label_y, list_legend, title):
     plt.close ("all")
-    fig =plt.figure ()
     plt.title (title, fontsize = 15)
     plt.xlabel (label_x, fontsize = 12)
     plt.ylabel (label_y, fontsize = 12)
@@ -122,30 +121,46 @@ def draw (dat_x, list_dat_y, label_x, label_y, title):
     num_marker = 6
     list_marker = ['v', '^', 'o', 's', '*', 'D']
         # triangle down, triangle up, circle, square, star, diamond
-    size_marker = 7 # fixed marker size
-    width_line = 3 # fixed line width
+    size_marker = 7
+    width_line = 3
 
-    size_line =len (dat_x)
-    for i in range (len (list_dat_y)):
-        dat_y =list_dat_y [i]
-        assert (size_line == len (dat_y))
+    assert (len (list_data_y) == len (list_legend))
+    size_line =len (data_x)
+    i = 0
+    for data_y in list_data_y:
+        assert (size_line == len (data_y))
         plt.plot (
-            dat_x,
-            dat_y,
-            markersize =size_marker,
-            linewidth =width_line,
-            linestyle =list_style [int (i % num_style)],
-            color =list_color [int (i % num_color)],
-            marker =list_marker [int (i % num_marker)])
-    # TODO: legend
+            data_x,
+            data_y,
+            markersize = size_marker,
+            linewidth = width_line,
+            linestyle = list_style [int (i % num_style)],
+            color = list_color [int (i % num_color)],
+            marker = list_marker [int (i % num_marker)],
+            label = list_legend [i])
+        i += 1
+    plt.legend (bbox_to_anchor = (1.05, 1), loc = 'upper left', borderaxespad = 0.)
 
-    path_fig_out =(
+    path_plot_out =(
         os.path.abspath (os.path.join (os.getcwd (), os.path.pardir))
-        +"/plt/" +title +".png")
-    if os.path.isfile(path_fig_out):
-        os.system("rm "+path_fig_out)
-    plt.savefig (path_fig_out, bbox_inches ="tight")
+        + "/plt/" + title.replace (" ", "_") +".png")
[…]

### 2019-08-17 dantzig_selector/presentation_B/1_introduction.tex
Creating new slides (with simulation)

\blank [big, force]

\Title {\TitleText}
\Subtitle {II. Completing the Proof}
\blank [big]

\Subtitle {\AuthorText}
\blank [big]

\Subsubtitle {\DateText}

\page [yes]
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Organization}
{
\I Introduction

\I Problem Setting and Proposed Method

\I Proving the performance bound: Sparsity, Concentration Inequality, and Expected Error

\I Conclusion and Future Work

\I References
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Background}
{
\I Multiple-input-multiple-output (MIMO) wireless communication is expected to be the next-generation r\'egime.

\I But channel response has to be known at the receiver to facilitate such algorithms as beamforming and channel calibration.

\I It calls for high complexity to estimate MIMO channels.

\I Meanwhile, millimeter wave (mmWave) channels often exhibit sparse properties.

\I Under mmWave setting, if the sparsity is exploited, can few observations suffice to estimate the channel?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Compressive Sensing}
{
\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \it{compressed sensing} (CS) address exactly that.

\I The problem can be considered to be inverting a wide, rectangular matrix.
With insufficient (even noisy) measurements, this does not make sense.

\I But what if we impose other conditions?
Indeed, it turns out that, when the signal is sparse, few observations may be sufficient for the reconstruction.
And Dantzig Selector (DS), proposed by Cand\`es and Tao (2006) in the advent, is a possible solution.
}

### 2019-08-17 dantzig_selector/presentation_B/3_proof.tex
Creating new slides (with simulation)

\Frame {The Need of Bounding the Expected Error}
{
\I Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but it is not clear it is true for \m {\M {P}}, for what design of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}.

\I Cand\`es and Tao established the case for real matrices, but it is not clear whether complex case applies.

\I Cand\`es and Tao showed the Big-O error bound in terms of (in our notation) \m {N_H}, but it is worth investigation whether, for practical values, the algorithm converges quickly enough.
}

\Frame {Restricted Isometry Property}
{
\I \m {\V {x}} is called \m {s}-sparse, if only \m {s} of its components are nonzero.

\I We say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {x}}^2
\leq \NC \VNm {\M{\Phi} \V {x}} _2^2
\leq \RB {1+\d_s} \VNm {\V {x}} _2^2
}

\I Interpretation: \m {\M{\Phi}} is \quotation {almost unitary} up to \quotation {relative error} \m {\d_s}.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof Strategy}
{
\I Show that \m {\V{g}} is almost sparse

\I Find \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^2}} and \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^4}}

\I Bound \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^k}} for \m {k=6,8,10,\dots}.

\I Bound the probability that \m {\Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2} \geq \e \VNm {\V{u}} _2 ^2} by Chernoff Bound.

\I Established that \m {\M{P}} satisfies RIP for such probability by invoking existing results

\I Substitute \m {\VNm {\V {g} _{\MC {K}}} _1} into the original Dantzig Selector Proof
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Let \m {s} be a small integer.
Call the vector of largest-magnitude \m {s^2 L} positions of \m {\V{g}} to be \m {\V{g}_A}, and remaining positions of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}

\I We can show that 
\Disp {
\NC \V{g}_K
\leq R
:= \NC \VNm {\MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}} _2
\leq \m {\F{1}{3 \R{N_H}}} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Design of \m {\M{F}_B}}
{
\I Set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by \m {\l_B >0}

\I The magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
\Disp {
\NC M_{B,2}
:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2}
=\l_R^2 \NR
\NC M_{B,4}
:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^4}
=2 \l_R^4 \NR
}

\I We have \m {\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} =0}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Design of \m {\M{F}_R}}
{
\I Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, giving
\Disp{
\NC M_{R,2}
:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R}}^2}
=\l_R^2 \NR
\NC M_{R,4}
:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R}}^4}
=\l_R^4 \NR
}

\I We have \m {\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2} =0}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Indicator Function}
{
\I To make expressions more compact, introduce the indication function \m {\i}, which \m {=1} only when the manner that arguments repeat agrees exactly with the subscripts

\I For example \m {\i_{2} \SB {7,7} =1}, and \m {\i_{2,2} \SB {0,3,3,0} =1}, but \m {\i_{2} \SB {5, 6} =0}

\I That is, for some injective \m {\s:\; \CB {0, \ldots, M-1} \mapsto \CB {0, \ldots, N-1}},
\Disp {
\NC \NC \i_{a_0, \ldots, a_{N-1}} \SB {x_0, \ldots, x_{M-1}} \NR
\NC =\NC \startcases
\NC 1, \MC \Q
x_0 \cdots x_{N-1}
=x_{\s \SB {0}} ^{a_0} \cdots x_{\s \SB {M-1}} ^{a_{M-1}} \NR
\NC 0, \NC \Q \Rm {otherwise} \NR
\stopcases \NR
}

}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Suffice to Ignore \m {\M{K}}}
{
\I Recall \m {\M {P} := \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}}

\I Define \m {\M{Q} :=\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R}}, then
\Disp {
\NC \V{u} ^\Adj \M{P} ^\Adj \M{P} \V{u}
= \NC \V{u} ^\Adj \M{Q} ^\Adj \M{Q} \V{u} \NR
}

\I Thus
\Disp {
\NC \VNm {\M{P} \V{u}} _2
= \NC \VNm {\M{Q} \V{u}} _2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Finding \m {\MB {E} \VNm {\M{P} \V{u}} _2 ^2}}
{
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{Q} \V{u}} _2 ^2} \NR
\NC = \NC \MB{E} \SB {
  \sum_{n_y=0}^{N_y-1}
  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
} \NR
\NC = \NC
2 \sum_{n_y=0}^{N_y-1}
\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
\MF {Re} \SB{
   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
}
\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
\NR
\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
\NR
\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Confirming the RIP of \m {\M{P}}}
{
\I Finding the variance
\Disp{
\NC \Ss{Var} \SB {\VNm {\M{P} \V{u}} _2 ^2}
\leq \NC \RB {4 N_H^2 N_Y^{-3} -1} \VNm {\V{u}} _2 ^4 \NR
}

\I Using the Chebyshev Bound
\Disp{
\NC \MB{P}
\SB {
  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \e \VNm {\V{u}} _2 ^2
}
\leq \NC \F {1} {\e^2} \RB {4 N_H^2 N_Y^{-3} -1} \NR
}
}

% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Expected Error of DS}
{
\I Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then, with \m {S =s^2 L},
\Disp {
\NC \VNm {\V {d}} _2
\leq \NC 32 s^2 L \log N_H \NR
}

\I Moreover, under the design condition
\Disp {
\NC \RB {2 N_H}^2
\approx \NC N_Y^3 \NR
}

\I The bound holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 16 \D {12}^S \d_{S}^{-S-2} \RB {N_H^2 N_Y^{-3} -\F{1}{4}} \NR
}

\I \m {\Rightarrow} Is \m {16 \D {12}^S \d_{S}^{-S-2}} unreasonably large?

\I \m {\Rightarrow} Can \m {N_H^2 N_Y^{-3} -1/4} be made small?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Technical Lemmata}
{
{\tfx
\I Define \m {\V {d} := \Hat {\V {g}} -\V {g}}

\I From optimality of \m {\Hat {\V {g}}}: \m {
\NC \VNm {\V {d} _{\MC {K}}} _1
\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {K}}} _1 \NR
}

\I From central limit theorem: \m {
\NC \MB {E} \SB {\Nm {\IP {\V {z}, \M {P} \DB {:, n_h}}}}
\leq \NC  2 \R {\log N_h} \NR
}

\I From above: \m {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_h} \NR
}

\I From DS paper: \m {
\NC \VNm {\V {d} _{\MC {AB}}} _2
\leq \NC \F {1}{1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}}{\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {K}}} _1 \NR
}

\I From DS paper: \m {
\NC \VNm {\V {d}} _2^2
\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{S} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
}
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof (1 of 2)}
{
\I By \m {\ell_p}-norm ineq., by Lemma for \m {\VNm {\M {P}^\Tr \M {P} \V {d}} _\infty},
\Disp {
\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
\leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty
\leq 4 \R {S \log N_h} \NR
}

\I By \m {\ell_p}-norm ineq., by Lemma for \m {\VNm {\V {d} _{\MC {AB}}} _2}, by above,
\Disp {
\NC \VNm {\V {d}_{\MC {A}}} _1
\leq \NC \R {S} \VNm {\V {d}_{\MC {A}}} _2 \NR
\NC \leq \NC \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
+4 \RB {1+\d_{2S}} S \R {\log N_h} \NR
}

\I By Lemma for \m {\VNm {\V {d} _{\MC {K}}} _1}, by above, by dropping terms,
\Disp {
\NC \VNm {\V {d} _{\MC {K}}} _1
\leq \NC 2 \RB {1+\d_{3S}} \VNm {\V {g} _{\MC {K}}} _1
+4 \RB {1+2\d_{3S}} S \R {\log N_h} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof (2 of 2)}
{
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC 16 S \log N_h
+8 \d_{3S} \R {\log N_h} 
+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {K}}} _1 \NR
\NC \leq \NC 32 s^2 L \log N_H
+\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
+\F {\pi} {9} \F {L} {s^2 N_H} \NR
\NC \leq \NC 32 s^2 L \log N_H \NR
}

1. Plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}

2. Plug in \m {S =s^2 L} and \m {N_h =N_H^2}
}

### 2019-08-18 dantzig_selector/presentation_B/1_introduction.tex
First draft of presentation

@@
 {
-\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \it{compressed sensing} (CS) address exactly that.
+\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \Emph {compressed sensing} (CS) address exactly that.
 

### 2019-08-18 dantzig_selector/presentation_B/3_proof.tex
First draft of presentation

@@
-\Frame {The Need of Bounding the Expected Error}
+\Frame {The Need of a Modified Proof}
 {
-\I Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but it is not clear it is true for \m {\M {P}}, for what design of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}.
+\I \Emph {Q1}: Dantzig Selector works for \Emph {sparse} vectors, but while \m {\M {H}} is sparse in the angular domain, is it sparse by itself?
 
-\I Cand\`es and Tao established the case for real matrices, but it is not clear whether complex case applies.
+\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and for what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?
 
-\I Cand\`es and Tao showed the Big-O error bound in terms of (in our notation) \m {N_H}, but it is worth investigation whether, for practical values, the algorithm converges quickly enough.
+\I \Emph{Q3}: Cand\`es and Tao established the case for real matrices, but does \Emph {complex} case apply?
+
+\I \Emph{Q4}: Cand\`es and Tao showed the Big-O error bound in terms of (in our notation) \m {N_H}, but does, for practical values, the algorithm converges for \Emph {high probability}?
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
+\Frame {Restricted Isometry Property}
+{
+\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.
+
+\I We say that \m {\M{P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
+\Disp {
+\NC \RB {1-\d_s} \VNm {\V {g}}^2
+\leq \NC \VNm {\M{P} \V {g}} _2^2
+\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
 }
 
-\Frame {Restricted Isometry Property}
-{
-\I \m {\V {x}} is called \m {s}-sparse, if only \m {s} of its components are nonzero.
+\I Interpretation: \m {\M{P}} is \Emph {almost unitary} up to relative error \m {\d_s}.
 
-\I We say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
+\I Set shorthand, for any unit vector \m {\V{u}},
 \Disp {
-\NC \RB {1-\d_s} \VNm {\V {x}}^2
-\leq \NC \VNm {\M{\Phi} \V {x}} _2^2
-\leq \RB {1+\d_s} \VNm {\V {x}} _2^2
+\NC \rho := \NC \VNm {\M{P} \V{u}}_2^2 \NR
 }
-
-\I Interpretation: \m {\M{\Phi}} is \quotation {almost unitary} up to \quotation {relative error} \m {\d_s}.
 }
@@
 
-\I Find \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^2}} and \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^4}}
+\I Find \m {\MB {E} \SB {\rho}} and \m {\MB {E} \SB {\rho^2}}, and bound \m {\MB {E} \SB {\rho ^k}} for \m {k=3,4,5,\dots}.
 
-\I Bound \m {\MB {E} \SB {\VNm {\M{P} \V{u}} _2 ^k}} for \m {k=6,8,10,\dots}.
+\I Bound the probability that \m {\Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2} \geq \e \VNm {\V{u}} _2 ^2}.
 
-\I Bound the probability that \m {\Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2} \geq \e \VNm {\V{u}} _2 ^2} by Chernoff Bound.
+\I Establish that \m {\M{P}} satisfies RIP for what probability
 
-\I Established that \m {\M{P}} satisfies RIP for such probability by invoking existing results
-
-\I Substitute \m {\VNm {\V {g} _{\MC {K}}} _1} into the original Dantzig Selector Proof
+\I Take into consideration how \m {\V{g}} is not exactly sparse
 }
@@
 {
-\I Let \m {s} be a small integer.
-Call the vector of largest-magnitude \m {s^2 L} positions of \m {\V{g}} to be \m {\V{g}_A}, and remaining positions of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}
+\I Call the vector of largest-magnitude \m {N_H L} positions of \m {\V{g}} to be \m {\V{g}_A}, and remaining positions of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}
 
@@
 \leq R
-:= \NC \VNm {\MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}} _2
-\leq \m {\F{1}{3 \R{N_H}}} \NR
+:=\m {\F{1}{3 \R{N_H}}} \NR
+}
+
+\I \m {R \to 0} as \m {N_H \to \infty}
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
+\Frame {Concentration Inequality}
+{
+
+\I According to Lemma 5.1 in Baraniuk et.\ al.\ (2008), it has been established that, if the \Emph {concentration inequality} holds that
+\Disp{
+\NC \MB{P}
+\SB {
+  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
+  \geq \F {\d_s} {2} \VNm {\V{u}} _2 ^2
+}
+\leq \NC B \RB {\d_s, N_Y} \NR
+}
+\I then, supppose the probability that RIP holds for \m {\M{P}} is \m {p},
+\Disp{
+\NC 1 -p
+\leq \NC \RB {\F {12 e N_H} {s \d_s}} ^s B \RB {\d_s, N_Y} \NR
+}
+
+\I Our task is reduced into establishment of the inequality!
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
+\Frame {Design of Beamformers}
+{
+\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of Central Limit Theorem,
+\Disp {
+\NC \MB {E} \SB {\rho ^{k}}
+\approx \NC 1
+\quad \Ss {in distribution} \NR
+}
+
+\I Unfortunately, they are \Emph {not i.i.d.}!
+\m {\Rightarrow} Need closer scrutiny.
+
+\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Standard Complex Normal, multiplied by a design constant \m {\l_B >0} (so that the magnitude follows Rayleigh distribution).
+
+\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_B}) be uniformly distributed on the unit circle on the complex plane, multiplied by a design constant \m {\l_B >0}.
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
+\Frame {Chernoff Inequality}
+{
+\I Imitating the Chernoff Inequality argument in classical probability, we have, for any \m {s >0} so that, supposedly, both sides \m {< \infty},
+\Disp {
+\NC p
+= \NC \MB{P} \SB {\rho \geq \RB {1 +\e} \MB{E} \SB {\rho}} \NR
+\NC =\NC \MB{P} \SB {\Ss {e} ^{s \rho} \geq \Ss {e} ^{s \RB {1 +\e}}} \NR
+\NC \leq \NC \Ss {e} ^{-s \RB {1 +\e}} \MB{E} \SB {\Ss {e} ^{s \rho}} \NR
+}
+
+\I Assuming the convergence of power series for a moment,
+\Disp {
+\NC \MB{E} \SB {\Ss {e} ^{s \rho}}
+=\NC \sum_{k=0}^\infty \F{s ^k} {k!} \MB{E} \SB {\rho ^k} \NR
+}
+
+\I But what are the \Emph {moments} of \m {\rho}?
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
+\Frame {Finding the First Moment}
+{
+\I It is easy show that
+\Disp {
+\NC \MB{E} \SB {\rho}
+= \NC N_Y^2 N_R^2 \l_B^4 \l_R^4 \D \VNm {\V{u}} _2 ^2 \NR
+}
+
+\I This motivates
+\Disp {
+\NC \l_B
+=\NC \F {1} {\R {N_Y}},
+\l_R
+=\F {1} {\R {N_R}} \NR
+}
+
+\I So that
+\Disp {
+\NC \MB{E} \SB {\rho}
+=\NC 1
 }
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Design of \m {\M{F}_B}}
+\Frame {Finding the Second Moment}
 {
-\I Set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by \m {\l_B >0}
-
-\I The magnitude \m {\M{F}_B \DB {n_R, n_Y}} follows Rayleigh distribution, having
+\I We can show that, after tedius calculation,
 \Disp {
-\NC M_{B,2}
-:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^2}
-=\l_R^2 \NR
-\NC M_{B,4}
-:=\NC \MB{E} \SB {\Nm {\M{F}_B \DB {n_R, n_Y}}^4}
-=2 \l_R^4 \NR
-}
-
-\I We have \m {\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} =0}
-}
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Design of \m {\M{F}_R}}
-{
-\I Let \m {\M{F}_R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane, giving
-\Disp{
-\NC M_{R,2}
-:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R}}^2}
-=\l_R^2 \NR
-\NC M_{R,4}
-:=\NC \MB{E} \SB {\Nm {\M{F}_R \DB {n_H, n_R}}^4}
-=\l_R^4 \NR
-}
-
-\I We have \m {\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2} =0}
-}
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Indicator Function}
-{
-\I To make expressions more compact, introduce the indication function \m {\i}, which \m {=1} only when the manner that arguments repeat agrees exactly with the subscripts
-
-\I For example \m {\i_{2} \SB {7,7} =1}, and \m {\i_{2,2} \SB {0,3,3,0} =1}, but \m {\i_{2} \SB {5, 6} =0}
-
-\I That is, for some injective \m {\s:\; \CB {0, \ldots, M-1} \mapsto \CB {0, \ldots, N-1}},
-\Disp {
-\NC \NC \i_{a_0, \ldots, a_{N-1}} \SB {x_0, \ldots, x_{M-1}} \NR
-\NC =\NC \startcases
-\NC 1, \MC \Q
-x_0 \cdots x_{N-1}
-=x_{\s \SB {0}} ^{a_0} \cdots x_{\s \SB {M-1}} ^{a_{M-1}} \NR
-\NC 0, \NC \Q \Rm {otherwise} \NR
-\stopcases \NR
-}
-
-}
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Suffice to Ignore \m {\M{K}}}
-{
-\I Recall \m {\M {P} := \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}}
-
-\I Define \m {\M{Q} :=\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R}}, then
-\Disp {
-\NC \V{u} ^\Adj \M{P} ^\Adj \M{P} \V{u}
-= \NC \V{u} ^\Adj \M{Q} ^\Adj \M{Q} \V{u} \NR
-}
-
-\I Thus
-\Disp {
-\NC \VNm {\M{P} \V{u}} _2
-= \NC \VNm {\M{Q} \V{u}} _2 \NR
+\NC \MB{E} \SB {\rho ^2}
+\leq \NC N_Y^4 N_R^4 \l_B^8 \l_R^8 \RB {1 +N_Y^{-2}} \D \VNm {\V{u}} _2 ^4 \NR
+\NC = \NC \RB {1 +N_Y^{-2}} \NR
 }
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Finding \m {\MB {E} \VNm {\M{P} \V{u}} _2 ^2}}
+\Frame {Bounding Higher Moments}
 {
-\Disp{
-\NC \NC \MB{E} \SB {\VNm {\M{Q} \V{u}} _2 ^2} \NR
-\NC = \NC \MB{E} \SB {
-  \sum_{n_y=0}^{N_y-1}
-  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
-} \NR
-\NC = \NC
-2 \sum_{n_y=0}^{N_y-1}
-\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
-\MF {Re} \SB{
-   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
-   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
-}
-\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
-\NR
-\NC \NC \FourQ +\sum_{n_y=0}^{N_y-1}
-   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
-\NR
-\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR
+\I We can show that, after a lot applications of various inequalities,
+\Disp {
+\NC \MB{E} \SB {\rho ^k}
+\leq \NC N_Y^{2k} N_R^{2k} \l_B^{4k} \l_R^{4k}
+\D \G \SB {k +1}^2
+\D \VNm {\V{u}} _2 ^k \NR
+\NC = \NC \G \SB {k +1}^2 \NR
 }
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Confirming the RIP of \m {\M{P}}}
+\Frame {Try to Substite the Moments of \m {\rho}...}
 {
-\I Finding the variance
-\Disp{
-\NC \Ss{Var} \SB {\VNm {\M{P} \V{u}} _2 ^2}
-\leq \NC \RB {4 N_H^2 N_Y^{-3} -1} \VNm {\V{u}} _2 ^4 \NR
+\I Plugging into the Chernoff Inequality we have
+\Disp {
+\NC \log p
+\leq \NC \Min {s >0} \Bigg [
+  -\RB {1 +\F{1}{2} \e -\F{1}{8} \e^2} s \NR
+  \NC \NC \FourQ +\log \RB{
+    1
+    +s \MB{E} \SB {\rho}
+    +\F{s ^2} {2} \MB{E} \SB {\rho^2}
+    +\dots
+  }
+\Bigg ] \NR
 }
 
-\I Using the Chebyshev Bound
+\I We want the exponent to go small, and it looks promising.
+
+\I But the remainder term of MGF, \m {\MB{E} \SB {\Ss {e} ^{s \rho}}}, seems to \Emph {diverge}!
+\Disp {
+\NC \sum_{k=3}^\infty \F{s ^k} {k!} \MB{E} \SB {\rho ^k}
+\leq \NC \sum_{k=3}^\infty \F{s ^k} {k!} \G \SB {k +1}^2
+= \sum_{k=3}^\infty k! \D s ^k
+\to \infty \NR
+}
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
+\Frame {Try Again for \m {\R {\rho}}...}
+{
+\I Take square roots on both sides so that \m {\sum_{k=3}^\infty s ^k} is finite for \m {s <1}.
+\Disp {
+\NC p
+= \NC \MB{P} \SB {\rho \geq \RB {1 +\e} \MB{E} \SB {\rho}} \NR
+\NC =\NC \MB{P} \SB {\Ss {e} ^{s \R {\rho}} \geq \Ss {e} ^{s \R {1 +\e}}} \NR
+\NC \leq \NC \Ss {e} ^{-s \R {1 +\e}} \MB{E} \SB {\Ss {e} ^{s \R {\rho}}} \NR
+}
+
+\I The \m {1/2} and \m {3/2} moments can be bounded by Cauchy Inequality:
+\Disp{
+\NC \F{1}{\R{1+N_Y^{-2}}}
+\leq \NC \MB{E} \SB {\R{\rho}}
+\leq 1, \NR
+\NC 1
+\leq \NC \MB{E} \SB {\rho ^{3/2}}
+\leq \R{1+N_Y^{-2}}, \NR
+}
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
+\Frame {Confirming the Concentration Ineq.}
+{
+\I Thus, Minimizing for \m {s} we have, for any \m {\e >0},
+\Disp {
+\NC \NC \log p \NR
+%
+\NC =\NC \Min {s >0} \Bigg [
+  -\RB {1 +\F{1}{2} \e -\F{1}{8} \e^2} s
+  +\MB{E} \SB {\R{\rho}} s
+  +\F{1}{2} \RB {\MB{E} \SB {\rho} -\MB{E} \SB {\R {\rho}}^2} s^2 \NR
+  \NC \NC \FourQ +\F{1}{6} \RB {-3 \MB{E} \SB {\R {\rho}} \MB{E} \SB {\rho} +2\MB{E} \SB {\R{\rho}} ^3 +\MB{E} \SB {\rho ^{3/2}}} s^3
+  +\dots
+\Bigg ] \NR
+%
+\NC =\NC \Min {s >0} \SB{
+  -\F{1}{2} \e s
+  +\F{1}{2} N_Y^{-2} \RB {1 -N_Y^{-2}} s^2
+  +N_Y^{-2} \RB {\F{1}{3} -\F{5}{24} N_Y^{-2}} s^3
+} \NR
+%
+\NC =\NC -\F{\e^2 N_Y^2} {8} \NR
+}
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %
+\Frame {Confirming the Concentration}
+{
+\I The lower tail can be proved in the same way as upper tail.
+
+\I Conbining we have
 \Disp{
@@
 }
-\leq \NC \F {1} {\e^2} \RB {4 N_H^2 N_Y^{-3} -1} \NR
+\leq \NC 2\exp \SB {-\F{N_Y^2}{8} \e^2} \NR
 }
 }
-
 % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 {
-\I Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
-Then, with \m {S =s^2 L},
+\I In answer of \Emph {Q3}, It can be checked that the generalization from real to complex does not affect the argument, but only loosen the bound by a multiple.
+
+\I In conclusion, and also in answer of \Emph {Q4}, the bound
 \Disp {
 \NC \VNm {\V {d}} _2
-\leq \NC 32 s^2 L \log N_H \NR
+\leq \NC 4 \R{2} \D \R{L N_H \log N_H} \NR
 }
 
-\I Moreover, under the design condition
+\I holds for probability \m {p}, 
 \Disp {
-\NC \RB {2 N_H}^2
-\approx \NC N_Y^3 \NR
+\NC p
+\geq \NC 1 -2 \D 6^{N_H L} \D \exp \SB {-\F{N_Y^2} {32}} \NR
 }
 
-\I The bound holds for probability \m {p}, with
-\Disp {
-\NC 1 -p
-\leq \NC 16 \D {12}^S \d_{S}^{-S-2} \RB {N_H^2 N_Y^{-3} -\F{1}{4}} \NR
+\I Note that \m {p \to 1} as \m {N_Y \to \infty} exponentially.
 }
-
-\I \m {\Rightarrow} Is \m {16 \D {12}^S \d_{S}^{-S-2}} unreasonably large?
-
-\I \m {\Rightarrow} Can \m {N_H^2 N_Y^{-3} -1/4} be made small?
-}
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Technical Lemmata}
-{
-{\tfx
-\I Define \m {\V {d} := \Hat {\V {g}} -\V {g}}
-
-\I From optimality of \m {\Hat {\V {g}}}: \m {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {K}}} _1 \NR
-}
-
-\I From central limit theorem: \m {
-\NC \MB {E} \SB {\Nm {\IP {\V {z}, \M {P} \DB {:, n_h}}}}
-\leq \NC  2 \R {\log N_h} \NR
-}
-
-\I From above: \m {
-\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC  4 \R {\log N_h} \NR
-}
-
-\I From DS paper: \m {
-\NC \VNm {\V {d} _{\MC {AB}}} _2
-\leq \NC \F {1}{1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}}{\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {K}}} _1 \NR
-}
-
-\I From DS paper: \m {
-\NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{S} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
-}
-}
-}
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Proof (1 of 2)}
-{
-\I By \m {\ell_p}-norm ineq., by Lemma for \m {\VNm {\M {P}^\Tr \M {P} \V {d}} _\infty},
-\Disp {
-\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
-\leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty
-\leq 4 \R {S \log N_h} \NR
-}
-
-\I By \m {\ell_p}-norm ineq., by Lemma for \m {\VNm {\V {d} _{\MC {AB}}} _2}, by above,
-\Disp {
-\NC \VNm {\V {d}_{\MC {A}}} _1
-\leq \NC \R {S} \VNm {\V {d}_{\MC {A}}} _2 \NR
-\NC \leq \NC \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
-+4 \RB {1+\d_{2S}} S \R {\log N_h} \NR
-}
-
-\I By Lemma for \m {\VNm {\V {d} _{\MC {K}}} _1}, by above, by dropping terms,
-\Disp {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\leq \NC 2 \RB {1+\d_{3S}} \VNm {\V {g} _{\MC {K}}} _1
-+4 \RB {1+2\d_{3S}} S \R {\log N_h} \NR
-}
-}
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Proof (2 of 2)}
-{
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC 16 S \log N_h
-+8 \d_{3S} \R {\log N_h} 
-+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {K}}} _1 \NR
-\NC \leq \NC 32 s^2 L \log N_H
-+\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
-+\F {\pi} {9} \F {L} {s^2 N_H} \NR
-\NC \leq \NC 32 s^2 L \log N_H \NR
-}
-
-1. Plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}
-
-2. Plug in \m {S =s^2 L} and \m {N_h =N_H^2}
-}

### 2019-08-18 dantzig_selector/presentation_B/5_conclusion.tex
First draft of presentation

--- 2019-08-15 dantzig_selector/presentation_A/5_slide.tex
@@
 {
-\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity
+\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity, and studied Dantzig Selector (DS).
 
-\I Towards that end, We adopt The Dantzig Selector (DS) rather than the popular Orthogonal Matching Pursuit (OMP)
+\I We modified DS for present setting: for almost sparsity, in the angular domain, for the almost-sparse condition, for the beamformer matrix in our setting, and for complex vectors.
 
-\I We generalized DS for complex vectors, and carried it out in the angular domain
-
-\I Analogous to original DS proof, we bound the expected square error, and the successful probability is also bounded by a constant explicit depending on system parameters \m {s} and \m{L}
+\I We bound the expected square error and the successful probability, in explicit expression of system parameters such as \m {N_H}, \m {N_Y}, and \m{L}.
 }
@@
 {
-\I Check the proof carefullly, especially the approximation technique
+\I Check the proof again, especially the approximation decision.
 
-\I Finish the simulation program
+\I Simulate many different parameters such as \m {N_H}, \m {N_Y}, and \m{L} and discuss extensively.
 
-\I Compare the probability bound with simulation result
+\I Verify (if correct) the successful-probability bound and observe how \m {N_Y, N_H} affects it (if any).
 
-\I Also implement OMP and compare they two
+\I Also implement (some or all of) OMP, LS, LASSO among others, and compare them.
 }

### 2019-08-18 dantzig_selector/presentation_B/3_proof.tex
Presentation: Fix minor error

@@
 
-\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and for what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?
+\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?
 
@@
 
-\I \Emph{Q4}: Cand\`es and Tao showed the Big-O error bound in terms of (in our notation) \m {N_H}, but does, for practical values, the algorithm converges for \Emph {high probability}?
+\I \Emph{Q4}: Cand\`es and Tao showed the Big-O error bound in terms of (in our case) \m {N_H}, but does, for practical values, the algorithm converges for \Emph {high probability}?
 }
@@
 {
-\I Show that \m {\V{g}} is almost sparse
+\I Show that \m {\V{g}} is almost sparse.
+
+\I Take into consideration how not exactly sparse \m {\V{g}} is.
 
@@
 
-\I Establish that \m {\M{P}} satisfies RIP for what probability
-
-\I Take into consideration how \m {\V{g}} is not exactly sparse
+\I Establish that \m {\M{P}} satisfies RIP for certain probability.
 }
@@
 {
-\I Call the vector of largest-magnitude \m {N_H L} positions of \m {\V{g}} to be \m {\V{g}_A}, and remaining positions of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}
+\I Call the vector of largest-magnitude \m {N_H L} components of \m {\V{g}} to be \m {\V{g}_A}, and remaining components of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}.
 
@@
 \Disp {
-\NC \V{g}_K
+\NC \VNm{\V{g}_K} _2
 \leq R
-:=\m {\F{1}{3 \R{N_H}}} \NR
+:=\m {\F{1}{3 \R{N_H}}}. \NR
 }
 
-\I \m {R \to 0} as \m {N_H \to \infty}
+\I Note that \m {R \to 0} as \m {N_H \to \infty}
 }
@@
 {
-\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of Central Limit Theorem,
+\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of \m {Central Limit Theorem},
 \Disp {
@@
 \approx \NC 1
-\quad \Ss {in distribution} \NR
+\quad \Ss {in\; distribution} \NR
 }
@@
 
-\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Standard Complex Normal, multiplied by a design constant \m {\l_B >0} (so that the magnitude follows Rayleigh distribution).
+\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Complex Standard Normal, multiplied by a design constant \m {\l_B >0} (so that the magnitude follows Rayleigh distribution).
 
-\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_B}) be uniformly distributed on the unit circle on the complex plane, multiplied by a design constant \m {\l_B >0}.
+\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_R}) be uniformly distributed on the unit circle on the complex plane, multiplied by a design constant \m {\l_B >0}.
 }
@@
 {
-\I Imitating the Chernoff Inequality argument in classical probability, we have, for any \m {s >0} so that, supposedly, both sides \m {< \infty},
+\I Imitating the \Emph {Chernoff Inequality} argument in classical probability, we have, for any \m {s >0} so that, supposedly, both sides \m {< \infty},
 \Disp {
@@
 =\NC \F {1} {\R {N_Y}},
-\l_R
+\quad \l_R
 =\F {1} {\R {N_R}} \NR
@@
 {
-\I We can show that, after tedius calculation,
+\I We can show that, by tedius calculation,
 \Disp {
@@
 {
-\I We can show that, after a lot applications of various inequalities,
+\I We can show that, with applications of various inequalities,
 \Disp {
@@
 \Disp {
-\NC \log p
-\leq \NC \Min {s >0} \Bigg [
-  -\RB {1 +\F{1}{2} \e -\F{1}{8} \e^2} s \NR
-  \NC \NC \FourQ +\log \RB{
-    1
-    +s \MB{E} \SB {\rho}
-    +\F{s ^2} {2} \MB{E} \SB {\rho^2}
-    +\dots
+\NC \NC \log p \NR
+\NC \leq \NC \Min {s >0} \SB {
+  -\RB {1 +\e} s
+  +\log \RB{
+    1 +s \MB{E} \SB {\rho}
+    +\F{s ^2} {2} \MB{E} \SB {\rho^2} +\dots
   }
-\Bigg ] \NR
+} \NR
 }
@@
 {
-\I Take square roots on both sides so that \m {\sum_{k=3}^\infty s ^k} is finite for \m {s <1}.
+\I Take square roots on both sides so that the remainder term is finite for \m {s <1}.
 \Disp {
@@
 
-\I The \m {1/2} and \m {3/2} moments can be bounded by Cauchy Inequality:
+\I The \m {1/2} and \m {3/2} moments can be bounded by Cauchy Ineq.:
 \Disp{
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Expected Error of DS}
+\Frame {Expected Error of Dantzig Selector}
 {

### 2019-08-18 dantzig_selector/presentation_B/5_conclusion.tex
Presentation: Fix minor error

@@
 
-\I We modified DS for present setting: for almost sparsity, in the angular domain, for the almost-sparse condition, for the beamformer matrix in our setting, and for complex vectors.
+\I We modified DS for present setting: for the almost-sparse condition, for the angular domain, for the beamformer matrix \m {\M {P}} in our setting, and for complex vectors.
 

### 2019-08-30 dantzig_selector/depr_presentation/1_slide.tex
Code: Rearrange methods into lambda expressions

--- 2019-05-29 dantzig_selector/presentation/1_slide.tex
@@
 
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
+\page [yes]
+% % % % % % % % % % % % % % % % % % % % % % % % % %
 \Frame {Organization}
 {
-\I Problem Configuration Proposed Method
+\I Problem Configuration
+
+\I Proposed Method
 
@@
 
-\I Concentration Inequality of \m {\M{P}}
-
-\I Restricted Isometry of \m {\M{P}}
+\I Concentration Inequality and Restricted Isometry of \m {\M{P}}
 
@@
 }
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
+% % % % % % % % % % % % % % % % % % % % % % % % % %
 \Frame {Background}
@@
 }
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
+% % % % % % % % % % % % % % % % % % % % % % % % % %
 \Frame {Compressive Sensing}
@@
 
-\I CS addresses the situation that the number of model parameters \m {N_p} the number of measurements \m {N_m}.
+\I CS addresses the situation that the number of model parameters \m {N_p \gg} the number of measurements \m {N_m}.
 
@@
 
-\I Work on CS reveals that few observations of the signal may be sufficient for us to resonstruct the signal when it is sparse.
+\I Much work on CS reveals that few observations of the signal may be sufficient for us to reconstruct the signal when it is sparse.
 
-\I In the advent, Cand\`es and Tao (2006) proposes the Dantzig Selector (DS) as an possible answer.
+\I In the advent, Cand\`es and Tao (2006) propose the Dantzig Selector (DS) as a possible answer.
 }
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
+% % % % % % % % % % % % % % % % % % % % % % % % % %
 \Frametitle {Notation}
-
+{
 {\tfx
@@
 \NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
-\NC \m {\MB {M}_{\MB {K}} \SB {M,N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
+\NC \m {\MB {M}_{\MB {K}} \SB {M,N}} \VL collection of \m {M} by \m {N} matrices \VL \m {\MB {K} =\MB {R}} or \m {\MB {C}} \AR \HL
 \stoptable
 }
-
-\page[yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+}
+% % % % % % % % % % % % % % % % % % % % % % % % % %

### 2019-08-30 dantzig_selector/code/src/algorithms.py

@@ -1,0 +1,213 @@
+import numpy as np
+import cvxpy as cp
+from sklearn.linear_model import Lasso as lasso
+import sys
+
+import constants as cst
+import functions as fct
+
+class Estimation:
+    def __init__ (self, pp, y, hh):
+        self.pp = pp
+        self.y = y
+        self.hh = hh
+        self.g_hat = np.zeros ((cst.nn_h), dtype = complex)
+        self.hh_hat = np.zeros ((cst.nn_hh, cst.nn_hh))
+        self.d = 0
+
+    def refresh ():
+        self.hh = np.zeros ((cst.nn_hh, cst.nn_hh), dtype = complex)
+        self.g_hat = np.zeros ((cst.nn_h), dtype = complex)
+        self.hh_hat = np.zeros ((cst.nn_hh, cst.nn_hh), dtype = complex)
+        self.d = 0
+
+    def convert ():
+        self.hh_hat = (kk
+            @ fct.inv_vectorize (self.g_hat, cst.nn_hh, cst.nn_hh)
+            @ kk.conj().T)
+        self.d = np.log2 (np.linalg.norm (hh_hat -hh, ord=2))
+
+# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
+
+def llss (est):
+    est.refresh ()
+    try:
+        pp_inv = np.linalg.pinv (pp_ss)
+    except np.linalg.LinAlgError:
+        print ("Least square fails!", flush = True)
+        return
+    est.g_hat = pp_inv @ y
+
+
+
+def lasso (est, gamma):
+    est.refresh ()
+    g = cp.Variable (cst.nn_h, complex = True)
+    prob = cp.Problem (
+        cp.Minimize (cp.norm (est.pp @ g - y, 2)),
+        [cp.norm (g, 1) <= gamma])
+    try:
+        prob.solve ()
+    except cp.error.SolverError:
+        print ("Lasso fails!", flush = True)
+        est.g_hat = np.linalg.pinv (est.pp) @ y
+        return
+    est.g_hat = g.value
+
+def oommpp_fixed_times (est, times):
+    est.refresh ()
+    r = y # remainder
+    tt = range (cst.nn_h) # list of column indices
+    ss = [] # extracted column indices
+    count_iter = 0
+    pp_ss_inv = np.zeros ((cst.nn_h, cst.nn_y))
+    while True:
+        count_iter += 1
+        lst_match = [abs (est.pp [:, i].conj().T @ r) for i in tt]
[…]

### 2019-08-30 dantzig_selector/code/src/classes.py

@@ -1,96 +1,0 @@
-import numpy as np
-import cvxpy as cp
-
-import constants as cst
-import functions as fct
-import sys
-
-
-class Ddss:
-    def __init__(self, pp, y, gamma):
-        self.pp = pp
-        self.y = y
-        self.gamma = gamma
-        self.g_hat = np.zeros ((cst.nn_h))
-
-    def run (self):
-        aa=[]
-        b=[]
-        c=[]
-        d=[]
-        for i in range (cst.nn_h):
-            aa.append (
-                np.concatenate (
-                    [fct.indication_repr_mat (i),
-                        np.zeros ((2 * cst.nn_h, cst.nn_h))],
-                    axis= 1))
-            b.append (np.zeros ((2 * cst.nn_h)))
-            c.append (
-                np.concatenate (
-                    [np.zeros ((2 * cst.nn_h)), fct.indication_vec (i)]))
-            d.append (0)
-        for i in range (cst.nn_h):
-            aa.append (
-                np.concatenate (
-                    [-fct.indication_repr_mat (i)
-                            @ fct.find_repr_mat (self.pp.conj().T)
-                            @ fct.find_repr_mat (self.pp),
-                        np.zeros ((2 * cst.nn_h, cst.nn_h))],
-                    axis= 1))
-            b.append (fct.indication_repr_mat (i)
-                @ fct.find_repr_mat (self.pp.conj().T)
-                @ fct.find_repr_vec (self.y))
-            c.append (np.zeros ((3 * cst.nn_h)))
-            d.append (self.gamma)
-        t = np.concatenate (
-            [np.zeros ((2 * cst.nn_h)),
-                np.ones ((cst.nn_h))])
-        x = cp.Variable (3 * cst.nn_h)
-
-        constr = [cp.SOC (c[i].T @ x + d[i], aa[i] @ x + b[i]) for i in range (2 * cst.nn_h)]
-        prob = cp.Problem (cp.Minimize (t.T@x), constr)
-        prob.solve ()
-
-        x_hat = x.value
-        g_repr_hat = x_hat [0 : 2 * cst.nn_h]
-        self.g_hat = fct.inv_find_repr_vec (g_repr_hat)
-
-class Oommpp:
-    def __init__(self, pp, y, epsilon):
-        self.pp = pp
-        self.y = y
-        self.epsilon = epsilon
[…]

### 2019-08-30 dantzig_selector/code/src/test.py

@@ -1,63 +1,38 @@
 #! /usr/bin/env python3
 
 import matplotlib.pyplot as plt # plotting functions
-import numpy as np
-import constants as cst
-import classes as cls
 import os # getcwd
-#import cvxpy as cp
+import numpy as np
+import cvxpy as cp
 
-import functions as fct
+#import functions as fct
+#import constants as cst
 
-a = [3,5,0]
-a.append(1)
-sorted (a)
-print (a)
-a = sorted (a)
-print (a)
-quit ()
+def Foo (a,b):
+    print (a)
+    print (b)
 
-pp = np.array ([[7,8,0], [4,5,2*1J]])
-g = np.array ([5,9,-3])
-z = np.array ([0.1,-0.2])
-y = pp @ g + z
-ss = set ([0,2])
-#lst_ip = [pp [:, i].conj().T @ z for i in list(ss)]
-#lst_ip = [np.array (pp [:, i]).conj().T @ z for i in list(ss)]
-print (pp [:, 2].conj())
+def Baz (fun, x):
+    print ("call!")
+    fun(x)
+
+Baz (lambda x: Foo(x,2), 3)
+
 quit()
 
-pp_ss = pp [:, list(ss)]
-pp_ss_inv = pp_ss.conj().T @ np.linalg.inv (pp_ss @ pp_ss.conj().T)
-g_ss = pp_ss_inv @ y
-g = np.zeros (3)
-for i in range (len(ss)):
-    g [sorted(ss)[i]] = g_ss[i] 
+for _ in range (500):
+    print ("experiment:", _)
+    pp =np.random.normal (0, 1, (10,50))
+    y =np.random.normal (0, 1, (10))
+    g = cp.Variable (50)
+    prob = cp.Problem (
+        cp.Minimize (cp.norm (g, 1)),
+        [cp.norm (pp.conj().T @ (pp @ g - y), "inf") <= 0.5])
+    prob.solve (solver = cp.CVXOPT)
+    g_hat = g.value
+    print (np.linalg.norm (g_hat, ord=1))
 
-print (g_ss)
-print (g)
 
-#ll_ss = Ll_ss (pp, y)
-#ll_ss. run
-
-# dat_x = np.array ([2,4,6,8])
-# dat_y1 =np.zeros (4)
-# dat_y2 =np.zeros (4)
-# for i in range(4):
[…]

### 2019-08-31 depr_presentation/main.tex
Code: Change plot marker

--- 2019-05-28 dantzig_selector/presentation/main.tex
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\blank [big, force]
-\Title {Dantzig Selector \\ Applied on mm-Wave MIMO: \\ Part I. Expected Error Analysis}
-\blank [big]
-\Subtitle {Presenter: Tzu-Yu Jeng \\ Advisor: Prof.\ H.J.\ Su}
-\blank [big]
-\Subsubtitle{May 30, 2019}
-\Subsubtitle{Graduate Instute of Commnication Engineering, \\ National Taiwan University}
-
-\page[yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Organization}
-
-\startitemize
-\I Problem Configuration Proposed Method
-\I Sparsity of Angular Channel Matrix
-\I Concentration Inequality of \m {\M{P}}
-\I Restricted Isometry of \m {\M{P}}
-\I Expected Error of Dantzig Selector
-\I Conclusion and Future Work
-\I References
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
+\input {./1_slide.tex}
+\input {./2_slide.tex}
+\input {./3_slide.tex}
+\input {./4_slide.tex}
+\input {./5_slide.tex}
 
 \stoptext
-
-\Frametitle {Background}
-\startitemize
-
-\I Multiple-input-multiple-output (MIMO) wireless communication is widely expected to be the next-generation communication scheme
-\I But reliable communication requires that the channel response be known at the receiver to facilitate, say, beamforming algorithm and channel calibration
-\I And in the MIMO system, estimating wireless channels calls for high complexity
-\I Meanwhile, in the millimeter wave r\`egime, which is often used together with MIMO, channel often exhibits sparse properties
-\I If the sparsity is exploited, can few observations suffice to estimate the channel?
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Compressive Sensing}
-\startitemize
-
-\I Recent developement on channel estimation is facilitated by advances of so-called compressed sensing (CS)
-\I CS addresses the common situation in statsitical applications that the number of model parameters \m {} the number of measurements \m {}.
-\I With insufficient (possibly noisy) measurements, how well can we recover all \m {} parameters?
-Of course, more assumption must be made.
-\I Work on CS reveals that few observations of the signal may be sufficient for us to resonstruct the signal when it is sparse.
-\I In the advent, Cand\`es and Tao (2006) proposes the Dantzig Selector (DS).
-It was first applied in channel estimation context
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Notation}
-\startitemize
-
-\I \m {} denotes vectors
-\I \m {} denotes matrices
-\I \m {} refers to either \m {} or \m {}.
-\I \m {} is the Hilbert space \m {} over \m {}
-\I \m {} is the collection of \m {} by \m {} matrices.
-\I \m {} denotes the \m {}-norm of \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Definitions: Sparsity}
-\startitemize
-
-\I Suppose \m {}.
-Let \m {}.
-Denote as \m {} the columns of \m {} having indices in \m {}.
-\I \m {} is called \m {}-sparse with support \m {}, \m {}, if only at most \m {} components of \m {} is nonzero.
-\I (New def.) We say \m {} is almost-\m {}-sparse with \m {}-residue \m {}, if \m {} where \m {} is sorted in magnitude.
-
-\stopitemize
 
@@
 \Frametitle {Performance Guarantee of DS}
-\startitemize
 
@@
 
-\stopitemize
-
 \page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 \Frametitle {Definition: Restricted Isometry Property}
-\startitemize
 
@@
 \Frametitle {Orthogonal Matching Pursuit}
-\startitemize
 
@@
 \Frametitle {Recent Literature on Compressive Channel Sensing}
-\startitemize
 
@@
 \Frametitle {Our Work}
-\startitemize
 
@@
 \Frametitle {Channel Model}
-\startitemize
 
@@
 \Frametitle {Precoder Setting}
-\startitemize
 
@@
 \Frametitle {Effective Channel}
-\startitemize
 
@@
 \I It remains to recover \m {} with knowledge of \m {}, while \m {}, \m {}, \m {}, and \m {} are in our control
-
-\stopitemize
 
@@
 \Frametitle {Proposed Program}
-\startitemize
 
@@
 }
-
-\stopitemize
 
@@
 }
-\startitemize[n]
 
@@
 \I Plug the previous eqn.\ into \m {}
-
-\stopitemize
 
@@
 \I Approximation of rectangle to integral
-
-\stopitemize
 
@@
 \I Drop the middle term (\m {}) and last term (small)
-
-\stopitemize
 
@@
 
-\Frametitle {Lemma: RIP Probability w.r.t.\ \m {}}
-Let \m {} be i.i.d.\ Radmacher, as defined in Lemma ().
-Then \m {} is RIP according to \m {} for at least probability
-\Disp{
-1 -2 \left( \F{12}{\d} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\d}{2} N_p \right]
-}
-{\small Source: Baraniuk, Davenport, DeVore, and Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices''}
-
 \page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Preparation for the Proof}
-\startitemize
-
-\I Use \m {} in our case
-\I Let \m {} be the index set of the largest \m {} components of \m {}, \m {} be the index set of the largest \m {} position of \m {} except \m {}, and \m {}
-\I Denote as \m {} the columns of \m {} having indices in \m {}.
-\I Denote \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Lemmata on Vector Supports}
-\startitemize
-
-\I \m {}
-\I \m {}
-\startitemize
-
-\I (modified to account nonzero \m {})
-
-\stopitemize
-
-\stopitemize
-{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Lemmata on RIP Matrix}
-For overwhelming probability,
-\startitemize
-
-\I \m {}
-\I \m {}
-\startitemize
-
-\I (generalized from real case)
-
-\stopitemize
-\I \m {}
-\startitemize
-
-\I (generalized from real case)
-
-\stopitemize
-
-\stopitemize
-{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (1/4)}
-\Disp{
-\|\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}\|_2
-\leq &\|\M{P}^\Tr \M{P} \V{d}\|_2 \NT \\
-\leq &\R{N_g} \|\M{P}^\Tr \M{P} \V{d}\|_\infty \NT \\
-\leq &4 \R{ N_g \log N_g }
-}
-\startitemize[n]
-
-\I Inclusion of larger support
-\I \m {} norm inequality
-\I Plug in the Lemma for \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (2/4)}
-\Disp{
-\| \V{d}_{A} \|_1
-\leq &\R{L} \| \V{d}_{A} \|_2 \NT \\
-\leq &\R{L} \| \V{d}_{\MC{AB}} \|_2 \NT \\
-\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
-}
-\startitemize[n]
-
-\I \m {} norm inequality
-\I Inclusion of larger support
-\I Plug in the Lemma for \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (3/4)}
-\Disp{
-\| \V{d}_{\MC{C}} \|_1
-\leq &\| \V{d}_{\MC{A}} \|_1 +2 \| \V{g}_{\MC{C}} \|_1 \NT \\
-\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1
-+\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
-+2 \| \V{g}_{\MC{C}} \|_1 \\
-\| \V{d}_{\MC{C}} \|_1
-\leq &\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
-+2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| \V{g}_{\MC{C}} \|_1
-}
-\startitemize[n]
-
-\I Copy the Lemma for \m {}
-\I Plug in the previous eqn.\ for \m {}
-\I Cancellation, simplification
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Proof (4/4)}
-\Disp{
-\| \V{d} \|_2^2
-\leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
-\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|\V{d}_{\MC{C}}\|_1^2 \NT \\
-&\quad +\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\
-&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g \\
-\|\V{d}\|_2^2
-\leq &\F{1}{4 \pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_g )^4
-}
-\startitemize[n]
-
-\I Copy the Lemma for \m {}
-\I Plug in the Lemma for \m {}
-\I Plug in the Lemma for \m {}, approximate using \m {}, and \m {}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Conclusion}
-\startitemize[n]
-
-\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity
-\I We adopt The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm
-\I We generalized DS for complex vectors, and we carried it out in the spatial frequency domain \m {}
-\I Analogous to original DS proof, we proved explicitly that the probability that the expected square error is bounded is overwhelming, where the bounding constant is an explicit function of \m {}, the number of path
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {Future Work}
-It remains to
-\startitemize[n]
-
-\I Find the explicit ``overwhelming'' probability
-\I Transform DS into Second Order Cone Problem
-\I Find the Lagrangian and dual problem
-\I Write the simulation, using Newton method
-\I Compare the probability bound with the simulation result
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {References}
-\startitemize[n]
-
-{ \small
-\I W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
-\I R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
-\I S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
-\I E J Cand\`es and J Romberg (2005), ``\m {}-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
-}
-\setcounter{countRef}{\value{enumi}}
-
-\stopitemize
-
-\page [yes] % % % % % % % % % % % % % % % % % % % % % % % % % %
-
-\Frametitle {References}
-\startitemize[n]
-
-\setcounter{enumi}{\value{countRef}} { \small
-\I E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
-\I E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \m {} is Much Larger than \m {}'', \textit{The Annals of Statistics}, Vol.35, No.6.
-\I J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep.
-Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
-\I J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
-}
-
-\stopitemize
-
 \stoptext

### 2019-08-31 presentation/1_introduction.tex
Code: Change plot marker

--- 2019-08-18 dantzig_selector/presentation_B/1_introduction.tex
@@
 
-\I Problem Setting and Proposed Method
+\I Problem setting and proposed method
 
-\I Proving the performance bound: Sparsity, Concentration Inequality, and Expected Error
+\I Proving the performance bound: sparsity, concentration inequality, and expected error
 
-\I Conclusion and Future Work
+\I Simulation (preliminary)
+
+\I Conclusion and future work
 
@@
 {
-\I Multiple-input-multiple-output (MIMO) wireless communication is expected to be the next-generation r\'egime.
+\I \Emph {Multiple-input-multiple-output} (MIMO) wireless communication is expected to be the next-generation r\'egime.
 
@@
 
-\I Meanwhile, millimeter wave (mmWave) channels often exhibit sparse properties.
+\I Meanwhile, \Emph {millimeter wave} (mmWave) channels often exhibit sparse properties.
 
-\I Under mmWave setting, if the sparsity is exploited, can few observations suffice to estimate the channel?
+\I Under mmWave setting, if the \Emph {sparsity} is exploited, it turns out few observations may suffice to estimate the channel.
 }

### 2019-08-31 report/2_problem_setting.tex
Code: Change plot marker

--- 2019-06-12 dantzig_selector/report/2_problem_setting.tex
@@
 \NC \V {a} \SB {\psi'}
-= \NC \F {1}{\R {N_H}} \sum_{n=0}^{N-1} \Ss {e}^{n \psi' \Ss {i}} \V {u}_n \NR
+= \NC \F {1}{\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u}_{n_h} \NR
 }
@@
 \a_l
-\V {a} \SB { \F {d_{\Rm {arr}}} {\l _{\Rm {arr}} \sin \f_l' }}
-\V {a} \SB { \F {d_{\Rm {arr}}} {\l _{\Rm {arr}} \sin \th_l' }}^\Adj \NR[+]
+\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
+\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR[+]
 }
@@
 = \NC \RB {
-\F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
+  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
   \; \Rm{Mod}\; \RB {2\pi}
@@
 = \NC \RB {
-\F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
+  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
   \; \Rm{Mod}\; \RB {2\pi}

### 2019-08-31 report/notation.tex
Code: Change plot marker

\starttitle [title={Notation}]

\starttable[|l|l|l|] \HL
\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
\NC \m {\RB {x+1} \RB {x+2}} \VL round parentheses \VL used only for precedence \AR \HL
\NC \m {f \SB {x}} \VL square brackets \VL used only for arguments or parameter \AR \HL
\NC \m {\CB {2, 3, 5, 7}} \VL curly braces \VL used only for sets \AR \HL
\NC \m {\V {v} \DB {3}} \VL double square brackets \VL used only for entry indices \AR \HL
\NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
\NC \m {\MF {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
\NC \m {\MF {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
\NC \m {\V {a}} \VL vector \VL  \AR \HL
\NC \m {\M {A}} \VL matrix \VL  \AR \HL
\NC \m {\V {1}} \VL all-1 vector \VL dimension will be clear from context \AR \HL
\NC \m {\V {0}} \VL all-0 vector \VL dimension will be clear from context \AR \HL
\NC \m {\V {a} \DB {n}} \VL \m {n}-th component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} \DB {m,n}} \VL \m {m,n}-th entry of \m {\M {A}} \VL  \AR \HL
\NC \m {\MB {K}} \VL either \m {\MB {R}} or \m {\MB {C}} \VL  \AR \HL
\NC \m {\MB {V}_{\MB {K}} \SB {N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL  \AR \HL
\NC \m {\MB {M}_{\MB {K}} \SB {M,N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
\NC \m {\V {a} \DB {0}} \VL the first component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} \DB {0,0}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
\NC \m {m\; \Rm{Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \Rm{Mod}\; n <n} \AR \HL
\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
\NC \m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
\NC  \VL component of \m {\V {a}} \VL  \AR \HL
\NC \m {\MB {P} \SB {A}} \VL probability of \m {A} \VL  \AR \HL
\NC \m {\MB {E} \SB {X}} \VL expectation of \m {X} \VL  \AR \HL
\NC \m {\Ss {Var} \SB {X}} \VL variance of \m {X} \VL  \AR \HL
\stoptable

\stopchapter

### 2019-08-31 code/src/algorithms.py

@@ -138,11 +138,11 @@ def oommpp_infty_norm (est, alpha):
         est.g_hat [ss[i]] = g_hat_ss[i] 
     est.convert ()
 
-def ddss_theory (est):
+def ddss_theory (est, sigma):
     est.refresh ()
-    est.d = (np.log2 (4 * np.sqrt (2 * cst.ll * np.log2 (cst.nn_hh))))
+    est.d = np.log2 (4 * np.sqrt (2 * cst.ll * np.log2 (cst.nn_hh))) * sigma
 
-def ddss_complex (est, gamma):
+def ddss (est, gamma):
     est.refresh ()
     g = cp.Variable (cst.nn_h, complex = True)
     prob = cp.Problem (
@@ -156,57 +156,5 @@ def ddss_complex (est, gamma):
         est.g_hat = (np.linalg.pinv (est.pp) @ est.y)
         return
     est.g_hat = g.value
-    est.convert ()
-
-# Deprecated!
-def ddss_real (est, gamma):
-    est.refresh ()
-    aa=[]
-    b=[]
-    c=[]
-    d=[]
-    for i in range (cst.nn_h):
-        aa.append (
-            np.concatenate (
-                [fct.indication_repr_mat (i),
-                    np.zeros ((2 * cst.nn_h, cst.nn_h))],
-                axis= 1))
-        b.append (np.zeros ((2 * cst.nn_h)))
-        c.append (
-            np.concatenate (
-                [np.zeros ((2 * cst.nn_h)), fct.indication_vec (i)]))
-        d.append (0)
-    for i in range (cst.nn_h):
-        aa.append (
-            np.concatenate (
-                [-fct.indication_repr_mat (i)
-                        @ fct.find_repr_mat (est.pp.conj().T)
-                        @ fct.find_repr_mat (est.pp),
-                    np.zeros ((2 * cst.nn_h, cst.nn_h))],
-                axis= 1))
-        b.append (fct.indication_repr_mat (i)
-            @ fct.find_repr_mat (est.pp.conj().T)
-            @ fct.find_repr_vec (est.y))
-        c.append (np.zeros ((3 * cst.nn_h)))
-        d.append (gamma)
-    t = np.concatenate (
-        [np.zeros ((2 * cst.nn_h)),
-            np.ones ((cst.nn_h))])
-    x = cp.Variable (3 * cst.nn_h) # real
-
[…]

### 2019-08-31 code/src/main.py

@@ -9,10 +9,11 @@ import constants as cst
 import functions as fct
 import algorithms as alg
 
-arr_sigma = np.array (
-    [2 ** x for x in list (
-        (np.array(range (cst.num_try_sigma))
-            - (cst.num_try_sigma - 1) / 2) / 2)])
+arr_sigma = (np.sqrt (2)
+    * np.array (
+        [2 ** x for x in list (
+            (np.array(range (cst.num_try_sigma))
+                - (cst.num_try_sigma - 1) / 2) / 2)]))
 arr_gamma_0_ddss = (np.sqrt (2 * np.log2 (cst.nn_h))
     * np.array (
         [2 ** x for x in list (
@@ -39,15 +40,15 @@ lst_method.append (
 # Orthogonal Matching Pursuit: limited l-infinity norm
 lst_legend.append ("OMP, $l_\infty$-norm")
 lst_method.append (
-    lambda x, y: alg.oommpp_infty_norm (x, y * 2 * np.sqrt (2 * np.log (cst.nn_hh))))
+    lambda x, y: alg.oommpp_infty_norm (x, 2 * y * np.sqrt (2 * np.log (cst.nn_hh))))
 # Dantzig Selector error bound
 lst_legend.append ("DS, theory")
 lst_method.append (
-    lambda x, y: alg.ddss_theory (x))
+    lambda x, y: alg.ddss_theory (x, np.sqrt(2) * y))
 for gamma_0 in arr_gamma_0_ddss:
     lst_legend.append ("DS, $\gamma$ = " + '%.2f' % gamma_0 + "$\sigma$")
     lst_method.append (
-        lambda x, y, g = gamma_0: alg.ddss_complex (x, np.sqrt (2) * y * g))
+        lambda x, y, g = gamma_0: alg.ddss (x, np.sqrt (2) * y * g))
 assert (len (lst_method) == len (lst_legend))
 num_method = len (lst_method)
 
@@ -57,7 +58,7 @@ lst_lst_err_abs = [] # each sigma, each method
 lst_lst_err_rel = [] # each sigma, each method
 for i_sigma in range (cst.num_try_sigma):
     sigma = arr_sigma [i_sigma]
-    print ("σ = " + '%.2f' % sigma + " :", sep = '')
+    print ("σ = ", '%.2f' % sigma, " :", sep = '')
     lst_err_abs = [0] * num_method
     norm_hh = 0
[…]

### 2019-08-31 dantzig_selector/code/src/constants.py

@@ -1,41 +1,0 @@
-# Adjusted part
-
-# # Set 0 (Uncomment to try these values)
-# nn_yy = 2
-# nn_rr = 4
-# nn_hh = 6
-# num_repeat = 8
-
-# # Set 1 (Uncomment to try these values)
-# nn_yy = 3
-# nn_rr = 6
-# nn_hh = 9
-# num_repeat = 12
-
-# # Set 2 (Uncomment to try these values)
-# nn_yy = 4
-# nn_rr = 8
-# nn_hh = 12
-# num_repeat = 18
-
-# Set 3 (Uncomment to try these values)
-nn_yy = 6
-nn_rr = 12
-nn_hh = 18
-num_repeat = 24
-
-# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
-
-# # Fixed part
-
-nn_y = nn_yy * nn_yy
-nn_h = nn_hh * nn_hh
-num_grid_phase = 16
-lG_ant = 3
-d_ant = 2
-ll = 4
-num_try_sigma = 2 * 3 + 1
-num_try_gamma = 2 * 2 + 1 # DS
-#num_method = 9 # LS, Lasso, OMP of 3 kinds, DS theory, DS 3 times
-max_iter_oommpp = 4 * nn_h
-

### 2019-09-05 paper/1_introduction.tex
Delete conversion from complex to real DS

--- 2019-06-17 dantzig_selector/report/1_introduction.tex
@@
 
-To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
-
+To motivate the need, we observe that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
 \Disp {
@@
 }
-
 In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
@@
 For \m {\MC {A} \subseteq \MC {T} \SB {N_p}}, denote
-\Disp{
+\Disp {
 \NC \V {x}  \DB {\MC {A}}
-=\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR[+]
+=\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR
 \NC \M {\Phi}  \DB {\MC {A}}
-=\NC \sum _{i \in \MC {A}} \M {\Phi} \DB {:,i} \NR[+]
+=\NC \sum _{i \in \MC {A}} \M {\Phi} \DB {:,i} \NR
 }
@@
 \leq \NC \VNm {\M{\Phi} \V {x}} _2^2 \NR
-\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
+\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR
 }
@@
 \LA \NC \startcases
-\NC \Min {\V {h}'} \Q \MC \VNm {\V {h}'} _1 \NR
+\NC \Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
 \NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {\Phi}^\Adj \RB {\M {\Phi} \V {h}' -\V {y}}} _\infty \leq \g \NR
@@
 \startitemize[n]
-\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
+\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}, \m {\eta >0}.
 \item Initialize
-\Disp{
+\Disp {
 \NC \V{r}
-\LA \NC \V{y} \NR[+]
+\LA \NC \V{y} \NR
 \NC S
-\LA \NC \varnothing \NR[+]
+\LA \NC \varnothing \NR
 }
@@
 \item Find
-\Disp{
+\Disp {
 \NC c
 \LA \NC \underset {i =0, \dots, N_p-1} {\Rm{argmax}}
-\Nm {\M{\Phi} \DB {:,i} \V{r}} \NR[+]
+\Nm {\M{\Phi} \DB {:,i} \V{r}} \NR
 }
@@
 \item Compute
-\Disp{
+\Disp {
 \NC \M{\Phi} ^\ddagger
-\LA \NC \RB {\M{\Phi} \DB {S} ^\Adj \M{\Phi} \DB {S}} ^{-1} \NR[+]
+\LA \NC \RB {\M{\Phi} \DB {S} ^\Adj \M{\Phi} \DB {S}} ^{-1} \M{\Phi} \DB {S} ^\Adj \NR
 \NC \V{r}
-\LA \NC \V{y} -\M{\Phi} ^\ddagger \V{y} \NR[+]
+\LA \NC \V{y} -\M{\Phi} \DB {S} ^\Adj \M{\Phi} ^\ddagger \V{y} \NR
 }
 \item Break if
-\Disp{
-\NC \VNm {\M{\Phi} ^\ddagger} _1
-<\NC 1 \NR[+]
+\Disp {
+\NC \VNm {\V{r}} _2
+<\NC \eta \NR
 }
@@
 \NC \Hat {\V {g}}
-\LA \NC \M{\Phi} ^\ddagger \V{y} \NR[+]
+\LA \NC \M{\Phi} ^\ddagger \V{y} \NR
 }
@@
 Formally,
-\Disp{
+\Disp {
 \NC \RB {\Rm{vec} \SB {\M{A}}} \DB {m_1}
-=\NC \M{A} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR[+]
+=\NC \M{A} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
 }
@@
 \NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
-=\NC x \NR[+]
+=\NC x \NR
 }
@@
 For \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}} and \m {\M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \MB {M}_{\MB {K}} \SB {N_1 N_3, N_2 N_4}} by
-\Disp{
+\Disp {
 \NC \NC \RB {\M{A} \otimes \M{B}} \DB {m_1, m_2} \NR
 \NC =\NC \M{A} \DB {\Fl{ m_1/N_3 }, \Fl{ m_2/N_4 }}
-\M{B} \DB {m_1\; \Rm{Mod}\; N_3, m_2\; \Rm{Mod}\; N_4} \NR[+]
+\M{B} \DB {m_1\; \Rm{Mod}\; N_3, m_2\; \Rm{Mod}\; N_4} \NR
 }
@@
 
-\Disp{
+\Disp {
 \NC \NC \RB {\Rm{vec} \SB {\M{A}\M{X}\M{B}}} \DB {m_1} \NR
@@
 \NC = \NC \sum _{n_2 =0} ^{N_2 -1} \sum _{n_3 =0} ^{N_3 -1}
-\M{A} \DB {m_1\; \Rm{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR[+]
+\M{A} \DB {m_1\; \Rm{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR
 }
@@
 
-\Disp{
+\Disp {
 \NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB{\M{X}} } \DB {m_1} \NR
@@
 \M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}
-\NR[+]
+\NR
 }

### 2019-09-05 paper/2_problem_setting.tex
Delete conversion from complex to real DS

--- 2019-08-31 report/2_problem_setting.tex
@@
-quad\startchapter [title={Problem Setting}]
+\startchapter [title={Problem Setting}]
 
@@
 \V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
-\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR[+]
+\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR
 }
@@
   \; \Rm{Mod}\; \RB {2\pi}
-} \NR[+]
+} \NR
 \NC \th_l
@@
   \; \Rm{Mod}\; \RB {2\pi}
-} \NR[+]
+} \NR
 }
@@
 \NC \Nm {\M {F}_R \DB {n_H, n_R}}
-= \NC 1, \NR[+]
+= \NC 1, \NR
 \NC \Nm {\M {W}_R \DB {n_R, n_H}}
-= \NC 1, \NR[+]
+= \NC 1, \NR
 \NC n_H
@@
 \Disp {
-\NC N_H \gg \NC N_R \NR[+]
-\NC N_R \gg \NC N_Y \NR[+]
+\NC N_H \gg \NC N_R \NR
+\NC N_R \gg \NC N_Y \NR
 }
@@
 Since we restrict our discussion to a specific slice of time, this random process may be simply taken to be a matrix \m {\M{Z}} with each entry being i.i.d.\ standard Gaussian.
-\Disp{
-\NC \M {Z} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR[+]
+\Disp {
+\NC \M {Z} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR
 }
@@
 \NC N_h
-= \NC N_H^2 \NR[+]
+= \NC N_H^2 \NR
 \NC N_y
-= \NC N_Y^2 \NR[+]
+= \NC N_Y^2 \NR
 }
@@
 \NC \V {h}
-:= \NC \Rm {vec} \SB {\M {H}} \NR[+]
+:= \NC \Rm {vec} \SB {\M {H}} \NR
 \NC \V {y}
@@
 \NC \V {y}
-:= \NC \Rm {vec} \SB {\M {Y}} \NR[+]
+:= \NC \Rm {vec} \SB {\M {Y}} \NR
 \NC \V {z}
@@
 \NC \V {z}
-:= \NC \Rm {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR[+]
+:= \NC \Rm {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR
 \NC \M {Q}
@@
 \NC \M {Q}
-:= \NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR[+]
+:= \NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR
 }
@@
 \NC \M {K} \DB {n_1, n_2}
-= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR[+]
+= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR
 \NC \Q n_1, n_2
@@
 Here recall that we have
-\Disp{
+\Disp {
 \NC \M {K}^\Adj \M {K}
-= \NC \M {I} \NR[+]
+= \NC \M {I} \NR
 }
@@
 \NC \M {G}
-=\NC \M {K}^\Adj \M {H} \M {K} \NR[+]
+=\NC \M {K}^\Adj \M {H} \M {K} \NR
 }
@@
 =\NC \M {W}_B \M {W}_R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F}_R \M {F}_B
-+\M {W}_B \M {W}_R \M {Z} \NR[+]
++\M {W}_B \M {W}_R \M {Z} \NR
 }
@@
 \NC \M {P}
-:=\NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}} \NR[+]
+:=\NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}} \NR
 }
@@
 \NC \V {g}
-:= \NC \Rm {vec} \SB {\M {G}} \NR[+]
+:= \NC \Rm {vec} \SB {\M {G}} \NR
 }
@@
 \NC \V {y}
-=\NC \M {P} \V {g} +\V {z} \NR[+]
+=\NC \M {P} \V {g} +\V {z} \NR
 }
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_h}}, \m{\g \geq 0}.
+\item Let \m{\g \geq 0} be given.
+\item Input \m {\M {F}_B \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_Y}, \M {F}_R \in \NC \MB {M}_{\MB {C}} \SB {N_H, N_R}, \M {W}_R \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_H}, \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R}}, \m {\M {Y} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y}},
+\item Find \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_h}} as in above.
 \item Calculate
@@
 \LA \NC \startcases
-\NC \Min {\V {g}' \in \MB {V}_{\MB {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR[+]
+\NC \Min {\V {g}' \in \MB {V}_{\MB {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR
 \NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR

### 2019-09-05 paper/3_1_almost_sparsity.tex
Delete conversion from complex to real DS

--- 2019-06-05 dantzig_selector/report/3_1_almost_sparsity.tex
@@
 
-Our plan is first to show that \m {\SB {\V {g}}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
-We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in previous sections.
+We first show that \m {\SB {\V {g}}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
+We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in Chapter 2.
 
-Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}} is the largest \m {S} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {S} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
+Let \m {\hat {\V {g}}} be the Dantzig Selector.
+Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}}, the largest \m {S} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {S} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
 For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
@@
 Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
-\Disp{
+\Disp {
 \NC \V{v} \DB {\s \SB {n}}
-\leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
+\leq \NC \V{v} \DB {\s \SB {n-1}} \NR
 \NC n =\NC 1, \ldots, N_p-1 \NR
@@
 For fixed \m {S}, define
-\Disp{
+\Disp {
 \NC \MC {S} \SB {\V{x}, S}
-=\NC \sum_{i=0} ^{S-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
+=\NC \sum_{i=0} ^{S-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR
 \NC \MC {C} \SB {\V{x}, S}
-=\NC \sum_{i=S} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR[+]
+=\NC \sum_{i=S} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR
 }
@@
 Now set
-\Disp{
+\Disp {
 \NC \V{g} _{\MC {A}}
-=\NC \MC {S} \SB {\V{g}, S} \NR[+]
+=\NC \MC {S} \SB {\V{g}, S} \NR
 \NC \V{g} _{\MC {K}}
-=\NC \MC {C} \SB {\V{g}, S} \NR[+]
+=\NC \MC {C} \SB {\V{g}, S} \NR
 \NC \V{g} _{\MC {B}}
-=\NC \MC {S} \SB {\V{g} _\MC {K}, S} \NR[+]
+=\NC \MC {S} \SB {\V{g} _\MC {K}, S} \NR
 }
@@
 \NC \VNm {\MC {C} \SB{\V {x}, s}} _p
-\leq \NC R. \NR[+]
+\leq \NC R. \NR
 }
@@
    \MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}
-} _2 ^2 \NR[+]
+} _2 ^2 \NR
 }
@@
 Note that by construction
-\Disp{
+\Disp {
 \NC \Nm {\psi \SB {\f, n_H}}
@@
 
-Now, it can be verified that
-\Result
-{Lemma}
-{
-For \m {-\pi \leq x < \pi}, we have
+Now, by the nature of alternating series, for \m {-\pi \leq x < \pi}, it holds that
 \Disp {
-\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}. \NR[+]
-}
+\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}. \NR
 }
@@
 \NC \leq \NC B \SB {\psi'} \NR
-\NC := \NC \F {48}{\Nm {\psi'^2 -24} \Nm {\psi'}} \NR[+]
+\NC := \NC \F {48}{\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
 \NC -\pi \leq \NC \psi' < \pi. \NR
@@
 } _2^2
-\NR[+]
+\NR
 }
@@
 \Bigg \| _{s/N_H} ^1 \NR
-\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR[+]
+\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR
 }
@@
 \NC R
-\leq \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {\R {s}} {38 N_H}. \NR[+]
+\leq \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {\R {s}} {38 N_H}. \NR
 }
@@
 Then, for all instances of \m {\f}, \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
-\Disp{
+\Disp {
 \NC R
-\leq \NC \m {\F{1}{3 \R{N_H}}} \NR[+]
+\leq \NC \m {\F{1}{3 \R{N_H}}} \NR
 }
@@
 Since the bound is also decreasing in \m {N_H}, for concreteness, let us plug in \m {N_H =4} for the upper bound, giving
-\Disp{
+\Disp {
 \NC R
-\leq \NC \F {1} {6} \NR[+]
+\leq \NC \F {1} {6} \NR
 }
@@
 Note that
-\Disp{
+\Disp {
 \NC \VNm {\M {G}}_F
-=\NC \VNm {\M {H}}_F \NR[+]
+=\NC \VNm {\M {H}}_F \NR
 }
@@
 
-\Disp{
+\Disp {
 \NC \VNm {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F
@@
 \Nm {\a_l} \VNm {\V {a} \SB {\f_l}} _2
-\VNm {\V {a} \SB {\th_l}} _2 \NR[+]
+\VNm {\V {a} \SB {\th_l}} _2 \NR
 }
@@
 Since \m {\ell_1}-norm will be used in later proof, we display the statement about \m {\ell_1}-norm.
-\Disp{
+\Disp {
 \NC \NC \MB {E} \SB {\VNm {\MC {C} \SB {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj}} _F} \NR
 \NC \leq \NC \F {1} {9 \R{N_H}} \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}} \NR
-\NC \leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR[+]
+\NC \leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR
 }

### 2019-09-05 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Delete conversion from complex to real DS

--- 2019-08-13 dantzig_selector/report/3_3_expected_error_analysis.tex
@@
-\startsection [title={Expected Error Analysis for Dantzig Selector}]
-\startsubsection [title={Generalizing Technical Lemmata for Complex Case}]
+\startsection [title={Generalizing the Dantzig Selector Bound}]
+\startsubsection [title={Technical Lemmata in Complex Case}]
 
-Let \m {\hat {\V {g}}} be the Dantzig Selector.
-For concreteness, we set
+The third and last part of our task is to plug in the almost-sparsity found in Section 3.1, and plug in the probablity found in Section 3.2.
+Set for short
+\PF {d:g,g}
+\Disp {
+\NC \V {d} 
+= \NC \Hat {\V {g}} -\V {g} \NR
+}
+And our task is to bound its expectation.
+
+We argue that \m {\V{g}} can essentially be seen as sparse, and for that purpose we ignore relevent terms.
+Also, we do not seek a very tight bound and will approximate \m {\d_{S}} by \m {1}.
+And, as shall be seen, it suffices to set
 \Disp {
 \NC \g 
-= \NC \R {2 \log N_h} \NR[+]
-}
-
-Other values are of course possible, but this is enough to illustrate our purpose.
-Also set for short
-\Disp {
-\NC \V {d} 
-= \NC \Hat {\V {g}} -\V {g} \NR[+]
+= \NC \R {2 \log N_h} \NR
 }
@@
 In accordance with (), set
-\Disp{
+\Disp {
 \NC S
@@
 }
+If we set again \m {s =\R{N_H}}, we get \m {S =N_H L}.
 
@@
 \NC \VNm {\V {d}} _2
-\leq \NC 32 S \log N_H \NR[+]
+\leq \NC 4 \R{2} \D \R{L N_H \log N_H} \NR
 }
@@
 \NC 1 -p
-\leq \NC 2 \D 6^S \D \exp \SB {-\F{N_Y^2} {32}} \NR[+]
+\leq \NC 2 \D 6^S \D \exp \SB {-\F{N_Y^2} {32}} \NR
 }

### 2019-09-05 paper/4_simulation.tex
Delete conversion from complex to real DS

--- 2019-05-28 dantzig_selector/report/4_simulation.tex
@@
 
-With the preperation of notation in the previous section, and a discussion on its theory, we shall now formulate our algorithm and focus on the practical aspect.
+After the introduction of problem configuration and analysis of expected square error, we shall formulate our algorithm and focus on the practical aspects.
+As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} \SB {h}}.
 
-As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} \SB {h}}.
-But it is not the end.
-In fact, Cand\`es and Tao's analysis in ``\m {\ell_1}-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
-Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
-Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
-Thus our proposed algorithm is not a corollary of the DS program outlines in ``\m {\ell_1}-MAGIC''.
+It is mentioned in ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) that the complex DS can be converted as an SOCP program.
+If so, primal-dual interior point algorithm (for example) may readily be applied on it to simplify the program, for which we may consult Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.\ 11 as a standard reference.
+But we will not implement that here.
+For brevity, we use Python Library CVXPY to solve the complex DS.
 
-\startsection [title={Representation by Real Matrices}]
-
-Since our setting is slightly different from ``\m {\ell_1}-MAGIC'', for completeness of exposition we write down derivation of the dual problem from the primal problem, as follows.
-Recapitulate that, as we explained in the above, DS involves the calculation of \m {\ell_1}-1 norm.
-This, for real vectors, can be transformed into a linear program (LP).
-But in the complex case, that becomes a quadratic expression of the real and imaginary part of the vector, and is no longer equivalent to an LP.
-Still, the comparison arising from primal-dual problem is not easily done in complex numbers, and we cast it into a real \m {\ell_1}-1 norm problem.
-Afterwards we will further transform the SOCP to a primal-dual algorithm, which is a well-known technique for convex optimization problems.
-The bound in the previous section is valid, since in the course of transformation, nothing is lost or weakened.
-
-For convenience, define the following real representation function for complex vectors.
-
-\Result
-{Definition}
-{
-For \m {\V{x} \in \MB {V}_{\MB {C}} \SB {M}}, we say that \m {\MC {R} \SB {\V{x}}} is the real representation of \m {\V{x}}, defined by
-\Disp {
-\NC \MC {R} \SB {\V{x}}
-\in \NC \MB {V}_{\MB {R}} \SB {2M} \NR
-\NC \MC {R} \SB {\V{x}} \DB {m}
-= \NC \startcases
-\NC \MF {Re} \SB {\V{x} \DB {m'}}, \MC m =2m' \NR
-\NC \MF {Im} \SB {\V{x} \DB {m'}}, \MC m =2m'+1 \NR
-\stopcases \NR[+]
-\NC m' 
-= \NC  0, 1, 2, \ldots, M-1 \NR
-}
-The bijectivity is obvious, and we define \m {\MC {R} ^{-1}} so that
-\Disp {
-\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V{x}}}
-=\NC \V{x} \NR[+]
-}
-}
-
-By the same token, a moment's reflection reveals the corresponding definition of real representation of matrices.
-
-\Result
-{Definition}
-{
-For \m {\M{A} \in \MB {M}_{\MB {C}} \SB {M_1, M_2}}, we say that \m {\MC {R} \SB {\M{A}}} is the real representation of \m {\M{A}}, defined by
-\Disp {
-\NC \MC {R} \SB {\M{A}}
-\in \NC \MB {M}_{\MB {R}} \SB {2M_1, 2M_2} \NR
-\NC \MC {R} \SB {\M{A}} \DB {m_1,m_2} =
-\NC \startcases
-\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
-\NC \MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
-\NC -\MF {Im} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
-\NC \MF {Re} \SB {\M{A} \DB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
-\stopcases \NR[+]
-\NC m_1 
-= \NC 0, 1, 2, \ldots, M_1 -1 \NR
-\NC m_2 
-= \NC 0, 1, 2, \ldots, M_2 -1 \NR
-}
-Notice that Here not all matrices in \m {\MB {M}_{\MB {R}} \SB {2M_1, 2M_2}} are images, and we will not call the inverse function anyway.
-}
-
-We continue the notation of program ().
-
-\Disp {
-\NC \T {\V {y}}
-\in \NC \MB {V}_{\MB {R}} \SB {2N_y} \NR
-\NC \T {\V {y}}
-= \NC \MC {R} \SB {\V {y}} \NR[+]
-\NC \T {\V {g}}
-\in \NC \MB {V}_{\MB {R}} \SB {2N_h} \NR
-\NC \T {\V {g}}
-= \NC \MC {R} \SB {\V {g}} \NR[+]
-\NC \T {\M {P}}
-\in \NC \MB {M}_{\MB {R}} \SB {2N_y, 2N_h} \NR
-\NC \T {\M {P}}
-= \NC \MC {R} \SB {\M {P}} \NR[+]
-\NC \T {\M {P}} ^\Adj
-\in \NC \MB {M}_{\MB {R}} \SB {2N_y, 2N_h} \NR
-\NC \T {\M {P}} ^\Adj
-= \NC \MC {R} \SB {\M {P} ^\Adj} \NR[+]
-\NC \T {\V {z}}
-\in \NC \MB {V}_{\MB {R}} \SB {2N_y} \NR
-\NC \T {\V {z}}
-= \NC \MC {R} \SB {\V {z}} \NR[+]
-}
-such that, by construction,
-\Disp {
-\NC \V {\T {y}}
-= \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}}
-}
-
-Finally, introduce the following matrices to identify the components where we want to take \m {\ell_2}-norm, in the manner similar to an indicator function.
-
-\Disp {
-\NC {\V {u}}_{n_h}
-\in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
-\NC {\V {u}}_{n_h} \DB {n_h'}
-= \NC
-\startcases
-1, \Q \MC n_h' =n_h \NR
-0, \Q \NC \Rm {otherwise} \NR
-\stopcases \NR[+]
-\NC {\T {\M {U}}}_{n_h} \in \NC \MB {M}_{\MB {R}} \SB {2N_h, 2N_h} \NR
-\NC {\T {\M {U}}}_{n_h} \DB {n_h', n_h''}
-= \NC
-\startcases
-1, \Q \MC n_h' =2n_h,\; n_h'' =2n_h \NR
-1, \Q \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
-0, \Q \NC \Rm {otherwise} \NR
-\stopcases \NR[+]
-\NC n_h, n_h', n_h'' 
-= \NC 0, 1, 2, \ldots, N_h -1 \NR
-}
-Moreover, denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
-Now, if we introduce vector \m{\V{m}}
-
-\Disp{
-\NC \V {m} \in \NC \MB {V}_{\MB {R}} \SB {N_h} \NR
-\NC \V{m} \DB{n_h}
-= \NC \Nm{\V{g} \DB{n_h}} \NR[+]
-\NC n_h, n_h', n_h'' 
-= \NC 0, 1, 2, \ldots, N_h -1 \NR
-}
-to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now takes the form
-\Disp {
-\NC \Hat {\T {\V {g}}}
-= \NC \startcases
-\NC \Min {\T {\V {g}}', \V {m}} \Q
-\MC \IP { \V {1}, \V {m} } \NR
-\NC \Rm {subject} \; \Rm {to} \Q
-\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
-\leq \IP { \V {u}_{n_h}, \V {m} } \NR
-\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
-\leq \g \NR
-\stopcases \NR[+]
-\NC n_h 
-= \NC 0, 1, 2, \ldots, N_h-1 \NR
-}
-
-\stopsection
-
-\startsection [title={Second Order Cone Programming}]
-
-We shall see furthermore that the program can be cast into an SOCP.
-To make the point clearer, we rewrite Program () into a stricter, extended block matrix form, by defining auxiliary variables with dimension
-
-\Disp{
-\NC \V{t}_i
-\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
-\NC \V{x}_i
-\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
-\NC \M{A}_i
-\NC \in \MB {M}_{\MB {R}} \SB {2N_h, 3N_h} \NR
-\NC \V{b}_i
-\NC \in \MB {V}_{\MB {R}} \SB {3N_h} \NR
-\NC \V{c}_i
-\NC \in \MB {V}_{\MB {R}} \SB {2N_h} \NR
-\NC d_i
-\NC \in \MB {R} ^+ \NR
-}
-
-defined below to be
-
-\Disp{
-\NC \V{t}
-= \NC \startTheMatrix
-\NC \V{0} \NR
-\NC \V{1} \NR
-\stopTheMatrix \NR[+]
-\NC \V{x}'
-= \NC \startTheMatrix
-\NC \T {\V {g}}' \NR
-\NC \V{m} \NR
-\stopTheMatrix \NR[+]
-}
-
-with
-
-\Disp{
-\NC \M{A}_i
-= \NC \startTheMatrix
-\NC \T {\M {U}}_{i}, \NC \M{0} \NR
-\stopTheMatrix \NR[+]
-\NC \V{b}_i
-= \NC \V{0} \NR[+]
-\NC \V{c}_i
-= \NC \startTheMatrix
-\NC \V{0} \NR
-\NC \V {u}_{i} \NR
-\stopTheMatrix \NR[+]
-\NC d_i
-= \NC 0 \NR[+]
-\NC i 
-= \NC 0, 1, 2, \ldots, N_h -1 \NR
-}
-
-And
-
-\Disp{
-\NC \M{A}_i
-= \NC \startTheMatrix
-\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M{0} \NR
-\stopTheMatrix \NR[+]
-\NC \V{b}_i
-=\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}} \NR[+]
-\NC \V{c}_i
-= \NC \V{0} \NR[+]
-\NC d_i
-= \NC \g \NR[+]
-\NC i 
-= \NC N_h, N_h +1, N_h +2, \ldots, 2N_h -1 \NR
-}
-
-The step that we convert \m {\Hat {\V {g}}} back is same as Algorithm () is same as before, but this is listed for sake of completeness.
-
-\Result
-{Algorithm}
-{
-\startitemize[n]
-\item Input \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_y}}, \m{\g > 0}.
-\item Define \m{\V{t}, \V{x}, \M{A}_i, \V{b}_i, \V{c}_i, d_i} according to ().
-\item Calculate
-\Disp{
-\NC \Hat {\V {x}}
-\LA \NC \startcases
-\NC \Min {\V {x}' \in \MB {V}_{\MB {C}} \SB {N_h}}
-\MC \IP {\V {t}, \V {x}'} \NR[+]
-\NC \Rm {subject} \; \Rm {to}
-\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V{b} _{i}} _2
-\leq \IP {\V{c}_{i}, \V {x}'} +\V{d}_i \NR
-\NC \MC i 
-=0, 1, 2, \ldots, 2N_h -1 \NR
-\stopcases \NR[+]
-}
-\item Extract
-\Disp{
-\NC \Hat{\T{\V{g}}}
-\LA \NC \Hat{\V{x}} \DB {0 : 2N_h-1} \NR[+]
-}
-\item Convert 
-\Disp{
-\NC \Hat{\V{g}}
-\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V{g}}}} \NR[+]
-}
-\item Calculate
-\Disp {
-\NC \Hat {G}
-\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR[+]
-}
-\item Calculate
-\Disp {
-\NC \Hat {\M {H}}
-\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR[+]
-}
-\item Output \m {\Hat {\M {H}}}.
-\stopitemize
-}
-
-\stopsection
-
-\startsection [title={Simulation}]
-
-One can convert primal-dual interior point algorithm to make the SOCP easier to calculate.
-We mention, again, Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.\ 11 as a standard reference, and ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) for discussion of SOCP applied to DS.
-
-However, for brevity we use Python Library CVXPY to solve the SOCP.
+\startsection [title={Parameters}]
 

### 2019-09-05 paper/references.tex
Delete conversion from complex to real DS

\starttitle [title={References}]

References are sorted first with alphabetical order, then, in case for exactly the same author(s), with year.

\startitemize[n]

\item D Achlioptas (2001). Database-friendly random projections. In Proceedings of the twentieth ACM SIGMOD-SIGACT-SIGART symposium on Principles of database systems (pp. 274-281). ACM.

\item M R Akdeniz et.\ al.\ (2014), ``Millimeter Wave Channel Modeling and Cellular Capacity Evaluation'', \It { IEEE Journal on Selected Areas in Communications}, Vol.\ 32, No.\ 6

\item A Alkhateeb, O E Ayach, G Leus, and R W Heath Jr (2014), ``Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems'', \It { IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 8, No.\ 5.

\item A Alkhateeb, G Leus, and R W Heath Jr.\ (2015), ``Compressed Sensing Based Multi-User Millimeter Wave Systems: How Many Measurements are Needed?'' \It { IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}

\item W U Bajwa, J Haupt, A M Sayeed, and R Nowak (2010), ``Compressed Channel Sensing: A New Approach to Estimating Sparse Multipath Channels'', Proceedings of the IEEE, Vol.\ 98, No.\ 6.

\item W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.

\item R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \It { Constructive Approximation} \Bf{28}: 253–263

\item Zvika Ben-Haim, Y C Eldar, and M Elad (2010), ``Coherence-Based Performance Guarantees for Estimating a Sparse Vector Under Random Noise'', \It { IEEE Transactions on Signal Processing}, Vol.\ 58, No.\ 10.

\item S Boyd, L Vandenberghe (2004), \It { Convex Optimization}. Cambridge U.\ Press.

\item E J Cand\`es, J Romberg, and T Tao (2006), ``Robust Uncertainty Principles: Exact Signal Reconstruction From Highly Incomplete Frequency Information'' \It { IEEE Transactions on Information Theory}, Vol.52, No.2.

\item E J Cand\`es and J Romberg (2005), ``\m {\ell_1}-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \Uurrll{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.

\item E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \It { IEEE Transactions on Information Theory}, Vol.51, No.12.

\item E J Cand\`es and T Tao (2006), ``Near-Optimal Signal Recovery From Random Projections: Universal Encoding Strategies?'' \It { IEEE Transactions on Information Theory}, Vol.52, No.12.

\item E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \m {p} is Much Larger than \m {n}'', \It { The Annals of Statistics}, Vol.35, No.6.

\item T T Cai and L Wang (2011), ``Orthogonal Matching Pursuit for Sparse Signal Recovery With Noise'', \It { IEEE Transactions on Information Theory}, Vol.\ 57, No.\ 7.

\item T T Cai, L Wang, and G Xu (2010), ``Stable Recovery of Sparse Signals and an Oracle Inequality'', \It { IEEE Transactions on Information Theory}, Vol.\ 56, No.\ 7.

\item M P Friedlander and M A Saunders (2007), ``Discussion: The Dantzig Selector: Statistical Estimation when \m {p} is Much Larger than \m {n}'', \It { The Annals of Statistics}, Vol.\ 35, No.\ 6.

\item Z Gao, L Dai, Z Wang, and S Chen (2015). ``Spatially Common Sparsity Based Adaptive Channel Estimation and Feedback for FDD Massive MIMO'', \It { IEEE Transactions on Signal Processing}, Vol.\ 63, No.\ 23.

\item A Goldsmith, S A Jafar, N Jindal, and S Vishwanath (2003), ``Capacity Limits of MIMO Channels'', \It { IEEE Journal on Selected Areas in Communications}, Vol.\ 21, No.\ 5.

\item R W Heath Jr, N González-Prelcic, S Rangan, W Roh, and A M Sayeed (2016), ``An Overview of Signal Processing Techniques for Millimeter Wave MIMO Systems'', \It { IEEE Journal of Selected Topics in Signal Processing}, Vol.\ 10, No.\ 3.

\item J Lee, G-T Gil, and Y H Lee (2016), ``Channel Estimation via Orthogonal Matching Pursuit for Hybrid MIMO Systems in Millimeter Wave Communications'', \It { IEEE Transactions on Communications}, Vol.\ 64, No.\ 6.

\item H Li, Q Gao, R Chen, R Tamrakar, S Sun, and W Chen, ``Codebook Design for Massive MIMO Systems in LTE'', \It { 2016 IEEE 83rd Vehicular Technology Conference (VTC Spring)}.

\item X Rao and V K N Lau (2014), ``Distributed Compressive CSIT Estimation and Feedback for FDD Multi-User Massive MIMO Systems'', \It { IEEE Transactions on Signal Processing}, Vol.\ 62, No.\ 12.

\item J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep. Retrieved from: \Uurrll{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}

\item J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \It { IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.

\stopitemize

\stoptitle

### 2019-09-05 paper/source.tex
Delete conversion from complex to real DS

\startchapter [title={Appendix: Source Code}]

\startsection [title={\tt{constants.py}}]

\typefile [code] [] {../../../code/channel-estimation-via-dantzig-selector-code/src/constants.py}

\stopsection

\startsection [title={\tt{functions.py}}]

\typefile [code] [] {../../../code/channel-estimation-via-dantzig-selector-code/src/functions.py}

\stopsection

\startsection [title={\tt{classes.py}}]

\typefile [code] [] {../../../code/channel-estimation-via-dantzig-selector-code/src/classes.py}

\stopsection

\startsection [title={\tt{main.py}}]

\typefile [code] [] {../../../code/channel-estimation-via-dantzig-selector-code/src/main.py}

\stopsection

\stopchapter

### 2019-09-22 paper/1_introduction.tex
Use BibTeX, conform to IEEE citation style

@@
 To motivate the need, we observe that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
-\Disp {
+\DispN {
 \NC N_p \gg N_m \NR
@@
 
-In this section, consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}} and \m {\V{\Phi} \in \MB {M}_{\MB {K}} \SB {N_m, N_p}}.
+In this section, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\V {\Phi} \in \MB {K} ^{N_m \D  N_p}}.
 Set \m {\MC {T} \RB {N_p} =\CB {0, \dots, N_p-1}} for short.
 For \m {\MC {A} \subseteq \MC {T} \SB {N_p}}, denote
-\Disp {
+\DispN {
 \NC \V {x}  \DB {\MC {A}}
@@
 \m {\V {x}} is called \m {s}-sparse, if there is \m {\MC {A} \subseteq \MC {T} \SB {N_p}} such that
-\Disp { 
-\NC \V{x} \DB {\MC {A}}
-=\NC \V{x} \NR
+\DispN { 
+\NC \V {x} \DB {\MC {A}}
+=\NC \V {x} \NR
 }
 with
-\Disp { 
+\DispN { 
 \NC \# \MC {A} \leq s. \NR
@@
 {
-For fixed \m {s =0, \dots N_p -1}, we say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
-\Disp {
+For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
+\DispN {
 \NC \RB {1-\d_s} \VNm {\V {x}}^2
-\leq \NC \VNm {\M{\Phi} \V {x}} _2^2 \NR
+\leq \NC \VNm {\M {\Phi} \V {x}} _2^2 \NR
 \NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR
@@
 
-\Disp {
+\DispN {
 \NC \V {y}
@@
 
-where (w.l.o.g.) \m {\V{z}} is an i.i.d.\ normalized Gaussian vector.
-How can we hope to estimate \m {\V{x}} when, in addition to insufficient observations, there are too few observations?
+where (w.l.o.g.) \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
+How can we hope to estimate \m {\V {x}} when, in addition to insufficient observations, there are too few observations?
 
@@
 \startitemize[n]
-\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}.
+\item Input \m {\M {\Phi} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}.
 \item Calculate
-\Disp {
+\DispN {
 \NC \Hat {\V {h}}
@@
 For the noiseless, real-number case,
-\Disp {
+\DispN {
 \NC \V {y}
@@
 \startitemize[n]
-\item Input \m {\M {\Phi} \in \MB {V}_\MB {R} \SB {N_m, N_p}}, \m {\V {y} \in \MB {V}_\MB {R} \SB {N_m}}, \m {\eta >0}.
+\item Input \m {\M {\Phi} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
 \item Initialize
-\Disp {
-\NC \V{r}
-\LA \NC \V{y} \NR
+\DispN {
+\NC \V {r}
+\LA \NC \V {y} \NR
 \NC S
@@
 \item Find
-\Disp {
+\DispN {
 \NC c
-\LA \NC \underset {i =0, \dots, N_p-1} {\Rm{argmax}}
-\Nm {\M{\Phi} \DB {:,i} \V{r}} \NR
+\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
+\Nm {\M {\Phi} \DB {:,i} \V {r}} \NR
 }
@@
 \item Compute
-\Disp {
-\NC \M{\Phi} ^\ddagger
-\LA \NC \RB {\M{\Phi} \DB {S} ^\Adj \M{\Phi} \DB {S}} ^{-1} \M{\Phi} \DB {S} ^\Adj \NR
-\NC \V{r}
-\LA \NC \V{y} -\M{\Phi} \DB {S} ^\Adj \M{\Phi} ^\ddagger \V{y} \NR
+\DispN {
+\NC \M {\Phi} ^\ddagger
+\LA \NC \RB {\M {\Phi} \DB {S} ^\Adj \M {\Phi} \DB {S}} ^{-1} \M {\Phi} \DB {S} ^\Adj \NR
+\NC \V {r}
+\LA \NC \V {y} -\M {\Phi} \DB {S} ^\Adj \M {\Phi} ^\ddagger \V {y} \NR
 }
 \item Break if
-\Disp {
-\NC \VNm {\V{r}} _2
+\DispN {
+\NC \VNm {\V {r}} _2
 <\NC \eta \NR
 }
-where \m {\VNm {\M{\Phi} ^\ddagger} _1} denotes the operator norm.
+where \m {\VNm {\M {\Phi} ^\ddagger} _1} denotes the operator norm.
 \item Output 
-\Disp {
+\DispN {
 \NC \Hat {\V {g}}
-\LA \NC \M{\Phi} ^\ddagger \V{y} \NR
+\LA \NC \M {\Phi} ^\ddagger \V {y} \NR
 }
@@
 }
-Here \m {\V{r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {h} is nonzero (where we have slightly abused the usage of double brackets).
+Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {h} is nonzero (where we have slightly abused the usage of double brackets).
 
@@
 {
-Define \m {\Rm {vec} \SB {\M {A}} \in \MB {V}_{\MB {K}} \SB {N_1, N_2}} to be the vectorization of \m {\M {A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}}.
+Define \m {\Rm {vec} \SB {\M {A}} \in \MB {K} ^{N_1, N_2}} to be the vectorization of \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}}.
 Formally,
-\Disp {
-\NC \RB {\Rm{vec} \SB {\M{A}}} \DB {m_1}
-=\NC \M{A} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
+\DispN {
+\NC \RB {\Rm {vec} \SB {\M {A}}} \DB {m_1}
+=\NC \M {A} \DB {m_1\; \Rm {Mod}\; N_1, \Fl { m_1/N_1 }} \NR
 }
 The bijectivity is obvious, and we define \m {\Rm {vec} ^{-1}} so that
-\Disp {
+\DispN {
 \NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
@@
 {
-For \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}} and \m {\M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \MB {M}_{\MB {K}} \SB {N_1 N_3, N_2 N_4}} by
-\Disp {
-\NC \NC \RB {\M{A} \otimes \M{B}} \DB {m_1, m_2} \NR
-\NC =\NC \M{A} \DB {\Fl{ m_1/N_3 }, \Fl{ m_2/N_4 }}
-\M{B} \DB {m_1\; \Rm{Mod}\; N_3, m_2\; \Rm{Mod}\; N_4} \NR
+For \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}} and \m {\M {B} \in \MB {K} ^{N_3 \D N_4}}, define the Kronecker product \m {\M {A} \otimes \M {B} \in \MB {K} ^{N_1 N_3 \D N_2 N_4}} by
+\DispN {
+\NC \NC \RB {\M {A} \otimes \M {B}} \DB {m_1, m_2} \NR
+\NC =\NC \M {A} \DB {\Fl { m_1/N_3 }, \Fl { m_2/N_4 }}
+\M {B} \DB {m_1\; \Rm {Mod}\; N_3, m_2\; \Rm {Mod}\; N_4} \NR
 }
@@
 {
-Suppose \m {\M{A} \in \MB {M}_{\MB {K}} \SB {N_1, N_2}, \M{X} \in \MB {M}_{\MB {K}} \SB {N_2, N_3}, \M{B} \in \MB {M}_{\MB {K}} \SB {N_3, N_4}},
+Suppose \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}, \M {X} \in \MB {K} ^{N_2 \D N_3}, \M {B} \in \MB {K} ^{N_3 \D N_4}},
 Then
-\Disp {
-\NC \Rm{vec} \SB {\M{A}\M{X}\M{B}}
-= \NC \RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB {\M{X}} \NR
+\DispN {
+\NC \Rm {vec} \SB {\M {A}\M {X}\M {B}}
+= \NC \RB {\M {B}^\Tr \otimes \M {A}} \Rm {vec} \SB {\M {X}} \NR
 }
@@
 
-The proof is not particularly easy to find, and we show it here.
-We thus verify that arbitrary components of lhs and rhs agree.
+To show this, we shall verify that arbitrary components of lhs and rhs agree.
 On one hand,
-
-\Disp {
-\NC \NC \RB {\Rm{vec} \SB {\M{A}\M{X}\M{B}}} \DB {m_1} \NR
-\NC = \NC \RB {\M{A}\M{X}\M{B}} \DB {m_1\; \Rm{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
+\DispN {
+\NC \NC \RB {\Rm {vec} \SB {\M {A}\M {X}\M {B}}} \DB {m_1} \NR
+\NC = \NC \RB {\M {A}\M {X}\M {B}} \DB {m_1\; \Rm {Mod}\; N_1, \Fl { m_1/N_1 }} \NR
 \NC = \NC \sum _{n_2 =0} ^{N_2 -1} \sum _{n_3 =0} ^{N_3 -1}
-\M{A} \DB {m_1\; \Rm{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR
+\M {A} \DB {m_1\; \Rm {Mod}\; N_1, n_2} \M {X} \DB {n_2, n_3} \M {B} \DB {n_3, \Fl { m_1/N_1 }} \NR
 }
-
 On the other hand,
-
-\Disp {
-\NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB{\M{X}} } \DB {m_1} \NR
-\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR
-\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
-\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR 
+\DispN {
+\NC \NC \RB {\RB {\M {B}^\Tr \otimes \M {A}} \Rm {vec} \SB {\M {X}}} \DB {m_1} \NR
+\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M {B}^\Tr \otimes \M {A}} \DB {m_1, m_2} \Rm {vec} \SB {\M {X}} \DB {m_2} \NR
+\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M {B}^\Tr} \DB {\Fl { m_1/N_1 }, \Fl { m_2/N_2 }}
+\M {A} \DB {m_1\; \Rm {Mod}\; N_1, m_2\; \Rm {Mod}\; N_2} \Rm {vec} \SB {\M {X}} \DB {m_2} \NR 
 \NC = \NC
 \sum _{m_2 =0} ^{N_2 N_3 -1}
-\M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
-\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \NR
+\M {B} \DB {\Fl { m_2/N_2 }, \Fl { m_1/N_1 }}
+\M {A} \DB {m_1\; \Rm {Mod}\; N_1, m_2\; \Rm {Mod}\; N_2} \NR
 \NC \NC \SixQ
-\M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}
+\M {X} \DB {m_2\; \Rm {Mod}\; N_2, \Fl { m_2/N_2 }}
 \NR
@@
 
-In () and (), the row indices of \m {\M{A}} and \m {\M{B}} already agree.
+In () and (), the row indices of \m {\M {A}} and \m {\M {B}} already agree.
 The key observation is that when \m {n_2} runs through \m {0, \dots, N_2-1} and \m {n_3} runs through \m {0, \dots, N_3-1}, it follows \m {n_2 n_3} runs through \m {0, \dots, N_2 N_3-1}.
@@
 \item Previous work simply assumes the bound of the norm of the channel matrix.
-\item The requirement that the sensing matrix should be elementwise i.i.d.\ Gaussian (Tropp and Gilvert 2007) seems to be more restrictive than RIP (Cand\`es and Tao 2007).
+\item The condition that the sensing matrix should be elementwise i.i.d.\ Normal (required by Tropp and Gilvert 2007) seems to be more restrictive than RIP (required by Cand\`es and Tao 2007).
 \item The quantization of angle in generating may be a problem, and that is difficult to analyze in OMP's setting

### 2019-09-22 paper/2_problem_setting.tex
Use BibTeX, conform to IEEE citation style

@@
 
-Since expression involving probability will get complicated, sometimes we explicitly mark the independence on event space index.
-
-Conceptually, we use \m {\O_t} to denote the event space of the transmitter end, \m {\O_h} to denote that of the communication channel itself, \m {\O_z} to denote that of the noise arising in the communication channel, and \m {\O_r} to denote that of the receiver end.
-It helps to think \m {\NC \O = \NC \O_t \times \O_h \times \O_n \times \O_r \NR} as the overall event space.
-
 We restrict our consideration to the uniform linear array, which can be modeled as
-\Disp {
+\DispN {
 \NC \V {a} \SB {\psi'}
-\in \NC \MB {V}_\MB {C} \SB {N_H} \NR
+\in \NC \MB {V} _\MB {C} \SB {N_H} \NR
 \NC \V {a} \SB {\psi'}
-= \NC \F {1}{\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u}_{n_h} \NR
+= \NC \F {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u} _{n_h} \NR
 }
@@
 And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
-\Disp {
-\NC \M{H}
+\DispN {
+\NC \M {H}
 =\NC \sum_{l=0} ^{L-1}
@@
 For our purpose, we may absorb the argument of \m {\V {a}} as
-\Disp {
+\DispN {
 \NC \f_l
@@
   2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
-  \; \Rm{Mod}\; \RB {2\pi}
+  \; \Rm {Mod}\; \RB {2\pi}
 } \NR
@@
   2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
-  \; \Rm{Mod}\; \RB {2\pi}
+  \; \Rm {Mod}\; \RB {2\pi}
 } \NR
@@
 to get a simpler form
-\Disp {
-\NC \M{H}
-\in \NC \MB {M}_\MB {C} \SB {N_H} \NR
-\NC \M{H}
+\DispN {
+\NC \M {H}
+\in \NC \\MB {C} ^{N_H \D N_H} \NR
+\NC \M {H}
 =\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
@@
 To set up notation, we list them as below.
-\Disp {
-\NC \M {F}_B \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_Y} \NR
-\NC \M {F}_R \in \NC \MB {M}_{\MB {C}} \SB {N_H, N_R} \NR
-\NC \M {W}_R \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_H} \NR
-\NC \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R} \NR
+\DispN {
+\NC \M {F} _B \in \NC \MB {C} ^{N_R \D  N_Y} \NR
+\NC \M {F} _R \in \NC \MB {C} ^{N_H \D  N_R} \NR
+\NC \M {W} _R \in \NC \MB {C} ^{N_R \D  N_H} \NR
+\NC \M {W} _B \in \NC \MB {C} ^{N_Y \D  N_R} \NR
 }
 Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
-\Disp {
-\NC \Nm {\M {F}_R \DB {n_H, n_R}}
+\DispN {
+\NC \Nm {\M {F} _R \DB {n_H, n_R}}
 = \NC 1, \NR
-\NC \Nm {\M {W}_R \DB {n_R, n_H}}
+\NC \Nm {\M {W} _R \DB {n_R, n_H}}
 = \NC 1, \NR
@@
 And we assume
-\Disp {
+\DispN {
 \NC N_H \gg \NC N_R \NR
+}
+\DispN {
 \NC N_R \gg \NC N_Y \NR
@@
 
-We consider zero-mean, unity-variance additive white Gaussian noise (AWGN).
-Since we restrict our discussion to a specific slice of time, this random process may be simply taken to be a matrix \m {\M{Z}} with each entry being i.i.d.\ standard Gaussian.
-\Disp {
-\NC \M {Z} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR
+Since we restrict our discussion to a specific snapshot of time, the noise term may be simply taken as a matrix \m {\M {Z}} with each entry being i.i.d.\ Standard Normal.
+\DispN {
+\NC \M {Z} \in \NC \MB {C} ^{N_Y \D  N_Y} \NR
 }
 We may introduce the effective channel
-\Disp {
-\NC \M{Y}
-:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
+\DispN {
+\NC \M {Y}
+:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
 }
-We restate the equation with event space index for greater clarity,
-\Disp {
-\NC \NC \M{Y} \SB {\o_t, \o_h, \o_z, \o_r} \NR
-\NC := \NC \M{W}_B \SB {\o_r} \M{W}_R \SB {\o_r} \RB {\M{H} \SB {\o_h} \M{F}_R \SB {\o_t} \M{F}_B \SB {\o_t} +\M{Z} \SB {\o_z} } \NR
-}
-
-Our task, then, is the recovery of \m {\M {H}}, and the design of \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}.
+Our task, then, is the recovery of \m {\M {H}}, and the design of \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.
 
@@
 First, for short we set
-\Disp {
+\DispN {
 \NC N_h
@@
 If we had followed the widely accepted approach of compressive channel sensing, we would have written
-\Disp {
+\DispN {
 \NC \V {h}
-\in \NC \MB {V}_{\MB {C}} \SB {N_h} \NR
+\in \NC \MB {C} ^{N_h} \NR
 \NC \V {h}
@@
 \NC \V {y}
-\in \NC \MB {V}_{\MB {C}} \SB {N_y} \NR
+\in \NC \MB {C} ^{N_y} \NR
 \NC \V {y}
@@
 \NC \V {z}
-\in \NC \MB {V}_{\MB {C}} \SB {N_y} \NR
+\in \NC \MB {C} ^{N_y} \NR
 \NC \V {z}
-:= \NC \Rm {vec} \SB {\M{W}_B \M{W}_R \M {Z}} \NR
+:= \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}} \NR
 \NC \M {Q}
-\in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
+\in \NC \MB {C} ^{N_y \D  N_h} \NR
 \NC \M {Q}
-:= \NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR
+:= \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R} \NR
 }
-to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M{H}}} to be
-\Disp {
+to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M {H}}} to be
+\DispN {
 \NC \V {y}
@@
 Introduce the discrete Fourier transform matrix \m {\M {K}} defined to be
-\Disp {
-\NC \M {K} \in  \NC \MB {M}_{\MB {C}} \SB {N_H, N_H} \NR
+\DispN {
+\NC \M {K} \in  \NC \MB {C} ^{N_H \D  N_H} \NR
 \NC \M {K} \DB {n_1, n_2}
-= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss{i} n_1 n_2 /N_H}, \NR
+= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N_H}, \NR
 \NC \Q n_1, n_2
@@
 }
-Roman \m{\Ss{e}} and \m{\Ss{i}} denote the natural base and imaginary unit, respectively.
+Roman \m {\Ss {e}} and \m {\Ss {i}} denote the natural base and imaginary unit, respectively.
 Here recall that we have
-\Disp {
+\DispN {
 \NC \M {K}^\Adj \M {K}
@@
 Observe that, if we write
-\Disp {
+\DispN {
 \NC \M {G}
@@
 which has the interpretation as the angular space (i.e., spatial frequency domain) representation of \m {\M {H}}, then
-\Disp {
+\DispN {
 \NC \M {Y}
-\in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y} \NR
+\in \NC \MB {C} ^{N_Y \D  N_Y} \NR
 \NC \M {Y}
-=\NC \M {W}_B \M {W}_R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F}_R \M {F}_B
-+\M {W}_B \M {W}_R \M {Z} \NR
+=\NC \M {W} _B \M {W} _R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F} _R \M {F} _B
++\M {W} _B \M {W} _R \M {Z} \NR
 }
@@
 To simplify notation, set
-\Disp {
+\DispN {
 \NC \M {P}
-\in \NC \MB {M}_{\MB {C}} \SB {N_y, N_h} \NR
+\in \NC \MB {C} ^{N_y \D  N_h} \NR
 \NC \M {P}
-:=\NC \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}} \NR
+:=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}} \NR
 }
 And accordingly
-\Disp {
+\DispN {
 \NC \V {g}
-\in \NC \MB {M}_{\MB {C}} \SB {N_h} \NR
+\in \NC \MB {M} _{\MB {C}} \SB {N_h} \NR
 \NC \V {g}
@@
 Then
-\Disp {
+\DispN {
 \NC \V {y}
@@
 \startitemize[n]
-\item Let \m{\g \geq 0} be given.
-\item Input \m {\M {F}_B \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_Y}, \M {F}_R \in \NC \MB {M}_{\MB {C}} \SB {N_H, N_R}, \M {W}_R \in \NC \MB {M}_{\MB {C}} \SB {N_R, N_H}, \M {W}_B \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_R}}, \m {\M {Y} \in \NC \MB {M}_{\MB {C}} \SB {N_Y, N_Y}},
-\item Find \m{\M {P} \in \MB {M}_{\MB {C}} \SB {N_y, N_h}}, \m{\V {y} \in \MB {V}_{\MB {C}} \SB {N_h}} as in above.
+\item Let \m {\g_{\Rm {DS}} \geq 0} be given.
+\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D  N_Y}, \M {F} _R \in \NC \MB {M} _{\MB {C}} \SB {N_H, N_R}, \M {W} _R \in \NC \MB {M} _{\MB {C}} \SB {N_R, N_H}, \M {W} _B \in \NC \MB {M} _{\MB {C}} \SB {N_Y, N_R}}, \m {\M {Y} \in \NC \MB {M} _{\MB {C}} \SB {N_Y, N_Y}},
+\item Find \m {\M {P} \in \MB {C} ^{N_y \D  N_h}}, \m {\V {y} \in \MB {C} ^{N_h}} as in above.
 \item Calculate
-\Disp {
+\DispN {
 \NC \Hat {\V {g}}
 \LA \NC \startcases
-\NC \Min {\V {g}' \in \MB {V}_{\MB {C}} \SB {N_h}}  \MC \VNm {\V {g}'} _1 \NR
-\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g \NR
+\NC \Min {\V {g}' \in \MB {C} ^{N_h}}  \MC \VNm {\V {g}'} _1 \NR
+\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\Rm {DS}} \NR
 \stopcases \NR
@@
 \item Convert \m {\Hat {\V {g}}} back to the space domain, namely
-\Disp {
+\DispN {
 \NC \Hat {G}
@@
 \item Recover the estimated \m {\Hat {\M {H}}}, as
-\Disp {
+\DispN {
 \NC \Hat {\M {H}}

### 2019-09-22 paper/3_1_almost_sparsity.tex
Use BibTeX, conform to IEEE citation style

@@
 
-We first show that \m {\SB {\V {g}}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
+We first show that \m {\V {g}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
 We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in Chapter 2.
 
-Let \m {\hat {\V {g}}} be the Dantzig Selector.
-Split \m {\V{g}} into two parts: \m {\V {g} _\MC {A}}, the largest \m {S} positions of \m {\V{g}}, \m {\V {g} _\MC {A}} the next \m {S} largest positions of \m {\V{g}}, and \m {\V {g} _\MC {K}} are the positions complement to \m {\V {g} _\MC {A}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _\MC {A} =\IP {0,3,0,0,8}}, \m {\V {g} _\MC {B} =\IP {-1,0,0,2,0}}, and \m {\V {g} _\MC {A} =\IP {-1,0,-4,2,0}}.
-We rephrase it formally.
+Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity index \m {S} be given.
+Split \m {\V {g}} into two parts: \m {\V {g} _{\MC {A}}}, the largest \m {S} components of \m {\V {g}}, \m {\V {g} _{\MC {A}}} the next \m {S} largest components of \m {\V {g}}, and \m {\V {g} _{\MC {C}}} are the components complement to \m {\V {g} _{\MC {A}}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\MC {A}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\MC {B}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\MC {A}} =\IP {-1,0,-4,2,0}}.
 
-\Result
-{Definition}
-{
-Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
-Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
-\Disp {
-\NC \V{v} \DB {\s \SB {n}}
-\leq \NC \V{v} \DB {\s \SB {n-1}} \NR
-\NC n =\NC 1, \ldots, N_p-1 \NR
-}
-Its existence is evident.
+We hope that \m {\VNm {\V {g} _{\MC {C}}} _1} is small.
 
-For fixed \m {S}, define
-\Disp {
-\NC \MC {S} \SB {\V{x}, S}
-=\NC \sum_{i=0} ^{S-1} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR
-\NC \MC {C} \SB {\V{x}, S}
-=\NC \sum_{i=S} ^{N_p} \V {x} \DB {\s \SB{i}} \V {u} _{\s \SB{i}} \NR
-}
-}
-
-Now set
-\Disp {
-\NC \V{g} _{\MC {A}}
-=\NC \MC {S} \SB {\V{g}, S} \NR
-\NC \V{g} _{\MC {K}}
-=\NC \MC {C} \SB {\V{g}, S} \NR
-\NC \V{g} _{\MC {B}}
-=\NC \MC {S} \SB {\V{g} _\MC {K}, S} \NR
-}
-We hope that \m {\VNm {\V{g} _\MC {K}}_1} is small.
-
-\Result
-{Definition}
-{
-For \m {\V {x} \in \MB {V}_{\MB {K}} \SB {N}}, we say \m {\V {x}} is almost-\m {s}-sparse according to the \m {\ell_p}-norm with remainder \m {R}, if
-\Disp {
-\NC \VNm {\MC {C} \SB{\V {x}, s}} _p
-\leq \NC R. \NR
-}
+\m {\M {H}} is the function of \m {\V {a}}, and we seek to establish that \m {\V {a}} is almost sparse.
+We define, similarly, \m {\V {a} _{\MC {A}}} and \m {\V {a} _{\MC {C}}}, with undetermined sparsity index \m {s}.
+First, we investigate
+\DispN {
+\NC \NC \VNm {\V {a} \SB {\f} _{\MC {C}}} _2 ^2 \NR
+\NC =\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\MC {C}}} _2 ^2 \NR
 }
@@
 Let \m {\f} be fixed.
-It suffices to bound
-\Disp {
-\NC \NC \VNm {
-   \MC {C} \SB {\M {K}^\Adj \V {a} \SB {\f}, s}
-} _2 ^2 \NR
-}
-
-Towards that end, introduce
-\Disp {
+Towards that end, 
+Introduce
+\DispN {
 \NC \psi \SB {\f, n_H}
@@
    \RB {
-      \RB {\f \; \Rm{Mod}\; \F{2\pi}{N_H}}
+      \RB {\f \; \Rm {Mod}\; \F {2\pi} {N_H}}
       +\F {2 \pi n_H} {N_H}
@@
    } \;
-   \Rm{Mod}\; \RB {2\pi}
+   \Rm {Mod}\; \RB {2\pi}
 }
@@
 Note that by construction
-\Disp {
+\DispN {
 \NC \Nm {\psi \SB {\f, n_H}}
@@
 And define the so-called Dirichlet kernel
-\Disp {
+\DispN {
 \NC D \SB {\psi'}
@@
 Then observe
-\Disp {
+\DispN {
 \NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {n_H}
-=\NC \F {1}{N_H} D \SB {\psi \SB {\f, n_H}} \NR
+=\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
 }
@@
 Now, by the nature of alternating series, for \m {-\pi \leq x < \pi}, it holds that
-\Disp {
-\NC \Nm {x - \F {x^3}{6}} \leq \NC \Nm {\sin x}. \NR
+\DispN {
+\NC \Nm {x - \F {x^3} {6}} \leq \NC \Nm {\sin x}. \NR
 }
@@
 Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
-\Disp {
+\DispN {
 \NC \Nm {D \SB {\psi'}}
-= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}}{\Nm {\sin \SB {\psi' /2}}} \NR
+= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
 \NC \leq \NC B \SB {\psi'} \NR
-\NC := \NC \F {48}{\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
+\NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
 \NC -\pi \leq \NC \psi' < \pi. \NR
@@
 Thus,
-\Disp {
-\NC R^2
-=\NC \F {1}{N_H^2}
+\DispN {
+\NC \VNm {\V {a} \SB {\f} _{\MC {C}}} _1
+=\NC \F {1} {N_H}
 \VNm {
-\MC {C}
-\SB{
+\RB {
    \sum_{n_H' =0}^{N_H -1}
       B \SB {\psi \SB {\f, n_H'}}
-   \V {u}_{n_H'},
-   s
-}
-} _2^2
+      \V {u} _{n_H'}
+} _{\MC {C}}
+} _1
 \NR
@@
 Anyway, a moment's reflection shows
-\Disp {
-\NC R^2
-\leq \NC \F {1}{N_H^2} \D \F {N_H}{2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
+\DispN {
+\NC \VNm {\V {a} \SB {\f} _{\MC {C}}} _1
+\leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
 \NC = \NC \F {2304} {N_H \pi^6}
-\int _{s /N_H} ^1 \F{1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
-\NC =\NC \F{1} {2\pi^2 N_H}
+\int _{s /N_H} ^1 \F {1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
+\NC =\NC \F {1} {2\pi^2 N_H}
 \RB {
@@
 +\F {4\pi^2 u} {24 -\pi^2 u^2}
-+\R{6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R{6}}}
++\R {6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R {6}}}
 }
@@
 \NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR
-}
-In the last step we bound the lower limit of the second and third term with \m {x' =0}, and leave the dominating \m {1/x'}.
-
-Expanding \m {R} gives
-\Disp {
-\NC R
-\leq \NC \F {2} {\pi} \D \F {1} {\R{s}} +\F {\R {s}} {38 N_H}. \NR
+\NC \approx \NC \F {4} {\pi^2 s} \NR
 }
 
-Fixing \m {N_H}, it shall be easy to see that rhs is strictly decreasing in \m {N_H}, and the value of \m {s} that minimizes it is about \m {s =5N_H}.
-In the range that we care, rhs is thus strictly decreasing in \m {s}.
-\m {N_H}.
+% % Deprecated!
+% \DispN {
+% \NC R^2
+% \leq \NC \F {1} {N_H^2} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
+% \NC = \NC \F {2304} {N_H \pi^6}
+% \int _{s /N_H} ^1 \F {1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
+% \NC =\NC \F {1} {2\pi^2 N_H}
+% \RB {
+%   -\F {8} {u}
+% +\F {4\pi^2 u} {24 -\pi^2 u^2}
+% +\R {6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R {6}}}
+% }
+% \Bigg \| _{s/N_H} ^1 \NR
+% \NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR
+% \NC \approx \NC \F {4} {\pi^2 s} \NR
+% }
+% In the last step we bound the lower limit of the second and third term with \m {x' =0}, and leave the dominating \m {1/x'}.
 
@@
 {
-Let \m {\f \SB {\o_h}} be given, and linear array response \m {\V {a} \SB {\f}} defined as in ().
+Let \m {\f } be given, and linear array response \m {\V {a} \SB {\f}} defined as in ().
 Suppose \m {N_H \geq 4}.
-Then, for all instances of \m {\f}, \m {\V {a} \SB {\f}} is almost-\m {s}-sparse according to the \m {\ell_2}-norm with remainder \m {R} to be
-\Disp {
-\NC R
-\leq \NC \m {\F{1}{3 \R{N_H}}} \NR
+Then, for any instance of \m {\f},
+\PF {R;2,p'}
+\DispN {
+\NC \VNm {\V {a} \SB {\f} _{\MC {C}}} _2
+\leq \NC \F {2} {\pi \R{s}} \NR
 }
@@
 
-Since the bound is also decreasing in \m {N_H}, for concreteness, let us plug in \m {N_H =4} for the upper bound, giving
-\Disp {
+Since the value of \m {s} is at our disposal, we try
+\PF {s;nn-hh,}
+\DispN {
+\NC s
+=\NC \R {\log N_H} \NR
+}
+so that
+\PF {R;2,p'}
+\DispN {
 \NC R
-\leq \NC \F {1} {6} \NR
+\leq \NC \F {2} {\pi \R{\log N_H}} \NR
 }
@@
 
-It remains to bound \m {\VNm {\M {G}} _F}.
+Recall that, by \m {\ell_p}-norm inequality,
+\DispN {
+\NC \VNm {\M {g} _{\MC {C}}} _1
+\leq \NC N_H \VNm {\M {g} _{\MC {C}}} _2 \NR
+}
+So it remains to bound \m {\VNm {\M {G}} _F}.
 Note that
-\Disp {
-\NC \VNm {\M {G}}_F
-=\NC \VNm {\M {H}}_F \NR
+\PF {G;H,a'-l}
+\DispN {
+\NC \VNm {\M {G}} _F
+=\NC \VNm {\M {H}} _F \NR
+\NC \NC \VNm {\sum _{l=0} ^{L-1} \a_l
+\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj} _F \NR
 }
-So it suffices to consider \m {\VNm {\M {H}} _F}.
-
-\Disp {
-\NC \VNm {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F
-\leq \NC \sum _{l=0} ^{L-1} \Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
+By triangle inequality, by the property of 2-norm and Frobenius norm,
+\PF {;a'-l,a,f'-l}
+\DispN {
+\NC \leq \NC \sum _{l=0} ^{L-1} \Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
 \NC \leq \NC
-\sum _{l=0} ^{L-1}
-\Nm {\a_l} \VNm {\V {a} \SB {\f_l}} _2
+\sum _{l=0} ^{L-1} \Nm {\a_l}
+\VNm {\V {a} \SB {\f_l}} _2
 \VNm {\V {a} \SB {\th_l}} _2 \NR
 }
-Lastly, we know \m {\ell_1}-norm is larger than \m {\ell_2}-norm.
-Since \m {\ell_1}-norm will be used in later proof, we display the statement about \m {\ell_1}-norm.
-\Disp {
-\NC \NC \MB {E} \SB {\VNm {\MC {C} \SB {\sum _{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj}} _F} \NR
-\NC \leq \NC \F {1} {9 \R{N_H}} \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}} \NR
-\NC \leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR
+It follows that
+\DispN {
+\NC \VNm {\M {H} _{\MC {C}}} _F
+\leq \NC
+\sum _{l=0} ^{L-1} \Nm {\a_l}
+\VNm {\V {a} \SB {\f_l} _{\MC {C}}} _2
+\VNm {\V {a} \SB {\th_l} _{\MC {C}}} _2 \NR
+\NC \leq \NC
+\VNm {\V {a} \SB {\f_l} _{\MC {C}}} _2
+\VNm {\V {a} \SB {\th_l} _{\MC {C}}} _2
+\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
+\NC \leq \NC
+\F {4} {\pi^2 \log N_H}
+\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
 }
+
+Observe that
+\DispN {
+\NC \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}}
+=\NC \F{\R {2} L} {\R {\pi}} \NR
+}
+\DispN {
+\NC \Ss {Var} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}}
+=\NC \RB {1 - \F{2}{\pi}} L \NR
+}
+
+We expect that
+\DispN {
+\NC \sum _{l=0} ^{L-1} \Nm {\a_l}
+\leq \NC L \R {\F {2} {\pi}}
+   +\R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2} \NR
+\NC \approx \NC \R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2} \NR
+}
+Thus, by Chebyshev inequality,
+\DispN {
+\NC \MB {P} \SB {
+   \sum _{l=0} ^{L-1} \Nm {\a_l}
+   \geq \R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2}
+}
+\leq \NC \F {1} {\RB {\log N_H} ^3} \NR
+}
+Summarizing, we have the following result.
 
@@
 {
-Let \m {\f \SB {\o_h}} and \m {\th \SB {\o_h}} be uniformly, independently distributed in \m {[0,2\pi)}, and let \m {\V {g} \in \MB{V}_\MB{C} \SB{N_h}} be defined as in ().
-If \m {N_h \geq 4^2 =16}, then \m {\V {g}} is almost-\m {s^2 L}-sparse with \m {\ell_1}-residue \m {R} to be
-\Disp {
-\NC R
-\leq \NC \F {\R{\pi} L} {3 \R{N_H}} \NR
+Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)},
+and let \m {\V {g} \in \MB {C} ^{N_h}} be defined as in ().
+Then the bound
+\PF {g-C;4,p'-2}
+\DispN {
+\NC \VNm {\M {g} _{\MC {C}}} _1
+\leq \NC \F {4} {\pi^2} \R {1 -\F {2} {\pi}} L N_H \R {\log N_H} \NR
+}
+holds with probability \m {p} such that
+\PF {1,p;1}
+\DispN {
+\NC 1 -p
+\leq \NC \F {1} {\RB {\log N_H} ^3} \NR
 }

### 2019-09-22 paper/3_2_isometry_new.tex
Use BibTeX, conform to IEEE citation style

\startsection [title={Restricted Isometry of Effective Beamformer}]
\startsubsection [title={Design of Beamformer Matrices}]

Our plan is setting the four precoder matrices to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.

Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ Normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
We know that the magnitude \m {\M {F} _B \DB {n_R, n_Y}} follows Rayleigh distribution.
\m {\M {W} _B ^\Tr \DB {n_Y, n_R}} is set in an entirely analolous manner.

In addition, let \m {\M {F} _R \DB {n_H, n_R}} be uniformly distributed on the unit circle on the complex plane.
\m {\M {W} _R ^\Tr \DB {n_Y, n_R}} is set in an entirely analolous manner.

Existent result () guarantee that both \m {\M {F} _B ^\Tr} and \m {\M {F} _R ^\Tr} are RIP, and same can be said of \m {\M {W} _B} and \m {\M {W} _R}.
Consider a sparse \m {\V {u}} or unity norm, then existent result guarantees that \m {\M {F} _R ^\Tr \V {u}} has almost unity norm.
If, furthermore, \m {\M {F} _R ^\Tr \V {u}} is sparse, we see that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has almost unity norm, and the RIP of \m {\M{P}} also follows by construction.

However, it is not clear that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, have RIP, nor that, \m {\M {P}}, the result of Kronecker product, is RIP.
In fact, the statement seems to be false in general.
Indeed, since a \m {\M {F} _R ^\Tr} of the same \m {\d} is sparse, up to a factor of isometry matrix, and \m {\M {F} _R ^\Tr} is generated randomly, it would seem to us that the probability that \m {\M {F} _R ^\Tr \V {u}} be sparse is exceedingly small.

But all is not lost.
At least we have made sure that \m {\M {F} _R ^\Tr \V {u}} has norm close to unity.
If we have a stronger result, that \m {\M {F} _B ^\Tr \V {u}} is almost unitary even for \It {not-sparse} vectors, then we are done.
That does sound somehow plausible, considering the Normal entries of \m {\M {F} _B ^\Tr} would introduce a Central-limit-theorem-like sum, though the summands are not independent, but weakly dependent.

%The function is denoted f
%Use f to denote the function
%Let f denote the function
%Call the function f
%the function is called f

\startsubsection [title={Confirming the Restricted Isometry}]

### 2019-09-22 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Use BibTeX, conform to IEEE citation style

@@
 Set for short
-\PF {d:g,g}
-\Disp {
+\PF {d;g,g}
+\DispN {
 \NC \V {d} 
@@
 }
-And our task is to bound its expectation.
+And our task is to bound the expectation \m {\MB {E} \SB {\V {d}}}.
 
-We argue that \m {\V{g}} can essentially be seen as sparse, and for that purpose we ignore relevent terms.
+We argue that \m {\V {g}} can essentially be seen as sparse, and for that purpose we ignore relevent terms.
 Also, we do not seek a very tight bound and will approximate \m {\d_{S}} by \m {1}.
 And, as shall be seen, it suffices to set
-\Disp {
+\PF {g';2,nn-h}
+\DispN {
 \NC \g
@@
 
-The rest follows \quotation {The Dantzig Selector} very closely.
-The generalization to complex vector is necessary in our setting.
-We spell out the proof when such generalization is nontrivial.
+The rest follows \quotation {The Dantzig Selector} very closely, but sometimes, the generalization to complex vector cannot be glossed over, and we have to examine.
+To start, we state several lemmata (or their generalization) shown in their paper.
 
@@
 {
-Let \m {\V {g}} and \m {\V {d}} be defined as above.
-Then
-\Disp {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {K}}} _1 \NR
+\PF {d-K;d-A,2-g-K}
+\DispN {
+\NC \VNm {\V {d} _{\MC {C}}} _1
+\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {C}}} _1 \NR
 }
@@
 
-To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {K}},
-\Disp {
+To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}}, while recalling that \m {\V {g} =\V {g} _{\MC {A}}},
+\PF {g,d-A,d-K}
+\DispN {
 \NC \VNm {\V {g}} _1
 -\VNm {\V {d} _{\MC {A}}} _1
-+\VNm {\V {d} _{\MC {K}}} _1
--\VNm {\V {g} _{\MC {K}}} _1
++\VNm {\V {d} _{\MC {C}}} _1
+-\VNm {\V {g} _{\MC {C}}} _1
 \leq \NC \VNm {\V {g} +\V {d}} _1 \NR
+\NC =\NC \VNm {\hat {\V {g}}} _1 \NR
 }
-In the first line, we recall \m {\V {g} =\V {g} _{\MC {A}}}.
 On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
-\Disp {
-\NC \VNm {\V {g} +\V {d}} _1
-=\NC \VNm {\hat {\V {g}}} _1 \NR
+\PF {g,d;g}
+\DispN {
 \NC \leq \NC \VNm {\V {g}} _1 \NR
-}
-The result follows by combining.
-
-\Result
-{Lemma}
-{
-\Disp {
-\NC \MB {E} \SB {\Nm {\IP {\V {z} \SB {\o_z}, \M {P} \DB {:, n_h}}}}
-\leq \NC  2 \R {\log N_h} \NR
-\NC n_h 
-=\NC 1, \ldots, N_h. \NR
-}
-with probability \m {\geq 1 -N_h^{-1}}.
-}
-
-Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
-
-Recall the following bound for \m {Q} function
-\Disp {
-\NC Q\SB {x}
-\leq \NC \F {1}{2} \Ss {e}^{-x^2/2} \NR
-}
-Particularly, for \m {x =\R {2 \log N_h}},
-\Disp {
-\NC Q\SB {\R {2 \log N_h}}
-=\NC \F {1}{N_h}. \NR
 }
@@
 {
-With the condition that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M{P}}},
-\Disp {
+Let \m {\M {P}} be fixed, and instance of \m {\V {z}} be given.
+Then the relation
+\PF {E,z,P}
+\DispN {
+\NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}}
+\leq \NC  2 \R {\log N_h} \NR
+\NC n_h 
+=\NC 1, \ldots, N_h. \NR
+}
+holds with probability \m {\geq 1 -N_h^{-1}}.
+}
+
+Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}, the quantity \m {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}} observes standard Normal.
+Recall the following bound for \m {Q} function
+\PF {Q,x;1}
+\DispN {
+\NC Q\SB {x}
+\leq \NC \F {1} {2} \Ss {e}^{-x^2/2} \NR
+}
+Particularly, for \m {x =\R {2 \log N_h}},
+\PF {Q,2;nn-h}
+\DispN {
+\NC Q\SB {\R {2 \log N_h}}
+=\NC \F {1} {N_h}. \NR
+}
+
+\Result
+{Lemma}
+{
+With the assumption that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M {P}}}, then
+\PF {P,P,d}
+\DispN {
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
@@
 }
-with probability \m {\geq 1 -N_h^{-1}}.
+holds with probability \m {\geq 1 -N_h^{-1}}.
 }
@@
 To show this, by definition
-\Disp {
+\PF {z,y,P}
+\DispN {
 \NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
@@
 By construction
-\Disp {
+\PF {P,n-y,y}
+\DispN {
 \NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
@@
 By triangle inequality, together with Lemma (), we have
-\Disp {
+\PF {P,n-y,y}
+\DispN {
 \NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
@@
 which implies
-\Disp {
+\PF {P,P,d} \DispN {
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
@@
 
-From \quotation {Dantzig Selector} Lemma 1, first equation, we have the result as below.
-The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
-The only thing that has to change accordingly is the interpretation of magnitude and the inner product, which are evident.
-
+The following two lemmata, coming from \quotation {Dantzig Selector} Lemma 1, will be stated without proof.
+The generalization from the original real vector spaces to present complex ones is valid, and completely straightforward.
+Note that the interpretation of magnitude and the inner product has to be changed accordingly.
 \Result
@@
 {
-With the condition that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M{P}}},
-\Disp {
+With the assumption that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M {P}}},
+\PF {d-A-B;1,1}
+\DispN {
 \NC \VNm {\V {d} _{\MC {AB}}} _2
-\leq \NC \F {1}{1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}}{\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {K}}} _1 \NR
+\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}} {\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {C}}} _1 \NR
 }
 }
-
-From \quotation {Dantzig Selector}, Lemma 1, second equation, we have the result as below.
-Again, their proof works with complex vector spaces in place of real ones too.
-
+And
 \Result
@@
 {
-\Disp {
+\PF {d-A-B;1,1}
+\DispN {
 \NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{S} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
+\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\MC {C}}} _1^2 \NR
 }
@@
 We are going to combine previous lemmata and show the main result.
-
-In accordance with (), set
-\Disp {
+Now, in view of the result in Section 3.1, \m {s} is free, and we set
+\PF {s,1,,}
+\DispN {
+\NC s
+=\NC 1 \NR
+}
+which is crude, but enough.
+Accordingly,
+\PF {S;L,nn-hh}
+\DispN {
 \NC S
-=\NC s^2 L \NR
+=\NC L \R {\log N_H} \NR
 }
-If we set again \m {s =\R{N_H}}, we get \m {S =N_H L}.
+Just for simplicity, we assume
+\PF {d'-S;1,2}
+\DispN {
+\NC \d_S
+\leq \NC \F {1} {2} \NR
+}
+and
+\PF {L;4,}
+\DispN {
+\NC L
+\geq \NC 4 \NR
+}
 
@@
 {
-Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
+Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as ()....
 Then the bound
-\Disp {
+\PF {d;4,2}
+\DispN {
 \NC \VNm {\V {d}} _2
-\leq \NC 4 \R{2} \D \R{L N_H \log N_H} \NR
+\leq \NC 4 \R {2} \D \R {L \log N_H} \NR
 }
 holds for probability \m {p}, with
-\Disp {
+\DispN {
 \NC 1 -p
-\leq \NC 2 \D 6^S \D \exp \SB {-\F{N_Y^2} {32}} \NR
+\leq \NC 2 \D 6^L \D \exp \SB {-\F {N_Y^2} {32}} \NR
 }
@@
 
-The first quantity we want to bound away is
-\Disp {
+By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {s,1,,} and \Rf {P,P,d},
+\PF {P-A-B,P,d}
+\DispN {
 \NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
@@
 \NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
-\NC \leq \NC 4 \R {S \log N_h} \NR
-}
-Thus, by virtue of Lemma (), and approximating \m {1 /(1 -\d_{2S}) =1 +\d_{2S}} and so on,
-\Disp {
-\NC \VNm {\V {d}_{\MC {A}}} _1
-\leq \NC \R {S} \VNm {\V {d}_{\MC {A}}} _2 \NR
-\NC \leq \NC \R {S} \VNm {\V {d} _{\MC {AB}}} _2 \NR
-\NC \leq \NC \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
-+4 \RB {1+\d_{2S}} S \R {\log N_h} \NR
+\NC \leq \NC 4 \R {2 L \log N_H} \NR
 }
 
-Next, we must eliminate \m {\VNm {d _{\MC {A}}} _1} in rhs of Lemma ().
-\Disp {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\NC \leq \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
-+4 \RB {1+\d_{2S}} S \R {\log N_h}
-+2 \VNm {\V {g} _{\MC {K}}} _1 \NR
+By \m {\ell_p} norm inequality, by the definition of truncation, by \Rf {d-A-B;1,1}, \PF {d'-S;1,2}, and \PF {P-A-B,P,d} just above,
+
+\PF {d-A;L,d-A}
+\DispN {
+\NC \VNm {\V {d} _{\MC {A}}} _1
+\leq \NC \R {L} \VNm {\V {d} _{\MC {A}}} _2 \NR
+\NC \leq \NC \R {L} \VNm {\V {d} _{\MC {AB}}} _2 \NR
+\NC \leq \NC 8 \R {2 \log N_H}
++\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {d} _{\MC {C}}} _1 \NR
 }
-Arranging and drop second order small terms like \m {\d_{2S} \d_{3S}}, that is,
-\Disp {
-\NC 1 \ll \NC S \NR
-\NC \ll \NC N_h \NR
+
+Next, we want to use \Rf {d-K;d-A,2-g-K} to eliminate \m {\VNm {d _{\MC {A}}} _1} in \Rf {d-A;L,d-A}.
+\PF {;8,2,nn-hh}
+\DispN {
+\NC \leq \NC 8 \R {2 \log N_H}
++\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \RB {\VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {C}}} _1} \NR
+\NC \leq \NC 8 \R {2 \log N_H}
++\F {2} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {g} _{\MC {C}}} _1 \NR
 }
-doing this we have
-\Disp {
-\NC \VNm {\V {d} _{\MC {K}}} _1
-\leq \NC 2 \RB {1+\d_{3S}} \VNm {\V {g} _{\MC {K}}} _1
-+4 \RB {1+2\d_{3S}} S \R {\log N_h} \NR
+And \Rf {g-C;4,p'-2} in Section 3.1 gives
+\PF {d-A;8,2}
+\DispN {
+\NC \VNm {\V {d} _{\MC {A}}} _1
+\leq \NC 8 \R {2 \log N_H}
++2\VNm {\V {g} _{\MC {C}}} _1 \NR
+\NC \leq \NC \RB {16 \R {2} +\F {4} {\pi^2} \R {1 -\F {2} {\pi}}} \log N_H \NR
 }
@@
 We are now in a position to bound \m {\VNm {d} _2^2}.
-Using Lemma () again, and only keeping to first order, we have
-\Disp {
+Using Lemma () again, we have
+\DispN {
 \NC \VNm {\V {d}} _2^2
-\leq \NC 16 S \log N_h
-+8 \d_{3S} \R {\log N_h} 
-+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {K}}} _1 \NR
+\leq \NC 32 S \log N_H
++8 \d_{3S} \R {2 \log N_H} 
++\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {C}}} _1 \NR
 }
-Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {K}}} _1}.
+Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {C}}} _1}.
 Again for simplicity, we keep only the first order small terms.
-Plug in \m {S =s^2 L} and \m {N_h =N_H^2} we get, finally,
-\Disp {
+\DispN {
 \NC \VNm {\V {d}} _2^2

### 2019-09-22 paper/4_simulation.tex
Use BibTeX, conform to IEEE citation style

@@
 
+We do three series of experiments, which are of size from small to large.
+In three experiments, we take respectively \m {L} to be \m {2, 3, 4}, \m {N_Y} to be \m {5, 7, 9}, \m {N_R} to be \m {10, 14, 18}, and \m {N_H} to be \m {20, 28, 36}.
+
+Other parameters are fixed in these experiments; 
+The number of grid of quantization of analog precoder is 16
+The wavelength of the EM wave that antenna is emitting, \m {\l _{\Rm{ant}} = 1}, is set to be 0.1.
+and the antenna spacing \m {d _{\Rm{ant}} =3}.
+Note that only their ratio matters.
+See chapter 2 for meaning of them.
+
+There are also parameters related to the convex optimization algorithm.
+The tolerance of absolute error in the primal-dual algorithm used in CVXPY is set as \m {10^{-4}}, and the tolerance of relative error, as \m {10^{-3}}.
+The maximal number of iteration of CVXPY is set to be \m {32}.
+On the other hand, the maximal number of iteration of OMP is set to be \m {4 N_H}.
+
+Each data point is repeated for 32 times, and taken average.
+We plot the absolute log error
+\DispN {
+\NC \eta_{\Rm{abs}}
+=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}, \NR
+}
+and relative log error.
+\DispN {
+\NC \eta_{\Rm{rel}}
+=\NC \F {\RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}}
+{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
+}
+The averaged error values are plotted along with the theoretical expected error of DS, derived in chap.\ 3, namely
+\DispN {
+\NC \eta_{\Rm{th}}
+=\NC \F{5}{2} + \log \RB{L N_H} + \log \log N_H \NR
+}
+
+Several threshold values occur in relevant alorithms.
+The threshold used in DS program is called \m {\g_{\Rm {DS}}} here, and another threshold of Lasso, called \m {\a}.
+Yet another threshold used for the residue norm used in OMP program is called \m {\eta}.
+Various several values are tried for them, determined as thus: Take a central value roughly corresponding to the theory, and mutiply or divided the central value by powers of 2, or
+
+Concretely, we set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}}, corresponding to Cand\`es \& Tao (2007)
+For comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
+For OMP, suggested values in Cai \& Wang (2011) is illuminating.
+There, Theorem 7 considered \m {\ell _2}-norm, and Theorem 8, \m {\ell _\infty}-norm.
+We make simplification and set respectively \m {\R {3} N_Y} and \m {2 \R {\log N_H}}
+
 \stopsection
+
+\startsubsection [title={On Complexity}]
+
+In general, complexity analysis of convex program is difficult, in that it is not easily ensured how many iteration the program uses.
+Specifically, the implementers of CVXPY, Diamond and Boyd \cite [DiB16], alleges that the program is usually converted in to primal-dual problem.
+
+However, if we use Newton method and assume self-concordance, there is an analysis in B \& V.
+Such analysis, in our opinion, still gives us an idea about the complexity of the DS program.
+
+It can be shown that DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.
+
+The function being minimized is \m {\underset {x} {\Rm{min}} \VNm {\V {g}}_1}.
+Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
+Then the number of iteration of Newton method is bounded by
+\DispN {
+\NC \F {\VNm {\V {g}} _1 - \VNm {\V {g} ^{\star}}} {\g} + \log_2 \log_2 \F {1} {\e} \NR
+}
+Here \m {\g} is a parameter related to the Backtracking algorithm, and \m {\e} the tolerance of error.
+The details can be found in Boyd \& Vandenberghe (2004).
+They cites various numerical experiements, and it turns out almost always that a value of \m {\g} close to 1 gives the best result, so we take \m {\g} as a constant.
+
+Numerically, we see that the complexity of DS is generally very high.
+But it also depends on the tolerence of error.
+% XXX criticism on DS complexity?
 

### 2019-09-29 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Add preliminary complexity analysis

@@
 
-The rest follows \quotation {The Dantzig Selector} very closely, but sometimes, the generalization to complex vector cannot be glossed over, and we have to examine.
+The rest follows \cite [CaT07] very closely, but sometimes, the generalization to complex vector cannot be glossed over, and we have to examine.
 To start, we state several lemmata (or their generalization) shown in their paper.
@@
 \NC \VNm {\V {d} _{\MC {C}}} _1
-\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {C}}} _1 \NR
+\leq \NC \VNm {\V {d} _{\MC {A}}} _1
++2\VNm {\V {g} _{\MC {C}}} _1 \NR
 }

### 2019-09-29 paper/4_simulation.tex
Add preliminary complexity analysis

@@
 
-After the introduction of problem configuration and analysis of expected square error, we shall formulate our algorithm and focus on the practical aspects.
-As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} \SB {h}}.
+\startsection [title={Result}]
 
-It is mentioned in ``\m {\ell_1}-MAGIC'' (Cand\`es and J Romberg 2005) that the complex DS can be converted as an SOCP program.
-If so, primal-dual interior point algorithm (for example) may readily be applied on it to simplify the program, for which we may consult Boyd and Vandenberghe (2004), {\it Convex Optimization} chap.\ 11 as a standard reference.
+\startsubsection [title={Settings}]
+
+We are ready to verify theoretical bound of DS by numerical experiments.
+DS is a convex optimization program, and there are many library devoted on that.
+We choose the Python Library CVXPY.
 But we will not implement that here.
-For brevity, we use Python Library CVXPY to solve the complex DS.
-
-\startsection [title={Parameters}]
 
@@
 We plot the absolute log error
+\PF {h'-ABS;h,h}
 \DispN {
@@
 and relative log error.
+\PF {h'-REL;h,h}
 \DispN {
@@
 The averaged error values are plotted along with the theoretical expected error of DS, derived in chap.\ 3, namely
+\PF {h'-TH;5,2}
 \DispN {
@@
 For comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
-For OMP, suggested values in Cai \& Wang (2011) is illuminating.
-There, Theorem 7 considered \m {\ell _2}-norm, and Theorem 8, \m {\ell _\infty}-norm.
+For OMP, suggested values in Cai \& Wang (2011) is illuminating, where they (in their Theorem 7) considered \m {\ell _2}-norm, and Theorem 8, \m {\ell _\infty}-norm.
 We make simplification and set respectively \m {\R {3} N_Y} and \m {2 \R {\log N_H}}
+
+\stopsubsection
+
+\startsubsection [title={Plots}]
+
+\stopsubsection
+
+\startsubsection [title={Discussion}]
+
+Reasonably, for all methods, a higher \m {\s} corresponds to higher \eta_{\Rm{rel}} and \eta_{\Rm{rel}}.
+The trends of absolute and relative error are the same, and in the below we call them simply error.
+
+From our simulation result, DS has usually the least error.
+For low SNR it is slightly but steadily outperforms OMP, and for high SNR the difference becomes vanishingly small and is sometimes surpassed by OMP.
+Different values of threshold \m {\g_{\Rm{DS}}} matter, and a smaller \m {\g_{\Rm{DS}}} does not necessarily give a lower error.
+It seems \m {\g_{\Rm{DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is intuitive.
+
+The error of OMP is slightly higher than DS, but the trend is less steady as well.
+Interestingly, different values of threshold \m {\eta} do not seem to affect much to performance, and often the iteration stablizes much earlier than is constrained by maximum iteration number.
+Lasso has substantially higher error than OMP, and Least Square (pseudo inverse) is still worse.
+
+Lastly, the theoretical bound for expected error of DS is much looser than the actual perfomance, and is well above the Least Square line, making it the highest line of all.
+Our bound is correct but not tight enough.
 
@@
 
-\startsubsection [title={On Complexity}]
+\startsection [title={Complexity}]
 
-In general, complexity analysis of convex program is difficult, in that it is not easily ensured how many iteration the program uses.
-Specifically, the implementers of CVXPY, Diamond and Boyd \cite [DiB16], alleges that the program is usually converted in to primal-dual problem.
+\startsubsection [title={Asymtotic Analysis}]
 
-However, if we use Newton method and assume self-concordance, there is an analysis in B \& V.
-Such analysis, in our opinion, still gives us an idea about the complexity of the DS program.
+We discuss the complexity of DS and OMP.
 
-It can be shown that DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.
+For DS, we note that, in general, complexity analysis of convex programs is difficult, in that it is not easily ensured how many iteration the program uses.
 
-The function being minimized is \m {\underset {x} {\Rm{min}} \VNm {\V {g}}_1}.
+There is an analysis in \cite [BoV04] of inequality constrained Newton method, in which they assumed self-concordance (discussed in p.496ff there, see also p.531).
+It is mentioned in Candès and Romberg \cite [CaR05] that the complex DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.
+However, it is not clear that Newton method is the fastest, nor that they are utilized in CVXPY.
+Specifically, the implementers of CVXPY, Diamond and Boyd \cite [DiB16], alleges that the program is usually converted in to primal-dual problem, and there are several different approaches in solving a primal-dual problem.
+But for our purpose, we only discuss the complexity analysis for Newton method.
+
+The function being minimized is \m {\VNm {\V {g}}_1}.
 Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
-Then the number of iteration of Newton method is bounded by
+Then \cite [BoV04] (p.505, eq.9.56) gives a bound of the number of iteration of Newton method.
+If just take that as the complexity bound for DS, it becomes
+\PF {cc-DS;cc-0,g-0}
 \DispN {
-\NC \F {\VNm {\V {g}} _1 - \VNm {\V {g} ^{\star}}} {\g} + \log_2 \log_2 \F {1} {\e} \NR
+\NC C_{\Rm{DS}}
+= \NC C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
++ \log_2 \log_2 \F {1} {\e} \NR
 }
-Here \m {\g} is a parameter related to the Backtracking algorithm, and \m {\e} the tolerance of error.
-The details can be found in Boyd \& Vandenberghe (2004).
-They cites various numerical experiements, and it turns out almost always that a value of \m {\g} close to 1 gives the best result, so we take \m {\g} as a constant.
+where \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error.
+According to the analysis of \cite [BoV04] (eq.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
+Also, \m {C_0} usually assumes the value of about several hundred;
+They gives an example \m {C_0 =375} (with their notation, \m {C_0 =\dfrac {20 -8\a} {\a \b \RB {1 -2\a}^2}}, where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).
 
-Numerically, we see that the complexity of DS is generally very high.
-But it also depends on the tolerence of error.
-% XXX criticism on DS complexity?
+Since we are doing big-O analysis, we feel that we have more license on making approximation.
+For concreteness, we may assume that we start the iteration by specifying the Least Square estimator as the initial value of \m {\V {g}_0}, namely
+\PF {g-0;g-LS,pp}
+\Disp {
+\NC \V {g}_0
+=\NC \V {g}_{\Rm {LS}} \NR
+\NC = \NC \RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {y} \NR
+}
+If we drop it, we may write the complexity of DS to be, simply,
+\PF {cc-DS;oo,g,g}
+\Disp {
+\NC C_{\Rm{DS}}
+=\NC \MC {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} \NR
+}
+For simplicity we assume
+\DispN {
+\PF {g;g,}
+\NC \V {g} ^\star
+\approx \NC \V {g} \NR
+}
+Indeed, this is the main objective of our investigation!
+And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
+\DispN {
+\PF {pp,pp;ii-nn-hh-2}
+\NC \M {P} ^\Adj \M {P}
+\approx \NC I _{N_{H}^2} \NR
+}
+Thus
+\Disp {
+\PF {cc;oo;g,pp}
+\NC C_{\Rm{DS}}
+=\NC \MC {O} \SB {
+   \VNm {\V {g} +\RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {z}
+   -\V {g}} _1} \NR
+\NC =\NC \MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} \NR
+}
+\m {\RB {\M {P} ^\Adj \V {z}} \DB {j}} Complex Normal distribution, and is easily bounded by \m {\s}.
+\Disp {
+\PF {;oo,nn-hh-2}
+\NC =\NC \MC {O} \SB {N_{H}^2 \s} \NR
+}
 
-\startsection [title={Discussion}]
+On the other hand, Tropp and Gilbert \cite [TrG07b] discussed the complexity of OMP, and they give
+\PF {cc-OMP;oo,nn-hh-2}
+\Disp {
+\NC C_{\Rm{OMP}}
+=\NC \MC {O} \SB {N_H^2 \log N_Y} \NR
+}
+And it would appear that this is greater than \m {C_{\Rm{DS}}}.
+However, we dropped some constants in analyzing \m {C_{\Rm{DS}}}, and here \m {\log N_Y} is really small in our case.
+If we drop it, then we get \m {\MC {O} \SB {N_H^2}} again.
 
-On the other hand, DS goes not without criticism for its large complexity (Friedlander and Saunders 2007).
-Indeed it is clear, even from the primal-dual implementation above, that DS requires memory for large dimensional vector, but OMP does not.
+At least our discussion suggests that, approximately
+\PF {cc-OMP;cc-DS}
+\Disp {
+\NC C_{\Rm{OMP}}
+\approx \NC C_{\Rm{DS}} \NR
+\NC \approx \NC \MC {O} \SB {N_H^2} \NR
+}
 
-And a meaningful comparison of bounds of OMP and DS is not easy, as their settings are somewhat different.
-The author thus criticises the tendency of current literature to mix up results for DS and OMP without clear justification.
-Indeed, DS calls for a RIP matrix and guarantees such performance even in noisy observation (Cand\`es and Tao 2005, 2007), while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
-On the other hand, as of OMP, besides the original justification of entrywise i.i.d.\ Gaussian sensing matrix (Tropp and Gilbert 2007a), and existent attempt to characterize MIP condition, there is much to be done OMP for Gaussian.
+\stopsubsection
+
+\startsubsection [title={Runtime Statistics}]
+
+Besides analytical bound, our result shows that DS indeed exhibits high complexity when (in our case) \m {N_H} grows, and the such rate of growth is significant, 
+Such computation cost is not suprising, even without knowing implementation details, from the nature of convex programming, being an iterative and random alrogithm.
+Moreover, DS requires a sizable memory for holding not only (in our case) \m {\M {P}}, and matrix multiplication of dimension \m {\M {N}_H^2}.
+Friedlander and Saunders \cite [FrS07] criticizes, according to their numerical experiments, that DS often gives a higher computational cost, compared to Lasso, corroborating our observation, 
+However we note that different settings of \m {\z}, tolerance of error, or maximal iteration number result in vastly different computation time.
+
+On the other hand, we see the complexity of OMP is several order of magnitude lower than that of DS.
+This is reasonable, given that it is a greedy alrogithm.
+In fact, the time OMP takes is negligibly small.
+
+Since LS involves the same target function as DS, the same argument also gives \m {C_{\Rm{Lasso}} =\MC {O} \SB {N_H^2}}.
+The numerical 
+We are not going to further discuss Lasso.
+
+\stopsubsection
 

### 2019-09-29 paper/5_conclusion.tex
Add preliminary complexity analysis

--- 2019-03-05 ongoing/report/5_conclusion.tex
@@
 
+Considering analytical bounds, it can be not easy to give meaningful comparison of existent bounds for these algorithms, as their settings are somewhat different, which we ought to keep in mind.
+Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation (Cand\`es and Tao 2005, 2007), while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
+On the other hand, as of OMP, besides the original justification of entrywise i.i.d.\ Gaussian sensing matrix (Tropp and Gilbert 2007a), there do not seem to be much analysis.
+and that (to add to complication) is still different from RIP.
+
 We cannot think OMP, or indeed every algorithm, as a universal solution.

### 2019-09-29 paper/conclusion.tex
Use BibTeX, conform to IEEE citation style
Add preliminary complexity analysis

--- 2019-03-05 ongoing/report/5_conclusion.tex
@@
 
-This article addresses the problem of effective and estimation of the millimeter wave channel by exploiting its sparsity.
-We motivated the problem, and provided a rather broad survey of recent literature.
-This article adopts The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
-Rather than exploiting the sparsity of space domain representation as existing literature does, we proceed the estimation algorithm in the spatial frequency domain.
-The technique is surely inspiring to future work, as many bounds are ready to be obtained once we change the physical model of the channel.
-In addition, we have, as a secondary product, derived the generalization of DS for complex vectors.
+This article addresses the problem of effective and estimation of the millimeter wave, multiple-input, multiple-output channel.
+We adopts the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
 
-Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Cand\`es and Tao (2007), that the probability that the expected square error is bounded is overwhelming.
-We thus have derived a probability bound of performance on a fairly general setting, where the bounding constant is expressed as an explicit function of physical parameters, such as the number of path.
+We proceed the estimation algorithm by exploiting its sparsity in spacial Fourier domain.
+We bounded the expected square error, and in doing so, following the spirit of Cand\`es and Tao \cite [CaT07], we characterizes the spacial sparsity, confirmed the restricted isometry of measurement matrix \m {\M {P}}, and justified the generalization for complex vectors space.
+The bound assumes a fairly general setting, and is expressed as an explicit function of physical parameters, such as the number of path \m {L} and channel dimension \m {N_H}.
 
-Afterwards we transformed DS into an SOCP, which is quite different as in the original DS (where we have an LP instead).
-Simulation is done, and DS's performance is compared to OMP.
-\color[red]{(To be done)}
-
-We cannot think OMP, or indeed every algorithm, as a universal solution.
-OMP trades off precision for time and space complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
-All in all, different problems requires different technique and algorihm within the current constraint, as is probably true in every discipline of engineering.
+Simulation is done, and DS's performance is compared to OMP, Lasso, and LS.
+In our case, DS performs better but gives higher complexity, and our analysis agrees the numerical experiment.
+Different problems requires solution within the feasible constraint, as is probably true in every discipline of engineering.
+Put concisely, no algorithm is a universal solution, and they trade off precision for time and space complexity, or conversely, among other things.
+We hope the investigation of DS can be a welcomed alternative added to the present literature of channel estimation.
 

### 2019-10-23 paper/1_introduction.tex
Add preliminary complexity analysis
Paraphrase chap 1

@@
 
-This section is organized as follows.
-We first provide the motivation, and then overview the existent literature on channel estimation.
-Particularly, we will summerize present results on DS and OMP, and argue that DS is a viable solution that has been ignored, and then claim our contribution in this article that will be shown in the later sections.
+\startsection [title={The Channel Sensing Problem}]
 
-\stopsection
+Multiple-input multiple-output (MIMO) communication system has been proposed to be incorporated into the 5G specification (Rappaport et.\ al.\ \cite [RSM13]).
+With a large number of antennae of both transmitter and receiver sides, it is expected to provide a large signal gain.
+However, its hardware overhead increases complexity and power consumption, and new precoders, and algorithms, are being invented to deal with this.
+Especially, millimeter waves (hereafter mm-wave), with smaller wavelength, leads to higher frequency bands, and thus wider bands to be available.
+In addition, the smaller closer spaced antennae makes it possible to increase the number of antennae.
+This being said, with more antennae present, conventional training-based algorithms also increase in complexity and storage.
 
-\startsection [title={Motivation of Compressed Channel Sensing}]
+The design of new algorithms that addressed these issues is thus necessary, and ideally, we would like to know the expression of channel in advance.
+The channel capacity is the major information theoretic metric to be considered in a communication system.
+Roughly, the capacity of a MIMO channel at perfect channel state information is well-known to be in the form \m {\log \det \RB {I +\Ss {snr}}}, but the expression of channel is hardly always available, and in fact, the explicit dependence of capacity on relevant parameters is often a difficult problem (Goldsmith et.\ al.\ \cite [GJJ03]).
+When the estimated channel is compromised, the ensuing analysis is also undermined.
 
-Multiple-input multiple-output (MIMO) communication system has been proposed to be the next-generation specification.
-With a large number of antennae of both transmitter and receiver sides (hereafter massive MIMO) is therefore expected to improve spectral efficiency.
-But MIMO presents new obstacles as well.
-The hardware overhead due to large number of antennas increases complexity and power consumption, and new precoders are being invented to take account of this.
-It is important to devise a feasible scheme, as the systems themselves are growing more complicated.
-Meanwhile, millimeter waves, having smaller wavelength, entails higher frequency bands, and thus wider available bandwith to be available.
-In addition, the smaller closer spaced antennae makes it possible to increase the number antennae.
-Consequently, this article considers MIMO in the millimeter r\`egime.
-
-The figure of merit of a MIMO system is usually considered to be the channel capacity.
-In vague terms, the capacity \m {C} of a MIMO channel \m {\M {H}} at perfect channel state information is well-known to be roughly in the form \m {\log \det \RB {I +\Rm {SNR}}}, but that knowledge is hardly always available.
-What makes things more difficult is the case that \m {\M {H}} is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
-It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
-Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
-Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \m {\log \det \RB {I +\Rm {SNR}}}.
-
-Therefore the real-time estimation, \m {\hat {\M {H}}}, of \m {\M {H}} is of paramount importance.
-Needless to say, when the \m {\hat {\M {H}}} is imprecise, resulting analysis is also undermined.
-With more antennae present, conventional training-based algorithms also increase in complexity and storage.
+It turns out that not only is the channel hard to estimate due to so many antennae, but the transmission is prone to noise corruption, 
 In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
-A design of new algorithms that addressed these issues is thus necessary.
 
@@
 
-It is a recent developement that the estimation of channels is facilitated by advances of compressed sensing.
-A series of paper by Cand\`es and Tao (2006) marks its advent.
-
-To motivate the need, we observe that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
-\DispN {
+It is a recent developement that the estimation of channels is facilitated by advances of the so-called \It {compressive sensing}.
+A series of paper by Candès and Tao marks its advent.
+They start by observing that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
+%
+\DispNum {N,p;Nm,Nm} {
 \NC N_p \gg N_m \NR
 }
-In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
-Of course, more assumption must be made to make the question meaningful.
-Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.
+%
+As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
+Another example, to quote \cite [CaT07], is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being.
 
-Cand\`es and Tao showed frst that that in the noiseless case (``Decoding by Linear Programming'', 2006), it is possible to recover the sparse signal, under a \m {\ell_1} minimization program.
-The work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
+But with insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
+Of course, more assumption must be made to make the question meaningful, since any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.
 
-Later they established a stronger result that (``The Dantzig Selector'', 2007), with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
-Such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
-Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
-In addition, they derived a probability bound of mean suqare error, showing the probability of successful recovery is overwhelming.
+They showed that in the noiseless case \cite [Can05], it is possible to recover the sparse signal, under a \m {\ell_1}-minimization program, revealing the phenomenon that fewer than \m {N_p} measurement suffices to resonstruct the \m {N_m}-dimensional signal, when it is sparse.
+Later they established a stronger result \cite [CaT07] that, with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too, but in doing so, we have to make a few carefully constructed, and seemingly random measurements.
 
-From the realistic perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
-Indeed, relevent code has been put on the web for the reader to access and verify (Cand\`es \& Romberg 2005).
-In this article we focus on DS, and we introduce several notions before we describe their work.
+From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
+Indeed, relevent code has been put on the web for the reader to access and verify (Candès \& Romberg \cite [CaR05]).
+In this paper we focus on DS, and we introduce several notions before we describe their work.
 
-In this section, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\V {\Phi} \in \MB {K} ^{N_m \D  N_p}}.
-Set \m {\MC {T} \RB {N_p} =\CB {0, \dots, N_p-1}} for short.
-For \m {\MC {A} \subseteq \MC {T} \SB {N_p}}, denote
-\DispN {
-\NC \V {x}  \DB {\MC {A}}
+To start, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\V {Q} \in \MB {K} ^{N_m \D  N_p}}.
+For \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}}, denote
+%
+\Disp {
+\NC \V {x}  _{\SB {\MC {A}}}
 =\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR
-\NC \M {\Phi}  \DB {\MC {A}}
-=\NC \sum _{i \in \MC {A}} \M {\Phi} \DB {:,i} \NR
+\NC \M {Q}  _{\SB {\MC {A}}}
+=\NC \sum _{i \in \MC {A}} \M {Q} _{\SB {:,i}} \NR
 }
-That is, respectfully, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MC {A}}.
+%
+That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MC {A}}.
 
@@
 \Result
-{Definition: Sparsity}
+{Definition}
 {
-\m {\V {x}} is called \m {s}-sparse, if there is \m {\MC {A} \subseteq \MC {T} \SB {N_p}} such that
-\DispN { 
-\NC \V {x} \DB {\MC {A}}
+\m {\V {x}} is called \m {s}-sparse, if there is some \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}} such that
+%
+\DispNum {x,A;x-,x-} {
+\NC \V {x} _{\SB {\MC {A}}}
 =\NC \V {x} \NR
 }
+%
 with
-\DispN { 
-\NC \# \MC {A} \leq s. \NR
+%
+\DispNum {A,A;s-,s-} { 
+\NC \# \MC {A} \leq \NC s. \NR
 }
@@
 
+And for given \m {s},
 \Result
-{Definition: Restricted Isometry Property}
+{Definition}
 {
-For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
-\DispN {
+For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies the restricted isometry property (hereafter RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
+%
+\DispNum {1,2;Qx,22} {
 \NC \RB {1-\d_s} \VNm {\V {x}}^2
-\leq \NC \VNm {\M {\Phi} \V {x}} _2^2 \NR
+\leq \NC \VNm {\M {Q} \V {x}} _2^2 \NR
 \NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR
@@
 }
-That is, \m {\Phi} is ``almost unitary'' up to ``relative error'' \m {\d_s}.
+%
+It helps to think that \m {\M {Q}} is almost unitary up to relative error \m {\d_s}.
 
-Now, consider a linear transformation with noise corruption,
-
-\DispN {
+Now, consider a linear transformation of real vectors with noise corruption,
+%
+\DispNum {y,y;Qx,xz} {
 \NC \V {y}
-=\NC \M {\Phi} \V {x} + \V {z} \NR
+=\NC \M {Q} \V {x} + \V {z} \NR
 }
-
-where (w.l.o.g.) \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
+%
+where, for example, \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
 How can we hope to estimate \m {\V {x}} when, in addition to insufficient observations, there are too few observations?
@@
 \Result
-{Algorithm: Dantzig Selector}
+{Algorithm}
 {
 \startitemize[n]
-\item Input \m {\M {\Phi} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}.
+\item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}.
 \item Calculate
-\DispN {
+%
+\DispNum {h,h;mi,yg'} {
 \NC \Hat {\V {h}}
@@
 \NC \Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
-\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {\Phi}^\Adj \RB {\M {\Phi} \V {h}' -\V {y}}} _\infty \leq \g \NR
+\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {Q}^\Adj \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
 \stopcases \NR
@@
 
-They was able to show that, with Algorithm (), the mean square error is bounded with overwhelming probability.
-And it can be shown that this \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
-Note that they confined their discussion for real vectors.
+Candès and Tao was able to show that, by Algorithm [3], \m {\V {x}} can be recovered, with the expected square error bounded with overwhelming probability.
+Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (hereafter LP), lending convex programming technique applicable.
+The constant \m {\d_s} in Definition [2] is crucial, and here one might ask that why don't we just take \m {Q} to be just any unitary matirx.
+Regarding this, we remark that the aforementioned performance bound is not tightest when \m {\d_s =0}, thus giving the RIP an important role.
+One common design choice of \m {\M {Q}} proposed is that every entry of \m {\M {Q}} shall be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
+Still, it remains unclear how to find RIP matrices efficiently, which became an active research area.
 
-The constant \m {\d} in the proof of DS is significant.
-Indeed, we may observe that in theorem (), the bound is not tightest when \m {\d=0}, i.e., that \m {\Phi} is fully unitary, rendering the RIP an important role.
-Here, it is not clear at first what matrices serves as the RIP condition.
+Meanwhile, back at the ranch, recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
+Luckily, physical evidences suggest that millimeter wave channels are in fact sparse in the frequency domain, and some scholars have thus applied compressive sensing techniques to the problem.
+One of the first attempt has been Bajwa et.\ al.\ \cite [BHS10], where they argue that the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
+What they explored was the estimation of single-antenna channel response with respect to time.
+The accompanying paper by the same team (Bajwa et.\ al.\ \cite [BHR08]) shows that \m {X} is RIP for overwhelming probability, providing the ground for the former paper.
 
-But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.
-
-We have summarised results in compressed sensing, and we now relate the matter to the communication scenario.
-Recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
-Meanwhile, physical evidences suggest that millimeter wave channels can be said to be sparse in the frequency domain in a certain senses.
-Some scholars thus has applied compressive sensing techniques to the problem.
-
-One of the first papers, Bajwa et.\ al.\ (2010) argues the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
-What they explored was the estimation of single-antenna channel response with respect to time.
-Another paper by the same group of scholars (Bajwa et.\ al.\ 2008) shows that \m {X} is RIP for overwhelming probability, providing the ground for the former paper.
-
-To explain the idea, consider a linear time-invariant channel that \m {y\SB {t} =\RB {x \star h} \SB {t} + z\SB {t}}, where \m {h\SB {t}} is the channel's impulse response, \m {y\SB {t}} is the output, and, for each time index, \m {x\SB {t}} is i.i.d.\ Rademacher, and \m {z\SB {t}} is i.i.d.\ Gaussian.
-Simply assuming \m {h} is sparse, and let the convolution with \m {x} be expressed by a matrix \m {X}, \m {X} is a Toeplitz matrix, so that \m {y =X h +z}.
-Then Bajwa et.\ al.\ was able to show that, \m {X} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.
+To illustrate, consider a linear time-invariant channel \m {y\SB {t} =\RB {x \star h} \SB {t} + z\SB {t}}, where \m {h\SB {t}} is the channel's impulse response, \m {y\SB {t}} is the output, and for each time index, signal \m {x\SB {t}} and noise \m {z\SB {t}} are both i.i.d.
+Simply assuming \m {h} is sparse, we may express the convolution between \m {h} with \m {x} by a matrix \m {X}, so that \m {\V {y} =\M {X} \V {h} +\V {z}} for some \m {\M {X}}.
+Then \cite [BHR08] showed that \m {\M {X}} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice performance bounds drawing directly from \cite [CaT07].
 
@@
 
-Around that time, Tropp and Gilbert (2007b) points out if we apply a greedy algorithm called Orthogonal Matching Pursuit (OMP), that an i.i.d.\ random matrix being generated the similar way as Baraniuk (2008) suggested, may perform sufficiently well, even recover the original signal in an overwhemingly probability too.
+Around that time, Tropp and Gilbert \cite [TrG07b] suggest that a greedy algorithm called Orthogonal Matching Pursuit (OMP), which also makes use of an i.i.d.\ random matrix, may also reconstruct the sparse signal sufficiently well in an overwhemingly probability.
 
-Same as before, consider an \m {s}-sparse \m {\V {x}}, with \m {N_p \gg N_s}.
-For the noiseless, real-number case,
-\DispN {
-\NC \V {y}
-=\NC \M {\Phi} \V {x}, \NR
-}
-We pick up the columns of \m {\M {\Phi}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.
+Still consider \Rf {y,y;Qx,xz}.
+We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.
 
 \Result
-{Algorithm: Orthogonal Matching Pursuit}
+{Algorithm}
 {
 \startitemize[n]
-\item Input \m {\M {\Phi} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
+\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
 \item Initialize
-\DispN {
+%
+\Disp {
 \NC \V {r}
@@
 \item Find
-\DispN {
+%
+\DispNum {c,c;i0,ir} {
 \NC c
 \LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
-\Nm {\M {\Phi} \DB {:,i} \V {r}} \NR
+\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
 }
+%
 and insert \m {S \LA S \cup {i}}.
 \item Compute
-\DispN {
-\NC \M {\Phi} ^\ddagger
-\LA \NC \RB {\M {\Phi} \DB {S} ^\Adj \M {\Phi} \DB {S}} ^{-1} \M {\Phi} \DB {S} ^\Adj \NR
+%
+\DispNum {Q,Q;QS,Qy} {
+\NC \M {Q} ^\ddagger
+\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
 \NC \V {r}
-\LA \NC \V {y} -\M {\Phi} \DB {S} ^\Adj \M {\Phi} ^\ddagger \V {y} \NR
+\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
 }
 \item Break if
-\DispN {
+%
+\DispNum {r,2;h',h'} {
 \NC \VNm {\V {r}} _2
@@
 }
-where \m {\VNm {\M {\Phi} ^\ddagger} _1} denotes the operator norm.
+%
+where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
 \item Output 
-\DispN {
+%
+\DispNum {g,g;Qy,Qy} {
 \NC \Hat {\V {g}}
-\LA \NC \M {\Phi} ^\ddagger \V {y} \NR
+\LA \NC \M {Q} ^\ddagger \V {y} \NR
 }
@@
 }
-Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {h} is nonzero (where we have slightly abused the usage of double brackets).
+%
+Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {\V {x}} is nonzero (where we have slightly abused the usage of subscript to indicate position indices).
+From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.
 
-From Tropp and Gilbert (2007a), the probability OMP recovers \m {h} completely is overwhelming.
-
-It is interesting to note that, ever since, the channel sensing scholars have applied OMP in favor of DS, due the simplicity of former's implementation, making OMP perhaps the most widely used channel estimation technique.
-
-For our purposes, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
-Let signal \m {\V {x}} be sent, and \m {\V {y}} be receiverd, that is
-
-\DispN {
-\NC \V {y}
-=\NC \M {W} \M {H} \M {F} \V {x} \NR
-}
-
-\Result
-{Definition.}
-{
-Define \m {\Rm {vec} \SB {\M {A}} \in \MB {K} ^{N_1, N_2}} to be the vectorization of \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}}.
-Formally,
-\DispN {
-\NC \RB {\Rm {vec} \SB {\M {A}}} \DB {m_1}
-=\NC \M {A} \DB {m_1\; \Rm {Mod}\; N_1, \Fl { m_1/N_1 }} \NR
-}
-The bijectivity is obvious, and we define \m {\Rm {vec} ^{-1}} so that
-\DispN {
-\NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
-=\NC x \NR
-}
-}
-
-\Result
-{Definition.}
-{
-For \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}} and \m {\M {B} \in \MB {K} ^{N_3 \D N_4}}, define the Kronecker product \m {\M {A} \otimes \M {B} \in \MB {K} ^{N_1 N_3 \D N_2 N_4}} by
-\DispN {
-\NC \NC \RB {\M {A} \otimes \M {B}} \DB {m_1, m_2} \NR
-\NC =\NC \M {A} \DB {\Fl { m_1/N_3 }, \Fl { m_2/N_4 }}
-\M {B} \DB {m_1\; \Rm {Mod}\; N_3, m_2\; \Rm {Mod}\; N_4} \NR
-}
-}
-
-With (), scholars often exploit the relation
-\Result
-{Lemma.}
-{
-Suppose \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}, \M {X} \in \MB {K} ^{N_2 \D N_3}, \M {B} \in \MB {K} ^{N_3 \D N_4}},
-Then
-\DispN {
-\NC \Rm {vec} \SB {\M {A}\M {X}\M {B}}
-= \NC \RB {\M {B}^\Tr \otimes \M {A}} \Rm {vec} \SB {\M {X}} \NR
-}
-}
-
-To show this, we shall verify that arbitrary components of lhs and rhs agree.
-On one hand,
-\DispN {
-\NC \NC \RB {\Rm {vec} \SB {\M {A}\M {X}\M {B}}} \DB {m_1} \NR
-\NC = \NC \RB {\M {A}\M {X}\M {B}} \DB {m_1\; \Rm {Mod}\; N_1, \Fl { m_1/N_1 }} \NR
-\NC = \NC \sum _{n_2 =0} ^{N_2 -1} \sum _{n_3 =0} ^{N_3 -1}
-\M {A} \DB {m_1\; \Rm {Mod}\; N_1, n_2} \M {X} \DB {n_2, n_3} \M {B} \DB {n_3, \Fl { m_1/N_1 }} \NR
-}
-On the other hand,
-\DispN {
-\NC \NC \RB {\RB {\M {B}^\Tr \otimes \M {A}} \Rm {vec} \SB {\M {X}}} \DB {m_1} \NR
-\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M {B}^\Tr \otimes \M {A}} \DB {m_1, m_2} \Rm {vec} \SB {\M {X}} \DB {m_2} \NR
-\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M {B}^\Tr} \DB {\Fl { m_1/N_1 }, \Fl { m_2/N_2 }}
-\M {A} \DB {m_1\; \Rm {Mod}\; N_1, m_2\; \Rm {Mod}\; N_2} \Rm {vec} \SB {\M {X}} \DB {m_2} \NR 
-\NC = \NC
-\sum _{m_2 =0} ^{N_2 N_3 -1}
-\M {B} \DB {\Fl { m_2/N_2 }, \Fl { m_1/N_1 }}
-\M {A} \DB {m_1\; \Rm {Mod}\; N_1, m_2\; \Rm {Mod}\; N_2} \NR
-\NC \NC \SixQ
-\M {X} \DB {m_2\; \Rm {Mod}\; N_2, \Fl { m_2/N_2 }}
-\NR
-}
-
-In () and (), the row indices of \m {\M {A}} and \m {\M {B}} already agree.
-The key observation is that when \m {n_2} runs through \m {0, \dots, N_2-1} and \m {n_3} runs through \m {0, \dots, N_3-1}, it follows \m {n_2 n_3} runs through \m {0, \dots, N_2 N_3-1}.
-We see two expressions are exactly the same, and we are done.
-
-The matrix consisting of the collection of possible response according to available paths --- called the dictionary --- plays the role of the sensing matrix of OMP.
-The combiner at the receiver end corresponds to the step where we map the data from high to low dimension.
+The matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.
 
@@
 
-The literature on Compressive Channel Sensing has since been vast, and we need not and cannot go through all of them here.
-Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.
+OMP has since been applied in a variety of ways, and here we restrict our attention to channel estimation.
+In fact, ever since, work on channel estimation seems to favored OMP instead of DS, nor other sparse algorithm, without clear justification, and this must have somthing to do with the simplicity of OMP implementation.
 
-Rao and Lau (2014) considers a distributed algorithm for a MU-MIMO and proposes a modified joint OMP algorithm, with the assumption on the sparsity of the channel and that channels seen by various users shall share the same positions of nonzero components.
+Alkhateeb et.\ al.\ \cite [AEL14] proposes an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
+Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discusses the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
+Gao et.\ al.\ \cite [LGC16] present the jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on positions of nonzero components.
+Hu, Wang, and He \cite [HWH13] applies OMP to estimate quantized path delay of each OFDM subcarrier, assuming the channel gain in each path is stationary.
+Lee, Gil, and Lee \cite [LGL16] considers a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.
 
-Alkhateeb et.\ al.\ (2014) suggests an adaptive OMP algorithm, using a (beam) code book with quantized AoA and AoD.
+Some further attempts include Manoj and Kannu \cite [MaK17], which formulate the sparse condition as overlapping block in the reconstructed signal, and encode possible blocks.
+Gurbuz, Yapici, and Guvenc \cite [GYG18] introduce perturbation of the quantized set of angles, on which the sensing matrix is based.
+Most recently, Panayirci et.\ al.\ \cite [PAU19] put forward a more thorough treatment, where in addition to application of OMP, they use a first stage of max-likelihood estimation of model parameters, and a second stage of maximum-a-posteriori estimation of channel gains.
 
-Alkhateeb, Leus, and Heath Jr.\ (2015) poses the interesting trade-off of number of OMP measurement and accuracy in an application of OMP.
-They work simplified all-phase-shifter combiner model, where every receiver antenna may only multiply the signal by a constant, and the channel model is assumed to take value on a quantized, non-uniform set of angles.
-Their work mainly focuses on numerical simulation, rather than mathematical proof.
+Performance guarantee of OMP is also studied, by refining or proposing different conditions.
+Cai, Wang, and Xu \cite [CWX10], under assumption on low coherence of columns of matrices, give new bound on OMP.
+Coherence-based assumptions, instead of almost-unitarity, make the condition easier to verify.
+Cai and Wang \cite [CaW11] extends the investigation to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] follow up and refine their bounds, and conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
 
-Since the notice of hybrid beamforming, scholars have also applied the same idea to hybrid systems.
-Lee, Gil, and Lee (2016) considers a hybrid beamforming system, where the composition of the precoders and combineres play the role of sensing matrix.
-The beambook phase is quantized, which may have been a source of error, and they have specifed a particular grid set of angles and argues the superiority.
-One of their simulations experiments utilizes DFT and permutated DFT matrix, instead of as originally suggested by Tropp and Gilbert (2007).
-
-Meanwhile, the improvement of OMP bound is also going on.
-Cai, Wang, and Xu (2010), making assumptions on MIP matrices, give new bound on OMP, and, in addition, Cai and Wang (2011) replicates the same for analysis for DS, among other convex algorithms.
-Indeed, MIP deals with correlation of columns of the sensing matrix, rather than the almost-unitarity, making the condition easier to verify.
-
-Ben-Haim et.\ al.\ (2010) follow up their work and refine their bounds, also considering MIP conditions.
-They conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
-Still, since the setting of OMP and DS is rather different, it remains unclear which of is better.
-
-Alkhateeb, Leus, and Heath (2015), being a recent paper, cites Ben-Haim et.\ al.\ (2010) as the main foundation for OMP perfomance bound.
-
-Gao et.\ al.\ (2015) discusses the jointly reconstruction of several high-dimensional sparse signals having the same positions of nonzero components, using different measurement matrices in a modified basis pursuit problem.
-
-We remark several observation on past literature, that has been, to the best of our knowledge, lacking or less than ideal.
-
-\startitemize
-\item Previous work favors OMP rather than DS, let alone other sparse algorithm.
-\item Previous work simply assumes the bound of the norm of the channel matrix.
-\item The condition that the sensing matrix should be elementwise i.i.d.\ Normal (required by Tropp and Gilvert 2007) seems to be more restrictive than RIP (required by Cand\`es and Tao 2007).
-\item The quantization of angle in generating may be a problem, and that is difficult to analyze in OMP's setting
-\item No bounds is derived that explicitly depends on the sparsity of the channel parameters as, say, number of channel paths and array response.
-\stopitemize
+\stopsection
 
@@
 
-We consider a system model where both digital and analog beamformer are i.i.d.\ random matrix combiner that serve readily as the sensing matrix satisfying the RIP property.
-We apply a convex program analogous of DS in order to directly estimate the channel under hypothesis of uniform linear array response.
-Moreover, inspired by the lines of proof of Cand\`es and Tao (2006), we give a bound that indicates our method is to be successful for overwhelming probability.
+With all these efforts, current literature of compressive channel estimation, in our view, has not satisfyingly responded several aspects.
+One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.
+At least in the uniform linear array setting, the angular domain can be used Fourier as sensing matrix, which researchers have correctly noted.
+But the true angle of arrival and departure is often slightly off.
+We can always use finer quantization, but that leads to higher complexity.
+Moreover, researchers usually assume that the channel matrix has small norm, but further justifications and explicit bounds, depending channel parameters (say on sparsity and dimension), may be desired.
 
-Our contribution includes:
+In this paper, we argue in favor of DS, rather than OMP, to be another viable solution that has been ignored.
+To elaborate, we consider a system model where both digital and analog beamformer are i.i.d.\ random matrices, so that the effective beamformer serves readily as the sensing matrix with RIP.
+Assuming uniform linear array, we apply a convex program inspired by DS so as to directly estimate the channel.
+We shall see that a modified DS can be done on the angular domain instead of the spatial domain, and for complex numbers instead of real numbers.
+Then along the lines of \cite [CaT07], we shall give a bound on expected square error, depending explicitly on the sparsity of the virtual channel matrix and the number of paths of the channel, which will surely future designers, in which the
+Furthermore, it holds under an overwhelming probability, which is also bounded quantitatively.
 
-\startitemize
-\item As a {\it prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
-\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
-\item Accordingly, the concern of quantization error of the virtual channel's phase angle (which is inevitable when designing the OMP beambook) has already been considered in the proof of our main bound.
-\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
-\stopitemize
+Lastly, we cast the convex probram to be a second order cone problem to facilitate efficient code.
+We claim that, in view of numerical results, DS is often superior to OMP among other methods in terms of performance, but takes higher complexity.
 

### 2019-10-23 paper/2_problem_setting.tex
Add preliminary complexity analysis
Paraphrase chap 1

@@
 We restrict our consideration to the uniform linear array, which can be modeled as
-\DispN {
+%
+\DispNum {a,y';VC,nh} {
 \NC \V {a} \SB {\psi'}
@@
 }
+%
 where \m {\Ss {e}} is the base of natural logarithm, and \m {\Ss {i}} the imaginary unit.
 
-And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
-\DispN {
+And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ \cite [ALS14]).
+%
+\DispNum {H,H;l0,ql} {
 \NC \M {H}
@@
 }
+%
 The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
 For our purpose, we may absorb the argument of \m {\V {a}} as
-\DispN {
+%
+\DispNum {f,l;2p,2p} {
 \NC \f_l
@@
 }
+%
 to get a simpler form
-\DispN {
+%
+\DispNum {H,H;CN,ql} {
 \NC \M {H}
-\in \NC \\MB {C} ^{N_H \D N_H} \NR
+\in \NC \MB {C} ^{N_H \D N_H} \NR
 \NC \M {H}
@@
 That is to say, each end consists of both digital and analog percoders and combiners, as follows.
-In the transmitter end, there are, in order seeing from the end, digital precoder \m {F_B} and analog precoder \m {F_R}.
-Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m {W_B} and analog combiner \m {W_R}.
-To set up notation, we list them as below.
-\DispN {
-\NC \M {F} _B \in \NC \MB {C} ^{N_R \D  N_Y} \NR
-\NC \M {F} _R \in \NC \MB {C} ^{N_H \D  N_R} \NR
-\NC \M {W} _R \in \NC \MB {C} ^{N_R \D  N_H} \NR
-\NC \M {W} _B \in \NC \MB {C} ^{N_Y \D  N_R} \NR
-}
+In the transmitter end, there are, in order seeing from the end, digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D  N_Y}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
+Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D  N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_Y \D  N_R}}.
+
 Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
-\DispN {
+%
+\Disp {
 \NC \Nm {\M {F} _R \DB {n_H, n_R}}
@@
 }
+%
 And we assume
-\DispN {
+%
+\DispNum {N,H;NY,NY} {
 \NC N_H \gg \NC N_R \NR
-}
-\DispN {
 \NC N_R \gg \NC N_Y \NR
@@
 
-This is analogous to (), and we will exploit the fact when applying compressive sensing techinique.
-
-Since we restrict our discussion to a specific snapshot of time, the noise term may be simply taken as a matrix \m {\M {Z}} with each entry being i.i.d.\ Standard Normal.
-\DispN {
-\NC \M {Z} \in \NC \MB {C} ^{N_Y \D  N_Y} \NR
+Since we restrict our discussion to a specific snapshot of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_Y \D  N_Y}} with each entry being i.i.d.\ Standard Normal.
+We may introduce the effective channel
+%
+\Disp {
+\NC \M {Y}
+:=\NC \M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
 }
-We may introduce the effective channel
-\DispN {
-\NC \M {Y}
-:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
-}
+%
 Our task, then, is the recovery of \m {\M {H}}, and the design of \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.
@@
 
-First, for short we set
-\DispN {
+To convert the problem into a linear system recovery problem, we need several definitions.
+%
+\Result
+{Definition}
+{
+Define \m {\Rm {vec} \SB {\M {A}} \in \MB {K} ^{N_1, N_2}} to be the vectorization of \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}}.
+Formally,
+%
+\DispNum {v,1;Am,N1} {
+\NC \RB {\Rm {vec} \SB {\M {A}}} _{\SB {m_1}}
+=\NC \M {A} _{\SB {m_1\; \Rm {Mod}}\; N_1, \Fl {m_1/N_1 }} \NR
+}
+%
+The bijectivity is obvious, and we define \m {\Rm {vec} ^{-1}} so that
+%
+\DispNum {v,x;x-,x-} {
+\NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
+=\NC x \NR
+}
+}
+
+\Result
+{Definition}
+{
+For \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}} and \m {\M {B} \in \MB {K} ^{N_3 \D N_4}}, define the Kronecker product \m {\M {A} \otimes \M {B} \in \MB {K} ^{N_1 N_3 \D N_2 N_4}} by
+%
+\DispNum {A,2;Am,N4} {
+\NC \NC \RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \NR
+\NC =\NC \M {A} _{\SB {\Fl {m_1/N_3 }, \Fl {m_2/N_4 }}}
+\M {B} _{\SB {m_1\; \Rm {Mod}\; N_3, m_2\; \Rm {Mod}\; N_4}} \NR
+}
+}
+
+And we will exploit the relation (whose proof is a strightforward application of definitions)
+\Result
+{Lemma}
+{
+Suppose \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}, \M {X} \in \MB {K} ^{N_2 \D N_3}, \M {B} \in \MB {K} ^{N_3 \D N_4}},
+Then
+%
+\DispNum {v,B;BA,cX} {
+\NC \Rm {vec} \SB {\M {A}\M {X}\M {B}}
+= \NC \RB {\M {B}^\Tr \otimes \M {A}} \Rm {vec} \SB {\M {X}} \NR
+}
+}
+
+Now, for short we set
+%
+\Disp {
 \NC N_h
@@
 }
+%
 If we had followed the widely accepted approach of compressive channel sensing, we would have written
-\DispN {
+%
+\Disp {
 \NC \V {h}
-\in \NC \MB {C} ^{N_h} \NR
-\NC \V {h}
-:= \NC \Rm {vec} \SB {\M {H}} \NR
+:= \NC \Rm {vec} \SB {\M {H}}
+\in \MB {C} ^{N_h} \NR
+%
 \NC \V {y}
-\in \NC \MB {C} ^{N_y} \NR
+:= \NC \Rm {vec} \SB {\M {Y}}
+\in \MB {C} ^{N_y} \NR
+%
+\NC \V {z}
+:= \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
+\in \MB {C} ^{N_y} \NR
+%
+\NC \M {Q}
+:= \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
+\in \MB {C} ^{N_y \D  N_h} \NR
+}
+%
+to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M {H}}} to be
+%
+\Disp {
 \NC \V {y}
-:= \NC \Rm {vec} \SB {\M {Y}} \NR
-\NC \V {z}
-\in \NC \MB {C} ^{N_y} \NR
-\NC \V {z}
-:= \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}} \NR
-\NC \M {Q}
-\in \NC \MB {C} ^{N_y \D  N_h} \NR
-\NC \M {Q}
-:= \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R} \NR
+=\NC \M {Q} \V {h} +\V {z} \NR
 }
-to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M {H}}} to be
-\DispN {
-\NC \V {y}
-=\M {Q} \V {h} +\V {z} \NR
-}
+%
 As we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
@@
 Introduce the discrete Fourier transform matrix \m {\M {K}} defined to be
-\DispN {
+%
+\Disp {
 \NC \M {K} \in  \NC \MB {C} ^{N_H \D  N_H} \NR
@@
 }
+%
 Roman \m {\Ss {e}} and \m {\Ss {i}} denote the natural base and imaginary unit, respectively.
 Here recall that we have
-\DispN {
+%
+\Disp {
 \NC \M {K}^\Adj \M {K}
@@
 }
+%
 Observe that, if we write
-\DispN {
+%
+\Disp {
 \NC \M {G}
@@
 }
+%
 which has the interpretation as the angular space (i.e., spatial frequency domain) representation of \m {\M {H}}, then
-\DispN {
-\NC \M {Y}
-\in \NC \MB {C} ^{N_Y \D  N_Y} \NR
+%
+\Disp {
 \NC \M {Y}
 =\NC \M {W} _B \M {W} _R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F} _R \M {F} _B
-+\M {W} _B \M {W} _R \M {Z} \NR
++\M {W} _B \M {W} _R \M {Z}
+\in \MB {C} ^{N_Y \D  N_Y} \NR
 }
+%
 If at the end of day, \m {\M {G}} is sparse, then we recover \m {\M {G}} instead, and our use of DS is fully justified.
@@
 To simplify notation, set
-\DispN {
+%
+\Disp {
 \NC \M {P}
-\in \NC \MB {C} ^{N_y \D  N_h} \NR
-\NC \M {P}
-:=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}} \NR
+:=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
+\in \MB {C} ^{N_y \D  N_h} \NR
 }
+%
 And accordingly
-\DispN {
+%
+\Disp {
 \NC \V {g}
-\in \NC \MB {M} _{\MB {C}} \SB {N_h} \NR
-\NC \V {g}
-:= \NC \Rm {vec} \SB {\M {G}} \NR
+:= \NC \Rm {vec} \SB {\M {G}}
+\in \MB {M} _{\MB {C}} \SB {N_h} \NR
 }
+%
 Then
-\DispN {
+%
+\Disp {
 \NC \V {y}
@@
 \item Let \m {\g_{\Rm {DS}} \geq 0} be given.
-\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D  N_Y}, \M {F} _R \in \NC \MB {M} _{\MB {C}} \SB {N_H, N_R}, \M {W} _R \in \NC \MB {M} _{\MB {C}} \SB {N_R, N_H}, \M {W} _B \in \NC \MB {M} _{\MB {C}} \SB {N_Y, N_R}}, \m {\M {Y} \in \NC \MB {M} _{\MB {C}} \SB {N_Y, N_Y}},
+\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D  N_Y}},
+\m {\M {F} _R \in \NC \MB {C} ^{N_H \D N_R}},
+\m {\M {W} _R \in \NC \MB {C} ^{N_R \D N_H}},
+\m {\M {W} _B \in \NC \MB {C} ^{N_Y \D N_R}},
+and \m {\M {Y} \in \NC \MB {C} ^{N_Y \D N_Y}}.
 \item Find \m {\M {P} \in \MB {C} ^{N_y \D  N_h}}, \m {\V {y} \in \MB {C} ^{N_h}} as in above.
 \item Calculate
-\DispN {
+%
+\Disp {
 \NC \Hat {\V {g}}
@@
 \item Convert \m {\Hat {\V {g}}} back to the space domain, namely
-\DispN {
+%
+\Disp {
 \NC \Hat {G}
-\LA \Rm {vec}^{-1} \SB {\Hat {g}} \NR
+\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
 }
 \item Recover the estimated \m {\Hat {\M {H}}}, as
-\DispN {
+%
+\Disp {
 \NC \Hat {\M {H}}
-\LA \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
+\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
 }

### 2019-10-23 paper/3_1_almost_sparsity.tex
Add preliminary complexity analysis
Paraphrase chap 1

@@
 
-We first show that \m {\V {g}} is almost sparse, and substitute the bound into the expected square error of DS, thus generalizing the original argument.
-We will continue to use the variables \m {\V {P}}, \m {\V {g}}, \m {\V {y}}, and \m {\V {z}} introduced in Chapter 2.
+Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity index \m {s} be given.
+Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MC {A}}}}, the largest \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MC {A}}}} the next \m {s} largest components of \m {\V {g}}, and \m {\V {g} _{\SB{\MC {C}}}} are the components complement to \m {\V {g} _{\SB{\MC {A}}}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MC {A}}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\SB{\MC {B}}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\SB{\MC {A}}} =\IP {-1,0,-4,2,0}}.
+In this section, the subscripts \m {\MC {A}, \MC {B}, \MC {C}} will keep bearing analogous meaning.
 
-Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity index \m {S} be given.
-Split \m {\V {g}} into two parts: \m {\V {g} _{\MC {A}}}, the largest \m {S} components of \m {\V {g}}, \m {\V {g} _{\MC {A}}} the next \m {S} largest components of \m {\V {g}}, and \m {\V {g} _{\MC {C}}} are the components complement to \m {\V {g} _{\MC {A}}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\MC {A}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\MC {B}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\MC {A}} =\IP {-1,0,-4,2,0}}.
+We hope that \m {\VNm {\V {g} _{\SB{\MC {C}}}} _1} is small.
+If so, we shall substitute the quantity into the expected square error of DS, thus generalizing the original argument.
+Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and \m {\M {G}} is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
+We define, similarly, \m {\V {a} _{\SB{\MC {A}}}} and \m {\V {a} _{\SB{\MC {C}}}}, with undetermined sparsity index
+%
+\Disp {
+\NC S
+\leq \NC \R {N_H}. \NR
+}
+%
+If \m {N_H} is large, we need not bother ourself with the requirement that \m {S} is an integer.
 
-We hope that \m {\VNm {\V {g} _{\MC {C}}} _1} is small.
-
-\m {\M {H}} is the function of \m {\V {a}}, and we seek to establish that \m {\V {a}} is almost sparse.
-We define, similarly, \m {\V {a} _{\MC {A}}} and \m {\V {a} _{\MC {C}}}, with undetermined sparsity index \m {s}.
 First, we investigate
-\DispN {
-\NC \NC \VNm {\V {a} \SB {\f} _{\MC {C}}} _2 ^2 \NR
-\NC =\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\MC {C}}} _2 ^2 \NR
+%
+\Disp {
+\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _2 ^2
+=\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB{\MC {C}}}} _2 ^2 \NR
 }
-
+%
 Let \m {\f} be fixed.
@@
 Introduce
-\DispN {
+%
+\Disp {
 \NC \psi \SB {\f, n_H}
@@
 }
+%
 Note that by construction
-\DispN {
+%
+\Disp {
 \NC \Nm {\psi \SB {\f, n_H}}
@@
 }
+%
 And define the so-called Dirichlet kernel
-\DispN {
+%
+\Disp {
 \NC D \SB {\psi'}
@@
 }
+%
 Then observe
-\DispN {
-\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} \DB {n_H}
+%
+\Disp {
+\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB {n_H}}
 =\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
@@
 Now, by the nature of alternating series, for \m {-\pi \leq x < \pi}, it holds that
-\DispN {
+%
+\Disp {
 \NC \Nm {x - \F {x^3} {6}} \leq \NC \Nm {\sin x}. \NR
@@
 Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
-\DispN {
+%
+\Disp {
 \NC \Nm {D \SB {\psi'}}
@@
 }
+%
 Thus,
-\DispN {
-\NC \VNm {\V {a} \SB {\f} _{\MC {C}}} _1
+%
+\Disp {
+\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _1
 =\NC \F {1} {N_H}
@@
       \V {u} _{n_H'}
-} _{\MC {C}}
+} _{\SB{\MC {C}}}
 } _1
@@
 }
+%
 Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
@@
 Anyway, a moment's reflection shows
-\DispN {
-\NC \VNm {\V {a} \SB {\f} _{\MC {C}}} _1
+%
+\Disp {
+\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _1
 \leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
@@
 % % Deprecated!
-% \DispN {
+% \Disp {
 % \NC R^2
@@
 Then, for any instance of \m {\f},
-\PF {R;2,p'}
-\DispN {
-\NC \VNm {\V {a} \SB {\f} _{\MC {C}}} _2
+%
+\DispNum {a;f',C} {
+\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _2
 \leq \NC \F {2} {\pi \R{s}} \NR
@@
 Since the value of \m {s} is at our disposal, we try
-\PF {s;nn-hh,}
-\DispN {
+%
+\DispNum {s;nn-hh,} {
 \NC s
@@
 }
+%
 so that
-\PF {R;2,p'}
-\DispN {
+%
+\DispNum {R;2,p'} {
 \NC R
@@
 Recall that, by \m {\ell_p}-norm inequality,
-\DispN {
-\NC \VNm {\M {g} _{\MC {C}}} _1
-\leq \NC N_H \VNm {\M {g} _{\MC {C}}} _2 \NR
+%
+\Disp {
+\NC \VNm {\M {g} _{\SB{\MC {C}}}} _2
+\leq \NC \VNm {\M {g} _{\SB{\MC {C}}}} _1 \NR
 }
-So it remains to bound \m {\VNm {\M {G}} _F}.
+%
+And just by definition
+%
+\Disp {
+\NC \VNm {\M {G} _{\SB{\MC {C}}}} _F
+\leq \NC \VNm {\M {g} _{\SB{\MC {C}}}} _2 \NR
+}
+%
+So it remains to bound \m {\VNm {\M {G} _{\SB{\MC {C}}}} _F}.
+
 Note that
-\PF {G;H,a'-l}
-\DispN {
-\NC \VNm {\M {G}} _F
-=\NC \VNm {\M {H}} _F \NR
-\NC \NC \VNm {\sum _{l=0} ^{L-1} \a_l
+%
+\DispNum {G;H,a'-l} {
+\NC \VNm {\M {G} _{\SB{\MC {C}}}} _F
+=\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F \NR
+}
+%
+And by definition
+%
+\Disp {
+\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F
+=\NC \VNm {\sum _{l=0} ^{L-1} \a_l
 \V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj} _F \NR
 }
+%
 By triangle inequality, by the property of 2-norm and Frobenius norm,
-\PF {;a'-l,a,f'-l}
-\DispN {
-\NC \leq \NC \sum _{l=0} ^{L-1} \Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
+%
+\DispNum {;a'-l,a,f'-l} {
+\NC \leq \NC \sum _{l=0} ^{L-1}
+\Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
 \NC \leq \NC
@@
 }
+%
 It follows that
-\DispN {
-\NC \VNm {\M {H} _{\MC {C}}} _F
+%
+\Disp {
+\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F
 \leq \NC
 \sum _{l=0} ^{L-1} \Nm {\a_l}
-\VNm {\V {a} \SB {\f_l} _{\MC {C}}} _2
-\VNm {\V {a} \SB {\th_l} _{\MC {C}}} _2 \NR
+\VNm {\V {a} \SB {\f_l} _{\SB{\MC {C}}}} _2
+\VNm {\V {a} \SB {\th_l} _{\SB{\MC {C}}}} _2 \NR
 \NC \leq \NC
-\VNm {\V {a} \SB {\f_l} _{\MC {C}}} _2
-\VNm {\V {a} \SB {\th_l} _{\MC {C}}} _2
+\VNm {\V {a} \SB {\f_l} _{\SB{\MC {C}}}} _2
+\VNm {\V {a} \SB {\th_l} _{\SB{\MC {C}}}} _2
 \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
@@
 Observe that
-\DispN {
+%
+\Disp {
 \NC \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}}
 =\NC \F{\R {2} L} {\R {\pi}} \NR
-}
-\DispN {
+%
 \NC \Ss {Var} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}}
@@
 We expect that
-\DispN {
+%
+\Disp {
 \NC \sum _{l=0} ^{L-1} \Nm {\a_l}
@@
 }
+%
 Thus, by Chebyshev inequality,
-\DispN {
+%
+\Disp {
 \NC \MB {P} \SB {
@@
 }
+%
 Summarizing, we have the following result.
@@
 Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)},
-and let \m {\V {g} \in \MB {C} ^{N_h}} be defined as in ().
+and let \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in ().
 Then the bound
-\PF {g-C;4,p'-2}
-\DispN {
-\NC \VNm {\M {g} _{\MC {C}}} _1
+%
+\DispNum {g-C;4,p'-2} {
+\NC \VNm {\M {g} _{\SB{\MC {C}}}} _1
 \leq \NC \F {4} {\pi^2} \R {1 -\F {2} {\pi}} L N_H \R {\log N_H} \NR
 }
+%
 holds with probability \m {p} such that
-\PF {1,p;1}
-\DispN {
+%
+\DispNum {1,p;1} {
 \NC 1 -p

### 2019-10-23 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Paraphrase chap 1

@@
 Set for short
-\PF {d;g,g}
-\DispN {
+%
+\DispNum {d,d;gg,gg} {
 \NC \V {d} 
@@
 }
+%
 And our task is to bound the expectation \m {\MB {E} \SB {\V {d}}}.
@@
 And, as shall be seen, it suffices to set
-\PF {g';2,nn-h}
-\DispN {
+%
+\DispNum {g',g';2N,Nh} {
 \NC \g
@@
 {
-\PF {d-K;d-A,2-g-K}
-\DispN {
-\NC \VNm {\V {d} _{\MC {C}}} _1
-\leq \NC \VNm {\V {d} _{\MC {A}}} _1
-+2\VNm {\V {g} _{\MC {C}}} _1 \NR
+%
+\DispNum {d,1;dA,C1} {
+\NC \VNm {\V {d} _{\SB{\MC {C}}}} _1
+\leq \NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
++2\VNm {\V {g} _{\SB{\MC {C}}}} _1 \NR
 }
@@
 
-To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}}, while recalling that \m {\V {g} =\V {g} _{\MC {A}}},
-\PF {g,d-A,d-K}
-\DispN {
+To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}}, while recalling that \m {\V {g} =\V {g} _{\SB{\MC {A}}}},
+%
+\DispNum {g,1;gd,g1} {
 \NC \VNm {\V {g}} _1
--\VNm {\V {d} _{\MC {A}}} _1
-+\VNm {\V {d} _{\MC {C}}} _1
--\VNm {\V {g} _{\MC {C}}} _1
+-\VNm {\V {d} _{\SB{\MC {A}}}} _1
++\VNm {\V {d} _{\SB{\MC {C}}}} _1
+-\VNm {\V {g} _{\SB{\MC {C}}}} _1
 \leq \NC \VNm {\V {g} +\V {d}} _1 \NR
@@
 }
+%
 On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
-\PF {g,d;g}
-\DispN {
+%
+\DispNum {--;g1,g1} {
 \NC \leq \NC \VNm {\V {g}} _1 \NR
@@
 Then the relation
-\PF {E,z,P}
-\DispN {
+%
+\DispNum {E,h;2N,Nh} {
 \NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}}
@@
 }
+%
 holds with probability \m {\geq 1 -N_h^{-1}}.
@@
 Recall the following bound for \m {Q} function
-\PF {Q,x;1}
-\DispN {
+%
+\DispNum {Q,x;12,22} {
 \NC Q\SB {x}
@@
 }
+%
 Particularly, for \m {x =\R {2 \log N_h}},
-\PF {Q,2;nn-h}
-\DispN {
+%
+\DispNum {Q,h;1N,Nh} {
 \NC Q\SB {\R {2 \log N_h}}
@@
 With the assumption that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M {P}}}, then
-\PF {P,P,d}
-\DispN {
+%
+\DispNum {P,d;4N,Nh} {
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
@@
 To show this, by definition
-\PF {z,y,P}
-\DispN {
+%
+\DispNum {z,y;Pg,ny} {
 \NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
@@
 }
+%
 By construction
-\PF {P,n-y,y}
-\DispN {
+%
+\DispNum {P,g;Py,Nh} {
 \NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
@@
 }
+%
 By triangle inequality, together with Lemma (), we have
-\PF {P,n-y,y}
-\DispN {
+%
+\DispNum {P,d;zP,Nh} {
 \NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
@@
 }
+%
 which implies
-\PF {P,P,d} \DispN {
+%
+\DispNum {P,d;4l,Nh} {
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
@@
 With the assumption that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M {P}}},
-\PF {d-A-B;1,1}
-\DispN {
-\NC \VNm {\V {d} _{\MC {AB}}} _2
-\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}} {\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {C}}} _1 \NR
+%
+\DispNum {d,2;11,C1} {
+\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
+\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}} {\RB {1-\d_{2S}} \R {S}} \VNm {d_{\SB{\MC {C}}}} _1 \NR
 }
 }
+%
 And
@@
 {
-\PF {d-A-B;1,1}
-\DispN {
+%
+\DispNum {d,2;dA,12} {
 \NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\MC {C}}} _1^2 \NR
+\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1^2 \NR
 }
@@
 Now, in view of the result in Section 3.1, \m {s} is free, and we set
-\PF {s,1,,}
-\DispN {
+%
+\DispNum {s,s;1-,1-} {
 \NC s
@@
 }
+%
 which is crude, but enough.
 Accordingly,
-\PF {S;L,nn-hh}
-\DispN {
+%
+\DispNum {S;L,nn-hh} {
 \NC S
@@
 }
+%
 Just for simplicity, we assume
-\PF {d'-S;1,2}
-\DispN {
+%
+\DispNum {d'-S;1,2} {
 \NC \d_S
@@
 }
+%
 and
-\PF {L;4,}
-\DispN {
+%
+\DispNum {L;4,} {
 \NC L
@@
 Then the bound
-\PF {d;4,2}
-\DispN {
+%
+\DispNum {d;4,2} {
 \NC \VNm {\V {d}} _2
@@
 }
+%
 holds for probability \m {p}, with
-\DispN {
+%
+\Disp {
 \NC 1 -p
@@
 By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {s,1,,} and \Rf {P,P,d},
-\PF {P-A-B,P,d}
-\DispN {
+%
+\DispNum {P-A-B,P,d} {
 \NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
@@
 
-By \m {\ell_p} norm inequality, by the definition of truncation, by \Rf {d-A-B;1,1}, \PF {d'-S;1,2}, and \PF {P-A-B,P,d} just above,
-
-\PF {d-A;L,d-A}
-\DispN {
-\NC \VNm {\V {d} _{\MC {A}}} _1
-\leq \NC \R {L} \VNm {\V {d} _{\MC {A}}} _2 \NR
-\NC \leq \NC \R {L} \VNm {\V {d} _{\MC {AB}}} _2 \NR
+By \m {\ell_p} norm inequality, by the definition of truncation, by \Rf {d-A-B;1,1}, \Rf {d'-S;1,2}, and \Rf {P-A-B,P,d} just above,
+%
+\DispNum {d-A;L,d-A} {
+\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
+\leq \NC \R {L} \VNm {\V {d} _{\SB{\MC {A}}}} _2 \NR
+\NC \leq \NC \R {L} \VNm {\V {d} _{\SB{\MC {AB}}}} _2 \NR
 \NC \leq \NC 8 \R {2 \log N_H}
-+\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {d} _{\MC {C}}} _1 \NR
++\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
 }
 
-Next, we want to use \Rf {d-K;d-A,2-g-K} to eliminate \m {\VNm {d _{\MC {A}}} _1} in \Rf {d-A;L,d-A}.
-\PF {;8,2,nn-hh}
-\DispN {
+Next, we want to use \Rf {d-K;d-A,2-g-K} to eliminate \m {\VNm {d _{\SB{\MC {A}}}} _1} in \Rf {d-A;L,d-A}.
+%
+\DispNum {;8,2,nn-hh} {
 \NC \leq \NC 8 \R {2 \log N_H}
-+\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \RB {\VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {C}}} _1} \NR
++\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \RB {\VNm {\V {d} _{\SB{\MC {A}}}} _1 +2\VNm {\V {g} _{\SB{\MC {C}}}} _1} \NR
 \NC \leq \NC 8 \R {2 \log N_H}
-+\F {2} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {g} _{\MC {C}}} _1 \NR
++\F {2} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {g} _{\SB{\MC {C}}}} _1 \NR
 }
+%
 And \Rf {g-C;4,p'-2} in Section 3.1 gives
-\PF {d-A;8,2}
-\DispN {
-\NC \VNm {\V {d} _{\MC {A}}} _1
+%
+\DispNum {d-A;8,2} {
+\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
 \leq \NC 8 \R {2 \log N_H}
-+2\VNm {\V {g} _{\MC {C}}} _1 \NR
++2\VNm {\V {g} _{\SB{\MC {C}}}} _1 \NR
 \NC \leq \NC \RB {16 \R {2} +\F {4} {\pi^2} \R {1 -\F {2} {\pi}}} \log N_H \NR
@@
 Using Lemma () again, we have
-\DispN {
+%
+\Disp {
 \NC \VNm {\V {d}} _2^2
@@
 +8 \d_{3S} \R {2 \log N_H} 
-+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {C}}} _1 \NR
++\F {\d_{3S}^2} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
 }
-Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {C}}} _1}.
+%
+Finally, plug in the bound for \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1}.
 Again for simplicity, we keep only the first order small terms.
-\DispN {
+%
+\Disp {
 \NC \VNm {\V {d}} _2^2
@@
 }
+%
 Set \m {\d_S =1} for the worst situation, and we get the desired bound.

### 2019-10-23 paper/4_simulation.tex
Paraphrase chap 1

@@
 \startchapter [title={Simulation}]
+
+We are ready to verify theoretical bound of DS by numerical experiments.
+DS is a convex optimization program, and there are many library devoted on that.
+For present purpose, we choose the ready-made Python library CVXPY.
+For the implementation details, see Diamond and Boyd \cite [DiB16]
+
+However, it turns out direct implementation of () exhibit extraordinarily large complexity, and we would like to recast the problem in a more tractable form.
+Towards that end, we found out that Candès and Romberg \cite [CaR05] has shown that DS can be simplified as an linear program (LP).
+However, the situation is more cubersome than that, since they deal with real vectors, but we consider the complex ones.
+Fortunately, they have briefly pointed out, complex DS can be recast as an second-order cone program (SOCP), and SOCP is one of the several standard convex programming problems for which there are already numerous efficient algorithms.
+
+Before describing the recast, for ease of treatment we would like to represent complex vector and matrices by real, extended vectors and matrices.
+\Result
+{Definition}
+{
+For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MC {R} \SB {\V {x}}} of \m {\V {x}} to be
+%
+\Disp {
+\NC \MC {R} \SB {\V {x}}
+\in \NC \MB {R} ^{2M} \NR
+\NC \MC {R} \SB {\V {x}} _{\SB {m}}
+= \NC \startcases
+\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
+\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
+\stopcases \NR
+\NC m' 
+= \NC  0, 1, 2, \ldots, M-1 \NR
+}
+%
+The injectivity is obvious, and we may define \m {\MC {R} ^{-1}} so that
+%
+\Disp {
+\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V {x}}}
+=\NC \V {x} \NR
+}
+}
+%
+Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
+\Result
+{Definition}
+{
+For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MC {R} \SB {\M {A}}} of \m {\M {A}} to be
+%
+\Disp {
+\NC \MC {R} \SB {\M {A}}
+\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
+\NC \MC {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
+\NC \startcases
+\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
+\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2') \NR
+\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2'+1) \NR
+\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2'+1) \NR
+\stopcases \NR
+\NC m_1 
+= \NC 0, 1, 2, \ldots, M_1 -1 \NR
+\NC m_2 
+= \NC 0, 1, 2, \ldots, M_2 -1 \NR
+}
+}
+
+With these, we define
+%
+\Disp {
+\NC \T {\V {y}}
+= \NC \MC {R} \SB {\V {y}}
+\in \MB {R} ^{2N_y} \NR
+%
+\NC \T {\V {g}}
+= \NC \MC {R} \SB {\V {g}}
+\in \MB {R} ^{2N_h} \NR
+%
+\NC \T {\M {P}}
+= \NC \MC {R} \SB {\M {P}}
+\in \MB {R} ^{2N_y \D 2N_h} \NR
+%
+\NC \T {\M {P}} ^\Adj
+= \NC \MC {R} \SB {\M {P} ^\Adj}
+\in \MB {R} ^{2N_y \D 2N_h} \NR
+%
+\NC \T {\V {z}}
+= \NC \MC {R} \SB {\V {z}}
+\in \MB {R} ^{2N_y} \NR
+}
+%
+such that, by construction,
+%
+\Disp {
+\NC \V {\T {y}}
+= \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}} \NR
+}
+
+Furthermore, introduce the following matrices to identify the components where we want to take \m {\ell_2}-norm, in the manner similar to an indicator function.
+%
+\Disp {
+\NC {\V {u}}_{n_h}
+\in \NC \MB {R} ^{N_h} \NR
+\NC \RB {\V {u}_{n_h}} _{\SB {n_h'}}
+= \NC
+\startcases
+1, \Q \MC n_h' =n_h \NR
+0, \Q \NC \Rm {otherwise} \NR
+\stopcases \NR
+\NC \T {\M {U}}_{n_h} \in \NC \MB {R} ^{2N_h \D 2N_h} \NR
+\NC \RB {\T {\M {U}}_{n_h}} _{\SB {n_h', n_h''}}
+= \NC
+\startcases
+1, \Q \MC n_h' =2n_h,\; n_h'' =2n_h \NR
+1, \Q \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
+0, \Q \NC \Rm {otherwise} \NR
+\stopcases \NR
+\NC n_h, n_h', n_h'' 
+= \NC 0, 1, 2, \ldots, N_h -1 \NR
+}
+%
+And denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
+Now, if we introduce vector \m{\V {m}}
+%
+\Disp{
+\NC \V {m} \in \NC \MB {R} ^{N_h} \NR
+\NC \V {m} \DB{n_h}
+= \NC \Nm{\V {g} \DB{n_h}} \NR
+\NC n_h, n_h', n_h'' 
+= \NC 0, 1, 2, \ldots, N_h -1 \NR
+}
+%
+to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now takes the form
+%
+\Disp {
+\NC \Hat {\T {\V {g}}}
+= \NC \startcases
+\NC \Min {\T {\V {g}}', \V {m}} \Q
+\MC \IP { \V {1}, \V {m} } \NR
+\NC \Rm {subject} \; \Rm {to} \Q
+\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
+\leq \IP { \V {u}_{n_h}, \V {m} } \NR
+\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
+\leq \g \NR
+\stopcases \NR
+\NC n_h 
+= \NC 0, 1, 2, \ldots, N_h-1 \NR
+}
+
+\stopsection
+
+\startsection [title={Second Order Cone Programming}]
+
+We shall see furthermore that the program can be cast into an SOCP.
+To make the point clearer, we rewrite Program () into an extended block matrix form, by defining auxiliary variables as follows,
+%
+\Disp{
+\NC \V {t}
+= \NC \startTheMatrix
+\NC \V {0} \NR
+\NC \V {1} \NR
+\stopTheMatrix
+\in \MB {R} ^{3N_h} \NR
+%
+\NC \V {x}'
+= \NC \startTheMatrix
+\NC \T {\V {g}}' \NR
+\NC \V {m} \NR
+\stopTheMatrix
+\in \MB {R} ^{3N_h} \NR
+}
+%
+with
+%
+\Disp{
+\NC \M {A}_i
+= \NC \startTheMatrix
+\NC \T {\M {U}}_{i}, \NC \M {0} \NR
+\stopTheMatrix
+\in \MB {R} ^{2N_h \D 3N_h} \NR
+%
+\NC \V {b}_i
+= \NC \V {0}
+\in \MB {R} ^{2N_h} \NR
+%
+\NC \V {c}_i
+= \NC \startTheMatrix
+\NC \V {0} \NR
+\NC \V {u}_{i} \NR
+\stopTheMatrix
+\in \MB {R} ^{3N_h} \NR
+%
+\NC d_i
+= \NC 0 \NR
+%
+\NC i 
+= \NC 0, 1, 2, \ldots, N_h -1 \NR
+}
+
+And
+%
+\Disp{
+\NC \M {A}_i
+= \NC \startTheMatrix
+\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
+\stopTheMatrix
+\in \MB {R} ^{2N_h \D 3N_h} \NR
+%
+\NC \V {b}_i
+=\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}}
+\in \MB {R} ^{2N_h} \NR
+%
+\NC \V {c}_i
+= \NC \V {0}
+\in \MB {R} ^{3N_h} \NR
+%
+\NC d_i
+= \NC \g \NR
+%
+\NC i 
+= \NC N_h, N_h +1, N_h +2, \ldots, 2N_h -1 \NR
+}
+%
+The step that we convert \m {\Hat {\V {g}}} back is same as Algorithm () is same as before, but this is listed for sake of completeness.
+
+\Result
+{Algorithm}
+{
+\startitemize[n]
+\item Input \m{\M {P} \in \MB {C} ^{N_y \D N_h}}, \m{\V {y} \in \MB {C} ^{N_y}}, \m{\g > 0}.
+\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
+\item Calculate
+%
+\Disp{
+\NC \Hat {\V {x}}
+\LA \NC \startcases
+\NC \Min {\V {x}' \in \MB {C} ^{N_h}}
+\MC \IP {\V {t}, \V {x}'} \NR
+\NC \Rm {subject} \; \Rm {to}
+\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
+\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
+\NC \MC i 
+=0, 1, 2, \ldots, 2N_h -1 \NR
+\stopcases \NR
+}
+\item Extract
+%
+\Disp{
+\NC \Hat{\T{\V {g}}}
+\LA \NC \Hat{\V {x}} _{\SB {0 : 2N_h-1}} \NR
+}
+\item Convert 
+%
+\Disp{
+\NC \Hat{\V {g}}
+\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
+}
+\item Calculate
+%
+\Disp {
+\NC \Hat {G}
+\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
+}
+\item Calculate
+%
+\Disp {
+\NC \Hat {\M {H}}
+\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
+}
+\item Output \m {\Hat {\M {H}}}.
+\stopitemize
+}
+
+\stopsection
 
@@
 \startsubsection [title={Settings}]
-
-We are ready to verify theoretical bound of DS by numerical experiments.
-DS is a convex optimization program, and there are many library devoted on that.
-We choose the Python Library CVXPY.
-But we will not implement that here.
 
@@
 
-Each data point is repeated for 32 times, and taken average.
-We plot the absolute log error
-\PF {h'-ABS;h,h}
-\DispN {
-\NC \eta_{\Rm{abs}}
-=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}, \NR
-}
-and relative log error.
-\PF {h'-REL;h,h}
-\DispN {
-\NC \eta_{\Rm{rel}}
-=\NC \F {\RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}}
-{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
-}
-The averaged error values are plotted along with the theoretical expected error of DS, derived in chap.\ 3, namely
-\PF {h'-TH;5,2}
-\DispN {
-\NC \eta_{\Rm{th}}
-=\NC \F{5}{2} + \log \RB{L N_H} + \log \log N_H \NR
-}
-
 Several threshold values occur in relevant alorithms.
@@
 
+Each data point is repeated for 32 times, and taken average.
+We plot the absolute log error
+%
+\DispNum {e',s;lo,vg} {
+\NC \e_{\Rm{abs}}
+=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}, \NR
+}
+%
+and relative log error.
+%
+\DispNum {e',l;lo,vg} {
+\NC \e_{\Rm{rel}}
+=\NC \F {\RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}}
+{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
+}
+%
+The averaged error values are plotted along with the theoretical expected error of DS, derived in chap.\ 3, namely
+%
+\DispNum {e',h;52,NH} {
+\NC \e_{\Rm{th}}
+=\NC \F{5}{2} + \log \RB{L N_H} + \log \log N_H \NR
+}
+
 \stopsubsection
@@
 
-Reasonably, for all methods, a higher \m {\s} corresponds to higher \eta_{\Rm{rel}} and \eta_{\Rm{rel}}.
+Reasonably, for all methods, a higher \m {\s} corresponds to higher \m {\eta_{\Rm{rel}}} and \m {\eta_{\Rm{rel}}}.
 The trends of absolute and relative error are the same, and in the below we call them simply error.
@@
 If just take that as the complexity bound for DS, it becomes
-\PF {cc-DS;cc-0,g-0}
-\DispN {
+%
+\DispNum {C,S;C0,1e'} {
 \NC C_{\Rm{DS}}
@@
 }
+%
 where \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error.
@@
 For concreteness, we may assume that we start the iteration by specifying the Least Square estimator as the initial value of \m {\V {g}_0}, namely
-\PF {g-0;g-LS,pp}
-\Disp {
+%
+\DispNum {g,0;gL,Py} {
 \NC \V {g}_0
@@
 }
+%
 If we drop it, we may write the complexity of DS to be, simply,
-\PF {cc-DS;oo,g,g}
-\Disp {
+%
+\DispNum {C,S;Og,g1} {
 \NC C_{\Rm{DS}}
@@
 }
+%
 For simplicity we assume
-\DispN {
-\PF {g;g,}
+%
+\DispNum {g-;g-,-g} {
 \NC \V {g} ^\star
@@
 }
+%
 Indeed, this is the main objective of our investigation!
 And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
-\DispN {
-\PF {pp,pp;ii-nn-hh-2}
+%
+\DispNum {P,P;IN,H2} {
 \NC \M {P} ^\Adj \M {P}
@@
 }
+%
 Thus
+%
 \Disp {
-\PF {cc;oo;g,pp}
 \NC C_{\Rm{DS}}
@@
 }
-\m {\RB {\M {P} ^\Adj \V {z}} \DB {j}} Complex Normal distribution, and is easily bounded by \m {\s}.
+
+If we agree that, for high probability,
+%
 \Disp {
-\PF {;oo,nn-hh-2}
-\NC =\NC \MC {O} \SB {N_{H}^2 \s} \NR
+\NC \MC {O} \RB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
+= \NC \s \MC {O} \RB {1} \NR
 }
 
-On the other hand, Tropp and Gilbert \cite [TrG07b] discussed the complexity of OMP, and they give
-\PF {cc-OMP;oo,nn-hh-2}
-\Disp {
+By condition (), it is easy to see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes Complex Standard Normal distribution.
+and is easily bounded by \m {\s}.
+%
+\DispNum {--;ON,2s} {
+\NC C_{\Rm{DS}}
+=\NC \MC {O} \SB {N_{H}^2 \s} \NR
+}
+
+On the other hand, Tropp and Gilbert \cite [TrG07a] discussed the complexity of OMP, and the proof of technical lemmata in it can be found in the companion paper \cite [TrG07b].
+They give
+%
+\DispNum {C,O;ON,NY} {
 \NC C_{\Rm{OMP}}
@@
 }
+%
 And it would appear that this is greater than \m {C_{\Rm{DS}}}.
-However, we dropped some constants in analyzing \m {C_{\Rm{DS}}}, and here \m {\log N_Y} is really small in our case.
-If we drop it, then we get \m {\MC {O} \SB {N_H^2}} again.
+However, \m {\log N_Y} is really small in our experiments.
+and we dropped some constants, too, in analyzing \m {C_{\Rm{DS}}}.
+If we drop \m {\log N_Y}, then we get \m {\MC {O} \SB {N_H^2}} again.
 
-At least our discussion suggests that, approximately
-\PF {cc-OMP;cc-DS}
-\Disp {
+In summary
+%
+\DispNum {C,P;CD,H2} {
 \NC C_{\Rm{OMP}}
 \approx \NC C_{\Rm{DS}} \NR
-\NC \approx \NC \MC {O} \SB {N_H^2} \NR
+\NC \approx \NC \s \MC {O} \SB {N_H^2} \NR
 }

### 2019-10-23 paper/5_conclusion.tex
Paraphrase chap 1

@@
 
-Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Cand\`es and Tao (2007), that the probability that the expected square error is bounded is overwhelming.
+Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Cand\`es and Tao \cite [CaT07], that the probability that the expected square error is bounded is overwhelming.
 We thus have derived a probability bound of performance on a fairly general setting, where the bounding constant is expressed as an explicit function of physical parameters, such as the number of path.
@@
 Simulation is done, and DS's performance is compared to OMP.
-\color[red]{(To be done)}
+DS is slightly but steadily more accurate than OMP, while DS exhibits rather high complexity.
 

### 2019-10-23 paper/abstract.tex
Delete conversion from complex to real DS
Paraphrase chap 1

--- 2019-04-22 dantzig_selector/report/abstract.tex
@@
 
-Multiple-input-multiple-output (MIMO) is widely expected to be used in the next-generation wireless communication.
-However, reliable communication in such r\`egime often desires that the channel state information be known at the receiver, necessary for example in beamforming algorithm and channel calibration, but it is usually not easy to estimate real-world wireless channel.
-
-Meanwhile, the millimeter wave channel, which is usually used in tandem with MIMO, often exhibits sparse properties, if the sparsity is exploited, few observations may suffice to estimate the channel.
-Such algorithm falls under the study of Compressive Sensing, an active area that has recently emerged.
-A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context, and as originally perceived, it ideal in certain senses.
-However, Orthogonal Matching Pursuit (OMP) later emerges as a solution with lower complexity, and following-up literature, as a result, usually used OMP rather than DS.
-In this article, we consider a hybrid structure at both the transmitter and receiver end, each of them having both digital and analog percoders and combiners.
-We argue in favor of DS, since DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, as well as in its tolerance of noise corruption.
-Indeed, we shall refine Tao and Cand\'es's bound, and generalize under current settings, thus giving a viable solution for the estimation of millimeter wave channel.
-Moreover, we show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
-Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.
+Multiple-input-multiple-output (MIMO) is expected to be the next-generation technology for wireless communication.
+However, for MIMO system it is not easy to estimate the channel, while reliable communication often requires that the channel state information be known at the receiver, necessary e.g.\ in beamforming and channel calibration.
+Meanwhile, the millimeter wave (mm-Wave) band, often used in MIMO context, is known to exhibit sparsity, and emerging work on compressive sensing suggests that if sparsity is exploited, fewer measurement suffices to estimate the channel.
+Dantzig Selector (DS), proposed by Tao and Cand\'es, has been introduced early in channel estimation literature.
+But Orthogonal Matching Pursuit (OMP) emerges, and having a lower complexity, it ends up being popular.
+In this paper, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
+Using pilot signal and designed random beamformer, we employ DS to estimate the channel, arguing in favor of its greater generality, its tolerance of noise corruption, and its lower averaged error, despite of having greater complexity.
+We then proved a bound for the expected square error of DS, as well as bounded probability of success, showing explicit dependency on the number of path and channel sparsity.
+DS can be cast as a second order cone problem (SOCP), so that feasible code for convex programming may be applied.
+Simulation is done on DS and other methods, and we discuss their respective merits.
 

### 2019-10-23 paper/appendix_source.tex
Paraphrase chap 1

\startchapter [title={Appendix: Source Code}]

\startsection [title={\tt {constants.py}}]

\typefile [Code] [] {../../../code/channel-estimation-via-dantzig-selector-code/src/constants.py}

\stopsection

\startsection [title={\tt {functions.py}}]

\typefile [Code] [] {../../../code/channel-estimation-via-dantzig-selector-code/src/functions.py}

\stopsection

\startsection [title={\tt {classes.py}}]

\typefile [Code] [] {../../../code/channel-estimation-via-dantzig-selector-code/src/classes.py}

\stopsection

\startsection [title={\tt {main.py}}]

\typefile [Code] [] {../../../code/channel-estimation-via-dantzig-selector-code/src/main.py}

\stopsection

\stopchapter

### 2019-10-23 paper/notation.tex
Use BibTeX, conform to IEEE citation style
Paraphrase chap 1

--- 2019-08-31 report/notation.tex
@@
 \NC \m {\CB {2, 3, 5, 7}} \VL curly braces \VL used only for sets \AR \HL
-\NC \m {\V {v} \DB {3}} \VL double square brackets \VL used only for entry indices \AR \HL
 \NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
@@
 \NC \m {\V {0}} \VL all-0 vector \VL dimension will be clear from context \AR \HL
-\NC \m {\V {a} \DB {n}} \VL \m {n}-th component of \m {\V {a}} \VL  \AR \HL
-\NC \m {\M {A} \DB {m,n}} \VL \m {m,n}-th entry of \m {\M {A}} \VL  \AR \HL
+\NC \m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL
+\NC \m {\M {A} _{\SB {m,n}}} \VL \m {m,n}-th entry of \m {\M {A}} \VL \AR \HL
+\NC \m {\V {a} _{\SB {0}}} \VL the first component of \m {\V {a}} \VL  \AR \HL
+\NC \m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
 \NC \m {\MB {K}} \VL either \m {\MB {R}} or \m {\MB {C}} \VL  \AR \HL
-\NC \m {\MB {V}_{\MB {K}} \SB {N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL  \AR \HL
-\NC \m {\MB {M}_{\MB {K}} \SB {M,N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
-\NC \m {\V {a} \DB {0}} \VL the first component of \m {\V {a}} \VL  \AR \HL
-\NC \m {\M {A} \DB {0,0}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
-\NC \m {m\; \Rm{Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \Rm{Mod}\; n <n} \AR \HL
+\NC \m {\MB {K} ^{N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL  \AR \HL
+\NC \m {\MB {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
+\NC \m {m\; \Rm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \Rm {Mod}\; n <n} \AR \HL
 \NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
@@
 \NC  \VL component of \m {\V {a}} \VL  \AR \HL
-\NC \m {\MB {P} \SB {A}} \VL probability of \m {A} \VL  \AR \HL
-\NC \m {\MB {E} \SB {X}} \VL expectation of \m {X} \VL  \AR \HL
-\NC \m {\Ss {Var} \SB {X}} \VL variance of \m {X} \VL  \AR \HL
+\NC \m {\MB {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
+\NC \m {\MB {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
+\NC \m {\Ss {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
 \stoptable

### 2019-10-29 paper/1_introduction.tex
Rewrite 3.1, 3.2

@@
 %
-\DispNum {N,p;Nm,Nm} {
-\NC N_p \gg N_m \NR
+\DispNum {N-p-Nm-Nm} {
+\NC N_p \gg \NC N_m \NR
 }
@@
 
-To start, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\V {Q} \in \MB {K} ^{N_m \D  N_p}}.
+To start, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}.
 For \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}}, denote
@@
 =\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR
+%
 \NC \M {Q}  _{\SB {\MC {A}}}
@@
 %
-\DispNum {x,A;x-,x-} {
+\DispNum {x-A-x--x-} {
 \NC \V {x} _{\SB {\MC {A}}}
@@
 %
-\DispNum {A,A;s-,s-} { 
-\NC \# \MC {A} \leq \NC s. \NR
+\DispNum {A-A-s--s-} { 
+\NC \Nm {\MC {A}} \leq \NC s. \NR
 }
@@
 {
-For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies the restricted isometry property (hereafter RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
+For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies \m {\d_s}-restricted isometry property (hereafter \m {\d_s}-RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if for all \m {s}-sparse \m {\V {x}}
 %
-\DispNum {1,2;Qx,22} {
-\NC \RB {1-\d_s} \VNm {\V {x}}^2
-\leq \NC \VNm {\M {Q} \V {x}} _2^2 \NR
-\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR
+\DispNum {1-2-Qx-22} {
+\NC \RB {1-\d_s} \VNm {\V {x}} _2 ^2
+\leq \NC \VNm {\M {Q} \V {x}} _2 ^2 \NR
+%
+\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \NR
 }
@@
 %
-\DispNum {y,y;Qx,xz} {
+\DispNum {y-y-Qx-xz} {
 \NC \V {y}
@@
 \item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}.
+%
 \item Calculate
 %
-\DispNum {h,h;mi,yg'} {
+\DispNum {h-h-mi-yg'} {
 \NC \Hat {\V {h}}
@@
 \NC \Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
+%
 \NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {Q}^\Adj \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
@@
 \item Output \m {\Hat {\V {h}}}.
+\stopitemize
 }
@@
 Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (hereafter LP), lending convex programming technique applicable.
-The constant \m {\d_s} in Definition [2] is crucial, and here one might ask that why don't we just take \m {Q} to be just any unitary matirx.
-Regarding this, we remark that the aforementioned performance bound is not tightest when \m {\d_s =0}, thus giving the RIP an important role.
+The constant \m {\d_s} in Definition [2] is crucial, and here we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
 One common design choice of \m {\M {Q}} proposed is that every entry of \m {\M {Q}} shall be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
@@
 
-Still consider \Rf {y,y;Qx,xz}.
+Still consider \Rf {y-y-Qx-xz}.
 We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.
@@
 \item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
+%
 \item Initialize
@@
 \LA \NC \V {y} \NR
+%
 \NC S
@@
 %
-\DispNum {c,c;i0,ir} {
+\DispNum {c-c-i0-ir} {
 \NC c
@@
 %
-\DispNum {Q,Q;QS,Qy} {
+\DispNum {Q-Q-QS-Qy} {
 \NC \M {Q} ^\ddagger
 \LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
+%
 \NC \V {r}
@@
 %
-\DispNum {r,2;h',h'} {
+\DispNum {r-2-h'-h'} {
 \NC \VNm {\V {r}} _2
@@
 %
-\DispNum {g,g;Qy,Qy} {
+\DispNum {g-g-Qy-Qy} {
 \NC \Hat {\V {g}}

### 2019-10-29 paper/3_1_almost_sparsity.tex
Rewrite 3.1, 3.2

@@
 Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and \m {\M {G}} is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
-We define, similarly, \m {\V {a} _{\SB{\MC {A}}}} and \m {\V {a} _{\SB{\MC {C}}}}, with undetermined sparsity index
-%
-\Disp {
-\NC S
-\leq \NC \R {N_H}. \NR
-}
-%
-If \m {N_H} is large, we need not bother ourself with the requirement that \m {S} is an integer.
+We define, similarly, \m {\V {a} _{\SB{\MC {A}}}} and \m {\V {a} _{\SB{\MC {C}}}}, with sparsity \m {s}.
+If \m {N_H} is large, we may forget for a moment the requirement that \m {s =1,2,3,\dots}.
 
@@
 Let \m {\f} be fixed.
-Towards that end, 
-Introduce
+Towards that end, introduce
 %
-\Disp {
+\DispNum {y'-H-f'M-p'p'} {
 \NC \psi \SB {\f, n_H}
@@
 %
-\Disp {
+\DispNum {y'-H-p'--p'-} {
 \NC \Nm {\psi \SB {\f, n_H}}
@@
 %
-\Disp {
+\DispNum {D-y'-nH-Hy'} {
 \NC D \SB {\psi'}
@@
 %
+Set for short
+%
+\DispNum {b-f'-Ka-af'} {
+\NC b \SB {\f}
+=\NC \M {K}^\Adj \V {a} \SB {\f} \NR
+}
+%
 Then observe
 %
-\Disp {
-\NC \RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB {n_H}}
+\DispNum {K-H-1N-nH} {
+\NC \RB {\V {b} \SB {\f}} _{\SB {n_H}}
 =\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
@@
 }
-
-Applying Lemma () to the denominator of () and bounding the nominator by 1, we have
+Therefore,
 %
-\Disp {
+\DispNum {D-y'-si-y'p'} {
 \NC \Nm {D \SB {\psi'}}
 = \NC \F {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
+%
 \NC \leq \NC B \SB {\psi'} \NR
+%
 \NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
+%
 \NC -\pi \leq \NC \psi' < \pi. \NR
@@
 %
-Thus,
+Combining \Rf {y'-H-f'M-p'p'}, \Rf {K-H-1N-nH}, and \Rf {D-y'-si-y'p'} we have
 %
 \Disp {
-\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _1
+\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _1
 =\NC \F {1} {N_H}
@@
 \Disp {
-\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _1
+\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _1
 \leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
-\NC = \NC \F {2304} {N_H \pi^6}
-\int _{s /N_H} ^1 \F {1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
-\NC =\NC \F {1} {2\pi^2 N_H}
-\RB {
-  -\F {8} {u}
-+\F {4\pi^2 u} {24 -\pi^2 u^2}
-+\R {6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R {6}}}
+%
+\NC = \NC \F {48} {N_H \pi^3}
+\int _{s /N_H} ^1 \F {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
+%
+\NC =\NC \F {1} {\pi} \log \F {N_H^2 /s^2 -\pi^2 /24} {1 -\pi^2 /24} \NR
+%
+\NC \simeq \NC \F {1} {\pi} \RB {\log N_H -\log s} \NR
 }
-\Bigg \| _{s/N_H} ^1 \NR
-\NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR
-\NC \approx \NC \F {4} {\pi^2 s} \NR
+%
+Since the value of \m {s} is at our disposal, we try
+%
+\DispNum {s-s-lo-NH} {
+\NC s
+=\NC \R {\log N_H} \NR
 }
-
-% % Deprecated!
-% \Disp {
-% \NC R^2
-% \leq \NC \F {1} {N_H^2} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
-% \NC = \NC \F {2304} {N_H \pi^6}
-% \int _{s /N_H} ^1 \F {1} {(24/\pi^2 -x'^2)^2 x'^2} dx' \NR
-% \NC =\NC \F {1} {2\pi^2 N_H}
-% \RB {
-%   -\F {8} {u}
-% +\F {4\pi^2 u} {24 -\pi^2 u^2}
-% +\R {6} \pi \tanh^{-1} \SB {\F {\pi u} {2\R {6}}}
-% }
-% \Bigg \| _{s/N_H} ^1 \NR
-% \NC \leq \NC \F {4} {\pi^2} \D \F {1} {s} +\F {0.032670} {N_H} \NR
-% \NC \approx \NC \F {4} {\pi^2 s} \NR
-% }
-% In the last step we bound the lower limit of the second and third term with \m {x' =0}, and leave the dominating \m {1/x'}.
+%
+so that, by \m {\ell_p}-norm inequality,
 
@@
 {
-Let \m {\f } be given, and linear array response \m {\V {a} \SB {\f}} defined as in ().
-Suppose \m {N_H \geq 4}.
-Then, for any instance of \m {\f},
+Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in {b-f'-Ka-af'}.
+Then, for any random instance of \m {\f},
 %
-\DispNum {a;f',C} {
-\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _2
-\leq \NC \F {2} {\pi \R{s}} \NR
+\DispNum {a-2-4N-NH} {
+\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _2
+\leq \NC \F {2} {\pi} \log N_H \NR
 }
-}
-
-Since the value of \m {s} is at our disposal, we try
-%
-\DispNum {s;nn-hh,} {
-\NC s
-=\NC \R {\log N_H} \NR
-}
-%
-so that
-%
-\DispNum {R;2,p'} {
-\NC R
-\leq \NC \F {2} {\pi \R{\log N_H}} \NR
 }
@@
 
-Recall that, by \m {\ell_p}-norm inequality,
+If that we set
+\DispNum {S-S-Ls-s2} {
+\NC S
+=\NC L s^2 \NR
+}
+by triangle inequality, by the property of 2-norm and Frobenius norm,
 %
 \Disp {
-\NC \VNm {\M {g} _{\SB{\MC {C}}}} _2
-\leq \NC \VNm {\M {g} _{\SB{\MC {C}}}} _1 \NR
+\NC \VNm {\V {g} _{\SB{\MC {C}}}} _1
+\leq \NC
+\sum _{l=0} ^{L-1} \Nm {\a_l}
+\VNm {\\V {b} \SB {\f_l} _{\SB{\MC {C}}}} _2
+\VNm {\\V {b} \SB {\th_l} _{\SB{\MC {C}}}} _2 \NR
+%
+\NC \leq \NC
+\VNm {\V {b} \SB {\f_l} _{\SB{\MC {C}}}} _2
+\VNm {\V {b} \SB {\th_l} _{\SB{\MC {C}}}} _2
+\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
+%
+\NC \leq \NC
+\F {4} {\pi^2} L \RB {\log N_H}^2 \D
+\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
 }
 %
-And just by definition
+The quantity \m {(1/L) \sum _{l=0} ^{L-1} \Nm {\a_l}} is a sample mean, and we may want to use Hoeffding inequality.
+Since it requires that the random variable shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2}, on which there is 95\% probability mass.
+%
+To do so, observe that
 %
 \Disp {
-\NC \VNm {\M {G} _{\SB{\MC {C}}}} _F
-\leq \NC \VNm {\M {g} _{\SB{\MC {C}}}} _2 \NR
+\NC \MB {E} \SB {\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
+=\NC \F{\R {2}} {\R {\pi}} \NR
+}
+So, by Hoeffding inequality, choose for simplicity
+%
+\DispNum {P-p'-2e-3p'} {
+\NC \MB {P} \SB {
+   \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
+   \geq \F {4 \R{2}} {\R {\pi}}
+}
+\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
 }
 %
-So it remains to bound \m {\VNm {\M {G} _{\SB{\MC {C}}}} _F}.
-
-Note that
+Now we have \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1 /\RB {\log N_H}^2 \leq 12 \R{2} /\pi ^{5/2} \leq 4/3}.
 %
-\DispNum {G;H,a'-l} {
-\NC \VNm {\M {G} _{\SB{\MC {C}}}} _F
-=\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F \NR
-}
-%
-And by definition
-%
-\Disp {
-\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F
-=\NC \VNm {\sum _{l=0} ^{L-1} \a_l
-\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj} _F \NR
-}
-%
-By triangle inequality, by the property of 2-norm and Frobenius norm,
-%
-\DispNum {;a'-l,a,f'-l} {
-\NC \leq \NC \sum _{l=0} ^{L-1}
-\Nm {\a_l}\VNm {\V {a} \SB {\f_l} \V {a} \SB {\th_l} ^\Adj } _F \NR
-\NC \leq \NC
-\sum _{l=0} ^{L-1} \Nm {\a_l}
-\VNm {\V {a} \SB {\f_l}} _2
-\VNm {\V {a} \SB {\th_l}} _2 \NR
-}
-%
-It follows that
-%
-\Disp {
-\NC \VNm {\M {H} _{\SB{\MC {C}}}} _F
-\leq \NC
-\sum _{l=0} ^{L-1} \Nm {\a_l}
-\VNm {\V {a} \SB {\f_l} _{\SB{\MC {C}}}} _2
-\VNm {\V {a} \SB {\th_l} _{\SB{\MC {C}}}} _2 \NR
-\NC \leq \NC
-\VNm {\V {a} \SB {\f_l} _{\SB{\MC {C}}}} _2
-\VNm {\V {a} \SB {\th_l} _{\SB{\MC {C}}}} _2
-\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
-\NC \leq \NC
-\F {4} {\pi^2 \log N_H}
-\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
-}
-
-Observe that
-%
-\Disp {
-\NC \MB {E} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}}
-=\NC \F{\R {2} L} {\R {\pi}} \NR
-%
-\NC \Ss {Var} \SB {\sum _{l=0} ^{L-1} \Nm {\a_l}}
-=\NC \RB {1 - \F{2}{\pi}} L \NR
-}
-
-We expect that
-%
-\Disp {
-\NC \sum _{l=0} ^{L-1} \Nm {\a_l}
-\leq \NC L \R {\F {2} {\pi}}
-   +\R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2} \NR
-\NC \approx \NC \R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2} \NR
-}
-%
-Thus, by Chebyshev inequality,
-%
-\Disp {
-\NC \MB {P} \SB {
-   \sum _{l=0} ^{L-1} \Nm {\a_l}
-   \geq \R {1 -\F {2} {\pi}} \R {L} \RB {\log N_H} ^{3/2}
-}
-\leq \NC \F {1} {\RB {\log N_H} ^3} \NR
-}
-%
-Summarizing, we have the following result.
-
 \Result
@@
 {
-Let \m {\f} and \m {\th} be uniformly, independently distributed in \m {[0,2\pi)},
-and let \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in ().
+Let \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in \Rf {g-g-ve-Nh}.
 Then the bound
 %
-\DispNum {g-C;4,p'-2} {
+\DispNum {g-C-4p'-NH} {
 \NC \VNm {\M {g} _{\SB{\MC {C}}}} _1
-\leq \NC \F {4} {\pi^2} \R {1 -\F {2} {\pi}} L N_H \R {\log N_H} \NR
+\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
 }
 %
-holds with probability \m {p} such that
+holds for probability \m {p}, with
 %
-\DispNum {1,p;1} {
+\DispNum {1-p-1N-H3} {
 \NC 1 -p
-\leq \NC \F {1} {\RB {\log N_H} ^3} \NR
+\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
 }

### 2019-10-29 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Rewrite 3.1, 3.2

@@
 %
-\DispNum {d,d;gg,gg} {
+\DispNum {d-d-gg-gg} {
 \NC \V {d} 
@@
 %
-\DispNum {g',g';2N,Nh} {
+\DispNum {g'-g'-2N-Nh} {
 \NC \g
@@
 }
-
-The rest follows \cite [CaT07] very closely, but sometimes, the generalization to complex vector cannot be glossed over, and we have to examine.
-To start, we state several lemmata (or their generalization) shown in their paper.
-
+%
+The lemmata below are taken from \cite [CaT07] and modified slightly in accordance to our settings, except possibly the generalization to complex vector.
+%
 \Result
@@
 %
-\DispNum {d,1;dA,C1} {
+\DispNum {d-1-dA-C1} {
 \NC \VNm {\V {d} _{\SB{\MC {C}}}} _1
@@
 }
-
+%
 To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}}, while recalling that \m {\V {g} =\V {g} _{\SB{\MC {A}}}},
 %
-\DispNum {g,1;gd,g1} {
+\Disp {
 \NC \VNm {\V {g}} _1
@@
 \leq \NC \VNm {\V {g} +\V {d}} _1 \NR
+%
 \NC =\NC \VNm {\hat {\V {g}}} _1 \NR
@@
 %
-\DispNum {--;g1,g1} {
+\DispNum {--;g1,g1;} {
 \NC \leq \NC \VNm {\V {g}} _1 \NR
 }
-
+%
 \Result
@@
 Let \m {\M {P}} be fixed, and instance of \m {\V {z}} be given.
-Then the relation
+Then
 %
-\DispNum {E,h;2N,Nh} {
+\DispNum {E-h-2N-Nh} {
 \NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}}
 \leq \NC  2 \R {\log N_h} \NR
+%
 \NC n_h 
@@
 }
-
+%
 Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}, the quantity \m {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}} observes standard Normal.
@@
 %
-\DispNum {Q,x;12,22} {
+\DispNum {Q-x-12-22} {
 \NC Q\SB {x}
@@
 %
-\DispNum {Q,h;1N,Nh} {
+\DispNum {Q-h-1N-Nh} {
 \NC Q\SB {\R {2 \log N_h}}
@@
 }
-
+%
 \Result
@@
 {
-With the assumption that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M {P}}}, then
+If \m {\M {P}} is \m {\d_S}-RIP,
 %
-\DispNum {P,d;4N,Nh} {
+\DispNum {P-d-4N-Nh} {
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
@@
 }
-
+%
 To show this, by definition
 %
-\DispNum {z,y;Pg,ny} {
+\DispNum {z-y-Pg-ny} {
 \NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
 = \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y}} \NR
+%
 \NC = \NC \IP {\M {P} \V {d}, \M {P} \DB {:,n_y}} \NR
@@
 %
-\DispNum {P,g;Py,Nh} {
+\DispNum {P-g-Py-Nh} {
 \NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
 \leq \NC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty \NR
+%
 \NC \leq \NC 2\R {\log N_h} \NR
@@
 %
-By triangle inequality, together with Lemma (), we have
+By triangle inequality, together with \Rf {E-h-2N-Nh}, we have
 %
-\DispNum {P,d;zP,Nh} {
+\DispNum {P-d-zP-Nh} {
 \NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
@@
 +\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y}} \NR
+%
 \NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
@@
 %
-\DispNum {P,d;4l,Nh} {
+\DispNum {P-d-4l-Nh} {
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
@@
 }
-
-The following two lemmata, coming from \quotation {Dantzig Selector} Lemma 1, will be stated without proof.
-The generalization from the original real vector spaces to present complex ones is valid, and completely straightforward.
-Note that the interpretation of magnitude and the inner product has to be changed accordingly.
-\Result
-{Lemma}
-{
-With the assumption that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M {P}}},
 %
-\DispNum {d,2;11,C1} {
-\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
-\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}} {\RB {1-\d_{2S}} \R {S}} \VNm {d_{\SB{\MC {C}}}} _1 \NR
-}
-}
-%
-And
+Lastly, the following two lemmata is taken from \cite [CaT07], Lemma 1.
+The generalization from real vector spaces to complex spaces is completely straightforward, while meaning of magnitude and inner product has to be changed.
 \Result
@@
 %
-\DispNum {d,2;dA,12} {
+\DispNum {d-2-dA-12} {
 \NC \VNm {\V {d}} _2^2
@@
 }
+The other one reads
+\DispNum {d-2-11-C1} {
+\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
+\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2
++\F {\T {\d}_{S, 2S}} {\RB {1-\d_{2S}} \R {S}} \VNm {d_{\SB{\MC {C}}}} _1 \NR
+}
+Here \m {\T {\d} _{s_1, s_2}} is called the \m {s_1,s_2}-restricted isometry constant, and is defined in \cite [Can05] (which uses \m {\th}), as follows.
+Let \m {\M {Q}'} be fixed.
+For all \m {s_1}-sparse \m {\V {x}_1}, for all \m {s_2}-sparse \m {\V {x}_2}, whose positions for nonzero components are disjoint,
+%
+\Disp {
+\NC \T {\d} _{s_1, s_2}
+= \NC \inf \CB {
+\d':\; \Nm {\IP {\M {Q}' \V {x}_1, \M {Q}' \V {x}_2}}
+   \leq \d' \VNm {\V {x}_1} \VNm {\V {x}_2}
+} \NR
+}
+%
+Here we use a result in \cite [Can05] that relates \m {\T {\d} _{s_1, s_2}} to \m {\d_s}, that is
+\DispNum {d-2-ds-s2} {
+\NC \T {\d} _{s_1, s_2}
+\leq \NC \d_{s_1+s_2} \NR
+}
+And we need another crude bound to relate \m {\d_{2S}} to \m {\d_{S}}.
+By triangle inequality, by power-mean inequality,
+\DispNum {Q-x-Qx-x2} {
+\NC \VNm {Q' \RB {\V {x}_1 + \V {x}_2}}
+%
+\leq \NC \VNm {Q' \V {x}_1}
++\VNm {Q' \V {x}_2} \NR
+%
+\NC \leq \NC \RB {1 +\d _{s}} \RB {\VNm {\V {x}_1} +\VNm {\V {x}_2}} \NR
+%
+\NC \leq \NC \RB {1 +\d _{s}} \D \R{2} \VNm {\V {x}_1 +\V {x}_2} \NR
+}
+Therefore
+\Disp {
+\NC \d_{2s}
+\leq \NC \R {2} \d_{s} \NR
+}
+By the same token,
+%
+\Result
+{Lemma}
+{
+If \m {\M {Q}'} has \m {\d}-RIP, then, for \m {M=1,2,3,\dots} so that \m {\d _{Ms}} is meaningful,
+%
+\DispNum {d-s-Md'-d's} {
+\NC \d_{Ms}
+\leq \NC \R {M} \d_{s} \NR
+}
+}
+%
+Thus we have, in view of \Rf {d-2-11-C1},
+\Result
+{Lemma}
+{
+If \m {\M {P}} is \m {\d_S}-RIP,
+%
+\DispNum {d-2-11-C1} {
+\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
+\leq \NC \F {1} {1-\R{2} \d_{S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2
++\F {\R{3} \d_{S}} {\RB {1-\R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\MC {C}}}} _1 \NR
+}
+}
+%
 
@@
 We are going to combine previous lemmata and show the main result.
-Now, in view of the result in Section 3.1, \m {s} is free, and we set
+For simplicity, set
 %
-\DispNum {s,s;1-,1-} {
-\NC s
-=\NC 1 \NR
+\DispNum {d'-S;18,18;} {
+\NC \d_S
+\leq \NC \F {1} {8} \NR
 }
 %
-which is crude, but enough.
-Accordingly,
-%
-\DispNum {S;L,nn-hh} {
+Thus
+\DispNum {S-S-4N-NH} {
 \NC S
-=\NC L \R {\log N_H} \NR
+=\NC L \log N_H \NR
 }
 %
-Just for simplicity, we assume
-%
-\DispNum {d'-S;1,2} {
-\NC \d_S
-\leq \NC \F {1} {2} \NR
-}
-%
-and
-%
-\DispNum {L;4,} {
-\NC L
-\geq \NC 4 \NR
-}
-
 \Result
@@
 {
-Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as ()....
+Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
 Then the bound
 %
-\DispNum {d;4,2} {
+\DispNum {d-2-42-NH} {
 \NC \VNm {\V {d}} _2
-\leq \NC 4 \R {2} \D \R {L \log N_H} \NR
+\leq \NC 4 \R {2L} \log N_H \NR
+}
 }
 %
-holds for probability \m {p}, with
+
+We start to prove \Rf {d-2-42-NH}.
+By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P-d-4N-Nh},
+%
+\DispNum {P-2-PP-NH} {
+\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
+\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
+%
+\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
+%
+\NC \leq \NC 4 \R {2 \log N_H} \NR
+}
+%
+By \m {\ell_p}-norm inequality, by the definition of truncation, by \Rf {d-2-11-C1}, and by \Rf {P-2-PP-NH} just above,
 %
 \Disp {
-\NC 1 -p
-\leq \NC 2 \D 6^L \D \exp \SB {-\F {N_Y^2} {32}} \NR
-}
-}
-
-By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {s,1,,} and \Rf {P,P,d},
+\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
+\leq \NC \R {S} \VNm {\V {d} _{\SB{\MC {A}}}} _2 \NR
 %
-\DispNum {P-A-B,P,d} {
-\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
-\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
-\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
-\NC \leq \NC 4 \R {2 L \log N_H} \NR
-}
-
-By \m {\ell_p} norm inequality, by the definition of truncation, by \Rf {d-A-B;1,1}, \Rf {d'-S;1,2}, and \Rf {P-A-B,P,d} just above,
+\NC \leq \NC \R {S} \VNm {\V {d} _{\SB{\MC {AB}}}} _2 \NR
 %
-\DispNum {d-A;L,d-A} {
-\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
-\leq \NC \R {L} \VNm {\V {d} _{\SB{\MC {A}}}} _2 \NR
-\NC \leq \NC \R {L} \VNm {\V {d} _{\SB{\MC {AB}}}} _2 \NR
-\NC \leq \NC 8 \R {2 \log N_H}
-+\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
-}
-
-Next, we want to use \Rf {d-K;d-A,2-g-K} to eliminate \m {\VNm {d _{\SB{\MC {A}}}} _1} in \Rf {d-A;L,d-A}.
-%
-\DispNum {;8,2,nn-hh} {
-\NC \leq \NC 8 \R {2 \log N_H}
-+\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \RB {\VNm {\V {d} _{\SB{\MC {A}}}} _1 +2\VNm {\V {g} _{\SB{\MC {C}}}} _1} \NR
-\NC \leq \NC 8 \R {2 \log N_H}
-+\F {2} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {g} _{\SB{\MC {C}}}} _1 \NR
+\NC \leq \NC 4 \R {2 \log N_H}
++\F {1} {\R{L \log N_H}} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
 }
 %
-And \Rf {g-C;4,p'-2} in Section 3.1 gives
+Next, we want to use \Rf {d-1-dA-C1} to eliminate \m {\VNm {d _{\SB{\MC {A}}}} _1}.
 %
-\DispNum {d-A;8,2} {
+\DispNum {8,2,nn-hh;} {
+\NC \leq \NC 4 \R {2 \log N_H}
++\F {1} {\R{L \log N_H}} \RB {\VNm {\V {d} _{\SB{\MC {A}}}} _1 +2\VNm {\V {g} _{\SB{\MC {C}}}} _1} \NR
+}
+%
+And \Rf {a-2-4N-NH} gives, after arrangement,
+%
+\DispNum {d-A;8,2;} {
 \NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
-\leq \NC 8 \R {2 \log N_H}
+\leq \NC 4 \R {2 \log N_H}
 +2\VNm {\V {g} _{\SB{\MC {C}}}} _1 \NR
+%
 \NC \leq \NC \RB {16 \R {2} +\F {4} {\pi^2} \R {1 -\F {2} {\pi}}} \log N_H \NR
 }
-
+%
 We are now in a position to bound \m {\VNm {d} _2^2}.
-Using Lemma () again, we have
+Using \Rf {d-2-dA-12} again, we have
 %
@@
 
+In addition to the bound, we shall discuss the four sources of error, namely
+\DispNum {q-q-2q-ar} {
+\NC q
+\simeq \NC 2 \RB {q _{\Rm {isom}, B} + q _{\Rm {isom}, R}} +q _{\Rm {nois}} +q _{\Rm {spar}} \NR
+}
+subscript for restricted isometry, noise, sparsity, respectively.
+
+Quoting previous results, they are
+\Disp {
+q
+\simeq \Ss {e} ^{N_B \d}
+}
+%
+Provided the design values
+\Disp {
+\NC N_R
+\leftarrow \NC \RB {\log N_H} ^{3/2} \NR
+%
+\NC N_B
+\leftarrow \NC \log \log N_H \NR
+}
+%
+And we get the estimation
+\Disp {
+\NC q
+=\NC \MC {O} \SB {\F {1} {\RB {\log N_H}^3}} \NR
+}
+%
 \stopsubsection

### 2019-10-29 paper/4_simulation.tex
Rewrite 3.1, 3.2

@@
 
-However, it turns out direct implementation of () exhibit extraordinarily large complexity, and we would like to recast the problem in a more tractable form.
+However, it turns out direct implementation of Algorithm 8 exhibit extraordinarily large complexity, and we would like to recast the problem in a more tractable form.
 Towards that end, we found out that Candès and Romberg \cite [CaR05] has shown that DS can be simplified as an linear program (LP).
@@
 %
-\Disp {
+\DispNum {R-x-R2-M1} {
 \NC \MC {R} \SB {\V {x}}
@@
 %
-\Disp {
+\DispNum {R-1-x--x-} {
 \NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V {x}}}
@@
 %
-\Disp {
+\DispNum {R-A-R2-21} {
 \NC \MC {R} \SB {\M {A}}
@@
 %
-\Disp {
+\DispNum {y---Ry-Ny} {
 \NC \T {\V {y}}
@@
 %
-\Disp {
+\DispNum {y---Pg-gz} {
 \NC \V {\T {y}}
@@
 %
-\Disp {
+\DispNum {u-h-RN-h1} {
 \NC {\V {u}}_{n_h}
@@
 %
-\Disp{
+\DispNum {m---RN-h1} {
 \NC \V {m} \in \NC \MB {R} ^{N_h} \NR
@@
 %
-\Disp {
+\DispNum {g---mi-h1} {
 \NC \Hat {\T {\V {g}}}
@@
 \NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
-\leq \g \NR
+\leq \g_{\Rm {DS}} \NR
 \stopcases \NR
@@
 We shall see furthermore that the program can be cast into an SOCP.
-To make the point clearer, we rewrite Program () into an extended block matrix form, by defining auxiliary variables as follows,
+To make the point clearer, we rewrite the program just above into an extended block matrix form, by defining auxiliary variables as follows,
 %
-\Disp{
+\DispNum {t---01-Nh} {
 \NC \V {t}
@@
 %
-\Disp{
+\DispNum {A-i-Ui-h1} {
 \NC \M {A}_i
@@
 \NC d_i
-= \NC \g \NR
+= \NC \g_{\Rm {DS}} \NR
 %
@@
 }
-%
-The step that we convert \m {\Hat {\V {g}}} back is same as Algorithm () is same as before, but this is listed for sake of completeness.
 
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {C} ^{N_y \D N_h}}, \m{\V {y} \in \MB {C} ^{N_y}}, \m{\g > 0}.
+\item Input \m{\M {P} \in \MB {C} ^{N_y \D N_h}}, \m{\V {y} \in \MB {C} ^{N_y}}, \m {\g_{\Rm {DS}} > 0}.
 \item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
@@
 %
-\Disp{
+\DispNum {x---mi-h1} {
 \NC \Hat {\V {x}}
@@
 %
-\Disp{
+\DispNum {g---x0-h1} {
 \NC \Hat{\T{\V {g}}}
@@
 %
-\Disp{
+\DispNum {g---R1-1g} {
 \NC \Hat{\V {g}}
@@
 
-Several threshold values occur in relevant alorithms.
-The threshold used in DS program is called \m {\g_{\Rm {DS}}} here, and another threshold of Lasso, called \m {\a}.
+Denote the threshold used in DS program to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
 Yet another threshold used for the residue norm used in OMP program is called \m {\eta}.
@@
 %
-\DispNum {e',s;lo,vg} {
+\DispNum {e'-s-lo-vg} {
 \NC \e_{\Rm{abs}}
@@
 %
-\DispNum {e',l;lo,vg} {
+\DispNum {e'-l-lo-vg} {
 \NC \e_{\Rm{rel}}
@@
 %
-\DispNum {e',h;52,NH} {
+\DispNum {e'-h-52-NH} {
 \NC \e_{\Rm{th}}
@@
 %
-\DispNum {C,S;C0,1e'} {
+\DispNum {C-S-C0-1e'} {
 \NC C_{\Rm{DS}}
@@
 %
-\DispNum {g,0;gL,Py} {
+\DispNum {g-0-gL-Py} {
 \NC \V {g}_0
@@
 %
-\DispNum {C,S;Og,g1} {
+\DispNum {C-S-Og-g1} {
 \NC C_{\Rm{DS}}
@@
 %
-\DispNum {g-;g-,-g} {
+\DispNum {g-;g-,-g;} {
 \NC \V {g} ^\star
@@
 %
-\DispNum {P,P;IN,H2} {
+\DispNum {P-P-IN-H2} {
 \NC \M {P} ^\Adj \M {P}
@@
 \Disp {
-\NC \MC {O} \RB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
+\NC \MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
 = \NC \s \MC {O} \RB {1} \NR
@@
 
-By condition (), it is easy to see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes Complex Standard Normal distribution.
+It is easy to see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes Complex Standard Normal distribution.
 and is easily bounded by \m {\s}.
 %
-\DispNum {--;ON,2s} {
+\DispNum {--;ON,2s;} {
 \NC C_{\Rm{DS}}
@@
 %
-\DispNum {C,O;ON,NY} {
+\DispNum {C-O-ON-NY} {
 \NC C_{\Rm{OMP}}
@@
 %
-\DispNum {C,P;CD,H2} {
+\DispNum {C-P-CD-H2} {
 \NC C_{\Rm{OMP}}

### 2019-10-30 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Finish 3.3

@@
 \NC \g
-= \NC \R {2 \log N_h} \NR
+= \NC \R {4 \log N_H} \NR
 }
@@
 %
-\DispNum {--;g1,g1;} {
+\Disp {
 \NC \leq \NC \VNm {\V {g}} _1 \NR
@@
 %
-\Result
-{Lemma}
-{
-Let \m {\M {P}} be fixed, and instance of \m {\V {z}} be given.
-Then
+To prove the next result, fix an instance of \m {\M {P}} and instance of \m {\V {z}}.
+We claim that
 %
 \DispNum {E-h-2N-Nh} {
-\NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}}
-\leq \NC  2 \R {\log N_h} \NR
+\NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}}
+\leq \NC  2 \R {2 \log N_H} \NR
 %
 \NC n_h 
-=\NC 1, \ldots, N_h. \NR
+=\NC 1, \ldots, N_H^2. \NR
 }
 %
-holds with probability \m {\geq 1 -N_h^{-1}}.
+This follows by the fact that \m {\M {P} _{\SB {:, n_g}}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}, the quantity \m {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}} observes Standard Normal.
+To bound the failure probability, recall the tail bound for \m {Q} function
+%
+\DispNum {Q-x-12-22} {
+\NC Q\SB {x'}
+\leq \NC \F {1} {2} \Ss {e}^{-x'^2 /2} \NR
 }
 %
-Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}, the quantity \m {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}} observes standard Normal.
-Recall the following bound for \m {Q} function
-%
-\DispNum {Q-x-12-22} {
-\NC Q\SB {x}
-\leq \NC \F {1} {2} \Ss {e}^{-x^2/2} \NR
-}
-%
-Particularly, for \m {x =\R {2 \log N_h}},
+Particularly, for \m {x' =\R {4 \log N_H}}, this gives the failure probability
 %
 \DispNum {Q-h-1N-Nh} {
-\NC Q\SB {\R {2 \log N_h}}
-=\NC \F {1} {N_h}. \NR
+\NC Q\SB {\R {4 \log N_H}}
+=\NC \F {1} {N_H^2}. \NR
 }
@@
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC  4 \R {\log N_h} \NR
+\leq \NC  4 \R {2 \log N_H} \NR
 }
 %
-holds with probability \m {\geq 1 -N_h^{-1}}.
+holds for probability \m {p} 
+%
+\DispNum {1-p-NH-H2} {
+\NC 1 -p
+\leq \NC N_H^{-2}. \NR
+}
 }
@@
 \DispNum {z-y-Pg-ny} {
-\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
-= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y}} \NR
+\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_y}}}
+= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} _{\SB {:,n_y}}} \NR
 %
-\NC = \NC \IP {\M {P} \V {d}, \M {P} \DB {:,n_y}} \NR
+\NC = \NC \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_y}}} \NR
 }
@@
 \DispNum {P-g-Py-Nh} {
-\NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
+\NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
 \leq \NC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty \NR
 %
-\NC \leq \NC 2\R {\log N_h} \NR
+\NC \leq \NC 2\R {2 \log N_H} \NR
 }
 %
-By triangle inequality, together with \Rf {E-h-2N-Nh}, we have
+By triangle inequality, together with \Rf {Q-h-1N-Nh}, we obtain the desired result.
 %
 \DispNum {P-d-zP-Nh} {
-\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
-\leq \NC \VNm {\IP {\V {z}, \M {P} \DB {:,n_y}}} _\infty
-+\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y}} \NR
+\NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \M {P} \V {d}} _\infty
+\leq \NC \VNm {\IP {\V {z}, \M {P} _{\SB {:,n_y}}}} _\infty
++\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_y}}} \NR
 %
-\NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
-}
-%
-which implies
-%
-\DispNum {P-d-4l-Nh} {
-\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC 4 \R {\log N_h}. \NR
+\NC \leq \NC 2 \R {2 \log N_H} +2 \R {2 \log N_H} \NR
 }
@@
 The generalization from real vector spaces to complex spaces is completely straightforward, while meaning of magnitude and inner product has to be changed.
+One of them reads
+%
+\DispNum {d-2-dA-12} {
+\NC \VNm {\V {d}} _2^2
+\leq \NC \VNm {\V {d} _{\SB {\MC {AB}}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1^2 \NR
+}
+%
+By power mean inequality, we get a statement cruder than \Rf {d-2-dA-12} that
+%
 \Result
@@
 %
-\DispNum {d-2-dA-12} {
-\NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1^2 \NR
+\DispNum {d-2-dA-C1} {
+\NC \VNm {\V {d}} _2
+\leq \NC \VNm {\V {d} _{\SB {\MC {AB}}}} _2 +\F {1} {\R {S}} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
 }
 }
-The other one reads
+%
+The other one of them reads
+%
 \DispNum {d-2-11-C1} {
 \NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
-\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2
+\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\SB {\MC {AB}}}^\Tr P d} _2
 +\F {\T {\d}_{S, 2S}} {\RB {1-\d_{2S}} \R {S}} \VNm {d_{\SB{\MC {C}}}} _1 \NR
 }
+%
 Here \m {\T {\d} _{s_1, s_2}} is called the \m {s_1,s_2}-restricted isometry constant, and is defined in \cite [Can05] (which uses \m {\th}), as follows.
@@
 %
-\NC \leq \NC \RB {1 +\d _{s}} \RB {\VNm {\V {x}_1} +\VNm {\V {x}_2}} \NR
+\NC \leq \NC \RB {1 +\d _{s'}} \RB {\VNm {\V {x}_1} +\VNm {\V {x}_2}} \NR
 %
-\NC \leq \NC \RB {1 +\d _{s}} \D \R{2} \VNm {\V {x}_1 +\V {x}_2} \NR
+\NC \leq \NC \RB {1 +\d _{s'}} \D \R{2} \VNm {\V {x}_1 +\V {x}_2} \NR
 }
@@
 \Disp {
-\NC \d_{2s}
-\leq \NC \R {2} \d_{s} \NR
+\NC \d_{2s'}
+\leq \NC \R {2} \d_{s'} \NR
 }
@@
 {
-If \m {\M {Q}'} has \m {\d}-RIP, then, for \m {M=1,2,3,\dots} so that \m {\d _{Ms}} is meaningful,
+If \m {\M {Q}'} has \m {\d_{s'}}-RIP, then, for \m {M=1,2,3,\dots} so that \m {\d _{Ms'}} is meaningful,
 %
 \DispNum {d-s-Md'-d's} {
-\NC \d_{Ms}
-\leq \NC \R {M} \d_{s} \NR
+\NC \d_{Ms'}
+\leq \NC \R {M} \d_{s'} \NR
 }
@@
 %
-Thus we have, in view of \Rf {d-2-11-C1},
+In particular,
+%
+\DispNum {d'-S-Ll-d's} {
+\NC \d_{S}
+\leq \NC \R {L} \RB {\log N_H} ^{1/4} \d_{s} \NR
+}
+%
+So \Rf {d-2-11-C1} becomes
+%
 \Result
@@
 \NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
-\leq \NC \F {1} {1-\R{2} \d_{S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2
+\leq \NC \F {1} {1-\R{2} \d_{S}} \VNm {P _{\SB {\MC {AB}}}^\Tr P d} _2
 +\F {\R{3} \d_{S}} {\RB {1-\R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\MC {C}}}} _1 \NR
@@
 }
-%
-
 \stopsubsection
@@
 %
-\DispNum {d'-S;18,18;} {
+\DispNum {d'-S-18-18} {
 \NC \d_S
@@
 \NC \VNm {\V {d}} _2
-\leq \NC 4 \R {2L} \log N_H \NR
+%
+\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
+}
+%
+holds for probability \m {p}, with
+%
+\DispNum {1-p-ON-13} {
+\NC 1 -p
+=\NC \MC {O} \SB {N_H ^{-1/3}} \NR
 }
 }
-%
 
-We start to prove \Rf {d-2-42-NH}.
+To prove \Rf {d-2-42-NH}, we simplify the expression for \m {\VNm {\V {d} _{\SB{\MC {AB}}}} _2} in \Rf {d-2-11-C1} and the one for \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1} in \Rf {d-1-dA-C1} and 
+In this section we substitute rough numbers.
+
 By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P-d-4N-Nh},
@@
 \DispNum {P-2-PP-NH} {
-\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
+\NC \VNm {\M {P} _{\SB {\MC {AB}}}^\Tr \M {P} \V {d}} _2
 \leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
@@
 %
-\NC \leq \NC 4 \R {2 \log N_H} \NR
+\NC \leq \NC 5.65 \R {\log N_H} \NR
 }
@@
 %
-\NC \leq \NC 4 \R {2 \log N_H}
-+\F {1} {\R{L \log N_H}} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
-}
-%
-Next, we want to use \Rf {d-1-dA-C1} to eliminate \m {\VNm {d _{\SB{\MC {A}}}} _1}.
-%
-\DispNum {8,2,nn-hh;} {
-\NC \leq \NC 4 \R {2 \log N_H}
-+\F {1} {\R{L \log N_H}} \RB {\VNm {\V {d} _{\SB{\MC {A}}}} _1 +2\VNm {\V {g} _{\SB{\MC {C}}}} _1} \NR
+\NC \leq \NC 1.21 L \R {\log N_H}^3
++0.262 \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
 }
@@
 %
-\DispNum {d-A;8,2;} {
+\DispNum {d-A1-16-H2} {
 \NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
-\leq \NC 4 \R {2 \log N_H}
-+2\VNm {\V {g} _{\SB{\MC {C}}}} _1 \NR
 %
-\NC \leq \NC \RB {16 \R {2} +\F {4} {\pi^2} \R {1 -\F {2} {\pi}}} \log N_H \NR
+\leq \NC 1.64 L \R {\log N_H}^3 +0.951 L \RB {\log N_H}^2 \NR
 }
 %
-We are now in a position to bound \m {\VNm {d} _2^2}.
-Using \Rf {d-2-dA-12} again, we have
+Then, substituting \Rf {g-C-4p'-NH} and \Rf {d-A1-16-H2} above into \Rf {d-1-dA-C1}, we get
+\DispNum {d-C1-16-H2} {
+\NC \VNm {\V {d} _{\SB{\MC {C}}}} _1
 %
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC 32 S \log N_H
-+8 \d_{3S} \R {2 \log N_H} 
-+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
+\leq \NC 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 \NR
 }
 %
-Finally, plug in the bound for \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1}.
-Again for simplicity, we keep only the first order small terms.
+And \Rf {d-2-11-C1} becomes
 %
-\Disp {
-\NC \VNm {\V {d}} _2^2
-\leq \NC 32 S \log N_H
-+\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
-+\F {\pi} {9} \F {L} {s^2 N_H} \NR
+\DispNum {d-2-16-H3} {
+\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
+%
+\leq \NC 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 \NR
+}
+We are now in a position to bound \m {\VNm {d} _2}, just by using \Rf {d-2-dA-C1} again, and plugging in \Rf {d-2-16-H3} and \Rf {d-C1-16-H2} above.
+
+In addition, we shall discuss the four events of failure, namely
+\DispNum {q-q-2q-ar} {
+\NC q
+\eqsim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
+}
+subscript respectively for restricted isometry, noise, sparsity, respectively.
+Quoting previous results \Rf {1-p-1N-H3}, \Rf {P-d-eN-d4}, \Rf {1-p-ex-d's}, and \Rf {1-p-NH-H2}, we make some approximation and set
+\DispNum {q-B-2e-Lp'} {
+\NC q _{\Rm {iso}, B}
+\lesssim \NC 2 \Ss {e} ^{-N_B /12} \NR
+%
+\NC q _{\Rm {iso}, R}
+\lesssim \NC 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
+%
+\NC q _{\Rm {no}}
+\lesssim \NC N_H ^{-2} \NR
+%
+\NC q _{\Rm {sp}}
+\lesssim \NC 2 \Ss {e} ^{-9L/\pi} \NR
 }
 %
-Set \m {\d_S =1} for the worst situation, and we get the desired bound.
-
-In addition to the bound, we shall discuss the four sources of error, namely
-\DispNum {q-q-2q-ar} {
-\NC q
-\simeq \NC 2 \RB {q _{\Rm {isom}, B} + q _{\Rm {isom}, R}} +q _{\Rm {nois}} +q _{\Rm {spar}} \NR
-}
-subscript for restricted isometry, noise, sparsity, respectively.
-
-Quoting previous results, they are
-\Disp {
-q
-\simeq \Ss {e} ^{N_B \d}
+If we provide the design values
+\DispNum {N-B-4l-H2} {
+\NC N_B
+\gtrsim \NC 4 \log N_H \NR
+%
+\NC N_R
+\gtrsim \NC 16 L \RB {\log N_H}^2 \NR
 }
 %
-Provided the design values
-\Disp {
-\NC N_R
-\leftarrow \NC \RB {\log N_H} ^{3/2} \NR
+It can be seen that
+\DispNum {q-p-qn-oR} {
+\NC q _{\Rm {sp}}
+\lesssim \NC q _{\Rm {no}} \NR
 %
-\NC N_B
-\leftarrow \NC \log \log N_H \NR
+\NC \lesssim \NC q _{\Rm {iso}, B} \NR
+%
+\NC \eqsim \NC q _{\Rm {iso}, R} \NR
 }
 %
-And we get the estimation
-\Disp {
+then we get the estimation
+\DispNum {q-q-ON-13} {
 \NC q
-=\NC \MC {O} \SB {\F {1} {\RB {\log N_H}^3}} \NR
+\eqsim \NC q _{\Rm {iso}, R} \NR
+%
+\NC \eqsim \NC q _{\Rm {iso}, B} \NR
+%
+\NC \eqsim \NC 2 N_H ^{-1/3} \NR
 }
 %
+
+%gC1 {g-C-4p'-NH}
+%dC1 {d-1-dA-C1}
+%PPd-infty {P-d-4N-Nh}
+%d2 {d-2-dA-C1}
+%dAB2 {d-2-11-C1}
+
 \stopsubsection

### 2019-11-05 paper/1_introduction.tex
Update Presentation

@@
 
-It turns out that not only is the channel hard to estimate due to so many antennae, but the transmission is prone to noise corruption, 
+It turns out that not only is the channel hard to estimate due to a large number of antennae, but the transmission is prone to noise corruption.
 In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
@@
 
-Now, consider a linear transformation of real vectors with noise corruption,
+Now, consider a linear transformation of real vectors added of noise,
 %
@@
 where, for example, \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
-How can we hope to estimate \m {\V {x}} when, in addition to insufficient observations, there are too few observations?
+How can we hope to estimate \m {\V {x}} when, in addition to insufficient measurements, there is also noise corruption?
 

### 2019-11-05 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Update Presentation

@@
 %
-And our task is to bound the expectation \m {\MB {E} \SB {\V {d}}}.
+And our task is to bound the error norm \m {\VNm {\V {d}} _2}, where \m {\V {d} =\V {g} -\Hat {\V {g}}}.
 
@@
 We are going to combine previous lemmata and show the main result.
-For simplicity, set
+For simplicity, set \m {S = Ls^2}, thus
+%
+\DispNum {S-S-4N-NH} {
+\NC S
+=\NC L \log N_H \NR
+}
+%
+And
 %
@@
 \leq \NC \F {1} {8} \NR
-}
-%
-Thus
-\DispNum {S-S-4N-NH} {
-\NC S
-=\NC L \log N_H \NR
 }
@@
 subscript respectively for restricted isometry, noise, sparsity, respectively.
-Quoting previous results \Rf {1-p-1N-H3}, \Rf {P-d-eN-d4}, \Rf {1-p-ex-d's}, and \Rf {1-p-NH-H2}, we make some approximation and set
+Quoting previous results \Rf {1-p-2e-s4}, \Rf {P-d-eN-d4}, \Rf {1-p-ex-d's}, and \Rf {1-p-NH-H2}, we make some approximation and set
 \DispNum {q-B-2e-Lp'} {
@@
 \NC q
-\eqsim \NC q _{\Rm {iso}, R} \NR
-%
-\NC \eqsim \NC q _{\Rm {iso}, B} \NR
-%
-\NC \eqsim \NC 2 N_H ^{-1/3} \NR
+\eqsim \NC 2 N_H ^{-1/3} \NR
 }

### 2019-11-05 paper/4_simulation.tex
Finish 3.3
Update Presentation

@@
 
-We are ready to verify theoretical bound of DS by numerical experiments.
+We are ready to verify bound of eror norm of DS by numerical experiments.
 DS is a convex optimization program, and there are many library devoted on that.
@@
 = \NC \MC {R} \SB {\V {y}}
-\in \MB {R} ^{2N_y} \NR
+\in \MB {R} ^{2 N_Y^2} \NR
 %
@@
 = \NC \MC {R} \SB {\V {g}}
-\in \MB {R} ^{2N_h} \NR
+\in \MB {R} ^{2 N_H^2} \NR
 %
@@
 = \NC \MC {R} \SB {\M {P}}
-\in \MB {R} ^{2N_y \D 2N_h} \NR
+\in \MB {R} ^{2 N_Y^2 \D 2 N_H^2} \NR
 %
@@
 = \NC \MC {R} \SB {\M {P} ^\Adj}
-\in \MB {R} ^{2N_y \D 2N_h} \NR
+\in \MB {R} ^{2 N_Y^2 \D 2 N_H^2} \NR
 %
@@
 = \NC \MC {R} \SB {\V {z}}
-\in \MB {R} ^{2N_y} \NR
+\in \MB {R} ^{2 N_Y^2} \NR
 }
@@
 \NC {\V {u}}_{n_h}
-\in \NC \MB {R} ^{N_h} \NR
+\in \NC \MB {R} ^{N_H^2} \NR
 \NC \RB {\V {u}_{n_h}} _{\SB {n_h'}}
@@
 \stopcases \NR
-\NC \T {\M {U}}_{n_h} \in \NC \MB {R} ^{2N_h \D 2N_h} \NR
+\NC \T {\M {U}}_{n_h} \in \NC \MB {R} ^{2 N_H^2 \D 2 N_H^2} \NR
 \NC \RB {\T {\M {U}}_{n_h}} _{\SB {n_h', n_h''}}
@@
 \NC n_h, n_h', n_h'' 
-= \NC 0, 1, 2, \ldots, N_h -1 \NR
+= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
 }
@@
 \DispNum {m---RN-h1} {
-\NC \V {m} \in \NC \MB {R} ^{N_h} \NR
+\NC \V {m} \in \NC \MB {R} ^{N_H^2} \NR
 \NC \V {m} \DB{n_h}
@@
 \NC n_h 
-= \NC 0, 1, 2, \ldots, N_h-1 \NR
+= \NC 0, 1, 2, \ldots, N_H^2-1 \NR
 }
@@
 \stopTheMatrix
-\in \MB {R} ^{3N_h} \NR
+\in \MB {R} ^{3 N_H^2} \NR
 %
@@
 \stopTheMatrix
-\in \MB {R} ^{3N_h} \NR
+\in \MB {R} ^{3 N_H^2} \NR
 }
@@
 \stopTheMatrix
-\in \MB {R} ^{2N_h \D 3N_h} \NR
+\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
 %
@@
 = \NC \V {0}
-\in \MB {R} ^{2N_h} \NR
+\in \MB {R} ^{2 N_H^2} \NR
 %
@@
 \NC i 
-= \NC 0, 1, 2, \ldots, N_h -1 \NR
+= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
 }
@@
 = \NC \startTheMatrix
-\NC -\T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
+\NC -\T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
 \stopTheMatrix
-\in \MB {R} ^{2N_h \D 3N_h} \NR
+\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
 %
 \NC \V {b}_i
-=\NC \T {\M {U}}_{i -N_h} \T {\M {P}}^\Adj \T {\V {y}}
-\in \MB {R} ^{2N_h} \NR
+=\NC \T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\V {y}}
+\in \MB {R} ^{2 N_H^2} \NR
 %
@@
 = \NC \V {0}
-\in \MB {R} ^{3N_h} \NR
+\in \MB {R} ^{3 N_H^2} \NR
 %
@@
 \NC i 
-= \NC N_h, N_h +1, N_h +2, \ldots, 2N_h -1 \NR
+= \NC N_H^2, N_H^2 +1, N_H^2 +2, \ldots, 2 N_H^2 -1 \NR
 }
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {C} ^{N_y \D N_h}}, \m{\V {y} \in \MB {C} ^{N_y}}, \m {\g_{\Rm {DS}} > 0}.
+\item Input \m{\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
 \item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
@@
 \LA \NC \startcases
-\NC \Min {\V {x}' \in \MB {C} ^{N_h}}
+\NC \Min {\V {x}' \in \MB {C} ^{N_H^2}}
 \MC \IP {\V {t}, \V {x}'} \NR
@@
 \NC \MC i 
-=0, 1, 2, \ldots, 2N_h -1 \NR
+=0, 1, 2, \ldots, 2 N_H^2 -1 \NR
 \stopcases \NR
@@
 \NC \Hat{\T{\V {g}}}
-\LA \NC \Hat{\V {x}} _{\SB {0 : 2N_h-1}} \NR
+\LA \NC \Hat{\V {x}} _{\SB {0 : 2 N_H^2-1}} \NR
 }
@@
 We do three series of experiments, which are of size from small to large.
-In three experiments, we take respectively \m {L} to be \m {2, 3, 4}, \m {N_Y} to be \m {5, 7, 9}, \m {N_R} to be \m {10, 14, 18}, and \m {N_H} to be \m {20, 28, 36}.
+In the following experiments, we take respectively \m {N_H} to be \m {16, 32, 48}, \m {N_Y} to be \m {\log N_H} (giving \m {3, 3, 4}), \m {N_R} to be \m {\RB {\log N_H}^2} (giving \m {8, 12, 15}).
 
 Other parameters are fixed in these experiments; 
-The number of grid of quantization of analog precoder is 16
-The wavelength of the EM wave that antenna is emitting, \m {\l _{\Rm{ant}} = 1}, is set to be 0.1.
+The number of grid of quantization of analog precoder is \m {16}.
+The number of paths \m {L} is \m {4}.
+The wavelength of the EM wave that antenna is emitting, \m {\l _{\Rm{ant}} = 1}, is set to be \m {0.1}.
 and the antenna spacing \m {d _{\Rm{ant}} =3}.
@@
 
-Each data point is repeated for 32 times, and taken average.
+Each data point is repeated for 16 times, and taken average.
 We plot the absolute log error
 %
-\DispNum {e'-s-lo-vg} {
-\NC \e_{\Rm{abs}}
+\DispNum {h'-s-lo-vg} {
+\NC \h_{\Rm{abs}}
 =\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}, \NR
@@
 %
-\DispNum {e'-l-lo-vg} {
-\NC \e_{\Rm{rel}}
-=\NC \F {\RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}}
+\DispNum {h'-l-lo-vg} {
+\NC \h_{\Rm{rel}}
+=\NC \F {\h_{\Ss{abs}}}
 {\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
@@
 %
-The averaged error values are plotted along with the theoretical expected error of DS, derived in chap.\ 3, namely
+The averaged error values are plotted along with the bound of error norm.
+Taking log of \Rf {d-2-42-NH} we have
 %
-\DispNum {e'-h-52-NH} {
-\NC \e_{\Rm{th}}
-=\NC \F{5}{2} + \log \RB{L N_H} + \log \log N_H \NR
+\Disp {
+\NC \log \SB {7.85 \R {L} \RB {\log N_H}^3}
+\lesssim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2.06 \NR
+}
+Thus we draw
+\DispNum {h'-h-12-H2} {
+\NC \h_{\Rm{th}}
+\eqsim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2 \NR
 }
@@
 
-\startsubsection [title={Plots}]
+\startsubsection [title={Plots for \m {N_H=32}}]
+
+\blank [big]
+\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
+
+\blank [big]
+\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
+
+\blank [big]
+\externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
+
+\stopsubsection
+
+\startsubsection [title={Plots for \m {N_H=48}}]
+
+\blank [big]
+\externalfigure [big-assorted-abs.png] [wfactor=fit, hfactor=fit]
+
+\blank [big]
+\externalfigure [big-assorted-rel.png] [wfactor=fit, hfactor=fit]
+
+\blank [big]
+\externalfigure [big-assorted-time.png] [wfactor=fit, hfactor=fit]
 
@@
 
-Lastly, the theoretical bound for expected error of DS is much looser than the actual perfomance, and is well above the Least Square line, making it the highest line of all.
+Lastly, the bound for error norm of DS is much looser than the actual perfomance, and is well above the Least Square line, making it the highest line of all.
 Our bound is correct but not tight enough.

### 2019-11-05 presentation-B/1_introduction.tex
Update Presentation

\blank [big, force]

\Title {\TitleText}
\Subtitle {III. Numerical Experiments}
\blank [big]

\Subtitle {\AuthorText}
\blank [big]

\Subsubtitle {\DateText}

\page [yes]
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Organization}
{
\I Introduction

\I Problem Setting and Proposed Method

\I Bounding the Error Norm

\I Numerical Experiments

\I Conclusion and Key References
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Background}
{
\I \Emph {Multiple-input multiple-output} (MIMO) communication system has been proposed to be incorporated into the 5G specification.
However, its hardware overhead increases complexity and power consumption.

\I The design of new algorithms that addressed these issues requires the expression of channel to be known.

\I Estimation of MIMO channels results in high complexity, due to the large number of antennae.

\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit \Emph {sparse} properties, and what if we exploit the sparsity to save for some measurements?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Compressive Sensing}
{
\I The situation that the number of model parameters is much larger than the number of measurements has been addressed by \Emph {compressed sensing} (CS) theory

\I A CS problem involves inverting a wide, rectangular matrix.
Indeed, with insufficient (even noisy) measurements, this does not make sense.

\I But it turns out that, when the signal is sparse, few measurements may be sufficient for the reconstruction.
And \Emph {Dantzig Selector} (DS), proposed by Cand\`es and Tao (2006) in the advent, is a possible solution.
}

### 2019-11-05 presentation-B/3_proof.tex
Update Presentation

\Frame {The Need of a Modified Proof}
{
\I \Emph {Q1}: DS is shown to work for \Emph {sparse} vectors, but is \m {\M {H}} really sparse?

\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?

\I \Emph{Q3}: Candès and Tao established the case for real matrices, but does \Emph {complex} case apply?

\I \Emph{Q4}: Candès and Tao showed the Big-\m {\MC {O}} of error norm depends on (in our case) \m {N_H}, but does the algorithm work successfully for \Emph {high probability}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Proof Strategy}
{
\I \m {\M {H}} is not sparse, but \m {\M {K}^\Adj \M {H} \M {K}} is.
Remove the largest-magnitude \m {S} components of \m {\V{g}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, so that it remains to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}}}.

\I Establish that \m {\M{W}_R} and \m {\M{W}_R} satisfies RIP, thus \m {\M{P}} satisfies RIP too, for high probability.

\I We then establish a modified bound of error norm based on Candès and Tao.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Restricted Isometry Property}
{
\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.

\I We say that \m {\M{P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {g}}^2
\leq \NC \VNm {\M{P} \V {g}} _2^2
\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
}

\I Verbally, \m {\M{P}} is \Emph {almost unitary} up to relative error \m {\d_s}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Suppose for concreteness,
\Disp {
\NC s
=\NC \R {\log N_H},
\Q S
= L s^2,
\Q \d_S
\leq \F {1} {8} \NR
}

\I We may show that 
\Disp {
\NC \VNm {\M {g} _{\SB{\MC {C}}}} _1
\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
}

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of \Emph {Central Limit Theorem}, for unit vector \m {\V {u}}
\Disp {
\NC \MB {E} \SB {\VNm {\M {P} \V {u}} _2 ^k}
\approx \NC 1
\Q \Ss {in\; distribution} \NR
}

\I Unfortunately, they are \Emph {not i.i.d.}, and that need closer scrutiny.

\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant

\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Effective Beamformers}
{
\I Is it true that if \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has?

\I Indeed, if so, \m {\M {P}} has approximately \m {2\d_s}-RIP, if there is no sparsity constraint:
\Disp {
\NC \VNm {P} _2
=\NC \VNm {\M {F}_B^\Tr \M {F}_B^\Tr} \VNm {\M {W}_B \M {W}_R} \NR
}

\I I argue that this is true for sparse \m {\V {g}}.
In fact, if \m {\M {G} =\M {U} \Rm {diag} \SB {\V {d}} \M {U} ^\Adj}, for some \m {S}-sparse \m {\V {d}} and unitary \m {\M {U}}.

\Disp {
\NC \NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} \M {U}
   \R {\Rm {abs} \SB {\V {d}}} \D
   \R {\Rm {abs} \SB {\V {d}}}
   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} \NR
%
\NC \eqsim \NC \VNm {\M {K} \M {H} \M {K} ^\Adj} _2 \RB {1 +2\d_s} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Digital Beamformers}
{
\I For \m {0 <\d_s <1}, unit vector \m {\V {u}}, \m {\M {W}_B} (resp.\ \m {\M {F} _B ^\Adj}) satisfies
%
\Disp {
\NC \Nm {\VNm {\M {W} _B \V {u}}^2 - 1}
\geq \NC \d_s \NR
}

\I holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \Ss {e} ^{-N_B \R {\d_s} /4} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {RIP of Analog Beamformers}
{
\I Suppose
%
\Disp {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
}
%
\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP...

\I for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Error Norm of Dantzig Selector}
{
\I In answer of \Emph {Q3}, it can be checked that the generalization to complex vectors only introduces the bound of a multiple \m {\R {2}}.

\I then the following bound holds for high probability:
\Disp {
\NC \VNm {\V {d}} _2
%
\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
}

}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Big-\m {O} of Success Probability (1/2)}
{
\I Denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
\Disp {
\NC q
\eqsim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
}

\I Then previous discussions
\Disp {
\NC q _{\Rm {iso}, B}
\lesssim \NC 2 \Ss {e} ^{-N_B /12} \NR
%
\NC q _{\Rm {iso}, R}
\lesssim \NC 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
%
\NC q _{\Rm {no}}
\lesssim \NC N_H ^{-2} \NR
%
\NC q _{\Rm {sp}}
\lesssim \NC 2 \Ss {e} ^{-9L/\pi} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Big-\m {O} of Success Probability (2/2)}
{
\I If we provide the design values
\Disp {
\NC N_B
\gtrsim \NC 4 \log N_H \NR
%
\NC N_R
\gtrsim \NC 16 L \RB {\log N_H}^2 \NR
}

\I It follows that
\Disp {
\NC q _{\Rm {sp}}
\lesssim \NC q _{\Rm {no}}
\lesssim q _{\Rm {iso}, B}
\eqsim q _{\Rm {iso}, R}
}

\I Then we get the estimation
\Disp {
\NC q
\eqsim 2 N_H ^{-1/3} \NR
}
}

### 2019-11-05 presentation-B/4_simulation.tex
Update Presentation

\Frame {Real Valued Representation}
{
\I To solve the convex optimization, we use Python package CVXPY.

\I Since it doesn't allow complex variables, we represent complex number by real part and imarinary parts.

\I For vectors, substitute
\Disp {
\NC a +b \Ss{i}
\leftrightarrow \NC \startTheMatrix
\NC a \NR
\NC b \NR
\stopTheMatrix \NR
}

\I For matrices, substitute
\Disp {
\NC a +b \Ss{i}
\leftrightarrow \NC \startTheMatrix
\NC a, \NC -b \NR
\NC b, \NC a \NR
\stopTheMatrix \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Algorithm Cast as SOCP (1/3)}
{
\I Given are \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_Y^2}}, \m{\g > 0}.
Let \m {\T {\V {y}}} be the real representation of \m {\V {y}}, and \m {\T {\M {P}}} that of \m {\M {P}}.

\I Define the indicator vectors and matrices as
\Disp {
\NC {\V {u}}_{n_h} \SB {n_h'}
= \NC \startcases
1, \Q \MC n_h' =n_h \NR
0, \Q \NC \Rm {otherwise} \NR
\stopcases \NR
%
\NC {\T {\M {U}}}_{n_h} \SB {n_h', n_h''}
= \NC \startcases
1, \Q \MC n_h' =2n_h,\; n_h'' =2n_h \NR
1, \Q \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
0, \Q \NC \Rm {otherwise} \NR
\stopcases \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Algorithm Cast as SOCP (2/3)}
{
\I To fit the form of SOCP, we just have to define \m {\V {t}, \M {A}_i, \V {b}_i, \V {c}_i, d_i}, for \m {i = 0, 1, \ldots, N_H^2 -1},
\Disp{
\NC \V {t}
= \NC \startTheMatrix
\NC \V {0} \NR
\NC \V {1} \NR
\stopTheMatrix,
\Q \M {A}_i
= \startTheMatrix
\NC \T {\M {U}}_{i}, \NC \M {0} \NR
\stopTheMatrix \NR
%
\NC \V {b}_i
=\NC \V {0},
\Q \V {c}_i
= \startTheMatrix
\NC \V {0} \NR
\NC \V {u}_{i} \NR
\stopTheMatrix,
\Q d_i
= 0 \NR
}

\I Similarly, for \m {i = N_H^2, N_H^2 +1, \ldots, 2N_H^2 -1},
\Disp{
\NC \M {A}_i
= \NC \startTheMatrix
\NC -\T {\M {U}}_{i -N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
\stopTheMatrix, \NR
%
\NC \V {b}_i
=\NC \T {\M {U}}_{i -N_H^2} \T {\M {P}}^\Adj \T {\V {y}},
\Q \V {c}_i
= \V {0},
\Q d_i
= \g \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Algorithm Cast as SOCP (3/3)}
{
\I Now, run the Second Order Cone Programming:
\Disp{
\NC \Hat {\V {x}}
\LA \NC \startcases
\NC \Min {\V {x}'}
\MC \IP {\V {t}, \V {x}'} \NR
\NC \Rm {subject} \; \Rm {to}
\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
\NC \MC i 
=0, 1, \ldots, 2N_H^2 -1 \NR
\stopcases \NR
}
\I Extract channel response as real vector:
\Disp {
\NC \Hat{\V {g}}
\LA \NC \MC{R} ^{-1} \SB {\Hat{\V {x}} \DB {0 : 2N_H^2-1}} \NR
}
\I Convert back from Angular domain and output:
\Disp {
\NC \Hat {\M {H}}
\LA \NC \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I Bound of log of error norm:
\Disp {
\NC \h_{\Ss{th}}
\eqsim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2 \NR
}
\I Log absolute / relative error:
\Disp {
\NC \h_{\Ss{abs}}
=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}} \NR
%
\NC \h_{\Ss{rel}}
=\NC \F {\h_{\Ss{abs}}}
{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Simulation Parameters}
{
\I Antennae number of channel \m {N_H = 16, 32, 48}
\I Antennae number of analog stage \m {N_R = \RB {\log N_H}^2}
\I Antennae number of digital stage \m {N_Y = \log N_H}
\I Analog beamformer quantization grid: \m {16}
\I Number of paths \m {L =4}
\I How many noise standard deviation tried: \m {12}
\I Number of repetition of each data point: \m {16}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Absolute Error, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Relative Error, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=32}}
{
\blank [big]
\externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Absolute Error, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Relative Error, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=48}}
{
\blank [big]
\externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{

\I \m {\eta _{\Ss {th}}} is in correct order of magnitude but not tight when \m {\s \gg 1}

\I The smaller the noise std., the smaller the error

\I It is \It {not} true that the smaller \m {\g _{\Ss {DS}}}, the smaller the error

\I We have reasonable results, but exceedingly high complexity

\I Have to do more experiments to smooth out the lines

\I The requirement \m {N_R \gtrsim 16 L \RB {\log N_H}^2} is demanding
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %

### 2019-11-05 presentation-B/5_conclusion.tex
Update Presentation

\Frame {Conclusion}
{
\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity, and studied Dantzig Selector (DS).

\I We modified DS for present setting: for the almost-sparse condition, for the angular domain, for the beamformer matrix \m {\M {P}} in our setting, and for complex vectors.

\I We bound the expected square error and , in explicit expression of system parameters such as \m {N_H}, \m {N_Y}, and \m{L}, and discussed with the big \m {\MC{O}} of the successful probability
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Future Work}
{
\I Investigate the reason of high complexity and reduce it

\I Run for bigger values of \m {N_H}, \m {N_Y}, and \m{L} if possible

\I Maybe try the real case and use existent code for DS

\I More literature review on OMP and other methods
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References}
{
{\tfx
\I E. Candès and J. Romberg, \It {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved from \Tt {www.acm.caltech.edu/l1magic/downloads/l1magic.pdf}, 2005.

\I E. Candès and T. Tao, ``The Dantzig Selector: Statistical estimation when \m {p} is much larger than \m {n}'', The annals of Statistics 35(6), 2313–2351, 2007.

\I M.P. Friedlander and M.A. Saunders, ``Discussion: the Dantzig Selector'', The Annals of Statistics 35(6), 2385–2391, 2007.

\I B. Klartag and E. Milman, \It {Geometric Aspects of Functional Analysis}, Springer, 2017.

\I B. Laurent and P. Massart, ``Adaptive estimation of a quadratic functional by model selection'', Annals of Statistics, 1302–1338, 2000.
}
}

### 2019-11-06 presentation-B/4_simulation.tex
Fix presentation typos

@@
 \I To solve the convex optimization, we use Python package CVXPY.
-
-\I Since it doesn't allow complex variables, we represent complex number by real part and imarinary parts.
+To save complexity, we represent a complex number by its real- and imarinary-parts.
 
@@
 {
-\I Given are \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_Y^2}}, \m{\g > 0}.
-Let \m {\T {\V {y}}} be the real representation of \m {\V {y}}, and \m {\T {\M {P}}} that of \m {\M {P}}.
+\I Given are \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_Y^2}}, \m{\g _{\Ss {DS}} > 0}.
+Let \m {\T {\V {y}}} and \m {\T {\M {P}}} respectively be their real representation.
 
@@
 \Q d_i
-= \g \NR
+= \g _{\Ss {DS}} \NR
 }
@@
 \stopcases \NR
-}
-\I Extract channel response as real vector:
-\Disp {
+%
 \NC \Hat{\V {g}}
-\LA \NC \MC{R} ^{-1} \SB {\Hat{\V {x}} \DB {0 : 2N_H^2-1}} \NR
-}
-\I Convert back from Angular domain and output:
-\Disp {
+\LA \NC \MC{R} ^{-1} \SB {\Hat{\V {x}} _{\SB {0 : 2N_H^2-1}}} \NR
+%
 \NC \Hat {\M {H}}

### 2019-11-06 presentation-B/5_conclusion.tex
Fix presentation typos

@@
 {
-\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity, and studied Dantzig Selector (DS).
+\I We propose a feasible method to estimate MIMO mm-Wave channel \m {\M {H}} by exploiting its sparsity, and employing Dantzig Selector (DS).
 
-\I We modified DS for present setting: for the almost-sparse condition, for the angular domain, for the beamformer matrix \m {\M {P}} in our setting, and for complex vectors.
+\I We modified DS for present setting, for the almost-sparse condition in the angular domain, with respect to the effective beamformer \m {\M {P}} in our setting, and concerning complex vectors.
 
-\I We bound the expected square error and , in explicit expression of system parameters such as \m {N_H}, \m {N_Y}, and \m{L}, and discussed with the big \m {\MC{O}} of the successful probability
+\I We bound the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the big \m {\MC{O}} of the successful probability
 }
@@
 {
-\I Investigate the reason of high complexity and reduce it
+\I Investigate the reason of high complexity and reduce it.
 
-\I Run for bigger values of \m {N_H}, \m {N_Y}, and \m{L} if possible
+\I Run for bigger values of \m {N_H}, \m {N_Y}, and \m{L} if possible.
 
-\I Maybe try the real case and use existent code for DS
+\I Maybe try the real case and use existent code for DS.
 
-\I More literature review on OMP and other methods
+\I More literature review on other methods.
 }

### 2020-02-27 paper/1_introduction.tex
Number eqns with `:` instead of `-`

@@
 %
-\DispNum {N-p-Nm-Nm} {
+\DispNum {N:p:Nm:Nm} {
 \NC N_p \gg \NC N_m \NR
@@
 To start, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}.
-For \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}}, denote
+For \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}}, denote
 %
 \Disp {
-\NC \V {x}  _{\SB {\MC {A}}}
-=\NC \sum _{i \in \MC {A}} \V {v} \V {u} _{i} \NR
+\NC \V {x}  _{\SB {\MS {A}}}
+=\NC \sum _{i \in \MS {A}} \V {v} \V {u} _{i} \NR
 %
-\NC \M {Q}  _{\SB {\MC {A}}}
-=\NC \sum _{i \in \MC {A}} \M {Q} _{\SB {:,i}} \NR
+\NC \M {Q}  _{\SB {\MS {A}}}
+=\NC \sum _{i \in \MS {A}} \M {Q} _{\SB {:,i}} \NR
 }
 %
-That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MC {A}}.
+That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MS {A}}.
 
@@
 {
-\m {\V {x}} is called \m {s}-sparse, if there is some \m {\MC {A} \subseteq \CB {0, \dots, N_p-1}} such that
+\m {\V {x}} is called \m {s}-sparse, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
 %
-\DispNum {x-A-x--x-} {
-\NC \V {x} _{\SB {\MC {A}}}
+\DispNum {x:A:x::x:} {
+\NC \V {x} _{\SB {\MS {A}}}
 =\NC \V {x} \NR
@@
 %
-\DispNum {A-A-s--s-} { 
-\NC \Nm {\MC {A}} \leq \NC s. \NR
+\DispNum {A:A:s::s:} { 
+\NC \Nm {\MS {A}} \leq \NC s. \NR
 }
@@
 %
-\DispNum {1-2-Qx-22} {
+\DispNum {1:2:Qx:22} {
 \NC \RB {1-\d_s} \VNm {\V {x}} _2 ^2
@@
 %
-\DispNum {y-y-Qx-xz} {
+\DispNum {y:y:Qx:xz} {
 \NC \V {y}
@@
 %
-\DispNum {h-h-mi-yg'} {
+\DispNum {h:h:mi:yg'} {
 \NC \Hat {\V {h}}
@@
 
-Still consider \Rf {y-y-Qx-xz}.
+Still consider \Rf {y:y:Qx:xz}.
 We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.
@@
 %
-\DispNum {c-c-i0-ir} {
+\DispNum {c:c:i0:ir} {
 \NC c
@@
 %
-\DispNum {Q-Q-QS-Qy} {
+\DispNum {Q:Q:QS:Qy} {
 \NC \M {Q} ^\ddagger
@@
 %
-\DispNum {r-2-h'-h'} {
+\DispNum {r:2:h':h'} {
 \NC \VNm {\V {r}} _2
@@
 %
-\DispNum {g-g-Qy-Qy} {
+\DispNum {g:g:Qy:Qy} {
 \NC \Hat {\V {g}}

### 2020-02-27 paper/3_1_almost_sparsity.tex
Finish 3.3
Number eqns with `:` instead of `-`

@@
 Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity index \m {s} be given.
-Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MC {A}}}}, the largest \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MC {A}}}} the next \m {s} largest components of \m {\V {g}}, and \m {\V {g} _{\SB{\MC {C}}}} are the components complement to \m {\V {g} _{\SB{\MC {A}}}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MC {A}}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\SB{\MC {B}}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\SB{\MC {A}}} =\IP {-1,0,-4,2,0}}.
-In this section, the subscripts \m {\MC {A}, \MC {B}, \MC {C}} will keep bearing analogous meaning.
+Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MS {A}}}}, the largest \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MS {A}}}} the next \m {s} largest components of \m {\V {g}}, and \m {\V {g} _{\SB{\MS {C}}}} are the components complement to \m {\V {g} _{\SB{\MS {A}}}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MS {A}}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\SB{\MS {B}}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\SB{\MS {A}}} =\IP {-1,0,-4,2,0}}.
+In this section, the subscripts \m {\MS {A}, \MS {B}, \MS {C}} will keep bearing analogous meaning.
 
-We hope that \m {\VNm {\V {g} _{\SB{\MC {C}}}} _1} is small.
+We hope that \m {\VNm {\V {g} _{\SB{\MS {C}}}} _1} is small.
 If so, we shall substitute the quantity into the expected square error of DS, thus generalizing the original argument.
 Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and \m {\M {G}} is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
-We define, similarly, \m {\V {a} _{\SB{\MC {A}}}} and \m {\V {a} _{\SB{\MC {C}}}}, with sparsity \m {s}.
+We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity \m {s}.
 If \m {N_H} is large, we may forget for a moment the requirement that \m {s =1,2,3,\dots}.
@@
 \Disp {
-\NC \VNm {\V {a} \SB {\f} _{\SB{\MC {C}}}} _2 ^2
-=\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB{\MC {C}}}} _2 ^2 \NR
+\NC \VNm {\V {a} \SB {\f} _{\SB{\MS {C}}}} _2 ^2
+=\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB{\MS {C}}}} _2 ^2 \NR
 }
@@
 %
-\DispNum {y'-H-f'M-p'p'} {
+\DispNum {y':H:f'M:p'p'} {
 \NC \psi \SB {\f, n_H}
 :=\NC \RB {
-   \RB {
-      \RB {\f \; \Rm {Mod}\; \F {2\pi} {N_H}}
-      +\F {2 \pi n_H} {N_H}
-      +\pi
+   \f \; \Rm {Mod}\; \F {2\pi} {N_H}
+   + \RB {\F {2 n_H} {N_H} + 1} \pi
 } \;
 \Rm {Mod}\; \RB {2\pi}
-}
--\pi \NR
+- \pi \NR
 }
@@
 %
-\DispNum {y'-H-p'--p'-} {
+\DispNum {y':H:p'::p':} {
 \NC \Nm {\psi \SB {\f, n_H}}
@@
 %
-\DispNum {D-y'-nH-Hy'} {
+\DispNum {D:y':nH:Hy'} {
 \NC D \SB {\psi'}
@@
 %
-\DispNum {b-f'-Ka-af'} {
+\DispNum {b:f':Ka:af'} {
 \NC b \SB {\f}
@@
 %
-\DispNum {K-H-1N-nH} {
+\DispNum {K:H:1N:nH} {
 \NC \RB {\V {b} \SB {\f}} _{\SB {n_H}}
@@
 
-Now, by the nature of alternating series, for \m {-\pi \leq x < \pi}, it holds that
+Now, by the nature of alternating series, for \m {- \pi \leq x < \pi}, it holds that
 %
@@
 %
-\DispNum {D-y'-si-y'p'} {
+\DispNum {D:y':si:y'p'} {
 \NC \Nm {D \SB {\psi'}}
@@
 %
-\NC -\pi \leq \NC \psi' < \pi. \NR
+\NC - \pi \leq \NC \psi' < \pi. \NR
 }
 %
-Combining \Rf {y'-H-f'M-p'p'}, \Rf {K-H-1N-nH}, and \Rf {D-y'-si-y'p'} we have
+Combining \Rf {y':H:f'M:p'p'}, \Rf {K:H:1N:nH}, and \Rf {D:y':si:y'p'} we have
 %
 \Disp {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _1
+\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
 =\NC \F {1} {N_H}
@@
       \V {u} _{n_H'}
-} _{\SB{\MC {C}}}
+} _{\SB{\MS {C}}}
 } _1
@@
 \Disp {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _1
+\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
 \leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
@@
 %
-\NC =\NC \F {1} {\pi} \log \F {N_H^2 /s^2 -\pi^2 /24} {1 -\pi^2 /24} \NR
+\NC =\NC \F {1} {\pi} \log \F {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \NR
 %
-\NC \simeq \NC \F {1} {\pi} \RB {\log N_H -\log s} \NR
+\NC \eqsim \NC \F {2} {\pi} \RB {\log N_H - \log s} \NR
+%
+\NC \leq \NC \F {2} {\pi} \log N_H \NR
 }
@@
 %
-\DispNum {s-s-lo-NH} {
+\DispNum {s:s:lo:NH} {
 \NC s
@@
 %
-\DispNum {a-2-4N-NH} {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\MC {C}}}} _2
+\DispNum {a:2:4N:NH} {
+\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _2
 \leq \NC \F {2} {\pi} \log N_H \NR
@@
 
-If that we set
-\DispNum {S-S-Ls-s2} {
+If we set that
+\DispNum {S:S:Ls:s2} {
 \NC S
@@
 \Disp {
-\NC \VNm {\V {g} _{\SB{\MC {C}}}} _1
+\NC \VNm {\V {g} _{\SB{\MS {C}}}} _1
 \leq \NC
 \sum _{l=0} ^{L-1} \Nm {\a_l}
-\VNm {\\V {b} \SB {\f_l} _{\SB{\MC {C}}}} _2
-\VNm {\\V {b} \SB {\th_l} _{\SB{\MC {C}}}} _2 \NR
+\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _2
+\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _2 \NR
 %
 \NC \leq \NC
-\VNm {\V {b} \SB {\f_l} _{\SB{\MC {C}}}} _2
-\VNm {\V {b} \SB {\th_l} _{\SB{\MC {C}}}} _2
+\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _2
+\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _2
 \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
@@
 %
-\DispNum {P-p'-2e-3p'} {
+\DispNum {P:p':2e:3p'} {
 \NC \MB {P} \SB {
@@
 }
-\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
+\leq \NC 2 \exp \SB {- \F {9L} {\pi}} \NR
 }
 %
-Now we have \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1 /\RB {\log N_H}^2 \leq 12 \R{2} /\pi ^{5/2} \leq 4/3}.
+Now we have \m {\VNm {\M {g} _{\SB{\MS {C}}}} _1 /\RB {\log N_H}^2 \leq 12 \R{2} /\pi ^{5/2} \leq 4/3}.
 %
@@
 {
-Let \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in \Rf {g-g-ve-Nh}.
+et \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in \Rf {g:g:ve:Nh}.
 Then the bound
 %
-\DispNum {g-C-4p'-NH} {
-\NC \VNm {\M {g} _{\SB{\MC {C}}}} _1
+\DispNum {g:C:4p':NH} {
+\NC \VNm {\M {g} _{\SB{\MS {C}}}} _1
 \leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
@@
 %
-\DispNum {1-p-1N-H3} {
+\DispNum {1:p:1N:H3} {
 \NC 1 -p
-\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
+\leq \NC 2 \exp \SB {- \F {9L} {\pi}} \NR
 }

### 2020-02-27 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Number eqns with `:` instead of `-`

@@
 %
-\DispNum {d-d-gg-gg} {
+\DispNum {d:d:gg:gg} {
 \NC \V {d} 
-= \NC \Hat {\V {g}} -\V {g} \NR
+= \NC \Hat {\V {g}} - \V {g} \NR
 }
 %
-And our task is to bound the error norm \m {\VNm {\V {d}} _2}, where \m {\V {d} =\V {g} -\Hat {\V {g}}}.
+And our task is to bound the error norm \m {\VNm {\V {d}} _2}, where \m {\V {d} =\V {g} - \Hat {\V {g}}}.
 
@@
 %
-\DispNum {g'-g'-2N-Nh} {
+\DispNum {g':g':2N:Nh} {
 \NC \g
@@
 %
-\DispNum {d-1-dA-C1} {
-\NC \VNm {\V {d} _{\SB{\MC {C}}}} _1
-\leq \NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
-+2\VNm {\V {g} _{\SB{\MC {C}}}} _1 \NR
+\DispNum {d:1:dA:C1} {
+\NC \VNm {\V {d} _{\SB{\MS {C}}}} _1
+\leq \NC \VNm {\V {d} _{\SB{\MS {A}}}} _1
++2\VNm {\V {g} _{\SB{\MS {C}}}} _1 \NR
 }
@@
 %
-To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}}, while recalling that \m {\V {g} =\V {g} _{\SB{\MC {A}}}},
+To show this, observe that with triangle inequality applied respectively on \m {\MS {A}} and \m {\MS {C}}, while recalling that \m {\V {g} =\V {g} _{\SB{\MS {A}}}},
 %
@@
 \NC \VNm {\V {g}} _1
--\VNm {\V {d} _{\SB{\MC {A}}}} _1
-+\VNm {\V {d} _{\SB{\MC {C}}}} _1
--\VNm {\V {g} _{\SB{\MC {C}}}} _1
-\leq \NC \VNm {\V {g} +\V {d}} _1 \NR
+- \VNm {\V {d} _{\SB{\MS {A}}}} _1
++ \VNm {\V {d} _{\SB{\MS {C}}}} _1
+- \VNm {\V {g} _{\SB{\MS {C}}}} _1
+\leq \NC \VNm {\V {g} + \V {d}} _1 \NR
 %
@@
 %
-\DispNum {E-h-2N-Nh} {
+\DispNum {E:h:2N:Nh} {
 \NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}}
@@
 %
-\DispNum {Q-x-12-22} {
+\DispNum {Q:x:12:22} {
 \NC Q\SB {x'}
@@
 %
-\DispNum {Q-h-1N-Nh} {
+\DispNum {Q:h:1N:Nh} {
 \NC Q\SB {\R {4 \log N_H}}
@@
 %
-\DispNum {P-d-4N-Nh} {
+\DispNum {P:d:4N:Nh} {
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
@@
 %
-\DispNum {1-p-NH-H2} {
+\DispNum {1:p:NH:H2} {
 \NC 1 -p
@@
 %
-\DispNum {z-y-Pg-ny} {
-\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_y}}}
-= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} _{\SB {:,n_y}}} \NR
+\DispNum {z:y:Pg:ny} {
+\NC \IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_y}}}
+= \NC \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_y}}} \NR
 %
@@
 %
-\DispNum {P-g-Py-Nh} {
-\NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
-\leq \NC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty \NR
+\DispNum {P:g:Py:Nh} {
+\NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
+\leq \NC \VNm {\M {P}^\Adj \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \NR
 %
@@
 %
-By triangle inequality, together with \Rf {Q-h-1N-Nh}, we obtain the desired result.
+By triangle inequality, together with \Rf {Q:h:1N:Nh}, we obtain the desired result.
 %
-\DispNum {P-d-zP-Nh} {
+\DispNum {P:d:zP:Nh} {
 \NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \M {P} \V {d}} _\infty
 \leq \NC \VNm {\IP {\V {z}, \M {P} _{\SB {:,n_y}}}} _\infty
-+\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_y}}} \NR
++ \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_y}}} \NR
 %
@@
 %
-\DispNum {d-2-dA-12} {
+\DispNum {d:2:dA:12} {
 \NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\SB {\MC {AB}}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1^2 \NR
+\leq \NC \VNm {\V {d} _{\SB {\MS {AB}}}} _2^2 + \F {1} {S} \VNm {\V {d} _{\SB{\MS {C}}}} _1^2 \NR
 }
 %
-By power mean inequality, we get a statement cruder than \Rf {d-2-dA-12} that
+By power mean inequality, we get a statement cruder than \Rf {d:2:dA:12} that
 %
@@
 %
-\DispNum {d-2-dA-C1} {
+\DispNum {d:2:dA:C1} {
 \NC \VNm {\V {d}} _2
-\leq \NC \VNm {\V {d} _{\SB {\MC {AB}}}} _2 +\F {1} {\R {S}} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
+\leq \NC \VNm {\V {d} _{\SB {\MS {AB}}}} _2 + \F {1} {\R {S}} \VNm {\V {d} _{\SB{\MS {C}}}} _1 \NR
 }
@@
 %
-\DispNum {d-2-11-C1} {
-\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
-\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\SB {\MC {AB}}}^\Tr P d} _2
-+\F {\T {\d}_{S, 2S}} {\RB {1-\d_{2S}} \R {S}} \VNm {d_{\SB{\MC {C}}}} _1 \NR
+\DispNum {d:2:11:C1} {
+\NC \VNm {\V {d} _{\SB{\MS {AB}}}} _2
+\leq \NC \F {1} {1- \d_{2S}} \VNm {P _{\SB {\MS {AB}}}^\Tr P d} _2
++ \F {\T {\d}_{S, 2S}} {\RB {1- \d_{2S}} \R {S}} \VNm {d_{\SB{\MS {C}}}} _1 \NR
 }
@@
 Here we use a result in \cite [Can05] that relates \m {\T {\d} _{s_1, s_2}} to \m {\d_s}, that is
-\DispNum {d-2-ds-s2} {
+\DispNum {d:2:ds:s2} {
 \NC \T {\d} _{s_1, s_2}
@@
 By triangle inequality, by power-mean inequality,
-\DispNum {Q-x-Qx-x2} {
+\DispNum {Q:x:Qx:x2} {
 \NC \VNm {Q' \RB {\V {x}_1 + \V {x}_2}}
@@
 \leq \NC \VNm {Q' \V {x}_1}
-+\VNm {Q' \V {x}_2} \NR
++ \VNm {Q' \V {x}_2} \NR
 %
-\NC \leq \NC \RB {1 +\d _{s'}} \RB {\VNm {\V {x}_1} +\VNm {\V {x}_2}} \NR
+\NC \leq \NC \RB {1 + \d _{s'}} \RB {\VNm {\V {x}_1} + \VNm {\V {x}_2}} \NR
 %
-\NC \leq \NC \RB {1 +\d _{s'}} \D \R{2} \VNm {\V {x}_1 +\V {x}_2} \NR
+\NC \leq \NC \RB {1 + \d _{s'}} \D \R{2} \VNm {\V {x}_1 + \V {x}_2} \NR
 }
@@
 %
-\DispNum {d-s-Md'-d's} {
+\DispNum {d:s:Md':d's} {
 \NC \d_{Ms'}
@@
 %
-\DispNum {d'-S-Ll-d's} {
+\DispNum {d':S:Ll:d's} {
 \NC \d_{S}
@@
 %
-So \Rf {d-2-11-C1} becomes
+So \Rf {d:2:11:C1} becomes
 %
@@
 %
-\DispNum {d-2-11-C1} {
-\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
-\leq \NC \F {1} {1-\R{2} \d_{S}} \VNm {P _{\SB {\MC {AB}}}^\Tr P d} _2
-+\F {\R{3} \d_{S}} {\RB {1-\R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\MC {C}}}} _1 \NR
+\DispNum {d:2:11:C1} {
+\NC \VNm {\V {d} _{\SB{\MS {AB}}}} _2
+\leq \NC \F {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\MS {AB}}}^\Tr P d} _2
++ \F {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\MS {C}}}} _1 \NR
 }
@@
 %
-\DispNum {S-S-4N-NH} {
+\DispNum {S:S:4N:NH} {
 \NC S
@@
 %
-\DispNum {d'-S-18-18} {
+\DispNum {d':S:18:18} {
 \NC \d_S
@@
 %
-\DispNum {d-2-42-NH} {
+\DispNum {d:2:OL:H3} {
 \NC \VNm {\V {d}} _2
-%
-\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
+\leq \NC \MS {O} \RB {\R {L} \R {\log N_H}^3} \NR
 }
@@
 %
-\DispNum {1-p-ON-13} {
+\DispNum {1:p:ON:13} {
 \NC 1 -p
-=\NC \MC {O} \SB {N_H ^{-1/3}} \NR
+=\NC \MS {O} \SB {N_H ^{-1/3}} \NR
 }
 }
-
-To prove \Rf {d-2-42-NH}, we simplify the expression for \m {\VNm {\V {d} _{\SB{\MC {AB}}}} _2} in \Rf {d-2-11-C1} and the one for \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1} in \Rf {d-1-dA-C1} and 
+To prove this, we simplify the expression for \m {\VNm {\V {d} _{\SB{\MS {AB}}}} _2} in \Rf {d:2:11:C1} and the one for \m {\VNm {\V {d} _{\SB{\MS {C}}}} _1} in \Rf {d:1:dA:C1} and 
 In this section we substitute rough numbers.
 
-By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P-d-4N-Nh},
+By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P:d:4N:Nh},
 %
-\DispNum {P-2-PP-NH} {
-\NC \VNm {\M {P} _{\SB {\MC {AB}}}^\Tr \M {P} \V {d}} _2
+\DispNum {P:2:PP:NH} {
+\NC \VNm {\M {P} _{\SB {\MS {AB}}}^\Tr \M {P} \V {d}} _2
 \leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
@@
 %
-By \m {\ell_p}-norm inequality, by the definition of truncation, by \Rf {d-2-11-C1}, and by \Rf {P-2-PP-NH} just above,
+By \m {\ell_p}-norm inequality, by the definition of truncation, by \Rf {d:2:11:C1}, and by \Rf {P:2:PP:NH} just above,
 %
 \Disp {
-\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
-\leq \NC \R {S} \VNm {\V {d} _{\SB{\MC {A}}}} _2 \NR
+\NC \VNm {\V {d} _{\SB{\MS {A}}}} _1
+\leq \NC \R {S} \VNm {\V {d} _{\SB{\MS {A}}}} _2 \NR
 %
-\NC \leq \NC \R {S} \VNm {\V {d} _{\SB{\MC {AB}}}} _2 \NR
+\NC \leq \NC \R {S} \VNm {\V {d} _{\SB{\MS {AB}}}} _2 \NR
 %
 \NC \leq \NC 1.21 L \R {\log N_H}^3
-+0.262 \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
++0.262 \VNm {\V {d} _{\SB{\MS {C}}}} _1 \NR
 }
 %
-And \Rf {a-2-4N-NH} gives, after arrangement,
+And \Rf {a:2:4N:NH} gives, after arrangement,
 %
-\DispNum {d-A1-16-H2} {
-\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
+\DispNum {d:A1:16:H2} {
+\NC \VNm {\V {d} _{\SB{\MS {A}}}} _1
 %
@@
 %
-Then, substituting \Rf {g-C-4p'-NH} and \Rf {d-A1-16-H2} above into \Rf {d-1-dA-C1}, we get
-\DispNum {d-C1-16-H2} {
-\NC \VNm {\V {d} _{\SB{\MC {C}}}} _1
+Then, substituting \Rf {g:C:4p':NH} and \Rf {d:A1:16:H2} above into \Rf {d:1:dA:C1}, we get
+\DispNum {d:C1:16:H2} {
+\NC \VNm {\V {d} _{\SB{\MS {C}}}} _1
 %
@@
 %
-And \Rf {d-2-11-C1} becomes
+And \Rf {d:2:11:C1} becomes
 %
-\DispNum {d-2-16-H3} {
-\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
+\DispNum {d:2:16:H3} {
+\NC \VNm {\V {d} _{\SB{\MS {AB}}}} _2
 %
@@
 }
-We are now in a position to bound \m {\VNm {d} _2}, just by using \Rf {d-2-dA-C1} again, and plugging in \Rf {d-2-16-H3} and \Rf {d-C1-16-H2} above.
+We are now in a position to bound \m {\VNm {d} _2}, just by using \Rf {d:2:dA:C1} again, and plugging in \Rf {d:2:16:H3} and \Rf {d:C1:16:H2} above.
+This gives
+\DispNum {d:2:42:NH} {
+\NC \VNm {\V {d}} _2
+\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
+}
 
-In addition, we shall discuss the four events of failure, namely
-\DispNum {q-q-2q-ar} {
+Furthermore, we discuss the four events of failure, as follows.
+Consider failure probabilities \m {q _{\Rm {iso}, B}}, \m {q _{\Rm {iso}, R}}, \m {q _{\Rm {no}}}, \m {q _{\Rm {sp}}}, respectively for restricted isometry, noise, sparsity.
+If all of them are small, a naive application of union bound suggests
+\DispNum {q:q:2q:ar} {
 \NC q
@@
 }
-subscript respectively for restricted isometry, noise, sparsity, respectively.
-Quoting previous results \Rf {1-p-2e-s4}, \Rf {P-d-eN-d4}, \Rf {1-p-ex-d's}, and \Rf {1-p-NH-H2}, we make some approximation and set
-\DispNum {q-B-2e-Lp'} {
+Quoting previous results \Rf {1:p:2e:s4}, \Rf {1:p:ex:d's}, \Rf {1:p:ex:d's}, and \Rf {1:p:NH:H2}, we make some approximation and set
+\DispNum {q:B:2e:Lp'} {
 \NC q _{\Rm {iso}, B}
@@
 If we provide the design values
-\DispNum {N-B-4l-H2} {
+\DispNum {N:B:4l:H2} {
 \NC N_B
@@
 It can be seen that
-\DispNum {q-p-qn-oR} {
+\DispNum {q:p:qn:oR} {
 \NC q _{\Rm {sp}}
@@
 then we get the estimation
-\DispNum {q-q-ON-13} {
+\DispNum {q:q:ON:13} {
 \NC q
@@
 }
-%
-
-%gC1 {g-C-4p'-NH}
-%dC1 {d-1-dA-C1}
-%PPd-infty {P-d-4N-Nh}
-%d2 {d-2-dA-C1}
-%dAB2 {d-2-11-C1}
 

### 2020-02-27 paper/4_simulation.tex
Number eqns with `:` instead of `-`

@@
 {
-For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MC {R} \SB {\V {x}}} of \m {\V {x}} to be
+For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
 %
-\DispNum {R-x-R2-M1} {
-\NC \MC {R} \SB {\V {x}}
+\DispNum {R:x:R2:M1} {
+\NC \MS {R} \SB {\V {x}}
 \in \NC \MB {R} ^{2M} \NR
-\NC \MC {R} \SB {\V {x}} _{\SB {m}}
+\NC \MS {R} \SB {\V {x}} _{\SB {m}}
 = \NC \startcases
@@
 %
-The injectivity is obvious, and we may define \m {\MC {R} ^{-1}} so that
+The injectivity is obvious, and we may define \m {\MS {R} ^{-1}} so that
 %
-\DispNum {R-1-x--x-} {
-\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V {x}}}
+\DispNum {R:1:x::x:} {
+\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
 =\NC \V {x} \NR
@@
 {
-For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MC {R} \SB {\M {A}}} of \m {\M {A}} to be
+For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
 %
-\DispNum {R-A-R2-21} {
-\NC \MC {R} \SB {\M {A}}
+\DispNum {R:A:R2:21} {
+\NC \MS {R} \SB {\M {A}}
 \in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
-\NC \MC {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
+\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
 \NC \startcases
-\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
-\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2') \NR
-\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2'+1) \NR
-\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2'+1) \NR
+\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
+\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
+\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
+\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
 \stopcases \NR
@@
 %
-\DispNum {y---Ry-Ny} {
+\DispNum {y:::Ry:Ny} {
 \NC \T {\V {y}}
-= \NC \MC {R} \SB {\V {y}}
+= \NC \MS {R} \SB {\V {y}}
 \in \MB {R} ^{2 N_Y^2} \NR
@@
 \NC \T {\V {g}}
-= \NC \MC {R} \SB {\V {g}}
+= \NC \MS {R} \SB {\V {g}}
 \in \MB {R} ^{2 N_H^2} \NR
@@
 \NC \T {\M {P}}
-= \NC \MC {R} \SB {\M {P}}
+= \NC \MS {R} \SB {\M {P}}
 \in \MB {R} ^{2 N_Y^2 \D 2 N_H^2} \NR
@@
 \NC \T {\M {P}} ^\Adj
-= \NC \MC {R} \SB {\M {P} ^\Adj}
+= \NC \MS {R} \SB {\M {P} ^\Adj}
 \in \MB {R} ^{2 N_Y^2 \D 2 N_H^2} \NR
@@
 \NC \T {\V {z}}
-= \NC \MC {R} \SB {\V {z}}
+= \NC \MS {R} \SB {\V {z}}
 \in \MB {R} ^{2 N_Y^2} \NR
@@
 %
-\DispNum {y---Pg-gz} {
+\DispNum {y:::Pg:gz} {
 \NC \V {\T {y}}
@@
 %
-\DispNum {u-h-RN-h1} {
+\DispNum {u:h:RN:h1} {
 \NC {\V {u}}_{n_h}
@@
 %
-And denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
-Now, if we introduce vector \m{\V {m}}
+And denote \m {\V {1}} to be the all-\m {1} vector for short, and \m {\V {0}} the all-\m {0} vector, whose dimension will be specified from context.
+Now, if we introduce vector \m {\V {m}}
 %
-\DispNum {m---RN-h1} {
+\DispNum {m:::RN:h1} {
 \NC \V {m} \in \NC \MB {R} ^{N_H^2} \NR
-\NC \V {m} \DB{n_h}
-= \NC \Nm{\V {g} \DB{n_h}} \NR
+\NC \V {m} \DB {n_h}
+= \NC \Nm {\V {g} \DB {n_h}} \NR
 \NC n_h, n_h', n_h'' 
@@
 %
-to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now takes the form
+to denote the entrywise complex modulus of \m {\V {g}}, we see that the convex optimization now takes the form
 %
-\DispNum {g---mi-h1} {
+\DispNum {g:::mi:h1} {
 \NC \Hat {\T {\V {g}}}
@@
 \NC \Min {\T {\V {g}}', \V {m}} \Q
-\MC \IP { \V {1}, \V {m} } \NR
+\MC \IP {\V {1}, \V {m}} \NR
 \NC \Rm {subject} \; \Rm {to} \Q
-\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
-\leq \IP { \V {u}_{n_h}, \V {m} } \NR
-\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
+\MC \VNm {\T {\M {U}}_{n_h} \T {\V {g}}'}_2
+\leq \IP {\V {u}_{n_h}, \V {m}} \NR
+\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB {\T {\M {P}} \T {\V {g}}' -\T {\V {y}}}}_2
 \leq \g_{\Rm {DS}} \NR
@@
 %
-\DispNum {t---01-Nh} {
+\DispNum {t:::01:Nh} {
 \NC \V {t}
@@
 %
-\DispNum {A-i-Ui-h1} {
+\DispNum {A:i:Ui:h1} {
 \NC \M {A}_i
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
-\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
+%
+\item Input \m {\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
+%
+\item Define \m {\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
+%
 \item Calculate
 %
-\DispNum {x---mi-h1} {
+\DispNum {x:::mi:h1} {
 \NC \Hat {\V {x}}
@@
 }
+%
 \item Extract
 %
-\DispNum {g---x0-h1} {
-\NC \Hat{\T{\V {g}}}
-\LA \NC \Hat{\V {x}} _{\SB {0 : 2 N_H^2-1}} \NR
+\DispNum {g:::x0:h1} {
+\NC \Hat {\T {\V {g}}}
+\LA \NC \Hat {\V {x}} _{\SB {0 : 2 N_H^2-1}} \NR
 }
+%
 \item Convert 
 %
-\DispNum {g---R1-1g} {
-\NC \Hat{\V {g}}
-\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
+\DispNum {g:::R1:1g} {
+\NC \Hat {\V {g}}
+\LA \NC \MS {R} ^{-1} \SB {\Hat {\T {\V {g}}}} \NR
 }
-\item Calculate
+%
+\item Find \m {\Hat {G}} by
 %
@@
 }
-\item Calculate
+%
+\item Find \m {\Hat {\M {H}}} by
 %
@@
 }
+%
 \item Output \m {\Hat {\M {H}}}.
+%
 \stopitemize
@@
 The number of paths \m {L} is \m {4}.
-The wavelength of the EM wave that antenna is emitting, \m {\l _{\Rm{ant}} = 1}, is set to be \m {0.1}.
-and the antenna spacing \m {d _{\Rm{ant}} =3}.
+The wavelength of the EM wave that antenna is emitting, \m {\l _{\Rm {ant}} = 1}, is set to be \m {0.1}.
+and the antenna spacing \m {d _{\Rm {ant}} =3}.
 Note that only their ratio matters.
@@
 %
-\DispNum {h'-s-lo-vg} {
-\NC \h_{\Rm{abs}}
-=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}, \NR
+\DispNum {h':s:lo:vg} {
+\NC \h_{\Rm {abs}}
+=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss {avg}}, \NR
 }
@@
 %
-\DispNum {h'-l-lo-vg} {
-\NC \h_{\Rm{rel}}
-=\NC \F {\h_{\Ss{abs}}}
-{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
+\DispNum {h':l:lo:vg} {
+\NC \h_{\Rm {rel}}
+=\NC \F {\h_{\Ss {abs}}}
+{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss {avg}}} \NR
 }
@@
 The averaged error values are plotted along with the bound of error norm.
-Taking log of \Rf {d-2-42-NH} we have
+As a basis for comparison, we approximate \Rf {d:2:42:NH} and take log, giving
 %
-\Disp {
-\NC \log \SB {7.85 \R {L} \RB {\log N_H}^3}
-\lesssim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2.06 \NR
-}
-Thus we draw
-\DispNum {h'-h-12-H2} {
-\NC \h_{\Rm{th}}
+\DispNum {h':h:12:H2} {
+\NC \h_{\Rm {th}}
 \eqsim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2 \NR
 }
+
+\startsubsection [title={Transformation by Diagonalization}]
+
+By Real Spectral Theorem, \m {\M {P} ^\Tr \M {P}} can be diagonized.
+Let
+\Disp {
+\NC \M {P} ^\Tr \M {P}
+= \NC \M {Q} \M {D} \M {Q} ^\Tr \NR
+}
+where
+\Disp {
+\NC \M {Q} ^\Tr \M {D} \M {Q}
+= \NC I \NR
+}
+It can be seen that only \m {2N_Y^2} of \m {2N_H^2} singular values are nonzero.
+Without loss of generality, suppose
+\Disp {
+\NC \MB {R} ^{2 N_H^2}
+= \NC \MS {U} \oplus \MS {V} \NR
+}
+with
+\Disp {
+\NC \Rm {dim} \; \MS {U}
+= \NC 2 N_Y^2 \NR
+\NC \Rm {dim} \; \MS {V}
+= \NC 2 N_H^2 -2 N_Y^2 \NR
+}
+such that
+\Disp {
+\NC \M {D}
+= \NC \startTheMatrix
+\NC \DU, \NC \M {0} \NR
+\NC \M {0}, \NC \M {0} \NR
+\stopTheMatrix \NR
+}
+
+Suppose
+\Disp {
+\NC \V {g}
+= \NC \gp - \gm \NR
+}
+with
+\Disp {
+\NC -\gp
+\preceq \NC 0 \NR
+\NC -\gm
+\preceq \NC 0 \NR
+}
+Introduce
+\Disp {
+\NC \fp
+= \NC \M {Q} ^\Tr \gp \NR
+\NC \fm
+= \NC \M {Q} ^\Tr \gm \NR
+}
+If we define
+\Disp {
+\NC \fp
+= \NC \fpU + \fpV \NR
+\NC \fm
+= \NC \fmU + \fmV \NR
+}
+That is, taking components of \m {\fp, \fm} respectively in \m {\MS {U}, \MS {V}}.
+Then we see that
+\Disp {
+\NC \fpU
+= \NC \QU ^\Tr \gp \NR
+\NC \fmU
+= \NC \QU ^\Tr \gm \NR
+\NC \fpV
+= \NC \QV ^\Tr \gp \NR
+\NC \fmV
+= \NC \QV ^\Tr \gm \NR
+}
+Here \m {\QU ^\Tr} is the abbreviation of \m {\RB {\QU} ^\Tr}.
+
+Notice that the constraint
+\Disp {
+\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}}
+\preceq \NC \g \V {1} \NR
+}
+can be written as
+\Disp {
+\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} - \g \V {1} + \sp
+= \NC \V {0} \NR
+\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} - \g \V {1} - \sm
+= \NC \V {0} \NR
+}
+with
+\Disp {
+\NC -\sp
+\preceq \NC 0 \NR
+\NC -\sm
+\preceq \NC 0 \NR
+}
+
+Now, define
+\Disp {
+\NC \kpU
+= \NC -\QU ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
+\NC \kmU
+= \NC -\QU ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
+\NC \kpV
+= \NC -\QV ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
+\NC \kmV
+= \NC -\QV ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
+}
+
+\stopsubsection
+
+\page [yes]
+
+\startsubsection [title={Plots for \m {N_H=16}}]
 
@@
 \blank [big]
-\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
+\externalfigure [medium-assorted-absolute.png] [wfactor=fit, hfactor=fit]
 
 \blank [big]
-\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
+\externalfigure [medium-assorted-relative.png] [wfactor=fit, hfactor=fit]
 
@@
 \externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\blank [big]
+\externalfigure [medium-ddss-absolute.png] [wfactor=fit, hfactor=fit]
+
+\blank [big]
+\externalfigure [medium-ddss-relative.png] [wfactor=fit, hfactor=fit]
+
+\blank [big]
+\externalfigure [medium-ddss-time.png] [wfactor=fit, hfactor=fit]
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\blank [big]
+\externalfigure [medium-oommpp-absolute.png] [wfactor=fit, hfactor=fit]
+
+\blank [big]
+\externalfigure [medium-oommpp-relative.png] [wfactor=fit, hfactor=fit]
+
+\blank [big]
+\externalfigure [medium-oommpp-time.png] [wfactor=fit, hfactor=fit]
 
@@
 \blank [big]
-\externalfigure [big-assorted-abs.png] [wfactor=fit, hfactor=fit]
+\externalfigure [big-assorted-absolute.png] [wfactor=fit, hfactor=fit]
 
 \blank [big]
-\externalfigure [big-assorted-rel.png] [wfactor=fit, hfactor=fit]
+\externalfigure [big-assorted-relative.png] [wfactor=fit, hfactor=fit]
 
@@
 
-Reasonably, for all methods, a higher \m {\s} corresponds to higher \m {\eta_{\Rm{rel}}} and \m {\eta_{\Rm{rel}}}.
+Reasonably, for all methods, a higher \m {\s} corresponds to higher \m {\eta_{\Rm {rel}}} and \m {\eta_{\Rm {rel}}}.
 The trends of absolute and relative error are the same, and in the below we call them simply error.
@@
 For low SNR it is slightly but steadily outperforms OMP, and for high SNR the difference becomes vanishingly small and is sometimes surpassed by OMP.
-Different values of threshold \m {\g_{\Rm{DS}}} matter, and a smaller \m {\g_{\Rm{DS}}} does not necessarily give a lower error.
-It seems \m {\g_{\Rm{DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is intuitive.
+Different values of threshold \m {\g_{\Rm {DS}}} matter, and a smaller \m {\g_{\Rm {DS}}} does not necessarily give a lower error.
+It seems \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is intuitive.
 
@@
 %
-\DispNum {C-S-C0-1e'} {
-\NC C_{\Rm{DS}}
+\DispNum {C:S:C0:1e'} {
+\NC C_{\Rm {DS}}
 = \NC C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
@@
 %
-\DispNum {g-0-gL-Py} {
+\DispNum {g:0:gL:Py} {
 \NC \V {g}_0
@@
 %
-\DispNum {C-S-Og-g1} {
-\NC C_{\Rm{DS}}
-=\NC \MC {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} \NR
+\DispNum {C:S:Og:g1} {
+\NC C_{\Rm {DS}}
+=\NC \MS {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} \NR
 }
@@
 %
-\DispNum {g-;g-,-g;} {
+\DispNum {g:;g:,:g;} {
 \NC \V {g} ^\star
@@
 %
-\DispNum {P-P-IN-H2} {
+\DispNum {P:P:IN:H2} {
 \NC \M {P} ^\Adj \M {P}
@@
 \Disp {
-\NC C_{\Rm{DS}}
-=\NC \MC {O} \SB {
+\NC C_{\Rm {DS}}
+=\NC \MS {O} \SB {
    \VNm {\V {g} +\RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {z}
    -\V {g}} _1} \NR
-\NC =\NC \MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} \NR
+\NC =\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} \NR
 }
@@
 \Disp {
-\NC \MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
-= \NC \s \MC {O} \RB {1} \NR
+\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
+= \NC \s \MS {O} \RB {1} \NR
 }
@@
 %
-\DispNum {--;ON,2s;} {
-\NC C_{\Rm{DS}}
-=\NC \MC {O} \SB {N_{H}^2 \s} \NR
+\DispNum {::;ON,2s;} {
+\NC C_{\Rm {DS}}
+=\NC \MS {O} \SB {N_{H}^2 \s} \NR
 }
@@
 %
-\DispNum {C-O-ON-NY} {
-\NC C_{\Rm{OMP}}
-=\NC \MC {O} \SB {N_H^2 \log N_Y} \NR
+\DispNum {C:O:ON:NY} {
+\NC C_{\Rm {OMP}}
+=\NC \MS {O} \SB {N_H^2 \log N_Y} \NR
 }
 %
-And it would appear that this is greater than \m {C_{\Rm{DS}}}.
+And it would appear that this is greater than \m {C_{\Rm {DS}}}.
 However, \m {\log N_Y} is really small in our experiments.
-and we dropped some constants, too, in analyzing \m {C_{\Rm{DS}}}.
-If we drop \m {\log N_Y}, then we get \m {\MC {O} \SB {N_H^2}} again.
+and we dropped some constants, too, in analyzing \m {C_{\Rm {DS}}}.
+If we drop \m {\log N_Y}, then we get \m {\MS {O} \SB {N_H^2}} again.
 
@@
 %
-\DispNum {C-P-CD-H2} {
-\NC C_{\Rm{OMP}}
-\approx \NC C_{\Rm{DS}} \NR
-\NC \approx \NC \s \MC {O} \SB {N_H^2} \NR
+\DispNum {C:P:CD:H2} {
+\NC C_{\Rm {OMP}}
+\approx \NC C_{\Rm {DS}} \NR
+\NC \approx \NC \s \MS {O} \SB {N_H^2} \NR
 }
@@
 
-Since LS involves the same target function as DS, the same argument also gives \m {C_{\Rm{Lasso}} =\MC {O} \SB {N_H^2}}.
+Since LS involves the same target function as DS, the same argument also gives \m {C_{\Rm {Lasso}} =\MS {O} \SB {N_H^2}}.
 The numerical 

### 2020-02-27 paper/notation.tex
Number eqns with `:` instead of `-`

@@
 \NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
-\NC \m {\RB {x+1} \RB {x+2}} \VL round parentheses \VL used only for precedence \AR \HL
-\NC \m {f \SB {x}} \VL square brackets \VL used only for arguments or parameter \AR \HL
-\NC \m {\CB {2, 3, 5, 7}} \VL curly braces \VL used only for sets \AR \HL
+\NC \m {\RB {1+3} \RB {2+4}} \VL round parentheses \VL used for precedence \AR \HL
+\NC \m {f \SB {x}} \VL square brackets \VL used for arguments or parameter \AR \HL
+\NC \m {\CB {2, 3, 5, 7}} \VL curly braces \VL used for sets \AR \HL
 \NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
@@
 \NC \m {\M {A}} \VL matrix \VL \AR \HL
-\NC \m {\V {1}} \VL all-1 vector \VL dimension will be clear from context \AR \HL
-\NC \m {\V {0}} \VL all-0 vector \VL dimension will be clear from context \AR \HL
+\NC \m {\V {1}} \VL all-1 vector \VL dimension will be specified \AR \HL
+\NC \m {\V {0}} \VL all-0 vector \VL dimension will be specified \AR \HL
 \NC \m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL

### 2020-02-27 presentation/2_setting.tex
Number eqns with `:` instead of `-`

\Frame {Channel Model}
{
\I Consider the uniform linear array
\Disp {
\NC \V {a} \SB {\psi'}
= \NC \F {1}{\R {N_H}} \sum_{n=0}^{N-1} \Ss {e}^{n \psi' \Ss {i}} \V {u}_n
\in \MB {C} ^{N_H} \NR
}

\I Consider the channel representation
\Disp {
\NC \M{H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB {\f_l'}
\V {a} \SB {\th_l'}^\Adj
\in \MB {C} ^{N_H \D N_H} \NR
}

\I where \m {L} is the number of paths, \m {\f_l'} is related to the angles of arrival, \m {\th_l'} is related to the angles of arrival.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Precoders and Combiners}
{
\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_Y}}

\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}

\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}

\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_Y \D N_R}}

\I With the unity magnitude constraint
\Disp {
\NC \Nm {\M {F}_R \SB {n_H, n_R}}
= \NC 1,
\Q \Nm {\M {W}_R \SB {n_R, n_H}}
= 1, \NR
}

\I Under the assumption
\Disp {
\NC N_H \gg \NC N_R \gg N_Y \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Effective Channel}
{
\I Consider Complex Standard Normal \m {\M{Z} \in \NC \MB {C} ^{N_H \D N_H}}

\I Introduce the effective channel
\Disp {
\NC \M{Y}
:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
}

\I Summarizing the dimension,
\Disp {
\NC \MB {C}^{N_Y}
\underset {\M{F}_B} {\mapsto} \NC \MB {C}^{N_R}
\underset {\M{F}_R} {\mapsto} \MB {C}^{N_H}
\underset {\M{H}} {\mapsto} \MB {C}^{N_H}
\underset {\M{W}_R} {\mapsto} \MB {C}^{N_R}
\underset {\M{W}_B} {\mapsto} \MB {C}^{N_Y} \NR
}

\I How do we \Emph {recover} \m {\M {H}} with knowledge of \m {\M {Y}}?

\I How do we \Emph {design} \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Transform to the Angular Domain}
{
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {Z}} \NR
}

\I Then we have a \Emph {linear equation}
\Disp {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Proposed Method}
{
\I Input \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{N_H^2}}, \m{\g_{\Ss {DS}} \geq 0}.

\I Calculate
\Disp {
\NC \Hat {\V {g}}
\LA \NC \startcases
\NC \Min {\V {g}'}  \MC \VNm {\V {g}'} _1 \NR
\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\Ss {DS}} \NR
\stopcases \NR
}

\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}

### 2020-02-27 presentation/3_proof.tex
Number eqns with `:` instead of `-`

--- 2019-11-05 presentation-B/3_proof.tex
@@
 \I \m {\M {H}} is not sparse, but \m {\M {K}^\Adj \M {H} \M {K}} is.
-Remove the largest-magnitude \m {S} components of \m {\V{g}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, so that it remains to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}}}.
+Remove the largest-magnitude \m {S} components of \m {\V{g}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, so that it remains to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.
 
-\I Establish that \m {\M{W}_R} and \m {\M{W}_R} satisfies RIP, thus \m {\M{P}} satisfies RIP too, for high probability.
+\I Establish that all four beamformers satisfy RIP, thus \m {\M{P}} satisfies RIP too, for high probability.
 
@@
 \Disp {
-\NC \RB {1-\d_s} \VNm {\V {g}}^2
+\NC \RB {1-\d_s} \VNm {\V {g}} _2^2
 \leq \NC \VNm {\M{P} \V {g}} _2^2
@@
 \NC \VNm {P} _2
-=\NC \VNm {\M {F}_B^\Tr \M {F}_B^\Tr} \VNm {\M {W}_B \M {W}_R} \NR
+=\NC \VNm {\M {F}_B^\Tr \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \NR
 }
@@
 \I I argue that this is true for sparse \m {\V {g}}.
-In fact, if \m {\M {G} =\M {U} \Rm {diag} \SB {\V {d}} \M {U} ^\Adj}, for some \m {S}-sparse \m {\V {d}} and unitary \m {\M {U}}.
+In fact, if \m {\M {K} ^\Adj \M {H} \M {K} =\M {U} \Rm {diag} \SB {\V {d}} \M {U} ^\Adj}, for some \m {S}-sparse \m {\V {d}} and unitary \m {\M {U}}, then
 
 \Disp {
-\NC \NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
-%
-\NC =\NC \VNm {
+\NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2
+=\NC \VNm {
    \M {W} _B \M {W} _R \M {K} \M {U}
@@
    \R {\Rm {abs} \SB {\V {d}}}
-   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} \NR
+   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
 %
-\NC \eqsim \NC \VNm {\M {K} \M {H} \M {K} ^\Adj} _2 \RB {1 +2\d_s} \NR
+\NC \eqsim \NC \VNm {\M {H}} _2 \RB {1 +2\d_s} \NR
 }
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {RIP of Digital Beamformers}
+\Frame {Isometry of Digital Beamformers}
 {
@@
 \Disp {
-\NC \Nm {\VNm {\M {W} _B \V {u}}^2 - 1}
+\NC \Nm {\VNm {\M {W} _B \V {u}} _2^2 - 1}
 \geq \NC \d_s \NR
@@
 
-\I then the following bound holds for high probability:
+\I then the following bound holds for high probability \m {p}:
 \Disp {
@@
 
+\I and we may bound failure probability \m {1-p}...
 }

### 2020-02-27 paper/4_simulation.tex
Deprecated: Diagonalization of DS as LP

@@
 However, the situation is more cubersome than that, since they deal with real vectors, but we consider the complex ones.
-Fortunately, they have briefly pointed out, complex DS can be recast as an second-order cone program (SOCP), and SOCP is one of the several standard convex programming problems for which there are already numerous efficient algorithms.
+Fortunately, they have briefly pointed out, complex DS can be recast as an linear program (LP),
+one of the basic convex programming problems for which there are already numerous efficient algorithms.
+Moreover, we show that this LP can be recast to another form with the total dimension of variables reduced.
 
-Before describing the recast, for ease of treatment we would like to represent complex vector and matrices by real, extended vectors and matrices.
+Before that, we again introduce some notation.
+We want to represent complex vector and matrices by real vectors and matrices, as follows.
 \Result
@@
 
-\startsection [title={Second Order Cone Programming}]
+\startsubsection [title={Transformation into Linear Program}]
 
-We shall see furthermore that the program can be cast into an SOCP.
-To make the point clearer, we rewrite the program just above into an extended block matrix form, by defining auxiliary variables as follows,
-%
-\DispNum {t:::01:Nh} {
-\NC \V {t}
+Next, we define some auxiliary variables, and prepare to rewrite Program ().
+The first idea is that \m {\V {g}} can be split into positive and negative parts, making the \m {\ell}-1 norm target function into a inner product, and this already makes Algorithm () a LP, just as noted by Tao [].
+The second idea is that, by Real Spectral Theorem, \m {\M {P} ^\Tr \M {P}} can be diagonized, and with suitable choice of variables, we may greatly reduce the overhead due to Newton step.
+This has not been remarked on the literature as far as we know.
+
+As pointed out above, let
+\Disp {
+\NC \M {P} ^\Tr \M {P}
+= \NC \M {Q} \M {D} \M {Q} ^\Tr \NR
+}
+where
+\Disp {
+\NC \M {Q} ^\Tr \M {Q}
+= \NC I \NR
+}
+It can be seen that only \m {2N_Y^2} of \m {2N_H^2} singular values are nonzero.
+Without loss of generality, suppose
+\Disp {
+\NC \MB {R} ^{2 N_H^2}
+= \NC \MS {U} \oplus \MS {V} \NR
+}
+with
+\Disp {
+\NC \Rm {dim} \; \MS {U}
+= \NC 2 N_Y^2 \NR
+\NC \Rm {dim} \; \MS {V}
+= \NC 2 N_H^2 -2 N_Y^2 \NR
+}
+such that
+\Disp {
+\NC \M {D}
 = \NC \startTheMatrix
-\NC \V {0} \NR
-\NC \V {1} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-%
-\NC \V {x}'
-= \NC \startTheMatrix
-\NC \T {\V {g}}' \NR
-\NC \V {m} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-}
-%
-with
-%
-\DispNum {A:i:Ui:h1} {
-\NC \M {A}_i
-= \NC \startTheMatrix
-\NC \T {\M {U}}_{i}, \NC \M {0} \NR
-\stopTheMatrix
-\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
-%
-\NC \V {b}_i
-= \NC \V {0}
-\in \MB {R} ^{2 N_H^2} \NR
-%
-\NC \V {c}_i
-= \NC \startTheMatrix
-\NC \V {0} \NR
-\NC \V {u}_{i} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-%
-\NC d_i
-= \NC 0 \NR
-%
-\NC i 
-= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
+\NC \DU, \NC \M {0} \NR
+\NC \M {0}, \NC \M {0} \NR
+\stopTheMatrix \NR
 }
 
-And
+Suppose
+\Disp {
+\NC \V {g}
+= \NC \gp - \gm \NR
+}
+with
+\Disp {
+\NC -\gp
+\preceq \NC 0 \NR
+\NC -\gm
+\preceq \NC 0 \NR
+}
+Introduce
+\Disp {
+\NC \fp
+= \NC \M {Q} ^\Tr \gp \NR
+\NC \fm
+= \NC \M {Q} ^\Tr \gm \NR
+}
+If we define
+\Disp {
+\NC \fp
+= \NC \fpU + \fpV \NR
+\NC \fm
+= \NC \fmU + \fmV \NR
+}
+That is, taking components of \m {\fp, \fm} respectively in \m {\MS {U}, \MS {V}}.
+Note that
+\Disp {
+\NC \fpU
+= \NC \QU ^\Tr \gp \NR
+\NC \fmU
+= \NC \QU ^\Tr \gm \NR
+\NC \fpV
+= \NC \QV ^\Tr \gp \NR
+\NC \fmV
+= \NC \QV ^\Tr \gm \NR
+}
+Here \m {\QU ^\Tr} is the abbreviation of \m {\RB {\QU} ^\Tr}.
+
+Notice that the constraint
+\Disp {
+\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}}
+\preceq \NC \g \V {1} \NR
+}
+can be written as
+\Disp {
+\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} - \g \V {1} + \tp
+= \NC \V {0} \NR
+\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} + \g \V {1} - \tm
+= \NC \V {0} \NR
+}
+for some \m {\tp, \tm} with
+\Disp {
+\NC -\tp
+\preceq \NC 0 \NR
+\NC -\tm
+\preceq \NC 0 \NR
+}
+
+Now, define
+\Disp {
+\NC \kp
+= \NC \M {Q} ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
+\NC \km
+= \NC \M {Q} ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
+}
+and that, similarly,
+\Disp {
+\NC \kp
+=\NC \kpU + \kpV \NR
+\NC \km
+=\NC \kmU + \kmV \NR
+}
+Again, allow us write it out for clarity that
+\Disp {
+\NC \kpU
+= \NC \QU ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
 %
-\DispNum {A:i:Ui:h1} {
-\NC \M {A}_i
-= \NC \startTheMatrix
-\NC -\T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
-\stopTheMatrix
-\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
+\NC \kmU
+= \NC \QU ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
 %
-\NC \V {b}_i
-=\NC \T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\V {y}}
-\in \MB {R} ^{2 N_H^2} \NR
+\NC \kpV
+= \NC \QV ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
 %
-\NC \V {c}_i
-= \NC \V {0}
-\in \MB {R} ^{3 N_H^2} \NR
+\NC \kmV
+= \NC \QV ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
+}
+And () becomes
+\Disp {
+\NC \DU \RB {\fpU - \fmU} + \QU ^\Tr \tp - \kpU
+=\NC 0 \NR
 %
-\NC d_i
-= \NC \g_{\Rm {DS}} \NR
+\NC \DU \RB {\fpU - \fmU} + \QU ^\Tr \tm - \kmU
+=\NC 0 \NR
 %
-\NC i 
-= \NC N_H^2, N_H^2 +1, N_H^2 +2, \ldots, 2 N_H^2 -1 \NR
+\NC \QV ^\Tr \tp - \kpV
+=\NC 0 \NR
+%
+\NC \QV ^\Tr \tm - \kmV
+=\NC 0 \NR
 }
+
+Our target function, in terms of new variables, reads
+\Disp {
+\NC \VNm {\V {g}} _1
+=\NC \IP {\V {1}, \gp} - \IP {\V {1}, \gm} \NR
 %
+\NC =\NC \IP {\M {Q} ^\Tr \V {1}, \fp} - \IP {\M {Q} ^\Tr \V {1}, \fm} \NR
+%
+\NC =\NC \IP {\M {Q} ^\Tr \V {1}, \fpU} - \IP {\M {Q} ^\Tr \V {1}, \fmU}
++ \IP {\M {Q} ^\Tr \V {1}, \fpV} - \IP {\M {Q} ^\Tr \V {1}, \fmV} \NR
+}
+
+This way, the matrix whose Hessian is required by Newton step would be much more sparse (Boyd p.565)
+
 \Result
@@
 %
-\item Calculate
+\item Solve the convex program
 %
 \DispNum {x:::mi:h1} {
-\NC \Hat {\V {x}}
-\LA \NC \startcases
-\NC \Min {\V {x}' \in \MB {C} ^{N_H^2}}
-\MC \IP {\V {t}, \V {x}'} \NR
-\NC \Rm {subject} \; \Rm {to}
-\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
-\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
-\NC \MC i 
-=0, 1, 2, \ldots, 2 N_H^2 -1 \NR
+\NC \startcases
+\NC \MC \fpU, \fpV, \fmU, \fmV, \sp, \sm: \NR
+%
+\NC \min
+\MC \IP {\M {Q} ^\Tr \V {1}, \fpU}
+- \IP {\M {Q} ^\Tr \V {1}, \fmU}
++ \IP {\M {Q} ^\Tr \V {1}, \fpV}
+- \IP {\M {Q} ^\Tr \V {1}, \fmV} \NR
+%
+\NC \Rm {subject} \; \Rm {to} \Q
+\MC -\QU \fpU -\QV \fpV \preceq 0 \NR
+%
+\NC \MC -\QU \fmU -\QV \fmV \preceq 0 \NR
+
+\NC \MC \DU \RB {\fpU - \fmU} + \QU ^\Tr \tp - \kpU = 0 \NR
+%
+\NC \MC \DU \RB {\fpU - \fmU} + \QU ^\Tr \tm - \kmU = 0 \NR
+%
+\NC \MC \QV ^\Tr \tp - \kpV = 0 \NR
+%
+\NC \MC \QV ^\Tr \tm - \kmV = 0 \NR
+%
+\NC \MC -\tp \preceq 0 \NR
+%
+\NC \MC -\tm \preceq 0 \NR
 \stopcases \NR
@@
 %
-\item Convert 
+\item Convert \m {\Hat {\V {g}}} by
 %
@@
 }
+
+\stopsubsection
 
@@
 }
-
-\startsubsection [title={Transformation by Diagonalization}]
-
-By Real Spectral Theorem, \m {\M {P} ^\Tr \M {P}} can be diagonized.
-Let
-\Disp {
-\NC \M {P} ^\Tr \M {P}
-= \NC \M {Q} \M {D} \M {Q} ^\Tr \NR
-}
-where
-\Disp {
-\NC \M {Q} ^\Tr \M {D} \M {Q}
-= \NC I \NR
-}
-It can be seen that only \m {2N_Y^2} of \m {2N_H^2} singular values are nonzero.
-Without loss of generality, suppose
-\Disp {
-\NC \MB {R} ^{2 N_H^2}
-= \NC \MS {U} \oplus \MS {V} \NR
-}
-with
-\Disp {
-\NC \Rm {dim} \; \MS {U}
-= \NC 2 N_Y^2 \NR
-\NC \Rm {dim} \; \MS {V}
-= \NC 2 N_H^2 -2 N_Y^2 \NR
-}
-such that
-\Disp {
-\NC \M {D}
-= \NC \startTheMatrix
-\NC \DU, \NC \M {0} \NR
-\NC \M {0}, \NC \M {0} \NR
-\stopTheMatrix \NR
-}
-
-Suppose
-\Disp {
-\NC \V {g}
-= \NC \gp - \gm \NR
-}
-with
-\Disp {
-\NC -\gp
-\preceq \NC 0 \NR
-\NC -\gm
-\preceq \NC 0 \NR
-}
-Introduce
-\Disp {
-\NC \fp
-= \NC \M {Q} ^\Tr \gp \NR
-\NC \fm
-= \NC \M {Q} ^\Tr \gm \NR
-}
-If we define
-\Disp {
-\NC \fp
-= \NC \fpU + \fpV \NR
-\NC \fm
-= \NC \fmU + \fmV \NR
-}
-That is, taking components of \m {\fp, \fm} respectively in \m {\MS {U}, \MS {V}}.
-Then we see that
-\Disp {
-\NC \fpU
-= \NC \QU ^\Tr \gp \NR
-\NC \fmU
-= \NC \QU ^\Tr \gm \NR
-\NC \fpV
-= \NC \QV ^\Tr \gp \NR
-\NC \fmV
-= \NC \QV ^\Tr \gm \NR
-}
-Here \m {\QU ^\Tr} is the abbreviation of \m {\RB {\QU} ^\Tr}.
-
-Notice that the constraint
-\Disp {
-\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}}
-\preceq \NC \g \V {1} \NR
-}
-can be written as
-\Disp {
-\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} - \g \V {1} + \sp
-= \NC \V {0} \NR
-\NC \M {P} ^\Tr \RB {\M {P} \V {g} - \V {y}} - \g \V {1} - \sm
-= \NC \V {0} \NR
-}
-with
-\Disp {
-\NC -\sp
-\preceq \NC 0 \NR
-\NC -\sm
-\preceq \NC 0 \NR
-}
-
-Now, define
-\Disp {
-\NC \kpU
-= \NC -\QU ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
-\NC \kmU
-= \NC -\QU ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
-\NC \kpV
-= \NC -\QV ^\Tr \RB {\M {P} ^\Tr \V {y} - \g \V {1}} \NR
-\NC \kmV
-= \NC -\QV ^\Tr \RB {\M {P} ^\Tr \V {y} + \g \V {1}} \NR
-}
-
-\stopsubsection
 
@@
 \stopchapter
+
+\stoptext
+
+\DispNum {t:::01:Nh} {
+\NC \V {t}
+= \NC \startTheMatrix
+\NC \V {0} \NR
+\NC \V {1} \NR
+\stopTheMatrix
+\in \MB {R} ^{3 N_H^2} \NR
+%
+\NC \V {x}'
+= \NC \startTheMatrix
+\NC \T {\V {g}}' \NR
+\NC \V {m} \NR
+\stopTheMatrix
+\in \MB {R} ^{3 N_H^2} \NR
+}
+%
+with
+%
+\DispNum {A:i:Ui:h1} {
+\NC \M {A}_i
+= \NC \startTheMatrix
+\NC \T {\M {U}}_{i}, \NC \M {0} \NR
+\stopTheMatrix
+\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
+%
+\NC \V {b}_i
+= \NC \V {0}
+\in \MB {R} ^{2 N_H^2} \NR
+%
+\NC \V {c}_i
+= \NC \startTheMatrix
+\NC \V {0} \NR
+\NC \V {u}_{i} \NR
+\stopTheMatrix
+\in \MB {R} ^{3 N_H^2} \NR
+%
+\NC d_i
+= \NC 0 \NR
+%
+\NC i 
+= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
+}
+
+And
+%
+\DispNum {A:i:Ui:h1} {
+\NC \M {A}_i
+= \NC \startTheMatrix
+\NC -\T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
+\stopTheMatrix
+\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
+%
+\NC \V {b}_i
+=\NC \T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\V {y}}
+\in \MB {R} ^{2 N_H^2} \NR
+%
+\NC \V {c}_i
+= \NC \V {0}
+\in \MB {R} ^{3 N_H^2} \NR
+%
+\NC d_i
+= \NC \g_{\Rm {DS}} \NR
+%
+\NC i 
+= \NC N_H^2, N_H^2 +1, N_H^2 +2, \ldots, 2 N_H^2 -1 \NR
+}

### 2020-03-24 presentation/1_introduction.tex
Update slides

--- 2019-08-17 dantzig_selector/presentation_B/1_introduction.tex
@@
 \Title {\TitleText}
-\Subtitle {II. Completing the Proof}
+\Subtitle {Numerical Experiments}
 \blank [big]
@@
 \page [yes]
-% % % % % % % % % % % % % % % % % % % % % % % % % %
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
 \Frame {Organization}
 {
-\I Introduction
+\I Problem Setting
 
-\I Problem Setting and Proposed Method
+\I Proposed Method
 
-\I Proving the performance bound: Sparsity, Concentration Inequality, and Expected Error
+\I Bound for the Error Norm
 
-\I Conclusion and Future Work
+\I Numerical Experiments
 
-\I References
+\I Conclusion and References
 }
-% % % % % % % % % % % % % % % % % % % % % % % % % %
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
 \Frame {Background}
 {
-\I Multiple-input-multiple-output (MIMO) wireless communication is expected to be the next-generation r\'egime.
+\I Multiple-input multiple-output (MIMO) communication system has been proposed as part of the 5G specification, but its hardware overhead increases complexity and power consumption.
 
-\I But channel response has to be known at the receiver to facilitate such algorithms as beamforming and channel calibration.
+\I The design of new algorithms addressing these issues requires channel information to be known.
 
-\I It calls for high complexity to estimate MIMO channels.
+\I Estimation of MIMO channels also results in high complexity, due to the large number of antennae.
 
-\I Meanwhile, millimeter wave (mmWave) channels often exhibit sparse properties.
-
-\I Under mmWave setting, if the sparsity is exploited, can few observations suffice to estimate the channel?
+\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we exploit to save for some measurements.
 }
-% % % % % % % % % % % % % % % % % % % % % % % % % %
-\Frame {Compressive Sensing}
-{
-\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \it{compressed sensing} (CS) address exactly that.
-
-\I The problem can be considered to be inverting a wide, rectangular matrix.
-With insufficient (even noisy) measurements, this does not make sense.
-
-\I But what if we impose other conditions?
-Indeed, it turns out that, when the signal is sparse, few observations may be sufficient for the reconstruction.
-And Dantzig Selector (DS), proposed by Cand\`es and Tao (2006) in the advent, is a possible solution.
-}

### 2020-03-24 presentation/2_setting.tex
Update slides

@@
 \Disp {
-\NC \M{H}
+\NC \m {H}
 =\NC \sum_{l=0} ^{L-1}
@@
 {
-\I Consider Complex Standard Normal \m {\M{Z} \in \NC \MB {C} ^{N_H \D N_H}}
+\I Consider Complex Standard Normal \m {\m {Z} \in \NC \MB {C} ^{N_H \D N_H}}
 
@@
 \Disp {
-\NC \M{Y}
-:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
+\NC \m {Y}
+:=\m {W}_B \m {W}_R \RB {\m {H} \m {F}_R \m {F}_B +\m {Z}} \NR
 }
 
-\I Summarizing the dimension,
+\I Their dimension is summarized for convenience:
 \Disp {
 \NC \MB {C}^{N_Y}
-\underset {\M{F}_B} {\mapsto} \NC \MB {C}^{N_R}
-\underset {\M{F}_R} {\mapsto} \MB {C}^{N_H}
-\underset {\M{H}} {\mapsto} \MB {C}^{N_H}
-\underset {\M{W}_R} {\mapsto} \MB {C}^{N_R}
-\underset {\M{W}_B} {\mapsto} \MB {C}^{N_Y} \NR
+\underset {\m {F}_B} {\mapsto} \NC \MB {C}^{N_R}
+\underset {\m {F}_R} {\mapsto} \MB {C}^{N_H}
+\underset {\m {H}} {\mapsto} \MB {C}^{N_H}
+\underset {\m {W}_R} {\mapsto} \MB {C}^{N_R}
+\underset {\m {W}_B} {\mapsto} \MB {C}^{N_Y} \NR
 }
 
-\I How do we \Emph {recover} \m {\M {H}} with knowledge of \m {\M {Y}}?
+\I Problem (a): How do we recover \m {\M {H}} with knowledge of \m {\M {Y}}?
 
-\I How do we \Emph {design} \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
+\I Problem (b): How do we design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
 }
@@
 \Q \M {P}
-:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
+:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
 \NC \V {g}
@@
 
-\I Then we have a \Emph {linear equation}
+\I Then we have a linear equation
 \Disp {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Compressive Sensing}
+{
+\I In our case, we have to essentially invert an underdetermined system, and usually, that is not well defined.
+
+\I Consider a simpler case: \m {\V {y} = \M {A} \V {x} + \V {z}}, where \m {\M {A} \in \MB {R} ^{N_m \D N_p}}, \m {\V {y} \in \MB {C} ^{N_m}}.
+
+\I If \m {\V {y} = \M {A} \V {x}_1 = \M {A} \V {x}_2}
+\Disp {
+\NC \V {x}_1 - \V {x}_2 \in \Rm {null}\; \M {A} \NR
+}
+Then \m {\V {x}_1, \V {x}_2} cannot be recovered.
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Restricted Isometry Property}
+{
+\I However, Candès and Tao shows that when the signal is sparse, few measurements may be sufficient for the reconstruction, with vanishing error norm, in overwhelming probability.
+
+\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.
+
+\I We say that \m {\m {P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
+\Disp {
+\NC \RB {1-\d_s} \VNm {\V {g}} _2^2
+\leq \NC \VNm {\m {P} \V {g}} _2^2
+\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
+}
+
+\I Verbally, \m {\m {P}} is \Emph {almost unitary} up to relative error \m {\d_s}.
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Dantzig Selector for Sparse Vectors}
+{
+\I Let \m {\V {x}} be \m {S}-sparse.
+If \m {\g_{\Ss {DS}} = \R {2 \log N_p}}, then
+\Disp {
+\NC \Hat {\V {x}}
+\LA \NC \startcases
+\NC \Min {\V {x}'}  \MC \VNm {\V {x}'} _1 \NR
+\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {A}^\intercal \RB {\V {y} -\M {A} \V {x}'}} _\infty \leq \g_{\Ss {DS}} \NR
+\stopcases \NR
+}
+with
+\Disp {
+\NC \VNm {\V {x} - \hat {\V {x}}} _2 ^2
+\leq \NC 32 S \sigma^2 \log N_p \NR
+}
+For high probability.
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
 \Frame {Proposed Method}
 {
-\I Input \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{N_H^2}}, \m{\g_{\Ss {DS}} \geq 0}.
+\I Back to our problem: Input \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.
 

### 2020-03-24 presentation/3_proof.tex
Update slides

--- 2019-11-05 presentation-B/3_proof.tex
@@
-\Frame {The Need of a Modified Proof}
+\Frame {Modifying the Original Proof}
 {
-\I \Emph {Q1}: DS is shown to work for \Emph {sparse} vectors, but is \m {\M {H}} really sparse?
+\I \Emph{Q1}: Candès and Tao established the case for real matrices, but does \Emph {complex} case apply?
 
-\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?
+\I \Emph {Q2}: DS works for \Emph {sparse} vectors, but as \m {\M {H}} is not sparse, does DS work?
 
-\I \Emph{Q3}: Candès and Tao established the case for real matrices, but does \Emph {complex} case apply?
+\I \Emph{Q3}: DS requires the measurement matrix to have restricted isometry property, but under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, is it true for \m {\M {P}}?
 
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Proof Strategy}
+\Frame {Real Valued Representation}
 {
-\I \m {\M {H}} is not sparse, but \m {\M {K}^\Adj \M {H} \M {K}} is.
-Remove the largest-magnitude \m {S} components of \m {\V{g}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, so that it remains to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}}}.
+\I To save complexity, we represent a complex number by its real- and imarinary-parts.
 
-\I Establish that \m {\M{W}_R} and \m {\M{W}_R} satisfies RIP, thus \m {\M{P}} satisfies RIP too, for high probability.
+\I For vectors, substitute
+\Disp {
+\NC a +b \Ss{i}
+\leftrightarrow \NC \startTheMatrix
+\NC a \NR
+\NC b \NR
+\stopTheMatrix \NR
+}
 
-\I We then establish a modified bound of error norm based on Candès and Tao.
+\I For matrices, substitute
+\Disp {
+\NC a +b \Ss{i}
+\leftrightarrow \NC \startTheMatrix
+\NC a, \NC -b \NR
+\NC b, \NC a \NR
+\stopTheMatrix \NR
+}
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Restricted Isometry Property}
+
+\Frame {Observations on Sparsity}
 {
-\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.
+\I \m {\M {H}} is not sparse, but \m {\M {K}^\Adj \M {H} \M {K}} is almost sparse.
+Call the largest-magnitude \m {S} components of \m {\V{g}} to be \m {\M {g} _{\SB{\MC {A}}}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, we still have to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.
 
-\I We say that \m {\M{P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
-\Disp {
-\NC \RB {1-\d_s} \VNm {\V {g}}^2
-\leq \NC \VNm {\M{P} \V {g}} _2^2
-\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
-}
+\I Establish that all four beamformers satisfy RIP, for high probability, thus \m {\m {P}} satisfies RIP too, for high probability.
 
-\I Verbally, \m {\M{P}} is \Emph {almost unitary} up to relative error \m {\d_s}.
+\I We then establish a modified bound of error norm.
 }
@@
 \Disp {
-\NC s
-=\NC \R {\log N_H},
-\Q S
-= L s^2,
+\NC S
+= L \log N_H,
 \Q \d_S
@@
 {
-\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of \Emph {Central Limit Theorem}, for unit vector \m {\V {u}}
-\Disp {
-\NC \MB {E} \SB {\VNm {\M {P} \V {u}} _2 ^k}
-\approx \NC 1
-\Q \Ss {in\; distribution} \NR
-}
+\I I argue in the treatise that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has?
 
-\I Unfortunately, they are \Emph {not i.i.d.}, and that need closer scrutiny.
+\I Try to set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant
 
-\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant
-
-\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {RIP of Effective Beamformers}
-{
-\I Is it true that if \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has?
-
-\I Indeed, if so, \m {\M {P}} has approximately \m {2\d_s}-RIP, if there is no sparsity constraint:
-\Disp {
-\NC \VNm {P} _2
-=\NC \VNm {\M {F}_B^\Tr \M {F}_B^\Tr} \VNm {\M {W}_B \M {W}_R} \NR
-}
-
-\I I argue that this is true for sparse \m {\V {g}}.
-In fact, if \m {\M {G} =\M {U} \Rm {diag} \SB {\V {d}} \M {U} ^\Adj}, for some \m {S}-sparse \m {\V {d}} and unitary \m {\M {U}}.
-
-\Disp {
-\NC \NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
-%
-\NC =\NC \VNm {
-   \M {W} _B \M {W} _R \M {K} \M {U}
-   \R {\Rm {abs} \SB {\V {d}}} \D
-   \R {\Rm {abs} \SB {\V {d}}}
-   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} \NR
-%
-\NC \eqsim \NC \VNm {\M {K} \M {H} \M {K} ^\Adj} _2 \RB {1 +2\d_s} \NR
-}
+\I And let each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
 }
@@
 \NC 1 -p
-\leq \NC 2 \Ss {e} ^{-N_B \R {\d_s} /4} \NR
+\leq \NC 2 \Ss {e} ^{-N_Y \R {\d_s} /4} \NR
 }
@@
 {
-\I In answer of \Emph {Q3}, it can be checked that the generalization to complex vectors only introduces the bound of a multiple \m {\R {2}}.
-
-\I then the following bound holds for high probability:
+\I The following bound holds for high probability \m {p}:
 \Disp {
-\NC \VNm {\V {d}} _2
+\NC \VNm {\Hat {\V {g}} - \V {g}} _2
 %
-\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
+\leq \NC 8 \R {L} \R {\log N_H}^3 \NR
 }
 
+\I where it hold for \m {p} that...
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Big-\m {O} of Success Probability (1/2)}
+\Frame {Big-\m {O} of Success Probability}
 {
@@
 \Disp {
-\NC q
-\eqsim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
+\NC q = 1-p
+\lesssim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
 }
 
-\I Then previous discussions
-\Disp {
-\NC q _{\Rm {iso}, B}
-\lesssim \NC 2 \Ss {e} ^{-N_B /12} \NR
-%
-\NC q _{\Rm {iso}, R}
-\lesssim \NC 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
-%
-\NC q _{\Rm {no}}
-\lesssim \NC N_H ^{-2} \NR
-%
-\NC q _{\Rm {sp}}
-\lesssim \NC 2 \Ss {e} ^{-9L/\pi} \NR
-}
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Big-\m {O} of Success Probability (2/2)}
-{
 \I If we provide the design values
 \Disp {
-\NC N_B
-\gtrsim \NC 4 \log N_H \NR
-%
-\NC N_R
-\gtrsim \NC 16 L \RB {\log N_H}^2 \NR
+\NC N_Y
+\gtrsim \NC 4 \log N_H, \Q
+N_R
+\gtrsim 16 L \RB {\log N_H}^2 \NR
 }
@@
 \lesssim q _{\Rm {iso}, B}
-\eqsim q _{\Rm {iso}, R}
-}
-
-\I Then we get the estimation
-\Disp {
+\eqsim q _{\Rm {iso}, R} \NR
+%
 \NC q
-\eqsim 2 N_H ^{-1/3} \NR
+\lesssim \NC 2 N_H ^{-1/3} \NR
 }

### 2020-03-24 presentation/4_simulation.tex
Update slides

% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Linear Programming}
{
\I Set \m {\V {1} = \IP {1, \dots, 1}}.
\I Calculate
\Disp {
\NC \Hat {\V {g}}, \Hat {\V {f}}
\LA \NC \startcases
   \NC \Min {\V {g}', \V {f}'}  \MC \IP {\V {1}, \V {f}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \V {g}' \leq \V {f}' \NR
   \NC \MC - \V {g}' \leq \V {f}' \NR
   \NC \MC \M {P}^\Adj \M {P} \V {g}' \leq \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \M {P}^\Adj \M {P} \V {g}' \leq - \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Two-Stage Estimation (1/2)}
{
\I Denote
\Disp {
\NC N_0 = \NC 2 N_H^2 \NR
\NC N_1 = \NC 2 N_H \NR
\NC N_2 = \NC 2 \lfloor \Rm {min} \SB {L \log \SB {N_H^2}, N_H} \rfloor \NR
}

\I Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}.

\I Choose the \m {N_1} largest component of \m {\Hat {\V {g}}_0} and call it \m {\V {g}_1}.
Choose corresponding columns of \m {\M {P}} and call it \m {\M {P} _1}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Two-Stage Estimation (2/2)}
{
\I Apply DS to \m {\V {y}, \M {P} _1} to get \m {\Hat {\V {g}}_1}.

\I Choose the \m {N_2} largest component of \m {\Hat {\V {g}}_1} and call it \m {\V {g}_2}.
Choose corresponding columns of \m {\M {P}_1} and call it \m {\M {P} _2}.

\I Apply pseudoinverse (linear square) to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}.

\I Assign corresponding components of \m {\Hat {\V {g}}_2} in \m {\Hat {\V {g}}}, and pad \m {0} otherwise.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I With some approximations, I suggest the following metric for spectral efficiency:
\I Denote \m {E := \Hat {H} - H}
\I Observe
\Disp {
\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj - \M {H} \M {H} ^\Adj} \V {x}
\lesssim 2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}} \NR
}
\I Define the spectral efficiency to be
\Disp {
\NC \log \det \SB {I + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Theoretical Metric}
{
\I For the theoretical error norm,
\Disp {
\NC \log d_{\Rm {th}}
\lesssim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H \NR
}
\I Define the theoretical spectral efficiency to be
\Disp {
\NC \log \det \SB {I + \RB {\s + \F {2 d_{\Rm {th}} \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Simulation Parameters}
{
\I Antennae number of channel \m {N_H = 16, 20, 24}
\I Antennae number of analog stage \m {N_R = \lfloor \R {N_H N_Y} \rfloor}
\I Antennae number of digital stage \m {N_Y = \lfloor N_H/3 \rfloor}
\I Number of paths \m {L =3}
\I Analog beamformer quantization grid: \m {16}
\I How many noise standard deviation tried: \m {7}
\I Number of repetition of each data point: \m {12}
\I Solved by Python CVXPY
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-small-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-small-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=20}}
{
\blank [big]
\externalfigure [assorted-medium-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=20}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Spectral Efficiency, \m {N_H=24}}
{
\blank [big]
\externalfigure [assorted-big-efficiency.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time Taken, \m {N_H=24}}
{
\blank [big]
\externalfigure [assorted-big-time.png] [factor=fit]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS is slightly better than others when \m {\s \gg 1}

\I \m {\eta _{\Ss {th}}} is in correct order of magnitude but not tight when \m {\s \gg 1}

\I The smaller the noise, the smaller the error

\I It is \It {not} true that the smaller \m {\g _{\Ss {DS}}}, the smaller the error

\I We have exceedingly high complexity than OMP

\I The requirement that \m {N_H \gg N_Y} is demanding
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity (1/2)}
{
\I In general, the complexity of convex optimization is hard to obtain.

\I However, there exist expressions for number of Newton steps in the course of optimization.
It is \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, which is at most \m {\MC {O} \SB {N_H^2}}.

\I Moreover, every Newton step requires a matrix inversion of dimension \m {N_H^2}, with at least \m {\MC {O} \SB {N_H^4}}.
This gives \m {\MC {O} \SB {N_H^6}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity (2/2)}
{
\I On the other hand, it is pointed out that Lasso (least absolute shrinkage and selection operator) has similar complexity with Least Angle regression, which has complexity \m {\MC {O} \SB {N_H^6}}.
Since DS and Lasso have similar form, we expect DS has similar complexity.

\I Clearly, the complexity of OMP is at most \m {\MC {O} \SB {N_H^2}}, so much smaller than DS.
}

### 2020-03-24 presentation/5_conclusion.tex
Update slides

\Frame {Conclusion}
{
\I We propose a method to estimate MIMO mm-Wave channel \m {\M {H}} by exploiting its sparsity, and employing Dantzig Selector (DS).

\I We modified DS for present setting, for the almost-sparse condition in the angular domain, using the effective beamformer \m {\M {P}}, and concerning complex vectors.

\I We have a bound of the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the asymptotic behavior of the successful probability.

\I We adopt linear programming to reduce complexity.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Future Work}
{
\I Is it possible to resort to less precision to reduce complexity, but retaining the performance?

\I Run for bigger values of \m {N_H}, \m {N_Y} and repeat for enough times to observe a definite result.

\I I want to know why DS is not as good as expected, and to provide discussion, before closing the case.

\I The proof section need some rewriting, but it is not big deal.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References}
{
{\tfx
\I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.

\I E Candès and J Romberg, \Quote {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved online, 2005.

\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \m {p} is much larger than \m {n}}, \It {The Annals of Statistics} 35(6), 2007.

\I B Efron and T Hastie, \Quote {Least angle regression}, \Quote {The Annals of statistics}, 32(2), 2004.

\I J Lee, G-T Lee, and H Yong, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 64(6), 2016.
}
}

### 2020-06-09 paper/4_simulation.tex
Revert simulation method description; add figures

--- 2019-11-05 paper/4_simulation.tex
@@
 However, the situation is more cubersome than that, since they deal with real vectors, but we consider the complex ones.
-Fortunately, they have briefly pointed out, complex DS can be recast as an second-order cone program (SOCP), and SOCP is one of the several standard convex programming problems for which there are already numerous efficient algorithms.
+Fortunately, they have briefly pointed out, complex DS can be recast as an linear program (LP), one of the several standard convex programming problems for which there are already several efficient algorithms.
 
-Before describing the recast, for ease of treatment we would like to represent complex vector and matrices by real, extended vectors and matrices.
-\Result
-{Definition}
-{
-For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MC {R} \SB {\V {x}}} of \m {\V {x}} to be
+\startsection [title={Method}]
+
+\startsubsection [title={Some Notation}]
+
+For brevity we shall represent complex vector and matrices by real ones, comprising of its real an imaginary parts.
+For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
 %
 \DispNum {R-x-R2-M1} {
-\NC \MC {R} \SB {\V {x}}
+\NC \MS {R} \SB {\V {x}}
 \in \NC \MB {R} ^{2M} \NR
-\NC \MC {R} \SB {\V {x}} _{\SB {m}}
+\NC \MS {R} \SB {\V {x}} _{\SB {m}}
 = \NC \startcases
@@
 %
-The injectivity is obvious, and we may define \m {\MC {R} ^{-1}} so that
+The injectivity is obvious, and we may define \m {\MS {R} ^{-1}} so that
 %
 \DispNum {R-1-x--x-} {
-\NC \MC {R} ^{-1} \SB {\MC {R} \SB {\V {x}}}
+\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
 =\NC \V {x} \NR
-}
 }
@@
 Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
-\Result
-{Definition}
-{
-For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MC {R} \SB {\M {A}}} of \m {\M {A}} to be
+For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
 %
 \DispNum {R-A-R2-21} {
-\NC \MC {R} \SB {\M {A}}
+\NC \MS {R} \SB {\M {A}}
 \in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
-\NC \MC {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
+\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
 \NC \startcases
@@
 }
-}
 
@@
 \NC \T {\V {y}}
-= \NC \MC {R} \SB {\V {y}}
+= \NC \MS {R} \SB {\V {y}}
 \in \MB {R} ^{2 N_Y^2} \NR
@@
 
-\stopsection
+\stopsubsection
 
-\startsection [title={Second Order Cone Programming}]
+\startsubsection [title={A Linear Program}]
 
@@
 %
-\DispNum {A-i-Ui-h1} {
+\DispNum {A-i-Ui-21} {
 \NC \M {A}_i
@@
 }
-
-And
 %
-\DispNum {A-i-Ui-h1} {
+and
+%
+\DispNum {A-i-Ui-21-"} {
 \NC \M {A}_i
@@
 \item Input \m{\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
-\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to ().
+\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to \Rf {t---01-Nh}, \Rf {A-i-Ui-h1}, \Rf {A-i-Ui-h1-"}.
 \item Calculate
@@
 \NC \Hat{\V {g}}
-\LA \NC \MC{R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
+\LA \NC \MS {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
 }
@@
 
+\stopsubsection
+
 \stopsection
@@
 The averaged error values are plotted along with the bound of error norm.
-Taking log of \Rf {d-2-42-NH} we have
+As a basis for comparison, we approximate \Rf {d:2:42:NH} and take log, giving
 %
-\Disp {
-\NC \log \SB {7.85 \R {L} \RB {\log N_H}^3}
-\lesssim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2.06 \NR
-}
-Thus we draw
-\DispNum {h'-h-12-H2} {
-\NC \h_{\Rm{th}}
+\DispNum {h':h:12:H2} {
+\NC \h_{\Rm {th}}
 \eqsim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2 \NR
@@
 
-\startsubsection [title={Plots for \m {N_H=32}}]
+\page [yes]
 
+\startsubsection [title={Assorted Plots}]
+
+For \m {N_H = 12}, noise vs spectral efficiency,
+%
 \blank [big]
-\externalfigure [medium-assorted-abs.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-small-spectral.png] [wfactor=fit, hfactor=fit]
 
+For \m {N_H = 18}, noise vs spectral efficiency,
+%
 \blank [big]
-\externalfigure [medium-assorted-rel.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-medium-spectral.png] [wfactor=fit, hfactor=fit]
 
+For \m {N_H = 24}, noise vs spectral efficiency,
+%
 \blank [big]
-\externalfigure [medium-assorted-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-big-spectral.png] [wfactor=fit, hfactor=fit]
+
+For \m {N_H = 18}, noise vs time taken,
+%
+\blank [big]
+\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
 
@@
 
-\startsubsection [title={Plots for \m {N_H=48}}]
+\page [yes]
 
+\startsubsection [title={Plots of Dantzig Selector}]
+
+For \m {N_H = 12}, noise vs spectral efficiency,
+%
 \blank [big]
-\externalfigure [big-assorted-abs.png] [wfactor=fit, hfactor=fit]
+\externalfigure [ddss-small-spectral.png] [wfactor=fit, hfactor=fit]
 
+For \m {N_H = 18}, noise vs spectral efficiency,
+%
 \blank [big]
-\externalfigure [big-assorted-rel.png] [wfactor=fit, hfactor=fit]
+\externalfigure [ddss-medium-spectral.png] [wfactor=fit, hfactor=fit]
 
+For \m {N_H = 24}, noise vs spectral efficiency,
+%
 \blank [big]
-\externalfigure [big-assorted-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [ddss-big-spectral.png] [wfactor=fit, hfactor=fit]
+
+For \m {N_H = 18}, noise vs time taken,
+%
+\blank [big]
+\externalfigure [ddss-medium-time.png] [wfactor=fit, hfactor=fit]
+
+\stopsubsection
+
+\page [yes]
+
+\startsubsection [title={Plots of Orthogonal Matching Pursuit}]
+
+For \m {N_H = 12}, noise vs spectral efficiency,
+%
+\blank [big]
+\externalfigure [oommpp-small-spectral.png] [wfactor=fit, hfactor=fit]
+
+For \m {N_H = 18}, noise vs spectral efficiency,
+%
+\blank [big]
+\externalfigure [oommpp-medium-spectral.png] [wfactor=fit, hfactor=fit]
+
+For \m {N_H = 24}, noise vs spectral efficiency,
+%
+\blank [big]
+\externalfigure [oommpp-big-spectral.png] [wfactor=fit, hfactor=fit]
+
+For \m {N_H = 18}, noise vs time taken,
+%
+\blank [big]
+\externalfigure [oommpp-medium-time.png] [wfactor=fit, hfactor=fit]
 

### 2020-06-09 presentation/1_introduction.tex
Update presentation

@@
 
-\I The design of new algorithms addressing these issues requires channel information to be known.
+\I The design of various algorithms requires channel information to be known.
 
@@
 
-\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we exploit to save for some measurements.
+\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we might exploit to reduce complexity.
 }

### 2020-06-09 presentation/2_setting.tex
Update presentation

@@
 
-\I Problem (a): How do we recover \m {\M {H}} with knowledge of \m {\M {Y}}?
+\I Problem (a): Recover \m {\M {H}} with knowledge of \m {\M {Y}}?
 
-\I Problem (b): How do we design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
+\I Problem (b): Design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
 }
@@
 
-\I Then we have a linear equation
+\I Then we have a linear equation, where we have to essentially invert an underdetermined system:
 \Disp {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Compressive Sensing}
+\Frame {Terminology}
 {
-\I In our case, we have to essentially invert an underdetermined system, and usually, that is not well defined.
-
-\I Consider a simpler case: \m {\V {y} = \M {A} \V {x} + \V {z}}, where \m {\M {A} \in \MB {R} ^{N_m \D N_p}}, \m {\V {y} \in \MB {C} ^{N_m}}.
-
-\I If \m {\V {y} = \M {A} \V {x}_1 = \M {A} \V {x}_2}
-\Disp {
-\NC \V {x}_1 - \V {x}_2 \in \Rm {null}\; \M {A} \NR
-}
-Then \m {\V {x}_1, \V {x}_2} cannot be recovered.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Restricted Isometry Property}
-{
-\I However, Candès and Tao shows that when the signal is sparse, few measurements may be sufficient for the reconstruction, with vanishing error norm, in overwhelming probability.
-
 \I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.
@@
 
-\I Verbally, \m {\m {P}} is \Emph {almost unitary} up to relative error \m {\d_s}.
+\I We may think \m {\m {P}} to be almost unitary up to relative error \m {\d_s}.
 }
@@
 {
+\I Candès and Tao shows that when the signal is sparse, few measurements may be sufficient for the reconstruction, with vanishing error norm, in overwhelming probability.
+
 \I Let \m {\V {x}} be \m {S}-sparse.

### 2020-06-09 presentation/3_proof.tex
Update presentation

@@
-\Frame {Modifying the Original Proof}
+\Frame {Modifying the Original Proof (1/2)}
 {
-\I \Emph{Q1}: Candès and Tao established the case for real matrices, but does \Emph {complex} case apply?
+\I DS works for real matrices, but we generalize by representing a complex number by its real- and imarinary-parts.
 
-\I \Emph {Q2}: DS works for \Emph {sparse} vectors, but as \m {\M {H}} is not sparse, does DS work?
-
-\I \Emph{Q3}: DS requires the measurement matrix to have restricted isometry property, but under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, is it true for \m {\M {P}}?
-
-\I \Emph{Q4}: Candès and Tao showed the Big-\m {\MC {O}} of error norm depends on (in our case) \m {N_H}, but does the algorithm work successfully for \Emph {high probability}?
+\I DS works for sparse vectors, but \m {\M {H}} is not sparse.
+We claim that \m {\M {K}^\Adj \M {H} \M {K}} is almost sparse.
+Call the largest-magnitude \m {S} components of \m {\V{g}} to be \m {\M {g} _{\SB{\MC {A}}}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, we have to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Real Valued Representation}
+\Frame {Modifying the Original Proof (2/2)}
 {
-\I To save complexity, we represent a complex number by its real- and imarinary-parts.
+\I DS requires the measurement matrix (in our case) \m {P} to have restricted isometry property.
+We shall design all four beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, so that for high probability, they satisfies RIP, thus \m {\m {P}} does too.
 
-\I For vectors, substitute
-\Disp {
-\NC a +b \Ss{i}
-\leftrightarrow \NC \startTheMatrix
-\NC a \NR
-\NC b \NR
-\stopTheMatrix \NR
-}
-
-\I For matrices, substitute
-\Disp {
-\NC a +b \Ss{i}
-\leftrightarrow \NC \startTheMatrix
-\NC a, \NC -b \NR
-\NC b, \NC a \NR
-\stopTheMatrix \NR
-}
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-
-\Frame {Observations on Sparsity}
-{
-\I \m {\M {H}} is not sparse, but \m {\M {K}^\Adj \M {H} \M {K}} is almost sparse.
-Call the largest-magnitude \m {S} components of \m {\V{g}} to be \m {\M {g} _{\SB{\MC {A}}}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, we still have to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.
-
-\I Establish that all four beamformers satisfy RIP, for high probability, thus \m {\m {P}} satisfies RIP too, for high probability.
-
-\I We then establish a modified bound of error norm.
+\I We know the Big-\m {\MC {O}} of error norm of DS depends on (in our case) \m {N_H}.
+We consider these failure events above, and claim that the algorithm works for high probability.
 }
@@
 {
-\I I argue in the treatise that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has?
+\I Let us set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant
 
-\I Try to set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant
+\I And set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
 
-\I And let each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
+\I It is argued in the treatise that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has too.
 }
@@
 %
-\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP...
-
-\I for probability \m {p}, with
+\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP for probability \m {p}, with
 \Disp {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Error Norm of Dantzig Selector}
+\Frame {Bound of Error Norm (1/2)}
 {
-\I The following bound holds for high probability \m {p}:
+\I The following bound holds for probability \m {p}:
 \Disp {
@@
 }
-
-\I where it hold for \m {p} that...
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Big-\m {O} of Success Probability}
-{
-\I Denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
+%
+\I where for \m {p}, denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
 \Disp {
@@
 
-\I If we provide the design values
+\I Then...
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Bound of Error Norm (2/2)}
+{
+\I For concreteness, set values
 \Disp {
-\NC N_Y
-\gtrsim \NC 4 \log N_H, \Q
-N_R
-\gtrsim 16 L \RB {\log N_H}^2 \NR
+\NC N_Y \gtrsim \NC 4 \log N_H, \NR
+\NC N_R \gtrsim \NC 16 L \RB {\log N_H}^2 \NR
 }
-
+%
 \I It follows that

### 2020-06-09 presentation/4_simulation.tex
Update presentation

@@
 
-\I Apply pseudoinverse (linear square) to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}.
+\I Apply pseudoinverse (least square) to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}.
 
@@
 {
-\I With some approximations, I suggest the following metric for spectral efficiency:
-\I Denote \m {E := \Hat {H} - H}
-\I Observe
+\I We call the following quantity \m {M} to be the efficiency, in view of approximate spectral efficiency:
+\I Denote \m {E := \Hat {H} - H}.
+Assume that
 \Disp {
-\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj - \M {H} \M {H} ^\Adj} \V {x}
+\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj \V {x} - \M {H} \M {H} ^\Adj \V {x}} _2
 \lesssim 2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}} \NR
 }
-\I Define the spectral efficiency to be
+\I Then define
 \Disp {
-\NC \log \det \SB {I + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
+\NC M
+= \log \det \SB {I + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
 }
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Theoretical Metric}
+\Frame {Theoretical Prediction}
 {
@@
 }
-\I Define the theoretical spectral efficiency to be
+\I Then we may well define the theoretical efficiency to be
 \Disp {
@@
 {
-\I Antennae number of channel \m {N_H = 16, 20, 24}
+\I Antennae number of channel \m {N_H = 12, 18, 24}
 \I Antennae number of analog stage \m {N_R = \lfloor \R {N_H N_Y} \rfloor}
@@
 \I How many noise standard deviation tried: \m {7}
-\I Number of repetition of each data point: \m {12}
 \I Solved by Python CVXPY
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Spectral Efficiency, \m {N_H=16}}
+\Frame {Repetition times}
+{
+\I Number of channels ...
+\I of each LS case: \m {64 \D 48}
+\I of each OMP case: \m {64 \D 24}
+\I of each Lasso case: \m {64 \D 2}
+\I of each DS case: \m {64 \D 1}
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Assorted, Efficiency, \m {N_H=12}}
 {
 \blank [big]
-\externalfigure [assorted-small-efficiency.png] [factor=fit]
+\externalfigure [assorted-small-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Time Taken, \m {N_H=16}}
+\Frame {Assorted, Efficiency, \m {N_H=18}}
 {
 \blank [big]
-\externalfigure [assorted-small-time.png] [factor=fit]
+\externalfigure [assorted-medium-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Spectral Efficiency, \m {N_H=20}}
+\Frame {Assorted, Efficiency, \m {N_H=24}}
 {
 \blank [big]
-\externalfigure [assorted-medium-efficiency.png] [factor=fit]
+\externalfigure [assorted-big-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Time Taken, \m {N_H=20}}
+\Frame {Assorted, Time Taken, \m {N_H=18}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Spectral Efficiency, \m {N_H=24}}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {DS, Efficiency, \m {N_H=12}}
 {
 \blank [big]
-\externalfigure [assorted-big-efficiency.png] [factor=fit]
+\externalfigure [ddss-small-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Time Taken, \m {N_H=24}}
+\Frame {DS, Efficiency, \m {N_H=18}}
 {
 \blank [big]
-\externalfigure [assorted-big-time.png] [factor=fit]
+\externalfigure [ddss-medium-spectral.png] [factor=fit]
 }
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {DS, Efficiency, \m {N_H=24}}
+{
+\blank [big]
+\externalfigure [ddss-big-spectral.png] [factor=fit]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {DS, Time Taken, \m {N_H=18}}
+{
+\blank [big]
+\externalfigure [ddss-medium-time.png] [factor=fit]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {OMP, Efficiency, \m {N_H=12}}
+{
+\blank [big]
+\externalfigure [oommpp-small-spectral.png] [factor=fit]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {OMP, Efficiency, \m {N_H=18}}
+{
+\blank [big]
+\externalfigure [oommpp-medium-spectral.png] [factor=fit]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {OMP, Efficiency, \m {N_H=24}}
+{
+\blank [big]
+\externalfigure [oommpp-big-spectral.png] [factor=fit]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {OMP, Time Taken, \m {N_H=18}}
+{
+\blank [big]
+\externalfigure [oommpp-medium-time.png] [factor=fit]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
@@
 {
-\I DS is slightly better than others when \m {\s \gg 1}
+\I DS wins with a narrow margin for smaller \m {\s}, but it gets poorer for larger \m {\s}.
 
-\I \m {\eta _{\Ss {th}}} is in correct order of magnitude but not tight when \m {\s \gg 1}
+\I \m {\eta _{\Ss {th}}} is in correct order of magnitude for larger \m {\s}, but an overestimation for smaller \m {\s}.
 
-\I The smaller the noise, the smaller the error
+\I The performance of DS seems not to be sensitive to \m {\g _{\Ss {DS}}}.
 
-\I It is \It {not} true that the smaller \m {\g _{\Ss {DS}}}, the smaller the error
+\I DS has very high complexity compared to OMP, and similar complexity with Lasso.
 
-\I We have exceedingly high complexity than OMP
-
-\I The requirement that \m {N_H \gg N_Y} is demanding
+\I The requirement that \m {N_H \gg N_R \gg N_Y} is demanding, and \m {2N_H^2} grows fast.
 }
@@
 {
-\I In general, the complexity of convex optimization is hard to obtain.
-
-\I However, there exist expressions for number of Newton steps in the course of optimization.
-It is \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
+\I The number of Newton steps in the course of optimization is \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
 Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, which is at most \m {\MC {O} \SB {N_H^2}}.
 
-\I Moreover, every Newton step requires a matrix inversion of dimension \m {N_H^2}, with at least \m {\MC {O} \SB {N_H^4}}.
-This gives \m {\MC {O} \SB {N_H^6}}.
+\I Every Newton step requires a matrix inversion of dimension \m {N_H^2}, with at least \m {\MC {O} \SB {N_H^4}}.
+
+\I This gives overall complexity to be \m {\MC {O} \SB {N_H^6}}.
 }
@@
 {
-\I On the other hand, it is pointed out that Lasso (least absolute shrinkage and selection operator) has similar complexity with Least Angle regression, which has complexity \m {\MC {O} \SB {N_H^6}}.
-Since DS and Lasso have similar form, we expect DS has similar complexity.
+\I Alternatively, Lasso (least absolute shrinkage and selection operator) has similar complexity with Least Angle regression, which has complexity \m {\MC {O} \SB {N_H^6}}.
 
-\I Clearly, the complexity of OMP is at most \m {\MC {O} \SB {N_H^2}}, so much smaller than DS.
+\I Since DS and Lasso have similar form, we expect DS has similar complexity.
+
+\I Clearly, the complexity of OMP is at most \m {\MC {O} \SB {N_H^2}}, much smaller than DS.
 }

### 2020-06-09 presentation/5_conclusion.tex
Update presentation

@@
 {
-\I We propose a method to estimate MIMO mm-Wave channel \m {\M {H}} by exploiting its sparsity, and employing Dantzig Selector (DS).
+\I We propose a method to estimate MIMO mm-Wave channel \m {\M {H}} by modifying Dantzig Selector (DS), exploiting the sparsity inherent in the problem.
 
-\I We modified DS for present setting, for the almost-sparse condition in the angular domain, using the effective beamformer \m {\M {P}}, and concerning complex vectors.
+\I We argue for its validity, for the almost-sparse condition in the angular domain, using the effective beamformer \m {\M {P}}, and concerning complex vectors.
 
-\I We have a bound of the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the asymptotic behavior of the successful probability.
+\I We propose a bound of the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the asymptotic behavior of the successful probability.
 
-\I We adopt linear programming to reduce complexity.
+\I We convert the problem into a linear program to reduce complexity, and run a two-stage version to estimate the position of components.
 }
@@
 {
-\I Is it possible to resort to less precision to reduce complexity, but retaining the performance?
+\I Is it possible to reduce complexity, while retaining the performance?
 
-\I Run for bigger values of \m {N_H}, \m {N_Y} and repeat for enough times to observe a definite result.
+\I Is the trend the same for bigger values of \m {N_H}?
 
-\I I want to know why DS is not as good as expected, and to provide discussion, before closing the case.
-
-\I The proof section need some rewriting, but it is not big deal.
+\I Why DS is not as good as expected, and is there any mistakes in the proof of error bound?
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {References}
+\Frame {References (1/2)}
 {
 {\tfx
+\I W U Bajwa, J Haupt, A M Sayeed, and R Nowak, \Quote {Compressed channel sensing: A new approach to estimating sparse multipath channels}, \It {Proceedings of the IEEE}, 98(6), 2010
+
 \I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.
@@
 \I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \m {p} is much larger than \m {n}}, \It {The Annals of Statistics} 35(6), 2007.
+}
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {References (2/2)}
+{
+{\tfx
+\I E J Candès and T Tao, \Quote {Decoding by Linear Programming}, \It {IEEE Transactions on Information Theory}, 51(12), 2005
 
-\I B Efron and T Hastie, \Quote {Least angle regression}, \Quote {The Annals of statistics}, 32(2), 2004.
+\I M P Friedlander and M A Saunders, \Quote {Discussion: the Dantzig selector: statistical estimation when p is much larger than n}, \It {The Annals of Statistics}, 35(6), 2007
 
 \I J Lee, G-T Lee, and H Yong, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 64(6), 2016.
+
+\I J A Tropp and A C Gilbert, \Quote {Signal recovery from random measurements via orthogonal matching pursuit}, \It {IEEE Transactions on information theory}, 53(12), 2007.
 }

### 2020-08-17 treatise/1_introduction.tex
Revise: failure plot, two-stage version

--- 2020-02-27 paper/1_introduction.tex
@@
 
-\startsection [title={The Channel Sensing Problem}]
+\startsection [title={Background: Estimation of MIMO Channel}]
 
-Multiple-input multiple-output (MIMO) communication system has been proposed to be incorporated into the 5G specification (Rappaport et.\ al.\ \cite [RSM13]).
-With a large number of antennae of both transmitter and receiver sides, it is expected to provide a large signal gain.
-However, its hardware overhead increases complexity and power consumption, and new precoders, and algorithms, are being invented to deal with this.
-Especially, millimeter waves (hereafter mm-wave), with smaller wavelength, leads to higher frequency bands, and thus wider bands to be available.
-In addition, the smaller closer spaced antennae makes it possible to increase the number of antennae.
-This being said, with more antennae present, conventional training-based algorithms also increase in complexity and storage.
+Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification (Rappaport et.\ al.\ \cite [RSM13]).
+With a large number of antennae on both transmitter and receiver, MIMO is expected to provide a large signal gain.
+The appeal of MIMO includes multiplexing gain (with parallel transmission of data), diversity gain (with redundant transmission using space-time coding), and antenna gain (with beamforming).
+The millimeter wave (mm-wave) is also suggested: its smaller wavelength results in higher frequency bands, and thus wider bands available.
+The antennae may be closer-spaced, making it possible to increase their number.
 
-The design of new algorithms that addressed these issues is thus necessary, and ideally, we would like to know the expression of channel in advance.
-The channel capacity is the major information theoretic metric to be considered in a communication system.
-Roughly, the capacity of a MIMO channel at perfect channel state information is well-known to be in the form \m {\log \det \RB {I +\Ss {snr}}}, but the expression of channel is hardly always available, and in fact, the explicit dependence of capacity on relevant parameters is often a difficult problem (Goldsmith et.\ al.\ \cite [GJJ03]).
-When the estimated channel is compromised, the ensuing analysis is also undermined.
+However, MIMO also leads to hardware overhead and increases complexity and power consumption.
+To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, can be calculated.
+Not only is the channel estimation difficult due to a large number of antennae, but the transmission is prone to noise corruption.
+With more antennae, conventional training-based algorithms also increase in complexity and storage.
 
-It turns out that not only is the channel hard to estimate due to a large number of antennae, but the transmission is prone to noise corruption.
-In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
+\startsection [title={Compressive Sensing}]
 
-\stopsection
-\startsection [title={The Dantzig Selector}]
+Then, a recent developement called compressive sensing turns out to be relevant.
+Generally speaking, it is a technique for reconstructing a signal in the case of underdetermined linear systems, if the sparsity of signal guarantees successful recovery in the majority of cases.
+A more common situation is that some signals are not sparse in the original basis, but there exists a certain basis on which the signal is sparse, and fewer measurements suffice, though constructing such bases is another undertaking.
 
-It is a recent developement that the estimation of channels is facilitated by advances of the so-called \It {compressive sensing}.
-A series of paper by Candès and Tao marks its advent.
-They start by observing that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, namely,
+\blank [big]
+\externalfigure [compressive-sensing.png] [wfactor=fit, hfactor=fit]
+
+The figure shows the signal in both original basis and Hermite polynomials basis.
+It is not sparse in the former, but is in the latter.
+Thus, the recovery from just a few Hermite polynomial components are able to approximate it well.
+(Source: Wikimedia Commons, retrived from \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
+
+In the beginning, a Candès and Tao \cite [Can05] pointed out that in various statsitical applications the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
 %
@@
 %
+They showed that in the noiseless case \cite [Can05], it is possible to recover the sparse signal, under a \m {\ell_1}-minimization program, revealing the phenomenon that fewer than \m {N_p} measurement suffices to resonstruct the \m {N_m}-dimensional signal, when it is sparse.
+
+Indeed, usually any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.
+But the sparsity constraint essentially restrict the underdetermined system so much that we obtain unique solution for most of the time.
+
 As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
-Another example, to quote \cite [CaT07], is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being.
+Another example is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being \cite [CaT07].
+
+\stopsection
+
+\startsection [title={The Dantzig Selector}]
 
 But with insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
-Of course, more assumption must be made to make the question meaningful, since any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.
-
-They showed that in the noiseless case \cite [Can05], it is possible to recover the sparse signal, under a \m {\ell_1}-minimization program, revealing the phenomenon that fewer than \m {N_p} measurement suffices to resonstruct the \m {N_m}-dimensional signal, when it is sparse.
-Later they established a stronger result \cite [CaT07] that, with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too, but in doing so, we have to make a few carefully constructed, and seemingly random measurements.
-
-From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
-Indeed, relevent code has been put on the web for the reader to access and verify (Candès \& Romberg \cite [CaR05]).
-In this paper we focus on DS, and we introduce several notions before we describe their work.
+A stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too, but in doing so, we have to make a few carefully constructed, and seemingly random measurements.
 
@@
 
-And for given \m {s},
 \Result
@@
 
-Candès and Tao was able to show that, by Algorithm [3], \m {\V {x}} can be recovered, with the expected square error bounded with overwhelming probability.
-Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program (hereafter LP), lending convex programming technique applicable.
-The constant \m {\d_s} in Definition [2] is crucial, and here we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
-One common design choice of \m {\M {Q}} proposed is that every entry of \m {\M {Q}} shall be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
-Still, it remains unclear how to find RIP matrices efficiently, which became an active research area.
+They were able to show \cite [CaT07] that Algorithm [3] recovers \m {\V {x}} with the expected square error bounded with overwhelming probability.
 
-Meanwhile, back at the ranch, recall that the overhead of channel estimation has been a concern in the millimeter wave MIMO setting.
+From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
+Indeed, relevent code has been put on their website for the reader to access and verify (Candès \& Romberg \cite [CaR05]).
+
+Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.
+The constant \m {\d_s} in Definition [2] is crucial, and here we can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
+One common proposal is choosing every entry of \m {\M {Q}} to be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
+However it remains a research problem to find RIP matrices efficiently.
+
+Back at the ranch, recall that the overhead of channel estimation has been a concern in the mm-wave MIMO setting.
 Luckily, physical evidences suggest that millimeter wave channels are in fact sparse in the frequency domain, and some scholars have thus applied compressive sensing techniques to the problem.
@@
 What they explored was the estimation of single-antenna channel response with respect to time.
-The accompanying paper by the same team (Bajwa et.\ al.\ \cite [BHR08]) shows that \m {X} is RIP for overwhelming probability, providing the ground for the former paper.
-
-To illustrate, consider a linear time-invariant channel \m {y\SB {t} =\RB {x \star h} \SB {t} + z\SB {t}}, where \m {h\SB {t}} is the channel's impulse response, \m {y\SB {t}} is the output, and for each time index, signal \m {x\SB {t}} and noise \m {z\SB {t}} are both i.i.d.
-Simply assuming \m {h} is sparse, we may express the convolution between \m {h} with \m {x} by a matrix \m {X}, so that \m {\V {y} =\M {X} \V {h} +\V {z}} for some \m {\M {X}}.
-Then \cite [BHR08] showed that \m {\M {X}} is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice performance bounds drawing directly from \cite [CaT07].
+The accompanying note by the same authors (Bajwa et.\ al.\ \cite [BHR08]) shows that \m {X} is RIP for overwhelming probability, providing the ground for the IEEE paper.
+Dealing with a linear time-invariant channel, \cite [BHR08] showed that if the convolution is seen as a linear system, the sensing matrix has RIP of overwhelmingly probability, and DS is ready to be applied, with some nice performance bounds drawing directly from \cite [CaT07].
 
 \stopsection
+
 \startsection [title={Orthogonal Matching Pursuit}]
@@
 %
-Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the estimated position where \m {\V {x}} is nonzero (where we have slightly abused the usage of subscript to indicate position indices).
+Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero-position of \m {\V {x}}, which \cite [CaT07] calls support (here we have slightly abused the usage of subscript to indicate component indices).
 From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.
-
-The matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.
-
-\stopsection
-
-\startsection [title={Further Development}]
-
-OMP has since been applied in a variety of ways, and here we restrict our attention to channel estimation.
-In fact, ever since, work on channel estimation seems to favored OMP instead of DS, nor other sparse algorithm, without clear justification, and this must have somthing to do with the simplicity of OMP implementation.
+It is instructive to note that the matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.
 
@@
 Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discusses the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
-Gao et.\ al.\ \cite [LGC16] present the jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on positions of nonzero components.
+Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero-positions.
 Hu, Wang, and He \cite [HWH13] applies OMP to estimate quantized path delay of each OFDM subcarrier, assuming the channel gain in each path is stationary.
-Lee, Gil, and Lee \cite [LGL16] considers a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.
+Lee, Gil, and Lee \cite [LGL16] consider a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.
 
@@
 
-\startsection [title={Our Contribution}]
+\startsection [title={Motivation and Contribution}]
 
-With all these efforts, current literature of compressive channel estimation, in our view, has not satisfyingly responded several aspects.
+Ever since, OMP has since been applied in a variety of ways.
+Especially, work on channel estimation seems to favored OMP for its low complexity.
 One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.
-At least in the uniform linear array setting, the angular domain can be used Fourier as sensing matrix, which researchers have correctly noted.
-But the true angle of arrival and departure is often slightly off.
-We can always use finer quantization, but that leads to higher complexity.
-Moreover, researchers usually assume that the channel matrix has small norm, but further justifications and explicit bounds, depending channel parameters (say on sparsity and dimension), may be desired.
+Indeed, in the uniform linear array setting, DFT matrix can be used as sensing matrix, but the true angle of arrival and departure is often slightly off.
+Meanwhile, as the nature of OMP is greedy, and it is dubious whether it achieves optimality.
+In addition, the assumption that the channel matrix is sparse, at least, warrant justification.
 
-In this paper, we argue in favor of DS, rather than OMP, to be another viable solution that has been ignored.
-To elaborate, we consider a system model where both digital and analog beamformer are i.i.d.\ random matrices, so that the effective beamformer serves readily as the sensing matrix with RIP.
-Assuming uniform linear array, we apply a convex program inspired by DS so as to directly estimate the channel.
-We shall see that a modified DS can be done on the angular domain instead of the spatial domain, and for complex numbers instead of real numbers.
-Then along the lines of \cite [CaT07], we shall give a bound on expected square error, depending explicitly on the sparsity of the virtual channel matrix and the number of paths of the channel, which will surely future designers, in which the
-Furthermore, it holds under an overwhelming probability, which is also bounded quantitatively.
+In this treatise, we argue that DS is worth trying as an alternative.
+As the next section shows, the effective beamformer serves readily as the sensing matrix with RIP.
+Assuming uniform linear array, the sparsity may be exploited, and a convex program analogous to DS can be used for estimation, which ensures several desirable properties.
+Along the lines of \cite [CaT07], we give a bound on expected square error, expressed in terms of on the sparsity and the number of paths, which will surely faciliate system design.
+We show that it holds under an overwhelming probability, which is also bounded quantitatively.
 
-Lastly, we cast the convex probram to be a second order cone problem to facilitate efficient code.
-We claim that, in view of numerical results, DS is often superior to OMP among other methods in terms of performance, but takes higher complexity.
+Moreover, we illustrate that the convex program is equivalent to a linear program, for which several efficient algorithms are known.
+In view of numerical results, DS is often superior to OMP among other methods, at the cost of higher complexity.
 

### 2020-08-17 treatise/2_problem_setting.tex
Revise: failure plot, two-stage version

--- 2019-10-23 paper/2_problem_setting.tex
@@
 %
-\DispNum {a,y';VC,nh} {
+\DispNum {a:y':VC:nh} {
 \NC \V {a} \SB {\psi'}
 \in \NC \MB {V} _\MB {C} \SB {N_H} \NR
+%
 \NC \V {a} \SB {\psi'}
@@
 %
-\DispNum {H,H;l0,ql} {
+\DispNum {H:H:l0:ql} {
 \NC \M {H}
@@
 %
-\DispNum {f,l;2p,2p} {
+\DispNum {f:l:2p:2p} {
 \NC \f_l
-= \NC \RB {
-  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
-  \; \Rm {Mod}\; \RB {2\pi}
-} \NR
+= \NC 2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
+  \; \Rm {Mod}\; \RB {2\pi} \NR
+%
 \NC \th_l
-= \NC \RB {
-  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
-  \; \Rm {Mod}\; \RB {2\pi}
-} \NR
+= \NC 2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
+  \; \Rm {Mod}\; \RB {2\pi} \NR
 }
@@
 %
-\DispNum {H,H;CN,ql} {
+\DispNum {H:H:l0:ql} {
 \NC \M {H}
-\in \NC \MB {C} ^{N_H \D N_H} \NR
-\NC \M {H}
-=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
+=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
+\in \MB {C} ^{N_H \D N_H} \NR
 }
@@
 
-We consider the hybrid configuration at both transmitter and receiver end.
+\externalfigure [system.png] [wfactor=fit, hfactor=fit]
+
+We consider the hybrid configuration at both transmitter and receiver end, as shown in the figure.
 That is to say, each end consists of both digital and analog percoders and combiners, as follows.
@@
 %
-\Disp {
+\DispNum {F:R:1::R1} {
 \NC \Nm {\M {F} _R \DB {n_H, n_R}}
 = \NC 1, \NR
+%
 \NC \Nm {\M {W} _R \DB {n_R, n_H}}
 = \NC 1, \NR
+%
 \NC n_H
 = \NC 0, \dots N_H-1, \NR
+%
 \NC n_R
@@
 %
-\DispNum {N,H;NY,NY} {
+\DispNum {N:H:NY:NY} {
 \NC N_H \gg \NC N_R \NR
+%
 \NC N_R \gg \NC N_Y \NR
@@
 %
-\Disp {
+\DispNum {Y:Y:WB:BZ} {
 \NC \M {Y}
@@
 %
-\DispNum {v,1;Am,N1} {
+\DispNum {v:1:Am:N1} {
 \NC \RB {\Rm {vec} \SB {\M {A}}} _{\SB {m_1}}
@@
 %
-\DispNum {v,x;x-,x-} {
+\DispNum {v:x:x::x:} {
 \NC \Rm {vec} ^{-1} \SB {\Rm {vec} \SB {x}}
@@
 %
-\DispNum {A,2;Am,N4} {
+\DispNum {A:2:Am:N4} {
 \NC \NC \RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \NR
+%
 \NC =\NC \M {A} _{\SB {\Fl {m_1/N_3 }, \Fl {m_2/N_4 }}}
@@
 \Result
-{Lemma}
+{Proposition}
 {
@@
 %
-\DispNum {v,B;BA,cX} {
+\DispNum {v:B:BA:cX} {
 \NC \Rm {vec} \SB {\M {A}\M {X}\M {B}}
@@
 
-Now, for short we set
+It would seem now appealing to write
 %
-\Disp {
-\NC N_h
-= \NC N_H^2 \NR
-\NC N_y
-= \NC N_Y^2 \NR
-}
-%
-If we had followed the widely accepted approach of compressive channel sensing, we would have written
-%
-\Disp {
+\DispNum {h:h:ve:Nh} {
 \NC \V {h}
 := \NC \Rm {vec} \SB {\M {H}}
-\in \MB {C} ^{N_h} \NR
+\in \MB {C} ^{N_H^2} \NR
 %
@@
 := \NC \Rm {vec} \SB {\M {Y}}
-\in \MB {C} ^{N_y} \NR
+\in \MB {C} ^{N_Y^2} \NR
 %
@@
 := \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
-\in \MB {C} ^{N_y} \NR
+\in \MB {C} ^{N_Y^2} \NR
 %
@@
 := \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
-\in \MB {C} ^{N_y \D  N_h} \NR
+\in \MB {C} ^{N_Y^2 \D N_H^2} \NR
 }
@@
 %
-\Disp {
+\DispNum {y:y:Qh:hz} {
 \NC \V {y}
@@
 \stopsection
-\startsection [title={Working in the Angular Space}]
+\startsection [title={The Angular Space}]
 
@@
 %
-\Disp {
+\DispNum {K:K:CN:H1} {
 \NC \M {K} \in  \NC \MB {C} ^{N_H \D N_H} \NR
+%
 \NC \M {K} \DB {n_1, n_2}
 = \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N_H}, \NR
+%
 \NC \Q n_1, n_2
@@
 %
-\Disp {
+\DispNum {K:K:I:::I} {
 \NC \M {K}^\Adj \M {K}
@@
 %
-\Disp {
+\DispNum {G:G:KH:HK} {
 \NC \M {G}
@@
 %
-\Disp {
+\DispNum {Y:Y:WB:NY} {
 \NC \M {Y}
-=\NC \M {W} _B \M {W} _R \M {K} \cdot \M {G} \cdot \M {K}^\Adj \M {F} _R \M {F} _B
+=\NC \M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\Adj \M {F} _R \M {F} _B
 +\M {W} _B \M {W} _R \M {Z}
@@
 If at the end of day, \m {\M {G}} is sparse, then we recover \m {\M {G}} instead, and our use of DS is fully justified.
-
-That is to say, a similar Kronecker product may be used.
 To simplify notation, set
 %
-\Disp {
+\DispNum {P:P:FB:Nh} {
 \NC \M {P}
 :=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
-\in \MB {C} ^{N_y \D  N_h} \NR
+\in \MB {C} ^{N_Y^2 \D N_H^2} \NR
 }
@@
 %
-\Disp {
+\DispNum {g:g:ve:Nh} {
 \NC \V {g}
 := \NC \Rm {vec} \SB {\M {G}}
-\in \MB {M} _{\MB {C}} \SB {N_h} \NR
+\in \MB {M} _{\MB {C}} \SB {N_H^2} \NR
 }
@@
 %
-\Disp {
+\DispNum {y:y:Pg:gz} {
 \NC \V {y}
@@
 and \m {\M {Y} \in \NC \MB {C} ^{N_Y \D N_Y}}.
-\item Find \m {\M {P} \in \MB {C} ^{N_y \D  N_h}}, \m {\V {y} \in \MB {C} ^{N_h}} as in above.
+\item Find \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
 \item Calculate
 %
-\Disp {
+\DispNum {g:g:mi:DS} {
 \NC \Hat {\V {g}}
 \LA \NC \startcases
-\NC \Min {\V {g}' \in \MB {C} ^{N_h}}  \MC \VNm {\V {g}'} _1 \NR
+\NC \Min {\V {g}' \in \MB {C} ^{N_H^2}}  \MC \VNm {\V {g}'} _1 \NR
+%
 \NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\Rm {DS}} \NR
@@
 %
-\Disp {
+\DispNum {G:G:ve:1g} {
 \NC \Hat {G}
@@
 %
-\Disp {
+\DispNum {H:H:KG:GK} {
 \NC \Hat {\M {H}}
@@
 
-It, then, will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.
-
 \stopsection

### 2020-08-17 treatise/3_1_almost_sparsity.tex
Revise: failure plot, two-stage version

--- 2020-02-27 paper/3_1_almost_sparsity.tex
@@
-\startsection [title={Almost-Sparsity of Angular Channel Response}]
+\startsection [title={Angular Channel Response is Almost-Sparse}]
+
 \startsubsection [title={Norm of Array Response}]
 
-Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity index \m {s} be given.
-Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MS {A}}}}, the largest \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MS {A}}}} the next \m {s} largest components of \m {\V {g}}, and \m {\V {g} _{\SB{\MS {C}}}} are the components complement to \m {\V {g} _{\SB{\MS {A}}}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MS {A}}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\SB{\MS {B}}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\SB{\MS {A}}} =\IP {-1,0,-4,2,0}}.
+Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity index \m {S} be fixed.
+Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MS {A}}}}, the largest \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MS {B}}}} the next \m {s} largest components of \m {\V {g}}, and \m {\V {g} _{\SB{\MS {C}}}} are the components complement to \m {\V {g} _{\SB{\MS {A}}}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MS {A}}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\SB{\MS {B}}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\SB{\MS {C}}} =\IP {-1,0,-4,2,0}}.
 In this section, the subscripts \m {\MS {A}, \MS {B}, \MS {C}} will keep bearing analogous meaning.
@@
 We hope that \m {\VNm {\V {g} _{\SB{\MS {C}}}} _1} is small.
-If so, we shall substitute the quantity into the expected square error of DS, thus generalizing the original argument.
-Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and \m {\M {G}} is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
-We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity \m {s}.
+If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
+Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
+We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity \m {s}, different from \m {S}.
 If \m {N_H} is large, we may forget for a moment the requirement that \m {s =1,2,3,\dots}.
@@
 %
-\Disp {
+\DispNum {a:2:Ka:22} {
 \NC \VNm {\V {a} \SB {\f} _{\SB{\MS {C}}}} _2 ^2
@@
 %
-\Disp {
-\NC \Nm {x - \F {x^3} {6}} \leq \NC \Nm {\sin x}. \NR
+\DispNum {x:6:si:nx} {
+\NC \Nm {x - \F {x^3} {6}}
+\leq \NC \Nm {\sin x}. \NR
 }
@@
 %
-\Disp {
+\DispNum {b:1:1N:C1} {
 \NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
@@
 %
-\Disp {
+\DispNum {b:1:1N:NH} {
 \NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
@@
 \Result
-{Lemma}
+{Proposition}
 {
-Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in {b-f'-Ka-af'}.
+Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in \Rf {b:f':Ka:af'}.
 Then, for any random instance of \m {\f},
@@
 %
-\Disp {
+\DispNum {g:1:l0:a'1} {
 \NC \VNm {\V {g} _{\SB{\MS {C}}}} _1
@@
 %
-The quantity \m {(1/L) \sum _{l=0} ^{L-1} \Nm {\a_l}} is a sample mean, and we may want to use Hoeffding inequality.
-Since it requires that the random variable shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2}, on which there is 95\% probability mass.
+The quantity
+\DispNum {1:l:::} {
+\NC \NC \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
+}
+is a sample mean, and we may want to use Hoeffding inequality.
+Since it requires that the random variable shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2}, on which there is 95 percent of the probability mass.
 %
@@
 %
-\Disp {
+\DispNum {E:1:2p':2p'} {
 \NC \MB {E} \SB {\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
@@
 %
-Now we have \m {\VNm {\M {g} _{\SB{\MS {C}}}} _1 /\RB {\log N_H}^2 \leq 12 \R{2} /\pi ^{5/2} \leq 4/3}.
+Now we have
+\DispNum {g:2:12:43} {
+\NC \F {\VNm {\M {g} _{\SB{\MS {C}}}} _1} {\RB {\log N_H}^2}
+\leq \NC \F {12 \R{2}} {\pi ^{5/2}}
+\leq 4/3. \NR
+}
 %
 \Result
-{Lemma}
+{Proposition}
 {

### 2020-08-17 treatise/3_2_confirming_restricted_isometry.tex
Revise: failure plot, two-stage version

\startsection [title={Restricted Isometry of Effective Beamformer}]

\startsubsection [title={Design of Beamformer Matrices}]

Our plan is setting the four precoder matrices to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.

Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ Normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_Y}}} follows Rayleigh distribution.
\m {\RB {\M {W} _B ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.

In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane.
\m {\RB {\M {W} _R ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.

It turns out we have results that guarantee that both \m {\M {F} _B ^\Tr} and \m {\M {F} _R ^\Tr} are RIP, and same can be said of \m {\M {W} _B} and \m {\M {W} _R}.
Consider a sparse \m {\V {u}} or unity norm, then we are sure that \m {\M {F} _R ^\Tr \V {u}} has almost unity norm.
If, furthermore, \m {\M {F} _R ^\Tr \V {u}} is sparse, we see that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has almost unity norm, and the RIP of \m {\M{P}} also follows by construction.

However, it is not clear that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, have RIP, nor that, \m {\M {P}}, the result of Kronecker product, is RIP.
In fact, the statement seems to be false in general.
Indeed, since a \m {\M {F} _R ^\Tr} of the same \m {\d} is sparse, up to a factor of isometry matrix, and \m {\M {F} _R ^\Tr} is generated randomly, it would seem to us that the probability that \m {\M {F} _R ^\Tr \V {u}} be sparse is exceedingly small.

But all is not lost.
At least we have made sure that \m {\M {F} _R ^\Tr \V {u}} has norm close to unity.
If we have a stronger result, that \m {\M {F} _B ^\Tr \V {u}} is almost unitary even for \It {not-sparse} vectors, then we are done.
That does sound somehow plausible, considering the Normal entries of \m {\M {F} _B ^\Tr} would introduce a Central-limit-theorem-like sum, though the summands are not independent, but weakly dependent.

\stopsubsection

\startsubsection [title={Operator Norm of Digital Beamformers}]

To start, use \m {\chi _{i,j}} to denote Complex Standard Normal random variables, and to simplify notation, let them be independent if they have different arguments.
With this,
%
\DispNum {C':C':WB:j2} {
\NC \VNm {\M {W} _B \V {u}} _2
=\NC \R {
   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \F {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
}
%
Essentially, we seek for a large- deviation result for i.i.d.\ sum of chi-square random variables now.
To so so, we may apply Lemma 1 in Laurent and Massart \cite [LaM00] for equal weights.
By some calculation, we have upper tail inequality, for \m {x > 0},
%
\DispNum {P:x:ex:ex} {
\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_B}} + \F {2x} {N_B}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
And lower tail inequality
%
\DispNum {P:x:ex:ex!} {
\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 + 2 \R {\F {x} {N_B}}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for failure probability.

\Result
{Proposition}
{
For \m {0 <\d_s <1},
%
\DispNum {W:1:ds:ds} {
\NC \Nm {\VNm {\M {W} _B \V {u}} _2 ^2 - 1}
\geq \NC \d_s \NR
}
holds for probability \m {p}, with
\DispNum {1:p:2e:s4} {
\NC 1 -p
\leq \NC 2 \Ss {e} ^{-N_B \R {\d_s} /4} \NR
}
}

\stopsubsection

\startsubsection [title={Operator Norm of Analog Beamformers}]

Here, we consult Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' collected in \cite [KlM17].
We need their Thm.\ 4.5; it gives a RIP guarantee w.r.t.\ \m {\d_s}, and probability lower bound, for DFT submatrix.
The estimation they give involve is expressed in terms of big- \m {\O} and big- \m {O}, and since our methodology is 
However, it can be seen that their argument allows precise constants, and they just did not spell out, which we briefly explain.
Roughly, they use Chernoff-Hoeffding bounds, but write the exponent in the form of \m {\Omega}.
Starting in their Thm.\ 2.2, we may substitute (say) \m {C \leftarrow 1/3} in place of their big- \m {\Omega}.
The conclusions, their Thm.\ 3.7 and Thm.\ 4.5, may be changed accordingly.
If modified with respect to our setting, the condition
%
\DispNum {N:R:sd':NH} {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
}
%
guarantees a failure probability \m {\d_s /N_H s}.
We would like to drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \Rf {N:R:sd':NH}.

\Result
{Theorem}
{
Suppose
%
\DispNum {N:R:sd'NH} {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
}
%
Then \m {\M {F}_R} (resp.\ \m {\M {W} _R}) has \m {\d_s}-RIP for probability \m {p}, with
\DispNum {1:p:ex:d's} {
\NC 1 -p
\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
}
}

\stopsubsection

\startsubsection [title={Confirming the Restricted Isometry}]

So, how do we relate RIP of \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} to that of \m {\M {P}}?
Notice, by the nature of operator norm,
\DispNum {P:2:FB:WR} {
\NC \VNm {P} _2
=\NC \VNm {\M {F}_B^\Tr \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \NR
}
Indeed, if it were not for the sparsity constraint, if both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {F}_B^\Tr \M {F}_B^\Tr} are \m {\d_s}-RIP, \m {\M {P}} has approximately \m {2\d_s}-RIP.
However, it is doubtful to assume that the Kronecker product of two RIP matrices exhibit RIP.

We suggest the following argument.
If all angles \m {\th_l, \f_l} are on exactly on the grid, then, with overwhelming probability, it is possible to write
\DispNum {G:G:Ud:dU} {
\NC \M {G}
=\NC \M {U} \Rm {diag} \SB {\V {d}'} \M {U} ^\Adj \NR
}
for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}}.
Clearly,
\DispNum {G:2:g2:g2} {
\NC \VNm {\M {G}} _2
=\NC \VNm {\V {g}} _2 \NR
%
\NC =\NC \VNm {\Rm {abs} \SB {\V {g}}} _2 \NR
}
where \m {\Rm {abs}} denotes elementwise taking absolute value.
Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\Adj \M {K}^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s}-RIP too, we see
\DispNum {W:2:WB:d's} {
\NC \NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} \M {U} \D
   \Rm {diag} \SB {\Rm {abs} \SB {\V {d}'}} \D
   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} \M {U}
   \R {\Rm {abs} \SB {\V {d}'}} \D
   \R {\Rm {abs} \SB {\V {d}'}}
   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} \M {U}
   \R {\Rm {abs} \SB {\V {d}'}}} _2 \D
   \VNm {\M {F} _B ^\Adj \M {F} _R ^\Adj \M {K} \M {U}
   \R {\Rm {abs} \SB {\V {d}'}}} _2 \NR
%
\NC \eqsim \NC \VNm {\M {G}} _2 \RB {1 +2\d_s} \NR
}
Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s}-RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant \m {\V {g}} in accordance to the form of \Rf {H:H:l0:ql}.

\stopsubsection

\stopsection

### 2020-08-17 treatise/3_3_generalizing_the_dantzig_selector_bound.tex
Revise: failure plot, two-stage version

--- 2020-02-27 paper/3_3_generalizing_the_dantzig_selector_bound.tex
@@
 \startsection [title={Generalizing the Dantzig Selector Bound}]
-\startsubsection [title={Technical Lemmata in Complex Case}]
+\startsubsection [title={Technical Propositions in Complex Case}]
 
@@
 %
-And our task is to bound the error norm \m {\VNm {\V {d}} _2}, where \m {\V {d} =\V {g} - \Hat {\V {g}}}.
+And our task is to bound the error norm \m {\VNm {\V {d}} _2}.
 
-We argue that \m {\V {g}} can essentially be seen as sparse, and for that purpose we ignore relevent terms.
-Also, we do not seek a very tight bound and will approximate \m {\d_{S}} by \m {1}.
+We argue that \m {\V {g}} can essentially be seen as sparse, and for that purpose we approximate irrelevent terms.
+For example, we generously bound \m {\d_{S}} by \m {1}.
 And, as shall be seen, it suffices to set
@@
 %
-The lemmata below are taken from \cite [CaT07] and modified slightly in accordance to our settings, except possibly the generalization to complex vector.
+The propositions below are taken from \cite [CaT07] and modified slightly in accordance to our settings, except possibly the generalization to complex vector.
 %
 \Result
-{Lemma}
+{Proposition}
 {
@@
 %
-\Disp {
+\DispNum {g:1:gd:g1} {
 \NC \VNm {\V {g}} _1
@@
 %
-On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
+Also, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
 %
-\Disp {
-\NC \leq \NC \VNm {\V {g}} _1 \NR
+\DispNum {g:1:g1:g1} {
+\NC \VNm {\hat {\V {g}}} _1
+\leq \NC \VNm {\V {g}} _1 \NR
 }
-%
-To prove the next result, fix an instance of \m {\M {P}} and instance of \m {\V {z}}.
+as desired.
+
+We turn our attention to the next result, and fix an instance of \m {\M {P}} and instance of \m {\V {z}}.
 We claim that
@@
 %
-This follows by the fact that \m {\M {P} _{\SB {:, n_g}}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}, the quantity \m {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}} observes Standard Normal.
+Start with the fact that \m {\M {P} _{\SB {:, n_g}}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
+Now, the quantity \m {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}} observes Standard Normal.
 To bound the failure probability, recall the tail bound for \m {Q} function
@@
 %
-Lastly, the following two lemmata is taken from \cite [CaT07], Lemma 1.
+Lastly, the following two propositions are taken from \cite [CaT07], Lemma 1.
 The generalization from real vector spaces to complex spaces is completely straightforward, while meaning of magnitude and inner product has to be changed.
-One of them reads
+One of the quoted propositions reads
 %
@@
 %
-By power mean inequality, we get a statement cruder than \Rf {d:2:dA:12} that
+By power mean inequality, we get a statement cruder than \Rf {d:2:dA:12}, as below.
 %
 \Result
-{Lemma}
+{Proposition}
 {
@@
 %
-The other one of them reads
+The other quoted proposition reads
 %
@@
 Let \m {\M {Q}'} be fixed.
-For all \m {s_1}-sparse \m {\V {x}_1}, for all \m {s_2}-sparse \m {\V {x}_2}, whose positions for nonzero components are disjoint,
+For all \m {s_1}-sparse \m {\V {x}_1}, for all \m {s_2}-sparse \m {\V {x}_2}, whose nonzero-positions are disjoint,
 %
-\Disp {
+\DispNum {d:2:in:x2} {
 \NC \T {\d} _{s_1, s_2}
@@
 Therefore
-\Disp {
+\DispNum {d:s:2s:2s} {
 \NC \d_{2s'}
@@
 
-We are going to combine previous lemmata and show the main result.
+We are going to combine previous propositions and show the main result.
 For simplicity, set \m {S = Ls^2}, thus
@@
 %
-And
+And, for concreteness,
 %
@@
 }
-To prove this, we simplify the expression for \m {\VNm {\V {d} _{\SB{\MS {AB}}}} _2} in \Rf {d:2:11:C1} and the one for \m {\VNm {\V {d} _{\SB{\MS {C}}}} _1} in \Rf {d:1:dA:C1} and 
-In this section we substitute rough numbers.
+To prove this, we simplify the expression for \m {\VNm {\V {d} _{\SB{\MS {AB}}}} _2} in \Rf {d:2:11:C1} and the one for \m {\VNm {\V {d} _{\SB{\MS {C}}}} _1} in \Rf {d:1:dA:C1}.
+In the below, we take the freedom to substitute rough numbers.
 
@@
 %
-\Disp {
+\DispNum {d:1:Sd:C1} {
 \NC \VNm {\V {d} _{\SB{\MS {A}}}} _1

### 2020-08-17 treatise/4_simulation.tex
Revise: failure plot, two-stage version

--- 2020-06-09 paper/4_simulation.tex
@@
 \item Input \m{\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
-\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to \Rf {t---01-Nh}, \Rf {A-i-Ui-h1}, \Rf {A-i-Ui-h1-"}.
+\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to \Rf {t---01-Nh}, \Rf {A-i-Ui-21}, \Rf {A-i-Ui-21-"}.
+
 \item Calculate
@@
 %
-\Disp {
+\DispNum {
 \NC \Hat {G}
@@
 %
-\Disp {
+\DispNum {
 \NC \Hat {\M {H}}
@@
 
+\startsection [title={A Two-Stage Estimation}]
+
+We also tried another version of DS, in which DS is done for a second time in estimated nonzero-position.
+The two-stage method was briefly mentioned \cite [CaT07] but without further validation by numerical experiments.
+The method starts by applying DS as before.
+Then, we extract largest positions of the estimated vector, and apply DS again.
+Last, we extract largest positions again, and apply LS.
+Note that the final vector has to be scrambled back to the original dimension.
+
+\Result
+{Algorithm}
+{
+\startitemize[n]
+\item Let \m {\g_{\Rm {DS}} \geq 0} be given, and \m {\M {P}}
+
+\item Set
+\Disp {
+\NC N_0
+=\NC 2 N_H^2, \NR
+\NC N_2
+=\NC \lfloor 4 \log N_H \rfloor, \NR
+\NC N_1
+=\NC \lfloor \R {N_0 N_2} \rfloor \NR
+}
+
+\item Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}, call the \m {N_1} largest component of \m {\Hat {\V {g}}_0} and to be \m {\V {g}_1}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _1}.
+
+\item Apply DS to \m {\V {y}, \M {P}_1} to get \m {\Hat {\V {g}}_1}, call the \m {N_2} largest component of \m {\Hat {\V {g}}_1} and to be \m {\V {g}_2}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _2}.
+
+\item Apply least square to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}, which corresponds to \m {\Hat {\V {g}}}.
+\stopitemize
+}
+
+It may be appropriate to scale \m {\g_{\Rm {DS}}} with respect to \m {N_H}.
+It is not clear to us for now what is most reasonable choice of \m {N_1, N_1, N_2}.
+
 \stopsection
@@
 
+To get some idea of the order of magnitude of noise-to-signal level, plug in some actual numbers.
+Consider only path loss in the simplest form according to Friis Law.
+Suppose the power of mobile phone antenna is 0.25 W,
+the carrier frequency is 5GHz,
+the base station is \m {1.5} km away,
+the noise is \m {–40} dB W.
+The noise-to-signal ratio would be
+\DispNum {1:8:02:24} {
+\NC 10^{-4} \F {1} {0.25} \R {\F {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
+=\NC 0.224 \NR
+}
+In the following simulation, we use dimensionless noise-to-signal level \\ \m {\s = 2^{-4}, 2^{-3.5}, 2^{-3}, 2^{-2.5}, 2^{-2}, 2^{-1.5}, 2^{-2}}.
+
 We do three series of experiments, which are of size from small to large.
-In the following experiments, we take respectively \m {N_H} to be \m {16, 32, 48}, \m {N_Y} to be \m {\log N_H} (giving \m {3, 3, 4}), \m {N_R} to be \m {\RB {\log N_H}^2} (giving \m {8, 12, 15}).
+In the following experiments, we take respectively \m {N_H} to be \m {8, 12, 16, 20, 24}.
+\m {N_Y} is set to be \m {\lfloor \log N_H \rfloor}, giving \m {2, 2, 3, 3, 3}.
+\m {N_R} to be \m {\lfloor \RB {\log N_H}^2 \rfloor}, giving \m {4, 6, 7, 9, 10}.
+Unfortunately, this is very far from achieving the design values \Rf {N:B:4l:H2}, and this may be part of the reason the results is not as successful as expected.
 
@@
 The number of paths \m {L} is \m {4}.
-The wavelength of the EM wave that antenna is emitting, \m {\l _{\Rm {ant}} = 1}, is set to be \m {0.1}.
-and the antenna spacing \m {d _{\Rm {ant}} =3}.
-Note that only their ratio matters.
-See chapter 2 for meaning of them.
+The wavelength of carrier \m {\l _{\Rm {ant}}}, is set to be \m {0.1}.
+and the antenna spacing \m {d _{\Rm {ant}} =0.2}.
+Only their ratio matters.
 
-There are also parameters related to the convex optimization algorithm.
-The tolerance of absolute error in the primal-dual algorithm used in CVXPY is set as \m {10^{-4}}, and the tolerance of relative error, as \m {10^{-3}}.
+For parameters related to the convex optimization algorithm, the tolerance of absolute error in the primal-dual algorithm used in CVXPY is set as \m {10^{-4}}, and the tolerance of relative error, as \m {10^{-3}}.
 The maximal number of iteration of CVXPY is set to be \m {32}.
@@
 Denote the threshold used in DS program to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
-Yet another threshold used for the residue norm used in OMP program is called \m {\eta}.
-Various several values are tried for them, determined as thus: Take a central value roughly corresponding to the theory, and mutiply or divided the central value by powers of 2, or
+Various several values are tried for them by first taking the theory value, and multiply or divide it by powers of 2.
 
@@
 
-Each data point is repeated for 16 times, and taken average.
-We plot the absolute log error
-%
-\DispNum {h':s:lo:vg} {
-\NC \h_{\Rm {abs}}
-=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss {avg}}, \NR
+Yet another threshold used for the remainder norm used in OMP program, \m {\h_{\Rm {OMP}}}.
+For its suggested values, see \cite [CaW11].
+We take \m {2 \R {\log N_H}} for infinity norm constraint, \m {\R {3 N_Y}} for 2-norm constraint.
+
+\startsubsection [title={Performance Metric}]
+
+Lee, Gil, and Lee \cite [LGL16] proposed the proformance metric
+\DispNum {h:h:lo:vg} {
+\NC \chi'
+=\NC \RB {
+   \F {\log_2 {\VNm {\V {h} -\Hat {\V {h}}} _2}}
+   {\log_2 {\VNm {\V {h}}_2}}
+} _{\Ss {avg}}, \NR
 }
-%
-and relative log error.
-%
-\DispNum {h':l:lo:vg} {
-\NC \h_{\Rm {rel}}
-=\NC \F {\h_{\Ss {abs}}}
-{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss {avg}}} \NR
+However, we find that when \m {\VNm {\V {h}}_2} is small, this can blow up.
+
+We propose another metric that is suggestive of spectral efficiency.
+Indeed, since we have not specified the channel, we can't logically use any particular channel capacity expression.
+But we may still adopt the MIMO capacity with perfect CSI, with an estimated quantity for SNR.
+Denote \m {\M {E} = \Hat {\M {H}} - \M {H}}.
+Assume that
+\Disp {
+\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj \V {x} - \M {H} \M {H} ^\Adj \V {x}} _2
+\lesssim 2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}} \NR
 }
-%
-The averaged error values are plotted along with the bound of error norm.
-As a basis for comparison, we approximate \Rf {d:2:42:NH} and take log, giving
-%
-\DispNum {h':h:12:H2} {
-\NC \h_{\Rm {th}}
-\eqsim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H +2 \NR
+
+Then \m {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}}} can be considered as part of the noise.
+In view of the MIMO channel, \m {\s} has to be multiplied by factor \m {\R {N_H}}, and \m {\VNm {\M {H}} _2} and \m {\VNm {\M {E}} _2} both divided by factor \m {\R {N_H}}.
+Therefore, we define the quantity
+\Disp {
+\NC \chi
+= \log \det \SB {\M {I} + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
 }
+
+Each data point is repeated for 24 times, and taken average.
 
@@
 
-Reasonably, for all methods, a higher \m {\s} corresponds to higher \m {\eta_{\Rm {rel}}} and \m {\eta_{\Rm {rel}}}.
-The trends of absolute and relative error are the same, and in the below we call them simply error.
+Reasonably, for all methods, a higher \m {\s} corresponds to lower \m {\chi}.
+For low noise, DS slightly but steadily outperforms other methods, but for high noise, DS degrades quickly.
 
-From our simulation result, DS has usually the least error.
-For low SNR it is slightly but steadily outperforms OMP, and for high SNR the difference becomes vanishingly small and is sometimes surpassed by OMP.
-Different values of threshold \m {\g_{\Rm {DS}}} matter, and a smaller \m {\g_{\Rm {DS}}} does not necessarily give a lower error.
-It seems \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is intuitive.
+Different values of threshold \m {\g_{\Rm {DS}}} does not seem matter much.
+It appears \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is intuitive.
 
-The error of OMP is slightly higher than DS, but the trend is less steady as well.
-Interestingly, different values of threshold \m {\eta} do not seem to affect much to performance, and often the iteration stablizes much earlier than is constrained by maximum iteration number.
-Lasso has substantially higher error than OMP, and Least Square (pseudo inverse) is still worse.
+For OMP, interestingly, different values of \m {\h_{\Rm {OMP}}} do not seem to affect much to performance, and often the iteration stablizes much earlier than is constrained by maximum iteration number.
+Lasso and Least Square usually has substantially lower \m {\chi} than OMP.
 
-Lastly, the bound for error norm of DS is much looser than the actual perfomance, and is well above the Least Square line, making it the highest line of all.
-Our bound is correct but not tight enough.
+The theory bound of DS is an overestimation for low noise, but underestimation for high noise.
+This suggest our bound is correct but not tight.
+
+\blank [big]
+\externalfigure [scatter-ddss-success.png] [wfactor=300]
+
+The figure above illustrates a case where DS succeeded.
+The true values of \m {\M {H}} entries are ordered with respect to absolute value, and corresponding estimated value in the first and second stage, are plotted agains the true values.
+We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.
+The subsequent application of DS on this smaller index set refines the estimated values.
+
+\blank [big]
+\externalfigure [scatter-ddss-failure.png] [wfactor=300]
+
+The figure above illustrates a case where DS succeeded.
+We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.
+Subsequent application of DS on the wrong index set fails, as a result.
 
@@
 
-There is an analysis in \cite [BoV04] of inequality constrained Newton method, in which they assumed self-concordance (discussed in p.496ff there, see also p.531).
-It is mentioned in Candès and Romberg \cite [CaR05] that the complex DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.
-However, it is not clear that Newton method is the fastest, nor that they are utilized in CVXPY.
-Specifically, the implementers of CVXPY, Diamond and Boyd \cite [DiB16], alleges that the program is usually converted in to primal-dual problem, and there are several different approaches in solving a primal-dual problem.
-But for our purpose, we only discuss the complexity analysis for Newton method.
+There is an analysis (Boyd and Vandenberghe \cite [BoV04]) of inequality constrained Newton method, in which they assumed self-concordance (p.496ff, also p.531).
+It is also pointed out (Candès and Romberg \cite [CaR05]) that the complex DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.
+
+However, it is not clear whether these results hold for methods faster than Newton method, and of course they are not necessarily utilized the same way in CVXPY.
+Specifically, the implementers of CVXPY, Diamond and Boyd \cite [DiB16], alleges that the program is usually converted in to primal-dual problem, for which and there are several different approaches.
+For our purpose, we only discuss the complexity analysis for Newton method.
 
@@
 Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
-Then \cite [BoV04] (p.505, eq.9.56) gives a bound of the number of iteration of Newton method.
-If just take that as the complexity bound for DS, it becomes
+Then (\cite [BoV04] p.505, Eqn.\ 9.56) gives a bound of the number of iteration of Newton method.
+If we just take that as the complexity bound for DS, it becomes
 %
@@
 
-Since we are doing big-O analysis, we feel that we have more license on making approximation.
-For concreteness, we may assume that we start the iteration by specifying the Least Square estimator as the initial value of \m {\V {g}_0}, namely
+Every step involves a inversion of \m {\MS {O} \SB {\M {P} ^\Adj \M {P}}}, which is of the same order of magnitude to the time needed for matrix multiplication.
+Since the dimension of \m {\M {P} ^\Adj \M {P}} is \m {N_H^2}, the cost of inversion is \m {\MS {O} \SB {N_H^4}}.
+
+We now take some license to approximate.
+Assume that we start the iteration by specifying the Least Square estimator as the initial value of \m {\V {g}_0}, namely
 %
@@
 %
-If we drop it, we may write the complexity of DS to be, simply,
+By above, we may write the complexity of DS to be
 %
@@
 \NC C_{\Rm {DS}}
-=\NC \MS {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} \NR
+=\NC \MS {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} N_H^4 \NR
 }
 %
-For simplicity we assume
+Also assume
 %
-\DispNum {g:;g:,:g;} {
+\DispNum {g:g:g;:;g} {
 \NC \V {g} ^\star
@@
 %
-Thus
+Thus, by \Rf {g:0:gL:Py}, \Rf {C:S:Og:g1}, and \Rf {g:g:g;:;g},
 %
-\Disp {
+\DispNum {C:S:Og:z1} {
 \NC C_{\Rm {DS}}
@@
    \VNm {\V {g} +\RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {z}
-   -\V {g}} _1} \NR
-\NC =\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} \NR
+   -\V {g}} _1} N_H^4 \NR
+\NC =\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} N_H^4 \NR
 }
@@
 %
-\Disp {
+\DispNum {O:j:sO:O1} {
 \NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
@@
 It is easy to see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes Complex Standard Normal distribution.
-and is easily bounded by \m {\s}.
+If the quantity can be estimated by \m {\s}, we have
 %
-\DispNum {::;ON,2s;} {
+\DispNum {C:S:ON:H6} {
 \NC C_{\Rm {DS}}
-=\NC \MS {O} \SB {N_{H}^2 \s} \NR
+=\NC \MS {O} \SB {N_{H}^6} \NR
 }
@@
 %
-\DispNum {C:O:ON:NY} {
+\DispNum {C:P:ON:NY} {
 \NC C_{\Rm {OMP}}
@@
 
-In summary
-%
-\DispNum {C:P:CD:H2} {
-\NC C_{\Rm {OMP}}
-\approx \NC C_{\Rm {DS}} \NR
-\NC \approx \NC \s \MS {O} \SB {N_H^2} \NR
-}
+Lastly, since LS involves the same target function as DS, the same argument is valid, giving \m {C_{\Rm {Lasso}} =\MS {O} \SB {N_H^6}}.
 
@@
 
-Besides analytical bound, our result shows that DS indeed exhibits high complexity when (in our case) \m {N_H} grows, and the such rate of growth is significant, 
-Such computation cost is not suprising, even without knowing implementation details, from the nature of convex programming, being an iterative and random alrogithm.
-Moreover, DS requires a sizable memory for holding not only (in our case) \m {\M {P}}, and matrix multiplication of dimension \m {\M {N}_H^2}.
-Friedlander and Saunders \cite [FrS07] criticizes, according to their numerical experiments, that DS often gives a higher computational cost, compared to Lasso, corroborating our observation, 
-However we note that different settings of \m {\z}, tolerance of error, or maximal iteration number result in vastly different computation time.
+Friedlander and Saunders \cite [FrS07] criticizes that DS often gives a higher computational cost, compared to Lasso.
+Agreeing their observation, simulation result shows that DS indeed exhibits high complexity when (in our case) \m {N_H} grows.
+It is not suprising from the nature of convex programming.
+On one hand, the algorithm is iterative and random.
+On the other hand, it requires a sizable memory when finding the inversion of (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
+However we note that different tolerance of error and value of maximal iteration number may result vastly different computation time.
 
-On the other hand, we see the complexity of OMP is several order of magnitude lower than that of DS.
+Meanwhile, we see the complexity of OMP is several order of magnitude lower than that of DS.
 This is reasonable, given that it is a greedy alrogithm.
@@
 
-Since LS involves the same target function as DS, the same argument also gives \m {C_{\Rm {Lasso}} =\MS {O} \SB {N_H^2}}.
-The numerical 
-We are not going to further discuss Lasso.
+Lasso usually takes time \m {1/2} to \m {1/4} of that of DS.
 
@@
 \stopchapter
-
-\stoptext
-
-\DispNum {t:::01:Nh} {
-\NC \V {t}
-= \NC \startTheMatrix
-\NC \V {0} \NR
-\NC \V {1} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-%
-\NC \V {x}'
-= \NC \startTheMatrix
-\NC \T {\V {g}}' \NR
-\NC \V {m} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-}
-%
-with
-%
-\DispNum {A:i:Ui:h1} {
-\NC \M {A}_i
-= \NC \startTheMatrix
-\NC \T {\M {U}}_{i}, \NC \M {0} \NR
-\stopTheMatrix
-\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
-%
-\NC \V {b}_i
-= \NC \V {0}
-\in \MB {R} ^{2 N_H^2} \NR
-%
-\NC \V {c}_i
-= \NC \startTheMatrix
-\NC \V {0} \NR
-\NC \V {u}_{i} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-%
-\NC d_i
-= \NC 0 \NR
-%
-\NC i 
-= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
-}
-
-And
-%
-\DispNum {A:i:Ui:h1} {
-\NC \M {A}_i
-= \NC \startTheMatrix
-\NC -\T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
-\stopTheMatrix
-\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
-%
-\NC \V {b}_i
-=\NC \T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\V {y}}
-\in \MB {R} ^{2 N_H^2} \NR
-%
-\NC \V {c}_i
-= \NC \V {0}
-\in \MB {R} ^{3 N_H^2} \NR
-%
-\NC d_i
-= \NC \g_{\Rm {DS}} \NR
-%
-\NC i 
-= \NC N_H^2, N_H^2 +1, N_H^2 +2, \ldots, 2 N_H^2 -1 \NR
-}

### 2020-08-17 treatise/5_conclusion.tex
Revise: failure plot, two-stage version

--- 2019-10-23 paper/5_conclusion.tex
@@
 
-We cannot think OMP, or indeed every algorithm, as a universal solution.
-OMP trades off precision for time and space complexity, and for DS the other way around is true, hence we cannot say which is definitely better than the other.
-All in all, different problems requires different technique and algorihm within the current constraint, as is probably true in every discipline of engineering.
+OMP trades off precision for time and space complexity, and for DS the other way around is true, hence we cannot say which one is universally better than the other.
+The investigation eloquently illustrates the fact that different problems requires different technique and algorihm within the current constraint, as is probably true in every discipline of engineering.
 

### 2020-08-17 treatise/abstract.tex
Revise: failure plot, two-stage version

\starttitle [title={Abstract}]

Multiple-input-multiple-output (MIMO) is the next-generation standard of wireless communication.
However, for MIMO system it is not easy to estimate the channel, while many communication algorithms often requires that the channel state information be known at the receiver.
Meanwhile, the millimeter wave (mm-Wave) band, often used in MIMO context, is known to exhibit sparsity, and results on compressive sensing suggests that sparsity implies that fewer channel measurement shall suffice.
For that reason, Orthogonal Matching Pursuit (OMP) is usually used, as it has a very lower complexity.
However, Dantzig Selector (DS), proposed by Tao and Candès, has long been introduced and ignored.
DS has several promising properties, and it is curious how it fares on the present problem.

In this treatise, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
Using pilot signal and designed random beamformer, we apply DS for channel estimation, arguing in favor of its greater generality, its tolerance of noise corruption, and its lower averaged error.
The treatise also gives a bound for the expected square error of DS, as well as bounded probability of success, and in so doing, showing dependency on the number of path and channel sparsity.

DS can be cast as a second order cone problem (SOCP), so that well known methods for convex programs may be used.
Simulation is done on DS and other methods, and we discuss their respective merits.
It turns out DS is often slightly better than other alternatives, while it has siginificantly greater complexity.

\stoptitle

### 2020-08-17 treatise/conclusion.tex
Revise: failure plot, two-stage version

\startchapter [title={Conclusion}]

This treatise studied the effective estimation of the millimeter wave, multiple-input, multiple-output (mm-wave MIMO) channel.
We adopts the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), which is most commonly used in literature, as the estimation algorithm, therefore exploiting the sparsity of the problem in spacial Fourier domain.
We bounded the expected square error following the spirit of Candès and Tao \cite [CaT07].
Towards that end, we characterized the spacial sparsity, confirmed the restricted isometry of measurement matrix \m {\M {P}}, and justified the generalization for complex vectors.
The bound assumes a fairly general setting, and is expressed in terms of physical parameters, such as the number of path \m {L} and channel dimension \m {N_H}.

Simulation is done, and DS's performance is compared to OMP, Lasso, and LS.
DS performs slightly better than others, but gives much higher complexity, agreeing our analysis.
Put concisely, no algorithm is a universal solution, as they trade off precision for time and space complexity, or conversely, among other things.
We hope that our inquiry of DS suggests a welcomed alternative added to the present literature of channel estimation.

\stopchapter

### 2020-10-21 presentation/1_introduction.tex
Rev `.gitignore`, rightly commit all images

@@
 \Title {\TitleText}
-\Subtitle {Numerical Experiments}
 \blank [big]
@@
 
-\Subsubtitle {\DateText}
+\Subsubtitle {\InstitutionText}
 
@@
 
-\I Bound for the Error Norm
+\I Error Analysis
 
@@
 
-\I Conclusion and References
+\I Conclusion
 }
@@
 {
-\I Multiple-input multiple-output (MIMO) communication system has been proposed as part of the 5G specification, but its hardware overhead increases complexity and power consumption.
+\I Multiple-input multiple-output (MIMO) systems \\ have been suggested in 5G communication.
 
-\I The design of various algorithms requires channel information to be known.
+\I Estimation of MIMO channels results in high complexity, due to a large number of antennae.
 
-\I Estimation of MIMO channels also results in high complexity, due to the large number of antennae.
+\I Meanwhile, millimeter wave (mm-Wave) channels are often sparse due its poor scattering nature
 
-\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we might exploit to reduce complexity.
+\I According to compressive sensing theory, we might exploit the sparsity to reduce complexity of estimation procedure.
 }
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Compressive Sensing}
+{
+\blank [big]
+\externalfigure [compressive-sensing.png] [factor=fit]
+
+\I The signal as shown in is not sparse in the basis on the left, but it is in the basis on the right.
+
+\I Thus, the recovery from just a few components are able to approximate it well.
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Work on Compressive Channel Sensing}
+{
+\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)
+
+\I Alkhateeb, Ayach, Leus, Heath (2014): mm-wave channel, adaptive training algorithm for given codebook
+
+\I Alkhateeb, Leus, and Heath (2015): single path mm-wave channel, all-phase-shifter beamformers,
+using Orthogonal Matching Pursuit (OMP)
+
+\I Lee, Lee, and Yong (2016): MIMO mm-wave channel, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Our Contribution}
+{
+\I Consider MIMO mm-wave channel, with hybrid beamforming
+
+\I Use a modified DS (convex programming), instead of OMP (greedy algorithm)
+
+\I Illustrate by experiments that DS has better performance
+
+\I Give an analysis of error norm and successful probability in terms of system parameters
+}

### 2020-10-21 presentation/2_setting.tex
Rev `.gitignore`, rightly commit all images

--- 2020-02-27 presentation/2_setting.tex
@@
-\Frame {Channel Model}
+\Frame {Channel Model and Beamformers}
 {
-\I Consider the uniform linear array
-\Disp {
-\NC \V {a} \SB {\psi'}
-= \NC \F {1}{\R {N_H}} \sum_{n=0}^{N-1} \Ss {e}^{n \psi' \Ss {i}} \V {u}_n
-\in \MB {C} ^{N_H} \NR
-}
+\I Given channel \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array
 
-\I Consider the channel representation
-\Disp {
-\NC \M{H}
-=\NC \sum_{l=0} ^{L-1}
-\a_l
-\V {a} \SB {\f_l'}
-\V {a} \SB {\th_l'}^\Adj
-\in \MB {C} ^{N_H \D N_H} \NR
-}
+\I Complex standard normal noise \m {\m {Z} \in \NC \MB {C} ^{N_H \D N_H}}
 
-\I where \m {L} is the number of paths, \m {\f_l'} is related to the angles of arrival, \m {\th_l'} is related to the angles of arrival.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Precoders and Combiners}
-{
 \I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_Y}}
-
 \I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}
@@
 \I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}
-
 \I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_Y \D N_R}}
 
-\I With the unity magnitude constraint
-\Disp {
-\NC \Nm {\M {F}_R \SB {n_H, n_R}}
-= \NC 1,
-\Q \Nm {\M {W}_R \SB {n_R, n_H}}
-= 1, \NR
-}
-
-\I Under the assumption
-\Disp {
-\NC N_H \gg \NC N_R \gg N_Y \NR
-}
+\I Magnitude constraint \m {\Nm {\M {F}_R \SB {n_H, n_R}} = 1}, \m {\Nm {\M {W}_R \SB {n_R, n_H}} = 1} 
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Effective Channel}
+\Frame {System Diagram}
 {
-\I Consider Complex Standard Normal \m {\M{Z} \in \NC \MB {C} ^{N_H \D N_H}}
+\blank [big]
+\externalfigure [system.png] [factor=fit]
 
-\I Introduce the effective channel
-\Disp {
-\NC \M{Y}
-:=\M{W}_B \M{W}_R \RB {\M{H} \M{F}_R \M{F}_B +\M{Z}} \NR
-}
+\I Problem (a): Recover \m {\M {H}} with knowledge of \\
+\m {\M {Y} :=\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}} }?
 
-\I Summarizing the dimension,
-\Disp {
-\NC \MB {C}^{N_Y}
-\underset {\M{F}_B} {\mapsto} \NC \MB {C}^{N_R}
-\underset {\M{F}_R} {\mapsto} \MB {C}^{N_H}
-\underset {\M{H}} {\mapsto} \MB {C}^{N_H}
-\underset {\M{W}_R} {\mapsto} \MB {C}^{N_R}
-\underset {\M{W}_B} {\mapsto} \MB {C}^{N_Y} \NR
-}
-
-\I How do we \Emph {recover} \m {\M {H}} with knowledge of \m {\M {Y}}?
-
-\I How do we \Emph {design} \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
+\I Problem (b): Design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Transform to the Angular Domain}
+\Frame {Cast to Linear System}
 {
@@
 
-\I Then we have a \Emph {linear equation}
+\I Then we have a underdetermined linear system:
 \Disp {
@@
 }
+
+\I When the signal is sparse, few measurements may be sufficient for the reconstruction
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Proposed Method}
+\Frame {Terminology}
 {
-\I Input \m{\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{N_H^2}}, \m{\g_{\Ss {DS}} \geq 0}.
+\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if at most \m {s} of its components are nonzero.
+
+\I We say that \m {\M {P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
+\Disp {
+\NC \RB {1-\d_s} \VNm {\V {g}} _2^2
+\leq \NC \VNm {\m {P} \V {g}} _2^2
+\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
+}
+
+\I We may think \m {\M {P}} to be almost unitary up to relative error \m {\d_s}.
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Applying Dantzig Selector}
+{
+\I We try to apply Dantzig Selector to our problem:
+
+\I Input \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.
 
@@
 }
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Design of Beamformers}
+{
+\I Let us set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ complex standard normal, up to a design constant
+
+\I And set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed in argument and unity magnitude, up to a design constant
+
+\I We will argue that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, thus \m {\M {P}} has too.
+
+\I Fix sparsity \m {s = L \RB {\log N_H}^2} for concreteness
+}

### 2020-10-21 presentation/3_proof.tex
Rev `.gitignore`, rightly commit all images

@@
-\Frame {Modifying the Original Proof (1/2)}
+\Frame {Error Analysis}
 {
-\I DS works for real matrices, but we generalize by representing a complex number by its real- and imarinary-parts.
+\I What's the difference of true value \m {\V {h}} and estimated value \m {\Hat {\V {h}}}?
 
-\I DS works for sparse vectors, but \m {\M {H}} is not sparse.
-We claim that \m {\M {K}^\Adj \M {H} \M {K}} is almost sparse.
-Call the largest-magnitude \m {S} components of \m {\V{g}} to be \m {\M {g} _{\SB{\MC {A}}}}, and call the remaining vector \m {\M {g} _{\SB{\MC {C}}}}, we have to bound \m {\VNm {\M {g} _{\SB{\MC {C}}}} _1}.
+\I Should account for the fact that \m {\V {g}} is not strictly sparse
+
+\I Should justify that all four beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, have RIP for high probability, thus \m {\m {P}} does too.
+
+\I Should investigate the Big \m {\MC {O}} of error norm by bounding failure events mentioned above.
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Modifying the Original Proof (2/2)}
+\Frame {The Bound}
 {
-\I DS requires the measurement matrix (in our case) \m {P} to have restricted isometry property.
-We shall design all four beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, so that for high probability, they satisfies RIP, thus \m {\m {P}} does too.
-
-\I We know the Big-\m {\MC {O}} of error norm of DS depends on (in our case) \m {N_H}.
-We consider these failure events above, and claim that the algorithm works for high probability.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {\V{g}} is Almost Sparse}
-{
-\I Suppose for concreteness,
-\Disp {
-\NC S
-= L \log N_H,
-\Q \d_S
-\leq \F {1} {8} \NR
-}
-
-\I We may show that 
-\Disp {
-\NC \VNm {\M {g} _{\SB{\MC {C}}}} _1
-\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
-}
-
-\I holds for probability \m {p}, with
-\Disp {
-\NC 1 -p
-\leq \NC 2 \exp \SB {-\F {9L} {\pi}} \NR
-}
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Design of Beamformers}
-{
-\I Let us set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ Complex Standard Normal, up to a design constant
-
-\I And set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed argument and unity magnitude, up to a design constant
-
-\I It is argued in the treatise that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, then \m {\M {P}} has too.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {RIP of Digital Beamformers}
-{
-\I For \m {0 <\d_s <1}, unit vector \m {\V {u}}, \m {\M {W}_B} (resp.\ \m {\M {F} _B ^\Adj}) satisfies
-%
-\Disp {
-\NC \Nm {\VNm {\M {W} _B \V {u}} _2^2 - 1}
-\geq \NC \d_s \NR
-}
-
-\I holds for probability \m {p}, with
-\Disp {
-\NC 1 -p
-\leq \NC 2 \Ss {e} ^{-N_Y \R {\d_s} /4} \NR
-}
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {RIP of Analog Beamformers}
-{
-\I Suppose
-%
-\Disp {
-\NC N_R
-\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
-}
-%
-\I Then \m {\M {W}_R} (resp.\ \m {\M {F} _R ^\Adj}) has \m {\d_s}-RIP for probability \m {p}, with
-\Disp {
-\NC 1 -p
-\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
-}
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Bound of Error Norm (1/2)}
-{
-\I The following bound holds for probability \m {p}:
+\I In conclusion, it holds for probability \m {p} that
 \Disp {
@@
 %
-\leq \NC 8 \R {L} \R {\log N_H}^3 \NR
+\leq \NC 8 \R {L} \RB {\log N_H} ^{3/2} \NR
 }
 %
-\I where for \m {p}, denote the four events of failure, subscript respectively for restricted isometry, noise, sparsity,
+\I For design values
 \Disp {
-\NC q = 1-p
-\lesssim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
-}
-
-\I Then...
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Bound of Error Norm (2/2)}
-{
-\I For concreteness, set values
-\Disp {
-\NC N_Y \gtrsim \NC 4 \log N_H, \NR
-\NC N_R \gtrsim \NC 16 L \RB {\log N_H}^2 \NR
+\NC N_Y \gtrsim \NC 4 \log N_H, \Q
+N_R \gtrsim 16 L \RB {\log N_H}^2 \NR
 }
 %
-\I It follows that
+\I And it holds that
 \Disp {
-\NC q _{\Rm {sp}}
-\lesssim \NC q _{\Rm {no}}
-\lesssim q _{\Rm {iso}, B}
-\eqsim q _{\Rm {iso}, R} \NR
-%
-\NC q
+\NC 1 - p
 \lesssim \NC 2 N_H ^{-1/3} \NR
 }
+%
+\I Unfortunately, the values are too big to simulate.
 }

### 2020-10-21 presentation/4_simulation.tex
Rev `.gitignore`, rightly commit all images

--- 2020-03-24 presentation/4_simulation.tex
@@
 {
-\I Set \m {\V {1} = \IP {1, \dots, 1}}.
+\I DS is equivalent to a linear program, which allows more efficient convex programming methods to be used.
+
 \I Calculate
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Two-Stage Estimation (1/2)}
+\Frame {Two-Stage Estimation}
 {
-\I Denote
-\Disp {
-\NC N_0 = \NC 2 N_H^2 \NR
-\NC N_1 = \NC 2 N_H \NR
-\NC N_2 = \NC 2 \lfloor \Rm {min} \SB {L \log \SB {N_H^2}, N_H} \rfloor \NR
-}
+\I Candès and Tao suggests a two stage version may be used to improve precision.
 
-\I Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}.
+\I Choose \m {N_0 = 2 N_H^2, N_2 = \lfloor 4 \log N_H \rfloor, N_1 = \lfloor \R {N_0 N_2} \rfloor}
 
-\I Choose the \m {N_1} largest component of \m {\Hat {\V {g}}_0} and call it \m {\V {g}_1}.
-Choose corresponding columns of \m {\M {P}} and call it \m {\M {P} _1}.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Two-Stage Estimation (2/2)}
-{
-\I Apply DS to \m {\V {y}, \M {P} _1} to get \m {\Hat {\V {g}}_1}.
+\I Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}, and take the \m {N_1} largest component of \m {\Hat {\V {g}}_0} to be \m {\V {g}_1}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _1}.
 
-\I Choose the \m {N_2} largest component of \m {\Hat {\V {g}}_1} and call it \m {\V {g}_2}.
-Choose corresponding columns of \m {\M {P}_1} and call it \m {\M {P} _2}.
+\I Apply DS to \m {\V {y}, \M {P}_1} to get \m {\Hat {\V {g}}_1}, and take the \m {N_2} largest component of \m {\Hat {\V {g}}_1} and to be \m {\V {g}_2}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _2}.
 
-\I Apply pseudoinverse (linear square) to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}.
-
-\I Assign corresponding components of \m {\Hat {\V {g}}_2} in \m {\Hat {\V {g}}}, and pad \m {0} otherwise.
+\I Apply least square to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}, which corresponds to \m {\Hat {\V {g}}}.
 }
@@
 {
-\I With some approximations, I suggest the following metric for spectral efficiency:
-\I Denote \m {E := \Hat {H} - H}
-\I Observe
+\I We call the following quantity \m {\chi} efficiency, which is suggestive of the MIMO channel capacity.
+
+\I Denote \m {\M {E} = \Hat {\M {H}} - \M {H}}.
 \Disp {
-\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj - \M {H} \M {H} ^\Adj} \V {x}
-\lesssim 2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}} \NR
+\NC \chi
+= \log \det \SB {\M {I} + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
 }
-\I Define the spectral efficiency to be
-\Disp {
-\NC \log \det \SB {I + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
-}
+
+\I The theoretical efficiency \m {\chi _{\Rm {th}}} is defined by plugging in \m {\V {d}}.
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Theoretical Metric}
+\Frame {Efficiency, \m {N_H=8}}
 {
-\I For the theoretical error norm,
-\Disp {
-\NC \log d_{\Rm {th}}
-\lesssim \NC \F {1} {2} \log L +\F {3} {2} \log \log N_H \NR
-}
-\I Define the theoretical spectral efficiency to be
-\Disp {
-\NC \log \det \SB {I + \RB {\s + \F {2 d_{\Rm {th}} \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
-}
+\blank [big]
+\externalfigure [assorted-very-small-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Simulation Parameters}
+\Frame {Efficiency, \m {N_H=12}}
 {
-\I Antennae number of channel \m {N_H = 16, 20, 24}
-\I Antennae number of analog stage \m {N_R = \lfloor \R {N_H N_Y} \rfloor}
-\I Antennae number of digital stage \m {N_Y = \lfloor N_H/3 \rfloor}
-\I Number of paths \m {L =3}
-\I Analog beamformer quantization grid: \m {16}
-\I How many noise standard deviation tried: \m {7}
-\I Number of repetition of each data point: \m {12}
-\I Solved by Python CVXPY
+\blank [big]
+\externalfigure [assorted-small-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Spectral Efficiency, \m {N_H=16}}
+\Frame {Efficiency, \m {N_H=16}}
 {
 \blank [big]
-\externalfigure [assorted-small-efficiency.png] [factor=fit]
+\externalfigure [assorted-medium-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Time Taken, \m {N_H=16}}
+\Frame {Efficiency, \m {N_H=20}}
 {
 \blank [big]
-\externalfigure [assorted-small-time.png] [factor=fit]
+\externalfigure [assorted-big-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Spectral Efficiency, \m {N_H=20}}
+\Frame {Efficiency, \m {N_H=24}}
 {
 \blank [big]
-\externalfigure [assorted-medium-efficiency.png] [factor=fit]
+\externalfigure [assorted-very-big-spectral.png] [factor=fit]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Time Taken, \m {N_H=20}}
+\Frame {Time, \m {N_H=16}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Spectral Efficiency, \m {N_H=24}}
+\Frame {Discussion}
+{
+\I DS wins narrowly for smaller \m {\s}, but deteriorates for larger \m {\s}.
+
+\I \m {\chi _{\Ss {th}}} is accurate for larger \m {\s}, but overestimates for smaller \m {\s}.
+
+\I The weaker constraint on sparsity conpromises DS's performance.
+
+\I DS has complexity much higher than OMP, but similar to Lasso.
+
+\I As \m {2N_H^2} grows fast, DS becomes less feasible.
+
+\I The two-stage version is not always better.
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {A Successful Case of Estimation}
 {
 \blank [big]
-\externalfigure [assorted-big-efficiency.png] [factor=fit]
+\externalfigure [scatter-ddss-success.png] [wfactor=150]
+
+\I When DS succeeds: soft thresholding (green) correctly guesses the true values of non-zero positions (black), and refines the estimated value (orange)
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Time Taken, \m {N_H=24}}
+\Frame {A Failed Case of Estimation}
 {
 \blank [big]
-\externalfigure [assorted-big-time.png] [factor=fit]
+\externalfigure [scatter-ddss-failure.png] [wfactor=150]
+
+\I When DS fails: soft thresholding (green) does not correctly guess the true values of non-zero positions (black), and the estimated value (orange) becomes worse
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Discussion}
+\Frame {Complexity}
 {
-\I DS is slightly better than others when \m {\s \gg 1}
+\I The number of Newton steps is about \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
+Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, or \m {\MC {O} \SB {N_H^2}}.
 
-\I \m {\eta _{\Ss {th}}} is in correct order of magnitude but not tight when \m {\s \gg 1}
+\I Every Newton step requires a matrix inversion of dimension \m {2 N_H^2}, with complexity \m {\MC {O} \SB {N_H^4}}, giving overall complexity \m {\MC {O} \SB {N_H^6}}.
 
-\I The smaller the noise, the smaller the error
+\I Complexity of Lasso can be similarly argued to be \m {\MC {O} \SB {N_H^6}}.
 
-\I It is \It {not} true that the smaller \m {\g _{\Ss {DS}}}, the smaller the error
-
-\I We have exceedingly high complexity than OMP
-
-\I The requirement that \m {N_H \gg N_Y} is demanding
+\I Clearly, OMP has complexity \m {\MC {O} \SB {N_H^2}}, much smaller than DS.
 }
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Complexity (1/2)}
-{
-\I In general, the complexity of convex optimization is hard to obtain.
-
-\I However, there exist expressions for number of Newton steps in the course of optimization.
-It is \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
-Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, which is at most \m {\MC {O} \SB {N_H^2}}.
-
-\I Moreover, every Newton step requires a matrix inversion of dimension \m {N_H^2}, with at least \m {\MC {O} \SB {N_H^4}}.
-This gives \m {\MC {O} \SB {N_H^6}}.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Complexity (2/2)}
-{
-\I On the other hand, it is pointed out that Lasso (least absolute shrinkage and selection operator) has similar complexity with Least Angle regression, which has complexity \m {\MC {O} \SB {N_H^6}}.
-Since DS and Lasso have similar form, we expect DS has similar complexity.
-
-\I Clearly, the complexity of OMP is at most \m {\MC {O} \SB {N_H^2}}, so much smaller than DS.
-}

### 2020-10-21 presentation/5_conclusion.tex
Rev `.gitignore`, rightly commit all images

@@
 {
-\I We propose a method to estimate MIMO mm-Wave channel \m {\M {H}} by modifying Dantzig Selector (DS), exploiting the sparsity inherent in the problem.
+\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.
 
-\I We argue for its validity, for the almost-sparse condition in the angular domain, using the effective beamformer \m {\M {P}}, and concerning complex vectors.
+\I We justify DS in present scenario with almost-sparse \m {\V {g}}, and show the RIP of effective beamformer \m {\M {P}}.
 
-\I We propose a bound of the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the asymptotic behavior of the successful probability.
+\I We propose a error norm analysis of DS in terms of parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigate the asymptotic successful probability.
 
-\I We convert the problem into a linear program to reduce complexity, and run a two-stage version to estimate the position of components.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Future Work}
-{
-\I Is it possible to reduce complexity, while retaining the performance?
+\I We convert DS into a linear program of lower complexity, and compare another two-stage version of DS.
 
-\I Is the trend the same for bigger values of \m {N_H}?
-
-\I Why DS is not as good as expected, and is there any mistakes in the proof of error bound?
+\I Experiments show DS does appear superior, at the cost of complexity much greater than OMP
 }
@@
 {\tfx
+\I A Alkhateeb, O E Ayach, G Leus, R W Heath, \Quote {Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems}, \It {IEEE Journal of Selected Topics in Signal Processing} 8(5), 2014
+
+\I A Alkhateeb, G Leus, and R W Heath, \Quote {Compressed sensing based multi-user millimeter wave systems: How many measurements are needed?}, in \It {2015 IEEE International Conference on Acoustics, Speech and Signal Processing}.
+
 \I W U Bajwa, J Haupt, A M Sayeed, and R Nowak, \Quote {Compressed channel sensing: A new approach to estimating sparse multipath channels}, \It {Proceedings of the IEEE}, 98(6), 2010
@@
 \I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.
-
-\I E Candès and J Romberg, \Quote {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved online, 2005.
-
-\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \m {p} is much larger than \m {n}}, \It {The Annals of Statistics} 35(6), 2007.
 }
@@
 {\tfx
-\I E J Candès and T Tao, \Quote {Decoding by Linear Programming}, \It {IEEE Transactions on Information Theory}, 51(12), 2005
+\I E Candès and J Romberg, \Quote {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved online, 2005.
 
-\I M P Friedlander and M A Saunders, \Quote {Discussion: the Dantzig selector: statistical estimation when p is much larger than n}, \It {The Annals of Statistics}, 35(6), 2007
+\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics} 35(6), 2007.
+
+\I M P Friedlander and M A Saunders, \Quote {Discussion: the Dantzig selector: statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics}, 35(6), 2007.
 

### 2020-10-21 treatise/1_introduction.tex
Rev `.gitignore`, rightly commit all images

@@
 With a large number of antennae on both transmitter and receiver, MIMO is expected to provide a large signal gain.
-The appeal of MIMO includes multiplexing gain (with parallel transmission of data), diversity gain (with redundant transmission using space-time coding), and antenna gain (with beamforming).
-The millimeter wave (mm-wave) is also suggested: its smaller wavelength results in higher frequency bands, and thus wider bands available.
-The antennae may be closer-spaced, making it possible to increase their number.
+The appeal of MIMO includes multiplexing gain (by parallel transmission of data), diversity gain (by redundant transmission with space-time coding), and antenna gain (by suitable beamforming).
+The millimeter wave (mm-wave) is also proposed, since its smaller wavelength, that is higher frequency, results in wider frequency bands available.
+The antennae, moreover, may be more closer-spaced, making it possible to increase their number.
 
-However, MIMO also leads to hardware overhead and increases complexity and power consumption.
-To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, can be calculated.
-Not only is the channel estimation difficult due to a large number of antennae, but the transmission is prone to noise corruption.
-With more antennae, conventional training-based algorithms also increase in complexity and storage.
+However, MIMO also gives rise to higher complexity, hence higher hardware overhead and power consumption.
+To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, may be found.
+Here, not only is the channel estimation difficult, due to the large antennae array, but the transmission in higher frequency is subject to noise corruption too.
+Consequently, conventional training-based algorithms now have large time and space complexity.
+
+\stopsection
 
@@
 
-Then, a recent developement called compressive sensing turns out to be relevant.
-Generally speaking, it is a technique for reconstructing a signal in the case of underdetermined linear systems, if the sparsity of signal guarantees successful recovery in the majority of cases.
-A more common situation is that some signals are not sparse in the original basis, but there exists a certain basis on which the signal is sparse, and fewer measurements suffice, though constructing such bases is another undertaking.
+Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel, which is a big square matrix of dimension same as number of antennae.
+Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and thus the degree of freedom.
+And that's when a recent developement called compressive sensing may help.
+Generally speaking, it is a technique for reconstructing a underdetermined linear system, if the sparsity of solution guarantees successful recovery in the majority of cases.
 
@@
 
-The figure shows the signal in both original basis and Hermite polynomials basis.
-It is not sparse in the former, but is in the latter.
-Thus, the recovery from just a few Hermite polynomial components are able to approximate it well.
-(Source: Wikimedia Commons, retrived from \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
-
-In the beginning, a Candès and Tao \cite [Can05] pointed out that in various statsitical applications the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
+It started when Candès and Tao \cite [Can05] noted in various statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
 %
@@
 %
-They showed that in the noiseless case \cite [Can05], it is possible to recover the sparse signal, under a \m {\ell_1}-minimization program, revealing the phenomenon that fewer than \m {N_p} measurement suffices to resonstruct the \m {N_m}-dimensional signal, when it is sparse.
+To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear transformation
+%
+\DispNum {y:y:Qx:Qx} {
+\NC \V {y}
+=\NC \M {Q} \V {x} + \V {z} \NR
+}
+Certainly, \m {\M {Q} \RB {\V {x} - \V {x}'} = 0}, then \m {\V {x}, \V {x}'} are indistinguishable.
+But if \m {\V {x}} is sparse, it essentially restrict the system so much that we obtain unique solution for most of the time.
 
-Indeed, usually any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.
-But the sparsity constraint essentially restrict the underdetermined system so much that we obtain unique solution for most of the time.
+Formally, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
+That is, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
+%
+\DispNum {x:A:x::x:} {
+\NC \V {x} _{\SB {\MS {A}}}
+=\NC \V {x} \NR
+}
+%
+with
+%
+\DispNum {A:A:s::s:} {
+\NC \Nm {\MS {A}} \leq \NC s. \NR
+}
+A more common situation is that some signals are not sparse in the original basis, but there exists a certain basis on which the signal is sparse, though constructing such bases is another undertaking.
+(Figure: a signal becomes sparse after transformation of basis.
+Retrived from Wikimedia Commons, \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
+
+Candès and Tao showed that (\It {ibid}), in the noiseless case, a \m {\ell_1}-minimization program covers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.
 
 As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
-Another example is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being \cite [CaT07].
+Such simplification is particularly important in medical imaging, since it is not only expensive, but also harmful to the body, to take too many images, but the imaging accuracy may be critical to the diagnosis (\It {ibid}).
 
@@
 
-But with insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
-A stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too, but in doing so, we have to make a few carefully constructed, and seemingly random measurements.
+But if the linear transformation is subject to noise,
+%
+\DispNum {y:y:Qx:xz} {
+\NC \V {y}
+=\NC \M {Q} \V {x} + \V {z} \NR
+}
+is it still possible to recover \m {\V {x}}?
 
-To start, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}.
+We introduce several notions.
 For \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}}, denote
@@
 That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MS {A}}.
-
-We say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
-Formally,
-\Result
-{Definition}
-{
-\m {\V {x}} is called \m {s}-sparse, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
-%
-\DispNum {x:A:x::x:} {
-\NC \V {x} _{\SB {\MS {A}}}
-=\NC \V {x} \NR
-}
-%
-with
-%
-\DispNum {A:A:s::s:} {
-\NC \Nm {\MS {A}} \leq \NC s. \NR
-}
-}
 
@@
 
-Now, consider a linear transformation of real vectors added of noise,
-%
-\DispNum {y:y:Qx:xz} {
-\NC \V {y}
-=\NC \M {Q} \V {x} + \V {z} \NR
-}
-%
-where, for example, \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
-How can we hope to estimate \m {\V {x}} when, in addition to insufficient measurements, there is also noise corruption?
+For concreteness, say \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
+If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig Selector (hencefore DS), recovery under the noisy case is again possible.
 
@@
 
-They were able to show \cite [CaT07] that Algorithm [3] recovers \m {\V {x}} with the expected square error bounded with overwhelming probability.
+Particularly, Algorithm [2] recovers \m {\V {x}} with the expected square error bounded with overwhelming probability.
 
@@
 Indeed, relevent code has been put on their website for the reader to access and verify (Candès \& Romberg \cite [CaR05]).
+Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.
 
-Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.
-The constant \m {\d_s} in Definition [2] is crucial, and here we can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
+Here the constant \m {\d_s} in Definition [1] is crucial:
+we must make a series of carefully chosen but seemingly random measurement.
+We can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
 One common proposal is choosing every entry of \m {\M {Q}} to be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
@@
 
-Back at the ranch, recall that the overhead of channel estimation has been a concern in the mm-wave MIMO setting.
-Luckily, physical evidences suggest that millimeter wave channels are in fact sparse in the frequency domain, and some scholars have thus applied compressive sensing techniques to the problem.
+Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are in fact sparse in the frequency domain.
+Some scholars have thus applied compressive sensing techniques.
 One of the first attempt has been Bajwa et.\ al.\ \cite [BHS10], where they argue that the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
@@
 Still consider \Rf {y:y:Qx:xz}.
-We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.
+We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.
 
@@
 
+Ever since, OMP has since been applied in a variety of ways.
 Alkhateeb et.\ al.\ \cite [AEL14] proposes an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
@@
 
-Ever since, OMP has since been applied in a variety of ways.
-Especially, work on channel estimation seems to favored OMP for its low complexity.
+From above we note that work on channel estimation seems to favored OMP for its low complexity.
 One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.

### 2020-10-22 treatise/4_simulation.tex
Rev `.gitignore`, rightly commit all images
Rightly commit some new figures and copied code

@@
 
+Each data point is repeated for 24 times, and taken average.
+
 \startsubsection [title={Performance Metric}]
 
-Lee, Gil, and Lee \cite [LGL16] proposed the proformance metric
+We use the performance metric proposed in Lee, Gil, and Lee \cite [LGL16],
 \DispNum {h:h:lo:vg} {
@@
 }
-However, we find that when \m {\VNm {\V {h}}_2} is small, this can blow up.
-
-We propose another metric that is suggestive of spectral efficiency.
-Indeed, since we have not specified the channel, we can't logically use any particular channel capacity expression.
-But we may still adopt the MIMO capacity with perfect CSI, with an estimated quantity for SNR.
-Denote \m {\M {E} = \Hat {\M {H}} - \M {H}}.
-Assume that
-\Disp {
-\NC \VNm {\RB {\M {H} + \M {E}} \RB {\M {H} + \M {E}} ^\Adj \V {x} - \M {H} \M {H} ^\Adj \V {x}} _2
-\lesssim 2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}} \NR
-}
-
-Then \m {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2 \VNm {\V {x}}} can be considered as part of the noise.
-In view of the MIMO channel, \m {\s} has to be multiplied by factor \m {\R {N_H}}, and \m {\VNm {\M {H}} _2} and \m {\VNm {\M {E}} _2} both divided by factor \m {\R {N_H}}.
-Therefore, we define the quantity
-\Disp {
-\NC \chi
-= \log \det \SB {\M {I} + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
-}
-
-Each data point is repeated for 24 times, and taken average.
+However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
 
@@
 
-\page [yes]
-
 \startsubsection [title={Assorted Plots}]
 
-For \m {N_H = 12}, noise vs spectral efficiency,
+In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
+Plots 1 to 5 have \m {N_H = 3 N_Y}, and the plots 6 to 10 has \m {N_H = 2 N_Y}.
 %
 \blank [big]
-\externalfigure [assorted-small-spectral.png] [wfactor=fit, hfactor=fit]
-
-For \m {N_H = 18}, noise vs spectral efficiency,
+%\externalfigure [assorted-wide-very-small-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-\externalfigure [assorted-medium-spectral.png] [wfactor=fit, hfactor=fit]
-
-For \m {N_H = 24}, noise vs spectral efficiency,
+%\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-\externalfigure [assorted-big-spectral.png] [wfactor=fit, hfactor=fit]
+%\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+%\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+\externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+%\externalfigure [assorted-narrow-very-small-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+%\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+\externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]
 
-For \m {N_H = 18}, noise vs time taken,
+As of the plot of time taken in minutes, we give only one of \m {N_H = 18}, as an example.
 %
@@
 
-\page [yes]
+\startsubsection [title={Plots of DS only}]
 
-\startsubsection [title={Plots of Dantzig Selector}]
+Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_Y} for each of them.
+Moreover, the bound of error norm suggested in chapter 3 is plotted.
 
-For \m {N_H = 12}, noise vs spectral efficiency,
 %
 \blank [big]
-\externalfigure [ddss-small-spectral.png] [wfactor=fit, hfactor=fit]
-
-For \m {N_H = 18}, noise vs spectral efficiency,
+%\externalfigure [ddss-very-small-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-\externalfigure [ddss-medium-spectral.png] [wfactor=fit, hfactor=fit]
-
-For \m {N_H = 24}, noise vs spectral efficiency,
+\externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-\externalfigure [ddss-big-spectral.png] [wfactor=fit, hfactor=fit]
-
-For \m {N_H = 18}, noise vs time taken,
+\externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-\externalfigure [ddss-medium-time.png] [wfactor=fit, hfactor=fit]
+%\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+%\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
+%
+As of the plot of time taken in minutes, we give only one of \m {N_H = 16}, as an example.
+%
+\blank [big]
+\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
 
@@
 
-\page [yes]
+\startsubsection [title={Plots of OMP only}]
 
-\startsubsection [title={Plots of Orthogonal Matching Pursuit}]
+Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_Y} for each of them.
 
-For \m {N_H = 12}, noise vs spectral efficiency,
 %
 \blank [big]
-\externalfigure [oommpp-small-spectral.png] [wfactor=fit, hfactor=fit]
-
-For \m {N_H = 18}, noise vs spectral efficiency,
+%\externalfigure [oommpp-very-small-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-\externalfigure [oommpp-medium-spectral.png] [wfactor=fit, hfactor=fit]
-
-For \m {N_H = 24}, noise vs spectral efficiency,
+%\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-\externalfigure [oommpp-big-spectral.png] [wfactor=fit, hfactor=fit]
-
-For \m {N_H = 18}, noise vs time taken,
+\externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-\externalfigure [oommpp-medium-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
+%
+\blank [big]
+\externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
+%
+As of the plot of time taken in minutes, we give only one of \m {N_H = 16}, as an example.
+%
+\blank [big]
+\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
 
@@
 
-Reasonably, for all methods, a higher \m {\s} corresponds to lower \m {\chi}.
-For low noise, DS slightly but steadily outperforms other methods, but for high noise, DS degrades quickly.
+In the assorted plot, DS steadily outperforms other methods, and LS is worse than DS, and Lasso still worse, and OMP still worse.
+However, it is not clear how higher \m {\s} corresponds to lower error.
+It seems when \m {\s} is further increased near the leftmost of the figures, the error might also increase rapidly, but in that case, many methods give overflown values.
 
-Different values of threshold \m {\g_{\Rm {DS}}} does not seem matter much.
-It appears \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is intuitive.
+Varying thresholds of DS (namely \m {\g_{\Rm {DS}}}) and OMP (namely \m {\h_{\Rm {OMP}}}) does not have significant effect on the output, and from the cases simulated, there can be no conclusive answer.
+Nevertheless, it appears \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is intuitive.
+Sometimes the iteration stablizes much earlier than is constrained by maximum iteration number.
 
-For OMP, interestingly, different values of \m {\h_{\Rm {OMP}}} do not seem to affect much to performance, and often the iteration stablizes much earlier than is constrained by maximum iteration number.
-Lasso and Least Square usually has substantially lower \m {\chi} than OMP.
+Our suggested bound, unfortunately, does not agree the simulated error of DS, and the matter remains to be investigated in the future.
+As pointed above, the simulated error is very constant around 1, so the suggested bound is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
+A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3 (despite our effort to estimate), and thus the validity of performance guarantee of DS becomes more dubious.
 
-The theory bound of DS is an overestimation for low noise, but underestimation for high noise.
-This suggest our bound is correct but not tight.
+\blank [big]
+\externalfigure [scatter-ddss-failure.png] [wfactor=300]
+
+To give some idea when DS works or not, the figure above illustrates a case where DS failed.
+We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.
+Subsequent application of DS on the wrong index set fails, as a result.
 
@@
 The subsequent application of DS on this smaller index set refines the estimated values.
-
-\blank [big]
-\externalfigure [scatter-ddss-failure.png] [wfactor=300]
-
-The figure above illustrates a case where DS succeeded.
-We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.
-Subsequent application of DS on the wrong index set fails, as a result.
 

### 2020-10-22 copy-code/classes.py

@@ -1,0 +1,156 @@
+import numpy as np
+from enum import Enum
+import sys
+
+import constants as cst
+import functions as fct
+
+
+class Beamformer:
+    def __init__ (s, ver):
+        s.ver = ver
+        s.pp = np.zeros ((cst.NN_Y (s.ver), cst.NN_H (s.ver)))
+
+    def generate (s):
+        kk = fct.get_kk (s.ver)
+        ff_bb = fct.pick_mat_bb (s.ver).T
+        ff_rr = fct.pick_mat_rr (s.ver).T
+        ww_bb = fct.pick_mat_bb (s.ver)
+        ww_rr = fct.pick_mat_rr (s.ver)
+        pp = np.kron (ff_bb.T @ ff_rr.T @ kk.conj (), ww_bb @ ww_rr @ kk)
+        s.pp = pp
+
+class Channel:
+    def __init__ (s, pp, s_g, ver):
+        s.ver = ver
+        s.pp = pp
+        s.s_g = s_g
+        s.hh = np.zeros ((cst.NN_HH (s.ver), cst.NN_HH (s.ver)), dtype = complex)
+        s.y = np.zeros ((cst.NN_Y (s.ver)))
+
+    def generate (s):
+        s.hh = fct.pick_hh (s.ver)
+        s.norm_hh = np.linalg.norm (s.hh, ord = 'fro')
+
+    def zero (s):
+        s.hh = np.zeros ((cst.NN_HH (s.ver), cst.NN_HH (s.ver)), dtype = complex)
+
+    def transmit (s):
+        kk = fct.get_kk (s.ver)
+        zz = fct.pick_zz (s.ver)
+        gg = kk.conj ().T @ s.hh @ kk
+        g = fct.vectorize (gg)
+        z = fct.vectorize (zz)
+        #s.y = s.pp @ g
+        s.y = s.pp @ g + (s.s_g / np.sqrt(2)) * z
+
+
+# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
+
+class Estimation:
+    def __init__ (s, cnt_each, hh, pp, y, s_g, ver):
+        s.ver = ver
+        s.cnt_each = cnt_each
+        s.hh = hh
+        s.pp = pp
+        s.y = y
+        s.s_g = s_g
+        s.g_r_h = np.zeros (2 * (cst.NN_H (s.ver)))
[…]

### 2020-10-22 copy-code/main.py

@@ -1,0 +1,23 @@
+#! /usr/bin/env python3
+
+import os
+
+import functions as fct
+import classes as cls
+
+# example
+NUM_REP_FIG = 6
+for i in range (NUM_REP_FIG):
+    print (
+        "~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~\n",
+        "Figure", i,
+        "~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~\n"
+    )
+    idx_hold = i + 1
+    ver = cls.Version (
+        cls.Focus.ASSORTED,
+        cls.Size.BIG,
+        cls.Ratio.WIDE,
+        str (idx_hold))
+
+    fct.execute (ver)

### 2020-10-23 presentation/4_simulation.tex
Update presentation figures

@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Two-Stage Estimation}
-{
-\I Candès and Tao suggests a two stage version may be used to improve precision.
-
-\I Choose \m {N_0 = 2 N_H^2, N_2 = \lfloor 4 \log N_H \rfloor, N_1 = \lfloor \R {N_0 N_2} \rfloor}
-
-\I Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}, and take the \m {N_1} largest component of \m {\Hat {\V {g}}_0} to be \m {\V {g}_1}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _1}.
-
-\I Apply DS to \m {\V {y}, \M {P}_1} to get \m {\Hat {\V {g}}_1}, and take the \m {N_2} largest component of \m {\Hat {\V {g}}_1} and to be \m {\V {g}_2}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _2}.
-
-\I Apply least square to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}, which corresponds to \m {\Hat {\V {g}}}.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
 \Frame {Performance Metric}
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Efficiency, \m {N_H=8}}
+\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=2N_Y}}
 {
 \blank [big]
-\externalfigure [assorted-very-small-spectral.png] [factor=fit]
+\externalfigure [assorted-narrow-very-big-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Efficiency, \m {N_H=12}}
+\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=3N_Y}}
 {
 \blank [big]
-\externalfigure [assorted-small-spectral.png] [factor=fit]
+\externalfigure [assorted-wide-very-big-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Efficiency, \m {N_H=16}}
+\Frame {\m {1/\s} vs \m {\chi}, OMP only, \m {N_H=24=3N_Y}}
 {
 \blank [big]
-\externalfigure [assorted-medium-spectral.png] [factor=fit]
+\externalfigure [oommpp-medium-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Efficiency, \m {N_H=20}}
+\Frame {\m {1/\s} vs \m {\chi}, DS only, \m {N_H=24=3N_Y}}
 {
 \blank [big]
-\externalfigure [assorted-big-spectral.png] [factor=fit]
+\externalfigure [ddss-medium-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Efficiency, \m {N_H=24}}
+\Frame {Time, assorted, \m {N_H=16}}
 {
 \blank [big]
-\externalfigure [assorted-very-big-spectral.png] [factor=fit]
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Time, \m {N_H=16}}
-{
-\blank [big]
-\externalfigure [assorted-medium-time.png] [factor=fit]
+\externalfigure [assorted-medium-time.png] [width=11cm]
 }
@@
 {
-\I DS wins narrowly for smaller \m {\s}, but deteriorates for larger \m {\s}.
+\I DS wins other method within the range drawn.
 
-\I \m {\chi _{\Ss {th}}} is accurate for larger \m {\s}, but overestimates for smaller \m {\s}.
+\I Simulated \m {\chi} does not show trend that estimated \m {\T {\chi}} predicts.
 
-\I The weaker constraint on sparsity conpromises DS's performance.
+\I The weaker constraint on sparsity might have conpromised DS's performance.
 
@@
 \I As \m {2N_H^2} grows fast, DS becomes less feasible.
-
-\I The two-stage version is not always better.
 }

### 2020-10-23 presentation/5_conclusion.tex
Update presentation figures

@@
 
-\I We convert DS into a linear program of lower complexity, and compare another two-stage version of DS.
+\I DS may be converted to be a linear program to reduce complexity.
 
-\I Experiments show DS does appear superior, at the cost of complexity much greater than OMP
+\I While DS does appear superior, it has complexity much greater than OMP.
 }

### 2020-10-23 treatise/1_introduction.tex
Update presentation figures

@@
 
-It started when Candès and Tao \cite [Can05] noted in various statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
+A series of investigation started when Candès and Tao \cite [Can05] noted in various statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
 %

### 2020-10-23 treatise/3_3_generalizing_the_dantzig_selector_bound.tex
Update presentation figures

@@
 }
+%
+For convenience we set
+\DispNum {c:c:Ll:H3} {
+\NC \T {\chi} :=\NC \R {L} \R {\log N_H}^3 \NR
+}
+
 To prove this, we simplify the expression for \m {\VNm {\V {d} _{\SB{\MS {AB}}}} _2} in \Rf {d:2:11:C1} and the one for \m {\VNm {\V {d} _{\SB{\MS {C}}}} _1} in \Rf {d:1:dA:C1}.

### 2020-10-23 treatise/4_simulation.tex
Update presentation figures

@@
 }
-In the following simulation, we use dimensionless noise-to-signal level \\ \m {\s = 2^{-4}, 2^{-3.5}, 2^{-3}, 2^{-2.5}, 2^{-2}, 2^{-1.5}, 2^{-2}}.
+In the following simulation, we use dimensionless noise-to-signal level \m {\s}.
+Its value start with \m {2^{-4}}, and increase by multiplying 2.
+For the plot of assorted methods, 8 values of \m {\s} are used; for the plots of only OMP, 9 values are used; for the plots of only OMP, 6 values are used.
 
-We do three series of experiments, which are of size from small to large.
-In the following experiments, we take respectively \m {N_H} to be \m {8, 12, 16, 20, 24}.
-\m {N_Y} is set to be \m {\lfloor \log N_H \rfloor}, giving \m {2, 2, 3, 3, 3}.
-\m {N_R} to be \m {\lfloor \RB {\log N_H}^2 \rfloor}, giving \m {4, 6, 7, 9, 10}.
+We take \m {N_H} to be \m {8, 12, 16, 20, 24}, respectively.
+For assorted plots, two series of plots are simulated.
+One series for \m {N_Y = \lfloor N_H /2 \rfloor}, giving \m {4, 6, 8, 10, 12};
+one series for \m {N_Y = \lfloor N_H /3 \rfloor}, giving \m {3, 4, 5, 7, 8}.
+For OMP and DS only plots, we just choose \m {N_Y = \lfloor N_H /3 \rfloor}.
+On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
 Unfortunately, this is very far from achieving the design values \Rf {N:B:4l:H2}, and this may be part of the reason the results is not as successful as expected.
@@
 
-Yet another threshold used for the remainder norm used in OMP program, \m {\h_{\Rm {OMP}}}.
-For its suggested values, see \cite [CaW11].
-We take \m {2 \R {\log N_H}} for infinity norm constraint, \m {\R {3 N_Y}} for 2-norm constraint.
+The threshold used for the remainder norm used in OMP program, \m {\h_{\Rm {OMP}}}, is suggested in \cite [CaW11].
+We take \m {2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\R {3 N_Y}} for 2-norm constraint.
 
-Each data point is repeated for 24 times, and taken average.
+Each data point for DS and Lasso is repeated for 256 times, and taken average.
+Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {12 \D 256} times.
 
@@
 Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_Y} for each of them.
-Moreover, the bound of error norm suggested in chapter 3 is plotted.
+Here, the bound \m {\T {\chi}} is shown.
 
@@
 
-Our suggested bound, unfortunately, does not agree the simulated error of DS, and the matter remains to be investigated in the future.
-As pointed above, the simulated error is very constant around 1, so the suggested bound is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
+Our \m {\T {\chi}}, unfortunately, does not agree the simulated error of DS, and the matter remains to be investigated in the future.
+As pointed above, the simulated error is very constant around 1, so \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
 A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3 (despite our effort to estimate), and thus the validity of performance guarantee of DS becomes more dubious.

### 2020-10-23 treatise/5_conclusion.tex
Update presentation figures

@@
 
-Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Cand\`es and Tao \cite [CaT07], that the probability that the expected square error is bounded is overwhelming.
-We thus have derived a probability bound of performance on a fairly general setting, where the bounding constant is expressed as an explicit function of physical parameters, such as the number of path.
+Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Candès and Tao \cite [CaT07], that for overwhelming probability, the expected square error is bounded.
 
-Afterwards we transformed DS into an SOCP, which is quite different as in the original DS (where we have an LP instead).
-Simulation is done, and DS's performance is compared to OMP.
-DS is slightly but steadily more accurate than OMP, while DS exhibits rather high complexity.
+We also point out that DS may be cast into an LP, and simulation is done.
+DS is steadily more accurate than all other methods, while exhibiting rather high complexity.
+Unfortunately, the program is prone to give overflown output, and we have not investigated range of parameter extensive enough for more conclusions.
 

### 2020-10-24 treatise/1_introduction.tex
Update discussion on numerical experiments

--- 2020-10-21 treatise/1_introduction.tex
@@
 
-\startsection [title={Background: Estimation of MIMO Channel}]
+\startsection [title={Estimation of MIMO channel}]
 
@@
 
-\startsection [title={Compressive Sensing}]
+\startsection [title={Compressive sensing}]
 
@@
 
-It started when Candès and Tao \cite [Can05] noted in various statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
+The figure above shows the generic situation in which a signal is ``crowded'' in the given basis, but is ``sparse'' in another basis.
+(Wikimedia Commons, \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
+In the given basis, more measurements are required to recover the signal, while fewer suffice in the sparse basis.
+But, even if we are guaranteed a sparse basis exists, it is still a nontrivial undertaking to construct it.
+
+A series of investigation started when Candès and Tao \cite [Can05].
+Let us say the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
 %
@@
 }
-A more common situation is that some signals are not sparse in the original basis, but there exists a certain basis on which the signal is sparse, though constructing such bases is another undertaking.
-(Figure: a signal becomes sparse after transformation of basis.
-Retrived from Wikimedia Commons, \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
 
@@
 
-\startsection [title={Motivation and Contribution}]
+\startsection [title={Contribution}]
 

### 2020-10-24 treatise/3_2_confirming_restricted_isometry.tex
Update discussion on numerical experiments

@@
-\startsection [title={Restricted Isometry of Effective Beamformer}]
+\startsection [title={Restricted isometry of effective beamformer}]
 
-\startsubsection [title={Design of Beamformer Matrices}]
+\startsubsection [title={Design of beamformer matrices}]
 
@@
 
-\startsubsection [title={Operator Norm of Digital Beamformers}]
+\startsubsection [title={Operator norm of digital beamformers}]
 
@@
 
-\startsubsection [title={Operator Norm of Analog Beamformers}]
+\startsubsection [title={Operator norm of analog beamformers}]
 
@@
 
-\startsubsection [title={Confirming the Restricted Isometry}]
+\startsubsection [title={Confirming the restricted isometry}]
 

### 2020-10-24 treatise/4_simulation.tex
Update discussion on numerical experiments

@@
 %
-\DispNum {R-x-R2-M1} {
+\DispNum {R:x:R2:M1} {
 \NC \MS {R} \SB {\V {x}}
@@
 %
-\DispNum {R-1-x--x-} {
+\DispNum {R:1:x::x:} {
 \NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
@@
 %
-\DispNum {R-A-R2-21} {
+\DispNum {R:A:R2:21} {
 \NC \MS {R} \SB {\M {A}}
@@
 %
-\DispNum {y---Ry-Ny} {
+\DispNum {y:::Ry:Ny} {
 \NC \T {\V {y}}
@@
 %
-\DispNum {m---RN-h1} {
+\DispNum {m:::RN:h1} {
 \NC \V {m} \in \NC \MB {R} ^{N_H^2} \NR
@@
 %
-\DispNum {g---mi-h1} {
+\DispNum {g:::mi:h1} {
 \NC \Hat {\T {\V {g}}}
@@
 %
-\DispNum {t---01-Nh} {
+\DispNum {t:t:01:Nh} {
 \NC \V {t}
@@
 %
-\DispNum {A-i-Ui-21} {
+\DispNum {A:i:Ui:21} {
 \NC \M {A}_i
@@
 %
-\DispNum {A-i-Ui-21-"} {
+\DispNum {A:i:Ui:21:"} {
 \NC \M {A}_i
@@
 \item Input \m{\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
-\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to \Rf {t---01-Nh}, \Rf {A-i-Ui-21}, \Rf {A-i-Ui-21-"}.
+\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to \Rf {t:t:01:Nh}, \Rf {A:i:Ui:21}, \Rf {A:i:Ui:21:"}.
 
@@
 %
-\DispNum {x---mi-h1} {
+\DispNum {x:::mi:h1} {
 \NC \Hat {\V {x}}
@@
 %
-\DispNum {g---x0-h1} {
+\DispNum {g:::x0:h1} {
 \NC \Hat{\T{\V {g}}}
@@
 %
-\DispNum {g---R1-1g} {
+\DispNum {g:::R1:1g} {
 \NC \Hat{\V {g}}
@@
 %
-\DispNum {
+\DispNum {G:G:ve:1g} {
 \NC \Hat {G}
@@
 %
-\DispNum {
+\DispNum {H:H:KG:GK} {
 \NC \Hat {\M {H}}
@@
 
-\startsection [title={A Two-Stage Estimation}]
+\startsubsection [title={A Two-Stage Version}]
 
-We also tried another version of DS, in which DS is done for a second time in estimated nonzero-position.
-The two-stage method was briefly mentioned \cite [CaT07] but without further validation by numerical experiments.
-The method starts by applying DS as before.
+We also tried another version of DS, in which DS is applied twice in estimated nonzero-position.
+The two-stage method was briefly mentioned \cite [CaT07] but without further justification by numerical experiments.
+To apply the method, we first apply DS as before.
 Then, we extract largest positions of the estimated vector, and apply DS again.
-Last, we extract largest positions again, and apply LS.
-Note that the final vector has to be scrambled back to the original dimension.
+Futhermore, we extract largest positions of the second estimated vector, and apply LS.
+The final vector's indices has to be scrambled back according to the original index.
 
@@
 
-It may be appropriate to scale \m {\g_{\Rm {DS}}} with respect to \m {N_H}.
-It is not clear to us for now what is most reasonable choice of \m {N_1, N_1, N_2}.
+Unfortunately, the two-stage method does not always appear to be better than the one-stage method, and we did not include the result in the figures.
+It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H},
+and it is not clear what is most reasonable choice of \m {N_1, N_1, N_2}.
 
-\stopsection
+\stopsubsection
 
@@
 
-Concretely, we set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}}, corresponding to Cand\`es \& Tao (2007)
-For comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
+In the plots of assorted methods, we set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} for concreteness, as suggested in \cite [CaT07].
+For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
 For OMP, suggested values in Cai \& Wang (2011) is illuminating, where they (in their Theorem 7) considered \m {\ell _2}-norm, and Theorem 8, \m {\ell _\infty}-norm.
-We make simplification and set respectively \m {\R {3} N_Y} and \m {2 \R {\log N_H}}
+We make simplification and set respectively \m {\R {3} N_Y} and \m {2 \R {\log N_H}}.
+Meanwhile, the threshold used for the remainder norm used in OMP program is suggested in \cite [CaW11].
+We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 N_Y}} for 2-norm constraint.
 
-The threshold used for the remainder norm used in OMP program, \m {\h_{\Rm {OMP}}}, is suggested in \cite [CaW11].
-We take \m {2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\R {3 N_Y}} for 2-norm constraint.
+In the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \h_{\Rm {OMP}} to observe the effects of thresholds.
 
@@
 
-\startsubsection [title={Performance Metric}]
-
-We use the performance metric proposed in Lee, Gil, and Lee \cite [LGL16],
+For performance metric, we follow Lee, Gil, and Lee \cite [LGL16],
 \DispNum {h:h:lo:vg} {
-\NC \chi'
+\NC \T {\chi}
 =\NC \RB {
@@
 However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
+It is not clear, either, whether \m {\T {\chi}} is a good indicator of channel capacity, since we do not fix a channel model in our investigation.
+
+The parameters related to precision of the Newton step may be adjusted from CVXPY's class methods.
+We set the maximum absolute tolerance to be \m {5 \D 10 ^ {-7}},
+the maximum absolute tolerance to be \m {5 \D 10 ^ {-6}},
+the maximum feasible tolerance to be \m {5 \D 10 ^ {-7}}.
+It remains to be investigated what values are most suitable for our purposes.
+If the tolerance parameters are too small, the program often gives overflown output, perhaps because it cannot find feasible solutions.
+On the other hand, if they are too big, the steps become imprecise and the program may fail to find correct solutions.
 
@@
 Friedlander and Saunders \cite [FrS07] criticizes that DS often gives a higher computational cost, compared to Lasso.
-Agreeing their observation, simulation result shows that DS indeed exhibits high complexity when (in our case) \m {N_H} grows.
-It is not suprising from the nature of convex programming.
-On one hand, the algorithm is iterative and random.
-On the other hand, it requires a sizable memory when finding the inversion of (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
+Agreeing their observation, simulation shows that DS indeed exhibits high complexity when (in our case) \m {N_H} grows.
+It is not suprising from the fact that the convex program requires a sizable memory when finding the Newton step, where our program has to calculate (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
 However we note that different tolerance of error and value of maximal iteration number may result vastly different computation time.

### 2020-10-24 treatise/abstract.tex
Update discussion on numerical experiments

@@
 Multiple-input-multiple-output (MIMO) is the next-generation standard of wireless communication.
-However, for MIMO system it is not easy to estimate the channel, while many communication algorithms often requires that the channel state information be known at the receiver.
-Meanwhile, the millimeter wave (mm-Wave) band, often used in MIMO context, is known to exhibit sparsity, and results on compressive sensing suggests that sparsity implies that fewer channel measurement shall suffice.
-For that reason, Orthogonal Matching Pursuit (OMP) is usually used, as it has a very lower complexity.
-However, Dantzig Selector (DS), proposed by Tao and Candès, has long been introduced and ignored.
-DS has several promising properties, and it is curious how it fares on the present problem.
+While the channel state information has to be known at the receiver for communication algorithms, for MIMO system the estimation is not easy.
+Meanwhile, the millimeter wave (mm-Wave) band, often used together with MIMO, is known to exhibit sparsity, and results on compressive sensing suggest that sparsity implies that fewer channel measurements shall suffice.
+In practice, Orthogonal Matching Pursuit (OMP) is usually used, as it has lower complexity.
 
+It is interesting to note that Dantzig Selector (DS), proposed by Tao and Candès, has seldom been applied.
+DS has several promising properties, and it is worthwhile to investigate how it performs on the channel sensing problem.
 In this treatise, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
-Using pilot signal and designed random beamformer, we apply DS for channel estimation, arguing in favor of its greater generality, its tolerance of noise corruption, and its lower averaged error.
+Using pilot signal and predetermind random beamformer, we apply DS for channel estimation, arguing in favor of its greater generality, its tolerance of noise corruption, and its lower averaged error.
 The treatise also gives a bound for the expected square error of DS, as well as bounded probability of success, and in so doing, showing dependency on the number of path and channel sparsity.
 
-DS can be cast as a second order cone problem (SOCP), so that well known methods for convex programs may be used.
+DS can be cast as a linear program (LP), so that known methods for convex programs may be applied.
 Simulation is done on DS and other methods, and we discuss their respective merits.
-It turns out DS is often slightly better than other alternatives, while it has siginificantly greater complexity.
+It turns out DS is steadily better than other alternatives, while it has siginificantly greater complexity.
 

### 2020-10-27 treatise/4_simulation.tex
Update figures

@@
 \blank [big]
-%\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
 %
@@
 
-As of the plot of time taken in minutes, we give only one of \m {N_H = 18}, as an example.
+As of the plot of time taken in minutes, we give only one of \m {N_H = 12}, as an example.
 %
 \blank [big]
-\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-small-time.png] [wfactor=fit, hfactor=fit]
 
@@
 \blank [big]
-%\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
+\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
 %
 \blank [big]
-%\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
-%
-As of the plot of time taken in minutes, we give only one of \m {N_H = 16}, as an example.
-%
-\blank [big]
-\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
 
@@
 \externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
-%
-As of the plot of time taken in minutes, we give only one of \m {N_H = 16}, as an example.
-%
-\blank [big]
-\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
 

### 2020-11-03 treatise/1_introduction.tex
Update figures

@@
 
-The figure above shows the generic situation in which a signal is ``crowded'' in the given basis, but is ``sparse'' in another basis.
+The figure above shows the generic situation in which a signal is ``crowded'' in the given basis, but is ``sparse'' in transformed basis.
 (Wikimedia Commons, \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
-In the given basis, more measurements are required to recover the signal, while fewer suffice in the sparse basis.
-But, even if we are guaranteed a sparse basis exists, it is still a nontrivial undertaking to construct it.
+More measurements are required to recover the signal in the former, while fewer suffice in the latter basis.
+But, even if we are guaranteed latter basis exists, it is still a nontrivial undertaking to construct it.
 
-A series of investigation started when Candès and Tao \cite [Can05].
+Candès and Tao \cite [Can05] first embarked a series of investigation on the problem.
 Let us say the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
@@
 
-Candès and Tao showed that (\It {ibid}), in the noiseless case, a \m {\ell_1}-minimization program covers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.
+Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program covers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.
 
 As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
-Such simplification is particularly important in medical imaging, since it is not only expensive, but also harmful to the body, to take too many images, but the imaging accuracy may be critical to the diagnosis (\It {ibid}).
+Such simplification is particularly important in medical imaging, since it is not only expensive, but also harmful to the body, to take too many images, but the imaging accuracy may be critical to the diagnosis \cite [CaT07].
 
@@
 %
-Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero-position of \m {\V {x}}, which \cite [CaT07] calls support (here we have slightly abused the usage of subscript to indicate component indices).
+Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero components of \m {\V {x}}, which \cite [CaT07] calls support (here we have slightly abused the usage of subscript to indicate component indices).
 From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.
@@
 
-Ever since, OMP has since been applied in a variety of ways.
-Alkhateeb et.\ al.\ \cite [AEL14] proposes an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
-Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discusses the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
-Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero-positions.
-Hu, Wang, and He \cite [HWH13] applies OMP to estimate quantized path delay of each OFDM subcarrier, assuming the channel gain in each path is stationary.
-Lee, Gil, and Lee \cite [LGL16] consider a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.
+OMP has since been applied widely in the literature.
+Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
+Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discussed the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
+Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero components.
+Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers, assuming the channel gain in each path is stationary.
+Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, with the effective beamformer serving as sensing matrix, where set of quantized angles was specially designed, and permuted DFT matrix is used.
 
-Some further attempts include Manoj and Kannu \cite [MaK17], which formulate the sparse condition as overlapping block in the reconstructed signal, and encode possible blocks.
-Gurbuz, Yapici, and Guvenc \cite [GYG18] introduce perturbation of the quantized set of angles, on which the sensing matrix is based.
-Most recently, Panayirci et.\ al.\ \cite [PAU19] put forward a more thorough treatment, where in addition to application of OMP, they use a first stage of max-likelihood estimation of model parameters, and a second stage of maximum-a-posteriori estimation of channel gains.
+Some further attempts include Manoj and Kannu \cite [MaK17], who formulated the sparse condition on submatrices of the signal for successful reconstruction.
+Gurbuz, Yapici, and Guvenc \cite [GYG18] introduced perturbation of the quantized set of angles, on which the sensing matrix is based.
+Panayirci et.\ al.\ \cite [PAU19] suggested, in addition to application of OMP, a concatenation of max-likelihood estimation of model parameters, and maximum-a-posteriori estimation of channel gains.
 
-Performance guarantee of OMP is also studied, by refining or proposing different conditions.
-Cai, Wang, and Xu \cite [CWX10], under assumption on low coherence of columns of matrices, give new bound on OMP.
-Coherence-based assumptions, instead of almost-unitarity, make the condition easier to verify.
-Cai and Wang \cite [CaW11] extends the investigation to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] follow up and refine their bounds, and conclude that OMP is better for low-SNR scenario, and DS is better for high-SNR.
+Performance guarantee of OMP is also studied on various conditions.
+Cai, Wang, and Xu \cite [CWX10], under assumption of low coherence of columns of matrices, instead of almost-unitarity, gave new bound on OMP.
+Cai and Wang \cite [CaW11] extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] followed up and refined their bounds, concluding that OMP is better for low-SNR scenario, and DS is better for high-SNR.
 
@@
 From above we note that work on channel estimation seems to favored OMP for its low complexity.
-One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.
-Indeed, in the uniform linear array setting, DFT matrix can be used as sensing matrix, but the true angle of arrival and departure is often slightly off.
-Meanwhile, as the nature of OMP is greedy, and it is dubious whether it achieves optimality.
-In addition, the assumption that the channel matrix is sparse, at least, warrant justification.
+One notable difficulty in channel estimation is that, in the uniform linear array setting, the quantized angle of arrival and departure, which the sensing matrix is based on, does not necessarily match the true ones \cite [GYG18].
+Also, as the nature of OMP is greedy, and it is not clear whether it achieves optimality, and the assumption that the channel matrix is sparse warrant justification too.
 
-In this treatise, we argue that DS is worth trying as an alternative.
-As the next section shows, the effective beamformer serves readily as the sensing matrix with RIP.
+In this treatise, we suggest DS as an alternative.
+Chapter 2 shows, the effective beamformer may serve as the sensing matrix with RIP.
 Assuming uniform linear array, the sparsity may be exploited, and a convex program analogous to DS can be used for estimation, which ensures several desirable properties.
-Along the lines of \cite [CaT07], we give a bound on expected square error, expressed in terms of on the sparsity and the number of paths, which will surely faciliate system design.
-We show that it holds under an overwhelming probability, which is also bounded quantitatively.
-
-Moreover, we illustrate that the convex program is equivalent to a linear program, for which several efficient algorithms are known.
-In view of numerical results, DS is often superior to OMP among other methods, at the cost of higher complexity.
+In chapter 3, along the lines of \cite [CaT07], we give a bound on expected square error, expressed in terms of the sparsity and the number of paths.
+We claim that the bound holds for overwhelming probability.
+In chapter 4, we remark that DS can be written as an linear program, for which efficient algorithms are known.
+We present numerical results, which show that DS is often superior to OMP among other methods, which is achieved at the cost of higher complexity.
 

### 2020-11-03 treatise/4_simulation.tex
Update figures

@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
-Plots 1 to 5 have \m {N_H = 3 N_Y}, and the plots 6 to 10 has \m {N_H = 2 N_Y}.
+In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24} (from ``very small'' to ``very big''), respectively.
+Plots 1 to 5 have \m {N_H = 3 N_Y} (``narrow''), and the plots 6 to 10 has \m {N_H = 2 N_Y} (``wide'').
 %
+Assorted, \m {N_H = 3 N_Y, N_H = 12}, error:
 \blank [big]
-%\externalfigure [assorted-wide-very-small-error.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
 %
+Assorted, \m {N_H = 3 N_Y, N_H = 16}, error:
 \blank [big]
-%\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
 %
-\blank [big]
-%\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
-%
+Assorted, \m {N_H = 3 N_Y, N_H = 20}, error:
 \blank [big]
@@
 %
+Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
@@
 %
-\blank [big]
-%\externalfigure [assorted-narrow-very-small-error.png] [wfactor=fit, hfactor=fit]
-%
+Assorted, \m {N_H = 2 N_Y, N_H = 12}, error:
 \blank [big]
@@
 %
+Assorted, \m {N_H = 2 N_Y, N_H = 16}, error:
 \blank [big]
-%\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
 %
+Assorted, \m {N_H = 2 N_Y, N_H = 20}, error:
 \blank [big]
@@
 %
+Assorted, \m {N_H = 2 N_Y, N_H = 24}, error:
 \blank [big]
@@
 
-As of the plot of time taken in minutes, we give only one of \m {N_H = 12}, as an example.
+As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
 %
 \blank [big]
-\externalfigure [assorted-small-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
 
@@
 Here, the bound \m {\T {\chi}} is shown.
-
 %
-\blank [big]
-%\externalfigure [ddss-very-small-error.png] [wfactor=fit, hfactor=fit]
-%
+Assorted, \m {N_H = 3 N_Y, N_H = 12}, error:
 \blank [big]
@@
 %
+Assorted, \m {N_H = 3 N_Y, N_H = 16}, error:
 \blank [big]
@@
 %
+Assorted, \m {N_H = 3 N_Y, N_H = 20}, error:
 \blank [big]
@@
 %
+Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
+%
+As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
+%
+\blank [big]
+\externalfigure [ddss-medium-time.png] [wfactor=fit, hfactor=fit]
 
@@
 %
+Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
-%\externalfigure [oommpp-very-small-error.png] [wfactor=fit, hfactor=fit]
+\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
 %
-\blank [big]
-%\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
-%
+Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
@@
 %
+Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
+%
+As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
+%
+\blank [big]
+\externalfigure [oommpp-medium-time.png] [wfactor=fit, hfactor=fit]
 
@@
 
-Our \m {\T {\chi}}, unfortunately, does not agree the simulated error of DS, and the matter remains to be investigated in the future.
-As pointed above, the simulated error is very constant around 1, so \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
-A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3 (despite our effort to estimate), and thus the validity of performance guarantee of DS becomes more dubious.
+Our \m {\T {\chi}}, 
+It is not clear, unfortunately, why the simulated error \m {\T {\chi}} does not agree the simulated error \m {\chi} of DS, and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
+The matter remains to be investigated in the future.
+As shown above, the \m {\chi} is very constant around 1, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
+A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts.
 
@@
 
-To give some idea when DS works or not, the figure above illustrates a case where DS failed.
+To give some idea of the case that DS works or fails, the figure above illustrates a case where DS failed.
 We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.

### 2020-11-03 treatise/5_conclusion.tex
Update figures

@@
 
-This article addresses the problem of effective and estimation of the millimeter wave channel by exploiting its sparsity.
-We motivated the problem, and provided a rather broad survey of recent literature.
-This article adopts The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm.
-Rather than exploiting the sparsity of space domain representation as existing literature does, we proceed the estimation algorithm in the spatial frequency domain.
-The technique is surely inspiring to future work, as many bounds are ready to be obtained once we change the physical model of the channel.
-In addition, we have, as a secondary product, derived the generalization of DS for complex vectors.
-
+The treatise addresses the problem of effective estimation of the millimeter wave channel by exploiting its sparsity.
+Towards that end, we try the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), which is a more common choice, as the estimation algorithm.
+We proceed by exploiting the sparsity of spatial frequency domain, rather than 
+the spatial domain itself, and suggested the generalization of DS for complex vectors work in present case.
 Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Candès and Tao \cite [CaT07], that for overwhelming probability, the expected square error is bounded.
@@
 DS is steadily more accurate than all other methods, while exhibiting rather high complexity.
-Unfortunately, the program is prone to give overflown output, and we have not investigated range of parameter extensive enough for more conclusions.
+Unfortunately, , and it remains to investigate why there is no obvious trend between the signal level and the relative error norm, and a wider range of parameter has to be tried for further conclusions.
+We also point out the Python package CVXPY sometimes gives overflown values.
 
-Considering analytical bounds, it can be not easy to give meaningful comparison of existent bounds for these algorithms, as their settings are somewhat different, which we ought to keep in mind.
-Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation (Cand\`es and Tao 2005, 2007), while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
-On the other hand, as of OMP, besides the original justification of entrywise i.i.d.\ Gaussian sensing matrix (Tropp and Gilbert 2007a), there do not seem to be much analysis.
-and that (to add to complication) is still different from RIP.
-
-OMP trades off precision for time and space complexity, and for DS the other way around is true, hence we cannot say which one is universally better than the other.
-The investigation eloquently illustrates the fact that different problems requires different technique and algorihm within the current constraint, as is probably true in every discipline of engineering.
+One must be careful in giving meaningful comparison of existent analytic bounds for compressive sensing algorithms, as they might work in different settings.
+Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation \cite [CaT07], while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
+OMP, on the other hand, requires only an entrywise i.i.d.\ Normal sensing matrix \cite [TrG07a], but much analysis remains to be done.
+OMP trades off precision for a lower time and space complexity, and for DS the other way around, and this eloquently illustrates that different technique suits different problems and constraints, as is true in every discipline of engineering.
 

### 2020-11-03 treatise/1_introduction.tex
New figures for time taken

@@
 
-Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification (Rappaport et.\ al.\ \cite [RSM13]).
+Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification \cite [RSM13].
 With a large number of antennae on both transmitter and receiver, MIMO is expected to provide a large signal gain.
-The appeal of MIMO includes multiplexing gain (by parallel transmission of data), diversity gain (by redundant transmission with space-time coding), and antenna gain (by suitable beamforming).
-The millimeter wave (mm-wave) is also proposed, since its smaller wavelength, that is higher frequency, results in wider frequency bands available.
+The appeal of MIMO includes multiplexing gain (by parallel transmission of data), diversity gain (by redundant transmission with space-time coding), and antenna gain (by suitable beamforming to improve signal level).
+The millimeter wave (mm-wave) is also proposed, since its smaller wavelength, and thus higher frequency, results in wider bands available.
 The antennae, moreover, may be more closer-spaced, making it possible to increase their number.
@@
 However, MIMO also gives rise to higher complexity, hence higher hardware overhead and power consumption.
-To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, may be found.
-Here, not only is the channel estimation difficult, due to the large antennae array, but the transmission in higher frequency is subject to noise corruption too.
-Consequently, conventional training-based algorithms now have large time and space complexity.
+To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, may be obtained.
+Not only is the channel estimation difficult, due to the large antennae array, but the transmission in higher frequency is subject to noise corruption too.
+As a result, conventional training-based algorithms lead to large time and space complexity.
 
@@
 
-Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel, which is a big square matrix of dimension same as number of antennae.
-Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and thus the degree of freedom.
-And that's when a recent developement called compressive sensing may help.
-Generally speaking, it is a technique for reconstructing a underdetermined linear system, if the sparsity of solution guarantees successful recovery in the majority of cases.
+Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel, which is a big square matrix of dimension \m {N_H}, the number of antennae.
+Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and that's when a recent developement called compressive sensing may help.
+Generally speaking, it is a technique for reconstructing a underdetermined linear system, when the sparsity of solution guarantees successful recovery in most cases.
 
@@
 
-The figure above shows the generic situation in which a signal is ``crowded'' in the given basis, but is ``sparse'' in transformed basis.
-(Wikimedia Commons, \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
+The figure above shows the generic situation in which a signal is “crowded” in the given basis, but is “sparse” in transformed basis.
+(image taken from Wikimedia Commons, \Uurrll {commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
 More measurements are required to recover the signal in the former, while fewer suffice in the latter basis.
@@
 }
-Certainly, \m {\M {Q} \RB {\V {x} - \V {x}'} = 0}, then \m {\V {x}, \V {x}'} are indistinguishable.
-But if \m {\V {x}} is sparse, it essentially restrict the system so much that we obtain unique solution for most of the time.
+Certainly, \m {\M {Q} \RB {\V {x}_1 - \V {x}_2} = 0}, then \m {\V {x}_1, \V {x}_2} are indistinguishable.
+But if \m {\V {x}} is supposed to be sparse, it essentially restricts the system so much that we obtain unique solution for most of the time.
 
-Formally, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
+To define this, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
 That is, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
@@
 
-Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program covers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.
+Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.
 
-As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
-Such simplification is particularly important in medical imaging, since it is not only expensive, but also harmful to the body, to take too many images, but the imaging accuracy may be critical to the diagnosis \cite [CaT07].
+As an application, it often occurs that a camera takes a high definition photo, and compresses the image later.
+But it may be desirable that a camera equipped with fewer sensors shall take a lower-resolution photo, to save computation and storage, and shall recover the image later.
+Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, while the imaging accuracy may be critical to the diagnosis too \cite [CaT07].
 
@@
 
-But if the linear transformation is subject to noise,
+Now, if the linear transformation is subject to noise \m {z},
 %
@@
 
-We introduce several notions.
+We agree on some conventions.
 For \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}}, denote
@@
 
-For concreteness, say \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
+For concreteness, say \m {\V {z}} is an i.i.d.\ normalized random normal vector.
 If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig Selector (hencefore DS), recovery under the noisy case is again possible.
@@
 
-From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
-Indeed, relevent code has been put on their website for the reader to access and verify (Candès \& Romberg \cite [CaR05]).
-Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.
+From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, allows techniques from convex optimization to be used.
+In fact, Candès \& Romberg provided an example implementation on their website (Candès \& Romberg \cite [CaR05]).
+In addition, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.
 
 Here the constant \m {\d_s} in Definition [1] is crucial:
-we must make a series of carefully chosen but seemingly random measurement.
+we must make a series of carefully chosen but random measurement.
 We can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
-One common proposal is choosing every entry of \m {\M {Q}} to be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
-However it remains a research problem to find RIP matrices efficiently.
+One common proposal is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive a algorithm that efficiently finds RIP matrices.
 
@@
 Some scholars have thus applied compressive sensing techniques.
-One of the first attempt has been Bajwa et.\ al.\ \cite [BHS10], where they argue that the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
-What they explored was the estimation of single-antenna channel response with respect to time.
-The accompanying note by the same authors (Bajwa et.\ al.\ \cite [BHR08]) shows that \m {X} is RIP for overwhelming probability, providing the ground for the IEEE paper.
-Dealing with a linear time-invariant channel, \cite [BHR08] showed that if the convolution is seen as a linear system, the sensing matrix has RIP of overwhelmingly probability, and DS is ready to be applied, with some nice performance bounds drawing directly from \cite [CaT07].
+An early attempt was Bajwa et.\ al.\ \cite [BHS10], where they argued that 
+if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
+The accompanying note by the same group \cite [BHR08] showed that \m {X} is RIP for overwhelming probability, justifying their work.
+And \cite [BHR08], which considered a linear time-invariant channel, showed that if the convolution with channel response can be seen as a linear system, whose sensing matrix has RIP of overwhelmingly probability, and DS is readlily applied.
 
@@
 
-Around that time, Tropp and Gilbert \cite [TrG07b] suggest that a greedy algorithm called Orthogonal Matching Pursuit (OMP), which also makes use of an i.i.d.\ random matrix, may also reconstruct the sparse signal sufficiently well in an overwhemingly probability.
-
-Still consider \Rf {y:y:Qx:xz}.
-We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.
+At the same time, Tropp and Gilbert \cite [TrG07b] suggested that a greedy algorithm called Orthogonal Matching Pursuit (OMP), which also makes use of an i.i.d.\ random matrix, may also reconstruct the sparse signal sufficiently well in an overwhemingly probability.
+In so doing, we still consider \Rf {y:y:Qx:xz}, and pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.
 
@@
 %
-Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero components of \m {\V {x}}, which \cite [CaT07] calls support (here we have slightly abused the usage of subscript to indicate component indices).
+Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero components of \m {\V {x}} (here we have slightly abused the usage of subscript).
 From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.

### 2020-11-03 treatise/3_1_almost_sparsity.tex
Update discussion on numerical experiments
New figures for time taken

@@
-\startsection [title={Angular Channel Response is Almost-Sparse}]
+\startsection [title={Angular channel response is almost-sparse}]
 
-\startsubsection [title={Norm of Array Response}]
+\startsubsection [title={Norm of array response}]
 
-Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity index \m {S} be fixed.
-Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MS {A}}}}, the largest \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MS {B}}}} the next \m {s} largest components of \m {\V {g}}, and \m {\V {g} _{\SB{\MS {C}}}} are the components complement to \m {\V {g} _{\SB{\MS {A}}}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MS {A}}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\SB{\MS {B}}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\SB{\MS {C}}} =\IP {-1,0,-4,2,0}}.
-In this section, the subscripts \m {\MS {A}, \MS {B}, \MS {C}} will keep bearing analogous meaning.
+Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity level \m {S} be fixed.
+Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MS {A}}}}, the largest-magnitude \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MS {B}}}} the next \m {s} largest-magnitude components of \m {\V {g}}, and \m {\V {g} _{\SB{\MS {C}}}} are the components complement to \m {\V {g} _{\SB{\MS {A}}}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MS {A}}} =\IP {0,0,-4,0,8}}, \m {\V {g} _{\SB{\MS {B}}} =\IP {0,3,0,2,0}}, and \m {\V {g} _{\SB{\MS {C}}} =\IP {-1,3,0,2,0}}.
+In this section, the subscripts \m {\MS {A}, \MS {B}, \MS {C}} will bear analogous meaning.
 
@@
 Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
-We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity \m {s}, different from \m {S}.
-If \m {N_H} is large, we may forget for a moment the requirement that \m {s =1,2,3,\dots}.
+We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity level \m {s} different from \m {S}.
+If \m {N_H} is large, we may forget for a moment that \m {s} is an integer.
 
@@
 %
-And define the so-called Dirichlet kernel
+And set for short
 %
@@
 %
-Set for short
+And
 %
 \DispNum {b:f':Ka:af'} {
-\NC b \SB {\f}
+\NC \V {b} \SB {\f}
 =\NC \M {K}^\Adj \V {a} \SB {\f} \NR
@@
 \NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
-=\NC \F {1} {N_H}
+\leq \NC \F {1} {N_H}
 \VNm {
@@
 %
-so that, by \m {\ell_p}-norm inequality,
+so that, by \m {\ell_p}-norm inequality, we have the following estimation.
 
@@
 \DispNum {a:2:4N:NH} {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _2
+\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
 \leq \NC \F {2} {\pi} \log N_H \NR
@@
 
-\startsubsection [title={Norm of Angular Channel Response}]
+\startsubsection [title={Norm of angular channel response}]
 
@@
 }
-by triangle inequality, by the property of 2-norm and Frobenius norm,
+by triangle inequality, by the property of Frobenius norm,
 %
@@
 \sum _{l=0} ^{L-1} \Nm {\a_l}
-\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _2
-\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _2 \NR
+\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _1
+\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _1 \NR
 %
 \NC \leq \NC
-\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _2
-\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _2
+\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _1
+\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _1
 \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
@@
 is a sample mean, and we may want to use Hoeffding inequality.
-Since it requires that the random variable shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2}, on which there is 95 percent of the probability mass.
+Since it requires that the r.v.\ shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2} for simplicity, on which there is 95 percent of the probability mass.
 %
@@
 }
-So, by Hoeffding inequality, choose for simplicity
+So, by Hoeffding inequality, choose also for simplicity
 %
@@
 \leq \NC \F {12 \R{2}} {\pi ^{5/2}}
-\leq 4/3. \NR
+\leq \F {4} {3}. \NR
 }

### 2020-11-03 treatise/3_2_confirming_restricted_isometry.tex
New figures for time taken

@@
 
-\startsubsection [title={Design of beamformer matrices}]
+\startsubsection [title={Design of beamformers}]
 
-Our plan is setting the four precoder matrices to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
-
-Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ Normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
+Our plan is setting the four beamformers to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
+Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
 We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_Y}}} follows Rayleigh distribution.
 \m {\RB {\M {W} _B ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.
-
 In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane.
@@
 In fact, the statement seems to be false in general.
-Indeed, since a \m {\M {F} _R ^\Tr} of the same \m {\d} is sparse, up to a factor of isometry matrix, and \m {\M {F} _R ^\Tr} is generated randomly, it would seem to us that the probability that \m {\M {F} _R ^\Tr \V {u}} be sparse is exceedingly small.
-
 But all is not lost.
-At least we have made sure that \m {\M {F} _R ^\Tr \V {u}} has norm close to unity.
-If we have a stronger result, that \m {\M {F} _B ^\Tr \V {u}} is almost unitary even for \It {not-sparse} vectors, then we are done.
-That does sound somehow plausible, considering the Normal entries of \m {\M {F} _B ^\Tr} would introduce a Central-limit-theorem-like sum, though the summands are not independent, but weakly dependent.
+Can we argue instead that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has similar norm with \m {\M {F} _R ^\Tr \V {u}}?
 
@@
 
-To start, use \m {\chi _{i,j}} to denote Complex Standard Normal random variables, and to simplify notation, let them be independent if they have different arguments.
+Use \m {\chi _{i,j}} to denote complex standard normal r.vs., and to simplify notation, let them be independent if they have different indices.
 With this,
@@
 %
-Essentially, we seek for a large- deviation result for i.i.d.\ sum of chi-square random variables now.
+Essentially, we seek for a large- deviation result for i.i.d.\ sum of chi-square r.vs.\ now.
 To so so, we may apply Lemma 1 in Laurent and Massart \cite [LaM00] for equal weights.
@@
 \DispNum {P:x:ex:ex!} {
-\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 + 2 \R {\F {x} {N_B}}}
+\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_B}}}
 \leq \NC \Ss {e} ^{-x} \NR
@@
 
-Here, we consult Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' collected in \cite [KlM17].
+Here, we consult Haviv and Regev, “The restricted isometry property of subsampled Fourier matrices” collected in \cite [KlM17].
 We need their Thm.\ 4.5; it gives a RIP guarantee w.r.t.\ \m {\d_s}, and probability lower bound, for DFT submatrix.

### 2020-11-03 treatise/4_simulation.tex
New figures for time taken

@@
 
-We are ready to verify bound of eror norm of DS by numerical experiments.
-DS is a convex optimization program, and there are many library devoted on that.
-For present purpose, we choose the ready-made Python library CVXPY.
+In this chapter we shall verify the bound \m {\T {\chi}} by numerical experiments.
+DS is a convex optimization program, and for present purpose, we choose the Python library CVXPY.
 For the implementation details, see Diamond and Boyd \cite [DiB16]
 
-However, it turns out direct implementation of Algorithm 8 exhibit extraordinarily large complexity, and we would like to recast the problem in a more tractable form.
-Towards that end, we found out that Candès and Romberg \cite [CaR05] has shown that DS can be simplified as an linear program (LP).
-However, the situation is more cubersome than that, since they deal with real vectors, but we consider the complex ones.
-Fortunately, they have briefly pointed out, complex DS can be recast as an linear program (LP), one of the several standard convex programming problems for which there are already several efficient algorithms.
+A direct implementation of Algorithm [7] exhibits extraordinarily large complexity, but Candès and Romberg \cite [CaR05] showed that DS can be simplified as an linear program (LP) (even though they assumed real vectors, and we consider the complex ones), which we reproduce below.
 
@@
 \NC \V {m} \in \NC \MB {R} ^{N_H^2} \NR
-\NC \V {m} \DB{n_h}
-= \NC \Nm{\V {g} \DB{n_h}} \NR
+\NC \V {m} _{\SB{n_h}}
+= \NC \Nm{\V {g} _{\SB {n_h}}} \NR
 \NC n_h, n_h', n_h'' 
@@
 
-We also tried another version of DS, in which DS is applied twice in estimated nonzero-position.
+We also tried another version of DS, in which DS is applied twice in estimated nonzero components.
 The two-stage method was briefly mentioned \cite [CaT07] but without further justification by numerical experiments.
 To apply the method, we first apply DS as before.
-Then, we extract largest positions of the estimated vector, and apply DS again.
-Futhermore, we extract largest positions of the second estimated vector, and apply LS.
+Then, we extract largest components of the estimated vector, and apply DS again.
+Futhermore, we extract largest components of the second estimated vector, and apply LS.
 The final vector's indices has to be scrambled back according to the original index.
@@
 In the following simulation, we use dimensionless noise-to-signal level \m {\s}.
-Its value start with \m {2^{-4}}, and increase by multiplying 2.
+Its value starts with \m {2^{-4}}, and is increased by being multiplied with 2.
 For the plot of assorted methods, 8 values of \m {\s} are used; for the plots of only OMP, 9 values are used; for the plots of only OMP, 6 values are used.
@@
 On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
-Unfortunately, this is very far from achieving the design values \Rf {N:B:4l:H2}, and this may be part of the reason the results is not as successful as expected.
+Unfortunately, this is very far from achieving the design values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
 
@@
 The number of paths \m {L} is \m {4}.
-The wavelength of carrier \m {\l _{\Rm {ant}}}, is set to be \m {0.1}.
-and the antenna spacing \m {d _{\Rm {ant}} =0.2}.
+The wavelength of carrier \m {\l _{\Rm {ant}}} is set to be \m {0.1}.
+and the antenna spacing \m {d _{\Rm {ant}}} is 0.2.
 Only their ratio matters.
@@
 The maximal number of iteration of CVXPY is set to be \m {32}.
-On the other hand, the maximal number of iteration of OMP is set to be \m {4 N_H}.
+On the other hand, the maximal number of iteration of OMP is set to be \m {4 N_Y}.
 
 Denote the threshold used in DS program to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
-Various several values are tried for them by first taking the theory value, and multiply or divide it by powers of 2.
+Different values are tried by multiplying or dividing them by powers of 2.
 
@@
 For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
-For OMP, suggested values in Cai \& Wang (2011) is illuminating, where they (in their Theorem 7) considered \m {\ell _2}-norm, and Theorem 8, \m {\ell _\infty}-norm.
-We make simplification and set respectively \m {\R {3} N_Y} and \m {2 \R {\log N_H}}.
+For OMP, suggested values in Cai \& Wang (2011) is illuminating, where they (in their Theorem 7) considered \m {\ell _2}-norm, and (in their Theorem 8), \m {\ell _\infty}-norm.
+We make simplification and set respectively \m {\R {3 N_Y}} and \m {2 \R {\log N_H}}.
 Meanwhile, the threshold used for the remainder norm used in OMP program is suggested in \cite [CaW11].
@@
 
-In the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \h_{\Rm {OMP}} to observe the effects of thresholds.
+In the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} to observe the effects of thresholds.
 
@@
 However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
-It is not clear, either, whether \m {\T {\chi}} is a good indicator of channel capacity, since we do not fix a channel model in our investigation.
+We do not know, either, whether \m {\T {\chi}} is a good indicator of channel capacity, since we do not fix a channel model in our investigation.
 
@@
 the maximum feasible tolerance to be \m {5 \D 10 ^ {-7}}.
-It remains to be investigated what values are most suitable for our purposes.
-If the tolerance parameters are too small, the program often gives overflown output, perhaps because it cannot find feasible solutions.
-On the other hand, if they are too big, the steps become imprecise and the program may fail to find correct solutions.
+It remains to be tested what values are most suitable for our purposes.
+If the tolerance parameters are too small, the program often gives overflowing values, perhaps because it cannot find feasible solutions.
+On the other hand, if they are too big, the steps are so imprecise that the program may fail to solve.
 
@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24} (from ``very small'' to ``very big''), respectively.
-Plots 1 to 5 have \m {N_H = 3 N_Y} (``narrow''), and the plots 6 to 10 has \m {N_H = 2 N_Y} (``wide'').
-%
+In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
+Plots 1 to 5 have \m {N_H = 3 N_Y}, and the plots 6 to 10 has \m {N_H = 2 N_Y}.
+
 Assorted, \m {N_H = 3 N_Y, N_H = 12}, error:
@@
 Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_Y} for each of them.
-Here, the bound \m {\T {\chi}} is shown.
+Here, \m {\T {\chi}} is shown too.
 %
@@
 
-In the assorted plot, DS steadily outperforms other methods, and LS is worse than DS, and Lasso still worse, and OMP still worse.
-However, it is not clear how higher \m {\s} corresponds to lower error.
-It seems when \m {\s} is further increased near the leftmost of the figures, the error might also increase rapidly, but in that case, many methods give overflown values.
+In the assorted plots, DS steadily outperforms other methods, and LS is worse than DS, and Lasso still worse, and OMP still worse.
+However, it is not clear how higher \m {\s} (dimensionless noise level) corresponds to lower \m {\T {\chi}} (simulated error).
+It seems when \m {\s} is further increased (leftmost of the figures), the error might also increase rapidly, but more parameters have to be simulated for a conclusion.
 
-Varying thresholds of DS (namely \m {\g_{\Rm {DS}}}) and OMP (namely \m {\h_{\Rm {OMP}}}) does not have significant effect on the output, and from the cases simulated, there can be no conclusive answer.
-Nevertheless, it appears \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is intuitive.
+Varying thresholds of DS (namely \m {\g_{\Rm {DS}}}) and OMP (namely \m {\h_{\Rm {OMP}}}) appears not to affect the estimation significantly.
+Nevertheless, it seems \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is reasonable.
 Sometimes the iteration stablizes much earlier than is constrained by maximum iteration number.
 
-Our \m {\T {\chi}}, 
-It is not clear, unfortunately, why the simulated error \m {\T {\chi}} does not agree the simulated error \m {\chi} of DS, and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
-The matter remains to be investigated in the future.
+Sadly, we remark that CVXPY sometimes gives overflowing answers, some of them as large as \m {10^11}.
+This indicates perhaps some typical-looking output may in fact be unreliable.
+To rid overflowing values, we discard output larger than a given threshold, like \m {10^4}, but there may be better methods.
+
+It is not clear, unfortunately, why \m {\T {\chi}} does not agree \m {\chi} (the error bound), and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
 As shown above, the \m {\chi} is very constant around 1, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
 A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts.
+These matters remain to be investigated in the future.
 
@@
 To give some idea of the case that DS works or fails, the figure above illustrates a case where DS failed.
-We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.
-Subsequent application of DS on the wrong index set fails, as a result.
+The true values of \m {\M {H}} entries are ordered with respect to their absolute value, and corresponding estimated values in the first and second stage are plotted against the true values.
+We see that the soft thresholding did not rule out smaller entries, so a second application of DS on the wrong index set fails too.
 
@@
 The figure above illustrates a case where DS succeeded.
-The true values of \m {\M {H}} entries are ordered with respect to absolute value, and corresponding estimated value in the first and second stage, are plotted agains the true values.
-We see that the soft thresholding policy does rule out those entries which are too small and gives a reasonable guess of the positions of non-zero entries.
-The subsequent application of DS on this smaller index set refines the estimated values.
+We see that the soft thresholding did rule out smaller entries, and gives a reasonable guess of the nonzero components, so a second application of DS on this smaller index set refines the estimated values.
 
@@
 
-We discuss the complexity of DS and OMP.
-
+We investigate the complexity of DS and OMP.
 For DS, we note that, in general, complexity analysis of convex programs is difficult, in that it is not easily ensured how many iteration the program uses.
-
 There is an analysis (Boyd and Vandenberghe \cite [BoV04]) of inequality constrained Newton method, in which they assumed self-concordance (p.496ff, also p.531).

### 2020-11-03 treatise/5_conclusion.tex
New figures for time taken

@@
 DS is steadily more accurate than all other methods, while exhibiting rather high complexity.
-Unfortunately, , and it remains to investigate why there is no obvious trend between the signal level and the relative error norm, and a wider range of parameter has to be tried for further conclusions.
-We also point out the Python package CVXPY sometimes gives overflown values.
+Unfortunately, and it remains to investigate why there is no obvious trend between the signal level and the relative error norm, and why CVXPY sometimes gives overflowing answers.
 

### 2020-11-03 treatise/acknowledgement.tex
New figures for time taken

\starttitle [title={Acknowledgement}]

For various reasons, I took very long time writing this treatise.
In the start, I came across the field of compressive sensing in 2018 when I was the TA of the course of Convex Optimization, and also when I was an intern in MediaTek.
I told Prof.\ Su of the proposal, which by then was hardly more than a vague stream of conciousness.
I thank him for always being generous to let students find their own topic of interest, and for having encouraged me to continue writing what would become of the present treatise, even not without procrastination and interruption.

I also want to thank Chu-Tong Liu, The PhD student of Prof.\ Su's, and also an aquaintence of mine since the freshman year, in that he gave me various suggestions when I was stuck and was tolerant when I did not, or even fail at all, to deliver a proper presentation.

Furthermore, I thank my parents, who in recent years was supportive of whatever goal I set up to do (or at least claim to work on), if slightly too credulous regarding my ability.
It was a tremendous luck that I did not have to mind the financial matters: something I ought to cherish, but did so only in later years.
I was happy to have been free to keep a sense of curiosity of the intricacy of the universe.

November 4, 2020

\stoptitle

### 2020-11-04 treatise/4_simulation.tex
Discuss runtime statistics

@@
 We investigate the complexity of DS and OMP.
-For DS, we note that, in general, complexity analysis of convex programs is difficult, in that it is not easily ensured how many iteration the program uses.
-There is an analysis (Boyd and Vandenberghe \cite [BoV04]) of inequality constrained Newton method, in which they assumed self-concordance (p.496ff, also p.531).
-It is also pointed out (Candès and Romberg \cite [CaR05]) that the complex DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.
-
+In general, complexity analysis of convex programs is difficult, in that it is not easily to determine how many iterations were used.
+There is an analysis by Boyd and Vandenberghe \cite [BoV04] of inequality constrained Newton method, in which they assumed self-concordance (p.496ff, also p.531).
+It is also pointed out by Candès and Romberg \cite [CaR05] that the complex DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.
+These results regard Newton method, which for our purpose, we only discuss the complexity analysis for Newton method.
 However, it is not clear whether these results hold for methods faster than Newton method, and of course they are not necessarily utilized the same way in CVXPY.
 Specifically, the implementers of CVXPY, Diamond and Boyd \cite [DiB16], alleges that the program is usually converted in to primal-dual problem, for which and there are several different approaches.
-For our purpose, we only discuss the complexity analysis for Newton method.
 
@@
 
-Friedlander and Saunders \cite [FrS07] criticizes that DS often gives a higher computational cost, compared to Lasso.
-Agreeing their observation, simulation shows that DS indeed exhibits high complexity when (in our case) \m {N_H} grows.
-It is not suprising from the fact that the convex program requires a sizable memory when finding the Newton step, where our program has to calculate (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
-However we note that different tolerance of error and value of maximal iteration number may result vastly different computation time.
+Use \m {t_{\Rm {OMP}} \SB {N_H}}, \m {t_{\Rm {Lasso}} \SB {N_H}}, \m {t_{\Rm {DS}} \SB {N_H}} to denote their respective time taken.
+We reproduce the arithmetic average (including different \m {\s}) of simlated values below, in seconds.
+\DispNum {t:2:95:55} {
+\NC t_{\Rm {OMP}} \SB {12} \NC = 0.0119 \NR % OK
+\NC t_{\Rm {OMP}} \SB {16} \NC = 0.0297 \NR % OK
+\NC t_{\Rm {OMP}} \SB {20} \NC = 0.0600 \NR % OK
+\NC t_{\Rm {OMP}} \SB {24} \NC = 0.155 \NR % OK
+%
+\NC t_{\Rm {Lasso}} \SB {12} \NC = 0.0436 \NR % OK
+\NC t_{\Rm {Lasso}} \SB {16} \NC = 0.176 \NR % OK
+\NC t_{\Rm {Lasso}} \SB {20} \NC = 0.471 \NR % OK
+\NC t_{\Rm {Lasso}} \SB {24} \NC = 1.26 \NR % OK
+%
+\NC t_{\Rm {DS}} \SB {12} \NC = 0.357 \NR % OK
+\NC t_{\Rm {DS}} \SB {16} \NC = 2.07 \NR % OK
+\NC t_{\Rm {DS}} \SB {20} \NC = 29.8 \NR % OK
+\NC t_{\Rm {DS}} \SB {24} \NC = 91.5 \NR % OK
+}
+Simulation indeed shows that \m {t_{\Rm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
+It is not suprising, regarding the fact that the convex program has to find the Newton step by calculating (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
+The matrix inversion is probably the bottleneck of complexity.
+However, as we noted above, that different tolerance level of and maximal iteration number may result in vastly different computation time.
 
-Meanwhile, we see the complexity of OMP is several order of magnitude lower than that of DS.
-This is reasonable, given that it is a greedy alrogithm.
-In fact, the time OMP takes is negligibly small.
+Meanwhile, \m {t_{\Rm {Lasso}}} and \m {t_{\Rm {OMP}}} are often an order of magnitude lower than \m {t_{\Rm {DS}}}.
+In general, \m {t_{\Rm {DS}} \gg t_{\Rm {Lasso}} \gg t_{\Rm {OMP}}}.
+It is now wonder that, given that OMP is a greedy alrogithm, the time OMP takes is negligibly small.
+But it is also notable that, while Lasso has form similar to DS, it takes much lower time.
 
-Lasso usually takes time \m {1/2} to \m {1/4} of that of DS.
+Assuming the complexity of each of three methods is polynomial time, we calculate a least square fit for the power of complexity, giving
+
+\DispNum {t:P:NH:83} {
+\NC t_{\Rm {OMP}} \NC \eqsim \MS {O} \SB {N_H^{3.6}} \NR
+\NC t_{\Rm {Lasso}} \NC \eqsim \MS {O} \SB {N_H^{4.8}} \NR
+\NC t_{\Rm {DS}} \NC \eqsim \MS {O} \SB {N_H^{8.3}} \NR
+}
 

### 2020-11-05 treatise/4_simulation.tex
Rev complexity discussion

@@
 
-Sadly, we remark that CVXPY sometimes gives overflowing answers, some of them as large as \m {10^11}.
+Sadly, we remark that CVXPY sometimes gives overflowing outputs, some of them as large as \m {10^11}.
 This indicates perhaps some typical-looking output may in fact be unreliable.
-To rid overflowing values, we discard output larger than a given threshold, like \m {10^4}, but there may be better methods.
+To rid overflowing values, we discard outputs larger than a given threshold, say \m {10^4}, and simply apply a least square.
+It is open whether there are better methods.
 
@@
 
-We investigate the complexity of DS and OMP.
-In general, complexity analysis of convex programs is difficult, in that it is not easily to determine how many iterations were used.
-There is an analysis by Boyd and Vandenberghe \cite [BoV04] of inequality constrained Newton method, in which they assumed self-concordance (p.496ff, also p.531).
-It is also pointed out by Candès and Romberg \cite [CaR05] that the complex DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.
-These results regard Newton method, which for our purpose, we only discuss the complexity analysis for Newton method.
-However, it is not clear whether these results hold for methods faster than Newton method, and of course they are not necessarily utilized the same way in CVXPY.
-Specifically, the implementers of CVXPY, Diamond and Boyd \cite [DiB16], alleges that the program is usually converted in to primal-dual problem, for which and there are several different approaches.
+We want to know the complexity of DS and OMP.
+In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many iterations were done.
+Boyd and Vandenberghe \cite [BoV04] analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496ff, also p.531).
+In our case, Candès and Romberg \cite [CaR05] pointed out that the complex DS can be cast into an second order cone programming (SOCP), and where self concordance holds.
+Diamond and Boyd (writers of CVXPY) \cite [DiB16] explained that convex programs are usually converted into primal-dual problems.
+The library we called in the simulation is ECOS, where Newton method is used.
+Of course, we are not certain there is no method faster than Newton method, and implmentation details of CVXPY may change the conclusion too.
 
-The function being minimized is \m {\VNm {\V {g}}_1}.
+We attemp to give a heuristic argument regarding the complexity of Newton steps.
+We say the function being minimized is \m {\VNm {\V {g}}_1}.
 Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
-Then (\cite [BoV04] p.505, Eqn.\ 9.56) gives a bound of the number of iteration of Newton method.
+Then Boyd and Vandenberghe \cite [BoV04] (p.505, Eqn.\ 9.56) gave a bound of the number of steps.
 If we just take that as the complexity bound for DS, it becomes
@@
 \NC C_{\Rm {DS}}
-= \NC C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
-+ \log_2 \log_2 \F {1} {\e} \NR
+= \NC \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
++ \log_2 \log_2 \F {1} {\e}} C_{\Rm {step}} \NR
 }
 %
-where \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error.
-According to the analysis of \cite [BoV04] (eq.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
-Also, \m {C_0} usually assumes the value of about several hundred;
-They gives an example \m {C_0 =375} (with their notation, \m {C_0 =\dfrac {20 -8\a} {\a \b \RB {1 -2\a}^2}}, where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).
+Here \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error, and \m {C_{\Rm {step}}} is the complexity of Newton step.
+According to their analysis (eq.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
+Also, \m {C_0} usually assumes the value of about several hundred.
+There was an example they gave in which \m {C_0 =375}, where, with their notation,
+\m {C_0 =(20 -8\a) / (\a \b \RB {1 -2\a}^2}), where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).
 
-Every step involves a inversion of \m {\MS {O} \SB {\M {P} ^\Adj \M {P}}}, which is of the same order of magnitude to the time needed for matrix multiplication.
-Since the dimension of \m {\M {P} ^\Adj \M {P}} is \m {N_H^2}, the cost of inversion is \m {\MS {O} \SB {N_H^4}}.
+Every Newton step involves a inversion of \m {\MS {O} \SB {\M {P} ^\Adj \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
+Since the dimension of \m {\M {P} ^\Adj \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\MS {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
+That is, we suppose \m {C_{\Rm {step}} = N_H^4}.
 
-We now take some license to approximate.
-Assume that we start the iteration by specifying the Least Square estimator as the initial value of \m {\V {g}_0}, namely
+We take some liberty to assume that, at the start the iteration, the least square estimator was taken to be the initial value of \m {\V {g}_0}, namely
 %
@@
 %
-Indeed, this is the main objective of our investigation!
+Indeed, this is the main thesis of our investigation.
 And by restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so
@@
 
+We see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes complex standard normal distribution.
 If we agree that, for high probability,
@@
 }
-
-It is easy to see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes Complex Standard Normal distribution.
-If the quantity can be estimated by \m {\s}, we have
+Then we simply have
 %
@@
 On the other hand, Tropp and Gilbert \cite [TrG07a] discussed the complexity of OMP, and the proof of technical lemmata in it can be found in the companion paper \cite [TrG07b].
-They give
+They gave
 %
@@
 %
-And it would appear that this is greater than \m {C_{\Rm {DS}}}.
-However, \m {\log N_Y} is really small in our experiments.
-and we dropped some constants, too, in analyzing \m {C_{\Rm {DS}}}.
-If we drop \m {\log N_Y}, then we get \m {\MS {O} \SB {N_H^2}} again.
+Here \m {\log N_Y} is small in our experiments, and if we dropped some constants and \m {\log N_Y}, then we may assume \m {\MS {O} \SB {N_H^2}}.
 
-Lastly, since LS involves the same target function as DS, the same argument is valid, giving \m {C_{\Rm {Lasso}} =\MS {O} \SB {N_H^6}}.
+Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\Rm {Lasso}} =\MS {O} \SB {N_H^6}}.
 
@@
 \DispNum {t:2:95:55} {
-\NC t_{\Rm {OMP}} \SB {12} \NC = 0.0119 \NR % OK
-\NC t_{\Rm {OMP}} \SB {16} \NC = 0.0297 \NR % OK
-\NC t_{\Rm {OMP}} \SB {20} \NC = 0.0600 \NR % OK
-\NC t_{\Rm {OMP}} \SB {24} \NC = 0.155 \NR % OK
+\NC t_{\Rm {OMP}} \SB {12} \NC = 0.0119,
+\FourQ t_{\Rm {OMP}} \SB {16} = 0.0297, \NR
+\NC t_{\Rm {OMP}} \SB {20} \NC = 0.0600,
+\FourQ t_{\Rm {OMP}} \SB {24} = 0.155, \NR
 %
-\NC t_{\Rm {Lasso}} \SB {12} \NC = 0.0436 \NR % OK
-\NC t_{\Rm {Lasso}} \SB {16} \NC = 0.176 \NR % OK
-\NC t_{\Rm {Lasso}} \SB {20} \NC = 0.471 \NR % OK
-\NC t_{\Rm {Lasso}} \SB {24} \NC = 1.26 \NR % OK
+\NC t_{\Rm {Lasso}} \SB {12} \NC = 0.0436,
+\FourQ t_{\Rm {Lasso}} \SB {16} = 0.176, \NR
+\NC t_{\Rm {Lasso}} \SB {20} \NC = 0.471,
+\FourQ t_{\Rm {Lasso}} \SB {24} = 1.26, \NR
 %
-\NC t_{\Rm {DS}} \SB {12} \NC = 0.357 \NR % OK
-\NC t_{\Rm {DS}} \SB {16} \NC = 2.07 \NR % OK
-\NC t_{\Rm {DS}} \SB {20} \NC = 29.8 \NR % OK
-\NC t_{\Rm {DS}} \SB {24} \NC = 91.5 \NR % OK
+\NC t_{\Rm {DS}} \SB {12} \NC = 0.357,
+\FourQ t_{\Rm {DS}} \SB {16} = 2.07, \NR
+\NC t_{\Rm {DS}} \SB {20} \NC = 29.8,
+\FourQ t_{\Rm {DS}} \SB {24} = 91.5, \NR
 }
@@
 
-Assuming the complexity of each of three methods is polynomial time, we calculate a least square fit for the power of complexity, giving
+Assuming the complexity of each of three methods is polynomial time, we calculate a least square fit for the power of complexity, giving the following estimated values, on which we add a tilde.
 
 \DispNum {t:P:NH:83} {
-\NC t_{\Rm {OMP}} \NC \eqsim \MS {O} \SB {N_H^{3.6}} \NR
-\NC t_{\Rm {Lasso}} \NC \eqsim \MS {O} \SB {N_H^{4.8}} \NR
-\NC t_{\Rm {DS}} \NC \eqsim \MS {O} \SB {N_H^{8.3}} \NR
+\NC \T {t}_{\Rm {OMP}} \NC \eqsim \MS {O} \SB {N_H^{3.6}} \NR
+\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \MS {O} \SB {N_H^{4.8}} \NR
+\NC \T {t}_{\Rm {DS}} \NC \eqsim \MS {O} \SB {N_H^{8.3}} \NR
 }

### 2020-11-08 presentation/1_introduction.tex
Incorporate rescaled plots

--- 2020-06-09 presentation/1_introduction.tex
@@
 {
-\I Multiple-input multiple-output (MIMO) communication system has been proposed as part of the 5G specification, but its hardware overhead increases complexity and power consumption.
+\I Estimation of Multiple-input multiple-output (MIMO) systems results in high complexity, due to a large number of antennae.
 
-\I The design of various algorithms requires channel information to be known.
+\I Millimeter wave (mm-Wave) channels are often sparse due its poor scattering nature
 
-\I Estimation of MIMO channels also results in high complexity, due to the large number of antennae.
+\I According to compressive sensing theory, we might exploit the sparsity to reduce complexity of estimation procedure.
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Terminology}
+{
+\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if at most \m {s} of its components are nonzero.
 
-\I Meanwhile, millimeter wave (mm-Wave) channels often exhibit sparse properties, which we might exploit to reduce complexity.
+\I We say that \m {\M {P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
+\Disp {
+\NC \RB {1-\d_s} \VNm {\V {g}} _2^2
+\leq \NC \VNm {\m {P} \V {g}} _2^2
+\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
 }
+
+\I We may think \m {\M {P}} to be almost unitary up to relative error \m {\d_s}.
+}

### 2020-11-08 presentation/2_setting.tex
Incorporate rescaled plots

@@
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {System Configuration}
+{
+\blank [big]
+\externalfigure [system.png] [factor=fit]
+
+\I Estimation of Multiple-input multiple-output (MIMO) systems results in high complexity, due to a large number of antennae.
+
+\I Problem (a): How to recover the channel with fewer measurements?
+
+\I Problem (b): How to design precoders and combiners?
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
 \Frame {Channel Model and Beamformers}
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {System Diagram}
+\Frame {Problem Description}
 {
-\blank [big]
-\externalfigure [system.png] [factor=fit]
+\I We have \m {\M {Y} =\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}}}
+%
+\I Problem (a): How to recover \m {\M {H}} with knowledge of \m {\M {Y}}?
 
-\I Problem (a): Recover \m {\M {H}} with knowledge of \\
-\m {\M {Y} :=\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}} }?
+\I Can we measure less than \m {N_H} times, but recover successfully for most cases?
 
-\I Problem (b): Design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
+\I Problem (b): How to design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
+
+\I What kind of matrices faciliates our goal?
 }
@@
 
-\I Then we have a underdetermined linear system:
-\Disp {
-\NC \V {y}
-=\NC \M {P} \V {g} +\V {z} \NR
-}
-
-\I When the signal is sparse, few measurements may be sufficient for the reconstruction
+\I We have an underdetermined system \m {\V {y} =\M {P} \V {g} +\V {z}}
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Terminology}
+\Frame {Compressive Sensing}
 {
-\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if at most \m {s} of its components are nonzero.
+\blank [big]
+\externalfigure [compressive-sensing.png] [factor=fit]
 
-\I We say that \m {\M {P}} satisfies the \Emph {restricted isometry property} (RIP) of sparsity \m {s} with respect to \m {0 < \d_s < 1}, if, for all \m {s}-sparse \m {\V {g}},
-\Disp {
-\NC \RB {1-\d_s} \VNm {\V {g}} _2^2
-\leq \NC \VNm {\m {P} \V {g}} _2^2
-\leq \RB {1+\d_s} \VNm {\V {g}} _2^2
+\I If \m {\V {g}} is sparse, few measurements may suffice for reconstruction.
+
+\I Can we find a basis on which \m {\V {g}} is sparse?
 }
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Literature on Compressive Channel Sensing}
+{
+\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)
 
-\I We may think \m {\M {P}} to be almost unitary up to relative error \m {\d_s}.
+\I Alkhateeb, Ayach, Leus, Heath (2014): mm-wave, adaptive training algorithm for given codebook
+
+\I Alkhateeb, Leus, and Heath (2015): single path mm-wave, all-phase-shifter beamformers, using Orthogonal Matching Pursuit (OMP)
+
+\I Lee, Lee, and Yong (2016): MIMO mm-wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Question}
+{
+\I Candès and Tao (2007) proposed a performance bound for DS, then can DS do better than OMP?
+
+\I Does convex programming (DS) trade accuracy with greedy algorithms (OMP)?
+
+\I May we verify a revised performance bound in the concrete case?
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Our Contribution}
+{
+\I Consider MIMO mm-wave channel, with hybrid beamforming
+
+\I Use a modified DS (convex programming), instead of OMP (greedy algorithm)
+
+\I Illustrate by experiments that DS has better performance
+
+\I Give an analysis of error norm and successful probability in terms of system parameters
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Design of Beamformers}
+{
+\I We set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ complex standard normal, up to a design constant
+
+\I We set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed in argument and unity magnitude, up to a design constant
+
+\I We argue that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, thus \m {\M {P}} has too.
 }
@@
 {
-\I We try to apply Dantzig Selector to our problem:
+\I Fix sparsity \m {s = L \RB {\log N_H}^2} for definiteness.
 
@@
 }
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Design of Beamformers}
-{
-\I Let us set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ complex standard normal, up to a design constant
-
-\I And set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed in argument and unity magnitude, up to a design constant
-
-\I We will argue that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, thus \m {\M {P}} has too.
-
-\I Fix sparsity \m {s = L \RB {\log N_H}^2} for concreteness
-}

### 2020-11-08 presentation/4_simulation.tex
Incorporate rescaled plots

@@
 \blank [big]
+\externalfigure [assorted-narrow-medium-error.png] [width=11cm]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=2N_Y}}
+{
+\blank [big]
 \externalfigure [assorted-narrow-very-big-error.png] [width=11cm]
@@
 \blank [big]
-\externalfigure [assorted-wide-very-big-error.png] [width=11cm]
+\externalfigure [assorted-wide-medium-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\chi}, OMP only, \m {N_H=24=3N_Y}}
+\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=3N_Y}}
 {
 \blank [big]
-\externalfigure [oommpp-medium-error.png] [width=11cm]
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\chi}, DS only, \m {N_H=24=3N_Y}}
-{
-\blank [big]
-\externalfigure [ddss-medium-error.png] [width=11cm]
+\externalfigure [assorted-wide-very-big-error.png] [width=11cm]
 }
@@
 
-\I The weaker constraint on sparsity might have conpromised DS's performance.
+\I The weaker constraint on sparsity might have compromised DS's performance.
 
@@
 
-\I When DS succeeds: soft thresholding (green) correctly guesses the true values of non-zero positions (black), and refines the estimated value (orange)
+\I Soft thresholding (green) correctly guesses true nonzero components (black), and refines the estimated value (orange)
 }
@@
 
-\I When DS fails: soft thresholding (green) does not correctly guess the true values of non-zero positions (black), and the estimated value (orange) becomes worse
+\I Soft thresholding (green) guesses wrong nonzero components (black), and the estimated value (orange) deteriorates
 }

### 2020-11-08 presentation/5_conclusion.tex
Incorporate rescaled plots

@@
 
-\I J Lee, G-T Lee, and H Yong, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 64(6), 2016.
+\I J Lee, G-T Gil, and Y H Lee, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 64(6), 2016.
 

### 2020-11-08 treatise/1_introduction.tex
Incorporate rescaled plots

@@
 Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel, which is a big square matrix of dimension \m {N_H}, the number of antennae.
-Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and that's when a recent developement called compressive sensing may help.
+Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and that's when a recent development called compressive sensing may help.
 Generally speaking, it is a technique for reconstructing a underdetermined linear system, when the sparsity of solution guarantees successful recovery in most cases.
@@
 \externalfigure [compressive-sensing.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {
+A generic situation in which a signal is “crowded” in the given basis, but is “sparse” in transformed basis.
+(Retrieved from \goto {\hyphenatedurl {Wikimedia Commons}} [url (commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif)])
+}
+\blank [big]
 
-The figure above shows the generic situation in which a signal is “crowded” in the given basis, but is “sparse” in transformed basis.
-(image taken from Wikimedia Commons, \Uurrll {commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})
 More measurements are required to recover the signal in the former, while fewer suffice in the latter basis.
@@
 For concreteness, say \m {\V {z}} is an i.i.d.\ normalized random normal vector.
-If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig Selector (hencefore DS), recovery under the noisy case is again possible.
+If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig Selector (hereafter DS), recovery under the noisy case is again possible.
 
@@
 The accompanying note by the same group \cite [BHR08] showed that \m {X} is RIP for overwhelming probability, justifying their work.
-And \cite [BHR08], which considered a linear time-invariant channel, showed that if the convolution with channel response can be seen as a linear system, whose sensing matrix has RIP of overwhelmingly probability, and DS is readlily applied.
+And \cite [BHR08], which considered a linear time-invariant channel, showed that if the convolution with channel response can be seen as a linear system, whose sensing matrix has RIP of overwhelmingly probability, and DS is readily applied.
 
@@
 
-At the same time, Tropp and Gilbert \cite [TrG07b] suggested that a greedy algorithm called Orthogonal Matching Pursuit (OMP), which also makes use of an i.i.d.\ random matrix, may also reconstruct the sparse signal sufficiently well in an overwhemingly probability.
+At the same time, Tropp and Gilbert \cite [TrG07b] suggested that a greedy algorithm called Orthogonal Matching Pursuit (OMP), which also makes use of an i.i.d.\ random matrix, may also reconstruct the sparse signal sufficiently well in an overwhelmingly probability.
 In so doing, we still consider \Rf {y:y:Qx:xz}, and pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.
@@
 Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero components of \m {\V {x}} (here we have slightly abused the usage of subscript).
-From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a perfomance guarantee.
+From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a performance guarantee.
 It is instructive to note that the matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.

### 2020-11-08 treatise/2_problem_setting.tex
Update discussion on numerical experiments
New figures for time taken
Incorporate rescaled plots

@@
-\startchapter [title={Problem Setting}]
+\startchapter [title={Problem setting}]
 
-\startsection [title={Channel Model}]
+\startsection [title={Channel model}]
 
@@
 \NC \V {a} \SB {\psi'}
-\in \NC \MB {V} _\MB {C} \SB {N_H} \NR
+\in \NC \MB {C} ^ {N_H} \NR
 %
@@
 
-\startsection [title={System Model}]
+\startsection [title={System model}]
 
+\blank [big]
 \externalfigure [system.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Schematic diagram of the hybrid beamforming system we consider.}
+\blank [big]
 
-We consider the hybrid configuration at both transmitter and receiver end, as shown in the figure.
-That is to say, each end consists of both digital and analog percoders and combiners, as follows.
-In the transmitter end, there are, in order seeing from the end, digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_Y}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
-Similarly, in the receiver end, there are, in order seeing from the end, digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_Y \D  N_R}}.
+We consider the hybrid beamforming at both transmitter and receiver end, as shown in the figure.
+That is to say, each end consists of both digital and analog precoders and combiners, as follows.
+In the transmitter end, there are (seeing towards receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_Y}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
+Similarly, in the receiver end, there are (seeing towards transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_Y \D  N_R}}.
 
@@
 \DispNum {F:R:1::R1} {
-\NC \Nm {\M {F} _R \DB {n_H, n_R}}
+\NC \Nm {\M {F} _R} _{\SB {n_H, n_R}}
 = \NC 1, \NR
 %
-\NC \Nm {\M {W} _R \DB {n_R, n_H}}
+\NC \Nm {\M {W} _R} _{\SB {n_R, n_H}}
 = \NC 1, \NR
@@
 %
-The bijectivity is obvious, and we define \m {\Rm {vec} ^{-1}} so that
+The bijection is obvious, and we define \m {\Rm {vec} ^{-1}} so that
 %
@@
 
-And we will exploit the relation (whose proof is a strightforward application of definitions)
+And we will exploit the relation, which is straightforward from definitions.
 \Result
@@
 \stopsection
-\startsection [title={The Angular Space}]
+\startsection [title={Angular space}]
 
@@
 %
-\NC \M {K} \DB {n_1, n_2}
+\NC \M {K} _{\SB {n_1, n_2}}
 = \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N_H}, \NR
@@
 := \NC \Rm {vec} \SB {\M {G}}
-\in \MB {M} _{\MB {C}} \SB {N_H^2} \NR
+\in \MB {C} ^ {N_H \D N_H} \NR
 }
@@
 \stopsection
-\startsection [title={Proposed Method}]
+\startsection [title={Proposed method}]
 

### 2020-11-08 treatise/3_1_almost_sparsity.tex
Incorporate rescaled plots

@@
 \DispNum {K:H:1N:nH} {
-\NC \RB {\V {b} \SB {\f}} _{\SB {n_H}}
+\NC \V {b} \SB {\f} _{\SB {n_H}}
 =\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
@@
 
-Now, by the nature of alternating series, for \m {- \pi \leq x < \pi}, it holds that
+By the nature of alternating series, for \m {- \pi \leq x < \pi}, it holds that
 %
@@
 }
-%
+
 Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
-We seek to bound the \quotation {rectangulars} with an integral, and we have to split the cases that \m {N_H} is odd and even.
+We seek to bound the rectangles with an integral, and we have to split the cases that \m {N_H} is odd and even.
 Anyway, a moment's reflection shows
@@
 %
-The quantity
-\DispNum {1:l:::} {
-\NC \NC \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
-}
-is a sample mean, and we may want to use Hoeffding inequality.
-Since it requires that the r.v.\ shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2} for simplicity, on which there is 95 percent of the probability mass.
-%
-To do so, observe that
+Then observe that
 %
@@
 }
-So, by Hoeffding inequality, choose also for simplicity
+By Hoeffding inequality,
 %

### 2020-11-08 treatise/3_2_confirming_restricted_isometry.tex
Incorporate rescaled plots

@@
 We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_Y}}} follows Rayleigh distribution.
-\m {\RB {\M {W} _B ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.
+\m {\RB {\M {W} _B ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analogous manner.
 In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane.
-\m {\RB {\M {W} _R ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.
+\m {\RB {\M {W} _R ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analogous manner.
 
@@
 
-Use \m {\chi _{i,j}} to denote complex standard normal r.vs., and to simplify notation, let them be independent if they have different indices.
-With this,
+Use \m {\chi _{i,j}} to denote independent complex standard normal r.vs.
+We know
 %
@@
 %
-Essentially, we seek for a large- deviation result for i.i.d.\ sum of chi-square r.vs.\ now.
+We want a large deviation result for i.i.d.\ sum of chi-square r.vs.
 To so so, we may apply Lemma 1 in Laurent and Massart \cite [LaM00] for equal weights.
@@
 {
-For \m {0 <\d_s <1},
+For \m {0 <\d_s <1}, it holds that
 %
@@
 }
-holds for probability \m {p}, with
+for probability \m {p}, with
 \DispNum {1:p:2e:s4} {
@@
 
-Here, we consult Haviv and Regev, “The restricted isometry property of subsampled Fourier matrices” collected in \cite [KlM17].
+Here, we consult Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} collected in \cite [KlM17].
 We need their Thm.\ 4.5; it gives a RIP guarantee w.r.t.\ \m {\d_s}, and probability lower bound, for DFT submatrix.
@@
 However, it can be seen that their argument allows precise constants, and they just did not spell out, which we briefly explain.
-Roughly, they use Chernoff-Hoeffding bounds, but write the exponent in the form of \m {\Omega}.
-Starting in their Thm.\ 2.2, we may substitute (say) \m {C \leftarrow 1/3} in place of their big- \m {\Omega}.
-The conclusions, their Thm.\ 3.7 and Thm.\ 4.5, may be changed accordingly.
+They use Chernoff-Hoeffding bounds, but write the exponent in the form of \m {\Omega}.
+Starting in their Thm.2.2, we may substitute (say) \m {C \leftarrow 1/3} in place of their big- \m {\Omega}.
+The conclusions, their Thm.3.7 and Thm.4.5, may be changed accordingly.
 If modified with respect to our setting, the condition
@@
 
-So, how do we relate RIP of \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} to that of \m {\M {P}}?
-Notice, by the nature of operator norm,
+So, how do we relate RIP of \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} to RIP of \m {\M {P}}?
+Notice
 \DispNum {P:2:FB:WR} {
@@
 }
-Indeed, if it were not for the sparsity constraint, if both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {F}_B^\Tr \M {F}_B^\Tr} are \m {\d_s}-RIP, \m {\M {P}} has approximately \m {2\d_s}-RIP.
+Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {F}_B^\Tr \M {F}_B^\Tr} are \m {\d_s}-RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s}-RIP.
 However, it is doubtful to assume that the Kronecker product of two RIP matrices exhibit RIP.
 
-We suggest the following argument.
-If all angles \m {\th_l, \f_l} are on exactly on the grid, then, with overwhelming probability, it is possible to write
+We try to argue as thus.
+If all angles \m {\th_l, \f_l} are exactly the multiples of \m {2 \pi/N_H}, then
 \DispNum {G:G:Ud:dU} {
@@
 \NC \VNm {\M {G}} _2
-=\NC \VNm {\V {g}} _2 \NR
-%
-\NC =\NC \VNm {\Rm {abs} \SB {\V {g}}} _2 \NR
+\NC =\VNm {\Rm {abs} \SB {\V {g}}} _2 \NR
 }
-where \m {\Rm {abs}} denotes elementwise taking absolute value.
+where \m {\Rm {abs}} denotes entrywise absolute value.
 Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\Adj \M {K}^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s}-RIP too, we see

### 2020-11-08 treatise/3_3_generalizing_the_dantzig_selector_bound.tex
Update discussion on numerical experiments
New figures for time taken
Incorporate rescaled plots

@@
-\startsection [title={Generalizing the Dantzig Selector Bound}]
-\startsubsection [title={Technical Propositions in Complex Case}]
+\startsection [title={Bound for the error norm}]
+\startsubsection [title={Technical propositions in complex case}]
 
-The third and last part of our task is to plug in the almost-sparsity found in Section 3.1, and plug in the probablity found in Section 3.2.
+The third and last part of our task is to plug in the almost-sparsity found in Section 3.1, and the failure probability found in Section 3.2.
 Set for short
@@
 %
-And our task is to bound the error norm \m {\VNm {\V {d}} _2}.
-
-We argue that \m {\V {g}} can essentially be seen as sparse, and for that purpose we approximate irrelevent terms.
-For example, we generously bound \m {\d_{S}} by \m {1}.
-And, as shall be seen, it suffices to set
+And we seek to bound \m {\VNm {\V {d}} _2}.
+To do so, we argue that \m {\V {g}} can be seen as sparse, and for that purpose we generously bound \m {\d_{S}} by \m {1}.
+As shall be seen, it suffices to set
 %
@@
 \NC \g
-= \NC \R {4 \log N_H} \NR
+= \NC 2 \R {\log N_H} \NR
 }
 %
-The propositions below are taken from \cite [CaT07] and modified slightly in accordance to our settings, except possibly the generalization to complex vector.
+The propositions below are taken from \cite [CaT07] and modified slightly in accordance to our settings, besides the generalization to complex vectors.
 %
@@
 }
-%
-To show this, observe that with triangle inequality applied respectively on \m {\MS {A}} and \m {\MS {C}}, while recalling that \m {\V {g} =\V {g} _{\SB{\MS {A}}}},
+
+To show this, apply triangle inequality respectively on \m {\MS {A}} and \m {\MS {C}}, and recall that \m {\V {g} =\V {g} _{\SB{\MS {A}}}},
 %
@@
 
-We turn our attention to the next result, and fix an instance of \m {\M {P}} and instance of \m {\V {z}}.
-We claim that
 %
-\DispNum {E:h:2N:Nh} {
-\NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}}
-\leq \NC  2 \R {2 \log N_H} \NR
+\Result
+{Proposition}
+{
+If \m {\M {P}} is \m {\d_S}-RIP, then it holds that
 %
-\NC n_h 
-=\NC 1, \ldots, N_H^2. \NR
+\DispNum {P:d:4N:Nh} {
+\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
+\leq \NC  4 \R {2 \log N_H} \NR
 }
 %
-Start with the fact that \m {\M {P} _{\SB {:, n_g}}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.
-Now, the quantity \m {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}} observes Standard Normal.
-To bound the failure probability, recall the tail bound for \m {Q} function
+for probability \m {p}, with
+%
+\DispNum {1:p:NH:H2} {
+\NC 1 -p
+\leq \NC N_H^{-2}. \NR
+}
+}
+
+To show this, we would like to bound \m {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}}, which observes standard normal.
+Recall the tail bound for \m {Q} function
 %
@@
 %
-Particularly, for \m {x' =\R {4 \log N_H}}, this gives the failure probability
+Particularly, fix threshold \m {x' =2 \R {\log N_H}}, yielding
 %
 \DispNum {Q:h:1N:Nh} {
-\NC Q\SB {\R {4 \log N_H}}
-=\NC \F {1} {N_H^2}. \NR
+\NC Q\SB {2 \R {\log N_H}}
+=\NC \F {1} {2 N_H^2}. \NR
 }
 %
-\Result
-{Proposition}
-{
-If \m {\M {P}} is \m {\d_S}-RIP,
-%
-\DispNum {P:d:4N:Nh} {
-\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC  4 \R {2 \log N_H} \NR
-}
-%
-holds for probability \m {p} 
-%
-\DispNum {1:p:NH:H2} {
-\NC 1 -p
-\leq \NC N_H^{-2}. \NR
-}
-}
-%
-To show this, by definition
+Now, by definition
 %
 \DispNum {z:y:Pg:ny} {
-\NC \IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_y}}}
-= \NC \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_y}}} \NR
+\NC \IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_h}}}
+= \NC \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \NR
 %
-\NC = \NC \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_y}}} \NR
+\NC = \NC \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} \NR
 }
@@
 \DispNum {P:g:Py:Nh} {
-\NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
+\NC \VNm {\M {P} _{\SB {:,n_h}}^\Adj \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
 \leq \NC \VNm {\M {P}^\Adj \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \NR
@@
 %
-By triangle inequality, together with \Rf {Q:h:1N:Nh}, we obtain the desired result.
+By triangle inequality, together with \Rf {Q:h:1N:Nh} and \Rf {P:g:Py:Nh}, we obtain the desired result.
 %
 \DispNum {P:d:zP:Nh} {
-\NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \M {P} \V {d}} _\infty
-\leq \NC \VNm {\IP {\V {z}, \M {P} _{\SB {:,n_y}}}} _\infty
-+ \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_y}}} \NR
+\NC \VNm {\M {P} _{\SB {:,n_h}}^\Adj \M {P} \V {d}} _\infty
+\leq \NC \VNm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}} _\infty
++ \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_h}}} \NR
 %
-\NC \leq \NC 2 \R {2 \log N_H} +2 \R {2 \log N_H} \NR
+\NC \simeq \NC 2 \R {2 \log N_H} +2 \R {2 \log N_H} \NR
 }
-%
+
 Lastly, the following two propositions are taken from \cite [CaT07], Lemma 1.
-The generalization from real vector spaces to complex spaces is completely straightforward, while meaning of magnitude and inner product has to be changed.
+The generalization from real vector spaces to complex spaces is trivial.
 One of the quoted propositions reads
@@
 %
-By power mean inequality, we get a statement cruder than \Rf {d:2:dA:12}, as below.
+By Jensen inequality,
 %
@@
 }
-%
-The other quoted proposition reads
+
+The other quoted proposition is
 %
@@
 %
-Here \m {\T {\d} _{s_1, s_2}} is called the \m {s_1,s_2}-restricted isometry constant, and is defined in \cite [Can05] (which uses \m {\th}), as follows.
+Here \m {\T {\d} _{s_1, s_2}} denotes the \m {s_1,s_2}-restricted isometry constant, and is defined in \cite [Can05] (which uses \m {\th}), as follows.
 Let \m {\M {Q}'} be fixed.
-For all \m {s_1}-sparse \m {\V {x}_1}, for all \m {s_2}-sparse \m {\V {x}_2}, whose nonzero-positions are disjoint,
+For all \m {s_1}-sparse \m {\V {x}_1}, for all \m {s_2}-sparse \m {\V {x}_2}, whose nonzero-components are disjoint,
 %
@@
 %
-Here we use a result in \cite [Can05] that relates \m {\T {\d} _{s_1, s_2}} to \m {\d_s}, that is
+\m {\T {\d} _{s_1, s_2}} can be related to \m {\d_s} by \cite [Can05]
 \DispNum {d:2:ds:s2} {
@@
 }
-And we need another crude bound to relate \m {\d_{2S}} to \m {\d_{S}}.
-By triangle inequality, by power-mean inequality,
+And it remains to relate \m {\d_{2S}} to \m {\d_{S}}.
+By triangle inequality, by Jensen inequality,
 \DispNum {Q:x:Qx:x2} {
@@
 
-\startsubsection [title={Main Result}]
+\startsubsection [title={Proposed bound}]
 
-We are going to combine previous propositions and show the main result.
+Finally, we shall show the proposed bound by combining previous propositions.
 For simplicity, set \m {S = Ls^2}, thus
@@
 Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
-Then the bound
+Then it holds that
 %
@@
 %
-holds for probability \m {p}, with
+for probability \m {p}, with
 %
@@
 %
-For convenience we set
-\DispNum {c:c:Ll:H3} {
-\NC \T {\chi} :=\NC \R {L} \R {\log N_H}^3 \NR
-}
-
-To prove this, we simplify the expression for \m {\VNm {\V {d} _{\SB{\MS {AB}}}} _2} in \Rf {d:2:11:C1} and the one for \m {\VNm {\V {d} _{\SB{\MS {C}}}} _1} in \Rf {d:1:dA:C1}.
-In the below, we take the freedom to substitute rough numbers.
-
+To show this, simplify the expression of \m {\VNm {\V {d} _{\SB{\MS {AB}}}} _2} in \Rf {d:2:11:C1} and \m {\VNm {\V {d} _{\SB{\MS {C}}}} _1} in \Rf {d:1:dA:C1}, and substitute rough numbers.
 By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P:d:4N:Nh},
@@
 }
-We are now in a position to bound \m {\VNm {d} _2}, just by using \Rf {d:2:dA:C1} again, and plugging in \Rf {d:2:16:H3} and \Rf {d:C1:16:H2} above.
-This gives
+We are now in a position to bound \m {\VNm {d} _2}, again by \Rf {d:2:dA:C1}, and plugging in \Rf {d:2:16:H3} and \Rf {d:C1:16:H2}, giving
 \DispNum {d:2:42:NH} {
@@
 }
+Therefore, we set
+\DispNum {c':c':8L:H3} {
+\NC \chi
+= \NC 8 \R {L} \R {\log N_H}^3 \NR
+}
+so that
+\DispNum {d:d:c'-:c'-} {
+\NC \VNm {\V {d}} _2
+\leq \NC \chi \NR
+}
 
-Furthermore, we discuss the four events of failure, as follows.
+We further investigate the four events of failure, as follows.
 Consider failure probabilities \m {q _{\Rm {iso}, B}}, \m {q _{\Rm {iso}, R}}, \m {q _{\Rm {no}}}, \m {q _{\Rm {sp}}}, respectively for restricted isometry, noise, sparsity.

### 2020-11-08 treatise/4_simulation.tex
Incorporate rescaled plots

@@
 %
-The injectivity is obvious, and we may define \m {\MS {R} ^{-1}} so that
+The injection is obvious, and we may define \m {\MS {R} ^{-1}} so that
 %
@@
 Then, we extract largest components of the estimated vector, and apply DS again.
-Futhermore, we extract largest components of the second estimated vector, and apply LS.
+Furthermore, we extract largest components of the second estimated vector, and apply LS.
 The final vector's indices has to be scrambled back according to the original index.
@@
 the noise is \m {–40} dB W.
-The noise-to-signal ratio would be
+If so, the noise-to-signal ratio is
 \DispNum {1:8:02:24} {
@@
 In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
-Plots 1 to 5 have \m {N_H = 3 N_Y}, and the plots 6 to 10 has \m {N_H = 2 N_Y}.
+Figures 3 to 6 have \m {N_H = 3 N_Y}, and figures 7 to 10 has \m {N_H = 2 N_Y}.
 
-Assorted, \m {N_H = 3 N_Y, N_H = 12}, error:
 \blank [big]
 \externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 12}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 16}, error:
 \blank [big]
 \externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 16}, error.}
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 20}, error:
 \blank [big]
 \externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 20}, error.}
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 24}, error.}
 %
-Assorted, \m {N_H = 2 N_Y, N_H = 12}, error:
 \blank [big]
 \externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 2 N_Y, N_H = 12}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 2 N_Y, N_H = 16}, error:
 \blank [big]
 \externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 2 N_Y, N_H = 16}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 2 N_Y, N_H = 20}, error:
 \blank [big]
 \externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 2 N_Y, N_H = 20}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 2 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 2 N_Y, N_H = 24}, error.}
+\blank [big]
 
@@
 \externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 16}, time.}
+\blank [big]
+
+We give one additional plot for extreme low signal level, in order to observe the trend of curves.
+\blank [big]
+\externalfigure [assorted-medium-low-signal-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 16}, low signal level, error.}
+\blank [big]
 
@@
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 12}, error:
 \blank [big]
 \externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 12}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 16}, error:
 \blank [big]
 \externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 16}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 20}, error:
 \blank [big]
 \externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 20}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 24}, error.}
+\blank [big]
 %
@@
 \externalfigure [ddss-medium-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 16}, time.}
+\blank [big]
 
@@
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 12}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 16}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 20}, error.}
+\blank [big]
 %
-Assorted, \m {N_H = 3 N_Y, N_H = 24}, error:
 \blank [big]
 \externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 24}, error.}
+\blank [big]
 %
@@
 \externalfigure [oommpp-medium-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 16}, time.}
+\blank [big]
 
@@
 
-In the assorted plots, DS steadily outperforms other methods, and LS is worse than DS, and Lasso still worse, and OMP still worse.
+In the assorted plots, DS steadily outperforms other methods.
+From lowest to highest error, it usually goes like this: DS, LS, Lasso, OMP.
+Though the result is encouraging for our purpose, we wonder why OMP is so bad.
+If OMP is even worse than LS, why was it adopted at all, in (say) Lee, Gil, and Lee \cite [LGL16]?
+But our configuration may not be comparable to theirs, due to different design of beamformers, so it remains to see how do OMP and DS compare under their settings.
+
 However, it is not clear how higher \m {\s} (dimensionless noise level) corresponds to lower \m {\T {\chi}} (simulated error).
@@
 Nevertheless, it seems \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is reasonable.
-Sometimes the iteration stablizes much earlier than is constrained by maximum iteration number.
+Sometimes the iteration stabilizes much earlier than is constrained by maximum iteration number.
 
@@
 
+To give some idea of the case that DS works or fails, figures 23 and 24 illustrate either cases.
+In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.
+When DS fails, the soft thresholding did not rule out smaller entries, thus a second application of DS on the wrong index set failed too.
+When DS succeeded, the soft thresholding gave a reasonable guess of the nonzero components, thus a second application of DS on this index set refined the estimated values.
+
 \blank [big]
 \externalfigure [scatter-ddss-failure.png] [wfactor=300]
-
-To give some idea of the case that DS works or fails, the figure above illustrates a case where DS failed.
-The true values of \m {\M {H}} entries are ordered with respect to their absolute value, and corresponding estimated values in the first and second stage are plotted against the true values.
-We see that the soft thresholding did not rule out smaller entries, so a second application of DS on the wrong index set fails too.
+\FigureCaption {A scatter plot of position versus magnitude for a case in which DS failed.}
+\blank [big]
 
@@
 \externalfigure [scatter-ddss-success.png] [wfactor=300]
-
-The figure above illustrates a case where DS succeeded.
-We see that the soft thresholding did rule out smaller entries, and gives a reasonable guess of the nonzero components, so a second application of DS on this smaller index set refines the estimated values.
+\FigureCaption {A scatter plot of position versus magnitude for a case in which DS succeeded.}
+\blank [big]
 
@@
 The library we called in the simulation is ECOS, where Newton method is used.
-Of course, we are not certain there is no method faster than Newton method, and implmentation details of CVXPY may change the conclusion too.
+Of course, we are not certain there is no method faster than Newton method, and implementation details of CVXPY may change the conclusion too.
 
@@
 Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
-Then Boyd and Vandenberghe \cite [BoV04] (p.505, Eqn.\ 9.56) gave a bound of the number of steps.
+Then Boyd and Vandenberghe \cite [BoV04] (p.505, Eqn.9.56) gave a bound of the number of steps.
 If we just take that as the complexity bound for DS, it becomes
@@
 Here \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error, and \m {C_{\Rm {step}}} is the complexity of Newton step.
-According to their analysis (eq.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
+According to their analysis (Eqn.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
 Also, \m {C_0} usually assumes the value of about several hundred.
@@
 
-On the other hand, Tropp and Gilbert \cite [TrG07a] discussed the complexity of OMP, and the proof of technical lemmata in it can be found in the companion paper \cite [TrG07b].
+On the other hand, Tropp and Gilbert \cite [TrG07a] discussed the complexity of OMP in the companion paper \cite [TrG07b].
 They gave
@@
 Use \m {t_{\Rm {OMP}} \SB {N_H}}, \m {t_{\Rm {Lasso}} \SB {N_H}}, \m {t_{\Rm {DS}} \SB {N_H}} to denote their respective time taken.
-We reproduce the arithmetic average (including different \m {\s}) of simlated values below, in seconds.
+We reproduce the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
 \DispNum {t:2:95:55} {
@@
 Simulation indeed shows that \m {t_{\Rm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
-It is not suprising, regarding the fact that the convex program has to find the Newton step by calculating (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
+It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
 The matrix inversion is probably the bottleneck of complexity.
@@
 In general, \m {t_{\Rm {DS}} \gg t_{\Rm {Lasso}} \gg t_{\Rm {OMP}}}.
-It is now wonder that, given that OMP is a greedy alrogithm, the time OMP takes is negligibly small.
+It is now wonder that, given that OMP is a greedy algorithm, the time OMP takes is negligibly small.
 But it is also notable that, while Lasso has form similar to DS, it takes much lower time.

### 2020-11-08 treatise/acknowledgement.tex
Incorporate rescaled plots

@@
 For various reasons, I took very long time writing this treatise.
-In the start, I came across the field of compressive sensing in 2018 when I was the TA of the course of Convex Optimization, and also when I was an intern in MediaTek.
+In the beginning, I came across the field of compressive sensing in 2018 when I was the TA of the course of Convex Optimization, and also when I was an intern in MediaTek.
 I told Prof.\ Su of the proposal, which by then was hardly more than a vague stream of conciousness.
-I thank him for always being generous to let students find their own topic of interest, and for having encouraged me to continue writing what would become of the present treatise, even not without procrastination and interruption.
+I thank him for always letting students find their own topic of interest, and for having encouraged me to continue writing what would become of this treatise, even not without procrastination and interruption.
+In addition to the stipend he kindly supplies, the warm faux-wood floor, comfortable sofas, and ergonomic chairs in the lab also helped.
 
-I also want to thank Chu-Tong Liu, The PhD student of Prof.\ Su's, and also an aquaintence of mine since the freshman year, in that he gave me various suggestions when I was stuck and was tolerant when I did not, or even fail at all, to deliver a proper presentation.
+The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing a work does teach some resilience to a previously weak mind.
+The three and half years are punctuated by Bachi martial art practice session, teaching assistant's preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I too hold dearly.
 
-Furthermore, I thank my parents, who in recent years was supportive of whatever goal I set up to do (or at least claim to work on), if slightly too credulous regarding my ability.
-It was a tremendous luck that I did not have to mind the financial matters: something I ought to cherish, but did so only in later years.
+I also thank Chu-Tong Liu, The PhD student of Prof.\ Su's, who I acquainted since in the freshman year, in that he provided me various suggestions when I was stuck and was lenient when I did not, or even fail at all, to deliver a proper presentation.
+And I enjoy the meals, trips, and board games with the fellow lab students, whose discussion, concern, jokes, and sarcasms are particularly enlightening when one is undergoing a writer's block.
+
+After all, I thank my parents, who in recent years was supportive of whatever goal I set up to do (or at least claim to work on), if slightly too credulous regarding my ability.
+It was a tremendous luck that I did not have to mind the financial matters for now, which is something I ought to treasure, but did so only in later years.
 I was happy to have been free to keep a sense of curiosity of the intricacy of the universe.

### 2020-11-08 copy-code/classes.py

@@ -41,7 +41,6 @@ class Channel:
         gg = kk.conj ().T @ s.hh @ kk
         g = fct.vectorize (gg)
         z = fct.vectorize (zz)
-        #s.y = s.pp @ g
         s.y = s.pp @ g + (s.s_g / np.sqrt(2)) * z
 
 
@@ -57,33 +56,23 @@ class Estimation:
         s.s_g = s_g
         s.g_r_h = np.zeros (2 * (cst.NN_H (s.ver)))
         s.hh_h = np.zeros ((cst.NN_HH (s.ver), cst.NN_HH (s.ver)), dtype = complex)
-        #s.d = 0
         s.rr = 0
 
     def zero (s):
         s.g_r_h = np.zeros (2 * (cst.NN_H (s.ver)))
         s.hh_h = np.zeros ((cst.NN_HH (s.ver), cst.NN_HH (s.ver)), dtype = complex)
-        #s.d = 0
         s.rr = 0
 
     def set_g_r_h (s, g_r_h):
         s.g_r_h = g_r_h
 
     def convert (s):
-        #nor = np.linalg.norm (s.g_r_h, ord = 1)
-        #if (nor > cst.D_MAX (s.ver) * cst.NN_H (s.ver)):
-        #    s.zero ()
         g_h = fct.inv_find_rep_vec (s.g_r_h)
         gg_h = fct.inv_vectorize (g_h, cst.NN_HH (s.ver), cst.NN_HH (s.ver))
         s.hh_h = (fct.get_kk (s.ver) @ gg_h @ fct.get_kk (s.ver).conj().T)
-        #s.d = np.linalg.norm (s.hh_h - s.hh, ord = 'fro')
 
         nor_hh = np.linalg.norm (s.hh, ord = 2)
         nor_ee = np.linalg.norm (s.hh - s.hh_h, ord = 2)
-        hh_tot = (np.sqrt (cst.NN_HH (s.ver))
-            * (s.s_g + 2 * nor_ee * nor_hh / (cst.NN_HH (s.ver) ** (3/2))) ** (-1)
-            * s.hh @ s.hh.conj().T)
-        #s.rr = np.log2 (np.abs (np.linalg.det (np.eye (cst.NN_HH (s.ver)) + hh_tot)))
         s.rr = nor_ee / nor_hh
         
         if (s.rr > cst.MAX_RR (s.ver)):
@@ -93,20 +82,13 @@ class Estimation:
             s.g_r_h = pp_r_inv @ y_r
[…]

### 2020-11-08 copy-code/functions.py

@@ -11,9 +11,12 @@ import cvxpy as cp
 
 def execute (ver):
     arr_s_g = (cst.S_G_INIT (ver)
-            * cst.VALUE_SPACING_S_G (ver) ** (np.array (range (cst.NUM_S_G (ver)))))
-    lst_h_g = list (cst.VALUE_SPACING_H_G (ver) ** (np.array (range (cst.NUM_H_G (ver)))))
-    lst_g_g = list (cst.VALUE_SPACING_G_G (ver) ** (np.array (range (cst.NUM_G_G (ver)))))
+            * cst.VALUE_SPACING_S_G (ver)
+            ** (np.array (range (cst.NUM_S_G (ver)))))
+    lst_h_g = list (cst.VALUE_SPACING_H_G (ver)
+            ** (np.array (range (cst.NUM_H_G (ver)))))
+    lst_g_g = list (cst.VALUE_SPACING_G_G (ver)
+            ** (np.array (range (cst.NUM_G_G (ver)))))
 
     lst_legend = []
     lst_num_rep_meth = []
@@ -39,7 +42,8 @@ def execute (ver):
 
         # Orthogonal Matching Pursuit: limited l-2 norm
         for h_g in lst_h_g:
-            lst_legend.append ("OMP, $l_2$-norm, $\eta$ = " + '%.2f' % h_g + "$\sigma$")
+            lst_legend.append ("OMP, $l_2$-norm, $\eta$ = "
+                    + '%.2f' % h_g + "$\sigma$")
             lst_num_rep_meth.append (cst.NUM_REP_OOMMPP (ver))
             lst_meth.append (
                 lambda x, y, h_g = h_g:
@@ -47,7 +51,8 @@ def execute (ver):
 
         # Orthogonal Matching Pursuit: limited l-infinity norm
         for h_g in lst_h_g:
-            lst_legend.append ("OMP, $l_\infty$-norm, $\eta$ = " + '%.2f' % h_g + "$\sigma$")
+            lst_legend.append ("OMP, $l_\infty$-norm, $\eta$ = "
+                    + '%.2f' % h_g + "$\sigma$")
             lst_num_rep_meth.append (cst.NUM_REP_OOMMPP (ver))
             lst_meth.append (
                 lambda x, y, h_g = h_g:
@@ -107,7 +112,8 @@ def execute (ver):
                 time_each_stop = time.time ()
 
                 lst_spec_eff [i_meth] += est.rr / num_rep_meth
[…]

### 2020-11-09 presentation/1_setting.tex
Rev contribution

--- 2020-11-08 presentation/2_setting.tex
@@
+\blank [big, force]
+
+\Title {\TitleText}
+\blank [big]
+
+\Subtitle {\AuthorText}
+\blank [big]
+
+\Subsubtitle {\InstitutionText}
+\Subsubtitle {November 2020}
+
+\page [yes]
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
@@
 
-\I Can we measure less than \m {N_H} times, but recover successfully for most cases?
+\I Can we measure less than \m {N_H^2} times, but recover successfully for most cases?
 
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Literature on Compressive Channel Sensing}
+\Frame {Literature on Compressive Sensing}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Question}
+\Frame {Questions}
 {
-\I Candès and Tao (2007) proposed a performance bound for DS, then can DS do better than OMP?
+\I How does greedy algorithms (like OMP) trade precision for complexity, and that the opposite is true of convex programs (like DS)?
 
-\I Does convex programming (DS) trade accuracy with greedy algorithms (OMP)?
+\I We consider the hybrid system as in Lee, Lee, and Yong (2016), where they proposed an optimal joint design by a nonconvex program, but made considerable approximation.
+Is the simplified solution still optimal?
 
-\I May we verify a revised performance bound in the concrete case?
+\I Candès and Tao (2007) derived a performance bound for DS.
+Does it prove DS to be better?
+Does it apply to our case?
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Our Contribution}
+\Frame {Contribution}
 {
-\I Consider MIMO mm-wave channel, with hybrid beamforming
+\I We demonstrate that the beamformer may serve as the sensing matrix, so DS can be applied.
 
-\I Use a modified DS (convex programming), instead of OMP (greedy algorithm)
+\I We give a bound (holding for high probability) on expected error norm
 
-\I Illustrate by experiments that DS has better performance
-
-\I Give an analysis of error norm and successful probability in terms of system parameters
+\I Numerical results illustrate that in our configuration DS is superior to OMP among other methods, but is achieved at the cost of higher complexity.
 }

### 2020-11-09 presentation/2_analysis.tex
Rev contribution

--- 2020-10-21 presentation/3_proof.tex
@@
 
-\I Should account for the fact that \m {\V {g}} is not strictly sparse
+\I Should consider that \m {\V {g}} is not strictly sparse
 
-\I Should justify that all four beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, have RIP for high probability, thus \m {\m {P}} does too.
+\I Should justify that if beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, have RIP for high probability, than \m {\m {P}} does too.
 
-\I Should investigate the Big \m {\MC {O}} of error norm by bounding failure events mentioned above.
+\I Should bound the big \m {\MC {O}} of error norm corresponding to these failure events.
 }
@@
 {
-\I In conclusion, it holds for probability \m {p} that
+\I We argue in the treatise that it holds for probability \m {p} that
 \Disp {
@@
 %
-\I For design values
+\I For ideal values
 \Disp {

### 2020-11-09 presentation/3_simulation.tex
Rev contribution

--- 2020-11-08 presentation/4_simulation.tex
@@
 {
-\I We call the following quantity \m {\chi} efficiency, which is suggestive of the MIMO channel capacity.
+\I Let the \m {\T {\chi}}, the relative 2-norm error, be the performance metric.
 
-\I Denote \m {\M {E} = \Hat {\M {H}} - \M {H}}.
 \Disp {
-\NC \chi
-= \log \det \SB {\M {I} + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
+\NC \T {\chi}
+=\NC \RB {
+   \F {\log_2 {\VNm {\V {h} -\Hat {\V {h}}} _2}}
+   {\log_2 {\VNm {\V {h}}_2}}
+} _{\Ss {avg}}, \NR
 }
 
-\I The theoretical efficiency \m {\chi _{\Rm {th}}} is defined by plugging in \m {\V {d}}.
+\I Also define \m {\chi} by plugging in \m {\V {d}} into \m {\T {\chi}}.
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=2N_Y}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=2N_Y}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=2N_Y}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=2N_Y}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=3N_Y}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=3N_Y}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=3N_Y}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=3N_Y}}
 {
@@
 \externalfigure [assorted-wide-very-big-error.png] [width=11cm]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {\It {ibid.}, low signal, assorted, \m {N_H=16=3N_Y}}
+{
+\blank [big]
+\externalfigure [assorted-medium-low-signal-error.png] [width=11cm]
 }
@@
 {
-\I DS wins other method within the range drawn.
+\I DS wins other method in the range drawn.
 
-\I Simulated \m {\chi} does not show trend that estimated \m {\T {\chi}} predicts.
+\I \m {\chi} does not show trend that \m {\T {\chi}} predicts.
 
-\I The weaker constraint on sparsity might have compromised DS's performance.
+\I The relaxed sparsity might compromise DS performance
 
@@
 \blank [big]
-\externalfigure [scatter-ddss-success.png] [wfactor=150]
+\externalfigure [scatter-ddss-success.png] [wfactor=180]
 
@@
 \blank [big]
-\externalfigure [scatter-ddss-failure.png] [wfactor=150]
+\externalfigure [scatter-ddss-failure.png] [wfactor=180]
 
@@
 {
-\I The number of Newton steps is about \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
-Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, or \m {\MC {O} \SB {N_H^2}}.
+\I Let \m {C} denote big-O estimation of complexity, then we argue in the treatise
+\Disp {
+\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_Y} \NR
+\NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR
+\NC C_{\Rm {DS}} =\NC \mathcal {O} \SB {N_{H}^6} \NR
+}
 
-\I Every Newton step requires a matrix inversion of dimension \m {2 N_H^2}, with complexity \m {\MC {O} \SB {N_H^4}}, giving overall complexity \m {\MC {O} \SB {N_H^6}}.
-
-\I Complexity of Lasso can be similarly argued to be \m {\MC {O} \SB {N_H^6}}.
-
-\I Clearly, OMP has complexity \m {\MC {O} \SB {N_H^2}}, much smaller than DS.
+\I Fitting runtime statistics one has
+\Disp {
+\NC \T {t}_{\Rm {OMP}} \NC \eqsim \mathcal {O} \SB {N_H^{3.6}} \NR
+\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \mathcal {O} \SB {N_H^{4.8}} \NR
+\NC \T {t}_{\Rm {DS}} \NC \eqsim \mathcal {O} \SB {N_H^{8.3}} \NR
 }
+}

### 2020-11-09 presentation/4_conclusion.tex
Rev contribution

--- 2020-11-08 presentation/5_conclusion.tex
@@
 {
-\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.
+\I We estimate MIMO mm-Wave channel \m {\M {H}} by using modifed DS.
 
-\I We justify DS in present scenario with almost-sparse \m {\V {g}}, and show the RIP of effective beamformer \m {\M {P}}.
+\I We justify DS under relaxed sparsity of \m {\V {g}}, and demonstrate the RIP of effective beamformer \m {\M {P}}.
 
-\I We propose a error norm analysis of DS in terms of parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigate the asymptotic successful probability.
+\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_Y}, and \m{L}, and approimate the asymptotic failure probability.
 
-\I DS may be converted to be a linear program to reduce complexity.
+\I By simulation we see that DS can be cast into be a linear program to reduce complexity, and appear to outperform other methods.
 
-\I While DS does appear superior, it has complexity much greater than OMP.
+\I DS trades off low time and space complexity high precision, and for OMP the opposite is true.
 }

### 2020-11-09 treatise/1_introduction.tex
Rev contribution

@@
 
-From above we note that work on channel estimation seems to favored OMP for its low complexity.
-One notable difficulty in channel estimation is that, in the uniform linear array setting, the quantized angle of arrival and departure, which the sensing matrix is based on, does not necessarily match the true ones \cite [GYG18].
-Also, as the nature of OMP is greedy, and it is not clear whether it achieves optimality, and the assumption that the channel matrix is sparse warrant justification too.
+We saw that the literature on channel estimation seems to favored OMP for its low complexity.
+Then one naturally wonders how greedy algorithms, like OMP, compare to convex programs, like DS.
+Can it be that greedy algorithms trade precision for complexity, and that the opposite is true of convex programs?
 
-In this treatise, we suggest DS as an alternative.
-Chapter 2 shows, the effective beamformer may serve as the sensing matrix with RIP.
-Assuming uniform linear array, the sparsity may be exploited, and a convex program analogous to DS can be used for estimation, which ensures several desirable properties.
-In chapter 3, along the lines of \cite [CaT07], we give a bound on expected square error, expressed in terms of the sparsity and the number of paths.
-We claim that the bound holds for overwhelming probability.
-In chapter 4, we remark that DS can be written as an linear program, for which efficient algorithms are known.
-We present numerical results, which show that DS is often superior to OMP among other methods, which is achieved at the cost of higher complexity.
+We consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite [LGL16], and aim to compare their result.
+Their work proposed an optimal beamformer, jointly designed on both ends via a nonconvex optimization problem, and due to its difficulty they have made considerable approximation.
+Is the simplified beamformer still optimal for OMP?
+Or will there be mismatch between the angles of sensing matrix and their true values, compromising the algorithm's accuracy?
+
+In this treatise, we illustrate, by the case of uniformly random angles, that DS may outperform OMP among other methods, and the nature of convex program also guarantees its performance.
+In chapter 2 we shall see that the effective beamformer may serve as the sensing matrix having RIP for high probability.
+The sparsity can be exploited this way, and DS may readily be applied.
+In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a bound (which holds for high probability) on expected error norm, expressed in terms of the suggested sparsity and the number of paths.
+In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms are known.
+Numerical results show that in our configuration DS is superior to OMP among other methods, but is achieved at the cost of higher complexity.
 

### 2020-11-09 treatise/4_simulation.tex
Rev contribution

@@
 It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H},
-and it is not clear what is most reasonable choice of \m {N_1, N_1, N_2}.
+and we do not know what most reasonable choice of \m {N_1, N_1, N_2} is.
 
@@
 Though the result is encouraging for our purpose, we wonder why OMP is so bad.
-If OMP is even worse than LS, why was it adopted at all, in (say) Lee, Gil, and Lee \cite [LGL16]?
-But our configuration may not be comparable to theirs, due to different design of beamformers, so it remains to see how do OMP and DS compare under their settings.
+Did we make mistakes?
+We do not think so.
+A crucial reason might be that in Lee, Gil, and Lee \cite [LGL16], the angles of departure and arrival is distributed within a cluster of standard deviation 15 degrees, and in ours, they are uniform on the unit circle.
+One is then tempted to say, we suggested a low complexity beamformer and high complexity estimation method, while they suggested a high complexity beamformer and low complexity estimation method, and the low complexity solution does not seem effective in our settings.
+It remains to see, however, how OMP and DS compare, if done exactly under their settings.
 
@@
 
-It is not clear, unfortunately, why \m {\T {\chi}} does not agree \m {\chi} (the error bound), and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
+We are not sure either, unfortunately, why \m {\T {\chi}} does not agree \m {\chi} (the error bound), and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
 As shown above, the \m {\chi} is very constant around 1, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.

### 2020-11-09 treatise/5_conclusion.tex
Rev contribution

@@
 Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation \cite [CaT07], while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
-OMP, on the other hand, requires only an entrywise i.i.d.\ Normal sensing matrix \cite [TrG07a], but much analysis remains to be done.
-OMP trades off precision for a lower time and space complexity, and for DS the other way around, and this eloquently illustrates that different technique suits different problems and constraints, as is true in every discipline of engineering.
+OMP, on the other hand, may require only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], but much of its property remains open.
+On the whole, DS trades off low time and space complexity high precision, and for OMP the opposite is true.
 

### 2020-11-10 presentation/1_setting.tex
Delete obsolete formulation on SOCP

@@
 
-\I Problem (a): How to recover the channel with fewer measurements?
+\I Problem (a): How to reconstruct the channel with fewer measurements?
 
@@
 {
-\I Given channel \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array
+\I Given MIMO channel representation \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array, having \m {L} paths.
 
-\I Complex standard normal noise \m {\m {Z} \in \NC \MB {C} ^{N_H \D N_H}}
+\I Complex standard normal noise \m {\M {Z} \in \NC \MB {C} ^{N_H \D N_H}}
 
-\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_Y}}
+\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_B}}
 \I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}
@@
 \I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}
-\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_Y \D N_R}}
+\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_B \D N_R}}
 
-\I Magnitude constraint \m {\Nm {\M {F}_R \SB {n_H, n_R}} = 1}, \m {\Nm {\M {W}_R \SB {n_R, n_H}} = 1} 
+\I Magnitude constraint \m {{\Nm {\M {F}_R}_{\SB {n_H, n_R}}} = 1}, \m {{\Nm {\M {W}_R}_{\SB {n_R, n_H}}} = 1} 
 }
@@
 
-\I What kind of matrices faciliates our goal?
+\I What kind of matrices facilitates our goal?
 }
@@
 
-\I Can we find a basis on which \m {\V {g}} is sparse?
+\I Can we find a basis on which \m {\V {g}} is likely to be sparse?
 }
@@
 
-\I Alkhateeb, Ayach, Leus, Heath (2014): mm-wave, adaptive training algorithm for given codebook
+\I Alkhateeb, Ayach, Leus, Heath (2014): mm-wave, adaptive training algorithm for given sensing matrix
 
@@
 {
-\I How does greedy algorithms (like OMP) trade precision for complexity, and that the opposite is true of convex programs (like DS)?
+\I Does greedy algorithms (like OMP) trade precision for complexity, and is the opposite true of convex programs (like DS)?
 
@@
 
-\I We give a bound (holding for high probability) on expected error norm
+\I We give a bound (holding for high probability) on expected error norm.
 
-\I Numerical results illustrate that in our configuration DS is superior to OMP among other methods, but is achieved at the cost of higher complexity.
+\I Numerical results illustrate that in our configuration DS is superior to OMP among other methods, at the cost of higher complexity.
 }
@@
 
-\I We argue that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have RIP, thus \m {\M {P}} has too.
+\I We argue that \m {\M {F} _R ^\Tr}, \m {\M {F} _B ^\Tr}, \m {\M {W} _R}, and \m {\M {W} _B} all have restricted isometry, thus \m {\M {P}} has too.
 }
@@
 
-\I Input \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.
+\I Input \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.
 

### 2020-11-10 presentation/2_analysis.tex
Delete obsolete formulation on SOCP

@@
 {
-\I What's the difference of true value \m {\V {h}} and estimated value \m {\Hat {\V {h}}}?
+\I Can we bound \m {\VNm {\V {h} -\Hat {\V {h}}} _2}?
 
-\I Should consider that \m {\V {g}} is not strictly sparse
+\I Does it matter that \m {\V {g}} is not strictly sparse?
 
-\I Should justify that if beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, have RIP for high probability, than \m {\m {P}} does too.
+\I If \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, all have restricted isometry, does \m {\m {P}} have too?
 
-\I Should bound the big \m {\MC {O}} of error norm corresponding to these failure events.
+\I Big \m {\MC {O}} probability of failure events?
 }
@@
 %
-\leq \NC 8 \R {L} \RB {\log N_H} ^{3/2} \NR
+\eqsim \NC \MC {O} \SB {\R {L} \RB {\log N_H} ^{3/2}} \NR
 }
@@
 \Disp {
-\NC N_Y \gtrsim \NC 4 \log N_H, \Q
+\NC N_B \gtrsim \NC 4 \log N_H, \Q
 N_R \gtrsim 16 L \RB {\log N_H}^2 \NR
@@
 \NC 1 - p
-\lesssim \NC 2 N_H ^{-1/3} \NR
+\eqsim \NC \MC {O} \SB {\Ss {e} ^{-N_B /12}}
+ \NR
 }

### 2020-11-10 presentation/3_simulation.tex
Delete obsolete formulation on SOCP

@@
 \I DS is equivalent to a linear program, which allows more efficient convex programming methods to be used.
-
-\I Calculate
+(Variables with tilde denote the real representation of complex matrices and vectors.)
 \Disp {
-\NC \Hat {\V {g}}, \Hat {\V {f}}
+\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
 \LA \NC \startcases
-   \NC \Min {\V {g}', \V {f}'}  \MC \IP {\V {1}, \V {f}'} \NR
-   \NC \Rm {subject} \; \Rm {to} \MC \V {g}' \leq \V {f}' \NR
-   \NC \MC - \V {g}' \leq \V {f}' \NR
-   \NC \MC \M {P}^\Adj \M {P} \V {g}' \leq \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
-   \NC \MC - \M {P}^\Adj \M {P} \V {g}' \leq - \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
+   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
+   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}',
+   \quad \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
+   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
+   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
 \stopcases \NR
 }
-\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
+\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {\T {\V {g}}}} \M {K}^\Adj}
 }
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=2N_Y}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=2N_B}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=2N_Y}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=2N_B}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=3N_Y}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=3N_B}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=3N_Y}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=3N_B}}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\It {ibid.}, low signal, assorted, \m {N_H=16=3N_Y}}
+\Frame {\It {ibid.}, low signal, \m {N_H=16=3N_B}}
 {
@@
 
-\I \m {\chi} does not show trend that \m {\T {\chi}} predicts.
+\I \m {\chi} does not show the trend that \m {\T {\chi}} predicts.
 
-\I The relaxed sparsity might compromise DS performance
+\I The relaxed condition on sparsity may have compromised performance of DS
 
@@
 \Disp {
-\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_Y} \NR
+\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_B} \NR
 \NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR
@@
 \Disp {
-\NC \T {t}_{\Rm {OMP}} \NC \eqsim \mathcal {O} \SB {N_H^{3.6}} \NR
-\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \mathcal {O} \SB {N_H^{4.8}} \NR
-\NC \T {t}_{\Rm {DS}} \NC \eqsim \mathcal {O} \SB {N_H^{8.3}} \NR
+\NC \T {C}_{\Rm {OMP}} \NC \eqsim \mathcal {O} \SB {N_H^{3.6}} \NR
+\NC \T {C}_{\Rm {Lasso}} \NC \eqsim \mathcal {O} \SB {N_H^{4.8}} \NR
+\NC \T {C}_{\Rm {DS}} \NC \eqsim \mathcal {O} \SB {N_H^{8.3}} \NR
 }

### 2020-11-10 presentation/4_conclusion.tex
Delete obsolete formulation on SOCP

--- 2020-11-08 presentation/5_conclusion.tex
@@
 {
-\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.
+\I We estimate MIMO mm-Wave channel \m {\M {H}} by using modified DS.
 
-\I We justify DS in present scenario with almost-sparse \m {\V {g}}, and show the RIP of effective beamformer \m {\M {P}}.
+\I We justify DS under relaxed condition on sparsity of \m {\V {g}}, and demonstrate the RIP of effective beamformer \m {\M {P}}.
 
-\I We propose a error norm analysis of DS in terms of parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigate the asymptotic successful probability.
+\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_B}, and \m{L}, and approximate the asymptotic failure probability.
 
-\I DS may be converted to be a linear program to reduce complexity.
+\I By simulation we see that DS appears to be superior to other methods.
 
-\I While DS does appear superior, it has complexity much greater than OMP.
+\I DS trades off low time and space complexity for high precision.
+For OMP, the opposite is true.
 }

### 2020-11-10 treatise/1_introduction.tex
Delete obsolete formulation on SOCP

@@
 
-Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel, which is a big square matrix of dimension \m {N_H}, the number of antennae.
+Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel representation.
+Our task amounts to invert a linear system whose dimension is the number of antennae.
 Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and that's when a recent development called compressive sensing may help.
@@
 \NC \V {y}
-=\NC \M {Q} \V {x} + \V {z} \NR
+=\NC \M {Q} \V {x} \NR
 }
@@
 
-Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.
+Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurements, under overwhelming probability.
 
@@
 
-From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, allows techniques from convex optimization to be used.
-In fact, Candès \& Romberg provided an example implementation on their website (Candès \& Romberg \cite [CaR05]).
-In addition, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.
+The formulation as an \m {\ell_1} minimization problem, which is convex.
+From the computational perspective, this allows techniques from convex optimization to be used.
+In fact, Candès and Romberg provided an example implementation on their website \cite [CaR05].
+In addition, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear Program, rendering convex programming technique applicable.
 
 Here the constant \m {\d_s} in Definition [1] is crucial:
-we must make a series of carefully chosen but random measurement.
+we must make a series of carefully chosen but random measurements.
 We can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
@@
 if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
-The accompanying note by the same group \cite [BHR08] showed that \m {X} is RIP for overwhelming probability, justifying their work.
+The accompanying note by the same group \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.
 And \cite [BHR08], which considered a linear time-invariant channel, showed that if the convolution with channel response can be seen as a linear system, whose sensing matrix has RIP of overwhelmingly probability, and DS is readily applied.
@@
 
-At the same time, Tropp and Gilbert \cite [TrG07b] suggested that a greedy algorithm called Orthogonal Matching Pursuit (OMP), which also makes use of an i.i.d.\ random matrix, may also reconstruct the sparse signal sufficiently well in an overwhelmingly probability.
-In so doing, we still consider \Rf {y:y:Qx:xz}, and pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.
+At the same time, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) may reconstruct a sparse signal sufficiently well in an overwhelmingly probability.
+In the situation of \Rf {y:y:Qx:xz}, we would pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.
 
@@
 From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a performance guarantee.
-It is instructive to note that the matrix consisting of a collection of columns that likely spans \m {\V {x}} plays the role of the sensing matrix in the previous section.
+
+OMP also makes use of an entrywise i.i.d.\ random matrix.
+It is instructive to note that the matrix columns is likely to span \m {\V {x}}, playing a role similar to the sensing matrix in the case of DS.
 
@@
 
-In this treatise, we illustrate, by the case of uniformly random angles, that DS may outperform OMP among other methods, and the nature of convex program also guarantees its performance.
+In this treatise, we illustrate that DS may outperform OMP and other methods.
 In chapter 2 we shall see that the effective beamformer may serve as the sensing matrix having RIP for high probability.
@@
 In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms are known.
-Numerical results show that in our configuration DS is superior to OMP among other methods, but is achieved at the cost of higher complexity.
+Numerical results show that in our configuration, where we have uniformly random angles of departure and arrival, DS is superior, but is achieved at the cost of higher complexity.
 

### 2020-11-10 treatise/2_problem_setting.tex
Delete obsolete formulation on SOCP

@@
 That is to say, each end consists of both digital and analog precoders and combiners, as follows.
-In the transmitter end, there are (seeing towards receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_Y}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
-Similarly, in the receiver end, there are (seeing towards transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_Y \D  N_R}}.
+In the transmitter end, there are (seeing towards receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_B}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
+Similarly, in the receiver end, there are (seeing towards transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_B \D  N_R}}.
 
@@
 %
-\NC N_R \gg \NC N_Y \NR
+\NC N_R \gg \NC N_B \NR
 }
 
-Since we restrict our discussion to a specific snapshot of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_Y \D N_Y}} with each entry being i.i.d.\ Standard Normal.
+Since we restrict our discussion to a specific snapshot of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_B \D N_B}} with each entry being i.i.d.\ Standard Normal.
 We may introduce the effective channel
@@
 \stopsection
-\startsubsection [title={Vectorization}]
+
+\startsection [title={Vectorization}]
 
@@
 {
-Define \m {\Rm {vec} \SB {\M {A}} \in \MB {K} ^{N_1, N_2}} to be the vectorization of \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}}.
+Define \m {\Rm {vec} \SB {\M {A}} \in \MB {K} ^{N_1 \D N_2}} to be the vectorization of \m {\M {A} \in \MB {K} ^{N_1 \D  N_2}}.
 Formally,
@@
 \DispNum {v:1:Am:N1} {
-\NC \RB {\Rm {vec} \SB {\M {A}}} _{\SB {m_1}}
-=\NC \M {A} _{\SB {m_1\; \Rm {Mod}}\; N_1, \Fl {m_1/N_1 }} \NR
+\NC \RB {\Rm {vec} \SB {\M {A}}} _{\SB {m}}
+=\NC \M {A} _{\SB {m\; \Rm {Mod}}\; N_1, \Fl {m/N_1 }} \NR
 }
@@
 := \NC \Rm {vec} \SB {\M {Y}}
-\in \MB {C} ^{N_Y^2} \NR
+\in \MB {C} ^{N_B^2} \NR
 %
@@
 := \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
-\in \MB {C} ^{N_Y^2} \NR
+\in \MB {C} ^{N_B^2} \NR
 %
@@
 := \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
-\in \MB {C} ^{N_Y^2 \D N_H^2} \NR
+\in \MB {C} ^{N_B^2 \D N_H^2} \NR
 }
@@
 \stopsection
+
 \startsection [title={Angular space}]
@@
 %
-Roman \m {\Ss {e}} and \m {\Ss {i}} denote the natural base and imaginary unit, respectively.
+Sans serif \m {\Ss {e}} and \m {\Ss {i}} denote the natural base and imaginary unit, respectively.
 Here recall that we have
@@
 +\M {W} _B \M {W} _R \M {Z}
-\in \MB {C} ^{N_Y \D N_Y} \NR
+\in \MB {C} ^{N_B \D N_B} \NR
 }
@@
 :=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
-\in \MB {C} ^{N_Y^2 \D N_H^2} \NR
+\in \MB {C} ^{N_B^2 \D N_H^2} \NR
 }
@@
 \item Let \m {\g_{\Rm {DS}} \geq 0} be given.
-\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D N_Y}},
+\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D N_B}},
 \m {\M {F} _R \in \NC \MB {C} ^{N_H \D N_R}},
 \m {\M {W} _R \in \NC \MB {C} ^{N_R \D N_H}},
-\m {\M {W} _B \in \NC \MB {C} ^{N_Y \D N_R}},
-and \m {\M {Y} \in \NC \MB {C} ^{N_Y \D N_Y}}.
-\item Find \m {\M {P} \in \MB {C} ^{N_Y^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
+\m {\M {W} _B \in \NC \MB {C} ^{N_B \D N_R}},
+and \m {\M {Y} \in \NC \MB {C} ^{N_B \D N_B}}.
+\item Find \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
 \item Calculate

### 2020-11-10 treatise/3_2_design_of_beamformers.tex
Rev contribution
Delete obsolete formulation on SOCP

--- 2020-11-08 treatise/3_2_confirming_restricted_isometry.tex
@@
-\startsection [title={Restricted isometry of effective beamformer}]
+\startsection [title={Design of Beamformers}]
 
@@
 Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
-We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_Y}}} follows Rayleigh distribution.
-\m {\RB {\M {W} _B ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analogous manner.
+We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_B}}} follows Rayleigh distribution.
+\m {\RB {\M {W} _B ^\Tr} _{\SB {n_B, n_R}}} is set in an entirely analogous manner.
 In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane.
-\m {\RB {\M {W} _R ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analogous manner.
+\m {\RB {\M {W} _R ^\Tr} _{\SB {n_B, n_R}}} is set in an entirely analogous manner.
 
-It turns out we have results that guarantee that both \m {\M {F} _B ^\Tr} and \m {\M {F} _R ^\Tr} are RIP, and same can be said of \m {\M {W} _B} and \m {\M {W} _R}.
+It turns out we have results that guarantee that both \m {\M {F} _B ^\Tr} and \m {\M {F} _R ^\Tr} have RIP, and same can be said of \m {\M {W} _B} and \m {\M {W} _R}.
 Consider a sparse \m {\V {u}} or unity norm, then we are sure that \m {\M {F} _R ^\Tr \V {u}} has almost unity norm.
@@
 
-However, it is not clear that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, have RIP, nor that, \m {\M {P}}, the result of Kronecker product, is RIP.
+However, it is not clear that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, have RIP, nor that, \m {\M {P}}, the result of Kronecker product, has RIP.
 In fact, the statement seems to be false in general.
@@
 
-Here, we consult Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} collected in \cite [KlM17].
-We need their Thm.\ 4.5; it gives a RIP guarantee w.r.t.\ \m {\d_s}, and probability lower bound, for DFT submatrix.
+Here, we consult Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17].
+We need their Thm.4.5, which guarantees RIP w.r.t.\ \m {\d_s}, and probability lower bound, for DFT submatrix.
 The estimation they give involve is expressed in terms of big- \m {\O} and big- \m {O}, and since our methodology is 
@@
 %
-Then \m {\M {F}_R} (resp.\ \m {\M {W} _R}) has \m {\d_s}-RIP for probability \m {p}, with
+Then \m {\M {F}_R} (respectively \m {\M {W} _R}) has \m {\d_s}-RIP for probability \m {p}, with
 \DispNum {1:p:ex:d's} {

### 2020-11-10 treatise/4_simulation.tex
Delete obsolete formulation on SOCP

@@
 
-In this chapter we shall verify the bound \m {\T {\chi}} by numerical experiments.
-DS is a convex optimization program, and for present purpose, we choose the Python library CVXPY.
+In this chapter we shall compare \Rf {d:2:OL:H3} with numerical experiments.
+For the convex optimization, we choose the Python library CVXPY.
 For the implementation details, see Diamond and Boyd \cite [DiB16]
-
-A direct implementation of Algorithm [7] exhibits extraordinarily large complexity, but Candès and Romberg \cite [CaR05] showed that DS can be simplified as an linear program (LP) (even though they assumed real vectors, and we consider the complex ones), which we reproduce below.
+A direct implementation of Algorithm [7] leads to extraordinarily large complexity, but Candès and Romberg \cite [CaR05] showed that DS can be cast as a linear program, which we illustrate below.
 
@@
 
-For brevity we shall represent complex vector and matrices by real ones, comprising of its real an imaginary parts.
+For brevity we shall represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
 For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
@@
 %
-\DispNum {y:::Ry:Ny} {
+
+\DispNum {y:y:Ry:Ny} {
 \NC \T {\V {y}}
 = \NC \MS {R} \SB {\V {y}}
-\in \MB {R} ^{2 N_Y^2} \NR
+\in \MB {R} ^{2 N_B^2} \NR
 %
@@
 = \NC \MS {R} \SB {\M {P}}
-\in \MB {R} ^{2 N_Y^2 \D 2 N_H^2} \NR
+\in \MB {R} ^{2 N_B^2 \D 2 N_H^2} \NR
 %
@@
 = \NC \MS {R} \SB {\M {P} ^\Adj}
-\in \MB {R} ^{2 N_Y^2 \D 2 N_H^2} \NR
+\in \MB {R} ^{2 N_B^2 \D 2 N_H^2} \NR
 %
@@
 = \NC \MS {R} \SB {\V {z}}
-\in \MB {R} ^{2 N_Y^2} \NR
+\in \MB {R} ^{2 N_B^2} \NR
 }
 %
-such that, by construction,
+so, by construction,
 %
-\DispNum {y:::Pg:gz} {
+\DispNum {y:y:Pg:gz} {
 \NC \V {\T {y}}
@@
 }
-
-Furthermore, introduce the following matrices to identify the components where we want to take \m {\ell_2}-norm, in the manner similar to an indicator function.
 %
-\DispNum {u:h:RN:h1} {
-\NC {\V {u}}_{n_h}
-\in \NC \MB {R} ^{N_H^2} \NR
-\NC \RB {\V {u}_{n_h}} _{\SB {n_h'}}
-= \NC
-\startcases
-1, \Q \MC n_h' =n_h \NR
-0, \Q \NC \Rm {otherwise} \NR
-\stopcases \NR
-\NC \T {\M {U}}_{n_h} \in \NC \MB {R} ^{2 N_H^2 \D 2 N_H^2} \NR
-\NC \RB {\T {\M {U}}_{n_h}} _{\SB {n_h', n_h''}}
-= \NC
-\startcases
-1, \Q \MC n_h' =2n_h,\; n_h'' =2n_h \NR
-1, \Q \MC n_h' =2n_h +1,\; n_h'' =2n_h +1 \NR
-0, \Q \NC \Rm {otherwise} \NR
-\stopcases \NR
-\NC n_h, n_h', n_h'' 
-= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
-}
-%
-And denote \m {\V {1}} to be the all-\m{1} vector for short, and \m {\V {0}} the all-\m{0} vector, whose dimension will be specified from context.
-Now, if we introduce vector \m{\V {m}}
-%
-\DispNum {m:::RN:h1} {
-\NC \V {m} \in \NC \MB {R} ^{N_H^2} \NR
-\NC \V {m} _{\SB{n_h}}
-= \NC \Nm{\V {g} _{\SB {n_h}}} \NR
-\NC n_h, n_h', n_h'' 
-= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
-}
-%
-to denote the entrywise complex modulus of \m{\V {g}}, we see that the convex optimization now takes the form
-%
-\DispNum {g:::mi:h1} {
-\NC \Hat {\T {\V {g}}}
-= \NC \startcases
-\NC \Min {\T {\V {g}}', \V {m}} \Q
-\MC \IP { \V {1}, \V {m} } \NR
-\NC \Rm {subject} \; \Rm {to} \Q
-\MC \VNm { \T {\M {U}}_{n_h} \T {\V {g}}' }_2
-\leq \IP { \V {u}_{n_h}, \V {m} } \NR
-\NC \MC \VNm { \T {\M {U}}_{n_h} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}}' -\T {\V {y}} } }_2
-\leq \g_{\Rm {DS}} \NR
-\stopcases \NR
-\NC n_h 
-= \NC 0, 1, 2, \ldots, N_H^2-1 \NR
-}
+And denote \m {\V {1}} to be the all-\m{1} vector, and \m {\V {0}} the all-\m{0} vector, whose dimension will be inferred from context.
 
@@
 
-We shall see furthermore that the program can be cast into an SOCP.
-To make the point clearer, we rewrite the program just above into an extended block matrix form, by defining auxiliary variables as follows,
-%
-\DispNum {t:t:01:Nh} {
-\NC \V {t}
-= \NC \startTheMatrix
-\NC \V {0} \NR
-\NC \V {1} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-%
-\NC \V {x}'
-= \NC \startTheMatrix
-\NC \T {\V {g}}' \NR
-\NC \V {m} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-}
-%
-with
-%
-\DispNum {A:i:Ui:21} {
-\NC \M {A}_i
-= \NC \startTheMatrix
-\NC \T {\M {U}}_{i}, \NC \M {0} \NR
-\stopTheMatrix
-\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
-%
-\NC \V {b}_i
-= \NC \V {0}
-\in \MB {R} ^{2 N_H^2} \NR
-%
-\NC \V {c}_i
-= \NC \startTheMatrix
-\NC \V {0} \NR
-\NC \V {u}_{i} \NR
-\stopTheMatrix
-\in \MB {R} ^{3 N_H^2} \NR
-%
-\NC d_i
-= \NC 0 \NR
-%
-\NC i 
-= \NC 0, 1, 2, \ldots, N_H^2 -1 \NR
-}
-%
-and
-%
-\DispNum {A:i:Ui:21:"} {
-\NC \M {A}_i
-= \NC \startTheMatrix
-\NC -\T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\M {P}}, \NC \M {0} \NR
-\stopTheMatrix
-\in \MB {R} ^{2 N_H^2 \D 3 N_H^2} \NR
-%
-\NC \V {b}_i
-=\NC \T {\M {U}}_{i - N_H^2} \T {\M {P}}^\Adj \T {\V {y}}
-\in \MB {R} ^{2 N_H^2} \NR
-%
-\NC \V {c}_i
-= \NC \V {0}
-\in \MB {R} ^{3 N_H^2} \NR
-%
-\NC d_i
-= \NC \g_{\Rm {DS}} \NR
-%
-\NC i 
-= \NC N_H^2, N_H^2 +1, N_H^2 +2, \ldots, 2 N_H^2 -1 \NR
-}
+We can now see that DS is equivalent to a linear program.
 
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {C} ^{ N_Y^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_Y^2}}, \m {\g_{\Rm {DS}} > 0}.
-\item Define \m{\V {t}, \V {x}, \M {A}_i, \V {b}_i, \V {c}_i, d_i} according to \Rf {t:t:01:Nh}, \Rf {A:i:Ui:21}, \Rf {A:i:Ui:21:"}.
-
+\item Input \m{\M {P} \in \MB {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_B^2}}, \m {\g_{\Rm {DS}} > 0}.
+%
+\item Define \m {\T {\V {y}}, \T {\V {g}}, \T {\M {P}}, \T {\M {P}} ^\Adj, \T {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
+%
 \item Calculate
-%
-\DispNum {x:::mi:h1} {
-\NC \Hat {\V {x}}
+\DispNum {g:f:gf:S1} {
+\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
 \LA \NC \startcases
-\NC \Min {\V {x}' \in \MB {C} ^{N_H^2}}
-\MC \IP {\V {t}, \V {x}'} \NR
-\NC \Rm {subject} \; \Rm {to}
-\Q  \MC \VNm {\M {A} _{i} \V {x}' +\V {b} _{i}} _2
-\leq \IP {\V {c}_{i}, \V {x}'} +\V {d}_i \NR
-\NC \MC i 
-=0, 1, 2, \ldots, 2 N_H^2 -1 \NR
+   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
+   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}' \NR
+   \NC \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
+   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
+   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
 \stopcases \NR
-}
-\item Extract
-%
-\DispNum {g:::x0:h1} {
-\NC \Hat{\T{\V {g}}}
-\LA \NC \Hat{\V {x}} _{\SB {0 : 2 N_H^2-1}} \NR
 }
@@
 Then, we extract largest components of the estimated vector, and apply DS again.
-Furthermore, we extract largest components of the second estimated vector, and apply LS.
-The final vector's indices has to be scrambled back according to the original index.
+Furthermore, we extract largest components of the second estimated vector, and apply Moore–Penrose inverse.
+The final indices set has to be scrambled back corresponding to the original ones.
 
@@
 
-\item Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}, call the \m {N_1} largest component of \m {\Hat {\V {g}}_0} and to be \m {\V {g}_1}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _1}.
+\item Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}, and call the \m {N_1} largest component of \m {\Hat {\V {g}}_0} to be \m {\V {g}_1}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _1}.
 
-\item Apply DS to \m {\V {y}, \M {P}_1} to get \m {\Hat {\V {g}}_1}, call the \m {N_2} largest component of \m {\Hat {\V {g}}_1} and to be \m {\V {g}_2}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _2}.
+\item Apply DS to \m {\V {y}, \M {P}_1} to get \m {\Hat {\V {g}}_1}, and call the \m {N_2} largest component of \m {\Hat {\V {g}}_1} to be \m {\V {g}_2}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _2}.
 
-\item Apply least square to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}, which corresponds to \m {\Hat {\V {g}}}.
+\item Apply Moore–Penrose inverse to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}, which corresponds to \m {\Hat {\V {g}}}.
 \stopitemize
@@
 
-Unfortunately, the two-stage method does not always appear to be better than the one-stage method, and we did not include the result in the figures.
+Unfortunately, the two-stage method does not always appear to be better than the one-stage method, and we did not include the method in the plots.
 It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H},
@@
 \startsubsection [title={Settings}]
+
+Beside DS, we have simulated OMP for three different stop conditions, Lasso, and Moore Penrose pseudoinverse (abbreviated LS for least square).
+For the plot of assorted methods, \m {8} values of \m {\s} are considered; for the plots of only OMP, \m {9} values are considered; for the plots of only OMP, \m {6} values are considered.
 
@@
 }
-In the following simulation, we use dimensionless noise-to-signal level \m {\s}.
-Its value starts with \m {2^{-4}}, and is increased by being multiplied with 2.
-For the plot of assorted methods, 8 values of \m {\s} are used; for the plots of only OMP, 9 values are used; for the plots of only OMP, 6 values are used.
+In the following simulation, we use dimensionless noise-to-signal levels starting with \m {2^{-4}}, and being multiplied with powers of \m {2}.
 
@@
 For assorted plots, two series of plots are simulated.
-One series for \m {N_Y = \lfloor N_H /2 \rfloor}, giving \m {4, 6, 8, 10, 12};
-one series for \m {N_Y = \lfloor N_H /3 \rfloor}, giving \m {3, 4, 5, 7, 8}.
-For OMP and DS only plots, we just choose \m {N_Y = \lfloor N_H /3 \rfloor}.
+One series for \m {N_B = \lfloor N_H /2 \rfloor}, giving \m {4, 6, 8, 10, 12};
+one series for \m {N_B = \lfloor N_H /3 \rfloor}, giving \m {3, 4, 5, 7, 8}.
+For OMP and DS only plots, we only consider \m {N_B = \lfloor N_H /3 \rfloor}.
 On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
@@
 The wavelength of carrier \m {\l _{\Rm {ant}}} is set to be \m {0.1}.
-and the antenna spacing \m {d _{\Rm {ant}}} is 0.2.
+and the antenna spacing \m {d _{\Rm {ant}}} is \m {0.2}.
 Only their ratio matters.
@@
 The maximal number of iteration of CVXPY is set to be \m {32}.
-On the other hand, the maximal number of iteration of OMP is set to be \m {4 N_Y}.
+On the other hand, the maximal number of iteration of OMP is set to be \m {4 N_B}.
 
 Denote the threshold used in DS program to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
-Different values are tried by multiplying or dividing them by powers of 2.
+Different values are produced by multiplying powers of \m {2}.
 
@@
 For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
-For OMP, suggested values in Cai \& Wang (2011) is illuminating, where they (in their Theorem 7) considered \m {\ell _2}-norm, and (in their Theorem 8), \m {\ell _\infty}-norm.
-We make simplification and set respectively \m {\R {3 N_Y}} and \m {2 \R {\log N_H}}.
-Meanwhile, the threshold used for the remainder norm used in OMP program is suggested in \cite [CaW11].
-We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 N_Y}} for 2-norm constraint.
+For OMP, suggested values in Cai and Wang \cite [CaW11] is illuminating, where they (in their Theorem 7) considered \m {\ell _2}-norm, and (in their Theorem 8), \m {\ell _\infty}-norm.
+We simply take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 N_B}} for 2-norm constraint.
 
@@
 
-Each data point for DS and Lasso is repeated for 256 times, and taken average.
+Each data point for DS and Lasso is repeated for \m {256} times, and taken average.
 Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {12 \D 256} times.
@@
 It remains to be tested what values are most suitable for our purposes.
-If the tolerance parameters are too small, the program often gives overflowing values, perhaps because it cannot find feasible solutions.
-On the other hand, if they are too big, the steps are so imprecise that the program may fail to solve.
+If the tolerance parameters are set too small, the program often gives overflowing values, perhaps because it was not able to find feasible solutions.
+On the other hand, if they are set too big, the Newton steps are so imprecise that the program fails too.
 
@@
 In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
-Figures 3 to 6 have \m {N_H = 3 N_Y}, and figures 7 to 10 has \m {N_H = 2 N_Y}.
+Figures 3 to 6 have \m {N_H = 3 N_B}, and figures 7 to 10 has \m {N_H = 2 N_B}.
 
@@
 \externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 12}, error.}
+\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 12}, error.}
 \blank [big]
@@
 \externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 16}, error.}
+\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, error.}
 %
@@
 \externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 20}, error.}
+\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 20}, error.}
 %
@@
 \externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 24}, error.}
+\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 24}, error.}
 %
@@
 \externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 2 N_Y, N_H = 12}, error.}
+\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 12}, error.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 2 N_Y, N_H = 16}, error.}
+\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 16}, error.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 2 N_Y, N_H = 20}, error.}
+\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 20}, error.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 2 N_Y, N_H = 24}, error.}
+\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 24}, error.}
 \blank [big]
@@
 \externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 16}, time.}
+\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, time.}
 \blank [big]
@@
 \externalfigure [assorted-medium-low-signal-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_Y, N_H = 16}, low signal level, error.}
+\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, low signal level, error.}
 \blank [big]
@@
 
-Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_Y} for each of them.
+Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
 Here, \m {\T {\chi}} is shown too.
@@
 \externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 12}, error.}
+\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 12}, error.}
 \blank [big]
@@
 \externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 16}, error.}
+\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 16}, error.}
 \blank [big]
@@
 \externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 20}, error.}
+\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 20}, error.}
 \blank [big]
@@
 \externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 24}, error.}
+\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 24}, error.}
 \blank [big]
@@
 \externalfigure [ddss-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_Y, N_H = 16}, time.}
+\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 16}, time.}
 \blank [big]
@@
 
-Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_Y} for each of them.
+Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
 
@@
 \externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 12}, error.}
+\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 12}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 16}, error.}
+\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 16}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 20}, error.}
+\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 20}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 24}, error.}
+\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 24}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_Y, N_H = 16}, time.}
+\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 16}, time.}
 \blank [big]
@@
 However, it is not clear how higher \m {\s} (dimensionless noise level) corresponds to lower \m {\T {\chi}} (simulated error).
-It seems when \m {\s} is further increased (leftmost of the figures), the error might also increase rapidly, but more parameters have to be simulated for a conclusion.
+It seems when \m {\s} is further increased (leftmost of the plots), the error might also increase rapidly, but more parameters have to be simulated for a conclusion.
 
@@
 
-Sadly, we remark that CVXPY sometimes gives overflowing outputs, some of them as large as \m {10^11}.
+Sadly, we remark that CVXPY sometimes gives overflowing outputs, some of them as large as \m {10^{11}}.
 This indicates perhaps some typical-looking output may in fact be unreliable.
-To rid overflowing values, we discard outputs larger than a given threshold, say \m {10^4}, and simply apply a least square.
-It is open whether there are better methods.
+We thus discard outputs larger than a given threshold, say \m {10^4}, and simply return the answer to be a Moore–Penrose inverse.
+It is unknown whether there are better methods.
 
-We are not sure either, unfortunately, why \m {\T {\chi}} does not agree \m {\chi} (the error bound), and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
-As shown above, the \m {\chi} is very constant around 1, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
-A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts.
+We are not sure either, unfortunately, why \m {\T {\chi}} does not agree \m {\chi}, and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
+As shown above, \m {\chi} is almost constant around \m {1}, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
+A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
 These matters remain to be investigated in the future.
 
-To give some idea of the case that DS works or fails, figures 23 and 24 illustrate either cases.
+We include Figure 12 for completeness's sake, where extreme low signal level is considered.
+Starting with \m {-30} dB, error of all methods grow significantly.
+However, the data may not be entirely reliable, since as we said we automatically discard overflowing values when the program blows up.
+All in all, the trend remains to be reproduced perhaps by simulating on a better device.
+
+We end this section by showing two cases where DS works or fails, in figures 23 and 24.
 In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.
@@
 
-We take some liberty to assume that, at the start the iteration, the least square estimator was taken to be the initial value of \m {\V {g}_0}, namely
+We take some liberty to assume that, at the start the iteration, the Moore–Penrose inverse was taken to be the initial value of \m {\V {g}_0}, namely
 %
@@
 \NC C_{\Rm {OMP}}
-=\NC \MS {O} \SB {N_H^2 \log N_Y} \NR
+=\NC \MS {O} \SB {N_H^2 \log N_B} \NR
 }
 %
-Here \m {\log N_Y} is small in our experiments, and if we dropped some constants and \m {\log N_Y}, then we may assume \m {\MS {O} \SB {N_H^2}}.
+Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\MS {O} \SB {N_H^2}}.
 
@@
 \startsubsection [title={Runtime Statistics}]
+
+All plots included in this treatise, in total, took probably one month to run.
+Figures 6 and 10 each took about \m {3} days.
+The computer has \m {32} GB RAM, and Intel Core i9 processor.
+Simulation ran on Linux subsystem 2 of Windows 10.
 

### 2020-11-10 treatise/abstract.tex
Delete obsolete formulation on SOCP

@@
 
-Multiple-input-multiple-output (MIMO) is the next-generation standard of wireless communication.
-While the channel state information has to be known at the receiver for communication algorithms, for MIMO system the estimation is not easy.
-Meanwhile, the millimeter wave (mm-Wave) band, often used together with MIMO, is known to exhibit sparsity, and results on compressive sensing suggest that sparsity implies that fewer channel measurements shall suffice.
-In practice, Orthogonal Matching Pursuit (OMP) is usually used, as it has lower complexity.
+Multiple-input-multiple-output (MIMO) is the future of wireless communication, but the large number of antennae makes it difficult to estimate its channel state information.
+Since millimeter wave (mm-Wave) band, often used together with MIMO, is known to exhibit sparsity, results on compressive sensing suggest that, on mm-Wave band, fewer channel measurements shall suffice.
+Current literature prefers orthogonal matching pursuit (OMP) due to its lower complexity.
+It is interesting to note that Dantzig Selector (DS), claimed to have various performance guarantee, has seldom been examined.
 
-It is interesting to note that Dantzig Selector (DS), proposed by Tao and Candès, has seldom been applied.
-DS has several promising properties, and it is worthwhile to investigate how it performs on the channel sensing problem.
 In this treatise, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
-Using pilot signal and predetermind random beamformer, we apply DS for channel estimation, arguing in favor of its greater generality, its tolerance of noise corruption, and its lower averaged error.
-The treatise also gives a bound for the expected square error of DS, as well as bounded probability of success, and in so doing, showing dependency on the number of path and channel sparsity.
-
-DS can be cast as a linear program (LP), so that known methods for convex programs may be applied.
-Simulation is done on DS and other methods, and we discuss their respective merits.
-It turns out DS is steadily better than other alternatives, while it has siginificantly greater complexity.
+Using pilot signal and 
+We demonstrate that DS can be applied on a entrywise i.i.d.\ random beamformer, and give a bound for its expected error norm, which holds for high probability.
+DS is cast as a linear program, and simulation is done.
+We argue that DS is steadily better in our configuration, while it has siginificantly greater complexity.
 

### 2020-11-10 treatise/conclusion.tex
Delete obsolete formulation on SOCP

@@
 
-This treatise studied the effective estimation of the millimeter wave, multiple-input, multiple-output (mm-wave MIMO) channel.
-We adopts the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), which is most commonly used in literature, as the estimation algorithm, therefore exploiting the sparsity of the problem in spacial Fourier domain.
-We bounded the expected square error following the spirit of Candès and Tao \cite [CaT07].
-Towards that end, we characterized the spacial sparsity, confirmed the restricted isometry of measurement matrix \m {\M {P}}, and justified the generalization for complex vectors.
-The bound assumes a fairly general setting, and is expressed in terms of physical parameters, such as the number of path \m {L} and channel dimension \m {N_H}.
-
+This treatise investigates effective estimation of the millimeter wave, multiple-input, multiple-output (mm-wave MIMO) channel.
+We adopt the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), which is most commonly used in literature, by exploiting the sparsity of the problem in spacial Fourier domain.
+We bounded the expected error norm following the spirit of Candès and Tao \cite [CaT07].
+To do so, we evaluate the sparsity, confirm the restricted isometry of sensing matrix \m {\M {P}}, and generalize the method for complex vectors.
+Our bound, on a general setting, is characterize in terms of physical parameters, such as the number of path \m {L} and channel dimension \m {N_H}.
 Simulation is done, and DS's performance is compared to OMP, Lasso, and LS.
-DS performs slightly better than others, but gives much higher complexity, agreeing our analysis.
-Put concisely, no algorithm is a universal solution, as they trade off precision for time and space complexity, or conversely, among other things.
-We hope that our inquiry of DS suggests a welcomed alternative added to the present literature of channel estimation.
+DS outperforms others, at the cost of higher complexity, agreeing our analysis.
+Put concisely, DS trades off time and space complexity for precision, and we hope that our inquiry provides a welcome alternative to the present literature.
 

### 2020-12-16 presentation/1_setting.tex
New DS narrow figures, OMP square figures

@@
 {
-\I Given MIMO channel representation \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array, having \m {L} paths.
+\I Given MIMO channel representation \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array, having \m {L} paths, with hybrid beamforming.
 
@@
 
-\I Magnitude constraint \m {{\Nm {\M {F}_R}_{\SB {n_H, n_R}}} = 1}, \m {{\Nm {\M {W}_R}_{\SB {n_R, n_H}}} = 1} 
+\I Magnitude constraint \m {\Nm {\M {F}_{R,\SB {n_H, n_R}}} = 1}, \m {\Nm {\M {W}_{R,\SB {n_H, n_R}}} = 1}
 }
@@
 \Q \V {z}
-:= \Rm {vec} \SB {\M {Z}} \NR
+:= \Rm {vec} \SB {\M {W}_B \M {W}_R \M {Z}} \NR
 }
@@
 
-\I If \m {\V {g}} is sparse, few measurements may suffice for reconstruction.
+\I If \m {\V {g}} is sparse, fewer measurements suffice for reconstruction.
 
@@
 {
-\I Fix sparsity \m {s = L \RB {\log N_H}^2} for definiteness.
-
 \I Input \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.

### 2020-12-16 treatise/1_introduction.tex
New DS narrow figures, OMP square figures

@@
 Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification \cite [RSM13].
-With a large number of antennae on both transmitter and receiver, MIMO is expected to provide a large signal gain.
-The appeal of MIMO includes multiplexing gain (by parallel transmission of data), diversity gain (by redundant transmission with space-time coding), and antenna gain (by suitable beamforming to improve signal level).
-The millimeter wave (mm-wave) is also proposed, since its smaller wavelength, and thus higher frequency, results in wider bands available.
-The antennae, moreover, may be more closer-spaced, making it possible to increase their number.
+With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain.
+The appeal of MIMO includes multiplexing gain (by parallel transmission of data), diversity gain (by redundant transmission with space-time coding), and antenna gain (by suitable beamforming to improve the signal level).
+Besides, the millimeter wave (mm-wave) is proposed, since its smaller wavelength, and thus higher frequency, makes wider bands available.
+The antennae, moreover, may be more closer-spaced, allowing us to increase their number.
 
@@
 To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, may be obtained.
-Not only is the channel estimation difficult, due to the large antennae array, but the transmission in higher frequency is subject to noise corruption too.
-As a result, conventional training-based algorithms lead to large time and space complexity.
+Not only is the channel estimation difficult, due to a large antennae array, but the transmission in higher frequency is subject to noise corruption too.
+As a result, conventional training-based algorithms lead to considerable time and space complexity.
 
@@
 
-Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel representation.
-Our task amounts to invert a linear system whose dimension is the number of antennae.
+The estimation of MIMO channel amounts to determining the parameters of the channel.
+If we consider a slow varying channel for simplicity, in terms of a channel representation, our task amounts to invert a linear system whose dimension is the number of antennae.
 Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and that's when a recent development called compressive sensing may help.
-Generally speaking, it is a technique for reconstructing a underdetermined linear system, when the sparsity of solution guarantees successful recovery in most cases.
 
@@
 \FigureCaption {
-A generic situation in which a signal is “crowded” in the given basis, but is “sparse” in transformed basis.
+A conceptual illustration of compressive sensing.
 (Retrieved from \goto {\hyphenatedurl {Wikimedia Commons}} [url (commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif)])
@@
 
+Figure 1 shows a generic situation in which a signal is crowded in the given basis, but is sparse in transformed basis.
+The black line on the left is the original signal, and the yellow line is the reconstruct signal.
+If the signal is sparse on certain new basis, as shown in the right, then for a good approximation, we may take only the largest components for reconstruction.
+
+Generally speaking, compressive sensing aims to reconstruct a underdetermined linear system, when the sparsity of solution guarantees successful recovery in most cases.
 More measurements are required to recover the signal in the former, while fewer suffice in the latter basis.
-But, even if we are guaranteed latter basis exists, it is still a nontrivial undertaking to construct it.
+But, even if we are sure that latter basis exists, it is still a nontrivial undertaking to construct it.
 
-Candès and Tao \cite [Can05] first embarked a series of investigation on the problem.
 Let us say the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
@@
 %
-To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear transformation
+To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear system
 %
@@
 Certainly, \m {\M {Q} \RB {\V {x}_1 - \V {x}_2} = 0}, then \m {\V {x}_1, \V {x}_2} are indistinguishable.
-But if \m {\V {x}} is supposed to be sparse, it essentially restricts the system so much that we obtain unique solution for most of the time.
+But if \m {\V {x}} is supposed to be sparse, is it likely to rule out some of the solutions?
 
@@
 
-Candès and Tao showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurements, under overwhelming probability.
+Candès and Tao \cite [Can05], one of the earlier investigations on compressive sensing, showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability.
 
 As an application, it often occurs that a camera takes a high definition photo, and compresses the image later.
-But it may be desirable that a camera equipped with fewer sensors shall take a lower-resolution photo, to save computation and storage, and shall recover the image later.
-Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, while the imaging accuracy may be critical to the diagnosis too \cite [CaT07].
+But it may be desirable that a camera equipped with fewer sensors shall take a lower resolution photo to save storage, and shall recover the image later.
+Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, while the accuracy is critical to the diagnosis too \cite [CaT07].
 
@@
 
-Now, if the linear transformation is subject to noise \m {z},
+If the linear system is, furthermore, subject to noise \m {z},
 %
@@
 For concreteness, say \m {\V {z}} is an i.i.d.\ normalized random normal vector.
-If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig Selector (hereafter DS), recovery under the noisy case is again possible.
+If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible under high probability.
 
@@
 %
-\item Calculate
+\item Compute the convex program
 %
@@
 
-Here the constant \m {\d_s} in Definition [1] is crucial:
-we must make a series of carefully chosen but random measurements.
-We can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
-One common proposal is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive a algorithm that efficiently finds RIP matrices.
+Here the constant \m {\d_s} in Definition [1] is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
+A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently finds RIP matrices.
 
@@
 The accompanying note by the same group \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.
-And \cite [BHR08], which considered a linear time-invariant channel, showed that if the convolution with channel response can be seen as a linear system, whose sensing matrix has RIP of overwhelmingly probability, and DS is readily applied.
 
@@
 
-At the same time, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) may reconstruct a sparse signal sufficiently well in an overwhelmingly probability.
-In the situation of \Rf {y:y:Qx:xz}, we would pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.
+At the same time, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal.
+Again consider the situation of \Rf {y:y:Qx:xz}.
 
@@
 \startitemize[n]
+%
 \item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
@@
 }
+%
 \item Start the loop with counter \m {i \LA 1}.
+%
 \item Find
@@
 and insert \m {S \LA S \cup {i}}.
+%
 \item Compute
@@
 }
+%
 \item Break if
@@
 %
-where \m {\VNm {\M {Q} ^\ddagger} _1} denotes the operator norm.
+otherwise, go to step 4.
+%
 \item Output 
@@
 %
-Here \m {\V {r}} can be thought of as the estimated noise, and \m {S} the number of estimated nonzero components of \m {\V {x}} (here we have slightly abused the usage of subscript).
-From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming, providing a performance guarantee.
+Here \m {\V {r}} can be thought of as the estimated noise.
+The columns of \m {\M {Q}} are chosen greedily, according to the inner product with \m {\V {r}}, to be \m {S}, the index set of estimated nonzero components of \m {\V {x}}.
+From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming.
 
@@
 
-OMP has since been applied widely in the literature.
+OMP has since been applied pervasively in the literature of channel sensing.
 Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
-Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discussed the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
-Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero components.
-Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers, assuming the channel gain in each path is stationary.
-Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, with the effective beamformer serving as sensing matrix, where set of quantized angles was specially designed, and permuted DFT matrix is used.
+Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discussed the trade-off between number of measurement and accuracy, implemented on an all-phase-shifter beamformers based on non-uniform and predetermined angles.
+Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals.
+Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers, assuming the stationary channel gain in each path.
+Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the effective beamformer serves as sensing matrix, based on a set of specially designed angles.
 
@@
 
-We consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite [LGL16], and aim to compare their result.
-Their work proposed an optimal beamformer, jointly designed on both ends via a nonconvex optimization problem, and due to its difficulty they have made considerable approximation.
-Is the simplified beamformer still optimal for OMP?
+We consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite [LGL16], and intend to compare their result.
+Their work proposed an optimal beamformer, jointly designed on both ends via a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
+Is the simplified design for the sensing matrix still optimal for OMP?
 Or will there be mismatch between the angles of sensing matrix and their true values, compromising the algorithm's accuracy?
 
-In this treatise, we illustrate that DS may outperform OMP and other methods.
+In this treatise, we illustrate that DS can outperform OMP and other methods.
 In chapter 2 we shall see that the effective beamformer may serve as the sensing matrix having RIP for high probability.
-The sparsity can be exploited this way, and DS may readily be applied.
+The sparsity can be exploited this way, and DS is readily applied.
 In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a bound (which holds for high probability) on expected error norm, expressed in terms of the suggested sparsity and the number of paths.
 In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms are known.
-Numerical results show that in our configuration, where we have uniformly random angles of departure and arrival, DS is superior, but is achieved at the cost of higher complexity.
+Numerical results show that in our configuration, where we have uniformly random angles of departure and arrival, DS is superior but at the cost of higher complexity.
 

### 2020-12-16 treatise/2_problem_setting.tex
New DS narrow figures, OMP square figures

@@
 %
-\DispNum {a:y':VC:nh} {
+\DispNum {a:y':CN:NH} {
 \NC \V {a} \SB {\psi'}
-\in \NC \MB {C} ^ {N_H} \NR
-%
-\NC \V {a} \SB {\psi'}
-= \NC \F {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u} _{n_h} \NR
+= \NC \F {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u} _{n_h}
+\in \MB {C} ^ {N_H} \NR
 }
@@
 \DispNum {F:R:1::R1} {
-\NC \Nm {\M {F} _R} _{\SB {n_H, n_R}}
+\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
 = \NC 1, \NR
 %
-\NC \Nm {\M {W} _R} _{\SB {n_R, n_H}}
+\NC \Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
 = \NC 1, \NR
@@
 
-To convert the problem into a linear system recovery problem, we need several definitions.
+We need several definitions.
 %
@@
 %
-to formulate our goal as sparse recovery problem of \m {\Rm {vec} \SB {\M {H}}} to be
+to formulate the problem as a linear system:
 %
@@
 %
-As we have motivated in previous sections, we want to use DS by considering sparse vector, and at the same time to get rid of the angle grid quantization problem.
-However, there is no guarantee, though, that \m {\V {h}} will be sparse.
+At this stage we would like to apply DS on sparse vectors, as motivated in chapter 1.
+However, there is no guarantee that \m {\V {h}} is sparse.
 
@@
 
-\startsection [title={Angular space}]
+\startsection [title={Spacial frequency domain}]
 
-Introduce the discrete Fourier transform matrix \m {\M {K}} defined to be
+Introduce the discrete Fourier transform matrix \m {\M {K}}
 %
@@
 %
-which has the interpretation as the angular space (i.e., spatial frequency domain) representation of \m {\M {H}}, then
+it can be interpreted as spatial frequency domain representation of \m {\M {H}}.
+Then
 %
@@
 %
-If at the end of day, \m {\M {G}} is sparse, then we recover \m {\M {G}} instead, and our use of DS is fully justified.
+If it turns out that \m {\M {G}} is sparse, then we may recover \m {\M {G}} instead, justifying the use of DS.
 To simplify notation, set
@@
 
-If so, our program reads
+Our plan now looks like:
 
@@
 \startitemize[n]
+%
 \item Let \m {\g_{\Rm {DS}} \geq 0} be given.
+%
 \item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D N_B}},
@@
 and \m {\M {Y} \in \NC \MB {C} ^{N_B \D N_B}}.
+%
 \item Find \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
-\item Calculate
+%
+\item Compute the convex program
 %
@@
 }
+%
 \item Convert \m {\Hat {\V {g}}} back to the space domain, namely
@@
 }
+%
 \item Recover the estimated \m {\Hat {\M {H}}}, as

### 2020-12-16 treatise/4_simulation.tex
New DS narrow figures, OMP square figures

@@
 \NC \startcases
-\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
-\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2') \NR
-\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1', 2m_2'+1) \NR
-\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC (m_1, m_2) = (2m_1'+1, 2m_2'+1) \NR
+\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
+\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
+\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
+\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
 \stopcases \NR
@@
 %
-\item Calculate
+\item Compute the convex program
 \DispNum {g:f:gf:S1} {
@@
 
-\startsubsection [title={Assorted Plots}]
+\startsubsection [title={Plots of Assorted Methods}]
 
-In the following, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively.
-Figures 3 to 6 have \m {N_H = 3 N_B}, and figures 7 to 10 has \m {N_H = 2 N_B}.
+In the following, we plot the reciprocal of noise level vs relative error norm, for different values and ratios of \m {N_H} and \m {N_B}.
 
 \blank [big]
-\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 12}, error.}
+\externalfigure [assorted-square-small-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 12}, error norm.}
 \blank [big]
@@
 \blank [big]
-\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, error.}
+\externalfigure [assorted-square-medium-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 18}, error norm.}
+\blank [big]
 %
 \blank [big]
-\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 20}, error.}
-%
+\externalfigure [assorted-square-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 24}, error norm.}
 \blank [big]
-\externalfigure [assorted-wide-very-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 24}, error.}
 %
@@
 \externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 12}, error.}
+\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 10}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 16}, error.}
+\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 15}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 20}, error.}
-\blank [big]
+\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 20}, error norm.}
 %
 \blank [big]
-\externalfigure [assorted-narrow-very-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 2 N_B, N_H = 24}, error.}
+\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 8}, error norm.}
+%
 \blank [big]
+\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 12}, error norm.}
+%
+\blank [big]
+\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 16}, error norm.}
 
@@
 \FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, time.}
-\blank [big]
-
-We give one additional plot for extreme low signal level, in order to observe the trend of curves.
-\blank [big]
-\externalfigure [assorted-medium-low-signal-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, low signal level, error.}
 \blank [big]
@@
 \blank [big]
-\externalfigure [ddss-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 12}, error.}
+\externalfigure [ddss-narrow-small-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_B = 10, N_H = 12}, error.}
 \blank [big]
@@
 \blank [big]
-\externalfigure [ddss-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 16}, error.}
+\externalfigure [ddss-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_B = 15, N_H = 18}, error.}
 \blank [big]
@@
 \blank [big]
-\externalfigure [ddss-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 20}, error.}
+\externalfigure [ddss-narrow-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_B = 20, N_H = 24}, error.}
 \blank [big]
 %
-\blank [big]
-\externalfigure [ddss-very-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 24}, error.}
-\blank [big]
-%
-As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
+As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
 %
 \blank [big]
-\externalfigure [ddss-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_H = 3 N_B, N_H = 16}, time.}
+\externalfigure [ddss-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {DS, \m {N_B = 15, N_H = 18}, time.}
 \blank [big]
@@
 \blank [big]
-\externalfigure [oommpp-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 12}, error.}
+\externalfigure [oommpp-square-small-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = N_B = 12}, error.}
 \blank [big]
@@
 \blank [big]
-\externalfigure [oommpp-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 16}, error.}
+\externalfigure [oommpp-square-medium-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = N_B = 18}, error.}
 \blank [big]
@@
 \blank [big]
-\externalfigure [oommpp-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 20}, error.}
+\externalfigure [oommpp-square-big-error.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = N_B = 24}, error.}
 \blank [big]
 %
-\blank [big]
-\externalfigure [oommpp-very-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 24}, error.}
-\blank [big]
-%
-As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
+As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
 %
 \blank [big]
-\externalfigure [oommpp-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 3 N_B, N_H = 16}, time.}
+\externalfigure [oommpp-square-medium-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {OMP, \m {N_H = N_B = 18}, time.}
 \blank [big]
@@
 
-We want to know the complexity of DS and OMP.
+We discuss the complexity of DS and OMP.
 In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many iterations were done.
-Boyd and Vandenberghe \cite [BoV04] analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496ff, also p.531).
+Boyd and Vandenberghe \cite [BoV04] analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496, also p.531).
 In our case, Candès and Romberg \cite [CaR05] pointed out that the complex DS can be cast into an second order cone programming (SOCP), and where self concordance holds.

### 2020-12-17 presentation/3_simulation.tex
New DS narrow figures, OMP square figures
Erase automatic figure titles

@@
 =\NC \RB {
-   \F {\log_2 {\VNm {\V {h} -\Hat {\V {h}}} _2}}
-   {\log_2 {\VNm {\V {h}}_2}}
+   \F {\VNm {\V {h} -\Hat {\V {h}}} _2}
+   {\VNm {\V {h}}_2}
 } _{\Ss {avg}}, \NR
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=2N_B}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=12,N_B=12}}
 {
 \blank [big]
-\externalfigure [assorted-narrow-medium-error.png] [width=11cm]
+\externalfigure [assorted-square-small-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=2N_B}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24,N_B=24}}
 {
 \blank [big]
-\externalfigure [assorted-narrow-very-big-error.png] [width=11cm]
+\externalfigure [assorted-square-big-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=3N_B}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=12,N_B=10}}
 {
 \blank [big]
-\externalfigure [assorted-wide-medium-error.png] [width=11cm]
+\externalfigure [assorted-narrow-small-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=3N_B}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24,N_B=20}}
 {
 \blank [big]
-\externalfigure [assorted-wide-very-big-error.png] [width=11cm]
+\externalfigure [assorted-narrow-big-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\It {ibid.}, low signal, \m {N_H=16=3N_B}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=12,N_B=8}}
 {
 \blank [big]
-\externalfigure [assorted-medium-low-signal-error.png] [width=11cm]
+\externalfigure [assorted-wide-small-error.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Time, assorted, \m {N_H=16}}
+\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24,N_B=16}}
 {
 \blank [big]
-\externalfigure [assorted-medium-time.png] [width=11cm]
+\externalfigure [assorted-wide-big-error.png] [width=11cm]
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {\m {1/\s} vs time, assorted, \m {N_H=18,N_B=15}}
+{
+\blank [big]
+\externalfigure [assorted-narrow-medium-time.png] [width=11cm]
 }
@@
 \I As \m {2N_H^2} grows fast, DS becomes less feasible.
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {A Successful Case of Estimation}
-{
-\blank [big]
-\externalfigure [scatter-ddss-success.png] [wfactor=180]
-
-\I Soft thresholding (green) correctly guesses true nonzero components (black), and refines the estimated value (orange)
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {A Failed Case of Estimation}
-{
-\blank [big]
-\externalfigure [scatter-ddss-failure.png] [wfactor=180]
-
-\I Soft thresholding (green) guesses wrong nonzero components (black), and the estimated value (orange) deteriorates
 }

### 2020-12-17 treatise/1_introduction.tex
Erase automatic figure titles

@@
 In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a bound (which holds for high probability) on expected error norm, expressed in terms of the suggested sparsity and the number of paths.
-In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms are known.
-Numerical results show that in our configuration, where we have uniformly random angles of departure and arrival, DS is superior but at the cost of higher complexity.
+In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms exist.
+Numerical results show that in our problem setting, DS is superior but costs higher complexity.
 

### 2020-12-17 treatise/4_simulation.tex
Erase automatic figure titles

@@
 \externalfigure [assorted-square-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 12}, error norm.}
+\FigureCaption {Assorted methods, small, \m {N_B = 12, N_H = 12}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-square-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 18}, error norm.}
+\FigureCaption {Assorted methods, medium, \m {N_B = 18, N_H = 18}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-square-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 24}, error norm.}
+\FigureCaption {Assorted methods, big, \m {N_B = 24, N_H = 24}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 10}, error norm.}
+\FigureCaption {Assorted methods, small, \m {N_B = 10, N_H = 12}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 15}, error norm.}
+\FigureCaption {Assorted methods, medium, \m {N_B = 15, N_H = 18}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 20}, error norm.}
+\FigureCaption {Assorted methods, big, \m {N_B = 20, N_H = 24}, error norm.}
 %
@@
 \externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, small, \m {N_H = 12, N_B = 8}, error norm.}
+\FigureCaption {Assorted methods, small, \m {N_B = 8, N_H = 12}, error norm.}
 %
@@
 \externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, medium, \m {N_H = 18, N_B = 12}, error norm.}
+\FigureCaption {Assorted methods, medium, \m {N_B = 12, N_H = 18}, error norm.}
 %
@@
 \externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, big, \m {N_H = 24, N_B = 16}, error norm.}
+\FigureCaption {Assorted methods, big, \m {N_B = 16, N_H = 24}, error norm.}
 
@@
 \blank [big]
-\externalfigure [assorted-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_H = 3 N_B, N_H = 16}, time.}
+\externalfigure [assorted-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
 \blank [big]
@@
 \externalfigure [oommpp-square-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = N_B = 12}, error.}
+\FigureCaption {OMP, \m {N_H = 12, N_B = 12}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-square-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = N_B = 18}, error.}
+\FigureCaption {OMP, \m {N_H = 18, N_B = 18}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-square-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = N_B = 24}, error.}
+\FigureCaption {OMP, \m {N_H = 24, N_B = 24}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-square-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = N_B = 18}, time.}
+\FigureCaption {OMP, \m {N_H = 18, N_B = 18}, time.}
 \blank [big]
@@
 From lowest to highest error, it usually goes like this: DS, LS, Lasso, OMP.
-Though the result is encouraging for our purpose, we wonder why OMP is so bad.
-Did we make mistakes?
-We do not think so.
-A crucial reason might be that in Lee, Gil, and Lee \cite [LGL16], the angles of departure and arrival is distributed within a cluster of standard deviation 15 degrees, and in ours, they are uniform on the unit circle.
-One is then tempted to say, we suggested a low complexity beamformer and high complexity estimation method, while they suggested a high complexity beamformer and low complexity estimation method, and the low complexity solution does not seem effective in our settings.
-It remains to see, however, how OMP and DS compare, if done exactly under their settings.
 
-However, it is not clear how higher \m {\s} (dimensionless noise level) corresponds to lower \m {\T {\chi}} (simulated error).
+We wonder why OMP is so bad.
+A crucial reason might be that in Lee, Gil, and Lee \cite [LGL16], they proposed a high-complexity convex program for the beamformers, which they gave approximation, and we have here a low-complexity, randomly-generated beamformers.
+It may also have something to do with the distribution of angles of departure and arrival;
+their distribution lies within a cluster of standard deviation 15 degrees, and in ours, they are uniform on the unit circle.
+It remains to see how OMP and DS compare, if done exactly under their settings.
+
+The trend between \m {\s} (dimensionless noise level) and \m {\T {\chi}} (simulated error) is not clear, especially for OMP and lasso.
 It seems when \m {\s} is further increased (leftmost of the plots), the error might also increase rapidly, but more parameters have to be simulated for a conclusion.
 
-Varying thresholds of DS (namely \m {\g_{\Rm {DS}}}) and OMP (namely \m {\h_{\Rm {OMP}}}) appears not to affect the estimation significantly.
-Nevertheless, it seems \m {\g_{\Rm {DS}}} is usually best chosen in the order of magnitude of \m {\s}, which is reasonable.
-Sometimes the iteration stabilizes much earlier than is constrained by maximum iteration number.
+Varying thresholds of DS (namely \m {\g_{\Rm {DS}}}) and OMP (namely \m {\h_{\Rm {OMP}}}) appears not to affect much.
+It may have been that the iteration stabilizes much earlier than is constrained by maximum iteration number.
+While we choose \m {\g_{\Rm {DS}}} to be in the order of magnitude of \m {\s}, it seems, as signal level is low, a greater value may be better.
 
-Sadly, we remark that CVXPY sometimes gives overflowing outputs, some of them as large as \m {10^{11}}.
+Unfortunately, we report that CVXPY sometimes gives overflowing outputs, some of them as large as \m {10^{11}}.
 This indicates perhaps some typical-looking output may in fact be unreliable.
 We thus discard outputs larger than a given threshold, say \m {10^4}, and simply return the answer to be a Moore–Penrose inverse.
-It is unknown whether there are better methods.
-
-We are not sure either, unfortunately, why \m {\T {\chi}} does not agree \m {\chi}, and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
-As shown above, \m {\chi} is almost constant around \m {1}, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
-A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
-These matters remain to be investigated in the future.
-
-We include Figure 12 for completeness's sake, where extreme low signal level is considered.
-Starting with \m {-30} dB, error of all methods grow significantly.
-However, the data may not be entirely reliable, since as we said we automatically discard overflowing values when the program blows up.
 All in all, the trend remains to be reproduced perhaps by simulating on a better device.
 
-We end this section by showing two cases where DS works or fails, in figures 23 and 24.
+We are not sure either why \m {\T {\chi}} is an overestimation of \m {\chi} by several orders of magnitude.
+A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect, which remain to be investigated in the future.
+
+We end this section by showing two cases where DS works or fails, in figures 21 and 22.
 In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.

### 2020-12-17 treatise/5_conclusion.tex
Erase automatic figure titles

@@
 The treatise addresses the problem of effective estimation of the millimeter wave channel by exploiting its sparsity.
-Towards that end, we try the Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), which is a more common choice, as the estimation algorithm.
-We proceed by exploiting the sparsity of spatial frequency domain, rather than 
-the spatial domain itself, and suggested the generalization of DS for complex vectors work in present case.
-Moreover, assuming the virtual channel model according to uniform linear array response, we managed to prove explicitly, following the spirit of Candès and Tao \cite [CaT07], that for overwhelming probability, the expected square error is bounded.
+To do so, we try the Dantzig Selector (DS) for channel estimation, rather than the more commonly used Orthogonal Matching Pursuit (OMP).
+We exploited the sparsity of spatial frequency domain, and generalized DS for complex vectors.
+We then proved explicitly that the expected error is bounded for overwhelming probability.
 
-We also point out that DS may be cast into an LP, and simulation is done.
-DS is steadily more accurate than all other methods, while exhibiting rather high complexity.
-Unfortunately, and it remains to investigate why there is no obvious trend between the signal level and the relative error norm, and why CVXPY sometimes gives overflowing answers.
+We also pointed out that DS may be cast into an linear program, for which simulation is done.
+DS is steadily more accurate than all other methods, while costing higher complexity.
+Moreover, we are not sure about the best value of the threshold, and it remains to prevent CVXPY from giving overflowing answers.
+Meanwhile, OMP and Lasso often fails, and we wonder whether they are really so bad, or we have not used correct parameters.
 
 One must be careful in giving meaningful comparison of existent analytic bounds for compressive sensing algorithms, as they might work in different settings.
-Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation \cite [CaT07], while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
-OMP, on the other hand, may require only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], but much of its property remains open.
+Indeed, DS requires a RIP linear transformation, and it is said to work in noisy linear systems \cite [CaT07]; here, RIP is not at all easy to justify rigorously, and a more feasible construction is even an ongoing research problem.
+OMP, on the other hand, require only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], but much of its property is yet to be studied.
 On the whole, DS trades off low time and space complexity high precision, and for OMP the opposite is true.

### 2020-12-18 presentation/3_simulation.tex
Rev: chap 1, chap 4

@@
 {
-\I DS wins other method in the range drawn.
+\I DS outperforms other methods under our settings.
 
-\I \m {\chi} does not show the trend that \m {\T {\chi}} predicts.
+\I \m {\T {\chi}} and \m {\chi} differ by some orders of magnitude.
 
-\I The relaxed condition on sparsity may have compromised performance of DS
+\I The relaxed sparsity may have compromised effectiveness of DS
 
@@
 
-\I As \m {2N_H^2} grows fast, DS becomes less feasible.
+\I \m {2N_H^2} grows fast, and DS can becomes less feasible.
 }

### 2020-12-18 presentation/4_conclusion.tex
Rev: chap 1, chap 4

@@
 {
-\I We estimate MIMO mm-Wave channel \m {\M {H}} by using modified DS.
+\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.
 
-\I We justify DS under relaxed condition on sparsity of \m {\V {g}}, and demonstrate the RIP of effective beamformer \m {\M {P}}.
+\I We justify DS under relaxed sparsity of \m {\V {g}}, and demonstrate the RIP of effective beamformer \m {\M {P}}.
 
@@
 
-\I By simulation we see that DS appears to be superior to other methods.
+\I Simulation shows that DS appears to be superior to other methods.
 
-\I DS trades off low time and space complexity for high precision.
-For OMP, the opposite is true.
+\I DS trades off low time and space complexity for high precision, but for OMP, the opposite is true.
 }

### 2020-12-18 treatise/1_introduction.tex
Rev: chap 1, chap 4

@@
 With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain.
-The appeal of MIMO includes multiplexing gain (by parallel transmission of data), diversity gain (by redundant transmission with space-time coding), and antenna gain (by suitable beamforming to improve the signal level).
-Besides, the millimeter wave (mm-wave) is proposed, since its smaller wavelength, and thus higher frequency, makes wider bands available.
-The antennae, moreover, may be more closer-spaced, allowing us to increase their number.
+The appeal of MIMO includes multiplexing gain (parallel transmission of data), diversity gain (redundant transmission with space-time coding), and antenna gain (suitable beamforming to improve the signal level).
+Besides, the millimeter wave (mm-wave) is suggested, since its smaller wavelength (and thus higher frequency) makes wider bands available.
+Moreover the antennae may be closer-spaced, allowing us to increase their number.
 
 However, MIMO also gives rise to higher complexity, hence higher hardware overhead and power consumption.
-To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, may be obtained.
+To obtain channel state information (so that channel capacity can be known for instance), new algorithms have to address these issues.
 Not only is the channel estimation difficult, due to a large antennae array, but the transmission in higher frequency is subject to noise corruption too.
@@
 
-The estimation of MIMO channel amounts to determining the parameters of the channel.
-If we consider a slow varying channel for simplicity, in terms of a channel representation, our task amounts to invert a linear system whose dimension is the number of antennae.
-Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and that's when a recent development called compressive sensing may help.
+If we consider a slow varying MIMO channel for simplicity, in terms of a channel representation, to estimate the channel is to determine the parameters of the representation.
+We shall see it amounts to invert a linear system whose dimension is the number of antennae, which is not very effective.
+Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
 
@@
 
-Generally speaking, compressive sensing aims to reconstruct a underdetermined linear system, when the sparsity of solution guarantees successful recovery in most cases.
-More measurements are required to recover the signal in the former, while fewer suffice in the latter basis.
-But, even if we are sure that latter basis exists, it is still a nontrivial undertaking to construct it.
+Generally speaking, compressive sensing aims to reconstruct a underdetermined linear system, when the sparsity of solution guarantees successful recovery for most cases.
+More measurements are required to recover the signal in the nonsparse basis, while fewer suffice in the sparse basis.
+But, even if we are sure that the sparse basis exists, its construction is another undertaking.
 
@@
 }
-Certainly, \m {\M {Q} \RB {\V {x}_1 - \V {x}_2} = 0}, then \m {\V {x}_1, \V {x}_2} are indistinguishable.
-But if \m {\V {x}} is supposed to be sparse, is it likely to rule out some of the solutions?
+Certainly, if \m {\M {Q} \RB {\V {x}_1 - \V {x}_2} = 0}, then \m {\V {x}_1, \V {x}_2} are indistinguishable.
+But if \m {\V {x}} is sparse, can we rule out some of the possibilities?
 
-To define this, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
+To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
 That is, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
@@
 
-If the linear system is, furthermore, subject to noise \m {z},
+If the linear system is moreover subject to noise \m {z},
 %
@@
 
-We agree on some conventions.
+We introduce some conventions.
 For \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}}, denote
@@
 
-Particularly, Algorithm [2] recovers \m {\V {x}} with the expected square error bounded with overwhelming probability.
-
-The formulation as an \m {\ell_1} minimization problem, which is convex.
-From the computational perspective, this allows techniques from convex optimization to be used.
-In fact, Candès and Romberg provided an example implementation on their website \cite [CaR05].
-In addition, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear Program, rendering convex programming technique applicable.
+Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability.
+The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear Program, rendering convex programming technique applicable.
+This allows techniques from convex optimization to be used, and Candès and Romberg provided an implementation on their website \cite [CaR05].
 
 Here the constant \m {\d_s} in Definition [1] is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
-A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently finds RIP matrices.
+A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
 
-Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are in fact sparse in the frequency domain.
-Some scholars have thus applied compressive sensing techniques.
-An early attempt was Bajwa et.\ al.\ \cite [BHS10], where they argued that 
-if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
-The accompanying note by the same group \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.
+Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
+An early attempt to apply compressive sensing was Bajwa et.\ al.\ \cite [BHS10], where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
+The accompanying note by the same researchers \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.
 
@@
 
-At the same time, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal.
+At the same time, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal in an underdetermined system.
 Again consider the situation of \Rf {y:y:Qx:xz}.
@@
 %
-\item Input \m {\M {Q} \in \MB {R} ^{N_m, N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
+\item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
 %
@@
 %
-\DispNum {c:c:i0:ir} {
-\NC c
-\LA \NC \underset {i =0, \dots, N_p-1} {\Rm {argmax}}
-\Nm {\M {Q} _{\SB {:,i}} \V {r}} \NR
+\DispNum {n:n:n0:nr} {
+\NC n
+\LA \NC \underset {n' =0, \dots, N_p-1} {\Rm {argmax}}
+\Nm {\M {Q} _{\SB {:,n'}} \V {r}} \NR
 }
 %
-and insert \m {S \LA S \cup {i}}.
+and append \m {S \LA S \cup {n}}.
 %
@@
 %
-Here \m {\V {r}} can be thought of as the estimated noise.
-The columns of \m {\M {Q}} are chosen greedily, according to the inner product with \m {\V {r}}, to be \m {S}, the index set of estimated nonzero components of \m {\V {x}}.
+The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix in the case of DS.
+In each step, we estimate the noise \m {\V {r}}, and find a new column most correlated with it, to refine the estimation for \m {\V {x}}.
 From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming.
 
-OMP also makes use of an entrywise i.i.d.\ random matrix.
-It is instructive to note that the matrix columns is likely to span \m {\V {x}}, playing a role similar to the sensing matrix in the case of DS.
-
-OMP has since been applied pervasively in the literature of channel sensing.
-Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
-Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discussed the trade-off between number of measurement and accuracy, implemented on an all-phase-shifter beamformers based on non-uniform and predetermined angles.
+OMP has since been pervasively used for channel sensing.
+Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles.
+Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamformers based on nonuniform fixed set of angles.
 Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals.
-Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers, assuming the stationary channel gain in each path.
-Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the effective beamformer serves as sensing matrix, based on a set of specially designed angles.
-
-Some further attempts include Manoj and Kannu \cite [MaK17], who formulated the sparse condition on submatrices of the signal for successful reconstruction.
-Gurbuz, Yapici, and Guvenc \cite [GYG18] introduced perturbation of the quantized set of angles, on which the sensing matrix is based.
-Panayirci et.\ al.\ \cite [PAU19] suggested, in addition to application of OMP, a concatenation of max-likelihood estimation of model parameters, and maximum-a-posteriori estimation of channel gains.
+Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers of stationary channel gain.
+Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the effective beamformer serves as sensing matrix, based on a designed set of angles.
+Manoj and Kannu \cite [MaK17] studied the sparse condition on submatrices of the signal for successful reconstruction.
+Gurbuz, Yapici, and Guvenc \cite [GYG18] introduced perturbation on the angles which the sensing matrix based on.
+Panayirci et.\ al.\ \cite [PAU19] proposed a concatenation of max-likelihood estimation of model parameters, and maximum-a-posteriori estimation of channel gains, by virtue of OMP.
 
 Performance guarantee of OMP is also studied on various conditions.
-Cai, Wang, and Xu \cite [CWX10], under assumption of low coherence of columns of matrices, instead of almost-unitarity, gave new bound on OMP.
-Cai and Wang \cite [CaW11] extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] followed up and refined their bounds, concluding that OMP is better for low-SNR scenario, and DS is better for high-SNR.
+Cai, Wang, and Xu \cite [CWX10], gave a new bound on performance of OMP under assumption of low coherence of columns of matrices, instead of almost unitarity.
+Cai and Wang \cite [CaW11] extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] followed up and refined their bounds, concluding that OMP is better for low SNR scenario, and DS is better for high SNR.
 
@@
 
-We saw that the literature on channel estimation seems to favored OMP for its low complexity.
-Then one naturally wonders how greedy algorithms, like OMP, compare to convex programs, like DS.
-Can it be that greedy algorithms trade precision for complexity, and that the opposite is true of convex programs?
+The literature on channel estimation favors OMP for its low complexity, but we wonder how greedy algorithms, such as OMP, compare to convex programs, such as DS.
+It might be that greedy algorithms trade precision for complexity, and that the opposite is true of convex programs.
 
-We consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite [LGL16], and intend to compare their result.
-Their work proposed an optimal beamformer, jointly designed on both ends via a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
-Is the simplified design for the sensing matrix still optimal for OMP?
-Or will there be mismatch between the angles of sensing matrix and their true values, compromising the algorithm's accuracy?
+In this treatise, we consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite [LGL16].
+They proposed a beamformer shown to be optimal, jointly designed on both ends by a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
+Is the approximated design still optimal, or do the angles of sensing matrix become less accurate?
 
-In this treatise, we illustrate that DS can outperform OMP and other methods.
-In chapter 2 we shall see that the effective beamformer may serve as the sensing matrix having RIP for high probability.
-The sparsity can be exploited this way, and DS is readily applied.
-In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a bound (which holds for high probability) on expected error norm, expressed in terms of the suggested sparsity and the number of paths.
-In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms exist.
-Numerical results show that in our problem setting, DS is superior but costs higher complexity.
+In chapter 2 we shall see that our proposed effective beamformer has RIP for high probability, which may serve as the sensing matrix for DS.
+In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a quantitative bound (which holds for high probability) on expected error norm.
+In chapter 4, we remark that DS can be cast as a linear program, for which more efficient algorithms exist.
+Numerical results show that in our problem setting, DS can be superior to other methods, but costs higher complexity.
 

### 2020-12-18 treatise/3_2_design_of_beamformers.tex
Rev: chap 1, chap 4

@@
 Our plan is setting the four beamformers to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
-Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
+Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ normal random variables with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
 We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_B}}} follows Rayleigh distribution.
@@
 %
-We want a large deviation result for i.i.d.\ sum of chi-square r.vs.
+We want a large deviation result for i.i.d.\ sum of chi-square random variables.
 To so so, we may apply Lemma 1 in Laurent and Massart \cite [LaM00] for equal weights.

### 2020-12-18 treatise/4_simulation.tex
Rev: chap 1, chap 4

@@
 In this chapter we shall compare \Rf {d:2:OL:H3} with numerical experiments.
-For the convex optimization, we choose the Python library CVXPY.
-For the implementation details, see Diamond and Boyd \cite [DiB16]
-A direct implementation of Algorithm [7] leads to extraordinarily large complexity, but Candès and Romberg \cite [CaR05] showed that DS can be cast as a linear program, which we illustrate below.
+For the convex optimization, we choose the Python library CVXPY \cite [DiB16].
+While a direct implementation of Algorithm [7] leads to extraordinarily large complexity, Candès and Romberg \cite [CaR05] showed that DS can be cast as a linear program, which we elaborate below.
 
@@
 
-For brevity we shall represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
+Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
 For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
@@
 
-We can now see that DS is equivalent to a linear program.
+It is now straightforward to see that DS is equivalent to a linear program.
 
@@
 We also tried another version of DS, in which DS is applied twice in estimated nonzero components.
-The two-stage method was briefly mentioned \cite [CaT07] but without further justification by numerical experiments.
-To apply the method, we first apply DS as before.
-Then, we extract largest components of the estimated vector, and apply DS again.
-Furthermore, we extract largest components of the second estimated vector, and apply Moore–Penrose inverse.
-The final indices set has to be scrambled back corresponding to the original ones.
+The two-stage method was briefly mentioned \cite [CaT07] without further numerical verification.
+It goes as follows:
+We first apply DS as before;
+we extract largest components of the estimated vector, and apply DS again;
+we extract largest components of the second estimated vector, and apply Moore–Penrose inverse;
+finally, indices set has to be scrambled back corresponding to the original ones.
 
@@
 
-Unfortunately, the two-stage method does not always appear to be better than the one-stage method, and we did not include the method in the plots.
-It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H},
-and we do not know what most reasonable choice of \m {N_1, N_1, N_2} is.
+Unfortunately, the two-stage method is not always more accurate than the one-stage method, so we did not include it in the plots.
+It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H}, and we do not know what the best choice is.
 
@@
 
-Beside DS, we have simulated OMP for three different stop conditions, Lasso, and Moore Penrose pseudoinverse (abbreviated LS for least square).
-For the plot of assorted methods, \m {8} values of \m {\s} are considered; for the plots of only OMP, \m {9} values are considered; for the plots of only OMP, \m {6} values are considered.
+In addition to DS, we shall simulate OMP for three different stop conditions, Lasso, and Moore Penrose pseudoinverse (marked as LS which stands for least square).
 
-To get some idea of the order of magnitude of noise-to-signal level, plug in some actual numbers.
+To get some idea on the order of magnitude of noise-to-signal level, plug in some actual numbers.
 Consider only path loss in the simplest form according to Friis Law.
-Suppose the power of mobile phone antenna is 0.25 W,
-the carrier frequency is 5GHz,
+Suppose the power of mobile phone antenna is \m {0.25} W,
+the carrier frequency is \m {5} GHz,
 the base station is \m {1.5} km away,
@@
 }
-In the following simulation, we use dimensionless noise-to-signal levels starting with \m {2^{-4}}, and being multiplied with powers of \m {2}.
 
-We take \m {N_H} to be \m {8, 12, 16, 20, 24}, respectively.
+We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}.
+For the plots of assorted methods, \m {7} values of \m {\s} are considered; for the plots of DS or OMP only, \m {9} values are considered.
+
+We take \m {N_H} to be \m {12, 18, 24}, respectively.
 For assorted plots, two series of plots are simulated.
-One series for \m {N_B = \lfloor N_H /2 \rfloor}, giving \m {4, 6, 8, 10, 12};
-one series for \m {N_B = \lfloor N_H /3 \rfloor}, giving \m {3, 4, 5, 7, 8}.
-For OMP and DS only plots, we only consider \m {N_B = \lfloor N_H /3 \rfloor}.
+The first series for \m {N_B = N_H}, giving \m {12, 18, 24}.
+The second series for \m {N_B = \lfloor 5 N_H /6 \rfloor}, giving \m {10, 15, 20}.
+The third series for \m {N_B = \lfloor 2 N_H /3 \rfloor}, giving \m {8, 12, 16}.
+For plots of OMP only, we consider \m {N_B = \lfloor N_H \rfloor}.
+For plots of DS only, we consider \m {N_B = \lfloor 5 N_H /6 \rfloor}.
 On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
-Unfortunately, this is very far from achieving the design values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
+Unfortunately, this is very far from achieving the ideal values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
 
-Other parameters are fixed in these experiments; 
-The number of grid of quantization of analog precoder is \m {16}.
+Other parameters are fixed in these experiments.
+The number of grid of quantization of analog beamformers is \m {16}.
 The number of paths \m {L} is \m {4}.
-The wavelength of carrier \m {\l _{\Rm {ant}}} is set to be \m {0.1}.
-and the antenna spacing \m {d _{\Rm {ant}}} is \m {0.2}.
-Only their ratio matters.
+The wavelength of carrier \m {\l _{\Rm {ant}}} is set to be \m {0.1}, and the antenna spacing \m {d _{\Rm {ant}}} is \m {0.2}; only their ratio matters.
 
-For parameters related to the convex optimization algorithm, the tolerance of absolute error in the primal-dual algorithm used in CVXPY is set as \m {10^{-4}}, and the tolerance of relative error, as \m {10^{-3}}.
-The maximal number of iteration of CVXPY is set to be \m {32}.
-On the other hand, the maximal number of iteration of OMP is set to be \m {4 N_B}.
+Denote the threshold for DS to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
+In the plots of assorted methods, we set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
+For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
+For OMP, suggested values in Cai and Wang \cite [CaW11] is illuminating, where they considered \m {\ell _2}-norm in their Theorem 7, and \m {\ell _\infty}-norm in their Theorem 8.
+We simply take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 N_B}} for 2-norm constraint.
+Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
+The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
 
-Denote the threshold used in DS program to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
-Different values are produced by multiplying powers of \m {2}.
-
-In the plots of assorted methods, we set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} for concreteness, as suggested in \cite [CaT07].
-For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
-For OMP, suggested values in Cai and Wang \cite [CaW11] is illuminating, where they (in their Theorem 7) considered \m {\ell _2}-norm, and (in their Theorem 8), \m {\ell _\infty}-norm.
-We simply take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 N_B}} for 2-norm constraint.
-
-In the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} to observe the effects of thresholds.
-
-Each data point for DS and Lasso is repeated for \m {256} times, and taken average.
+Each data point for DS and Lasso is repeated for \m {256} times, and taken arithmetic average.
 Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {12 \D 256} times.
@@
 However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
-We do not know, either, whether \m {\T {\chi}} is a good indicator of channel capacity, since we do not fix a channel model in our investigation.
+We do not know either whether \m {\T {\chi}} is a good indicator of channel capacity; it seems to be, but actually we did not consider a definite a channel model in this treatise.
 
@@
 We set the maximum absolute tolerance to be \m {5 \D 10 ^ {-7}},
-the maximum absolute tolerance to be \m {5 \D 10 ^ {-6}},
+the maximum relative tolerance to be \m {5 \D 10 ^ {-6}},
 the maximum feasible tolerance to be \m {5 \D 10 ^ {-7}}.
-It remains to be tested what values are most suitable for our purposes.
 If the tolerance parameters are set too small, the program often gives overflowing values, perhaps because it was not able to find feasible solutions.
-On the other hand, if they are set too big, the Newton steps are so imprecise that the program fails too.
+And if they are set too big, the Newton steps get imprecise and the performance is poorer.
+More tests are necessary to determine the best choice of parameters.
 
@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm, for different values and ratios of \m {N_H} and \m {N_B}.
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H} and \m {N_B}.
 
@@
 \externalfigure [assorted-square-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, small, \m {N_B = 12, N_H = 12}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-square-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, medium, \m {N_B = 18, N_H = 18}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-square-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, big, \m {N_B = 24, N_H = 24}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, small, \m {N_B = 10, N_H = 12}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, medium, \m {N_B = 15, N_H = 18}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, big, \m {N_B = 20, N_H = 24}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
 %
@@
 \externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, small, \m {N_B = 8, N_H = 12}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
 %
@@
 \externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, medium, \m {N_B = 12, N_H = 18}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
 %
@@
 \externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, big, \m {N_B = 16, N_H = 24}, error norm.}
+\FigureCaption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}
 
@@
 
-Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
+Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
 Here, \m {\T {\chi}} is shown too.
@@
 
-Again, we plot the reciprocal of noise level vs relative error norm, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
+Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
 
@@
 
-We wonder why OMP is so bad.
-A crucial reason might be that in Lee, Gil, and Lee \cite [LGL16], they proposed a high-complexity convex program for the beamformers, which they gave approximation, and we have here a low-complexity, randomly-generated beamformers.
+The performance of OMP appears poor.
+In most cases, the estimation fails, and we have \m {\T {\chi}} close to the unity.
+Varying thresholds of OMP, namely \m {\h_{\Rm {OMP}}}, does not give different result.
+
+A crucial reason might be that Lee, Gil, and Lee \cite [LGL16] proposed a high-complexity nonconvex program for the beamformers, which they gave approximation, and we have here a low-complexity, randomly-generated beamformers.
 It may also have something to do with the distribution of angles of departure and arrival;
 their distribution lies within a cluster of standard deviation 15 degrees, and in ours, they are uniform on the unit circle.
-It remains to see how OMP and DS compare, if done exactly under their settings.
+It remains to see how OMP and DS compare, if done according to their procedure.
 
-The trend between \m {\s} (dimensionless noise level) and \m {\T {\chi}} (simulated error) is not clear, especially for OMP and lasso.
-It seems when \m {\s} is further increased (leftmost of the plots), the error might also increase rapidly, but more parameters have to be simulated for a conclusion.
+The performance of Lasso also fails mostly, and \m {\T {\chi}} even increase as \m {\s} decreases, which is strange.
 
-Varying thresholds of DS (namely \m {\g_{\Rm {DS}}}) and OMP (namely \m {\h_{\Rm {OMP}}}) appears not to affect much.
+For Moore Penrose pseudoinverse, \m {\T {\chi}} decreases steadily as \m {\s} decreases.
+
+For DS itself, \m {\T {\chi}} decreases as \m {\s} increases, which is expected, but \m {\T {\chi}} does not go down indefinitely, even for very low \m {\s}.
+The values of threshold of DS \m {\g_{\Rm {DS}}} are chosen within the order of magnitude of \m {\s}.
+For high signal level, \m {\g_{\Rm {DS}}} does not affect much, but for low signal level a greater value may be more effective.
 It may have been that the iteration stabilizes much earlier than is constrained by maximum iteration number.
-While we choose \m {\g_{\Rm {DS}}} to be in the order of magnitude of \m {\s}, it seems, as signal level is low, a greater value may be better.
 
-Unfortunately, we report that CVXPY sometimes gives overflowing outputs, some of them as large as \m {10^{11}}.
-This indicates perhaps some typical-looking output may in fact be unreliable.
-We thus discard outputs larger than a given threshold, say \m {10^4}, and simply return the answer to be a Moore–Penrose inverse.
-All in all, the trend remains to be reproduced perhaps by simulating on a better device.
+Unfortunately, we report that CVXPY sometimes gives overflowing values, some of them as large as \m {10^{11}}.
+This probably indicates some typical-looking output may in fact be unreliable.
+Therefore we have discarded outputs larger than a given threshold, for instance \m {10^4}, and simply return the answer to be a Moore–Penrose inverse.
 
@@
 
-We end this section by showing two cases where DS works or fails, in figures 21 and 22.
+We end the discussion by showing two cases where DS works or fails, in figures 21 and 22.
 In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.

### 2020-12-18 treatise/5_conclusion.tex
Rev: chap 1, chap 4

@@
 We exploited the sparsity of spatial frequency domain, and generalized DS for complex vectors.
-We then proved explicitly that the expected error is bounded for overwhelming probability.
+We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
 
-We also pointed out that DS may be cast into an linear program, for which simulation is done.
-DS is steadily more accurate than all other methods, while costing higher complexity.
-Moreover, we are not sure about the best value of the threshold, and it remains to prevent CVXPY from giving overflowing answers.
-Meanwhile, OMP and Lasso often fails, and we wonder whether they are really so bad, or we have not used correct parameters.
+We also remarked that DS may be cast into an linear program, which help reduce complexity.
+Simulation is done, and DS appears more accurate than all other methods, while costing higher complexity.
+However, much has to be investigated for more diverse parameters, and on a more powerful computer, for a definite conclusion.
+We are not sure about the best value of the threshold, and we also have to prevent CVXPY from giving overflowing values.
+Meanwhile, OMP and Lasso often fails, and we wonder whether they are really so bad, or we have not followed the literature correctly.
 
-One must be careful in giving meaningful comparison of existent analytic bounds for compressive sensing algorithms, as they might work in different settings.
-Indeed, DS requires a RIP linear transformation, and it is said to work in noisy linear systems \cite [CaT07]; here, RIP is not at all easy to justify rigorously, and a more feasible construction is even an ongoing research problem.
-OMP, on the other hand, require only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], but much of its property is yet to be studied.
-On the whole, DS trades off low time and space complexity high precision, and for OMP the opposite is true.
+Note that we must be careful in giving meaningful comparison between compressive sensing algorithms, as they might work in different settings.
+DS requires a RIP linear transformation, and it works for noisy linear systems \cite [CaT07]; here, it is not easy to justify RIP rigorously, and a more feasible construction is even a research problem.
+OMP, on the other hand, requires only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], but much of its property is yet to be studied.
+On the whole, DS trades off low time- and space-complexity for high precision, and for OMP the opposite is true.
 

### 2020-12-19 treatise/1_introduction.tex
Chap 3, 4: Slight rev

@@
 {
-For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies \m {\d_s}-restricted isometry property (hereafter \m {\d_s}-RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if for all \m {s}-sparse \m {\V {x}}
+For fixed \m {s =0, \dots N_p -1}, we say that \m {\M {Q}} satisfies \m {\d_s}-restricted isometry property (hereafter \m {\d_s} RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if for all \m {s}-sparse \m {\V {x}}
 %

### 2020-12-19 treatise/2_problem_setting.tex
Chap 3, 4: Slight rev

@@
 
-We restrict our consideration to the uniform linear array, which can be modeled as
+For simplicity we suppose uniform linear arrays, for which the response be modeled as thus,
 %
@@
 
-And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ \cite [ALS14]).
+And consider the virtual representation of the MIMO channel, as in Akdeniz et.\ al.\ \cite [ALS14],
 %
@@
 %
-The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
-For our purpose, we may absorb the argument of \m {\V {a}} as
+The physical meaning of \m {\f_l'} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l'}, the \m {l}-th angle of arrival wave, and \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
+For our purpose, we may absorb the arguments of \m {\V {a}}
 %
@@
 \externalfigure [system.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Schematic diagram of the hybrid beamforming system we consider.}
+\FigureCaption {Schematic diagram of the hybrid beamforming system we consider, based on Akdeniz et.\ al.\ \cite [ALS14].}
 \blank [big]
 
-We consider the hybrid beamforming at both transmitter and receiver end, as shown in the figure.
-That is to say, each end consists of both digital and analog precoders and combiners, as follows.
-In the transmitter end, there are (seeing towards receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_B}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
-Similarly, in the receiver end, there are (seeing towards transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_B \D  N_R}}.
+We consider the hybrid beamforming at both transmitter and receiver ends, as shown in Figure 2.
+Each end consists of both digital and analog precoders and combiners.
+In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_B}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_B \D  N_R}}.
 
-Recall that analog precoder is restricted to have value with magnitude being unity, i.e.,
+Recall that analog precoders may only have values of unity magnitude,
 %
@@
 
-Since we restrict our discussion to a specific snapshot of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_B \D N_B}} with each entry being i.i.d.\ Standard Normal.
-We may introduce the effective channel
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
+Let us introduce the effective channel
 %
@@
 %
-Our task, then, is the recovery of \m {\M {H}}, and the design of \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.
+Our task then amounts to recovering \m {\M {H}}, and designing \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.
 
@@
 
-We need several definitions.
+We need several notations.
 %
@@
 \NC \RB {\Rm {vec} \SB {\M {A}}} _{\SB {m}}
-=\NC \M {A} _{\SB {m\; \Rm {Mod}}\; N_1, \Fl {m/N_1 }} \NR
+=\NC \M {A} _{\SB {m\; \Rm {Mod}\; N_1, \Fl {m/N_1 }}} \NR
 }
@@
 
-And we will exploit the relation, which is straightforward from definitions.
+The following relation, which is straightforward from definitions, is going be used below.
 \Result
@@
 
-It would seem now appealing to write
+It is more appealing to write
 %
@@
 %
-At this stage we would like to apply DS on sparse vectors, as motivated in chapter 1.
-However, there is no guarantee that \m {\V {h}} is sparse.
+At this stage, we intend to apply DS, but there is no guarantee that \m {\V {h}} must be sparse.
 
@@
 
-Introduce the discrete Fourier transform matrix \m {\M {K}}
+Denote the discrete Fourier transform matrix to be \m {\M {K}},
 %
@@
 %
-Sans serif \m {\Ss {e}} and \m {\Ss {i}} denote the natural base and imaginary unit, respectively.
-Here recall that we have
+Recall that we have
 %
@@
 %
-Observe that, if we write
+If we write
 %
@@
 %
-it can be interpreted as spatial frequency domain representation of \m {\M {H}}.
-Then
+then \m {\M {G}} can be interpreted as spatial frequency domain representation of \m {\M {H}}.
 %
@@
 %
-If it turns out that \m {\M {G}} is sparse, then we may recover \m {\M {G}} instead, justifying the use of DS.
-To simplify notation, set
+If we are sure that \m {\M {G}} is sparse, then we recover \m {\M {G}} instead.
+Set for brevity
 %
@@
 %
-And accordingly
+and
 %
@@
 %
-Then
+accordingly
 %
@@
 
-Our plan now looks like:
+Our plan becomes now
 
@@
 \DispNum {G:G:ve:1g} {
-\NC \Hat {G}
-\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
+\NC \Hat {\M {G}}
+\LA \NC \Rm {vec}^{-1} \SB {\Hat {\V {g}}} \NR
 }

### 2020-12-19 treatise/3_1_sparsity_of_channel.tex
Rev contribution
Chap 3, 4: Slight rev

--- 2020-11-08 treatise/3_1_almost_sparsity.tex
@@
-\startsection [title={Angular channel response is almost-sparse}]
+\startsection [title={Sparsity of channel}]
 
@@
 %
-\NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
+\NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \NR
 %
@@
 Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
-We seek to bound the rectangles with an integral, and we have to split the cases that \m {N_H} is odd and even.
-Anyway, a moment's reflection shows
+We are going to bound the rectangles by an integral, where we have to split the cases that \m {N_H} is odd and even.
 %
@@
 %
-Since the value of \m {s} is at our disposal, we try
+Since the value of \m {s} is at our disposal, we choose
 %
@@
 
-If we set that
+If we further choose that
 \DispNum {S:S:Ls:s2} {

### 2020-12-19 treatise/3_2_design_of_beamformers.tex
Chap 3, 4: Slight rev

--- 2020-11-10 treatise/3_2_design_of_beamformers.tex
@@
-\startsection [title={Design of Beamformers}]
+\startsection [title={Design of beamformers}]
 
@@
 
-Our plan is setting the four beamformers to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
-Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
+We want to set the four beamformers to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
+Let us simply set each entry of \m {\M {F} _B} to be i.i.d.\ normal random variables with mean \m {0}, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
 We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_B}}} follows Rayleigh distribution.
-\m {\RB {\M {W} _B ^\Tr} _{\SB {n_B, n_R}}} is set in an entirely analogous manner.
-In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane.
-\m {\RB {\M {W} _R ^\Tr} _{\SB {n_B, n_R}}} is set in an entirely analogous manner.
+\m {\RB {\M {W} _B ^\Tr} _{\SB {n_B, n_R}}} is set similarly.
+In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane, multiplied by a normalizing constant \m {\l_R >0}.
+\m {\RB {\M {W} _R ^\Tr} _{\SB {n_R, n_H}}} is set similarly.
 
-It turns out we have results that guarantee that both \m {\M {F} _B ^\Tr} and \m {\M {F} _R ^\Tr} have RIP, and same can be said of \m {\M {W} _B} and \m {\M {W} _R}.
-Consider a sparse \m {\V {u}} or unity norm, then we are sure that \m {\M {F} _R ^\Tr \V {u}} has almost unity norm.
-If, furthermore, \m {\M {F} _R ^\Tr \V {u}} is sparse, we see that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has almost unity norm, and the RIP of \m {\M{P}} also follows by construction.
+It turns out we have results that guarantee that both \m {\M {F} _B ^\Tr} and \m {\M {F} _R ^\Tr} have RIP, and the same can be said of \m {\M {W} _B} and \m {\M {W} _R}.
+Consider a sparse \m {\V {u}} with unity norm, then we are sure that \m {\M {F} _R ^\Tr \V {u}} has almost unity norm.
+If, furthermore, \m {\M {F} _R ^\Tr \V {u}} is sparse, we see that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has almost unity norm, and the RIP of \m {\M{P}} also follows.
 
-However, it is not clear that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, have RIP, nor that, \m {\M {P}}, the result of Kronecker product, has RIP.
+However, we cannot be sure that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, has RIP, nor do we know that \m {\M {P}}, the result of Kronecker product, has RIP.
 In fact, the statement seems to be false in general.
-But all is not lost.
+What now?
 Can we argue instead that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has similar norm with \m {\M {F} _R ^\Tr \V {u}}?
@@
 
-Use \m {\chi _{i,j}} to denote independent complex standard normal r.vs.
-We know
+Use \m {\chi _{i,j}} to denote independent complex standard normal random variables.
+It follows that
 %
@@
 %
-We want a large deviation result for i.i.d.\ sum of chi-square r.vs.
-To so so, we may apply Lemma 1 in Laurent and Massart \cite [LaM00] for equal weights.
-By some calculation, we have upper tail inequality, for \m {x > 0},
+We need a large deviation result for i.i.d.\ sum of chi-square random variables.
+To do so, we apply Lemma \m {1} in Laurent and Massart \cite [LaM00] for equal weights, with \m {x > 0} below.
+By some calculation, we have the upper tail inequality
 %
@@
 %
-And lower tail inequality
+and the lower tail inequality
 %
@@
 %
-With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for failure probability.
+With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for overall failure probability.
 
@@
 
-Here, we consult Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17].
-We need their Thm.4.5, which guarantees RIP w.r.t.\ \m {\d_s}, and probability lower bound, for DFT submatrix.
-The estimation they give involve is expressed in terms of big- \m {\O} and big- \m {O}, and since our methodology is 
-However, it can be seen that their argument allows precise constants, and they just did not spell out, which we briefly explain.
-They use Chernoff-Hoeffding bounds, but write the exponent in the form of \m {\Omega}.
-Starting in their Thm.2.2, we may substitute (say) \m {C \leftarrow 1/3} in place of their big- \m {\Omega}.
-The conclusions, their Thm.3.7 and Thm.4.5, may be changed accordingly.
-If modified with respect to our setting, the condition
+In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17], Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
+We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
+The conclusions, 
+Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
 %
@@
 %
-guarantees a failure probability \m {\d_s /N_H s}.
-We would like to drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \Rf {N:R:sd':NH}.
+Drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \Rf {N:R:sd':NH}, to get the statement below.
 
@@
 %
-Then \m {\M {F}_R} (respectively \m {\M {W} _R}) has \m {\d_s}-RIP for probability \m {p}, with
+Then \m {\M {F}_R} (respectively \m {\M {W} _R}) has \m {\d_s} RIP for probability \m {p}, with
 \DispNum {1:p:ex:d's} {
@@
 }
-Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {F}_B^\Tr \M {F}_B^\Tr} are \m {\d_s}-RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s}-RIP.
-However, it is doubtful to assume that the Kronecker product of two RIP matrices exhibit RIP.
+Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {F}_B^\Tr \M {F}_B^\Tr} are \m {\d_s} RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s} RIP.
+However, it is doubtful to assume that their Kronecker product still has RIP.
 
-We try to argue as thus.
+We argue as follows.
 If all angles \m {\th_l, \f_l} are exactly the multiples of \m {2 \pi/N_H}, then
@@
 where \m {\Rm {abs}} denotes entrywise absolute value.
-Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\Adj \M {K}^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s}-RIP too, we see
+Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\Adj \M {K}^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
 \DispNum {W:2:WB:d's} {
@@
 }
-Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s}-RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant \m {\V {g}} in accordance to the form of \Rf {H:H:l0:ql}.
+Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} according to the form \Rf {H:H:l0:ql}.
 

### 2020-12-19 treatise/3_3_bound_for_error_norm.tex
Rev contribution
Delete obsolete formulation on SOCP
Rev: chap 1, chap 4
Chap 3, 4: Slight rev

--- 2020-11-08 treatise/3_3_generalizing_the_dantzig_selector_bound.tex
@@
-\startsection [title={Bound for the error norm}]
+\startsection [title={Bound for expected error norm}]
+
 \startsubsection [title={Technical propositions in complex case}]
 
-The third and last part of our task is to plug in the almost-sparsity found in Section 3.1, and the failure probability found in Section 3.2.
+The third and last part of our task is to plug in the almost-sparsity found in Section \m {3.1}, and the failure probability found in Section \m {3.2}.
 Set for short
@@
 %
-And we seek to bound \m {\VNm {\V {d}} _2}.
-To do so, we argue that \m {\V {g}} can be seen as sparse, and for that purpose we generously bound \m {\d_{S}} by \m {1}.
-As shall be seen, it suffices to set
+To bound \m {\VNm {\V {d}} _2}, we illustrate that \m {\V {g}} can be seen as sparse, and for that purpose we generously bound \m {\d_{S}} by \m {1}.
+We shall see below that it suffices to set
 %
@@
 %
-The propositions below are taken from \cite [CaT07] and modified slightly in accordance to our settings, besides the generalization to complex vectors.
+The propositions below are taken from \cite [CaT07] and modified slightly in accordance to our settings, in addition to the generalization to complex vectors.
 %
@@
 
-To show this, apply triangle inequality respectively on \m {\MS {A}} and \m {\MS {C}}, and recall that \m {\V {g} =\V {g} _{\SB{\MS {A}}}},
+To show this, apply triangle inequality respectively on \m {\MS {A}} and \m {\MS {C}}, and recall that \m {\V {g} \eqsim \V {g} _{\SB{\MS {A}}}},
 %
@@
 {
-If \m {\M {P}} is \m {\d_S}-RIP, then it holds that
+If \m {\M {P}} has \m {\d_S} RIP, then it holds that
 %
@@
 
-Lastly, the following two propositions are taken from \cite [CaT07], Lemma 1.
-The generalization from real vector spaces to complex spaces is trivial.
-One of the quoted propositions reads
+Lastly, the following two propositions are taken from \cite [CaT07], Lemma \m {1}.
+The generalization from real vector spaces to complex spaces is obvious.
+The first quoted propositions reads
 %
@@
 
-The other quoted proposition is
+The second quoted proposition reads
 %
@@
 }
-And it remains to relate \m {\d_{2S}} to \m {\d_{S}}.
-By triangle inequality, by Jensen inequality,
-\DispNum {Q:x:Qx:x2} {
-\NC \VNm {Q' \RB {\V {x}_1 + \V {x}_2}}
-%
-\leq \NC \VNm {Q' \V {x}_1}
-+ \VNm {Q' \V {x}_2} \NR
-%
-\NC \leq \NC \RB {1 + \d _{s'}} \RB {\VNm {\V {x}_1} + \VNm {\V {x}_2}} \NR
-%
-\NC \leq \NC \RB {1 + \d _{s'}} \D \R{2} \VNm {\V {x}_1 + \V {x}_2} \NR
-}
-Therefore
-\DispNum {d:s:2s:2s} {
-\NC \d_{2s'}
-\leq \NC \R {2} \d_{s'} \NR
-}
-By the same token,
+We also make the assumption
 %
@@
 {
-If \m {\M {Q}'} has \m {\d_{s'}}-RIP, then, for \m {M=1,2,3,\dots} so that \m {\d _{Ms'}} is meaningful,
+If \m {\M {Q}'} has \m {\d_{s'}} RIP, then, for \m {M=1,2,3,\dots} for which \m {\d _{Ms'}} is meaningful,
 %
@@
 {
-If \m {\M {P}} is \m {\d_S}-RIP,
+If \m {\M {P}} has \m {\d_S} RIP,
 %
@@
 \NC \VNm {\V {d}} _2
-\leq \NC \MS {O} \RB {\R {L} \R {\log N_H}^3} \NR
+\eqsim \NC \MS {O} \SB {\R {L} \R {\log N_H}^3} \NR
 }
@@
 \NC 1 -p
-=\NC \MS {O} \SB {N_H ^{-1/3}} \NR
+\eqsim \NC \MS {O} \SB {\Ss {e} ^{-N_B /12}} \NR
 }
@@
 
-We further investigate the four events of failure, as follows.
+We end this chapter by remarking on the four events of failure, as follows.
 Consider failure probabilities \m {q _{\Rm {iso}, B}}, \m {q _{\Rm {iso}, R}}, \m {q _{\Rm {no}}}, \m {q _{\Rm {sp}}}, respectively for restricted isometry, noise, sparsity.
@@
 }
-Quoting previous results \Rf {1:p:2e:s4}, \Rf {1:p:ex:d's}, \Rf {1:p:ex:d's}, and \Rf {1:p:NH:H2}, we make some approximation and set
+Quoting previous results \Rf {1:p:2e:s4}, \Rf {1:p:ex:d's}, \Rf {d:1:dA:C1}, and \Rf {1:p:NH:H2}, we make some approximation and set
 \DispNum {q:B:2e:Lp'} {
@@
 %
-If we provide the design values
+If we provide the ideal values
 \DispNum {N:B:4l:H2} {
@@
 %
-\NC \lesssim \NC q _{\Rm {iso}, B} \NR
+\NC \lesssim \NC q _{\Rm {iso}, R} \NR
 %
-\NC \eqsim \NC q _{\Rm {iso}, R} \NR
+\NC \eqsim \NC q _{\Rm {iso}, B} \NR
 }
@@
 \NC q
-\eqsim \NC 2 N_H ^{-1/3} \NR
+\eqsim \NC 2 \Ss {e} ^{-N_B /12} \NR
 }

### 2020-12-31 treatise-context/1_introduction.tex
Create pdflatex version

--- 2020-12-19 treatise/1_introduction.tex
@@
 They proposed a beamformer shown to be optimal, jointly designed on both ends by a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
-Is the approximated design still optimal, or do the angles of sensing matrix become less accurate?
+Is the approximated design still optimal, or are the angles of sensing matrix not sufficiently precise?
 
@@
 In chapter 4, we remark that DS can be cast as a linear program, for which more efficient algorithms exist.
-Numerical results show that in our problem setting, DS can be superior to other methods, but costs higher complexity.
+Numerical results show that in our problem configuration, DS is superior to other methods.
+Indeed, DS is much more accurate than the least square, and both OMP and Lasso often fails.
 

### 2020-12-31 treatise-context/3_3_bound_for_error_norm.tex
Create pdflatex version

--- 2020-12-19 treatise/3_3_bound_for_error_norm.tex
@@
 \leq \NC \VNm {\V {d} _{\SB{\MS {A}}}} _1
-+2\VNm {\V {g} _{\SB{\MS {C}}}} _1 \NR
++\VNm {\V {g} _{\SB{\MS {C}}}} _1 \NR
 }
@@
 
-To show this, apply triangle inequality respectively on \m {\MS {A}} and \m {\MS {C}}, and recall that \m {\V {g} \eqsim \V {g} _{\SB{\MS {A}}}},
+To show this, apply triangle inequality respectively on \m {\MS {A}} and \m {\MS {C}},
 %
@@
 
-To show this, we would like to bound \m {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}}, which observes standard normal.
+To show this, by definition,
+%
+\DispNum {z:y:Pg:ny} {
+\NC \IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_h}}}
+= \NC \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \NR
+%
+\NC = \NC \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} \NR
+}
+%
+On one hand, \m {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}} observes standard normal.
 Recall the tail bound for \m {Q} function
@@
 %
-Now, by definition
-%
-\DispNum {z:y:Pg:ny} {
-\NC \IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_h}}}
-= \NC \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \NR
-%
-\NC = \NC \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} \NR
-}
-%
-By construction
+On the other hand, by construction
 %
@@
 }
-%
-By triangle inequality, together with \Rf {Q:h:1N:Nh} and \Rf {P:g:Py:Nh}, we obtain the desired result.
+
+Now, by triangle inequality, together with \Rf {Q:h:1N:Nh} and \Rf {P:g:Py:Nh}, we obtain the desired result.
 %
@@
 \NC \VNm {\M {P} _{\SB {:,n_h}}^\Adj \M {P} \V {d}} _\infty
-\leq \NC \VNm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}} _\infty
+\leq \NC \Nm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}}
 + \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_h}}} \NR
@@
 }
-We also make the assumption
-%
-\Result
-{Proposition}
-{
-If \m {\M {Q}'} has \m {\d_{s'}} RIP, then, for \m {M=1,2,3,\dots} for which \m {\d _{Ms'}} is meaningful,
-%
-\DispNum {d:s:Md':d's} {
-\NC \d_{Ms'}
-\leq \NC \R {M} \d_{s'} \NR
-}
-}
-%
-In particular,
+
+We also make the approximation that
 %
@@
 }
-%
-To show this, simplify the expression of \m {\VNm {\V {d} _{\SB{\MS {AB}}}} _2} in \Rf {d:2:11:C1} and \m {\VNm {\V {d} _{\SB{\MS {C}}}} _1} in \Rf {d:1:dA:C1}, and substitute rough numbers.
-By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P:d:4N:Nh},
+
+To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P:d:4N:Nh},
 %
@@
 %
-And \Rf {a:2:4N:NH} gives, after arrangement,
-%
-\DispNum {d:A1:16:H2} {
-\NC \VNm {\V {d} _{\SB{\MS {A}}}} _1
-%
-\leq \NC 1.64 L \R {\log N_H}^3 +0.951 L \RB {\log N_H}^2 \NR
-}
-%
-Then, substituting \Rf {g:C:4p':NH} and \Rf {d:A1:16:H2} above into \Rf {d:1:dA:C1}, we get
+Then, substituting \Rf {g:C:4p':NH} and \Rf {d:1:Sd:C1} above into \Rf {d:1:dA:C1}, we get
 \DispNum {d:C1:16:H2} {
@@
 }
-%
-And \Rf {d:2:11:C1} becomes
+
+Now \Rf {d:2:11:C1} becomes
 %
@@
 }
-We are now in a position to bound \m {\VNm {d} _2}, again by \Rf {d:2:dA:C1}, and plugging in \Rf {d:2:16:H3} and \Rf {d:C1:16:H2}, giving
+and we are ready to estimate \m {\VNm {d} _2}, again by \Rf {d:2:dA:C1}, and plugging in \Rf {d:2:16:H3} and \Rf {d:C1:16:H2}, giving
 \DispNum {d:2:42:NH} {
@@
 }
-Quoting previous results \Rf {1:p:2e:s4}, \Rf {1:p:ex:d's}, \Rf {d:1:dA:C1}, and \Rf {1:p:NH:H2}, we make some approximation and set
+Quoting previous results \Rf {1:p:2e:s4}, \Rf {1:p:ex:d's}, \Rf {1:p:NH:H2}, and \Rf {1:p:1N:H3}, we make some approximation and set
 \DispNum {q:B:2e:Lp'} {

### 2020-12-31 treatise-context/4_simulation.tex
Create pdflatex version

--- 2020-12-18 treatise/4_simulation.tex
@@
 
-\startsubsection [title={Some Notation}]
+\startsubsection [title={Some notation}]
 
@@
 
-\startsubsection [title={Plots of Assorted Methods}]
+\startsubsection [title={Plots of assorted methods}]
 
@@
 
-The performance of OMP appears poor.
+The performance of OMP appears to be poor.
 In most cases, the estimation fails, and we have \m {\T {\chi}} close to the unity.
@@
 We are not sure either why \m {\T {\chi}} is an overestimation of \m {\chi} by several orders of magnitude.
-A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect, which remain to be investigated in the future.
+A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
 
-We end the discussion by showing two cases where DS works or fails, in figures 21 and 22.
+In figures 21 and 22, we reproduce two cases of success and failure of DS.
 In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.
@@
 
-\startsubsection [title={Asymtotic Analysis}]
+\startsubsection [title={Asymtotic analysis}]
 
@@
 
-\startsubsection [title={Runtime Statistics}]
+\startsubsection [title={Runtime statistics}]
 
@@
 
+However, note that we must be careful in giving meaningful comparison between compressive sensing algorithms, as they might work in different settings.
+DS requires a RIP linear transformation, and it works for noisy linear systems \cite [CaT07].
+Here, it is not easy to justify RIP rigorously, and a more feasible construction is even a research problem.
+OMP, on the other hand, requires only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], of which much is yet to be studied.
+All in all, we might say that on the whole, DS trades off low time- and space-complexity for high precision, and for OMP the opposite is true.
+
 \stopsubsection

### 2020-12-31 treatise-context/5_conclusion.tex
Create pdflatex version

--- 2020-12-18 treatise/5_conclusion.tex
@@
 
-We also remarked that DS may be cast into an linear program, which help reduce complexity.
-Simulation is done, and DS appears more accurate than all other methods, while costing higher complexity.
-However, much has to be investigated for more diverse parameters, and on a more powerful computer, for a definite conclusion.
-We are not sure about the best value of the threshold, and we also have to prevent CVXPY from giving overflowing values.
-Meanwhile, OMP and Lasso often fails, and we wonder whether they are really so bad, or we have not followed the literature correctly.
-
-Note that we must be careful in giving meaningful comparison between compressive sensing algorithms, as they might work in different settings.
-DS requires a RIP linear transformation, and it works for noisy linear systems \cite [CaT07]; here, it is not easy to justify RIP rigorously, and a more feasible construction is even a research problem.
-OMP, on the other hand, requires only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], but much of its property is yet to be studied.
-On the whole, DS trades off low time- and space-complexity for high precision, and for OMP the opposite is true.
+DS is cast into an linear program, which help reduce complexity.
+Simulation is done, and DS's performance is compared to OMP, Lasso, and LS, and we see that DS indeed outperforms other methods.
+Despite of its higher complexity, in the low noise scenario, DS can be \m {10} times more accurate, and the gain of spectral efficiency may justify its use.
 

### 2020-12-31 treatise-pdflatex/1_introduction.tex
Create pdflatex version

--- 2020-12-31 treatise-context/1_introduction.tex
@@
 
-Let us say the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
+Let us say the number of model parameters \m {N_p \in \mathbb {N}} is much larger than the number of measurements \m {N_m \in \mathbb {N}}, that is,
 %
@@
 %
-To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear system
+To start, consider \m {\V {x}, \V {x}' \in \mathbb {K} ^{N_p}} and \m {\M {Q} \in \mathbb {K} ^{N_m \D  N_p}}, and the linear system
 %
@@
 To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
-That is, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
+That is, if there is some \m {\mathscr {A} \subseteq \CB {0, \dots, N_p-1}} such that
 %
 \DispNum {x:A:x::x:} {
-\NC \V {x} _{\SB {\MS {A}}}
+\NC \V {x} _{\SB {\mathscr {A}}}
 =\NC \V {x} \NR
@@
 \DispNum {A:A:s::s:} {
-\NC \Nm {\MS {A}} \leq \NC s. \NR
+\NC \Nm {\mathscr {A}} \leq \NC s. \NR
 }
@@
 We introduce some conventions.
-For \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}}, denote
+For \m {\mathscr {A} \subseteq \CB {0, \dots, N_p-1}}, denote
 %
 \Disp {
-\NC \V {x}  _{\SB {\MS {A}}}
-=\NC \sum _{i \in \MS {A}} \V {v} \V {u} _{i} \NR
+\NC \V {x}  _{\SB {\mathscr {A}}}
+=\NC \sum _{i \in \mathscr {A}} \V {v} \V {u} _{i} \NR
 %
-\NC \M {Q}  _{\SB {\MS {A}}}
-=\NC \sum _{i \in \MS {A}} \M {Q} _{\SB {:,i}} \NR
+\NC \M {Q}  _{\SB {\mathscr {A}}}
+=\NC \sum _{i \in \mathscr {A}} \M {Q} _{\SB {:,i}} \NR
 }
 %
-That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MS {A}}.
+That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\mathscr {A}}.
 
@@
 \startitemize[n]
-\item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}.
+\item Input \m {\M {Q} \in \mathbb {R} ^{N_m \D N_p}} and \m {\V {y} \in \mathbb {R} ^{N_m}}.
 %
@@
 \DispNum {h:h:mi:yg'} {
-\NC \Hat {\V {h}}
-\LA \NC \startcases
+\NC \hat {\V {h}}
+\leftarrow \NC \startcases
 \NC \Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
 %
-\NC \Rm {subject} \; \Rm {to} \Q \MC \VNm {\M {Q}^\Adj \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
+\NC \mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {Q}^\dagger \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
 \stopcases \NR
 }
-\item Output \m {\Hat {\V {h}}}.
+\item Output \m {\hat {\V {h}}}.
 \stopitemize
@@
 %
-\item Input \m {\M {Q} \in \MB {R} ^{N_m \D N_p}} and \m {\V {y} \in \MB {R} ^{N_m}}, \m {\eta >0}.
+\item Input \m {\M {Q} \in \mathbb {R} ^{N_m \D N_p}} and \m {\V {y} \in \mathbb {R} ^{N_m}}, \m {\eta >0}.
 %
@@
 \NC \V {r}
-\LA \NC \V {y} \NR
+\leftarrow \NC \V {y} \NR
 %
 \NC S
-\LA \NC \varnothing \NR
+\leftarrow \NC \varnothing \NR
 }
 %
-\item Start the loop with counter \m {i \LA 1}.
+\item Start the loop with counter \m {i \leftarrow 1}.
 %
@@
 \NC n
-\LA \NC \underset {n' =0, \dots, N_p-1} {\Rm {argmax}}
+\leftarrow \NC \underset {n' =0, \dots, N_p-1} {\mathrm {argmax}}
 \Nm {\M {Q} _{\SB {:,n'}} \V {r}} \NR
@@
 %
-and append \m {S \LA S \cup {n}}.
+and append \m {S \leftarrow S \cup {n}}.
 %
@@
 \NC \M {Q} ^\ddagger
-\LA \NC \RB {\M {Q} _{\SB {S}} ^\Adj \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\Adj \NR
+\leftarrow \NC \RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \NR
 %
 \NC \V {r}
-\LA \NC \V {y} -\M {Q} _{\SB {S}} ^\Adj \M {Q} ^\ddagger \V {y} \NR
+\leftarrow \NC \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} \NR
 }
@@
 \DispNum {g:g:Qy:Qy} {
-\NC \Hat {\V {g}}
-\LA \NC \M {Q} ^\ddagger \V {y} \NR
+\NC \hat {\V {g}}
+\leftarrow \NC \M {Q} ^\ddagger \V {y} \NR
 }

### 2020-12-31 treatise-pdflatex/2_problem_setting.tex
Create pdflatex version

\startchapter [title={Problem setting}]

\startsection [title={Channel model}]

For simplicity we suppose uniform linear arrays, for which the response be modeled as thus,
%
\DispNum {a:y':CN:NH} {
\NC \V {a} \SB {\psi'}
= \NC \frac {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
\in \mathbb {C} ^ {N_H} \NR
}
%
where \m {\mathsf {e}} is the base of natural logarithm, and \m {\mathsf {i}} the imaginary unit.

And consider the virtual representation of the MIMO channel, as in Akdeniz et.\ al.\ \cite [ALS14],
%
\DispNum {H:H:l0:ql} {
\NC \M {H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l'}
\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l'}^\dagger \NR
}
%
The physical meaning of \m {\f_l'} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l'}, the \m {l}-th angle of arrival wave, and \m {d_{\mathrm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the arguments of \m {\V {a}}
%
\DispNum {f:l:2p:2p} {
\NC \f_l
= \NC 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
  \; \mathrm {Mod}\; \RB {2\pi} \NR
%
\NC \th_l
= \NC 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
  \; \mathrm {Mod}\; \RB {2\pi} \NR
}
%
to get a simpler form
%
\DispNum {H:H:l0:ql} {
\NC \M {H}
=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
\in \mathbb {C} ^{N_H \D N_H} \NR
}

\stopsection

\startsection [title={System model}]

\blank [big]
\externalfigure [system.png] [wfactor=fit, hfactor=fit]
\FigureCaption {Schematic diagram of the hybrid beamforming system we consider, based on Akdeniz et.\ al.\ \cite [ALS14].}
\blank [big]

We consider the hybrid beamforming at both transmitter and receiver ends, as shown in Figure 2.
Each end consists of both digital and analog precoders and combiners.
In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_B}} and analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D  N_R}}.
Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \mathbb {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \mathbb {C} ^{N_B \D  N_R}}.

Recall that analog precoders may only have values of unity magnitude,
%
\DispNum {F:R:1::R1} {
\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
= \NC 1, \NR
%
\NC \Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
= \NC 1, \NR
%
\NC n_H
= \NC 0, \dots N_H-1, \NR
%
\NC n_R
= \NC 0, \dots N_R-1 \NR
}
%
And we assume
%
\DispNum {N:H:NY:NY} {
\NC N_H \gg \NC N_R \NR
%
\NC N_R \gg \NC N_B \NR
}

Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
Let us introduce the effective channel
%
\DispNum {Y:Y:WB:BZ} {
\NC \M {Y}
:=\NC \M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
}
%
Our task then amounts to recovering \m {\M {H}}, and designing \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.

\stopsection

\startsection [title={Vectorization}]

We need several notations.
%
\Result
{Definition}
{
Define \m {\mathrm {vec} \SB {\M {A}} \in \mathbb {K} ^{N_1 \D N_2}} to be the vectorization of \m {\M {A} \in \mathbb {K} ^{N_1 \D  N_2}}.
Formally,
%
\DispNum {v:1:Am:N1} {
\NC \RB {\mathrm {vec} \SB {\M {A}}} _{\SB {m}}
=\NC \M {A} _{\SB {m\; \mathrm {Mod}\; N_1, \Fl {m/N_1 }}} \NR
}
%
The bijection is obvious, and we define \m {\mathrm {vec} ^{-1}} so that
%
\DispNum {v:x:x::x:} {
\NC \mathrm {vec} ^{-1} \SB {\mathrm {vec} \SB {x}}
=\NC x \NR
}
}

\Result
{Definition}
{
For \m {\M {A} \in \mathbb {K} ^{N_1 \D  N_2}} and \m {\M {B} \in \mathbb {K} ^{N_3 \D N_4}}, define the Kronecker product \m {\M {A} \otimes \M {B} \in \mathbb {K} ^{N_1 N_3 \D N_2 N_4}} by
%
\DispNum {A:2:Am:N4} {
\NC \NC \RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \NR
%
\NC =\NC \M {A} _{\SB {\Fl {m_1/N_3 }, \Fl {m_2/N_4 }}}
\M {B} _{\SB {m_1\; \mathrm {Mod}\; N_3, m_2\; \mathrm {Mod}\; N_4}} \NR
}
}

The following relation, which is straightforward from definitions, is going be used below.
\Result
{Proposition}
{
Suppose \m {\M {A} \in \mathbb {K} ^{N_1 \D  N_2}, \M {X} \in \mathbb {K} ^{N_2 \D N_3}, \M {B} \in \mathbb {K} ^{N_3 \D N_4}},
Then
%
\DispNum {v:B:BA:cX} {
\NC \mathrm {vec} \SB {\M {A}\M {X}\M {B}}
= \NC \RB {\M {B}^\intercal \otimes \M {A}} \mathrm {vec} \SB {\M {X}} \NR
}
}

It is more appealing to write
%
\DispNum {h:h:ve:Nh} {
\NC \V {h}
:= \NC \mathrm {vec} \SB {\M {H}}
\in \mathbb {C} ^{N_H^2} \NR
%
\NC \V {y}
:= \NC \mathrm {vec} \SB {\M {Y}}
\in \mathbb {C} ^{N_B^2} \NR
%
\NC \V {z}
:= \NC \mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
\in \mathbb {C} ^{N_B^2} \NR
%
\NC \M {Q}
:= \NC \RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
\in \mathbb {C} ^{N_B^2 \D N_H^2} \NR
}
%
to formulate the problem as a linear system:
%
\DispNum {y:y:Qh:hz} {
\NC \V {y}
=\NC \M {Q} \V {h} +\V {z} \NR
}
%
At this stage, we intend to apply DS, but there is no guarantee that \m {\V {h}} must be sparse.

\stopsection

\startsection [title={Spacial frequency domain}]

Denote the discrete Fourier transform matrix to be \m {\M {K}},
%
\DispNum {K:K:CN:H1} {
\NC \M {K} \in  \NC \mathbb {C} ^{N_H \D N_H} \NR
%
\NC \M {K} _{\SB {n_1, n_2}}
= \NC \frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \NR
%
\NC \quad n_1, n_2
= \NC 0, 1, \dots, N_H-1 \NR
}
%
Recall that we have
%
\DispNum {K:K:I:::I} {
\NC \M {K}^\dagger \M {K}
= \NC \M {I} \NR
}
%
If we write
%
\DispNum {G:G:KH:HK} {
\NC \M {G}
=\NC \M {K}^\dagger \M {H} \M {K} \NR
}
%
then \m {\M {G}} can be interpreted as spatial frequency domain representation of \m {\M {H}}.
%
\DispNum {Y:Y:WB:NY} {
\NC \M {Y}
=\NC \M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\dagger \M {F} _R \M {F} _B
+\M {W} _B \M {W} _R \M {Z}
\in \mathbb {C} ^{N_B \D N_B} \NR
}
%
If we are sure that \m {\M {G}} is sparse, then we recover \m {\M {G}} instead.
Set for brevity
%
\DispNum {P:P:FB:Nh} {
\NC \M {P}
:=\NC \RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
\in \mathbb {C} ^{N_B^2 \D N_H^2} \NR
}
%
and
%
\DispNum {g:g:ve:Nh} {
\NC \V {g}
:= \NC \mathrm {vec} \SB {\M {G}}
\in \mathbb {C} ^ {N_H \D N_H} \NR
}
%
accordingly
%
\DispNum {y:y:Pg:gz} {
\NC \V {y}
=\NC \M {P} \V {g} +\V {z} \NR
}

\stopsection
\startsection [title={Proposed method}]

Our plan becomes now

\Result
{Algorithm}
{
\startitemize[n]
%
\item Let \m {\g_{\mathrm {DS}} \geq 0} be given.
%
\item Input \m {\M {F} _B \in \NC \mathbb {C} ^{N_R \D N_B}},
\m {\M {F} _R \in \NC \mathbb {C} ^{N_H \D N_R}},
\m {\M {W} _R \in \NC \mathbb {C} ^{N_R \D N_H}},
\m {\M {W} _B \in \NC \mathbb {C} ^{N_B \D N_R}},
and \m {\M {Y} \in \NC \mathbb {C} ^{N_B \D N_B}}.
%
\item Find \m {\M {P} \in \mathbb {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \mathbb {C} ^{N_H^2}} as in above.
%
\item Compute the convex program
%
\DispNum {g:g:mi:DS} {
\NC \hat {\V {g}}
\leftarrow \NC \startcases
\NC \Min {\V {g}' \in \mathbb {C} ^{N_H^2}}  \MC \VNm {\V {g}'} _1 \NR
%
\NC \mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \NR
\stopcases \NR
}
%
\item Convert \m {\hat {\V {g}}} back to the space domain, namely
%
\DispNum {G:G:ve:1g} {
\NC \hat {\M {G}}
\leftarrow \NC \mathrm {vec}^{-1} \SB {\hat {\V {g}}} \NR
}
%
\item Recover the estimated \m {\hat {\M {H}}}, as
%
\DispNum {H:H:KG:GK} {
\NC \hat {\M {H}}
\leftarrow \NC \M {K} \hat {\M {G}} \M {K}^\dagger \NR
}
%
\item Output \m {\hat {\M {H}}}.
%
\stopitemize
}

\stopsection
\stopchapter

### 2020-12-31 treatise-pdflatex/3_1_sparsity_of_channel.tex
Create pdflatex version

--- 2020-12-19 treatise/3_1_sparsity_of_channel.tex
@@
 Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity level \m {S} be fixed.
-Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MS {A}}}}, the largest-magnitude \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MS {B}}}} the next \m {s} largest-magnitude components of \m {\V {g}}, and \m {\V {g} _{\SB{\MS {C}}}} are the components complement to \m {\V {g} _{\SB{\MS {A}}}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MS {A}}} =\IP {0,0,-4,0,8}}, \m {\V {g} _{\SB{\MS {B}}} =\IP {0,3,0,2,0}}, and \m {\V {g} _{\SB{\MS {C}}} =\IP {-1,3,0,2,0}}.
-In this section, the subscripts \m {\MS {A}, \MS {B}, \MS {C}} will bear analogous meaning.
+Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\mathscr {A}}}}, the largest-magnitude \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\mathscr {B}}}} the next \m {s} largest-magnitude components of \m {\V {g}}, and \m {\V {g} _{\SB{\mathscr {C}}}} are the components complement to \m {\V {g} _{\SB{\mathscr {A}}}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\mathscr {A}}} =\IP {0,0,-4,0,8}}, \m {\V {g} _{\SB{\mathscr {B}}} =\IP {0,3,0,2,0}}, and \m {\V {g} _{\SB{\mathscr {C}}} =\IP {-1,3,0,2,0}}.
+In this section, the subscripts \m {\mathscr {A}, \mathscr {B}, \mathscr {C}} will bear analogous meaning.
 
-We hope that \m {\VNm {\V {g} _{\SB{\MS {C}}}} _1} is small.
+We hope that \m {\VNm {\V {g} _{\SB{\mathscr {C}}}} _1} is small.
 If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
 Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
-We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity level \m {s} different from \m {S}.
+We define, similarly, \m {\V {a} _{\SB{\mathscr {A}}}} and \m {\V {a} _{\SB{\mathscr {C}}}}, with sparsity level \m {s} different from \m {S}.
 If \m {N_H} is large, we may forget for a moment that \m {s} is an integer.
@@
 \DispNum {a:2:Ka:22} {
-\NC \VNm {\V {a} \SB {\f} _{\SB{\MS {C}}}} _2 ^2
-=\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB{\MS {C}}}} _2 ^2 \NR
+\NC \VNm {\V {a} \SB {\f} _{\SB{\mathscr {C}}}} _2 ^2
+=\NC \VNm {\RB {\M {K}^\dagger \V {a} \SB {\f}} _{\SB{\mathscr {C}}}} _2 ^2 \NR
 }
@@
 :=\NC \RB {
-   \f \; \Rm {Mod}\; \F {2\pi} {N_H}
-   + \RB {\F {2 n_H} {N_H} + 1} \pi
+   \f \; \mathrm {Mod}\; \frac {2\pi} {N_H}
+   + \RB {\frac {2 n_H} {N_H} + 1} \pi
 } \;
-\Rm {Mod}\; \RB {2\pi}
+\mathrm {Mod}\; \RB {2\pi}
 - \pi \NR
@@
 \NC D \SB {\psi'}
-:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
+:= \NC \sum_{n_H=0}^{N_H-1} \mathsf {e}^{i n_H \psi'} \NR
 }
@@
 \NC \V {b} \SB {\f}
-=\NC \M {K}^\Adj \V {a} \SB {\f} \NR
+=\NC \M {K}^\dagger \V {a} \SB {\f} \NR
 }
@@
 \NC \V {b} \SB {\f} _{\SB {n_H}}
-=\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
+=\NC \frac {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
 }
@@
 \DispNum {x:6:si:nx} {
-\NC \Nm {x - \F {x^3} {6}}
+\NC \Nm {x - \frac {x^3} {6}}
 \leq \NC \Nm {\sin x}. \NR
@@
 \NC \Nm {D \SB {\psi'}}
-= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
+= \NC \frac {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
 %
@@
 %
-\NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \NR
+\NC := \NC \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \NR
 %
@@
 \DispNum {b:1:1N:C1} {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
-\leq \NC \F {1} {N_H}
+\NC \VNm {\V {b} \SB {\f} _{\SB{\mathscr {C}}}} _1
+\leq \NC \frac {1} {N_H}
 \VNm {
@@
       \V {u} _{n_H'}
-} _{\SB{\MS {C}}}
+} _{\SB{\mathscr {C}}}
 } _1
@@
 \DispNum {b:1:1N:NH} {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
-\leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
+\NC \VNm {\V {b} \SB {\f} _{\SB{\mathscr {C}}}} _1
+\leq \NC \frac {1} {N_H} \D \frac {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
 %
-\NC = \NC \F {48} {N_H \pi^3}
-\int _{s /N_H} ^1 \F {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
+\NC = \NC \frac {48} {N_H \pi^3}
+\int _{s /N_H} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
 %
-\NC =\NC \F {1} {\pi} \log \F {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \NR
+\NC =\NC \frac {1} {\pi} \log \frac {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \NR
 %
-\NC \eqsim \NC \F {2} {\pi} \RB {\log N_H - \log s} \NR
+\NC \eqsim \NC \frac {2} {\pi} \RB {\log N_H - \log s} \NR
 %
-\NC \leq \NC \F {2} {\pi} \log N_H \NR
+\NC \leq \NC \frac {2} {\pi} \log N_H \NR
 }
@@
 \DispNum {a:2:4N:NH} {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
-\leq \NC \F {2} {\pi} \log N_H \NR
+\NC \VNm {\V {b} \SB {\f} _{\SB{\mathscr {C}}}} _1
+\leq \NC \frac {2} {\pi} \log N_H \NR
 }
@@
 \DispNum {g:1:l0:a'1} {
-\NC \VNm {\V {g} _{\SB{\MS {C}}}} _1
+\NC \VNm {\V {g} _{\SB{\mathscr {C}}}} _1
 \leq \NC
 \sum _{l=0} ^{L-1} \Nm {\a_l}
-\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _1
-\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _1 \NR
+\VNm {\V {b} \SB {\f_l} _{\SB{\mathscr {C}}}} _1
+\VNm {\V {b} \SB {\th_l} _{\SB{\mathscr {C}}}} _1 \NR
 %
 \NC \leq \NC
-\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _1
-\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _1
+\VNm {\V {b} \SB {\f_l} _{\SB{\mathscr {C}}}} _1
+\VNm {\V {b} \SB {\th_l} _{\SB{\mathscr {C}}}} _1
 \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
@@
 \NC \leq \NC
-\F {4} {\pi^2} L \RB {\log N_H}^2 \D
-\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
+\frac {4} {\pi^2} L \RB {\log N_H}^2 \D
+\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
 }
@@
 \DispNum {E:1:2p':2p'} {
-\NC \MB {E} \SB {\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
+\NC \mathbb {E} \SB {\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
 =\NC \F{\R {2}} {\R {\pi}} \NR
@@
 \DispNum {P:p':2e:3p'} {
-\NC \MB {P} \SB {
-   \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
-   \geq \F {4 \R{2}} {\R {\pi}}
+\NC \mathbb {P} \SB {
+   \frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
+   \geq \frac {4 \R{2}} {\R {\pi}}
 }
-\leq \NC 2 \exp \SB {- \F {9L} {\pi}} \NR
+\leq \NC 2 \exp \SB {- \frac {9L} {\pi}} \NR
 }
@@
 \DispNum {g:2:12:43} {
-\NC \F {\VNm {\M {g} _{\SB{\MS {C}}}} _1} {\RB {\log N_H}^2}
-\leq \NC \F {12 \R{2}} {\pi ^{5/2}}
-\leq \F {4} {3}. \NR
+\NC \frac {\VNm {\M {g} _{\SB{\mathscr {C}}}} _1} {\RB {\log N_H}^2}
+\leq \NC \frac {12 \R{2}} {\pi ^{5/2}}
+\leq \frac {4} {3}. \NR
 }
@@
 {
-et \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in \Rf {g:g:ve:Nh}.
+Let \m {\V {g} \in \mathbb {C} ^{N_H^2}} be defined as in \Rf {g:g:ve:Nh}.
 Then the bound
@@
 \DispNum {g:C:4p':NH} {
-\NC \VNm {\M {g} _{\SB{\MS {C}}}} _1
-\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
+\NC \VNm {\M {g} _{\SB{\mathscr {C}}}} _1
+\leq \NC \frac {4} {3} \RB {\log N_H}^2 \NR
 }
@@
 \NC 1 -p
-\leq \NC 2 \exp \SB {- \F {9L} {\pi}} \NR
+\leq \NC 2 \exp \SB {- \frac {9L} {\pi}} \NR
 }

### 2020-12-31 treatise-pdflatex/3_2_design_of_beamformers.tex
Create pdflatex version

--- 2020-12-19 treatise/3_2_design_of_beamformers.tex
@@
 It turns out we have results that guarantee that both \m {\M {F} _B ^\Tr} and \m {\M {F} _R ^\Tr} have RIP, and the same can be said of \m {\M {W} _B} and \m {\M {W} _R}.
-Consider a sparse \m {\V {u}} with unity norm, then we are sure that \m {\M {F} _R ^\Tr \V {u}} has almost unity norm.
-If, furthermore, \m {\M {F} _R ^\Tr \V {u}} is sparse, we see that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has almost unity norm, and the RIP of \m {\M{P}} also follows.
+Consider a sparse \m {\V {u}} with unity norm, then we are sure that \m {\M {F} _R ^\intercal \V {u}} has almost unity norm.
+If, furthermore, \m {\M {F} _R ^\intercal \V {u}} is sparse, we see that \m {\M {F} _B ^\intercal \M {F} _R ^\intercal \V {u}} has almost unity norm, and the RIP of \m {\M{P}} also follows.
 
-However, we cannot be sure that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, has RIP, nor do we know that \m {\M {P}}, the result of Kronecker product, has RIP.
+However, we cannot be sure that \m {\M {F} _B ^\intercal \M {F} _R ^\Tr}, the product of two RIP matrices, has RIP, nor do we know that \m {\M {P}}, the result of Kronecker product, has RIP.
 In fact, the statement seems to be false in general.
 What now?
-Can we argue instead that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has similar norm with \m {\M {F} _R ^\Tr \V {u}}?
+Can we argue instead that \m {\M {F} _B ^\intercal \M {F} _R ^\intercal \V {u}} has similar norm with \m {\M {F} _R ^\intercal \V {u}}?
 
@@
 =\NC \R {
-   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \F {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
+   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
 }
@@
 \DispNum {P:x:ex:ex} {
-\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_B}} + \F {2x} {N_B}}
-\leq \NC \Ss {e} ^{-x} \NR
+\NC \mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_B}} + \frac {2x} {N_B}}
+\leq \NC \mathsf {e} ^{-x} \NR
 }
@@
 \DispNum {P:x:ex:ex!} {
-\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_B}}}
-\leq \NC \Ss {e} ^{-x} \NR
+\NC \mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_B}}}
+\leq \NC \mathsf {e} ^{-x} \NR
 }
@@
 \NC 1 -p
-\leq \NC 2 \Ss {e} ^{-N_B \R {\d_s} /4} \NR
+\leq \NC 2 \mathsf {e} ^{-N_B \R {\d_s} /4} \NR
 }
@@
 \NC N_R
-\geq \NC \F {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
+\geq \NC \frac {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
 }
@@
 \NC N_R
-\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
+\geq \NC \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
 }
@@
 \NC 1 -p
-\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
+\leq \NC \RB {\frac {\d_s} {N_H s}} ^{1/3} \NR
 }
@@
 \NC \VNm {P} _2
-=\NC \VNm {\M {F}_B^\Tr \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \NR
+=\NC \VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \NR
 }
-Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {F}_B^\Tr \M {F}_B^\Tr} are \m {\d_s} RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s} RIP.
+Since both \m {\M {F}_B^\intercal \M {F}_B^\Tr} and \m {\M {F}_B^\intercal \M {F}_B^\Tr} are \m {\d_s} RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s} RIP.
 However, it is doubtful to assume that their Kronecker product still has RIP.
@@
 \NC \M {G}
-=\NC \M {U} \Rm {diag} \SB {\V {d}'} \M {U} ^\Adj \NR
+=\NC \M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger \NR
 }
@@
 \NC \VNm {\M {G}} _2
-\NC =\VNm {\Rm {abs} \SB {\V {g}}} _2 \NR
+\NC =\VNm {\mathrm {abs} \SB {\V {g}}} _2 \NR
 }
-where \m {\Rm {abs}} denotes entrywise absolute value.
-Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\Adj \M {K}^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
+where \m {\mathrm {abs}} denotes entrywise absolute value.
+Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\dagger \M {K}^\dagger \M {F} _R^\dagger \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
 \DispNum {W:2:WB:d's} {
@@
    \M {W} _B \M {W} _R \M {K} \M {U} \D
-   \Rm {diag} \SB {\Rm {abs} \SB {\V {d}'}} \D
-   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
+   \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
+   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \NR
 %
@@
    \M {W} _B \M {W} _R \M {K} \M {U}
-   \R {\Rm {abs} \SB {\V {d}'}} \D
-   \R {\Rm {abs} \SB {\V {d}'}}
-   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
+   \R {\mathrm {abs} \SB {\V {d}'}} \D
+   \R {\mathrm {abs} \SB {\V {d}'}}
+   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \NR
 %
@@
    \M {W} _B \M {W} _R \M {K} \M {U}
-   \R {\Rm {abs} \SB {\V {d}'}}} _2 \D
-   \VNm {\M {F} _B ^\Adj \M {F} _R ^\Adj \M {K} \M {U}
-   \R {\Rm {abs} \SB {\V {d}'}}} _2 \NR
+   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \D
+   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} \M {U}
+   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \NR
 %

### 2020-12-31 treatise-pdflatex/3_3_bound_for_error_norm.tex
Create pdflatex version

--- 2020-12-31 treatise-context/3_3_bound_for_error_norm.tex
@@
 \NC \V {d} 
-= \NC \Hat {\V {g}} - \V {g} \NR
+= \NC \hat {\V {g}} - \V {g} \NR
 }
@@
 \DispNum {d:1:dA:C1} {
-\NC \VNm {\V {d} _{\SB{\MS {C}}}} _1
-\leq \NC \VNm {\V {d} _{\SB{\MS {A}}}} _1
-+\VNm {\V {g} _{\SB{\MS {C}}}} _1 \NR
+\NC \VNm {\V {d} _{\SB{\mathscr {C}}}} _1
+\leq \NC \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
++\VNm {\V {g} _{\SB{\mathscr {C}}}} _1 \NR
 }
@@
 
-To show this, apply triangle inequality respectively on \m {\MS {A}} and \m {\MS {C}},
+To show this, apply triangle inequality respectively on \m {\mathscr {A}} and \m {\mathscr {C}},
 %
@@
 \NC \VNm {\V {g}} _1
-- \VNm {\V {d} _{\SB{\MS {A}}}} _1
-+ \VNm {\V {d} _{\SB{\MS {C}}}} _1
-- \VNm {\V {g} _{\SB{\MS {C}}}} _1
+- \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
++ \VNm {\V {d} _{\SB{\mathscr {C}}}} _1
+- \VNm {\V {g} _{\SB{\mathscr {C}}}} _1
 \leq \NC \VNm {\V {g} + \V {d}} _1 \NR
@@
 \DispNum {P:d:4N:Nh} {
-\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
+\NC \VNm {\M {P}^\dagger \M {P} \V {d}} _\infty
 \leq \NC  4 \R {2 \log N_H} \NR
@@
 \NC Q\SB {x'}
-\leq \NC \F {1} {2} \Ss {e}^{-x'^2 /2} \NR
+\leq \NC \frac {1} {2} \mathsf {e}^{-x'^2 /2} \NR
 }
@@
 \NC Q\SB {2 \R {\log N_H}}
-=\NC \F {1} {2 N_H^2}. \NR
+=\NC \frac {1} {2 N_H^2}. \NR
 }
@@
 \DispNum {P:g:Py:Nh} {
-\NC \VNm {\M {P} _{\SB {:,n_h}}^\Adj \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
-\leq \NC \VNm {\M {P}^\Adj \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \NR
+\NC \VNm {\M {P} _{\SB {:,n_h}}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
+\leq \NC \VNm {\M {P}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \NR
 %
@@
 \DispNum {P:d:zP:Nh} {
-\NC \VNm {\M {P} _{\SB {:,n_h}}^\Adj \M {P} \V {d}} _\infty
+\NC \VNm {\M {P} _{\SB {:,n_h}}^\dagger \M {P} \V {d}} _\infty
 \leq \NC \Nm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}}
@@
 \NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\SB {\MS {AB}}}} _2^2 + \F {1} {S} \VNm {\V {d} _{\SB{\MS {C}}}} _1^2 \NR
+\leq \NC \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2^2 + \frac {1} {S} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1^2 \NR
 }
@@
 \NC \VNm {\V {d}} _2
-\leq \NC \VNm {\V {d} _{\SB {\MS {AB}}}} _2 + \F {1} {\R {S}} \VNm {\V {d} _{\SB{\MS {C}}}} _1 \NR
+\leq \NC \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \NR
 }
@@
 \DispNum {d:2:11:C1} {
-\NC \VNm {\V {d} _{\SB{\MS {AB}}}} _2
-\leq \NC \F {1} {1- \d_{2S}} \VNm {P _{\SB {\MS {AB}}}^\Tr P d} _2
-+ \F {\T {\d}_{S, 2S}} {\RB {1- \d_{2S}} \R {S}} \VNm {d_{\SB{\MS {C}}}} _1 \NR
+\NC \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
+\leq \NC \frac {1} {1- \d_{2S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
++ \frac {\tilde {\d}_{S, 2S}} {\RB {1- \d_{2S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \NR
 }
 %
-Here \m {\T {\d} _{s_1, s_2}} denotes the \m {s_1,s_2}-restricted isometry constant, and is defined in \cite [Can05] (which uses \m {\th}), as follows.
+Here \m {\tilde {\d} _{s_1, s_2}} denotes the \m {s_1,s_2}-restricted isometry constant, and is defined in \cite [Can05] (which uses \m {\th}), as follows.
 Let \m {\M {Q}'} be fixed.
@@
 \DispNum {d:2:in:x2} {
-\NC \T {\d} _{s_1, s_2}
+\NC \tilde {\d} _{s_1, s_2}
 = \NC \inf \CB {
@@
 %
-\m {\T {\d} _{s_1, s_2}} can be related to \m {\d_s} by \cite [Can05]
+\m {\tilde {\d} _{s_1, s_2}} can be related to \m {\d_s} by \cite [Can05]
 \DispNum {d:2:ds:s2} {
-\NC \T {\d} _{s_1, s_2}
+\NC \tilde {\d} _{s_1, s_2}
 \leq \NC \d_{s_1+s_2} \NR
@@
 \DispNum {d:2:11:C1} {
-\NC \VNm {\V {d} _{\SB{\MS {AB}}}} _2
-\leq \NC \F {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\MS {AB}}}^\Tr P d} _2
-+ \F {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\MS {C}}}} _1 \NR
+\NC \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
+\leq \NC \frac {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
++ \frac {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \NR
 }
@@
 \NC \d_S
-\leq \NC \F {1} {8} \NR
+\leq \NC \frac {1} {8} \NR
 }
@@
 \NC \VNm {\V {d}} _2
-\eqsim \NC \MS {O} \SB {\R {L} \R {\log N_H}^3} \NR
+\eqsim \NC \mathscr {O} \SB {\R {L} \R {\log N_H}^3} \NR
 }
@@
 \NC 1 -p
-\eqsim \NC \MS {O} \SB {\Ss {e} ^{-N_B /12}} \NR
+\eqsim \NC \mathscr {O} \SB {\mathsf {e} ^{-N_B /12}} \NR
 }
@@
 \DispNum {P:2:PP:NH} {
-\NC \VNm {\M {P} _{\SB {\MS {AB}}}^\Tr \M {P} \V {d}} _2
-\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
+\NC \VNm {\M {P} _{\SB {\mathscr {AB}}}^\intercal \M {P} \V {d}} _2
+\leq \NC \VNm {\M {P}^\intercal \M {P} \V {d}} _2 \NR
 %
-\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
+\NC \leq \NC \R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \NR
 %
@@
 \DispNum {d:1:Sd:C1} {
-\NC \VNm {\V {d} _{\SB{\MS {A}}}} _1
-\leq \NC \R {S} \VNm {\V {d} _{\SB{\MS {A}}}} _2 \NR
+\NC \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
+\leq \NC \R {S} \VNm {\V {d} _{\SB{\mathscr {A}}}} _2 \NR
 %
-\NC \leq \NC \R {S} \VNm {\V {d} _{\SB{\MS {AB}}}} _2 \NR
+\NC \leq \NC \R {S} \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2 \NR
 %
 \NC \leq \NC 1.21 L \R {\log N_H}^3
-+0.262 \VNm {\V {d} _{\SB{\MS {C}}}} _1 \NR
++0.262 \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \NR
 }
@@
 \DispNum {d:C1:16:H2} {
-\NC \VNm {\V {d} _{\SB{\MS {C}}}} _1
+\NC \VNm {\V {d} _{\SB{\mathscr {C}}}} _1
 %
@@
 \DispNum {d:2:16:H3} {
-\NC \VNm {\V {d} _{\SB{\MS {AB}}}} _2
+\NC \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
 %
@@
 We end this chapter by remarking on the four events of failure, as follows.
-Consider failure probabilities \m {q _{\Rm {iso}, B}}, \m {q _{\Rm {iso}, R}}, \m {q _{\Rm {no}}}, \m {q _{\Rm {sp}}}, respectively for restricted isometry, noise, sparsity.
+Consider failure probabilities \m {q _{\mathrm {iso}, B}}, \m {q _{\mathrm {iso}, R}}, \m {q _{\mathrm {no}}}, \m {q _{\mathrm {sp}}}, respectively for restricted isometry, noise, sparsity.
 If all of them are small, a naive application of union bound suggests
@@
 \NC q
-\eqsim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
+\eqsim \NC 2 \RB {q _{\mathrm {iso}, B} + q _{\mathrm {iso}, R}} +q _{\mathrm {no}} +q _{\mathrm {sp}} \NR
 }
@@
 \DispNum {q:B:2e:Lp'} {
-\NC q _{\Rm {iso}, B}
-\lesssim \NC 2 \Ss {e} ^{-N_B /12} \NR
+\NC q _{\mathrm {iso}, B}
+\lesssim \NC 2 \mathsf {e} ^{-N_B /12} \NR
 %
-\NC q _{\Rm {iso}, R}
+\NC q _{\mathrm {iso}, R}
 \lesssim \NC 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
 %
-\NC q _{\Rm {no}}
+\NC q _{\mathrm {no}}
 \lesssim \NC N_H ^{-2} \NR
 %
-\NC q _{\Rm {sp}}
-\lesssim \NC 2 \Ss {e} ^{-9L/\pi} \NR
+\NC q _{\mathrm {sp}}
+\lesssim \NC 2 \mathsf {e} ^{-9L/\pi} \NR
 }
@@
 \DispNum {q:p:qn:oR} {
-\NC q _{\Rm {sp}}
-\lesssim \NC q _{\Rm {no}} \NR
+\NC q _{\mathrm {sp}}
+\lesssim \NC q _{\mathrm {no}} \NR
 %
-\NC \lesssim \NC q _{\Rm {iso}, R} \NR
+\NC \lesssim \NC q _{\mathrm {iso}, R} \NR
 %
-\NC \eqsim \NC q _{\Rm {iso}, B} \NR
+\NC \eqsim \NC q _{\mathrm {iso}, B} \NR
 }
@@
 \NC q
-\eqsim \NC 2 \Ss {e} ^{-N_B /12} \NR
+\eqsim \NC 2 \mathsf {e} ^{-N_B /12} \NR
 }

### 2020-12-31 treatise-pdflatex/4_simulation.tex
Create pdflatex version

--- 2020-12-31 treatise-context/4_simulation.tex
@@
 Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
-For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
+For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathscr {R} \SB {\V {x}}} of \m {\V {x}} to be
 %
 \DispNum {R:x:R2:M1} {
-\NC \MS {R} \SB {\V {x}}
-\in \NC \MB {R} ^{2M} \NR
-\NC \MS {R} \SB {\V {x}} _{\SB {m}}
+\NC \mathscr {R} \SB {\V {x}}
+\in \NC \mathbb {R} ^{2M} \NR
+\NC \mathscr {R} \SB {\V {x}} _{\SB {m}}
 = \NC \startcases
-\NC \MF {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
-\NC \MF {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
+\NC \mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
+\NC \mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
 \stopcases \NR
@@
 %
-The injection is obvious, and we may define \m {\MS {R} ^{-1}} so that
+The injection is obvious, and we may define \m {\mathscr {R} ^{-1}} so that
 %
 \DispNum {R:1:x::x:} {
-\NC \MS {R} ^{-1} \SB {\MS {R} \SB {\V {x}}}
+\NC \mathscr {R} ^{-1} \SB {\mathscr {R} \SB {\V {x}}}
 =\NC \V {x} \NR
@@
 Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
-For \m {\M {A} \in \MB {C} ^{M_1 \D M_2}}, define real representation \m {\MS {R} \SB {\M {A}}} of \m {\M {A}} to be
+For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathscr {R} \SB {\M {A}}} of \m {\M {A}} to be
 %
 \DispNum {R:A:R2:21} {
-\NC \MS {R} \SB {\M {A}}
-\in \NC \MB {R} ^{2M_1 \D 2M_2} \NR
-\NC \MS {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
+\NC \mathscr {R} \SB {\M {A}}
+\in \NC \mathbb {R} ^{2M_1 \D 2M_2} \NR
+\NC \mathscr {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
 \NC \startcases
-\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
-\NC \MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
-\NC -\MF {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
-\NC \MF {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
+\NC \mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
+\NC \mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
+\NC -\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
+\NC \mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
 \stopcases \NR
@@
 \DispNum {y:y:Ry:Ny} {
-\NC \T {\V {y}}
-= \NC \MS {R} \SB {\V {y}}
-\in \MB {R} ^{2 N_B^2} \NR
+\NC \tilde {\V {y}}
+= \NC \mathscr {R} \SB {\V {y}}
+\in \mathbb {R} ^{2 N_B^2} \NR
 %
-\NC \T {\V {g}}
-= \NC \MS {R} \SB {\V {g}}
-\in \MB {R} ^{2 N_H^2} \NR
+\NC \tilde {\V {g}}
+= \NC \mathscr {R} \SB {\V {g}}
+\in \mathbb {R} ^{2 N_H^2} \NR
 %
-\NC \T {\M {P}}
-= \NC \MS {R} \SB {\M {P}}
-\in \MB {R} ^{2 N_B^2 \D 2 N_H^2} \NR
+\NC \tilde {\M {P}}
+= \NC \mathscr {R} \SB {\M {P}}
+\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \NR
 %
-\NC \T {\M {P}} ^\Adj
-= \NC \MS {R} \SB {\M {P} ^\Adj}
-\in \MB {R} ^{2 N_B^2 \D 2 N_H^2} \NR
+\NC \tilde {\M {P}} ^\Adj
+= \NC \mathscr {R} \SB {\M {P} ^\Adj}
+\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \NR
 %
-\NC \T {\V {z}}
-= \NC \MS {R} \SB {\V {z}}
-\in \MB {R} ^{2 N_B^2} \NR
+\NC \tilde {\V {z}}
+= \NC \mathscr {R} \SB {\V {z}}
+\in \mathbb {R} ^{2 N_B^2} \NR
 }
@@
 \DispNum {y:y:Pg:gz} {
-\NC \V {\T {y}}
-= \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}} \NR
+\NC \V {\tilde {y}}
+= \NC \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \NR
 }
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_B^2}}, \m {\g_{\Rm {DS}} > 0}.
+\item Input \m{\M {P} \in \mathbb {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \mathbb {C} ^{ N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
 %
-\item Define \m {\T {\V {y}}, \T {\V {g}}, \T {\M {P}}, \T {\M {P}} ^\Adj, \T {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
+\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
 %
@@
 \DispNum {g:f:gf:S1} {
-\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
-\LA \NC \startcases
-   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
-   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}' \NR
-   \NC \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
-   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
-   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
+\NC \hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
+\leftarrow \NC \startcases
+   \NC \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \NR
+   \NC \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \NR
+   \NC \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \NR
+   \NC \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \NR
+   \NC \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \NR
 \stopcases \NR
@@
 \NC \Hat{\V {g}}
-\LA \NC \MS {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
+\leftarrow \NC \mathscr {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
 }
@@
 \DispNum {G:G:ve:1g} {
-\NC \Hat {G}
-\LA \NC \Rm {vec}^{-1} \SB {\Hat {g}} \NR
+\NC \hat {G}
+\leftarrow \NC \mathrm {vec}^{-1} \SB {\hat {g}} \NR
 }
@@
 \DispNum {H:H:KG:GK} {
-\NC \Hat {\M {H}}
-\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
+\NC \hat {\M {H}}
+\leftarrow \NC \M {K} \hat {\M {G}} \M {K}^\dagger \NR
 }
-\item Output \m {\Hat {\M {H}}}.
+\item Output \m {\hat {\M {H}}}.
 \stopitemize
@@
 \startitemize[n]
-\item Let \m {\g_{\Rm {DS}} \geq 0} be given, and \m {\M {P}}
+\item Let \m {\g_{\mathrm {DS}} \geq 0} be given, and \m {\M {P}}
 
@@
 
-\item Apply DS to \m {\V {y}, \M {P}} to get \m {\Hat {\V {g}}_0}, and call the \m {N_1} largest component of \m {\Hat {\V {g}}_0} to be \m {\V {g}_1}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _1}.
+\item Apply DS to \m {\V {y}, \M {P}} to get \m {\hat {\V {g}}_0}, and call the \m {N_1} largest component of \m {\hat {\V {g}}_0} to be \m {\V {g}_1}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _1}.
 
-\item Apply DS to \m {\V {y}, \M {P}_1} to get \m {\Hat {\V {g}}_1}, and call the \m {N_2} largest component of \m {\Hat {\V {g}}_1} to be \m {\V {g}_2}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _2}.
+\item Apply DS to \m {\V {y}, \M {P}_1} to get \m {\hat {\V {g}}_1}, and call the \m {N_2} largest component of \m {\hat {\V {g}}_1} to be \m {\V {g}_2}, and corresponding columns of \m {\M {P}} to be \m {\M {P} _2}.
 
-\item Apply Moore–Penrose inverse to \m {\V {y}, \M {P} _2} to get \m {\Hat {\V {g}}_2}, which corresponds to \m {\Hat {\V {g}}}.
+\item Apply Moore–Penrose inverse to \m {\V {y}, \M {P} _2} to get \m {\hat {\V {g}}_2}, which corresponds to \m {\hat {\V {g}}}.
 \stopitemize
@@
 Unfortunately, the two-stage method is not always more accurate than the one-stage method, so we did not include it in the plots.
-It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H}, and we do not know what the best choice is.
+It might have something to do with appropriately scaling \m {\g_{\mathrm {DS}}} with respect to \m {N_H}, and we do not know what the best choice is.
 
@@
 \DispNum {1:8:02:24} {
-\NC 10^{-4} \F {1} {0.25} \R {\F {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
+\NC 10^{-4} \frac {1} {0.25} \R {\frac {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
 =\NC 0.224 \NR
@@
 The number of paths \m {L} is \m {4}.
-The wavelength of carrier \m {\l _{\Rm {ant}}} is set to be \m {0.1}, and the antenna spacing \m {d _{\Rm {ant}}} is \m {0.2}; only their ratio matters.
+The wavelength of carrier \m {\l _{\mathrm {ant}}} is set to be \m {0.1}, and the antenna spacing \m {d _{\mathrm {ant}}} is \m {0.2}; only their ratio matters.
 
-Denote the threshold for DS to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
-In the plots of assorted methods, we set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
-For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
+Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
+In the plots of assorted methods, we set \m {\g_{\mathrm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
+For sake of comparison, \m {\g_{\mathrm {Lasso}} = 2 \R {\log N_H}} too.
 For OMP, suggested values in Cai and Wang \cite [CaW11] is illuminating, where they considered \m {\ell _2}-norm in their Theorem 7, and \m {\ell _\infty}-norm in their Theorem 8.
-We simply take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 N_B}} for 2-norm constraint.
-Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
+We simply take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\mathrm {OMP}} = \R {3 N_B}} for 2-norm constraint.
+Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\mathrm {DS}}} and \m {\h_{\mathrm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
 The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
@@
 \DispNum {h:h:lo:vg} {
-\NC \T {\chi}
+\NC \tilde {\chi}
 =\NC \RB {
-   \F {\log_2 {\VNm {\V {h} -\Hat {\V {h}}} _2}}
+   \frac {\log_2 {\VNm {\V {h} -\hat {\V {h}}} _2}}
    {\log_2 {\VNm {\V {h}}_2}}
-} _{\Ss {avg}}, \NR
+} _{\mathsf {avg}}, \NR
 }
 However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
-We do not know either whether \m {\T {\chi}} is a good indicator of channel capacity; it seems to be, but actually we did not consider a definite a channel model in this treatise.
+We do not know either whether \m {\tilde {\chi}} is a good indicator of channel capacity; it seems to be, but actually we did not consider a definite a channel model in this treatise.
 
@@
 Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
-Here, \m {\T {\chi}} is shown too.
+Here, \m {\tilde {\chi}} is shown too.
 %
@@
 The performance of OMP appears to be poor.
-In most cases, the estimation fails, and we have \m {\T {\chi}} close to the unity.
-Varying thresholds of OMP, namely \m {\h_{\Rm {OMP}}}, does not give different result.
+In most cases, the estimation fails, and we have \m {\tilde {\chi}} close to the unity.
+Varying thresholds of OMP, namely \m {\h_{\mathrm {OMP}}}, does not give different result.
 
@@
 
-The performance of Lasso also fails mostly, and \m {\T {\chi}} even increase as \m {\s} decreases, which is strange.
+The performance of Lasso also fails mostly, and \m {\tilde {\chi}} even increase as \m {\s} decreases, which is strange.
 
-For Moore Penrose pseudoinverse, \m {\T {\chi}} decreases steadily as \m {\s} decreases.
+For Moore Penrose pseudoinverse, \m {\tilde {\chi}} decreases steadily as \m {\s} decreases.
 
-For DS itself, \m {\T {\chi}} decreases as \m {\s} increases, which is expected, but \m {\T {\chi}} does not go down indefinitely, even for very low \m {\s}.
-The values of threshold of DS \m {\g_{\Rm {DS}}} are chosen within the order of magnitude of \m {\s}.
-For high signal level, \m {\g_{\Rm {DS}}} does not affect much, but for low signal level a greater value may be more effective.
+For DS itself, \m {\tilde {\chi}} decreases as \m {\s} increases, which is expected, but \m {\tilde {\chi}} does not go down indefinitely, even for very low \m {\s}.
+The values of threshold of DS \m {\g_{\mathrm {DS}}} are chosen within the order of magnitude of \m {\s}.
+For high signal level, \m {\g_{\mathrm {DS}}} does not affect much, but for low signal level a greater value may be more effective.
 It may have been that the iteration stabilizes much earlier than is constrained by maximum iteration number.
@@
 
-We are not sure either why \m {\T {\chi}} is an overestimation of \m {\chi} by several orders of magnitude.
+We are not sure either why \m {\tilde {\chi}} is an overestimation of \m {\chi} by several orders of magnitude.
 A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
@@
 \DispNum {C:S:C0:1e'} {
-\NC C_{\Rm {DS}}
+\NC C_{\mathrm {DS}}
 = \NC \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
-+ \log_2 \log_2 \F {1} {\e}} C_{\Rm {step}} \NR
++ \log_2 \log_2 \frac {1} {\e}} C_{\mathrm {step}} \NR
 }
 %
-Here \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error, and \m {C_{\Rm {step}}} is the complexity of Newton step.
+Here \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error, and \m {C_{\mathrm {step}}} is the complexity of Newton step.
 According to their analysis (Eqn.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
@@
 
-Every Newton step involves a inversion of \m {\MS {O} \SB {\M {P} ^\Adj \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
-Since the dimension of \m {\M {P} ^\Adj \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\MS {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
-That is, we suppose \m {C_{\Rm {step}} = N_H^4}.
+Every Newton step involves a inversion of \m {\mathscr {O} \SB {\M {P} ^\dagger \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
+Since the dimension of \m {\M {P} ^\dagger \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\mathscr {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
+That is, we suppose \m {C_{\mathrm {step}} = N_H^4}.
 
@@
 \NC \V {g}_0
-=\NC \V {g}_{\Rm {LS}} \NR
-\NC = \NC \RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {y} \NR
+=\NC \V {g}_{\mathrm {LS}} \NR
+\NC = \NC \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \NR
 }
@@
 \DispNum {C:S:Og:g1} {
-\NC C_{\Rm {DS}}
-=\NC \MS {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} N_H^4 \NR
+\NC C_{\mathrm {DS}}
+=\NC \mathscr {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \NR
 }
@@
 \DispNum {P:P:IN:H2} {
-\NC \M {P} ^\Adj \M {P}
+\NC \M {P} ^\dagger \M {P}
 \approx \NC I _{N_{H}^2} \NR
@@
 \DispNum {C:S:Og:z1} {
-\NC C_{\Rm {DS}}
-=\NC \MS {O} \SB {
-   \VNm {\V {g} +\RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {z}
+\NC C_{\mathrm {DS}}
+=\NC \mathscr {O} \SB {
+   \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
    -\V {g}} _1} N_H^4 \NR
-\NC =\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} N_H^4 \NR
+\NC =\NC \mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \NR
 }
 
-We see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes complex standard normal distribution.
+We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
 If we agree that, for high probability,
@@
 \DispNum {O:j:sO:O1} {
-\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
-= \NC \s \MS {O} \RB {1} \NR
+\NC \mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
+= \NC \s \mathscr {O} \RB {1} \NR
 }
@@
 \DispNum {C:S:ON:H6} {
-\NC C_{\Rm {DS}}
-=\NC \MS {O} \SB {N_{H}^6} \NR
+\NC C_{\mathrm {DS}}
+=\NC \mathscr {O} \SB {N_{H}^6} \NR
 }
@@
 \DispNum {C:P:ON:NY} {
-\NC C_{\Rm {OMP}}
-=\NC \MS {O} \SB {N_H^2 \log N_B} \NR
+\NC C_{\mathrm {OMP}}
+=\NC \mathscr {O} \SB {N_H^2 \log N_B} \NR
 }
 %
-Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\MS {O} \SB {N_H^2}}.
+Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathscr {O} \SB {N_H^2}}.
 
-Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\Rm {Lasso}} =\MS {O} \SB {N_H^6}}.
+Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\mathrm {Lasso}} =\mathscr {O} \SB {N_H^6}}.
 
@@
 
-Use \m {t_{\Rm {OMP}} \SB {N_H}}, \m {t_{\Rm {Lasso}} \SB {N_H}}, \m {t_{\Rm {DS}} \SB {N_H}} to denote their respective time taken.
+Use \m {t_{\mathrm {OMP}} \SB {N_H}}, \m {t_{\mathrm {Lasso}} \SB {N_H}}, \m {t_{\mathrm {DS}} \SB {N_H}} to denote their respective time taken.
 We reproduce the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
 \DispNum {t:2:95:55} {
-\NC t_{\Rm {OMP}} \SB {12} \NC = 0.0119,
-\FourQ t_{\Rm {OMP}} \SB {16} = 0.0297, \NR
-\NC t_{\Rm {OMP}} \SB {20} \NC = 0.0600,
-\FourQ t_{\Rm {OMP}} \SB {24} = 0.155, \NR
+\NC t_{\mathrm {OMP}} \SB {12} \NC = 0.0119,
+t_{\mathrm {OMP}} \SB {16} = 0.0297, \NR
+\NC t_{\mathrm {OMP}} \SB {20} \NC = 0.0600,
+t_{\mathrm {OMP}} \SB {24} = 0.155, \NR
 %
-\NC t_{\Rm {Lasso}} \SB {12} \NC = 0.0436,
-\FourQ t_{\Rm {Lasso}} \SB {16} = 0.176, \NR
-\NC t_{\Rm {Lasso}} \SB {20} \NC = 0.471,
-\FourQ t_{\Rm {Lasso}} \SB {24} = 1.26, \NR
+\NC t_{\mathrm {Lasso}} \SB {12} \NC = 0.0436,
+t_{\mathrm {Lasso}} \SB {16} = 0.176, \NR
+\NC t_{\mathrm {Lasso}} \SB {20} \NC = 0.471,
+t_{\mathrm {Lasso}} \SB {24} = 1.26, \NR
 %
-\NC t_{\Rm {DS}} \SB {12} \NC = 0.357,
-\FourQ t_{\Rm {DS}} \SB {16} = 2.07, \NR
-\NC t_{\Rm {DS}} \SB {20} \NC = 29.8,
-\FourQ t_{\Rm {DS}} \SB {24} = 91.5, \NR
+\NC t_{\mathrm {DS}} \SB {12} \NC = 0.357,
+t_{\mathrm {DS}} \SB {16} = 2.07, \NR
+\NC t_{\mathrm {DS}} \SB {20} \NC = 29.8,
+t_{\mathrm {DS}} \SB {24} = 91.5, \NR
 }
-Simulation indeed shows that \m {t_{\Rm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
+Simulation indeed shows that \m {t_{\mathrm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
 It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
@@
 
-Meanwhile, \m {t_{\Rm {Lasso}}} and \m {t_{\Rm {OMP}}} are often an order of magnitude lower than \m {t_{\Rm {DS}}}.
-In general, \m {t_{\Rm {DS}} \gg t_{\Rm {Lasso}} \gg t_{\Rm {OMP}}}.
+Meanwhile, \m {t_{\mathrm {Lasso}}} and \m {t_{\mathrm {OMP}}} are often an order of magnitude lower than \m {t_{\mathrm {DS}}}.
+In general, \m {t_{\mathrm {DS}} \gg t_{\mathrm {Lasso}} \gg t_{\mathrm {OMP}}}.
 It is now wonder that, given that OMP is a greedy algorithm, the time OMP takes is negligibly small.
@@
 \DispNum {t:P:NH:83} {
-\NC \T {t}_{\Rm {OMP}} \NC \eqsim \MS {O} \SB {N_H^{3.6}} \NR
-\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \MS {O} \SB {N_H^{4.8}} \NR
-\NC \T {t}_{\Rm {DS}} \NC \eqsim \MS {O} \SB {N_H^{8.3}} \NR
+\NC \tilde {t}_{\mathrm {OMP}} \NC \eqsim \mathscr {O} \SB {N_H^{3.6}} \NR
+\NC \tilde {t}_{\mathrm {Lasso}} \NC \eqsim \mathscr {O} \SB {N_H^{4.8}} \NR
+\NC \tilde {t}_{\mathrm {DS}} \NC \eqsim \mathscr {O} \SB {N_H^{8.3}} \NR
 }

### 2020-12-31 treatise-pdflatex/abstract.tex
Create pdflatex version

--- 2020-11-10 treatise/abstract.tex
@@
 Multiple-input-multiple-output (MIMO) is the future of wireless communication, but the large number of antennae makes it difficult to estimate its channel state information.
-Since millimeter wave (mm-Wave) band, often used together with MIMO, is known to exhibit sparsity, results on compressive sensing suggest that, on mm-Wave band, fewer channel measurements shall suffice.
+Since millimeter wave (mm-Wave) band, which is often used together with MIMO, is known to exhibit sparsity, results on compressive sensing suggest that, on mm-Wave band, fewer channel measurements shall suffice.
 Current literature prefers orthogonal matching pursuit (OMP) due to its lower complexity.
@@
 
-In this treatise, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
-Using pilot signal and 
-We demonstrate that DS can be applied on a entrywise i.i.d.\ random beamformer, and give a bound for its expected error norm, which holds for high probability.
-DS is cast as a linear program, and simulation is done.
-We argue that DS is steadily better in our configuration, while it has siginificantly greater complexity.
+In this treatise, we consider a mm-Wave MIMO channel, and a hybrid beamforming structure at both the transmitter and receiver end.
+We demonstrate that DS can be applied on a entrywise i.i.d.\ random beamformers, and give a bound for its expected error norm, which holds for high probability.
+DS is cast as a linear program, and simulation is done, showing that, in our problem setting, DS is superior in terms of relative error norm.
 

### 2020-12-31 treatise-pdflatex/foreword.tex
Create pdflatex version

\starttitle [title={Foreword}]

I came across the field of compressive sensing in 2018, to begin with, when I was the TA of the course of Convex Optimization, and read about it again as an intern in MediaTek.
Prof.\ Su always had students find their own topic of interest, and I thank him for having encouraged me to continue writing what would become of this treatise, even if when I first told him of the proposal, it was hardly more than a stream of conciousness.
In addition to the stipend he kindly supplied, the warm faux-wood floor, comfortable sofas, and ergonomic chairs in the lab also helped.
For various reasons, I took very long time writing this treatise, and I thank the advisor for his tolerance on my procrastination, if that is not too late.

The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
The three and half years are punctuated by Bāchí martial art practice session, teaching assistant's preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I too hold dearly.

In addition, I thank Chu-Tong Liu, a fellow PhD student of Prof.\ Su's, who I have acquainted in the undergraduate freshman year, in that he gave me valuable suggestions when I was stuck, and was lenient when I did not, or even failed at all to, deliver a proper presentation.
I too cherish the decent meals, trips, and board games enjoyed together with fellow lab students, whose discussion, concern, joke, and sarcasm are particularly enlightening when one is undergoing a writer's block.

After all, I thank my parents, who in recent years was supportive of whatever goal I set up to do (or at least claimed to work on), if slightly too credulous in my ability.
It so was a tremendous luck that I did not have to mind financial matters in the master student years, which is something I ought to treasure.
I am happy to have kept a sense of curiosity for the intricate universe.

November 4, 2020

\stoptitle

### 2020-12-31 treatise-pdflatex/notation.tex
Create pdflatex version

--- 2020-02-27 paper/notation.tex
@@
 \NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
-\NC \m {\RB {1+3} \RB {2+4}} \VL round parentheses \VL used for precedence \AR \HL
-\NC \m {f \SB {x}} \VL square brackets \VL used for arguments or parameter \AR \HL
-\NC \m {\CB {2, 3, 5, 7}} \VL curly braces \VL used for sets \AR \HL
 \NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
-\NC \m {\MF {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
-\NC \m {\MF {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
+\NC \m {\mathfrak {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
+\NC \m {\mathfrak {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
 \NC \m {\V {a}} \VL vector \VL \AR \HL
@@
 \NC \m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
-\NC \m {\MB {K}} \VL either \m {\MB {R}} or \m {\MB {C}} \VL  \AR \HL
-\NC \m {\MB {K} ^{N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL  \AR \HL
-\NC \m {\MB {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
-\NC \m {m\; \Rm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \Rm {Mod}\; n <n} \AR \HL
+\NC \m {\mathbb {K}} \VL either \m {\mathbb {R}} or \m {\mathbb {C}} \VL  \AR \HL
+\NC \m {\mathbb {K} ^{N}} \VL Hilbert space \m {\mathbb {K}^N} over \m {\mathbb {K}} \VL  \AR \HL
+\NC \m {\mathbb {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
+\NC \m {m\; \mathrm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \mathrm {Mod}\; n <n} \AR \HL
 \NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
@@
 \NC  \VL component of \m {\V {a}} \VL  \AR \HL
-\NC \m {\MB {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
-\NC \m {\MB {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
-\NC \m {\Ss {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
+\NC \m {\mathbb {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
+\NC \m {\mathbb {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
+\NC \m {\mathsf {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
 \stoptable

### 2020-12-31 treatise-pdflatex/1_introduction.tex
Convert: newcommand, organization

@@
-\startchapter [title={Introduction}]
+\chapter {Introduction}
 
-\startsection [title={Estimation of MIMO channel}]
+\section {Estimation of MIMO channel}
 
-Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification \cite [RSM13].
+Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification \cite {RSM13}.
 With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain.
@@
 
-\stopsection
-
-\startsection [title={Compressive sensing}]
+\section {Compressive sensing}
 
@@
 We shall see it amounts to invert a linear system whose dimension is the number of antennae, which is not very effective.
-Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
+Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite {ALS14}, which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
 
@@
 \DispNum {N:p:Nm:Nm} {
-\NC N_p \gg \NC N_m \NR
+N_p \gg N_m \NR
 }
@@
 \DispNum {y:y:Qx:Qx} {
-\NC \V {y}
-=\NC \M {Q} \V {x} \NR
+\V {y}
+=\M {Q} \V {x} \NR
 }
@@
 \DispNum {x:A:x::x:} {
-\NC \V {x} _{\SB {\mathscr {A}}}
-=\NC \V {x} \NR
+\V {x} _{\SB {\mathscr {A}}}
+=\V {x} \NR
 }
@@
 \DispNum {A:A:s::s:} {
-\NC \Nm {\mathscr {A}} \leq \NC s. \NR
+\Nm {\mathscr {A}} \leq s. \NR
 }
 
-Candès and Tao \cite [Can05], one of the earlier investigations on compressive sensing, showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability.
+Candès and Tao \cite {Can05}, one of the earlier investigations on compressive sensing, showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability.
 
@@
 But it may be desirable that a camera equipped with fewer sensors shall take a lower resolution photo to save storage, and shall recover the image later.
-Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, while the accuracy is critical to the diagnosis too \cite [CaT07].
+Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, while the accuracy is critical to the diagnosis too \cite {CaT07}.
 
-\stopsection
-
-\startsection [title={The Dantzig Selector}]
+\section {The Dantzig Selector}
 
@@
 \DispNum {y:y:Qx:xz} {
-\NC \V {y}
-=\NC \M {Q} \V {x} + \V {z} \NR
+\V {y}
+=\M {Q} \V {x} + \V {z} \NR
 }
@@
 \Disp {
-\NC \V {x}  _{\SB {\mathscr {A}}}
-=\NC \sum _{i \in \mathscr {A}} \V {v} \V {u} _{i} \NR
+\V {x}  _{\SB {\mathscr {A}}}
+=\sum _{i \in \mathscr {A}} \V {v} \V {u} _{i} \NR
 %
-\NC \M {Q}  _{\SB {\mathscr {A}}}
-=\NC \sum _{i \in \mathscr {A}} \M {Q} _{\SB {:,i}} \NR
+\M {Q}  _{\SB {\mathscr {A}}}
+=\sum _{i \in \mathscr {A}} \M {Q} _{\SB {:,i}} \NR
 }
@@
 \DispNum {1:2:Qx:22} {
-\NC \RB {1-\d_s} \VNm {\V {x}} _2 ^2
-\leq \NC \VNm {\M {Q} \V {x}} _2 ^2 \NR
+\RB {1-\d_s} \VNm {\V {x}} _2 ^2
+\leq \VNm {\M {Q} \V {x}} _2 ^2 \NR
 %
-\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \NR
+\leq \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \NR
 }
@@
 For concreteness, say \m {\V {z}} is an i.i.d.\ normalized random normal vector.
-If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible under high probability.
+If so, a stronger result was established \cite {CaT07} that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible under high probability.
 
@@
 \DispNum {h:h:mi:yg'} {
-\NC \hat {\V {h}}
-\leftarrow \NC \startcases
-\NC \Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
+\hat {\V {h}}
+\leftarrow \startcases
+\Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
 %
-\NC \mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {Q}^\dagger \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
+\mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {Q}^\dagger \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
 \stopcases \NR
@@
 The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear Program, rendering convex programming technique applicable.
-This allows techniques from convex optimization to be used, and Candès and Romberg provided an implementation on their website \cite [CaR05].
+This allows techniques from convex optimization to be used, and Candès and Romberg provided an implementation on their website \cite {CaR05}.
 
 Here the constant \m {\d_s} in Definition [1] is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
-A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
+A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite {BDD08} that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
 
 Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
-An early attempt to apply compressive sensing was Bajwa et.\ al.\ \cite [BHS10], where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
-The accompanying note by the same researchers \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.
+An early attempt to apply compressive sensing was Bajwa et.\ al.\ \cite {BHS10}, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
+The accompanying note by the same researchers \cite {BHR08} showed that \m {X} has RIP for overwhelming probability, justifying their work.
 
-\stopsection
+\section {Orthogonal Matching Pursuit}
 
-\startsection [title={Orthogonal Matching Pursuit}]
-
-At the same time, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal in an underdetermined system.
+At the same time, Tropp and Gilbert \cite {TrG07b} suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal in an underdetermined system.
 Again consider the situation of \Rf {y:y:Qx:xz}.
@@
 \Disp {
-\NC \V {r}
-\leftarrow \NC \V {y} \NR
+\V {r}
+\leftarrow \V {y} \NR
 %
-\NC S
-\leftarrow \NC \varnothing \NR
+S
+\leftarrow \varnothing \NR
 }
@@
 \DispNum {n:n:n0:nr} {
-\NC n
-\leftarrow \NC \underset {n' =0, \dots, N_p-1} {\mathrm {argmax}}
+n
+\leftarrow \underset {n' =0, \dots, N_p-1} {\mathrm {argmax}}
 \Nm {\M {Q} _{\SB {:,n'}} \V {r}} \NR
@@
 \DispNum {Q:Q:QS:Qy} {
-\NC \M {Q} ^\ddagger
-\leftarrow \NC \RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \NR
+\M {Q} ^\ddagger
+\leftarrow \RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \NR
 %
-\NC \V {r}
-\leftarrow \NC \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} \NR
+\V {r}
+\leftarrow \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} \NR
 }
@@
 \DispNum {r:2:h':h'} {
-\NC \VNm {\V {r}} _2
-<\NC \eta \NR
+\VNm {\V {r}} _2
+<\eta \NR
 }
@@
 \DispNum {g:g:Qy:Qy} {
-\NC \hat {\V {g}}
-\leftarrow \NC \M {Q} ^\ddagger \V {y} \NR
+\hat {\V {g}}
+\leftarrow \M {Q} ^\ddagger \V {y} \NR
 }
@@
 In each step, we estimate the noise \m {\V {r}}, and find a new column most correlated with it, to refine the estimation for \m {\V {x}}.
-From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming.
+From Tropp and Gilbert \cite {TrG07a}, the probability that OMP recovers \m {\V {x}} completely is overwhelming.
 
 OMP has since been pervasively used for channel sensing.
-Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles.
-Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamformers based on nonuniform fixed set of angles.
-Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals.
-Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers of stationary channel gain.
-Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the effective beamformer serves as sensing matrix, based on a designed set of angles.
-Manoj and Kannu \cite [MaK17] studied the sparse condition on submatrices of the signal for successful reconstruction.
-Gurbuz, Yapici, and Guvenc \cite [GYG18] introduced perturbation on the angles which the sensing matrix based on.
-Panayirci et.\ al.\ \cite [PAU19] proposed a concatenation of max-likelihood estimation of model parameters, and maximum-a-posteriori estimation of channel gains, by virtue of OMP.
+Alkhateeb et.\ al.\ \cite {AEL14} proposed an adaptive algorithm with a beam codebook for quantized angles.
+Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamformers based on nonuniform fixed set of angles.
+Gao et.\ al.\ \cite {LGC16} proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals.
+Hu, Wang, and He \cite {HWH13} applied OMP to estimate quantized path delay of OFDM subcarriers of stationary channel gain.
+Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the effective beamformer serves as sensing matrix, based on a designed set of angles.
+Manoj and Kannu \cite {MaK17} studied the sparse condition on submatrices of the signal for successful reconstruction.
+Gurbuz, Yapici, and Guvenc \cite {GYG18} introduced perturbation on the angles which the sensing matrix based on.
+Panayirci et.\ al.\ \cite {PAU19} proposed a concatenation of max-likelihood estimation of model parameters, and maximum-a-posteriori estimation of channel gains, by virtue of OMP.
 
 Performance guarantee of OMP is also studied on various conditions.
-Cai, Wang, and Xu \cite [CWX10], gave a new bound on performance of OMP under assumption of low coherence of columns of matrices, instead of almost unitarity.
-Cai and Wang \cite [CaW11] extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] followed up and refined their bounds, concluding that OMP is better for low SNR scenario, and DS is better for high SNR.
+Cai, Wang, and Xu \cite {CWX10}, gave a new bound on performance of OMP under assumption of low coherence of columns of matrices, instead of almost unitarity.
+Cai and Wang \cite {CaW11} extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite {BEE10} followed up and refined their bounds, concluding that OMP is better for low SNR scenario, and DS is better for high SNR.
 
-\stopsection
-
-\startsection [title={Contribution}]
+\section {Contribution}
 
@@
 
-In this treatise, we consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite [LGL16].
+In this treatise, we consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite {LGL16}.
 They proposed a beamformer shown to be optimal, jointly designed on both ends by a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
@@
 In chapter 2 we shall see that our proposed effective beamformer has RIP for high probability, which may serve as the sensing matrix for DS.
-In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a quantitative bound (which holds for high probability) on expected error norm.
+In chapter 3, along the lines of Candès and Tao \cite {CaT07}, we give a quantitative bound (which holds for high probability) on expected error norm.
 In chapter 4, we remark that DS can be cast as a linear program, for which more efficient algorithms exist.
@@
 Indeed, DS is much more accurate than the least square, and both OMP and Lasso often fails.
-
-\stopsection
-
-\stopchapter

### 2020-12-31 treatise-pdflatex/2_problem_setting.tex
Convert: newcommand, organization

@@
-\startchapter [title={Problem setting}]
+\chapter {Problem setting}
 
-\startsection [title={Channel model}]
+\section {Channel model}
 
@@
 \DispNum {a:y':CN:NH} {
-\NC \V {a} \SB {\psi'}
-= \NC \frac {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
+\V {a} \SB {\psi'}
+= \frac {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
 \in \mathbb {C} ^ {N_H} \NR
@@
 
-And consider the virtual representation of the MIMO channel, as in Akdeniz et.\ al.\ \cite [ALS14],
+And consider the virtual representation of the MIMO channel, as in Akdeniz et.\ al.\ \cite {ALS14},
 %
 \DispNum {H:H:l0:ql} {
-\NC \M {H}
-=\NC \sum_{l=0} ^{L-1}
+\M {H}
+=\sum_{l=0} ^{L-1}
 \a_l
@@
 \DispNum {f:l:2p:2p} {
-\NC \f_l
-= \NC 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
+\f_l
+= 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
   \; \mathrm {Mod}\; \RB {2\pi} \NR
 %
-\NC \th_l
-= \NC 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
+\th_l
+= 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
   \; \mathrm {Mod}\; \RB {2\pi} \NR
@@
 \DispNum {H:H:l0:ql} {
-\NC \M {H}
-=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
+\M {H}
+=\sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
 \in \mathbb {C} ^{N_H \D N_H} \NR
@@
 
-\stopsection
-
-\startsection [title={System model}]
+\section {System model}
 
@@
 \externalfigure [system.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Schematic diagram of the hybrid beamforming system we consider, based on Akdeniz et.\ al.\ \cite [ALS14].}
+\FigureCaption {Schematic diagram of the hybrid beamforming system we consider, based on Akdeniz et.\ al.\ \cite {ALS14}.}
 \blank [big]
@@
 \DispNum {F:R:1::R1} {
-\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
-= \NC 1, \NR
+\Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
+= 1, \NR
 %
-\NC \Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
-= \NC 1, \NR
+\Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
+= 1, \NR
 %
-\NC n_H
-= \NC 0, \dots N_H-1, \NR
+n_H
+= 0, \dots N_H-1, \NR
 %
-\NC n_R
-= \NC 0, \dots N_R-1 \NR
+n_R
+= 0, \dots N_R-1 \NR
 }
@@
 \DispNum {N:H:NY:NY} {
-\NC N_H \gg \NC N_R \NR
+N_H \gg N_R \NR
 %
-\NC N_R \gg \NC N_B \NR
+N_R \gg N_B \NR
 }
 
-Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
 Let us introduce the effective channel
@@
 \DispNum {Y:Y:WB:BZ} {
-\NC \M {Y}
-:=\NC \M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
+\M {Y}
+:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
 }
@@
 
-\stopsection
-
-\startsection [title={Vectorization}]
+\section {Vectorization}
 
@@
 \DispNum {v:1:Am:N1} {
-\NC \RB {\mathrm {vec} \SB {\M {A}}} _{\SB {m}}
-=\NC \M {A} _{\SB {m\; \mathrm {Mod}\; N_1, \Fl {m/N_1 }}} \NR
+\RB {\mathrm {vec} \SB {\M {A}}} _{\SB {m}}
+=\M {A} _{\SB {m\; \mathrm {Mod}\; N_1, \Fl {m/N_1 }}} \NR
 }
@@
 \DispNum {v:x:x::x:} {
-\NC \mathrm {vec} ^{-1} \SB {\mathrm {vec} \SB {x}}
-=\NC x \NR
+\mathrm {vec} ^{-1} \SB {\mathrm {vec} \SB {x}}
+=x \NR
 }
@@
 \DispNum {A:2:Am:N4} {
-\NC \NC \RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \NR
+\RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \NR
 %
-\NC =\NC \M {A} _{\SB {\Fl {m_1/N_3 }, \Fl {m_2/N_4 }}}
+=\M {A} _{\SB {\Fl {m_1/N_3 }, \Fl {m_2/N_4 }}}
 \M {B} _{\SB {m_1\; \mathrm {Mod}\; N_3, m_2\; \mathrm {Mod}\; N_4}} \NR
@@
 \DispNum {v:B:BA:cX} {
-\NC \mathrm {vec} \SB {\M {A}\M {X}\M {B}}
-= \NC \RB {\M {B}^\intercal \otimes \M {A}} \mathrm {vec} \SB {\M {X}} \NR
+\mathrm {vec} \SB {\M {A}\M {X}\M {B}}
+= \RB {\M {B}^\intercal \otimes \M {A}} \mathrm {vec} \SB {\M {X}} \NR
 }
@@
 \DispNum {h:h:ve:Nh} {
-\NC \V {h}
-:= \NC \mathrm {vec} \SB {\M {H}}
+\V {h}
+:= \mathrm {vec} \SB {\M {H}}
 \in \mathbb {C} ^{N_H^2} \NR
 %
-\NC \V {y}
-:= \NC \mathrm {vec} \SB {\M {Y}}
+\V {y}
+:= \mathrm {vec} \SB {\M {Y}}
 \in \mathbb {C} ^{N_B^2} \NR
 %
-\NC \V {z}
-:= \NC \mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
+\V {z}
+:= \mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
 \in \mathbb {C} ^{N_B^2} \NR
 %
-\NC \M {Q}
-:= \NC \RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
+\M {Q}
+:= \RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
 \in \mathbb {C} ^{N_B^2 \D N_H^2} \NR
@@
 \DispNum {y:y:Qh:hz} {
-\NC \V {y}
-=\NC \M {Q} \V {h} +\V {z} \NR
+\V {y}
+=\M {Q} \V {h} +\V {z} \NR
 }
@@
 
-\stopsection
-
-\startsection [title={Spacial frequency domain}]
+\section {Spacial frequency domain}
 
@@
 \DispNum {K:K:CN:H1} {
-\NC \M {K} \in  \NC \mathbb {C} ^{N_H \D N_H} \NR
+\M {K} \in  \mathbb {C} ^{N_H \D N_H} \NR
 %
-\NC \M {K} _{\SB {n_1, n_2}}
-= \NC \frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \NR
+\M {K} _{\SB {n_1, n_2}}
+= \frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \NR
 %
-\NC \quad n_1, n_2
-= \NC 0, 1, \dots, N_H-1 \NR
+\quad n_1, n_2
+= 0, 1, \dots, N_H-1 \NR
 }
@@
 \DispNum {K:K:I:::I} {
-\NC \M {K}^\dagger \M {K}
-= \NC \M {I} \NR
+\M {K}^\dagger \M {K}
+= \M {I} \NR
 }
@@
 \DispNum {G:G:KH:HK} {
-\NC \M {G}
-=\NC \M {K}^\dagger \M {H} \M {K} \NR
+\M {G}
+=\M {K}^\dagger \M {H} \M {K} \NR
 }
@@
 \DispNum {Y:Y:WB:NY} {
-\NC \M {Y}
-=\NC \M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\dagger \M {F} _R \M {F} _B
+\M {Y}
+=\M {W} _B \M {W} _R \M {K} \D \M {G} \D \M {K}^\dagger \M {F} _R \M {F} _B
 +\M {W} _B \M {W} _R \M {Z}
@@
 \DispNum {P:P:FB:Nh} {
-\NC \M {P}
-:=\NC \RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
+\M {P}
+:=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
 \in \mathbb {C} ^{N_B^2 \D N_H^2} \NR
@@
 \DispNum {g:g:ve:Nh} {
-\NC \V {g}
-:= \NC \mathrm {vec} \SB {\M {G}}
+\V {g}
+:= \mathrm {vec} \SB {\M {G}}
 \in \mathbb {C} ^ {N_H \D N_H} \NR
@@
 \DispNum {y:y:Pg:gz} {
-\NC \V {y}
-=\NC \M {P} \V {g} +\V {z} \NR
+\V {y}
+=\M {P} \V {g} +\V {z} \NR
 }
 
-\stopsection
-\startsection [title={Proposed method}]
+\section {Proposed method}
 
@@
 %
-\item Input \m {\M {F} _B \in \NC \mathbb {C} ^{N_R \D N_B}},
-\m {\M {F} _R \in \NC \mathbb {C} ^{N_H \D N_R}},
-\m {\M {W} _R \in \NC \mathbb {C} ^{N_R \D N_H}},
-\m {\M {W} _B \in \NC \mathbb {C} ^{N_B \D N_R}},
-and \m {\M {Y} \in \NC \mathbb {C} ^{N_B \D N_B}}.
+\item Input \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_B}},
+\m {\M {F} _R \in \mathbb {C} ^{N_H \D N_R}},
+\m {\M {W} _R \in \mathbb {C} ^{N_R \D N_H}},
+\m {\M {W} _B \in \mathbb {C} ^{N_B \D N_R}},
+and \m {\M {Y} \in \mathbb {C} ^{N_B \D N_B}}.
 %
@@
 \DispNum {g:g:mi:DS} {
-\NC \hat {\V {g}}
-\leftarrow \NC \startcases
-\NC \Min {\V {g}' \in \mathbb {C} ^{N_H^2}}  \MC \VNm {\V {g}'} _1 \NR
+\hat {\V {g}}
+\leftarrow \startcases
+\Min {\V {g}' \in \mathbb {C} ^{N_H^2}}  \MC \VNm {\V {g}'} _1 \NR
 %
-\NC \mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \NR
+\mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \NR
 \stopcases \NR
@@
 \DispNum {G:G:ve:1g} {
-\NC \hat {\M {G}}
-\leftarrow \NC \mathrm {vec}^{-1} \SB {\hat {\V {g}}} \NR
+\hat {\M {G}}
+\leftarrow \mathrm {vec}^{-1} \SB {\hat {\V {g}}} \NR
 }
@@
 \DispNum {H:H:KG:GK} {
-\NC \hat {\M {H}}
-\leftarrow \NC \M {K} \hat {\M {G}} \M {K}^\dagger \NR
+\hat {\M {H}}
+\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger \NR
 }
@@
 }
-
-\stopsection
-\stopchapter

### 2020-12-31 treatise-pdflatex/3_2_design_of_beamformers.tex
Convert: newcommand, organization

@@
-\startsection [title={Design of beamformers}]
+\section {Design of beamformers}
 
-\startsubsection [title={Design of beamformers}]
+\subsection {Design of beamformers}
 
@@
 
-\stopsubsection
-
-\startsubsection [title={Operator norm of digital beamformers}]
+\subsection {Operator norm of digital beamformers}
 
@@
 \DispNum {C':C':WB:j2} {
-\NC \VNm {\M {W} _B \V {u}} _2
-=\NC \R {
+\VNm {\M {W} _B \V {u}} _2
+=\R {
    \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
@@
 We need a large deviation result for i.i.d.\ sum of chi-square random variables.
-To do so, we apply Lemma \m {1} in Laurent and Massart \cite [LaM00] for equal weights, with \m {x > 0} below.
+To do so, we apply Lemma \m {1} in Laurent and Massart \cite {LaM00} for equal weights, with \m {x > 0} below.
 By some calculation, we have the upper tail inequality
@@
 \DispNum {P:x:ex:ex} {
-\NC \mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_B}} + \frac {2x} {N_B}}
-\leq \NC \mathsf {e} ^{-x} \NR
+\mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_B}} + \frac {2x} {N_B}}
+\leq \mathsf {e} ^{-x} \NR
 }
@@
 \DispNum {P:x:ex:ex!} {
-\NC \mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_B}}}
-\leq \NC \mathsf {e} ^{-x} \NR
+\mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_B}}}
+\leq \mathsf {e} ^{-x} \NR
 }
@@
 \DispNum {W:1:ds:ds} {
-\NC \Nm {\VNm {\M {W} _B \V {u}} _2 ^2 - 1}
-\geq \NC \d_s \NR
+\Nm {\VNm {\M {W} _B \V {u}} _2 ^2 - 1}
+\geq \d_s \NR
 }
@@
 \DispNum {1:p:2e:s4} {
-\NC 1 -p
-\leq \NC 2 \mathsf {e} ^{-N_B \R {\d_s} /4} \NR
+1 -p
+\leq 2 \mathsf {e} ^{-N_B \R {\d_s} /4} \NR
 }
@@
 
-\stopsubsection
+\subsection {Operator norm of analog beamformers}
 
-\startsubsection [title={Operator norm of analog beamformers}]
-
-In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17], Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
+In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite {KlM17}, Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
 We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
@@
 \DispNum {N:R:sd':NH} {
-\NC N_R
-\geq \NC \frac {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
+N_R
+\geq \frac {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
 }
@@
 \DispNum {N:R:sd'NH} {
-\NC N_R
-\geq \NC \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
+N_R
+\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
 }
@@
 \DispNum {1:p:ex:d's} {
-\NC 1 -p
-\leq \NC \RB {\frac {\d_s} {N_H s}} ^{1/3} \NR
+1 -p
+\leq \RB {\frac {\d_s} {N_H s}} ^{1/3} \NR
 }
@@
 
-\stopsubsection
-
-\startsubsection [title={Confirming the restricted isometry}]
+\subsection {Confirming the restricted isometry}
 
@@
 \DispNum {P:2:FB:WR} {
-\NC \VNm {P} _2
-=\NC \VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \NR
+\VNm {P} _2
+=\VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \NR
 }
@@
 \DispNum {G:G:Ud:dU} {
-\NC \M {G}
-=\NC \M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger \NR
+\M {G}
+=\M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger \NR
 }
@@
 \DispNum {G:2:g2:g2} {
-\NC \VNm {\M {G}} _2
-\NC =\VNm {\mathrm {abs} \SB {\V {g}}} _2 \NR
+\VNm {\M {G}} _2
+=\VNm {\mathrm {abs} \SB {\V {g}}} _2 \NR
 }
@@
 \DispNum {W:2:WB:d's} {
-\NC \NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
+\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
 %
-\NC =\NC \VNm {
+=\VNm {
    \M {W} _B \M {W} _R \M {K} \M {U} \D
@@
 %
-\NC =\NC \VNm {
+=\VNm {
    \M {W} _B \M {W} _R \M {K} \M {U}
@@
 %
-\NC \eqsim \NC \VNm {\M {G}} _2 \RB {1 +2\d_s} \NR
+\eqsim \VNm {\M {G}} _2 \RB {1 +2\d_s} \NR
 }
 Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} according to the form \Rf {H:H:l0:ql}.
-
-\stopsubsection
-
-\stopsection

### 2020-12-31 treatise-pdflatex/3_3_bound_for_error_norm.tex
Convert: newcommand, organization

@@
-\startsection [title={Bound for expected error norm}]
+\section {Bound for expected error norm}
 
-\startsubsection [title={Technical propositions in complex case}]
+\subsection {Technical propositions in complex case}
 
@@
 \DispNum {d:d:gg:gg} {
-\NC \V {d} 
-= \NC \hat {\V {g}} - \V {g} \NR
+\V {d} 
+= \hat {\V {g}} - \V {g} \NR
 }
@@
 \DispNum {g':g':2N:Nh} {
-\NC \g
-= \NC 2 \R {\log N_H} \NR
+\g
+= 2 \R {\log N_H} \NR
 }
 %
-The propositions below are taken from \cite [CaT07] and modified slightly in accordance to our settings, in addition to the generalization to complex vectors.
+The propositions below are taken from \cite {CaT07} and modified slightly in accordance to our settings, in addition to the generalization to complex vectors.
 %
@@
 \DispNum {d:1:dA:C1} {
-\NC \VNm {\V {d} _{\SB{\mathscr {C}}}} _1
-\leq \NC \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
+\VNm {\V {d} _{\SB{\mathscr {C}}}} _1
+\leq \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
 +\VNm {\V {g} _{\SB{\mathscr {C}}}} _1 \NR
@@
 \DispNum {g:1:gd:g1} {
-\NC \VNm {\V {g}} _1
+\VNm {\V {g}} _1
 - \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
@@
 - \VNm {\V {g} _{\SB{\mathscr {C}}}} _1
-\leq \NC \VNm {\V {g} + \V {d}} _1 \NR
+\leq \VNm {\V {g} + \V {d}} _1 \NR
 %
-\NC =\NC \VNm {\hat {\V {g}}} _1 \NR
+=\VNm {\hat {\V {g}}} _1 \NR
 }
@@
 \DispNum {g:1:g1:g1} {
-\NC \VNm {\hat {\V {g}}} _1
-\leq \NC \VNm {\V {g}} _1 \NR
+\VNm {\hat {\V {g}}} _1
+\leq \VNm {\V {g}} _1 \NR
 }
@@
 \DispNum {P:d:4N:Nh} {
-\NC \VNm {\M {P}^\dagger \M {P} \V {d}} _\infty
-\leq \NC  4 \R {2 \log N_H} \NR
+\VNm {\M {P}^\dagger \M {P} \V {d}} _\infty
+\leq  4 \R {2 \log N_H} \NR
 }
@@
 \DispNum {1:p:NH:H2} {
-\NC 1 -p
-\leq \NC N_H^{-2}. \NR
+1 -p
+\leq N_H^{-2}. \NR
 }
@@
 \DispNum {z:y:Pg:ny} {
-\NC \IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_h}}}
-= \NC \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \NR
+\IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_h}}}
+= \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \NR
 %
-\NC = \NC \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} \NR
+= \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} \NR
 }
@@
 \DispNum {Q:x:12:22} {
-\NC Q\SB {x'}
-\leq \NC \frac {1} {2} \mathsf {e}^{-x'^2 /2} \NR
+Q\SB {x'}
+\leq \frac {1} {2} \mathsf {e}^{-x'^2 /2} \NR
 }
@@
 \DispNum {Q:h:1N:Nh} {
-\NC Q\SB {2 \R {\log N_H}}
-=\NC \frac {1} {2 N_H^2}. \NR
+Q\SB {2 \R {\log N_H}}
+=\frac {1} {2 N_H^2}. \NR
 }
@@
 \DispNum {P:g:Py:Nh} {
-\NC \VNm {\M {P} _{\SB {:,n_h}}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
-\leq \NC \VNm {\M {P}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \NR
+\VNm {\M {P} _{\SB {:,n_h}}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
+\leq \VNm {\M {P}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \NR
 %
-\NC \leq \NC 2\R {2 \log N_H} \NR
+\leq 2\R {2 \log N_H} \NR
 }
@@
 \DispNum {P:d:zP:Nh} {
-\NC \VNm {\M {P} _{\SB {:,n_h}}^\dagger \M {P} \V {d}} _\infty
-\leq \NC \Nm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}}
+\VNm {\M {P} _{\SB {:,n_h}}^\dagger \M {P} \V {d}} _\infty
+\leq \Nm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}}
 + \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_h}}} \NR
 %
-\NC \simeq \NC 2 \R {2 \log N_H} +2 \R {2 \log N_H} \NR
+\simeq 2 \R {2 \log N_H} +2 \R {2 \log N_H} \NR
 }
 
-Lastly, the following two propositions are taken from \cite [CaT07], Lemma \m {1}.
+Lastly, the following two propositions are taken from \cite {CaT07}, Lemma \m {1}.
 The generalization from real vector spaces to complex spaces is obvious.
@@
 \DispNum {d:2:dA:12} {
-\NC \VNm {\V {d}} _2^2
-\leq \NC \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2^2 + \frac {1} {S} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1^2 \NR
+\VNm {\V {d}} _2^2
+\leq \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2^2 + \frac {1} {S} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1^2 \NR
 }
@@
 \DispNum {d:2:dA:C1} {
-\NC \VNm {\V {d}} _2
-\leq \NC \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \NR
+\VNm {\V {d}} _2
+\leq \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \NR
 }
@@
 \DispNum {d:2:11:C1} {
-\NC \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
-\leq \NC \frac {1} {1- \d_{2S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
+\VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
+\leq \frac {1} {1- \d_{2S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
 + \frac {\tilde {\d}_{S, 2S}} {\RB {1- \d_{2S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \NR
@@
 %
-Here \m {\tilde {\d} _{s_1, s_2}} denotes the \m {s_1,s_2}-restricted isometry constant, and is defined in \cite [Can05] (which uses \m {\th}), as follows.
+Here \m {\tilde {\d} _{s_1, s_2}} denotes the \m {s_1,s_2}-restricted isometry constant, and is defined in \cite {Can05} (which uses \m {\th}), as follows.
 Let \m {\M {Q}'} be fixed.
@@
 \DispNum {d:2:in:x2} {
-\NC \tilde {\d} _{s_1, s_2}
-= \NC \inf \CB {
+\tilde {\d} _{s_1, s_2}
+= \inf \CB {
 \d':\; \Nm {\IP {\M {Q}' \V {x}_1, \M {Q}' \V {x}_2}}
@@
 %
-\m {\tilde {\d} _{s_1, s_2}} can be related to \m {\d_s} by \cite [Can05]
+\m {\tilde {\d} _{s_1, s_2}} can be related to \m {\d_s} by \cite {Can05}
 \DispNum {d:2:ds:s2} {
-\NC \tilde {\d} _{s_1, s_2}
-\leq \NC \d_{s_1+s_2} \NR
+\tilde {\d} _{s_1, s_2}
+\leq \d_{s_1+s_2} \NR
 }
@@
 \DispNum {d':S:Ll:d's} {
-\NC \d_{S}
-\leq \NC \R {L} \RB {\log N_H} ^{1/4} \d_{s} \NR
+\d_{S}
+\leq \R {L} \RB {\log N_H} ^{1/4} \d_{s} \NR
 }
@@
 \DispNum {d:2:11:C1} {
-\NC \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
-\leq \NC \frac {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
+\VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
+\leq \frac {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
 + \frac {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \NR
@@
 }
-\stopsubsection
 
-\startsubsection [title={Proposed bound}]
+\subsection {Proposed bound}
 
@@
 \DispNum {S:S:4N:NH} {
-\NC S
-=\NC L \log N_H \NR
+S
+=L \log N_H \NR
 }
@@
 \DispNum {d':S:18:18} {
-\NC \d_S
-\leq \NC \frac {1} {8} \NR
+\d_S
+\leq \frac {1} {8} \NR
 }
@@
 \DispNum {d:2:OL:H3} {
-\NC \VNm {\V {d}} _2
-\eqsim \NC \mathscr {O} \SB {\R {L} \R {\log N_H}^3} \NR
+\VNm {\V {d}} _2
+\eqsim \mathscr {O} \SB {\R {L} \R {\log N_H}^3} \NR
 }
@@
 \DispNum {1:p:ON:13} {
-\NC 1 -p
-\eqsim \NC \mathscr {O} \SB {\mathsf {e} ^{-N_B /12}} \NR
+1 -p
+\eqsim \mathscr {O} \SB {\mathsf {e} ^{-N_B /12}} \NR
 }
@@
 \DispNum {P:2:PP:NH} {
-\NC \VNm {\M {P} _{\SB {\mathscr {AB}}}^\intercal \M {P} \V {d}} _2
-\leq \NC \VNm {\M {P}^\intercal \M {P} \V {d}} _2 \NR
+\VNm {\M {P} _{\SB {\mathscr {AB}}}^\intercal \M {P} \V {d}} _2
+\leq \VNm {\M {P}^\intercal \M {P} \V {d}} _2 \NR
 %
-\NC \leq \NC \R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \NR
+\leq \R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \NR
 %
-\NC \leq \NC 5.65 \R {\log N_H} \NR
+\leq 5.65 \R {\log N_H} \NR
 }
@@
 \DispNum {d:1:Sd:C1} {
-\NC \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
-\leq \NC \R {S} \VNm {\V {d} _{\SB{\mathscr {A}}}} _2 \NR
+\VNm {\V {d} _{\SB{\mathscr {A}}}} _1
+\leq \R {S} \VNm {\V {d} _{\SB{\mathscr {A}}}} _2 \NR
 %
-\NC \leq \NC \R {S} \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2 \NR
+\leq \R {S} \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2 \NR
 %
-\NC \leq \NC 1.21 L \R {\log N_H}^3
+\leq 1.21 L \R {\log N_H}^3
 +0.262 \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \NR
@@
 \DispNum {d:C1:16:H2} {
-\NC \VNm {\V {d} _{\SB{\mathscr {C}}}} _1
+\VNm {\V {d} _{\SB{\mathscr {C}}}} _1
 %
-\leq \NC 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 \NR
+\leq 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 \NR
 }
@@
 \DispNum {d:2:16:H3} {
-\NC \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
+\VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
 %
-\leq \NC 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 \NR
+\leq 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 \NR
 }
@@
 \DispNum {d:2:42:NH} {
-\NC \VNm {\V {d}} _2
-\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
+\VNm {\V {d}} _2
+\leq 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
 }
@@
 \DispNum {c':c':8L:H3} {
-\NC \chi
-= \NC 8 \R {L} \R {\log N_H}^3 \NR
+\chi
+= 8 \R {L} \R {\log N_H}^3 \NR
 }
@@
 \DispNum {d:d:c'-:c'-} {
-\NC \VNm {\V {d}} _2
-\leq \NC \chi \NR
+\VNm {\V {d}} _2
+\leq \chi \NR
 }
@@
 \DispNum {q:q:2q:ar} {
-\NC q
-\eqsim \NC 2 \RB {q _{\mathrm {iso}, B} + q _{\mathrm {iso}, R}} +q _{\mathrm {no}} +q _{\mathrm {sp}} \NR
+q
+\eqsim 2 \RB {q _{\mathrm {iso}, B} + q _{\mathrm {iso}, R}} +q _{\mathrm {no}} +q _{\mathrm {sp}} \NR
 }
@@
 \DispNum {q:B:2e:Lp'} {
-\NC q _{\mathrm {iso}, B}
-\lesssim \NC 2 \mathsf {e} ^{-N_B /12} \NR
+q _{\mathrm {iso}, B}
+\lesssim 2 \mathsf {e} ^{-N_B /12} \NR
 %
-\NC q _{\mathrm {iso}, R}
-\lesssim \NC 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
+q _{\mathrm {iso}, R}
+\lesssim 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
 %
-\NC q _{\mathrm {no}}
-\lesssim \NC N_H ^{-2} \NR
+q _{\mathrm {no}}
+\lesssim N_H ^{-2} \NR
 %
-\NC q _{\mathrm {sp}}
-\lesssim \NC 2 \mathsf {e} ^{-9L/\pi} \NR
+q _{\mathrm {sp}}
+\lesssim 2 \mathsf {e} ^{-9L/\pi} \NR
 }
@@
 \DispNum {N:B:4l:H2} {
-\NC N_B
-\gtrsim \NC 4 \log N_H \NR
+N_B
+\gtrsim 4 \log N_H \NR
 %
-\NC N_R
-\gtrsim \NC 16 L \RB {\log N_H}^2 \NR
+N_R
+\gtrsim 16 L \RB {\log N_H}^2 \NR
 }
@@
 \DispNum {q:p:qn:oR} {
-\NC q _{\mathrm {sp}}
-\lesssim \NC q _{\mathrm {no}} \NR
+q _{\mathrm {sp}}
+\lesssim q _{\mathrm {no}} \NR
 %
-\NC \lesssim \NC q _{\mathrm {iso}, R} \NR
+\lesssim q _{\mathrm {iso}, R} \NR
 %
-\NC \eqsim \NC q _{\mathrm {iso}, B} \NR
+\eqsim q _{\mathrm {iso}, B} \NR
 }
@@
 \DispNum {q:q:ON:13} {
-\NC q
-\eqsim \NC 2 \mathsf {e} ^{-N_B /12} \NR
+q
+\eqsim 2 \mathsf {e} ^{-N_B /12} \NR
 }
-
-\stopsubsection
-\stopsection

### 2020-12-31 treatise-pdflatex/4_simulation.tex
Convert: newcommand, organization

@@
-\startchapter [title={Simulation}]
+\chapter {Simulation}
 
 In this chapter we shall compare \Rf {d:2:OL:H3} with numerical experiments.
-For the convex optimization, we choose the Python library CVXPY \cite [DiB16].
-While a direct implementation of Algorithm [7] leads to extraordinarily large complexity, Candès and Romberg \cite [CaR05] showed that DS can be cast as a linear program, which we elaborate below.
+For the convex optimization, we choose the Python library CVXPY \cite {DiB16}.
+While a direct implementation of Algorithm [7] leads to extraordinarily large complexity, Candès and Romberg \cite {CaR05} showed that DS can be cast as a linear program, which we elaborate below.
 
-\startsection [title={Method}]
+\section {Method}
 
-\startsubsection [title={Some notation}]
+\subsection {Some notation}
 
@@
 \DispNum {R:x:R2:M1} {
-\NC \mathscr {R} \SB {\V {x}}
-\in \NC \mathbb {R} ^{2M} \NR
-\NC \mathscr {R} \SB {\V {x}} _{\SB {m}}
-= \NC \startcases
-\NC \mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
-\NC \mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
+\mathscr {R} \SB {\V {x}}
+\in \mathbb {R} ^{2M} \NR
+\mathscr {R} \SB {\V {x}} _{\SB {m}}
+= \startcases
+\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
+\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
 \stopcases \NR
-\NC m' 
-= \NC  0, 1, 2, \ldots, M-1 \NR
+m' 
+=  0, 1, 2, \ldots, M-1 \NR
 }
@@
 \DispNum {R:1:x::x:} {
-\NC \mathscr {R} ^{-1} \SB {\mathscr {R} \SB {\V {x}}}
-=\NC \V {x} \NR
+\mathscr {R} ^{-1} \SB {\mathscr {R} \SB {\V {x}}}
+=\V {x} \NR
 }
@@
 \DispNum {R:A:R2:21} {
-\NC \mathscr {R} \SB {\M {A}}
-\in \NC \mathbb {R} ^{2M_1 \D 2M_2} \NR
-\NC \mathscr {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
-\NC \startcases
-\NC \mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
-\NC \mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
-\NC -\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
-\NC \mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
+\mathscr {R} \SB {\M {A}}
+\in \mathbb {R} ^{2M_1 \D 2M_2} \NR
+\mathscr {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
+\startcases
+\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
+\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
+-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
+\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
 \stopcases \NR
-\NC m_1 
-= \NC 0, 1, 2, \ldots, M_1 -1 \NR
-\NC m_2 
-= \NC 0, 1, 2, \ldots, M_2 -1 \NR
+m_1 
+= 0, 1, 2, \ldots, M_1 -1 \NR
+m_2 
+= 0, 1, 2, \ldots, M_2 -1 \NR
 }
@@
 \DispNum {y:y:Ry:Ny} {
-\NC \tilde {\V {y}}
-= \NC \mathscr {R} \SB {\V {y}}
+\tilde {\V {y}}
+= \mathscr {R} \SB {\V {y}}
 \in \mathbb {R} ^{2 N_B^2} \NR
 %
-\NC \tilde {\V {g}}
-= \NC \mathscr {R} \SB {\V {g}}
+\tilde {\V {g}}
+= \mathscr {R} \SB {\V {g}}
 \in \mathbb {R} ^{2 N_H^2} \NR
 %
-\NC \tilde {\M {P}}
-= \NC \mathscr {R} \SB {\M {P}}
+\tilde {\M {P}}
+= \mathscr {R} \SB {\M {P}}
 \in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \NR
 %
-\NC \tilde {\M {P}} ^\Adj
-= \NC \mathscr {R} \SB {\M {P} ^\Adj}
+\tilde {\M {P}} ^\Adj
+= \mathscr {R} \SB {\M {P} ^\Adj}
 \in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \NR
 %
-\NC \tilde {\V {z}}
-= \NC \mathscr {R} \SB {\V {z}}
+\tilde {\V {z}}
+= \mathscr {R} \SB {\V {z}}
 \in \mathbb {R} ^{2 N_B^2} \NR
@@
 \DispNum {y:y:Pg:gz} {
-\NC \V {\tilde {y}}
-= \NC \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \NR
+\V {\tilde {y}}
+= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \NR
 }
@@
 
-\stopsubsection
-
-\startsubsection [title={A Linear Program}]
+\subsection {A Linear Program}
 
@@
 \DispNum {g:f:gf:S1} {
-\NC \hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
-\leftarrow \NC \startcases
-   \NC \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \NR
-   \NC \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \NR
-   \NC \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \NR
-   \NC \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \NR
-   \NC \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \NR
+\hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
+\leftarrow \startcases
+   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \NR
+   \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \NR
+   \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \NR
+   \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \NR
+   \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \NR
 \stopcases \NR
@@
 \DispNum {g:::R1:1g} {
-\NC \Hat{\V {g}}
-\leftarrow \NC \mathscr {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
+\Hat{\V {g}}
+\leftarrow \mathscr {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
 }
@@
 \DispNum {G:G:ve:1g} {
-\NC \hat {G}
-\leftarrow \NC \mathrm {vec}^{-1} \SB {\hat {g}} \NR
+\hat {G}
+\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} \NR
 }
@@
 
-\stopsubsection
-
-\startsubsection [title={A Two-Stage Version}]
+\subsection {A Two-Stage Version}
 
 We also tried another version of DS, in which DS is applied twice in estimated nonzero components.
-The two-stage method was briefly mentioned \cite [CaT07] without further numerical verification.
+The two-stage method was briefly mentioned \cite {CaT07} without further numerical verification.
 It goes as follows:
@@
 \Disp {
-\NC N_0
-=\NC 2 N_H^2, \NR
-\NC N_2
-=\NC \lfloor 4 \log N_H \rfloor, \NR
-\NC N_1
-=\NC \lfloor \R {N_0 N_2} \rfloor \NR
+N_0
+=2 N_H^2, \NR
+N_2
+=\lfloor 4 \log N_H \rfloor, \NR
+N_1
+=\lfloor \R {N_0 N_2} \rfloor \NR
 }
@@
 
-\stopsubsection
+\section {Result}
 
-\startsection [title={Result}]
-
-\startsubsection [title={Settings}]
+\subsection {Settings}
 
@@
 \DispNum {1:8:02:24} {
-\NC 10^{-4} \frac {1} {0.25} \R {\frac {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
-=\NC 0.224 \NR
+10^{-4} \frac {1} {0.25} \R {\frac {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
+=0.224 \NR
 }
@@
 Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
-In the plots of assorted methods, we set \m {\g_{\mathrm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
+In the plots of assorted methods, we set \m {\g_{\mathrm {DS}} = 2 \R {\log N_H}} as suggested in \cite {CaT07}.
 For sake of comparison, \m {\g_{\mathrm {Lasso}} = 2 \R {\log N_H}} too.
-For OMP, suggested values in Cai and Wang \cite [CaW11] is illuminating, where they considered \m {\ell _2}-norm in their Theorem 7, and \m {\ell _\infty}-norm in their Theorem 8.
+For OMP, suggested values in Cai and Wang \cite {CaW11} is illuminating, where they considered \m {\ell _2}-norm in their Theorem 7, and \m {\ell _\infty}-norm in their Theorem 8.
 We simply take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\mathrm {OMP}} = \R {3 N_B}} for 2-norm constraint.
@@
 
-For performance metric, we follow Lee, Gil, and Lee \cite [LGL16],
+For performance metric, we follow Lee, Gil, and Lee \cite {LGL16},
 \DispNum {h:h:lo:vg} {
-\NC \tilde {\chi}
-=\NC \RB {
+\tilde {\chi}
+=\RB {
    \frac {\log_2 {\VNm {\V {h} -\hat {\V {h}}} _2}}
@@
 
-\stopsubsection
-
-\startsubsection [title={Plots of assorted methods}]
+\subsection {Plots of assorted methods}
 
@@
 
-\stopsubsection
-
-\startsubsection [title={Plots of DS only}]
+\subsection {Plots of DS only}
 
@@
 
-\stopsubsection
-
-\startsubsection [title={Plots of OMP only}]
+\subsection {Plots of OMP only}
 
@@
 
-\stopsubsection
-
-\startsubsection [title={Discussion}]
+\subsection {Discussion}
 
@@
 
-A crucial reason might be that Lee, Gil, and Lee \cite [LGL16] proposed a high-complexity nonconvex program for the beamformers, which they gave approximation, and we have here a low-complexity, randomly-generated beamformers.
+A crucial reason might be that Lee, Gil, and Lee \cite {LGL16} proposed a high-complexity nonconvex program for the beamformers, which they gave approximation, and we have here a low-complexity, randomly-generated beamformers.
 It may also have something to do with the distribution of angles of departure and arrival;
@@
 
-\stopsection
+\section {Complexity}
 
-\startsection [title={Complexity}]
-
-\startsubsection [title={Asymtotic analysis}]
+\subsection {Asymtotic analysis}
 
@@
 In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many iterations were done.
-Boyd and Vandenberghe \cite [BoV04] analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496, also p.531).
-In our case, Candès and Romberg \cite [CaR05] pointed out that the complex DS can be cast into an second order cone programming (SOCP), and where self concordance holds.
-Diamond and Boyd (writers of CVXPY) \cite [DiB16] explained that convex programs are usually converted into primal-dual problems.
+Boyd and Vandenberghe \cite {BoV04} analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496, also p.531).
+In our case, Candès and Romberg \cite {CaR05} pointed out that the complex DS can be cast into an second order cone programming (SOCP), and where self concordance holds.
+Diamond and Boyd (writers of CVXPY) \cite {DiB16} explained that convex programs are usually converted into primal-dual problems.
 The library we called in the simulation is ECOS, where Newton method is used.
@@
 Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
-Then Boyd and Vandenberghe \cite [BoV04] (p.505, Eqn.9.56) gave a bound of the number of steps.
+Then Boyd and Vandenberghe \cite {BoV04} (p.505, Eqn.9.56) gave a bound of the number of steps.
 If we just take that as the complexity bound for DS, it becomes
@@
 \DispNum {C:S:C0:1e'} {
-\NC C_{\mathrm {DS}}
-= \NC \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
+C_{\mathrm {DS}}
+= \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
 + \log_2 \log_2 \frac {1} {\e}} C_{\mathrm {step}} \NR
@@
 \DispNum {g:0:gL:Py} {
-\NC \V {g}_0
-=\NC \V {g}_{\mathrm {LS}} \NR
-\NC = \NC \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \NR
+\V {g}_0
+=\V {g}_{\mathrm {LS}} \NR
+= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \NR
 }
@@
 \DispNum {C:S:Og:g1} {
-\NC C_{\mathrm {DS}}
-=\NC \mathscr {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \NR
+C_{\mathrm {DS}}
+=\mathscr {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \NR
 }
@@
 \DispNum {g:g:g;:;g} {
-\NC \V {g} ^\star
-\approx \NC \V {g} \NR
+\V {g} ^\star
+\approx \V {g} \NR
 }
@@
 \DispNum {P:P:IN:H2} {
-\NC \M {P} ^\dagger \M {P}
-\approx \NC I _{N_{H}^2} \NR
+\M {P} ^\dagger \M {P}
+\approx I _{N_{H}^2} \NR
 }
@@
 \DispNum {C:S:Og:z1} {
-\NC C_{\mathrm {DS}}
-=\NC \mathscr {O} \SB {
+C_{\mathrm {DS}}
+=\mathscr {O} \SB {
    \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
    -\V {g}} _1} N_H^4 \NR
-\NC =\NC \mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \NR
+=\mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \NR
 }
@@
 \DispNum {O:j:sO:O1} {
-\NC \mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
-= \NC \s \mathscr {O} \RB {1} \NR
+\mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
+= \s \mathscr {O} \RB {1} \NR
 }
@@
 \DispNum {C:S:ON:H6} {
-\NC C_{\mathrm {DS}}
-=\NC \mathscr {O} \SB {N_{H}^6} \NR
+C_{\mathrm {DS}}
+=\mathscr {O} \SB {N_{H}^6} \NR
 }
 
-On the other hand, Tropp and Gilbert \cite [TrG07a] discussed the complexity of OMP in the companion paper \cite [TrG07b].
+On the other hand, Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}.
 They gave
@@
 \DispNum {C:P:ON:NY} {
-\NC C_{\mathrm {OMP}}
-=\NC \mathscr {O} \SB {N_H^2 \log N_B} \NR
+C_{\mathrm {OMP}}
+=\mathscr {O} \SB {N_H^2 \log N_B} \NR
 }
@@
 
-\stopsubsection
-
-\startsubsection [title={Runtime statistics}]
+\subsection {Runtime statistics}
 
@@
 \DispNum {t:2:95:55} {
-\NC t_{\mathrm {OMP}} \SB {12} \NC = 0.0119,
+t_{\mathrm {OMP}} \SB {12} = 0.0119,
 t_{\mathrm {OMP}} \SB {16} = 0.0297, \NR
-\NC t_{\mathrm {OMP}} \SB {20} \NC = 0.0600,
+t_{\mathrm {OMP}} \SB {20} = 0.0600,
 t_{\mathrm {OMP}} \SB {24} = 0.155, \NR
 %
-\NC t_{\mathrm {Lasso}} \SB {12} \NC = 0.0436,
+t_{\mathrm {Lasso}} \SB {12} = 0.0436,
 t_{\mathrm {Lasso}} \SB {16} = 0.176, \NR
-\NC t_{\mathrm {Lasso}} \SB {20} \NC = 0.471,
+t_{\mathrm {Lasso}} \SB {20} = 0.471,
 t_{\mathrm {Lasso}} \SB {24} = 1.26, \NR
 %
-\NC t_{\mathrm {DS}} \SB {12} \NC = 0.357,
+t_{\mathrm {DS}} \SB {12} = 0.357,
 t_{\mathrm {DS}} \SB {16} = 2.07, \NR
-\NC t_{\mathrm {DS}} \SB {20} \NC = 29.8,
+t_{\mathrm {DS}} \SB {20} = 29.8,
 t_{\mathrm {DS}} \SB {24} = 91.5, \NR
 }
-Simulation indeed shows that \m {t_{\mathrm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
+Simulation indeed shows that \m {t_{\mathrm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite {FrS07} on the high complexity of DS.
 It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
@@
 \DispNum {t:P:NH:83} {
-\NC \tilde {t}_{\mathrm {OMP}} \NC \eqsim \mathscr {O} \SB {N_H^{3.6}} \NR
-\NC \tilde {t}_{\mathrm {Lasso}} \NC \eqsim \mathscr {O} \SB {N_H^{4.8}} \NR
-\NC \tilde {t}_{\mathrm {DS}} \NC \eqsim \mathscr {O} \SB {N_H^{8.3}} \NR
+\tilde {t}_{\mathrm {OMP}} \eqsim \mathscr {O} \SB {N_H^{3.6}} \NR
+\tilde {t}_{\mathrm {Lasso}} \eqsim \mathscr {O} \SB {N_H^{4.8}} \NR
+\tilde {t}_{\mathrm {DS}} \eqsim \mathscr {O} \SB {N_H^{8.3}} \NR
 }
@@
 However, note that we must be careful in giving meaningful comparison between compressive sensing algorithms, as they might work in different settings.
-DS requires a RIP linear transformation, and it works for noisy linear systems \cite [CaT07].
+DS requires a RIP linear transformation, and it works for noisy linear systems \cite {CaT07}.
 Here, it is not easy to justify RIP rigorously, and a more feasible construction is even a research problem.
-OMP, on the other hand, requires only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], of which much is yet to be studied.
+OMP, on the other hand, requires only an entrywise i.i.d.\ sensing matrix \cite {TrG07a}, of which much is yet to be studied.
 All in all, we might say that on the whole, DS trades off low time- and space-complexity for high precision, and for OMP the opposite is true.
-
-\stopsubsection
-
-\stopsection
-
-\stopchapter

### 2020-12-31 treatise-pdflatex/notation.tex
Convert: newcommand, organization

@@
 \starttable[|l|l|l|] \HL
-\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
-\NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
-\NC \m {\mathfrak {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
-\NC \m {\mathfrak {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
-\NC \m {\V {a}} \VL vector \VL \AR \HL
-\NC \m {\M {A}} \VL matrix \VL \AR \HL
-\NC \m {\V {1}} \VL all-1 vector \VL dimension will be specified \AR \HL
-\NC \m {\V {0}} \VL all-0 vector \VL dimension will be specified \AR \HL
-\NC \m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL
-\NC \m {\M {A} _{\SB {m,n}}} \VL \m {m,n}-th entry of \m {\M {A}} \VL \AR \HL
-\NC \m {\V {a} _{\SB {0}}} \VL the first component of \m {\V {a}} \VL  \AR \HL
-\NC \m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
-\NC \m {\mathbb {K}} \VL either \m {\mathbb {R}} or \m {\mathbb {C}} \VL  \AR \HL
-\NC \m {\mathbb {K} ^{N}} \VL Hilbert space \m {\mathbb {K}^N} over \m {\mathbb {K}} \VL  \AR \HL
-\NC \m {\mathbb {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
-\NC \m {m\; \mathrm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \mathrm {Mod}\; n <n} \AR \HL
-\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
-\NC \m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
-\NC  \VL component of \m {\V {a}} \VL  \AR \HL
-\NC \m {\mathbb {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
-\NC \m {\mathbb {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
-\NC \m {\mathsf {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
+Expression \VL Meaning or Definition \VL More Explanation \SR \HL
+\m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
+\m {\mathfrak {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
+\m {\mathfrak {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
+\m {\V {a}} \VL vector \VL \AR \HL
+\m {\M {A}} \VL matrix \VL \AR \HL
+\m {\V {1}} \VL all-1 vector \VL dimension will be specified \AR \HL
+\m {\V {0}} \VL all-0 vector \VL dimension will be specified \AR \HL
+\m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL
+\m {\M {A} _{\SB {m,n}}} \VL \m {m,n}-th entry of \m {\M {A}} \VL \AR \HL
+\m {\V {a} _{\SB {0}}} \VL the first component of \m {\V {a}} \VL  \AR \HL
+\m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
+\m {\mathbb {K}} \VL either \m {\mathbb {R}} or \m {\mathbb {C}} \VL  \AR \HL
+\m {\mathbb {K} ^{N}} \VL Hilbert space \m {\mathbb {K}^N} over \m {\mathbb {K}} \VL  \AR \HL
+\m {\mathbb {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
+\m {m\; \mathrm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \mathrm {Mod}\; n <n} \AR \HL
+\m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
+\m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
+ \VL component of \m {\V {a}} \VL  \AR \HL
+\m {\mathbb {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
+\m {\mathbb {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
+\m {\mathsf {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
 \stoptable
-
-\stopchapter

### 2021-01-02 treatise-pdflatex/1_introduction.tex
Front matter passes compilation

@@
 
-\blank [big]
-\externalfigure [compressive-sensing.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {
+\bigskip
+\begin {figure} [hbt]
+\centering
+\includegraphics [width = \textwidth] {compressive-sensing.png}
+\caption {
 A conceptual illustration of compressive sensing.
-(Retrieved from \goto {\hyphenatedurl {Wikimedia Commons}} [url (commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif)])
+(Retrieved from \href {commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif} {Wikimedia Commons})
 }
-\blank [big]
+\end {figure}
+\bigskip
 
@@
 \DispNum {N:p:Nm:Nm} {
-N_p \gg N_m \NR
+N_p \gg N_m \\
 }
@@
 \V {y}
-=\M {Q} \V {x} \NR
+=\M {Q} \V {x} \\
 }
@@
 \V {x} _{\SB {\mathscr {A}}}
-=\V {x} \NR
+=\V {x} \\
 }
@@
 \DispNum {A:A:s::s:} {
-\Nm {\mathscr {A}} \leq s. \NR
+\Nm {\mathscr {A}} \leq s. \\
 }
@@
 \V {y}
-=\M {Q} \V {x} + \V {z} \NR
+=\M {Q} \V {x} + \V {z} \\
 }
@@
 \V {x}  _{\SB {\mathscr {A}}}
-=\sum _{i \in \mathscr {A}} \V {v} \V {u} _{i} \NR
+=\sum _{i \in \mathscr {A}} \V {v} \V {u} _{i} \\
 %
 \M {Q}  _{\SB {\mathscr {A}}}
-=\sum _{i \in \mathscr {A}} \M {Q} _{\SB {:,i}} \NR
+=\sum _{i \in \mathscr {A}} \M {Q} _{\SB {:,i}} \\
 }
@@
 \RB {1-\d_s} \VNm {\V {x}} _2 ^2
-\leq \VNm {\M {Q} \V {x}} _2 ^2 \NR
+\leq \VNm {\M {Q} \V {x}} _2 ^2 \\
 %
-\leq \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \NR
+\leq \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \\
 }
@@
 \leftarrow \startcases
-\Min {\V {h}'} \MC \VNm {\V {h}'} _1 \NR
+\Min {\V {h}'} \MC \VNm {\V {h}'} _1 \\
 %
-\mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {Q}^\dagger \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \NR
-\stopcases \NR
+\mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {Q}^\dagger \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \\
+\stopcases \\
 }
@@
 At the same time, Tropp and Gilbert \cite {TrG07b} suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal in an underdetermined system.
-Again consider the situation of \Rf {y:y:Qx:xz}.
+Again consider the situation of \ref {y:y:Qx:xz}.
 
@@
 \V {r}
-\leftarrow \V {y} \NR
+\leftarrow \V {y} \\
 %
 S
-\leftarrow \varnothing \NR
+\leftarrow \varnothing \\
 }
@@
 \leftarrow \underset {n' =0, \dots, N_p-1} {\mathrm {argmax}}
-\Nm {\M {Q} _{\SB {:,n'}} \V {r}} \NR
+\Nm {\M {Q} _{\SB {:,n'}} \V {r}} \\
 }
@@
 \M {Q} ^\ddagger
-\leftarrow \RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \NR
+\leftarrow \RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \\
 %
 \V {r}
-\leftarrow \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} \NR
+\leftarrow \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} \\
 }
@@
 \VNm {\V {r}} _2
-<\eta \NR
+<\eta \\
 }
@@
 \hat {\V {g}}
-\leftarrow \M {Q} ^\ddagger \V {y} \NR
+\leftarrow \M {Q} ^\ddagger \V {y} \\
 }

### 2021-01-02 treatise-pdflatex/3_2_design_of_beamformers.tex
Front matter passes compilation

@@
 =\R {
-   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
+   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \\
 }
@@
 \mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_B}} + \frac {2x} {N_B}}
-\leq \mathsf {e} ^{-x} \NR
+\leq \mathsf {e} ^{-x} \\
 }
@@
 \mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_B}}}
-\leq \mathsf {e} ^{-x} \NR
+\leq \mathsf {e} ^{-x} \\
 }
@@
 \Nm {\VNm {\M {W} _B \V {u}} _2 ^2 - 1}
-\geq \d_s \NR
+\geq \d_s \\
 }
@@
 1 -p
-\leq 2 \mathsf {e} ^{-N_B \R {\d_s} /4} \NR
+\leq 2 \mathsf {e} ^{-N_B \R {\d_s} /4} \\
 }
@@
 N_R
-\geq \frac {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
+\geq \frac {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \\
 }
@@
 N_R
-\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
+\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H \\
 }
@@
 1 -p
-\leq \RB {\frac {\d_s} {N_H s}} ^{1/3} \NR
+\leq \RB {\frac {\d_s} {N_H s}} ^{1/3} \\
 }
@@
 \VNm {P} _2
-=\VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \NR
+=\VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \\
 }
@@
 \M {G}
-=\M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger \NR
+=\M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger \\
 }
@@
 \VNm {\M {G}} _2
-=\VNm {\mathrm {abs} \SB {\V {g}}} _2 \NR
+=\VNm {\mathrm {abs} \SB {\V {g}}} _2 \\
 }
@@
 \DispNum {W:2:WB:d's} {
-\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
+\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \\
 %
@@
    \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
-   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \NR
+   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \\
 %
@@
    \R {\mathrm {abs} \SB {\V {d}'}}
-   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \NR
+   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \\
 %
@@
    \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} \M {U}
-   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \NR
+   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \\
 %
-\eqsim \VNm {\M {G}} _2 \RB {1 +2\d_s} \NR
+\eqsim \VNm {\M {G}} _2 \RB {1 +2\d_s} \\
 }

### 2021-01-02 treatise-pdflatex/3_3_bound_for_error_norm.tex
Front matter passes compilation

@@
 \V {d} 
-= \hat {\V {g}} - \V {g} \NR
+= \hat {\V {g}} - \V {g} \\
 }
@@
 \g
-= 2 \R {\log N_H} \NR
+= 2 \R {\log N_H} \\
 }
@@
 \leq \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
-+\VNm {\V {g} _{\SB{\mathscr {C}}}} _1 \NR
++\VNm {\V {g} _{\SB{\mathscr {C}}}} _1 \\
 }
@@
 - \VNm {\V {g} _{\SB{\mathscr {C}}}} _1
-\leq \VNm {\V {g} + \V {d}} _1 \NR
+\leq \VNm {\V {g} + \V {d}} _1 \\
 %
-=\VNm {\hat {\V {g}}} _1 \NR
+=\VNm {\hat {\V {g}}} _1 \\
 }
@@
 \VNm {\hat {\V {g}}} _1
-\leq \VNm {\V {g}} _1 \NR
+\leq \VNm {\V {g}} _1 \\
 }
@@
 \VNm {\M {P}^\dagger \M {P} \V {d}} _\infty
-\leq  4 \R {2 \log N_H} \NR
+\leq  4 \R {2 \log N_H} \\
 }
@@
 1 -p
-\leq N_H^{-2}. \NR
+\leq N_H^{-2}. \\
 }
@@
 \IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_h}}}
-= \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \NR
+= \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \\
 %
-= \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} \NR
+= \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} \\
 }
@@
 Q\SB {x'}
-\leq \frac {1} {2} \mathsf {e}^{-x'^2 /2} \NR
+\leq \frac {1} {2} \mathsf {e}^{-x'^2 /2} \\
 }
@@
 Q\SB {2 \R {\log N_H}}
-=\frac {1} {2 N_H^2}. \NR
+=\frac {1} {2 N_H^2}. \\
 }
@@
 \VNm {\M {P} _{\SB {:,n_h}}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
-\leq \VNm {\M {P}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \NR
+\leq \VNm {\M {P}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \\
 %
-\leq 2\R {2 \log N_H} \NR
+\leq 2\R {2 \log N_H} \\
 }
@@
 \leq \Nm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}}
-+ \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_h}}} \NR
++ \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_h}}} \\
 %
-\simeq 2 \R {2 \log N_H} +2 \R {2 \log N_H} \NR
+\simeq 2 \R {2 \log N_H} +2 \R {2 \log N_H} \\
 }
@@
 \VNm {\V {d}} _2^2
-\leq \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2^2 + \frac {1} {S} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1^2 \NR
+\leq \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2^2 + \frac {1} {S} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1^2 \\
 }
@@
 \VNm {\V {d}} _2
-\leq \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \NR
+\leq \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \\
 }
@@
 \leq \frac {1} {1- \d_{2S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
-+ \frac {\tilde {\d}_{S, 2S}} {\RB {1- \d_{2S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \NR
++ \frac {\tilde {\d}_{S, 2S}} {\RB {1- \d_{2S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \\
 }
@@
    \leq \d' \VNm {\V {x}_1} \VNm {\V {x}_2}
-} \NR
+} \\
 }
@@
 \tilde {\d} _{s_1, s_2}
-\leq \d_{s_1+s_2} \NR
+\leq \d_{s_1+s_2} \\
 }
@@
 \d_{S}
-\leq \R {L} \RB {\log N_H} ^{1/4} \d_{s} \NR
+\leq \R {L} \RB {\log N_H} ^{1/4} \d_{s} \\
 }
@@
 \leq \frac {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
-+ \frac {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \NR
++ \frac {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \\
 }
@@
 S
-=L \log N_H \NR
+=L \log N_H \\
 }
@@
 \d_S
-\leq \frac {1} {8} \NR
+\leq \frac {1} {8} \\
 }
@@
 \VNm {\V {d}} _2
-\eqsim \mathscr {O} \SB {\R {L} \R {\log N_H}^3} \NR
+\eqsim \mathscr {O} \SB {\R {L} \R {\log N_H}^3} \\
 }
@@
 1 -p
-\eqsim \mathscr {O} \SB {\mathsf {e} ^{-N_B /12}} \NR
+\eqsim \mathscr {O} \SB {\mathsf {e} ^{-N_B /12}} \\
 }
@@
 \VNm {\M {P} _{\SB {\mathscr {AB}}}^\intercal \M {P} \V {d}} _2
-\leq \VNm {\M {P}^\intercal \M {P} \V {d}} _2 \NR
+\leq \VNm {\M {P}^\intercal \M {P} \V {d}} _2 \\
 %
-\leq \R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \NR
+\leq \R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \\
 %
-\leq 5.65 \R {\log N_H} \NR
+\leq 5.65 \R {\log N_H} \\
 }
@@
 \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
-\leq \R {S} \VNm {\V {d} _{\SB{\mathscr {A}}}} _2 \NR
+\leq \R {S} \VNm {\V {d} _{\SB{\mathscr {A}}}} _2 \\
 %
-\leq \R {S} \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2 \NR
+\leq \R {S} \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2 \\
 %
 \leq 1.21 L \R {\log N_H}^3
-+0.262 \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \NR
++0.262 \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \\
 }
@@
 %
-\leq 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 \NR
+\leq 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 \\
 }
@@
 %
-\leq 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 \NR
+\leq 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 \\
 }
@@
 \VNm {\V {d}} _2
-\leq 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
+\leq 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \\
 }
@@
 \chi
-= 8 \R {L} \R {\log N_H}^3 \NR
+= 8 \R {L} \R {\log N_H}^3 \\
 }
@@
 \VNm {\V {d}} _2
-\leq \chi \NR
+\leq \chi \\
 }
@@
 q
-\eqsim 2 \RB {q _{\mathrm {iso}, B} + q _{\mathrm {iso}, R}} +q _{\mathrm {no}} +q _{\mathrm {sp}} \NR
+\eqsim 2 \RB {q _{\mathrm {iso}, B} + q _{\mathrm {iso}, R}} +q _{\mathrm {no}} +q _{\mathrm {sp}} \\
 }
@@
 q _{\mathrm {iso}, B}
-\lesssim 2 \mathsf {e} ^{-N_B /12} \NR
+\lesssim 2 \mathsf {e} ^{-N_B /12} \\
 %
 q _{\mathrm {iso}, R}
-\lesssim 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
+\lesssim 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \\
 %
 q _{\mathrm {no}}
-\lesssim N_H ^{-2} \NR
+\lesssim N_H ^{-2} \\
 %
 q _{\mathrm {sp}}
-\lesssim 2 \mathsf {e} ^{-9L/\pi} \NR
+\lesssim 2 \mathsf {e} ^{-9L/\pi} \\
 }
@@
 N_B
-\gtrsim 4 \log N_H \NR
+\gtrsim 4 \log N_H \\
 %
 N_R
-\gtrsim 16 L \RB {\log N_H}^2 \NR
+\gtrsim 16 L \RB {\log N_H}^2 \\
 }
@@
 q _{\mathrm {sp}}
-\lesssim q _{\mathrm {no}} \NR
+\lesssim q _{\mathrm {no}} \\
 %
-\lesssim q _{\mathrm {iso}, R} \NR
+\lesssim q _{\mathrm {iso}, R} \\
 %
-\eqsim q _{\mathrm {iso}, B} \NR
+\eqsim q _{\mathrm {iso}, B} \\
 }
@@
 q
-\eqsim 2 \mathsf {e} ^{-N_B /12} \NR
+\eqsim 2 \mathsf {e} ^{-N_B /12} \\
 }

### 2021-01-02 treatise-pdflatex/4_simulation.tex
Front matter passes compilation

@@
 \mathscr {R} \SB {\V {x}}
-\in \mathbb {R} ^{2M} \NR
+\in \mathbb {R} ^{2M} \\
 \mathscr {R} \SB {\V {x}} _{\SB {m}}
 = \startcases
-\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \NR
-\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \NR
-\stopcases \NR
+\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \\
+\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \\
+\stopcases \\
 m' 
-=  0, 1, 2, \ldots, M-1 \NR
+=  0, 1, 2, \ldots, M-1 \\
 }
@@
 \mathscr {R} ^{-1} \SB {\mathscr {R} \SB {\V {x}}}
-=\V {x} \NR
+=\V {x} \\
 }
@@
 \mathscr {R} \SB {\M {A}}
-\in \mathbb {R} ^{2M_1 \D 2M_2} \NR
+\in \mathbb {R} ^{2M_1 \D 2M_2} \\
 \mathscr {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
 \startcases
-\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \NR
-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \NR
--\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \NR
-\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \NR
-\stopcases \NR
+\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
+\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
+-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
+\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
+\stopcases \\
 m_1 
-= 0, 1, 2, \ldots, M_1 -1 \NR
+= 0, 1, 2, \ldots, M_1 -1 \\
 m_2 
-= 0, 1, 2, \ldots, M_2 -1 \NR
+= 0, 1, 2, \ldots, M_2 -1 \\
 }
@@
 = \mathscr {R} \SB {\V {y}}
-\in \mathbb {R} ^{2 N_B^2} \NR
+\in \mathbb {R} ^{2 N_B^2} \\
 %
@@
 = \mathscr {R} \SB {\V {g}}
-\in \mathbb {R} ^{2 N_H^2} \NR
+\in \mathbb {R} ^{2 N_H^2} \\
 %
@@
 = \mathscr {R} \SB {\M {P}}
-\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \NR
+\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
 %
@@
 = \mathscr {R} \SB {\M {P} ^\Adj}
-\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \NR
+\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
 %
@@
 = \mathscr {R} \SB {\V {z}}
-\in \mathbb {R} ^{2 N_B^2} \NR
+\in \mathbb {R} ^{2 N_B^2} \\
 }
@@
 \V {\tilde {y}}
-= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \NR
+= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \\
 }
@@
 \leftarrow \startcases
-   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \NR
-   \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \NR
-   \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \NR
-   \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \NR
-   \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \NR
-\stopcases \NR
+   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \\
+   \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
+   \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
+   \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
+   \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
+\stopcases \\
 }
@@
 \Hat{\V {g}}
-\leftarrow \mathscr {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \NR
+\leftarrow \mathscr {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \\
 }
@@
 \hat {G}
-\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} \NR
+\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} \\
 }
@@
 \hat {\M {H}}
-\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger \NR
+\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger \\
 }
@@
 N_0
-=2 N_H^2, \NR
+=2 N_H^2, \\
 N_2
-=\lfloor 4 \log N_H \rfloor, \NR
+=\lfloor 4 \log N_H \rfloor, \\
 N_1
-=\lfloor \R {N_0 N_2} \rfloor \NR
+=\lfloor \R {N_0 N_2} \rfloor \\
 }
@@
 10^{-4} \frac {1} {0.25} \R {\frac {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
-=0.224 \NR
+=0.224 \\
 }
@@
    {\log_2 {\VNm {\V {h}}_2}}
-} _{\mathsf {avg}}, \NR
+} _{\mathsf {avg}}, \\
 }
@@
 \externalfigure [assorted-square-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
+\caption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-square-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
+\caption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-square-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
+\caption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
+\caption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
+\caption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
 \blank [big]
@@
 \externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
+\caption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
 %
@@
 \externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
+\caption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
 %
@@
 \externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
+\caption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
 %
@@
 \externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}
+\caption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}
 
@@
 \externalfigure [assorted-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
+\caption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
 \blank [big]
@@
 \externalfigure [ddss-narrow-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_B = 10, N_H = 12}, error.}
+\caption {DS, \m {N_B = 10, N_H = 12}, error.}
 \blank [big]
@@
 \externalfigure [ddss-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_B = 15, N_H = 18}, error.}
+\caption {DS, \m {N_B = 15, N_H = 18}, error.}
 \blank [big]
@@
 \externalfigure [ddss-narrow-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_B = 20, N_H = 24}, error.}
+\caption {DS, \m {N_B = 20, N_H = 24}, error.}
 \blank [big]
@@
 \externalfigure [ddss-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_B = 15, N_H = 18}, time.}
+\caption {DS, \m {N_B = 15, N_H = 18}, time.}
 \blank [big]
@@
 \externalfigure [oommpp-square-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 12, N_B = 12}, error.}
+\caption {OMP, \m {N_H = 12, N_B = 12}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-square-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 18, N_B = 18}, error.}
+\caption {OMP, \m {N_H = 18, N_B = 18}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-square-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 24, N_B = 24}, error.}
+\caption {OMP, \m {N_H = 24, N_B = 24}, error.}
 \blank [big]
@@
 \externalfigure [oommpp-square-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 18, N_B = 18}, time.}
+\caption {OMP, \m {N_H = 18, N_B = 18}, time.}
 \blank [big]
@@
 \externalfigure [scatter-ddss-failure.png] [wfactor=300]
-\FigureCaption {A scatter plot of position versus magnitude for a case in which DS failed.}
+\caption {A scatter plot of position versus magnitude for a case in which DS failed.}
 \blank [big]
@@
 \externalfigure [scatter-ddss-success.png] [wfactor=300]
-\FigureCaption {A scatter plot of position versus magnitude for a case in which DS succeeded.}
+\caption {A scatter plot of position versus magnitude for a case in which DS succeeded.}
 \blank [big]
@@
 = \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
-+ \log_2 \log_2 \frac {1} {\e}} C_{\mathrm {step}} \NR
++ \log_2 \log_2 \frac {1} {\e}} C_{\mathrm {step}} \\
 }
@@
 \V {g}_0
-=\V {g}_{\mathrm {LS}} \NR
-= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \NR
+=\V {g}_{\mathrm {LS}} \\
+= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \\
 }
@@
 C_{\mathrm {DS}}
-=\mathscr {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \NR
+=\mathscr {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \\
 }
@@
 \V {g} ^\star
-\approx \V {g} \NR
+\approx \V {g} \\
 }
@@
 \M {P} ^\dagger \M {P}
-\approx I _{N_{H}^2} \NR
+\approx I _{N_{H}^2} \\
 }
@@
    \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
-   -\V {g}} _1} N_H^4 \NR
-=\mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \NR
+   -\V {g}} _1} N_H^4 \\
+=\mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \\
 }
@@
 \mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
-= \s \mathscr {O} \RB {1} \NR
+= \s \mathscr {O} \RB {1} \\
 }
@@
 C_{\mathrm {DS}}
-=\mathscr {O} \SB {N_{H}^6} \NR
+=\mathscr {O} \SB {N_{H}^6} \\
 }
@@
 C_{\mathrm {OMP}}
-=\mathscr {O} \SB {N_H^2 \log N_B} \NR
+=\mathscr {O} \SB {N_H^2 \log N_B} \\
 }
@@
 t_{\mathrm {OMP}} \SB {12} = 0.0119,
-t_{\mathrm {OMP}} \SB {16} = 0.0297, \NR
+t_{\mathrm {OMP}} \SB {16} = 0.0297, \\
 t_{\mathrm {OMP}} \SB {20} = 0.0600,
-t_{\mathrm {OMP}} \SB {24} = 0.155, \NR
+t_{\mathrm {OMP}} \SB {24} = 0.155, \\
 %
 t_{\mathrm {Lasso}} \SB {12} = 0.0436,
-t_{\mathrm {Lasso}} \SB {16} = 0.176, \NR
+t_{\mathrm {Lasso}} \SB {16} = 0.176, \\
 t_{\mathrm {Lasso}} \SB {20} = 0.471,
-t_{\mathrm {Lasso}} \SB {24} = 1.26, \NR
+t_{\mathrm {Lasso}} \SB {24} = 1.26, \\
 %
 t_{\mathrm {DS}} \SB {12} = 0.357,
-t_{\mathrm {DS}} \SB {16} = 2.07, \NR
+t_{\mathrm {DS}} \SB {16} = 2.07, \\
 t_{\mathrm {DS}} \SB {20} = 29.8,
-t_{\mathrm {DS}} \SB {24} = 91.5, \NR
+t_{\mathrm {DS}} \SB {24} = 91.5, \\
 }
@@
 \DispNum {t:P:NH:83} {
-\tilde {t}_{\mathrm {OMP}} \eqsim \mathscr {O} \SB {N_H^{3.6}} \NR
-\tilde {t}_{\mathrm {Lasso}} \eqsim \mathscr {O} \SB {N_H^{4.8}} \NR
-\tilde {t}_{\mathrm {DS}} \eqsim \mathscr {O} \SB {N_H^{8.3}} \NR
+\tilde {t}_{\mathrm {OMP}} \eqsim \mathscr {O} \SB {N_H^{3.6}} \\
+\tilde {t}_{\mathrm {Lasso}} \eqsim \mathscr {O} \SB {N_H^{4.8}} \\
+\tilde {t}_{\mathrm {DS}} \eqsim \mathscr {O} \SB {N_H^{8.3}} \\
 }

### 2021-01-02 treatise-pdflatex/foreword.tex
Front matter passes compilation

@@
-\starttitle [title={Foreword}]
+\chapter* {Foreword}
 
@@
 The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
-The three and half years are punctuated by Bāchí martial art practice session, teaching assistant's preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I too hold dearly.
+The three and half years are punctuated by Bachi martial art practice session, teaching assistant's preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I too hold dearly.
 
@@
 November 4, 2020
-
-\stoptitle

### 2021-01-02 treatise-pdflatex/make.sh

@@ -1,6 +1,13 @@
 #!/usr/bin/env bash
 
+NAME=main
+
 clear
-context main.tex
-cp -f main.pdf main_1.pdf
-cp -f main.pdf main_2.pdf
+#rm ${NAME}.out ${NAME}.log ${NAME}.bcf ${NAME}.aux ${NAME}.run.xml
+pdflatex -halt-on-error ${NAME}.tex
+biber ${NAME}
+pdflatex -halt-on-error ${NAME}.tex
+cp -f ${NAME}.pdf ${NAME}_1.pdf
+cp -f ${NAME}.pdf ${NAME}_2.pdf
+
+

### 2021-01-02 treatise-pdflatex/make.sh
Chap 2 compiles

@@ -3,10 +3,11 @@
 NAME=main
 
 clear
-#rm ${NAME}.out ${NAME}.log ${NAME}.bcf ${NAME}.aux ${NAME}.run.xml
-pdflatex -halt-on-error ${NAME}.tex
+rm ${NAME}.out ${NAME}.log ${NAME}.bcf ${NAME}.aux ${NAME}.run.xml
+pdflatex -halt-on-error ${NAME}
 biber ${NAME}
-pdflatex -halt-on-error ${NAME}.tex
+pdflatex -halt-on-error ${NAME}
+pdflatex -halt-on-error ${NAME}
 cp -f ${NAME}.pdf ${NAME}_1.pdf
 cp -f ${NAME}.pdf ${NAME}_2.pdf
 

### 2021-01-03 treatise-pdflatex/1_introduction.tex
Chap 2 compiles
Conversion: compile chap 1

@@
 To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
-That is, if there is some \m {\mathscr {A} \subseteq \CB {0, \dots, N_p-1}} such that
+That is, if there is some \m {\mathcal {A} \subseteq \CB {0, \dots, N_p-1}} such that
 %
 \DispNum {x:A:x::x:} {
-\V {x} _{\SB {\mathscr {A}}}
+\V {x} _{\SB {\mathcal {A}}}
 =\V {x} \\
@@
 \DispNum {A:A:s::s:} {
-\Nm {\mathscr {A}} \leq s. \\
+\Nm {\mathcal {A}} \leq s. \\
 }
@@
 We introduce some conventions.
-For \m {\mathscr {A} \subseteq \CB {0, \dots, N_p-1}}, denote
+For \m {\mathcal {A} \subseteq \CB {0, \dots, N_p-1}}, denote
 %
 \Disp {
-\V {x}  _{\SB {\mathscr {A}}}
-=\sum _{i \in \mathscr {A}} \V {v} \V {u} _{i} \\
+\V {x}  _{\SB {\mathcal {A}}}
+=\sum _{i \in \mathcal {A}} \V {v} \V {u} _{i} \\
 %
-\M {Q}  _{\SB {\mathscr {A}}}
-=\sum _{i \in \mathscr {A}} \M {Q} _{\SB {:,i}} \\
+\M {Q}  _{\SB {\mathcal {A}}}
+=\sum _{i \in \mathcal {A}} \M {Q} _{\SB {:,i}} \\
 }
 %
-That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\mathscr {A}}.
+That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\mathcal {A}}.
 
@@
 {
-\startitemize[n]
+\begin {itemize}
 \item Input \m {\M {Q} \in \mathbb {R} ^{N_m \D N_p}} and \m {\V {y} \in \mathbb {R} ^{N_m}}.
@@
 \hat {\V {h}}
-\leftarrow \startcases
-\Min {\V {h}'} \MC \VNm {\V {h}'} _1 \\
+\leftarrow \begin {cases}
+\Min {\V {h}'} & \VNm {\V {h}'} _1 \\
 %
-\mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {Q}^\dagger \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \\
-\stopcases \\
+\mathrm {subject} \; \mathrm {to} \quad & \VNm {\M {Q}^\dagger \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \\
+\end {cases} \\
 }
 \item Output \m {\hat {\V {h}}}.
-\stopitemize
+\end {itemize}
 }
@@
 {
-\startitemize[n]
+\begin {itemize}
 %
@@
 }
-\stopitemize
+\end {itemize}
 }

### 2021-01-03 treatise-pdflatex/3_1_sparsity_of_channel.tex
Convert: newcommand, organization
Front matter passes compilation
Conversion: compile chap 1

@@
-\startsection [title={Sparsity of channel}]
+\section {Sparsity of channel}
 
-\startsubsection [title={Norm of array response}]
+\subsection {Norm of array response}
 
 Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity level \m {S} be fixed.
-Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\mathscr {A}}}}, the largest-magnitude \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\mathscr {B}}}} the next \m {s} largest-magnitude components of \m {\V {g}}, and \m {\V {g} _{\SB{\mathscr {C}}}} are the components complement to \m {\V {g} _{\SB{\mathscr {A}}}}.
-For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\mathscr {A}}} =\IP {0,0,-4,0,8}}, \m {\V {g} _{\SB{\mathscr {B}}} =\IP {0,3,0,2,0}}, and \m {\V {g} _{\SB{\mathscr {C}}} =\IP {-1,3,0,2,0}}.
-In this section, the subscripts \m {\mathscr {A}, \mathscr {B}, \mathscr {C}} will bear analogous meaning.
+Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\mathcal {A}}}}, the largest-magnitude \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\mathcal {B}}}} the next \m {s} largest-magnitude components of \m {\V {g}}, and \m {\V {g} _{\SB{\mathcal {C}}}} are the components complement to \m {\V {g} _{\SB{\mathcal {A}}}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\mathcal {A}}} =\IP {0,0,-4,0,8}}, \m {\V {g} _{\SB{\mathcal {B}}} =\IP {0,3,0,2,0}}, and \m {\V {g} _{\SB{\mathcal {C}}} =\IP {-1,3,0,2,0}}.
+In this section, the subscripts \m {\mathcal {A}, \mathcal {B}, \mathcal {C}} will bear analogous meaning.
 
-We hope that \m {\VNm {\V {g} _{\SB{\mathscr {C}}}} _1} is small.
+We hope that \m {\VNm {\V {g} _{\SB{\mathcal {C}}}} _1} is small.
 If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
 Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
-We define, similarly, \m {\V {a} _{\SB{\mathscr {A}}}} and \m {\V {a} _{\SB{\mathscr {C}}}}, with sparsity level \m {s} different from \m {S}.
+We define, similarly, \m {\V {a} _{\SB{\mathcal {A}}}} and \m {\V {a} _{\SB{\mathcal {C}}}}, with sparsity level \m {s} different from \m {S}.
 If \m {N_H} is large, we may forget for a moment that \m {s} is an integer.
@@
 \DispNum {a:2:Ka:22} {
-\NC \VNm {\V {a} \SB {\f} _{\SB{\mathscr {C}}}} _2 ^2
-=\NC \VNm {\RB {\M {K}^\dagger \V {a} \SB {\f}} _{\SB{\mathscr {C}}}} _2 ^2 \NR
+\VNm {\V {a} \SB {\f} _{\SB{\mathcal {C}}}} _2 ^2
+=\VNm {\RB {\M {K}^\dagger \V {a} \SB {\f}} _{\SB{\mathcal {C}}}} _2 ^2 \\
 }
@@
 \DispNum {y':H:f'M:p'p'} {
-\NC \psi \SB {\f, n_H}
-:=\NC \RB {
+\psi \SB {\f, n_H}
+:=\RB {
    \f \; \mathrm {Mod}\; \frac {2\pi} {N_H}
@@
 \mathrm {Mod}\; \RB {2\pi}
-- \pi \NR
+- \pi \\
 }
@@
 \DispNum {y':H:p'::p':} {
-\NC \Nm {\psi \SB {\f, n_H}}
-\leq \NC \pi \NR
+\Nm {\psi \SB {\f, n_H}}
+\leq \pi \\
 }
@@
 \DispNum {D:y':nH:Hy'} {
-\NC D \SB {\psi'}
-:= \NC \sum_{n_H=0}^{N_H-1} \mathsf {e}^{i n_H \psi'} \NR
+D \SB {\psi'}
+:= \sum_{n_H=0}^{N_H-1} \mathsf {e}^{i n_H \psi'} \\
 }
@@
 \DispNum {b:f':Ka:af'} {
-\NC \V {b} \SB {\f}
-=\NC \M {K}^\dagger \V {a} \SB {\f} \NR
+\V {b} \SB {\f}
+=\M {K}^\dagger \V {a} \SB {\f} \\
 }
@@
 \DispNum {K:H:1N:nH} {
-\NC \V {b} \SB {\f} _{\SB {n_H}}
-=\NC \frac {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
+\V {b} \SB {\f} _{\SB {n_H}}
+=\frac {1} {N_H} D \SB {\psi \SB {\f, n_H}} \\
 }
@@
 \DispNum {x:6:si:nx} {
-\NC \Nm {x - \frac {x^3} {6}}
-\leq \NC \Nm {\sin x}. \NR
+\Nm {x - \frac {x^3} {6}}
+\leq \Nm {\sin x}. \\
 }
@@
 \DispNum {D:y':si:y'p'} {
-\NC \Nm {D \SB {\psi'}}
-= \NC \frac {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
+\Nm {D \SB {\psi'}}
+= \frac {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \\
 %
-\NC \leq \NC B \SB {\psi'} \NR
+\leq B \SB {\psi'} \\
 %
-\NC := \NC \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \NR
+:= \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \\
 %
-\NC - \pi \leq \NC \psi' < \pi. \NR
+- \pi \leq \psi' < \pi. \\
 }
@@
 \DispNum {b:1:1N:C1} {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\mathscr {C}}}} _1
-\leq \NC \frac {1} {N_H}
+\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
+\leq \frac {1} {N_H}
 \VNm {
@@
       \V {u} _{n_H'}
-} _{\SB{\mathscr {C}}}
+} _{\SB{\mathcal {C}}}
 } _1
-\NR
+\\
 }
@@
 \DispNum {b:1:1N:NH} {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\mathscr {C}}}} _1
-\leq \NC \frac {1} {N_H} \D \frac {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
+\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
+\leq \frac {1} {N_H} \D \frac {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \\
 %
-\NC = \NC \frac {48} {N_H \pi^3}
-\int _{s /N_H} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
+= \frac {48} {N_H \pi^3}
+\int _{s /N_H} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \\
 %
-\NC =\NC \frac {1} {\pi} \log \frac {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \NR
+=\frac {1} {\pi} \log \frac {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \\
 %
-\NC \eqsim \NC \frac {2} {\pi} \RB {\log N_H - \log s} \NR
+\eqsim \frac {2} {\pi} \RB {\log N_H - \log s} \\
 %
-\NC \leq \NC \frac {2} {\pi} \log N_H \NR
+\leq \frac {2} {\pi} \log N_H \\
 }
@@
 \DispNum {s:s:lo:NH} {
-\NC s
-=\NC \R {\log N_H} \NR
+s
+=\R {\log N_H} \\
 }
@@
 \DispNum {a:2:4N:NH} {
-\NC \VNm {\V {b} \SB {\f} _{\SB{\mathscr {C}}}} _1
-\leq \NC \frac {2} {\pi} \log N_H \NR
+\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
+\leq \frac {2} {\pi} \log N_H \\
 }
@@
 
-\stopsubsection
-
-\startsubsection [title={Norm of angular channel response}]
+\subsection {Norm of angular channel response}
 
@@
 \DispNum {S:S:Ls:s2} {
-\NC S
-=\NC L s^2 \NR
+S
+=L s^2 \\
 }
@@
 \DispNum {g:1:l0:a'1} {
-\NC \VNm {\V {g} _{\SB{\mathscr {C}}}} _1
+\VNm {\V {g} _{\SB{\mathcal {C}}}} _1
 \leq \NC
 \sum _{l=0} ^{L-1} \Nm {\a_l}
-\VNm {\V {b} \SB {\f_l} _{\SB{\mathscr {C}}}} _1
-\VNm {\V {b} \SB {\th_l} _{\SB{\mathscr {C}}}} _1 \NR
+\VNm {\V {b} \SB {\f_l} _{\SB{\mathcal {C}}}} _1
+\VNm {\V {b} \SB {\th_l} _{\SB{\mathcal {C}}}} _1 \\
 %
-\NC \leq \NC
-\VNm {\V {b} \SB {\f_l} _{\SB{\mathscr {C}}}} _1
-\VNm {\V {b} \SB {\th_l} _{\SB{\mathscr {C}}}} _1
-\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
+\leq \NC
+\VNm {\V {b} \SB {\f_l} _{\SB{\mathcal {C}}}} _1
+\VNm {\V {b} \SB {\th_l} _{\SB{\mathcal {C}}}} _1
+\sum _{l=0} ^{L-1} \Nm {\a_l} \\
 %
-\NC \leq \NC
+\leq \NC
 \frac {4} {\pi^2} L \RB {\log N_H}^2 \D
-\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
+\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \\
 }
@@
 \DispNum {E:1:2p':2p'} {
-\NC \mathbb {E} \SB {\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
-=\NC \F{\R {2}} {\R {\pi}} \NR
+\mathbb {E} \SB {\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
+=\F{\R {2}} {\R {\pi}} \\
 }
@@
 \DispNum {P:p':2e:3p'} {
-\NC \mathbb {P} \SB {
+\mathbb {P} \SB {
    \frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
@@
 }
-\leq \NC 2 \exp \SB {- \frac {9L} {\pi}} \NR
+\leq 2 \exp \SB {- \frac {9L} {\pi}} \\
 }
@@
 \DispNum {g:2:12:43} {
-\NC \frac {\VNm {\M {g} _{\SB{\mathscr {C}}}} _1} {\RB {\log N_H}^2}
-\leq \NC \frac {12 \R{2}} {\pi ^{5/2}}
-\leq \frac {4} {3}. \NR
+\frac {\VNm {\M {g} _{\SB{\mathcal {C}}}} _1} {\RB {\log N_H}^2}
+\leq \frac {12 \R{2}} {\pi ^{5/2}}
+\leq \frac {4} {3}. \\
 }
@@
 \DispNum {g:C:4p':NH} {
-\NC \VNm {\M {g} _{\SB{\mathscr {C}}}} _1
-\leq \NC \frac {4} {3} \RB {\log N_H}^2 \NR
+\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
+\leq \frac {4} {3} \RB {\log N_H}^2 \\
 }
@@
 \DispNum {1:p:1N:H3} {
-\NC 1 -p
-\leq \NC 2 \exp \SB {- \frac {9L} {\pi}} \NR
+1 -p
+\leq 2 \exp \SB {- \frac {9L} {\pi}} \\
 }
 }
-
-\stopsubsection
-\stopsection

### 2021-01-03 treatise-pdflatex/4_simulation.tex
Conversion: compile chap 1

@@
 Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
-For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathscr {R} \SB {\V {x}}} of \m {\V {x}} to be
+For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathcal {R} \SB {\V {x}}} of \m {\V {x}} to be
 %
 \DispNum {R:x:R2:M1} {
-\mathscr {R} \SB {\V {x}}
+\mathcal {R} \SB {\V {x}}
 \in \mathbb {R} ^{2M} \\
-\mathscr {R} \SB {\V {x}} _{\SB {m}}
+\mathcal {R} \SB {\V {x}} _{\SB {m}}
 = \startcases
@@
 %
-The injection is obvious, and we may define \m {\mathscr {R} ^{-1}} so that
+The injection is obvious, and we may define \m {\mathcal {R} ^{-1}} so that
 %
 \DispNum {R:1:x::x:} {
-\mathscr {R} ^{-1} \SB {\mathscr {R} \SB {\V {x}}}
+\mathcal {R} ^{-1} \SB {\mathcal {R} \SB {\V {x}}}
 =\V {x} \\
@@
 Accordingly, the following generalization to complex matrices is valid, once we call the ring representation of complex numbers.
-For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathscr {R} \SB {\M {A}}} of \m {\M {A}} to be
+For \m {\M {A} \in \mathbb {C} ^{M_1 \D M_2}}, define real representation \m {\mathcal {R} \SB {\M {A}}} of \m {\M {A}} to be
 %
 \DispNum {R:A:R2:21} {
-\mathscr {R} \SB {\M {A}}
+\mathcal {R} \SB {\M {A}}
 \in \mathbb {R} ^{2M_1 \D 2M_2} \\
-\mathscr {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
+\mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
 \startcases
@@
 \tilde {\V {y}}
-= \mathscr {R} \SB {\V {y}}
+= \mathcal {R} \SB {\V {y}}
 \in \mathbb {R} ^{2 N_B^2} \\
@@
 \tilde {\V {g}}
-= \mathscr {R} \SB {\V {g}}
+= \mathcal {R} \SB {\V {g}}
 \in \mathbb {R} ^{2 N_H^2} \\
@@
 \tilde {\M {P}}
-= \mathscr {R} \SB {\M {P}}
+= \mathcal {R} \SB {\M {P}}
 \in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
@@
 \tilde {\M {P}} ^\Adj
-= \mathscr {R} \SB {\M {P} ^\Adj}
+= \mathcal {R} \SB {\M {P} ^\Adj}
 \in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
@@
 \tilde {\V {z}}
-= \mathscr {R} \SB {\V {z}}
+= \mathcal {R} \SB {\V {z}}
 \in \mathbb {R} ^{2 N_B^2} \\
@@
 \Hat{\V {g}}
-\leftarrow \mathscr {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \\
+\leftarrow \mathcal {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \\
 }
@@
 
-Every Newton step involves a inversion of \m {\mathscr {O} \SB {\M {P} ^\dagger \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
-Since the dimension of \m {\M {P} ^\dagger \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\mathscr {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
+Every Newton step involves a inversion of \m {\mathcal {O} \SB {\M {P} ^\dagger \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
+Since the dimension of \m {\M {P} ^\dagger \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\mathcal {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
 That is, we suppose \m {C_{\mathrm {step}} = N_H^4}.
@@
 C_{\mathrm {DS}}
-=\mathscr {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \\
+=\mathcal {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \\
 }
@@
 C_{\mathrm {DS}}
-=\mathscr {O} \SB {
+=\mathcal {O} \SB {
    \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
    -\V {g}} _1} N_H^4 \\
-=\mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \\
+=\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \\
 }
@@
 \DispNum {O:j:sO:O1} {
-\mathscr {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
-= \s \mathscr {O} \RB {1} \\
+\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
+= \s \mathcal {O} \RB {1} \\
 }
@@
 C_{\mathrm {DS}}
-=\mathscr {O} \SB {N_{H}^6} \\
+=\mathcal {O} \SB {N_{H}^6} \\
 }
@@
 C_{\mathrm {OMP}}
-=\mathscr {O} \SB {N_H^2 \log N_B} \\
+=\mathcal {O} \SB {N_H^2 \log N_B} \\
 }
 %
-Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathscr {O} \SB {N_H^2}}.
+Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathcal {O} \SB {N_H^2}}.
 
-Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\mathrm {Lasso}} =\mathscr {O} \SB {N_H^6}}.
+Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\mathrm {Lasso}} =\mathcal {O} \SB {N_H^6}}.
 
@@
 \DispNum {t:P:NH:83} {
-\tilde {t}_{\mathrm {OMP}} \eqsim \mathscr {O} \SB {N_H^{3.6}} \\
-\tilde {t}_{\mathrm {Lasso}} \eqsim \mathscr {O} \SB {N_H^{4.8}} \\
-\tilde {t}_{\mathrm {DS}} \eqsim \mathscr {O} \SB {N_H^{8.3}} \\
+\tilde {t}_{\mathrm {OMP}} \eqsim \mathcal {O} \SB {N_H^{3.6}} \\
+\tilde {t}_{\mathrm {Lasso}} \eqsim \mathcal {O} \SB {N_H^{4.8}} \\
+\tilde {t}_{\mathrm {DS}} \eqsim \mathcal {O} \SB {N_H^{8.3}} \\
 }

### 2021-01-03 treatise-pdflatex/3_1_sparsity_of_channel.tex
Conversion: compile chap 3

@@
 \VNm {\V {a} \SB {\f} _{\SB{\mathcal {C}}}} _2 ^2
-=\VNm {\RB {\M {K}^\dagger \V {a} \SB {\f}} _{\SB{\mathcal {C}}}} _2 ^2 \\
+=\VNm {\RB {\M {K}^\dagger \V {a} \SB {\f}} _{\SB{\mathcal {C}}}} _2 ^2 
 }
@@
 \mathrm {Mod}\; \RB {2\pi}
-- \pi \\
+- \pi 
 }
@@
 \Nm {\psi \SB {\f, n_H}}
-\leq \pi \\
+\leq \pi 
 }
@@
 D \SB {\psi'}
-:= \sum_{n_H=0}^{N_H-1} \mathsf {e}^{i n_H \psi'} \\
+:= \sum_{n_H=0}^{N_H-1} \mathsf {e}^{i n_H \psi'} 
 }
@@
 \V {b} \SB {\f}
-=\M {K}^\dagger \V {a} \SB {\f} \\
+=\M {K}^\dagger \V {a} \SB {\f} 
 }
@@
 \V {b} \SB {\f} _{\SB {n_H}}
-=\frac {1} {N_H} D \SB {\psi \SB {\f, n_H}} \\
+=\frac {1} {N_H} D \SB {\psi \SB {\f, n_H}} 
 }
@@
 \Nm {x - \frac {x^3} {6}}
-\leq \Nm {\sin x}. \\
+\leq \Nm {\sin x}. 
 }
@@
 %
-- \pi \leq \psi' < \pi. \\
+- \pi \leq \psi' < \pi. 
 }
 %
-Combining \Rf {y':H:f'M:p'p'}, \Rf {K:H:1N:nH}, and \Rf {D:y':si:y'p'} we have
+Combining \eqref {y':H:f'M:p'p'}, \eqref {K:H:1N:nH}, and \eqref {D:y':si:y'p'} we have
 %
@@
 } _1
-\\
 }
@@
 %
-\leq \frac {2} {\pi} \log N_H \\
+\leq \frac {2} {\pi} \log N_H 
 }
@@
 s
-=\R {\log N_H} \\
+=\R {\log N_H} 
 }
@@
 {
-Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in \Rf {b:f':Ka:af'}.
+Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in \eqref {b:f':Ka:af'}.
 Then, for any random instance of \m {\f},
@@
 \VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
-\leq \frac {2} {\pi} \log N_H \\
+\leq \frac {2} {\pi} \log N_H 
 }
@@
 S
-=L s^2 \\
+=L s^2 
 }
@@
 \VNm {\V {g} _{\SB{\mathcal {C}}}} _1
-\leq \NC
+\leq 
 \sum _{l=0} ^{L-1} \Nm {\a_l}
@@
 %
-\leq \NC
+\leq 
 \VNm {\V {b} \SB {\f_l} _{\SB{\mathcal {C}}}} _1
@@
 %
-\leq \NC
+\leq 
 \frac {4} {\pi^2} L \RB {\log N_H}^2 \D
-\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \\
+\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} 
 }
@@
 \mathbb {E} \SB {\frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
-=\F{\R {2}} {\R {\pi}} \\
+=\frac{\R {2}} {\R {\pi}} 
 }
@@
 }
-\leq 2 \exp \SB {- \frac {9L} {\pi}} \\
+\leq 2 \exp \SB {- \frac {9L} {\pi}} 
 }
@@
 \leq \frac {12 \R{2}} {\pi ^{5/2}}
-\leq \frac {4} {3}. \\
+\leq \frac {4} {3}. 
 }
@@
 {
-Let \m {\V {g} \in \mathbb {C} ^{N_H^2}} be defined as in \Rf {g:g:ve:Nh}.
+Let \m {\V {g} \in \mathbb {C} ^{N_H^2}} be defined as in \eqref {g:g:ve:Nh}.
 Then the bound
@@
 \VNm {\M {g} _{\SB{\mathcal {C}}}} _1
-\leq \frac {4} {3} \RB {\log N_H}^2 \\
+\leq \frac {4} {3} \RB {\log N_H}^2 
 }
@@
 1 -p
-\leq 2 \exp \SB {- \frac {9L} {\pi}} \\
+\leq 2 \exp \SB {- \frac {9L} {\pi}} 
 }

### 2021-01-03 treatise-pdflatex/3_2_design_of_beamformers.tex
Conversion: compile chap 3

@@
 =\R {
-   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \\
+   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
 }
@@
 \mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_B}} + \frac {2x} {N_B}}
-\leq \mathsf {e} ^{-x} \\
+\leq \mathsf {e} ^{-x} 
 }
@@
 \mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_B}}}
-\leq \mathsf {e} ^{-x} \\
+\leq \mathsf {e} ^{-x} 
 }
@@
 \Nm {\VNm {\M {W} _B \V {u}} _2 ^2 - 1}
-\geq \d_s \\
+\geq \d_s 
 }
@@
 1 -p
-\leq 2 \mathsf {e} ^{-N_B \R {\d_s} /4} \\
+\leq 2 \mathsf {e} ^{-N_B \R {\d_s} /4} 
 }
@@
 N_R
-\geq \frac {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \\
+\geq \frac {s} {\d_s^2} \RB {\log \frac{1}{\d_s}}^2 \RB {\log \frac{s}{\d_s}}^2 \log N_H 
 }
 %
-Drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \Rf {N:R:sd':NH}, to get the statement below.
+Drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \eqref {N:R:sd':NH}, to get the statement below.
 
@@
 N_R
-\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H \\
+\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H 
 }
@@
 1 -p
-\leq \RB {\frac {\d_s} {N_H s}} ^{1/3} \\
+\leq \RB {\frac {\d_s} {N_H s}} ^{1/3} 
 }
@@
 \VNm {P} _2
-=\VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 \\
+=\VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 
 }
@@
 \M {G}
-=\M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger \\
+=\M {U} \mathrm {diag} \SB {\V {d}'} \M {U} ^\dagger 
 }
@@
 \VNm {\M {G}} _2
-=\VNm {\mathrm {abs} \SB {\V {g}}} _2 \\
+=\VNm {\mathrm {abs} \SB {\V {g}}} _2 
 }
@@
 %
-\eqsim \VNm {\M {G}} _2 \RB {1 +2\d_s} \\
+\eqsim \VNm {\M {G}} _2 \RB {1 +2\d_s} 
 }
-Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} according to the form \Rf {H:H:l0:ql}.
+Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} according to the form \eqref {H:H:l0:ql}.

### 2021-01-03 treatise-pdflatex/3_3_bound_for_error_norm.tex
Conversion: compile chap 1
Conversion: compile chap 3

@@
 \V {d} 
-= \hat {\V {g}} - \V {g} \\
+= \hat {\V {g}} - \V {g} 
 }
@@
 \g
-= 2 \R {\log N_H} \\
+= 2 \R {\log N_H} 
 }
@@
 \DispNum {d:1:dA:C1} {
-\VNm {\V {d} _{\SB{\mathscr {C}}}} _1
-\leq \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
-+\VNm {\V {g} _{\SB{\mathscr {C}}}} _1 \\
+\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
+\leq \VNm {\V {d} _{\SB{\mathcal {A}}}} _1
++\VNm {\V {g} _{\SB{\mathcal {C}}}} _1 
 }
@@
 
-To show this, apply triangle inequality respectively on \m {\mathscr {A}} and \m {\mathscr {C}},
+To show this, apply triangle inequality respectively on \m {\mathcal {A}} and \m {\mathcal {C}},
 %
@@
 \VNm {\V {g}} _1
-- \VNm {\V {d} _{\SB{\mathscr {A}}}} _1
-+ \VNm {\V {d} _{\SB{\mathscr {C}}}} _1
-- \VNm {\V {g} _{\SB{\mathscr {C}}}} _1
+- \VNm {\V {d} _{\SB{\mathcal {A}}}} _1
++ \VNm {\V {d} _{\SB{\mathcal {C}}}} _1
+- \VNm {\V {g} _{\SB{\mathcal {C}}}} _1
 \leq \VNm {\V {g} + \V {d}} _1 \\
 %
-=\VNm {\hat {\V {g}}} _1 \\
+=\VNm {\hat {\V {g}}} _1 
 }
@@
 \VNm {\hat {\V {g}}} _1
-\leq \VNm {\V {g}} _1 \\
+\leq \VNm {\V {g}} _1 
 }
@@
 \VNm {\M {P}^\dagger \M {P} \V {d}} _\infty
-\leq  4 \R {2 \log N_H} \\
+\leq  4 \R {2 \log N_H} 
 }
@@
 1 -p
-\leq N_H^{-2}. \\
+\leq N_H^{-2}. 
 }
@@
 %
-= \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} \\
+= \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} 
 }
@@
 Q\SB {x'}
-\leq \frac {1} {2} \mathsf {e}^{-x'^2 /2} \\
+\leq \frac {1} {2} \mathsf {e}^{-x'^2 /2} 
 }
@@
 Q\SB {2 \R {\log N_H}}
-=\frac {1} {2 N_H^2}. \\
+=\frac {1} {2 N_H^2}. 
 }
@@
 %
-\leq 2\R {2 \log N_H} \\
+\leq 2\R {2 \log N_H} 
 }
 
-Now, by triangle inequality, together with \Rf {Q:h:1N:Nh} and \Rf {P:g:Py:Nh}, we obtain the desired result.
+Now, by triangle inequality, together with \eqref {Q:h:1N:Nh} and \eqref {P:g:Py:Nh}, we obtain the desired result.
 %
@@
 %
-\simeq 2 \R {2 \log N_H} +2 \R {2 \log N_H} \\
+\simeq 2 \R {2 \log N_H} +2 \R {2 \log N_H} 
 }
@@
 \VNm {\V {d}} _2^2
-\leq \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2^2 + \frac {1} {S} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1^2 \\
+\leq \VNm {\V {d} _{\SB {\mathcal {AB}}}} _2^2 + \frac {1} {S} \VNm {\V {d} _{\SB{\mathcal {C}}}} _1^2 
 }
@@
 \VNm {\V {d}} _2
-\leq \VNm {\V {d} _{\SB {\mathscr {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \\
+\leq \VNm {\V {d} _{\SB {\mathcal {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathcal {C}}}} _1 
 }
@@
 %
-\DispNum {d:2:11:C1} {
-\VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
-\leq \frac {1} {1- \d_{2S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
-+ \frac {\tilde {\d}_{S, 2S}} {\RB {1- \d_{2S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \\
+\Disp {
+\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
+\leq \frac {1} {1- \d_{2S}} \VNm {P _{\SB {\mathcal {AB}}}^\intercal P d} _2
++ \frac {\tilde {\d}_{S, 2S}} {\RB {1- \d_{2S}} \R {S}} \VNm {d_{\SB{\mathcal {C}}}} _1 
 }
@@
    \leq \d' \VNm {\V {x}_1} \VNm {\V {x}_2}
-} \\
+} 
 }
@@
 \tilde {\d} _{s_1, s_2}
-\leq \d_{s_1+s_2} \\
+\leq \d_{s_1+s_2} 
 }
@@
 \d_{S}
-\leq \R {L} \RB {\log N_H} ^{1/4} \d_{s} \\
+\leq \R {L} \RB {\log N_H} ^{1/4} \d_{s} 
 }
 %
-So \Rf {d:2:11:C1} becomes
+So we have
 %
@@
 \DispNum {d:2:11:C1} {
-\VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
-\leq \frac {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\mathscr {AB}}}^\intercal P d} _2
-+ \frac {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\mathscr {C}}}} _1 \\
+\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
+\leq \frac {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\mathcal {AB}}}^\intercal P d} _2
++ \frac {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\mathcal {C}}}} _1 
 }
@@
 S
-=L \log N_H \\
+=L \log N_H 
 }
@@
 \d_S
-\leq \frac {1} {8} \\
+\leq \frac {1} {8} 
 }
@@
 \VNm {\V {d}} _2
-\eqsim \mathscr {O} \SB {\R {L} \R {\log N_H}^3} \\
+\eqsim \mathcal {O} \SB {\R {L} \R {\log N_H}^3} 
 }
@@
 1 -p
-\eqsim \mathscr {O} \SB {\mathsf {e} ^{-N_B /12}} \\
+\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_B /12}} 
 }
@@
 
-To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P:d:4N:Nh},
+To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by \eqref {P:d:4N:Nh},
 %
 \DispNum {P:2:PP:NH} {
-\VNm {\M {P} _{\SB {\mathscr {AB}}}^\intercal \M {P} \V {d}} _2
+\VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
 \leq \VNm {\M {P}^\intercal \M {P} \V {d}} _2 \\
@@
 %
-\leq 5.65 \R {\log N_H} \\
+\leq 5.65 \R {\log N_H} 
 }
 %
-By \m {\ell_p}-norm inequality, by the definition of truncation, by \Rf {d:2:11:C1}, and by \Rf {P:2:PP:NH} just above,
+By \m {\ell_p}-norm inequality, by the definition of truncation, by \eqref {d:2:11:C1}, and by \eqref {P:2:PP:NH} just above,
 %
 \DispNum {d:1:Sd:C1} {
-\VNm {\V {d} _{\SB{\mathscr {A}}}} _1
-\leq \R {S} \VNm {\V {d} _{\SB{\mathscr {A}}}} _2 \\
+\VNm {\V {d} _{\SB{\mathcal {A}}}} _1
+\leq \R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \\
 %
-\leq \R {S} \VNm {\V {d} _{\SB{\mathscr {AB}}}} _2 \\
+\leq \R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \\
 %
 \leq 1.21 L \R {\log N_H}^3
-+0.262 \VNm {\V {d} _{\SB{\mathscr {C}}}} _1 \\
++0.262 \VNm {\V {d} _{\SB{\mathcal {C}}}} _1 
 }
 %
-Then, substituting \Rf {g:C:4p':NH} and \Rf {d:1:Sd:C1} above into \Rf {d:1:dA:C1}, we get
+Then, substituting \eqref {g:C:4p':NH} and \eqref {d:1:Sd:C1} above into \eqref {d:1:dA:C1}, we get
 \DispNum {d:C1:16:H2} {
-\VNm {\V {d} _{\SB{\mathscr {C}}}} _1
+\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
 %
-\leq 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 \\
+\leq 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 
 }
 
-Now \Rf {d:2:11:C1} becomes
+Now \eqref {d:2:11:C1} becomes
 %
 \DispNum {d:2:16:H3} {
-\VNm {\V {d} _{\SB{\mathscr {AB}}}} _2
+\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
 %
-\leq 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 \\
+\leq 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 
 }
-and we are ready to estimate \m {\VNm {d} _2}, again by \Rf {d:2:dA:C1}, and plugging in \Rf {d:2:16:H3} and \Rf {d:C1:16:H2}, giving
+and we are ready to estimate \m {\VNm {d} _2}, again by \eqref {d:2:dA:C1}, and plugging in \eqref {d:2:16:H3} and \eqref {d:C1:16:H2}, giving
 \DispNum {d:2:42:NH} {
 \VNm {\V {d}} _2
-\leq 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \\
+\leq 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 
 }
@@
 \chi
-= 8 \R {L} \R {\log N_H}^3 \\
+= 8 \R {L} \R {\log N_H}^3 
 }
@@
 \VNm {\V {d}} _2
-\leq \chi \\
+\leq \chi 
 }
@@
 q
-\eqsim 2 \RB {q _{\mathrm {iso}, B} + q _{\mathrm {iso}, R}} +q _{\mathrm {no}} +q _{\mathrm {sp}} \\
+\eqsim 2 \RB {q _{\mathrm {iso}, B} + q _{\mathrm {iso}, R}} +q _{\mathrm {no}} +q _{\mathrm {sp}} 
 }
-Quoting previous results \Rf {1:p:2e:s4}, \Rf {1:p:ex:d's}, \Rf {1:p:NH:H2}, and \Rf {1:p:1N:H3}, we make some approximation and set
+Quoting previous results \eqref {1:p:2e:s4}, \eqref {1:p:ex:d's}, \eqref {1:p:NH:H2}, and \eqref {1:p:1N:H3}, we make some approximation and set
 \DispNum {q:B:2e:Lp'} {
@@
 q _{\mathrm {sp}}
-\lesssim 2 \mathsf {e} ^{-9L/\pi} \\
+\lesssim 2 \mathsf {e} ^{-9L/\pi} 
 }
@@
 N_R
-\gtrsim 16 L \RB {\log N_H}^2 \\
+\gtrsim 16 L \RB {\log N_H}^2 
 }
@@
 %
-\eqsim q _{\mathrm {iso}, B} \\
+\eqsim q _{\mathrm {iso}, B} 
 }
@@
 q
-\eqsim 2 \mathsf {e} ^{-N_B /12} \\
+\eqsim 2 \mathsf {e} ^{-N_B /12} 
 }

### 2021-01-03 treatise-pdflatex/4_simulation.tex
Conversion: compile chap 3

@@
 
-In this chapter we shall compare \Rf {d:2:OL:H3} with numerical experiments.
+In this chapter we shall compare \eqref {d:2:OL:H3} with numerical experiments.
 For the convex optimization, we choose the Python library CVXPY \cite {DiB16}.
@@
 \mathcal {R} \SB {\V {x}} _{\SB {m}}
-= \startcases
-\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, \MC m =2m' \\
-\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, \MC m =2m'+1 \\
-\stopcases \\
+= \begin {cases}
+\mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, & m =2m' \\
+\mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, & m =2m'+1 \\
+\end {cases} \\
 m' 
-=  0, 1, 2, \ldots, M-1 \\
+=  0, 1, 2, \ldots, M-1 
 }
@@
 \mathcal {R} ^{-1} \SB {\mathcal {R} \SB {\V {x}}}
-=\V {x} \\
+=\V {x} 
 }
@@
 \mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
-\startcases
-\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
--\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
-\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, \MC \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
-\stopcases \\
+\begin {cases}
+\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
+\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'} \\
+-\mathfrak {Im} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'+1} \\
+\mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
+\end {cases} \\
 m_1 
@@
 m_2 
-= 0, 1, 2, \ldots, M_2 -1 \\
+= 0, 1, 2, \ldots, M_2 -1 
 }
@@
 = \mathcal {R} \SB {\V {z}}
-\in \mathbb {R} ^{2 N_B^2} \\
+\in \mathbb {R} ^{2 N_B^2} 
 }
@@
 %
-\DispNum {y:y:Pg:gz} {
+\Disp {
 \V {\tilde {y}}
-= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} \\
+= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
 }
@@
 {
-\startitemize[n]
+\begin {itemize}
 \item Input \m{\M {P} \in \mathbb {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \mathbb {C} ^{ N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
 %
-\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \Rf {y:y:Ry:Ny}.
+\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \eqref {y:y:Ry:Ny}.
 %
@@
 \hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
-\leftarrow \startcases
-   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  \MC \IP {\V {1}, \tilde {\V {f}}'} \\
-   \mathrm {subject} \; \mathrm {to} \MC \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
-   \MC - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
-   \MC \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
-   \MC - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
-\stopcases \\
+\leftarrow \begin {cases}
+   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  & \IP {\V {1}, \tilde {\V {f}}'} \\
+   \mathrm {subject} \; \mathrm {to} & \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
+   & - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
+   & \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
+   & - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
+\end {cases} 
 }
@@
 \Hat{\V {g}}
-\leftarrow \mathcal {R} ^{-1} \SB {\Hat{\T{\V {g}}}} \\
+\leftarrow \mathcal {R} ^{-1} \SB {\Hat{\T{\V {g}}}} 
 }
@@
 \hat {G}
-\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} \\
+\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} 
 }
@@
 \hat {\M {H}}
-\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger \\
+\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger 
 }
 \item Output \m {\hat {\M {H}}}.
-\stopitemize
+\end {itemize}
 }
@@
 {
-\startitemize[n]
+\begin {itemize}
 \item Let \m {\g_{\mathrm {DS}} \geq 0} be given, and \m {\M {P}}
@@
 N_1
-=\lfloor \R {N_0 N_2} \rfloor \\
+=\lfloor \R {N_0 N_2} \rfloor 
 }
@@
 \item Apply Moore–Penrose inverse to \m {\V {y}, \M {P} _2} to get \m {\hat {\V {g}}_2}, which corresponds to \m {\hat {\V {g}}}.
-\stopitemize
+\end {itemize}
 }
@@
 10^{-4} \frac {1} {0.25} \R {\frac {5 \D 10^9 \D 4 \pi \D 1500} {3 \D 10^8}}
-=0.224 \\
+=0.224 
 }
@@
 On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
-Unfortunately, this is very far from achieving the ideal values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
+Unfortunately, this is very far from achieving the ideal values \eqref {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
 
@@
    {\log_2 {\VNm {\V {h}}_2}}
-} _{\mathsf {avg}}, \\
+} _{\mathsf {avg}}, 
 }
@@
 
-\blank [big]
-\externalfigure [assorted-square-small-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-square-small-error.png}
 \caption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [assorted-square-medium-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-square-medium-error.png}
 \caption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [assorted-square-big-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-square-big-error.png}
 \caption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-narrow-small-error.png}
 \caption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-narrow-medium-error.png}
 \caption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-narrow-big-error.png}
 \caption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
+\end {figure}
 %
-\blank [big]
-\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-wide-small-error.png}
 \caption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
+\end {figure}
 %
-\blank [big]
-\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-wide-medium-error.png}
 \caption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
+\end {figure}
 %
-\blank [big]
-\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-wide-big-error.png}
 \caption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}
+\end {figure}
 
@@
 %
-\blank [big]
-\externalfigure [assorted-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {assorted-narrow-medium-time.png}
 \caption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
-\blank [big]
+\end {figure}
 
@@
 %
-\blank [big]
-\externalfigure [ddss-narrow-small-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {ddss-narrow-small-error.png}
 \caption {DS, \m {N_B = 10, N_H = 12}, error.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [ddss-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {ddss-narrow-medium-error.png}
 \caption {DS, \m {N_B = 15, N_H = 18}, error.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [ddss-narrow-big-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {ddss-narrow-big-error.png}
 \caption {DS, \m {N_B = 20, N_H = 24}, error.}
-\blank [big]
+\end {figure}
 %
@@
 %
-\blank [big]
-\externalfigure [ddss-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {ddss-narrow-medium-time.png}
 \caption {DS, \m {N_B = 15, N_H = 18}, time.}
-\blank [big]
+\end {figure}
 
@@
 %
-\blank [big]
-\externalfigure [oommpp-square-small-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {oommpp-square-small-error.png}
 \caption {OMP, \m {N_H = 12, N_B = 12}, error.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [oommpp-square-medium-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {oommpp-square-medium-error.png}
 \caption {OMP, \m {N_H = 18, N_B = 18}, error.}
-\blank [big]
+\end {figure}
 %
-\blank [big]
-\externalfigure [oommpp-square-big-error.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {oommpp-square-big-error.png}
 \caption {OMP, \m {N_H = 24, N_B = 24}, error.}
-\blank [big]
+\end {figure}
 %
@@
 %
-\blank [big]
-\externalfigure [oommpp-square-medium-time.png] [wfactor=fit, hfactor=fit]
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {oommpp-square-medium-time.png}
 \caption {OMP, \m {N_H = 18, N_B = 18}, time.}
-\blank [big]
+\end {figure}
 
@@
 
-\blank [big]
-\externalfigure [scatter-ddss-failure.png] [wfactor=300]
+\bigskip
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {scatter-ddss-failure.png}
 \caption {A scatter plot of position versus magnitude for a case in which DS failed.}
-\blank [big]
-
-\blank [big]
-\externalfigure [scatter-ddss-success.png] [wfactor=300]
+\end {figure}
+%
+\begin {figure} [hbt]
 \caption {A scatter plot of position versus magnitude for a case in which DS succeeded.}
-\blank [big]
+\includegraphics [width = \textwidth] {scatter-ddss-success.png}
+\end {figure}
+\bigskip
 
@@
 = \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
-+ \log_2 \log_2 \frac {1} {\e}} C_{\mathrm {step}} \\
++ \log_2 \log_2 \frac {1} {\e}} C_{\mathrm {step}} 
 }
@@
 =\V {g}_{\mathrm {LS}} \\
-= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} \\
+= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} 
 }
@@
 C_{\mathrm {DS}}
-=\mathcal {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 \\
+=\mathcal {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 
 }
@@
 \V {g} ^\star
-\approx \V {g} \\
+\approx \V {g} 
 }
@@
 \M {P} ^\dagger \M {P}
-\approx I _{N_{H}^2} \\
+\approx I _{N_{H}^2} 
 }
 %
-Thus, by \Rf {g:0:gL:Py}, \Rf {C:S:Og:g1}, and \Rf {g:g:g;:;g},
+Thus, by \eqref {g:0:gL:Py}, \eqref {C:S:Og:g1}, and \eqref {g:g:g;:;g},
 %
@@
    -\V {g}} _1} N_H^4 \\
-=\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 \\
+=\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 
 }
@@
 \mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
-= \s \mathcal {O} \RB {1} \\
+= \s \mathcal {O} \RB {1} 
 }
@@
 C_{\mathrm {DS}}
-=\mathcal {O} \SB {N_{H}^6} \\
+=\mathcal {O} \SB {N_{H}^6} 
 }
@@
 C_{\mathrm {OMP}}
-=\mathcal {O} \SB {N_H^2 \log N_B} \\
+=\mathcal {O} \SB {N_H^2 \log N_B} 
 }
@@
 t_{\mathrm {DS}} \SB {20} = 29.8,
-t_{\mathrm {DS}} \SB {24} = 91.5, \\
+t_{\mathrm {DS}} \SB {24} = 91.5, 
 }
@@
 \tilde {t}_{\mathrm {Lasso}} \eqsim \mathcal {O} \SB {N_H^{4.8}} \\
-\tilde {t}_{\mathrm {DS}} \eqsim \mathcal {O} \SB {N_H^{8.3}} \\
+\tilde {t}_{\mathrm {DS}} \eqsim \mathcal {O} \SB {N_H^{8.3}} 
 }

### 2021-01-03 treatise-pdflatex/functions.py

@@ -1,0 +1,566 @@
+import numpy as np
+import scipy as sp
+import matplotlib.pyplot as plt
+import os
+import time
+import random
+
+import constants as cst
+import classes as cls
+import cvxpy as cp
+
+def execute (ver):
+    arr_s_g = (cst.S_G_INIT (ver)
+            * cst.VALUE_SPACING_S_G (ver)
+            ** (np.array (range (cst.NUM_S_G (ver)))))
+    lst_h_g = list (cst.VALUE_SPACING_H_G (ver)
+            ** (np.array (range (cst.NUM_H_G (ver)))))
+    lst_g_g = list (cst.VALUE_SPACING_G_G (ver)
+            ** (np.array (range (cst.NUM_G_G (ver)))))
+
+    lst_legend = []
+    lst_num_rep_meth = []
+    lst_meth = [] # arguments: (est, s_g)
+
+    if (True):
+        # Least Square
+        lst_legend.append ("LS")
+        lst_num_rep_meth.append (cst.NUM_REP_LLSS (ver))
+        lst_meth.append (lambda x, y: llss (x, ver))
+
+    if (ver.focus == cls.Focus.ASSORTED):
+        # Lasso
+        lst_legend.append ("Lasso")
+        lst_num_rep_meth.append (cst.NUM_REP_LASSO (ver))
+        lst_meth.append (lambda x, y: lasso_qqpp (x, cst.G_G_LASSO (ver) * y, ver))
+
+    if (ver.focus == cls.Focus.ASSORTED or ver.focus == cls.Focus.OOMMPP):
+        # Orthogonal Matching Pursuit: fixed iteration number
+        lst_legend.append ("OMP, $N_H$ times")
+        lst_num_rep_meth.append (cst.NUM_REP_OOMMPP (ver))
+        lst_meth.append (lambda x, y: oommpp_fixed_times (x, cst.NN_HH (ver), ver))
+
+        # Orthogonal Matching Pursuit: limited l-2 norm
+        for h_g in lst_h_g:
+            lst_legend.append ("OMP, $l_2$-norm, $\eta$ = "
+                    + '%.2f' % h_g + "$\sigma$")
+            lst_num_rep_meth.append (cst.NUM_REP_OOMMPP (ver))
+            lst_meth.append (
+                lambda x, y, h_g = h_g:
+                oommpp_2_norm (x, h_g * cst.H_G_OOMMPP_2_NORM (ver) * y, ver))
+
[…]

### 2021-01-03 treatise-pdflatex/main.py

@@ -1,0 +1,24 @@
+#! /usr/bin/env python3
+
+import os
+
+import functions as fct
+import classes as cls
+
+# example
+NUM_REP_FIG = 6 # example
+for i in range (NUM_REP_FIG):
+    print (
+        "~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~\n",
+        "Figure", i,
+        "~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~ ~\n"
+    )
+    idx_hold = i + 1
+    # example
+    ver = cls.Version (
+        cls.Focus.ASSORTED,
+        cls.Size.BIG,
+        cls.Ratio.WIDE,
+        str (idx_hold))
+
+    fct.execute (ver)

### 2021-01-03 treatise-pdflatex/make.sh

@@ -3,7 +3,7 @@
 NAME=main
 
 clear
-rm ${NAME}.out ${NAME}.log ${NAME}.bcf ${NAME}.aux ${NAME}.run.xml
+#rm ${NAME}.out ${NAME}.log ${NAME}.bcf ${NAME}.aux ${NAME}.run.xml
 pdflatex -halt-on-error ${NAME}
 biber ${NAME}
 pdflatex -halt-on-error ${NAME}

### 2021-01-25 treatise-context/1_introduction.tex
Include Lasso literature

@@
 
-Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification \cite [RSM13].
-With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain.
-The appeal of MIMO includes multiplexing gain (parallel transmission of data), diversity gain (redundant transmission with space-time coding), and antenna gain (suitable beamforming to improve the signal level).
-Besides, the millimeter wave (mm-wave) is suggested, since its smaller wavelength (and thus higher frequency) makes wider bands available.
-Moreover the antennae may be closer-spaced, allowing us to increase their number.
+Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification.
+With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain, by virtue of either parallel transmission of data, redundant transmission, or beamforming which improves the signal level.
+Besides, the millimeter wave (mm-wave) is adopted, since its smaller wavelength (and thus higher frequency) makes wider bands available.
+Moreover the antennae may be closer-spaced, allowing us to increase their number \cite [RSM13].
+However, also because of the larger antennae array, and larger noise corruption in higher frequency, estimation of MIMO channel state information gives rise to higher complexity, and hence higher hardware overhead and power consumption.
+Indeed, RF chains are more expensive and power consuming, so there is a growing attention on hybrid beamforming, where there are not fewer RF chain than the antennae.
 
-However, MIMO also gives rise to higher complexity, hence higher hardware overhead and power consumption.
-To obtain channel state information (so that channel capacity can be known for instance), new algorithms have to address these issues.
-Not only is the channel estimation difficult, due to a large antennae array, but the transmission in higher frequency is subject to noise corruption too.
-As a result, conventional training-based algorithms lead to considerable time and space complexity.
+If we consider a slow varying MIMO channel for simplicity, in terms of a channel representation, to estimate the channel is to determine the parameters of the representation.
+It amounts to invert a linear system whose dimension is the number of antennae, as we shall see in chapter 2 in more detail.
+In this case, it is pointed out that conventional training based algorithms are not very effective.
 
@@
 
-If we consider a slow varying MIMO channel for simplicity, in terms of a channel representation, to estimate the channel is to determine the parameters of the representation.
-We shall see it amounts to invert a linear system whose dimension is the number of antennae, which is not very effective.
 Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
@@
 But, even if we are sure that the sparse basis exists, its construction is another undertaking.
+In our settings, it is not trivially obvious that hybrid beamforming structure fits the compressive sensing problem, and a method to generating the sensing matrix and pilot vectors in the estimation stage has to be devised and justified.
+
+Compressive sensing approaches can be divided into two categories, the convex programming approach, and greedy approach \cite [RDD18].
+We will discuss one from each in more details: Dantzig Selector and Orthogonal Matching Pursuit.
+
+\stopsection
+
+\startsection [title={The Dantzig Selector}]
 
@@
 
-Candès and Tao \cite [Can05], one of the earlier investigations on compressive sensing, showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability.
+Candès and Tao \cite [Can05] showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability.
 
@@
 Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, while the accuracy is critical to the diagnosis too \cite [CaT07].
-
-\stopsection
-
-\startsection [title={The Dantzig Selector}]
 
@@
 For concreteness, say \m {\V {z}} is an i.i.d.\ normalized random normal vector.
-If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible under high probability.
+If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig selector (DS), recovery under the noisy case is again possible under high probability.
 
@@
 
-Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
-An early attempt to apply compressive sensing was Bajwa et.\ al.\ \cite [BHS10], where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
+Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
+Bajwa et.\ al.\ \cite [BHS10] used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
 The accompanying note by the same researchers \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.
+
+Some instead applied least absolute shrinkage and selection operator (Lasso).
+Indeed, it can be shown that Lasso and DS have similar behavior \cite [AsR10].
+
+Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite [LLL17].
+Destino, Juntti, and Nagaraj used an adaptive Lasso \cite [DJN15], in which they jointly optimize the sensing matrix and pilot vectors.
+Vlachos, Alexandropoulos, and Thompson \cite [VAT19] used Lasso on hybrid beamforming with an additional random spatial sampling device.
 
@@
 
-At the same time, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal in an underdetermined system.
+In addition to convex programming approaches, Tropp and Gilbert \cite [TrG07b] suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal in an underdetermined system.
 Again consider the situation of \Rf {y:y:Qx:xz}.
@@
 
-OMP has since been pervasively used for channel sensing.
+OMP has since been commonly used for channel estimation.
 Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles.
 Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamformers based on nonuniform fixed set of angles.
-Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals.
 Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers of stationary channel gain.
 Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the effective beamformer serves as sensing matrix, based on a designed set of angles.
-Manoj and Kannu \cite [MaK17] studied the sparse condition on submatrices of the signal for successful reconstruction.
-Gurbuz, Yapici, and Guvenc \cite [GYG18] introduced perturbation on the angles which the sensing matrix based on.
-Panayirci et.\ al.\ \cite [PAU19] proposed a concatenation of max-likelihood estimation of model parameters, and maximum-a-posteriori estimation of channel gains, by virtue of OMP.
+Gao, Dai, and Wang proposed a variant which we have the assumption of spatially common sparsity \cite [GDW15].
 
@@
 
-The literature on channel estimation favors OMP for its low complexity, but we wonder how greedy algorithms, such as OMP, compare to convex programs, such as DS.
-It might be that greedy algorithms trade precision for complexity, and that the opposite is true of convex programs.
+Do greedy algorithms trade precision for complexity, and is the opposite true of convex programs?
+In this treatise, we consider a hybrid structure with uniform linear array as in Lee, Gil, and Lee \cite [LGL16].
+They proposed a beamformer shown to be optimal, jointly designed on both ends by a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
+Still, it is not clear whether the approximated scheme is optimal.
 
-In this treatise, we consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite [LGL16].
-They proposed a beamformer shown to be optimal, jointly designed on both ends by a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
-Is the approximated design still optimal, or are the angles of sensing matrix not sufficiently precise?
-
+We illustrate that, with randomly generated beamformers, DS estimates the channel with better accuracy than other methods.
+The setting is more general than \cite [LLL17] and more simple than \cite [VAT19], and the beamformer generation less complicated than \cite [DJN15].
 In chapter 2 we shall see that our proposed effective beamformer has RIP for high probability, which may serve as the sensing matrix for DS.
@@
 Numerical results show that in our problem configuration, DS is superior to other methods.
-Indeed, DS is much more accurate than the least square, and both OMP and Lasso often fails.
+
+Since DS is more accurate than the least square, OMP, and Lasso, it may be used when precision is crucial, possibly in combination of these lower-complexity methods.
+It shall be useful when the ratio of the antenna and RF chain is larger, or when there does not allow many stage of estimation, that is, when the observable data is less sufficient.
 

### 2021-01-26 treatise-context/1_introduction.tex
Change parameters `N_{B,t}` and `N_{B,r}`

@@
 
-Since DS is more accurate than the least square, OMP, and Lasso, it may be used when precision is crucial, possibly in combination of these lower-complexity methods.
-It shall be useful when the ratio of the antenna and RF chain is larger, or when there does not allow many stage of estimation, that is, when the observable data is less sufficient.
-
 \stopsection

### 2021-01-26 treatise-context/2_problem_setting.tex
Chap 2 compiles
Conversion: compile chap 3
Change parameters `N_{B,t}` and `N_{B,r}`

--- 2020-12-19 treatise/2_problem_setting.tex
@@
 %
-\DispNum {H:H:l0:ql} {
+\DispNum {H:H:l0:NH} {
 \NC \M {H}
@@
 Each end consists of both digital and analog precoders and combiners.
-In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_R \D N_B}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_R}}.
-Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_B \D  N_R}}.
+In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_{B,t} \D N_{B,t}}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_{B,t}}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_{B,r} \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_{B,r} \D  N_{B,r}}}.
 
@@
 %
-\NC n_R
-= \NC 0, \dots N_R-1 \NR
+\NC n_{B,t}
+= \NC 0, \dots N_{B,t}-1 \NR
+%
+\NC n_{B,r}
+= \NC 0, \dots N_{B,r}-1 \NR
 }
@@
 \DispNum {N:H:NY:NY} {
-\NC N_H \gg \NC N_R \NR
+\NC N_H \gg \NC N_{B,t}, N_{R,t} \NR
 %
-\NC N_R \gg \NC N_B \NR
+\NC N_{B,t}, N_{R,t} \gg \NC N_B \NR
 }
@@
 %
-\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D N_B}},
-\m {\M {F} _R \in \NC \MB {C} ^{N_H \D N_R}},
-\m {\M {W} _R \in \NC \MB {C} ^{N_R \D N_H}},
-\m {\M {W} _B \in \NC \MB {C} ^{N_B \D N_R}},
-and \m {\M {Y} \in \NC \MB {C} ^{N_B \D N_B}}.
+\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_{B,t} \D N_{B,t}}},
+\m {\M {F} _R \in \NC \MB {C} ^{N_H \D N_{B,t}}},
+\m {\M {W} _R \in \NC \MB {C} ^{N_{B,r} \D N_H}},
+\m {\M {W} _B \in \NC \MB {C} ^{N_{B,r} \D N_{B,r}}},
+and \m {\M {Y} \in \NC \MB {C} ^{N_{B,r} \D N_{B,t}}}.
 %
-\item Find \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
+\item Find \m {\M {P} \in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
 %
@@
 %
-\DispNum {G:G:ve:1g} {
+\Disp {
 \NC \Hat {\M {G}}
@@
 %
-\DispNum {H:H:KG:GK} {
+\Disp {
 \NC \Hat {\M {H}}

### 2021-01-26 treatise-context/3_2_design_of_beamformers.tex
Change parameters `N_{B,t}` and `N_{B,r}`

--- 2020-12-19 treatise/3_2_design_of_beamformers.tex
@@
-\startsection [title={Design of beamformers}]
+\startsection [title={Generation of beamformers}]
 
-\startsubsection [title={Design of beamformers}]
+\startsubsection [title={Generation of beamformers}]
 
@@
 Use \m {\chi _{i,j}} to denote independent complex standard normal random variables.
-It follows that
+It follows that (respectively for \m {N_{B,r}})
 %
@@
 =\NC \R {
-   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \F {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
+   \sum _{i=0} ^{N_{B,t}-1} \VNm {\sum _{j=0} ^{N_{B,t}-1} \F {1} {\R{N_{B,t}}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
 }
@@
 \DispNum {P:x:ex:ex} {
-\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_B}} + \F {2x} {N_B}}
+\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_{B,t}}} + \F {2x} {N_{B,t}}}
 \leq \NC \Ss {e} ^{-x} \NR
@@
 \DispNum {P:x:ex:ex!} {
-\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_B}}}
+\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_{B,t}}}}
 \leq \NC \Ss {e} ^{-x} \NR
@@
 %
-With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for overall failure probability.
+With substitution \m {\d_s =16x^2 /N_{B,t}^2}, the upper tail can be simplified with \m {x <N_{B,t}}, and we get the following bound for overall failure probability.
 
@@
 \NC 1 -p
-\leq \NC 2 \Ss {e} ^{-N_B \R {\d_s} /4} \NR
+\leq \NC 2 \Ss {e} ^{-N_{B,t} \R {\d_s} /4} \NR
 }
@@
 We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
-The conclusions, 
-Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
+Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP .
+In conclusion, (respectively for \m {N_{B,r}})
 %
 \DispNum {N:R:sd':NH} {
-\NC N_R
+\NC N_{B,t}
 \geq \NC \F {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
@@
 \DispNum {N:R:sd'NH} {
-\NC N_R
+\NC N_{B,t}
 \geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR

### 2021-01-26 treatise-context/4_simulation.tex
Conversion: compile chap 3
Change parameters `N_{B,t}` and `N_{B,r}`

@@
 %
-\DispNum {y:y:Pg:gz} {
+\Disp {
 \NC \V {\T {y}}
@@
 We take \m {N_H} to be \m {12, 18, 24}, respectively.
-For assorted plots, two series of plots are simulated.
-The first series for \m {N_B = N_H}, giving \m {12, 18, 24}.
-The second series for \m {N_B = \lfloor 5 N_H /6 \rfloor}, giving \m {10, 15, 20}.
-The third series for \m {N_B = \lfloor 2 N_H /3 \rfloor}, giving \m {8, 12, 16}.
-For plots of OMP only, we consider \m {N_B = \lfloor N_H \rfloor}.
-For plots of DS only, we consider \m {N_B = \lfloor 5 N_H /6 \rfloor}.
-On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
+For assorted plots, three series of plots are simulated.
+The first series for \m {N_{B,t} = N_H/3} and \m {N_{B,r} = N_H/4}.
+The second series for \m {N_{B,t} = N_H/4} and \m {N_{B,r} = N_H/3}.
+The third series for \m {N_{B,t} = N_H/3} and \m {N_{B,r} = N_H/3}.
 Unfortunately, this is very far from achieving the ideal values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.

### 2021-01-26 treatise-context/5_conclusion.tex
Change parameters `N_{B,t}` and `N_{B,r}`

@@
 To do so, we try the Dantzig Selector (DS) for channel estimation, rather than the more commonly used Orthogonal Matching Pursuit (OMP).
-We exploited the sparsity of spatial frequency domain, and generalized DS for complex vectors.
+We exploited the sparsity of spatial frequency domain, and justified the RIP of effective beamformer for the hybrid structure.
 We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
-
 DS is cast into an linear program, which help reduce complexity.
 Simulation is done, and DS's performance is compared to OMP, Lasso, and LS, and we see that DS indeed outperforms other methods.
-Despite of its higher complexity, in the low noise scenario, DS can be \m {10} times more accurate, and the gain of spectral efficiency may justify its use.
+
+DS is more accurate but has higher complexity, so it may be used (possibly in combination of other methods) in the scenario that precision is crucial, and when the observable data is less sufficient.
+For example, when the ratio of the antenna and RF chain is larger, or when the application does not allow many stages of estimation, it might be the case that only DS can recover successfully.
 

### 2021-02-07 treatise-context/4_simulation.tex
New figures via BPDN

@@
 
-\startsubsection [title={Plots of assorted methods}]
+\startsubsection [title={Plots of \m {N_H = 6}}]
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H} and \m {N_B}.
-
-\blank [big]
-\externalfigure [assorted-square-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
-\blank [big]
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,t}}.
 %
 \blank [big]
-\externalfigure [assorted-square-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
-\blank [big]
+\externalfigure [error-small-square-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
 %
 \blank [big]
-\externalfigure [assorted-square-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
-\blank [big]
+\externalfigure [error-small-tall-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
 %
 \blank [big]
-\externalfigure [assorted-narrow-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
-\blank [big]
+\externalfigure [error-small-wide-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {2} stages, error.}
 %
 \blank [big]
-\externalfigure [assorted-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
-\blank [big]
+\externalfigure [error-small-square-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
 %
 \blank [big]
-\externalfigure [assorted-narrow-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
+\externalfigure [error-small-tall-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
 %
 \blank [big]
-\externalfigure [assorted-wide-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
-%
-\blank [big]
-\externalfigure [assorted-wide-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
-%
-\blank [big]
-\externalfigure [assorted-wide-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}
-
-As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
-%
-\blank [big]
-\externalfigure [assorted-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
-\blank [big]
+\externalfigure [error-small-wide-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {4} stages, error.}
 
@@
 
-\startsubsection [title={Plots of DS only}]
+\startsubsection [title={Plots of \m {N_H = 12}}]
 
-Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
-Here, \m {\T {\chi}} is shown too.
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,t}}.
 %
 \blank [big]
-\externalfigure [ddss-narrow-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_B = 10, N_H = 12}, error.}
-\blank [big]
+\externalfigure [error-medium-square-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
 %
 \blank [big]
-\externalfigure [ddss-narrow-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_B = 15, N_H = 18}, error.}
-\blank [big]
+\externalfigure [error-medium-tall-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
 %
 \blank [big]
-\externalfigure [ddss-narrow-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_B = 20, N_H = 24}, error.}
-\blank [big]
-%
-As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
+\externalfigure [error-medium-wide-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {2} stages, error.}
 %
 \blank [big]
-\externalfigure [ddss-narrow-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {DS, \m {N_B = 15, N_H = 18}, time.}
+\externalfigure [error-medium-square-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
+%
 \blank [big]
+\externalfigure [error-medium-tall-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
+%
+\blank [big]
+\externalfigure [error-medium-wide-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {4} stages, error.}
+
+\startsubsection [title={Plots of \m {N_H = 18}}]
+
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,t}}.
+%
+\blank [big]
+\externalfigure [error-big-square-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {2} stages, error.}
+%
+\blank [big]
+\externalfigure [error-big-tall-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 9, N_H = 18}, with \m {2} stages, error.}
+%
+\blank [big]
+\externalfigure [error-big-wide-two.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 6, N_H = 18}, with \m {2} stages, error.}
+%
+\blank [big]
+\externalfigure [error-big-square-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {4} stages, error.}
+%
+\blank [big]
+\externalfigure [error-big-tall-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 9, N_H = 18}, with \m {4} stages, error.}
+%
+\blank [big]
+\externalfigure [error-big-wide-four.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 6, N_H = 18}, with \m {4} stages, error.}
 
@@
 
-\startsubsection [title={Plots of OMP only}]
+\startsubsection [title={Plots of time}]
 
-Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
+Regarding runtime statistics, we only plot the case where \m {N_{B,t} = N_{B,r} = N_H /2} with \m {2} stages.
 
-%
 \blank [big]
-\externalfigure [oommpp-square-small-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 12, N_B = 12}, error.}
+\externalfigure [small-square-two-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, error.}
 \blank [big]
-%
+
 \blank [big]
-\externalfigure [oommpp-square-medium-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 18, N_B = 18}, error.}
+\externalfigure [medium-square-two-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, error.}
 \blank [big]
-%
+
 \blank [big]
-\externalfigure [oommpp-square-big-error.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 24, N_B = 24}, error.}
-\blank [big]
-%
-As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
-%
-\blank [big]
-\externalfigure [oommpp-square-medium-time.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {OMP, \m {N_H = 18, N_B = 18}, time.}
+\externalfigure [big-square-four-time.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, error.}
 \blank [big]

### 2021-02-07 treatise-context/functions.py

@@ -1,566 +1,460 @@
 import numpy as np
 import scipy as sp
+import cvxpy as cp
 import matplotlib.pyplot as plt
+
 import os
 import time
 import random
 
 import constants as cst
 import classes as cls
-import cvxpy as cp
 
 def execute (ver):
-    arr_s_g = (cst.S_G_INIT (ver)
-            * cst.VALUE_SPACING_S_G (ver)
-            ** (np.array (range (cst.NUM_S_G (ver)))))
-    lst_h_g = list (cst.VALUE_SPACING_H_G (ver)
-            ** (np.array (range (cst.NUM_H_G (ver)))))
-    lst_g_g = list (cst.VALUE_SPACING_G_G (ver)
-            ** (np.array (range (cst.NUM_G_G (ver)))))
+   cnt_met = 0
+   cnt_chan = 0
+   lst_lst_err = [] # each s_g, each method
+   lst_lst_time = [] # each s_g, each method
+   lst_met = cst.LST_MET ()
 
-    lst_legend = []
-    lst_num_rep_meth = []
-    lst_meth = [] # arguments: (est, s_g)
+   lst_chan_met = np.array (list (map (cst.NUM_CHAN_MET, lst_met)))
+   num_chan_tot = cst.NUM_S_G () * lst_chan_met.sum ()
 
-    if (True):
-        # Least Square
-        lst_legend.append ("LS")
-        lst_num_rep_meth.append (cst.NUM_REP_LLSS (ver))
-        lst_meth.append (lambda x, y: llss (x, ver))
+   time_tot_start = time.time ()
+   for i_s_g in range (cst.NUM_S_G ()):
+      s_g = cst.S_G_INIT () * (cst.SCALE_S_G () ** i_s_g)
+      print ("σ = ", '%.2f' % s_g, " :", sep = '')
+      lst_err = [0] * cst.NUM_MET ()
+      lst_time = [0] * cst.NUM_MET ()
+      for j_met in range (cst.NUM_MET ()):
+         met = lst_met [j_met]
+         cnt_met += 1
+         num_chan_met = cst.NUM_CHAN_MET (met)
 
-    if (ver.focus == cls.Focus.ASSORTED):
-        # Lasso
-        lst_legend.append ("Lasso")
-        lst_num_rep_meth.append (cst.NUM_REP_LASSO (ver))
-        lst_meth.append (lambda x, y: lasso_qqpp (x, cst.G_G_LASSO (ver) * y, ver))
[…]

### 2021-02-09 presentation/1_setting.tex
Discuss complexity

@@
 
-\I Problem (b): How to design precoders and combiners?
+\I Problem (b): How to generate precoders and combiners?
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Channel Model and Beamformers}
+\Frame {Channel model and beamforming matrices}
 {
@@
 
-\I Problem (b): How to design \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
+\I Problem (b): How to generate \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
 
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Compressive Sensing}
+\Frame {Compressive sensing}
 {
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Literature on Compressive Sensing}
+\Frame {Literature review}
 {
@@
 
-\I Alkhateeb, Ayach, Leus, Heath (2014): mm-wave, adaptive training algorithm for given sensing matrix
+\I Destino, Juntti, and Nagaraj (2015): MIMO, digital beamforming, using Lasso
 
-\I Alkhateeb, Leus, and Heath (2015): single path mm-wave, all-phase-shifter beamformers, using Orthogonal Matching Pursuit (OMP)
+\I Vlachos, Alexandropoulos, and Thompson (2019): MIMO, hybrid beamforming, mm wave, using Lasso
 
-\I Lee, Lee, and Yong (2016): MIMO mm-wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Questions}
-{
-\I Does greedy algorithms (like OMP) trade precision for complexity, and is the opposite true of convex programs (like DS)?
+\I Alkhateeb, Leus, and Heath (2015): single path mm wave, all phase shifter beamforming, using Orthogonal Matching Pursuit (OMP)
 
-\I We consider the hybrid system as in Lee, Lee, and Yong (2016), where they proposed an optimal joint design by a nonconvex program, but made considerable approximation.
-Is the simplified solution still optimal?
-
-\I Candès and Tao (2007) derived a performance bound for DS.
-Does it prove DS to be better?
-Does it apply to our case?
+\I Lee, Lee, and Yong (2016): MIMO mm wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
 }
@@
 {
-\I We demonstrate that the beamformer may serve as the sensing matrix, so DS can be applied.
+\I Due to the constraint of hybrid beamforming, designs for pure digital beamforming on sensing matrix might not work.
 
-\I We give a bound (holding for high probability) on expected error norm.
+\I We claim that DS is superior in higher noise and fewer samples than OMP.
 
-\I Numerical results illustrate that in our configuration DS is superior to OMP among other methods, at the cost of higher complexity.
+\I We propose a low complexity random generation of beamforming matrices, and justify that it may serve as the sensing matrix.
+
+\I We give a asymptotic bound on expected error norm.
 }

### 2021-02-09 presentation/3_simulation.tex
Discuss complexity

@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Linear Programming}
+\Frame {Reducing the complexity}
 {
-\I DS is equivalent to a linear program, which allows more efficient convex programming methods to be used.
-(Variables with tilde denote the real representation of complex matrices and vectors.)
-\Disp {
-\NC \Hat {\T {\V {g}}}, \Hat {\T {\V {f}}}
-\LA \NC \startcases
-   \NC \Min {\T {\V {g}}', \T {\V {f}}'}  \MC \IP {\V {1}, \T {\V {f}}'} \NR
-   \NC \Rm {subject} \; \Rm {to} \MC \T {\V {g}}' \preceq \T {\V {f}}',
-   \quad \MC - \T {\V {g}}' \preceq \T {\V {f}}' \NR
-   \NC \MC \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
-   \NC \MC - \T {\M {P}}^\Adj \T {\M {P}} \T {\V {g}}' \preceq - \T {\M {P}}^\Adj \T {\V {y}} + \g_{\Ss {DS}} \V {1} \NR
-\stopcases \NR
-}
-\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {\T {\V {g}}}} \M {K}^\Adj}
+\I Casting to a linear program
+
+\I A successive estimation of the nonzero components (not used in the final set of figures)
+
+\I Use the basis pursuit denoising form
 }
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=12,N_B=12}}
+\Frame {Error norm (2 stages), \m {N_H=6, N_{B,t}=3, N_{B,t}=2}}
 {
 \blank [big]
-\externalfigure [assorted-square-small-error.png] [width=11cm]
+\externalfigure [error-small-wide-two.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24,N_B=24}}
+\Frame {Error norm (2 stages), \m {N_H=6, N_{B,t}=2, N_{B,t}=3}}
 {
 \blank [big]
-\externalfigure [assorted-square-big-error.png] [width=11cm]
+\externalfigure [error-small-tall-two.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=12,N_B=10}}
+\Frame {Error norm (2 stages), \m {N_H=12, N_{B,t}=6, N_{B,t}=4}}
 {
 \blank [big]
-\externalfigure [assorted-narrow-small-error.png] [width=11cm]
+\externalfigure [error-small-wide-two.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24,N_B=20}}
+\Frame {Error norm (2 stages), \m {N_H=12, N_{B,t}=4, N_{B,t}=6}}
 {
 \blank [big]
-\externalfigure [assorted-narrow-big-error.png] [width=11cm]
+\externalfigure [error-small-tall-two.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=12,N_B=8}}
+\Frame {Error norm (2 stages), \m {N_H=18, N_{B,t}=9, N_{B,t}=6}}
 {
 \blank [big]
-\externalfigure [assorted-wide-small-error.png] [width=11cm]
+\externalfigure [error-small-wide-two.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24,N_B=16}}
+\Frame {Error norm (2 stages), \m {N_H=18, N_{B,t}=6, N_{B,t}=9}}
 {
 \blank [big]
-\externalfigure [assorted-wide-big-error.png] [width=11cm]
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {\m {1/\s} vs time, assorted, \m {N_H=18,N_B=15}}
-{
-\blank [big]
-\externalfigure [assorted-narrow-medium-time.png] [width=11cm]
+\externalfigure [error-small-tall-two.png] [width=11cm]
 }
@@
 {
-\I DS outperforms other methods under our settings.
+\I DS outperforms other methods in the high noise case
+
+\I DS requires less sampling to recover for given channel instance.
+
+\I The relaxed sparsity may have compromised effectiveness of DS.
+
+\I DS has complexity much higher than OMP, and somewhat higher than Lasso.
 
 \I \m {\T {\chi}} and \m {\chi} differ by some orders of magnitude.
-
-\I The relaxed sparsity may have compromised effectiveness of DS
-
-\I DS has complexity much higher than OMP, but similar to Lasso.
-
-\I \m {2N_H^2} grows fast, and DS can becomes less feasible.
 }
@@
 
-\I Fitting runtime statistics one has
-\Disp {
-\NC \T {C}_{\Rm {OMP}} \NC \eqsim \mathcal {O} \SB {N_H^{3.6}} \NR
-\NC \T {C}_{\Rm {Lasso}} \NC \eqsim \mathcal {O} \SB {N_H^{4.8}} \NR
-\NC \T {C}_{\Rm {DS}} \NC \eqsim \mathcal {O} \SB {N_H^{8.3}} \NR
+\I Fitting the exponent of runtime statistics roughly agrees these result.
+
+\I In certain conditions it is pointed out Lasso and DS are equivalent.
 }
-}

### 2021-02-09 presentation/4_conclusion.tex
Discuss complexity

@@
 
-\I Simulation shows that DS appears to be superior to other methods.
+\I We suggest several ways of reducing the complexity, and illustrate in simulation that DS often outperforms other methods.
 
-\I DS trades off low time and space complexity for high precision, but for OMP, the opposite is true.
+\I We suspect that in cases of higher noise, less sample, or less sparsity, DS is more suitable, so it may be used in combination to other methods.
 }
@@
 {\tfx
-\I A Alkhateeb, O E Ayach, G Leus, R W Heath, \Quote {Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems}, \It {IEEE Journal of Selected Topics in Signal Processing} 8(5), 2014
-
 \I A Alkhateeb, G Leus, and R W Heath, \Quote {Compressed sensing based multi-user millimeter wave systems: How many measurements are needed?}, in \It {2015 IEEE International Conference on Acoustics, Speech and Signal Processing}.
 
-\I W U Bajwa, J Haupt, A M Sayeed, and R Nowak, \Quote {Compressed channel sensing: A new approach to estimating sparse multipath channels}, \It {Proceedings of the IEEE}, 98(6), 2010
+\I W U Bajwa, J Haupt, A M Sayeed, and R Nowak, \Quote {Compressed channel sensing: A new approach to estimating sparse multipath channels}, \It {Proceedings of the IEEE}, 2010
 
 \I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.
+
+\I Destino, Juntti, and Nagaraj (2015): \Quote {Leveraging sparsity into massive MIMO channel estimation with the adaptive-LASSO}, in \It {IEEE Global Conference on Signal and Information Processing}
 }
@@
 
-\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics} 35(6), 2007.
+\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics}, 2007.
 
-\I M P Friedlander and M A Saunders, \Quote {Discussion: the Dantzig selector: statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics}, 35(6), 2007.
+\I E Vlachos, G C Alexandropoulos, and J Thompson (2019): \Quote {Wideband MIMO channel estimation for hybrid beamforming millimeter wave systems via random spatial sampling}, \It {IEEE Journal of Selected Topics in Signal Processing}, 2019
 
-\I J Lee, G-T Gil, and Y H Lee, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 64(6), 2016.
+\I J Lee, G-T Gil, and Y H Lee, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 2016.
 
-\I J A Tropp and A C Gilbert, \Quote {Signal recovery from random measurements via orthogonal matching pursuit}, \It {IEEE Transactions on information theory}, 53(12), 2007.
+\I J A Tropp and A C Gilbert, \Quote {Signal recovery from random measurements via orthogonal matching pursuit}, \It {IEEE Transactions on information theory}, 2007.
 }

### 2021-02-09 treatise-context/2_problem_setting.tex
Discuss complexity

@@
 %
-\NC N_{B,t}, N_{R,t} \gg \NC N_B \NR
+\NC N_{B,t}, N_{B,t} \NR
 }
 
-Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_{B,r} \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
 Let us introduce the effective channel

### 2021-02-09 treatise-context/4_simulation.tex
Discuss complexity

@@
 = \NC \MS {R} \SB {\V {y}}
-\in \MB {R} ^{2 N_B^2} \NR
+\in \MB {R} ^{2 N_{B,r} N_{B,t}} \NR
 %
@@
 = \NC \MS {R} \SB {\M {P}}
-\in \MB {R} ^{2 N_B^2 \D 2 N_H^2} \NR
+\in \MB {R} ^{2 N_{B,r} N_{B,t} \D 2 N_H^2} \NR
 %
@@
 = \NC \MS {R} \SB {\M {P} ^\Adj}
-\in \MB {R} ^{2 N_B^2 \D 2 N_H^2} \NR
+\in \MB {R} ^{2 N_{B,r} N_{B,t} \D 2 N_H^2} \NR
 %
@@
 = \NC \MS {R} \SB {\V {z}}
-\in \MB {R} ^{2 N_B^2} \NR
+\in \MB {R} ^{2 N_{B,r} N_{B,t}} \NR
 }
@@
 
-\startsubsection [title={A Linear Program}]
+\startsubsection [title={Linear Program}]
 
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \MB {C} ^{ N_B^2}}, \m {\g_{\Rm {DS}} > 0}.
+\item Input \m{\M {P} \in \MB {C} ^{N_{B,r} N_{B,t} \D N_H^2}}, \m{\V {y} \in \MB {C} ^{N_{B,r} N_{B,t}}}, \m {\g_{\Rm {DS}} > 0}.
 %
@@
 
-\startsubsection [title={A Two-Stage Version}]
+\startsection [title={Variants}]
 
-We also tried another version of DS, in which DS is applied twice in estimated nonzero components.
-The two-stage method was briefly mentioned \cite [CaT07] without further numerical verification.
-It goes as follows:
-We first apply DS as before;
-we extract largest components of the estimated vector, and apply DS again;
-we extract largest components of the second estimated vector, and apply Moore–Penrose inverse;
-finally, indices set has to be scrambled back corresponding to the original ones.
+We remark some possible variants of DS, either to enhance the accuracy, or to reduce the complexity, or both.
+
+\startsubsection [title={Successive estimation of nonzero components}]
+
+We may applied DS more than once to better estimate the nonzero components, which let us call the successive estimation method.
+We apply DS for the first time.
+Then we extract largest components of the estimated vector, and apply DS again.
+Then we extract largest components of the second estimated vector, and apply Moore–Penrose inverse.
+Finally, the resulting indices set has to be scrambled back corresponding to the original ones.
+The idea is mentioned \cite [CaT07] without further numerical verification.
 
@@
 
-Unfortunately, the two-stage method is not always more accurate than the one-stage method, so we did not include it in the plots.
-It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H}, and we do not know what the best choice is.
+If more than one stage of estimation is possible, that is, there are more than one data set, the second step may be run on the second dataset, and so on.
+It is not impossible to run it for three or more times, but we are not sure that is helpful.
+
+From our observation, it is not obvious whether the successive estimation method is more accurate.
+It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H}, and it is not obvious what the best choice is.
+We do not use this method in the plots included here.
+
+\stopsubsection
+
+\startsubsection [title={Basis pursuit denoising}]
+
+It is known that DS is equivalent to the basis pursuit denoising form below, for suitable \m {\l} (\cite [BoV04], p.334).
+
+\Disp {
+\NC \Hat {\V {g}}
+\LA \NC \Min {\V {g}' \in \MB {C} ^{N_H^2}}
+\RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty} \NR
+}
+
+However, there is not simple way to determine the value of \m {\l}.
+We try \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.
 
@@
 For OMP, suggested values in Cai and Wang \cite [CaW11] is illuminating, where they considered \m {\ell _2}-norm in their Theorem 7, and \m {\ell _\infty}-norm in their Theorem 8.
-We simply take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 N_B}} for 2-norm constraint.
+We simply take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 \R {N_{B,r} N_{B,t}}}} for 2-norm constraint.
 Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
-The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
+The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.
 
@@
 
-\startsubsection [title={Plots of time}]
+\startsubsection [title={Plots of runtime}]
 
@@
 \blank [big]
-\externalfigure [small-square-two-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [time-small-square-two.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, error.}
@@
 \blank [big]
-\externalfigure [medium-square-two-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [time-medium-square-two.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, error.}
@@
 \blank [big]
-\externalfigure [big-square-four-time.png] [wfactor=fit, hfactor=fit]
+\externalfigure [time-big-square-two.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, error.}
@@
 
-In the assorted plots, DS steadily outperforms other methods.
-From lowest to highest error, it usually goes like this: DS, LS, Lasso, OMP.
+From the simulation, DS outperforms other methods in most of the datasets.
+In the scenario of low noise, \m {\T {\chi}} values of OMP and Lasso are close to DS.
+But in the scenario of high noise, \m {\T {\chi}} values of OMP and Lasso blow up quickly.
 
-The performance of OMP appears to be poor.
-In most cases, the estimation fails, and we have \m {\T {\chi}} close to the unity.
-Varying thresholds of OMP, namely \m {\h_{\Rm {OMP}}}, does not give different result.
+It is intuitive that when \m {N_{B,t} /N_{B,r}} is smaller, \m {\T {\chi}} is smaller, because we have a higher sample rate.
+As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, the DS line improves more significantly, and \m {\T {\chi}} falls nearly always below \m {0} dB for \m {N_{B,t} > N_{B,r}} case.
 
-A crucial reason might be that Lee, Gil, and Lee \cite [LGL16] proposed a high-complexity nonconvex program for the beamformers, which they gave approximation, and we have here a low-complexity, randomly-generated beamformers.
-It may also have something to do with the distribution of angles of departure and arrival;
-their distribution lies within a cluster of standard deviation 15 degrees, and in ours, they are uniform on the unit circle.
-It remains to see how OMP and DS compare, if done according to their procedure.
+The design of sample matrix seems to have a lot to do with the performance of OMP.
+In Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the beamformers, while we have here a low-complexity, random generation of beamformers.
+It may also have something to do with the distribution of angles of departure and arrival.
 
-The performance of Lasso also fails mostly, and \m {\T {\chi}} even increase as \m {\s} decreases, which is strange.
+The performance of Lasso also fails mostly for low noise.
+Recall from above that \m {\g} (or \m {\l}) is crucial to the performance, but cannot be obtained in advance.
+Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
+We should not however there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
 
-For Moore Penrose pseudoinverse, \m {\T {\chi}} decreases steadily as \m {\s} decreases.
+For Moore Penrose pseudoinverse, \m {\T {\chi}} increases tremendously as \m {\s} decreases, and the trend is steady and may serve as a upper bound.
 
-For DS itself, \m {\T {\chi}} decreases as \m {\s} increases, which is expected, but \m {\T {\chi}} does not go down indefinitely, even for very low \m {\s}.
+For DS itself, \m {\T {\chi}} decreases as \m {\s} increases, which is expected, but \m {\T {\chi}} does not go down indefinitely.
 The values of threshold of DS \m {\g_{\Rm {DS}}} are chosen within the order of magnitude of \m {\s}.
-For high signal level, \m {\g_{\Rm {DS}}} does not affect much, but for low signal level a greater value may be more effective.
 It may have been that the iteration stabilizes much earlier than is constrained by maximum iteration number.
@@
 
-We are not sure either why \m {\T {\chi}} is an overestimation of \m {\chi} by several orders of magnitude.
-A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
+\m {\T {\chi}} is not shown in the figure, because the big O bound is much larger than \m {\chi}.
+It is possible that the nonsparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
+It is curious to see whether for very large \m {N_H}, whether \m {\T {\chi}} and \m {\T {\chi}} will be asymptotically close.
 
-In figures 21 and 22, we reproduce two cases of success and failure of DS.
+In figures 24 and 25, we reproduce two cases of success and failure of DS.
 In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.
@@
 
-\startsubsection [title={Asymtotic analysis}]
+We discuss the complexity of DS, Lasso, and OMP.
 
-We discuss the complexity of DS and OMP.
-In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many iterations were done.
-Boyd and Vandenberghe \cite [BoV04] analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496, also p.531).
-In our case, Candès and Romberg \cite [CaR05] pointed out that the complex DS can be cast into an second order cone programming (SOCP), and where self concordance holds.
-Diamond and Boyd (writers of CVXPY) \cite [DiB16] explained that convex programs are usually converted into primal-dual problems.
-The library we called in the simulation is ECOS, where Newton method is used.
-Of course, we are not certain there is no method faster than Newton method, and implementation details of CVXPY may change the conclusion too.
+\startsubsection [title={Dantzig selector}]
 
-We attemp to give a heuristic argument regarding the complexity of Newton steps.
-We say the function being minimized is \m {\VNm {\V {g}}_1}.
-Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
+\stopsubsection
+
+\stopsubsection
+
+In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many steps were calculated.
+Suppose a linear program has \m {N} dimension variable and \m {M} inequality constraints, then the complexity is \m {\MS {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite [BoV04], p.6).
+For our case, that would be \m {\MS {O} \SB {4 N_H ^4 \D 8 N_H^2} = \MS {O} \SB {N_H^6}}.
+
+Alternatively, suppose Newton method is used, and we have self-concordance for linear program.
+Then the number of Newton steps is bounded \cite [BoV04] by
+%
+\Disp {
+\NC C_{\Rm {Newton}}
+= \NC \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
++ \log_2 \log_2 \F {1} {\e}} \NR
+}
+%
+Let \m {\V {g} _0} denote the starting value of \m {\V {g}'}, and \m {\V {g} ^{\star}} the the point of convergence.
 Then Boyd and Vandenberghe \cite [BoV04] (p.505, Eqn.9.56) gave a bound of the number of steps.
@@
 Here \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error, and \m {C_{\Rm {step}}} is the complexity of Newton step.
-According to their analysis (Eqn.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
-Also, \m {C_0} usually assumes the value of about several hundred.
-There was an example they gave in which \m {C_0 =375}, where, with their notation,
-\m {C_0 =(20 -8\a) / (\a \b \RB {1 -2\a}^2}), where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).
 
@@
 
-We take some liberty to assume that, at the start the iteration, the Moore–Penrose inverse was taken to be the initial value of \m {\V {g}_0}, namely
+We therefore assume that, at the start the iteration, the Moore–Penrose inverse was taken to be the initial value of \m {\V {g}_0}, namely
 %
@@
 
-We see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} observes complex standard normal distribution.
+We see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} follows complex standard normal distribution.
 If we agree that, for high probability,
@@
 }
-Then we simply have
+Then we have
 %
@@
 
-On the other hand, Tropp and Gilbert \cite [TrG07a] discussed the complexity of OMP in the companion paper \cite [TrG07b].
-They gave
+\startsubsection [title={Orthogonal matching pursuit}]
+
+Tropp and Gilbert \cite [TrG07a] discussed the complexity of OMP in the companion paper \cite [TrG07b], giving
 %
@@
 \NC C_{\Rm {OMP}}
-=\NC \MS {O} \SB {N_H^2 \log N_B} \NR
+=\NC \MS {O} \SB {N_H^2 \log \RB {N_{B,r} N_{B,t}}} \NR
 }
 %
-Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\MS {O} \SB {N_H^2}}.
+Here \m {\log \RB {N_{B,r} N_{B,t}}} is small in our experiments, and if we dropped it, we may take
+\DispNum {C:P:ON:H2} {
+\NC C_{\Rm {OMP}}
+=\NC \MS {O} \SB {N_H^2} \NR
+}
 
-Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\Rm {Lasso}} =\MS {O} \SB {N_H^6}}.
+\startsubsection [title={Lasso}]
+
+Lasso is equivalent to a QCQP, and there is not always a closed form for its complexity.
+However, Lasso and DS are equivalent in certain conditions \cite [AsR10], and we may suppose here they have the same complexity.
+Alternatively, an argument similar to the above one for DS is valid for Lasso.
+
+Therefore we take
+\DispNum {C:o:ON:H6} {
+\NC C_{\Rm {Lasso}}
+=\NC \MS {O} \SB {N_H^6} \NR
+}
 
@@
 We reproduce the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
-\DispNum {t:2:95:55} {
-\NC t_{\Rm {OMP}} \SB {12} \NC = 0.0119,
-\FourQ t_{\Rm {OMP}} \SB {16} = 0.0297, \NR
-\NC t_{\Rm {OMP}} \SB {20} \NC = 0.0600,
-\FourQ t_{\Rm {OMP}} \SB {24} = 0.155, \NR
+They are: \m {
+ t_{\Rm {OMP}} \SB {12}  = 0.0119,
+ t_{\Rm {OMP}} \SB {16} = 0.0297, 
+ t_{\Rm {OMP}} \SB {20}  = 0.0600,
+ t_{\Rm {OMP}} \SB {24} = 0.155, 
 %
-\NC t_{\Rm {Lasso}} \SB {12} \NC = 0.0436,
-\FourQ t_{\Rm {Lasso}} \SB {16} = 0.176, \NR
-\NC t_{\Rm {Lasso}} \SB {20} \NC = 0.471,
-\FourQ t_{\Rm {Lasso}} \SB {24} = 1.26, \NR
+ t_{\Rm {Lasso}} \SB {12}  = 0.0436,
+ t_{\Rm {Lasso}} \SB {16} = 0.176, 
+ t_{\Rm {Lasso}} \SB {20}  = 0.471,
+ t_{\Rm {Lasso}} \SB {24} = 1.26, 
 %
-\NC t_{\Rm {DS}} \SB {12} \NC = 0.357,
-\FourQ t_{\Rm {DS}} \SB {16} = 2.07, \NR
-\NC t_{\Rm {DS}} \SB {20} \NC = 29.8,
-\FourQ t_{\Rm {DS}} \SB {24} = 91.5, \NR
-}
-Simulation indeed shows that \m {t_{\Rm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
+ t_{\Rm {DS}} \SB {12}  = 0.357,
+ t_{\Rm {DS}} \SB {16} = 2.07, 
+ t_{\Rm {DS}} \SB {20}  = 29.8,
+ t_{\Rm {DS}} \SB {24} = 91.5
+}.
+
+Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
 It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.

### 2021-02-10 presentation/1_setting.tex
Rev contribution

@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Channel model and beamforming matrices}
+\Frame {Channel model and beamforming}
 {
@@
 
-\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_B}}
+\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_{B,t}}}
 \I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}
@@
 \I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}
-\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_B \D N_R}}
+\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_{B,r} \D N_R}}
 
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Problem Description}
+\Frame {Cast to Linear System}
 {
 \I We have \m {\M {Y} =\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}}}
-%
-\I Problem (a): How to recover \m {\M {H}} with knowledge of \m {\M {Y}}?
-
-\I Can we measure less than \m {N_H^2} times, but recover successfully for most cases?
-
-\I Problem (b): How to generate \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
-
-\I What kind of matrices facilitates our goal?
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Cast to Linear System}
-{
 \I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
@@
 }
+\I We have an underdetermined system \m {\V {y} =\M {P} \V {g} +\V {z}}
+}
+% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
+\Frame {Problem Description}
+{
+\I Problem (a): How to recover \m {\M {H}} with knowledge of \m {\M {Y}}?
 
-\I We have an underdetermined system \m {\V {y} =\M {P} \V {g} +\V {z}}
+Can we measure less than \m {N_H^2} times, but recover successfully for most cases?
+
+\I Problem (b): How to generate \m {\M {W}_R}, \m {\M {W}_B}, \m {\M {F}_R}, and \m {\M {F}_B}?
+
+What kind of matrices facilitates our goal?
 }
@@
 {
-\I Due to the constraint of hybrid beamforming, designs for pure digital beamforming on sensing matrix might not work.
+\I Due to the constraint of hybrid beamforming, designs for fully digital beamforming on sensing matrix might not directly work.
+
+\I We propose a low complexity random generation of beamforming matrices, and justify that it may serve as the sensing matrix for DS.
 
 \I We claim that DS is superior in higher noise and fewer samples than OMP.
-
-\I We propose a low complexity random generation of beamforming matrices, and justify that it may serve as the sensing matrix.
-
 \I We give a asymptotic bound on expected error norm.
@@
 {
-\I Input \m {\M {P} \in \MB {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.
+\I Input \m {\M {P} \in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}}, \m {\g_{\Ss {DS}} \geq 0}.
 

### 2021-02-10 presentation/3_simulation.tex
Rev contribution

@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Error norm (2 stages), \m {N_H=6, N_{B,t}=3, N_{B,t}=2}}
+\Frame {Error norm (1/6)}
 {
+\I \m {N_H=6, N_{B,t}=3, N_{B,r}=2}, 2 stages
 \blank [big]
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Error norm (2 stages), \m {N_H=6, N_{B,t}=2, N_{B,t}=3}}
+\Frame {Error norm (2/6)}
 {
+\I \m {N_H=6, N_{B,t}=2, N_{B,r}=3}, 2 stages
 \blank [big]
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Error norm (2 stages), \m {N_H=12, N_{B,t}=6, N_{B,t}=4}}
+\Frame {Error norm (3/6)}
 {
+\I \m {N_H=12, N_{B,t}=6, N_{B,r}=4}, 2 stages
 \blank [big]
-\externalfigure [error-small-wide-two.png] [width=11cm]
+\externalfigure [error-medium-wide-two.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Error norm (2 stages), \m {N_H=12, N_{B,t}=4, N_{B,t}=6}}
+\Frame {Error norm (4/6)}
 {
+\I \m {N_H=12, N_{B,t}=4, N_{B,r}=6}, 2 stages
 \blank [big]
-\externalfigure [error-small-tall-two.png] [width=11cm]
+\externalfigure [error-medium-tall-two.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Error norm (2 stages), \m {N_H=18, N_{B,t}=9, N_{B,t}=6}}
+\Frame {Error norm (5/6)}
 {
+\I \m {N_H=18, N_{B,t}=9, N_{B,r}=6}, 2 stages
 \blank [big]
-\externalfigure [error-small-wide-two.png] [width=11cm]
+\externalfigure [error-big-wide-two.png] [width=11cm]
 }
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Error norm (2 stages), \m {N_H=18, N_{B,t}=6, N_{B,t}=9}}
+\Frame {Error norm (6/6)}
 {
+\I \m {N_H=18, N_{B,t}=6, N_{B,r}=9}, 2 stages
 \blank [big]
-\externalfigure [error-small-tall-two.png] [width=11cm]
+\externalfigure [error-big-tall-two.png] [width=11cm]
 }
@@
 {
-\I Let \m {C} denote big-O estimation of complexity, then we argue in the treatise
+\I Let \m {C} denote big-O estimation of complexity, then
 \Disp {
-\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_B} \NR
+\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log \R {N_{B,t} N_{B,r}}} \NR
 \NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR

### 2021-02-10 treatise-context/1_introduction.tex
Rev contribution

@@
 
-Some instead applied least absolute shrinkage and selection operator (Lasso).
-Indeed, it can be shown that Lasso and DS have similar behavior \cite [AsR10].
+Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
+In fact, it can be shown that Lasso and DS have similar behavior \cite [AsR10].
 
@@
 Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles.
-Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamformers based on nonuniform fixed set of angles.
+Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
 Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers of stationary channel gain.
-Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the effective beamformer serves as sensing matrix, based on a designed set of angles.
-Gao, Dai, and Wang proposed a variant which we have the assumption of spatially common sparsity \cite [GDW15].
+Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the sensing matrix serves as sensing matrix, based on a designed set of angles.
+Gao, Dai, and Wang proposed a variant which there is the assumption of spatially common sparsity \cite [GDW15].
 
@@
 
-Do greedy algorithms trade precision for complexity, and is the opposite true of convex programs?
-In this treatise, we consider a hybrid structure with uniform linear array as in Lee, Gil, and Lee \cite [LGL16].
-They proposed a beamformer shown to be optimal, jointly designed on both ends by a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
-Still, it is not clear whether the approximated scheme is optimal.
+Because the limit of hybrid structure, the designs which use a fully digital beamforming is not directly usable, and the designs which use only analog beamforming might not be optimal, which we have to investigate.
+Moreover, we demonstrate that convex programming outperforms greedy methods, and may be necessary in less ideal situations.
 
-We illustrate that, with randomly generated beamformers, DS estimates the channel with better accuracy than other methods.
-The setting is more general than \cite [LLL17] and more simple than \cite [VAT19], and the beamformer generation less complicated than \cite [DJN15].
-In chapter 2 we shall see that our proposed effective beamformer has RIP for high probability, which may serve as the sensing matrix for DS.
-In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a quantitative bound (which holds for high probability) on expected error norm.
-In chapter 4, we remark that DS can be cast as a linear program, for which more efficient algorithms exist.
-Numerical results show that in our problem configuration, DS is superior to other methods.
+In this treatise, we consider a hybrid structure with uniform linear array.
+We generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
+In chapter 2 we shall see that our proposed sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS.
+In chapter 3, we give a quantitative bound (which holds for high probability) on expected error norm.
+In chapter 4, numerical results show that in our problem configuration, DS is superior to other methods.
+Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.
+
+We claim that, for given number of sampling, DS recovers more successfully than OMP.
+Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] with only analog combiner,
+our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite [LGL16],
+and we do not rely on additional assumption on spatially as in Gao, Dai, and Wang \cite [GDW15].
+
+It is different from Bajwa et.\ al.\ \cite [BHS10], and while they require a series of random pilot vectors and the sensing stage take considerable time, we require only random sensing matrices and take just a few time frames.
+
+In addition, we claim that with the same threshold, DS is better than Lasso.
+Again, the proposed method is more general than Lian, Liu and Lau \cite [LLL17] with only analog combiner,
+and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite [DJN15],
+and we do not require special device as in Vlachos, Alexandropoulos, and Thompson \cite [VAT19].
 

### 2021-02-10 treatise-context/4_simulation.tex
Rev contribution

@@
 It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H}, and it is not obvious what the best choice is.
-We do not use this method in the plots included here.
+We have not used this method in the plots included here.
 
@@
 
-However, there is not simple way to determine the value of \m {\l}.
-We try \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.
+However, there is not simple way to determine the value of \m {\l} in advance.
+We have tried \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.
 
@@
 
-In addition to DS, we shall simulate OMP for three different stop conditions, Lasso, and Moore Penrose pseudoinverse (marked as LS which stands for least square).
+In addition to DS, we shall simulate OMP for two different stop conditions, Lasso, and Moore Penrose pseudoinverse (marked as LS which stands for least square).
 
@@
 
-We take \m {N_H} to be \m {12, 18, 24}, respectively.
+We take \m {N_H} to be \m {6, 12, 18}, respectively.
 For assorted plots, three series of plots are simulated.
-The first series for \m {N_{B,t} = N_H/3} and \m {N_{B,r} = N_H/4}.
-The second series for \m {N_{B,t} = N_H/4} and \m {N_{B,r} = N_H/3}.
-The third series for \m {N_{B,t} = N_H/3} and \m {N_{B,r} = N_H/3}.
+The first series for \m {N_{B,t} = N_H/2} and \m {N_{B,r} = N_H/3}.
+The second series for \m {N_{B,t} = N_H/3} and \m {N_{B,r} = N_H/2}.
+The third series for \m {N_{B,t} = N_H/2} and \m {N_{B,r} = N_H/2}.
 Unfortunately, this is very far from achieving the ideal values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
@@
 Other parameters are fixed in these experiments.
-The number of grid of quantization of analog beamformers is \m {16}.
-The number of paths \m {L} is \m {4}.
-The wavelength of carrier \m {\l _{\Rm {ant}}} is set to be \m {0.1}, and the antenna spacing \m {d _{\Rm {ant}}} is \m {0.2}; only their ratio matters.
+The number of grid of quantization of phase shifters is \m {16}.
+The number of paths \m {L = NN_HH /2}.
+The ratio of the wavelength of carrier over the antenna spacing, \m {\l _{\Rm {ant}} / d _{\Rm {ant}} = 1 / 2}.
 
 Denote the threshold for DS to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
-In the plots of assorted methods, we set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
+We set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
 For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
-For OMP, suggested values in Cai and Wang \cite [CaW11] is illuminating, where they considered \m {\ell _2}-norm in their Theorem 7, and \m {\ell _\infty}-norm in their Theorem 8.
-We simply take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\Rm {OMP}} = \R {3 \R {N_{B,r} N_{B,t}}}} for 2-norm constraint.
+For OMP, we consult Cai and Wang \cite [CaW11] for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
+We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3 \R {N_{B,r} N_{B,t}}}} for 2-norm condition.
 Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
@@
 Each data point for DS and Lasso is repeated for \m {256} times, and taken arithmetic average.
-Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {12 \D 256} times.
+Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {8 \D 256} times.
 
-For performance metric, we follow Lee, Gil, and Lee \cite [LGL16],
+For performance metric, we follow Lee, Gil, and Lee \cite [LGL16] to use
 \DispNum {h:h:lo:vg} {
@@
 }
-However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
-We do not know either whether \m {\T {\chi}} is a good indicator of channel capacity; it seems to be, but actually we did not consider a definite a channel model in this treatise.
+However, we remark that when \m {\VNm {\V {h}}_2} is small, this can blow up.
+Indeed, since we did not consider a definite a channel model in this treatise, \m {\T {\chi}} may not necessarily be proportional to the channel capacity
 
@@
 And if they are set too big, the Newton steps get imprecise and the performance is poorer.
-More tests are necessary to determine the best choice of parameters.
+It remains to determine the best choice of parameters.
 
@@
 The design of sample matrix seems to have a lot to do with the performance of OMP.
-In Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the beamformers, while we have here a low-complexity, random generation of beamformers.
+In Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
 It may also have something to do with the distribution of angles of departure and arrival.

### 2021-02-10 treatise-pdflatex/2_problem_setting.tex
Front matter passes compilation
Chap 2 compiles
Conversion: compile chap 3
Rev contribution

@@
 = \frac {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
-\in \mathbb {C} ^ {N_H} \NR
+\in \mathbb {C} ^ {N_H} 
 }
@@
 \V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l'}
-\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l'}^\dagger \NR
+\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l'}^\dagger 
 }
@@
 = 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
-  \; \mathrm {Mod}\; \RB {2\pi} \NR
+  \; \mathrm {Mod}\; \RB {2\pi} \\
 %
@@
 = 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
-  \; \mathrm {Mod}\; \RB {2\pi} \NR
+  \; \mathrm {Mod}\; \RB {2\pi} 
 }
@@
 %
-\DispNum {H:H:l0:ql} {
+\DispNum {H:H:l0:NH} {
 \M {H}
 =\sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
-\in \mathbb {C} ^{N_H \D N_H} \NR
+\in \mathbb {C} ^{N_H \D N_H} 
 }
@@
 
-\blank [big]
-\externalfigure [system.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Schematic diagram of the hybrid beamforming system we consider, based on Akdeniz et.\ al.\ \cite {ALS14}.}
-\blank [big]
+\begin {figure} [hbt]
+\centering
+\includegraphics [width = \textwidth] {system.png}
+\caption {Schematic diagram of the hybrid beamforming system we consider, based on Akdeniz et.\ al.\ \cite {ALS14}.}
+\end {figure}
 
@@
 Each end consists of both digital and analog precoders and combiners.
-In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_B}} and analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D  N_R}}.
-Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \mathbb {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \mathbb {C} ^{N_B \D  N_R}}.
+In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_{B,t}}} and analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D  N_R}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \mathbb {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D  N_R}}.
 
@@
 \Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
-= 1, \NR
+= 1, \\
 %
 \Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
-= 1, \NR
+= 1, \\
 %
 n_H
-= 0, \dots N_H-1, \NR
+= 0, \dots N_H-1, \\
 %
 n_R
-= 0, \dots N_R-1 \NR
+= 0, \dots N_R-1 
 }
@@
 \DispNum {N:H:NY:NY} {
-N_H \gg N_R \NR
+N_H \gg N_R \\
 %
-N_R \gg N_B \NR
+N_R \gg N_{B,r}, N_{B,r}
 }
 
-Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}} with each entry being i.i.d.\ standard normal.
 Let us introduce the effective channel
@@
 \M {Y}
-:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} \NR
+:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} 
 }
@@
 \RB {\mathrm {vec} \SB {\M {A}}} _{\SB {m}}
-=\M {A} _{\SB {m\; \mathrm {Mod}\; N_1, \Fl {m/N_1 }}} \NR
+=\M {A} _{\SB {m\; \mathrm {Mod}\; N_1, \Fl {m/N_1 }}} 
 }
@@
 \mathrm {vec} ^{-1} \SB {\mathrm {vec} \SB {x}}
-=x \NR
+=x 
 }
@@
 \DispNum {A:2:Am:N4} {
-\RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \NR
+\RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \\
 %
 =\M {A} _{\SB {\Fl {m_1/N_3 }, \Fl {m_2/N_4 }}}
-\M {B} _{\SB {m_1\; \mathrm {Mod}\; N_3, m_2\; \mathrm {Mod}\; N_4}} \NR
+\M {B} _{\SB {m_1\; \mathrm {Mod}\; N_3, m_2\; \mathrm {Mod}\; N_4}} 
 }
@@
 \mathrm {vec} \SB {\M {A}\M {X}\M {B}}
-= \RB {\M {B}^\intercal \otimes \M {A}} \mathrm {vec} \SB {\M {X}} \NR
+= \RB {\M {B}^\intercal \otimes \M {A}} \mathrm {vec} \SB {\M {X}} 
 }
@@
 := \mathrm {vec} \SB {\M {H}}
-\in \mathbb {C} ^{N_H^2} \NR
+\in \mathbb {C} ^{N_H^2} \\
 %
@@
 := \mathrm {vec} \SB {\M {Y}}
-\in \mathbb {C} ^{N_B^2} \NR
+\in \mathbb {C} ^{N_{B,t} N_{B,r}} \\
 %
@@
 := \mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
-\in \mathbb {C} ^{N_B^2} \NR
+\in \mathbb {C} ^{N_{B,t} N_{B,r}} \\
 %
@@
 := \RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
-\in \mathbb {C} ^{N_B^2 \D N_H^2} \NR
+\in \mathbb {C} ^{N_{B,t} N_{B,r} \D N_H^2} 
 }
@@
 \V {y}
-=\M {Q} \V {h} +\V {z} \NR
+=\M {Q} \V {h} +\V {z} 
 }
@@
 \DispNum {K:K:CN:H1} {
-\M {K} \in  \mathbb {C} ^{N_H \D N_H} \NR
+\M {K} \in  \mathbb {C} ^{N_H \D N_H} \\
 %
 \M {K} _{\SB {n_1, n_2}}
-= \frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \NR
+= \frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \\
 %
 \quad n_1, n_2
-= 0, 1, \dots, N_H-1 \NR
+= 0, 1, \dots, N_H-1 
 }
@@
 \M {K}^\dagger \M {K}
-= \M {I} \NR
+= \M {I} 
 }
@@
 \M {G}
-=\M {K}^\dagger \M {H} \M {K} \NR
+=\M {K}^\dagger \M {H} \M {K} 
 }
@@
 +\M {W} _B \M {W} _R \M {Z}
-\in \mathbb {C} ^{N_B \D N_B} \NR
+\in \mathbb {C} ^{N_{B,t} \D N_{B,r}} 
 }
@@
 :=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
-\in \mathbb {C} ^{N_B^2 \D N_H^2} \NR
+\in \mathbb {C} ^{N_{B,t} \D N_{B,r} \D N_H^2} 
 }
@@
 := \mathrm {vec} \SB {\M {G}}
-\in \mathbb {C} ^ {N_H \D N_H} \NR
+\in \mathbb {C} ^ {N_H \D N_H} 
 }
@@
 \V {y}
-=\M {P} \V {g} +\V {z} \NR
+=\M {P} \V {g} +\V {z} 
 }
@@
 %
-\item Input \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_B}},
+\item Input \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_{B,t}}},
 \m {\M {F} _R \in \mathbb {C} ^{N_H \D N_R}},
 \m {\M {W} _R \in \mathbb {C} ^{N_R \D N_H}},
-\m {\M {W} _B \in \mathbb {C} ^{N_B \D N_R}},
-and \m {\M {Y} \in \mathbb {C} ^{N_B \D N_B}}.
+\m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_R}},
+and \m {\M {Y} \in \mathbb {C} ^{N_{B,r} \D N_{B,t}}}.
 %
-\item Find \m {\M {P} \in \mathbb {C} ^{N_B^2 \D N_H^2}}, \m {\V {y} \in \mathbb {C} ^{N_H^2}} as in above.
+\item Find \m {\M {P} \in \mathbb {C} ^{N_{B,r} N_{B,t} \D N_H^2}}, \m {\V {y} \in \mathbb {C} ^{N_H^2}} as in above.
 %
@@
 \hat {\V {g}}
-\leftarrow \startcases
-\Min {\V {g}' \in \mathbb {C} ^{N_H^2}}  \MC \VNm {\V {g}'} _1 \NR
+\leftarrow \begin {cases}
+\Min {\V {g}' \in \mathbb {C} ^{N_H^2}} & \VNm {\V {g}'} _1 \\
 %
-\mathrm {subject} \; \mathrm {to} \quad \MC \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \NR
-\stopcases \NR
+\mathrm {subject} \; \mathrm {to} \quad & \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \\
+\end {cases} 
 }
@@
 %
-\DispNum {G:G:ve:1g} {
+\Disp {
 \hat {\M {G}}
-\leftarrow \mathrm {vec}^{-1} \SB {\hat {\V {g}}} \NR
+\leftarrow \mathrm {vec}^{-1} \SB {\hat {\V {g}}} 
 }
@@
 %
-\DispNum {H:H:KG:GK} {
+\Disp {
 \hat {\M {H}}
-\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger \NR
+\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger 
 }
@@
 %
-\stopitemize
+\end {itemize}
 }

### 2021-02-10 treatise-pdflatex/3_2_design_of_beamformers.tex
Rev contribution

@@
 =\R {
-   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
+   \sum _{i=0} ^{N_{B,t}-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_{B,t}}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
 }
@@
 \DispNum {P:x:ex:ex} {
-\mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_B}} + \frac {2x} {N_B}}
+\mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_{B,t}}} + \frac {2x} {N_{B,t}}}
 \leq \mathsf {e} ^{-x} 
@@
 \DispNum {P:x:ex:ex!} {
-\mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_B}}}
+\mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_{B,t}}}}
 \leq \mathsf {e} ^{-x} 
@@
 1 -p
-\leq 2 \mathsf {e} ^{-N_B \R {\d_s} /4} 
+\leq 2 \mathsf {e} ^{-N_{B,t} \R {\d_s} /4} 
 }

### 2021-02-10 treatise-pdflatex/4_simulation.tex
Rev contribution

@@
 = \mathcal {R} \SB {\V {y}}
-\in \mathbb {R} ^{2 N_B^2} \\
+\in \mathbb {R} ^{2 N_{B,t} N_{B,r}} \\
 %
@@
 = \mathcal {R} \SB {\M {P}}
-\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
+\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \\
 %
@@
 = \mathcal {R} \SB {\M {P} ^\Adj}
-\in \mathbb {R} ^{2 N_B^2 \D 2 N_H^2} \\
+\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \\
 %
@@
 = \mathcal {R} \SB {\V {z}}
-\in \mathbb {R} ^{2 N_B^2} 
+\in \mathbb {R} ^{2 N_{B,t} N_{B,r}} 
 }
@@
 
-\subsection {Plots of assorted methods}
-
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H} and \m {N_B}.
+\subsection {Plots of \m {N_H = 6}}
 
 \begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-square-small-error.png}
-\caption {Assorted methods, \m {N_B = 12, N_H = 12}, error norm.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-square-medium-error.png}
-\caption {Assorted methods, \m {N_B = 18, N_H = 18}, error norm.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-square-big-error.png}
-\caption {Assorted methods, \m {N_B = 24, N_H = 24}, error norm.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-narrow-small-error.png}
-\caption {Assorted methods, \m {N_B = 10, N_H = 12}, error norm.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-narrow-medium-error.png}
-\caption {Assorted methods, \m {N_B = 15, N_H = 18}, error norm.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-narrow-big-error.png}
-\caption {Assorted methods, \m {N_B = 20, N_H = 24}, error norm.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-wide-small-error.png}
-\caption {Assorted methods, \m {N_B = 8, N_H = 12}, error norm.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-wide-medium-error.png}
-\caption {Assorted methods, \m {N_B = 12, N_H = 18}, error norm.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-wide-big-error.png}
-\caption {Assorted methods, \m {N_B = 16, N_H = 24}, error norm.}
+\includegraphics [width = \textwidth] {error-small-square-two.png}
+\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
 \end {figure}
 
-As for the plot of time taken in minutes, we give only one example of \m {N_H = 16}.
-%
 \begin {figure} [hbt]
-\includegraphics [width = \textwidth] {assorted-narrow-medium-time.png}
-\caption {Assorted methods, \m {N_B = 15, N_H = 18}, time.}
+\includegraphics [width = \textwidth] {error-small-tall-two.png}
+\caption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
 \end {figure}
 
-\subsection {Plots of DS only}
-
-Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
-Here, \m {\tilde {\chi}} is shown too.
-%
 \begin {figure} [hbt]
-\includegraphics [width = \textwidth] {ddss-narrow-small-error.png}
-\caption {DS, \m {N_B = 10, N_H = 12}, error.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {ddss-narrow-medium-error.png}
-\caption {DS, \m {N_B = 15, N_H = 18}, error.}
-\end {figure}
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {ddss-narrow-big-error.png}
-\caption {DS, \m {N_B = 20, N_H = 24}, error.}
-\end {figure}
-%
-As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
-%
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {ddss-narrow-medium-time.png}
-\caption {DS, \m {N_B = 15, N_H = 18}, time.}
+\includegraphics [width = \textwidth] {error-small-wide-two.png}
+\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {2} stages, error.}
 \end {figure}
 
-\subsection {Plots of OMP only}
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-square-four.png}
+\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
+\end {figure}
 
-Again, we plot the reciprocal of noise level vs relative error norm in log scale, for \m {N_H = 8, 12, 16, 20, 24}, respectively, and \m {N_H = 3 N_B} for each of them.
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-tall-four.png}
+\caption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
+\end {figure}
 
-%
 \begin {figure} [hbt]
-\includegraphics [width = \textwidth] {oommpp-square-small-error.png}
-\caption {OMP, \m {N_H = 12, N_B = 12}, error.}
+\includegraphics [width = \textwidth] {error-small-wide-four.png}
+\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {4} stages, error.}
 \end {figure}
-%
+
+\subsection {Plots of \m {N_H = 12}}
+
 \begin {figure} [hbt]
-\includegraphics [width = \textwidth] {oommpp-square-medium-error.png}
-\caption {OMP, \m {N_H = 18, N_B = 18}, error.}
+\includegraphics [width = \textwidth] {error-medium-square-two.png}
+\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
 \end {figure}
-%
+
 \begin {figure} [hbt]
-\includegraphics [width = \textwidth] {oommpp-square-big-error.png}
-\caption {OMP, \m {N_H = 24, N_B = 24}, error.}
+\includegraphics [width = \textwidth] {error-medium-tall-two.png}
+\caption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
 \end {figure}
-%
-As for the plot of time taken in minutes, we give only one example of \m {N_H = 18}.
-%
+
 \begin {figure} [hbt]
-\includegraphics [width = \textwidth] {oommpp-square-medium-time.png}
-\caption {OMP, \m {N_H = 18, N_B = 18}, time.}
+\includegraphics [width = \textwidth] {error-medium-wide-two.png}
+\caption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {2} stages, error.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-medium-square-four.png}
+\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-medium-tall-four.png}
+\caption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-medium-wide-four.png}
+\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 12}, with \m {4} stages, error.}
+\end {figure}
+
+\subsection {Plots of \m {N_H = 18}}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-square-two.png}
+\caption {\m {N_{B,t} = 12, N_{B,r} = 12, N_H = 18}, with \m {2} stages, error.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-tall-two.png}
+\caption {\m {N_{B,t} = 8, N_{B,r} = 12, N_H = 18}, with \m {2} stages, error.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-wide-two.png}
+\caption {\m {N_{B,t} = 12, N_{B,r} = 8, N_H = 18}, with \m {2} stages, error.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-square-two.png}
+\caption {\m {N_{B,t} = 12, N_{B,r} = 12, N_H = 18}, with \m {4} stages, error.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-tall-two.png}
+\caption {\m {N_{B,t} = 8, N_{B,r} = 12, N_H = 18}, with \m {4} stages, error.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-wide-two.png}
+\caption {\m {N_{B,t} = 12, N_{B,r} = 8, N_H = 18}, with \m {4} stages, error.}
+\end {figure}
+
+\subsection {Plots of runtime}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-small-square-two.png}
+\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, time.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-medium-square-two.png}
+\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, time.}
+\end {figure}
+
+\begin {figure} [hbt]
+\includegraphics [width = \textwidth] {error-big-square-two.png}
+\caption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {4} stages, time.}
 \end {figure}
@@
 C_{\mathrm {OMP}}
-=\mathcal {O} \SB {N_H^2 \log N_B} 
+=\mathcal {O} \SB {N_H^2 \log \R {N_{B,t} N_{B,r}}} 
 }
 %
-Here \m {\log N_B} is small in our experiments, and if we dropped some constants and \m {\log N_B}, then we may assume \m {\mathcal {O} \SB {N_H^2}}.
+Here \m {\log N_{B,t}, \log N_{B,r}} are small in our experiments, and if we drop them we may assume \m {\mathcal {O} \SB {N_H^2}}.
 

### 2021-02-11 presentation/4_conclusion.tex
Transfer chap 1, 4 to LaTeX

@@
 
-\I Destino, Juntti, and Nagaraj (2015): \Quote {Leveraging sparsity into massive MIMO channel estimation with the adaptive-LASSO}, in \It {IEEE Global Conference on Signal and Information Processing}
+\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics}, 2007.
 }
@@
 {\tfx
-\I E Candès and J Romberg, \Quote {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved online, 2005.
-
-\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics}, 2007.
-
-\I E Vlachos, G C Alexandropoulos, and J Thompson (2019): \Quote {Wideband MIMO channel estimation for hybrid beamforming millimeter wave systems via random spatial sampling}, \It {IEEE Journal of Selected Topics in Signal Processing}, 2019
+\I G Destino, M Juntti, and S Nagaraj (2015): \Quote {Leveraging sparsity into massive MIMO channel estimation with the adaptive-LASSO}, in \It {IEEE Global Conference on Signal and Information Processing}
 
@@
 \I J A Tropp and A C Gilbert, \Quote {Signal recovery from random measurements via orthogonal matching pursuit}, \It {IEEE Transactions on information theory}, 2007.
+
+\I E Vlachos, G C Alexandropoulos, and J Thompson (2019): \Quote {Wideband MIMO channel estimation for hybrid beamforming millimeter wave systems via random spatial sampling}, \It {IEEE Journal of Selected Topics in Signal Processing}, 2019
 }

### 2021-02-11 treatise-context/1_introduction.tex
Transfer chap 1, 4 to LaTeX

@@
 
-Candès and Tao \cite [Can05] showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability.
+It is shown that in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability \cite [Can05].
 
@@
 
-Because the limit of hybrid structure, the designs which use a fully digital beamforming is not directly usable, and the designs which use only analog beamforming might not be optimal, which we have to investigate.
-Moreover, we demonstrate that convex programming outperforms greedy methods, and may be necessary in less ideal situations.
+Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
+Moreover, it appears possible that that convex programming outperforms greedy methods, and is necessary in less ideal situations.
 
-In this treatise, we consider a hybrid structure with uniform linear array.
-We generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
-In chapter 2 we shall see that our proposed sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS.
-In chapter 3, we give a quantitative bound (which holds for high probability) on expected error norm.
-In chapter 4, numerical results show that in our problem configuration, DS is superior to other methods.
+In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
+In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
+In chapter 3, we shall see that our proposed sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
+and we give a quantitative bound (which holds for high probability) on expected error norm.
+In chapter 4, numerical results show that DS is superior to other methods for our problem.
 Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.
 
-We claim that, for given number of sampling, DS recovers more successfully than OMP.
+It appears that, for given number of sampling, DS recovers more successfully than OMP.
 Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] with only analog combiner,
-our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite [LGL16],
-and we do not rely on additional assumption on spatially as in Gao, Dai, and Wang \cite [GDW15].
+and our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite [LGL16],
+and we do not rely on additional assumption on sparsity as in Gao, Dai, and Wang \cite [GDW15].
 
-It is different from Bajwa et.\ al.\ \cite [BHS10], and while they require a series of random pilot vectors and the sensing stage take considerable time, we require only random sensing matrices and take just a few time frames.
+It also is different from Bajwa et.\ al.\ \cite [BHS10];
+while they require a series of random pilot vectors and consequently the sensing stage take considerable time, we require only i.i.d.\ random sensing matrices and take just a few time frames.
 
-In addition, we claim that with the same threshold, DS is better than Lasso.
-Again, the proposed method is more general than Lian, Liu and Lau \cite [LLL17] with only analog combiner,
+In addition, it seems that with the same threshold, DS is better than Lasso.
+Again, our proposed method is more general than Lian, Liu and Lau \cite [LLL17] with only analog combiner,
 and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite [DJN15],

### 2021-02-11 treatise-context/4_simulation.tex
Transfer chap 1, 4 to LaTeX

@@
 
-We may applied DS more than once to better estimate the nonzero components, which let us call the successive estimation method.
-We apply DS for the first time.
-Then we extract largest components of the estimated vector, and apply DS again.
-Then we extract largest components of the second estimated vector, and apply Moore–Penrose inverse.
-Finally, the resulting indices set has to be scrambled back corresponding to the original ones.
-The idea is mentioned \cite [CaT07] without further numerical verification.
+We can apply DS more than once to better estimate the nonzero components;
+let us call it the successive estimation \cite [CaT07].
+We apply DS for the first time, and we extract largest components of the estimated vector.
+Then and apply DS again, and we extract largest components of the second estimated vector.
+Finally, we apply Moore–Penrose inverse as the solution.
+The resulting indices set has to be scrambled back according to the original indices.
 
@@
 
-If more than one stage of estimation is possible, that is, there are more than one data set, the second step may be run on the second dataset, and so on.
-It is not impossible to run it for three or more times, but we are not sure that is helpful.
+If more than one stage of estimation is possible, that is, there are more than one data sets, the second stage may be run on the second dataset, and so on.
+It is possible in theory to run it for three or more times.
 
-From our observation, it is not obvious whether the successive estimation method is more accurate.
-It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H}, and it is not obvious what the best choice is.
+From our observation, it is not conclusive whether the successive estimation method is more accurate, and whether a third or more stage is helpful.
+It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H}.
 We have not used this method in the plots included here.
@@
 However, there is not simple way to determine the value of \m {\l} in advance.
-We have tried \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.
+We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.
 
@@
 
-We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}.
-For the plots of assorted methods, \m {7} values of \m {\s} are considered; for the plots of DS or OMP only, \m {9} values are considered.
-
+We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
 We take \m {N_H} to be \m {6, 12, 18}, respectively.
@@
 The number of grid of quantization of phase shifters is \m {16}.
-The number of paths \m {L = NN_HH /2}.
+The number of paths \m {L = N_H /2}.
 The ratio of the wavelength of carrier over the antenna spacing, \m {\l _{\Rm {ant}} / d _{\Rm {ant}} = 1 / 2}.
@@
 For OMP, we consult Cai and Wang \cite [CaW11] for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
-We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3 \R {N_{B,r} N_{B,t}}}} for 2-norm condition.
+We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3} \SB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
 Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
@@
 Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {8 \D 256} times.
+
+The parameters related to precision of the Newton step may be adjusted from CVXPY's class methods.
+We set the maximum absolute tolerance to be \m {5 \D 10 ^ {-7}},
+the maximum relative tolerance to be \m {5 \D 10 ^ {-6}},
+the maximum feasible tolerance to be \m {5 \D 10 ^ {-7}}.
+If the tolerance parameters are set too small, the program often gives overflowing values, perhaps because it was not able to find feasible solutions.
+And if they are set too big, the Newton steps get imprecise and the performance is poorer.
+It remains to determine the best choice of parameters.
 
@@
 However, we remark that when \m {\VNm {\V {h}}_2} is small, this can blow up.
-Indeed, since we did not consider a definite a channel model in this treatise, \m {\T {\chi}} may not necessarily be proportional to the channel capacity
-
-The parameters related to precision of the Newton step may be adjusted from CVXPY's class methods.
-We set the maximum absolute tolerance to be \m {5 \D 10 ^ {-7}},
-the maximum relative tolerance to be \m {5 \D 10 ^ {-6}},
-the maximum feasible tolerance to be \m {5 \D 10 ^ {-7}}.
-If the tolerance parameters are set too small, the program often gives overflowing values, perhaps because it was not able to find feasible solutions.
-And if they are set too big, the Newton steps get imprecise and the performance is poorer.
-It remains to determine the best choice of parameters.
+Indeed, since we did not consider a definite a channel model in this treatise, \m {\T {\chi}} may not necessarily be proportional to the channel capacity.
 
@@
 
-\stopsubsection
-
-In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many steps were calculated.
 Suppose a linear program has \m {N} dimension variable and \m {M} inequality constraints, then the complexity is \m {\MS {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite [BoV04], p.6).
 For our case, that would be \m {\MS {O} \SB {4 N_H ^4 \D 8 N_H^2} = \MS {O} \SB {N_H^6}}.
+But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.
 
-Alternatively, suppose Newton method is used, and we have self-concordance for linear program.
+Alternatively, suppose Newton method is used.
+Here, we have self-concordance for linear program.
+Let \m {\V {g} _0} denote the starting value of \m {\V {g}'}, and \m {\V {g} ^{\star}} the the point of convergence.
 Then the number of Newton steps is bounded \cite [BoV04] by
@@
 %
-Let \m {\V {g} _0} denote the starting value of \m {\V {g}'}, and \m {\V {g} ^{\star}} the the point of convergence.
-Then Boyd and Vandenberghe \cite [BoV04] (p.505, Eqn.9.56) gave a bound of the number of steps.
-If we just take that as the complexity bound for DS, it becomes
+If we just take that as the complexity bound for DS,
 %
@@
 
-Lasso is equivalent to a QCQP, and there is not always a closed form for its complexity.
-However, Lasso and DS are equivalent in certain conditions \cite [AsR10], and we may suppose here they have the same complexity.
+Lasso is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
+However, Lasso and DS are equivalent in certain conditions \cite [AsR10], and we may suppose here they have the same complexity, \m {\MS {O} \SB {N_H^6}}.
+
 Alternatively, an argument similar to the above one for DS is valid for Lasso.
@@
 
-All plots included in this treatise, in total, took probably one month to run.
-Figures 6 and 10 each took about \m {3} days.
+All plots included in this treatise, in total, took about one month to run.
+Figures for \m {N_H = 18} each took about \m {3} days.
 The computer has \m {32} GB RAM, and Intel Core i9 processor.
-Simulation ran on Linux subsystem 2 of Windows 10.
+Simulation was run on Linux subsystem 2 of Windows 10.
 
 Use \m {t_{\Rm {OMP}} \SB {N_H}}, \m {t_{\Rm {Lasso}} \SB {N_H}}, \m {t_{\Rm {DS}} \SB {N_H}} to denote their respective time taken.
-We reproduce the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
+We here copy the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
 They are: \m {
@@
 
-Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
-It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
+Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
+It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
 The matrix inversion is probably the bottleneck of complexity.
@@
 In general, \m {t_{\Rm {DS}} \gg t_{\Rm {Lasso}} \gg t_{\Rm {OMP}}}.
-It is now wonder that, given that OMP is a greedy algorithm, the time OMP takes is negligibly small.
+It is not surprising that, given that OMP is a greedy algorithm, the time OMP takes is negligibly small.
 But it is also notable that, while Lasso has form similar to DS, it takes much lower time.

### 2021-02-11 treatise-context/5_conclusion.tex
Transfer chap 1, 4 to LaTeX

--- 2020-12-31 treatise-context/5_conclusion.tex
@@
 
-The treatise addresses the problem of effective estimation of the millimeter wave channel by exploiting its sparsity.
-To do so, we try the Dantzig Selector (DS) for channel estimation, rather than the more commonly used Orthogonal Matching Pursuit (OMP).
-We exploited the sparsity of spatial frequency domain, and generalized DS for complex vectors.
+The treatise aims to answer the problem of effective estimation of the MIMO millimeter wave channel by exploiting its sparsity.
+To do so, we try the Dantzig Selector (DS) for channel estimation.
+We exploited the sparsity of spatial frequency domain, and justified the RIP of effective beamformer for the hybrid structure.
 We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
+Regarding the complexity, we also suggested several ways to reduce it without losing much performance, as justified by simulation.
+Simulation is done, and we see that DS indeed outperforms other methods.
 
-DS is cast into an linear program, which help reduce complexity.
-Simulation is done, and DS's performance is compared to OMP, Lasso, and LS, and we see that DS indeed outperforms other methods.
-Despite of its higher complexity, in the low noise scenario, DS can be \m {10} times more accurate, and the gain of spectral efficiency may justify its use.
+It seems that DS is more accurate but has higher complexity.
+When the number of RF chain is more limited, or fewer stages of estimation is possible, it might be the case that only DS can recover successfully.
+Therefore, DS may be used, possibly in combination of other methods, in the scenario that precision is crucial, and when the sample is less sufficient and the noise level is higher.
 

### 2021-02-11 treatise-context/abstract.tex
Transfer chap 1, 4 to LaTeX

\starttitle [title={Abstract}]

Multiple-input multiple-output communication system in millimeter wave band is gradually being adopted.
However, channel estimation becomes considerably difficult, due to the larger antennae array, and greedy algorithms such as Orthogonal Matching Pursuit are sometimes used reduce the complexity.
Meanwhile, hybrid beamforming is often used to reduce the number of RF chains, and with such constraint, fully digital designs cannot be directly applied, and fully analog designs might not be optimal.

We consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
We generate random beamforming matrices, and use Dantzig Selector to estimate the channel in the space frequency domain, and we give a quantitative bound (which holds for high probability) on expected error norm.

To reduce the complexity, we cast it as a linear program, and also suggest the basis pursuit denoising form.
Numerical results show that DS is superior, especially when the sample is less sufficient and the noise level is higher.
We therefore propose that DS may be used as the number of RF chains is more limited, or when fewer stages of estimation is possible.

\stoptitle

### 2021-02-11 treatise-pdflatex/4_simulation.tex
Transfer chap 1, 4 to LaTeX

@@
 
-\subsection {A Two-Stage Version}
+\section {Variants}
 
-We also tried another version of DS, in which DS is applied twice in estimated nonzero components.
-The two-stage method was briefly mentioned \cite {CaT07} without further numerical verification.
-It goes as follows:
-We first apply DS as before;
-we extract largest components of the estimated vector, and apply DS again;
-we extract largest components of the second estimated vector, and apply Moore–Penrose inverse;
-finally, indices set has to be scrambled back corresponding to the original ones.
+We remark some possible variants of DS, either to enhance the accuracy, or to reduce the complexity, or both.
+
+\subsection {Successive estimation of nonzero components}
+
+We can apply DS more than once to better estimate the nonzero components;
+let us call it the successive estimation \cite [CaT07].
+We apply DS for the first time, and we extract largest components of the estimated vector.
+Then and apply DS again, and we extract largest components of the second estimated vector.
+Finally, we apply Moore–Penrose inverse as the solution.
+The resulting indices set has to be scrambled back according to the original indices.
 
@@
 
-Unfortunately, the two-stage method is not always more accurate than the one-stage method, so we did not include it in the plots.
-It might have something to do with appropriately scaling \m {\g_{\mathrm {DS}}} with respect to \m {N_H}, and we do not know what the best choice is.
+If more than one stage of estimation is possible, that is, there are more than one data sets, the second stage may be run on the second dataset, and so on.
+It is possible in theory to run it for three or more times.
+
+From our observation, it is not conclusive whether the successive estimation method is more accurate, and whether a third or more stage is helpful.
+It might have something to do with appropriately scaling \m {\g_{\mathrm {DS}}} with respect to \m {N_H}.
+We have not used this method in the plots included here.
+
+\subsection {Basis pursuit denoising}
+
+It is known that DS is equivalent to the basis pursuit denoising form below, for suitable \m {\l} (\cite {BoV04}, p.334).
+
+\Disp {
+\Hat {\V {g}}
+\leftarrow \Min {\V {g}' \in \mathbb {C} ^{N_H^2}}
+\RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty}
+}
+
+However, there is not simple way to determine the value of \m {\l} in advance.
+We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\mathrm {DS}}} in the simulation.
 
@@
 
-We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}.
-For the plots of assorted methods, \m {7} values of \m {\s} are considered; for the plots of DS or OMP only, \m {9} values are considered.
-
-We take \m {N_H} to be \m {12, 18, 24}, respectively.
-For assorted plots, two series of plots are simulated.
-The first series for \m {N_B = N_H}, giving \m {12, 18, 24}.
-The second series for \m {N_B = \lfloor 5 N_H /6 \rfloor}, giving \m {10, 15, 20}.
-The third series for \m {N_B = \lfloor 2 N_H /3 \rfloor}, giving \m {8, 12, 16}.
-For plots of OMP only, we consider \m {N_B = \lfloor N_H \rfloor}.
-For plots of DS only, we consider \m {N_B = \lfloor 5 N_H /6 \rfloor}.
-On the other hand, \m {N_R} always set to be \m {\lfloor \RB {\log N_H}^2 \rfloor}.
+We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
+We take \m {N_H} to be \m {6, 12, 18}, respectively.
+For assorted plots, three series of plots are simulated.
+The first series for \m {N_{B,t} = N_H/2} and \m {N_{B,r} = N_H/3}.
+The second series for \m {N_{B,t} = N_H/3} and \m {N_{B,r} = N_H/2}.
+The third series for \m {N_{B,t} = N_H/2} and \m {N_{B,r} = N_H/2}.
 Unfortunately, this is very far from achieving the ideal values \eqref {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
@@
 Other parameters are fixed in these experiments.
-The number of grid of quantization of analog beamformers is \m {16}.
-The number of paths \m {L} is \m {4}.
-The wavelength of carrier \m {\l _{\mathrm {ant}}} is set to be \m {0.1}, and the antenna spacing \m {d _{\mathrm {ant}}} is \m {0.2}; only their ratio matters.
+The number of grid of quantization of phase shifters is \m {16}.
+The number of paths \m {L = N_H /2}.
+The ratio of the wavelength of carrier over the antenna spacing, \m {\l _{\mathrm {ant}} / d _{\mathrm {ant}} = 1 / 2}.
 
 Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
-In the plots of assorted methods, we set \m {\g_{\mathrm {DS}} = 2 \R {\log N_H}} as suggested in \cite {CaT07}.
+We set \m {\g_{\mathrm {DS}} = 2 \R {\log N_H}} as suggested in \cite {CaT07}.
 For sake of comparison, \m {\g_{\mathrm {Lasso}} = 2 \R {\log N_H}} too.
-For OMP, suggested values in Cai and Wang \cite {CaW11} is illuminating, where they considered \m {\ell _2}-norm in their Theorem 7, and \m {\ell _\infty}-norm in their Theorem 8.
-We simply take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm constraint, \m {\h_{\mathrm {OMP}} = \R {3 N_B}} for 2-norm constraint.
+For OMP, we consult Cai and Wang \cite {CaW11} for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
+We take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3} \SB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
 Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\mathrm {DS}}} and \m {\h_{\mathrm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
-The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
+The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.
 
@@
 
-For performance metric, we follow Lee, Gil, and Lee \cite {LGL16},
+The parameters related to precision of the Newton step may be adjusted from CVXPY's class methods.
+We set the maximum absolute tolerance to be \m {5 \D 10 ^ {-7}},
+the maximum relative tolerance to be \m {5 \D 10 ^ {-6}},
+the maximum feasible tolerance to be \m {5 \D 10 ^ {-7}}.
+If the tolerance parameters are set too small, the program often gives overflowing values, perhaps because it was not able to find feasible solutions.
+And if they are set too big, the Newton steps get imprecise and the performance is poorer.
+It remains to determine the best choice of parameters.
+
+For performance metric, we follow Lee, Gil, and Lee \cite [LGL16] to use
 \DispNum {h:h:lo:vg} {
@@
 }
-However, we note that when \m {\VNm {\V {h}}_2} is small, this can blow up.
-We do not know either whether \m {\tilde {\chi}} is a good indicator of channel capacity; it seems to be, but actually we did not consider a definite a channel model in this treatise.
-
-The parameters related to precision of the Newton step may be adjusted from CVXPY's class methods.
-We set the maximum absolute tolerance to be \m {5 \D 10 ^ {-7}},
-the maximum relative tolerance to be \m {5 \D 10 ^ {-6}},
-the maximum feasible tolerance to be \m {5 \D 10 ^ {-7}}.
-If the tolerance parameters are set too small, the program often gives overflowing values, perhaps because it was not able to find feasible solutions.
-And if they are set too big, the Newton steps get imprecise and the performance is poorer.
-More tests are necessary to determine the best choice of parameters.
+However, we remark that when \m {\VNm {\V {h}}_2} is small, this can blow up.
+Indeed, since we did not consider a definite a channel model in this treatise, \m {\T {\chi}} may not necessarily be proportional to the channel capacity.
 
@@
 
-\begin {figure} [hbt]
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,t}}.
+
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-small-square-two.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-small-tall-two.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-small-wide-two.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-small-square-four.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-small-tall-four.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-small-wide-four.png}
@@
 
-\begin {figure} [hbt]
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,t}}.
+
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-medium-square-two.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-medium-tall-two.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-medium-wide-two.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-medium-square-four.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-medium-tall-four.png}
@@
 
-\begin {figure} [hbt]
+\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-medium-wide-four.png}
-\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 12}, with \m {4} stages, error.}
+\caption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {4} stages, error.}
 \end {figure}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-small-square-two.png}
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,t}}.
+
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-square-two.png}
 \caption {\m {N_{B,t} = 12, N_{B,r} = 12, N_H = 18}, with \m {2} stages, error.}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-small-tall-two.png}
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-tall-two.png}
 \caption {\m {N_{B,t} = 8, N_{B,r} = 12, N_H = 18}, with \m {2} stages, error.}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-small-wide-two.png}
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-wide-two.png}
 \caption {\m {N_{B,t} = 12, N_{B,r} = 8, N_H = 18}, with \m {2} stages, error.}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-small-square-two.png}
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-square-four.png}
 \caption {\m {N_{B,t} = 12, N_{B,r} = 12, N_H = 18}, with \m {4} stages, error.}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-small-tall-two.png}
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-tall-four.png}
 \caption {\m {N_{B,t} = 8, N_{B,r} = 12, N_H = 18}, with \m {4} stages, error.}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-small-wide-two.png}
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-wide-four.png}
 \caption {\m {N_{B,t} = 12, N_{B,r} = 8, N_H = 18}, with \m {4} stages, error.}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-small-square-two.png}
+Regarding runtime statistics, we only plot the case where \m {N_{B,t} = N_{B,r} = N_H /2} with \m {2} stages.
+
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {time-small-square-two.png}
 \caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, time.}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-medium-square-two.png}
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {time-medium-square-two.png}
 \caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, time.}
@@
 
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {error-big-square-two.png}
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {time-big-square-two.png}
 \caption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {4} stages, time.}
@@
 
-In figures 21 and 22, we reproduce two cases of success and failure of DS.
+In figures 24 and 25, we reproduce two cases of success and failure of DS.
 In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.
@@
 \bigskip
-\begin {figure} [hbt]
-\includegraphics [width = \textwidth] {scatter-ddss-failure.png}
+\begin {figure} [H]
+\includegraphics [width = 0.8 \textwidth] {scatter-ddss-failure.png}
 \caption {A scatter plot of position versus magnitude for a case in which DS failed.}
@@
 %
-\begin {figure} [hbt]
+\begin {figure} [H]
+\includegraphics [width = 0.8 \textwidth] {scatter-ddss-success.png}
 \caption {A scatter plot of position versus magnitude for a case in which DS succeeded.}
-\includegraphics [width = \textwidth] {scatter-ddss-success.png}
 \end {figure}
@@
 
-\subsection {Asymtotic analysis}
+We discuss the complexity of DS, Lasso, and OMP.
 
-We discuss the complexity of DS and OMP.
-In general, complexity of convex programs is difficult to analyze, in that it is not easily to determine how many iterations were done.
-Boyd and Vandenberghe \cite {BoV04} analyzed complexity of inequality constrained Newton method, in which self-concordance is assumed (p.496, also p.531).
-In our case, Candès and Romberg \cite {CaR05} pointed out that the complex DS can be cast into an second order cone programming (SOCP), and where self concordance holds.
-Diamond and Boyd (writers of CVXPY) \cite {DiB16} explained that convex programs are usually converted into primal-dual problems.
-The library we called in the simulation is ECOS, where Newton method is used.
-Of course, we are not certain there is no method faster than Newton method, and implementation details of CVXPY may change the conclusion too.
+\subsection {Dantzig Selector}
 
-We attemp to give a heuristic argument regarding the complexity of Newton steps.
-We say the function being minimized is \m {\VNm {\V {g}}_1}.
-Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
-Then Boyd and Vandenberghe \cite {BoV04} (p.505, Eqn.9.56) gave a bound of the number of steps.
-If we just take that as the complexity bound for DS, it becomes
+Suppose a linear program has \m {N} dimension variable and \m {M} inequality constraints, then the complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite {BoV04}, p.6).
+For our case, that would be \m {\mathcal {O} \SB {4 N_H ^4 \D 8 N_H^2} = \mathcal {O} \SB {N_H^6}}.
+But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.
+
+Alternatively, suppose Newton method is used.
+Here, we have self-concordance for linear program.
+Let \m {\V {g} _0} denote the starting value of \m {\V {g}'}, and \m {\V {g} ^{\star}} the the point of convergence.
+Then the number of Newton steps is bounded \cite {BoV04} by
+%
+\Disp {
+C_{\mathrm {Newton}}
+= \RB {C_0 \VNm {\V {g}_0 -\V {g} ^{\star}}_1
++ \log_2 \log_2 \frac {1} {\e}}
+}
+%
+If we just take that as the complexity bound for DS,
 %
@@
 Here \m {C_0} is constant related to implementation of Newton method, and \m {\e} the tolerance of error, and \m {C_{\mathrm {step}}} is the complexity of Newton step.
-According to their analysis (Eqn.9.57), for most cases \m {-\log_2 \log_2 \e} can be bounded by \m {6}.
-Also, \m {C_0} usually assumes the value of about several hundred.
-There was an example they gave in which \m {C_0 =375}, where, with their notation,
-\m {C_0 =(20 -8\a) / (\a \b \RB {1 -2\a}^2}), where \m {\a = 0.1, \b = 0.8, \e =0.01}, and \m {\a, \b} are parameters used in the Backtrack Line Tracing algorithm).
 
@@
 
-On the other hand, Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}.
-They gave
+\subsection {Orthogonal matching pursuit}
+
+Tropp and Gilbert \cite {TrG07a} discussed the complexity of OMP in the companion paper \cite {TrG07b}, giving
 %
@@
 C_{\mathrm {OMP}}
-=\mathcal {O} \SB {N_H^2 \log \R {N_{B,t} N_{B,r}}} 
+=\mathcal {O} \SB {N_H^2 \log \RB {N_{B,r} N_{B,t}}}
 }
 %
-Here \m {\log N_{B,t}, \log N_{B,r}} are small in our experiments, and if we drop them we may assume \m {\mathcal {O} \SB {N_H^2}}.
+Here \m {\log \RB {N_{B,r} N_{B,t}}} is small in our experiments, and if we dropped it, we may take
+\DispNum {C:P:ON:H2} {
+C_{\mathrm {OMP}}
+=\mathcal {O} \SB {N_H^2}
+}
 
-Lastly, since Lasso involves the same target function as DS, the same argument is valid, giving \m {C_{\mathrm {Lasso}} =\mathcal {O} \SB {N_H^6}}.
+\subsection {Lasso}
+
+Lasso is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
+However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity, \m {\mathcal {O} \SB {N_H^6}}.
+
+Alternatively, an argument similar to the above one for DS is valid for Lasso.
+
+Therefore we take
+\DispNum {C:o:ON:H6} {
+C_{\mathrm {Lasso}}
+=\mathcal {O} \SB {N_H^6}
+}
 
@@
 
-All plots included in this treatise, in total, took probably one month to run.
-Figures 6 and 10 each took about \m {3} days.
+All plots included in this treatise, in total, took about one month to run.
+Figures for \m {N_H = 18} each took about \m {3} days.
 The computer has \m {32} GB RAM, and Intel Core i9 processor.
-Simulation ran on Linux subsystem 2 of Windows 10.
+Simulation was run on Linux subsystem 2 of Windows 10.
 
 Use \m {t_{\mathrm {OMP}} \SB {N_H}}, \m {t_{\mathrm {Lasso}} \SB {N_H}}, \m {t_{\mathrm {DS}} \SB {N_H}} to denote their respective time taken.
-We reproduce the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
-\DispNum {t:2:95:55} {
-t_{\mathrm {OMP}} \SB {12} = 0.0119,
-t_{\mathrm {OMP}} \SB {16} = 0.0297, \\
-t_{\mathrm {OMP}} \SB {20} = 0.0600,
-t_{\mathrm {OMP}} \SB {24} = 0.155, \\
+We here copy the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
+They are:
+\m {t_{\mathrm {OMP}} \SB {12}  = 0.0119,}
+\m {t_{\mathrm {OMP}} \SB {16} = 0.0297, }
+\m {t_{\mathrm {OMP}} \SB {20}  = 0.0600,}
+\m {t_{\mathrm {OMP}} \SB {24} = 0.155, }
 %
-t_{\mathrm {Lasso}} \SB {12} = 0.0436,
-t_{\mathrm {Lasso}} \SB {16} = 0.176, \\
-t_{\mathrm {Lasso}} \SB {20} = 0.471,
-t_{\mathrm {Lasso}} \SB {24} = 1.26, \\
+\m { t_{\mathrm {Lasso}} \SB {12}  = 0.0436,}
+\m { t_{\mathrm {Lasso}} \SB {16} = 0.176, }
+\m { t_{\mathrm {Lasso}} \SB {20}  = 0.471,}
+\m { t_{\mathrm {Lasso}} \SB {24} = 1.26, }
 %
-t_{\mathrm {DS}} \SB {12} = 0.357,
-t_{\mathrm {DS}} \SB {16} = 2.07, \\
-t_{\mathrm {DS}} \SB {20} = 29.8,
-t_{\mathrm {DS}} \SB {24} = 91.5, 
-}
-Simulation indeed shows that \m {t_{\mathrm {DS}}} grows tremendously with (in our case) \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite {FrS07} on the high complexity of DS.
-It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating (in our case) \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
+\m { t_{\mathrm {DS}} \SB {12}  = 0.357,}
+\m { t_{\mathrm {DS}} \SB {16} = 2.07, }
+\m { t_{\mathrm {DS}} \SB {20}  = 29.8,}
+\m { t_{\mathrm {DS}} \SB {24} = 91.5}
+
+Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite {FrS07} on the high complexity of DS.
+It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
 The matrix inversion is probably the bottleneck of complexity.

### 2021-02-11 treatise-pdflatex/5_conclusion.tex
Convert: newcommand, organization
Conversion: compile chap 3
Transfer chap 1, 4 to LaTeX

--- 2020-12-31 treatise-context/5_conclusion.tex
@@
-\startchapter [title={Conclusion}]
+\chapter {Conclusion}
 
-The treatise addresses the problem of effective estimation of the millimeter wave channel by exploiting its sparsity.
-To do so, we try the Dantzig Selector (DS) for channel estimation, rather than the more commonly used Orthogonal Matching Pursuit (OMP).
-We exploited the sparsity of spatial frequency domain, and generalized DS for complex vectors.
+The treatise aims to answer the problem of effective estimation of the MIMO millimeter wave channel by exploiting its sparsity.
+To do so, we try the Dantzig Selector (DS) for channel estimation.
+We exploited the sparsity of spatial frequency domain, and justified the RIP of effective beamformer for the hybrid structure.
 We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
+Regarding the complexity, we also suggested several ways to reduce it without losing much performance, as justified by simulation.
+Simulation is done, and we see that DS indeed outperforms other methods.
 
-DS is cast into an linear program, which help reduce complexity.
-Simulation is done, and DS's performance is compared to OMP, Lasso, and LS, and we see that DS indeed outperforms other methods.
-Despite of its higher complexity, in the low noise scenario, DS can be \m {10} times more accurate, and the gain of spectral efficiency may justify its use.
-
-\stopchapter
+It seems that DS is more accurate but has higher complexity.
+When the number of RF chain is more limited, or fewer stages of estimation is possible, it might be the case that only DS can recover successfully.
+Therefore, DS may be used, possibly in combination of other methods, in the scenario that precision is crucial, and when the sample is less sufficient and the noise level is higher.

### 2021-02-11 treatise-pdflatex/abstract.tex
Front matter passes compilation
Transfer chap 1, 4 to LaTeX

@@
-\starttitle [title={Abstract}]
+\chapter* {Abstract}
 
-Multiple-input-multiple-output (MIMO) is the future of wireless communication, but the large number of antennae makes it difficult to estimate its channel state information.
-Since millimeter wave (mm-Wave) band, which is often used together with MIMO, is known to exhibit sparsity, results on compressive sensing suggest that, on mm-Wave band, fewer channel measurements shall suffice.
-Current literature prefers orthogonal matching pursuit (OMP) due to its lower complexity.
-It is interesting to note that Dantzig Selector (DS), claimed to have various performance guarantee, has seldom been examined.
+Multiple-input multiple-output communication system in millimeter wave band is gradually being adopted.
+However, channel estimation becomes considerably difficult, due to the larger antennae array, and greedy algorithms such as Orthogonal Matching Pursuit are sometimes used reduce the complexity.
+Meanwhile, hybrid beamforming is often used to reduce the number of RF chains, and with such constraint, fully digital designs cannot be directly applied, and fully analog designs might not be optimal.
 
-In this treatise, we consider a mm-Wave MIMO channel, and a hybrid beamforming structure at both the transmitter and receiver end.
-We demonstrate that DS can be applied on a entrywise i.i.d.\ random beamformers, and give a bound for its expected error norm, which holds for high probability.
-DS is cast as a linear program, and simulation is done, showing that, in our problem setting, DS is superior in terms of relative error norm.
+We consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
+We generate random beamforming matrices, and use Dantzig Selector to estimate the channel in the space frequency domain, and we give a quantitative bound (which holds for high probability) on expected error norm.
 
-\stoptitle
+To reduce the complexity, we cast it as a linear program, and also suggest the basis pursuit denoising form.
+Numerical results show that DS is superior, especially when the sample is less sufficient and the noise level is higher.
+We therefore propose that DS may be used as the number of RF chains is more limited, or when fewer stages of estimation is possible.

### 2021-02-11 treatise-pdflatex/functions.py

@@ -23,7 +23,7 @@ def execute (ver):
    time_tot_start = time.time ()
    for i_s_g in range (cst.NUM_S_G ()):
       s_g = cst.S_G_INIT () * (cst.SCALE_S_G () ** i_s_g)
-      print ("σ = ", '%.2f' % s_g, " :", sep = '')
+      print ("noise: ", '%.2f' % s_g, " :", sep = '')
       lst_err = [0] * cst.NUM_MET ()
       lst_time = [0] * cst.NUM_MET ()
       for j_met in range (cst.NUM_MET ()):

### 2021-02-12 treatise-context/4_simulation.tex
check chap 2, 3 LaTeX

@@
 From the simulation, DS outperforms other methods in most of the datasets.
-In the scenario of low noise, \m {\T {\chi}} values of OMP and Lasso are close to DS.
-But in the scenario of high noise, \m {\T {\chi}} values of OMP and Lasso blow up quickly.
+With low noise, \m {\T {\chi} _{\Rm {DS}} \approx \T {\chi} _{\Rm {OMP}} \approx \T {\chi} _{\Rm {Lasso}} \approx \T {\chi} _{\Rm {LS}}}.
+But with high noise, \m {\T {\chi} _{\Rm {OMP}}, \T {\chi} _{\Rm {Lasso}}, \T {\chi} _{\Rm {LS}}} blow up quickly,
+and it is usually true that \m {\T {\chi} _{\Rm {DS}} \leq \T {\chi} _{\Rm {OMP}} \leq \T {\chi} _{\Rm {Lasso}} \leq \T {\chi} _{\Rm {LS}}}.
 
-It is intuitive that when \m {N_{B,t} /N_{B,r}} is smaller, \m {\T {\chi}} is smaller, because we have a higher sample rate.
-As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, the DS line improves more significantly, and \m {\T {\chi}} falls nearly always below \m {0} dB for \m {N_{B,t} > N_{B,r}} case.
+For OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
+We keep in mind that a different design of sensing matrix, or a distribution of angles, will affect the performance of OMP.
 
-The design of sample matrix seems to have a lot to do with the performance of OMP.
-In Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
-It may also have something to do with the distribution of angles of departure and arrival.
+For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
+Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
+Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
 
-The performance of Lasso also fails mostly for low noise.
-Recall from above that \m {\g} (or \m {\l}) is crucial to the performance, but cannot be obtained in advance.
-Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
-We should not however there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
-
-For Moore Penrose pseudoinverse, \m {\T {\chi}} increases tremendously as \m {\s} decreases, and the trend is steady and may serve as a upper bound.
-
-For DS itself, \m {\T {\chi}} decreases as \m {\s} increases, which is expected, but \m {\T {\chi}} does not go down indefinitely.
-The values of threshold of DS \m {\g_{\Rm {DS}}} are chosen within the order of magnitude of \m {\s}.
-It may have been that the iteration stabilizes much earlier than is constrained by maximum iteration number.
+For DS itself, first, \m {\T {\chi} _{\Rm {DS}}} certainly decreases as \m {\s} increases, but it does not decrease indefinitely.
+Second, \m {\T {\chi} _{\Rm {DS}}} decreases as \m {N_H} increases.
+Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\T {\chi} _{\Rm {DS}}} is smaller, because we have a higher sample rate.
+As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, \m {\T {\chi} _{\Rm {DS}}} improves more significantly.
 
@@
 \NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
-= \NC \s \MS {O} \RB {1} \NR
+= \NC \s N_H^2 \MS {O} \RB {1} \NR
 }

### 2021-02-12 treatise-pdflatex/4_simulation.tex
check chap 2, 3 LaTeX

@@
 
-In the assorted plots, DS steadily outperforms other methods.
-From lowest to highest error, it usually goes like this: DS, LS, Lasso, OMP.
+From the simulation, DS outperforms other methods in most of the datasets.
+With low noise, \m {\tilde {\chi} _{\mathrm {DS}} \approx \tilde {\chi} _{\mathrm {OMP}} \approx \tilde {\chi} _{\mathrm {Lasso}} \approx \tilde {\chi} _{\mathrm {LS}}}.
+But with high noise, \m {\tilde {\chi} _{\mathrm {OMP}}, \tilde {\chi} _{\mathrm {Lasso}}, \tilde {\chi} _{\mathrm {LS}}} blow up quickly,
+and it is usually true that \m {\tilde {\chi} _{\mathrm {DS}} \leq \tilde {\chi} _{\mathrm {OMP}} \leq \tilde {\chi} _{\mathrm {Lasso}} \leq \tilde {\chi} _{\mathrm {LS}}}.
 
-The performance of OMP appears to be poor.
-In most cases, the estimation fails, and we have \m {\tilde {\chi}} close to the unity.
-Varying thresholds of OMP, namely \m {\h_{\mathrm {OMP}}}, does not give different result.
+For OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
+We keep in mind that a different design of sensing matrix, or a distribution of angles, will affect the performance of OMP.
 
-A crucial reason might be that Lee, Gil, and Lee \cite {LGL16} proposed a high-complexity nonconvex program for the beamformers, which they gave approximation, and we have here a low-complexity, randomly-generated beamformers.
-It may also have something to do with the distribution of angles of departure and arrival;
-their distribution lies within a cluster of standard deviation 15 degrees, and in ours, they are uniform on the unit circle.
-It remains to see how OMP and DS compare, if done according to their procedure.
+For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
+Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
+Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
 
-The performance of Lasso also fails mostly, and \m {\tilde {\chi}} even increase as \m {\s} decreases, which is strange.
-
-For Moore Penrose pseudoinverse, \m {\tilde {\chi}} decreases steadily as \m {\s} decreases.
-
-For DS itself, \m {\tilde {\chi}} decreases as \m {\s} increases, which is expected, but \m {\tilde {\chi}} does not go down indefinitely, even for very low \m {\s}.
-The values of threshold of DS \m {\g_{\mathrm {DS}}} are chosen within the order of magnitude of \m {\s}.
-For high signal level, \m {\g_{\mathrm {DS}}} does not affect much, but for low signal level a greater value may be more effective.
-It may have been that the iteration stabilizes much earlier than is constrained by maximum iteration number.
+For DS itself, first, \m {\tilde {\chi} _{\mathrm {DS}}} certainly decreases as \m {\s} increases, but it does not decrease indefinitely.
+Second, \m {\tilde {\chi} _{\mathrm {DS}}} decreases as \m {N_H} increases.
+Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\tilde {\chi} _{\mathrm {DS}}} is smaller, because we have a higher sample rate.
+As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, \m {\tilde {\chi} _{\mathrm {DS}}} improves more significantly.
 
@@
 
-We are not sure either why \m {\tilde {\chi}} is an overestimation of \m {\chi} by several orders of magnitude.
-A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
+\m {\tilde {\chi}} is not shown in the figure, because the big O bound is much larger than \m {\chi}.
+It is possible that the nonsparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
+It is curious to see whether for very large \m {N_H}, whether \m {\tilde {\chi}} and \m {\tilde {\chi}} will be asymptotically close.
 
@@
 \mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
-= \s \mathcal {O} \RB {1} 
+= \s N_H^2 \mathcal {O} \RB {1} 
 }

### 2021-02-12 treatise-pdflatex/1_introduction.tex
Conversion: compile chap 3
LaTeX chap 1 literature review

@@
 
-\bigskip
 \begin {figure} [hbt]
@@
 \end {figure}
-\bigskip
 
@@
 \DispNum {N:p:Nm:Nm} {
-N_p \gg N_m \\
+N_p \gg N_m 
 }
@@
 \V {y}
-=\M {Q} \V {x} \\
+=\M {Q} \V {x} 
 }
@@
 \V {x} _{\SB {\mathcal {A}}}
-=\V {x} \\
+=\V {x} 
 }
@@
 \DispNum {A:A:s::s:} {
-\Nm {\mathcal {A}} \leq s. \\
+\Nm {\mathcal {A}} \leq s. 
 }
@@
 \V {y}
-=\M {Q} \V {x} + \V {z} \\
+=\M {Q} \V {x} + \V {z} 
 }
@@
 \M {Q}  _{\SB {\mathcal {A}}}
-=\sum _{i \in \mathcal {A}} \M {Q} _{\SB {:,i}} \\
+=\sum _{i \in \mathcal {A}} \M {Q} _{\SB {:,i}} 
 }
@@
 %
-\leq \RB {1+\d_s} \VNm {\V {x}} _2 ^2 \\
+\leq \RB {1+\d_s} \VNm {\V {x}} _2 ^2 
 }
@@
 \mathrm {subject} \; \mathrm {to} \quad & \VNm {\M {Q}^\dagger \RB {\M {Q} \V {h}' -\V {y}}} _\infty \leq \g \\
-\end {cases} \\
+\end {cases} 
 }
@@
 
-Here the constant \m {\d_s} in Definition [1] is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
+Here the constant \m {\d_s} is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
 A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite {BDD08} that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
 
-Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
-An early attempt to apply compressive sensing was Bajwa et.\ al.\ \cite {BHS10}, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
+Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
+Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
 The accompanying note by the same researchers \cite {BHR08} showed that \m {X} has RIP for overwhelming probability, justifying their work.
+
+Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
+In fact, it can be shown that Lasso and DS have similar behavior \cite {AsR10}.
+Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite {LLL17}.
+Destino, Juntti, and Nagaraj used an adaptive Lasso \cite {DJN15}, in which they jointly optimize the sensing matrix and pilot vectors.
+Vlachos, Alexandropoulos, and Thompson \cite {VAT19} used Lasso on hybrid beamforming with an additional random spatial sampling device.
 
@@
 At the same time, Tropp and Gilbert \cite {TrG07b} suggested likewise that a greedy algorithm called orthogonal matching pursuit (OMP) which also aims to reconstruct a sparse signal in an underdetermined system.
-Again consider the situation of \ref {y:y:Qx:xz}.
+Again consider the situation of \eqref {y:y:Qx:xz}.
 
@@
 S
-\leftarrow \varnothing \\
+\leftarrow \varnothing 
 }
@@
 \leftarrow \underset {n' =0, \dots, N_p-1} {\mathrm {argmax}}
-\Nm {\M {Q} _{\SB {:,n'}} \V {r}} \\
+\Nm {\M {Q} _{\SB {:,n'}} \V {r}} 
 }
@@
 \V {r}
-\leftarrow \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} \\
+\leftarrow \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} 
 }
@@
 \VNm {\V {r}} _2
-<\eta \\
+<\eta 
 }
@@
 \hat {\V {g}}
-\leftarrow \M {Q} ^\ddagger \V {y} \\
+\leftarrow \M {Q} ^\ddagger \V {y} 
 }
@@
 
-OMP has since been pervasively used for channel sensing.
+OMP has since been commonly used for channel estimation.
 Alkhateeb et.\ al.\ \cite {AEL14} proposed an adaptive algorithm with a beam codebook for quantized angles.
-Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamformers based on nonuniform fixed set of angles.
-Gao et.\ al.\ \cite {LGC16} proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals.
+Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
 Hu, Wang, and He \cite {HWH13} applied OMP to estimate quantized path delay of OFDM subcarriers of stationary channel gain.
-Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the effective beamformer serves as sensing matrix, based on a designed set of angles.
-Manoj and Kannu \cite {MaK17} studied the sparse condition on submatrices of the signal for successful reconstruction.
-Gurbuz, Yapici, and Guvenc \cite {GYG18} introduced perturbation on the angles which the sensing matrix based on.
-Panayirci et.\ al.\ \cite {PAU19} proposed a concatenation of max-likelihood estimation of model parameters, and maximum-a-posteriori estimation of channel gains, by virtue of OMP.
+Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the sensing matrix serves as sensing matrix, based on a designed set of angles.
+Gao, Dai, and Wang proposed a variant which there is the assumption of spatially common sparsity \cite {GDW15}.
 

### 2021-02-14 treatise-context/1_introduction.tex
LaTeX chap 1 literature review
LaTeX: align equations

@@
 
-Here the constant \m {\d_s} in Definition [1] is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
-A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
+Here the constant \m {\d_s} is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
+A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}} _2} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
 
 Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
-Bajwa et.\ al.\ \cite [BHS10] used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
-The accompanying note by the same researchers \cite [BHR08] showed that \m {X} has RIP for overwhelming probability, justifying their work.
+Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response,
+and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.
 
@@
 In fact, it can be shown that Lasso and DS have similar behavior \cite [AsR10].
-
 Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite [LLL17].
@@
 \LA \NC \underset {n' =0, \dots, N_p-1} {\Rm {argmax}}
-\Nm {\M {Q} _{\SB {:,n'}} \V {r}} \NR
+\Nm {\M {Q} _{\SB {:,n'}} ^\Adj \V {r}} \NR
 }
@@
 %
-The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix in the case of DS.
+The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix of DS.
 In each step, we estimate the noise \m {\V {r}}, and find a new column most correlated with it, to refine the estimation for \m {\V {x}}.
-From Tropp and Gilbert \cite [TrG07a], the probability that OMP recovers \m {\V {x}} completely is overwhelming.
+It is shown that the probability that OMP recovers \m {\V {x}} completely is overwhelming \cite [TrG07a].
 

### 2021-02-14 treatise-context/2_problem_setting.tex
Transfer chap 1, 4 to LaTeX
check chap 2, 3 LaTeX
LaTeX: align equations

@@
 \DispNum {F:R:1::R1} {
-\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
+\NC \Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
 = \NC 1, \NR
 %
-\NC \Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
+\NC \Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
 = \NC 1, \NR
@@
 %
-\NC n_{B,t}
+\NC n_{R,t}
 = \NC 0, \dots N_{B,t}-1 \NR
 %
-\NC n_{B,r}
+\NC n_{R,r}
 = \NC 0, \dots N_{B,r}-1 \NR
@@
 \NC N_H \gg \NC N_{B,t}, N_{R,t} \NR
-%
-\NC N_{B,t}, N_{B,t} \NR
 }
 
-Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_{B,r} \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_H \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
 Let us introduce the effective channel
@@
 %
-Our task then amounts to recovering \m {\M {H}}, and designing \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.
+Our task then amounts to recovering \m {\M {H}}, and generating \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.
 
@@
 := \NC \Rm {vec} \SB {\M {Y}}
-\in \MB {C} ^{N_B^2} \NR
+\in \MB {C} ^{N_{B,t} N_{B,r}} \NR
 %
@@
 := \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
-\in \MB {C} ^{N_B^2} \NR
+\in \MB {C} ^{N_{B,t} N_{B,r}} \NR
 %
@@
 := \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
-\in \MB {C} ^{N_B^2 \D N_H^2} \NR
+\in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2} \NR
 }
@@
 +\M {W} _B \M {W} _R \M {Z}
-\in \MB {C} ^{N_B \D N_B} \NR
+\in \MB {C} ^{N_{B,r} \D N_{B,t}} \NR
 }
@@
 :=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
-\in \MB {C} ^{N_B^2 \D N_H^2} \NR
+\in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2} \NR
 }

### 2021-02-14 treatise-context/3_2_generating_beamforming_matrices.tex
LaTeX: align equations

--- 2021-01-26 treatise-context/3_2_design_of_beamformers.tex
@@
-\startsection [title={Generation of beamformers}]
+\startsection [title={Generating beamforming matrices}]
 
-\startsubsection [title={Generation of beamformers}]
+\startsubsection [title={The plan}]
 
-We want to set the four beamformers to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
+We want to set the four beamforming matrices to be i.i.d.\ random matrix, hoping that the resulting \m {\M {P}} has RIP.
 Let us simply set each entry of \m {\M {F} _B} to be i.i.d.\ normal random variables with mean \m {0}, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
@@
 
-\startsubsection [title={Operator norm of digital beamformers}]
+\startsubsection [title={Operator norm of digital beamforming matrices}]
 
@@
 
-\startsubsection [title={Operator norm of analog beamformers}]
+\startsubsection [title={Operator norm of analog beamforming matrices}]
 

### 2021-02-14 treatise-pdflatex/1_introduction.tex
LaTeX: align equations

@@
 \V {x}  _{\SB {\mathcal {A}}}
-=\sum _{i \in \mathcal {A}} \V {v} \V {u} _{i} \\
+=&\sum _{i \in \mathcal {A}} \V {v} \V {u} _{i} \\
 %
 \M {Q}  _{\SB {\mathcal {A}}}
-=\sum _{i \in \mathcal {A}} \M {Q} _{\SB {:,i}} 
+=&\sum _{i \in \mathcal {A}} \M {Q} _{\SB {:,i}} 
 }
@@
 \RB {1-\d_s} \VNm {\V {x}} _2 ^2
-\leq \VNm {\M {Q} \V {x}} _2 ^2 \\
+\leq &\VNm {\M {Q} \V {x}} _2 ^2 \notag \\
 %
-\leq \RB {1+\d_s} \VNm {\V {x}} _2 ^2 
+\leq &\RB {1+\d_s} \VNm {\V {x}} _2 ^2 
 }
@@
 Here the constant \m {\d_s} is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
-A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite {BDD08} that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
+A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite {BDD08} that if \m {\VNm {\M {Q} \V {x}} _2} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
 
 Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
-Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response.
-The accompanying note by the same researchers \cite {BHR08} showed that \m {X} has RIP for overwhelming probability, justifying their work.
+Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response,
+and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.
 
@@
 \V {r}
-\leftarrow \V {y} \\
+\leftarrow &\V {y} \\
 %
 S
-\leftarrow \varnothing 
+\leftarrow &\varnothing 
 }
@@
 \leftarrow \underset {n' =0, \dots, N_p-1} {\mathrm {argmax}}
-\Nm {\M {Q} _{\SB {:,n'}} \V {r}} 
+\Nm {\M {Q} _{\SB {:,n'}} ^\dagger \V {r}} 
 }
@@
 \M {Q} ^\ddagger
-\leftarrow \RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \\
+\leftarrow &\RB {\M {Q} _{\SB {S}} ^\dagger \M {Q} _{\SB {S}}} ^{-1} \M {Q} _{\SB {S}} ^\dagger \\
 %
 \V {r}
-\leftarrow \V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} 
+\leftarrow &\V {y} -\M {Q} _{\SB {S}} ^\dagger \M {Q} ^\ddagger \V {y} 
 }
@@
 %
-The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix in the case of DS.
+The columns of \m {\M {Q}} are chosen greedily, and we expect its columns to span \m {\V {x}}, playing a role similar to the sensing matrix of DS.
 In each step, we estimate the noise \m {\V {r}}, and find a new column most correlated with it, to refine the estimation for \m {\V {x}}.
-From Tropp and Gilbert \cite {TrG07a}, the probability that OMP recovers \m {\V {x}} completely is overwhelming.
+It is shown that the probability that OMP recovers \m {\V {x}} completely is overwhelming \cite {TrG07a}.
 
@@
 
-The literature on channel estimation favors OMP for its low complexity, but we wonder how greedy algorithms, such as OMP, compare to convex programs, such as DS.
-It might be that greedy algorithms trade precision for complexity, and that the opposite is true of convex programs.
+Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
+Moreover, it appears possible that that convex programming outperforms greedy methods, and is necessary in less ideal situations.
 
-In this treatise, we consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite {LGL16}.
-They proposed a beamformer shown to be optimal, jointly designed on both ends by a nonconvex optimization program, and due to its difficulty they have made considerable approximation.
-Is the approximated design still optimal, or are the angles of sensing matrix not sufficiently precise?
+In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
+In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
+In chapter 3, we shall see that our proposed sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
+and we give a quantitative bound (which holds for high probability) on expected error norm.
+In chapter 4, numerical results show that DS is superior to other methods for our problem.
+Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.
 
-In chapter 2 we shall see that our proposed effective beamformer has RIP for high probability, which may serve as the sensing matrix for DS.
-In chapter 3, along the lines of Candès and Tao \cite {CaT07}, we give a quantitative bound (which holds for high probability) on expected error norm.
-In chapter 4, we remark that DS can be cast as a linear program, for which more efficient algorithms exist.
-Numerical results show that in our problem configuration, DS is superior to other methods.
-Indeed, DS is much more accurate than the least square, and both OMP and Lasso often fails.
+It appears that, for given number of sampling, DS recovers more successfully than OMP.
+Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} with only analog combiner,
+and our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite {LGL16},
+and we do not rely on additional assumption on sparsity as in Gao, Dai, and Wang \cite {GDW15}.
+
+It also is different from Bajwa et.\ al.\ \cite {BHS10};
+while they require a series of random pilot vectors and consequently the sensing stage take considerable time, we require only i.i.d.\ random sensing matrices and take just a few time frames.
+
+In addition, it seems that with the same threshold, DS is better than Lasso.
+Again, our proposed method is more general than Lian, Liu and Lau \cite {LLL17} with only analog combiner,
+and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite {DJN15},
+and we do not require special device as in Vlachos, Alexandropoulos, and Thompson \cite {VAT19}.

### 2021-02-14 treatise-pdflatex/2_problem_setting.tex
Transfer chap 1, 4 to LaTeX
check chap 2, 3 LaTeX
LaTeX: align equations

@@
 \f_l
-= 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
+= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
   \; \mathrm {Mod}\; \RB {2\pi} \\
@@
 \th_l
-= 2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
+= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
   \; \mathrm {Mod}\; \RB {2\pi} 
@@
 Each end consists of both digital and analog precoders and combiners.
-In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_{B,t}}} and analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D  N_R}}.
-Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \mathbb {C} ^{N_R \D N_H}} and analog combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D  N_R}}.
+In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_{B,t} \D N_{B,t}}} and analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D N_{B,t}}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \mathbb {C} ^{N_{B,r} \D N_H}} and analog combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}}.
 
@@
 \DispNum {F:R:1::R1} {
-\Nm {\RB {\M {F} _R} _{\SB {n_H, n_R}}}
-= 1, \\
+\Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
+= &1, \\
 %
-\Nm {\RB {\M {W} _R} _{\SB {n_R, n_H}}}
-= 1, \\
+\Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
+= &1, \\
 %
 n_H
-= 0, \dots N_H-1, \\
+= &0, \dots N_H-1, \\
 %
-n_R
-= 0, \dots N_R-1 
+n_{R,t}
+= &0, \dots N_{B,t}-1  \\
+%
+n_{R,r}
+= &0, \dots N_{B,r}-1 
 }
@@
 \DispNum {N:H:NY:NY} {
-N_H \gg N_R \\
-%
-N_R \gg N_{B,r}, N_{B,r}
+N_H \gg N_{B,t}, N_{B,r}
 }
 
-Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}} with each entry being i.i.d.\ standard normal.
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_H \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
 Let us introduce the effective channel
@@
 \DispNum {A:2:Am:N4} {
-\RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \\
+&\RB {\M {A} \otimes \M {B}} _{\SB {m_1, m_2}} \notag \\
 %
-=\M {A} _{\SB {\Fl {m_1/N_3 }, \Fl {m_2/N_4 }}}
+= &\M {A} _{\SB {\Fl {m_1/N_3 }, \Fl {m_2/N_4 }}}
 \M {B} _{\SB {m_1\; \mathrm {Mod}\; N_3, m_2\; \mathrm {Mod}\; N_4}} 
@@
 \V {h}
-:= \mathrm {vec} \SB {\M {H}}
+:= &\mathrm {vec} \SB {\M {H}}
 \in \mathbb {C} ^{N_H^2} \\
@@
 \V {y}
-:= \mathrm {vec} \SB {\M {Y}}
+:= &\mathrm {vec} \SB {\M {Y}}
 \in \mathbb {C} ^{N_{B,t} N_{B,r}} \\
@@
 \V {z}
-:= \mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
+:= &\mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
 \in \mathbb {C} ^{N_{B,t} N_{B,r}} \\
@@
 \M {Q}
-:= \RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
+:= &\RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
 \in \mathbb {C} ^{N_{B,t} N_{B,r} \D N_H^2} 
@@
 \DispNum {K:K:CN:H1} {
-\M {K} \in  \mathbb {C} ^{N_H \D N_H} \\
+\M {K} \in &\mathbb {C} ^{N_H \D N_H} \notag \\
 %
 \M {K} _{\SB {n_1, n_2}}
-= \frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \\
+= &\frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \notag \\
 %
 \quad n_1, n_2
-= 0, 1, \dots, N_H-1 
+= &0, 1, \dots, N_H-1 
 }
@@
 +\M {W} _B \M {W} _R \M {Z}
-\in \mathbb {C} ^{N_{B,t} \D N_{B,r}} 
+\in \mathbb {C} ^{N_{B,r} \D N_{B,t}} 
 }
@@
 :=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
-\in \mathbb {C} ^{N_{B,t} \D N_{B,r} \D N_H^2} 
+\in \mathbb {C} ^{N_{B,t} N_{B,r} \D N_H^2} 
 }

### 2021-02-14 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
LaTeX: align equations

--- 2021-02-10 treatise-pdflatex/3_2_design_of_beamformers.tex
@@
-\section {Design of beamformers}
+\section {Generating beamforming matrices}
 
-\subsection {Design of beamformers}
+\subsection {The plan}
 
-We want to set the four beamformers to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
+We want to set the four beamforming matrices to be i.i.d.\ random matrix, hoping that the resulting \m {\M {P}} has RIP.
 Let us simply set each entry of \m {\M {F} _B} to be i.i.d.\ normal random variables with mean \m {0}, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
@@
 
-\subsection {Operator norm of digital beamformers}
+\subsection {Operator norm of digital beamforming matrices}
 
@@
 
-\subsection {Operator norm of analog beamformers}
+\subsection {Operator norm of analog beamforming matrices}
 
-In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite {KlM17}, Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
+In Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' \cite {KlM17}, Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
 We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
-The conclusions, 
 Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
@@
 \DispNum {W:2:WB:d's} {
-\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \\
+&\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \notag \\
 %
-=\VNm {
+= &\VNm {
    \M {W} _B \M {W} _R \M {K} \M {U} \D
    \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
-   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \\
+   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
 %
-=\VNm {
+= &\VNm {
    \M {W} _B \M {W} _R \M {K} \M {U}
@@
    \R {\mathrm {abs} \SB {\V {d}'}}
-   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \\
+   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
 %
-=\VNm {
+= &\VNm {
    \M {W} _B \M {W} _R \M {K} \M {U}
@@
    \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} \M {U}
-   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \\
+   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \notag \\
 %
-\eqsim \VNm {\M {G}} _2 \RB {1 +2\d_s} 
+\eqsim &\VNm {\M {G}} _2 \RB {1 +2\d_s} 
 }

### 2021-02-15 treatise-context/4_simulation.tex
copy corrected system diagram

@@
 
-In this chapter we shall compare \Rf {d:2:OL:H3} with numerical experiments.
-For the convex optimization, we choose the Python library CVXPY \cite [DiB16].
+To do convex optimization, we choose the Python library CVXPY.
 While a direct implementation of Algorithm [7] leads to extraordinarily large complexity, Candès and Romberg \cite [CaR05] showed that DS can be cast as a linear program, which we elaborate below.
@@
 
-Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
+Let us represent complex vector and matrices by real vector and matrices.
 For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be

### 2021-02-15 treatise-context/5_conclusion.tex
copy corrected system diagram

@@
 
-It seems that DS is more accurate but has higher complexity.
-When the number of RF chain is more limited, or fewer stages of estimation is possible, it might be the case that only DS can recover successfully.
-Therefore, DS may be used, possibly in combination of other methods, in the scenario that precision is crucial, and when the sample is less sufficient and the noise level is higher.
+We believe that DS is more accurate while having higher complexity.
+When the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
+Therefore, DS may be used in the scenario that precision is crucial, and in the scenario that the number of RF chain is more limited or fewer stages of estimation is possible.
 

### 2021-02-15 treatise-pdflatex/4_simulation.tex
LaTeX: align equations
copy corrected system diagram

@@
 
-In this chapter we shall compare \eqref {d:2:OL:H3} with numerical experiments.
-For the convex optimization, we choose the Python library CVXPY \cite {DiB16}.
+To do convex optimization, we choose the Python library CVXPY.
 While a direct implementation of Algorithm [7] leads to extraordinarily large complexity, Candès and Romberg \cite {CaR05} showed that DS can be cast as a linear program, which we elaborate below.
@@
 
-Let us represent complex vector and matrices by real ones, consisting of its real and imaginary parts.
+Let us represent complex vector and matrices by real vector and matrices.
 For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathcal {R} \SB {\V {x}}} of \m {\V {x}} to be
@@
 \mathcal {R} \SB {\V {x}}
-\in \mathbb {R} ^{2M} \\
+\in &\mathbb {R} ^{2M} \notag \\
 \mathcal {R} \SB {\V {x}} _{\SB {m}}
-= \begin {cases}
+= &\begin {cases}
 \mathfrak {Re} \SB {\V {x} _{\SB {m'}}}, & m =2m' \\
 \mathfrak {Im} \SB {\V {x} _{\SB {m'}}}, & m =2m'+1 \\
-\end {cases} \\
+\end {cases} \notag \\
 m' 
-=  0, 1, 2, \ldots, M-1 
+= &0, 1, 2, \ldots, M-1 
 }
@@
 \mathcal {R} \SB {\M {A}}
-\in \mathbb {R} ^{2M_1 \D 2M_2} \\
-\mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}} =
-\begin {cases}
+\in &\mathbb {R} ^{2M_1 \D 2M_2} \notag \\
+\mathcal {R} \SB {\M {A}} _{\SB {m_1,m_2}}
+= &\begin {cases}
 \mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1', 2m_2'} \\
@@
 \mathfrak {Re} \SB {\M {A} _{\SB {m_1',m_2'}}}, & \RB {m_1, m_2} = \RB {2m_1'+1, 2m_2'+1} \\
-\end {cases} \\
+\end {cases} \notag \\
 m_1 
-= 0, 1, 2, \ldots, M_1 -1 \\
+= &0, 1, 2, \ldots, M_1 -1 \notag \\
 m_2 
-= 0, 1, 2, \ldots, M_2 -1 
+= &0, 1, 2, \ldots, M_2 -1 
 }
@@
 With these, we define
-%
 
@@
 \tilde {\V {y}}
-= \mathcal {R} \SB {\V {y}}
-\in \mathbb {R} ^{2 N_{B,t} N_{B,r}} \\
+= &\mathcal {R} \SB {\V {y}}
+\in \mathbb {R} ^{2 N_{B,t} N_{B,r}} \notag \\
 %
 \tilde {\V {g}}
-= \mathcal {R} \SB {\V {g}}
-\in \mathbb {R} ^{2 N_H^2} \\
+= &\mathcal {R} \SB {\V {g}}
+\in \mathbb {R} ^{2 N_H^2} \notag \\
 %
 \tilde {\M {P}}
-= \mathcal {R} \SB {\M {P}}
-\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \\
+= &\mathcal {R} \SB {\M {P}}
+\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \notag \\
 %
 \tilde {\M {P}} ^\Adj
-= \mathcal {R} \SB {\M {P} ^\Adj}
-\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \\
+= &\mathcal {R} \SB {\M {P} ^\Adj}
+\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \notag \\
 %
 \tilde {\V {z}}
-= \mathcal {R} \SB {\V {z}}
+= &\mathcal {R} \SB {\V {z}}
 \in \mathbb {R} ^{2 N_{B,t} N_{B,r}} 
@@
 N_0
-=2 N_H^2, \\
+= &2 N_H^2, \\
 N_2
-=\lfloor 4 \log N_H \rfloor, \\
+= &\lfloor 4 \log N_H \rfloor, \\
 N_1
-=\lfloor \R {N_0 N_2} \rfloor 
+= &\lfloor \R {N_0 N_2} \rfloor 
 }
@@
 \V {g}_0
-=\V {g}_{\mathrm {LS}} \\
+=\V {g}_{\mathrm {LS}}
 = \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} 
@@
    \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
-   -\V {g}} _1} N_H^4 \\
+   -\V {g}} _1} N_H^4
 =\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 
@@
 \DispNum {t:P:NH:83} {
-\tilde {t}_{\mathrm {OMP}} \eqsim \mathcal {O} \SB {N_H^{3.6}} \\
-\tilde {t}_{\mathrm {Lasso}} \eqsim \mathcal {O} \SB {N_H^{4.8}} \\
-\tilde {t}_{\mathrm {DS}} \eqsim \mathcal {O} \SB {N_H^{8.3}} 
+\tilde {t}_{\mathrm {OMP}} \eqsim &\mathcal {O} \SB {N_H^{3.6}} \\
+\tilde {t}_{\mathrm {Lasso}} \eqsim &\mathcal {O} \SB {N_H^{4.8}} \\
+\tilde {t}_{\mathrm {DS}} \eqsim &\mathcal {O} \SB {N_H^{8.3}} 
 }

### 2021-02-15 treatise-pdflatex/5_conclusion.tex
copy corrected system diagram

@@
 
-It seems that DS is more accurate but has higher complexity.
-When the number of RF chain is more limited, or fewer stages of estimation is possible, it might be the case that only DS can recover successfully.
-Therefore, DS may be used, possibly in combination of other methods, in the scenario that precision is crucial, and when the sample is less sufficient and the noise level is higher.
+We believe that DS is more accurate while having higher complexity.
+When the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
+Therefore, DS may be used in the scenario that precision is crucial, and in the scenario that the number of RF chain is more limited or fewer stages of estimation is possible.

### 2021-02-18 treatise-context/1_introduction.tex
minor typos

@@
 
-It is shown that in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability \cite [Can05].
+It is shown that in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_p}-dimensional signal, with \m {N_m} measurements, under overwhelming probability \cite [Can05].
 
@@
 
-For concreteness, say \m {\V {z}} is an i.i.d.\ normalized random normal vector.
-If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig selector (DS), recovery under the noisy case is again possible under high probability.
+For concreteness, say \m {\V {z}} is an i.i.d.\ random normal vector.
+If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig selector (DS), recovery under the noisy case is again possible.
 
@@
 Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability.
-The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear Program, rendering convex programming technique applicable.
-This allows techniques from convex optimization to be used, and Candès and Romberg provided an implementation on their website \cite [CaR05].
+The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program, for which techniques from convex optimization may be used, and Candès and Romberg provided an implementation on their website \cite [CaR05].
 
 Here the constant \m {\d_s} is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
-A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}} _2} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
+A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established \cite [BDD08] that if \m {\VNm {\M {Q} \V {x}} _2} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
 
@@
 OMP has since been commonly used for channel estimation.
-Alkhateeb et.\ al.\ \cite [AEL14] proposed an adaptive algorithm with a beam codebook for quantized angles.
 Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
-Hu, Wang, and He \cite [HWH13] applied OMP to estimate quantized path delay of OFDM subcarriers of stationary channel gain.
-Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the sensing matrix serves as sensing matrix, based on a designed set of angles.
-Gao, Dai, and Wang proposed a variant which there is the assumption of spatially common sparsity \cite [GDW15].
+Hu, Wang, and He \cite [HWH13] applied OMP to estimate path delay of OFDM subcarriers.
+Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix.
+Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite [GDW15].
 
 Performance guarantee of OMP is also studied on various conditions.
-Cai, Wang, and Xu \cite [CWX10], gave a new bound on performance of OMP under assumption of low coherence of columns of matrices, instead of almost unitarity.
+Cai, Wang, and Xu \cite [CWX10] gave a new bound on performance of OMP under assumption of low coherence of columns.
 Cai and Wang \cite [CaW11] extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite [BEE10] followed up and refined their bounds, concluding that OMP is better for low SNR scenario, and DS is better for high SNR.
@@
 while they require a series of random pilot vectors and consequently the sensing stage take considerable time, we require only i.i.d.\ random sensing matrices and take just a few time frames.
+Also, their constraint on \m {\ell_0} norm may not hold, and they restrict to single antenna case.
 

### 2021-02-18 treatise-context/2_problem_setting.tex
minor typos

@@
 
-For simplicity we suppose uniform linear arrays, for which the response be modeled as thus,
+For simplicity we suppose uniform linear arrays, for which the response would be,
 %
@@
 \externalfigure [system.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {Schematic diagram of the hybrid beamforming system we consider, based on Akdeniz et.\ al.\ \cite [ALS14].}
+\FigureCaption {Schematic diagram of the hybrid beamforming system we consider.}
 \blank [big]

### 2021-02-18 treatise-context/4_simulation.tex
minor typos

@@
 We can apply DS more than once to better estimate the nonzero components;
-let us call it the successive estimation \cite [CaT07].
+let us call it the successive estimation \cite {CaT07}.
 We apply DS for the first time, and we extract largest components of the estimated vector.
-Then and apply DS again, and we extract largest components of the second estimated vector.
-Finally, we apply Moore–Penrose inverse as the solution.
+Then we apply DS again, and we extract largest components of the second estimated vector.
+Finally, we apply Moore–Penrose inverse to get the returned solution.
 The resulting indices set has to be scrambled back according to the original indices.
@@
 From our observation, it is not conclusive whether the successive estimation method is more accurate, and whether a third or more stage is helpful.
-It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H}.
+It might have something to do with appropriately scaling \m {N_1, N_2} with respect to \m {N_H}.
 We have not used this method in the plots included here.
@@
 Second, \m {\T {\chi} _{\Rm {DS}}} decreases as \m {N_H} increases.
-Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\T {\chi} _{\Rm {DS}}} is smaller, because we have a higher sample rate.
-As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, \m {\T {\chi} _{\Rm {DS}}} improves more significantly.
+Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\T {\chi} _{\Rm {DS}}} is also smaller, because we have a higher sample rate.
 
@@
 
-\m {\T {\chi}} is not shown in the figure, because the big O bound is much larger than \m {\chi}.
+\m {\chi} is not shown in the figure, because the big O bound is much larger than \m {\T {\chi}}.
 It is possible that the nonsparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
@@
 \DispNum {O:j:sO:O1} {
-\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
+\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}}}
 = \NC \s N_H^2 \MS {O} \RB {1} \NR
 }
-Then we have
+Then we simply have
 %

### 2021-02-18 treatise-pdflatex/1_introduction.tex
minor typos

@@
 
-Candès and Tao \cite {Can05}, one of the earlier investigations on compressive sensing, showed that, in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_m}-dimensional signal, with \m {N_p} measurements, under overwhelming probability.
+It is shown that in the noiseless case, a \m {\ell_1}-minimization program recovers the \m {N_p}-dimensional signal, with \m {N_m} measurements, under overwhelming probability \cite {Can05}.
 
@@
 
-For concreteness, say \m {\V {z}} is an i.i.d.\ normalized random normal vector.
-If so, a stronger result was established \cite {CaT07} that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible under high probability.
+For concreteness, say \m {\V {z}} is an i.i.d.\ random normal vector.
+If so, a stronger result was established \cite {CaT07} that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible.
 
@@
 Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability.
-The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear Program, rendering convex programming technique applicable.
-This allows techniques from convex optimization to be used, and Candès and Romberg provided an implementation on their website \cite {CaR05}.
+The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program, for which techniques from convex optimization may be used, and Candès and Romberg provided an implementation on their website \cite {CaR05}.
 
 Here the constant \m {\d_s} is significant, since we can't just take \m {\M {Q}} to be any unitary matrix, for which \m {\d_s =0}.
-A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established by Baraniuk et.\ al.\ \cite {BDD08} that if \m {\VNm {\M {Q} \V {x}} _2} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
+A common approach is choosing i.i.d.\ entries of \m {\M {Q}}, and it was established \cite {BDD08} that if \m {\VNm {\M {Q} \V {x}} _2} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability, but it remains to conceive an algorithm that efficiently generates RIP matrices.
 
@@
 OMP has since been commonly used for channel estimation.
-Alkhateeb et.\ al.\ \cite {AEL14} proposed an adaptive algorithm with a beam codebook for quantized angles.
 Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
-Hu, Wang, and He \cite {HWH13} applied OMP to estimate quantized path delay of OFDM subcarriers of stationary channel gain.
-Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the sensing matrix serves as sensing matrix, based on a designed set of angles.
-Gao, Dai, and Wang proposed a variant which there is the assumption of spatially common sparsity \cite {GDW15}.
+Hu, Wang, and He \cite {HWH13} applied OMP to estimate path delay of OFDM subcarriers.
+Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix.
+Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite {GDW15}.
 
 Performance guarantee of OMP is also studied on various conditions.
-Cai, Wang, and Xu \cite {CWX10}, gave a new bound on performance of OMP under assumption of low coherence of columns of matrices, instead of almost unitarity.
+Cai, Wang, and Xu \cite {CWX10} gave a new bound on performance of OMP under assumption of low coherence of columns.
 Cai and Wang \cite {CaW11} extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite {BEE10} followed up and refined their bounds, concluding that OMP is better for low SNR scenario, and DS is better for high SNR.

### 2021-02-18 treatise-pdflatex/2_problem_setting.tex
minor typos

@@
 \includegraphics [width = \textwidth] {system.png}
-\caption {Schematic diagram of the hybrid beamforming system we consider, based on Akdeniz et.\ al.\ \cite {ALS14}.}
+\caption {Schematic diagram of the hybrid beamforming system we consider.}
 \end {figure}

### 2021-02-18 treatise-pdflatex/4_simulation.tex
minor typos

@@
 We apply DS for the first time, and we extract largest components of the estimated vector.
-Then and apply DS again, and we extract largest components of the second estimated vector.
-Finally, we apply Moore–Penrose inverse as the solution.
+Then we apply DS again, and we extract largest components of the second estimated vector.
+Finally, we apply Moore–Penrose inverse to get the returned solution.
 The resulting indices set has to be scrambled back according to the original indices.
@@
 From our observation, it is not conclusive whether the successive estimation method is more accurate, and whether a third or more stage is helpful.
-It might have something to do with appropriately scaling \m {\g_{\mathrm {DS}}} with respect to \m {N_H}.
+It might have something to do with appropriately scaling \m {N_1, N_2} with respect to \m {N_H}.
 We have not used this method in the plots included here.
@@
 Second, \m {\tilde {\chi} _{\mathrm {DS}}} decreases as \m {N_H} increases.
-Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\tilde {\chi} _{\mathrm {DS}}} is smaller, because we have a higher sample rate.
-As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, \m {\tilde {\chi} _{\mathrm {DS}}} improves more significantly.
+Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\tilde {\chi} _{\mathrm {DS}}} is also smaller, because we have a higher sample rate.
 
@@
 
-\m {\tilde {\chi}} is not shown in the figure, because the big O bound is much larger than \m {\chi}.
+\m {\chi} is not shown in the figure, because the big O bound is much larger than \m {\tilde {\chi}}.
 It is possible that the nonsparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
@@
 \DispNum {O:j:sO:O1} {
-\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
+\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}}}
 = \s N_H^2 \mathcal {O} \RB {1} 

### 2021-03-02 treatise-context/1_introduction.tex
Slight rev contribution

@@
 To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
+We use subscript in square brackets, like \m {\MS {A}}, to denote extraction of components.
 That is, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
@@
 
-Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability.
+Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability and is nearly optimal \cite [CaT07].
 The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program, for which techniques from convex optimization may be used, and Candès and Romberg provided an implementation on their website \cite [CaR05].
@@
 and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.
+However, there seems to be no work by now which addresses the constraint of hybrid beamforming.
 
@@
 Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
-Moreover, it appears possible that that convex programming outperforms greedy methods, and is necessary in less ideal situations.
+Indeed, if DS is shown to be optimal \cite [CaT07], then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary in less ideal situations.
 
@@
 In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
-In chapter 3, we shall see that our proposed sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
+Because of the hybrid structure, here it is not possible to generate the sensing matrix by i.i.d.\ entries, which requires a fully digital structure.
+But in chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
 and we give a quantitative bound (which holds for high probability) on expected error norm.
 In chapter 4, numerical results show that DS is superior to other methods for our problem.
+Since DS is more accurate, it can be used when the sample is less sufficient and the noise level is higher, where it might be the case that only DS can recover successfully.
 Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.

### 2021-03-02 treatise-context/5_conclusion.tex
minor typos
Slight rev contribution

@@
 To do so, we try the Dantzig Selector (DS) for channel estimation.
-We exploited the sparsity of spatial frequency domain, and justified the RIP of effective beamformer for the hybrid structure.
+We exploited the sparsity of spatial frequency domain, and justified the RIP of effective beamforming matrix for the hybrid structure.
 We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
@@
 
-We believe that DS is more accurate while having higher complexity.
-When the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
-Therefore, DS may be used in the scenario that precision is crucial, and in the scenario that the number of RF chain is more limited or fewer stages of estimation is possible.
+We corroborate the prediction that DS is nearly optimal, and it may extract more information than other methods do when the sampling rate is low.
+Since DS is more accurate while having higher complexity, when the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
+Therefore, DS may be used in the scenario that precision is crucial, as well as that the number of RF chain is more limited or fewer stages of estimation is possible.
 

### 2021-03-02 treatise-pdflatex/1_introduction.tex
Slight rev contribution

@@
 To be precise, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
+We use subscript in square brackets, like \m {\mathcal {A}}, to denote extraction of components.
 That is, if there is some \m {\mathcal {A} \subseteq \CB {0, \dots, N_p-1}} such that
@@
 For concreteness, say \m {\V {z}} is an i.i.d.\ random normal vector.
-If so, a stronger result was established \cite {CaT07} that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible.
+If so, a stronger result was established that, with another \m {\ell_1} minimization program called Dantzig selector (hereafter DS), recovery under the noisy case is again possible.
 
@@
 
-Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability.
+Algorithm [2] recovers \m {\V {x}} with the expected error norm bounded with overwhelming probability and is nearly optimal \cite {CaT07}.
 The \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a linear program, for which techniques from convex optimization may be used, and Candès and Romberg provided an implementation on their website \cite {CaR05}.
@@
 Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
-Moreover, it appears possible that that convex programming outperforms greedy methods, and is necessary in less ideal situations.
+Indeed, if DS is shown to be optimal \cite {CaT07}, then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary in less ideal situations.
 

### 2021-03-02 treatise-pdflatex/5_conclusion.tex
minor typos
Slight rev contribution

@@
 
-We believe that DS is more accurate while having higher complexity.
-When the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
-Therefore, DS may be used in the scenario that precision is crucial, and in the scenario that the number of RF chain is more limited or fewer stages of estimation is possible.
+We corroborate the prediction that DS is nearly optimal, and it may extract more information than other methods do when the sampling rate is low.
+Since DS is more accurate while having higher complexity, when the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
+Therefore, DS may be used in the scenario that precision is crucial, as well as that the number of RF chain is more limited or fewer stages of estimation is possible.

### 2021-03-02 treatise-pdflatex/notation.tex
Slight rev contribution

@@
-\starttitle [title={Notation}]
+\chapter*{Notation}
 
-\starttable[|l|l|l|] \HL
-Expression \VL Meaning or Definition \VL More Explanation \SR \HL
-\m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
-\m {\mathfrak {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
-\m {\mathfrak {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
-\m {\V {a}} \VL vector \VL \AR \HL
-\m {\M {A}} \VL matrix \VL \AR \HL
-\m {\V {1}} \VL all-1 vector \VL dimension will be specified \AR \HL
-\m {\V {0}} \VL all-0 vector \VL dimension will be specified \AR \HL
-\m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL
-\m {\M {A} _{\SB {m,n}}} \VL \m {m,n}-th entry of \m {\M {A}} \VL \AR \HL
-\m {\V {a} _{\SB {0}}} \VL the first component of \m {\V {a}} \VL  \AR \HL
-\m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
-\m {\mathbb {K}} \VL either \m {\mathbb {R}} or \m {\mathbb {C}} \VL  \AR \HL
-\m {\mathbb {K} ^{N}} \VL Hilbert space \m {\mathbb {K}^N} over \m {\mathbb {K}} \VL  \AR \HL
-\m {\mathbb {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
-\m {m\; \mathrm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \mathrm {Mod}\; n <n} \AR \HL
-\m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
-\m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
- \VL component of \m {\V {a}} \VL  \AR \HL
-\m {\mathbb {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
-\m {\mathbb {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
-\m {\mathsf {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
-\stoptable
+\begin{center}
+\begin{tabular}{ l | c | r }
+\hline
+ Expression  &  Meaning or Definition  &  More Explanation  \\ \hline
+ \m {\Nm {a}}  &  magnitude  &  for real or complex numbers  \\ \hline
+ \m {\mathfrak {Re} \SB {a}}  &  real part  &  for complex numbers  \\ \hline
+ \m {\mathfrak {Im} \SB {a}}  &  imaginary part  &  for complex numbers  \\ \hline
+ \m {\V {a}}  &  vector  &   \\ \hline
+ \m {\M {A}}  &  matrix  &   \\ \hline
+ \m {\V {1}}  &  all-1 vector  &  dimension will be specified  \\ \hline
+ \m {\V {0}}  &  all-0 vector  &  dimension will be specified  \\ \hline
+ \m {\V {a} _{\SB {n}}}  &  \m {n}-th component of \m {\V {a}}  &   \\ \hline
+ \m {\M {A} _{\SB {m,n}}}  &  \m {m,n}-th entry of \m {\M {A}}  &   \\ \hline
+ \m {\V {a} _{\SB {0}}}  &  the first component of \m {\V {a}}  &    \\ \hline
+ \m {\M {A} _{\SB {0,0}}}  &  the upper-left entry of \m {\V {A}}  &    \\ \hline
+ \m {\mathbb {K}}  &  either \m {\mathbb {R}} or \m {\mathbb {C}}  &    \\ \hline
+ \m {\mathbb {K} ^{N}}  &  Hilbert space \m {\mathbb {K}^N} over \m {\mathbb {K}}  &    \\ \hline
+ \m {\mathbb {K} ^{M \D N}}  &  collection of \m {M} by \m {N} matrices  &    \\ \hline
+ \m {m\; \mathrm {Mod}\; n}  &  remainder of \m {m} divided by \m {n}  &  with \m {m, n \geq 0} and \m {0 \leq m\; \mathrm {Mod}\; n <n}  \\ \hline
+ \m {\VNm {\V {a}} _p}  &  \m {\ell_p}-norm of \m {\V {a}}  &  \m {p >0}  \\ \hline
+ \m {\VNm {\V {a}} _\infty}  &  the maximum-magnitude  &   \\ \hline
+   &  component of \m {\V {a}}  &    \\ \hline
+ \m {\mathbb {P} \SB {A}}  &  probability of event \m {A}  &    \\ \hline
+ \m {\mathbb {E} \SB {X}}  &  expectation of random variable \m {X}  &    \\ \hline
+ \m {\mathrm {Var} \SB {X}}  &  variance of random variable \m {X}  &    \\ \hline
+\end{tabular}
+\end{center}

### 2021-03-04 treatise-context/1_introduction.tex
Criticize Bajwa et al

@@
 
-It also is different from Bajwa et.\ al.\ \cite [BHS10];
-while they require a series of random pilot vectors and consequently the sensing stage take considerable time, we require only i.i.d.\ random sensing matrices and take just a few time frames.
-Also, their constraint on \m {\ell_0} norm may not hold, and they restrict to single antenna case.
+Our work is also an improvement to Bajwa et.\ al.\ \cite [BHS10].
+First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
+Second, for mm waves, the channel might have a short response, requiring us to send the training signals in a short interval of time, which may not be practical.
+Third, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
+Fourth, generating random sequences can lead to high complexity \cite [LGL16].
 

### 2021-03-04 treatise-pdflatex/1_introduction.tex
Criticize Bajwa et al

@@
 
-It also is different from Bajwa et.\ al.\ \cite {BHS10};
-while they require a series of random pilot vectors and consequently the sensing stage take considerable time, we require only i.i.d.\ random sensing matrices and take just a few time frames.
-Also, their constraint on \m {\ell_0} norm may not hold, and they restrict to single antenna case.
+Our work is also an improvement to Bajwa et.\ al.\ \cite {BHS10}.
+First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
+Second, for mm waves, the channel might have a short response, requiring us to send the training signals in a short interval of time, which may not be practical.
+Third, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
+Fourth, generating random sequences can lead to high complexity \cite {LGL16}.
 

### 2021-03-05 treatise-context/1_introduction.tex
Rev criticize to Bajwa et al

@@
 First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
-Second, for mm waves, the channel might have a short response, requiring us to send the training signals in a short interval of time, which may not be practical.
-Third, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
-Fourth, generating random sequences can lead to high complexity \cite [LGL16].
+Second, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
+Third, generating random sequences can lead to high complexity \cite [LGL16].
 

### 2021-03-05 treatise-pdflatex/1_introduction.tex
Rev criticize to Bajwa et al

@@
 First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
-Second, for mm waves, the channel might have a short response, requiring us to send the training signals in a short interval of time, which may not be practical.
-Third, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
-Fourth, generating random sequences can lead to high complexity \cite {LGL16}.
+Second, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
+Third, generating random sequences can lead to high complexity \cite {LGL16}.
 

### 2021-03-14 treatise-context/1_introduction.tex
Slightly correct grammar

@@
 
-Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification.
-With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain, by virtue of either parallel transmission of data, redundant transmission, or beamforming which improves the signal level.
-Besides, the millimeter wave (mm-wave) is adopted, since its smaller wavelength (and thus higher frequency) makes wider bands available.
+Multiple-input multiple-output (MIMO) communication systems will be part of the 5G specification.
+With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain.
+Parallel and redundant transmission of data improves the error-correcting ability, and beamforming improves the signal level.
+The millimeter wave (mm-wave) is adopted, since its smaller wavelength (and thus higher frequency) makes wider bands available.
 Moreover the antennae may be closer-spaced, allowing us to increase their number \cite [RSM13].
-However, also because of the larger antennae array, and larger noise corruption in higher frequency, estimation of MIMO channel state information gives rise to higher complexity, and hence higher hardware overhead and power consumption.
-Indeed, RF chains are more expensive and power consuming, so there is a growing attention on hybrid beamforming, where there are not fewer RF chain than the antennae.
+However, because of a larger antennae array and of larger noise corruption in higher frequency, estimation of MIMO channel state information gives rise to higher complexity, and hence higher hardware overhead and power consumption.
+Indeed, RF chains are more expensive and power-consuming, so there is growing attention on hybrid beamforming, where there are not fewer RF chain than the antennae.
 
@@
 It amounts to invert a linear system whose dimension is the number of antennae, as we shall see in chapter 2 in more detail.
-In this case, it is pointed out that conventional training based algorithms are not very effective.
+In this case, it is pointed out that conventional training-based algorithms are not very effective.
 
@@
 
-Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
+Fortunately, physical evidence has suggested that mm-wave channels are poor in scattering \cite [ALS14], which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
 
@@
 
-Figure 1 shows a generic situation in which a signal is crowded in the given basis, but is sparse in transformed basis.
+Figure 1 shows a generic situation in which a signal is crowded in the given basis, but sparse in the transformed basis.
 The black line on the left is the original signal, and the yellow line is the reconstruct signal.
-If the signal is sparse on certain new basis, as shown in the right, then for a good approximation, we may take only the largest components for reconstruction.
+If the signal is sparse on a certain new basis, as shown in the right, then for a good approximation, we may take only the largest components for reconstruction.
 
-Generally speaking, compressive sensing aims to reconstruct a underdetermined linear system, when the sparsity of solution guarantees successful recovery for most cases.
+Generally speaking, compressive sensing aims to reconstruct an underdetermined linear system, when the sparsity of solution guarantees successful recovery for most cases.
 More measurements are required to recover the signal in the nonsparse basis, while fewer suffice in the sparse basis.
 But, even if we are sure that the sparse basis exists, its construction is another undertaking.
-In our settings, it is not trivially obvious that hybrid beamforming structure fits the compressive sensing problem, and a method to generating the sensing matrix and pilot vectors in the estimation stage has to be devised and justified.
+In our settings for hybrid beamforming structure, a way of generating the sensing matrix and pilot vectors in the estimation stage has to be devised and justified.
 
-Compressive sensing approaches can be divided into two categories, the convex programming approach, and greedy approach \cite [RDD18].
-We will discuss one from each in more details: Dantzig Selector and Orthogonal Matching Pursuit.
+Compressive sensing approaches can be divided into two categories, the convex programming approach and the greedy approach \cite [RDD18].
+We will discuss one from each in more detail: Dantzig Selector and Orthogonal Matching Pursuit.
 
@@
 
-As an application, it often occurs that a camera takes a high definition photo, and compresses the image later.
-But it may be desirable that a camera equipped with fewer sensors shall take a lower resolution photo to save storage, and shall recover the image later.
-Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, while the accuracy is critical to the diagnosis too \cite [CaT07].
+As an application, it often occurs that a camera takes a high definition photo and compresses the image later.
+But it may be desirable that a camera equipped with fewer sensors shall take a lower resolution photo to save storage, and recover the image later.
+Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, and the accuracy is critical to the diagnosis too \cite [CaT07].
 
@@
 
-Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
-Indeed, if DS is shown to be optimal \cite [CaT07], then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary in less ideal situations.
+Due to the constraint of hybrid structure, the designs which use fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
+Indeed, if DS is shown to be optimal \cite [CaT07], then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary for less ideal situations.
 
-In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
+In this treatise, we consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
 In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
@@
 But in chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
-and we give a quantitative bound (which holds for high probability) on expected error norm.
+and we give a quantitative bound (which holds for high probability) on the expected error norm.
 In chapter 4, numerical results show that DS is superior to other methods for our problem.
 Since DS is more accurate, it can be used when the sample is less sufficient and the noise level is higher, where it might be the case that only DS can recover successfully.
-Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.
+Considering its higher complexity, we remark that it can be cast as a linear program, and the basis pursuit denoising form may be used.
 
-It appears that, for given number of sampling, DS recovers more successfully than OMP.
-Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] with only analog combiner,
+It appears that, for a given number of sampling, DS recovers more successfully than OMP.
+Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] with only an analog combiner,
 and our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite [LGL16],
-and we do not rely on additional assumption on sparsity as in Gao, Dai, and Wang \cite [GDW15].
+and we do not rely on additional assumptions on sparsity as in Gao, Dai, and Wang \cite [GDW15].
 
 Our work is also an improvement to Bajwa et.\ al.\ \cite [BHS10].
-First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
-Second, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
+First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
+Second, with the further constraint of hybrid beamforming, it is unclear whether their guarantee theorem for recovery is still valid.
 Third, generating random sequences can lead to high complexity \cite [LGL16].
@@
 In addition, it seems that with the same threshold, DS is better than Lasso.
-Again, our proposed method is more general than Lian, Liu and Lau \cite [LLL17] with only analog combiner,
+Again, our proposed method is more general than Lian, Liu and Lau \cite [LLL17] with only an analog combiner,
 and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite [DJN15],
-and we do not require special device as in Vlachos, Alexandropoulos, and Thompson \cite [VAT19].
+and we do not require special devices as in Vlachos, Alexandropoulos, and Thompson \cite [VAT19].
 

### 2021-03-14 treatise-context/5_conclusion.tex
Slightly correct grammar

@@
 
-The treatise aims to answer the problem of effective estimation of the MIMO millimeter wave channel by exploiting its sparsity.
+The treatise aims to answer the problem of effective estimating a MIMO millimeter-wave channel by exploiting its sparsity.
 To do so, we try the Dantzig Selector (DS) for channel estimation.
-We exploited the sparsity of spatial frequency domain, and justified the RIP of effective beamforming matrix for the hybrid structure.
+We exploited the sparsity in the spatial frequency domain, and justified the RIP of effective beamforming matrix for the hybrid structure.
 We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
-Regarding the complexity, we also suggested several ways to reduce it without losing much performance, as justified by simulation.
+We also suggested several ways to reduce the complexity without losing much performance, as justified by simulation.
 Simulation is done, and we see that DS indeed outperforms other methods.
@@
 We corroborate the prediction that DS is nearly optimal, and it may extract more information than other methods do when the sampling rate is low.
-Since DS is more accurate while having higher complexity, when the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
-Therefore, DS may be used in the scenario that precision is crucial, as well as that the number of RF chain is more limited or fewer stages of estimation is possible.
+When the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
+Therefore, one may use DS in the scenario that precision is crucial, as well as that the number of RF chains is more limited or fewer stages of estimation is possible.
 

### 2021-03-14 treatise-context/abstract.tex
Slightly correct grammar

@@
 
-Multiple-input multiple-output communication system in millimeter wave band is gradually being adopted.
-However, channel estimation becomes considerably difficult, due to the larger antennae array, and greedy algorithms such as Orthogonal Matching Pursuit are sometimes used reduce the complexity.
-Meanwhile, hybrid beamforming is often used to reduce the number of RF chains, and with such constraint, fully digital designs cannot be directly applied, and fully analog designs might not be optimal.
+Multiple-input multiple-output communication systems in the millimeter-wave band are gradually being adopted.
+A larger antennae array makes channel estimation more difficult.
+Meanwhile, hybrid beamforming, which utilizes fewer RF chains, is applied too, so that new estimation methods have to be designed.
+This can be seen as a compressive sensing problem, for which Orthogonal Matching Pursuit is usually used.
 
-We consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
-We generate random beamforming matrices, and use Dantzig Selector to estimate the channel in the space frequency domain, and we give a quantitative bound (which holds for high probability) on expected error norm.
-
-To reduce the complexity, we cast it as a linear program, and also suggest the basis pursuit denoising form.
+We consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
+We generate random beamforming matrices and use Dantzig Selector to estimate the channel in the space frequency domain.
+Then, we give a quantitative bound (which holds for high probability) on the expected error norm.
+To reduce the complexity, we cast it as a linear program, and suggest the basis pursuit denoising form.
 Numerical results show that DS is superior, especially when the sample is less sufficient and the noise level is higher.
-We therefore propose that DS may be used as the number of RF chains is more limited, or when fewer stages of estimation is possible.
+We therefore propose that DS may be used, when the number of RF chains is more limited or when fewer stages of estimation are possible.
 

### 2021-03-14 treatise-pdflatex/1_introduction.tex
Slightly correct grammar

@@
 
-Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification \cite {RSM13}.
+Multiple-input multiple-output (MIMO) communication systems will be part of the 5G specification.
 With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain.
-The appeal of MIMO includes multiplexing gain (parallel transmission of data), diversity gain (redundant transmission with space-time coding), and antenna gain (suitable beamforming to improve the signal level).
-Besides, the millimeter wave (mm-wave) is suggested, since its smaller wavelength (and thus higher frequency) makes wider bands available.
-Moreover the antennae may be closer-spaced, allowing us to increase their number.
+Parallel and redundant transmission of data improves the error-correcting ability, and beamforming improves the signal level.
+The millimeter wave (mm-wave) is adopted, since its smaller wavelength (and thus higher frequency) makes wider bands available.
+Moreover the antennae may be closer-spaced, allowing us to increase their number \cite {RSM13}.
+However, because of a larger antennae array and of larger noise corruption in higher frequency, estimation of MIMO channel state information gives rise to higher complexity, and hence higher hardware overhead and power consumption.
+Indeed, RF chains are more expensive and power-consuming, so there is growing attention on hybrid beamforming, where there are not fewer RF chain than the antennae.
 
-However, MIMO also gives rise to higher complexity, hence higher hardware overhead and power consumption.
-To obtain channel state information (so that channel capacity can be known for instance), new algorithms have to address these issues.
-Not only is the channel estimation difficult, due to a large antennae array, but the transmission in higher frequency is subject to noise corruption too.
-As a result, conventional training-based algorithms lead to considerable time and space complexity.
+If we consider a slow varying MIMO channel for simplicity, in terms of a channel representation, to estimate the channel is to determine the parameters of the representation.
+It amounts to invert a linear system whose dimension is the number of antennae, as we shall see in chapter 2 in more detail.
+In this case, it is pointed out that conventional training-based algorithms are not very effective.
 
@@
 
-If we consider a slow varying MIMO channel for simplicity, in terms of a channel representation, to estimate the channel is to determine the parameters of the representation.
-We shall see it amounts to invert a linear system whose dimension is the number of antennae, which is not very effective.
-Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite {ALS14}, which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
+Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
 
@@
 
-Figure 1 shows a generic situation in which a signal is crowded in the given basis, but is sparse in transformed basis.
+Figure 1 shows a generic situation in which a signal is crowded in the given basis, but sparse in the transformed basis.
 The black line on the left is the original signal, and the yellow line is the reconstruct signal.
-If the signal is sparse on certain new basis, as shown in the right, then for a good approximation, we may take only the largest components for reconstruction.
+If the signal is sparse on a certain new basis, as shown in the right, then for a good approximation, we may take only the largest components for reconstruction.
 
-Generally speaking, compressive sensing aims to reconstruct a underdetermined linear system, when the sparsity of solution guarantees successful recovery for most cases.
+Generally speaking, compressive sensing aims to reconstruct an underdetermined linear system, when the sparsity of solution guarantees successful recovery for most cases.
 More measurements are required to recover the signal in the nonsparse basis, while fewer suffice in the sparse basis.
 But, even if we are sure that the sparse basis exists, its construction is another undertaking.
+In our settings for hybrid beamforming structure, a way of generating the sensing matrix and pilot vectors in the estimation stage has to be devised and justified.
+
+Compressive sensing approaches can be divided into two categories, the convex programming approach and the greedy approach \cite {RDD18}.
+We will discuss one from each in more detail: Dantzig Selector and Orthogonal Matching Pursuit.
 
@@
 
-As an application, it often occurs that a camera takes a high definition photo, and compresses the image later.
-But it may be desirable that a camera equipped with fewer sensors shall take a lower resolution photo to save storage, and shall recover the image later.
-Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, while the accuracy is critical to the diagnosis too \cite {CaT07}.
+As an application, it often occurs that a camera takes a high definition photo and compresses the image later.
+But it may be desirable that a camera equipped with fewer sensors shall take a lower resolution photo to save storage, and recover the image later.
+Such advantage can be useful in medical imaging, since it is not only expensive, but also harmful, to take too many images, and the accuracy is critical to the diagnosis too \cite {CaT07}.
 
@@
 
-Due to the constraint of hybrid structure, the designs which use a fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
-Indeed, if DS is shown to be optimal \cite {CaT07}, then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary in less ideal situations.
+Due to the constraint of hybrid structure, the designs which use fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
+Indeed, if DS is shown to be optimal \cite {CaT07}, then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary for less ideal situations.
 
-In this treatise, we consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
+In this treatise, we consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
 In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
@@
 But in chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
-and we give a quantitative bound (which holds for high probability) on expected error norm.
+and we give a quantitative bound (which holds for high probability) on the expected error norm.
 In chapter 4, numerical results show that DS is superior to other methods for our problem.
 Since DS is more accurate, it can be used when the sample is less sufficient and the noise level is higher, where it might be the case that only DS can recover successfully.
-Considering its higher complexity, we remark that it can be cast as a linear program, and basis pursuit denoising form may be used.
+Considering its higher complexity, we remark that it can be cast as a linear program, and the basis pursuit denoising form may be used.
 
-It appears that, for given number of sampling, DS recovers more successfully than OMP.
-Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} with only analog combiner,
+It appears that, for a given number of sampling, DS recovers more successfully than OMP.
+Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} with only an analog combiner,
 and our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite {LGL16},
-and we do not rely on additional assumption on sparsity as in Gao, Dai, and Wang \cite {GDW15}.
+and we do not rely on additional assumptions on sparsity as in Gao, Dai, and Wang \cite {GDW15}.
 
 Our work is also an improvement to Bajwa et.\ al.\ \cite {BHS10}.
-First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
-Second, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
+First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
+Second, with the further constraint of hybrid beamforming, it is unclear whether their guarantee theorem for recovery is still valid.
 Third, generating random sequences can lead to high complexity \cite {LGL16}.
@@
 In addition, it seems that with the same threshold, DS is better than Lasso.
-Again, our proposed method is more general than Lian, Liu and Lau \cite {LLL17} with only analog combiner,
+Again, our proposed method is more general than Lian, Liu and Lau \cite {LLL17} with only an analog combiner,
 and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite {DJN15},
-and we do not require special device as in Vlachos, Alexandropoulos, and Thompson \cite {VAT19}.
+and we do not require special devices as in Vlachos, Alexandropoulos, and Thompson \cite {VAT19}.

### 2021-03-14 treatise-pdflatex/5_conclusion.tex
Slightly correct grammar

@@
 We corroborate the prediction that DS is nearly optimal, and it may extract more information than other methods do when the sampling rate is low.
-Since DS is more accurate while having higher complexity, when the sample is less sufficient and the noise level is higher, sometimes only DS can recover successfully.
-Therefore, DS may be used in the scenario that precision is crucial, as well as that the number of RF chain is more limited or fewer stages of estimation is possible.
+When the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
+Therefore, one may use DS in the scenario that precision is crucial, as well as that the number of RF chains is more limited or fewer stages of estimation is possible.

### 2021-03-14 treatise-pdflatex/abstract.tex
Slightly correct grammar

@@
 
-Multiple-input multiple-output communication system in millimeter wave band is gradually being adopted.
-However, channel estimation becomes considerably difficult, due to the larger antennae array, and greedy algorithms such as Orthogonal Matching Pursuit are sometimes used reduce the complexity.
-Meanwhile, hybrid beamforming is often used to reduce the number of RF chains, and with such constraint, fully digital designs cannot be directly applied, and fully analog designs might not be optimal.
+Multiple-input multiple-output communication systems in the millimeter-wave band are gradually being adopted.
+A larger antennae array makes channel estimation more difficult.
+Meanwhile, hybrid beamforming, which utilizes fewer RF chains, is applied too, so that new estimation methods have to be designed.
+This can be seen as a compressive sensing problem, for which Orthogonal Matching Pursuit is usually used.
 
-We consider a hybrid structure with uniform linear array with both precoders and combiners on each side.
-We generate random beamforming matrices, and use Dantzig Selector to estimate the channel in the space frequency domain, and we give a quantitative bound (which holds for high probability) on expected error norm.
-
-To reduce the complexity, we cast it as a linear program, and also suggest the basis pursuit denoising form.
+We consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
+We generate random beamforming matrices and use Dantzig Selector to estimate the channel in the space frequency domain.
+Then, we give a quantitative bound (which holds for high probability) on the expected error norm.
+To reduce the complexity, we cast it as a linear program, and suggest the basis pursuit denoising form.
 Numerical results show that DS is superior, especially when the sample is less sufficient and the noise level is higher.
-We therefore propose that DS may be used as the number of RF chains is more limited, or when fewer stages of estimation is possible.
+We therefore propose that DS may be used, when the number of RF chains is more limited or when fewer stages of estimation are possible.

### 2021-03-15 treatise-context/2_problem_setting.tex
Chap 4: double check grammar

@@
 
-We consider the hybrid beamforming at both transmitter and receiver ends, as shown in Figure 2.
+We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
 Each end consists of both digital and analog precoders and combiners.
-In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \MB {C} ^{N_{B,t} \D N_{B,t}}} and analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_{B,t}}}.
-Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \MB {C} ^{N_{B,r} \D N_H}} and analog combiner \m {\M {W} _B \in \MB {C} ^{N_{B,r} \D  N_{B,r}}}.
+In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \MB {C} ^{N_{B,t} \D N_{B,t}}} and the analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_{B,t}}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \MB {C} ^{N_{B,r} \D  N_{B,r}}} and the analog combiner \m {\M {W} _R \in \MB {C} ^{N_{B,r} \D N_H}}.
 
@@
 \DispNum {N:H:NY:NY} {
-\NC N_H \gg \NC N_{B,t}, N_{R,t} \NR
+\NC N_H \gg \NC N_{B,t}, N_{B,r} \NR
 }

### 2021-03-15 treatise-context/3_2_generating_beamforming_matrices.tex
Chap 4: double check grammar

@@
 
-In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17], Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
+In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17], Theorem \m {4.5} states a big O bound for the failure probability of a DFT submatrix with \m {\d_s} RIP.
 We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
-Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP .
+Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
 In conclusion, (respectively for \m {N_{B,r}})

### 2021-03-15 treatise-context/4_simulation.tex
Slightly correct grammar
Chap 4: double check grammar

@@
 
-Let us represent complex vector and matrices by real vector and matrices.
+Let us represent complex vectors and matrices by real vectors and matrices.
 For \m {\V {x} \in \MB {C} ^{M}}, define the real representation \m {\MS {R} \SB {\V {x}}} of \m {\V {x}} to be
@@
 
-If more than one stage of estimation is possible, that is, there are more than one data sets, the second stage may be run on the second dataset, and so on.
+If more than one stage of estimation is possible, that is, there are more than one dataset, the second stage may be run on the second dataset, and so on.
 It is possible in theory to run it for three or more times.
@@
 
-However, there is not simple way to determine the value of \m {\l} in advance.
+However, there is no simple way to determine the value of \m {\l} in advance.
 We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.
@@
 For OMP, we consult Cai and Wang \cite [CaW11] for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
-We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3} \SB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
-Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\Rm {DS}}} and \m {\h_{\Rm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
+We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3} \RB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
 The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.
@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,t}}.
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,r}}.
 %
@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,t}}.
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,r}}.
 %
@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,t}}.
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,r}}.
 %
@@
 For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
-Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
+Thus, for sake of comparison, we set the same threshold for Lasso and DS.
 Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
@@
 
-Suppose a linear program has \m {N} dimension variable and \m {M} inequality constraints, then the complexity is \m {\MS {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite [BoV04], p.6).
+Suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\MS {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite [BoV04], p.6).
 For our case, that would be \m {\MS {O} \SB {4 N_H ^4 \D 8 N_H^2} = \MS {O} \SB {N_H^6}}.
@@
 
-Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite [FrS07] on the high complexity of DS.
-It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
-The matrix inversion is probably the bottleneck of complexity.
-However, as we noted above, that different tolerance level of and maximal iteration number may result in vastly different computation time.
+Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with \m {N_H}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
+This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
+By the way, different tolerance levels and maximal iteration numbers may result in vastly different computation time.
 

### 2021-03-15 treatise-context/5_conclusion.tex
Chap 4: double check grammar

@@
 
-The treatise aims to answer the problem of effective estimating a MIMO millimeter-wave channel by exploiting its sparsity.
-To do so, we try the Dantzig Selector (DS) for channel estimation.
-We exploited the sparsity in the spatial frequency domain, and justified the RIP of effective beamforming matrix for the hybrid structure.
-We then proved quantitatively that the expected error norm is bounded for overwhelming probability.
-We also suggested several ways to reduce the complexity without losing much performance, as justified by simulation.
-Simulation is done, and we see that DS indeed outperforms other methods.
+The treatise aims to answer the problem of effective estimating a MIMO mm-wave channel by exploiting its sparsity.
+To do so, we apply the Dantzig Selector (DS), by exploiting the sparsity in the spatial frequency domain, and justified the restricted isometry of the effective beamforming matrix.
+We then prove quantitatively that the expected error norm is bounded for overwhelming probability.
+We also suggest several ways of reducing the complexity without losing much performance.
+Simulation is done, and we see that DS indeed outperforms other methods in most datasets.
 
@@
 When the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
-Therefore, one may use DS in the scenario that precision is crucial, as well as that the number of RF chains is more limited or fewer stages of estimation is possible.
+Therefore, one may use DS in the scenario that precision is crucial, as well as the case that the number of RF chains is more limited or fewer stages of estimation are possible.
 

### 2021-03-15 treatise-pdflatex/2_problem_setting.tex
Chap 4: double check grammar

@@
 
-We consider the hybrid beamforming at both transmitter and receiver ends, as shown in Figure 2.
+We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
 Each end consists of both digital and analog precoders and combiners.
-In the transmitter end, there are (seeing towards the receiver end), digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_{B,t} \D N_{B,t}}} and analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D N_{B,t}}}.
-Similarly, in the receiver end, there are (seeing towards the transmitter end) digital combiner \m {\M {W} _R \in \mathbb {C} ^{N_{B,r} \D N_H}} and analog combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}}.
+In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_{B,t} \D N_{B,t}}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D N_{B,t}}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_{B,r} \D N_H}}.
 

### 2021-03-15 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
Chap 4: double check grammar

@@
 
-In Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' \cite {KlM17}, Theorem \m {4.5} states a DFT submatrix has \m {\d_s} RIP with failure probability lower than a certain Big-O bound.
+In Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' \cite {KlM17}, Theorem \m {4.5} states a big O bound for the failure probability of a DFT submatrix with \m {\d_s} RIP.
 We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
 Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
+In conclusion, (respectively for \m {N_{B,r}})
 %

### 2021-03-15 treatise-pdflatex/4_simulation.tex
Slightly correct grammar
Chap 4: double check grammar

@@
 
-Let us represent complex vector and matrices by real vector and matrices.
+Let us represent complex vectors and matrices by real vectors and matrices.
 For \m {\V {x} \in \mathbb {C} ^{M}}, define the real representation \m {\mathcal {R} \SB {\V {x}}} of \m {\V {x}} to be
@@
 
-However, there is not simple way to determine the value of \m {\l} in advance.
+However, there is no simple way to determine the value of \m {\l} in advance.
 We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\mathrm {DS}}} in the simulation.
@@
 For OMP, we consult Cai and Wang \cite {CaW11} for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
-We take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3} \SB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
-Particularly, in the plots of DS only or OMP only, we vary the values of \m {\g_{\mathrm {DS}}} and \m {\h_{\mathrm {OMP}}} by powers of \m {2}, to observe the effects of thresholds.
+We take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3} \RB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
 The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.
@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,t}}.
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,r}}.
 
@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,t}}.
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,r}}.
 
@@
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,t}}.
+In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,r}}.
 
@@
 
-Suppose a linear program has \m {N} dimension variable and \m {M} inequality constraints, then the complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite {BoV04}, p.6).
+Suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite {BoV04}, p.6).
 For our case, that would be \m {\mathcal {O} \SB {4 N_H ^4 \D 8 N_H^2} = \mathcal {O} \SB {N_H^6}}.
@@
 
-Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_H}, agreeing the criticism by Friedlander and Saunders \cite {FrS07} on the high complexity of DS.
-It is not surprising, regarding the fact that the convex program has to find the Newton step by calculating \m {\M {P}}, a matrix of dimension \m {\M {N}_H^2}.
-The matrix inversion is probably the bottleneck of complexity.
-However, as we noted above, that different tolerance level of and maximal iteration number may result in vastly different computation time.
+Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_H}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
+This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
+By the way, different tolerance levels and maximal iteration numbers may result in vastly different computation time.
 

### 2021-03-15 treatise-pdflatex/5_conclusion.tex
Chap 4: double check grammar

@@
 When the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
-Therefore, one may use DS in the scenario that precision is crucial, as well as that the number of RF chains is more limited or fewer stages of estimation is possible.
+Therefore, one may use DS in the scenario that precision is crucial, as well as the case that the number of RF chains is more limited or fewer stages of estimation are possible.

### 2021-03-20 presentation/1_setting.tex
copy corrected system diagram
Fix presentation typos

@@
 
-\I Estimation of Multiple-input multiple-output (MIMO) systems results in high complexity, due to a large number of antennae.
+\I Consider a multiple-input multiple-output (MIMO) system with hybrid structure, so we have fewer RF chains than the antennas
 
-\I Problem (a): How to reconstruct the channel with fewer measurements?
+\I Problem (a): Can we estimate the channel with fewer measurements?
 
-\I Problem (b): How to generate precoders and combiners?
+\I Problem (b): What precoders and combiners help the estimation?
 }
@@
 
-\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_{B,t}}}
-\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}
+\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_{B,t} \D N_{B,t}}}
+\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_{B,t}}}
 
-\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}
-\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_{B,r} \D N_R}}
+\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_{B,r} \D N_H}}
+\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_{B,r} \D N_{B,r}}}
 
-\I Magnitude constraint \m {\Nm {\M {F}_{R,\SB {n_H, n_R}}} = 1}, \m {\Nm {\M {W}_{R,\SB {n_H, n_R}}} = 1}
+\I Magnitude constraint \m {\Nm {\M {F}_{R,\SB {n_H, n_{R,t}}}} = 1}, \m {\Nm {\M {W}_{R,\SB {n_H, n_{R,r}}}} = 1}
 }
@@
 {
-\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)
+\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, no beamforming, linear invariant system, using Dantzig Selector (DS)
 
@@
 
-\I Alkhateeb, Leus, and Heath (2015): single path mm wave, all phase shifter beamforming, using Orthogonal Matching Pursuit (OMP)
+\I Alkhateeb, Leus, and Heath (2015): single path mm wave, analog beamforming, using Orthogonal Matching Pursuit (OMP)
 
@@
 {
-\I Due to the constraint of hybrid beamforming, designs for fully digital beamforming on sensing matrix might not directly work.
+\I Due to the constraint of hybrid beamforming, sensing matrix designs for fully digital beamforming does not directly work.
 
-\I We propose a low complexity random generation of beamforming matrices, and justify that it may serve as the sensing matrix for DS.
+\I We propose a low complexity, i.i.d.\ random beamforming matrices, and justify that it may serve as the sensing matrix for DS.
 

### 2021-03-20 presentation/4_conclusion.tex
Fix presentation typos

@@
 {
-\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.
+\I We estimate MIMO mm wave channel \m {\M {H}} by using a modified DS.
 
@@
 
-\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_B}, and \m{L}, and approximate the asymptotic failure probability.
+\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_{B,t}}, \m {N_{B,r}}, and \m{L}, and approximate the asymptotic failure probability.
 

### 2021-03-20 treatise-context/1_introduction.tex
Fix presentation typos

@@
 Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite [LLL17].
-Destino, Juntti, and Nagaraj used an adaptive Lasso \cite [DJN15], in which they jointly optimize the sensing matrix and pilot vectors.
-Vlachos, Alexandropoulos, and Thompson \cite [VAT19] used Lasso on hybrid beamforming with an additional random spatial sampling device.
+Destino, Juntti, and Nagaraj used an adaptive Lasso \cite [DJN15], and Vlachos, Alexandropoulos, and Thompson \cite [VAT19] used Lasso on hybrid beamforming with an additional random spatial sampling device.
+Both Destino et al and Vlachos et al optimize formulate an algorithm to jointly find the channel and the sensing matrix, which can result in high complexity.
 
@@
 Hu, Wang, and He \cite [HWH13] applied OMP to estimate path delay of OFDM subcarriers.
-Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix.
+Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix;
+the analog stage is a Fourier matrix, and the digital stage consists of a collection of columns vectors of a unitary matrix.
 Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite [GDW15].
@@
 In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
-Because of the hybrid structure, here it is not possible to generate the sensing matrix by i.i.d.\ entries, which requires a fully digital structure.
-But in chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
+To the best of our knowledge, the sensing matrix with i.i.d.\ entries in both analog and digital stages has not been discussed on the literature.
+In chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
 and we give a quantitative bound (which holds for high probability) on the expected error norm.
@@
 First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
-Second, with the further constraint of hybrid beamforming, it is unclear whether their guarantee theorem for recovery is still valid.
-Third, generating random sequences can lead to high complexity \cite [LGL16].
+Second, with the further constraint of hybrid beamforming, the channel matrix is downsampled, it is unclear whether their guarantee for successful signal recovery is still valid.
+Third, generating random sequences can lead to high complexity \cite [LGL16], and we instead use random beamforming matrices.
 

### 2021-03-20 treatise-pdflatex/1_introduction.tex
Fix presentation typos

@@
 Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite {LLL17}.
-Destino, Juntti, and Nagaraj used an adaptive Lasso \cite {DJN15}, in which they jointly optimize the sensing matrix and pilot vectors.
-Vlachos, Alexandropoulos, and Thompson \cite {VAT19} used Lasso on hybrid beamforming with an additional random spatial sampling device.
+Destino, Juntti, and Nagaraj used an adaptive Lasso \cite {DJN15}, and Vlachos, Alexandropoulos, and Thompson \cite {VAT19} used Lasso on hybrid beamforming with an additional random spatial sampling device.
+Both Destino et al and Vlachos et al optimize formulate an algorithm to jointly find the channel and the sensing matrix, which can result in high complexity.
 
@@
 Hu, Wang, and He \cite {HWH13} applied OMP to estimate path delay of OFDM subcarriers.
-Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix.
+Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix;
+the analog stage is a Fourier matrix, and the digital stage consists of a collection of columns vectors of a unitary matrix.
 Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite {GDW15}.
@@
 First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
-Second, with the further constraint of hybrid beamforming, it is unclear whether their guarantee theorem for recovery is still valid.
-Third, generating random sequences can lead to high complexity \cite {LGL16}.
+Second, with the further constraint of hybrid beamforming, the channel matrix is downsampled, it is unclear whether their guarantee for successful signal recovery is still valid.
+Third, generating random sequences can lead to high complexity \cite {LGL16}, and we instead use random beamforming matrices.
 

### 2021-03-21 presentation/3_simulation.tex
Fix presentation typos
Revise presentation

@@
 {
-\I Casting to a linear program
+\I Casting to a linear program (not used now)
 
-\I A successive estimation of the nonzero components (not used in the final set of figures)
+\I Successively estimate the nonzero components (not used now)
 
 \I Use the basis pursuit denoising form
-}
-% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Performance Metric}
-{
-\I Let the \m {\T {\chi}}, the relative 2-norm error, be the performance metric.
 
 \Disp {
-\NC \T {\chi}
-=\NC \RB {
-   \F {\VNm {\V {h} -\Hat {\V {h}}} _2}
-   {\VNm {\V {h}}_2}
-} _{\Ss {avg}}, \NR
+\NC \Hat {\V {g}}
+\LA \NC \Min {\V {g}'} 
+\CB {
+\VNm {\V {g}'} _1 
++ \l_{\Ss {DS}} \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty
+} \NR
 }
-
-\I Also define \m {\chi} by plugging in \m {\V {d}} into \m {\T {\chi}}.
 }
@@
 {
-\I DS outperforms other methods in the high noise case
+\I DS outperforms other methods in the high noise case and less measurement
 
-\I DS requires less sampling to recover for given channel instance.
-
-\I The relaxed sparsity may have compromised effectiveness of DS.
+\I The relaxed sparsity may have compromised its effectiveness.
 
@@
 
-\I \m {\T {\chi}} and \m {\chi} differ by some orders of magnitude.
+\I Unfortunately, the values are too small to verify the asymptotic bound.
 }
@@
 \Disp {
-\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log \R {N_{B,t} N_{B,r}}} \NR
+\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_{B,t} N_{B,r}} \NR
 \NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR

### 2021-03-27 treatise-pdflatex/2_problem_setting.tex
Section 3.2: change dimension

@@
 \DispNum {a:y':CN:NH} {
-\V {a} \SB {\psi'}
-= \frac {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
-\in \mathbb {C} ^ {N_H} 
+\V {a} \SB {\psi', N}
+= \frac {1} {\R {N}} \sum_{n_h=0}^{N-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
+\in \mathbb {C} ^ {N} 
 }
@@
 \a_l
-\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l'}
-\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l'}^\dagger 
+\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l', N_{H,r}}
+\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l', N_{H,r}}^\dagger 
 }
@@
 =\sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
-\in \mathbb {C} ^{N_H \D N_H} 
+\in \mathbb {C} ^{N_{H,r} \D N_{H,t}} 
 }
@@
 Each end consists of both digital and analog precoders and combiners.
-In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_{B,t} \D N_{B,t}}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_H \D N_{B,t}}}.
-Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_{B,r}}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_{B,r} \D N_H}}.
+In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_B}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_B \D N_{H,r}}}.
 
@@
 %
-n_H
-= &0, \dots N_H-1, \\
+n_{H,t}
+= &0, \dots N_{H,t}-1, \\
+%
+n_{H,r}
+= &0, \dots N_{H,r}-1, \\
 %
 n_{R,t}
-= &0, \dots N_{B,t}-1  \\
+= &0, \dots N_B-1  \\
 %
 n_{R,r}
-= &0, \dots N_{B,r}-1 
+= &0, \dots N_B-1 
 }
@@
 \DispNum {N:H:NY:NY} {
-N_H \gg N_{B,t}, N_{B,r}
+N_{H,t}, N_{H,t} \gg N_B, N_B
 }
 
-Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_H \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
 Let us introduce the effective channel
@@
 := &\mathrm {vec} \SB {\M {H}}
-\in \mathbb {C} ^{N_H^2} \\
+\in \mathbb {C} ^{N_{H,t} N_{H,r}} \\
 %
@@
 := &\mathrm {vec} \SB {\M {Y}}
-\in \mathbb {C} ^{N_{B,t} N_{B,r}} \\
+\in \mathbb {C} ^{N_B N_B} \\
 %
@@
 := &\mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
-\in \mathbb {C} ^{N_{B,t} N_{B,r}} \\
+\in \mathbb {C} ^{N_B N_B} \\
 %
@@
 := &\RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
-\in \mathbb {C} ^{N_{B,t} N_{B,r} \D N_H^2} 
+\in \mathbb {C} ^{N_B N_B \D N_{H,t} N_{H,r}} 
 }
@@
 \DispNum {K:K:CN:H1} {
-\M {K} \in &\mathbb {C} ^{N_H \D N_H} \notag \\
+\M {K} \in &\mathbb {C} ^{N_{H,t} \D N_{H,r}} \notag \\
 %
-\M {K} _{\SB {n_1, n_2}}
-= &\frac {1} {\R {N_H}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N_H}, \notag \\
+\M {K} _{\SB {n_1, n_2}} \SB {N}
+= &\frac {1} {\R {N}} \mathsf {e}^{2\pi \mathsf {i} n_1 n_2 /N}, \notag \\
 %
 \quad n_1, n_2
-= &0, 1, \dots, N_H-1 
+= &0, 1, \dots, N-1 
 }
@@
 +\M {W} _B \M {W} _R \M {Z}
-\in \mathbb {C} ^{N_{B,r} \D N_{B,t}} 
+\in \mathbb {C} ^{N_B \D N_B} 
 }
@@
 :=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
-\in \mathbb {C} ^{N_{B,t} N_{B,r} \D N_H^2} 
+\in \mathbb {C} ^{N_B N_B \D N_{H,t} N_{H,r}} 
 }
@@
 := \mathrm {vec} \SB {\M {G}}
-\in \mathbb {C} ^ {N_H \D N_H} 
+\in \mathbb {C} ^ {N_{H,t} \D N_{H,r}} 
 }
@@
 %
-\item Input \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_{B,t}}},
-\m {\M {F} _R \in \mathbb {C} ^{N_H \D N_R}},
-\m {\M {W} _R \in \mathbb {C} ^{N_R \D N_H}},
-\m {\M {W} _B \in \mathbb {C} ^{N_{B,r} \D N_R}},
-and \m {\M {Y} \in \mathbb {C} ^{N_{B,r} \D N_{B,t}}}.
+\item Input \m {\M {F} _B \in \mathbb {C} ^{N_{R,t} \D N_B}},
+\m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_R}},
+\m {\M {W} _R \in \mathbb {C} ^{N_{R,r} \D N_{H,r}}},
+\m {\M {W} _B \in \mathbb {C} ^{N_B \D N_{R,r}}},
+and \m {\M {Y} \in \mathbb {C} ^{N_B \D N_B}}.
 %
-\item Find \m {\M {P} \in \mathbb {C} ^{N_{B,r} N_{B,t} \D N_H^2}}, \m {\V {y} \in \mathbb {C} ^{N_H^2}} as in above.
+\item Find \m {\M {P} \in \mathbb {C} ^{N_B N_B \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \mathbb {C} ^{N_{H,t} N_{H,r}}} as in above.
 %
@@
 \leftarrow \begin {cases}
-\Min {\V {g}' \in \mathbb {C} ^{N_H^2}} & \VNm {\V {g}'} _1 \\
+\Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}} & \VNm {\V {g}'} _1 \\
 %

### 2021-03-27 treatise-pdflatex/3_1_sparsity_of_channel.tex
LaTeX: align equations
minor typos
Section 3.2: change dimension

@@
 We define, similarly, \m {\V {a} _{\SB{\mathcal {A}}}} and \m {\V {a} _{\SB{\mathcal {C}}}}, with sparsity level \m {s} different from \m {S}.
-If \m {N_H} is large, we may forget for a moment that \m {s} is an integer.
+If \m {N} is large, we may forget for a moment that \m {s} is an integer.
 
@@
 :=\RB {
-   \f \; \mathrm {Mod}\; \frac {2\pi} {N_H}
-   + \RB {\frac {2 n_H} {N_H} + 1} \pi
+   \f \; \mathrm {Mod}\; \frac {2\pi} {N}
+   + \RB {\frac {2 n_H} {N} + 1} \pi
 } \;
@@
 D \SB {\psi'}
-:= \sum_{n_H=0}^{N_H-1} \mathsf {e}^{i n_H \psi'} 
+:= \sum_{n_H=0}^{N-1} \mathsf {e}^{i n_H \psi'} 
 }
@@
 \V {b} \SB {\f} _{\SB {n_H}}
-=\frac {1} {N_H} D \SB {\psi \SB {\f, n_H}} 
+=\frac {1} {N} D \SB {\psi \SB {\f, n_H}} 
 }
@@
 \Nm {D \SB {\psi'}}
-= \frac {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \\
+= &\frac {\Nm {\sin \SB {N \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \notag \\
 %
-\leq B \SB {\psi'} \\
+\leq &B \SB {\psi'} \notag \\
 %
-:= \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \\
+:= &\frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \notag \\
 %
-- \pi \leq \psi' < \pi. 
+- \pi \leq &\psi' < \pi. 
 }
@@
 \VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
-\leq \frac {1} {N_H}
+\leq \frac {1} {N}
 \VNm {
 \RB {
-   \sum_{n_H' =0}^{N_H -1}
+   \sum_{n_H' =0}^{N -1}
       B \SB {\psi \SB {\f, n_H'}}
@@
 Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
-We are going to bound the rectangles by an integral, where we have to split the cases that \m {N_H} is odd and even.
+We are going to bound the rectangles by an integral, where we have to split the cases that \m {N} is odd and even.
 %
@@
 \VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
-\leq \frac {1} {N_H} \D \frac {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \\
+\leq &\frac {1} {N} \D \frac {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \SB {\psi'} ^2 d \psi' \notag \\
 %
-= \frac {48} {N_H \pi^3}
-\int _{s /N_H} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \\
+= &\frac {48} {N \pi^3}
+\int _{s /N} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \notag \\
 %
-=\frac {1} {\pi} \log \frac {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \\
+= &\frac {1} {\pi} \log \frac {N^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \notag \\
 %
-\eqsim \frac {2} {\pi} \RB {\log N_H - \log s} \\
+\eqsim &\frac {2} {\pi} \RB {\log N - \log s} \notag \\
 %
-\leq \frac {2} {\pi} \log N_H 
+\leq &\frac {2} {\pi} \log N 
 }
@@
 s
-=\R {\log N_H} 
+=\R {\log N} 
 }
@@
 \VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
-\leq \frac {2} {\pi} \log N_H 
+\leq \frac {2} {\pi} \log N 
 }
@@
 \leq 
-\sum _{l=0} ^{L-1} \Nm {\a_l}
+&\sum _{l=0} ^{L-1} \Nm {\a_l}
 \VNm {\V {b} \SB {\f_l} _{\SB{\mathcal {C}}}} _1
-\VNm {\V {b} \SB {\th_l} _{\SB{\mathcal {C}}}} _1 \\
+\VNm {\V {b} \SB {\th_l} _{\SB{\mathcal {C}}}} _1 \notag \\
 %
 \leq 
-\VNm {\V {b} \SB {\f_l} _{\SB{\mathcal {C}}}} _1
-\VNm {\V {b} \SB {\th_l} _{\SB{\mathcal {C}}}} _1
-\sum _{l=0} ^{L-1} \Nm {\a_l} \\
-%
-\leq 
-\frac {4} {\pi^2} L \RB {\log N_H}^2 \D
+&\frac {4} {\pi^2} L \RB {\log N_{H,t}} \RB {\log N_{H,r}} \D
 \frac {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} 
@@
 \DispNum {g:2:12:43} {
-\frac {\VNm {\M {g} _{\SB{\mathcal {C}}}} _1} {\RB {\log N_H}^2}
+\frac {\VNm {\M {g} _{\SB{\mathcal {C}}}} _1} {\RB {\log N_{H,t}} \RB {\log N_{H,r}}}
 \leq \frac {12 \R{2}} {\pi ^{5/2}}
@@
 {
-Let \m {\V {g} \in \mathbb {C} ^{N_H^2}} be defined as in \eqref {g:g:ve:Nh}.
+Let \m {\V {g} \in \mathbb {C} ^{N_{H,t} \D N_{H,r}}} be defined as in \eqref {g:g:ve:Nh}.
 Then the bound
@@
 \VNm {\M {g} _{\SB{\mathcal {C}}}} _1
-\leq \frac {4} {3} \RB {\log N_H}^2 
+\leq \frac {4} {3} \RB {\log N_{H,t}} \RB {\log N_{H,r}} 
 }

### 2021-03-27 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
Section 3.2: change dimension

@@
 \DispNum {C':C':WB:j2} {
-\VNm {\M {W} _B \V {u}} _2
+\VNm {\M {F} _B \V {u}} _2
 =\R {
-   \sum _{i=0} ^{N_{B,t}-1} \VNm {\sum _{j=0} ^{N_R-1} \frac {1} {\R{N_{B,t}}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
+   \sum _{i=0} ^{N_{R,t}-1} \VNm {\sum _{j=0} ^{N_B-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
 }
@@
 To do so, we apply Lemma \m {1} in Laurent and Massart \cite {LaM00} for equal weights, with \m {x > 0} below.
-By some calculation, we have the upper tail inequality
+By some calculation, we have the upper tail inequality (respectively for \m {N_{R,r}})
 %
 \DispNum {P:x:ex:ex} {
-\mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_{B,t}}} + \frac {2x} {N_{B,t}}}
+\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_{R,t}}} + \frac {2x} {N_{R,t}}}
 \leq \mathsf {e} ^{-x} 
@@
 \DispNum {P:x:ex:ex!} {
-\mathbb {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_{B,t}}}}
+\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_{R,t}}}}
 \leq \mathsf {e} ^{-x} 
@@
 %
-With substitution \m {\d_s =16x^2 /N_{B,t}^2}, the upper tail can be simplified with \m {x <N_{B,t}}, and we get the following bound for overall failure probability.
+With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for overall failure probability.
 
@@
 \DispNum {W:1:ds:ds} {
-\Nm {\VNm {\M {W} _B \V {u}} _2 ^2 - 1}
+\Nm {\VNm {\M {F} _B \V {u}} _2 ^2 - 1}
 \geq \d_s 
@@
 1 -p
-\leq 2 \mathsf {e} ^{-N_{B,t} \R {\d_s} /4} 
+\leq 2 \mathsf {e} ^{-N_{R,t} \R {\d_s} /4} 
 }
@@
 \DispNum {N:R:sd':NH} {
-N_R
+N_{R,t}
 \geq \frac {s} {\d_s^2} \RB {\log \frac{1}{\d_s}}^2 \RB {\log \frac{s}{\d_s}}^2 \log N_H 
@@
 \DispNum {N:R:sd'NH} {
-N_R
+N_{R,t}
 \geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H 

### 2021-03-29 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
Sec 3.3: Rev proof

@@
 Use \m {\chi _{i,j}} to denote independent complex standard normal random variables.
-It follows that (respectively for \m {N_{B,r}})
+It follows that (respectively for \m {\M {W} _B})
 %
@@
 =\R {
-   \sum _{i=0} ^{N_{R,t}-1} \VNm {\sum _{j=0} ^{N_B-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
+   \sum _{i=0} ^{N_R-1} \VNm {\sum _{j=0} ^{N_B-1} \frac {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} 
 }
@@
 To do so, we apply Lemma \m {1} in Laurent and Massart \cite {LaM00} for equal weights, with \m {x > 0} below.
-By some calculation, we have the upper tail inequality (respectively for \m {N_{R,r}})
+By some calculation, we have the upper tail inequality (respectively for \m {\M {W} _B})
 %
 \DispNum {P:x:ex:ex} {
-\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_{R,t}}} + \frac {2x} {N_{R,t}}}
+\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\frac {x} {N_R}} + \frac {2x} {N_R}}
 \leq \mathsf {e} ^{-x} 
@@
 \DispNum {P:x:ex:ex!} {
-\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_{R,t}}}}
+\mathbb {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\frac {x} {N_R}}}
 \leq \mathsf {e} ^{-x} 
@@
 1 -p
-\leq 2 \mathsf {e} ^{-N_{R,t} \R {\d_s} /4} 
+\leq 2 \mathsf {e} ^{-N_R \R {\d_s} /4} 
 }
@@
 We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
-Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
-In conclusion, (respectively for \m {N_{B,r}})
+Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_{H,t} s} RIP.
+In conclusion, (respectively for \m {\M {W} _R})
 %
 \DispNum {N:R:sd':NH} {
-N_{R,t}
-\geq \frac {s} {\d_s^2} \RB {\log \frac{1}{\d_s}}^2 \RB {\log \frac{s}{\d_s}}^2 \log N_H 
+N_R
+\geq \frac {s} {\d_s^2} \RB {\log \frac{1}{\d_s}}^2 \RB {\log \frac{s}{\d_s}}^2 \log N_{H,t}
 }
@@
 \DispNum {N:R:sd'NH} {
-N_{R,t}
+N_R
 \geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H 

### 2021-03-29 treatise-pdflatex/3_3_bound_for_error_norm.tex
Rev contribution
Transfer chap 1, 4 to LaTeX
LaTeX: align equations
copy corrected system diagram
minor typos
Section 3.2: change dimension
Sec 3.3: Rev proof

@@
 %
+And for convenience, let
+\Disp {
+N_h
+= N_{H,t} N_{H,r}
+}
+
+%
 To bound \m {\VNm {\V {d}} _2}, we illustrate that \m {\V {g}} can be seen as sparse, and for that purpose we generously bound \m {\d_{S}} by \m {1}.
@@
 \g
-= 2 \R {\log N_H} 
+= \R {2 \log N_h} 
 }
@@
 - \VNm {\V {g} _{\SB{\mathcal {C}}}} _1
-\leq \VNm {\V {g} + \V {d}} _1 \\
+\leq \VNm {\V {g} + \V {d}} _1
 %
@@
 \VNm {\M {P}^\dagger \M {P} \V {d}} _\infty
-\leq  4 \R {2 \log N_H} 
+\leq  2 \R {2 \log N_h} 
 }
@@
 1 -p
-\leq N_H^{-2}. 
+\leq N_h.
 }
@@
 \IP {\V {z} - \RB {\V {y} - \M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_h}}}
-= \IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \\
+= &\IP {\M {P} \hat {\V {g}} - \M {P} \V {g}, \M {P} _{\SB {:,n_h}}} \notag \\
 %
-= \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} 
+= &\IP {\M {P} \V {d}, \M {P} _{\SB {:,n_h}}} 
 }
@@
 %
-Particularly, fix threshold \m {x' =2 \R {\log N_H}}, yielding
+Particularly, fix threshold \m {x' =\R {2 \log N_h}}, yielding
 %
 \DispNum {Q:h:1N:Nh} {
-Q\SB {2 \R {\log N_H}}
-=\frac {1} {2 N_H^2}. 
+Q\SB {\R {2 \log N_h}}
+=\frac {1} {2 N_h}. 
 }
@@
 \VNm {\M {P} _{\SB {:,n_h}}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty
-\leq \VNm {\M {P}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \\
+\leq &\VNm {\M {P}^\dagger \RB {\V {y} - \M {P} \hat {\V {g}}}} _\infty \notag \\
 %
-\leq 2\R {2 \log N_H} 
+\leq &2\R {\log N_h} 
 }
@@
 \VNm {\M {P} _{\SB {:,n_h}}^\dagger \M {P} \V {d}} _\infty
-\leq \Nm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}}
-+ \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_h}}} \\
+\leq &\Nm {\IP {\V {z}, \M {P} _{\SB {:,n_h}}}}
++ \IP {\V {y} - \M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_h}}} \notag \\
 %
-\simeq 2 \R {2 \log N_H} +2 \R {2 \log N_H} 
+\simeq &\R {2 \log N_h} + \R {2 \log N_h} 
 }
@@
 \d_{S}
-\leq \R {L} \RB {\log N_H} ^{1/4} \d_{s} 
+\leq \R {L} \RB {\log N_h} ^{1/4} \d_{s} 
 }
@@
 S
-=L \log N_H 
+=L \log N_h 
 }
@@
 \VNm {\V {d}} _2
-\eqsim \mathcal {O} \SB {\R {L} \R {\log N_H}^3} 
+\eqsim \mathcal {O} \SB {\R {L} \R {\log N_h}^3} 
 }
@@
 \VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
-\leq \VNm {\M {P}^\intercal \M {P} \V {d}} _2 \\
+\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \notag \\
 %
-\leq \R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \\
+\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \notag \\
 %
-\leq 5.65 \R {\log N_H} 
+\leq &2.83 \R {L} \log N_h
 }
@@
 \VNm {\V {d} _{\SB{\mathcal {A}}}} _1
-\leq \R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \\
+\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \notag \\
 %
-\leq \R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \\
+\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \notag \\
 %
-\leq 1.21 L \R {\log N_H}^3
+\leq &3.44 L \R {\log N_h}^3
 +0.262 \VNm {\V {d} _{\SB{\mathcal {C}}}} _1 
@@
 %
-\leq 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 
+\leq 5.12 L \RB {\log N_h}^2
 }
@@
 %
-\leq 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 
+\leq 3.44 \R {L} \log N_h + 1.35 \R {L} \R {\log N_h} ^3
 }
@@
 \VNm {\V {d}} _2
-\leq 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 
+\leq 4.79 \R {L} \R {\log N_h}^3
 }
@@
 \chi
-= 8 \R {L} \R {\log N_H}^3 
+= \R {L} \R {\log N_h}^3
 }
@@
 \VNm {\V {d}} _2
-\leq \chi 
+= \mathcal {O} \RB {\chi}
 }
@@
 q _{\mathrm {iso}, B}
-\lesssim 2 \mathsf {e} ^{-N_B /12} \\
+\lesssim &2 \mathsf {e} ^{-N_B /12} \notag \\
 %
 q _{\mathrm {iso}, R}
-\lesssim 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \\
+\lesssim &2 N_h ^{-1/3} \RB {\log N_h} ^{-1/6} \notag \\
 %
 q _{\mathrm {no}}
-\lesssim N_H ^{-2} \\
+\lesssim &N_h ^{-1} \notag \\
 %
 q _{\mathrm {sp}}
-\lesssim 2 \mathsf {e} ^{-9L/\pi} 
+\lesssim &2 \mathsf {e} ^{-9L/\pi} 
 }
@@
 N_B
-\gtrsim 4 \log N_H \\
-%
-N_R
-\gtrsim 16 L \RB {\log N_H}^2 
+\gtrsim 16 L \RB {\log N_h}^2 
 }
@@
 q _{\mathrm {sp}}
-\lesssim q _{\mathrm {no}} \\
+\lesssim q _{\mathrm {no}}
 %
-\lesssim q _{\mathrm {iso}, R} \\
+\lesssim q _{\mathrm {iso}, R}
 %

### 2021-03-29 treatise-pdflatex/4_simulation.tex
Sec 3.3: Rev proof

@@
 = &\mathcal {R} \SB {\V {y}}
-\in \mathbb {R} ^{2 N_{B,t} N_{B,r}} \notag \\
+\in \mathbb {R} ^{2 N_B ^2} \notag \\
 %
@@
 = &\mathcal {R} \SB {\V {g}}
-\in \mathbb {R} ^{2 N_H^2} \notag \\
+\in \mathbb {R} ^{2 N_{H,t} N_{H,r}} \notag \\
 %
@@
 = &\mathcal {R} \SB {\M {P}}
-\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \notag \\
+\in \mathbb {R} ^{2 N_B ^2 \D 2 N_{H,t} N_{H,r}} \notag \\
 %
@@
 = &\mathcal {R} \SB {\M {P} ^\Adj}
-\in \mathbb {R} ^{2 N_{B,t} N_{B,r} \D 2 N_H^2} \notag \\
+\in \mathbb {R} ^{2 N_B ^2 \D 2 N_{H,t} N_{H,r}} \notag \\
 %
@@
 = &\mathcal {R} \SB {\V {z}}
-\in \mathbb {R} ^{2 N_{B,t} N_{B,r}} 
+\in \mathbb {R} ^{2 N_B ^2} 
 }
@@
 \begin {itemize}
-\item Input \m{\M {P} \in \mathbb {C} ^{ N_B^2 \D N_H^2}}, \m{\V {y} \in \mathbb {C} ^{ N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
+\item Input \m {\M {P} \in \mathbb {C} ^{N_B^2 \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \mathbb {C} ^{N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
 %
@@
 N_0
-= &2 N_H^2, \\
+= &2 N_{H,t} N_{H,r}, \\
 N_2
-= &\lfloor 4 \log N_H \rfloor, \\
+= &4 \lfloor \log N_{H,t} + \log N_{H,r} \rfloor, \\
 N_1
@@
 From our observation, it is not conclusive whether the successive estimation method is more accurate, and whether a third or more stage is helpful.
-It might have something to do with appropriately scaling \m {N_1, N_2} with respect to \m {N_H}.
+It might have something to do with appropriately scaling \m {N_1, N_2} with respect to \m {N_{H,t}, N_{H,r}}.
 We have not used this method in the plots included here.
@@
 For assorted plots, three series of plots are simulated.
-The first series for \m {N_{B,t} = N_H/2} and \m {N_{B,r} = N_H/3}.
-The second series for \m {N_{B,t} = N_H/3} and \m {N_{B,r} = N_H/2}.
-The third series for \m {N_{B,t} = N_H/2} and \m {N_{B,r} = N_H/2}.
+The first series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 2 N_B}.
+The second series for \m {N_{H,t} = 2 N_H} and \m {N_{H,r} = 3 N_H}.
+The third series for \m {N_{H,t} = 3 N_H} and \m {N_{H,r} = 2 N_H}.
 Unfortunately, this is very far from achieving the ideal values \eqref {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
@@
 The number of grid of quantization of phase shifters is \m {16}.
-The number of paths \m {L = N_H /2}.
+The number of paths \m {L = \R {N_{H,t} N_{H,r}}}.
 The ratio of the wavelength of carrier over the antenna spacing, \m {\l _{\mathrm {ant}} / d _{\mathrm {ant}} = 1 / 2}.
@@
 Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
-We set \m {\g_{\mathrm {DS}} = 2 \R {\log N_H}} as suggested in \cite {CaT07}.
-For sake of comparison, \m {\g_{\mathrm {Lasso}} = 2 \R {\log N_H}} too.
+We set \m {\g_{\mathrm {DS}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} as suggested in \cite {CaT07}.
+For sake of comparison, \m {\g_{\mathrm {Lasso}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} too.
 For OMP, we consult Cai and Wang \cite {CaW11} for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
-We take \m {\h_{\mathrm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3} \RB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
-The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.
+We take \m {\h_{\mathrm {OMP}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3 N_B}} for 2-norm condition.
+The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
 

### 2021-03-29 treatise-context/2_problem_setting.tex
Change dimension: context version

@@
 \NC \V {a} \SB {\psi'}
-= \NC \F {1} {\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u} _{n_h}
-\in \MB {C} ^ {N_H} \NR
+= \NC \F {1} {\R {N}} \sum_{n_h=0}^{N-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u} _{n_h}
+\in \MB {C} ^ {N} \NR
 }
@@
 \a_l
-\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
-\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR
+\V {a} \SB {2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
+\V {a} \SB {2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR
 }
@@
 =\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj
-\in \MB {C} ^{N_H \D N_H} \NR
+\in \MB {C} ^{N_{H,r} \D N_{H,t}} \NR
 }
@@
 Each end consists of both digital and analog precoders and combiners.
-In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \MB {C} ^{N_{B,t} \D N_{B,t}}} and the analog precoder \m {\M {F} _R \in \MB {C} ^{N_H \D  N_{B,t}}}.
-Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \MB {C} ^{N_{B,r} \D  N_{B,r}}} and the analog combiner \m {\M {W} _R \in \MB {C} ^{N_{B,r} \D N_H}}.
+In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \MB {C} ^{N_B \D N_B}} and the analog precoder \m {\M {F} _R \in \MB {C} ^{N_{H,t} \D N_B}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \MB {C} ^{N_B \D N_B}} and the analog combiner \m {\M {W} _R \in \MB {C} ^{N_B \D N_{H,r}}}.
 
@@
 %
-\NC n_H
-= \NC 0, \dots N_H-1, \NR
+\NC n_{H,t}
+= \NC 0, \dots N_{H,t}-1, \NR
 %
-\NC n_{R,t}
-= \NC 0, \dots N_{B,t}-1 \NR
+\NC n_{H,r}
+= \NC 0, \dots N_{H,r}-1 \NR
 %
-\NC n_{R,r}
-= \NC 0, \dots N_{B,r}-1 \NR
+\NC n_{R,t}, n_{R,r}
+= \NC 0, \dots N_R-1 \NR
 }
@@
 \DispNum {N:H:NY:NY} {
-\NC N_H \gg \NC N_{B,t}, N_{B,r} \NR
+\NC N_{H,t}, N_{H,r} \gg N_B \NR
 }
 
-Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_H \D N_{B,t}}} with each entry being i.i.d.\ standard normal.
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \NC \MB {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
 Let us introduce the effective channel
@@
 := \NC \Rm {vec} \SB {\M {H}}
-\in \MB {C} ^{N_H^2} \NR
+\in \MB {C} ^{N_{H,t} N_{H,r}} \NR
 %
@@
 := \NC \Rm {vec} \SB {\M {Y}}
-\in \MB {C} ^{N_{B,t} N_{B,r}} \NR
+\in \MB {C} ^{N_B ^2} \NR
 %
@@
 := \NC \Rm {vec} \SB {\M {W} _B \M {W} _R \M {Z}}
-\in \MB {C} ^{N_{B,t} N_{B,r}} \NR
+\in \MB {C} ^{N_B ^2} \NR
 %
@@
 := \NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R}
-\in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2} \NR
+\in \MB {C} ^{N_B ^2 \D N_{H,t} N_{H,r}} \NR
 }
@@
 \DispNum {K:K:CN:H1} {
-\NC \M {K} \in  \NC \MB {C} ^{N_H \D N_H} \NR
+\NC \M {K} = \NC \M {K} \SB {N} \in \MB {C} ^{N \D N} \NR
 %
 \NC \M {K} _{\SB {n_1, n_2}}
-= \NC \F {1} {\R {N_H}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N_H}, \NR
+= \NC \F {1} {\R {N}} \Ss {e}^{2\pi \Ss {i} n_1 n_2 /N}, \NR
 %
 \NC \Q n_1, n_2
-= \NC 0, 1, \dots, N_H-1 \NR
+= \NC 0, 1, \dots, N-1 \NR
 }
@@
 :=\NC \RB {\M {F} _B^\Tr \M {F} _R^\Tr \M {K}^\ast} \otimes \RB {\M {W} _B \M {W} _R \M {K}}
-\in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2} \NR
+\in \MB {C} ^{N_B^2 \D N_{H,t} N_{H,r}} \NR
 }
@@
 := \NC \Rm {vec} \SB {\M {G}}
-\in \MB {C} ^ {N_H \D N_H} \NR
+\in \MB {C} ^ {N_{H,t} \D N_{H,r}} \NR
 }
@@
 %
-\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_{B,t} \D N_{B,t}}},
-\m {\M {F} _R \in \NC \MB {C} ^{N_H \D N_{B,t}}},
-\m {\M {W} _R \in \NC \MB {C} ^{N_{B,r} \D N_H}},
-\m {\M {W} _B \in \NC \MB {C} ^{N_{B,r} \D N_{B,r}}},
-and \m {\M {Y} \in \NC \MB {C} ^{N_{B,r} \D N_{B,t}}}.
+\item Input \m {\M {F} _B \in \NC \MB {C} ^{N_R \D N_B}},
+\m {\M {F} _R \in \NC \MB {C} ^{N_{H,t} \D N_R}},
+\m {\M {W} _R \in \NC \MB {C} ^{N_R \D N_{H,r}}},
+\m {\M {W} _B \in \NC \MB {C} ^{N_B \D N_R}},
+and \m {\M {Y} \in \NC \MB {C} ^{N_B \D N_B}}.
 %
-\item Find \m {\M {P} \in \MB {C} ^{N_{B,t} N_{B,r} \D N_H^2}}, \m {\V {y} \in \MB {C} ^{N_H^2}} as in above.
+\item Find \m {\M {P} \in \MB {C} ^{N_{B,t} N_{B,r} \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \MB {C} ^{N_B^2}} as in above.
 %
@@
 \LA \NC \startcases
-\NC \Min {\V {g}' \in \MB {C} ^{N_H^2}}  \MC \VNm {\V {g}'} _1 \NR
+\NC \Min {\V {g}' \in \MB {C} ^{N_{H,t} N_{H,r}}}  \MC \VNm {\V {g}'} _1 \NR
 %

### 2021-03-29 treatise-context/3_2_generating_beamforming_matrices.tex
Change dimension: context version

@@
 =\NC \R {
-   \sum _{i=0} ^{N_{B,t}-1} \VNm {\sum _{j=0} ^{N_{B,t}-1} \F {1} {\R{N_{B,t}}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
+   \sum _{i=0} ^{N_R-1} \VNm {\sum _{j=0} ^{N_B-1} \F {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
 }
@@
 \DispNum {P:x:ex:ex} {
-\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_{B,t}}} + \F {2x} {N_{B,t}}}
+\NC \MB {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_R}} + \F {2x} {N_R}}
 \leq \NC \Ss {e} ^{-x} \NR
@@
 \DispNum {P:x:ex:ex!} {
-\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_{B,t}}}}
+\NC \MB {P} \SB {\VNm {\M {F} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_R}}}
 \leq \NC \Ss {e} ^{-x} \NR
@@
 \NC 1 -p
-\leq \NC 2 \Ss {e} ^{-N_{B,t} \R {\d_s} /4} \NR
+\leq \NC 2 \Ss {e} ^{-N_R \R {\d_s} /4} \NR
 }
@@
 We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
-Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_H s} RIP.
-In conclusion, (respectively for \m {N_{B,r}})
+Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s / N_{H,t} s} RIP.
+In conclusion, (respectively for \m {\M {W} _R})
 %
 \DispNum {N:R:sd':NH} {
-\NC N_{B,t}
-\geq \NC \F {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
+\NC N_R
+\geq \NC \frac {s} {\d_s^2} \RB {\log \frac{1}{\d_s}}^2 \RB {\log \frac{s}{\d_s}}^2 \log N_{H,t} \NR
 }
@@
 \DispNum {N:R:sd'NH} {
-\NC N_{B,t}
-\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_H \NR
+\NC N_R
+\geq \NC \F {s} {\d_s^2} \RB {\log s}^2 \log N_{H,t} \NR
 }
@@
 \NC 1 -p
-\leq \NC \RB {\F {\d_s} {N_H s}} ^{1/3} \NR
+\leq \NC \RB {\F {\d_s} {N_{H,t} s}} ^{1/3} \NR
 }
@@
 We argue as follows.
-If all angles \m {\th_l, \f_l} are exactly the multiples of \m {2 \pi/N_H}, then
+If angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,t}}), then
 \DispNum {G:G:Ud:dU} {

### 2021-03-29 treatise-context/3_3_bound_for_error_norm.tex
Conversion: compile chap 3
Transfer chap 1, 4 to LaTeX
Change dimension: context version

@@
 %
+And for convenience, let
+\Disp {
+\NC N_h
+= \NC N_{H,t} N_{H,r} \NR
+}
+%
 To bound \m {\VNm {\V {d}} _2}, we illustrate that \m {\V {g}} can be seen as sparse, and for that purpose we generously bound \m {\d_{S}} by \m {1}.
@@
 \NC \g
-= \NC 2 \R {\log N_H} \NR
+= \NC \R {\log N_h} \NR
 }
@@
 \NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
-\leq \NC  4 \R {2 \log N_H} \NR
+\leq \NC 2 \R {2 \log N_h} \NR
 }
@@
 \NC 1 -p
-\leq \NC N_H^{-2}. \NR
+\leq \NC N_h^{-1}. \NR
 }
@@
 %
-Particularly, fix threshold \m {x' =2 \R {\log N_H}}, yielding
+Particularly, fix threshold \m {x' =\R {2 \log N_h}}, yielding
 %
 \DispNum {Q:h:1N:Nh} {
-\NC Q\SB {2 \R {\log N_H}}
-=\NC \F {1} {2 N_H^2}. \NR
+\NC Q\SB {\R {2 \log N_h}}
+=\NC \F {1} {2 N_h}. \NR
 }
@@
 %
-\NC \leq \NC 2\R {2 \log N_H} \NR
+\NC \leq \NC 2\R {\log N_h} \NR
 }
@@
 %
-\NC \simeq \NC 2 \R {2 \log N_H} +2 \R {2 \log N_H} \NR
+\NC \simeq \NC \R {2 \log N_h} + \R {2 \log N_h} \NR
 }
@@
 %
-\DispNum {d:2:11:C1} {
+\Disp {
 \NC \VNm {\V {d} _{\SB{\MS {AB}}}} _2
@@
 \NC \d_{S}
-\leq \NC \R {L} \RB {\log N_H} ^{1/4} \d_{s} \NR
+\leq \NC \R {L} \RB {\log N_h} ^{1/4} \d_{s} \NR
 }
 %
-So \Rf {d:2:11:C1} becomes
+So we have
 %
@@
 \NC S
-=\NC L \log N_H \NR
+=\NC L \log N_h \NR
 }
@@
 \NC \VNm {\V {d}} _2
-\eqsim \NC \MS {O} \SB {\R {L} \R {\log N_H}^3} \NR
+\eqsim \NC \MS {O} \SB {\R {L} \R {\log N_h}^3} \NR
 }
@@
 %
-\NC \leq \NC 5.65 \R {\log N_H} \NR
+\NC \leq \NC 2.83 \R {\log N_h} \NR
 }
@@
 %
-\NC \leq \NC 1.21 L \R {\log N_H}^3
+\NC \leq \NC 3.44 L \R {\log N_h}^3
 +0.262 \VNm {\V {d} _{\SB{\MS {C}}}} _1 \NR
@@
 %
-\leq \NC 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 \NR
+\leq \NC 5.12 L \RB {\log N_h}^2 \NR
 }
@@
 %
-\leq \NC 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 \NR
+\leq \NC 3.44 \R {L} \log N_h +1.35 \R {L} \R {\log N_h}^3 \NR
 }
@@
 \NC \VNm {\V {d}} _2
-\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
+\leq \NC 4.79 \R {L} \R {\log N_h}^3 \NR
 }
@@
 \NC \chi
-= \NC 8 \R {L} \R {\log N_H}^3 \NR
+= \NC \R {L} \R {\log N_h}^3 \NR
 }
@@
 \NC q _{\Rm {iso}, R}
-\lesssim \NC 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
+\lesssim \NC 2 N_h ^{-1/3} \RB {\log N_h} ^{-1/6} \NR
 %
 \NC q _{\Rm {no}}
-\lesssim \NC N_H ^{-2} \NR
+\lesssim \NC N_h ^{-1} \NR
 %
@@
 \NC N_B
-\gtrsim \NC 4 \log N_H \NR
+\gtrsim \NC 2 \log N_h \NR
 %
 \NC N_R
-\gtrsim \NC 16 L \RB {\log N_H}^2 \NR
+\gtrsim \NC 4 L \RB {\log N_h}^2 \NR
 }

### 2021-03-29 treatise-context/4_simulation.tex
Change dimension: context version

@@
 = \NC \MS {R} \SB {\V {y}}
-\in \MB {R} ^{2 N_{B,r} N_{B,t}} \NR
+\in \MB {R} ^{2 N_B ^2} \NR
 %
@@
 = \NC \MS {R} \SB {\V {g}}
-\in \MB {R} ^{2 N_H^2} \NR
+\in \MB {R} ^{2 N_{H,t} N_{H,r}} \NR
 %
@@
 = \NC \MS {R} \SB {\M {P}}
-\in \MB {R} ^{2 N_{B,r} N_{B,t} \D 2 N_H^2} \NR
+\in \MB {R} ^{2 N_B ^2 \D 2 N_{H,t} N_{H,r}} \NR
 %
@@
 = \NC \MS {R} \SB {\M {P} ^\Adj}
-\in \MB {R} ^{2 N_{B,r} N_{B,t} \D 2 N_H^2} \NR
+\in \MB {R} ^{2 N_B ^2 \D 2 N_{H,t} N_{H,r}} \NR
 %
@@
 = \NC \MS {R} \SB {\V {z}}
-\in \MB {R} ^{2 N_{B,r} N_{B,t}} \NR
+\in \MB {R} ^{2 N_B ^2} \NR
 }
@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {C} ^{N_{B,r} N_{B,t} \D N_H^2}}, \m{\V {y} \in \MB {C} ^{N_{B,r} N_{B,t}}}, \m {\g_{\Rm {DS}} > 0}.
+\item Input \m{\M {P} \in \MB {C} ^{N_{B,r} N_{B,t} \D N_{H,t} N_{H,r}}}, \m{\V {y} \in \MB {C} ^{N_{B,r} N_{B,t}}}, \m {\g_{\Rm {DS}} > 0}.
 %
@@
 \NC N_0
-=\NC 2 N_H^2, \NR
+=\NC 2 N_{H,t} N_{H,r}, \NR
 \NC N_2
-=\NC \lfloor 4 \log N_H \rfloor, \NR
+=\NC \lfloor 4 \log \log N_{H,t} + \log N_{H,r} \rfloor, \NR
 \NC N_1
@@
 \NC \Hat {\V {g}}
-\LA \NC \Min {\V {g}' \in \MB {C} ^{N_H^2}}
+\LA \NC \Min {\V {g}' \in \MB {C} ^{N_{H,t} N_{H,r}}}
 \RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty} \NR
@@
 However, there is no simple way to determine the value of \m {\l} in advance.
-We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\Rm {DS}}} in the simulation.
+We have tried basis pursuit denoising, with \m {\l = N_{H,t} N_{H,r} / \g_{\Rm {DS}}} in the simulation.
 
@@
 We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
-We take \m {N_H} to be \m {6, 12, 18}, respectively.
-For assorted plots, three series of plots are simulated.
-The first series for \m {N_{B,t} = N_H/2} and \m {N_{B,r} = N_H/3}.
-The second series for \m {N_{B,t} = N_H/3} and \m {N_{B,r} = N_H/2}.
-The third series for \m {N_{B,t} = N_H/2} and \m {N_{B,r} = N_H/2}.
+We take \m {N_Y} to be \m {4, 6, 8}, respectively.
+Three series of plots are simulated.
+The first series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 2 N_B}.
+The second series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 3 N_B}.
+The third series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 2 N_B}.
 Unfortunately, this is very far from achieving the ideal values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
@@
 The number of grid of quantization of phase shifters is \m {16}.
-The number of paths \m {L = N_H /2}.
+The number of paths \m {L = \R {N_{H,t} N_{H,r}}}.
 The ratio of the wavelength of carrier over the antenna spacing, \m {\l _{\Rm {ant}} / d _{\Rm {ant}} = 1 / 2}.
@@
 Denote the threshold for DS to be \m {\g_{\Rm {DS}}}, and similar threshold of Lasso to be \m {\g_{\Rm {Lasso}}}.
-We set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}} as suggested in \cite [CaT07].
-For sake of comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
+We set \m {\g_{\Rm {DS}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} as suggested in \cite [CaT07].
+For sake of comparison, \m {\g_{\Rm {Lasso}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} too.
 For OMP, we consult Cai and Wang \cite [CaW11] for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
-We take \m {\h_{\Rm {OMP}} = 2 \R {\log N_H}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3} \RB {N_{B,r} N_{B,t}} ^ {1/4}} for 2-norm condition.
-The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 \R {N_{B,r} N_{B,t}}}.
+We take \m {\h_{\Rm {OMP}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3 N_B}} for 2-norm condition.
+The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
 
@@
 
-For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
+For Lasso, \m {\g _{\Rm {Lasso}}} (or \m {\l _{\Rm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
 Thus, for sake of comparison, we set the same threshold for Lasso and DS.
@@
 Suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\MS {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite [BoV04], p.6).
-For our case, that would be \m {\MS {O} \SB {4 N_H ^4 \D 8 N_H^2} = \MS {O} \SB {N_H^6}}.
+For our case, that would be \m {\MS {O} \SB {4 N_{H,t} ^2 N_{H,r} ^2 \D 8 N_{H,t} N_{H,r}} = \MS {O} \SB {N_{H,t} ^3 N_{H,r} ^3}}.
 But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.
@@
 Every Newton step involves a inversion of \m {\MS {O} \SB {\M {P} ^\Adj \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
-Since the dimension of \m {\M {P} ^\Adj \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\MS {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
-That is, we suppose \m {C_{\Rm {step}} = N_H^4}.
+Since the dimension of \m {\M {P} ^\Adj \M {P}} is \m {N_{H,t} N_{H,r}}, the cost of inversion may be roughly considered to be \m {\MS {O} \SB {N_{H,t} ^2 N_{H,r} ^2}}, as we know from newer results on the complexity of matrix inversion.
+That is, we suppose \m {C_{\Rm {step}} = N_{H,t} ^2 N_{H,r} ^2}.
 
@@
 \NC \M {P} ^\Adj \M {P}
-\approx \NC I _{N_{H}^2} \NR
+\approx \NC I _{N_{H,t} N_{H,r}} \NR
 }
@@
    \VNm {\V {g} +\RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {z}
-   -\V {g}} _1} N_H^4 \NR
-\NC =\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} N_H^4 \NR
+   -\V {g}} _1} N_{H,t} ^2 N_{H,r} ^2 \NR
+\NC =\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} N_{H,t} ^2 N_{H,r} ^2 \NR
 }
@@
 \NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}}}
-= \NC \s N_H^2 \MS {O} \RB {1} \NR
+= \NC \s N_{H,t} N_{H,r} \MS {O} \RB {1} \NR
 }
@@
 \NC C_{\Rm {DS}}
-=\NC \MS {O} \SB {N_{H}^6} \NR
+=\NC \MS {O} \SB {N_{H,t} ^3 N_{H,r} ^3} \NR
 }
@@
 \NC C_{\Rm {OMP}}
-=\NC \MS {O} \SB {N_H^2 \log \RB {N_{B,r} N_{B,t}}} \NR
+=\NC \MS {O} \SB {N_{H,t} N_{H,r} \log N_B} \NR
 }
 %
-Here \m {\log \RB {N_{B,r} N_{B,t}}} is small in our experiments, and if we dropped it, we may take
+Here \m {\log N_B} is small in our experiments, and if we dropped it, we may take
 \DispNum {C:P:ON:H2} {
 \NC C_{\Rm {OMP}}
-=\NC \MS {O} \SB {N_H^2} \NR
+=\NC \MS {O} \SB {N_{H,t} N_{H,r}} \NR
 }
@@
 Lasso is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
-However, Lasso and DS are equivalent in certain conditions \cite [AsR10], and we may suppose here they have the same complexity, \m {\MS {O} \SB {N_H^6}}.
+However, Lasso and DS are equivalent in certain conditions \cite [AsR10], and we may suppose here they have the same complexity, \m {\MS {O} \SB {N_{H,t} ^3 N_{H,r} ^3}}.
 
@@
 \NC C_{\Rm {Lasso}}
-=\NC \MS {O} \SB {N_H^6} \NR
+=\NC \MS {O} \SB {N_{H,t} ^3 N_{H,r} ^3} \NR
 }
@@
 All plots included in this treatise, in total, took about one month to run.
-Figures for \m {N_H = 18} each took about \m {3} days.
+Figures for \m {N_{H,t}, N_{H,r} \geq 24} each took about \m {3} days.
 The computer has \m {32} GB RAM, and Intel Core i9 processor.
@@
 
-Use \m {t_{\Rm {OMP}} \SB {N_H}}, \m {t_{\Rm {Lasso}} \SB {N_H}}, \m {t_{\Rm {DS}} \SB {N_H}} to denote their respective time taken.
+Abbreviate \m {N_h = N_{H,t} \D N_{H,r}} as in the last chapter.
+Use \m {t_{\Rm {OMP}} \SB {N_h}}, \m {t_{\Rm {Lasso}} \SB {N_h}}, \m {t_{\Rm {DS}} \SB {N_h}} to denote their respective time taken.
 We here copy the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
@@
 
-Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with \m {N_H}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
+Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with \m {N_h}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
 This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
@@
 \DispNum {t:P:NH:83} {
-\NC \T {t}_{\Rm {OMP}} \NC \eqsim \MS {O} \SB {N_H^{3.6}} \NR
-\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \MS {O} \SB {N_H^{4.8}} \NR
-\NC \T {t}_{\Rm {DS}} \NC \eqsim \MS {O} \SB {N_H^{8.3}} \NR
+\NC \T {t}_{\Rm {OMP}} \NC \eqsim \MS {O} \SB {N_h^{3.6}} \NR
+\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \MS {O} \SB {N_h^{4.8}} \NR
+\NC \T {t}_{\Rm {DS}} \NC \eqsim \MS {O} \SB {N_h^{8.3}} \NR
 }

### 2021-03-29 treatise-pdflatex/4_simulation.tex
Change dimension: context version

@@
 \Hat {\V {g}}
-\leftarrow \Min {\V {g}' \in \mathbb {C} ^{N_H^2}}
+\leftarrow \Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}}
 \RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty}
@@
 However, there is no simple way to determine the value of \m {\l} in advance.
-We have tried basis pursuit denoising, with \m {\l = N_H^2 / \g_{\mathrm {DS}}} in the simulation.
+We have tried basis pursuit denoising, with \m {\l = N_{H,t} N_{H,r} / \g_{\mathrm {DS}}} in the simulation.
 
@@
 We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
-We take \m {N_H} to be \m {6, 12, 18}, respectively.
-For assorted plots, three series of plots are simulated.
+We take \m {N_Y} to be \m {4, 6, 8}, respectively.
+Three series of plots are simulated.
 The first series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 2 N_B}.
-The second series for \m {N_{H,t} = 2 N_H} and \m {N_{H,r} = 3 N_H}.
-The third series for \m {N_{H,t} = 3 N_H} and \m {N_{H,r} = 2 N_H}.
+The second series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 3 N_B}.
+The third series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 2 N_B}.
 Unfortunately, this is very far from achieving the ideal values \eqref {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
@@
 
-For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
+For Lasso, \m {\g _{\mathrm {Lasso}}} (or \m {\l _{\mathrm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
 Thus, for sake of comparison, we set the same threshold for Lasso and DS.
@@
 \mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}}}
-= \s N_H^2 \mathcal {O} \RB {1} 
+= \s N_{H,t} N_{H,r} \mathcal {O} \RB {1} 
 }
@@
 C_{\mathrm {DS}}
-=\mathcal {O} \SB {N_{H}^6} 
+=\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3} 
 }
@@
 C_{\mathrm {OMP}}
-=\mathcal {O} \SB {N_H^2 \log \RB {N_{B,r} N_{B,t}}}
+=\mathcal {O} \SB {N_{H,t} N_{H,r} \log N_B} 
 }
@@
 C_{\mathrm {OMP}}
-=\mathcal {O} \SB {N_H^2}
+=\mathcal {O} \SB {N_{H,t} N_{H,r}}
 }
@@
 Lasso is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
-However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity, \m {\mathcal {O} \SB {N_H^6}}.
+However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity, \m {\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3}}.
 
@@
 C_{\mathrm {Lasso}}
-=\mathcal {O} \SB {N_H^6}
+=\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3}
 }
@@
 
-Use \m {t_{\mathrm {OMP}} \SB {N_H}}, \m {t_{\mathrm {Lasso}} \SB {N_H}}, \m {t_{\mathrm {DS}} \SB {N_H}} to denote their respective time taken.
+Abbreviate \m {N_h = N_{H,t} \D N_{H,r}} as in the last chapter.
+Use \m {t_{\mathrm {OMP}} \SB {N_h}}, \m {t_{\mathrm {Lasso}} \SB {N_h}}, \m {t_{\mathrm {DS}} \SB {N_h}} to denote their respective time taken.
 We here copy the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
@@
 
-Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_H}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
+Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_h}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
 This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
@@
 \DispNum {t:P:NH:83} {
-\tilde {t}_{\mathrm {OMP}} \eqsim &\mathcal {O} \SB {N_H^{3.6}} \\
-\tilde {t}_{\mathrm {Lasso}} \eqsim &\mathcal {O} \SB {N_H^{4.8}} \\
-\tilde {t}_{\mathrm {DS}} \eqsim &\mathcal {O} \SB {N_H^{8.3}} 
+\tilde {t}_{\mathrm {OMP}} \eqsim &\mathcal {O} \SB {N_h^{3.6}} \\
+\tilde {t}_{\mathrm {Lasso}} \eqsim &\mathcal {O} \SB {N_h^{4.8}} \\
+\tilde {t}_{\mathrm {DS}} \eqsim &\mathcal {O} \SB {N_h^{8.3}} 
 }

### 2021-03-29 treatise-pdflatex/foreword.tex
Change dimension: context version

@@
 
-I came across the field of compressive sensing in 2018, to begin with, when I was the TA of the course of Convex Optimization, and read about it again as an intern in MediaTek.
-Prof.\ Su always had students find their own topic of interest, and I thank him for having encouraged me to continue writing what would become of this treatise, even if when I first told him of the proposal, it was hardly more than a stream of conciousness.
-In addition to the stipend he kindly supplied, the warm faux-wood floor, comfortable sofas, and ergonomic chairs in the lab also helped.
+I came across the field of compressive sensing in 2018, to begin with, when I was the TA of the course on convex optimization by Prof.\ Borching Su, and read about it again as an intern in MediaTek.
+Prof.\ Hsuan-Jung Su always had students find their own topic of interest, and I thank him for having encouraged me to continue writing what would become of this treatise, even if when I first told him of the proposal, it was hardly more than a stream of consciousness.
+In addition to the stipend he kindly supplied, the warm faux-wood floor, comfortable sofas, and ergonomic chairs in the lab are also impressive.
 For various reasons, I took very long time writing this treatise, and I thank the advisor for his tolerance on my procrastination, if that is not too late.
+And at my presentation, Prof.\ Borching Su and Prof.\ I-Hsiang Wang, the oral defense committee, gave a lot suggestions, which are equally indispensable.
 
 The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
-The three and half years are punctuated by Bachi martial art practice session, teaching assistant's preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I too hold dearly.
+The three and half years are punctuated by Bachi martial art practice session, TA preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I hold dearly.
 
-In addition, I thank Chu-Tong Liu, a fellow PhD student of Prof.\ Su's, who I have acquainted in the undergraduate freshman year, in that he gave me valuable suggestions when I was stuck, and was lenient when I did not, or even failed at all to, deliver a proper presentation.
-I too cherish the decent meals, trips, and board games enjoyed together with fellow lab students, whose discussion, concern, joke, and sarcasm are particularly enlightening when one is undergoing a writer's block.
+In addition, I thank Chu-Tong Liu, a fellow PhD student, who I have acquainted in the undergraduate freshman year, in that he gave me valuable helps when I was stuck, and was lenient when I did not deliver a proper presentation.
+I too cherish the decent meals, trips, and board games enjoyed together with lab students, whose discussion, concern, joke, and sarcasm are particularly enlightening when one is undergoing a writer's block.
 
 After all, I thank my parents, who in recent years was supportive of whatever goal I set up to do (or at least claimed to work on), if slightly too credulous in my ability.
-It so was a tremendous luck that I did not have to mind financial matters in the master student years, which is something I ought to treasure.
-I am happy to have kept a sense of curiosity for the intricate universe.
+It so was a tremendous luck that I did not have to mind financial matters in the master student years.
+Therefore, I am happy to have kept a sense of curiosity for the intricate universe.
 

### 2021-03-30 treatise-context/3_2_generating_beamforming_matrices.tex
double check context version

@@
 \DispNum {C':C':WB:j2} {
-\NC \VNm {\M {W} _B \V {u}} _2
+\NC \VNm {\M {F} _B \V {u}} _2
 =\NC \R {
@@
 To do so, we apply Lemma \m {1} in Laurent and Massart \cite [LaM00] for equal weights, with \m {x > 0} below.
-By some calculation, we have the upper tail inequality
+By some calculation, we have the upper tail inequality (respectively for \m {\M {W} _B})
 %
@@
 \DispNum {W:1:ds:ds} {
-\NC \Nm {\VNm {\M {W} _B \V {u}} _2 ^2 - 1}
+\NC \Nm {\VNm {\M {F} _B \V {u}} _2 ^2 - 1}
 \geq \NC \d_s \NR
@@
 In Haviv and Regev, \quotation {The restricted isometry property of subsampled Fourier matrices} \cite [KlM17], Theorem \m {4.5} states a big O bound for the failure probability of a DFT submatrix with \m {\d_s} RIP.
-We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
+We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C = 1/3}.
 Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s / N_{H,t} s} RIP.
@@
 We argue as follows.
-If angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,t}}), then
+If angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then
 \DispNum {G:G:Ud:dU} {

### 2021-03-30 treatise-context/4_simulation.tex
double check context version

@@
 \startitemize[n]
-\item Input \m{\M {P} \in \MB {C} ^{N_{B,r} N_{B,t} \D N_{H,t} N_{H,r}}}, \m{\V {y} \in \MB {C} ^{N_{B,r} N_{B,t}}}, \m {\g_{\Rm {DS}} > 0}.
+\item Input \m{\M {P} \in \MB {C} ^{N_B^2 \D N_{H,t} N_{H,r}}}, \m{\V {y} \in \MB {C} ^{N_B ^2}}, \m {\g_{\Rm {DS}} > 0}.
 %
@@
 \NC N_2
-=\NC \lfloor 4 \log \log N_{H,t} + \log N_{H,r} \rfloor, \NR
+=\NC 4 \lfloor \log N_{H,t} + \log N_{H,r} \rfloor, \NR
 \NC N_1
@@
 We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
-We take \m {N_Y} to be \m {4, 6, 8}, respectively.
+We take \m {N_B} to be \m {4, 6, 8}, respectively.
 Three series of plots are simulated.
@@
 Second, \m {\T {\chi} _{\Rm {DS}}} decreases as \m {N_H} increases.
-Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\T {\chi} _{\Rm {DS}}} is also smaller, because we have a higher sample rate.
 
@@
 It is possible that the nonsparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
-It is curious to see whether for very large \m {N_H}, whether \m {\T {\chi}} and \m {\T {\chi}} will be asymptotically close.
+It is curious to see whether for very large \m {N_H}, whether \m {\T {\chi}} and \m {\chi} will be asymptotically close.
 
-In figures 24 and 25, we reproduce two cases of success and failure of DS.
+In the below, we reproduce two cases of success and failure of DS.
 In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.
@@
 We discuss the complexity of DS, Lasso, and OMP.
+Abbreviate \m {N_h = N_{H,t} N_{H,r}} as in the last chapter.
 
@@
 Suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\MS {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite [BoV04], p.6).
-For our case, that would be \m {\MS {O} \SB {4 N_{H,t} ^2 N_{H,r} ^2 \D 8 N_{H,t} N_{H,r}} = \MS {O} \SB {N_{H,t} ^3 N_{H,r} ^3}}.
+For our case, that would be \m {\MS {O} \SB {4 N_h ^2 \D 8 N_h} = \MS {O} \SB {N_h ^3}}.
 But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.
@@
 Every Newton step involves a inversion of \m {\MS {O} \SB {\M {P} ^\Adj \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
-Since the dimension of \m {\M {P} ^\Adj \M {P}} is \m {N_{H,t} N_{H,r}}, the cost of inversion may be roughly considered to be \m {\MS {O} \SB {N_{H,t} ^2 N_{H,r} ^2}}, as we know from newer results on the complexity of matrix inversion.
-That is, we suppose \m {C_{\Rm {step}} = N_{H,t} ^2 N_{H,r} ^2}.
+Since the dimension of \m {\M {P} ^\Adj \M {P}} is \m {N_h \D N_h}, the cost of inversion may be roughly considered to be \m {\MS {O} \SB {N_h ^2}}, as we know from newer results on the complexity of matrix inversion.
+That is, we suppose \m {C_{\Rm {step}} = N_h ^2}.
 
@@
 \NC C_{\Rm {DS}}
-=\NC \MS {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} N_H^4 \NR
+=\NC \MS {O} \SB {\VNm {\V {g}_{\Rm {LS}} -\V {g} ^\star} _1} N_h^2 \NR
 }
@@
 \NC \M {P} ^\Adj \M {P}
-\approx \NC I _{N_{H,t} N_{H,r}} \NR
+\approx \NC I _{N_h} \NR
 }
@@
    \VNm {\V {g} +\RB {\M {P} ^\Adj \M {P}} ^{-1} \M {P} ^\Adj \V {z}
-   -\V {g}} _1} N_{H,t} ^2 N_{H,r} ^2 \NR
-\NC =\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} N_{H,t} ^2 N_{H,r} ^2 \NR
+   -\V {g}} _1} N_h ^2 \NR
+\NC =\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1} N_h ^2 \NR
 }
@@
 \NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}}}
-= \NC \s N_{H,t} N_{H,r} \MS {O} \RB {1} \NR
+= \NC \s N_h \MS {O} \RB {1} \NR
 }
@@
 \NC C_{\Rm {DS}}
-=\NC \MS {O} \SB {N_{H,t} ^3 N_{H,r} ^3} \NR
+=\NC \MS {O} \SB {N_h ^3} \NR
 }
@@
 \NC C_{\Rm {OMP}}
-=\NC \MS {O} \SB {N_{H,t} N_{H,r} \log N_B} \NR
-}
-%
-Here \m {\log N_B} is small in our experiments, and if we dropped it, we may take
-\DispNum {C:P:ON:H2} {
-\NC C_{\Rm {OMP}}
-=\NC \MS {O} \SB {N_{H,t} N_{H,r}} \NR
+=\NC \MS {O} \SB {L \RB {\log N_h} ^2} \NR
 }
@@
 Lasso is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
-However, Lasso and DS are equivalent in certain conditions \cite [AsR10], and we may suppose here they have the same complexity, \m {\MS {O} \SB {N_{H,t} ^3 N_{H,r} ^3}}.
+However, Lasso and DS are equivalent in certain conditions \cite [AsR10], and we may suppose here they have the same complexity, \m {\MS {O} \SB {N_h ^3}}.
 
@@
 \NC C_{\Rm {Lasso}}
-=\NC \MS {O} \SB {N_{H,t} ^3 N_{H,r} ^3} \NR
+=\NC \MS {O} \SB {N_h ^3} \NR
 }
@@
 
-Abbreviate \m {N_h = N_{H,t} \D N_{H,r}} as in the last chapter.
-Use \m {t_{\Rm {OMP}} \SB {N_h}}, \m {t_{\Rm {Lasso}} \SB {N_h}}, \m {t_{\Rm {DS}} \SB {N_h}} to denote their respective time taken.
-We here copy the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
-They are: \m {
- t_{\Rm {OMP}} \SB {12}  = 0.0119,
- t_{\Rm {OMP}} \SB {16} = 0.0297, 
- t_{\Rm {OMP}} \SB {20}  = 0.0600,
- t_{\Rm {OMP}} \SB {24} = 0.155, 
-%
- t_{\Rm {Lasso}} \SB {12}  = 0.0436,
- t_{\Rm {Lasso}} \SB {16} = 0.176, 
- t_{\Rm {Lasso}} \SB {20}  = 0.471,
- t_{\Rm {Lasso}} \SB {24} = 1.26, 
-%
- t_{\Rm {DS}} \SB {12}  = 0.357,
- t_{\Rm {DS}} \SB {16} = 2.07, 
- t_{\Rm {DS}} \SB {20}  = 29.8,
- t_{\Rm {DS}} \SB {24} = 91.5
-}.
-
 Simulation illustrates that \m {t_{\Rm {DS}}} grows tremendously with \m {N_h}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
-This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
+This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {N_h}.
 By the way, different tolerance levels and maximal iteration numbers may result in vastly different computation time.
@@
 \DispNum {t:P:NH:83} {
-\NC \T {t}_{\Rm {OMP}} \NC \eqsim \MS {O} \SB {N_h^{3.6}} \NR
-\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \MS {O} \SB {N_h^{4.8}} \NR
-\NC \T {t}_{\Rm {DS}} \NC \eqsim \MS {O} \SB {N_h^{8.3}} \NR
+\NC \T {t}_{\Rm {OMP}} \NC \eqsim \MS {O} \SB {N_h^{1.8}} \NR
+\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \MS {O} \SB {N_h^{2.4}} \NR
+\NC \T {t}_{\Rm {DS}} \NC \eqsim \MS {O} \SB {N_h^{4.2}} \NR
 }

### 2021-03-30 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
Change dimension: context version
double check context version

@@
 In Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' \cite {KlM17}, Theorem \m {4.5} states a big O bound for the failure probability of a DFT submatrix with \m {\d_s} RIP.
-We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C \leftarrow 1/3}.
+We argue that their argument can be refined to give precise constants, by Chernoff-Hoeffding bounds and their theorem \m {2.2} with (say) \m {C = 1/3}.
 Their Theorem \m {3.7} and Theorem \m {4.5} may be changed accordingly, so that the relation below gives a bound for failure probability for \m {\d_s /N_{H,t} s} RIP.
@@
 N_R
-\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_H 
+\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_{H,t}
 }
@@
 1 -p
-\leq \RB {\frac {\d_s} {N_H s}} ^{1/3} 
+\leq \RB {\frac {\d_s} {N_{H,t} s}} ^{1/3} 
 }
@@
 We argue as follows.
-If all angles \m {\th_l, \f_l} are exactly the multiples of \m {2 \pi/N_H}, then
+If angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then
 \DispNum {G:G:Ud:dU} {

### 2021-03-30 treatise-pdflatex/4_simulation.tex
double check context version

@@
 Second, \m {\tilde {\chi} _{\mathrm {DS}}} decreases as \m {N_H} increases.
-Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\tilde {\chi} _{\mathrm {DS}}} is also smaller, because we have a higher sample rate.
 
@@
 It is possible that the nonsparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
-It is curious to see whether for very large \m {N_H}, whether \m {\tilde {\chi}} and \m {\tilde {\chi}} will be asymptotically close.
+It is curious to see whether for very large \m {N_H}, whether \m {\tilde {\chi}} and \m {\chi} will be asymptotically close.
 
-In figures 24 and 25, we reproduce two cases of success and failure of DS.
+In the below, we reproduce two cases of success and failure of DS.
 In both figures the true values of \m {\M {H}} entries are ordered by magnitude, and corresponding estimated values in the first and second stage are plotted against them.
@@
 Suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used (\cite {BoV04}, p.6).
-For our case, that would be \m {\mathcal {O} \SB {4 N_H ^4 \D 8 N_H^2} = \mathcal {O} \SB {N_H^6}}.
+For our case, that would be \m {\mathcal {O} \SB {4 N_h ^2 \D 8 N_h} = \mathcal {O} \SB {N_h ^3}}.
 But other algorithms exist, where, in general, complexity of convex programs is difficult to analyze, as it is not easily to determine how many steps were calculated.
@@
 Every Newton step involves a inversion of \m {\mathcal {O} \SB {\M {P} ^\dagger \M {P}}}, having the same order of magnitude to the time needed for matrix multiplication.
-Since the dimension of \m {\M {P} ^\dagger \M {P}} is \m {N_H^2}, the cost of inversion may be roughly considered to be \m {\mathcal {O} \SB {N_H^4}}, as we know from newer results on the complexity of matrix inversion.
-That is, we suppose \m {C_{\mathrm {step}} = N_H^4}.
+Since the dimension of \m {\M {P} ^\dagger \M {P}} is \m {N_h \D N_h}, the cost of inversion may be roughly considered to be \m {\mathcal {O} \SB {N_h^2}}, as we know from newer results on the complexity of matrix inversion.
+That is, we suppose \m {C_{\mathrm {step}} = N_h^2}.
 
@@
 C_{\mathrm {DS}}
-=\mathcal {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_H^4 
+=\mathcal {O} \SB {\VNm {\V {g}_{\mathrm {LS}} -\V {g} ^\star} _1} N_h^2 
 }
@@
 \M {P} ^\dagger \M {P}
-\approx I _{N_{H}^2} 
+\approx I _{N_h} 
 }
@@
    \VNm {\V {g} +\RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {z}
-   -\V {g}} _1} N_H^4
-=\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_H^4 
+   -\V {g}} _1} N_h ^2
+=\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _1} N_h ^2 
 }
 
-We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
+We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} follows complex standard normal distribution.
 If we agree that, for high probability,
@@
 \mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}}}
-= \s N_{H,t} N_{H,r} \mathcal {O} \RB {1} 
+= \s N_h \mathcal {O} \RB {1} 
 }
@@
 C_{\mathrm {DS}}
-=\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3} 
+=\mathcal {O} \SB {N_h ^3} 
 }
@@
 C_{\mathrm {OMP}}
-=\mathcal {O} \SB {N_{H,t} N_{H,r} \log N_B} 
-}
-%
-Here \m {\log \RB {N_{B,r} N_{B,t}}} is small in our experiments, and if we dropped it, we may take
-\DispNum {C:P:ON:H2} {
-C_{\mathrm {OMP}}
-=\mathcal {O} \SB {N_{H,t} N_{H,r}}
+=\mathcal {O} \SB {L \RB {\log N_h} ^2} 
 }
@@
 Lasso is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
-However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity, \m {\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3}}.
+However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity, \m {\mathcal {O} \SB {N_h ^3}}.
 
@@
 C_{\mathrm {Lasso}}
-=\mathcal {O} \SB {N_{H,t} ^3 N_{H,r} ^3}
+=\mathcal {O} \SB {N_h ^3}
 }
@@
 
-Abbreviate \m {N_h = N_{H,t} \D N_{H,r}} as in the last chapter.
-Use \m {t_{\mathrm {OMP}} \SB {N_h}}, \m {t_{\mathrm {Lasso}} \SB {N_h}}, \m {t_{\mathrm {DS}} \SB {N_h}} to denote their respective time taken.
-We here copy the arithmetic average (including different \m {\s}) of simulated values below, in seconds.
-They are:
-\m {t_{\mathrm {OMP}} \SB {12}  = 0.0119,}
-\m {t_{\mathrm {OMP}} \SB {16} = 0.0297, }
-\m {t_{\mathrm {OMP}} \SB {20}  = 0.0600,}
-\m {t_{\mathrm {OMP}} \SB {24} = 0.155, }
-%
-\m { t_{\mathrm {Lasso}} \SB {12}  = 0.0436,}
-\m { t_{\mathrm {Lasso}} \SB {16} = 0.176, }
-\m { t_{\mathrm {Lasso}} \SB {20}  = 0.471,}
-\m { t_{\mathrm {Lasso}} \SB {24} = 1.26, }
-%
-\m { t_{\mathrm {DS}} \SB {12}  = 0.357,}
-\m { t_{\mathrm {DS}} \SB {16} = 2.07, }
-\m { t_{\mathrm {DS}} \SB {20}  = 29.8,}
-\m { t_{\mathrm {DS}} \SB {24} = 91.5}
-
 Simulation illustrates that \m {t_{\mathrm {DS}}} grows tremendously with \m {N_h}, agreeing Friedlander and Saunders \cite {FrS07} who noted the high complexity of DS.
-This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {\M {N}_H^2}.
+This is not surprising, since the inversion of \m {\M {P} \M {P} ^\Adj} is probably the bottleneck of complexity, which has dimension \m {N_h}.
 By the way, different tolerance levels and maximal iteration numbers may result in vastly different computation time.
@@
 \DispNum {t:P:NH:83} {
-\tilde {t}_{\mathrm {OMP}} \eqsim &\mathcal {O} \SB {N_h^{3.6}} \\
-\tilde {t}_{\mathrm {Lasso}} \eqsim &\mathcal {O} \SB {N_h^{4.8}} \\
-\tilde {t}_{\mathrm {DS}} \eqsim &\mathcal {O} \SB {N_h^{8.3}} 
+\tilde {t}_{\mathrm {OMP}} \eqsim &\mathcal {O} \SB {N_h^{1.8}} \\
+\tilde {t}_{\mathrm {Lasso}} \eqsim &\mathcal {O} \SB {N_h^{2.4}} \\
+\tilde {t}_{\mathrm {DS}} \eqsim &\mathcal {O} \SB {N_h^{4.2}} 
 }

### 2021-04-06 treatise-context/4_simulation.tex
Backup new figures for nonsquare channel

@@
 We take \m {\h_{\Rm {OMP}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} for \m {\infty}-norm condition, \m {\h_{\Rm {OMP}} = \R {3 N_B}} for 2-norm condition.
-The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
 
-Each data point for DS and Lasso is repeated for \m {256} times, and taken arithmetic average.
-Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {8 \D 256} times.
+However, one must keep in mind that for OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix.
+Since we have here a low-complexity, random generation of beamforming matrices, a different design of sensing matrix may affect the performance of OMP.
+
+For Lasso, \m {\g _{\Rm {Lasso}}} (or \m {\l _{\Rm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
+Thus, for sake of comparison, we set the same threshold for Lasso and DS.
+In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\Rm {DS}} =  2 N_{H,t} N_{H,r} / \g _{\Rm {DS}}} and \m {\l _{\Rm {Lasso}} =  1 / \g _{\Rm {Lasso}}}.
+Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
 
@@
 It remains to determine the best choice of parameters.
+
+The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
+Each data point for DS and Lasso is repeated for \m {256} times, and taken arithmetic average.
+Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {8 \D 256} times.
 
@@
 
-\startsubsection [title={Plots of \m {N_H = 6}}]
+\startsubsection [title={Plots of assorted methods}]
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,r}}.
+In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
 %
 \blank [big]
-\externalfigure [error-small-square-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
+\externalfigure [error-medium-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
 %
 \blank [big]
-\externalfigure [error-small-tall-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
+\externalfigure [error-medium-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
 %
 \blank [big]
-\externalfigure [error-small-wide-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {2} stages, error.}
+\externalfigure [error-medium-tall-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
 %
 \blank [big]
-\externalfigure [error-small-square-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
+\externalfigure [error-small-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
 %
 \blank [big]
-\externalfigure [error-small-tall-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
+\externalfigure [error-small-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
 %
 \blank [big]
-\externalfigure [error-small-wide-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {4} stages, error.}
+\externalfigure [error-small-tall-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
+%
+\blank [big]
+\externalfigure [error-big-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
+%
+\blank [big]
+\externalfigure [error-big-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
+%
+\blank [big]
+\externalfigure [error-big-tall-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
 
@@
 
-\startsubsection [title={Plots of \m {N_H = 12}}]
+\startsubsection [title={Plots of different number of stages}]
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,r}}.
+In the following, we plot for \m {N_B = 4}, for different number of stages.
 %
 \blank [big]
-\externalfigure [error-medium-square-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
+\externalfigure [error-medium-square-three-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
 %
 \blank [big]
-\externalfigure [error-medium-tall-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
+\externalfigure [error-medium-wide-three-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
 %
 \blank [big]
-\externalfigure [error-medium-wide-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {2} stages, error.}
+\externalfigure [error-medium-tall-three-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
 %
 \blank [big]
-\externalfigure [error-medium-square-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
+\externalfigure [error-medium-square-three-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
 %
 \blank [big]
-\externalfigure [error-medium-tall-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
+\externalfigure [error-medium-wide-three-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
 %
 \blank [big]
-\externalfigure [error-medium-wide-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {4} stages, error.}
+\externalfigure [error-medium-tall-three-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
 
-\startsubsection [title={Plots of \m {N_H = 18}}]
+\startsubsection [title={Plots of different thresholds}]
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,r}}.
+In the following, we plot for different values of threshold, focusing on each of OMP, Lasso, DS.
 %
 \blank [big]
-\externalfigure [error-big-square-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {2} stages, error.}
+\externalfigure [error-medium-square-six-oommpp.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
 %
 \blank [big]
-\externalfigure [error-big-tall-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 9, N_H = 18}, with \m {2} stages, error.}
+\externalfigure [error-medium-wide-six-oommpp.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
 %
 \blank [big]
-\externalfigure [error-big-wide-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 6, N_H = 18}, with \m {2} stages, error.}
+\externalfigure [error-medium-tall-six-oommpp.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
 %
 \blank [big]
-\externalfigure [error-big-square-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {4} stages, error.}
+\externalfigure [error-medium-square-six-lasso.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
 %
 \blank [big]
-\externalfigure [error-big-tall-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 9, N_H = 18}, with \m {4} stages, error.}
+\externalfigure [error-medium-wide-six-lasso.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
 %
 \blank [big]
-\externalfigure [error-big-wide-four.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 6, N_H = 18}, with \m {4} stages, error.}
+\externalfigure [error-medium-tall-six-lasso.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
+%
+\blank [big]
+\externalfigure [error-medium-square-six-ddss.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
+%
+\blank [big]
+\externalfigure [error-medium-wide-six-ddss.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
+%
+\blank [big]
+\externalfigure [error-medium-tall-six-ddss.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
 
@@
 
-Regarding runtime statistics, we only plot the case where \m {N_{B,t} = N_{B,r} = N_H /2} with \m {2} stages.
-
+When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B} with \m {6} stages.
+%
 \blank [big]
-\externalfigure [time-small-square-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, error.}
+\externalfigure [time-medium-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
+%
 \blank [big]
-
+\externalfigure [time-small-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
+%
 \blank [big]
-\externalfigure [time-medium-square-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, error.}
-\blank [big]
-
-\blank [big]
-\externalfigure [time-big-square-two.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, error.}
-\blank [big]
+\externalfigure [time-big-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
 
@@
 From the simulation, DS outperforms other methods in most of the datasets.
-With low noise, \m {\T {\chi} _{\Rm {DS}} \approx \T {\chi} _{\Rm {OMP}} \approx \T {\chi} _{\Rm {Lasso}} \approx \T {\chi} _{\Rm {LS}}}.
-But with high noise, \m {\T {\chi} _{\Rm {OMP}}, \T {\chi} _{\Rm {Lasso}}, \T {\chi} _{\Rm {LS}}} blow up quickly,
-and it is usually true that \m {\T {\chi} _{\Rm {DS}} \leq \T {\chi} _{\Rm {OMP}} \leq \T {\chi} _{\Rm {Lasso}} \leq \T {\chi} _{\Rm {LS}}}.
+With low noise, \m {\T {\chi} _{\Rm {DS}} \approx \T {\chi} _{\Rm {OMP}} \leq \T {\chi} _{\Rm {Lasso}} \leq \T {\chi} _{\Rm {LS}}},
+although sometimes \m {\T {\chi} _{\Rm {DS}} \geq \T {\chi} _{\Rm {OMP}}}.
+With high noise, \m {\T {\chi} _{\Rm {DS}} \approx \T {\chi} _{\Rm {Lasso}} \leq \T {\chi} _{\Rm {OMP}} \leq \T {\chi} _{\Rm {LS}}}.
+although sometimes \m {\T {\chi} _{\Rm {DS}} \geq \T {\chi} _{\Rm {Lasso}}}.
+LS is so much poorer that it is not a main contender.
+In general, we can say that DS gives a ideal regularization for both low noise and high noise, and in between, DS is even better than both of them.
 
-For OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
-We keep in mind that a different design of sensing matrix, or a distribution of angles, will affect the performance of OMP.
-
-For Lasso, \m {\g _{\Rm {Lasso}}} (or \m {\l _{\Rm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
-Thus, for sake of comparison, we set the same threshold for Lasso and DS.
-Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
-
-For DS itself, first, \m {\T {\chi} _{\Rm {DS}}} certainly decreases as \m {\s} increases, but it does not decrease indefinitely.
-Second, \m {\T {\chi} _{\Rm {DS}}} decreases as \m {N_H} increases.
+Differing thresholds does not to seem have much effect on OMP and DS.
+But for Lasso, a tighter threshold may result in a better estimation, but it may also blow up for high signal cases.
+Increasing the number of stages obviously improves the estimation for all methods, and the main observation still applies.
 

### 2021-04-06 treatise-pdflatex/4_simulation.tex
Backup new figures for nonsquare channel

@@
 For sake of comparison, \m {\g_{\mathrm {Lasso}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} too.
+
 For OMP, we consult Cai and Wang \cite {CaW11} for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
 We take \m {\h_{\mathrm {OMP}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3 N_B}} for 2-norm condition.
-The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
 
-Each data point for DS and Lasso is repeated for \m {256} times, and taken arithmetic average.
-Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {12 \D 256} times.
+However, one must keep in mind that for OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix.
+Since we have here a low-complexity, random generation of beamforming matrices, a different design of sensing matrix may affect the performance of OMP.
+
+For Lasso, \m {\g _{\mathrm {Lasso}}} (or \m {\l _{\mathrm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
+Thus, for sake of comparison, we set the same threshold for Lasso and DS.
+In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\mathrm {DS}} =  2 N_{H,t} N_{H,r} / \g _{\mathrm {DS}}} and \m {\l _{\mathrm {Lasso}} =  1 / \g _{\mathrm {Lasso}}}.
+Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
 
@@
 It remains to determine the best choice of parameters.
+
+The maximal number of iteration of CVXPY is set to be \m {32}, and that of OMP is set to be \m {4 N_B}.
+Each data point for DS and Lasso is repeated for \m {256} times, and taken arithmetic average.
+Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {12 \D 256} times.
 
@@
 
-\subsection {Plots of \m {N_H = 12}}
+\subsection {Plots of assorted methods}
 
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 12} over \m {N_{B,t}} and \m {N_{B,r}}.
-
+In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-square-two.png}
-\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-square-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-wide-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-tall-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-small-square-six-usual.png}
+\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-small-wide-six-usual.png}
+\caption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-small-tall-six-usual.png}
+\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-square-six-usual.png}
+\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-wide-six-usual.png}
+\caption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-big-tall-six-usual.png}
+\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
 \end {figure}
 
+\subsection {Plots of different number of stages}
+
+In the following, we plot for \m {N_B = 4}, for different number of stages.
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-tall-two.png}
-\caption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {2} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-square-three-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
 \end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-wide-three-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-tall-three-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-square-three-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-wide-three-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-tall-three-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
 
+\subsection {Plots of different thresholds}
+
+In the following, we plot for different values of threshold, focusing on each of OMP, Lasso, DS.
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-wide-two.png}
-\caption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {2} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-square-six-oommpp.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
 \end {figure}
-
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-square-four.png}
-\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-wide-six-oommpp.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
 \end {figure}
-
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-tall-four.png}
-\caption {\m {N_{B,t} = 4, N_{B,r} = 6, N_H = 12}, with \m {4} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-tall-six-oommpp.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
 \end {figure}
-
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-wide-four.png}
-\caption {\m {N_{B,t} = 6, N_{B,r} = 4, N_H = 12}, with \m {4} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-square-six-lasso.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
 \end {figure}
-
-\subsection {Plots of \m {N_H = 18}}
-
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 18} over \m {N_{B,t}} and \m {N_{B,r}}.
-
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-square-two.png}
-\caption {\m {N_{B,t} = 12, N_{B,r} = 12, N_H = 18}, with \m {2} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-wide-six-lasso.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
 \end {figure}
-
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-tall-two.png}
-\caption {\m {N_{B,t} = 8, N_{B,r} = 12, N_H = 18}, with \m {2} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-tall-six-lasso.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
 \end {figure}
-
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-wide-two.png}
-\caption {\m {N_{B,t} = 12, N_{B,r} = 8, N_H = 18}, with \m {2} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-square-six-ddss.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
 \end {figure}
-
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-square-four.png}
-\caption {\m {N_{B,t} = 12, N_{B,r} = 12, N_H = 18}, with \m {4} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-wide-six-ddss.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
 \end {figure}
-
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-tall-four.png}
-\caption {\m {N_{B,t} = 8, N_{B,r} = 12, N_H = 18}, with \m {4} stages, error.}
-\end {figure}
-
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-wide-four.png}
-\caption {\m {N_{B,t} = 12, N_{B,r} = 8, N_H = 18}, with \m {4} stages, error.}
+\includegraphics [width = \textwidth] {error-medium-tall-six-ddss.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
 \end {figure}
@@
 
-Regarding runtime statistics, we only plot the case where \m {N_{B,t} = N_{B,r} = N_H /2} with \m {2} stages.
-
+When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B} with \m {6} stages.
+%
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-small-square-two.png}
-\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, time.}
+\includegraphics [width = \textwidth] {time-medium-square-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {time-small-square-six-usual.png}
+\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {time-big-square-six-usual.png}
+\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
 \end {figure}
 
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {time-medium-square-two.png}
-\caption {\m {N_{B,t} = 6, N_{B,r} = 6, N_H = 12}, with \m {4} stages, time.}
-\end {figure}
-
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {time-big-square-two.png}
-\caption {\m {N_{B,t} = 9, N_{B,r} = 9, N_H = 18}, with \m {4} stages, time.}
-\end {figure}
+\stopsubsection
 
@@
 From the simulation, DS outperforms other methods in most of the datasets.
-With low noise, \m {\tilde {\chi} _{\mathrm {DS}} \approx \tilde {\chi} _{\mathrm {OMP}} \approx \tilde {\chi} _{\mathrm {Lasso}} \approx \tilde {\chi} _{\mathrm {LS}}}.
-But with high noise, \m {\tilde {\chi} _{\mathrm {OMP}}, \tilde {\chi} _{\mathrm {Lasso}}, \tilde {\chi} _{\mathrm {LS}}} blow up quickly,
-and it is usually true that \m {\tilde {\chi} _{\mathrm {DS}} \leq \tilde {\chi} _{\mathrm {OMP}} \leq \tilde {\chi} _{\mathrm {Lasso}} \leq \tilde {\chi} _{\mathrm {LS}}}.
+With low noise, \m {\tilde {\chi} _{\mathrm {DS}} \approx \tilde {\chi} _{\mathrm {OMP}} \leq \tilde {\chi} _{\mathrm {Lasso}} \leq \tilde {\chi} _{\mathrm {LS}}},
+although sometimes \m {\tilde {\chi} _{\mathrm {DS}} \geq \tilde {\chi} _{\mathrm {OMP}}}.
+With high noise, \m {\tilde {\chi} _{\mathrm {DS}} \approx \tilde {\chi} _{\mathrm {Lasso}} \leq \tilde {\chi} _{\mathrm {OMP}} \leq \tilde {\chi} _{\mathrm {LS}}}.
+although sometimes \m {\tilde {\chi} _{\mathrm {DS}} \geq \tilde {\chi} _{\mathrm {Lasso}}}.
+LS is so much poorer that it is not a main contender.
+In general, we can say that DS gives a ideal regularization for both low noise and high noise, and in between, DS is even better than both of them.
 
-For OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
-We keep in mind that a different design of sensing matrix, or a distribution of angles, will affect the performance of OMP.
-
-For Lasso, \m {\g _{\mathrm {Lasso}}} (or \m {\l _{\mathrm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
-Thus, for sake of comparison, we set the same threshold for Lasso and DS.
-Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
-
-For DS itself, first, \m {\tilde {\chi} _{\mathrm {DS}}} certainly decreases as \m {\s} increases, but it does not decrease indefinitely.
-Second, \m {\tilde {\chi} _{\mathrm {DS}}} decreases as \m {N_H} increases.
+Differing thresholds does not to seem have much effect on OMP and DS.
+But for Lasso, a tighter threshold may result in a better estimation, but it may also blow up for high signal cases.
+Increasing the number of stages obviously improves the estimation for all methods, and the main observation still applies.
 

### 2021-04-06 treatise-context/functions.py

@@ -15,7 +15,7 @@ def execute (ver):
    cnt_chan = 0
    lst_lst_err = [] # each s_g, each method
    lst_lst_time = [] # each s_g, each method
-   lst_met = cst.LST_MET ()
+   lst_met = cst.LST_MET (ver)
 
    lst_chan_met = np.array (list (map (cst.NUM_CHAN_MET, lst_met)))
    num_chan_tot = cst.NUM_S_G () * lst_chan_met.sum ()
@@ -23,33 +23,34 @@ def execute (ver):
    time_tot_start = time.time ()
    for i_s_g in range (cst.NUM_S_G ()):
       s_g = cst.S_G_INIT () * (cst.SCALE_S_G () ** i_s_g)
-      print ("σ = ", '%.2f' % s_g, " :", sep = '')
-      lst_err = [0] * cst.NUM_MET ()
-      lst_time = [0] * cst.NUM_MET ()
-      for j_met in range (cst.NUM_MET ()):
+      print ("noise = ", '%.2f' % s_g, " :", sep = '')
+      lst_err = [0] * cst.NUM_MET (ver)
+      lst_time = [0] * cst.NUM_MET (ver)
+      for j_met in range (cst.NUM_MET (ver)):
          met = lst_met [j_met]
          cnt_met += 1
          num_chan_met = cst.NUM_CHAN_MET (met)
 
          for _ in range (num_chan_met):
             print ("channel instance ", cnt_chan, "...", sep = '', end = '\r', flush = True)
-            kk = get_kk (ver)
+            kk_t = get_kk (cst.NN_HH_t (ver))
+            kk_r = get_kk (cst.NN_HH_r (ver))
             cnt_chan += 1
             hh = pick_hh (ver)
-            gg = kk.conj ().T @ hh @ kk
+            gg = kk_r.conj ().T @ hh @ kk_t
             g = vectorize (gg)
             norm_hh = np.linalg.norm (hh, ord = 'fro')
-            g_r_h = np.zeros (2 * cst.NN_H (ver))
+            g_r_h = np.zeros (2 * cst.NN_HH_t (ver) * cst.NN_HH_r (ver))
 
             y_tot = None
             pp_tot = None
             time_chan_start = time.time ()
[…]

### 2021-04-06 treatise-context/main.py

@@ -5,9 +5,37 @@ import os
 import functions as fct
 import classes as cls
 
-ver = cls.Version (cls.Size.SMALL, cls.Ratio.TALL, cls.Stage.ONE)
-fct.execute (ver)
-ver = cls.Version (cls.Size.SMALL, cls.Ratio.WIDE, cls.Stage.ONE)
-fct.execute (ver)
-ver = cls.Version (cls.Size.SMALL, cls.Ratio.SQUARE, cls.Stage.ONE)
-fct.execute (ver)
+fct.execute (cls.Version (cls.Data.SMALL, cls.Channel.TALL, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.SMALL, cls.Channel.WIDE, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.SMALL, cls.Channel.SQUARE, cls.Stage.SIX, cls.Threshold.USUAL))
+
+
+'''
+fct.execute (cls.Version (cls.Data.MEDIUM, cls.Channel.TALL, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.MEDIUM, cls.Channel.WIDE, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.MEDIUM, cls.Channel.SQUARE, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.SMALL, cls.Channel.TALL, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.SMALL, cls.Channel.WIDE, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.SMALL, cls.Channel.SQUARE, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.BIG, cls.Channel.TALL, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.BIG, cls.Channel.WIDE, cls.Stage.SIX, cls.Threshold.USUAL))
+fct.execute (cls.Version (cls.Data.BIG, cls.Channel.SQUARE, cls.Stage.SIX, cls.Threshold.USUAL))
+
[…]

### 2021-04-06 treatise-pdflatex/classes.py

@@ -1,37 +1,50 @@
 import numpy as np
-from enum import Enum
-import sys
 
 import constants as cst
 import functions as fct
 
 # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
 
-class Version:
-   def __init__ (s, size, ratio, stage):
-      s.size = size
-      s.ratio = ratio
+class Version (object):
+   def __init__ (s, data, channel, stage, threshold):
+      s.data = data
+      s.channel = channel
+      s.threshold = threshold
       s.stage= stage
 
-class Method (Enum):
+class Method (object):
    LLSS = 1
-   LASSO = 2
+   OOMMPP_TWO_LAX = 2
    OOMMPP_TWO = 3
-   OOMMPP_INFTY = 4
-   DDSS = 5
+   OOMMPP_TWO_TENSE = 4
+   OOMMPP_INFTY_LAX = 5
+   OOMMPP_INFTY = 6
+   OOMMPP_INFTY_TENSE = 7
+   LASSO_LAX = 8
+   LASSO = 9
+   LASSO_TENSE = 10
+   DDSS_LAX = 11
+   DDSS = 12
+   DDSS_TENSE = 13
 
-class Size (Enum):
+class Data (object):
    SMALL = 1
    MEDIUM = 2
    BIG = 3
 
-class Ratio (Enum):
-   TALL = 1
-   WIDE = 2
-   SQUARE = 3
+class Channel (object):
+   SQUARE = 1
+   TALL = 2
+   WIDE = 3
 
-class Stage (Enum):
-   ONE = 1
-   TWO = 2
-   FOUR = 3
+class Stage (object):
+   THREE = 1
+   SIX = 2
+   NINE = 3
+
+class Threshold (object):
+   USUAL = 1
+   OOMMPP = 2
+   LASSO = 3
+   DDSS = 4
 

### 2021-04-09 treatise-context/4_simulation.tex
New figures

@@
 \blank [big]
-\externalfigure [error-medium-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [error-medium-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [error-medium-tall-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [error-small-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [error-small-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-small-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [error-small-tall-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-small-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [error-big-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-big-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [error-big-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-big-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [error-big-tall-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-big-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
+
+\stopsubsection
+
+\startsubsection [title={Plots of \m {N_Y = N_R}}]
+
+In the following, we plot for \m {N_Y = N_R}, for different ratios of \m {N_{H,t}, N_{H,r}}.
+%
+\blank [big]
+\externalfigure [error-medium-equal-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
+%
+\blank [big]
+\externalfigure [error-medium-equal-tall-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
+%
+\blank [big]
+\externalfigure [error-medium-equal-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
 
@@
 \blank [big]
-\externalfigure [error-medium-square-three-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-square-three-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
@@
 \blank [big]
-\externalfigure [error-medium-wide-three-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-wide-three-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
@@
 \blank [big]
-\externalfigure [error-medium-tall-three-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-tall-three-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
@@
 \blank [big]
-\externalfigure [error-medium-square-three-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-square-nine-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
@@
 \blank [big]
-\externalfigure [error-medium-wide-three-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-wide-nine-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
@@
 \blank [big]
-\externalfigure [error-medium-tall-three-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-tall-three-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
@@
 \blank [big]
-\externalfigure [error-medium-square-six-oommpp.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-square-six-oommpp.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \blank [big]
-\externalfigure [error-medium-wide-six-oommpp.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-wide-six-oommpp.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \blank [big]
-\externalfigure [error-medium-tall-six-oommpp.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-tall-six-oommpp.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \blank [big]
-\externalfigure [error-medium-square-six-lasso.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-square-six-lasso.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \blank [big]
-\externalfigure [error-medium-wide-six-lasso.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-wide-six-lasso.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \blank [big]
-\externalfigure [error-medium-tall-six-lasso.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-tall-six-lasso.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \blank [big]
-\externalfigure [error-medium-square-six-ddss.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-square-six-ddss.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
@@
 \blank [big]
-\externalfigure [error-medium-wide-six-ddss.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-wide-six-ddss.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
@@
 \blank [big]
-\externalfigure [error-medium-tall-six-ddss.png] [wfactor=fit, hfactor=fit]
+\externalfigure [error-medium-more-tall-six-ddss.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
@@
 \blank [big]
-\externalfigure [time-medium-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [time-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [time-small-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [time-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \blank [big]
-\externalfigure [time-big-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\externalfigure [time-big-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}

### 2021-04-09 treatise-pdflatex/4_simulation.tex
New figures

@@
 
-\subsection {Plots of \m {N_H = 6}}
-
-In the following, we plot the reciprocal of noise level vs relative error norm in log scale, for different values and ratios of \m {N_H = 6} over \m {N_{B,t}} and \m {N_{B,r}}.
-
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-square-two.png}
-\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
-\end {figure}
-
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-tall-two.png}
-\caption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {2} stages, error.}
-\end {figure}
-
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-wide-two.png}
-\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {2} stages, error.}
-\end {figure}
-
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-square-four.png}
-\caption {\m {N_{B,t} = 3, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
-\end {figure}
-
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-tall-four.png}
-\caption {\m {N_{B,t} = 2, N_{B,r} = 3, N_H = 6}, with \m {4} stages, error.}
-\end {figure}
-
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-wide-four.png}
-\caption {\m {N_{B,t} = 3, N_{B,r} = 2, N_H = 6}, with \m {4} stages, error.}
-\end {figure}
-
 \subsection {Plots of assorted methods}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-square-six-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-square-six-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-wide-six-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-wide-six-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-tall-six-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-tall-six-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-square-six-usual.png}
+\includegraphics [width = \textwidth] {error-small-more-square-six-usual.png}
 \caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-wide-six-usual.png}
+\includegraphics [width = \textwidth] {error-small-more-wide-six-usual.png}
 \caption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-tall-six-usual.png}
+\includegraphics [width = \textwidth] {error-small-more-tall-six-usual.png}
 \caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-square-six-usual.png}
+\includegraphics [width = \textwidth] {error-big-more-square-six-usual.png}
 \caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-wide-six-usual.png}
+\includegraphics [width = \textwidth] {error-big-more-wide-six-usual.png}
 \caption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-tall-six-usual.png}
+\includegraphics [width = \textwidth] {error-big-more-tall-six-usual.png}
 \caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
+\end {figure}
+
+\subsection {Plots of \m {N_Y = N_R}}
+
+In the following, we plot for \m {N_Y = N_R = 4}, for different ratios of \m {N_{H,t}, N_{H,r}}.
+%
+\begin {figure} [H]
+\includegraphics {error-medium-equal-square-six-usual.png}
+\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 8, N_{H,r} = 8}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics {error-medium-equal-tall-six-usual.png}
+\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
+\end {figure}externalfigure
+%
+\begin {figure} [H]
+\includegraphics {error-medium-equal-wide-six-usual.png}
+\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
 \end {figure}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-square-three-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-square-three-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-wide-three-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-wide-three-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-tall-three-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-tall-three-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-square-three-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-square-nine-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-wide-three-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-wide-nine-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-tall-three-usual.png}
+\includegraphics [width = \textwidth] {error-medium-more-tall-nine-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
+\end {figure}
 
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-square-six-oommpp.png}
+\includegraphics [width = \textwidth] {error-medium-more-square-six-oommpp.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-wide-six-oommpp.png}
+\includegraphics [width = \textwidth] {error-medium-more-wide-six-oommpp.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-tall-six-oommpp.png}
+\includegraphics [width = \textwidth] {error-medium-more-tall-six-oommpp.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-square-six-lasso.png}
+\includegraphics [width = \textwidth] {error-medium-more-square-six-lasso.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-wide-six-lasso.png}
+\includegraphics [width = \textwidth] {error-medium-more-wide-six-lasso.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-tall-six-lasso.png}
+\includegraphics [width = \textwidth] {error-medium-more-tall-six-lasso.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-square-six-ddss.png}
+\includegraphics [width = \textwidth] {error-medium-more-square-six-ddss.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-wide-six-ddss.png}
+\includegraphics [width = \textwidth] {error-medium-more-wide-six-ddss.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-tall-six-ddss.png}
+\includegraphics [width = \textwidth] {error-medium-more-tall-six-ddss.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-medium-square-six-usual.png}
+\includegraphics [width = \textwidth] {time-medium-more-square-six-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-small-square-six-usual.png}
+\includegraphics [width = \textwidth] {time-small-more-square-six-usual.png}
 \caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-big-square-six-usual.png}
+\includegraphics [width = \textwidth] {time-big-more-square-six-usual.png}
 \caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
 \end {figure}
-
-\stopsubsection
 

### 2021-04-10 treatise-context/1_introduction.tex
Update presentation figures

@@
 
-It appears that, for a given number of sampling, DS recovers more successfully than OMP.
+It appears that, for a given number of sampling, DS recovers better than OMP, except perhaps in high noise scenario.
 Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] with only an analog combiner,
@@
 
-In addition, it seems that with the same threshold, DS is better than Lasso.
+In addition, it seems that with the same threshold, DS recovers better than Lasso, except perhaps in low noise scenario.
 Again, our proposed method is more general than Lian, Liu and Lau \cite [LLL17] with only an analog combiner,
@@
 and we do not require special devices as in Vlachos, Alexandropoulos, and Thompson \cite [VAT19].
+Overall, it is clear that DS leads to a relatively better regularization than OMP and Lasso.
 

### 2021-04-10 treatise-context/4_simulation.tex
Update presentation figures

@@
 
-We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
-We take \m {N_B} to be \m {4, 6, 8}, respectively.
+We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-2}}, and being multiplied by powers of \m {\R {2}}, for \m {6} values.
+We take \m {N_B} to be \m {2, 4, 6}, respectively.
 Three series of plots are simulated.
-The first series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 2 N_B}.
-The second series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 3 N_B}.
-The third series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 2 N_B}.
+The first series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 3 N_B}.
+The second series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 4 N_B}.
+The third series for \m {N_{H,t} = 4 N_B} and \m {N_{H,r} = 3 N_B}.
 Unfortunately, this is very far from achieving the ideal values \Rf {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
@@
 The number of grid of quantization of phase shifters is \m {16}.
-The number of paths \m {L = \R {N_{H,t} N_{H,r}}}.
+The number of paths \m {L = \lfloor \R {N_{H,t} N_{H,r}} / 2 \rfloor}.
 The ratio of the wavelength of carrier over the antenna spacing, \m {\l _{\Rm {ant}} / d _{\Rm {ant}} = 1 / 2}.
@@
 We set \m {\g_{\Rm {DS}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} as suggested in \cite [CaT07].
-For sake of comparison, \m {\g_{\Rm {Lasso}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} too.
+For sake of comparison, \m {\g_{\Rm {Lasso}} = \g_{\Rm {DS}}} too.
 For OMP, we consult Cai and Wang \cite [CaW11] for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
@@
 
-For Lasso, \m {\g _{\Rm {Lasso}}} (or \m {\l _{\Rm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
+For Lasso, \m {\l _{\Rm {Lasso}}} is also crucial to the performance, but cannot be obtained in advance.
 Thus, for sake of comparison, we set the same threshold for Lasso and DS.
@@
 In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
+We fix \m {N_R = \RB {3/2} N_B}.
 %
@@
 
-In the following, we plot for different values of threshold, focusing on each of OMP, Lasso, DS.
+In the following, we plot for different thresholds, for \m {N_B = 4}, focusing on each of OMP, Lasso, DS.
 %
@@
 
-When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B} with \m {6} stages.
+When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B}.
 %
@@
 LS is so much poorer that it is not a main contender.
-In general, we can say that DS gives a ideal regularization for both low noise and high noise, and in between, DS is even better than both of them.
+These trends is true with different number of stages, and with the case \m {N_B = N_R}.
+In general, we can say that overall, DS gives a better regularization for both low noise and high noise scenario, and in most cases, DS is even better than both of them.
 

### 2021-04-10 treatise-context/5_conclusion.tex
Update presentation figures

@@
 
-We corroborate the prediction that DS is nearly optimal, and it may extract more information than other methods do when the sampling rate is low.
-When the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
+We corroborate the prediction that DS gives better regularization, and it may extract more information than other methods do when the sampling rate is low.
+In particular, when the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
 Therefore, one may use DS in the scenario that precision is crucial, as well as the case that the number of RF chains is more limited or fewer stages of estimation are possible.

### 2021-04-10 treatise-pdflatex/4_simulation.tex
Update presentation figures

@@
 
-We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-4}}, and being multiplied by powers of \m {2}, for \m {6} values.
-We take \m {N_B} to be \m {4, 6, 8}, respectively.
+We use dimensionless noise level \m {\s} which takes value starting with \m {2^{-2}}, and being multiplied by powers of \m {\R {2}}, for \m {6} values.
+We take \m {N_B} to be \m {2, 4, 6}, respectively.
 Three series of plots are simulated.
-The first series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 2 N_B}.
-The second series for \m {N_{H,t} = 2 N_B} and \m {N_{H,r} = 3 N_B}.
-The third series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 2 N_B}.
+The first series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 3 N_B}.
+The second series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 4 N_B}.
+The third series for \m {N_{H,t} = 4 N_B} and \m {N_{H,r} = 3 N_B}.
 Unfortunately, this is very far from achieving the ideal values \eqref {N:B:4l:H2}, and this may be part of the reason the result is not as successful as expected.
@@
 The number of grid of quantization of phase shifters is \m {16}.
-The number of paths \m {L = \R {N_{H,t} N_{H,r}}}.
+The number of paths \m {L = \lfloor \R {N_{H,t} N_{H,r}} / 2 \rfloor}.
 The ratio of the wavelength of carrier over the antenna spacing, \m {\l _{\mathrm {ant}} / d _{\mathrm {ant}} = 1 / 2}.
@@
 Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
-We set \m {\g_{\mathrm {DS}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} as suggested in \cite {CaT07}.
-For sake of comparison, \m {\g_{\mathrm {Lasso}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} too.
+We set \m {\g_{\mathrm {DS}} = 2 \R {2 \log \RB {N_{H,t} N_{H,r}}}} as suggested in \cite {CaT07}.
+For sake of comparison, \m {\g_{\mathrm {Lasso}} = \g_{\mathrm {DS}}}.
 
@@
 
-For Lasso, \m {\g _{\mathrm {Lasso}}} (or \m {\l _{\mathrm {Lasso}}}) is also crucial to the performance, but cannot be obtained in advance.
+For Lasso, \m {\l _{\mathrm {Lasso}}} is also crucial to the performance, but cannot be obtained in advance.
 Thus, for sake of comparison, we set the same threshold for Lasso and DS.
-In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\mathrm {DS}} =  2 N_{H,t} N_{H,r} / \g _{\mathrm {DS}}} and \m {\l _{\mathrm {Lasso}} =  1 / \g _{\mathrm {Lasso}}}.
+In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\mathrm {DS}} =  N_{H,t} N_{H,r} / \g _{\mathrm {DS}}} and \m {\l _{\mathrm {Lasso}} =  1 / \g _{\mathrm {Lasso}}}.
 Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

### 2021-04-10 treatise-pdflatex/functions.py

@@ -170,7 +170,7 @@ def lasso (pp_r, y_r, g_g, ver):
    k = - 2 * pp_r.T @ y_r
    qq = pp_r.T @ pp_r
    g_r = cp.Variable ((nn))
-   l_g = 2 * np.sqrt (cst.NN_HH_t (ver) * cst.NN_HH_r (ver)) / g_g
+   l_g = 1 / g_g
 
    prob = cp.Problem (
          cp.Minimize (
@@ -193,7 +193,7 @@ def ddss (pp_r, y_r, g_g, ver):
    k = pp_r.T @ y_r
    qq = pp_r.T @ pp_r
    c = np.ones ((nn))
-   l_g = 2 * np.sqrt (cst.NN_HH_t (ver) * cst.NN_HH_r (ver)) / g_g
+   l_g = cst.NN_HH_t (ver) * cst.NN_HH_r (ver) / g_g
 
    prob = cp.Problem (
          cp.Minimize (

### 2021-04-12 treatise-context/3_2_generating_beamforming_matrices.tex
Dimension of Fourier matrix

@@
 where \m {\Rm {abs}} denotes entrywise absolute value.
-Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\Adj \M {K}^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
+Then if we notice that \m {\M {W} _B \M {W} _R \M {K} _r \M {U}} and \m {\M {U} ^\Adj \M {K} _t ^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
 \DispNum {W:2:WB:d's} {
@@
 \NC =\NC \VNm {
-   \M {W} _B \M {W} _R \M {K} \M {U} \D
+   \M {W} _B \M {W} _R \M {K} _r \M {U} \D
    \Rm {diag} \SB {\Rm {abs} \SB {\V {d}'}} \D
-   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
+   \M {U} ^\Adj \M {K} _t ^\Adj \M {F} _R \M {F} _B} _2 \NR
 %
 \NC =\NC \VNm {
-   \M {W} _B \M {W} _R \M {K} \M {U}
+   \M {W} _B \M {W} _R \M {K} _r \M {U}
    \R {\Rm {abs} \SB {\V {d}'}} \D
    \R {\Rm {abs} \SB {\V {d}'}}
-   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
+   \M {U} ^\Adj \M {K} _t ^\Adj \M {F} _R \M {F} _B} _2 \NR
 %
 \NC =\NC \VNm {
-   \M {W} _B \M {W} _R \M {K} \M {U}
+   \M {W} _B \M {W} _R \M {K} _r \M {U}
    \R {\Rm {abs} \SB {\V {d}'}}} _2 \D
-   \VNm {\M {F} _B ^\Adj \M {F} _R ^\Adj \M {K} \M {U}
+   \VNm {\M {F} _B ^\Adj \M {F} _R ^\Adj \M {K} _t \M {U}
    \R {\Rm {abs} \SB {\V {d}'}}} _2 \NR

### 2021-04-12 treatise-context/5_conclusion.tex
Dimension of Fourier matrix

@@
 
-We corroborate the prediction that DS gives better regularization, and it may extract more information than other methods do when the sampling rate is low.
+Since we have RIP, a whole series of compressive sensing techniques become possible.
+But moreover, we corroborate the prediction that DS gives better regularization, and it may extract more information than other methods do when the sampling rate is low.
 In particular, when the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
-Therefore, one may use DS in the scenario that precision is crucial, as well as the case that the number of RF chains is more limited or fewer stages of estimation are possible.
+Therefore, one may use DS for sake of higher precision, or with limited RF chains and fewer stages of estimation, for example, in the ultra reliable or low latency scenario.
 

### 2021-04-12 treatise-pdflatex/4_simulation.tex
Dimension of Fourier matrix

@@
 \hat {\M {H}}
-\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger 
+\leftarrow \M {K} _r \hat {\M {G}} \M {K}^\dagger _t
 }
@@
 Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
-We set \m {\g_{\mathrm {DS}} = 2 \R {2 \log \RB {N_{H,t} N_{H,r}}}} as suggested in \cite {CaT07}.
+We set \m {\g_{\mathrm {DS}} = 2 \log \RB {N_{H,t} N_{H,r}}} as suggested in \cite {CaT07}.
 For sake of comparison, \m {\g_{\mathrm {Lasso}} = \g_{\mathrm {DS}}}.
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-square-six-usual.png}
-\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
-\end {figure}
-%
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-wide-six-usual.png}
-\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
-\end {figure}
-%
-\begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-tall-six-usual.png}
-\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
-\end {figure}
-%
-\begin {figure} [H]
 \includegraphics [width = \textwidth] {error-small-more-square-six-usual.png}
@@
 \caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-more-square-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-more-wide-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
+\includegraphics [width = \textwidth] {error-medium-more-tall-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
 \end {figure}
@@
 \begin {figure} [H]
+\includegraphics {error-medium-equal-wide-six-usual.png}
+\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
+\end {figure}
+%
+\begin {figure} [H]
 \includegraphics {error-medium-equal-tall-six-usual.png}
@@
 \end {figure}externalfigure
-%
-\begin {figure} [H]
-\includegraphics {error-medium-equal-wide-six-usual.png}
-\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
-\end {figure}
 
@@
 
-In the following, we plot for \m {N_B = 4}, for different number of stages.
+In the following, we plot for \m {N_B = 4}, for different number of stages \m {3} and \m {9}.
+We fix \m {N_R = \RB {3/2} N_B} with \m {6} stages again and in the below.
 %
@@
 \includegraphics [width = \textwidth] {error-medium-more-square-three-usual.png}
-\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {3} stages, error.}
 \end {figure}
@@
 \includegraphics [width = \textwidth] {error-medium-more-square-nine-usual.png}
-\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {9} stages, error.}
 \end {figure}
@@
 \includegraphics [width = \textwidth] {error-medium-more-square-six-oommpp.png}
-\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
 \end {figure}
@@
 \includegraphics [width = \textwidth] {error-medium-more-square-six-lasso.png}
-\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
 \end {figure}
@@
 \includegraphics [width = \textwidth] {error-medium-more-square-six-ddss.png}
-\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
 \end {figure}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-medium-more-square-six-usual.png}
-\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
+\includegraphics [width = \textwidth] {time-small-more-square-six-usual.png}
+\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
 \end {figure}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-small-more-square-six-usual.png}
-\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
+\includegraphics [width = \textwidth] {time-medium-more-square-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
 \end {figure}
@@
 Differing thresholds does not to seem have much effect on OMP and DS.
-But for Lasso, a tighter threshold may result in a better estimation, but it may also blow up for high signal cases.
+Except for Lasso, where a tighter threshold may improve the accuracy, but a overtly tight threshold may also result in a blow up for high signal cases.
 Increasing the number of stages obviously improves the estimation for all methods, and the main observation still applies.

### 2021-04-26 treatise-context/abstract.tex
Update presentation figures
Add keywords

@@
 To reduce the complexity, we cast it as a linear program, and suggest the basis pursuit denoising form.
-Numerical results show that DS is superior, especially when the sample is less sufficient and the noise level is higher.
+Numerical results show that DS gives a superb regularization, especially when the sample is less sufficient and the noise level is higher.
 We therefore propose that DS may be used, when the number of RF chains is more limited or when fewer stages of estimation are possible.
 
+Keywords: channel estimation, compressive sensing, sparsity, Dantzig Selector, regularization, restricted isometry
+
 \stoptitle

### 2021-04-28 presentation/1_setting.tex
Revise presentation
pdflatex: Shrink figure width

@@
 \Subsubtitle {\InstitutionText}
-\Subsubtitle {November 2020}
+\Subsubtitle {March 2021}
 
@@
 
-\I We claim that DS is superior in higher noise and fewer samples than OMP.
+\I We claim that DS is superior to OMP in situation with higher noise and fewer samples.
 \I We give a asymptotic bound on expected error norm.
@@
 % XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
-\Frame {Design of Beamformers}
+\Frame {Generating beamforming matrices}
 {
@@
 
-\I We set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be uniformly distributed in argument and unity magnitude, up to a design constant
+\I We set each entry of \m {\m {F}_R} (resp.\ \m {\m {W}_R}) be i.i.d.\ uniformly distributed in argument and unity magnitude, up to a design constant
 

### 2021-04-28 presentation/3_simulation.tex
pdflatex: Shrink figure width

@@
 {
-\I \m {N_H=6, N_{B,t}=3, N_{B,r}=2}, 2 stages
+\I \m {N_B=2, N_R=3, N_{H,t}=6, N_{H,r}=8}, 6 stages
 \blank [big]
-\externalfigure [error-small-wide-two.png] [width=11cm]
+\externalfigure [error-small-more-tall-six-usual.png] [width=11cm]
 }
@@
 {
-\I \m {N_H=6, N_{B,t}=2, N_{B,r}=3}, 2 stages
+\I \m {N_B=2, N_R=3, N_{H,t}=8, N_{H,r}=6}, 6 stages
 \blank [big]
-\externalfigure [error-small-tall-two.png] [width=11cm]
+\externalfigure [error-small-more-wide-six-usual.png] [width=11cm]
 }
@@
 {
-\I \m {N_H=12, N_{B,t}=6, N_{B,r}=4}, 2 stages
+\I \m {N_B=4, N_R=6, N_{H,t}=12, N_{H,r}=16}, 6 stages
 \blank [big]
-\externalfigure [error-medium-wide-two.png] [width=11cm]
+\externalfigure [error-small-more-tall-six-usual.png] [width=11cm]
 }
@@
 {
-\I \m {N_H=12, N_{B,t}=4, N_{B,r}=6}, 2 stages
+\I \m {N_B=4, N_R=6, N_{H,t}=16, N_{H,r}=12}, 6 stages
 \blank [big]
-\externalfigure [error-medium-tall-two.png] [width=11cm]
+\externalfigure [error-small-more-wide-six-usual.png] [width=11cm]
 }
@@
 {
-\I \m {N_H=18, N_{B,t}=9, N_{B,r}=6}, 2 stages
+\I \m {N_B=6, N_R=8, N_{H,t}=18, N_{H,r}=24}, 6 stages
 \blank [big]
-\externalfigure [error-big-wide-two.png] [width=11cm]
+\externalfigure [error-small-more-tall-six-usual.png] [width=11cm]
 }
@@
 {
-\I \m {N_H=18, N_{B,t}=6, N_{B,r}=9}, 2 stages
+\I \m {N_B=6, N_R=8, N_{H,t}=24, N_{H,r}=18}, 6 stages
 \blank [big]
-\externalfigure [error-big-tall-two.png] [width=11cm]
+\externalfigure [error-small-more-wide-six-usual.png] [width=11cm]
 }

### 2021-04-28 treatise-context/3_1_sparsity_of_channel.tex
minor typos
pdflatex: Shrink figure width

--- 2020-12-19 treatise/3_1_sparsity_of_channel.tex
@@
 We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity level \m {s} different from \m {S}.
-If \m {N_H} is large, we may forget for a moment that \m {s} is an integer.
+If \m {N} is large, we may forget for a moment that \m {s} is an integer.
 
@@
 :=\NC \RB {
-   \f \; \Rm {Mod}\; \F {2\pi} {N_H}
-   + \RB {\F {2 n_H} {N_H} + 1} \pi
+   \f \; \Rm {Mod}\; \F {2\pi} {N}
+   + \RB {\F {2 n_H} {N} + 1} \pi
 } \;
@@
 \NC D \SB {\psi'}
-:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
+:= \NC \sum_{n_H=0}^{N-1} \Ss {e}^{i n_H \psi'} \NR
 }
@@
 \NC \V {b} \SB {\f} _{\SB {n_H}}
-=\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
+=\NC \F {1} {N} D \SB {\psi \SB {\f, n_H}} \NR
 }
@@
 \NC \Nm {D \SB {\psi'}}
-= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
+= \NC \F {\Nm {\sin \SB {N \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
 %
@@
 \NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
-\leq \NC \F {1} {N_H}
+\leq \NC \F {1} {N}
 \VNm {
 \RB {
-   \sum_{n_H' =0}^{N_H -1}
+   \sum_{n_H' =0}^{N -1}
       B \SB {\psi \SB {\f, n_H'}}
@@
 \NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
-\leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
+\leq \NC \F {1} {N} \D \F {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
 %
-\NC = \NC \F {48} {N_H \pi^3}
-\int _{s /N_H} ^1 \F {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
+\NC = \NC \F {48} {N \pi^3}
+\int _{s /N} ^1 \F {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
 %
-\NC =\NC \F {1} {\pi} \log \F {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \NR
+\NC =\NC \F {1} {\pi} \log \F {N^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \NR
 %
-\NC \eqsim \NC \F {2} {\pi} \RB {\log N_H - \log s} \NR
+\NC \eqsim \NC \F {2} {\pi} \RB {\log N - \log s} \NR
 %
-\NC \leq \NC \F {2} {\pi} \log N_H \NR
+\NC \leq \NC \F {2} {\pi} \log N \NR
 }
@@
 \NC s
-=\NC \R {\log N_H} \NR
+=\NC \R {\log N} \NR
 }
@@
 \NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
-\leq \NC \F {2} {\pi} \log N_H \NR
+\leq \NC \F {2} {\pi} \log N \NR
 }
@@
 \NC \leq \NC
-\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _1
-\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _1
-\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
-%
-\NC \leq \NC
-\F {4} {\pi^2} L \RB {\log N_H}^2 \D
+\F {4} {\pi^2} L \RB {\log N_{H,t}} \RB {\log N_{H,r}} \D
 \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
@@
 \DispNum {g:2:12:43} {
-\NC \F {\VNm {\M {g} _{\SB{\MS {C}}}} _1} {\RB {\log N_H}^2}
-\leq \NC \F {12 \R{2}} {\pi ^{5/2}}
+\NC \F {\VNm {\M {g} _{\SB{\MS {C}}}} _1} {L \RB {\log N_{H,t}} \RB {\log N_{H,r}}}
+\leq \NC \F {16 \R{2}} {\pi ^{5/2}}
 \leq \F {4} {3}. \NR
@@
 %
+Finally, by AM-GM inequality,
 \Result
@@
 {
-et \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in \Rf {g:g:ve:Nh}.
+Let \m {\V {g} \in \MB {C} ^{N_{H,t} \D N_{H,r}}} be defined as in \Rf {g:g:ve:Nh}.
 Then the bound
@@
 \NC \VNm {\M {g} _{\SB{\MS {C}}}} _1
-\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
+\leq \NC \F {1} {3} L \RB {\log N_{H,t} + \log N_{H,r}} ^2 \NR
 }

### 2021-04-28 treatise-context/4_simulation.tex
pdflatex: Shrink figure width

@@
 \NC \Hat {\M {H}}
-\LA \NC \M {K} \Hat {\M {G}} \M {K}^\Adj \NR
+\LA \NC \M {K} _r \Hat {\M {G}} \M {K}^\Adj _t \NR
 }
@@
 Thus, for sake of comparison, we set the same threshold for Lasso and DS.
-In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\Rm {DS}} =  2 N_{H,t} N_{H,r} / \g _{\Rm {DS}}} and \m {\l _{\Rm {Lasso}} =  1 / \g _{\Rm {Lasso}}}.
+In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\Rm {DS}} =  N_{H,t} N_{H,r} / \g _{\Rm {DS}}} and \m {\l _{\Rm {Lasso}} =  1 / \g _{\Rm {Lasso}}}.
 Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
@@
 \blank [big]
-\externalfigure [error-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
-%
-\blank [big]
-\externalfigure [error-medium-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
-%
-\blank [big]
-\externalfigure [error-medium-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
-%
-\blank [big]
 \externalfigure [error-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
@@
 \FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
+%
+\blank [big]
+\externalfigure [error-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
+%
+\blank [big]
+\externalfigure [error-medium-more-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
+%
+\blank [big]
+\externalfigure [error-medium-more-tall-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
 %
@@
 \blank [big]
+\externalfigure [error-medium-equal-wide-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
+%
+\blank [big]
 \externalfigure [error-medium-equal-tall-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
-%
-\blank [big]
-\externalfigure [error-medium-equal-wide-six-usual.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
 
@@
 \externalfigure [error-medium-more-square-six-oommpp.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
 %
@@
 \externalfigure [error-medium-more-square-six-lasso.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
 %
@@
 \externalfigure [error-medium-more-square-six-ddss.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
+\FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
 %
@@
 \blank [big]
+\externalfigure [time-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
+\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
+%
+\blank [big]
 \externalfigure [time-medium-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
 \FigureCaption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
-%
-\blank [big]
-\externalfigure [time-small-more-square-six-usual.png] [wfactor=fit, hfactor=fit]
-\FigureCaption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
 %

### 2021-04-28 treatise-context/foreword.tex
pdflatex: Shrink figure width

--- 2021-03-29 treatise-pdflatex/foreword.tex
@@
-\chapter* {Foreword}
+\starttitle [title={Foreword}]
 
@@
 The present treatise is far from being remarkable, but I suppose the course of devising, clarifying, speculating, verifying, programming, debugging, googling, and polishing does teach some resilience to a weak mind.
-The three and half years are punctuated by Bachi martial art practice session, TA preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I hold dearly.
+The three and half years are punctuated by Bāchí martial art practice session, TA preparation and scoring, chess club meeting, MediaTek internship, and the two semester courses of Real Analysis and Advanced Statistical Inference, which are recollections I hold dearly.
 
@@
 November 4, 2020
+
+\stoptitle

### 2021-04-28 treatise-pdflatex/1_introduction.tex
pdflatex: Shrink figure width

@@
 
-It appears that, for a given number of sampling, DS recovers more successfully than OMP.
+It appears that, for a given number of sampling, DS recovers better than OMP, except perhaps in high noise scenario.
 Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} with only an analog combiner,
@@
 
-In addition, it seems that with the same threshold, DS is better than Lasso.
+In addition, it seems that with the same threshold, DS recovers better than Lasso, except perhaps in low noise scenario.
 Again, our proposed method is more general than Lian, Liu and Lau \cite {LLL17} with only an analog combiner,
@@
 and we do not require special devices as in Vlachos, Alexandropoulos, and Thompson \cite {VAT19}.
+Overall, it is clear that DS leads to a relatively better regularization than OMP and Lasso.

### 2021-04-28 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
pdflatex: Shrink figure width

@@
 where \m {\mathrm {abs}} denotes entrywise absolute value.
-Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\dagger \M {K}^\dagger \M {F} _R^\dagger \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
+Then if we notice that \m {\M {W} _B \M {W} _R \M {K} _r \M {U}} and \m {\M {U} ^\dagger \M {K}^\dagger _t \M {F} _R^\dagger \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
 \DispNum {W:2:WB:d's} {
@@
 = &\VNm {
-   \M {W} _B \M {W} _R \M {K} \M {U} \D
+   \M {W} _B \M {W} _R \M {K} _r \M {U} \D
    \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
-   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
+   \M {U} ^\dagger \M {K} _t ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
 %
 = &\VNm {
-   \M {W} _B \M {W} _R \M {K} \M {U}
+   \M {W} _B \M {W} _R \M {K} _r \M {U}
    \R {\mathrm {abs} \SB {\V {d}'}} \D
    \R {\mathrm {abs} \SB {\V {d}'}}
-   \M {U} ^\dagger \M {K} ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
+   \M {U} ^\dagger \M {K} _t ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
 %
 = &\VNm {
-   \M {W} _B \M {W} _R \M {K} \M {U}
+   \M {W} _B \M {W} _R \M {K} _r \M {U}
    \R {\mathrm {abs} \SB {\V {d}'}}} _2 \D
-   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} \M {U}
+   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} _t \M {U}
    \R {\mathrm {abs} \SB {\V {d}'}}} _2 \notag \\

### 2021-04-28 treatise-pdflatex/4_simulation.tex
pdflatex: Shrink figure width

@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-more-square-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-small-more-square-six-usual.png}
 \caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-more-wide-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-small-more-wide-six-usual.png}
 \caption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-small-more-tall-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-small-more-tall-six-usual.png}
 \caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-square-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-six-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-wide-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-six-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-tall-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-six-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-more-square-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-big-more-square-six-usual.png}
 \caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-more-wide-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-big-more-wide-six-usual.png}
 \caption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-big-more-tall-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-big-more-tall-six-usual.png}
 \caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics {error-medium-equal-square-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-equal-square-six-usual.png}
 \caption {\m {N_B = 4, N_R = 4, N_{H,t} = 8, N_{H,r} = 8}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics {error-medium-equal-wide-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-equal-wide-six-usual.png}
 \caption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics {error-medium-equal-tall-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-equal-tall-six-usual.png}
 \caption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-square-three-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-three-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {3} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-wide-three-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-three-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-tall-three-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-three-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-square-nine-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-nine-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {9} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-wide-nine-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-nine-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-tall-nine-usual.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-nine-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-square-six-oommpp.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-six-oommpp.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-wide-six-oommpp.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-six-oommpp.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-tall-six-oommpp.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-six-oommpp.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-square-six-lasso.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-six-lasso.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-wide-six-lasso.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-six-lasso.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-tall-six-lasso.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-six-lasso.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-square-six-ddss.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-square-six-ddss.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-wide-six-ddss.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-wide-six-ddss.png}
 \caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {error-medium-more-tall-six-ddss.png}
+\includegraphics [width = 0.8 \textwidth] {error-medium-more-tall-six-ddss.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-small-more-square-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {time-small-more-square-six-usual.png}
 \caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-medium-more-square-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {time-medium-more-square-six-usual.png}
 \caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
@@
 \begin {figure} [H]
-\includegraphics [width = \textwidth] {time-big-more-square-six-usual.png}
+\includegraphics [width = 0.8 \textwidth] {time-big-more-square-six-usual.png}
 \caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}

### 2021-04-28 treatise-pdflatex/5_conclusion.tex
pdflatex: Shrink figure width

@@
 
-We corroborate the prediction that DS gives better regularization, and it may extract more information than other methods do when the sampling rate is low.
+Since we have RIP, a whole series of compressive sensing techniques become possible.
+But moreover, we corroborate the prediction that DS gives better regularization, and it may extract more information than other methods do when the sampling rate is low.
 In particular, when the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
-Therefore, one may use DS in the scenario that precision is crucial, as well as the case that the number of RF chains is more limited or fewer stages of estimation are possible.
+Therefore, one may use DS for sake of higher precision, or with limited RF chains and fewer stages of estimation, for example, in the ultra reliable or low latency scenario.

### 2021-04-28 treatise-pdflatex/abstract.tex
Update presentation figures
pdflatex: Shrink figure width

@@
 To reduce the complexity, we cast it as a linear program, and suggest the basis pursuit denoising form.
-Numerical results show that DS is superior, especially when the sample is less sufficient and the noise level is higher.
+Numerical results show that DS gives a superb regularization, especially when the sample is less sufficient and the noise level is higher.
 We therefore propose that DS may be used, when the number of RF chains is more limited or when fewer stages of estimation are possible.
+
+Keywords: channel estimation, compressive sensing, sparsity, Dantzig Selector, regularization, restricted isometry

### 2021-04-28 treatise-context/classes.py

@@ -1,0 +1,50 @@
+import numpy as np
+
+import constants as cst
+import functions as fct
+
+# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
+
+class Version (object):
+   def __init__ (s, data, channel, stage, threshold):
+      s.data = data
+      s.channel = channel
+      s.threshold = threshold
+      s.stage= stage
+
+class Method (object):
+   LLSS = 1
+   OOMMPP_TWO_LAX = 2
+   OOMMPP_TWO = 3
+   OOMMPP_TWO_TENSE = 4
+   OOMMPP_INFTY_LAX = 5
+   OOMMPP_INFTY = 6
+   OOMMPP_INFTY_TENSE = 7
+   LASSO_LAX = 8
+   LASSO = 9
+   LASSO_TENSE = 10
+   DDSS_LAX = 11
+   DDSS = 12
+   DDSS_TENSE = 13
+
+class Data (object):
+   SMALL = 1
+   MEDIUM = 2
+   BIG = 3
+
+class Channel (object):
+   SQUARE = 1
+   TALL = 2
+   WIDE = 3
+
+class Stage (object):
+   THREE = 1
+   SIX = 2
+   NINE = 3
+
+class Threshold (object):
+   USUAL = 1
+   OOMMPP = 2
+   LASSO = 3
+   DDSS = 4
+

### 2021-04-28 treatise-context/functions.py

@@ -1,0 +1,477 @@
+import numpy as np
+import scipy as sp
+import cvxpy as cp
+import matplotlib.pyplot as plt
+
+import os
+import time
+import random
+
+import constants as cst
+import classes as cls
+
+def execute (ver):
+   cnt_met = 0
+   cnt_chan = 0
+   lst_lst_err = [] # each s_g, each method
+   lst_lst_time = [] # each s_g, each method
+   lst_met = cst.LST_MET (ver)
+
+   lst_chan_met = np.array (list (map (cst.NUM_CHAN_MET, lst_met)))
+   num_chan_tot = cst.NUM_S_G () * lst_chan_met.sum ()
+
+   time_tot_start = time.time ()
+   for i_s_g in range (cst.NUM_S_G ()):
+      s_g = cst.S_G_INIT () * (cst.SCALE_S_G () ** i_s_g)
+      print ("noise = ", '%.2f' % s_g, " :", sep = '')
+      lst_err = [0] * cst.NUM_MET (ver)
+      lst_time = [0] * cst.NUM_MET (ver)
+      for j_met in range (cst.NUM_MET (ver)):
+         met = lst_met [j_met]
+         cnt_met += 1
+         num_chan_met = cst.NUM_CHAN_MET (met)
+
+         for _ in range (num_chan_met):
+            print ("channel instance ", cnt_chan, "...", sep = '', end = '\r', flush = True)
+            kk_t = get_kk (cst.NN_HH_t (ver))
+            kk_r = get_kk (cst.NN_HH_r (ver))
+            cnt_chan += 1
+            hh = pick_hh (ver)
+            gg = kk_r.conj ().T @ hh @ kk_t
+            g = vectorize (gg)
+            norm_hh = np.linalg.norm (hh, ord = 'fro')
+            g_r_h = np.zeros (2 * cst.NN_HH_t (ver) * cst.NN_HH_r (ver))
+
+            y_tot = None
+            pp_tot = None
+            time_chan_start = time.time ()
+            for _ in range (cst.NUM_STAGE (ver)):
+               ff_bb = pick_mat_bb (ver).T
+               ff_rr = pick_mat_rr_t (ver).T
+               ww_bb = pick_mat_bb (ver)
+               ww_rr = pick_mat_rr_r (ver)
[…]

### 2021-04-28 treatise-pdflatex/constants.py

@@ -1,0 +1,205 @@
+import numpy as np
+import classes as cls
+
+def NN_YY (ver):
+   switcher = {
+      cls.Data.SMALL : 2,
+      cls.Data.MEDIUM : 4,
+      cls.Data.BIG : 6,
+   }
+   return switcher [ver.data]
+
+def NN_RR (ver):
+   return int ((3/2) * NN_YY (ver))
+
+def NN_HH_t (ver):
+   switcher = {
+      cls.Channel.SQUARE : 3 * NN_YY (ver),
+      cls.Channel.TALL : 3 * NN_YY (ver),
+      cls.Channel.WIDE : 4 * NN_YY (ver),
+   }
+   return switcher [ver.channel]
+
+def NN_HH_r (ver):
+   switcher = {
+      cls.Channel.SQUARE : 3 * NN_YY (ver),
+      cls.Channel.TALL : 4 * NN_YY (ver),
+      cls.Channel.WIDE : 3 * NN_YY (ver),
+   }
+   return switcher [ver.channel]
+
+
+# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
+
+def LAMBDA_ANT (ver):
+   return 1
+
+def DIST_ANT (ver):
+   return 3
+
+def LL (ver):
+   return int (np.sqrt (NN_HH_t (ver) * NN_HH_r (ver)) / 2)
+
+# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # #
+
+def NUM_MET (ver):
+   switcher = {
+      cls.Threshold.USUAL: 5,
+      cls.Threshold.OOMMPP : 8,
+      cls.Threshold.LASSO : 6,
+      cls.Threshold.DDSS : 6,
+   }
+   return switcher [ver.threshold]
+
+def NUM_STAGE (ver):
+   switcher = {
+      cls.Stage.THREE : 3,
+      cls.Stage.SIX : 6,
+      cls.Stage.NINE : 9
+   }
+   return switcher [ver.stage]
+
+def NUM_CHAN_BASIC ():
+   return 96
+
+def NUM_CHAN_MET (met):
+   switcher = {
+      cls.Method.LLSS : 8,
+      cls.Method.OOMMPP_TWO_LAX : 4,
+      cls.Method.OOMMPP_TWO : 4,
+      cls.Method.OOMMPP_TWO_TENSE : 4,
+      cls.Method.OOMMPP_INFTY_LAX : 4,
+      cls.Method.OOMMPP_INFTY : 4,
[…]

### 2021-06-05 article/main.tex
Copy IEEE template

\documentclass[journal]{IEEEtran}

\begin{document}

\title{Dantzig Selector Applied on mm-Wave MIMO Channel Estimation and and Error Analysis}

\author{Tzu-Yu Jeng
        Hsuan-Jung Su%
\thanks{Hsuan-Jung Su is with the Department
of Electrical Engineering, National Taiwan University.}
\thanks{Manuscript received April 1, 2020; revised April 1, 2021.}}

\markboth{IEEE Journal of whatever,~Vol.~0, No.~0, June~2020}%
{Jeng and Su: Dantzig Selector Applied on mm-Wave MIMO Channel Estimation}

\maketitle

\begin{abstract}
Multiple-input multiple-output communication systems in the millimeter-wave band are gradually being adopted.
A larger antennae array makes channel estimation more difficult.
Meanwhile, hybrid beamforming, which utilizes fewer RF chains, is applied too, so that new estimation methods have to be designed.
This can be seen as a compressive sensing problem, for which Orthogonal Matching Pursuit is usually used.

We consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
We generate random beamforming matrices and use Dantzig Selector to estimate the channel in the space frequency domain.
Then, we give a quantitative bound (which holds for high probability) on the expected error norm.
To reduce the complexity, we cast it as a linear program, and suggest the basis pursuit denoising form.
Numerical results show that DS gives a superb regularization, especially when the sample is less sufficient and the noise level is higher.
We therefore propose that DS may be used, when the number of RF chains is more limited or when fewer stages of estimation are possible.
\end{abstract}

\begin{IEEEkeywords}
channel estimation, compressive sensing, sparsity, Dantzig Selector, regularization, restricted isometry
\end{IEEEkeywords}

\section{Introduction}

I wish you the best of success.
%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
%for IEEE journal papers produced under \LaTeX\ using
%IEEEtran.cls version 1.8b and later.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

\section{Conclusion}
The conclusion goes here.

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

\section{Proof of the First Zonklar Equation}
Appendix two text goes here.

\section*{Acknowledgment}

The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

\end{document}

### 2021-06-05 treatise-pdflatex/1_introduction.tex
Import bibliography for article

@@
 
-Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
+Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite {ALS14}, which reduces the number of paths, and it is now that a recent development called compressive sensing may help.
 

### 2021-06-06 article/main.tex
Recover history

@@
 \documentclass[journal]{IEEEtran}
+
+\usepackage [utf8] {inputenc}
+\usepackage [english] {babel}
+\usepackage [final] {microtype}
+\usepackage {graphicx}
+\usepackage {csquotes}
+\usepackage {amssymb}
+\usepackage {amsmath}
+\usepackage {amsfonts}
+\usepackage {mathtools}
+\usepackage {float}
+\usepackage {hyperref}
+\usepackage {listingsutf8}
+\usepackage{chngcntr}
+
+\renewcommand {\a} {\alpha}
+\renewcommand {\b} {\beta}
+\newcommand {\g} {\gamma}
+\newcommand {\G} {\Gamma}
+\newcommand {\h} {\eta}
+\renewcommand {\d} {\delta}
+\newcommand {\e} {\varepsilon}
+\newcommand {\f} {\varphi}
+\renewcommand {\l} {\lambda}
+\newcommand {\s} {\sigma}
+\renewcommand {\i} {\iota}
+\renewcommand {\th} {\vartheta}
+\newcommand {\z} {\zeta}
+\renewcommand {\O} {\Omega}
+\renewcommand {\o} {\omega}
+\newcommand {\D} {\cdot}
+\newcommand {\Adj} {\dagger}
+\newcommand {\Tr} {\intercal}
+
+\newcommand {\m} [1] {\( #1 \)}
+\newcommand {\V} [1] {\underline {#1}}
+\newcommand {\M} [1] {\underline {\underline {#1}}}
+\newcommand {\T} [1] {\tilde {#1}}
+\newcommand {\RB} [1] {\left( #1 \right)}
+\newcommand {\SB} [1] {\left[ #1 \right]}
+\newcommand {\CB} [1] {\left\{ #1 \right\}}
+\newcommand {\DB} [1] {\left[ \! \left[ #1 \right] \! \right]}
+\newcommand {\Fl} [1] {\left \lfloor #1 \right \rfloor}
+\newcommand {\Cl} [1] {\left \lfloor #1 \right \rfloor}
+\newcommand {\Nm} [1] {\left \vert #1 \right \vert}
+\newcommand {\VNm} [1] {\left \Vert #1 \right \Vert}
+\newcommand {\R} [1] {\sqrt {#1}}
+\newcommand {\Min} [1] {\underset {#1} {\mathrm {min}}\;}
+\newcommand {\IP} [1] {\left \langle #1 \right \rangle}
+\newcommand {\Stack} [1] {\startsubstack #1 \stopsubstack}
+\newcommand {\DispNum} [2] {
+   \begin {align}
+      \label {#1}
+      #2
+   \end {align}
+}
+\newcommand {\Disp} [1] {
+   \begin {align*}
+      #1
+   \end {align*}
+}
+\newcounter {result}
+\newcommand {\Result} [2] {
+   \par
+   \refstepcounter {result}
+   \textbf {\theresult \; #1} \par
+   #2 \par
+   \hfill $\blacksquare$ \par
+}
 
@@
 
-I wish you the best of success.
-%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-%for IEEE journal papers produced under \LaTeX\ using
-%IEEEtran.cls version 1.8b and later.
+\subsection {Background}
 
-\hfill mds
+Multiple-input multiple-output (MIMO) communication systems will be part of the 5G specification.
+With a large number of antennae on both transmitter and receiver ends, MIMO is expected to provide a large signal gain.
+Parallel and redundant transmission of data improves the error-correcting ability, and beamforming improves the signal level.
+The millimeter wave (mm-wave) is adopted, since its smaller wavelength (and thus higher frequency) makes wider bands available.
+Moreover the antennae may be closer-spaced, allowing us to increase their number \cite {RSM13}.
+However, because of a larger antennae array and of larger noise corruption in higher frequency, estimation of MIMO channel state information gives rise to higher complexity, and hence higher hardware overhead and power consumption.
+Indeed, RF chains are more expensive and power-consuming, so there is growing attention on hybrid beamforming, where there are not fewer RF chain than the antennae.
 
-\hfill August 26, 2015
+If we consider a slow varying MIMO channel for simplicity, in terms of a channel representation, to estimate the channel is to determine the parameters of the representation.
+It amounts to invert a linear system whose dimension is the number of antennae, for which conventional training-based algorithms are not very effective.
 
-\subsection{Subsection Heading Here}
-Subsection text here.
+Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite {ALS14}, which reduces the number of paths, and compressive sensing techniques may be used.
+Generally speaking, compressive sensing aims to reconstruct an underdetermined linear system, when the sparsity of solution guarantees successful recovery for most cases.
+In our settings for hybrid beamforming structure, a way of generating the sensing matrix and pilot vectors in the estimation stage has to be devised and justified.
+
+Compressive sensing approaches can be divided into two categories, the convex programming approach and the greedy approach \cite {RDD18}.
+We will discuss one from each in more detail: Dantzig Selector and Orthogonal Matching Pursuit.
+
+Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
+Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response,
+and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.
+However, there seems to be no work by now which addresses the constraint of hybrid beamforming.
+
+Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
+In fact, it can be shown that Lasso and DS have similar behavior \cite {AsR10}.
+Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite {LLL17}.
+Destino, Juntti, and Nagaraj used an adaptive Lasso \cite {DJN15}, and Vlachos, Alexandropoulos, and Thompson \cite {VAT19} used Lasso on hybrid beamforming with an additional random spatial sampling device.
+Both Destino et al and Vlachos et al optimize formulate an algorithm to jointly find the channel and the sensing matrix, which can result in high complexity.
+
+OMP has since been commonly used for channel estimation.
+Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
+Hu, Wang, and He \cite {HWH13} applied OMP to estimate path delay of OFDM subcarriers.
+Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix;
+the analog stage is a Fourier matrix, and the digital stage consists of a collection of columns vectors of a unitary matrix.
+Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite {GDW15}.
+
+Performance guarantee of OMP is also studied on various conditions.
+Cai, Wang, and Xu \cite {CWX10} gave a new bound on performance of OMP under assumption of low coherence of columns.
+Cai and Wang \cite {CaW11} extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite {BEE10} followed up and refined their bounds, concluding that OMP is better for low SNR scenario, and DS is better for high SNR.
+
+\subsection {Contribution}
+
+Due to the constraint of hybrid structure, the designs which use fully digital beamforming cannot be directly applied, and the designs which use only analog beamforming might not be optimal.
+Indeed, if DS is shown to be optimal \cite {CaT07}, then if we can overcome the problem of complexity among other difficulties, it may turn out to outperform greedy methods, and is even necessary for less ideal situations.
+
+In this treatise, we consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
+We shall generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
+To the best of our knowledge, the sensing matrix with i.i.d.\ entries in both analog and digital stages has not been discussed on the literature.
+We shall see that in our proposed method, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
+for which we give a quantitative bound, holding for high probability, on the expected error norm.
+Numerical results show that DS is superior to other methods for our problem.
+Since DS is more accurate, it can be used when the sample is less sufficient and the noise level is higher, where it might be the case that only DS can recover successfully.
+Considering its higher complexity, we remark that it can be cast as a linear program, and the basis pursuit denoising form may be used.
+
+It appears that, for a given number of sampling, DS recovers better than OMP, except perhaps in high noise scenario.
+Moreover, our setting is more general than Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} with only an analog combiner,
+and our random generation of sensing matrix is simpler than Lee, Gil, and Lee \cite {LGL16},
+and we do not rely on additional assumptions on sparsity as in Gao, Dai, and Wang \cite {GDW15}.
+
+Our work is also an improvement to Bajwa et.\ al.\ \cite {BHS10}.
+First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
+Second, with the further constraint of hybrid beamforming, the channel matrix is downsampled, it is unclear whether their guarantee for successful signal recovery is still valid.
+Third, generating random sequences can lead to high complexity \cite {LGL16}, and we instead use random beamforming matrices.
+
+In addition, it seems that with the same threshold, DS recovers better than Lasso, except perhaps in low noise scenario.
+Again, our proposed method is more general than Lian, Liu and Lau \cite {LLL17} with only an analog combiner,
+and our sensing matrix is generated more simply than in Destino, Juntti, and Nagaraj \cite {DJN15},
+and we do not require special devices as in Vlachos, Alexandropoulos, and Thompson \cite {VAT19}.
+Overall, it is clear that DS leads to a relatively better regularization than OMP and Lasso.
+
+\section{Configuration}
 
 \section{Conclusion}
-The conclusion goes here.
+
+The treatise aims to answer the problem of effective estimating a MIMO mm-wave channel by exploiting its sparsity.
+To do so, we apply the Dantzig Selector (DS), by exploiting the sparsity in the spatial frequency domain, and justified the restricted isometry of the effective beamforming matrix.
+We then prove quantitatively that the expected error norm is bounded for overwhelming probability.
+We also suggest several ways of reducing the complexity without losing much performance.
+Simulation is done, and we see that DS indeed outperforms other methods in most datasets.
+
+Since we have RIP, a whole series of compressive sensing techniques become possible.
+But moreover, we corroborate the prediction that DS gives better regularization, and it may extract more information than other methods do when the sampling rate is low.
+In particular, when the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
+Therefore, one may use DS for sake of higher precision, or with limited RF chains and fewer stages of estimation, for example, in the ultra reliable or low latency scenario.
 
@@
 
-The authors would like to thank...
+The authors would like to thank the heaven.
 
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
+\begin{thebibliography}{30}
+\bibitem{RSM13}
+T.
+S.
+Rappaport, S.
+Sun, R.
+Mayzus, H.
+Zhao, Y.
+Azar, K.
+Wang, G.
+N.
+Wong, J.
+K.
+Schulz, M.
+Samimi, and F.
+Gutierrez, “Millimeter wave mobile communications for 5g cellular: It will work!” IEEE access, vol.
+1, pp.
+335–349, 2013.
 
-\begin{thebibliography}{1}
+\bibitem{RDD18}
+M. Rani, S. B. Dhok, and R. Deshmukh, “A systematic review of compressive sensing: Concepts, implementations and applications,” IEEE Access, vol. 6, pp. 4875–4894, 2018.
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+\bibitem{CaT05}
+E. J. Candès and T. Tao, “Decoding by linear programming,” IEEE Transactions on Information Theory, vol. 51, no. 12, p. 4203, 2005.
+
+\bibitem{CaT07}
+E. Candès and T. Tao, “The dantzig selector: Statistical estimation when p is much larger than n,” The annals of Statistics, vol. 35, no. 6, pp. 2313–2351, 2007.
+
+\bibitem{CaR05}
+E. Candès and J. Romberg, `11-magic: Recovery of sparse signals via convex programming. retrieved from , 2005.
+
+\bibitem{BDD08}
+[6] R. Baraniuk, M. Davenport, R. DeVore, and M. Wakin, “A simple proof of the restricted isometry property for random matrices,” Constructive Approximation, vol. 28, no. 3, pp. 253–263, 2008.
+
+\bibitem{BHS10}
+W. U. Bajwa, J. Haupt, A. M. Sayeed, and R. Nowak, “Compressed channel sensing: A new approach to estimating sparse multipath channels,” Proceedings of the IEEE, vol. 98, no. 6, pp. 1058–1076, 2010.
+
+\bibitem{BHR08}
+W. U. Bajwa, J. Haupt, G. Raz, and R. Nowak, “Compressed channel sensing,” 2008 42nd Annual Conference on Information Sciences and Systems, pp. 5–10, 2008.
+
+\bibitem{AsR10}
+M. S. Asif and J. Romberg, “On the lasso and dantzig selector equivalence,” 2010 44th Annual Conference on Information Sciences and Systems (CISS), pp. 1–6, 2010.
+
+\bibitem{LLL17}
+L. Lian, A. Liu, and V. K. Lau, “Optimal-tuned weighted lasso for massive mimo channel estimation with limited rf chains,” IEEE Global Communications Conference, pp. 1–6, 2017.
+
+\bibitem{DJN15}
+G.
+Destino, M.
+Juntti, and S.
+Nagaraj, “Leveraging sparsity into massive mimo channel estimation with the adaptive-lasso,” IEEE Global Conference on Signal and Information Processing (GlobalSIP), pp.
+166–170, 2015.
+
+\bibitem{VAT19}
+E.
+Vlachos, G.
+C.
+Alexandropoulos, and J.
+Thompson, “Wideband mimo channel estimation for hybrid beamforming millimeter wave systems via random spatial sampling,” IEEE Journal of Selected Topics in Signal Processing, vol.
+13, no.
+5, pp.
+1136–1150, 2019.
+
+\bibitem{TrG07a}
+J. A. Tropp and A. C. Gilbert, “Signal recovery from random measurements via orthogonal matching pursuit,” IEEE Transactions on information theory, vol. 53, no. 12, pp. 4655–4666, 2007.
+
+\bibitem{TrG07b}
+J. A. Tropp and A. C. Gilbert, “Signal recovery from random measurements via orthogonal match-
+ing pursuit: The gaussian case,” 2007.
+
+\bibitem{ALH15}
+A.
+Alkhateeb, G.
+Leus, and R.
+W.
+Heath, “Compressed sensing based multi-user millimeter wave systems: How many measurements are needed?” 2015 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), pp.
+2909–2913, 2015.
+
+\bibitem{HWH13}
+D. Hu, X. Wang, and L. He, “A new sparse channel estimation and tracking method for time-varying ofdm systems,” IEEE Transactions on Vehicular Technology, vol. 62, no. 9, pp. 4648–4653, 2013.
+
+\bibitem{LGL16}
+J.
+Lee, G.-T.
+Gil, and Y.
+H.
+Lee, “Channel estimation via orthogonal matching pursuit for hybrid mimo systems in millimeter wave communications,” IEEE Transactions on Communications, vol.
+64, no.
+6, pp.
+2370–2386, 2016.
+
+\bibitem{GDW15}
+Z.
+Gao, L.
+Dai, Z.
+Wang, and S.
+Chen, “Spatially common sparsity based adaptive channel estimation and feedback for fdd massive mimo,” IEEE Transactions on Signal Processing, vol.
+63, no.
+23, pp.
+6169–6183, 2015.
+
+\bibitem{CWX10}
+T. T. Cai, L. Wang, and G. Xu, “Stable recovery of sparse signals and an oracle inequality,” IEEE Transactions on Information Theory, vol. 56, no. 7, pp. 3516–3522, 2010.
+
+\bibitem{CaW11}
+T. T. Cai and L. Wang, “Orthogonal matching pursuit for sparse signal recovery with noise,” Information Theory, IEEE Transactions on, 2011.
+
+\bibitem{BEE10}
+Z.
+Ben-Haim, Y.
+C.
+Eldar, and M.
+Elad, “Coherence-based performance guarantees for estimating a sparse vector under random noise,” IEEE Transactions on Signal Processing, vol.
+58, no.
+10, pp.
+5030–5043, 2010.
+
+\bibitem{ALS14}
+M.
+R.
+Akdeniz, Y.
+Liu, M.
+K.
+Samimi, S.
+Sun, S.
+Rangan, T.
+S.
+Rappaport, and E.
+Erkip, “Millimeter wave channel modeling and cellular capacity evaluation,” IEEE journal on selected areas in communications, vol.
+32, no.
+6, pp.
+1164–1179, 2014.
+
+\bibitem{LaM00}
+B. Laurent and P. Massart, “Adaptive estimation of a quadratic functional by model selection,” Annals of Statistics, pp. 1302–1338, 2000.
+
+\bibitem{KlM17}
+B. Klartag and E. Milman, Geometric Aspects of Functional Analysis. Springer, 2017.
+
+\bibitem{BoV04}
+S. Boyd and L. Vandenberghe, Convex optimization. Cambridge U. press, 2004.
+
+\bibitem{FrS07}
+M. P. Friedlander and M. A. Saunders, “Discussion: The dantzig selector: Statistical estimation when p is much larger than n,” The Annals of Statistics, vol. 35, no. 6, pp. 2385–2391, 2007.
 

### 2021-06-06 article/main.tex
Copy selected figures for article

@@
 \usepackage [final] {microtype}
-\usepackage {graphicx}
-\usepackage {csquotes}
 \usepackage {amssymb}
@@
 \usepackage {amsfonts}
+\usepackage {graphicx}
+\usepackage {dblfloatfix}
+\usepackage {csquotes}
 \usepackage {mathtools}
@@
 \newcommand {\Stack} [1] {\startsubstack #1 \stopsubstack}
-\newcommand {\DispNum} [2] {
-   \begin {align}
-      \label {#1}
-      #2
-   \end {align}
-}
 \newcommand {\Disp} [1] {
@@
    \end {align*}
-}
-\newcounter {result}
-\newcommand {\Result} [2] {
-   \par
-   \refstepcounter {result}
-   \textbf {\theresult \; #1} \par
-   #2 \par
-   \hfill $\blacksquare$ \par
 }
@@
 
-\author{Tzu-Yu Jeng
+\author{Tzu-Yu Jeng \\
         Hsuan-Jung Su%
@@
 
-We consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
+We consider a single user, hybrid structure with a uniform linear array with both precoders and combiners on each side.
 We generate random beamforming matrices and use Dantzig Selector to estimate the channel in the space frequency domain.
@@
 \end{IEEEkeywords}
+
+\begin {figure*} [!b]
+\centering
+\includegraphics [width = \textwidth] {system.png}
+\caption {Schematic diagram of the hybrid beamforming system we consider.}
+\end {figure*}
 
@@
 It amounts to invert a linear system whose dimension is the number of antennae, for which conventional training-based algorithms are not very effective.
-
 Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite {ALS14}, which reduces the number of paths, and compressive sensing techniques may be used.
@@
 
+\subsection {Literature}
+
 Compressive sensing approaches can be divided into two categories, the convex programming approach and the greedy approach \cite {RDD18}.
 We will discuss one from each in more detail: Dantzig Selector and Orthogonal Matching Pursuit.
+For the the convex programming approach, Dantzig Selector (DS) is one of the earlier method, and it recovers the sparse signal with expected error norm bounded with overwhelming probability, and near optimality \cite {CaT07}.
+DS is an minimization problem on \m {\ell_1}-norm, with \m {\ell_\infty}-constraint, which may be recast as a linear program, so that techniques from convex optimization may be used.
+For our purpose in MIMO channel estimation, physical evidences suggest that mm-wave channels are sparse in the number of paths.
+Bajwa et.\ al.\ \cite {BHS10} used DS to estimate the time-dependent single-antenna channel response,
+and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.
+Some later results show that Least absolute shrinkage and selection operator (Lasso) and DS have similar behavior \cite {AsR10}.
+Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite {LLL17};
+Destino, Juntti, and Nagaraj used an adaptive Lasso \cite {DJN15};
+Vlachos, Alexandropoulos, and Thompson \cite {VAT19} used Lasso on hybrid beamforming with an additional random spatial sampling device.
+These formulations rely on joint optimization on the estimated channel and the sensing matrix, which can result in high complexity.
 
-Back to our problem of MIMO channel estimation, recall that, luckily, physical evidences suggest that mm-wave channels are sparse in the number of paths.
-Bajwa et.\ al.\ \cite {BHS10} used DS, where they argued that if the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, DS may be applied to estimate the time-dependent single-antenna channel response,
-and in the accompanying note \cite {BHR08} they justified that \m {X} has RIP for overwhelming probability.
-However, there seems to be no work by now which addresses the constraint of hybrid beamforming.
-
-Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
-In fact, it can be shown that Lasso and DS have similar behavior \cite {AsR10}.
-Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite {LLL17}.
-Destino, Juntti, and Nagaraj used an adaptive Lasso \cite {DJN15}, and Vlachos, Alexandropoulos, and Thompson \cite {VAT19} used Lasso on hybrid beamforming with an additional random spatial sampling device.
-Both Destino et al and Vlachos et al optimize formulate an algorithm to jointly find the channel and the sensing matrix, which can result in high complexity.
-
-OMP has since been commonly used for channel estimation.
+On the other hand, OMP has since been commonly used for channel estimation.
 Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
 Hu, Wang, and He \cite {HWH13} applied OMP to estimate path delay of OFDM subcarriers.
-Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix;
-the analog stage is a Fourier matrix, and the digital stage consists of a collection of columns vectors of a unitary matrix.
-Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite {GDW15}.
-
-Performance guarantee of OMP is also studied on various conditions.
-Cai, Wang, and Xu \cite {CWX10} gave a new bound on performance of OMP under assumption of low coherence of columns.
-Cai and Wang \cite {CaW11} extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite {BEE10} followed up and refined their bounds, concluding that OMP is better for low SNR scenario, and DS is better for high SNR.
+Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix.
+Gao, Dai, and Wang \cite {GDW15} proposed a variant of OMP which there is the assumption of spatially common sparsity.
+For the performance guarantee of OMP, Cai, Wang, and Xu \cite {CWX10} gave a new bound on performance of OMP under assumption of low coherence of columns.
+Cai and Wang \cite {CaW11} extended the study to DS and other convex programs for sparse recovery, and Ben-Haim et.\ al.\ \cite {BEE10} refined their bounds, concluding that OMP is better for low SNR scenario, and DS is better for high SNR.
 
@@
 
-\section{Configuration}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\section{System model}
+
+\subsection {Channel model}
+
+For simplicity we suppose uniform linear arrays, for which the response would be,
+%
+\Disp {
+\V {a} \SB {\psi', N}
+= \frac {1} {\R {N}} \sum_{n_h=0}^{N-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
+\in \mathbb {C} ^ {N} 
+}
+
+And consider the virtual representation of the MIMO channel, \cite {ALS14},
+%
+\Disp {
+\M {H}
+=\sum_{l=0} ^{L-1}
+\a_l
+\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l', N_{H,r}}
+\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l', N_{H,t}}^\dagger 
+}
+%
+The physical meaning of \m {\f_l'} is the \m {l}-th angle of incidence of departure electronic wave, and \m {\th_l'}, the \m {l}-th angle of arrival wave, and \m {d_{\mathrm {arr}}} is the distance between two adjacent antennae.
+
+\subsection {System model}
+
+We consider hybrid beamforming at both the transmitter and receiver ends, as shown in Figure 2.
+Each end consists of both digital and analog precoders and combiners.
+In the transmitter end, there are (seeing towards the receiver end), the digital precoder \m {\M {F} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog precoder \m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_B}}.
+Similarly, in the receiver end, there are (seeing towards the transmitter end) the digital combiner \m {\M {W} _B \in \mathbb {C} ^{N_B \D N_B}} and the analog combiner \m {\M {W} _R \in \mathbb {C} ^{N_B \D N_{H,r}}}.
+Recall that analog precoders may only have values of unity magnitude.
+%
+\Disp {
+\Nm {\RB {\M {F} _R} _{\SB {n_H, n_{R,t}}}}
+= &1, \\
+%
+\Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
+= &1,
+}
+%
+where we assume \m {N_{H,t}, N_{H,r} \gg N_B}.
+
+Since we restrict our discussion to a short interval of time, the noise term may be simply taken as a matrix \m {\M {Z} \in \mathbb {C} ^{N_B \D N_B}} with each entry being i.i.d.\ standard normal.
+Let us introduce the effective channel
+%
+\Disp {
+\M {Y}
+:=\M {W} _B \M {W} _R \RB {\M {H} \M {F} _R \M {F} _B +\M {Z}} 
+}
+%
+Our task then amounts to recovering \m {\M {H}}, and generating \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.
+
+\subsection{Proposed method}
+
+Let vec stand for vectorization of matrices along each column, and \m {\otimes} for Kronecker product.
+Then it is more appealing to write
+\Disp {
+\V {h}
+:= &\mathrm {vec} \SB {\M {H}} \\
+\V {y}
+:= &\mathrm {vec} \SB {\M {Y}} \\
+\V {z}
+:= &\mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}} \\
+\M {Q}
+:= &\RB {\M {F} _B^\intercal \M {F} _R^\Tr} \otimes \RB {\M {W} _B \M {W} _R} \\
+}
+to formulate the problem as a linear system:
+\Disp {
+\V {y}
+=\M {Q} \V {h} +\V {z} 
+}
+
+At this stage, it is not obvious that \m {\V {h}} must be sparse, so we apply discrete Fourier transform matrix \m {\M {K}} on both sides.
+Indeed, if we write
+\Disp {
+\M {G}
+=\M {K}^\dagger _r \M {H} \M {K} _t
+}
+then
+\Disp {
+\M {Y}
+=\M {W} _B \M {W} _R \M {K} _r \D \M {G} \D \M {K}^\dagger _t \M {F} _R \M {F} _B
++\M {W} _B \M {W} _R \M {Z}
+}
+Now, set for brevity
+\Disp {
+\M {P}
+:=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast _t} \otimes \RB {\M {W} _B \M {W} _R \M {K} _r}
+}
+and
+\Disp {
+\V {g}
+:= \mathrm {vec} \SB {\M {G}}
+}
+accordingly
+\Disp {
+\V {y}
+=\M {P} \V {g} +\V {z} 
+}
+
+In short, our plan becomes
+
+\begin {itemize}
+\item Let \m {\g_{\mathrm {DS}} \geq 0} be given.
+\item Input \m {\M {F} _B \in \mathbb {C} ^{N_R \D N_B}},
+\m {\M {F} _R \in \mathbb {C} ^{N_{H,t} \D N_R}},
+\m {\M {W} _R \in \mathbb {C} ^{N_R \D N_{H,r}}},
+\m {\M {W} _B \in \mathbb {C} ^{N_B \D N_R}},
+and \m {\M {Y} \in \mathbb {C} ^{N_B \D N_B}}.
+\item Find \m {\M {P} \in \mathbb {C} ^{N_B ^2 \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \mathbb {C} ^{N_B ^2}} as in above.
+\item Compute the convex program
+\Disp {
+\hat {\V {g}}
+\leftarrow \begin {cases}
+\Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}} & \VNm {\V {g}'} _1 \\
+\mathrm {subject} \; \mathrm {to} \quad & \VNm {\M {P}^\dagger \RB {\V {y} -\M {P} \V {g}'}} _\infty \leq \g_{\mathrm {DS}} \\
+\end {cases} 
+}
+\item Convert \m {\hat {\V {g}}} back to the space domain, namely
+\Disp {
+\hat {\M {G}}
+\leftarrow \mathrm {vec}^{-1} \SB {\hat {\V {g}}} 
+}
+\item Recover the estimated \m {\hat {\M {H}}}, as
+\Disp {
+\hat {\M {H}}
+\leftarrow \M {K} _r \hat {\M {G}} \M {K}^\dagger _t
+}
+\item Output \m {\hat {\M {H}}}.
+\end {itemize}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\section{Error Analysis}
+
+\subsection {Sparsity of channel}
+
+To simplify expressions, define
+%
+\Disp {
+\f_l
+= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \f_l'
+  \; \mathrm {mod}\; \RB {2\pi} \\
+%
+\th_l
+= &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
+  \; \mathrm {mod}\; \RB {2\pi} 
+}
+
+\textbf {Proposition}
+Let \m {\f} be given.
+Then, for any random instance of \m {\f},
+%
+\Disp {
+\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
+\leq \frac {2} {\pi} \log N 
+}
+
+\textbf {Proposition}
+The bound
+%
+\Disp {
+\VNm {\M {g} _{\SB{\mathcal {C}}}} _1
+\leq \frac {1} {3} L \RB {\log N_{H,t} + \log N_{H,r}} ^2
+}
+%
+holds for probability \m {p}, with
+%
+\Disp {
+1 -p
+\leq 2 \exp \SB {- \frac {9L} {\pi}} 
+}
+
+% % % % % % % % % % % % % % % %
+
+\subsection {Generating beamforming matrices}
+
+\textbf {Proposition}
+It holds that
+%
+\Disp {
+\Nm {\VNm {\M {F} _B \V {u}} _2 ^2 - 1}
+\geq \d_s 
+}
+for probability \m {p}, with
+\Disp {
+1 -p
+\leq 2 \mathsf {e} ^{-N_R \R {\d_s} /4} 
+}
+
+\textbf {Proposition}
+Suppose
+\Disp {
+N_R
+\geq \frac {s} {\d_s^2} \RB {\log s}^2 \log N_{H,t}
+}
+Then \m {\M {F}_R} (respectively \m {\M {W} _R}) has \m {\d_s} RIP for probability \m {p}, with
+\Disp {
+1 -p
+\leq \RB {\frac {\d_s} {N_{H,t} s}} ^{1/3} 
+}
+
+% % % % % % % % % % % % % % % %
+
+\subsection {Bound for expected error norm}
+
+The propositions below are taken from \cite {CaT07} and modified slightly in accordance to our settings, in addition to the generalization to complex vectors.
+%
+\textbf {Proposition}
+{
+\Disp {
+\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
+\leq \VNm {\V {d} _{\SB{\mathcal {A}}}} _1
++\VNm {\V {g} _{\SB{\mathcal {C}}}} _1 
+}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\section{Simulation}
+
+\subsection{Settings}
+
+Let \m {\mathcal {R}} denote the representation of complex vectors and matrices by real vectors and matrices.
+With definitions \m {\tilde {\V {y}} = \mathcal {R} \SB {\V {y}}},
+\m {\tilde {\V {g}} = \mathcal {R} \SB {\V {g}}},
+\m {\tilde {\M {P}} = \mathcal {R} \SB {\M {P}}},
+\m {\tilde {\V {z}} = \mathcal {R} \SB {\V {z}}},
+we have by construction
+%
+\Disp {
+\V {\tilde {y}}
+= \M {\tilde {P}} \V {\tilde {g}} +\V {\tilde {z}} 
+}
+
+To do convex optimization, we choose the Python library CVXPY.
+Considering its high complexity, there are several possible methods.
+First of all, it is equivalent to a linear program.
+Moreover, we may apply DS more than once to better estimate the nonzero components:
+We apply DS for the first time, and we extract largest components of the estimated vector, then apply Moore–Penrose inverse to get the returned solution, before scrambling back the resulting indices to the original ones.
+In doing such successive estimation, it is possible to have more than one stage of extraction \cite {CaT07}.
+
+Alternatively, in our investigation, we cast DS into a basis pursuit denoising form, for suitable \m {\l} \cite {BoV04} as below.
+
+\Disp {
+\Hat {\V {g}}
+\leftarrow \Min {\V {g}' \in \mathbb {C} ^{N_{H,t} N_{H,r}}}
+\RB {\VNm {\V {g}'} _1 + \l \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \V {g}'}} _\infty}
+}
+
+However, there is no simple way to determine the value of \m {\l} in advance.
+We have tried \m {\l = N_{H,t} N_{H,r} / \g_{\mathrm {DS}}} in the simulation.
+
+In addition to DS, we shall simulate OMP for three different stop conditions, Lasso, and Moore Penrose pseudoinverse (marked as LS which stands for least square).
+Each data point for DS and Lasso is repeated for \m {256} times, and taken arithmetic average.
+Other methods are repeated for more times: OMP for \m {4 \D 256} times, LS for \m {12 \D 256} times.
+
+Let \m {1/\s} be the SNR, which takes value starting with \m {2^{-2}}, and being multiplied by powers of \m {\R {2}}, for \m {6} values.
+We take \m {N_B} to be \m {2, 4, 6}, respectively.
+Three series of plots are simulated.
+The first series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 3 N_B}.
+The second series for \m {N_{H,t} = 3 N_B} and \m {N_{H,r} = 4 N_B}.
+The third series for \m {N_{H,t} = 4 N_B} and \m {N_{H,r} = 3 N_B}.
+Unfortunately, this is very far from achieving the ideal values for which our approximation is valid, and this may be part of the reason the result is not as successful as expected.
+
+Other parameters are fixed in these experiments.
+The number of grid of quantization of phase shifters is \m {16}.
+The number of paths \m {L = \lfloor \R {N_{H,t} N_{H,r}} / 2 \rfloor}.
+The ratio of the wavelength of carrier over the antenna spacing, \m {\l _{\mathrm {ant}} / d _{\mathrm {ant}} = 1 / 2}.
+
+Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
+We set \m {\g_{\mathrm {DS}} = 2 \log \RB {N_{H,t} N_{H,r}}} as suggested in \cite {CaT07}.
+For sake of comparison, \m {\g_{\mathrm {Lasso}} = \g_{\mathrm {DS}}}.
+
+For OMP, we consult Cai and Wang \cite {CaW11} for \m {\ell _2}-norm condition in their Theorem 7, and \m {\ell _\infty}-norm condition in their Theorem 8.
+We take \m {\h_{\mathrm {OMP}} = \R {2 \log \RB {N_{H,t} N_{H,r}}}} for \m {\infty}-norm condition, \m {\h_{\mathrm {OMP}} = \R {3 N_B}} for 2-norm condition.
+
+For Lasso, \m {\l _{\mathrm {Lasso}}} is also crucial to the performance, but cannot be obtained in advance.
+Thus, for sake of comparison, we set the same threshold for Lasso and DS.
+In view of the fact that \m {\VNm {g} _1 \leq 2 N_{H,t} N_{H,r} \VNm {g} _\infty}, we tentatively set \m {\l _{\mathrm {DS}} =  N_{H,t} N_{H,r} / \g _{\mathrm {DS}}} and \m {\l _{\mathrm {Lasso}} =  1 / \g _{\mathrm {Lasso}}}.
+Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.
+
+For performance metric, we also follow Lee, Gil, and Lee \cite {LGL16} to use
+\Disp {
+\tilde {\chi}
+=\RB {
+   \frac {\log_2 {\VNm {\V {h} -\hat {\V {h}}} _2}}
+   {\log_2 {\VNm {\V {h}}_2}}
+} _{\mathsf {avg}}, 
+}
+However, we remark that when \m {\VNm {\V {h}}_2} is small, this can blow up.
+Indeed, since we did not consider a definite a channel model in this treatise, \m {\T {\chi}} may not necessarily be proportional to the channel capacity.
+
+\subsection {Result}
+
+In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
+We fix \m {N_R = \RB {3/2} N_B}, and with \m {6} sets of observation.
+
+\begin {figure} [H]
+\includegraphics [width = 0.45 \textwidth]
+{error-small-more-tall-six-usual.png}
+\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, error.}
+\end {figure}
+
+\begin {figure} [H]
+\includegraphics [width = 0.45 \textwidth]
+{error-small-more-wide-six-usual.png}
+\caption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, error.}
+\end {figure}
+
+\begin {figure} [H]
+\includegraphics [width = 0.45 \textwidth]
+{error-medium-more-tall-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, error.}
+\end {figure}
+
+\begin {figure} [H]
+\includegraphics [width = 0.45 \textwidth]
+{error-medium-more-wide-six-usual.png}
+\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, error.}
+\end {figure}
+
+\begin {figure} [H]
+\includegraphics [width = 0.45 \textwidth]
+{error-big-more-tall-six-usual.png}
+\caption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, error.}
+\end {figure}
+
+\begin {figure} [H]
+\includegraphics [width = 0.45 \textwidth]
+{error-big-more-wide-six-usual.png}
+\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, error.}
+\end {figure}
+
+\subsection {Discussion}
+
+From the simulation, DS outperforms other methods in most of the datasets.
+With low noise, \m {\tilde {\chi} _{\mathrm {DS}} \approx \tilde {\chi} _{\mathrm {OMP}} \leq \tilde {\chi} _{\mathrm {Lasso}} \leq \tilde {\chi} _{\mathrm {LS}}},
+although sometimes \m {\tilde {\chi} _{\mathrm {DS}} \geq \tilde {\chi} _{\mathrm {OMP}}}.
+With high noise, \m {\tilde {\chi} _{\mathrm {DS}} \approx \tilde {\chi} _{\mathrm {Lasso}} \leq \tilde {\chi} _{\mathrm {OMP}} \leq \tilde {\chi} _{\mathrm {LS}}}.
+although sometimes \m {\tilde {\chi} _{\mathrm {DS}} \geq \tilde {\chi} _{\mathrm {Lasso}}}.
+LS is so much poorer that it is not a main contender.
+These trends is true with different number of stages, and with the case \m {N_B = N_R}.
+In general, we can say that overall, DS gives a better regularization for both low noise and high noise scenario, and in most cases, DS is even better than both of them.
+
+Differing thresholds does not to seem have much effect on OMP and DS.
+Meanwhile for Lasso, where a suitable threshold may improve the accuracy, but a excessively tight threshold may also result in a overfitting, and blowing up for high signal cases.
+Increasing the number of stages obviously improves the estimation for all methods.
+
+Unfortunately, we report that CVXPY sometimes gives overflowing values, some of them as large as \m {10^{11}}.
+This probably indicates some typical-looking output may in fact be unreliable.
+Therefore we have discarded outputs larger than a given threshold, for instance \m {10^4}, and simply return the answer to be a Moore–Penrose inverse.
+
+\m {\chi} is not shown in the figure, because the big O bound is much larger than \m {\tilde {\chi}}.
+It is possible that the nonsparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
+It is curious to see whether for very large \m {N_H}, whether \m {\tilde {\chi}} and \m {\chi} will be asymptotically close.
+
+\subsection {Complexity}
+
+We discuss the complexity of DS, Lasso, and OMP.
+Abbreviate \m {N_h = N_{H,t} N_{H,r}}.
+
+For DS, suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used \cite {BoV04}.
+For our case, that would be \m {\mathcal {O} \SB {4 N_h ^2 \D 8 N_h} = \mathcal {O} \SB {N_h ^3}}.
+
+Alternatively, suppose Newton method is used.
+Here, we have self-concordance for linear program \cite {BoV04}.
+Let \m {\V {g} _0} denote the starting value of \m {\V {g}'}, and \m {\V {g} ^{\star}} the the point of convergence.
+Then the number of Newton steps, which we take to be the complexity, is bounded by \cite {BoV04}
+\Disp {
+C_{\mathrm {Newton}}
+\propto \RB {\VNm {\V {g}_0 -\V {g} ^{\star}}_1
++ \log_2 \log_2 \frac {1} {\e}}
+}
+
+Assume that, at the start the iteration, the Moore–Penrose inverse is close to the initial value of \m {\V {g}_0}, namely
+%
+\Disp {
+\V {g}_0
+=\V {g}_{\mathrm {LS}}
+= \RB {\M {P} ^\dagger \M {P}} ^{-1} \M {P} ^\dagger \V {y} 
+}
+And suppose that, in view of restricted isometry, \m {\M {P}} has unity-normed, almost orthogonal columns, so that
+\m {\M {P} ^\dagger \M {P} \approx I _{N_h}}
+Moreover, assume that \m {\V {g} ^\star \approx \V {g}}.
+Then we simply have
+\Disp {
+C_{\mathrm {DS}}
+=\mathcal {O} \SB {N_h ^3} 
+}
+
+For OMP \cite {TrG07}, \m {C_{\mathrm {OMP}} =\mathcal {O} \SB {L \RB {\log N_h} ^2}}.
+
+For Lasso, it is equivalent to a quadratically constrained quadratic program, and there is not always a closed form for its complexity.
+However, Lasso and DS are equivalent in certain conditions \cite {AsR10}, and we may suppose here they have the same complexity.
+Alternatively, an argument similar to the above one for DS is valid for Lasso.
+Therefore we take \m {C_{\mathrm {Lasso}} =\mathcal {O} \SB {N_h ^3}}.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \begin{thebibliography}{30}
@@
 Samimi, and F.
-Gutierrez, “Millimeter wave mobile communications for 5g cellular: It will work!” IEEE access, vol.
+Gutierrez, “Millimeter wave mobile communications for 5g cellular: It will work!” \textit {IEEE access}, vol.
 1, pp.
@@
 \bibitem{RDD18}
-M. Rani, S. B. Dhok, and R. Deshmukh, “A systematic review of compressive sensing: Concepts, implementations and applications,” IEEE Access, vol. 6, pp. 4875–4894, 2018.
+M. Rani, S. B. Dhok, and R. Deshmukh, “A systematic review of compressive sensing: Concepts, implementations and applications,” \textit {IEEE Access}, vol. 6, pp. 4875–4894, 2018.
 
 \bibitem{CaT05}
-E. J. Candès and T. Tao, “Decoding by linear programming,” IEEE Transactions on Information Theory, vol. 51, no. 12, p. 4203, 2005.
+E. J. Candès and T. Tao, “Decoding by linear programming,” \textit {IEEE Transactions on Information Theory}, vol. 51, no. 12, p. 4203, 2005.
 
 \bibitem{CaT07}
-E. Candès and T. Tao, “The dantzig selector: Statistical estimation when p is much larger than n,” The annals of Statistics, vol. 35, no. 6, pp. 2313–2351, 2007.
-
-\bibitem{CaR05}
-E. Candès and J. Romberg, `11-magic: Recovery of sparse signals via convex programming. retrieved from , 2005.
+E. Candès and T. Tao, “The dantzig selector: Statistical estimation when p is much larger than n,” \textit {The annals of Statistics}, vol. 35, no. 6, pp. 2313–2351, 2007.
 
 \bibitem{BDD08}
-[6] R. Baraniuk, M. Davenport, R. DeVore, and M. Wakin, “A simple proof of the restricted isometry property for random matrices,” Constructive Approximation, vol. 28, no. 3, pp. 253–263, 2008.
+[6] R.
+Baraniuk, M.
+Davenport, R.
+DeVore, and M.
+Wakin, “A simple proof of the restricted isometry property for random matrices,” \textit {Constructive Approximation}, vol.
+28, no.
+3, pp.
+253–263, 2008.
 
 \bibitem{BHS10}
-W. U. Bajwa, J. Haupt, A. M. Sayeed, and R. Nowak, “Compressed channel sensing: A new approach to estimating sparse multipath channels,” Proceedings of the IEEE, vol. 98, no. 6, pp. 1058–1076, 2010.
+W.
+U.
+Bajwa, J.
+Haupt, A.
+M.
+Sayeed, and R.
+Nowak, “Compressed channel sensing: A new approach to estimating sparse multipath channels,” \textit {Proceedings of the IEEE}, vol.
+98, no.
+6, pp.
+1058–1076, 2010.
 
 \bibitem{BHR08}
-W. U. Bajwa, J. Haupt, G. Raz, and R. Nowak, “Compressed channel sensing,” 2008 42nd Annual Conference on Information Sciences and Systems, pp. 5–10, 2008.
+W. U. Bajwa, J. Haupt, G. Raz, and R. Nowak, “Compressed channel sensing,” 2008 \textit {42nd Annual Conference on Information Sciences and Systems}, pp. 5–10, 2008.
 
 \bibitem{AsR10}
-M. S. Asif and J. Romberg, “On the lasso and dantzig selector equivalence,” 2010 44th Annual Conference on Information Sciences and Systems (CISS), pp. 1–6, 2010.
+M. S. Asif and J. Romberg, “On the lasso and dantzig selector equivalence,” 2010 \textit {44th Annual Conference on Information Sciences and Systems} (CISS), pp. 1–6, 2010.
 
 \bibitem{LLL17}
-L. Lian, A. Liu, and V. K. Lau, “Optimal-tuned weighted lasso for massive mimo channel estimation with limited rf chains,” IEEE Global Communications Conference, pp. 1–6, 2017.
+L. Lian, A. Liu, and V. K. Lau, “Optimal-tuned weighted lasso for massive mimo channel estimation with limited rf chains,” \textit {IEEE Global Communications Conference}, pp. 1–6, 2017.
 
@@
 Juntti, and S.
-Nagaraj, “Leveraging sparsity into massive mimo channel estimation with the adaptive-lasso,” IEEE Global Conference on Signal and Information Processing (GlobalSIP), pp.
+Nagaraj, “Leveraging sparsity into massive mimo channel estimation with the adaptive-lasso,” \textit {IEEE Global Conference on Signal and Information Processing} (GlobalSIP), pp.
 166–170, 2015.
@@
 Alexandropoulos, and J.
-Thompson, “Wideband mimo channel estimation for hybrid beamforming millimeter wave systems via random spatial sampling,” IEEE Journal of Selected Topics in Signal Processing, vol.
+Thompson, “Wideband mimo channel estimation for hybrid beamforming millimeter wave systems via random spatial sampling,” \textit {IEEE Journal of Selected Topics in Signal Processing}, vol.
 13, no.
@@
 
-\bibitem{TrG07a}
-J. A. Tropp and A. C. Gilbert, “Signal recovery from random measurements via orthogonal matching pursuit,” IEEE Transactions on information theory, vol. 53, no. 12, pp. 4655–4666, 2007.
-
-\bibitem{TrG07b}
-J. A. Tropp and A. C. Gilbert, “Signal recovery from random measurements via orthogonal match-
-ing pursuit: The gaussian case,” 2007.
+\bibitem{TrG07}
+J. A. Tropp and A. C. Gilbert, “Signal recovery from random measurements via orthogonal matching pursuit,” \textit {IEEE Transactions on information theory}, vol. 53, no. 12, pp. 4655–4666, 2007.
 
@@
 W.
-Heath, “Compressed sensing based multi-user millimeter wave systems: How many measurements are needed?” 2015 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), pp.
+Heath, “Compressed sensing based multi-user millimeter wave systems: How many measurements are needed?” 2015 \textit {IEEE International Conference on Acoustics, Speech and Signal Processing} (ICASSP), pp.
 2909–2913, 2015.
@@
 \bibitem{HWH13}
-D. Hu, X. Wang, and L. He, “A new sparse channel estimation and tracking method for time-varying ofdm systems,” IEEE Transactions on Vehicular Technology, vol. 62, no. 9, pp. 4648–4653, 2013.
+D.
+Hu, X.
+Wang, and L.
+He, “A new sparse channel estimation and tracking method for time-varying ofdm systems,” \textit {IEEE Transactions on Vehicular Technology}, vol.
+62, no.
+9, pp.
+4648–4653, 2013.
 
@@
 H.
-Lee, “Channel estimation via orthogonal matching pursuit for hybrid mimo systems in millimeter wave communications,” IEEE Transactions on Communications, vol.
+Lee, “Channel estimation via orthogonal matching pursuit for hybrid mimo systems in millimeter wave communications,” \textit {IEEE Transactions on Communications}, vol.
 64, no.
@@
 Wang, and S.
-Chen, “Spatially common sparsity based adaptive channel estimation and feedback for fdd massive mimo,” IEEE Transactions on Signal Processing, vol.
+Chen, “Spatially common sparsity based adaptive channel estimation and feedback for fdd massive mimo,” \textit {IEEE Transactions on Signal Processing}, vol.
 63, no.
@@
 \bibitem{CWX10}
-T. T. Cai, L. Wang, and G. Xu, “Stable recovery of sparse signals and an oracle inequality,” IEEE Transactions on Information Theory, vol. 56, no. 7, pp. 3516–3522, 2010.
+T. T. Cai, L. Wang, and G. Xu, “Stable recovery of sparse signals and an oracle inequality,” \textit {IEEE Transactions on Information Theory}, vol. 56, no. 7, pp. 3516–3522, 2010.
 
 \bibitem{CaW11}
-T. T. Cai and L. Wang, “Orthogonal matching pursuit for sparse signal recovery with noise,” Information Theory, IEEE Transactions on, 2011.
+T. T. Cai and L. Wang, “Orthogonal matching pursuit for sparse signal recovery with noise,” \textit {IEEE Transactions on Information Theory}, 2011.
 
@@
 Eldar, and M.
-Elad, “Coherence-based performance guarantees for estimating a sparse vector under random noise,” IEEE Transactions on Signal Processing, vol.
+Elad, “Coherence-based performance guarantees for estimating a sparse vector under random noise,” \textit {IEEE Transactions on Signal Processing}, vol.
 58, no.
@@
 Rappaport, and E.
-Erkip, “Millimeter wave channel modeling and cellular capacity evaluation,” IEEE journal on selected areas in communications, vol.
+Erkip, “Millimeter wave channel modeling and cellular capacity evaluation,” \textit {IEEE journal on selected areas in communications}, vol.
 32, no.
@@
 \bibitem{LaM00}
-B. Laurent and P. Massart, “Adaptive estimation of a quadratic functional by model selection,” Annals of Statistics, pp. 1302–1338, 2000.
+B. Laurent and P. Massart, “Adaptive estimation of a quadratic functional by model selection,” \textit {Annals of Statistics}, pp. 1302–1338, 2000.
 
 \bibitem{KlM17}
-B. Klartag and E. Milman, Geometric Aspects of Functional Analysis. Springer, 2017.
+B. Klartag and E. Milman, \textit {Geometric Aspects of Functional Analysis}. Springer, 2017.
 
 \bibitem{BoV04}
-S. Boyd and L. Vandenberghe, Convex optimization. Cambridge U. press, 2004.
+S. Boyd and L. Vandenberghe, \textit {Convex optimization}. Cambridge U. press, 2004.
 
 \bibitem{FrS07}
-M. P. Friedlander and M. A. Saunders, “Discussion: The dantzig selector: Statistical estimation when p is much larger than n,” The Annals of Statistics, vol. 35, no. 6, pp. 2385–2391, 2007.
+M. P. Friedlander and M. A. Saunders, “Discussion: The dantzig selector: Statistical estimation when p is much larger than n,” \textit {The Annals of Statistics}, vol. 35, no. 6, pp. 2385–2391, 2007.
 

### 2021-06-06 treatise-pdflatex/4_simulation.tex
Copy selected figures for article

@@
 We can apply DS more than once to better estimate the nonzero components;
-let us call it the successive estimation \cite [CaT07].
+let us call it the successive estimation \cite {CaT07}.
 We apply DS for the first time, and we extract largest components of the estimated vector.
@@
 
-However, one must keep in mind that for OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix.
+However, one must keep in mind that for OMP, in Lee, Gil, and Lee \cite {LGL16}, a high-complexity nonconvex program is used to design the sensing matrix.
 Since we have here a low-complexity, random generation of beamforming matrices, a different design of sensing matrix may affect the performance of OMP.
@@
 
-For performance metric, we follow Lee, Gil, and Lee \cite [LGL16] to use
+For performance metric, we follow Lee, Gil, and Lee \cite {LGL16} to use
 \DispNum {h:h:lo:vg} {

### 2021-06-07 article/main.tex
Copy the proof in chap 3 into article

@@
 
+Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity level \m {S} be fixed.
+Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\mathcal {A}}}}, the largest-magnitude \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\mathcal {B}}}} the next \m {s} largest-magnitude components of \m {\V {g}}, and \m {\V {g} _{\SB{\mathcal {C}}}} are the components complement to \m {\V {g} _{\SB{\mathcal {A}}}}.
+For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\mathcal {A}}} =\IP {0,0,-4,0,8}}, \m {\V {g} _{\SB{\mathcal {B}}} =\IP {0,3,0,2,0}}, and \m {\V {g} _{\SB{\mathcal {C}}} =\IP {-1,3,0,2,0}}.
+In this section, the subscripts \m {\mathcal {A}, \mathcal {B}, \mathcal {C}} will bear analogous meaning.
+
+We hope that \m {\VNm {\V {g} _{\SB{\mathcal {C}}}} _1} is small.
+If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
+Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
+We define, similarly, \m {\V {a} _{\SB{\mathcal {A}}}} and \m {\V {a} _{\SB{\mathcal {C}}}}, with sparsity level \m {s} different from \m {S}.
+If \m {N} is large, we may forget for a moment that \m {s} is an integer.
+
 \subsection {Sparsity of channel}
@@
 
-\textbf {Proposition}
+\textbf {Proposition 1}
 Let \m {\f} be given.
@@
 
-\textbf {Proposition}
+To show this, introduce
+\Disp {
+\psi \SB {\f, n_H}
+:=\RB {
+   \f \; \mathrm {Mod}\; \frac {2\pi} {N}
+   + \RB {\frac {2 n_H} {N} + 1} \pi
+} \;
+\mathrm {mod}\; \RB {2\pi}
+- \pi 
+}
+Also define
+\Disp {
+\Nm {D \SB {\psi'}}
+:= &\frac {\Nm {\sin \SB {N \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \\
+\leq &B \SB {\psi'}
+:= \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \\
+}
+Then,
+\Disp {
+\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
+\leq \frac {1} {N}
+\VNm {
+\RB {
+   \sum_{n_H' =0}^{N -1}
+      B \SB {\psi \SB {\f, n_H'}}
+      \V {u} _{n_H'}
+} _{\SB{\mathcal {C}}}
+} _1
+}
+Or, if we drop \m {s},
+\Disp {
+\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
+\leq &\frac {1} {N} \D \frac {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \SB {\psi'} ^2 d \psi' \\
+= &\frac {48} {N \pi^3}
+\int _{s /N} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \\
+\leq &\frac {2} {\pi} \log N 
+}
+
+\textbf {Proposition 2}
 The bound
@@
 
-\textbf {Proposition}
+To investigate \m {\VNm {\M {F} _B \V {u}} _2} (respectively for \m {\M {W} _B}), we need a large deviation result for i.i.d.\ sum of chi-square random variables \cite {LaM00}, as below.
+
+\textbf {Proposition 3}
 It holds that
@@
 
-\textbf {Proposition}
+To investigate \m {\VNm {\M {F} _B \V {u}} _2} (respectively for \m {\M {W} _B}), we apply a bound for the failure probability of a DFT submatrix with \m {\d_s} RIP, in Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' \cite {KlM17}, and drop lower ordered terms as below,
+
+\textbf {Proposition 4}
 Suppose
@@
 
+Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {W}_B \M {W}_R} are \m {\d_s} RIP, it does appear (if we ignore the sparsity constraint) that \m {\M {P}} has approximately \m {2\d_s} RIP.
+However, it remain to show that their Kronecker product still has RIP.
+
+Nevertheless, notice that if angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}},
+\Disp {
+&\VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \notag \\
+= &\VNm {
+   \M {W} _B \M {W} _R \M {K} _r \M {U} \D
+   \mathrm {diag} \SB {\mathrm {abs} \SB {\V {d}'}} \D
+   \M {U} ^\dagger \M {K} _t ^\dagger \M {F} _R \M {F} _B} _2 \notag \\
+= &\VNm {
+   \M {W} _B \M {W} _R \M {K} _r \M {U}
+   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \D
+   \VNm {\M {F} _B ^\dagger \M {F} _R ^\dagger \M {K} _t \M {U}
+   \R {\mathrm {abs} \SB {\V {d}'}}} _2 \notag \\
+\eqsim &\VNm {\M {G}} _2 \RB {1 +2\d_s} 
+}
+Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}}.
+
 % % % % % % % % % % % % % % % %
@@
 
-The propositions below are taken from \cite {CaT07} and modified slightly in accordance to our settings, in addition to the generalization to complex vectors.
+Set for short \m {\V {d} = \hat {\V {g}} - \V {g}}.
+And for convenience, let \m {N_h = N_{H,t} N_{H,r}}.
 %
-\textbf {Proposition}
-{
+To bound \m {\VNm {\V {d}} _2}, we illustrate that \m {\V {g}} can be seen as sparse, and for that purpose we generously bound \m {\d_{S}} by \m {1}.
+We shall see below that it suffices to set
+\Disp {
+\g
+= \R {2 \log N_h} 
+}
+
+The propositions below are taken from \cite {CaT07} and modified slightly according to our settings.
+
+\textbf {Proposition 5}
 \Disp {
@@
 }
+
+\textbf {Proposition 6}
+\Disp {
+\VNm {\M {P}^\dagger \M {P} \V {d}} _\infty
+\leq 2 \R {2 \log N_h} 
+}
+for probability \m {p}, with
+\Disp {
+1 -p
+\leq N_h^{-1}.
+}
+
+\textbf {Proposition 7}
+\Disp {
+\VNm {\V {d}} _2
+\leq \VNm {\V {d} _{\SB {\mathcal {AB}}}} _2 + \frac {1} {\R {S}} \VNm {\V {d} _{\SB{\mathcal {C}}}} _1 
+}
+
+\textbf {Proposition 8}
+\Disp {
+\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
+\leq \frac {1} {1- \R{2} \d_{S}} \VNm {P _{\SB {\mathcal {AB}}}^\intercal P d} _2
++ \frac {\R{3} \d_{S}} {\RB {1- \R{2} \d_{S}} \R {S}} \VNm {d_{\SB{\mathcal {C}}}} _1 
+}
+
+Finally, we shall show the proposed bound.
+For simplicity, set \m {S = Ls^2}, thus \m {S =L \log N_h}.
+And, for concreteness, suppose \m {\d_S \leq \frac {1} {8}}.
+
+\textbf {Theorem 9}
+Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
+Then it holds that
+\Disp {
+\VNm {\V {d}} _2
+\eqsim \mathcal {O} \SB {\R {L} \R {\log N_h}^3} 
+}
+for probability \m {p}, with
+\Disp {
+1 -p
+\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_B /12}} 
+}
+
+To show this, by the definition of truncation, by \m {\ell_p} norm inequality, by Proposition 6,
+\Disp {
+\VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
+\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \notag \\
+\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \notag \\
+\leq &2.83 \R {L} \log N_h
+}
+By \m {\ell_p}-norm inequality, by the definition of truncation, by Proposition 8, and by above,
+\Disp {
+\VNm {\V {d} _{\SB{\mathcal {A}}}} _1
+\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \notag \\
+\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \notag \\
+\leq &3.44 L \R {\log N_h}^3
++0.262 \VNm {\V {d} _{\SB{\mathcal {C}}}} _1
+}
+Then, substituting this and Proposition 2 above into Proposition 5, we get
+\Disp {
+\VNm {\V {d} _{\SB{\mathcal {C}}}} _1
+\leq 5.12 L \RB {\log N_h}^2
+}
+Now Proposition 8 becomes
+\Disp {
+\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2
+\leq 3.44 \R {L} \log N_h + 1.35 \R {L} \R {\log N_h} ^3
+}
+Finally, by plugging \m {\VNm {\V {d} _{\SB{\mathcal {AB}}}} _2} and \m {\VNm {\V {d} _{\SB{\mathcal {C}}}} _1} into Proposition 7, we get
+\Disp {
+\VNm {\V {d}} _2
+\leq 4.79 \R {L} \R {\log N_h}^3
+}
+Therefore, we set \m {\chi = \R {L} \R {\log N_h}^3}, so that \m {\VNm {\V {d}} _2 = \mathcal {O} \RB {\chi}}, as claimed.
 
@@
 We discuss the complexity of DS, Lasso, and OMP.
-Abbreviate \m {N_h = N_{H,t} N_{H,r}}.
-
 For DS, suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used \cite {BoV04}.

### 2021-06-07 treatise-pdflatex/3_2_generating_beamforming_matrices.tex
Copy the proof in chap 3 into article

@@
 \Result
-{Theorem}
+{Proposition}
 {
@@
 \VNm {P} _2
-=\VNm {\M {F}_B^\intercal \M {F}_B^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 
+=\VNm {\M {F}_B^\Tr \M {F}_R^\Tr} _2 \VNm {\M {W}_B \M {W}_R} _2 
 }
-Since both \m {\M {F}_B^\intercal \M {F}_B^\Tr} and \m {\M {F}_B^\intercal \M {F}_B^\Tr} are \m {\d_s} RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s} RIP.
+Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {W}_B \M {W}_R} are \m {\d_s} RIP, it does appear, if we ignore for a moment the sparsity constraint, that \m {\M {P}} has approximately \m {2\d_s} RIP.
 However, it is doubtful to assume that their Kronecker product still has RIP.

### 2021-06-07 article/main.tex
Correct probability bound for digital beamforming

@@
 The bound
-%
 \Disp {
@@
 }
-%
 holds for probability \m {p}, with
-%
 \Disp {
@@
 }
+This is proved by using Proposition 1 with triangle inequality, and bound the sample mean by Hoeffding inequality.
 
@@
 
-To investigate \m {\VNm {\M {F} _B \V {u}} _2} (respectively for \m {\M {W} _B}), we need a large deviation result for i.i.d.\ sum of chi-square random variables \cite {LaM00}, as below.
+To investigate \m {\VNm {\M {F} _B \V {u}} _2} (respectively for \m {\M {W} _B}), for \m {\V {u}} is a unit vector, we need a large deviation result for i.i.d.\ sum of chi-square random variables \cite {LaM00}, as below.
 
@@
 
-Since both \m {\M {F}_B^\Tr \M {F}_B^\Tr} and \m {\M {W}_B \M {W}_R} are \m {\d_s} RIP, it does appear (if we ignore the sparsity constraint) that \m {\M {P}} has approximately \m {2\d_s} RIP.
+Since both \m {\M {F}_B^\Tr \M {F}_R^\Tr} and \m {\M {W}_B \M {W}_R} are \m {\d_s} RIP, it does appear (if we ignore the sparsity constraint) that \m {\M {P}} has approximately \m {2\d_s} RIP.
 However, it remain to show that their Kronecker product still has RIP.
@@
 1 -p
-\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_B /12}} 
+\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_R \R {\d_s} /4}} 
 }
@@
 Therefore, we set \m {\chi = \R {L} \R {\log N_h}^3}, so that \m {\VNm {\V {d}} _2 = \mathcal {O} \RB {\chi}}, as claimed.
+The failure probability is taken from Proposition 3.
 
@@
 
+First, complex numbers have to be recorded as the real and imaginary parts, to speed up calculation.
 Let \m {\mathcal {R}} denote the representation of complex vectors and matrices by real vectors and matrices.
@@
 
-\appendices
-\section{Proof of the First Zonklar Equation}
-Appendix one text goes here.
-
-\section{Proof of the First Zonklar Equation}
-Appendix two text goes here.
-
 \section*{Acknowledgment}

### 2021-06-07 treatise-context/3_2_generating_beamforming_matrices.tex
Correct probability bound for digital beamforming

@@
 %
-With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for overall failure probability.
+With substitution \m {\d_s =16x^2 /N_R^2}, the upper tail can be simplified with \m {x <N_R}, and we get the following bound for overall failure probability.
 

### 2021-06-08 article/main.tex
Use round brackets for functions

@@
 
+We use an underline like \m {\V {v}} for vectors, two underlines like \m {\M {M}} for matrices.
+A dagger \m {\dagger} stands for Hermitian, and \m {\intercal} for transpose.
+A subscript with brackets like \m {\M {M} _{\SB{1,2}}} is its corresponding entry.
+
 For simplicity we suppose uniform linear arrays, for which the response would be,
-%
 \Disp {
-\V {a} \SB {\psi', N}
+\V {a} \RB {\psi', N}
 = \frac {1} {\R {N}} \sum_{n_h=0}^{N-1} \mathsf {e} ^{\mathsf {i} n_h \psi'} \V {u} _{n_h}
@@
 }
-
 And consider the virtual representation of the MIMO channel, \cite {ALS14},
-%
 \Disp {
@@
 \a_l
-\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l', N_{H,r}}
-\V {a} \SB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l', N_{H,t}}^\dagger 
+\V {a} \RB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \f_l', N_{H,r}}
+\V {a} \RB { 2\pi \frac {d_{\mathrm {arr}}} {\l _{\mathrm {arr}}} \sin \th_l', N_{H,t}}^\dagger 
 }
-%
 The physical meaning of \m {\f_l'} is the \m {l}-th angle of incidence of departure electronic wave, and \m {\th_l'}, the \m {l}-th angle of arrival wave, and \m {d_{\mathrm {arr}}} is the distance between two adjacent antennae.
@@
 Recall that analog precoders may only have values of unity magnitude.
-%
 \Disp {
@@
 = &1, \\
-%
 \Nm {\RB {\M {W} _R} _{\SB {n_{R,r}, n_H}}}
@@
 }
-%
 where we assume \m {N_{H,t}, N_{H,r} \gg N_B}.
@@
 Let us introduce the effective channel
-%
 \Disp {
@@
 }
-%
 Our task then amounts to recovering \m {\M {H}}, and generating \m {\M {W} _R}, \m {\M {W} _B}, \m {\M {F} _R}, and \m {\M {F} _B}.
@@
 \V {h}
-:= &\mathrm {vec} \SB {\M {H}} \\
+:= &\mathrm {vec} \RB {\M {H}} \\
 \V {y}
-:= &\mathrm {vec} \SB {\M {Y}} \\
+:= &\mathrm {vec} \RB {\M {Y}} \\
 \V {z}
-:= &\mathrm {vec} \SB {\M {W} _B \M {W} _R \M {Z}} \\
+:= &\mathrm {vec} \RB {\M {W} _B \M {W} _R \M {Z}} \\
 \M {Q}
@@
 }
-Now, set for brevity
+Now, set
 \Disp {
 \M {P}
-:=\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast _t} \otimes \RB {\M {W} _B \M {W} _R \M {K} _r}
+:= &\RB {\M {F} _B^\intercal \M {F} _R^\intercal \M {K}^\ast _t} \otimes \RB {\M {W} _B \M {W} _R \M {K} _r} \\
+\V {g}
+:= &\mathrm {vec} \RB {\M {G}}
 }
-and
-\Disp {
-\V {g}
-:= \mathrm {vec} \SB {\M {G}}
-}
-accordingly
+Accordingly
 \Disp {
@@
 
-In short, our plan becomes
-
+In short, our algorithm can be summarized more succinctly as below.
 \begin {itemize}
@@
 \hat {\M {G}}
-\leftarrow \mathrm {vec}^{-1} \SB {\hat {\V {g}}} 
+\leftarrow \mathrm {vec}^{-1} \RB {\hat {\V {g}}} 
 }
@@
 To simplify expressions, define
-%
 \Disp {
@@
   \; \mathrm {mod}\; \RB {2\pi} \\
-%
 \th_l
 = &2\pi \frac {d_{\mathrm {arr}}} {\l_{\mathrm {arr}}} \sin \th_l'
-  \; \mathrm {mod}\; \RB {2\pi} 
+  \; \mathrm {mod}\; \RB {2\pi}  \\
+\V {b} \RB {\f}
+= &\M {K}^\Adj \V {a} \RB {\f}
 }
@@
 Then, for any random instance of \m {\f},
-%
 \Disp {
-\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
+\VNm {\V {b} \RB {\f} _{\SB{\mathcal {C}}}} _1
 \leq \frac {2} {\pi} \log N 
@@
 \Disp {
-\psi \SB {\f, n_H}
+\psi \RB {\f, n_H}
 :=\RB {
-   \f \; \mathrm {Mod}\; \frac {2\pi} {N}
+   \f \; \mathrm {mod}\; \frac {2\pi} {N}
    + \RB {\frac {2 n_H} {N} + 1} \pi
@@
 }
-Also define
+By using suitable remainder terms to estimate the Maclaurin series,
 \Disp {
-\Nm {D \SB {\psi'}}
-:= &\frac {\Nm {\sin \SB {N \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \\
-\leq &B \SB {\psi'}
+\frac {\Nm {\sin \RB {N \psi'/2}}} {\Nm {\sin \RB {\psi' /2}}}
+\leq &B \RB {\psi'}
 := \frac {48} {\Nm {\psi'^2 -24} \Nm {\psi'}}, \\
 }
-Then,
+Then, a simple verification shows
 \Disp {
-\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
+\VNm {\V {b} \RB {\f} _{\SB{\mathcal {C}}}} _1
 \leq \frac {1} {N}
@@
    \sum_{n_H' =0}^{N -1}
-      B \SB {\psi \SB {\f, n_H'}}
+      B \RB {\psi \RB {\f, n_H'}}
       \V {u} _{n_H'}
@@
 }
-Or, if we drop \m {s},
+Or, if we carry out the integral and drop \m {s},
 \Disp {
-\VNm {\V {b} \SB {\f} _{\SB{\mathcal {C}}}} _1
-\leq &\frac {1} {N} \D \frac {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \SB {\psi'} ^2 d \psi' \\
+\VNm {\V {b} \RB {\f} _{\SB{\mathcal {C}}}} _1
+\leq &\frac {1} {N} \D \frac {N} {2\pi} \D 2 \int_{\pi s/N}^{\pi} B \RB {\psi} ^2 d \psi \\
 = &\frac {48} {N \pi^3}
-\int _{s /N} ^1 \frac {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \\
+\int _{s /N} ^1 \frac {1} {\RB {24/\pi^2 -x^2} ^2 x^2} dx \\
 \leq &\frac {2} {\pi} \log N 
@@
 1 -p
-\leq 2 \exp \SB {- \frac {9L} {\pi}} 
+\leq 2 \exp \RB {- \frac {9L} {\pi}} 
 }
@@
 }
-Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}}.
+Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} for which the channel is sparse.
 
@@
 For simplicity, set \m {S = Ls^2}, thus \m {S =L \log N_h}.
-And, for concreteness, suppose \m {\d_S \leq \frac {1} {8}}.
+And, for concreteness, suppose \m {\d_S \leq 1/8}.
 
@@
 \VNm {\V {d}} _2
-\eqsim \mathcal {O} \SB {\R {L} \R {\log N_h}^3} 
+\eqsim \mathcal {O} \RB {\R {L} \R {\log N_h}^3} 
 }
@@
 1 -p
-\eqsim \mathcal {O} \SB {\mathsf {e} ^{-N_R \R {\d_s} /4}} 
+\eqsim \mathcal {O} \RB {\mathsf {e} ^{-N_R \R {\d_s} /4}} 
 }
@@
 \VNm {\M {P} _{\SB {\mathcal {AB}}}^\intercal \M {P} \V {d}} _2
-\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \notag \\
-\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \notag \\
+\leq &\VNm {\M {P}^\intercal \M {P} \V {d}} _2 \\
+\leq &\R {S} \VNm {\M {P}^\intercal \M {P} \V {d}} _\infty \\
 \leq &2.83 \R {L} \log N_h
@@
 \VNm {\V {d} _{\SB{\mathcal {A}}}} _1
-\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \notag \\
-\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \notag \\
+\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {A}}}} _2 \\
+\leq &\R {S} \VNm {\V {d} _{\SB{\mathcal {AB}}}} _2 \\
 \leq &3.44 L \R {\log N_h}^3
@@
 Let \m {\mathcal {R}} denote the representation of complex vectors and matrices by real vectors and matrices.
-With definitions \m {\tilde {\V {y}} = \mathcal {R} \SB {\V {y}}},
-\m {\tilde {\V {g}} = \mathcal {R} \SB {\V {g}}},
-\m {\tilde {\M {P}} = \mathcal {R} \SB {\M {P}}},
-\m {\tilde {\V {z}} = \mathcal {R} \SB {\V {z}}},
+With definitions \m {\tilde {\V {y}} = \mathcal {R} \RB {\V {y}}},
+\m {\tilde {\V {g}} = \mathcal {R} \RB {\V {g}}},
+\m {\tilde {\M {P}} = \mathcal {R} \RB {\M {P}}},
+\m {\tilde {\V {z}} = \mathcal {R} \RB {\V {z}}},
 we have by construction
-%
 \Disp {
@@
 Alternatively, in our investigation, we cast DS into a basis pursuit denoising form, for suitable \m {\l} \cite {BoV04} as below.
-
 \Disp {
@@
 }
-
 However, there is no simple way to determine the value of \m {\l} in advance.
@@
 We discuss the complexity of DS, Lasso, and OMP.
-For DS, suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \SB {N^2 M}}, assuming the Dantzig simplex method is used \cite {BoV04}.
-For our case, that would be \m {\mathcal {O} \SB {4 N_h ^2 \D 8 N_h} = \mathcal {O} \SB {N_h ^3}}.
+For DS, suppose a linear program has an \m {N} dimensional variable and \m {M} inequality constraints, then its complexity is \m {\mathcal {O} \RB {N^2 M}}, assuming the Dantzig simplex method is used \cite {BoV04}.
+For our case, that would be \m {\mathcal {O} \RB {4 N_h ^2 \D 8 N_h} = \mathcal {O} \RB {N_h ^3}}.
 
@@
 \Disp {
-C_{\mathrm {Newton}}
+N_{\mathrm {Newton}}
 \propto \RB {\VNm {\V {g}_0 -\V {g} ^{\star}}_1
@@
 C_{\mathrm {DS}}
-=\mathcal {O} \SB {N_h ^3} 
+=\mathcal {O} \RB {N_h ^3} 
 }
 
-For OMP \cite {TrG07}, \m {C_{\mathrm {OMP}} =\mathcal {O} \SB {L \RB {\log N_h} ^2}}.
+For OMP \cite {TrG07}, \m {C_{\mathrm {OMP}} =\mathcal {O} \RB {L \RB {\log N_h} ^2}}.
 
@@
 Alternatively, an argument similar to the above one for DS is valid for Lasso.
-Therefore we take \m {C_{\mathrm {Lasso}} =\mathcal {O} \SB {N_h ^3}}.
+Therefore we take \m {C_{\mathrm {Lasso}} =\mathcal {O} \RB {N_h ^3}}.
 
@@
 335–349, 2013.
-
 \bibitem{RDD18}
 M. Rani, S. B. Dhok, and R. Deshmukh, “A systematic review of compressive sensing: Concepts, implementations and applications,” \textit {IEEE Access}, vol. 6, pp. 4875–4894, 2018.
-
 \bibitem{CaT05}
 E. J. Candès and T. Tao, “Decoding by linear programming,” \textit {IEEE Transactions on Information Theory}, vol. 51, no. 12, p. 4203, 2005.
-
 \bibitem{CaT07}
 E. Candès and T. Tao, “The dantzig selector: Statistical estimation when p is much larger than n,” \textit {The annals of Statistics}, vol. 35, no. 6, pp. 2313–2351, 2007.
-
 \bibitem{BDD08}
@@
 253–263, 2008.
-
 \bibitem{BHS10}
@@
 1058–1076, 2010.
-
 \bibitem{BHR08}
 W. U. Bajwa, J. Haupt, G. Raz, and R. Nowak, “Compressed channel sensing,” 2008 \textit {42nd Annual Conference on Information Sciences and Systems}, pp. 5–10, 2008.
-
 \bibitem{AsR10}
 M. S. Asif and J. Romberg, “On the lasso and dantzig selector equivalence,” 2010 \textit {44th Annual Conference on Information Sciences and Systems} (CISS), pp. 1–6, 2010.
-
 \bibitem{LLL17}
 L. Lian, A. Liu, and V. K. Lau, “Optimal-tuned weighted lasso for massive mimo channel estimation with limited rf chains,” \textit {IEEE Global Communications Conference}, pp. 1–6, 2017.
-
 \bibitem{DJN15}
@@
 166–170, 2015.
-
 \bibitem{VAT19}
@@
 1136–1150, 2019.
-
 \bibitem{TrG07}
 J. A. Tropp and A. C. Gilbert, “Signal recovery from random measurements via orthogonal matching pursuit,” \textit {IEEE Transactions on information theory}, vol. 53, no. 12, pp. 4655–4666, 2007.
-
 \bibitem{ALH15}
@@
 2909–2913, 2015.
-
 \bibitem{HWH13}
@@
 4648–4653, 2013.
-
 \bibitem{LGL16}
@@
 2370–2386, 2016.
-
 \bibitem{GDW15}
@@
 6169–6183, 2015.
-
 \bibitem{CWX10}
 T. T. Cai, L. Wang, and G. Xu, “Stable recovery of sparse signals and an oracle inequality,” \textit {IEEE Transactions on Information Theory}, vol. 56, no. 7, pp. 3516–3522, 2010.
-
 \bibitem{CaW11}
 T. T. Cai and L. Wang, “Orthogonal matching pursuit for sparse signal recovery with noise,” \textit {IEEE Transactions on Information Theory}, 2011.
-
 \bibitem{BEE10}
@@
 5030–5043, 2010.
-
 \bibitem{ALS14}
@@
 1164–1179, 2014.
-
 \bibitem{LaM00}
 B. Laurent and P. Massart, “Adaptive estimation of a quadratic functional by model selection,” \textit {Annals of Statistics}, pp. 1302–1338, 2000.
-
 \bibitem{KlM17}
 B. Klartag and E. Milman, \textit {Geometric Aspects of Functional Analysis}. Springer, 2017.
-
 \bibitem{BoV04}
 S. Boyd and L. Vandenberghe, \textit {Convex optimization}. Cambridge U. press, 2004.
-
 \bibitem{FrS07}
